---
title: "Contract Classification: Schema 1 to Schema 2"
subtitle: "Definitive reconciliation and overview"
author: "Matthias Uckert and Ann-Kristin"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-tools: true
    df-print: kable
    embed-resources: true
    theme: cosmo
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here())
```


```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
# Keep _Classification.R in the same folder as this .qmd.
source("1_code/00-Scripts/_Classification.R")

fmt_ <- function(x) format(x, big.mark = ",")

# Paths: add your own; the first that exists is used.
.paths_parq <- c(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractData/Classification/ClassifyContracts/Classification/Classifications.parquet",
  ""   # <- Ann-Kristin: your Classifications.parquet path here
)
.paths_db <- c(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MaterialContractClassification/DocumentClassification/01-Classification/classification_data.db",
  ""   # <- Ann-Kristin: your classification_data.db path here
)
.path_parq <- cls_pick_path(.paths_parq, "Classifications.parquet")
.path_db   <- cls_pick_path(.paths_db, "classification_data.db")
```

::: {.callout-tip title="How to read this document"}
This is a **working document** that doubles as a draft for the paper. Sections 1
and 2 (the classification logic and the old-to-new reconciliation) are written
to be paper-ready. Section 3 (error diagnostics) is for our review only and
would be dropped or condensed for the manuscript. Every number recomputes on
render, so the prose stays in sync with the data on whichever machine runs it.
:::

# Classification logic

We classify each material contract into a single primary contract category,
with an optional secondary category for documents that genuinely span two
types, plus a binary amendment flag (Original / Amended). Two classification
schemes exist: the original **Schema 1** used in the first submission, and the
revised **Schema 2** introduced for this revision. The final label set
reconciles the two.

## Old scheme (Schema 1) {#sec-old}

Schema 1 was produced by manual annotation through the `rLabelDocs` interface
(stored in `Classifications.parquet`) and follows the categorisation of
Verrecchia and Weber (2006) as described in the manuscript: seven broad
categories resolving into ten specific contract types, plus the binary
amendment flag.

```{r}
#| label: tax-s1
.s1_taxonomy <- tibble::tribble(
  ~Level1,                 ~Level2,
  "Employment",            "Compensation",
  "Employment",            "Legal",
  "Financial Instruments", "Debt",
  "Financial Instruments", "Equity",
  "Purchases Or Sales",    "Inventory or Services",
  "Purchases Or Sales",    "Assets",
  "Leases",                NA_character_,
  "License",               NA_character_,
  "M&A",                   NA_character_,
  "Other",                 NA_character_
)
.s1_taxonomy
```

## New scheme (Schema 2) {#sec-new}

In response to Reviewer 2, the scheme was revised to align with more recent
literature (Boone et al. 2016; Bao et al. 2022, 2025, as cited in the project
overview). Schema 2 sharpens category boundaries, splits two ambiguous
categories, and adds previously missing types. It comprises twelve specific
categories under seven Level-1 groups:

```{r}
#| label: tax-s2
.s2_taxonomy <- tibble::tribble(
  ~Level1,                  ~Level2,                 ~DocClass,
  "Financial Instruments",  "Credit",                "Financial Instruments: Credit",
  "Financial Instruments",  "Equity",                "Financial Instruments: Equity",
  "Leases",                 NA_character_,           "Leases",
  "Employment",             "Compensation",          "Employment: Compensation",
  "Employment",             "Legal",                 "Employment: Legal",
  "Purchases and Sales",    "Assets",                "Purchases and Sales: Assets",
  "Purchases and Sales",    "R&D",                   "R&D",
  "Purchases and Sales",    "Customer / Supplier",   "Customer / Supplier",
  "Licenses",               NA_character_,           "Licenses",
  "Other",                  NA_character_,           "Other",
  "Business Structure",     "Peer Agreements",       "Business Structure: Peer Agreements",
  "Business Structure",     "Investment and Merger", "Business Structure: Investment and Merger"
)
.s2_taxonomy
```

The substantive changes from Schema 1 are: the old **Debt** category is renamed
**Credit**; the old **Inventory or Services** category is split into **R&D** and
**Customer / Supplier**; the old **M&A** category is split into **Business
Structure: Peer Agreements** and **Business Structure: Investment and Merger**;
and the remaining categories are unchanged or renamed only.

## Combination rule {#sec-rule}

The two schemes are reconciled per document as follows (from the project
overview, June 2026):

1. If a Schema-2 label exists for a document, **use it**.
2. Otherwise, if the document's Schema-1 label belongs to a *name-change* or
   *unchanged* category, **map it forward** to its Schema-2 name.
3. Otherwise the Schema-1 label belongs to a *split* category (Inventory or
   Services, or M&A). These carry **no Schema-1 fallback** ("use S2 only"): the
   document is marked `UNRESOLVED` and requires a Schema-2 label. It is never
   carried forward under an outdated label.

The amendment flag (Original / Amended) is taken from Schema 1 only.

The forward map below is the operative version of this rule. Only name-change
and unchanged rows are eligible for fallback; the split rows are listed for
completeness but deliberately excluded from the map, which is what forces
`UNRESOLVED`.

```{r}
#| label: map-overview
.s1_s2_overview <- tibble::tribble(
  ~Schema1,                                  ~Transition,  ~Schema2,                                       ~Rule,
  "Fin. Instruments: Debt",                  "name change", "Financial Instruments: Credit",                "S2 if exists, else S1",
  "Fin. Instruments: Equity",                "unchanged",   "Financial Instruments: Equity",                "S2 if exists, else S1",
  "Empoyment: Compensation",                 "unchanged",   "Employment: Compensation",                     "S2 if exists, else S1",
  "Empoyment: Legal",                        "unchanged",   "Employment: Legal",                            "S2 if exists, else S1",
  "Leases: Leases Category",                 "name change", "Leases",                                       "S2 if exists, else S1",
  "License: License Category",               "name change", "Licenses",                                     "S2 if exists, else S1",
  "Other: Other Category",                   "name change", "Other",                                        "S2 if exists, else S1",
  "Purchases/Sales: Assets",                 "name change", "Purchases and Sales: Assets",                  "S2 if exists, else S1",
  "Purchases/Sales: Inventory or Services",  "split",       "R&D / Customer / Supplier",                    "S2 only -> UNRESOLVED if missing",
  "MergerAcquisition: M&A Category",         "split",       "Business Structure: Peer / Investment",        "S2 only -> UNRESOLVED if missing"
)
.s1_s2_overview
```

Note the source typo "Empoyment" in the Schema-1 labels; it is preserved here
because the map keys on the strings as they appear in the data.

```{r}
#| label: maps-operative
# Forward map actually used by the pipeline (name-change + unchanged only).
.s1_to_s2 <- tibble::tribble(
  ~DocClassS1,                  ~DocClass,
  "Purchases/Sales: Assets",    "Purchases and Sales: Assets",
  "Other: Other Category",      "Other",
  "License: License Category",  "Licenses",
  "Leases: Leases Category",    "Leases",
  "Fin. Instruments: Debt",     "Financial Instruments: Credit",
  "Fin. Instruments: Equity",   "Financial Instruments: Equity",
  "Empoyment: Compensation",    "Employment: Compensation",
  "Empoyment: Legal",           "Employment: Legal"
)

# Raw S2 label -> canonical. Accumulator for case / spacing / redundancy drift
# in what was typed in the labeling app; the validation check feeds this table.
.s2_relabel <- tibble::tribble(
  ~DocClassRaw,                                        ~DocClass,
  "Purchases and Sales: Purchases and Sales-Assets",   "Purchases and Sales: Assets",
  "Business structure: Investment and merger",         "Business Structure: Investment and Merger",
  "Business structure: Peer Agreements",               "Business Structure: Peer Agreements"
)
.s2_relabel
```

# Reconciliation (old to new)

```{r}
#| label: pipeline
log_      <- cls_read_log(.path_db)
raw_s2_   <- cls_raw_s2_counts(log_)
s2_       <- cls_build_s2(log_, .s2_relabel)
s1_       <- cls_build_s1(.path_parq, .s1_to_s2)
final_    <- cls_combine(s2_, s1_, .s2_taxonomy)
checks_   <- cls_validate(final_, .s2_taxonomy, .s2_relabel, raw_s2_)
recon_    <- cls_reconcile_s1(log_, s1_)
selfdual_ <- cls_self_duals(log_)
coverage_ <- cls_coverage(s2_, s1_, final_)

kpi_ <- list(
  n_final    = nrow(final_),
  n_s2       = sum(final_$Provenance == "S2"),
  n_fb       = sum(final_$Provenance == "S1_fallback"),
  n_unres    = sum(final_$Provenance == "UNRESOLVED"),
  n_dual     = sum(final_$DualClass == 1L),
  n_orphan   = sum(is.na(final_$AmendType)),
  n_selfdual = nrow(selfdual_),
  n_disagree = sum(!recon_$Agree, na.rm = TRUE)
)
kpi_$pct_s2 <- round(100 * kpi_$n_s2 / kpi_$n_final, 1)
kpi_$pct_fb <- round(100 * kpi_$n_fb / kpi_$n_final, 1)
all_pass_   <- all(checks_$Status == "PASS")
```

```{r}
#| label: banner
#| output: asis
#| code-fold: false
if (all_pass_) {
  cat("::: {.callout-note title='Validation: PASS'}\nAll structural checks passed (canonical label set, one row per document, no unmapped labels).\n:::\n")
} else {
  cat("::: {.callout-important title='Validation: FAIL'}\nA structural check failed -- see Section 3. A failure on the label-mapping check means a new raw label needs a row in `.s2_relabel`.\n:::\n")
}
```

Of **`r fmt_(kpi_$n_final)`** documents, **`r fmt_(kpi_$n_s2)`** (`r kpi_$pct_s2`%)
carry a new Schema-2 label and **`r fmt_(kpi_$n_fb)`** (`r kpi_$pct_fb`%) retain a
Schema-1 label mapped forward; **`r kpi_$n_unres`** remain unresolved. The
Schema-2 re-labeling was therefore *targeted* at the split and changed
categories rather than applied wall-to-wall, which is exactly what the "retain
S1 where only S1 exists" rule prescribes (see @fig-provenance).

## Source coverage

How the old (parquet) and new (log) document sets overlap. `n_s1_only` are
documents that retain a mapped Schema-1 label; `n_s2_only` are documents present
only in the new log (these have no amendment flag, see @sec-orphans).

```{r}
#| label: ovw-coverage
#| code-fold: false
coverage_
```

## Provenance

Where each final label came from.

```{r}
#| label: ovw-prov
#| code-fold: false
final_ |> dplyr::count(Provenance)
```

## Forward map in action

Which Schema-1 labels actually fell back (no Schema-2 label existed), and the
canonical category each was mapped to. This is the operative reconciliation.

```{r}
#| label: ovw-fallback
#| code-fold: false
final_ |>
  dplyr::filter(Provenance == "S1_fallback") |>
  dplyr::count(DocClassS1, DocClassFinal1)
```

## S1 source reconciliation {#sec-recon}

The pipeline takes Schema-1 from the parquet. This check confirms that choice is
safe by comparing it against the log's own Schema-1 entries: `TRUE` where they
agree, `FALSE` where they differ, `NA` where only one source has the document.

```{r}
#| label: ovw-recon
#| code-fold: false
recon_ |> dplyr::count(Agree)
```

Agreement is near-total; the `r kpi_$n_disagree` disagreements are detailed in
@sec-disagree.

# Potential errors and mismatches

::: {.callout-warning title="Working-document section"}
Each subsection below explains what the mismatch is, why it arises, whether it
affects the final classification, and what (if anything) to do about it. These
are diagnostics for our review and would not appear in the paper.
:::

## Unresolved documents {#sec-unresolved}

These are documents whose only label is an old Schema-1 **split** category --
`Inventory or Services` or `M&A` -- with no Schema-2 label
(**`r kpi_$n_unres`** documents). They arise because the combination rule gives
split categories no Schema-1 fallback: the old category maps to two or more new
ones, so the correct destination cannot be inferred mechanically and has to be
set by hand. Until that happens, each has no final label (`DocClassFinal1` is
`NA`) and is excluded from every category count below -- so this is the one
mismatch that genuinely blocks a complete dataset. Action: assign each a
Schema-2 label. All `r kpi_$n_unres` here are old `Inventory or Services`
contracts, so each belongs in R&D, Customer / Supplier, or Purchases and Sales:
Assets depending on its content.

```{r}
#| label: err-unresolved
#| code-fold: false
final_ |>
  dplyr::filter(Provenance == "UNRESOLVED") |>
  dplyr::select(DocID, DocClassS1, AmendType)
```

## Documents missing from the old parquet {#sec-orphans}

**`r kpi_$n_orphan`** documents carry a Schema-2 label but have no row in the
old parquet, so they have no amendment flag (`AmendType` is `NA`, since the flag
comes only from Schema 1). **Confirmed: these are documents we deliberately
added during the revision**, not a join failure. Two things support that: they
concentrate in the new and expanded categories (54 are Customer / Supplier, the
rest sit in Business Structure, R&D, and Licenses), and 983 of the 1,058
Schema-2 documents do match the parquet, so the DocID key itself is sound -- a
format mismatch would have stranded far more than `r kpi_$n_orphan`. The only
consequence is that the classification sample grows from 4,327 to
**`r fmt_(kpi_$n_final)`**, and these documents have a full Schema-2
classification but no Original/Amended flag. Action: either accept the `NA`, or
backfill the flag by running the amendment classifier over these IDs.

```{r}
#| label: err-orphans
#| code-fold: false
final_ |>
  dplyr::filter(is.na(AmendType)) |>
  dplyr::count(DocClassFinal1)
```

## S1 source disagreements {#sec-disagree}

These are documents where the old parquet and the new log hold **different**
Schema-1 labels for the same document (`Agree == FALSE`), plus the one document
that exists in only one source (`Agree == NA`). They occur because the parquet
and the log were two separate labeling passes, and a few contracts -- usually
genuinely ambiguous ones, such as a document the parquet calls M&A and the log
calls Equity -- were labeled inconsistently between them. **None of them affect
the final result.** Every one either carries a Schema-2 label (which overrides
both old labels) or sits in a name-change category that resolves identically
whichever source is used, and the pipeline takes Schema 1 from the parquet
throughout. They are shown only as a transparency check on that source choice,
and because they point to contracts whose type is genuinely contestable. Action:
none required; optionally eyeball them to sanity-check the ambiguous cases.

```{r}
#| label: err-disagree
#| code-fold: false
recon_ |> dplyr::filter(!Agree | is.na(Agree))
```

## Dual-label hygiene {#sec-selfdual}

These are documents that were dual-classified with the **same** category in
both slots, i.e. primary equals secondary (**`r kpi_$n_selfdual`** document) --
almost certainly a slip in the labeling interface where the category was picked
twice. The pipeline collapses them back to a single label (it sets the secondary
to `NA` in `cls_build_s2`), so they do **not** inflate the dual-classification
counts or the multi-label population in Section 4. They are listed here only so
they can be fixed at source if desired; no downstream action is required.

```{r}
#| label: err-selfdual
#| code-fold: false
selfdual_
```

## Label drift handled

This lists every distinct raw Schema-2 label as it was typed in the labeling
app, with how the pipeline handled it: `canonical` (already matches the
taxonomy), `relabeled` (a case, spacing, or redundancy variant fixed via
`.s2_relabel` -- for example the lowercase `Business structure: ...` or the
redundant `Purchases and Sales: Purchases and Sales-Assets`), or `UNKNOWN` (an
unrecognised label). Drift happens because the app accepts the label more or
less as free text, so the same category can be entered in slightly different
forms. Relabeled variants are folded into their canonical name before any
counting, and an `UNKNOWN` would fail the structural check in Section 2,
flagging a new variant to add to `.s2_relabel`. One thing to note when reading
the table: the counts include secondary (dual) labels and come from the
Schema-2 log only, so they deliberately do **not** match the final category
totals, which also include Schema-1 fallback. Action: if any row reads
`UNKNOWN`, add it to `.s2_relabel` and re-render.

```{r}
#| label: err-drift
#| code-fold: false
raw_s2_ |>
  dplyr::mutate(
    Disposition = dplyr::case_when(
      Value %in% .s2_taxonomy$DocClass   ~ "canonical",
      Value %in% .s2_relabel$DocClassRaw ~ "relabeled",
      TRUE                               ~ "UNKNOWN"
    )
  ) |>
  dplyr::arrange(Disposition, dplyr::desc(n_raw))
```

# Overviews

## Distribution by hierarchy {#sec-dist}

The headline distribution, ready for a Table-1 view. The `NA` row (if any) is
the unresolved documents.

```{r}
#| label: ovw-dist
#| code-fold: false
final_ |> dplyr::count(Level1, Level2, DocClassFinal1)
```

```{r}
#| label: fig-distribution
#| fig-cap: "Distribution of contracts across the twelve Schema-2 categories, coloured by Level-1 group."
#| fig-width: 8
#| fig-height: 5
cls_plot_distribution(final_)
```

## Amendment flag

```{r}
#| label: ovw-amend
#| code-fold: false
final_ |> dplyr::count(AmendType)
```

```{r}
#| label: fig-amend
#| fig-cap: "Share of amendments within each category, ordered from least to most amended."
#| fig-width: 8
#| fig-height: 5
cls_plot_amend(final_)
```

## Dual classifications {#sec-dual}

The **`r fmt_(kpi_$n_dual)`** documents with a genuine secondary category, and
the primary / secondary pairs. This is the multi-label population relevant to
Reviewer 2's multi-label point.

```{r}
#| label: ovw-dual
#| code-fold: false
final_ |>
  dplyr::filter(DualClass == 1L) |>
  dplyr::count(DocClassFinal1, DocClassFinal2)
```

```{r}
#| label: fig-dual
#| fig-cap: "Co-occurrence of primary (rows) and secondary (columns) categories among dual-classified contracts."
#| fig-width: 8
#| fig-height: 7
cls_plot_dual(final_)
```

## Category by provenance

A cross-tab of how much of each final category comes from new Schema-2 work
versus mapped Schema-1 labels.

```{r}
#| label: ovw-prov-class
#| code-fold: false
final_ |>
  dplyr::count(Level1, Provenance) |>
  tidyr::pivot_wider(names_from = Provenance, values_from = n, values_fill = 0L)
```

```{r}
#| label: fig-provenance
#| fig-cap: "Provenance composition by category: new Schema-2 labels versus Schema-1 labels mapped forward. The Schema-2 re-labeling was targeted at the split and changed categories."
#| fig-width: 8
#| fig-height: 5
cls_plot_provenance(final_)
```

## Validation detail

```{r}
#| label: ovw-checks
#| code-fold: false
checks_
```

# Open decisions and next steps

1. **Schema-2 coverage is intentional.** Three-quarters of final labels are
   mapped Schema-1, by design of the "retain S1" rule. Confirm the paper text
   describes the sample's provenance accordingly.
2. **Unresolved documents** (@sec-unresolved) need a per-document call.
3. **Documents added during the revision** (@sec-orphans) -- confirmed as
   deliberate additions, so the sample is now `r fmt_(kpi_$n_final)`. The only
   open point is whether to backfill the amendment flag for these
   `r kpi_$n_orphan` documents or accept `NA`.
4. **Dual classifications** (@sec-dual) -- decide how `DocClassFinal2` enters the
   analysis (multi-label, drop, or primary-only).
5. **S1 source** is settled in favour of the parquet (@sec-recon); the
   reconciliation section can be retired once we are both satisfied.
6. **Schema 3.** The log contains a third `DocClass` schema that is unused here.
   Confirm it is scratch.

# Export

Disabled by default. Enable once the open decisions are settled.

```{r}
#| label: export
#| eval: false
.path_out <- "0_data/Classification.parquet"
arrow::write_parquet(final_, .path_out)
```

# Appendix: session info

```{r}
#| label: sessioninfo
#| code-fold: true
sessionInfo()
```
