---
title: "EDGAR Acquisition -- Index and Landing Pages (01A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01A-EdgarIndex.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

EDGAR publishes a quarterly master index listing every filing since 1993, and for each filing a landing page listing the
documents attached to it. This document mirrors both locally and parses the landing HTML into a single table,
`LandingPageAll.parquet`, holding twenty-one metadata fields per filing.

No document is downloaded here. The landing pages say *what* each filing contains; fetching the contents is 01B, which
reads the link tables mirrored below. The two are separate scripts because they fail differently and at different
scales. The index is a few thousand files and completes in an afternoon. The documents are 1.8 million and took days,
during which any interruption has to be recoverable without repeating what already succeeded.

## Which filings are in scope

Only a minority of EDGAR form types can carry a material contract. Mirroring the landing page of every filing would
multiply the acquisition cost by roughly a factor of ten for filings that cannot contain the object of study, so the
frame is restricted to seventeen types: the periodic reports, the current report that must disclose a material
definitive agreement, the registration statements that attach material agreements as exhibits, each with its amendment
variant, and the confidential-treatment order itself.

Amendment variants are enumerated rather than matched by prefix. A pattern such as `^8-K` would also capture 8-K12B and
8-K15D5, which are not current reports.

The frame closes at 2024. This is a closure rule, not a data limit: EDGAR keeps publishing, so an open-ended frame would
grow between renders and no two runs of the pipeline would describe the same corpus.

## How the acquisition switch works

Two steps here reach the SEC over the network, and both sit behind `.lP$Param$Acquire`, which defaults to `FALSE`. The
*checks* never sit behind it. On every render this document computes how much of the selected frame has been mirrored
and reports the shortfall, whether or not it fetched anything.

The distinction matters. An earlier version of this pipeline gated the work and the diagnostic together behind a single
flag, which meant a document with a badly incomplete mirror rendered exactly like a complete one: no error, no warning,
and a coverage figure that was never computed. Gating only the network call costs one parquet scan per render and makes
the state of the mirror a reported result rather than an assumption.

## Where the mirror lives

The mirror is `0_edgar/`, not `2_output/`. It is a local copy of somebody else's data rather than something this script
derived, and it is shared: 01B writes its third subtree. Keeping it outside the per-script output directories means
neither script writes into the other's, and the single-writer rule holds at the level it should -- 01A owns
`MasterIndex/` and `DocumentLinks/`, 01B owns `DocumentData/`.

# Configuration

```{r}
#| label: config
.lP <- list(
  Input = list(
    Edgar = here::here("0_edgar")                                        # the local EDGAR mirror
  ),
  Cache = list(
    RawExtract = utils_file_path(.dir_main, "Cache", "RawExtract")       # one parsed table per year-quarter
  ),
  Output = list(
    LandingPageAll = utils_file_path(.dir_main, "LandingPageAll.parquet"),   # the one downstream artifact
    Figures        = utils_file_path(.dir_main, "Figures")                   # figure files for the manuscript
  ),
  Param = list(
    User    = "Matthias.Uckert@Outlook.com",   # SEC requires a contact address on every request
    Forms   = edg_sec_forms(),                 # the seventeen types in scope
    MaxYear = 2024L,                           # frame closure; fixed so renders are comparable
    Workers = 10L,                             # parallel workers for landing-page parsing
    Acquire = FALSE                            # TRUE permits the two network steps to run
  )
)

# rGetEDGAR derives its whole directory tree from one root, and creates what is missing. Calling it
# here rather than typing the subpaths means the layout cannot drift from what the package expects.
.lP$Edgar <- rGetEDGAR::get_directories(fs::dir_create(.lP$Input$Edgar))

fs::dir_exists(.lP$Input$Edgar)
```

`rGetEDGAR` is installed from `0_data/Binaries/` and is not on CRAN. If the call above fails, the package is missing from
the project library rather than the path being wrong.

# Index

The master index is the population. The frame is the subset of it that needs a landing page: the seventeen form types,
up to the closing year, deduplicated on `HashIndex`.

```{r}
#| label: index-select
vec_hash_index <- edg_select_index(
  .dir_master = .lP$Edgar$MasterIndex$DirParquet,   # mirrored master index
  .forms      = .lP$Param$Forms,                    # the seventeen types in scope
  .max_year   = .lP$Param$MaxYear                   # frame closure year
)

length(vec_hash_index)
```

# Acquisition

Both chunks below are gated. Each reports what it did or did not do, so the render is a record either way.

The master index comes first because everything else is selected from it.

```{r}
#| label: acquire-master-index
if (isTRUE(.lP$Param$Acquire)) {
  rGetEDGAR::edgar_get_master_index(
    .dir     = .lP$Input$Edgar,      # mirror root; the package derives MasterIndex/ from it
    .user    = .lP$Param$User,       # contact address sent with every request
    .from    = NULL,                 # NULL starts at the earliest quarter EDGAR publishes
    .to      = NULL,                 # NULL runs to the latest available
    .verbose = TRUE                  # stream progress
  )
} else {
  cli::cli_alert_info("Acquisition is OFF: the master index was not refreshed.")
}
```

Landing pages and document links arrive from the same request. Ten requests per second is the SEC's published fair-access
ceiling and the package enforces it, so this step is bounded by the SEC rather than by local hardware.

```{r}
#| label: acquire-document-links
if (isTRUE(.lP$Param$Acquire)) {
  rGetEDGAR::edgar_get_document_links(
    .dir      = .lP$Input$Edgar,     # mirror root; the package derives DocumentLinks/ from it
    .user     = .lP$Param$User,      # contact address sent with every request
    .hash_idx = vec_hash_index,      # the frame selected above
    .verbose  = TRUE                 # stream progress
  )
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: no landing pages were fetched.")
}
```

Coverage of the frame, computed on every render regardless of the switch.

```{r}
#| label: report-mirror-coverage
edg_report_links(
  .dir_master = .lP$Edgar$MasterIndex$DirParquet,      # the population
  .forms      = .lP$Param$Forms,                       # the seventeen types in scope
  .max_year   = .lP$Param$MaxYear,                     # frame closure year
  .path_htmls = .lP$Edgar$DocLinks$DirMain$HTMLs,      # mirrored landing pages
  .path_links = .lP$Edgar$DocLinks$DirMain$Links,      # mirrored link tables
  .acquire    = .lP$Param$Acquire                      # reported, so a gap and a switch are distinguishable
)
```

A small residue of missing index files is expected and tolerated. These are filings whose landing page EDGAR no longer
serves, and they are lost to any method, not to this one.

# Landing pages

Parsing is local work on already-mirrored bytes, so it is not gated. It runs on every render and does nothing when
there is nothing new, because it inspects its own output first: each year-quarter has one file, the function reads the
`HashIndex` values already in it, and parses only the rest.

That idempotence is what buys the ungated call. A step that is cheap when complete does not need a switch, and a step
without a switch cannot be left switched off.

```{r}
#| label: parse-landing-pages
tab_parse_log <- edg_parse_landing(
  .path_htmls = .lP$Edgar$DocLinks$DirMain$HTMLs,   # mirrored landing pages, one dataset per quarter
  .dir_raw    = .lP$Cache$RawExtract,               # destination for the per-quarter parsed tables
  .workers    = .lP$Param$Workers,                  # parallel workers; also the chunk count per quarter
  .quiet      = FALSE                               # FALSE reports each quarter as it is processed
)

sum(tab_parse_log$nParsed)
```

Everything arrives from the HTML as character, because that is what the page contains. Cleaning converts types once,
centrally, so no downstream script has to decide whether `FilingDate` is a date or a string, and turns the empty strings
that unpopulated cells produce into genuine missing values. Left alone, an empty string counts as a present observation
in every summary and joins as a real key.

Rows whose parse failed are dropped here but retained in the per-quarter cache, so the failure rate stays computable
from the two together.

```{r}
#| label: clean-landing-pages
tab_landing <- edg_clean_landing(
  .dir_raw  = .lP$Cache$RawExtract,        # per-quarter parsed tables
  .path_out = .lP$Output$LandingPageAll    # the cleaned table downstream reads
)

nrow(tab_landing)
```

# Results

```{r}
#| label: report-landing
edg_report_landing(.tab = tab_landing)
```

Report date is absent on a large share of filings by design: 8-K is a current report and covers no period. Filing date
is different -- it should never be missing, and a nonzero share in that column is a parse failure rather than a
property of the form.

# Validation

Two consistency checks between what was parsed and what survived cleaning. The prediction in each case is zero, and a
nonzero result names a specific fault rather than a general concern.

```{r}
#| label: validate-landing
# Every quarter that has mirrored HTML should have a parsed table, and the parsed rows should
# account for every HashIndex the cleaning step kept. A shortfall in the first is an interrupted
# parse; in the second, a duplicate HashIndex across quarters.
tibble::tibble(
  QuartersWithHtml   = nrow(tab_parse_log),
  QuartersParsed     = sum(tab_parse_log$nTotal > 0L),
  RowsParsed         = sum(tab_parse_log$nTotal),
  RowsKept           = nrow(tab_landing),
  DuplicateHashIndex = sum(duplicated(tab_landing$HashIndex))
) |>
  tbl_out(.title = "Parse against clean")
```

`RowsKept` is below `RowsParsed` by exactly the number of parse failures, which are excluded by the `Error == 0` filter.
`DuplicateHashIndex` should be zero: the hash identifies a filing, and a repeat means one filing was mirrored under two
quarters.

# Deployment

`LandingPageAll.parquet` is written by the cleaning step above and is the only artifact of this script that anything
downstream reads. 01B selects documents from it; 01C filters it to the filings whose documents were actually retrieved
and publishes that as `LandingPage.parquet`.

The two are deliberately separate files rather than one file filtered in place. The unfiltered version is the
denominator for every coverage statement made later, and a pipeline that overwrites its own denominator cannot report
how much it lost.

```{r}
#| label: deploy-report
fs::file_info(.lP$Output$LandingPageAll) |>
  dplyr::select("path", "size") |>
  tbl_out(.title = "Written")
```

# Overview

```{r}
#| label: fig-coverage-by-year
#| fig-height: 3.4
#| fig-cap: "Filings mirrored per calendar year. The frame closes in 2024, so the final year is
#|   partial by construction rather than by attrition."
gg_coverage <- edg_plot_coverage(.tab = edg_landing_coverage(.tab = tab_landing))

plot_save(
  .plot    = gg_coverage,               # the figure
  .name    = "coverage-by-year",        # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_coverage
```

```{r}
#| label: overview-all
edg_report_all(
  .lp  = .lP,            # configuration, so the reporters resolve their own paths
  .tab = tab_landing     # the cleaned landing table
)
```

# Next

**01B-EdgarDocuments** reads the link tables mirrored here together with `LandingPageAll.parquet`, selects the Exhibit-10
exhibits, CT orders and Item 1.01 8-Ks, downloads and parses them into `0_edgar/DocumentData/Parsed/`, and writes the
`DocID` to `Path` index every later script uses to locate a document's text.
