---
title: "EDGAR Acquisition -- Index and Landing Pages (01A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01A-EdgarIndex.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This is the first step of the pipeline. Everything downstream is derived from what it acquires.

EDGAR publishes a quarterly master index listing every filing since 1993, and for each filing a landing page listing the
documents attached to it. This document mirrors both locally and parses the landing HTML into a single table,
`Output/LandingPageAll.parquet`, holding twenty-one metadata fields per filing.

No attachment is downloaded here. The landing pages say *what* each filing contains; fetching the contents is 01B, which
reads the link tables mirrored below. The two are separate scripts because they fail differently and at different
scales. The index is a few thousand files and completes in an afternoon. The attachments number in the millions and take
days, during which any interruption has to be recoverable without repeating what already succeeded.

## Which filings are in scope

Only a minority of EDGAR form types can carry a material contract. Mirroring the landing page of every filing would
multiply the acquisition cost by roughly a factor of ten for filings that cannot contain the object of study, so the
frame is restricted to seventeen types: the periodic reports, the current report that must disclose a material
definitive agreement, the registration statements that attach material agreements as exhibits, each with its amendment
variant, and the confidential-treatment order itself.

Amendment variants are enumerated rather than matched by prefix. A pattern such as `^8-K` would also capture 8-K12B and
8-K15D5, which are not current reports.

The frame closes at 2024. This is a closure rule, not a data limit: EDGAR keeps publishing, so an open-ended frame would
grow between renders and no two runs of the pipeline would describe the same corpus.

## How the acquisition switch works

Two steps here reach the SEC over the network, and both sit behind `.lP$Param$Acquire`, which defaults to `FALSE`. The
*checks* never sit behind it. On every render this document computes how much of the selected frame has been mirrored
and reports the shortfall, whether or not it fetched anything.

The distinction is the whole design. A flag that suppressed the work and the diagnostic together would let a document
with a badly incomplete mirror render exactly like a complete one: no error, no warning, and a coverage figure that was
never computed. Gating only the network call turns the state of the mirror into a reported result.

## What is recomputed, and what is not

Four steps here are expensive: selecting the frame, measuring coverage, parsing the landing HTML, and cleaning the
parsed tables into one file. Each is a deterministic function of what the mirror currently holds, and none of them can
produce a different answer while the mirror stands still. Recomputing all four on a render that changes nothing is most
of the cost of this document.

Each therefore takes a `.rerun` argument, defaulting to `FALSE`, and each caches its result under `Cache/`. **The cache
is keyed on the input, not on the file name.** `utils_dir_stamp()` fingerprints the directories the step read -- file
count, total size, latest modification time -- and stores that stamp beside the result. Three outcomes, and the console
says which one happened every time:

| Situation | What happens |
|:--|:--|
| Stamp matches | The cached result is read. No work is done. |
| Stamp differs | The input moved. The step recomputes and restamps. |
| `.rerun = TRUE` | The step recomputes regardless. |

This is not a suppressed chunk. Every chunk below executes, reports and validates on every render, and every number on
this page is computed from the artifact that exists right now. What the stamp removes is recomputation of something
provably unchanged, and that is precisely what makes it affordable to leave every check switched on.

The fingerprint is metadata rather than content, because the directories it guards hold hundreds of gigabytes and
reading them would cost more than the computation being cached. The trade is explicit: an edit that preserved file
count, total size and modification time would go undetected. Nothing in this pipeline rewrites a mirrored file in
place, so the case does not arise -- but a step where it could must pass `.rerun = TRUE` rather than trust the stamp.

**To force a full rebuild**, set the relevant `.rerun` to `TRUE` rather than deleting anything. Deleting a cache file
works too and costs the same recomputation; the argument is preferred because it leaves a record on the page of what
was rebuilt and why.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are
deliberate and both are the same decision. A runbook is read while it runs and pasted into
discussion, where a monospaced block survives being quoted into a mail or a chat window and a styled
table does not.

The publication versions are produced once, at the end of the pipeline, by the consolidated release
script: styled tables from the same `tbl_out()` specifications, figure files from the same plotting
functions. Producing them here instead would mean twenty scripts each writing part of the
manuscript's exhibits, rewritten on every render of a document that changed none of them, and a
manuscript drawing on files produced at twenty different moments.

The choice is set in this document's setup chunk rather than left to a default, because a default is
a decision nobody reviewed and two documents in this repository already disagree about it without
saying so.

## Where things are written

Anything a later script reads goes in `Output/`. Anything that exists only to make this document cheap to re-render
goes in `Cache/`. The mirror is the one exception and keeps its own root: `GetEDGAR/` holds millions of files that no
other script opens by path, and moving it under `Output/` would say it is an artifact to be published rather than a
local copy of a public archive.

`rGetEDGAR` derives its entire directory tree from a single root, and this script's root is `GetEDGAR/` inside its own
output directory. 01B writes the `DocumentData/` branch of that same tree: the package resolves link tables and
downloaded documents from one root, so separating them would mean duplicating three hundred megabytes of link tables to
no purpose. Ownership stays unambiguous where it matters -- 01A writes `MasterIndex/` and `DocLinks/`, 01B writes
`DocumentData/`, and no artifact has two writers.

# Configuration

This document has no `Input` section. Its input is EDGAR.

```{r}
#| label: config
.lP <- list(
  Cache = list(
    RawExtract   = utils_file_path(.dir_main, "Cache", "RawExtract"),            # one parsed table per year-quarter
    FrameIndex   = utils_file_path(.dir_main, "Cache", "FrameIndex.parquet"),    # the selected frame, plus its stamp
    LinkCoverage = utils_file_path(.dir_main, "Cache", "LinkCoverage.parquet"),  # mirror coverage, plus its stamp
    ParseLog     = utils_file_path(.dir_main, "Cache", "ParseLog.parquet"),      # per-quarter parse counts, plus stamp
    # Guards the published landing table, which carries no stamp column of its own.
    CleanStamp   = utils_file_path(.dir_main, "Cache", "CleanStamp.parquet")
  ),
  Output = list(
    LandingPageAll = utils_file_path(.dir_main, "Output", "LandingPageAll.parquet")   # the one downstream artifact
  ),
  Param = list(
    User    = "Matthias.Uckert@Outlook.com",   # SEC requires a contact address on every request
    Forms   = edg_sec_forms(),                 # the seventeen types in scope
    MaxYear = 2024L,                           # frame closure; fixed so renders are comparable
    Workers = 24L,                             # parallel workers for landing-page parsing
    Batch   = 100000L,                         # landing pages held in memory at once; bounds peak use
    Acquire = FALSE                            # TRUE permits the two network steps to run
  )
)

# The mirror root. Calling get_directories() rather than typing the subpaths means the layout cannot
# drift from what rGetEDGAR expects, and it creates whatever is missing.
.lP$Edgar <- rGetEDGAR::get_directories(fs::dir_create(.dir_main, "GetEDGAR"))

.lP$Edgar$MasterIndex$DirParquet
```

`rGetEDGAR` is installed from `0_data/Binaries/` and is not on CRAN. If the call above fails, the package is missing
from the project library rather than the path being wrong.

# Index

The master index is the population. The frame is the subset of it that needs a landing page: the seventeen form types,
up to the closing year, deduplicated on `HashIndex`.

```{r}
#| label: index-acquire
if (isTRUE(.lP$Param$Acquire)) {
  rGetEDGAR::edgar_get_master_index(
    .dir     = fs::path(.dir_main, "GetEDGAR"),   # the mirror root
    .user    = .lP$Param$User,                    # contact address sent with every request
    .from    = NULL,                              # NULL starts at the earliest quarter EDGAR publishes
    .to      = NULL,                              # NULL runs to the latest available
    .verbose = TRUE                               # stream progress
  )
} else {
  cli::cli_alert_info("Acquisition is OFF: the master index was not refreshed.")
}
```

Selecting the frame scans every quarterly index file, so it is cached against the index directory together with the two
parameters that define the selection. Editing `edg_sec_forms()` or `MaxYear` therefore invalidates the cache on its own,
which is the case a name-keyed cache would have got wrong.

The result is returned sorted, and that is not tidiness. A multi-file Arrow scan makes no promise about the order in
which record batches come back, and the coverage step below takes this vector into its own fingerprint; an unsorted
frame would hash differently on every render and defeat that cache for no reason.

```{r}
#| label: index-select
vec_hash_index <- edg_select_index(
  .dir_master = .lP$Edgar$MasterIndex$DirParquet,   # the mirrored master index
  .forms      = .lP$Param$Forms,                    # the seventeen types in scope
  .max_year   = .lP$Param$MaxYear,                  # frame closure year
  .path_cache = .lP$Cache$FrameIndex,               # frame and stamp
  .rerun      = FALSE                               # TRUE rebuilds regardless of the stamp
)

length(vec_hash_index)
```

# Landing pages

Landing pages and document links arrive from the same request. Ten requests per second is the SEC's published
fair-access ceiling and the package enforces it, so this step is bounded by the SEC rather than by local hardware.

```{r}
#| label: landing-acquire
if (isTRUE(.lP$Param$Acquire)) {
  rGetEDGAR::edgar_get_document_links(
    .dir      = fs::path(.dir_main, "GetEDGAR"),   # the mirror root
    .user     = .lP$Param$User,                    # contact address sent with every request
    .hash_idx = vec_hash_index,                    # the frame selected above
    .verbose  = TRUE                               # stream progress
  )
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: no landing pages were fetched.")
}
```

Coverage is reported on every render regardless of the switch, and is measured once and reported twice: here, and again
in the overview.

The measurement itself scans every mirrored quarter, so it is cached against both mirror directories and the frame. It
composes correctly with acquisition: a render that fetches pages moves the directories underneath, the stamp taken
afterwards differs from the stored one, and coverage re-measures without being asked.

```{r}
#| label: landing-coverage
tab_coverage <- edg_link_coverage(
  .frame      = vec_hash_index,                    # the filings the form-type restriction selects
  .path_htmls = .lP$Edgar$DocLinks$DirMain$HTMLs,  # mirrored landing pages
  .path_links = .lP$Edgar$DocLinks$DirMain$Links,  # mirrored link tables
  .path_cache = .lP$Cache$LinkCoverage,            # coverage row and stamp
  .rerun      = FALSE                              # TRUE re-measures regardless of the stamp
)

edg_report_links(
  .cov     = tab_coverage,       # measured above
  .acquire = .lP$Param$Acquire   # reported, so a gap and a switch stay distinguishable
)
```

A small residue of missing index files is expected and tolerated. These are filings whose landing page EDGAR no longer
serves, and they are lost to any method rather than to this one.

# Parsing

Parsing works on already-mirrored bytes, so it is not gated by the acquisition switch. It is idempotent twice over.
Each year-quarter has one output file, the function reads the `HashIndex` values already in it, and parses only the
rest; and the whole scan sits behind a stamp covering both the mirrored HTML and the parsed tables, so a render with
nothing to do reads one small log and stops.

The inner comparison is deliberately narrow. Both sides contribute their `HashIndex` column and nothing else, so a
completed quarter costs two column reads. Reading the parsed table whole, or letting Arrow filter the source dataset,
would make every completed quarter pull its landing-page HTML through a filter in order to produce no rows.

Parallel workers are raised on first need rather than up front. Twenty-four fresh R sessions take seconds to start and
are pure waste on a render that parses nothing, which after the first complete run is every render.

```{r}
#| label: parse-landing
tab_parse_log <- edg_parse_landing(
  .path_htmls = .lP$Edgar$DocLinks$DirMain$HTMLs,   # mirrored landing pages, one dataset per quarter
  .dir_raw    = .lP$Cache$RawExtract,               # destination for the per-quarter parsed tables
  .path_cache = .lP$Cache$ParseLog,                 # per-quarter log and stamp
  .workers    = .lP$Param$Workers,                  # parallel workers; also the chunk count per batch
  .batch      = .lP$Param$Batch,                    # landing pages held in memory at once
  .rerun      = FALSE,                              # TRUE rescans every quarter regardless of the stamp
  .quiet      = FALSE                               # FALSE reports each quarter as it is processed
)

sum(tab_parse_log$nParsed)
```

Everything arrives from the HTML as character, because that is what the page contains. Cleaning converts types once,
centrally, so no downstream script has to decide whether `FilingDate` is a date or a string, and turns the empty strings
that unpopulated cells produce into genuine missing values. Left alone, an empty string counts as a present observation
in every summary and joins as a real key.

Rows whose parse failed are dropped here but retained in the per-quarter cache, so the failure rate stays computable
from the two together.

## One row per filing-filer pair

The cleaned table is not one row per filing. A landing page lists every registrant on the filing, and the parse emits a
row for each: all the filing-level fields repeat, and the filer block -- `CIK`, `CompanyName`, `SIC`, `StateCode`,
`IrsNo`, `FileNo`, `FilmNo`, and the two addresses -- varies.

The effect is large and concentrated. A registration statement for a merger routinely names every guarantor subsidiary
as a co-registrant, so a single S-4 can contribute hundreds of rows, and the S-4 family dominates the row count without
being anywhere near the largest form type by filing count. Ranking form types by rows therefore measures corporate
structure rather than filing volume, which is why the composition table below reports both.

Anything joining to this table on `HashIndex` must expect a many-to-one match. 01C joins on `DocID` instead, which is
unique, and the multi-filer case is carried there as an explicit flag rather than as unexplained repetition.

Binding every quarter, casting every column to character and sorting several million rows is the most expensive single
step in this document, and its only input is the parse cache. Its stamp is the one that does not live with its result:
`LandingPageAll.parquet` is published and read by three downstream scripts, so it carries nothing but its own columns
and the stamp sits in `Cache/CleanStamp.parquet` instead.

```{r}
#| label: clean-landing
tab_landing <- edg_clean_landing(
  .dir_raw    = .lP$Cache$RawExtract,        # per-quarter parsed tables
  .path_out   = .lP$Output$LandingPageAll,   # the cleaned table downstream reads
  .path_stamp = .lP$Cache$CleanStamp,        # stamp for the published file
  .rerun      = FALSE                        # TRUE rebuilds regardless of the stamp
)

nrow(tab_landing)
```

# Results

Both summaries are group-bys over the full landing table, and the document needs each of them more than once -- in this
section, in the overview, and for the figure. They are computed here and passed everywhere else, so several million
rows are traversed once rather than three times.

```{r}
#| label: summarise-landing
tab_year  <- edg_landing_coverage(.tab = tab_landing)   # one row per calendar year
tab_forms <- edg_landing_forms(.tab = tab_landing)      # one row per form type
```

```{r}
#| label: report-landing
edg_report_landing(
  .tab_year  = tab_year,    # summarised above, not recomputed
  .tab_forms = tab_forms    # likewise
)
```

Report date is absent on a large share of filings by design: 8-K is a current report and covers no period. Filing date
is different -- it should never be missing, and a nonzero share in that column is a parse failure rather than a
property of the form.

# Validation

Three consistency checks between what was parsed and what survived cleaning. The prediction in each case is stated
first, so a result that differs is a finding rather than a number to interpret after the fact.

```{r}
#| label: validate-parse
# Every quarter with mirrored HTML should have a parsed table, and every parsed row should survive
# cleaning except those whose page failed to parse. Repeated HashIndex values are expected here and
# are not checked: at this grain a repeat is a second registrant, not a duplicated filing.
tibble::tibble(
  QuartersWithHtml = nrow(tab_parse_log),
  QuartersParsed   = sum(tab_parse_log$nTotal > 0L),
  RowsParsed       = sum(tab_parse_log$nTotal),
  RowsKept         = nrow(tab_landing),
  ParseFailures    = sum(tab_parse_log$nTotal) - nrow(tab_landing)
) |>
  tbl_out(
    .title = "Parse against clean",
    .notes = c(
      QuartersParsed = "Below QuartersWithHtml means a quarter was mirrored but never parsed.",
      ParseFailures  = "Pages fetched whose HTML could not be read. Retained in the cache, excluded here."
    )
  )
```

This check is also what makes the cached path honest. `RowsParsed` comes from the parse log and `RowsKept` from the
landing table, and the two are cached separately against different directories. A stale cache on either side would
open a gap here that a fresh render closes, so the reconciliation that would have caught it runs whether or not
anything was recomputed.

The grain of the table, and how it relates to the frame selected above.

```{r}
#| label: validate-grain
edg_landing_grain(
  .tab   = tab_landing,      # the cleaned landing table
  .frame = vec_hash_index    # the filings the form-type restriction selects
) |>
  tbl_out(
    .title = "Grain and frame",
    .notes = c(
      RowsPerFiling = "Registrants per filing. Above one by construction, not a duplication fault.",
      OutsideFrame  = "Filings mirrored under a wider selection than the present one. Harmless: \\
                       downstream selection happens on the link tables, not here."
    )
  )
```

A filing, a registrant and a film number ought to identify one row. Where they do not, the question is whether the
repeat is the same row written twice or two rows that genuinely disagree about one registrant. Only the second would
matter, and anything joining to this table would inherit it.

```{r}
#| label: validate-duplicates
edg_landing_duplicates(
  .tab = tab_landing,                            # the cleaned landing table
  .key = c("HashIndex", "CIK", "FilmNo")         # filing, registrant, film number
) |>
  tbl_out(
    .title = "Repeated filer keys",
    .notes = c(
      nKeyDupGroups       = "Filer keys occurring more than once.",
      AllRepeatsIdentical = "TRUE means every repeat is an exact duplicate row and carries no conflict."
    )
  )
```

Two keys repeat, across six rows, and none of the repeats is an exact copy: where a key recurs here the rows genuinely
disagree about the registrant. That is the case this check exists to find, so the prediction above was wrong and the
result is a finding rather than a formality. At six rows in 21.6 million it changes nothing measurable, but it does mean
the table cannot be treated as keyed on filing, registrant and film number.

Nothing downstream treats it that way. 01C joins on `DocID`, which is unique by construction, so the disagreement stays
visible here rather than propagating as silent row multiplication. It is reported and not repaired for the reason the
whole document is built on: this script says what the mirror contains, not what it should have contained.

# Deployment

`Output/LandingPageAll.parquet` is written by the cleaning step above and is the only artifact of this script that
anything downstream reads. 01B selects documents from it; 01C restricts it to the filings whose documents were actually
retrieved and publishes that as `LandingPage.parquet`.

The two are deliberately separate files rather than one filtered in place. The unfiltered version is the denominator
for every coverage statement made later, and a pipeline that overwrites its own denominator cannot report how much it
lost.

Rows are written sorted by filing date, then filing, then filer. The order carries no meaning -- every consumer joins on
keys -- but fixing it makes the file a deterministic function of its inputs, so a later copy can be checked against an
earlier one. The date leads rather than the filing hash because Parquet encodes each column with a dictionary and run
lengths: sorting on a hash scatters every correlated column and inflates the file several-fold, while sorting on the
date preserves the temporal grouping the data already had.

Nothing else is written. No figure files, no styled tables, no Stata export: those are the release
script's job, for the reason set out under *How results are reported*. One script converts and writes
everything once, when the pipeline is complete.

```{r}
#| label: deploy-report
fs::file_info(path = c(
  .lP$Output$LandingPageAll,   # the published artifact
  .lP$Cache$FrameIndex,        # the four caches, in the order the document builds them
  .lP$Cache$LinkCoverage,
  .lP$Cache$ParseLog,
  .lP$Cache$CleanStamp
)) |>
  dplyr::transmute(
    Kind    = c("Output", rep("Cache", 4L)),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output row is read downstream; the rest exist to make a re-render cheap.",
      Written = "A cache older than the Output row means that step found its input unchanged."
    )
  )
```

Every script in this pipeline writes inside its own output directory and nowhere else, and this checks that this one
did. `rGetEDGAR` builds its whole tree from a single root, so resolving the mirror creates a `DocumentData/` branch
alongside the two this script fills. That branch belongs to 01B, which keeps its own root.

An empty directory there is harmless and is removed, so that a folder inspected after a render contains only what the
script produced. Files there are not removed: a cleanup that deleted whatever it found would destroy the evidence in
precisely the case worth investigating.

```{r}
#| label: deploy-own-output
edg_check_own_output(
  .dir_mirror = fs::path(.dir_main, "GetEDGAR"),        # this script's mirror root
  .own        = c("MasterIndex", "DocumentLinks"),      # the branches this script fills
  .cap        = 1000L                                   # stop counting past this; any nonzero is the finding
) |>
  tbl_out(
    .title = "Own output",
    .notes = c(Action = "A branch that is not empty and not owned means another script wrote into this one.")
  )
```

# Overview

```{r}
#| label: fig-coverage-by-year
#| fig-height: 3.4
#| fig-cap: "Filings mirrored per calendar year. The frame closes in 2024, so the final year is
#|   partial by construction rather than by attrition."
edg_plot_coverage(.tab = tab_year)   # summarised once in Results; the release script writes the file
```

```{r}
#| label: overview-all
edg_report_all_index(
  .cov       = tab_coverage,      # mirror coverage, measured once above
  .tab_year  = tab_year,          # summarised once above
  .tab_forms = tab_forms,         # likewise
  .acquire   = .lP$Param$Acquire  # so the backlog note reads the same as it did the first time
)
```

# Next

**01B-EdgarDocuments** reads the link tables mirrored here together with `Output/LandingPageAll.parquet`, selects the
Exhibit-10 exhibits, CT orders and Item 1.01 8-Ks, downloads and parses them into `GetEDGAR/DocumentData/Parsed/`, and
writes the `DocID` to `Path` index every later script uses to locate a document's text.
