---
title: "EDGAR Acquisition -- Documents (01B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01A owns the mirror layout and the form vocabulary this document selects from. Sourcing its
# library rather than restating any of it is what keeps the two in agreement.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "01A-EdgarIndex"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01B-EdgarDocuments.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

01A mirrored the landing pages, which say what each filing contains. This document decides which of those attachments
are worth retrieving, fetches and parses them, and writes `FilePaths.parquet` -- the `DocID` to `Path` index every later
script uses to locate a document's text on disk.

Nothing is measured about the documents here. Word counts, stopword ratios, parse-error rates and the quality rules that
drop a document from the study are 01C. The division is by cost and failure mode: this script is network-bound and has
to survive interruption; 01C is local, cheap, and re-runs from scratch in minutes.

## What gets downloaded, and why only this

Three groups, and the reasoning differs for each.

**Exhibit 10 attachments** are the object of study. Regulation S-K Item 601(b)(10) requires a registrant to file its
material contracts as exhibits, and Exhibit 10 is where they land.

**CT orders** are the SEC's confidential-treatment orders. They are not contracts, but they record which contract terms
a filer was permitted to withhold, which is the only direct evidence of what redaction removed.

**8-K filings reporting Item 1.01** are current reports announcing entry into a material definitive agreement. The
filing carries the firm's own narrative summary of the contract, which makes it the comparison case: the same
agreement, described by the filer rather than drafted by the parties.

Everything else attached to the same filings is left on EDGAR. At ten requests per second, downloading attachments that
cannot answer the research question would extend acquisition from days into weeks.

## Why exhibit types come from a lookup rather than a pattern

Filers do not spell exhibit types consistently. `EX-10.1`, `EX-10`, `EXHIBIT 10.23` and dozens of further variants all
denote the same thing. Matching them with a regular expression is how a study silently excludes whichever spellings its
author did not anticipate, and the exclusion is invisible because the omitted documents never enter any count.

`rGetEDGAR` ships a lookup enumerating observed raw strings against a modal type, and this document reads it. The
mapping is then versioned with the package rather than with this project.

## Where the documents land

Every script in this pipeline writes inside its own output directory and nowhere else. That is not tidiness: it is what
makes the dependency graph readable from the filesystem, and what guarantees that deleting one script's output cannot
damage another's.

`rGetEDGAR` makes that awkward here. It resolves link tables and downloaded documents from a single root, reading
`<root>/DocLinks/` and writing `<root>/DocumentData/`, so handing it 01A's root would place a million documents inside
01A's directory. This script therefore keeps its own root and stages the link tables into it first.

The staged copy is a cache, not a second source. 01A remains the only writer of the link tables; what sits here is a
clone refreshed whenever the original differs, and deleting it costs one re-run of the chunk below. The trade is a
regenerable duplicate against an ownership rule, and the duplicate is the cheaper thing to give up -- it rebuilds from
one command, whereas a rule broken once has to be honoured by every script written afterwards.

That is also why the mirror root is named on its own rather than filed under `Cache/` or `Output/`. Anything a later
script reads goes in `Output/`; anything existing only to make a re-render cheap goes in `Cache/`; and the mirror is
neither, because it holds both kinds of thing at once. `DocLinks/` is a genuine cache, the clone described above.
`DocumentData/Parsed/` is the corpus. A heading meaning *safe to delete* over 1.46 million documents that cannot be
rebuilt without 1.46 million requests is a heading somebody will eventually act on.

## The parsed tree is the only copy

Documents are fetched with `.keep_orig = FALSE`, which discards the original bytes once parsing succeeds. There is no
local source to re-parse from, and re-deriving the tree means one request per document at ten per second. That is why
acquisition is gated, and why nothing in this document deletes anything.

## What is recomputed, and what is not

One step here is expensive: walking the parsed tree to build the `DocID` to `Path` index. It takes about a minute, over
1.46 million files, and its answer cannot change unless a document was added or removed.

`edg_index_documents()` therefore takes a `.rerun` argument defaulting to `FALSE`, and fingerprints the tree before
deciding whether to walk it. The fingerprint is not a file listing -- listing the tree is the cost being avoided. It is
the number of `DocType`/`YQ` directories and their modification times, which move whenever a document is added or
removed inside one: roughly four hundred `stat` calls in place of one and a half million.

Two consequences, and both are the point. The index stays honest, because it is rebuilt whenever the tree it describes
has moved rather than whenever somebody remembers to ask. And the same call can be made twice -- once before the
download to decide what is outstanding, once after to pick up whatever arrived -- with the second costing nothing on the
common case where nothing arrived.

What a directory timestamp cannot see is a document rewritten in place. Nothing here does that: each parsed document is
written once and never returned to. Where that assumption needs testing, `.rerun = TRUE` forces the full walk.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are deliberate and both
are the same decision. A runbook is read while it runs and pasted into discussion, where a monospaced block survives
being quoted into a mail or a chat window and a styled table does not.

The publication versions are produced once, at the end of the pipeline, by the consolidated release script: styled
tables from the same `tbl_out()` specifications, figure files from the same plotting functions. Producing them here
instead would mean twenty scripts each writing part of the manuscript's exhibits, rewritten on every render of a
document that changed none of them.

# Configuration

```{r}
#| label: config
.dir_index <- here::here("2_output", "01A-EdgarIndex")

.lP <- list(
  Input = list(
    IndexMirror    = fs::path(.dir_index, "GetEDGAR"),                            # 01A's mirror, read only
    LandingPageAll = fs::path(.dir_index, "Output", "LandingPageAll.parquet")     # written by 01A, read only
  ),
  Cache = list(
    TreeStamp = utils_file_path(.dir_main, "Cache", "TreeStamp.parquet")   # fingerprint the index was built under
  ),
  Output = list(
    FilePaths = utils_file_path(.dir_main, "Output", "FilePaths.parquet")   # the DocID to Path index
  ),
  Param = list(
    User    = "Matthias.Uckert@Outlook.com",   # SEC requires a contact address on every request
    Item    = "1.01",                          # the 8-K item denoting a material definitive agreement
    Workers = 5L,                              # download workers; the SEC rate limit binds before this does
    Acquire = FALSE                            # TRUE permits the download to run
  )
)

# THE MIRROR ROOT IS NEITHER CACHE NOR OUTPUT, and is named at the top level for that reason. It
# holds the staged link tables, which are a cache, and the parsed corpus, which is irreplaceable.
# See "Where the documents land" above.
.lP$Mirror <- utils_file_path(.dir_main, "GetEDGAR")

# 01A's tree is asserted to exist before it is resolved. get_directories() creates whatever is
# missing, so calling it on an absent root would silently manufacture an empty mirror inside 01A's
# directory instead of reporting that 01A has not run.
stopifnot("01A's mirror is missing; render 01A first" = fs::dir_exists(.lP$Input$IndexMirror))

edgar_index_    <- rGetEDGAR::get_directories(.lP$Input$IndexMirror)   # 01A's, read only
.lP$Input$Links <- edgar_index_$DocLinks$DirMain$Links

.lP$Edgar <- rGetEDGAR::get_directories(.lP$Mirror)                    # this script's own

fs::file_exists(.lP$Input$LandingPageAll)
```

# Staging

The link tables are cloned into this script's root so that the download reads and writes in one place, and that place is
this script's own. Refreshed by comparing file names and byte sizes rather than timestamps: a clone shares data blocks
with its source, so its modification time says nothing about whether the contents still agree.

```{r}
#| label: stage-links
edg_stage_links(
  .dir_src = .lP$Input$Links,                    # 01A's link tables
  .dir_dst = .lP$Edgar$DocLinks$DirMain$Links,   # this script's staged copy
  .quiet   = FALSE                               # FALSE reports how many were copied
)
```

# Selection

The three groups below are the inclusion rule for the entire study, so they are composed here rather than hidden behind
a function call. Each is a filter on the mirrored link tables; the plumbing that resolves raw exhibit types and file
extensions lives in the library.

```{r}
#| label: select-documents
# 1. Exhibit 10 -- the material contracts themselves.
tab_ex10 <- edg_links_with_ext(
  .path_links = .lP$Edgar$DocLinks$DirMain$Links,   # staged link tables
  .types      = edg_doc_types(.mod = "Exhibit 10"), # every observed spelling of an Exhibit 10 type
  .hash_index = NULL                                # NULL keeps all filings
)

# 2. CT orders -- the record of what redaction was permitted to remove.
tab_ctos <- edg_links_with_ext(
  .path_links = .lP$Edgar$DocLinks$DirMain$Links,   # staged link tables
  .types      = edg_doc_types(.mod = "CTO"), # confidential-treatment orders
  .hash_index = NULL                         # NULL keeps all filings
)

# 3. 8-K filings reporting Item 1.01 -- the filer's own summary of the same agreements. Restricted
#    to filings whose landing page lists the item, not to all 8-Ks: an 8-K reporting only a change
#    of auditor carries no contract narrative.
vec_item_hash <- edg_hash_with_item(
  .path_landing = .lP$Input$LandingPageAll,   # unfiltered landing table from 01A
  .item         = .lP$Param$Item,             # "1.01"
  .fixed        = TRUE                        # match literally; see the validation section
)

tab_08ks <- edg_links_with_ext(
  .path_links = .lP$Edgar$DocLinks$DirMain$Links,          # staged link tables
  .types      = edg_doc_types(.mod = c("8-K", "8-K/A")),   # current reports and their amendments
  .hash_index = vec_item_hash                              # only those reporting the item
)

tab_selected <- dplyr::bind_rows(
  dplyr::mutate(tab_ex10, Group = "Exhibit10"),
  dplyr::mutate(tab_ctos, Group = "CTO"),
  dplyr::mutate(tab_08ks, Group = "8-K")
)

nrow(tab_selected)
```

What is already on disk is subtracted from that. The parsed tree is the ledger: a `DocID` with a file under it has been
retrieved, and nothing further needs to be remembered.

The index below is that ledger read into a table, not a second record that can drift from it. It is rebuilt whenever the
tree's fingerprint has moved and reused otherwise, so the two cannot disagree without the disagreement being detected.
The identical call appears again after the download, and that is the point rather than an oversight: the fingerprint
moves exactly when the second answer would differ from the first.

```{r}
#| label: index-on-disk
tab_index <- edg_index_documents(
  .dir_parsed = .lP$Edgar$DocumentData$Parsed,   # root of the parsed tree
  .path_out   = .lP$Output$FilePaths,            # the index downstream reads
  .path_stamp = .lP$Cache$TreeStamp,             # fingerprint the index was built under
  .rerun      = FALSE                            # TRUE re-walks regardless of the fingerprint
)

vec_on_disk <- tab_index$DocID

length(vec_on_disk)
```

```{r}
#| label: report-outstanding
tab_outstanding <- edg_outstanding(
  .tab_sel  = tab_selected,   # everything the rule selects
  .ids_disk = vec_on_disk     # what is on disk
)

edg_report_selection(
  .tab_out = tab_outstanding,     # summarised above, not recomputed
  .acquire = .lP$Param$Acquire    # reported, so a gap and a switch stay distinguishable
)

use_docids <- setdiff(tab_selected$DocID, vec_on_disk)
```

Two things can leave a document outstanding, and they need different responses. A count that is stable across renders is
links the SEC no longer serves, which are lost to any method rather than to this one; a count that jumps is an
interrupted acquisition, which the switch above will finish.

On the present corpus it is neither: every selected document is on disk, and every document on disk is selected. The
retrieved corpus is exactly the inclusion rule applied to the mirror, with no attrition in either direction. That is
worth stating rather than assuming, because it is the one place where a selection rule and the corpus it produced could
have drifted apart without anything downstream noticing.

# Acquisition

Gated, and reports what it did either way. PDF parsing raises errors on a minority of documents; these are recorded per
document and quantified in 01C rather than suppressed here.

```{r}
#| label: acquire-documents
if (isTRUE(.lP$Param$Acquire) && length(use_docids) > 0L) {
  rGetEDGAR::edgar_download_document(
    .dir       = .lP$Mirror,         # this script's own root: links staged in, documents written out
    .user      = .lP$Param$User,     # contact address sent with every request
    .doc_ids   = use_docids,         # only what is outstanding
    .keep_orig = FALSE,              # discard originals after parsing; see below
    .workers   = .lP$Param$Workers,  # the SEC rate limit binds before this does
    .verbose   = TRUE                # stream progress
  )
} else {
  cli::cli_alert_info("Acquisition is OFF or nothing outstanding: no documents were fetched.")
}
```

`.keep_orig = FALSE` is stated explicitly rather than left at its default because it is irreversible. It discards the
original bytes once parsing succeeds, which is why the parsed tree has no local source to be rebuilt from.

# Index

The identical call from the Selection section, made again now that the download has run. If anything was fetched, the
directories holding it carry a new modification time, the fingerprint differs and the tree is re-walked. If nothing was
fetched -- which is every render once the corpus is complete -- the fingerprint is unchanged and this costs one small
read.

That is what the fingerprint buys over keying the rebuild on the acquisition switch. The switch says whether this render
was *permitted* to add documents, not whether it did, so a permitted render that fetched nothing used to pay a full
one-minute walk to reproduce the file it already had.

```{r}
#| label: rebuild-file-index
tab_index <- edg_index_documents(
  .dir_parsed = .lP$Edgar$DocumentData$Parsed,   # root of the parsed tree
  .path_out   = .lP$Output$FilePaths,            # the index downstream reads
  .path_stamp = .lP$Cache$TreeStamp,             # fingerprint the index was built under
  .rerun      = FALSE                            # TRUE re-walks regardless of the fingerprint
)

nrow(tab_index)
```

# Results

The composition table is needed twice, here and in the Overview, and each computation groups the whole index. It is
computed once and passed to both.

```{r}
#| label: summarise-corpus
tab_composition <- edg_corpus_composition(.tab_idx = tab_index)   # one row per document type
```

```{r}
#| label: report-corpus
edg_report_documents(.tab_cmp = tab_composition)
```

The two tables in this document group the 8-K family differently, and the difference is not a discrepancy. Selection
assigns a `Group` in the chunk above and puts current reports and their amendments together; this table takes `DocType`
from the parsed tree, where the two are separate directories. The 292,740 8-K documents selected are the 284,240 8-K
and 8,500 8-KA documents here.

Quarter coverage differs by group because the forms carrying each began at different dates. Exhibit 10 runs the full
EDGAR history; the 8-K item structure that makes Item 1.01 identifiable dates from the 2004 reform, and CT orders
appear only where confidential treatment was sought.

# Validation

Three checks. Each states its expected value first, so a result that differs is a finding rather than a number to
interpret after the fact.

```{r}
#| label: validate-index
# 1. No duplicate DocID: the identifier derives from the filename, so a repeat means one document
#    was written under two year-quarters.
# 2. Every indexed document was selected. A document on disk that the rule does not select would
#    enter the corpus without ever having been chosen.
# 3. Matching the item code as a pattern rather than literally puts a wildcard in the middle of it.
#    No 8-K item code has the shape that would exploit that, so the two should agree exactly.
n_loose_ <- length(edg_hash_with_item(
  .path_landing = .lP$Input$LandingPageAll,   # unfiltered landing table from 01A
  .item         = .lP$Param$Item,             # "1.01"
  .fixed        = FALSE                       # as a pattern, for comparison only
))

tibble::tibble(
  DuplicateDocID   = sum(duplicated(tab_index$DocID)),
  IndexedNotChosen = sum(!tab_index$DocID %in% tab_selected$DocID),
  ItemFixed        = length(vec_item_hash),
  ItemPattern      = n_loose_,
  ItemDifference   = n_loose_ - length(vec_item_hash)
) |>
  tbl_out(
    .title = "Index and match-rule checks",
    .notes = c(
      IndexedNotChosen = "Nonzero means documents on disk that the inclusion rule does not select.",
      ItemDifference   = "Nonzero means the pattern matched item codes the literal string did not."
    )
  )
```

Two things about where this script wrote. A nested `GetEDGAR/` inside its own root would mean the download resolved its
tree differently from the rest of the document, leaving documents where nothing looks for them. And no document should
ever appear under 01A's root, which this script reads from and must never write to.

The second is counted rather than tested for existence, and the distinction matters here more than anywhere. Resolving
01A's tree in the Configuration chunk calls `get_directories()`, which creates whatever is missing -- including a
`DocumentData/` branch that 01A itself removes at the end of its own render. A check asking whether that directory
exists therefore reports a violation this document committed against itself by looking. What is being asked is whether
any *document* landed there, and the answer is a count.

The path is reported relative to the project root. An absolute path is correct on one machine and wrong on every other,
and this page is published.

```{r}
#| label: validate-mirror-root
# The count recurses, which is instantaneous over an empty tree and slow over a full one. That
# asymmetry is acceptable: a slow answer here means documents are in a directory this script does
# not own, which is worth waiting to learn.
dir_docs_01a_ <- fs::path(.lP$Input$IndexMirror, "DocumentData")

tibble::tibble(
  ParsedRoot  = as.character(fs::path_rel(.lP$Edgar$DocumentData$Parsed, start = here::here())),
  StrayNested = fs::dir_exists(fs::path(.lP$Mirror, "GetEDGAR")),
  DocsIn01A   = if (fs::dir_exists(dir_docs_01a_)) {
    length(fs::dir_ls(path = dir_docs_01a_, recurse = TRUE, type = "file"))
  } else {
    0L
  }
) |>
  tbl_out(
    .title = "Where this script wrote",
    .notes = c(
      StrayNested = "Must be FALSE. TRUE means the download resolved a different tree from the rest of this document.",
      DocsIn01A   = "Must be zero. The empty branch itself is created by this document's own get_directories() call."
    )
  )
```

# Deployment

`Output/FilePaths.parquet` is the only artifact of this script, and the single writer of the `DocID` to `Path` mapping.
Every later script reads it rather than re-walking the tree.

Nothing else is written. No figure files, no styled tables: those are the release script's job, for the reason set out
under *How results are reported*. The one other file this script owns is `Cache/TreeStamp.parquet`, which records the
fingerprint the index was built under and exists solely so the next render can tell whether the walk is needed.

```{r}
#| label: deploy-report
fs::file_info(path = c(.lP$Output$FilePaths, .lP$Cache$TreeStamp)) |>
  dplyr::transmute(
    Kind    = c("Output", "Cache"),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output row is read downstream.",
      Written = "A stamp older than this render means the tree had not moved and no walk was needed."
    )
  )
```

# Overview

```{r}
#| label: fig-corpus-by-year
#| fig-height: 3.4
#| fig-cap: "Documents retrieved per calendar year by group. The 8-K series begins in 2004, when the
#|   item structure that makes a material-agreement report identifiable was introduced."
edg_plot_corpus(.tab = edg_corpus_by_quarter(.tab_idx = tab_index))
```

```{r}
#| label: overview-all
edg_report_all_docs(
  .tab_out = tab_outstanding,     # summarised once above
  .tab_cmp = tab_composition,     # likewise
  .acquire = .lP$Param$Acquire    # so the backlog note reads the same as it did the first time
)
```

# Next

**01C-EdgarMetaData** reads this index and measures the documents: word counts, stopword ratios and parse errors. It
applies the quality rules that drop a document from the study, restricts the landing table and the master index to the
filings that survived, and consolidates everything into `FullMetaData.parquet`, which is what 02, 03 and 04 read.
