---
title: "01B -- EDGAR"
subtitle: "The documents behind every in-scope filing, as filed, one parquet per quarter"
date: today
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
source(here::here("1_code", "_Commons", "_Initialize.R"))
init_setup()
init_source_commons()
```

# Purpose

The second filing stage. For every in-scope filing in `01A`'s `Filings` it fetches the complete submission
from EDGAR, splits it into its documents, and keeps the ones later stages read, exactly as filed, in one
parquet per quarter. Nothing is parsed beyond that split: sections, tables and text are later stages' work,
and they read what this one leaves on disk.

## What it fetches, and why not keep it

EDGAR keeps every filing as one complete submission file: each document the filer submitted, behind a
header carrying the accession number, the form and the period of report. Its address needs nothing but the
CIK and the accession number, both in `Filings`, so there is no index to scrape and no document map to keep.

Kept whole, the series projects to about 1.6 TB: most of a submission is images, PDFs and exhibits nobody
here reads (the 800-filing pilot). So each quarter is split as soon as it is on disk, and the parquet keeps
the content of every document whose type matches `Keep`:

- the 10-K or 20-F itself;
- EX-13, where some 10-K filers put the annual report and with it the MD&A and the statements. In a 20-F,
  Exhibit 13 is the Section 906 certification: small, and kept by the same rule;
- EX-99, where some 20-F filers put their audited statements and others the statements of an investee.
  Which is which is read from the description by the stage that uses them;
- the label linkbase, the labels a filer declares, printed or not. It is 4.6% of a 10-K submission's
  bytes and 3.4% of a 20-F's (2025q2), about 4 to 5 GB on disk for the series.

Every other document keeps its type, file name, description and size, so the record still says what each
submission held. The rule is written into every row, and a quarter split under another rule is refused
rather than mixed: a later stage must be able to tell a document that was never filed from one that was
filed and not kept.

## The split is not ours

`secsgml` parses the SGML container of a submission; its author has run it over the whole EDGAR corpus.
`_python/split_submissions.py` turns its output into rows and does nothing else. Content is stored as
bytes, not text: filings arrive in UTF-8, Latin-1, Windows-1252 and now and then in bytes valid in no
encoding, and decoding here could only fail or change what was filed.

## The accession number is the key

Every row carries its `Adsh`, so a document is joined to its filing by construction. Nothing this stage
fetches from the SEC ever needs matching.

## Resumable, per filing

A filing is done when its header row is in one of its quarter's parquets. A render fetches what is not
done, splits the arrivals into a new part, reads the part back, and only then -- when `KeepRaw` is `FALSE`
-- deletes the complete files of the filings it holds, so the peak on disk is one quarter. Requests stay
below the SEC's published fair-access ceiling of ten a second (SEC, *Accessing EDGAR Data*), and a run of
consecutive failures stops the loop instead of turning every remaining filing into a failure.

A 403 is its own case. The SEC answers too many requests with a 403 and lifts the block once the rate has
stayed below the ceiling for ten minutes; it serves the same page to an undeclared user agent, so the text
cannot tell the two apart. The timing can. A 403 before anything in the render was fetched is the user
agent or a block already in place, and stops the render at once; a 403 after successful fetches is waited
out for `BlockWait` seconds and the filing tried again, up to `MaxBlocks` times.

## EDGAR-CORPUS, as a benchmark

The item-parsed 10-K corpus of Loukas et al. (ECONLP 2021), 1993-2020, is fetched as published and pinned
to one revision. It is someone else's parse, with the numerical tables removed and keyed on CIK and period
year, so it is kept as the yardstick a later parse is compared against. Each year ships as three files
that are one corpus cut at random; all three are fetched.

# Configuration

```{r}
#| label: config

.lP <- init_config(
  .script  = "01B-EDGAR",
  .inputs  = c(Filings = "01A:Filings"),                     # the download universe: every FSDS submission
  .outputs = c(
    "Raw/",                                                  # complete submissions, <Qtr>/<Adsh>.txt; transient
    "Documents/",                                            # the kept documents, <Qtr>/part-NNN.parquet
    "EdgarCorpus/",                                          # the corpus as published; empty if not requested
    "Downloads",                                             # one row per planned filing: outcome, what is kept
    "CorpusFiles"                                            # one row per requested corpus file
  ),
  .params  = list(
    Quarters     = "2025q2",                                 # the test: one full quarter; NULL = every quarter
    UserAgent    = "University of Amsterdam - M. Uckert m.uckert@uva.nl",  # the SEC returns 403 without one
    Rate         = 5L,                                       # requests a second; the SEC's ceiling is 10
    MaxRunFail   = 25L,                                      # consecutive failures that stop the loop
    MaxFailShare = 0.01,                                     # gate: planned filings allowed without documents
    Keep         = "(10-K|20-F|EX-(13|99)([.\\s].*)?|EX-101\\.LAB)",  # types kept whole, a full-match regex
    KeepRaw      = TRUE,                                     # the test keeps the complete files; FALSE deletes
                                                             #   each quarter's once its parquet is read back
    BlockWait    = 600,                                      # seconds to wait out a rate block: the SEC's ten minutes
    MaxBlocks    = 3L,                                       # waits for one filing before the render stops
    CorpusYears  = 2018L,                                    # EDGAR-CORPUS period years; NULL skips the corpus
    CorpusSplits = c("train", "validate", "test"),           # all three: one corpus, cut at random
    CorpusRev    = "7e90f0f342569b35213445f809cfaf3b91f9964f"  # pinned revision of the Hugging Face repository
  ),
  .duck    = list(MemoryLimit = "32GB", TempDir = NULL)      # the default; this stage opens no database
)

source(.lP$Fun)
```

## The test

Coverage is `Quarters`, and the unit is a whole quarter. The test is 2025q2: recent, and a quarter in which
both forms are well represented. `KeepRaw = TRUE` leaves its complete files in `Raw/`, so a change to
`Keep` re-splits the quarter without a second download: delete `Documents/2025q2/`, which the keep rule
check asks for anyway, and render. The full run sets `Quarters` to `NULL` and `KeepRaw` to `FALSE`.

# Input

## Filings

Every FSDS submission of every form, with the scope flagged rather than applied.

```{r}
#| label: input-filings

tab_filings_ <- arrow::read_parquet(.lP$Input$Filings)
qtrs_ <- edg_quarters(
  .tab_filings = tab_filings_,                               # the universe the quarters are checked against
  .qtrs        = .lP$Params$Quarters                         # NULL resolves to every quarter it holds
)
```

## What is fetched

The rule that defines the download list, in the open: in scope, in the requested quarters. Nothing else
bounds it.

```{r}
#| label: input-scope

tab_scope_ <- tab_filings_ |>
  dplyr::filter(
    .data$InScope,                                           # D7: 10-K or 20-F, no amendment, PrevRpt 0
    .data$Qtr %in% qtrs_                                     # the requested quarters
  )
```

## The download list

The address and the file name. The keys are checked on the way: a missing CIK or a malformed accession
number could only produce failures, and stops the render here instead.

```{r}
#| label: input-plan

tab_plan_ <- edg_plan(.tab_scope = tab_scope_)
```

## Where the rows went

```{r}
#| label: input-funnel
#| results: asis

edg_report_plan(
  .tab_filings = tab_filings_,                               # every submission, for the drops
  .qtrs        = qtrs_,                                      # the requested quarters
  .tab_plan    = tab_plan_                                   # what survived
)
```

# Acquire

## Fetch, split, keep

Quarter by quarter: fetch what no parquet holds yet, split the arrivals into a new part, read it back, and
account for every filing. Complete files are deleted only after that, and only when `KeepRaw` is `FALSE`.

```{r}
#| label: acquire-documents

tab_status_ <- edg_acquire(
  .tab_plan     = tab_plan_,                                 # what to fetch
  .dir_raw      = .lP$Output$Raw,                            # where complete submissions land
  .dir_docs     = .lP$Output$Documents,                      # where the kept documents go
  .keep         = .lP$Params$Keep,                           # which document types keep their content
  .keep_raw     = .lP$Params$KeepRaw,                        # keep the complete files after the split
  .user_agent   = .lP$Params$UserAgent,                      # declared to the SEC with every request
  .rate         = .lP$Params$Rate,                           # requests a second
  .max_run_fail = .lP$Params$MaxRunFail,                     # consecutive failures that stop the loop
  .block_wait   = .lP$Params$BlockWait,                      # seconds to wait out a rate block
  .max_blocks   = .lP$Params$MaxBlocks,                      # waits for one filing before stopping
  .root         = .lP$Root                                   # for _python/
)
```

## What the parquets hold

The index of every document in every parquet, without the content, and one row per planned filing.

```{r}
#| label: acquire-index

tab_index_ <- edg_index(
  .dir_docs = .lP$Output$Documents,                          # every part of every quarter
  .qtrs     = NULL                                           # all quarters, so the projection sees them all
)
tab_downloads_ <- edg_downloads(
  .tab_status = tab_status_,                                 # what happened to each planned filing
  .tab_index  = tab_index_                                   # what its parquet holds
)
```

```{r}
#| label: acquire-arrived
#| results: asis

edg_report_downloads(.tab_downloads = tab_downloads_)
```

## Where the bytes go

What a submission is made of, by form and document type, and what share of it is kept. This is the table
that says whether a type left out should be kept -- for 20-F filers in particular, whose annual report can
sit in an exhibit.

```{r}
#| label: acquire-types
#| results: asis

tab_types_ <- edg_types(.tab_index = tab_index_, .tab_downloads = tab_downloads_)
edg_report_types(.tab_types = tab_types_)
```

## EDGAR-CORPUS

Every split of every requested year, at the pinned revision.

```{r}
#| label: acquire-corpus

tab_corpus_plan_ <- edg_corpus_plan(
  .years    = .lP$Params$CorpusYears,                        # NULL: nothing to fetch
  .splits   = .lP$Params$CorpusSplits,                       # the published splits
  .revision = .lP$Params$CorpusRev                           # a fixed release, not the repository's head
)
tab_corpus_ <- edg_corpus_fetch_all(
  .tab_corpus_plan = tab_corpus_plan_,                       # what to fetch
  .dir_corpus      = .lP$Output$EdgarCorpus,                 # where it goes
  .user_agent      = .lP$Params$UserAgent                    # sent with every request
)
```

```{r}
#| label: acquire-corpus-report
#| results: asis

edg_report_corpus(.tab_corpus = tab_corpus_)
```

# Gate

## Downloads

One row per planned filing; every held filing in a parquet exactly once; filings without their documents
within `MaxFailShare`, a split without the filing's own form counting as one; and, when complete files are
deleted, none left behind for a held filing.

```{r}
#| label: gate-downloads

edg_gate_downloads(
  .tab_plan       = tab_plan_,                               # what was asked for
  .tab_downloads  = tab_downloads_,                          # what the parquets hold
  .max_fail_share = .lP$Params$MaxFailShare,                 # tolerated share without documents
  .dir_raw        = .lP$Output$Raw,                          # checked for leftovers
  .keep_raw       = .lP$Params$KeepRaw                       # whether leftovers are expected
)
```

## Corpus

```{r}
#| label: gate-corpus

edg_gate_corpus(.tab_corpus = tab_corpus_)
```

# Validation

## Size by filing year and form

The complete submission and what is kept of it. Filing year is the year of the FSDS quarter.

```{r}
#| label: validation-size
#| results: asis

tab_size_ <- edg_size_by_year(.tab_downloads = tab_downloads_)
edg_report_size(.tab_size = tab_size_)
```

## The full series, projected

The number the design turns on is disk. If the projected parquets fit, this is the stage; if they do not,
the next cut is the `Keep` list, which the bytes table above prices type by type.

```{r}
#| label: validation-projection
#| results: asis

tab_projection_ <- edg_projection(
  .tab_downloads = tab_downloads_,                           # the sizes and the pace
  .tab_filings   = tab_filings_,                             # the universe projected to
  .tab_index     = tab_index_,                               # what is held, every quarter
  .dir_docs      = .lP$Output$Documents                      # the parquets' sizes on disk
)
edg_report_projection(.tab_projection = tab_projection_)
```

# Overview

## Megabytes kept per filing

```{r}
#| label: fig-size
#| fig-height: !expr plot_height(.n_rows = nrow(tab_size_))

edg_plot_size(.tab_size = tab_size_)
```

# Results

```{r}
#| label: results
#| results: asis

step_report()
edg_report_coverage(
  .tab_downloads = tab_downloads_,                           # what this render found and did
  .tab_filings   = tab_filings_,                             # the full series, for scale
  .qtrs          = qtrs_                                     # the requested quarters
)
```

# Deployment

```{r}
#| label: deploy

utils_write_parquet(.tab = tab_downloads_, .path = .lP$Output$Downloads)
utils_write_parquet(.tab = tab_corpus_,    .path = .lP$Output$CorpusFiles)
# Documents/, Raw/ and EdgarCorpus/ were written file by file in # Acquire.

cli::cli_alert_success("Written to {.path {(.lP)$Dir}}.")
```

# Next

## The full series

Set `Quarters` to `NULL` and `KeepRaw` to `FALSE`. The parquets are kept, so the full run starts from them,
and the peak on disk is one quarter of complete files.

## The keep list

The bytes table prices it type by type. A change is a change to `Keep`, and it applies to quarters split
afterwards; quarters already split under the old rule are refused until they are split again.

## Items

A later pair reads `Documents/` and splits the 10-K and 20-F documents into items, with the tables kept.
Existing item parsers are the first candidates; the 20-F item list is the one piece nobody ships.

## Matching the corpus

EDGAR-CORPUS joins to `Filings` on CIK and period year, the only key it carries. Then the two parses are
compared item by item, which is what the benchmark is for.
