---
title: "EDGAR Acquisition -- Document Metadata (01C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01A owns the mirror layout; 01B owns the document index. Sourcing both rather than restating any
# of it is what keeps the three in agreement.
purrr::walk(
  .x = c("01A-EdgarIndex", "01B-EdgarDocuments"),
  .f = function(.s) {
    source(
      file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
      encoding = "UTF-8"
    )
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01C-EdgarMetaData.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

01B put the documents on disk and indexed them. This is the first script that opens them.

It measures every document, decides which are too damaged to analyse, restricts the upstream metadata to the filings
that survived, and joins everything into `FullMetaData.parquet` -- the single table that 02, 03 and 04 read. Everything
the rest of the pipeline knows about a document that is not its text comes from here.

Nothing here touches the network, so nothing here is gated. Every step inspects its own output and does only what is
missing. This is the document in the family where "everything runs" holds without qualification, and it is also where
most of the numbers a referee will ask about are produced.

## Flagged, not deleted

Documents failing the quality rules are marked `Removed = 1` and kept in the table. A pipeline that drops them cannot
report its own attrition, and how much was excluded and why is a result rather than an implementation detail. Every
downstream script filters on the flag; none of them has to know the rule.

## The same attachment, fetched several times

A filing can name many registrants, and its attachments are listed under each of them. Acquisition follows that listing,
so one attachment becomes one file per registrant. Roughly one document in six on disk is a repeat of this kind, and the
share is not uniform -- it concentrates in registration statements, which carry the most co-registrants.

That has to be measured here, because every count made downstream is otherwise read against the wrong denominator.
`HashDocument` identifies the attachment and `DocID` identifies a registrant's copy of it, so the grouping is exact and
needs no content comparison. What does need checking is whether the copies actually agree, and the answer comes from
what was measured after parsing them rather than from the file size EDGAR reported.

The flag is added; nothing is removed. Whether to analyse one copy or all of them is a downstream decision and differs
by task: classification wants one, entity extraction may want each, because the registrant-side metadata differs even
where the text does not.

## What the rules are for

The three rules catch failures of *conversion*, not properties of the contract. A PDF that rendered as coordinates, an
attachment that is a hyperlink to a document rather than the document, a page of a financial statement filed under an
exhibit number: these arrive looking like data and are not.

Each threshold sits far from anything a real agreement produces, which is deliberate. A blunt rule that removes wreckage
is defensible; a finely tuned one that removes short agreements is a research decision disguised as data cleaning.

| Rule | Fires when | What it catches |
|:--|:--|:--|
| Too short | 10 words or fewer after the header | stubs, links, empty conversions |
| Not prose | under 20% stopwords **and** under 100 words | tables and conversion debris |
| Mostly digits | 75% or more tokens numeric | financial statements |

Every rate below is reported by group -- contracts, 8-K reports, CT orders -- and never pooled. Exhibit 10 is
eighty-three per cent of the corpus, so a pooled figure is the Exhibit 10 figure with the other two averaged into
invisibility: a problem confined to CT orders would have to be forty times worse than one in contracts before it moved
the pooled number by the same amount.

The second rule needs its length condition. Ordinary English runs far above twenty per cent stopwords, but a *long*
document that runs low is an exhibit schedule -- legitimate content, densely tabular. Only a short one is debris.

## The adjusted word count

Every parsed document begins with the SEC's own header block: `<TYPE>`, `<SEQUENCE>`, `<FILENAME>`, `<DESCRIPTION>`.
Those words are counted along with the contract's, so an attachment containing nothing but a header does not measure as
empty. `nWordsAdj` subtracts them, and the emptiness rule is applied to that rather than to the raw count.

## What is recomputed, and what is not

Two things here are expensive and neither can produce a different answer while its inputs stand still.

**Measurement** is three passes over 1.8 million documents, each opening every file once: parse status, text
statistics, stopword counts. Each takes a `.rerun` argument defaulting to `FALSE` and each reconciles its cache
against the index rather than merely checking that the cache file exists. Whatever the cache does not cover is
measured and appended, so a first run is hours, a later one with nothing new is seconds, and a later one after 01B
fetched a thousand documents costs a thousand documents.

That reconciliation is not a refinement. Returning the cache on existence alone is right only while the corpus is
unchanged; once it grows, the documents missing from the cache join to `NA` in the statistics table and are dropped
outright by the consolidation's inner join, leaving `FullMetaData.parquet` quietly short. The most expensive step in
the pipeline had the weakest cache key in it.

**Restriction** cuts three corpus-sized tables -- thirty-two million link rows, the whole master index, twenty-one
million landing rows -- down to the retrieved documents. That is minutes of semi-joins for an answer determined by the
mirror and the index, so it is fingerprinted against both, together with the identifier set itself. A re-acquisition
upstream or a changed corpus invalidates it without anyone having to remember.

Neither of these is a suppressed chunk. Every chunk below executes, reports and validates on every render, and each
step says on the console which path it took.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are deliberate and both
are the same decision. A runbook is read while it runs and pasted into discussion, where a monospaced block survives
being quoted into a mail or a chat window and a styled table does not.

The publication versions are produced once, at the end of the pipeline, by the consolidated release script: styled
tables from the same `tbl_out()` specifications, figure files from the same plotting functions.

Reports sit with the step that produced them rather than in one `# Results` section, because each is the argument for
the step above it: parse failures belong beside the measurement, exclusion rates beside the rules, redundancy beside
the consolidation. The Overview restates all three together.

## Where things are written

Anything a later script reads goes in `Output/`. Anything that exists only to make a re-render cheap goes in `Cache/`.
This script reads 01A's mirror and 01B's index and writes into neither.

# Configuration

```{r}
#| label: config
.dir_index <- here::here("2_output", "01A-EdgarIndex")
.dir_docs  <- here::here("2_output", "01B-EdgarDocuments")

.lP <- list(
  Input = list(
    Mirror         = fs::path(.dir_index, "GetEDGAR"),                            # the mirror 01A established
    LandingPageAll = fs::path(.dir_index, "Output", "LandingPageAll.parquet"),    # unfiltered, written by 01A
    FilePaths      = fs::path(.dir_docs, "Output", "FilePaths.parquet"),          # DocID to Path, written by 01B
    # Both point at the short list. That is what produced the published measurements and is kept
    # deliberately; the validation section below reports that the two dictionaries are identical
    # rather than leaving it to be discovered from a file path.
    StopShort      = here::here("0_data", "Dictionaries", "LoughranMcDonald", "StopWords_Generic.txt"),
    StopLong       = here::here("0_data", "Dictionaries", "LoughranMcDonald", "StopWords_Generic.txt")
  ),
  Cache = list(
    StopWords     = utils_file_path(.dir_main, "Cache", "StopWords.parquet"),      # standardised dictionary
    DocErrors     = utils_file_path(.dir_main, "Cache", "DocErrors.parquet"),      # pass 1: parse status
    DocStats      = utils_file_path(.dir_main, "Cache", "DocStats.parquet"),       # pass 2: text statistics
    DocStop       = utils_file_path(.dir_main, "Cache", "DocStop.parquet"),        # pass 3: stopword counts
    RestrictStamp = utils_file_path(.dir_main, "Cache", "RestrictStamp.parquet"),  # guards the restricted tables
    OutputStamp   = utils_file_path(.dir_main, "Cache", "OutputStamp.parquet")     # guards the three derived tables
  ),
  Output = list(
    DocStats     = utils_file_path(.dir_main, "Output", "DocStats.parquet"),       # per-document measurements
    RemovedDocs  = utils_file_path(.dir_main, "Output", "RemovedDocs.parquet"),    # what the rules flagged, and why
    LinkData     = utils_file_path(.dir_main, "Output", "LinkData.parquet"),       # links, restricted to retrieved
    MasterIndex  = utils_file_path(.dir_main, "Output", "MasterIndex.parquet"),    # index, restricted to retrieved
    LandingPage  = utils_file_path(.dir_main, "Output", "LandingPage.parquet"),    # landing, restricted to retrieved
    FullMetaData = utils_file_path(.dir_main, "Output", "FullMetaData.parquet")    # the one table downstream reads
  ),
  Param = list(
    Workers      = 10L,   # parallel workers; also the number of chunks each pass is split into
    # The quality thresholds. Stated here rather than inside the rule function because they are the
    # numbers a referee is most likely to query, and they are argued in the Purpose section above.
    MaxWords     = 10L,   # rule 1: words after the header, at or below which a document is a stub
    MaxStop      = 20,    # rule 2: stopword percentage, at or below which a document is not prose
    MaxWordsStop = 100L,  # rule 2: and only among documents at or below this length
    MinNums      = 75     # rule 3: percentage of numeric tokens at or above which it is a table
  )
)

# Resolving 01A's tree creates whatever branch is missing, including an empty DocumentData/ that
# belongs to 01B. It is read-only here and 01A removes it on its next render.
.lP$Edgar <- rGetEDGAR::get_directories(.lP$Input$Mirror)

# Named individually so that a failure says which input is missing rather than that one of them is.
need_ <- c(
  FilePaths      = .lP$Input$FilePaths,
  LandingPageAll = .lP$Input$LandingPageAll,
  StopShort      = .lP$Input$StopShort,
  StopLong       = .lP$Input$StopLong
)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

# Reported relative to the project root. An absolute path is correct on one machine and wrong on
# every other, and this page is published.
tibble::tibble(
  Input = names(need_),
  Path  = as.character(fs::path_rel(unname(need_), start = here::here()))
) |>
  tbl_out(.title = "Inputs")
```

Failing here, rather than three passes later, is deliberate: a missing input should stop the document at the point the
path is declared, not after hours of measurement. The check aborts rather than reporting, and names the input that is
missing.

# Input

```{r}
#| label: load-index
tab_index <- arrow::read_parquet(.lP$Input$FilePaths)

nrow(tab_index)
```

# Measurement

The stopword dictionary is standardised with the same function that standardised the document text, so a word is spelled
identically on both sides of the comparison. Standardising only one side is how a stopword count comes out
systematically low without anything appearing to be wrong.

```{r}
#| label: build-dictionary
tab_stopdict <- edg_stopword_dict(
  .path_short = .lP$Input$StopShort,    # short Loughran-McDonald list
  .path_long  = .lP$Input$StopLong,     # long Loughran-McDonald list
  .path_out   = .lP$Cache$StopWords     # standardised, cached for the workers to read
)

nrow(tab_stopdict)
```

Three passes, one function. They differ only in what they compute per file, and sharing the traversal means they cannot
drift apart in how they chunk, how they handle a failure, or which documents they cover. Each writes a cache and skips
if it is present.

Two arguments exist because a worker is a fresh R session holding the installed packages and nothing else. `.sources`
names the library each worker must read before it can measure anything; `.args` carries the extra arguments as data.
Closing a value into an anonymous function reads more naturally, but the closure's environment is this session's global
environment, which is not sent, so in the worker the configuration list does not exist.

```{r}
#| label: measure-errors
tab_errors <- edg_measure_corpus(
  .tab_idx  = tab_index,               # every document on disk
  .path_out = .lP$Cache$DocErrors,     # cache; present means finished
  .fun      = edg_doc_error,           # reads the parse status recorded at download time
  .sources  = .path_fun,               # workers are fresh sessions; they source this library
  .workers  = .lP$Param$Workers,       # parallel workers
  .label    = "parse errors",          # shown in progress output
  .rerun    = FALSE                    # FALSE measures only what the cache does not already cover
)
```

```{r}
#| label: measure-stats
tab_stats_raw <- edg_measure_corpus(
  .tab_idx  = tab_index,               # every document on disk
  .path_out = .lP$Cache$DocStats,      # cache; present means finished
  .fun      = edg_doc_stats,           # word, character and numeric counts plus the header fields
  .sources  = .path_fun,               # workers are fresh sessions; they source this library
  .workers  = .lP$Param$Workers,       # parallel workers
  .label    = "text statistics",       # shown in progress output
  .rerun    = FALSE                    # FALSE measures only what the cache does not already cover
)
```

```{r}
#| label: measure-stopwords
tab_stop_raw <- edg_measure_corpus(
  .tab_idx  = tab_index,                                    # every document on disk
  .path_out = .lP$Cache$DocStop,                            # cache; present means finished
  .fun      = edg_doc_stopwords,                            # stopword shares against both lists
  .args     = list(.path_stop = .lP$Cache$StopWords),       # passed as data, not closed over
  .sources  = .path_fun,                                    # workers are fresh sessions
  .workers  = .lP$Param$Workers,                            # parallel workers
  .label    = "stopword counts",                            # shown in progress output
  .rerun    = FALSE                                         # FALSE measures only what is not covered
)
```

Both summaries are wanted twice, here and in the Overview, and the first joins two tables of 1.77 million rows. They
are computed once and passed to both.

```{r}
#| label: summarise-errors
tab_error_summary  <- edg_error_summary(.tab_err = tab_errors, .tab_idx = tab_index)   # one row per group
tab_error_messages <- edg_error_messages(.tab_err = tab_errors)                        # one row per message
```

```{r}
#| label: report-errors
edg_report_errors(
  .tab_sum = tab_error_summary,     # summarised above, not recomputed
  .tab_msg = tab_error_messages     # likewise
)
```

The three passes are joined into one table per document. The adjusted word count is computed here, and the numeric share
is capped at one: the numerator counts numeric tokens with one pattern and the denominator counts words with another, so
on documents that are almost entirely digits the two disagree enough to exceed unity. The cap is honest because the
quantity is only ever used against a threshold well below it.

```{r}
#| label: build-docstats
tab_docstats <- edg_doc_statistics(
  .tab_stats = tab_stats_raw,   # text statistics pass
  .tab_stop  = tab_stop_raw     # stopword pass
)

nrow(tab_docstats)
```

# Selection

The three rules decide what is analysable, so their thresholds are stated here rather than buried in the library. Each
is passed by name, and each sits far from anything a real agreement produces: that distance is what makes the rules
defensible as data cleaning rather than as a research decision in disguise.

```{r}
#| label: flag-removals
tab_removed <- edg_flag_removals(
  .tab_stats      = tab_docstats,             # the per-document measurements
  .tab_idx        = tab_index,                # supplies the document type for reporting
  .max_words      = .lP$Param$MaxWords,       # 10: an agreement cannot be stated in ten words
  .max_stop       = .lP$Param$MaxStop,        # 20 pct: ordinary English runs far above this
  .max_words_stop = .lP$Param$MaxWordsStop,   # 100: a LONG document low on stopwords is a schedule
  .min_nums       = .lP$Param$MinNums         # 75 pct numeric: a financial table, not a contract
)

nrow(tab_removed)
```

The rules are applied in that order and a document caught by two is attributed to the first, so the counts below are a
partition rather than three overlapping sets.

```{r}
#| label: summarise-removals
tab_removal_summary <- edg_removal_summary(.tab_rem = tab_removed, .tab_idx = tab_index)   # by rule
tab_survival        <- edg_survival_summary(.tab_rem = tab_removed, .tab_idx = tab_index)  # by group
```

```{r}
#| label: report-removals
edg_report_removals(
  .tab_sum  = tab_removal_summary,   # summarised above; the figure and the Overview reuse it
  .tab_surv = tab_survival           # likewise
)
```

# Restriction

Three upstream tables are restricted to the filings whose documents were actually retrieved. The unrestricted versions
stay where 01A and 01B wrote them, because they are the denominators for every coverage statement made later, and a
pipeline that overwrites its own denominator cannot report how much it lost.

The restriction is by document first and filing second. Links are cut to the documents on disk; the filings those links
belong to then define the master-index and landing subsets. Cutting all three on the same identifier would be wrong,
because a filing is in scope when *one* of its attachments was retrieved rather than when all of them were.

```{r}
#| label: restrict-upstream
lst_restricted <- edg_restrict_upstream(
  .tab_idx      = tab_index,                             # the corpus that actually exists
  .dir_links    = .lP$Edgar$DocLinks$DirMain$Links,      # 01A's mirrored link tables
  .dir_master   = .lP$Edgar$MasterIndex$DirParquet,      # 01A's mirrored master index
  .path_landing = .lP$Input$LandingPageAll,              # 01A's unfiltered landing table
  .paths_out    = list(                                  # named for the function, not the config
    Links   = .lP$Output$LinkData,                       # links, restricted to retrieved documents
    Master  = .lP$Output$MasterIndex,                    # index, restricted to their filings
    Landing = .lP$Output$LandingPage                     # landing pages, restricted to their filings
  ),
  .path_stamp   = .lP$Cache$RestrictStamp,               # fingerprint the three were built under
  .rerun        = FALSE                                  # TRUE rebuilds regardless of the fingerprint
)

tab_links   <- lst_restricted$Links
tab_master  <- lst_restricted$Master
tab_landing <- lst_restricted$Landing

c(Links = nrow(tab_links), Master = nrow(tab_master), Landing = nrow(tab_landing))
```

# Consolidation

The consolidated table joins the three restricted tables to the document statistics. Two derived columns are added. It
is built here and written in Deployment, after the checks below have run: an artifact three script families read should
not reach disk before the checks that would have caught a fault in it.

`MultFiler` and `nCIK` mark documents listed under more than one registrant. `FilerCopiesAgree` records whether those
copies match on all three length measures, and `PrimaryFiler` designates exactly one of them.

The primary is the lowest `DocID` -- which orders by CIK -- among copies that passed the quality rules. Filing date is
not a tiebreak, because every copy of one attachment belongs to the same filing and carries the same date. Preferring a
surviving copy matters: a failed conversion under one registrant would otherwise discard an attachment that reads
perfectly under another.

`Removed` carries the quality decision. In both cases the row stays.

One kind of repetition is deliberately **not** detected here. Two parties to one agreement each exhibit their own copy
under separate accessions, which produces different URLs and therefore different `HashDocument` values. Finding those
requires hashing the text of every document, which is a fourth pass over the corpus; it is worth doing and is not
attempted in this version.

```{r}
#| label: build-metadata
rem_ids_ <- tab_removed$DocID

tab_metadata <- tab_links |>
  dplyr::inner_join(tab_master, by = dplyr::join_by("HashIndex", "CIK", "YQ")) |>
  dplyr::inner_join(tab_docstats, by = dplyr::join_by("DocID")) |>
  dplyr::mutate(
    nCIK      = dplyr::n(),
    MultFiler = as.integer(.data$nCIK > 1L),
    .by       = "HashDocument"
  ) |>
  dplyr::mutate(Removed = as.integer(.data$DocID %in% rem_ids_)) |>
  dplyr::inner_join(
    y  = dplyr::select(tab_index, "DocID", DocTypeMod = "DocType", DocPath = "Path"),
    by = dplyr::join_by("DocID")
  ) |>
  dplyr::rename(DocTypeRaw = "DocType") |>
  dplyr::relocate("DocTypeMod", .after = "DocTypeRaw")

tab_metadata <- edg_flag_filer_copies(.tab = tab_metadata)

nrow(tab_metadata)
```

```{r}
#| label: summarise-filer-copies
tab_filer_summary      <- edg_filer_summary(.tab = tab_metadata)        # one row per group
tab_filer_distribution <- edg_filer_distribution(.tab = tab_metadata)   # registrants per attachment
```

```{r}
#| label: report-filer-copies
edg_report_filer_copies(
  .tab_sum  = tab_filer_summary,        # summarised above, restated in the Overview
  .tab_dist = tab_filer_distribution    # likewise
)
```

`nGroupsDiffer` is the check that matters. Copies of one attachment should agree on character, word and numeric-token
count, because they are the same file fetched twice. A group that disagrees means two requests for one URL returned
different content, which would be an acquisition fault rather than a counting one. One group disagrees, and the
Validation section below shows which and whether it reaches the analysis sample.

# Validation

Four checks. Each states its expectation first, so a result that differs is a finding rather than a number to interpret
afterwards.

```{r}
#| label: validate-metadata
# 1. The two inner joins can only lose rows. Anything lost is a document whose link row has no
#    matching index entry, which is a join failure rather than a filtering decision.
# 2. Every flagged document should appear in the final table, marked rather than absent.
# 3. DocID identifies a document, so it should be unique.
# 4. Jointly filed copies of the same agreement should be byte-identical. Where they are not, the
#    joint filing is not in fact the same document.
tibble::tibble(
  RowsLinks       = nrow(tab_links),
  RowsMetaData    = nrow(tab_metadata),
  LostInJoin      = nrow(tab_links) - nrow(tab_metadata),
  FlaggedTotal    = nrow(tab_removed),
  FlaggedInTable  = sum(tab_metadata$Removed),
  DuplicateDocID  = sum(duplicated(tab_metadata$DocID))
) |>
  tbl_out(
    .title = "Consolidation checks",
    .notes = c(
      LostInJoin     = "Nonzero means link rows with no matching master-index entry.",
      FlaggedInTable = "Should equal FlaggedTotal: flagged documents are marked, not dropped."
    )
  )
```

```{r}
#| label: validate-dictionaries
# The two stopword lists are read from the same file, so every long-list measure equals its
# short-list counterpart. Reported rather than silently carried: a reader seeing nStopLong beside
# nStopShort would otherwise reasonably assume the two came from different dictionaries.
tibble::tibble(
  PathShort      = as.character(.lP$Input$StopShort),
  PathLong       = as.character(.lP$Input$StopLong),
  SamePath       = identical(as.character(.lP$Input$StopShort), as.character(.lP$Input$StopLong)),
  nComparable    = sum(!is.na(tab_docstats$pStopShort) & !is.na(tab_docstats$pStopLong)),
  nNotComparable = sum(is.na(tab_docstats$pStopShort) | is.na(tab_docstats$pStopLong)),
  ShareIdentical = mean(tab_docstats$pStopShort == tab_docstats$pStopLong, na.rm = TRUE)
) |>
  dplyr::select(-"PathShort", -"PathLong") |>
  tbl_out(
    .title  = "Stopword dictionaries",
    .pct    = "ShareIdentical",
    .digits = 1L,
    .notes  = c(
      nNotComparable = "Documents with no tokens, where the share is undefined rather than unequal.",
      ShareIdentical = "Of the comparable documents. One file means this is 100 pct."
    )
  )
```

```{r}
#| label: validate-primary
# Exactly one primary per attachment, no more and no less. A group with none would mean every copy
# was flagged for removal and the tiebreak fell through; a group with two would mean the ordering is
# not total.
tab_metadata |>
  dplyr::summarise(nPrimary = sum(.data$PrimaryFiler), .by = "HashDocument") |>
  dplyr::summarise(
    nAttachments = dplyr::n(),
    nNoPrimary   = sum(.data$nPrimary == 0L),
    nTwoOrMore   = sum(.data$nPrimary > 1L)
  ) |>
  tbl_out(
    .title = "Primary selection",
    .notes = c(nNoPrimary = "Must be zero: every attachment needs exactly one designated copy.")
  )
```

Where copies of one attachment disagree, the count alone is not actionable. Which attachment, how far apart the copies
are, how many registrants filed it, and whether the quality rules already removed it are what decide whether it
matters, so all four are reported.

```{r}
#| label: validate-disagreements
edg_filer_disagreements(.tab = tab_metadata) |>
  utils::head(10L) |>
  tbl_out(
    .title = "Attachments whose copies disagree",
    .notes = c(
      nRemoved    = "Copies the quality rules flagged. A disagreement among discarded copies changes nothing.",
      SpreadChars = "Characters between the shortest and longest copy of one attachment."
    )
  )
```

One attachment in 1.49 million disagrees, and every copy of it was already flagged. Eight registrants filed it and the
copies split between 187 and 219 characters, which is a stub under either measurement and far below anything the
emptiness rule keeps; `nRemoved` is eight of eight. The disagreement therefore never reaches the analysis sample, which
is what makes it a curiosity rather than a fault to chase.

The check earns its place regardless of how little it finds. What it exists to catch is two requests for one URL
returning different content, and at any scale that would place every downstream count of distinct attachments on copies
that are not copies of each other.

# Deployment

Six artifacts. Three were written by the restriction step above, because there they are cache and published table at
once; the other three are written here, so that nothing is committed to disk before the checks above have passed.

The write is guarded, and the reason is not disk time. Five documents downstream -- 01D, 01E, 02B, 03A and 04C --
fingerprint their own caches against `FullMetaData.parquet`. Rewriting it unconditionally moves its modification time on
every render of this document, so every one of those caches misses and rebuilds although the bytes are identical. A
fingerprint is only as stable as the file it points at.

All three are a deterministic function of the same things: the three measurement caches, the restriction, and the four
quality thresholds. One fingerprint therefore covers all three, and it is computed here rather than inside the writer so
that what determines the outputs is visible next to them.

```{r}
#| label: write-outputs
stamp_outputs <- utils_dir_stamp(
  .dirs  = unlist(.lP$Cache[c("DocErrors", "DocStats", "DocStop", "RestrictStamp")]),   # what was measured
  .extra = .lP$Param[c("MaxWords", "MaxStop", "MaxWordsStop", "MinNums")]               # and under which rules
)

edg_write_metadata(
  .tabs = list(
    DocStats     = tab_docstats,    # per-document measurements
    RemovedDocs  = tab_removed,     # what the rules flagged, and why
    FullMetaData = tab_metadata     # the one table downstream reads
  ),
  .paths_out  = .lP$Output[c("DocStats", "RemovedDocs", "FullMetaData")],   # names checked, not matched
  .stamp      = stamp_outputs,      # computed above
  .path_stamp = .lP$Cache$OutputStamp,
  .rerun      = FALSE               # TRUE writes regardless of the fingerprint
)

c(DocStats = nrow(tab_docstats), Removed = nrow(tab_removed), MetaData = nrow(tab_metadata))
```

Nothing else is written. No figure files, no styled tables: those are the release script's job, for the reason set out
under *How results are reported*.

```{r}
#| label: deploy-report
fs::file_info(path = c(unlist(.lP$Output), unlist(.lP$Cache))) |>
  dplyr::transmute(
    Kind    = c(rep("Output", length(.lP$Output)), rep("Cache", length(.lP$Cache))),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output rows are read downstream; the rest make a re-render cheap.",
      Written = "A cache older than this render means that step found its input unchanged."
    )
  )
```

# Overview

```{r}
#| label: fig-removals-by-rule
#| fig-height: 2.4
#| fig-cap: "Documents flagged by each quality rule, split by group. Rules are applied in order, so a
#|   document caught by two is attributed to the first. Rule 1 is the emptiness test, 2 the prose
#|   test, 3 the numeric test."
edg_plot_removals(.tab = tab_removal_summary)   # summarised in Selection; the release script writes the file
```

```{r}
#| label: overview-all
edg_report_all_meta(
  .err_sum  = tab_error_summary,          # summarised once in Measurement
  .err_msg  = tab_error_messages,         # likewise
  .rem_sum  = tab_removal_summary,        # summarised once in Selection
  .rem_surv = tab_survival,               # likewise
  .fil_sum  = tab_filer_summary,          # summarised once in Consolidation
  .fil_dist = tab_filer_distribution      # likewise
)
```

# Next

**02-SelectSample** merges `FullMetaData.parquet` to Compustat and defines the descriptive and estimation samples. It is
a sibling of the classification and entity families rather than an ancestor: **03** reads this table directly for
contract classification, and **04** for named-entity extraction. All three filter on `Removed == 0`.
