---
title: "8-K Items and Item 1.01 Summaries (01D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01C owns the corpus traversal this document reuses, and the group vocabulary. Sourcing the chain
# rather than reimplementing either is what keeps one definition of how the corpus is walked.
purrr::walk(
  .x = c("01A-EdgarIndex", "01B-EdgarDocuments", "01C-EdgarMetaData"),
  .f = function(.s) {
    source(
      file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
      encoding = "UTF-8"
    )
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01D-Item101.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Two things, because they are the same fact read at two depths. Every 8-K declares which items it reports; that list is
parsed here into one row per filing and item, classified into voluntary, mandatory and exhibits, and published. An 8-K
reporting Item 1.01 also carries the filer's own summary of the agreement it has just entered into; that section is
located inside the filing's HTML and its text extracted.

The list is what decides which documents the extraction is attempted on, so the two were never separable. Before this
document owned both, the parse existed twice -- once here as a literal search over a pipe-joined string, once in 05B
with a real code parser and a different rule for filings whose registrants disagree. Two implementations of *which
filings report which items* is two answers, and the fact that they happened to agree on this corpus is luck rather
than design.

Regulation requires the 8-K within four business days of entering the agreement, but leaves the filer discretion over
whether to attach the contract itself then or defer it to the next periodic report. The summary is therefore the one
account of the agreement that always exists at the moment of entry, which is what makes it worth extracting separately
from the contract it describes.

## Why this is a 01-family script

It is a property of a document, derived by opening it, exactly like the word counts in 01C. Nothing about it depends on
which sample a document ends up in, so running it after sample selection would order it by accident rather than by
dependency.

That is a deliberate change from the arrangement it replaces, which filtered to the descriptive sample first. The flag
this produces now means one thing corpus-wide: an 8-K reporting Item 1.01 either has an extracted summary or has a
recorded reason why not, and never "was never attempted".

## Nothing is pre-filtered

Format is not a filter either. A document that is not markup is attempted with an anchor appropriate to plain text,
because a heading there is a heading by starting a line rather than by following a tag. Applying the markup anchor to a
text filing finds one or two boundaries in a document with six, and the first span then runs to the end of the filing.

Every candidate leaves exactly one row carrying one of eight outcomes, which is what makes the failure modes countable.

## Extracted is not the same as correct

Three of those outcomes exist because an earlier version counted their documents as successes.

Some filers set the item list as a table: numbers in one column, bodies in another. The document then reads, in both
the markup and the rendered text, as *"Item 1.01 Item 3.02 Entry into a Material Definitive Agreement Unregistered
Sales of Equity Securities"* -- every number, then every title, then the bodies. Slicing between adjacent markers
returns the few characters between two numbers, which is where thousands of nine-character summaries came from.

Those are now recorded as `heading-only` and not extracted. The test is on what remains after the item code and the
regulated title are removed, not on total length: the title is a fixed forty characters that says nothing about the
agreement, and a threshold on the whole string has to be guessed -- guessing it at fifty put two of the three shortest
extractions in the corpus exactly on the boundary. With the heading subtracted, a bare heading measures zero and a
one-sentence summary measures eighty-eight.

Taking the following span instead would return this item's body concatenated with the next item's, and for text
analysis contaminated text is worse than a known gap: a clean exclusion is countable, a silent error is not.

`markers-unparsed` separates a document with no boundaries from one whose boundaries carry no readable item code,
which happens when a filing agent wraps a heading across nested elements. The two look identical in a coverage
statistic and need different responses.

## Where the text goes

`Output/Item101.parquet` holds it, keyed on `DocID`. The register in 02 carries a flag and joins to this for the text.
Roughly a quarter of a million summaries is on the order of a gigabyte, and putting that in the register would make the
one table nobody can load.

The item tables are the opposite case. `Output/FilingItems.parquet` is one row per filing and item, keyed on
`HashIndex`; `Output/FilingItemFlags.parquet` is the same information collapsed to one row per filing, with the counts
and indicators an analysis asks for. Both are small, both are wanted on every row, and 02 joins the second onto the
register by `HashIndex` -- which is how a contract attachment comes to know what else its parent filing reported.

The item list is read from **01A's** landing table rather than 01C's. 01A holds every filing EDGAR indexed; 01C holds
only those carrying a retrieved Exhibit 10. The superset costs nothing at four million rows, and restricting it later
is a join whereas widening it later is a rebuild.

Anything a later script reads goes in `Output/`; anything existing only to make a re-render cheap goes in `Cache/`.

## What is recomputed, and what is not

Three steps take a `.rerun` argument defaulting to `FALSE`, and each fingerprints its inputs before deciding.

**Building the item tables** reads two and a third million landing rows and collapses four million item rows, which is
minutes rather than seconds. Both are a pure function of the landing table, the vocabulary and the parse rules, and all
three enter the fingerprint. Unlike the other two steps, this one reads its own output back rather than recomputing it,
because here the output is the expensive thing rather than a projection of it.

**Building the candidate set** reads 01C's consolidated table and 01B's index in full -- half a gigabyte of parquet --
to answer a question fixed by those two files, the item list and the item code. All four enter the fingerprint.

**Writing the summaries** is the gigabyte described above, and what it contains is a pure function of the extraction
cache and the candidate set. Only the write is guarded: the join that produces the table costs seconds and every report
below reads it, so skipping the computation would save nothing and would leave the reports describing a file rather
than an object.

The extraction pass itself is 01C's, and carries 01C's contract: it reconciles its cache against the candidate set
rather than trusting that a cache file exists, and measures whatever is not already covered.

The summary date heuristics are derived from the extraction cache rather than computed inside the worker. The pattern
that reads a contract date out of a summary is deliberately narrow and will be widened; putting a tunable rule behind a
corpus pass measured in hours is how a rule stops being tuned.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are deliberate and both
are the same decision. A runbook is read while it runs and pasted into discussion, where a monospaced block survives
being quoted into a mail or a chat window and a styled table does not.

The publication versions are produced once, at the end of the pipeline, by the consolidated release script: styled
tables from the same `tbl_out()` specifications, figure files from the same plotting functions.

# Configuration

```{r}
#| label: config
.dir_indx <- here::here("2_output", "01A-EdgarIndex")
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")
.dir_docs <- here::here("2_output", "01B-EdgarDocuments")

.lP <- list(
  Input = list(
    LandingAll = fs::path(.dir_indx, "Output", "LandingPageAll.parquet"),  # written by 01A, carries item lists
    MetaData   = fs::path(.dir_meta, "Output", "FullMetaData.parquet"),    # written by 01C
    FilePaths  = fs::path(.dir_docs, "Output", "FilePaths.parquet"),       # written by 01B
    # THE LOUGHRAN-MCDONALD UNCERTAINTY LIST, a versioned file rather than a package download.
    # Written once from tidytext::get_sentiments("loughran") -- the snippet is under *The summary as
    # text* -- and committed, so a render never reaches for the network.
    Lexicon    = "0_data/Lexicons/LM_Uncertainty.txt"
  ),
  Cache = list(
    Candidates  = utils_file_path(.dir_main, "Cache", "Candidates.parquet"),   # the documents to attempt
    Extracted   = utils_file_path(.dir_main, "Cache", "Extracted.parquet"),    # the pass over the corpus
    ItemStamp   = utils_file_path(.dir_main, "Cache", "ItemStamp.parquet"),    # guards the two item tables
    OutputStamp = utils_file_path(.dir_main, "Cache", "OutputStamp.parquet")   # guards the published summaries
  ),
  Output = list(
    FilingItems     = utils_file_path(.dir_main, "Output", "FilingItems.parquet"),      # filing x item
    FilingItemFlags = utils_file_path(.dir_main, "Output", "FilingItemFlags.parquet"),  # one row per filing
    Item101         = utils_file_path(.dir_main, "Output", "Item101.parquet")           # spans, outcomes and text
  ),
  Param = list(
    Item     = "1.01",   # the item denoting entry into a material definitive agreement
    MinChars = 30L,      # body characters, after the heading and title are removed
    Workers  = 24L       # parallel workers; also the number of chunks the pass is split into
  )
)

# Named individually so that a failure says which input is missing rather than that one of them is.
need_ <- unlist(.lP$Input)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

# Reported relative to the project root. An absolute path is correct on one machine and wrong on
# every other, and this page is published.
tibble::tibble(
  Input = names(need_),
  Path  = as.character(fs::path_rel(unname(need_), start = here::here()))
) |>
  tbl_out(.title = "Inputs")
```

# Items

Every 8-K declares which items it reports, and EDGAR publishes that list on the filing's landing page. Parsing it is
the first thing this document does, because the list is what decides which documents the extraction is attempted on,
and because nothing else in the pipeline holds 8-K items in a form anything can join to.

The vocabulary below is declared rather than derived. Forty-six codes: thirty-three from the form as reformed on 23
August 2004 and thirteen from the form before it, which is the complete legal vocabulary of each. A corpus-wide count
returns exactly these and one 1996 stray, and that is the check that the parser is reading codes rather than inventing
them.

`ItemKind` is the research decision in the file. Three kinds, not two. **Voluntary** is the registrant's choice of
whether and when: 2.02 and 7.01 are *furnished* rather than filed, which is the Section 18 safe harbour, and 8.01 is
filed but the rule says the registrant *may, at its option, disclose*. **Exhibits** is not a disclosure event at all --
it says the filing carries financial statements or exhibits -- and counting it as either of the others makes every
contract-bearing 8-K look one item busier than it is. **Mandatory** is everything triggered by an event outside the
registrant's control.

Item 2.02 is the contested one, and `ItemFurnished` exists so the argument can be had with a filter rather than a
re-read. It is required *once* the registrant announces results, but the announcement is discretionary, which is why
the bundling literature counts it as voluntary.

```{r}
#| label: report-vocabulary
.itm_items |>
  dplyr::select("ItemCode", "ItemEra", "ItemKind", "ItemFurnished", "ItemSuccessor", "ItemLabelShort") |>
  tbl_out(
    .title = "The item vocabulary",
    .notes = c(
      ItemKind       = "Voluntary, Mandatory or Exhibits. The pre-reform codes carry the kind of their successor.",
      ItemFurnished  = "Furnished rather than filed: the Section 18 safe harbour, and the narrower reading of voluntary.",
      ItemSuccessor  = "What a pre-reform code became in 2004. Item 13 has none; the reform did not carry it forward.",
      ItemLabelShort = "For tables only. The published data carries EDGAR's own label."
    )
  )
```

`ItemSuccessor` is what makes a count comparable across the reform at all. Four of the mappings decide the voluntary
measure: 5 becomes 8.01, 9 becomes 7.01, 12 becomes 2.02, and 7 becomes 9.01. Counting only the dotted codes -- which
is what a literal search for `Item 2.02` does -- returns zero for every filing before 23 August 2004, and an outcome
that is structurally zero before treatment measures the reform's numbering rather than anyone's behaviour.

## Reading the list

The landing table is keyed on filing **and registrant**, so a filing co-filed by forty-one affiliated entities appears
forty-one times carrying the same list. Collapsing before unnesting is not optional: skipping it multiplies every item
count by the number of registrants and reports a maximum of 205 items on a filing where the true maximum is 13.

Where registrants disagree the filing is dropped rather than one version being chosen, because there is no basis for
choosing and the alternative is a silent coin flip. In practice the rule never fires -- EDGAR generates the list once
per accession and stamps it on every registrant row, which is the same reason no code carries two label spellings --
but a guard whose firing count is reported costs nothing, and a guard that was never written costs a silent error.

```{r}
#| label: build-items
lst_items <- itm_build_items(
  .path_landing = .lP$Input$LandingAll,          # 01A, one row per filing and registrant
  .path_long    = .lP$Output$FilingItems,        # filing x item
  .path_flags   = .lP$Output$FilingItemFlags,    # one row per filing
  .path_stamp   = .lP$Cache$ItemStamp,           # fingerprint, and the build counts
  .rerun        = FALSE                          # TRUE rebuilds regardless of the fingerprint
)

tab_long  <- lst_items$Long
tab_flags <- lst_items$Flags

itm_report_build(.stats = lst_items$Stats)
```

The code is read with the pattern anchored at the head of the string, so whatever follows is the label and no colon is
ever split on. That matters more than it sounds: Item 5.02's regulated title carries two further colons, and splitting
on them turns one item into four.

`itm_item_flags()` collapses the long table to one row per filing, and it is where the era rule lives.
`nItemsVoluntary` counts 2.02, 7.01 and 8.01 on a post-reform filing and 12, 9 and 5 on a pre-reform one, because those
are the same three items under two numbering schemes. Classification is by code rather than by date: the code is what
the filer wrote and what EDGAR labelled, and the handful of filings where the two disagree are reported below rather
than reconciled silently.

It collapses them as run arithmetic rather than as a grouped summarise. Two million groups cost three and a half
minutes in dplyr, and no reformulation of the expressions moved it -- precomputing the indicators and summing plain
columns came out slower, because the per-group dispatch is the cost rather than the work. Since the long table is
sorted, a group is a run and a group sum is one difference of a cumulative sum: eight seconds, for an answer the gate
suite checks is identical to the version it replaced. `itm_runs()` asserts the contiguity that makes it valid rather
than assuming it.

Both tables are written here rather than under *Deployment*, and read back where the fingerprint says they are current.
That is a departure from how the rest of this document works, and the reason is that here the expensive step **is** the
output: building from the landing file is minutes, reading back is seconds, and a separate cache would be the same four
million rows stored twice. The vocabulary and the parse rules enter the fingerprint, so reclassifying a code rebuilds
both without anyone having to remember that no input file changed.

The counts above are stored beside the fingerprint, so the page reports the same numbers whether it built the tables or
read them. A published document that gets quieter as it gets faster is worse than a slow one.

## What the list says

```{r}
#| label: report-codes
tab_codes <- itm_code_table(.long = tab_long)

tab_codes |>
  tbl_out(
    .title = "Every code observed, against the vocabulary",
    .notes = c(
      pFilings  = "Share of filings carrying an item list, so the column sums above one hundred.",
      YearFirst = "Measured, not declared. Several codes postdate their own era: 12 arrives in 2003, 1.05 in 2023.",
      Status    = "unregistered means the vocabulary does not know it; registered, unseen means the corpus does not."
    )
  )
```

The first-seen column is the reason no effective dates are declared in the vocabulary. Item 12 does not exist before
2003, so even a correct pre-reform mapping gives a voluntary count that rises across 2001 to 2004 as the item itself
comes into being. Anything reading a pre-post difference off these counts has to answer that first.

```{r}
#| label: report-era
itm_era_cross(.long = tab_long) |>
  tbl_out(
    .title = "Item era against the side of the reform the filing fell on",
    .notes = c(
      FiledSide = "Which side of 23 August 2004 the filing date fell on. The era comes from the code.",
      nFilings  = "Rows where the two disagree are filers numbering by the wrong form, not a parsing error."
    )
  )
```

```{r}
#| label: report-per-filing
itm_items_per_filing(.flags = tab_flags) |>
  tbl_out(
    .title = "How many items a filing declares",
    .notes = c(nItems = "The maximum is what says whether a fixed-width reshape downstream is safe.")
  )
```

## Checks

```{r}
#| label: validate-items
itm_check_items(.long = tab_long, .flags = tab_flags, .codes = tab_codes) |>
  itm_report_checks(.title = "Item tables")
```

Two of these are worth reading rather than skimming. The unregistered-code check is **windowed to the sample period**:
one filing in 1996 reports `Item 57`, which is a filer error rather than a taxonomy, and stopping a render for it would
teach everyone to ignore the check that exists to catch the next real item -- Item 1.05 arrived in December 2023 and
the next one will arrive without warning. The row itself is kept, carries no era and no kind, and appears in the table
above.

*Every registered code is seen* is expected to pass on the full corpus and to fail on any subset of it, which is the
point: it is how you find out that a restricted frame is missing a taxonomy rather than missing filings.

# Candidates

Candidates are every 8-K document whose filing reports the item. Because the list is now parsed, the item is matched as
a **code** rather than as a substring of a joined string. The old rule searched for `1.01` literally; written as a
regular expression that pattern carries a wildcard in the middle and would also match `1101`, and written literally it
would match a filing reporting Item 11.01 if one existed. Neither case arises, but a rule that is accidentally right is
worth replacing with one that is right on purpose, and the parsed table makes it free.

```{r}
#| label: build-candidates
tab_candidates <- itm_candidates(
  .path_meta   = .lP$Input$MetaData,     # 01C's consolidated table
  .tab_items   = tab_long,               # one row per filing and item
  .path_index  = .lP$Input$FilePaths,    # DocID to Path, from 01B
  .item        = .lP$Param$Item,         # "1.01"
  .path_cache  = .lP$Cache$Candidates,   # candidate set and the fingerprint it was built under
  .rerun       = FALSE                   # TRUE rebuilds regardless of the fingerprint
)

nrow(tab_candidates)
```

# Extraction

The pass reuses 01C's corpus traversal: one function applied to every document, work sent to the workers in chunks
rather than one file at a time, and the result cached so a completed pass costs one parquet read. The first run opens
every candidate and is measured in hours.

Each worker is a fresh R session, so it is told to source this document's library before it measures anything, and the
item code reaches it as data rather than captured in a closure over a configuration list the worker does not have.

For each document: read the HTML with whitespace collapsed and the two entity spellings of a non-breaking space
replaced, locate every item boundary, take the one that is Item 1.01, and render that span as text.

The anchor depends on the format, because a heading is marked differently in each. In markup a heading follows a
closing tag, so the pattern is `>\s*ITEM`; without that anchor the word "item" inside a sentence -- and it appears
inside most agreements -- produces a boundary where there is none. In plain text there are almost no tags, so the same
anchor finds one or two boundaries in a document with six, and there a heading is a heading by starting a line.

The header window is stripped of tags before the item code is read, and every kind of space is replaced with a plain
one first. Filing agents set headings with typographic spacing -- thin, hair, en, em, narrow no-break -- written either
as entities or as the characters themselves, and to a pattern expecting whitespace between "Item" and its number every
one of them is an ordinary character. A thin space accounts for almost every unparsed heading filed after 2022.

The numeric ranges are enumerated rather than matched loosely, because a pattern wide enough to catch every space
reference in the U+2000 block also catches the curly quotation marks two positions above it, and those are content.

A signature block is located alongside the items because it terminates the last one; without it the final section would
run to the end of the document and swallow the exhibit index. Where no signature is found, the last span runs to the end
regardless: discarding it instead would lose any filing whose only boundary is the item itself, and extracting too much
is visible in the length distribution whereas extracting nothing leaves no trace.

```{r}
#| label: extract-items
tab_extracted <- edg_measure_corpus(
  .tab_idx  = tab_candidates,                          # the documents to attempt
  .path_out = .lP$Cache$Extracted,                     # cache; present means finished
  .fun      = itm_process_doc,                         # locate and render, one document
  .args     = list(.item = .lP$Param$Item,             # passed as data, not closed over
                   .min_chars = .lP$Param$MinChars),   # body chars below this: heading, not summary
  .sources  = .path_fun,                               # workers are fresh sessions; they source this library
  .workers  = .lP$Param$Workers,                       # parallel workers
  .label    = "Item 1.01 extraction",                  # shown in progress output
  .rerun    = FALSE                                    # FALSE measures only what the cache does not cover
)

nrow(tab_extracted)
```

```{r}
#| label: build-output
tab_item101 <- tab_extracted |>
  dplyr::left_join(
    y  = dplyr::select(tab_candidates, "DocID", "HashIndex", "YQ", "DocTypeMod", "Removed", "ItemCodes", "nItems"),
    by = dplyr::join_by("DocID")
  ) |>
  itm_summary_dates() |>
  itm_summary_measures(.lexicon = itm_read_lexicon(.path = .lP$Input$Lexicon)) |>
  itm_summary_attached(.path_meta = .lP$Input$MetaData) |>
  dplyr::relocate(
    "DocID", "HashIndex", "YQ", "DocTypeMod", "DocExt", "Removed", "Outcome", "ItemCodes", "nItems"
  )

nrow(tab_item101)
```

## The summary as text

Eight more columns, computed here because the text is in memory here and nowhere else needs to load
it. They are Table 7 of the paper: how long the summary is, how readable, how hedged, and how many
figures it carries. Counts are stored; a rate per thousand words is one division downstream.

The uncertainty list is Loughran and McDonald's. It reaches this document as a file of three hundred
words, written once by the call the old pipeline made at every render and never since:

```r
fs::dir_create("0_data/Lexicons")
tidytext::get_sentiments("loughran") |>
  dplyr::filter(sentiment == "uncertainty") |>
  dplyr::pull(word) |>
  readr::write_lines("0_data/Lexicons/LM_Uncertainty.txt")
```

That call needs `tidytext` and `textdata` and asks to download on first use, which is why it is run
by hand and its output committed rather than repeated inside a render.

`HasExhibit10` is the split that table is built on. An 8-K that announces an agreement either attaches
the contract or leaves it for the next periodic report, and only here -- where every summary is a row
whether or not a contract rode with it -- can the two be compared. A contract-level release sees only
the attached ones.

```{r}
#| label: build-measures-check
itm_measures_summary(.tab = tab_item101)
```

The published comparison had delayed summaries seventy-six words longer, more uncertain, and carrying
fewer numbers. If the two rows above do not show that ordering, the measures moved, not the paper.

`nItems` here is what the parent filing declares and `nCodesRead` is what this document's own headings yielded, which
are different numbers and used to share a name. `ItemCodes` replaces the pipe-joined label string the table used to
carry: the labels are a property of the code and live in `FilingItems.parquet`, so repeating them on a quarter of a
million rows bought nothing.

## How many agreements a summary describes

The paper restricts to *8-K filings containing exactly one contract summary within Item 1.01, excluding cases with
multiple concurrent agreements*. That restriction was implemented by counting distinct `On <Month> <D>, <YYYY>`
openings in the summary and keeping the ones with exactly one, because the regulated narrative opens that way.

It is a proxy for the number of agreements described rather than a count of them, and it is stored as a count rather
than applied as a filter. A filter here would make a summary that was excluded and a summary that was never extracted
indistinguishable downstream, which is the failure this document exists to avoid. The analysis that wants exactly one
keeps `SummaryIsSingle`; nothing else has to know.

```{r}
#| label: report-summary-dates
itm_summary_date_bands(.tab = tab_item101) |>
  tbl_out(
    .title = "Distinct agreement dates named in a recovered summary",
    .notes = c(
      nSummaryDates = "Zero means the narrative does not open the regulated way, not that no agreement is described.",
      pDocs         = "Share of recovered summaries. Failed outcomes carry no text and are excluded."
    )
  )
```

# Results

Six summaries, each computed once here and reused by every report, figure and overview below. The table they are
computed from carries the text of a quarter of a million summaries, so a summary derived twice is a second traversal of
a gigabyte to produce numbers that must agree with the first by construction.

```{r}
#| label: summarise-outcomes
tab_outcome_summary <- itm_outcome_summary(.tab = tab_item101)   # by HTML against everything else
tab_format_detail   <- itm_format_detail(.tab = tab_item101, .min = 50L)   # by actual extension
tab_length_summary  <- itm_length_summary(.tab = tab_item101)    # quartiles, by outcome
tab_length_bands    <- itm_length_bands(.tab = tab_item101)      # the plausibility bands
tab_outcome_year    <- itm_outcome_by_year(.tab = tab_item101)   # full breakdown per year
tab_coverage_year   <- itm_coverage_by_year(.tab = tab_item101)  # extracted share per year
```

```{r}
#| label: report-outcomes
itm_report_all(
  .tab_out  = tab_outcome_summary,   # summarised above; the Overview restates the same four
  .tab_fmt  = tab_format_detail,
  .tab_len  = tab_length_summary,
  .tab_band = tab_length_bands
)
```

The length comparison is the check on the longest-span rule. A filing with a table of contents lists Item 1.01 twice,
once as a line in the contents and once as the section itself, and an earlier implementation discarded those documents
entirely for being ambiguous. Taking the longest span keeps them, on the reasoning that a contents entry is a line and a
section is paragraphs. If that reasoning were wrong the ambiguous group would sit far below the unambiguous one.

## Extracted is not the same as correct

A span that renders is recorded as a success whatever it contains, and two failure modes survive that test. A summary of
a few dozen characters is a heading whose section is missing, which happens when the next marker sits immediately after
this one. A summary of a hundred thousand characters is a span that never terminated, which happens when no later
marker was found and the slice ran to the end of the filing.

Neither is visible in the outcome. The bands below are deliberately coarse -- they are meant to establish whether a
problem exists, not to fix a threshold -- and the examples show what sits at each end, because a count without an
example invites a cutoff to be chosen from the number rather than from the documents.

```{r}
#| label: report-lengths
tab_length_bands |>
  tbl_out(
    .title  = "Plausibility of the extracted lengths",
    .pct    = "Share",
    .digits = 1L
  )
```

```{r}
#| label: report-examples
itm_examples(.tab = tab_item101, .n = 3L, .chars = 160L) |>
  tbl_out(
    .title = "The shortest and longest extractions",
    .notes = c(Preview = "The first 160 characters, whitespace collapsed.")
  )
```

## Where the failures are

```{r}
#| label: report-format-detail
tab_format_detail |>
  tbl_out(
    .title  = "Outcomes by file extension",
    .pct    = "ShareExtracted",
    .digits = 1L,
    .notes  = c(Ext = "Formats below fifty documents are pooled. Attempted, not excluded.")
  )
```

```{r}
#| label: report-outcome-year
tab_outcome_year |>
  tbl_out(
    .title  = "Outcomes by year",
    .pct    = "ShareExtracted",
    .digits = 1L,
    .notes  = c(
      NoMarkers = "No item boundary found at all: a change in filing format rather than in behaviour.",
      NotFound  = "Boundaries found but none of them this item: a change in what filers report."
    )
  )
```

A year that falls because documents stopped carrying item markers is a change in filing format; one that falls because
the markers are present but Item 1.01 is not among them is a change in what filers report. They need different
responses, and the share alone distinguishes neither.

# Validation

Three checks. Each states its expectation first, so a result that differs is a finding rather than a number to
interpret afterwards.

```{r}
#| label: validate-extraction
# 1. Every candidate should leave exactly one row: the pass is one row in, one row out.
# 2. DocID identifies a document, so it should be unique.
# 3. An extracted row must carry text and a span; a failed row must carry neither. A row with an
#    outcome of extracted and no text would mean the outcome is not describing what happened.
tibble::tibble(
  nCandidates    = nrow(tab_candidates),
  nRows          = nrow(tab_item101),
  DuplicateDocID = sum(duplicated(tab_item101$DocID)),
  ExtractedNoText = sum(
    tab_item101$Outcome %in% c("extracted", "ambiguous-longest") & is.na(tab_item101$ItemText)
  ),
  FailedWithText = sum(
    !tab_item101$Outcome %in% c("extracted", "ambiguous-longest") & !is.na(tab_item101$ItemText)
  )
) |>
  tbl_out(
    .title = "Extraction consistency",
    .notes = c(
      nRows           = "Must equal nCandidates: one row in, one row out, whatever the outcome.",
      ExtractedNoText = "Nonzero means an outcome claims a success the row does not carry."
    )
  )
```

# Deployment

Three artifacts, of which two are already on disk: `Output/FilingItems.parquet` and
`Output/FilingItemFlags.parquet` were written under *Items*, for the reason given there.
`Output/Item101.parquet` is written here, and carries one row per candidate document: the outcome, the span if one was
found, and the text if it was rendered.

02B reads the flags table by `HashIndex`, which is what puts the parent filing's item counts on every attachment
including the Exhibit 10s, and it reads the summaries by `DocID` to mark whether one was extracted. Nothing here writes
into another script's output, and nothing writes back into this one.

The write is guarded and the checks above are not. A gigabyte is not rewritten to produce a file that already holds the
same rows, but nothing is left unverified on that account: every number on this page was computed from the table in
memory, and the fingerprint below records what the file on disk was built from.

```{r}
#| label: deploy-item101
itm_write_item101(
  .tab         = tab_item101,           # the joined table, one row per candidate
  .path_out    = .lP$Output$Item101,    # the published artifact
  .path_source = .lP$Cache$Extracted,   # the extraction cache it derives from
  .path_stamp  = .lP$Cache$OutputStamp, # fingerprint the file was last written under
  .rerun       = FALSE                  # TRUE writes regardless of the fingerprint
)
```

Nothing else is written. No figure files, no styled tables: those are the release script's job, for the reason set out
under *How results are reported*.

```{r}
#| label: deploy-report
fs::file_info(path = c(unlist(.lP$Output), unlist(.lP$Cache))) |>
  dplyr::transmute(
    Kind    = c(rep("Output", length(.lP$Output)), rep("Cache", length(.lP$Cache))),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output row is read downstream; the rest make a re-render cheap.",
      Written = "A cache older than this render means that step found its input unchanged."
    )
  )
```

# Overview

```{r}
#| label: fig-coverage
#| fig-height: 3.4
#| fig-cap: "Item 1.01 extraction per calendar year, split into documents whose summary was recovered
#|   and those where it was not. The early years are thin because the item structure that makes a
#|   material-agreement report identifiable dates from the 2004 reform."
itm_plot_coverage(.tab = tab_coverage_year)   # summarised in Results; the release script writes the file
```

```{r}
#| label: fig-outcome-share
#| fig-height: 3.4
#| fig-cap: "How the outcomes compose each year, as shares. Filing volume varies fourfold across the
#|   period, so counts would show that rather than what is being asked."
itm_plot_outcome_share(.tab = tab_outcome_year)   # summarised in Results
```

```{r}
#| label: fig-length
#| fig-height: 3.4
#| fig-cap: "Distribution of summary length, on a log scale because the range spans four orders of
#|   magnitude. The mass below a few hundred characters and the tail beyond a hundred thousand are
#|   the two failure modes that pass the outcome test."
itm_plot_length(.tab = tab_item101)   # the only figure needing the row-level table
```

```{r}
#| label: overview-all
itm_report_all(
  .tab_out  = tab_outcome_summary,   # summarised once in Results
  .tab_fmt  = tab_format_detail,
  .tab_len  = tab_length_summary,
  .tab_band = tab_length_bands
)
```

# Known limits

The date heuristic is the weakest thing on this page, and it is worth being precise about how weak.
Of the recovered summaries, roughly one in six names no date the pattern reads. A probe over twenty
thousand of those measured where the gap is, and the answer splits three ways.

**The narrative opens some other way.** A case-insensitive `on` would catch 37.7% of the bucket on
its own -- the date arrives mid-sentence, as in *the Company entered into a lease on April 9, 2015*
-- and `effective`, `dated` or `as of` would catch 48.5%. Those two do almost all of the available
work: relaxing further, to abbreviated months, ordinal days, day-before-month, numeric dates and
*the 15th day of July*, adds one percentage point between them.

**The section is a pointer rather than a summary.** Every one of the eight hardest misses sampled
read some version of *The information set forth in Item 3.02 below is incorporated herein by
reference*. The filer reported Item 1.01 and put the substance in a different item of the same 8-K.
That is a third failure mode passing the outcome test, alongside the two under *Extracted is not the
same as correct*, and no date pattern will ever read it because there is no date to read.

**The summary genuinely names no date.** 68.6% of the bucket contains a four-digit year anywhere in
the text and 66.7% a month-name date, so about a third of it names nothing datelike at all. The
relaxations above reach 63.9% against that 66.7% ceiling, which is the useful thing the probe
established: the pattern is not the binding constraint for most of what is left.

## Why it was not widened

Two reasons, and the second is the stronger one.

The narrow pattern is what the published filter used, so leaving it alone keeps that filter exactly
reproducible.

More importantly, a broader pattern reads dates that are not the agreement date. One sampled summary
opens *0.25% Convertible Senior Notes due 2023. On the Closing Date, Zendesk and Wil...* -- the
narrative gives no date at all, and the only month-name date in the text belongs to the instrument's
maturity. Since the count is a proxy for how many agreements a summary describes, a match like that
does not fix a zero; it manufactures a one. And a document can move from one date to two as readily
as from zero to one, so widening shrinks the sample the published filter keeps at the same time as
it grows it. Which way the net falls is not knowable without measuring it, and measuring it is not
what this script is for.

The count is stored rather than applied, so none of this is load-bearing here: an analysis that
wants a different rule reads `ItemText` and applies it. What would help more than a wider pattern is
a measured column separating the pointer case from the genuinely dateless one, which is a rule about
cross-references rather than about dates, and is not built.

## A few, as they are

```{r}
#| label: report-summary-examples
itm_summary_examples(.tab = tab_item101, .n = 4L) |>
  tbl_out(
    .title = "Summaries at each date count, with what the current pattern matched",
    .notes = c(
      Dates   = "Sampled on a fixed seed, so this table is the same on a re-render.",
      Match   = "Two dashes mean the pattern found nothing; the preview says whether that is fair.",
      Preview = "The item heading and regulated title are stripped -- every summary carries the same forty characters."
    )
  )
```

# Next

**01E-CtoExhibits** does the equivalent for confidential-treatment orders: extracts the exhibit references each order
names and links them back to the contracts they cover.

**02-SelectSample** reads both outputs: the flags table by `HashIndex`, so every register row carries what its parent
filing reported, and the summaries by `DocID`, so every 8-K report row carries whether one was recovered.

**05B-ItemTaxonomy** becomes a consumer of `FilingItems.parquet` rather than a second parser of the same landing table.
Its argument about what the 2004 reform moved is unchanged; what changes is that the numbers behind it now come from
the pipeline rather than from a parse that exists only in that document.
