---
title: "8-K Item 1.01 Summaries (01D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01C owns the corpus traversal this document reuses, and the group vocabulary. Sourcing the chain
# rather than reimplementing either is what keeps one definition of how the corpus is walked.
purrr::walk(
  .x = c("01A-EdgarIndex", "01B-EdgarDocuments", "01C-EdgarMetaData"),
  .f = function(.s) {
    source(
      file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
      encoding = "UTF-8"
    )
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01D-Item101.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

An 8-K reporting Item 1.01 carries the filer's own summary of a material agreement it has just entered into. This
locates that section inside the filing's HTML and extracts its text.

Regulation requires the 8-K within four business days of entering the agreement, but leaves the filer discretion over
whether to attach the contract itself then or defer it to the next periodic report. The summary is therefore the one
account of the agreement that always exists at the moment of entry, which is what makes it worth extracting separately
from the contract it describes.

## Why this is a 01-family script

It is a property of a document, derived by opening it, exactly like the word counts in 01C. Nothing about it depends on
which sample a document ends up in, so running it after sample selection would order it by accident rather than by
dependency.

That is a deliberate change from the arrangement it replaces, which filtered to the descriptive sample first. The flag
this produces now means one thing corpus-wide: an 8-K reporting Item 1.01 either has an extracted summary or has a
recorded reason why not, and never "was never attempted".

## Nothing is pre-filtered

Format is not a filter either. A document that is not markup is attempted with an anchor appropriate to plain text,
because a heading there is a heading by starting a line rather than by following a tag. Applying the markup anchor to a
text filing finds one or two boundaries in a document with six, and the first span then runs to the end of the filing.

Every candidate leaves exactly one row carrying one of eight outcomes, which is what makes the failure modes countable.

## Extracted is not the same as correct

Three of those outcomes exist because an earlier version counted their documents as successes.

Some filers set the item list as a table: numbers in one column, bodies in another. The document then reads, in both
the markup and the rendered text, as *"Item 1.01 Item 3.02 Entry into a Material Definitive Agreement Unregistered
Sales of Equity Securities"* -- every number, then every title, then the bodies. Slicing between adjacent markers
returns the few characters between two numbers, which is where thousands of nine-character summaries came from.

Those are now recorded as `heading-only` and not extracted. The test is on what remains after the item code and the
regulated title are removed, not on total length: the title is a fixed forty characters that says nothing about the
agreement, and a threshold on the whole string has to be guessed -- guessing it at fifty put two of the three shortest
extractions in the corpus exactly on the boundary. With the heading subtracted, a bare heading measures zero and a
one-sentence summary measures eighty-eight.

Taking the following span instead would return this item's body concatenated with the next item's, and for text
analysis contaminated text is worse than a known gap: a clean exclusion is countable, a silent error is not.

`markers-unparsed` separates a document with no boundaries from one whose boundaries carry no readable item code,
which happens when a filing agent wraps a heading across nested elements. The two look identical in a coverage
statistic and need different responses.

## Where the text goes

`Item101.parquet` holds it, keyed on `DocID`. The register in 02 carries a flag and joins to this for the text. Roughly
a quarter of a million summaries is on the order of a gigabyte, and putting that in the register would make the one
table nobody can load.

# Configuration

```{r}
#| label: config
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")
.dir_docs <- here::here("2_output", "01B-EdgarDocuments")

.lP <- list(
  Input = list(
    MetaData    = fs::path(.dir_meta, "FullMetaData.parquet"),   # written by 01C
    LandingPage = fs::path(.dir_meta, "LandingPage.parquet"),    # written by 01C, carries the item lists
    FilePaths   = fs::path(.dir_docs, "FilePaths.parquet")       # written by 01B
  ),
  Cache = list(
    Extracted = utils_file_path(.dir_main, "Cache", "Extracted.parquet")   # the pass over the corpus
  ),
  Output = list(
    Item101 = utils_file_path(.dir_main, "Item101.parquet"),   # spans, outcomes and text
    Figures = utils_file_path(.dir_main, "Figures")            # figure files for the manuscript
  ),
  Param = list(
    Item     = "1.01",   # the item denoting entry into a material definitive agreement
    MinChars = 30L,      # body characters, after the heading and title are removed
    Workers  = 24L       # parallel workers; also the number of chunks the pass is split into
  )
)

# Named individually so that a failure says which input is missing rather than that one of them is.
need_ <- unlist(.lP$Input)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

tibble::tibble(Input = names(need_), Path = unname(need_)) |> tbl_out(.title = "Inputs")
```

# Candidates

The item list lives on the landing table, at one row per filing and registrant, so a filing's items appear once per
registrant. Where every registrant agrees the row is kept; where they do not the filing is dropped rather than one
version being chosen, because there is no basis for choosing and the alternative is a silent coin flip on the variable
that decides what gets extracted.

02 needs the same rule and sources it from here rather than restating it.

```{r}
#| label: build-items
tab_items <- itm_filing_items(.path_landing = .lP$Input$LandingPage)

nrow(tab_items)
```

Candidates are every 8-K document whose filing reports the item. The code is matched literally: written as a regular
expression it carries a wildcard in the middle and would also match `1101`, and although no item code has that shape,
a rule that is accidentally loose is worth not carrying forward.

```{r}
#| label: build-candidates
tab_candidates <- itm_candidates(
  .path_meta   = .lP$Input$MetaData,     # 01C's consolidated table
  .tab_items   = tab_items,              # filings whose registrants agree on the item list
  .path_index  = .lP$Input$FilePaths,    # DocID to Path, from 01B
  .item        = .lP$Param$Item          # "1.01"
)

nrow(tab_candidates)
```

# Extraction

The pass reuses 01C's corpus traversal: one function applied to every document, work sent to the workers in chunks
rather than one file at a time, and the result cached so a completed pass costs one parquet read. The first run opens
every candidate and is measured in hours.

Each worker is a fresh R session, so it is told to source this document's library before it measures anything, and the
item code reaches it as data rather than captured in a closure over a configuration list the worker does not have.

For each document: read the HTML with whitespace collapsed and the two entity spellings of a non-breaking space
replaced, locate every item boundary, take the one that is Item 1.01, and render that span as text.

The anchor depends on the format, because a heading is marked differently in each. In markup a heading follows a
closing tag, so the pattern is `>\s*ITEM`; without that anchor the word "item" inside a sentence -- and it appears
inside most agreements -- produces a boundary where there is none. In plain text there are almost no tags, so the same
anchor finds one or two boundaries in a document with six, and there a heading is a heading by starting a line.

The header window is stripped of tags before the item code is read, and every kind of space is replaced with a plain
one first. Filing agents set headings with typographic spacing -- thin, hair, en, em, narrow no-break -- written either
as entities or as the characters themselves, and to a pattern expecting whitespace between "Item" and its number every
one of them is an ordinary character. A thin space accounts for almost every unparsed heading filed after 2022.

The numeric ranges are enumerated rather than matched loosely, because a pattern wide enough to catch every space
reference in the U+2000 block also catches the curly quotation marks two positions above it, and those are content.

A signature block is located alongside the items because it terminates the last one; without it the final section would
run to the end of the document and swallow the exhibit index. Where no signature is found, the last span runs to the end
regardless: discarding it instead would lose any filing whose only boundary is the item itself, and extracting too much
is visible in the length distribution whereas extracting nothing leaves no trace.

```{r}
#| label: extract-items
tab_extracted <- edg_measure_corpus(
  .tab_idx  = tab_candidates,                          # the documents to attempt
  .path_out = .lP$Cache$Extracted,                     # cache; present means finished
  .fun      = itm_process_doc,                         # locate and render, one document
  .args     = list(.item = .lP$Param$Item,             # passed as data, not closed over
                   .min_chars = .lP$Param$MinChars),   # body chars below this: heading, not summary
  .sources  = .path_fun,                               # workers are fresh sessions; they source this library
  .workers  = .lP$Param$Workers,                       # parallel workers
  .label    = "Item 1.01 extraction"                   # shown in progress output
)

nrow(tab_extracted)
```

```{r}
#| label: build-output
tab_item101 <- tab_extracted |>
  dplyr::left_join(
    y  = dplyr::select(tab_candidates, "DocID", "HashIndex", "YQ", "DocTypeMod", "Removed", "Items"),
    by = dplyr::join_by("DocID")
  ) |>
  dplyr::relocate("DocID", "HashIndex", "YQ", "DocTypeMod", "DocExt", "Removed", "Outcome", "Items")

arrow::write_parquet(tab_item101, .lP$Output$Item101)
nrow(tab_item101)
```

# Results

```{r}
#| label: report-outcomes
itm_report_all(.tab = tab_item101)
```

The length comparison is the check on the longest-span rule. A filing with a table of contents lists Item 1.01 twice,
once as a line in the contents and once as the section itself, and an earlier implementation discarded those documents
entirely for being ambiguous. Taking the longest span keeps them, on the reasoning that a contents entry is a line and a
section is paragraphs. If that reasoning were wrong the ambiguous group would sit far below the unambiguous one.

## Extracted is not the same as correct

A span that renders is recorded as a success whatever it contains, and two failure modes survive that test. A summary of
a few dozen characters is a heading whose section is missing, which happens when the next marker sits immediately after
this one. A summary of a hundred thousand characters is a span that never terminated, which happens when no later
marker was found and the slice ran to the end of the filing.

Neither is visible in the outcome. The bands below are deliberately coarse -- they are meant to establish whether a
problem exists, not to fix a threshold -- and the examples show what sits at each end, because a count without an
example invites a cutoff to be chosen from the number rather than from the documents.

```{r}
#| label: report-lengths
itm_length_bands(.tab = tab_item101) |>
  tbl_out(
    .title  = "Plausibility of the extracted lengths",
    .pct    = "Share",
    .digits = 1L
  )
```

```{r}
#| label: report-examples
itm_examples(.tab = tab_item101, .n = 3L, .chars = 160L) |>
  tbl_out(
    .title = "The shortest and longest extractions",
    .notes = c(Preview = "The first 160 characters, whitespace collapsed.")
  )
```

## Where the failures are

```{r}
#| label: report-format-detail
itm_format_detail(.tab = tab_item101, .min = 50L) |>
  tbl_out(
    .title  = "Outcomes by file extension",
    .pct    = "ShareExtracted",
    .digits = 1L,
    .notes  = c(Ext = "Formats below fifty documents are pooled. Attempted, not excluded.")
  )
```

```{r}
#| label: report-outcome-year
itm_outcome_by_year(.tab = tab_item101) |>
  tbl_out(
    .title  = "Outcomes by year",
    .pct    = "ShareExtracted",
    .digits = 1L,
    .notes  = c(
      NoMarkers = "No item boundary found at all: a change in filing format rather than in behaviour.",
      NotFound  = "Boundaries found but none of them this item: a change in what filers report."
    )
  )
```

A year that falls because documents stopped carrying item markers is a change in filing format; one that falls because
the markers are present but Item 1.01 is not among them is a change in what filers report. They need different
responses, and the share alone distinguishes neither.

# Validation

Three checks. Each states its expectation first, so a result that differs is a finding rather than a number to
interpret afterwards.

```{r}
#| label: validate-extraction
# 1. Every candidate should leave exactly one row: the pass is one row in, one row out.
# 2. DocID identifies a document, so it should be unique.
# 3. An extracted row must carry text and a span; a failed row must carry neither. A row with an
#    outcome of extracted and no text would mean the outcome is not describing what happened.
tibble::tibble(
  nCandidates    = nrow(tab_candidates),
  nRows          = nrow(tab_item101),
  DuplicateDocID = sum(duplicated(tab_item101$DocID)),
  ExtractedNoText = sum(
    tab_item101$Outcome %in% c("extracted", "ambiguous-longest") & is.na(tab_item101$ItemText)
  ),
  FailedWithText = sum(
    !tab_item101$Outcome %in% c("extracted", "ambiguous-longest") & !is.na(tab_item101$ItemText)
  )
) |>
  tbl_out(
    .title = "Extraction consistency",
    .notes = c(
      nRows           = "Must equal nCandidates: one row in, one row out, whatever the outcome.",
      ExtractedNoText = "Nonzero means an outcome claims a success the row does not carry."
    )
  )
```



# Deployment

`Item101.parquet` is the only artifact of this script. It carries one row per candidate document: the outcome, the span
if one was found, and the text if it was rendered.

02B reads it to mark each document in the register with whether a summary was extracted, and joins to it for the text
itself. It also carries the filing's item list, so 02B reads that rather than restating the rule for deduplicating it.
Nothing here writes into another script's output, and nothing writes back into this one.

```{r}
#| label: deploy-report
fs::file_info(.lP$Output$Item101) |>
  dplyr::select("path", "size") |>
  tbl_out(.title = "Written")
```

# Overview

```{r}
#| label: fig-coverage
#| fig-height: 3.4
#| fig-cap: "Item 1.01 extraction per calendar year, split into documents whose summary was recovered
#|   and those where it was not. The early years are thin because the item structure that makes a
#|   material-agreement report identifiable dates from the 2004 reform."
gg_coverage <- itm_plot_coverage(.tab = itm_coverage_by_year(.tab = tab_item101))

plot_save(
  .plot    = gg_coverage,               # the figure
  .name    = "item101-coverage",        # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_coverage
```

```{r}
#| label: fig-outcome-share
#| fig-height: 3.4
#| fig-cap: "How the outcomes compose each year, as shares. Filing volume varies fourfold across the
#|   period, so counts would show that rather than what is being asked."
gg_share <- itm_plot_outcome_share(.tab = itm_outcome_by_year(.tab = tab_item101))

plot_save(
  .plot    = gg_share,                  # the figure
  .name    = "item101-outcome-share",   # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_share
```

```{r}
#| label: fig-length
#| fig-height: 3.4
#| fig-cap: "Distribution of summary length, on a log scale because the range spans four orders of
#|   magnitude. The mass below a few hundred characters and the tail beyond a hundred thousand are
#|   the two failure modes that pass the outcome test."
gg_length <- itm_plot_length(.tab = tab_item101)

plot_save(
  .plot    = gg_length,                 # the figure
  .name    = "item101-length",          # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a distribution is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_length
```

```{r}
#| label: overview-all
itm_report_all(.tab = tab_item101)
```

# Next

**01E-CtoExhibits** does the equivalent for confidential-treatment orders: extracts the exhibit references each order
names and links them back to the contracts they cover.

**02-SelectSample** reads this to mark the register, and sources `itm_filing_items()` rather than restating the rule
for deduplicating item lists.
