---
title: "Confidential-Treatment Orders (01E)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01C owns the corpus traversal this document reuses. Sourcing the chain rather than reimplementing
# it is what keeps one definition of how the corpus is walked.
purrr::walk(
  .x = c("01A-EdgarIndex", "01B-EdgarDocuments", "01C-EdgarMetaData"),
  .f = function(.s) {
    source(
      file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
      encoding = "UTF-8"
    )
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01E-CtoExhibits.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

A confidential-treatment order is a letter from the SEC granting a filer permission to withhold parts of an exhibit from
public view, for a stated period. Until 2019 a filer wanting to redact a material contract had to apply for one, so the
orders are the only direct record of what redaction removed and of when it was due to become public.

This parses those letters and links each exhibit reference back to the contract it covers.

## It is a join, not a matching problem

The letters are a generated form. One template, unchanged from 2008 to 2024; ninety-six per cent name the source form
type, ninety-eight the source filing date. So the link is `CIK` plus form plus filing date into the master index, then
exhibit number into that filing. Two exact hops, no fuzzy matching.

That matters because the alternative is expensive. An earlier approach re-downloaded each order as a PDF from the SEC
and extracted its text, which meant fighting an extractor that inserts spaces inside words -- patterns written as
`F\s*i\s*l\s*e` rather than `File`, and nine variants of the exhibit pattern to cover what the spacing broke. 01B
already parsed these documents once, and the text carries no such damage: a thousand orders read in under three
seconds.

## The reference formats, and why order matters

Most orders list `Exhibit 10.15 through December 31, 2016` and name the source filing once, in the opening paragraph.
A minority name it per exhibit instead, either inline or as a small table, and those are precisely the orders covering
exhibits from more than one filing.

So the per-reference formats are tried first. Reading one of those orders with the general pattern would attach every
exhibit to whichever filing the opening paragraph happened to name, which for these orders is one of several -- an error
that produces a confident and wrong link rather than a visible failure.

## Status comes from the title

`ORDER GRANTING CONFIDENTIAL TREATMENT` is the title line and says what the order does. Searching the body for "amend"
instead finds `to a Form 10-K filed on August 23, 2018, as amended`, which describes the source filing; on this corpus
that mistake marks a fifth of plain grants as amendments. The two are recorded separately.

Denials are rare -- roughly three in a thousand -- and matter out of proportion to that: the filer applied to withhold
and was refused, and therefore had to disclose.

## Nothing is dropped

Every reference that parses is kept, with the point at which its chain broke recorded: not an Exhibit 10, source filing
not named, filing not in the index, filing ambiguous, exhibit not in the filing, exhibit ambiguous, linked. An
unresolved reference is a countable quantity; a discarded one is not.

# Configuration

```{r}
#| label: config
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")
.dir_docs <- here::here("2_output", "01B-EdgarDocuments")

.lP <- list(
  Input = list(
    MetaData  = fs::path(.dir_meta, "FullMetaData.parquet"),                         # written by 01C
    Mirror    = here::here("2_output", "01A-EdgarIndex", "GetEDGAR"),                # 01A's mirror
    FilePaths = fs::path(.dir_docs, "FilePaths.parquet")                             # written by 01B
  ),
  Cache = list(
    Parsed = utils_file_path(.dir_main, "Cache", "Parsed.parquet")   # the pass over the orders
  ),
  Output = list(
    CtoExhibits = utils_file_path(.dir_main, "CtoExhibits.parquet"),   # one row per reference
    Figures     = utils_file_path(.dir_main, "Figures")                # figure files for the manuscript
  ),
  Param = list(
    Workers   = 8L,   # the orders are a kilobyte each; more would cost more to start than to use
    Tolerance = 3L    # days either side, where no filing matches the date exactly
  )
)

# Named individually so that a failure says which input is missing rather than that one of them is,
# and checked before the mirror is resolved so an absent mirror is reported here rather than by
# whatever tries to read it first. One of these is a directory, so both kinds of existence count.
need_ <- unlist(.lP$Input)
miss_ <- need_[!fs::file_exists(need_) & !fs::dir_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

# The master index comes from 01A's mirror, unrestricted. 01C also publishes one, filtered to
# filings whose documents were retrieved -- two and a half per cent of EDGAR -- and joining against
# that would make every filing we hold no documents from look as though EDGAR had never heard of it.
.lP$Edgar <- rGetEDGAR::get_directories(.lP$Input$Mirror)

tibble::tibble(Input = names(need_), Path = unname(need_)) |> tbl_out(.title = "Inputs")
```

# The orders

```{r}
#| label: load-orders
tab_orders <- arrow::open_dataset(sources = .lP$Input$MetaData) |>
  dplyr::filter(grepl("^CTO", .data$DocTypeMod)) |>
  dplyr::select("DocID", "HashIndex", "CIK", "CompanyName", "DateFiled", "YQ", "Removed") |>
  dplyr::collect() |>
  dplyr::left_join(
    y  = dplyr::select(arrow::read_parquet(.lP$Input$FilePaths), "DocID", "Path"),
    by = dplyr::join_by("DocID")
  )

nrow(tab_orders)
```

The volume of orders is itself a result. They run at roughly thirteen hundred a year through 2018 and then collapse:
the 2019 FAST Act amendments let a filer redact immaterial competitively-harmful information without applying at all.
Any analysis spanning that change is looking at two different disclosure regimes, and a reader seeing two dozen orders
in a recent year should see the reason rather than infer a data problem.

```{r}
#| label: report-volume
tab_orders |>
  dplyr::mutate(Year = as.integer(format(.data$DateFiled, "%Y"))) |>
  dplyr::summarise(nOrders = dplyr::n(), nFilers = dplyr::n_distinct(.data$CIK), .by = "Year") |>
  dplyr::arrange(.data$Year) |>
  tbl_out(
    .title = "Orders per year",
    .notes = c(nOrders = "The fall after 2018 is the FAST Act, not attrition in the data.")
  )
```

# Parsing

One pass over the orders, reusing 01C's traversal. Unlike the passes there, this one returns several rows per document
-- one per exhibit reference -- so the traversal is told to check that every order is accounted for rather than that
every order produced exactly one row.

```{r}
#| label: parse-orders
tab_parsed <- edg_measure_corpus(
  .tab_idx  = tab_orders,             # the orders to parse
  .path_out = .lP$Cache$Parsed,       # cache; present means finished
  .fun      = cto_parse_order,        # order-level fields plus one row per reference
  .sources  = .path_fun,              # workers are fresh sessions; they source this library
  .workers  = .lP$Param$Workers,      # parallel workers
  .label    = "CTO parsing",          # shown in progress output
  .rows     = "many"                  # one order yields one row per exhibit it names
)

nrow(tab_parsed)
```

```{r}
#| label: join-orders
tab_refs <- tab_parsed |>
  dplyr::left_join(
    y  = dplyr::select(tab_orders, "DocID", "HashIndex", "CIK", "CompanyName", "DateFiled", "YQ"),
    by = dplyr::join_by("DocID")
  ) |>
  dplyr::relocate("DocID", "CIK", "DateFiled", "Status", "RefFormat", "ExhibitNo", "ReleaseDate")

c(orders = dplyr::n_distinct(tab_refs$DocID), references = sum(!is.na(tab_refs$ExhibitNo)))
```

# Linking

The filing side of the join, against **every filing EDGAR published** rather than only those we hold documents from.
That distinction is not pedantic: the restricted index is two and a half per cent of the full one, and joining against
it reported half of its failures as filings EDGAR had never heard of when they were indexed all along. What we lack in
those cases is the exhibit, not the filing, and the two are separate limits.

A filer can lodge two filings of the same type on the same day, so `CIK` plus form plus date does not always identify
one. Where it does not, the reference is left unresolved and counted: taking the first candidate would produce a link
indistinguishable from a correct one and right about half the time.

Some orders quote the date a filing was accepted rather than the date the index records, which differs by a day either
side. An exact match is preferred; where there is none, a filing within three days is accepted only if it is the only
one, and the fact that a tolerance was used is recorded so its effect can be measured and switched off.

Using the full index also exposes ambiguity the restricted one hid, since a filer lodging two filings of a type on one
day had only one of them in the restricted index. That is worth exposing -- but a reference to an exhibit can only
resolve to a filing whose exhibits exist, so where exactly one candidate has any, the choice is determined rather than
guessed. Where two do, the reference stays ambiguous.

```{r}
#| label: link-filing
tab_master <- arrow::open_dataset(sources = .lP$Edgar$MasterIndex$DirParquet) |>
  dplyr::select("CIK", "FormType", "DateFiled", "HashIndex") |>
  dplyr::collect() |>
  dplyr::distinct()

# Built before the filing hop rather than after it, because which filings hold exhibits is what
# breaks a tie between two filings of the same type on the same day.
tab_exhibits <- arrow::open_dataset(sources = .lP$Input$MetaData) |>
  dplyr::filter(grepl("^Exhibit10", .data$DocTypeMod)) |>
  dplyr::select("DocID", "HashIndex", "DocTypeRaw") |>
  dplyr::collect() |>
  dplyr::mutate(ExhibitNo = cto_exhibit_number(.x = .data$DocTypeRaw))

tab_linked <- cto_link_filing(
  .tab_ref   = dplyr::select(tab_refs, -"HashIndex"),   # the order's own filing is not the target
  .tab_mst   = tab_master,                              # every filing EDGAR published, not just ours
  .hash_docs = unique(tab_exhibits$HashIndex),          # filings we hold exhibits from, for the tie-break
  .tolerance = .lP$Param$Tolerance                      # days either side where no date matches
)

c(
  before      = nrow(tab_refs),
  after       = nrow(tab_linked),
  duplicates  = nrow(tab_refs) - nrow(tab_linked),   # orders listing one exhibit twice, identically
  oneFiling   = mean(tab_linked$nFilings == 1L)
)
```

The exhibit side. The order writes `10.1` and the filing side writes `EX-10.1`, so both are reduced to the bare number.
An unnumbered `EX-10` reduces to `10` and cannot match a numbered reference, which is the right outcome: the order named
a specific exhibit and the filer did not number one.

```{r}
#| label: link-document
tab_cto <- cto_link_document(.tab_ref = tab_linked, .tab_docs = tab_exhibits)

arrow::write_parquet(tab_cto, .lP$Output$CtoExhibits)
nrow(tab_cto)
```

# Results

```{r}
#| label: report-all
cto_report_all(.tab = tab_cto)
```

```{r}
#| label: report-linkage-year
cto_link_by_year(.tab = tab_cto) |>
  tbl_out(
    .title  = "Linkage by year of the order",
    .pct    = "ShareLinked",
    .digits = 1L,
    .notes  = c(ShareLinked = "A fall in one year is a change in how orders were written, not in \\
                               how many contracts were redacted.")
  )
```

# Validation

Four checks. Each states its expectation first, so a result that differs is a finding rather than a number to interpret
afterwards.

```{r}
#| label: validate-parse
# 1. Every order should be accounted for, whether or not any reference parsed.
# 2. A linked reference must carry a contract identifier, and an unlinked one must not: a status
#    that claims a resolution the row does not carry is worse than no status.
# 3. A linked contract must belong to the filing the reference named.
tibble::tibble(
  nOrders        = nrow(tab_orders),
  nOrdersSeen    = dplyr::n_distinct(tab_cto$DocID),
  nReferences    = sum(!is.na(tab_cto$ExhibitNo)),
  LinkedNoDoc    = sum(tab_cto$LinkStatus %in% cto_status_ok() & is.na(tab_cto$DocIDContract)),
  UnlinkedWithDoc = sum(!tab_cto$LinkStatus %in% cto_status_ok() & !is.na(tab_cto$DocIDContract))
) |>
  tbl_out(
    .title = "Parse and link consistency",
    .notes = c(
      nOrdersSeen = "Must equal nOrders: an order with no parsable reference still returns a row.",
      LinkedNoDoc = "Nonzero means a status claims a link the row does not carry."
    )
  )
```

```{r}
#| label: validate-contracts
# 4. A contract should be covered by one order. Where two orders name it, one is usually an
#    extension of the other, so the count is reported by whether an extension is involved.
tab_cto |>
  dplyr::filter(!is.na(.data$DocIDContract)) |>
  dplyr::summarise(nOrders = dplyr::n_distinct(.data$DocID), .by = "DocIDContract") |>
  dplyr::summarise(
    nContracts     = dplyr::n(),
    nOneOrder      = sum(.data$nOrders == 1L),
    nSeveralOrders = sum(.data$nOrders > 1L),
    MaxOrders      = max(.data$nOrders)
  ) |>
  tbl_out(
    .title = "Orders per linked contract",
    .notes = c(nSeveralOrders = "Usually an extension of an earlier grant, which names the same filing.")
  )
```

# Deployment

`CtoExhibits.parquet` is the only artifact of this script: one row per exhibit reference, carrying the order that made
it, the exhibit and release date, the linked contract where the chain completed, and the point at which it broke where
it did not.

02 reads it to mark each contract in the register with whether an order covers it. The text of the orders stays in the
corpus; nothing here writes into another script's output.

What this does **not** yet do is check that a linked contract is actually redacted. The order says the SEC permitted a
redaction; whether the filed document shows one is a property of its text, and belongs with the entity extraction that
locates redaction markers. Until that exists, a link is a permission rather than an observation.

```{r}
#| label: deploy-report
fs::file_info(.lP$Output$CtoExhibits) |>
  dplyr::select("path", "size") |>
  tbl_out(.title = "Written")
```

# Overview

```{r}
#| label: fig-linkage
#| fig-height: 3.4
#| fig-cap: "Exhibit references per year of the order, split into those linked to a contract and
#|   those left unresolved. The collapse after 2018 is the FAST Act removing the requirement to
#|   apply, not a failure of the linkage."
gg_link <- cto_plot_linkage(.tab = tab_cto)

plot_save(
  .plot    = gg_link,                   # the figure
  .name    = "cto-linkage",             # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_link
```

```{r}
#| label: overview-all
cto_report_all(.tab = tab_cto)
```

# Next

**02-SelectSample** reads this and 01D to mark the register: whether an order covers a contract, and whether an 8-K
summary was extracted for a filing.

The checks the workflow calls for beyond the linkage -- that a covered contract shows redaction markers, that an
unredacted version appears after the release date, that a denied application led to disclosure -- all need the text of
the contracts themselves, and belong downstream of the entity extraction that reads it.
