---
title: "Compustat Fundamentals (02A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/02A-Compustat.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Downloads the annual and quarterly Compustat fundamentals and converts each firm-quarter into a date interval, so that
a filing date can be matched to the quarter it falls in.

This script does not know what a contract is. Separating acquisition from the register that consumes it means the
register can be rebuilt without carrying the WRDS machinery, and a second external source becomes another script here
rather than another section of an already long one.

## Matching a filing date to a fiscal quarter

A filing carries a date; Compustat carries fiscal quarters. Matching them means turning each quarter into an interval
and asking which one contains the filing date -- which is only well defined if a firm has one observation per quarter,
and Compustat does not guarantee that.

Four deduplications run in order, each keeping the observation with the larger total assets: the same quarter can appear
under two gvkeys after a restructuring, under two CIKs, or simply twice. Sorting on assets keeps the parent rather than
a subsidiary shell where the two differ.

Each quarter's interval then runs to the start of the next. A firm that stops reporting would otherwise leave an
interval running to its next appearance years later, and a filing in that gap would be matched to a quarter it has no
business being matched to, so any interval longer than one quarter is truncated.

The deduplications have a consequence worth stating: after them the mapping between CIK and gvkey is exactly one to one,
so a firm that changed gvkey -- through a restructuring, say -- retains one identity and not both. That is what makes
"the filer is not in Compustat" and "the firm is not in Compustat" the same test, and it is checked below rather than
assumed.

## Frozen acquisition

Both WRDS calls sit behind `.lP$Param$Acquire`, defaulting to `FALSE`, exactly as the EDGAR downloads do in 01A and
01B. Credentials are read inside those chunks and nowhere else, so a missing key file is an error only when a
connection is actually wanted -- the document renders without one.

# Configuration

```{r}
#| label: config
.lP <- list(
  Input = list(
    Credentials = here::here("0_data", "ApiKeys", "WRDS.txt")    # read only when acquiring
  ),
  Output = list(
    AnnualData   = utils_file_path(.dir_main, "AnnualData.parquet"),     # raw annual fundamentals
    QuarterData  = utils_file_path(.dir_main, "QuarterData.parquet"),    # raw quarterly fundamentals
    QuarterRange = utils_file_path(.dir_main, "QuarterRange.parquet"),   # one interval per firm-quarter
    Figures      = utils_file_path(.dir_main, "Figures")
  ),
  Param = list(
    Acquire = FALSE    # TRUE permits the two WRDS downloads to run
  )
)

tibble::tibble(
  Item   = c(names(.lP$Output), "Credentials"),
  Path   = c(unname(unlist(.lP$Output)), .lP$Input$Credentials),
  Exists = fs::file_exists(c(unname(unlist(.lP$Output)), .lP$Input$Credentials)) |
    fs::dir_exists(c(unname(unlist(.lP$Output)), .lP$Input$Credentials))
) |>
  tbl_out(.title = "Paths", .notes = c(Exists = "Credentials are read only when acquiring."))
```

`rWRDS` is installed from `0_data/Binaries/` and is not on CRAN.

# Acquisition

Both chunks are gated and report what they did either way. `apply_screening_conditions()` is the package's standard
academic filter; requiring a non-missing CIK is what makes the table joinable to EDGAR at all, since CIK is the only
identifier the two sources share.

```{r}
#| label: acquire-annual
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "funda") |>
    dplyr::distinct() |>
    dplyr::mutate(fqtr = 4L) |>                       # annual data is the fourth quarter by convention
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Output$AnnualData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: annual fundamentals were not refreshed.")
}
```

```{r}
#| label: acquire-quarterly
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "fundq") |>
    dplyr::distinct() |>
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Output$QuarterData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: quarterly fundamentals were not refreshed.")
}
```

```{r}
#| label: check-inputs
# Checked after the gate rather than before it, because with acquisition on these are outputs and
# with it off they are inputs. Either way nothing below can run without them.
need_ <- c(AnnualData = .lP$Output$AnnualData, QuarterData = .lP$Output$QuarterData)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort(
    "Missing fundamentals: {paste(names(miss_), collapse = ', ')}. Set Acquire = TRUE to download."
  )
}

fs::file_info(need_) |>
  dplyr::mutate(Item = names(need_)) |>
  dplyr::select("Item", "size", "modification_time") |>
  tbl_out(.title = "Fundamentals on disk")
```

# The matching frame

```{r}
#| label: build-range
tab_range <- cmp_quarter_range(
  .path_quarter = .lP$Output$QuarterData,     # quarterly fundamentals
  .path_out     = .lP$Output$QuarterRange     # one interval per firm-quarter
)

nrow(tab_range)
```

# Results

```{r}
#| label: report-all
cmp_report_all(.tab_range = tab_range)
```

# Validation

Three checks. Each states its expectation first, so a result that differs is a finding rather than a number to
interpret afterwards.

```{r}
#| label: validate-range
# 1. A firm-quarter should appear once: the four deduplications exist to make that true.
# 2. Every interval must start before it ends, or a filing date can fall in no quarter at all.
# 3. No interval should exceed one quarter, which is what the truncation enforces.
tibble::tibble(
  nRows        = nrow(tab_range),
  nCIK         = dplyr::n_distinct(tab_range$CIK),
  nGvkey       = dplyr::n_distinct(tab_range$gvkey),
  nPairs       = dplyr::n_distinct(paste(tab_range$CIK, tab_range$gvkey)),
  DuplicateFQ  = sum(duplicated(tab_range[c("gvkey", "fyear", "fqtr")])),
  BadInterval  = sum(tab_range$DateStop <= tab_range$DateStart, na.rm = TRUE),
  OverOneQtr   = sum(tab_range$dQtrs > 1L, na.rm = TRUE),
  MissingDates = sum(is.na(tab_range$DateStart) | is.na(tab_range$DateStop))
) |>
  tbl_out(
    .title = "Interval consistency",
    .notes = c(
      nPairs      = "Equal to nCIK and nGvkey means the identifiers map one to one after deduplication.",
      DuplicateFQ = "Must be zero: the deduplications are what make one quarter one observation.",
      OverOneQtr  = "Counted before truncation is applied, so a nonzero value here is expected."
    )
  )
```

# Deployment

Three files. The two downloads are frozen: nothing here rewrites them unless acquisition is switched on, so a render
costs one read of the quarterly file and the deduplication over it.

```{r}
#| label: deploy-report
fs::file_info(unlist(.lP$Output)[1:3]) |>
  dplyr::mutate(Item = names(unlist(.lP$Output))[1:3]) |>
  dplyr::select("Item", "size") |>
  tbl_out(.title = "Written")
```

# Overview

```{r}
#| label: fig-coverage
#| fig-height: 3.4
#| fig-cap: "Firm-quarters in the matching frame per calendar year. The frame extends well before and
#|   after the window any sample uses, which is harmless: a filing outside the window is excluded by
#|   the sample ladder rather than by the absence of a quarter to match it to."
gg_cov <- tab_range |>
  dplyr::mutate(Year = lubridate::year(.data$DateStart)) |>
  dplyr::filter(.data$Year >= 1990L) |>
  dplyr::summarise(nQuarters = dplyr::n(), .by = "Year") |>
  ggplot2::ggplot(ggplot2::aes(x = .data$Year, y = .data$nQuarters)) +
  ggplot2::geom_col(fill = plot_pal_seq(1L)) +
  plot_scale_y_count() +
  ggplot2::labs(x = NULL, y = "Firm-quarters") +
  plot_theme(.grid = "y")

plot_save(
  .plot    = gg_cov,                    # the figure
  .name    = "compustat-coverage",      # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_cov
```

```{r}
#| label: overview-all
cmp_report_all(.tab_range = tab_range)
```

# Next

**02B-Register** reads `QuarterRange.parquet` and joins it to the corpus, applies the sample ladder, and writes the one
table every downstream script reads.
