---
title: "Compustat Fundamentals (02A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/02A-Compustat.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Downloads the annual and quarterly Compustat fundamentals and converts each firm-quarter into a date interval, so that
a filing date can be matched to the quarter it falls in.

This script does not know what a contract is. Separating acquisition from the register that consumes it means the
register can be rebuilt without carrying the WRDS machinery, and a second external source becomes another script here
rather than another section of an already long one.

## Matching a filing date to a fiscal quarter

A filing carries a date; Compustat carries fiscal quarters. Matching them means turning each quarter into an interval
and asking which one contains the filing date -- which is only well defined if a firm has one observation per quarter,
and Compustat does not guarantee that.

Four deduplications run in order, each keeping the observation with the larger total assets: the same quarter can appear
under two gvkeys after a restructuring, under two CIKs, or simply twice. Sorting on assets keeps the parent rather than
a subsidiary shell where the two differ.

Each quarter then becomes a fixed window: `datadate`, the date the fiscal quarter closed, through one quarter later.
A filing reporting a quarter arrives in the months after it closes, so that window is where it falls.

The obvious alternative -- run each interval to the start of the firm's next observation -- fails in two ways. A firm
that stops reporting leaves an interval running to its next appearance years later, and a filing anywhere in that gap
is matched to a quarter it has no business being matched to. A firm reporting irregularly produces intervals that
overlap, and a filing then matches several quarters at once, which 02B has to discard as ambiguous.

The fixed window removes the first failure and bounds the second. An interval cannot stretch, so the gap problem does
not arise at all. Overlap is not eliminated: where a firm reports two quarters less than three calendar months apart --
a stub quarter after a fiscal year-end change, or a 52/53-week calendar whose quarter ends drift -- the windows still
cross. The Validation section counts them, and it is about one firm-quarter in a thousand.

That residue is left rather than repaired, because there is no basis for repairing it. A filing landing inside two
quarters genuinely has two candidates, and 02B discards it as ambiguous rather than choosing. What the fixed window
buys is that the ambiguity is confined to firms whose own reporting is irregular, instead of arising wherever a firm
ever paused.

What it gives up is the few days before an unusually early next filing. That is the smallest of the three losses and
the only bounded one.

The deduplications have a consequence worth stating: after them the mapping between CIK and gvkey is exactly one to one,
so a firm that changed gvkey -- through a restructuring, say -- retains one identity and not both. That is what makes
"the filer is not in Compustat" and "the firm is not in Compustat" the same test, and it is checked below rather than
assumed.

## Frozen acquisition

Both WRDS calls sit behind `.lP$Param$Acquire`, defaulting to `FALSE`, exactly as the EDGAR downloads do in 01A and
01B. Credentials are read inside those chunks and nowhere else, so a missing key file is an error only when a
connection is actually wanted -- the document renders without one.

The annual fundamentals are acquired and, at present, read by nothing: this document uses only the quarterly file, and
no script downstream opens either. They are kept because the WRDS call is the expensive part and the analysis will want
annual controls; they are named here so that a reader does not go looking for the consumer of a table that has none yet.

## Where things are written

`QuarterRange.parquet` is what 02B reads, so it goes in `Output/`. The two downloads are neither an output nor a cache:
they are a local copy of a licensed external archive, they cannot be rebuilt without WRDS credentials, and nothing
downstream opens them. They sit at the script root for the same reason 01A's `GetEDGAR/` tree does -- a heading meaning
*safe to delete* over a file that costs a credentialed download to replace is a heading somebody will act on.

## What is recomputed, and what is not

Four sorted deduplications over the whole of Compustat are the only real work here, and they cannot produce a different
answer while the quarterly download stands still. `cmp_quarter_range()` therefore takes a `.rerun` argument defaulting
to `FALSE` and fingerprints that file before deciding.

The result is also the published artifact, which makes the guard matter for a second reason. 02B reads it, and a
fingerprint downstream is only as stable as the modification time of the file it points at: rewriting this on every
render would make any cache keyed on it miss although the bytes were identical.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are deliberate and both
are the same decision. A runbook is read while it runs and pasted into discussion, where a monospaced block survives
being quoted into a mail or a chat window and a styled table does not.

The publication versions are produced once, at the end of the pipeline, by the consolidated release script: styled
tables from the same `tbl_out()` specifications, figure files from the same plotting functions.

# Configuration

```{r}
#| label: config
.lP <- list(
  Input = list(
    Credentials = here::here("0_data", "ApiKeys", "WRDS.txt")    # read only when acquiring
  ),
  # NEITHER OUTPUT NOR CACHE. A local copy of a licensed archive; see "Where things are written".
  Download = list(
    AnnualData  = utils_file_path(.dir_main, "AnnualData.parquet"),    # raw annual fundamentals
    QuarterData = utils_file_path(.dir_main, "QuarterData.parquet")    # raw quarterly fundamentals
  ),
  Cache = list(
    RangeStamp = utils_file_path(.dir_main, "Cache", "RangeStamp.parquet")   # guards the frame below
  ),
  Output = list(
    QuarterRange = utils_file_path(.dir_main, "Output", "QuarterRange.parquet")   # one interval per firm-quarter
  ),
  Param = list(
    Acquire = FALSE    # TRUE permits the two WRDS downloads to run
  )
)

# Reported relative to the project root. An absolute path is correct on one machine and wrong on
# every other, and this page is published.
show_ <- c(.lP$Download, .lP$Output, Credentials = .lP$Input$Credentials)

tibble::tibble(
  Item   = names(show_),
  Kind   = c(rep("Download", length(.lP$Download)), rep("Output", length(.lP$Output)), "Input"),
  Path   = as.character(fs::path_rel(unname(unlist(show_)), start = here::here())),
  Exists = fs::file_exists(unname(unlist(show_)))
) |>
  tbl_out(.title = "Paths", .notes = c(Exists = "Credentials are read only when acquiring."))
```

`rWRDS` is installed from `0_data/Binaries/` and is not on CRAN.

# Acquisition

Both chunks are gated and report what they did either way. `apply_screening_conditions()` is the package's standard
academic filter; requiring a non-missing CIK is what makes the table joinable to EDGAR at all, since CIK is the only
identifier the two sources share.

```{r}
#| label: acquire-annual
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "funda") |>
    dplyr::distinct() |>
    dplyr::mutate(fqtr = 4L) |>                       # annual data is the fourth quarter by convention
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Download$AnnualData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: annual fundamentals were not refreshed.")
}
```

```{r}
#| label: acquire-quarterly
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "fundq") |>
    dplyr::distinct() |>
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Download$QuarterData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: quarterly fundamentals were not refreshed.")
}
```

```{r}
#| label: check-inputs
# Checked after the gate rather than before it, because with acquisition on these are outputs and
# with it off they are inputs. Either way nothing below can run without them.
need_ <- unlist(.lP$Download)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort(
    "Missing fundamentals: {paste(names(miss_), collapse = ', ')}. Set Acquire = TRUE to download."
  )
}

fs::file_info(path = need_) |>
  dplyr::transmute(
    Item     = names(need_),
    Size     = .data$size,
    Acquired = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Fundamentals on disk",
    .notes = c(Acquired = "Frozen unless Acquire is TRUE, so this date is when WRDS was last called.")
  )
```

# The matching frame

```{r}
#| label: build-range
tab_range <- cmp_quarter_range(
  .path_quarter = .lP$Download$QuarterData,     # quarterly fundamentals, frozen
  .path_out     = .lP$Output$QuarterRange,      # one interval per firm-quarter
  .path_stamp   = .lP$Cache$RangeStamp,         # fingerprint the frame was built under
  .rerun        = FALSE                         # TRUE rebuilds regardless of the fingerprint
)

nrow(tab_range)
```

# Results

Both summaries are shown here and again in the Overview, and the second is what the figure plots. They are computed
once and passed to all three.

```{r}
#| label: summarise-range
tab_coverage <- cmp_coverage_summary(.tab_range = tab_range)                    # one row
tab_by_year  <- cmp_quarters_by_year(.tab_range = tab_range, .year_min = 1990L) # one row per year
```

```{r}
#| label: report-all
cmp_report_all(
  .tab_cov  = tab_coverage,   # summarised above, not recomputed
  .tab_year = tab_by_year     # likewise; the figure plots the same table
)
```

# Validation

Three checks. Each states its expectation first, so a result that differs is a finding rather than a number to
interpret afterwards.

```{r}
#| label: validate-range
# 1. A firm-quarter should appear once: the four deduplications exist to make that true.
# 2. Every interval must start before it ends, or a filing date can fall in no quarter at all.
# 3. Some of a firm's intervals will overlap, and a filing landing inside two of them is one 02B
#    discards as ambiguous. The prediction is a small nonzero count concentrated in firms that
#    changed a fiscal year end or report on a 52/53-week calendar -- not zero, because the fixed
#    window bounds overlap rather than preventing it.
tibble::tibble(
  nRows        = nrow(tab_range),
  nCIK         = dplyr::n_distinct(tab_range$CIK),
  nGvkey       = dplyr::n_distinct(tab_range$gvkey),
  nPairs       = dplyr::n_distinct(paste(tab_range$CIK, tab_range$gvkey)),
  DuplicateFQ  = sum(duplicated(tab_range[c("gvkey", "fyear", "fqtr")])),
  BadInterval  = sum(tab_range$DateStop <= tab_range$DateStart, na.rm = TRUE),
  nOverlapping = tab_range |>
    dplyr::arrange(.data$gvkey, .data$DateStart) |>
    dplyr::mutate(NextStart = dplyr::lead(.data$DateStart), .by = "gvkey") |>
    dplyr::filter(!is.na(.data$NextStart), .data$NextStart < .data$DateStop) |>
    nrow(),
  MissingDates = sum(is.na(tab_range$DateStart) | is.na(tab_range$DateStop))
) |>
  tbl_out(
    .title = "Interval consistency",
    .notes = c(
      nPairs       = "Equal to nCIK and nGvkey means the identifiers map one to one after deduplication.",
      DuplicateFQ  = "Must be zero: the deduplications are what make one quarter one observation.",
      nOverlapping = "Quarters whose window runs past the start of the firm's next. Expected small \\
                      and nonzero; 02B counts the filings that actually land in one."
    )
  )
```

# Deployment

One artifact. `Output/QuarterRange.parquet` is the only file 02B reads, and it is written only when the download it
derives from has moved. The two downloads are frozen unless acquisition is switched on, so a render with nothing to do
costs one read of the published frame.

Nothing else is written. No figure files, no styled tables: those are the release script's job, for the reason set out
under *How results are reported*.

```{r}
#| label: deploy-report
fs::file_info(path = c(unlist(.lP$Output), unlist(.lP$Download), unlist(.lP$Cache))) |>
  dplyr::transmute(
    Kind    = c(
      rep("Output", length(.lP$Output)),
      rep("Download", length(.lP$Download)),
      rep("Cache", length(.lP$Cache))
    ),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output row is read downstream; Download is the frozen acquisition.",
      Written = "A stamp older than this render means the download had not moved and no rebuild was needed."
    )
  )
```

# Overview

```{r}
#| label: fig-coverage
#| fig-height: 3.4
#| fig-cap: "Firm-quarters in the matching frame per calendar year. The frame extends well before and
#|   after the window any sample uses, which is harmless: a filing outside the window is excluded by
#|   the sample ladder rather than by the absence of a quarter to match it to."
cmp_plot_coverage(.tab = tab_by_year)   # summarised in Results; the release script writes the file
```

```{r}
#| label: overview-all
cmp_report_all(
  .tab_cov  = tab_coverage,   # summarised once in Results
  .tab_year = tab_by_year
)
```

# Next

**02B-Register** reads `QuarterRange.parquet` and joins it to the corpus, applies the sample ladder, and writes the one
table every downstream script reads.
