---
title: "The Document Register (02B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01C owns the group vocabulary this document reports by. Sourcing it rather than restating the
# mapping is what keeps one definition of what a contract, a report and an order are.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/02B-Register.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

One row per document, every decision recorded as a column, nothing removed. This is the table every downstream script
reads: 03 to classify, 04 to extract entities, and any analysis to define its sample.

It joins the corpus to Compustat, applies the sample ladder, and attaches what 01D found in the 8-K reports and what
01E found in the confidential-treatment orders.

## Nothing is removed

The register has exactly as many rows as 01C published. A document outside the window, one that failed a quality rule,
one whose filer is not in Compustat, one that matched two fiscal quarters -- each is marked and kept.

That matters for a reason beyond tidiness. If every stage filters, then reconciling two numbers means reconstructing
which filters each had applied; if nothing filters, every number is a count over one table and the difference between
any two is a column. Completeness is true by construction rather than by arithmetic.

It is also a change from the arrangement this replaces, which deleted the documents matching more than one Compustat
quarter. Three hundred and thirty-two of them, which is nothing -- but they were deleted outside the ladder, so no table
in the paper accounted for them.

## The two samples, and why there are two

**The descriptive sample** is every well-formatted document filed inside the window. It is what the corpus can describe,
and it does not require the filer to be in Compustat: roughly a fifth of EDGAR registrants never are, being foreign
private issuers, funds, or firms too small to be covered.

**The estimation sample** is the subset that also matched a Compustat quarter. It is what a regression can use.

Reporting only the second would understate the corpus by whatever share of filers Compustat misses; reporting only the
first would overstate what the analysis rests on.

## No absolute paths, but the public URL stays

A path written on one machine is wrong on every other. The register carries `DocType`, `YQ` and `DocID`, which together
determine where a document is, and `utils_doc_path()` rebuilds it at read time. That is what lets this table be archived
and used by someone who did not run the pipeline.

`UrlDocument` is a different thing and is kept: it is the document's address on EDGAR, identical on every machine, and
the only way a reader of the archive can fetch the original.

## One table, sorted by group

Contracts, 8-K reports and CT orders are one file rather than three. Parquet keeps minimum and maximum values per row
group, so sorting by group means a reader asking only for 8-K documents skips the contract row groups without reading
them. One artifact, and the column sets cannot drift apart.

# Configuration

```{r}
#| label: config
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")

.lP <- list(
  Input = list(
    MetaData     = fs::path(.dir_meta, "FullMetaData.parquet"),                            # 01C
    Item101      = here::here("2_output", "01D-Item101", "Item101.parquet"),               # 01D
    CtoExhibits  = here::here("2_output", "01E-CtoExhibits", "CtoExhibits.parquet"),       # 01E
    QuarterRange = here::here("2_output", "02A-Compustat", "QuarterRange.parquet")         # 02A
  ),
  Output = list(
    Documents = utils_file_path(.dir_main, "Documents.parquet"),   # the register
    Overview  = utils_file_path(.dir_main, "Overview"),            # the selection tables
    Figures   = utils_file_path(.dir_main, "Figures")
  ),
  Param = list(
    YearMin   = 2001L,   # window floor; a research decision, argued below
    YearMax   = 2024L,   # window ceiling, matching the acquisition frame closed in 01A
    StepFinal = 6L       # the ladder step denoting the final sample
  )
)

# Named individually so that a failure says which input is missing rather than that one of them is.
need_ <- unlist(.lP$Input)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

tibble::tibble(Input = names(need_), Path = unname(need_)) |> tbl_out(.title = "Inputs")
```

# Merging

```{r}
#| label: load-range
tab_range <- arrow::read_parquet(.lP$Input$QuarterRange)

nrow(tab_range)
```

The interval join returns more than one row for a document where two of a firm's quarter windows overlap. Something has
to collapse those, and what is true of such a document is that its filing date does not determine a fiscal quarter --
so the Compustat fields are set to missing and one row is kept. The ladder then attributes it explicitly, rather than
its disappearing.

```{r}
#| label: merge-compustat
tab_merged <- reg_merge_compustat(
  .path_meta = .lP$Input$MetaData,   # 01C's consolidated table, every document
  .tab_range = tab_range             # one interval per firm-quarter, from 02A
) |>
  dplyr::mutate(Group = edg_doc_group(.doc_type = .data$DocTypeMod))

c(documents = nrow(tab_merged), groups = dplyr::n_distinct(tab_merged$Group))
```

# Selection

The ladder below is the sample definition for the entire study, so it is written here rather than hidden behind a
function call. It is applied to every group identically; the thresholds and their order are the argument a referee would
want to see.

Order matters. A malformatted document filed outside the window is attributed to the window, not to the quality rule,
because the window is the prior restriction. A document whose filer is absent from Compustat is attributed to coverage
rather than to matching, because there was nothing to match against. And a document that matched several quarters is
attributed after the one that matched none, because both are match failures and this one is the narrower.

```{r}
#| label: apply-ladder
tab_flagged <- tab_merged |>
  dplyr::mutate(
    SampleStepDesc = dplyr::case_when(
      !dplyr::between(lubridate::year(.data$DateFiled),
                      .lP$Param$YearMin, .lP$Param$YearMax) ~ "01-Less: Outside 2001 - 2024",
      .data$Removed == 1L                                   ~ "02-Less: Malformatted Documents",
      !.data$CIK %in% tab_range$CIK                         ~ "03-Less: CIK not in Compustat",
      .data$nQuarters > 1L                                  ~ "04-Less: Matched several Compustat quarters",
      is.na(.data$gvkey)                                    ~ "05-Less: No Compustat Match on Filing Date",
      .default                                              = "06-Final Sample"
    )
  ) |>
  reg_sample_flags(.step_final = .lP$Param$StepFinal) |>
  reg_derive()

dplyr::count(tab_flagged, SampleStepDesc)
```

The window floor of `r .lP$Param$YearMin` is a research decision rather than a data limit: EDGAR carries filings from
1993, but the modern 8-K item structure that makes a material definitive agreement identifiable dates from the 2004
reform, and the years before 2001 are thin enough that including them would add noise without adding statistical power.
The ceiling matches the acquisition frame closed in 01A, so the two cannot drift apart.

# Attaching

`HasItem101` is zero rather than missing for a document that was never a candidate. A candidate is an 8-K whose filing
reports the item, so a contract having no summary is not an absence of information -- it is the wrong kind of document
to have one.

```{r}
#| label: attach-item101
tab_flagged <- reg_attach_item101(.tab = tab_flagged, .path_item = .lP$Input$Item101)

c(candidates = sum(!is.na(tab_flagged$Item101Outcome)), extracted = sum(tab_flagged$HasItem101))
```

One order can cover several exhibits and one contract can be covered by several orders, most often because a grant was
later extended. Both release dates are kept: the earliest is when any part of the redaction becomes releasable, the
latest when all of it does, and which matters depends on the question.

```{r}
#| label: attach-cto
tab_flagged <- reg_attach_cto(.tab = tab_flagged, .path_cto = .lP$Input$CtoExhibits)

c(covered = sum(tab_flagged$HasCto), withExtension = sum(tab_flagged$CtoIsExtension))
```

# Deployment

```{r}
#| label: write-register
tab_register <- reg_shape(.tab = tab_flagged)

arrow::write_parquet(tab_register, .lP$Output$Documents)

purrr::walk(
  .x = sort(unique(tab_register$Group)),
  .f = function(.g) {
    arrow::write_parquet(
      x    = reg_sample_table(.tab = tab_register, .group = .g),
      sink = fs::path(.lP$Output$Overview, paste0("SampleSelect", .g, ".parquet"))
    )
  }
)

c(rows = nrow(tab_register), cols = ncol(tab_register))
```

Nothing is exported to Stata. Format conversion is not this script's concern: every stage would otherwise carry its own
exporter, they would drift in how they name and order things, and the tables would be rewritten on every render of a
document that does not change them. One release script converts everything once, when the pipeline is complete.

A downstream script opens a document by rebuilding its path:

```r
utils_doc_path(
  .dir_mirror = here::here("2_output", "01B-EdgarDocuments", "GetEDGAR"),
  .doc_type   = tab$DocType,
  .yq         = tab$YQ,
  .doc_id     = tab$DocID
)
```

```{r}
#| label: deploy-report
fs::file_info(.lP$Output$Documents) |>
  dplyr::select("path", "size") |>
  tbl_out(.title = "Written")
```

# Results

```{r}
#| label: report-all
reg_report_all(.tab = tab_register)
```

# Validation

Five checks. Each states its expectation first, so a result that differs is a finding rather than a number to interpret
afterwards.

```{r}
#| label: validate-register
# 1. The register must hold every document 01C published: nothing is removed anywhere in this script.
# 2. DocID identifies a document, so it must be unique.
# 3. Every estimation-sample row must carry a gvkey; the ladder places a missing one at step 05.
# 4. The estimation sample is a subset of the descriptive sample by construction.
# 5. No absolute path may survive into the register, or the table cannot leave this machine.
n_corpus_ <- arrow::open_dataset(sources = .lP$Input$MetaData) |>
  dplyr::summarise(n = dplyr::n()) |>
  dplyr::collect() |>
  dplyr::pull(.data$n)

tibble::tibble(
  nCorpus        = n_corpus_,
  nRegister      = nrow(tab_register),
  DuplicateDocID = sum(duplicated(tab_register$DocID)),
  EstiNoGvkey    = sum(tab_register$EstiSample == 1L & is.na(tab_register$gvkey)),
  EstiNotDesc    = sum(tab_register$EstiSample == 1L & tab_register$DescSample == 0L),
  PathColumns    = sum(grepl("(?i)path", names(tab_register)))
) |>
  tbl_out(
    .title = "Register consistency",
    .notes = c(
      nRegister   = "Must equal nCorpus: this script marks documents, it does not remove them.",
      PathColumns = "Must be zero: a path is rebuilt from DocType, YQ and DocID at read time."
    )
  )
```

```{r}
#| label: validate-groups
# Every group must be complete on its own terms, not only in aggregate: a shortfall in the CT orders
# would be invisible in a total dominated by contracts.
tab_register |>
  dplyr::summarise(nRegister = dplyr::n(), .by = "Group") |>
  dplyr::left_join(
    y = arrow::open_dataset(sources = .lP$Input$MetaData) |>
      dplyr::select("DocTypeMod") |>
      dplyr::collect() |>
      dplyr::mutate(Group = edg_doc_group(.doc_type = .data$DocTypeMod)) |>
      dplyr::summarise(nCorpus = dplyr::n(), .by = "Group"),
    by = dplyr::join_by("Group")
  ) |>
  dplyr::mutate(Difference = .data$nRegister - .data$nCorpus) |>
  tbl_out(
    .title = "Completeness by group",
    .notes = c(Difference = "Must be zero on every row.")
  )
```

# Overview

```{r}
#| label: fig-samples
#| fig-height: 3.4
#| fig-cap: "Material contracts per year, split by whether they reach the estimation sample, the
#|   descriptive sample only, or neither. The gap between the two samples is Compustat coverage,
#|   which removes far more than the quality rules do."
gg_samples <- reg_plot_samples(.tab = dplyr::filter(tab_register, .data$Group == "Exhibit10"))

plot_save(
  .plot    = gg_samples,                # the figure
  .name    = "register-samples",        # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_samples
```

```{r}
#| label: overview-all
reg_report_all(.tab = tab_register)
```

# Next

**03** classifies the contracts and **04** extracts named entities, both reading `Documents.parquet` and rebuilding
document paths with `utils_doc_path()`.

A release script will convert the register and the tables it points at into the formats an analysis needs, once the
pipeline is complete. Doing it here would mean rewriting a gigabyte on every render of a document that does not change
it.
