---
title: "The Document Register (02B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# TABLE MODE IS DECLARED, NOT DEFAULTED. tbl_out() reads this option and falls back to "console"
# when nothing sets it, so a document that says nothing still renders console blocks -- but says
# nothing about whether that was chosen. It is chosen: see "How results are reported" below. Setting
# this to "kable" previews the styled path, and every chunk producing a table then needs
# `#| results: asis` or knitr wraps the markup in a code block.
options(
  cli.num_colors = 1,          # plain ASCII; ANSI codes paste as garbage
  cli.width      = 120,        # matches the 125-column source margin
  mc.table_mode  = "console"   # "console" or "kable"
)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01C owns the group vocabulary this document reports by. Sourcing it rather than restating the
# mapping is what keeps one definition of what a contract, a report and an order are.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/02B-Register.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

One row per document, every decision recorded as a column, nothing removed. This is the table every downstream script
reads: 03 to classify, 04 to extract entities, and any analysis to define its sample.

It joins the corpus to Compustat, applies the sample ladder, and attaches what 01D recovered from each 8-K report.

## What belongs here, and what does not

The register carries a fact about a document that is not already in 01C's metadata, plus the ladder. It carries a fact
about something **larger** than a document -- a filing, a firm-quarter -- only where the ladder had to compute it
anyway.

Compustat qualifies, and it is the only thing that does. Ladder steps 03, 04 and 05 *are* the match outcomes, so
`gvkey`, `datadate`, `fyear` and `fqtr` are a by-product of work already done; making a downstream script redo an
interval join over the whole corpus to recover them would be effort for nothing.

Two things used to be here and are not. The filing's 8-K item list arrived through a document-level join, so it was
missing on every row that was not an Item 1.01 candidate -- which is every contract. The confidential-treatment
linkage was a clean join on `DocID`, but nothing here needs it: 03 and 04 read twelve named columns and it is none of
them, and the export is the only consumer. Both are now joined where they are used, on `HashIndex` and `DocID`
respectively, which is one line in each case and puts them on rows where they mean something.

The register lost a column doing this rather than gaining one.

## Nothing is removed

The register has exactly as many rows as 01C published. A document outside the window, one that failed a quality rule,
one whose filer is not in Compustat, one that matched two fiscal quarters -- each is marked and kept.

That matters for a reason beyond tidiness. If every stage filters, then reconciling two numbers means reconstructing
which filters each had applied; if nothing filters, every number is a count over one table and the difference between
any two is a column. Completeness is true by construction rather than by arithmetic.

It is also a change from the arrangement this replaces, which deleted the documents matching more than one Compustat
quarter. Three hundred and thirty-two of them, which is nothing -- but they were deleted outside the ladder, so no table
in the paper accounted for them.

## The two samples, and why there are two

**The descriptive sample** is every well-formatted document filed inside the window. It is what the corpus can describe,
and it does not require the filer to be in Compustat: roughly a fifth of EDGAR registrants never are, being foreign
private issuers, funds, or firms too small to be covered.

**The estimation sample** is the subset that also matched a Compustat quarter. It is what a regression can use.

Reporting only the second would understate the corpus by whatever share of filers Compustat misses; reporting only the
first would overstate what the analysis rests on.

## No absolute paths, but the public URL stays

A path written on one machine is wrong on every other. The register carries `DocType`, `YQ` and `DocID`, which together
determine where a document is, and `utils_doc_path()` rebuilds it at read time. That is what lets this table be archived
and used by someone who did not run the pipeline.

`UrlDocument` is a different thing and is kept: it is the document's address on EDGAR, identical on every machine, and
the only way a reader of the archive can fetch the original.

## One table, sorted by group

Contracts, 8-K reports and CT orders are one file rather than three. Parquet keeps minimum and maximum values per row
group, so sorting by group means a reader asking only for 8-K documents skips the contract row groups without reading
them. One artifact, and the column sets cannot drift apart.

## What is recomputed, and what is not

Two steps take a `.rerun` argument defaulting to `FALSE`, and each fingerprints its inputs before deciding.

**The interval join** is the expensive one. It runs on three columns rather than forty -- only `DocID`, `CIK` and
`DateFiled` decide which quarter a document falls in, and carrying the whole consolidated table through a non-equi
join moves 1.77 million rows of text statistics for nothing. What is cached is the narrow result: six columns per
document rather than forty-five.

**The write** is guarded for a different reason. Five documents downstream read this register, and a fingerprint
downstream is only as stable as the modification time of the file it points at. Rewriting it on every render would
make every cache keyed on it miss although the bytes were identical -- which is precisely what 01C did to five
documents before it was guarded.

The ladder itself is not cached and runs on every render. It is the sample definition, it costs seconds, and a
document that skipped it would be reporting a sample it had not applied.

## How results are reported

Tables print as fixed-width console blocks, and figures are displayed rather than saved. Both are deliberate and both
are the same decision. A runbook is read while it runs and pasted into discussion, where a monospaced block survives
being quoted into a mail or a chat window and a styled table does not.

The per-group sample-selection tables are in the same category and are no longer written to disk. They are manuscript
exhibits, `reg_sample_table()` produces them, and the consolidated release script calls it once at the end of the
pipeline -- alongside the figures, the styled tables and the Stata export. Nothing downstream reads them.

# Configuration

```{r}
#| label: config
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")

.lP <- list(
  Input = list(
    MetaData     = fs::path(.dir_meta, "Output", "FullMetaData.parquet"),                            # 01C
    Item101      = here::here("2_output", "01D-GetItems", "Output", "Item101.parquet"),              # 01D
    QuarterRange = here::here("2_output", "02A-Compustat", "Output", "QuarterRange.parquet")         # 02A
  ),
  Cache = list(
    QuarterMatch = utils_file_path(.dir_main, "Cache", "QuarterMatch.parquet"),   # DocID to fiscal quarter
    OutputStamp  = utils_file_path(.dir_main, "Cache", "OutputStamp.parquet")     # guards the register
  ),
  Output = list(
    Documents = utils_file_path(.dir_main, "Output", "Documents.parquet")   # the register
  ),
  Param = list(
    YearMin   = 2001L,   # window floor; a research decision, argued below
    YearMax   = 2024L,   # window ceiling, matching the acquisition frame closed in 01A
    StepFinal = 6L       # the ladder step denoting the final sample
  )
)

# Named individually so that a failure says which input is missing rather than that one of them is.
need_ <- unlist(.lP$Input)
miss_ <- need_[!fs::file_exists(need_)]
if (length(miss_) > 0L) {
  cli::cli_abort("Missing input{?s}: {paste(names(miss_), unname(miss_), sep = ' -> ', collapse = '; ')}")
}

# Reported relative to the project root. An absolute path is correct on one machine and wrong on
# every other, and this page is published.
tibble::tibble(
  Input = names(need_),
  Path  = as.character(fs::path_rel(unname(need_), start = here::here()))
) |>
  tbl_out(.title = "Inputs")
```

# Merging

```{r}
#| label: load-range
tab_range <- arrow::read_parquet(.lP$Input$QuarterRange)

nrow(tab_range)
```

The interval join returns more than one row for a document where two of a firm's quarter windows overlap. Something has
to collapse those, and what is true of such a document is that its filing date does not determine a fiscal quarter --
so the Compustat fields are set to missing and one row is kept. The ladder then attributes it explicitly, rather than
its disappearing.

```{r}
#| label: merge-compustat
stamp_merge <- utils_dir_stamp(
  .dirs = c(.lP$Input$MetaData, .lP$Input$QuarterRange)   # the two the match is determined by
)

tab_merged <- reg_merge_compustat(
  .path_meta  = .lP$Input$MetaData,        # 01C's consolidated table, every document
  .tab_range  = tab_range,                 # one interval per firm-quarter, from 02A
  .stamp      = stamp_merge,               # computed above
  .path_cache = .lP$Cache$QuarterMatch,    # DocID to fiscal quarter, and its fingerprint
  .rerun      = FALSE                      # TRUE rematches regardless of the fingerprint
) |>
  dplyr::mutate(Group = edg_doc_group(.doc_type = .data$DocTypeMod))

c(documents = nrow(tab_merged), groups = dplyr::n_distinct(tab_merged$Group))
```

# Selection

The ladder below is the sample definition for the entire study, so it is written here rather than hidden behind a
function call. It is applied to every group identically; the thresholds and their order are the argument a referee would
want to see.

Order matters. A malformatted document filed outside the window is attributed to the window, not to the quality rule,
because the window is the prior restriction. A document whose filer is absent from Compustat is attributed to coverage
rather than to matching, because there was nothing to match against. And a document that matched several quarters is
attributed after the one that matched none, because both are match failures and this one is the narrower.

```{r}
#| label: apply-ladder
tab_flagged <- tab_merged |>
  dplyr::mutate(
    SampleStepDesc = dplyr::case_when(
      !dplyr::between(lubridate::year(.data$DateFiled),
                      .lP$Param$YearMin, .lP$Param$YearMax) ~ "01-Less: Outside 2001 - 2024",
      .data$Removed == 1L                                   ~ "02-Less: Malformatted Documents",
      !.data$CIK %in% tab_range$CIK                         ~ "03-Less: CIK not in Compustat",
      .data$nQuarters > 1L                                  ~ "04-Less: Matched several Compustat quarters",
      is.na(.data$gvkey)                                    ~ "05-Less: No Compustat Match on Filing Date",
      .default                                              = "06-Final Sample"
    )
  ) |>
  reg_sample_flags(.step_final = .lP$Param$StepFinal) |>
  reg_derive()

dplyr::count(tab_flagged, SampleStepDesc, name = "nDocs") |>
  tbl_out(
    .title = "Where the ladder places each document",
    .notes = c(nDocs = "Every document is on exactly one step; the per-group tables below split this.")
  )
```

The window floor of `r .lP$Param$YearMin` is a research decision rather than a data limit: EDGAR carries filings from
1993, but the modern 8-K item structure that makes a material definitive agreement identifiable dates from the 2004
reform, and the years before 2001 are thin enough that including them would add noise without adding statistical power.
The ceiling matches the acquisition frame closed in 01A, so the two cannot drift apart.

# Attaching

`HasSummary` is zero rather than missing for a document that was never a candidate. A candidate is an 8-K whose filing
reports the item, so a contract having no summary is not an absence of information -- it is the wrong kind of document
to have one.

The name matters. `HasSummary` says 01D recovered a narrative from **this document**, which is a fact about our
extractor. Whether the parent filing **reports** Item 1.01 is a different fact, it lives in 01D's per-filing table, and
until now the two shared the name `HasItem101` -- one name carrying two meanings that disagree wherever both are
defined, because a filing can report the item while the extraction fails.

```{r}
#| label: attach-item101
tab_flagged <- reg_attach_item101(.tab = tab_flagged, .path_item = .lP$Input$Item101)

c(candidates = sum(!is.na(tab_flagged$Item101Outcome)), extracted = sum(tab_flagged$HasSummary))
```

# The register

`reg_shape()` drops the path columns, orders the rest into identity, location, content, quality, filer, sample and
extraction blocks, and sorts by group.

```{r}
#| label: shape-register
tab_register <- reg_shape(.tab = tab_flagged)

c(rows = nrow(tab_register), cols = ncol(tab_register))
```

# Results

Both summaries are shown here and again in the Overview, and the sample table is derived once per group. They are
computed once and passed to both.

```{r}
#| label: summarise-register
tab_group_summary <- reg_group_summary(.tab = tab_register)   # one row per group

lst_sample_tables <- sort(unique(tab_register$Group)) |>
  purrr::set_names() |>
  purrr::map(\(.g) reg_sample_table(.tab = tab_register, .group = .g))   # the ladder, per group
```

```{r}
#| label: report-all
reg_report_all(
  .tab_grp     = tab_group_summary,   # summarised above; the Overview restates the same two
  .tab_samples = lst_sample_tables
)
```

# Validation

Five checks. Each states its expectation first, so a result that differs is a finding rather than a number to interpret
afterwards.

```{r}
#| label: validate-register
# 1. The register must hold every document 01C published: nothing is removed anywhere in this script.
# 2. DocID identifies a document, so it must be unique.
# 3. Every estimation-sample row must carry a gvkey; the ladder places a missing one at step 05.
# 4. The estimation sample is a subset of the descriptive sample by construction.
# 5. No absolute path may survive into the register, or the table cannot leave this machine.
n_corpus_ <- arrow::open_dataset(sources = .lP$Input$MetaData) |>
  dplyr::summarise(n = dplyr::n()) |>
  dplyr::collect() |>
  dplyr::pull(.data$n)

tibble::tibble(
  nCorpus        = n_corpus_,
  nRegister      = nrow(tab_register),
  DuplicateDocID = sum(duplicated(tab_register$DocID)),
  EstiNoGvkey    = sum(tab_register$EstiSample == 1L & is.na(tab_register$gvkey)),
  EstiNotDesc    = sum(tab_register$EstiSample == 1L & tab_register$DescSample == 0L),
  PathColumns    = sum(grepl("(?i)path", names(tab_register)))
) |>
  tbl_out(
    .title = "Register consistency",
    .notes = c(
      nRegister   = "Must equal nCorpus: this script marks documents, it does not remove them.",
      PathColumns = "Must be zero: a path is rebuilt from DocType, YQ and DocID at read time."
    )
  )
```

```{r}
#| label: validate-groups
# Every group must be complete on its own terms, not only in aggregate: a shortfall in the CT orders
# would be invisible in a total dominated by contracts.
tab_register |>
  dplyr::summarise(nRegister = dplyr::n(), .by = "Group") |>
  dplyr::left_join(
    y = arrow::open_dataset(sources = .lP$Input$MetaData) |>
      dplyr::select("DocTypeMod") |>
      dplyr::collect() |>
      dplyr::mutate(Group = edg_doc_group(.doc_type = .data$DocTypeMod)) |>
      dplyr::summarise(nCorpus = dplyr::n(), .by = "Group"),
    by = dplyr::join_by("Group")
  ) |>
  dplyr::mutate(Difference = .data$nRegister - .data$nCorpus) |>
  tbl_out(
    .title = "Completeness by group",
    .notes = c(Difference = "Must be zero on every row.")
  )
```

# Deployment

`Output/Documents.parquet` is the only artifact of this script, and it is written only when something that determines
it has moved. The fingerprint covers all four inputs and the three sample parameters, so editing the window floor
invalidates it on its own.

That guard matters beyond disk time. Five documents downstream read this register, and a fingerprint downstream is only
as stable as the modification time of the file it points at.

Nothing else is written. No Stata export, no figure files, no styled tables, and no per-group sample-selection tables:
one release script converts everything once, when the pipeline is complete. Every stage carrying its own exporter is
how the naming and ordering of published tables drift apart.

A downstream script opens a document by rebuilding its path:

```r
utils_doc_path(
  .dir_mirror = here::here("2_output", "01B-EdgarDocuments", "GetEDGAR"),
  .doc_type   = tab$DocType,
  .yq         = tab$YQ,
  .doc_id     = tab$DocID
)
```

```{r}
#| label: deploy-register
stamp_register <- utils_dir_stamp(
  .dirs  = unlist(.lP$Input),   # the corpus, the matching frame, and what 01D recovered
  .extra = .lP$Param            # and the window and ladder parameters
)

reg_write_register(
  .tab        = tab_register,          # one row per document
  .path_out   = .lP$Output$Documents,  # the published artifact
  .stamp      = stamp_register,        # computed above
  .path_stamp = .lP$Cache$OutputStamp, # fingerprint the file was last written under
  .rerun      = FALSE                  # TRUE writes regardless of the fingerprint
)
```

```{r}
#| label: deploy-report
fs::file_info(path = c(unlist(.lP$Output), unlist(.lP$Cache))) |>
  dplyr::transmute(
    Kind    = c(rep("Output", length(.lP$Output)), rep("Cache", length(.lP$Cache))),
    File    = as.character(fs::path_file(.data$path)),
    Size    = .data$size,
    Written = format(.data$modification_time, "%Y-%m-%d %H:%M")
  ) |>
  tbl_out(
    .title = "Written",
    .notes = c(
      Kind    = "Only the Output row is read downstream; the rest make a re-render cheap.",
      Written = "A cache older than this render means that step found its input unchanged."
    )
  )
```

# Overview

```{r}
#| label: fig-samples
#| fig-height: 3.4
#| fig-cap: "Material contracts per year, split by whether they reach the estimation sample, the
#|   descriptive sample only, or neither. The gap between the two samples is Compustat coverage,
#|   which removes far more than the quality rules do."
reg_plot_samples(.tab = dplyr::filter(tab_register, .data$Group == "Exhibit10"))
```

```{r}
#| label: overview-all
reg_report_all(
  .tab_grp     = tab_group_summary,   # summarised once in Results
  .tab_samples = lst_sample_tables
)
```

# Next

**03** classifies the contracts and **04** extracts named entities, both reading `Documents.parquet` and rebuilding
document paths with `utils_doc_path()`.

A release script will convert the register and the tables it points at into the formats an analysis needs, once the
pipeline is complete. Doing it here would mean rewriting a gigabyte on every render of a document that does not change
it.
