---
title: "Contract Classification -- BERT Trainer (03B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = FALSE, warning = FALSE)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_Format.R", encoding = "UTF-8")

# 03A owns prep + the shared scoring / leaderboard / plot / cache layer (clf_*).
# Source it first so this runbook inherits that tooling; then source 03B's own
# wrapper (bert_*). init_create_script_fun resolves each script's paired .R.
source(init_create_script_fun(here::here(), "03A-ClassifyPrepare"), encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

# What 03B is

03B is the **BERT trainer**. The model search is already done (see the state
document): the crowned configuration is legal-bert, 6 epochs, unweighted, LR
2e-5, 256 or 512 tokens. So 03B is not a search -- it is the **re-homing** of that
validated pipeline into the 03A-consuming, logged, cached layout, reproducing the
headline numbers off the existing run folders.

It does three things and nothing else:

1. **Isolate the wrapper.** `bert_train` / `bert_cv` / `bert_sweep` deal fold ids
   to the contracts-engine Python trainer across the CLI + parquet seam. No
   scoring lives here -- 03A owns that.
2. **Quiet, logged runs.** The engine streams each fold's epoch logs and warnings
   into the run's `run.log`; `bert_train` captures the terse stdout and prints one
   formatted cli line per run. A serial sweep reads as a progress strip.
3. **Score through 03A.** Pooled out-of-fold predictions go through the same
   `clf_*` scoring and plotting layer keyword (03C) and the router (03D) use, so
   every method is compared on byte-for-byte identical folds.

Training is **serial** by design: it is MPS-bound on the M3 Ultra, and concurrent
jobs contend for the one GPU. (This is the single structural difference from 03C's
parallel `kw_sweep`.) Disk caching (`clf_cache`, from 03A) makes re-renders free --
the results sections below read the existing runs once and memoise.

## Path Tree

`prepared.parquet` is read from **03A's** output directory (03A is its sole
writer). Runs are written under 03B's own `runs/` -- the same tree
`clf_load_overall` / `clf_pool_predictions` read for the results.

```{r}
.lP <- list(
  Input = list(
    # 03A is the sole writer of prepared.parquet; resolve its path via the same
    # dir helper 03A used, so this never drifts from where 03A actually wrote it.
    Prepared = utils_file_path(
      init_create_script_dir(here::here(), "03A-ClassifyPrepare"), "prepared.parquet"
    )
  ),
  Runs = list(
    Bert = here::here("2_output", "03B-ClassifyTrainBERT", "runs")
  ),
  Output = list(
    Classification = utils_file_path(.dir_main, "classification"),
    ModelFinal     = utils_file_path(.dir_main, "model_final")
  ),
  Engine = list(
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "classify_train.py")
  )
)
```

## Load the prepared sample

03A built and froze the folds; here we only read them back, for the join-side of
scoring (the dual-class second label, the round slice, the broad rollup) and a
quick confirmation that the splits we train on are the shared ones.

```{r}
tab_prep <- arrow::read_parquet(.lP$Input$Prepared)
cli::cli_alert_info("Loaded {nrow(tab_prep)} prepared docs from 03A")

clf_fold_overview(tab_prep, "ClassDetailed") |>
  fmt_table(.caption = "Shared folds we train on -- detailed taxonomy (from 03A)")
```

# Training

The runs already exist (the sweep was executed once and its folders live under
`.lP$Runs$Bert`). The chunks in this section are therefore the **record of how the
runs were produced**, marked `eval: false`. They are idempotent -- the engine
skips any run whose metrics already exist -- so re-running only fills genuine gaps;
flip a chunk to `eval: true` (or run it interactively) to add or, with
`.overwrite = TRUE`, redo runs. Nothing here needs to run on render.

## Manual checks

A seconds-long smoke run (lands under `runs/_smoke`, excluded from results) to
confirm the seam and `[device] mps`, then one real fold with the model saved.

```{r}
#| eval: false
bert_train(.lP$Input$Prepared,
  .label_col = "ClassDetailed",
  .runs_root = .lP$Runs$Bert, .smoke = TRUE
)
```

```{r}
#| eval: false
bert_train(.lP$Input$Prepared,
  .label_col = "ClassDetailed", .test_fold = 1L,
  .runs_root = .lP$Runs$Bert, .save_model = TRUE
)
```

By default a run prints a single cli line on completion (full detail in its
`run.log`). To watch a fold train live -- per-epoch loss and the progress bar
streaming to the console -- pass `.verbose = TRUE`. It works on `bert_train`,
`bert_cv`, `bert_sweep`, and `bert_fit_final`.

```{r}
#| eval: false
bert_train(.lP$Input$Prepared,
  .label_col = "ClassDetailed", .test_fold = 1L,
  .runs_root = .lP$Runs$Bert, .verbose = TRUE
)
```

## Sweep -- Phase A (contract-type taxonomy)

The class sweep that produced the crowned config. Axes: model x level x LR x
max_len x class_weights x folds (epochs swept {3, 6}). 2x2x2x2x2x2x5 = 320 runs,
~35-40h on the M3 Ultra. Built once; left here as the as-run record.

```{r}
#| eval: false
grid_main <- tidyr::expand_grid(
  model         = c("roberta-base", "nlpaueb/legal-bert-base-uncased"),
  label_col     = c("ClassDetailed", "ClassBroad"),
  lr            = c(2e-5, 3e-5),
  max_len       = c(256L, 512L),
  epochs        = c(3, 6),
  class_weights = c(FALSE, TRUE),
  fold          = 1:5
)
bert_sweep(.lP$Input$Prepared, grid_main, .runs_root = .lP$Runs$Bert)
```

## Sweep -- Amendment (Original vs Amended)

The binary amendment task off `AmendType`, reusing the same harness
(`--label-col AmendType`; the engine drops the NA-amendment docs). Mild imbalance,
front-loaded signal, so a focused grid: 2 models x 2 max_len x 5 folds = 20 runs.

```{r}
#| eval: false
grid_amend <- tidyr::expand_grid(
  model         = c("roberta-base", "nlpaueb/legal-bert-base-uncased"),
  label_col     = "AmendType",
  lr            = 2e-5,
  max_len       = c(256L, 512L),
  epochs        = 6,
  class_weights = FALSE,
  fold          = 1:5
)
bert_sweep(.lP$Input$Prepared, grid_amend, .runs_root = .lP$Runs$Bert)
```

**Phase B (long-context probe) was dropped.** It was gated on 512 clearly beating
256; they came in near-identical (~0.002-0.003 macro-F1), so the Longformer probe
would not change a conclusion -- the contract-type signal is front-loaded in the
opening pages. No long-context runs are part of the final sweep.

# Results

Everything below reads the **existing** run folders through 03A's scoring layer.
`clf_cache` memoises the costly reads, so the first render populates the cache and
every later render is a cache hit. After a fresh sweep, refresh with
`options(clf.cache.overwrite = TRUE)` once.

```{r}
tab_overall <- clf_cache("bert_overall", clf_load_overall(.lP$Runs$Bert))
```

## Leaderboards and axis effects

Per task (tasks differ in difficulty, so view them separately). legal-bert leads;
6 epochs beats 3; class weighting is roughly neutral at 6 epochs; LR 2e-5 ~ 3e-5;
256 ~ 512.

```{r}
clf_leaderboard_show(tab_overall, .label_col = "ClassDetailed", .n = 15L) |>
  fmt_table(.caption = "Top configurations -- detailed taxonomy (12 classes)")
```

```{r}
clf_leaderboard_show(tab_overall, .label_col = "ClassBroad", .n = 15L) |>
  fmt_table(.caption = "Top configurations -- broad taxonomy (7 classes)")
```

```{r}
clf_leaderboard_show(tab_overall, .label_col = "AmendType", .n = 10L) |>
  fmt_table(.caption = "Top configurations -- amendment task")
```

```{r}
#| fig-cap: "Leaderboard: macro-F1 (mean +/- sd across folds), detailed taxonomy."
clf_plot_leaderboard(tab_overall, .label_col = "ClassDetailed", .n = 15L)
```

Which lever actually moved macro-F1, within the detailed task (each row averages
over all other axes on the balanced grid):

```{r}
purrr::map(
  c("Model", "MaxLen", "Epochs", "ClassWeights", "LR"),
  \(.axis) clf_effect(tab_overall, .axis, .label_col = "ClassDetailed") |>
    dplyr::rename(Level = 1) |>
    dplyr::mutate(Level = as.character(Level)) |> # axes differ in type; bind as text
    dplyr::mutate(Axis = .axis) |>
    dplyr::relocate(Axis)
) |>
  purrr::list_rbind() |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Marginal effect of each sweep axis on macro-F1 (detailed)")
```

## Crowned detailed configuration

The top-ranked detailed config, scored on its pooled out-of-fold predictions
(each doc predicted once, by a model that did not train on it).

```{r}
best_det_ <- clf_leaderboard(dplyr::filter(tab_overall, .data$LabelCol == "ClassDetailed")) |>
  dplyr::slice(1) |>
  dplyr::pull(.data$ConfigName)

pred_det <- clf_cache("bert_pred_det", clf_pool_predictions(.lP$Runs$Bert, best_det_))
```

```{r}
clf_scores(pred_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Crowned detailed config -- headline scores (strict, pooled OOF)")
```

```{r}
clf_perclass(pred_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Crowned detailed config -- per-class precision / recall / F1")
```

```{r}
#| fig-cap: "Per-class F1, crowned detailed configuration."
clf_plot_perclass(pred_det)
```

```{r}
#| fig-cap: "Confusion heatmap (row-normalised), crowned detailed configuration."
#| fig-height: 4.5
clf_plot_confusion(pred_det, .normalize = TRUE)
```

## Dual-class: strict vs lenient

Strict scores the primary label only; lenient also accepts a dual-class doc's
second label. The gap is what the dual-class ambiguity costs, and it is
retroactive -- no retraining, just a different scoring rule on the same
predictions.

```{r}
pred_det_dc <- pred_det |> clf_add_second_label(tab_prep)

dplyr::bind_rows(
  clf_scores(pred_det_dc, .lenient = FALSE),
  clf_scores(pred_det_dc, .lenient = TRUE)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Strict vs lenient headline (dual-class second label)")
```

```{r}
#| fig-cap: "Strict vs lenient per-class F1; the gap is the dual-class cost."
#| fig-height: 3.8
clf_plot_strict_lenient(pred_det_dc)
```

## Detailed rolled up vs broad direct

Does predicting the fine 12 classes and aggregating to the 7 broad parents beat
predicting the 7 broad classes directly? Both scored at the broad level. If they
match, one model serves both granularities.

```{r}
best_broad_ <- clf_leaderboard(dplyr::filter(tab_overall, .data$LabelCol == "ClassBroad")) |>
  dplyr::slice(1) |>
  dplyr::pull(.data$ConfigName)

pred_broad <- clf_cache("bert_pred_broad", clf_pool_predictions(.lP$Runs$Bert, best_broad_))
rolled_ <- clf_rollup_to_broad(pred_det, tab_prep)

dplyr::bind_rows(
  clf_scores(rolled_) |> dplyr::mutate(Approach = "ClassDetailed -> rolled up", .before = 1),
  clf_scores(pred_broad) |> dplyr::mutate(Approach = "ClassBroad direct", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Detailed-rolled-up vs broad-direct (both scored at broad level)")
```

## Amendment

```{r}
best_amend_ <- clf_leaderboard(dplyr::filter(tab_overall, .data$LabelCol == "AmendType")) |>
  dplyr::slice(1) |>
  dplyr::pull(.data$ConfigName)

pred_amend <- clf_cache("bert_pred_amend", clf_pool_predictions(.lP$Runs$Bert, best_amend_))
```

```{r}
clf_scores(pred_amend) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Amendment -- headline scores (strict, pooled OOF)")
```

```{r}
clf_perclass(pred_amend) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Amendment -- per-class precision / recall / F1")
```

```{r}
clf_confusion(pred_amend) |>
  fmt_table(.caption = "Amendment -- confusion matrix")
```

## Round-sliced robustness

Headline detailed metrics on the Round2 (gold) labels only vs all labels. Round2
is enriched for the hard rare classes, so this is the honest "hard subset" number,
not a regression -- it shows the result is not propped up by the automated Round1
labels.

```{r}
pred_det_round2 <- pred_det |>
  clf_add_labelround(tab_prep) |>
  dplyr::filter(.data$LabelRound == "Round2")

dplyr::bind_rows(
  clf_scores(pred_det) |> dplyr::mutate(Labels = "All (Round1 + Round2)", .before = 1),
  clf_scores(pred_det_round2) |> dplyr::mutate(Labels = "Round2 only (gold)", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Round-sliced robustness (detailed taxonomy)")
```

# Save the classification

The crowned config's pooled **out-of-fold** predictions are the honest per-document
classification: every doc labelled once, by a model blind to it, with its full
softmax probability vector. We assemble that into one tidy table and persist it.
The probabilities are the raw material for the calibration and confidence analyses
below and for 03D routing.

```{r}
class_det <- clf_cache(
  "bert_class_det",
  bert_classification(.lP$Runs$Bert, best_det_, .tab_prep = tab_prep)
)
```

```{r}
class_det |>
  dplyr::slice_head(n = 8) |>
  dplyr::select(DocID, TrueLabel, PredLabel, Top1Prob, Top2Class, Top2Prob, Margin, Correct) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Per-document classification (head; full table adds one P_<Class> column per class)")
```

Persist it. Parquet is canonical; a CSV rides along for convenience. (For the Stata
hand-off pass `.dta = TRUE` -- it rewrites the per-class probability columns to
`P01..P12` with a codebook, since Stata forbids spaces in variable names.)

```{r}
bert_save_classification(class_det, .lP$Output$Classification, .csv = TRUE, .dta = FALSE)
```

# Confidence and calibration

Three questions about how much to trust a BERT prediction, all answered from the
table just built -- no retraining.

## Calibration -- is an 80%-confident prediction right 80% of the time?

This is **calibration**. The reliability table bins the top-1 probability and
compares mean confidence to empirical accuracy in each bin; the summary reduces it
to ECE (doc-weighted mean gap), MCE (worst bin), and a multiclass Brier score.
Fine-tuned transformers are typically a little **over-confident** -- expect accuracy
to sit just below confidence in the top bins.

```{r}
bert_calibration_metrics(class_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 4))) |>
  fmt_table(.caption = "Calibration summary (ECE, MCE, multiclass Brier; lower is better)")
```

```{r}
bert_calibration(class_det) |>
  dplyr::mutate(dplyr::across(c(MeanConf, Accuracy, Gap), ~ round(.x, 3))) |>
  fmt_table(.caption = "Reliability table: confidence bin vs empirical accuracy")
```

```{r}
#| fig-cap: "Reliability diagram: mean confidence vs empirical accuracy (dashed = perfect calibration; points sized by docs in bin)."
bert_plot_reliability(class_det)
```

## Decision margin -- first guess vs second guess

The **margin** is top-1 minus top-2 probability: large when BERT is decisive, small
when it is torn between two classes. If correct predictions carry a clearly larger
margin than incorrect ones, the margin is a usable confidence signal for routing or
a reject option.

```{r}
bert_margin_summary(class_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Decision margin (top-1 minus top-2) by outcome")
```

```{r}
#| fig-cap: "Margin distribution for correct vs incorrect predictions."
#| fig-height: 3
bert_plot_margin(class_det)
```

## Confidence vs accuracy -- the risk-coverage curve

"At what confidence is BERT reliably right?" Keep only docs whose top-1 probability
clears a rising floor and watch accuracy climb as coverage falls. This is the BERT
twin of 03C's selective layer: it quantifies how accurately the model can label a
confident fraction, and feeds the 03D routing decision.

```{r}
bert_confidence_accuracy(class_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  fmt_table(.caption = "Confidence floor -> coverage and accuracy on the kept subset")
```

```{r}
#| fig-cap: "Risk-coverage: accuracy on the kept subset as a rising confidence floor shrinks coverage."
bert_plot_risk_coverage(class_det)
```

# Deploy: the final all-data model

The CV sweep has already certified the configuration; the deployable artifact is
that same config fit **once on all labelled docs** (no folds, no hold-out -- the
honest number is already paid for). `bert_crowned_config` reads the crowned recipe
straight off the leaderboard, and `bert_fit_final` trains and saves it (weights,
tokenizer, label map) under `model_final/`. This is what 03E / the full-corpus
apply loads.

```{r}
cfg_det <- bert_crowned_config(tab_overall, "ClassDetailed")
cfg_det
```

```{r}
#| eval: false
# ~12 min on the M3 Ultra; writes model_final/<config>__FINAL/model.
bert_fit_final(.lP$Input$Prepared, cfg_det, .model_dir = .lP$Output$ModelFinal, .verbose = TRUE)
```

The amendment classifier deploys identically -- `bert_crowned_config(tab_overall,
"AmendType")` then `bert_fit_final(...)` -- if a saved amendment model is wanted
downstream too.

```{r}
#| eval: false
cfg_amend <- bert_crowned_config(tab_overall, "AmendType")
bert_fit_final(.lP$Input$Prepared, cfg_amend, .model_dir = .lP$Output$ModelFinal, .verbose = TRUE)
```

# Next

03B reproduces the crowned numbers under the new layout, scored through 03A, and now
also persists the per-document classification (with probabilities) and the
deployable all-data model. From here the runs feed the consumers, both pure readers
of this layer:

- **03D-ClassifyOrchestrate** -- pool a BERT config and a keyword config from their
  separate roots (`clf_pool_predictions(c(.lP$Runs$Bert, .lP$Runs$Kw), ...)`) and
  test per-class precision routing; expect BERT-dominant, in which case the null
  result is itself the finding and keyword stands as the interpretable contrast.
- **03E-ClassifyDocuments** -- retrain the chosen config on all labelled data (no
  folds, real early stopping on a clean val split), then apply to the full EDGAR
  Exhibit-10 corpus and persist labels + scores for Stata.
