---
title: "Contract Classification -- Keyword / RegEx"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here())

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)

# Shared, method-agnostic helpers from the BERT track: clf_prepare_sample (so the
# keyword folds are byte-for-byte the BERT folds) and the overview / scoring layer
# (clf_load_overall, clf_pool_predictions, clf_leaderboard*, clf_effect,
# clf_add_second_label). Read-only -- sourcing it does NOT touch BERT training,
# and the keyword track runs stand-alone while BERT is still sweeping.
source(init_create_script_fun(here::here(), "03-Classification"))
```

## Path Tree

Keyword runs are written into the 03b runs root ONLY -- never the BERT folder.
ConfigName carries `keyword-{source}` plus the stopword regime and token length,
so configs never collide. The head-to-head with BERT (below) loads both roots and
binds them. The prepared parquet is keyword-specific (`prepared_kw.parquet`)
because it carries DocDesc, which the BERT prepared parquet drops.

```{r}
.lP <- list(
  Input = list(
    ClassificationSample = "0_data/Classification.parquet",
    MetaData = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    DirContracts = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/",
    BertRunsDir = here::here("2_output", "03-Classification", "runs")
  ),
  Cache = list(
    ContractFiles = utils_file_path(.dir_main, "Cache", "ContractFiles.parquet")
  ),
  Output = list(
    Prepared = utils_file_path(.dir_main, "prepared_kw.parquet"),
    RunsDir  = utils_file_path(.dir_main, "runs")
  )
)
```

## Load Sample

Identical load to the BERT track. DocDesc (filer title) and DocName are the
keyword inputs here, not reserved. AmendType drives the amendment task;
DocClassFinal2 (dual-class second label) feeds lenient scoring.

```{r}
fils_contract <- utils_list_project_files(.lP$Input$DirContracts, .lP$Cache$ContractFiles, FALSE)
fils_class_sample <- arrow::open_dataset(.lP$Input$ClassificationSample) |>
  dplyr::select(DocID, AmendType, DocClassFinal1, DocClassFinal2, DualClass, Level1, Level2, Provenance) |>
  dplyr::left_join(
    y = arrow::open_dataset(.lP$Input$MetaData) |>
      dplyr::select(DocID, DocDesc, DocName),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::collect() |>
  dplyr::left_join(fils_contract, by = dplyr::join_by(DocID))
```

## Prepare Sample

Reuse clf_prepare_sample with the SAME seed/k as BERT (folds are identical), then
re-attach DocDesc / DocName and write `prepared_kw.parquet`. The keyword engine
mines and scores on the title (DocDesc), the body (Text), or both.

```{r}
tab_prep <- clf_prepare_sample(
  .tab_input   = fils_class_sample,
  .path_labels = .lP$Input$ClassificationSample,
  .k           = 5L,
  .seed        = 42L
)
kw_write_prepared(tab_prep, fils_class_sample, .lP$Output$Prepared)

tab_prep_kw <- arrow::read_parquet(.lP$Output$Prepared)
```

## Step 0 -- Diagnostics

Run before any modelling. (a) DocDesc coverage: if below 100%, the docdesc-only
model abstains on the gaps and Coverage reports it. (b) Header leakage: if DocDesc
is restated verbatim near the top of Text, mining Text partly relearns DocDesc and
the docdesc-vs-text contrast is muddied -- in which case consider stripping a
header zone (the analog of Storm stripping the Kadaster registration prefix).

```{r}
kw_diag_desc_coverage(tab_prep_kw) |> print(n = Inf)
```

```{r}
kw_diag_header_leak(tab_prep_kw, .n_chars = 300L)
```

## Fold Overview

Identical folds to the BERT track (same function, same seed); a quick confirm.

```{r}
clf_fold_overview(tab_prep_kw, "ClassDetailed") |> print(n = Inf)
clf_fold_overview(tab_prep_kw, "AmendType") |> print(n = Inf)
```

## Mine + Score (manual checks)

Run one at a time. Smoke takes a second or two and lands under runs/_smoke;
confirm the [mine] / [score] lines and [done] coverage. Then one real fold, ls the
run folder, and peek the mined lexicon (the interpretable payoff). The default
stopword regime is now `english_domain` (English function words + SEC/exhibit
boilerplate), so the ConfigName carries `SWendom_TL3`.

```{r}
kw_train(.lP$Output$Prepared,
  .label_col = "ClassDetailed", .source = "text",
  .runs_root = .lP$Output$RunsDir, .smoke = TRUE
)
```

```{r}
kw_train(.lP$Output$Prepared,
  .label_col = "ClassDetailed", .source = "combined", .test_fold = 1L,
  .runs_root = .lP$Output$RunsDir
)
fs::dir_ls(fs::path(.lP$Output$RunsDir, "ClassDetailed__keyword-combined__K25_N3_A2_SWendom_TL3_S42_F1"))
```

```{r}
kw_load_lexicon(.lP$Output$RunsDir,
  "ClassDetailed__keyword-combined__K25_N3_A2_SWendom_TL3_S42",
  .top_per_class = 12L
) |> print(n = Inf)
```

## Sweep -- Source Race (class taxonomy)

The main event: race the three text sources (DocDesc / Text / combined) AND the
stopword regime (none vs english_domain -- the lesson from the title dump, which
showed the body lexicon clogged with function-word junk). kw_sweep fans the runs
across cores (CPU-bound, won't fight BERT). Knobs (topk, n-gram, alpha,
min_token_len) stay at defaults; sweep them once a source/stopword combo wins.
  3 sources x 2 stopwords x 2 levels x 5 folds = 60 runs.

```{r}
grid_src <- tidyr::expand_grid(
  source    = c("docdesc", "text", "combined"),
  stopwords = c("none", "english_domain"),
  label_col = c("ClassDetailed", "ClassBroad"),
  fold      = 1:5
)
kw_sweep(grid_src, .lP$Output$Prepared, .runs_root = .lP$Output$RunsDir)
```

## Sweep -- Amendment (Original vs Amended)

Asymmetric binary: "Original" is defined by the ABSENCE of amendment language, so
only the "Amended" lexicon is mined and the rule is Amended-if-it-fires-else-
Original (no abstention). The signal is front-loaded and standardised ("AMENDED
AND RESTATED..."), so this is likely the strongest keyword result. Same source x
stopword race; label_col and positive_class ride as constant grid columns.
  3 sources x 2 stopwords x 5 folds = 30 runs.

```{r}
grid_amend <- tidyr::expand_grid(
  source    = c("docdesc", "text", "combined"),
  stopwords = c("none", "english_domain"),
  fold      = 1:5
) |>
  dplyr::mutate(label_col = "AmendType", positive_class = "Amended")

kw_sweep(grid_amend, .lP$Output$Prepared, .runs_root = .lP$Output$RunsDir)
```

## Results -- Leaderboards

kw_leaderboard_show surfaces Source + Stopwords + Coverage across the keyword
configs (read from the 03b root). For the head-to-head, the keyword and BERT
overall tables are loaded from their separate roots and bound -- BERT rows are
filled with NA on the keyword-only columns, and may be partial while BERT sweeps.

```{r}
tab_overall <- clf_load_overall(.lP$Output$RunsDir)

# Keyword configs, per task (Source + Stopwords + Coverage visible)
kw_leaderboard_show(tab_overall, .label_col = "ClassDetailed")
kw_leaderboard_show(tab_overall, .label_col = "ClassBroad")
kw_leaderboard_show(tab_overall, .label_col = "AmendType")
```

```{r}
# Head-to-head with BERT: bind the two isolated roots (guarded if BERT not yet run)
tab_both <- dplyr::bind_rows(
  tab_overall,
  if (fs::dir_exists(.lP$Input$BertRunsDir)) clf_load_overall(.lP$Input$BertRunsDir)
)
clf_leaderboard_show(tab_both, .label_col = "ClassDetailed", .n = 15L)
clf_leaderboard_show(tab_both, .label_col = "AmendType", .n = 10L)
```

## Results -- Winning Keyword Config

Pooled out-of-fold for the best keyword detailed config, scored abstention-aware
(an abstention costs recall and protects precision; Coverage reports the
abstention rate). The confusion matrix keeps a "(none)" column showing which true
classes the lexicon had no signal for.

```{r}
best_kw_det_ <- clf_leaderboard(
  dplyr::filter(tab_overall, !is.na(.data$Source), .data$LabelCol == "ClassDetailed")
) |>
  dplyr::slice(1) |>
  dplyr::pull(.data$ConfigName)

pred_kw_det <- clf_pool_predictions(.lP$Output$RunsDir, .config_name = best_kw_det_)

kw_scores(pred_kw_det)
kw_perclass(pred_kw_det)
kw_confusion(pred_kw_det)
```

## Results -- Dual-Class Strict vs Lenient

Strict scores the primary only; lenient accepts either of a dual-class doc's two
labels. Same retroactive re-scoring as the BERT track -- the second label is joined
onto the pooled predictions, no re-running.

```{r}
pred_kw_dc <- pred_kw_det |> clf_add_second_label(tab_prep_kw)

dplyr::bind_rows(
  kw_scores(pred_kw_dc, .lenient = FALSE),
  kw_scores(pred_kw_dc, .lenient = TRUE)
)
```

```{r}
# Per-class precision/recall shift (strict vs lenient)
kw_perclass(pred_kw_dc, .lenient = FALSE)
kw_perclass(pred_kw_dc, .lenient = TRUE)
```

## Results -- Amendment

```{r}
best_kw_amend_ <- clf_leaderboard(
  dplyr::filter(tab_overall, !is.na(.data$Source), .data$LabelCol == "AmendType")
) |>
  dplyr::slice(1) |>
  dplyr::pull(.data$ConfigName)

pred_kw_amend <- clf_pool_predictions(.lP$Output$RunsDir, .config_name = best_kw_amend_)

kw_scores(pred_kw_amend)
kw_perclass(pred_kw_amend)
kw_confusion(pred_kw_amend)
```

## Results -- Mined Lexicon (interpretable payoff)

The terms the winning config learned, with their mean training precision weight
and fold stability. High-weight, all-fold terms are the trustworthy signals -- and
the natural seed list for an optional human-prune pass later.

```{r}
kw_load_lexicon(.lP$Output$RunsDir, best_kw_det_,
  .min_folds = 3L, .top_per_class = 15L
) |> print(n = Inf)
```
