---
title: "Contract Classification -- Keyword Sweep (03C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = FALSE, warning = FALSE)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_Format.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

# 03A owns the common layer (prep + scoring + plots); source it, then this file.
cat("03A function file: ")
(.path_fun_prep <- init_create_script_fun(here::here(), "03A-ClassifyPrepare"))
source(.path_fun_prep)

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

# What 03C is

03C is the **keyword classifier**: a transparent, lexical counterpart to BERT
(03B) on the *identical* frozen folds. For each contract type it mines a per-class
lexicon (the discriminative terms and n-grams) on the training folds and predicts
the held-out fold by which class's lexicon fires hardest, abstaining (`(none)`)
when nothing fires. It exists for the head-to-head: where keyword matches BERT, the
cheaper, fully-interpretable method wins; where it lags, that gap motivates routing
(03D).

Two things make this clean rather than a parallel re-implementation:

- **It reuses 03A's prepared parquet and scoring layer.** The single
  `prepared.parquet` already carries `DocDesc`, so there is no keyword-specific
  prep -- the engine points `--data` at 03A's output. And scoring goes through
  `clf_scores` / `clf_perclass` / `clf_confusion`, which are abstention-aware by
  default (`.none = "(none)"`); keyword was the reason that layer was built that
  way, so there are no `kw_*` scoring siblings to drift.
- **The engine writes the same run-folder schema as the BERT trainer**
  (`predictions` / `metrics_overall` / `metrics_perclass` / `config.json`) plus
  `lexicon.parquet`. So `clf_load_overall` binds keyword and BERT runs together,
  and 03D consumes both with no special-casing.

The method adds three concepts: **Source** (`text` body, `docdesc` filer title, or
`combined`), **Coverage** (the share of docs it predicts, i.e. 1 - abstention
rate), and the `(none)` abstention sentinel.

Scope note: amendment classification is settled to BERT (lexical separation is
intractable -- "amended and restated" is a naming convention in genuine originals,
keyword ~0.62 vs BERT ~0.86 macro-F1), so this sweep targets `ClassDetailed` (and
optionally `ClassBroad`), not `AmendType`.

This document renders end to end -- no chunks are gated off. The engine steps (the
smoke check and the sweep) shell out to Python, but the sweep is idempotent: a run
that already exists is skipped, so re-rendering is cheap once the grid is on disk.
Everything downstream is wrapped in `clf_cache()`: the first knit after a sweep
computes and stores each result under `2_output/_cache`, and later renders reuse it
without re-reading the runs. To rebuild after a fresh sweep, set
`options(clf.cache.overwrite = TRUE)` (or pass `.overwrite = TRUE` to a single call).

## Paths

`prepared.parquet` is read from 03A's output directory (same path construction 03A
wrote it with, so it always matches). Keyword runs live under 03C's own runs root,
separate from BERT's; `clf_load_overall(c(bert_runs, kw_runs))` binds both for 03D.

```{r}
.dir_prep <- init_create_script_dir(here::here(), "03A-ClassifyPrepare")

.lP <- list(
  Input = list(
    Prepared = utils_file_path(.dir_prep, "prepared.parquet")
  ),
  Output = list(
    RunsDir = utils_file_path(.dir_main, "runs")
  ),
  Engine = list(
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "keyword_train.py")
  )
)
```

```{r}
tab_prep <- arrow::read_parquet(.lP$Input$Prepared)
```

# Step 0 diagnostics

Two checks on the data before modelling -- both are keyword-specific validity
questions that the BERT track does not care about.

## DocDesc coverage

How much of the sample carries a non-empty filer title. Where it is empty, a
`docdesc` model has nothing to mine and must abstain -- which `Coverage` then
reports honestly.

```{r}
kw_diag_desc_coverage(tab_prep) |>
  fmt_table(.caption = "DocDesc coverage (overall and per class)", .pct = "Coverage")
```

## Header leakage

Does the body restate the title verbatim near the top? If so, mining `text`
partly relearns `docdesc`, and the two are not independent feature sources. High
leakage means `combined` is closer to `text` than its name suggests.

```{r}
kw_diag_header_leak(tab_prep, .n_chars = 300L) |>
  fmt_table(.caption = "Body restates the title verbatim in the first 300 chars?", .pct = "LeakShare")
```

# The sweep grid

The primary sweep: the three source fields at the settled defaults (`stopwords =
none`, since legal boilerplate function-word n-grams are the discriminative
signal, not noise), five folds each. Optional columns
(`topk`, `ngram_max`, `min_token_len`, `alpha`, `stopwords`) override per row;
anything omitted falls back to the `kw_command` defaults.

```{r}
grid_main <- tidyr::expand_grid(
  label_col = "ClassDetailed",
  source    = c("text", "docdesc", "combined"),
  stopwords = "none",
  fold      = 1:5
)
grid_main |> fmt_table(.caption = "Primary keyword sweep grid (15 cells)")
```

To confirm the stopwords finding or run the topk / min_df starvation probe, widen
the grid -- e.g. `stopwords = c("none", "english_domain")` crossed with
`topk = c(15L, 25L, 40L)` -- and bind it to `grid_main` before sweeping. The extra
axes flow straight through `kw_sweep`.

# Run the sweep

A quick seam check first -- one tiny cell on a 40/10 subset, end to end, to
confirm the R -> Python -> parquet path before committing the full grid:

```{r}
kw_train(.lP$Input$Prepared,
  .label_col = "ClassDetailed", .source = "combined",
  .test_fold = 1L, .runs_root = .lP$Output$RunsDir, .smoke = TRUE
)
```

Then the grid. Each cell is an independent, CPU-bound shell-out; `kw_sweep`
dispatches them across mirai daemons (spun up for the sweep, torn down on exit),
discards the console, and tees each run's narrative to its `run.log`. It prints a
compact performance table for the freshly-run cells and returns it.

```{r}
perf <- kw_sweep(grid_main, .lP$Input$Prepared, .runs_root = .lP$Output$RunsDir)
```

# Score the sweep

All scoring goes through 03A's shared layer, so these numbers are directly
comparable with BERT's. `clf_load_overall` binds the per-run `metrics_overall`
rows -- that bound table *is* the master log. The disk reads are wrapped in
`clf_cache()`: the first knit after a sweep computes and stores each result under
`2_output/_cache`, and later renders reuse it without re-reading the runs or
recomputing. To rebuild after a fresh sweep, set
`options(clf.cache.overwrite = TRUE)` (or pass `.overwrite = TRUE` to one call).

```{r}
tab_overall <- clf_cache("kw_overall", clf_load_overall(.lP$Output$RunsDir))
kw_leaderboard_show(tab_overall, .label_col = "ClassDetailed", .n = 15L) |>
  fmt_table(.caption = "Keyword configurations -- detailed taxonomy", .wide = TRUE)
```

Marginal effect of the source field (averaged over everything else):

```{r}
clf_effect(tab_overall, "Source", .label_col = "ClassDetailed") |>
  fmt_table(.caption = "Macro-F1 by source field")
```

The winning config's pooled out-of-fold predictions, scored strict (and per
class). `clf_plot_perclass` / `clf_plot_confusion` from 03A render the figures. The
pooled predictions are cached under a key that carries the winning `ConfigName`, so
a new best config misses the cache and recomputes on its own.

```{r}
best_kw <- kw_leaderboard(dplyr::filter(tab_overall, LabelCol == "ClassDetailed")) |>
  dplyr::slice(1) |>
  dplyr::pull(ConfigName)
pred_kw <- clf_cache(
  paste0("kw_pred__", best_kw),
  clf_pool_predictions(.lP$Output$RunsDir, best_kw)
)
```

```{r}
clf_scores(pred_kw) |>
  fmt_table(.caption = "Best keyword config -- headline scores")
```

```{r}
clf_perclass(pred_kw) |>
  fmt_table(.caption = "Best keyword config -- per class")
```

```{r}
#| fig-cap: "Best keyword config: per-class F1 (pooled out-of-fold)."
clf_plot_perclass(pred_kw)
```

# Inspect the mined lexicon

The interpretable payoff: the actual terms the model keys on, pooled across folds
with their training precision weight and fold-stability. In the `docdesc` zone
these are clean contract-type names ("credit agreement", "lease dated"); in the
`text` zone they are the boilerplate verbal fingerprints ("the consultant shall",
"the borrower", "this lease shall") that the stopwords-hurt finding predicted. The
sparse classes are diagnostic too: R&D mines firm-specific tokens (company names),
which is exactly why it generalises poorly -- a data-sparsity signal, not a tuning
one.

This is a large reference table; `.top_per_class` caps the depth shown. Raise it
(or set it to `NULL`, and drop `.min_folds`) for the full lexicon -- better suited
to a supplementary appendix than the main flow.

```{r}
kw_lex <- clf_cache(
  paste0("kw_lexicon__", best_kw),
  kw_load_lexicon(.lP$Output$RunsDir, best_kw, .min_folds = 3L, .top_per_class = 6L)
)
kw_lex |>
  fmt_table(
    .caption = "Mined lexicon: stable terms, top per class per zone",
    .digits = 3, .wide = TRUE
  )
```

# Selective classification: a high-precision subset

The per-class numbers showed high precision but low recall on the hard classes:
the lexicon is usually right when it commits, and pays mostly for being forced to
guess on ambiguous documents. Gating on the confidence `Score` makes that a
deliberate choice -- classify only what the lexicon is sure about, defer the rest.
This is the keyword arm of 03D routing: keyword owns the fraction it can label
precisely, BERT takes the remainder. None of this re-mines anything; it reads the
scores already on disk.

The precision-coverage tradeoff for the best config, swept over a single global
`Score` cutoff -- selective accuracy (precision on the classified subset) against
coverage:

```{r}
pc_curve <- kw_precision_coverage(pred_kw)
pc_curve |> fmt_table(.caption = "Precision-coverage tradeoff (global Score cutoff)")
```

```{r}
#| fig-cap: "Selective accuracy against coverage: the precision bought by abstaining."
kw_plot_precision_coverage(pc_curve)
```

A single global cutoff is blunt, since `Score` is only loosely comparable across
classes. Calibrating a cutoff *per class* to a target precision is the real
operating point -- each class contributes the slice it can label at >= 95%
precision, and `Recall` reports how much of that class we still recover there:

```{r}
calib <- kw_calibrate(pred_kw, .target_precision = 0.95, .min_keep = 5L)
calib |> fmt_table(
  .caption = "Per-class operating points at 95% target precision",
  .digits = 3, .wide = TRUE
)
```

Applying those per-class cutoffs gives the high-precision keyword layer. Its
coverage and selective accuracy -- not `clf_scores` accuracy, which would count
every deferral as wrong -- are the headline for routing:

```{r}
thr_ <- calib |>
  dplyr::select(Label, Threshold) |>
  tibble::deframe()
pred_hi <- kw_gate(pred_kw, thr_)
kw_selective_summary(pred_hi) |>
  fmt_table(
    .caption = "High-precision keyword layer (per-class gated)",
    .pct = c("Coverage", "SelAccuracy")
  )
```

Whatever this layer covers is what 03D would let keyword own; everything it
abstains on routes to BERT. The same gate works on the curated HQ gazetteer once
that lands -- supply HQ terms as the lexicon, score, then calibrate identically.

# Next

03C produces the keyword runs in their own root; 03A's overview tooling reads them,
and 03D compares methods.

- **HQ gazetteer** -- supply the curated high-quality keywords (`keywords_06_2025.xlsx`,
  `HQ == 1`) to the engine as a fixed `--lexicon` instead of mining, then calibrate
  with the same `kw_calibrate` / `kw_gate`. A deterministic, fully interpretable
  high-precision layer to compare against the gated statistical model above.
- **03B-ClassifyTrainBERT** -- the BERT sweep into `2_output/03B-.../runs`, same
  logging contract (per-run `run.log`, quiet console, `clf_load_overall` as the
  master log). Serial, since it is GPU/MPS-bound.
- **03D-ClassifyOrchestrate** -- per-class precision routing from the pooled CV
  predictions of the best BERT and best keyword configs (bound via
  `clf_load_overall(c(bert_runs, kw_runs))`), plus the optional Ollama pass on the
  hard residue. Pure consumer of this layer.
