---
title: "Contract Classification -- The Keyword Table (03C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# Figure geometry is NOT set here -- it is declared once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message = TRUE, # mandatory: cli writes through the message stream under knitr, so
  # message = FALSE would discard this document's entire output
  warning = FALSE,
  comment = "" # drops the "##" prefix, so console blocks copy verbatim
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns sample preparation, the shared scoring layer and the category vocabulary. Sourcing it here
# is what makes the keyword and transformer arms comparable: both are scored by the same code on the
# same folds rather than by two similar implementations that disagree at the third decimal, and both
# draw the twelve categories in the same order.
source(init_create_script_fun(here::here(), "03A-ClassifyPrepare"), encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

The transformer classifier trained in 03B is the deployed model. This stage produces something it
cannot: a short, ranked, human-readable table of terms per contract type, applicable to EDGAR with a
text editor and no GPU, carrying a stated precision and a stated coverage.

That is an artifact rather than a model, and it needs a different objective. A keyword classifier
tuned for accuracy maximises an aggregate score and will accept any term that helps it, including
terms no reader could act on. A keyword table tuned for publication accepts only terms that mean what
they appear to mean, and reports honestly how much of the corpus it therefore declines to label.

## How a term earns its place

**Power** is the Wilson 95 percent lower bound on a term's training precision. It is bounded in
`[0, 1]` and monotone in both precision and evidence:

| Occurrences | Raw precision | Power |
|:--|--:|--:|
| 2 of 2 | 1.000 | 0.342 |
| 10 of 10 | 1.000 | 0.722 |
| 45 of 50 | 0.900 | 0.786 |
| 190 of 200 | 0.950 | 0.910 |

Raw precision cannot distinguish a coincidence from a pattern; it ranks two-of-two above
one-hundred-and-ninety-of-two-hundred. Power ranks them the other way and reads directly as "a hit
means this category at least this often, with 95 percent confidence". It is the sort key of the
published table and the evidence gate at scoring time.

Power is deliberately **not** the precision gate. Setting precision to one in the Wilson formula
leaves `Power_max(n) = n / (n + 3.84)`, so Power carries a support-dependent ceiling: a perfect term
needs 44 occurrences to reach 0.92 at all. The thinnest category in this sample holds 71 documents, so
no term within it can clear a high global Power threshold however clean it is. A single threshold on
Power therefore selects for category size rather than term quality and empties every small category by
arithmetic. Precision has no ceiling, so precision is the promise and Power is the evidence.

Three further rules follow from the artifact goal. A **directional guard** admits a term only where
its precision exceeds the category's base rate. **Greedy marginal reach** accepts a term only where it
catches documents no accepted term caught, which removes nested n-grams, near-synonyms and boilerplate
variants under one rule that works on document overlap rather than surface form. The **maximum-Power
decision** scores a document by the single best term that fired rather than by a weighted sum, so
every label traces to one printable term; a sum is not inspectable, and the two rules agree at the
operating point anyway, because most documents fire either no term or one.

## Two independent arms

Mining can only surface terms frequent enough to clear a document-frequency floor and distinctive
enough to win a greedy slot. Reading contracts is not subject to either constraint, and can propose
terminology that is rare, that lost to a longer n-gram containing it, or that a lawyer would name and
a frequency table would never isolate. This document evaluates both arms and their union on identical
folds under identical rules, so the only thing differing between them is where the terms came from.

## Where the work happens

The mining engine emits statistics; every decision is taken in R. Mining is expensive and selection is
cheap, so binding the floors into the engine would force a re-mine for every floor combination.
Splitting them keeps the mining grid at a few hundred cells and leaves the selection sweep
interactive. It also makes the engine task-agnostic: the amendment decision rule is a decision, so it
lives here.

The same line divides matching from deciding, and it has to, because **a table's precision is a
property of how its terms are matched**. Terms are n-grams formed after stopword removal, so a term
mined as `corporation borrower` came from "the corporation and the borrower" and cannot be found by
searching for it. Any second implementation of the match -- a substring search over raw text, however
carefully written -- under-matches the table it is applied to, and reports a precision that describes a
system nobody runs. So matching lives in Python and is called by every stage that needs it, including
this one; the decision lives in R and is called by both. Which of the two produced a set of hits is
invisible to the rule that turns them into labels.

# Configuration

```{r}
#| label: config-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")

# THE TERM LISTS ARE A SUPPLIED INPUT, not something this document rebuilds -- the same standing as
# 03A's label spine. They were produced by a reading session over contrastive document bundles; the
# method is described under "The generated arm" below, and the lists themselves are archived with
# the data rather than regenerated from code.
.dir_cowork <- fs::path(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractData",
  "KeyWordsClaude"
)

# ONE GENERATOR FOR BOTH THRESHOLD GRIDS. Written as two seq() calls they agree to the eye and not to
# the bit: 11 of the 29 published thresholds would differ from their extended twins in the last place,
# because the accumulated representation error depends on where the sequence started. The published
# grid would then not be a subset of the probe grid in any sense a value comparison can see. Generated
# once and sliced, it is one, and the robustness check below is provably probing the same thresholds
# the tables were chosen from. The slice is taken on the same integer scale the comparison uses.
.taus_probe <- seq(0.10, 0.96, by = 0.02)

.lP <- list(
  Input = list(
    Prepared      = utils_file_path(.dir_prep, "prepared.parquet"),
    TermsDetailed = fs::path(.dir_cowork, "detailed", "cowork_terms_detailed.parquet"),
    TermsBroad    = fs::path(.dir_cowork, "broad", "cowork_terms_broad.parquet"),
    TermsAmend    = fs::path(.dir_cowork, "amendment", "cowork_terms_amendment.parquet")
  ),
  Output = list(
    Mines = utils_file_path(.dir_main, "mines"),
    Runs  = utils_file_path(.dir_main, "runs"),
    Table = utils_file_path(.dir_main, "table"),
    Union = utils_file_path(.dir_main, "table", "union_terms_detailed.parquet")
  ),
  Engine = list(
    Python = here::here("contracts-classify", ".venv", "bin", "python"),
    Script = here::here("contracts-classify", "keyword_train.py"),
    # The applier. One interpreter for both, because a table matched under a different tokenisation
    # from the one it was mined under fires on different documents and says nothing about it.
    ScriptApply = here::here("contracts-classify", "keyword_apply.py")
  ),
  Param = list(
    # The promise, and the breadth required of a table before a threshold is acceptable. Both are
    # per task because both are properties of the task rather than of the method: amendment is held
    # lower for the structural reason argued in Robustness, and a breadth floor written for twelve
    # categories is unreachable by a seven-category table and meaningless for a two-category one.
    # Nine of twelve, five of seven -- the same three-quarters -- and both of two, since a binary
    # table that only ever names one class is not a table.
    TargetPrecision = c(ClassDetailed = 0.95, ClassBroad = 0.95, AmendType = 0.85),
    MinClasses      = c(ClassDetailed = 9L, ClassBroad = 5L, AmendType = 2L),
    Tolerance       = 0.01, # precision band treated as indistinguishable; roughly two SEs here
    MinFolds        = 3L, # fold agreement required of a published term
    HoldoutFold     = 5L, # the fold the generated arm never read
    # The thresholds a published table is chosen from, and the same grid extended downward for the
    # robustness check. The first is a slice of the second, not a second sequence that resembles it.
    TausPublished   = .taus_probe[round(.taus_probe * 1e4) >= 4000L],
    TausProbe       = .taus_probe,
    Seed            = 42L # fixed upstream in 03A and reused unchanged
  )
)
```

A mine is named after its hyperparameters and carries no fingerprint of the data it consumed. Change
the sample without emptying `mines/`, and every cell will be reported as already complete while
serving results computed from folds that no longer exist. Superseded mines should be renamed rather
than deleted, since discovery globs a known directory and a renamed sibling is invisible to the code
while remaining available as a record.

# The sample

```{r}
#| label: load-prepared-sample
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(.lP$Input$Prepared)
```

The filer title is mined as a separate arm, so the share of documents carrying one bounds what that
arm can reach. The prediction, before looking: title coverage is high and roughly even across
categories, because a missing title reflects a filing-format accident rather than anything about the
contract.

```{r}
#| label: sample-docdesc-coverage
tab_prep |>
  dplyr::summarise(
    N = dplyr::n(),
    nHasDesc = sum(!is.na(DocDesc) & trimws(DocDesc) != ""),
    ShareHas = mean(!is.na(DocDesc) & trimws(DocDesc) != ""),
    .by = ClassDetailed
  ) |>
  dplyr::arrange(ShareHas) |>
  dplyr::mutate(ShareHas = tbl_pct(ShareHas)) |>
  tbl_say(.title = "Documents carrying a filer title")
```

The title also appears verbatim in the opening characters of the body in almost every document. As a
feature source that makes the title arm redundant, since any model reading the body already reads it.
As a mining ground for a published table it is the better field, because it is short: a term mined
from a filer's own title is close to a contract-type name by construction, where a term mined from the
body is a fragment of operative language. The consequence to expect is a measurable convergence
between the two arms at narrow truncation windows, widening as the window grows.

# Mining the candidate terms

The engine is checked end to end on a tiny subsample before the grid is committed, so a broken seam
surfaces in seconds rather than after the sweep.

```{r}
#| label: mine-smoke-one-cell
kw_mine(
  .path_data  = .lP$Input$Prepared, # sample written by 03A
  .label_col  = "ClassDetailed", # any task will do for a seam check
  .source     = "docdesc", # the cheapest field to mine
  .test_fold  = 1L, # an arbitrary held-out fold
  .mines_root = .lP$Output$Mines, # smoke mines land in a _smoke subfolder
  .python     = .lP$Engine$Python,
  .script     = .lP$Engine$Script,
  .smoke      = TRUE # tiny subsample; checks the seam, not the result
)
```

The grid crosses three tasks, two source fields, five truncation windows, two n-gram lengths and two
stopword regimes, over five folds plus an all-data mine.

Two of those axes deserve a stated expectation. **The truncation window** runs well past the 512
tokens the transformer reads: 256 and 512 words are the like-for-like comparison, and 1024, 2048 and
the whole document are windows no transformer in this study can see. If performance keeps rising past
512 words there is signal deeper in these contracts than the deployed model reads, which would matter
beyond this stage. If it flattens, that independently corroborates the assumption the pipeline already
rests on, from a method that had every opportunity to find something further in and did not.

**The stopword regime** is swept rather than fixed because its answer depends on the objective. Under
an accuracy objective, function-word collocations are discriminative and removing them costs
performance. Under a readability objective they are unusable, whatever they score. The two regimes are
therefore judged on the terms they produce, not on the accuracy column.

```{r}
#| label: mine-build-grid
grid_mine <- kw_mine_grid(
  .label_cols   = c("ClassDetailed", "ClassBroad", "AmendType"), # every task, mined directly
  .nwords_text  = c(256L, 512L, 1024L, 2048L, 0L), # 0 keeps the whole document
  .ngram_max    = c(2L, 3L), # longest n-gram mined
  .stopwords    = c("none", "english_domain"), # judged on readability, not accuracy
  .folds        = 1:5, # folds dealt once, in 03A
  .with_alldata = TRUE # fold 0 produces the published table
)

grid_mine |>
  dplyr::count(Source, Stopwords, NWords, name = "Cells") |>
  dplyr::mutate(Window = dplyr::if_else(NWords == 0L, "full", as.character(NWords))) |>
  dplyr::select(Source, Stopwords, Window, Cells) |>
  tbl_say(.title = paste0("Mining grid: ", nrow(grid_mine), " cells"))
```

Categories are mined directly at both levels rather than rolling one up into the other. Mining is
one-against-the-rest at whatever level it runs, so a term shared evenly by three detailed categories
belonging to one broad parent scores about one third precision against each of them and is discarded,
despite marking the parent cleanly. Those terms are reachable only by working at the broad level.

The sweep is idempotent: the engine skips any cell already on disk, so this chunk runs on every render
and costs seconds after the first.

```{r}
#| label: mine-execute-sweep
kw_mine_sweep(
  .grid       = grid_mine, # what to mine
  .path_data  = .lP$Input$Prepared, # sample written by 03A
  .mines_root = .lP$Output$Mines, # destination; existing cells are skipped
  .python     = .lP$Engine$Python,
  .script     = .lP$Engine$Script,
  .workers    = 24L, # measured: the full grid completes in minutes
  .overwrite  = FALSE # FALSE skips work already present on disk
)

idx_mine <- kw_mine_index(.mines_root = .lP$Output$Mines)
```

```{r}
#| label: mine-report-index
idx_mine |>
  dplyr::filter(Fold > 0L, Mode == "mine") |>
  dplyr::summarise(
    nCells = dplyr::n(),
    mVocab = round(mean(nVocab)),
    mCand = round(mean(nCand)),
    mSeconds = round(mean(MineSec), 1),
    .by = c(LabelCol, Source, NWords)
  ) |>
  dplyr::mutate(Window = dplyr::if_else(NWords == 0L, "full", as.character(NWords))) |>
  dplyr::select(LabelCol, Source, Window, nCells, mVocab, mCand, mSeconds) |>
  tbl_say(.title = "What was mined")
```

# Choosing the configuration

The mining axes are resolved first, under one fixed selection. Crossing mining and selection at once
searches a far wider space than the transformer sweep did on the same 4,400 documents, and the winner
of a wide search on a small sample is partly a winner by luck.

```{r}
#| label: choose-sweep-windows
perf_mines <- kw_sweep_mines(
  .mine_index      = idx_mine, # every fold mine
  .min_precision   = 0.95, # the promise; held fixed while mining axes vary
  .min_hits        = 5L, # minimum positive-class training hits
  .min_tot         = 5L, # minimum total training hits
  .min_reach       = 0.01, # greedy acceptance bar, as a share of the category
  .max_terms       = 25L, # per-category cap
  .min_filers      = 5L, # minimum distinct registrants
  .min_filer_ratio = 0.5, # registrants per hit; catches one firm's own template
  .drop_repeats    = TRUE, # discard n-grams with a repeated token
  .tau             = 0.70, # evidence floor
  .runs_root       = NULL # NULL evaluates without writing run folders
)
```

```{r}
#| label: choose-report-detailed
kw_report_mines(.tab = perf_mines, .label_col = "ClassDetailed")
```

```{r}
#| label: choose-report-broad
kw_report_mines(.tab = perf_mines, .label_col = "ClassBroad")
```

```{r}
#| label: choose-report-amendment
kw_report_mines(.tab = perf_mines, .label_col = "AmendType")
```

The configuration carried forward is chosen by precision with ties broken on coverage. A precision
difference inside one percentage point is indistinguishable from the fold-to-fold spread, so taking
the maximum among such rows buys nothing measurable while discarding real coverage and, where the
winner is a wide truncation window, twenty times the mining time.

The stopword regime is stated rather than inferred. Its criterion is the readability of the terms
produced, and no column reports that, so a tiebreak on coverage would decide the axis on precisely
the ground this document rejects. Removing stopwords costs a little coverage and returns content-word
phrases in place of fragments carrying function words, so `english_domain` is preferred wherever the
two regimes are indistinguishable on the promise.

The coverage floor is advisory rather than binding, and the distinction matters because two documents
consume this choice. A table labelling less than a quarter of the corpus is not a usable artifact, so
the floor is the right bar for what this stage publishes. It is the wrong bar for what 03D consumes:
a source that commits rarely and is nearly always right is exactly what a cascade wants, since the
transformer backfills everything it declines. Enforcing one threshold for both purposes deleted the
second silently -- a source clearing nothing at the publication bar returned no rows, and mine
selection, run writing and the router's arm inventory all inherited the absence without an error
anywhere. Where nothing clears the floor the best configuration is now returned regardless, flagged
and announced. The published table filters on that flag; the router does not.

```{r}
#| label: choose-crown-per-task
cfg_mine <- purrr::map(
  .x = c("ClassDetailed", "ClassBroad", "AmendType"),
  .f = function(.task) {
    purrr::map(c("text", "docdesc"), function(.src) {
      kw_summarise_mines(.tab = perf_mines, .label_col = .task) |>
        dplyr::filter(Source == .src) |>
        kw_choose_config(
          .tolerance    = 0.01, # precision band treated as a tie
          .min_coverage = 0.25, # below this a configuration is not publishable
          .prefer       = list(Stopwords = "english_domain"), # readability, judged outside the table
          .fallback     = TRUE # keep the best configuration even where none clears the floor
        ) |>
        dplyr::mutate(LabelCol = .task, .before = 1L)
    }) |>
      purrr::list_rbind()
  }
) |>
  purrr::list_rbind()

cfg_mine |>
  dplyr::mutate(
    Window    = dplyr::if_else(NWords == 0L, "full", as.character(NWords)),
    Coverage  = tbl_pct(mCoverage),
    Precision = tbl_pct(mPrecision),
    MacroF1   = sprintf("%.3f", mMacroF1)
  ) |>
  dplyr::select(LabelCol, Source, Stopwords, Window, NgramMax,
    Classes = mClasses, Coverage,
    Precision, MacroF1, Publishable
  ) |>
  tbl_say(.title = "Mining configuration carried forward")
```

A row marked not publishable is still evaluated, still written as a run, and still available to 03D.
It is excluded only from the table this stage ships.

The selection floors are then swept over the winning mining configurations only.

```{r}
#| label: choose-sweep-selection
grid_sel <- kw_select_grid(
  .min_precision = 0.95, # the promise, fixed
  .min_hits      = 5L, # evidence floor, fixed: Power already encodes it
  .min_tot       = 5L, # evidence floor, fixed
  .min_reach     = c(0.005, 0.01, 0.02, 0.05), # the greedy bar; the axis that shortens the list
  .max_terms     = c(15L, 25L, 40L) # per-category cap
)

idx_sel <- idx_mine |>
  dplyr::semi_join(cfg_mine, by = dplyr::join_by(LabelCol, Source, NWords, NgramMax, Stopwords)) |>
  dplyr::filter(Fold > 0L)

perf_sel <- kw_sweep_selection(
  .mine_index = idx_sel, # winning mining configurations only
  .grid_sel   = grid_sel, # floors to cross
  .tau        = 0.70, # evidence floor, held fixed while floors vary
  .runs_root  = NULL # NULL evaluates without writing run folders
)
```

```{r}
#| label: choose-report-floors
kw_report_selection(.tab = perf_sel, .label_col = "ClassDetailed", .n = 12L)
```

```{r}
#| label: choose-crown-floors
sel_best <- kw_summarise_selection(.tab = perf_sel, .label_col = "ClassDetailed") |>
  kw_choose_config(
    .tolerance    = 0.01, # precision band treated as a tie
    .min_coverage = 0.25, # below this a configuration is not publishable
    .prefer       = NULL, # no axis here is chosen on grounds the table does not report
    .fallback     = TRUE # these floors are swept over an already-publishable mine
  )

sel_best |>
  dplyr::mutate(Coverage = tbl_pct(mCoverage), Precision = tbl_pct(mPrecision)) |>
  dplyr::select(MinReach, MaxTerms, Terms = mTerms, Classes = mClasses, Coverage, Precision) |>
  tbl_say(.title = "Selection floors carried forward")
```

The floors govern list length and marginal reach, and neither depends on how much text the miner
read, so they are settled once per task and held while the window varies. Settling them here rather
than at deployment keeps the selection decisions in the section that reports the evidence for them,
and gives the robustness checks below the same numbers the published tables will use rather than a
second copy computed from the same sweep.

```{r}
#| label: choose-task-floors
floors_task <- purrr::map(
  .x = c("ClassDetailed", "ClassBroad", "AmendType"),
  .f = function(.task) {
    kw_task_floors(
      .perf_sel     = perf_sel, # selection sweep, every task
      .label_col    = .task, # task
      .tolerance    = .lP$Param$Tolerance, # differences too small to measure
      .min_coverage = 0.25 # below this, not publishable
    )
  }
) |>
  purrr::set_names(c("ClassDetailed", "ClassBroad", "AmendType"))
```

Which tables exist is settled here for the same reason. Every task is crossed with every window the
mining sweep covered, because the window is this arm's cost knob and its coverage knob at once and
which one to ship is a decision worth leaving open until someone has throughput figures. The crossing
is named once and read twice: the robustness checks below probe exactly the cells Deployment
publishes, which they could not be relied on to do if each built its own grid.

```{r}
#| label: choose-publish-plan
# The full-document cell is recorded as zero words upstream and travels as zero here; only the file
# name spells it out.
plan_pub <- tidyr::expand_grid(
  Task   = c("ClassDetailed", "ClassBroad", "AmendType"),
  NWords = sort(unique(idx_mine$NWords))
)
```

# Results

The threshold filters a fixed lexicon at scoring time, so a whole curve costs one join per fold. This
curve is the instrument the stage produces: a reader consults it to choose an operating point, and the
paper reports it as a sensitivity surface rather than a single tuned number.

```{r}
#| label: results-trace-tau-curve
dirs_detailed <- idx_sel |>
  dplyr::filter(LabelCol == "ClassDetailed", Source == "text") |>
  dplyr::pull(MineDir)

curve_detailed <- kw_tau_curve(
  .mine_dirs     = dirs_detailed, # fold mines of the chosen configuration
  .taus          = seq(0.40, 0.96, by = 0.02), # evidence floors to trace
  .min_precision = 0.95, # the promise, fixed across the curve
  .min_hits      = sel_best$MinHits,
  .min_tot       = sel_best$MinTot,
  .min_reach     = sel_best$MinReach,
  .max_terms     = sel_best$MaxTerms
)
```

Two constraints govern the choice, not one. Realised precision must reach the target, and the
resulting table must still label a required number of categories. The second constraint exists because
of the Power ceiling argued in the Purpose: without it the rule returns a very precise table that has
quietly dropped every small category, not because their terms were poor but because those categories
are too small for any term to clear a high threshold.

The target carries a tolerance for the same reason the configuration choice does. Around two thousand
documents are classified here, so the standard error of a proportion near the target is close to half
a percentage point. Comparing hard against the target would treat differences the sample cannot
measure as decisive, and because raising the threshold removes small categories first, the cost of
that false precision is paid in breadth. Among thresholds reaching the target within tolerance, the
one labelling most categories is preferred.

```{r}
#| label: results-report-operating-point
op_detailed <- kw_report_tau(
  .curve            = curve_detailed,
  .target_precision = .lP$Param$TargetPrecision[["ClassDetailed"]], # this task's promise
  .tolerance        = .lP$Param$Tolerance, # differences this small are not measurable here
  .min_classes      = .lP$Param$MinClasses[["ClassDetailed"]], # categories it must reach
  .every            = 2L # the curve is dense; print every other row
)
```

The runs at the chosen operating point are written to disk, in the schema the transformer trainer
uses, so a single leaderboard ranks both arms of the study.

```{r}
#| label: results-write-runs
perf_final <- kw_sweep_selection(
  .mine_index = idx_sel,
  .grid_sel = sel_best |>
    dplyr::select(MinPrecision, MinHits, MinTot, MinReach, MaxTerms) |>
    dplyr::mutate(SelName = "final"),
  .tau = op_detailed$Tau, # the chosen operating point
  .runs_root = .lP$Output$Runs # these are the runs the paper cites
)

pred_final <- perf_final |>
  dplyr::filter(LabelCol == "ClassDetailed", Source == "text") |>
  dplyr::pull(Pred) |>
  purrr::list_rbind()
```

```{r}
#| label: results-report-scores
clf_report_scores(pred_final, .title = "Keyword table at the operating point")
```

```{r}
#| label: results-report-perclass
clf_report_perclass(pred_final, .title = "Per category")
```

Per-category recall is the cost the table pays for its promise. A category with high precision and low
recall is one the table labels rarely and reliably, which is the intended behaviour; a category with
no rows at all is one the table declines entirely, and that is a finding about the category rather
than a gap to be closed by lowering the bar.

```{r}
#| label: results-confusion-table
clf_confusion(pred_final) |> tbl_say(.title = "Confusion, rows are true labels")
```

Every committed label traces to one term, so the reason for it can be printed rather than asserted.

```{r}
#| label: results-audit-correct
kw_report_audit(.tab_pred = pred_final, .per_class = 2L, .wrong = FALSE)
```

```{r}
#| label: results-audit-wrong
kw_report_audit(.tab_pred = pred_final, .per_class = 2L, .wrong = TRUE)
```

# The generated arm

Contrastive document bundles were written, pairing documents of a category with documents drawn from
the rest so that a term appearing in both can be recognised as worthless. A reading session proposed
terms from those bundles, and the responses were folded into one term list per task.

The bundles were drawn from folds one to four, so the session read those documents together with their
labels. Only the held-out fold is absent from every bundle, and it is therefore the only honest
estimate for this arm. Power is still computed on the folds the session read, which makes the Power
values optimistic for both arms alike; the precision and coverage reported below are not.

```{r}
#| label: generated-evaluate
purrr::walk(
  .x = c(.lP$Input$TermsDetailed, .lP$Input$TermsBroad, .lP$Input$TermsAmend),
  .f = function(.p) {
    if (!fs::file_exists(.p)) {
      cli::cli_abort(c(
        "Missing term list {.path {(.p)}}.",
        "i" = "The term lists are a supplied input, archived with the data. See Configuration."
      ))
    }
  }
)

cfg_detailed <- cfg_mine |> dplyr::filter(LabelCol == "ClassDetailed", Source == "text")

perf_generated <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Input$TermsDetailed, # the supplied term list; see Configuration
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords, # same window as the mined arm
  .stopwords     = cfg_detailed$Stopwords, # same regime; a mismatch makes mined terms unmatchable
  .folds         = .lP$Param$HoldoutFold, # the only fold the session never read
  .tau           = op_detailed$Tau, # same evidence floor as the mined arm
  .min_precision = 0.95, # same promise; both arms clear the same gate
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

The session was instructed to propose generously, on the reasoning that a term which fails is discarded
at no cost while a term never proposed cannot be recovered. Survival is therefore expected to be low,
and a low rate is not itself a problem; what matters is whether the survivors reach categories the
mined arm could not.

```{r}
#| label: generated-survival
terms_generated <- arrow::read_parquet(.lP$Input$TermsDetailed)

kw_survival(.proposed = terms_generated, .lexicon = perf_generated$Lexicon[[1]]) |>
  dplyr::mutate(ShareSurvive = tbl_pct(ShareSurvive)) |>
  tbl_say(.title = "Proposed terms surviving the precision and evidence gates")
```

# Validation

The union combines the two arms. Its mined half is taken from the fold mine trained on exactly the
folds the session read, not from the all-data mine, so that neither half has seen the evaluation fold.

Both halves are scored under the mined arm's stopword regime. Where a regime is in force the miner
forms n-grams after removal, so a mined term names two words that need not be adjacent in the raw
text; scoring it without the regime returns zero hits for every such term, and a union assembled that
way silently reduces to the list whose terms happened to survive. Supplied terms are folded to the
same tokenised form on the way in, so a phrase written in full English and a phrase mined after
removal describe the same pattern.

```{r}
#| label: validate-build-union
lex_mined_holdout <- kw_select(
  .mine = kw_load_mine(
    .mine_dir = idx_sel |>
      dplyr::filter(
        LabelCol == "ClassDetailed", Source == "text",
        Fold == .lP$Param$HoldoutFold
      ) |>
      dplyr::pull(MineDir)
  ),
  .min_precision = 0.95,
  .min_hits = sel_best$MinHits,
  .min_tot = sel_best$MinTot,
  .min_reach = sel_best$MinReach,
  .max_terms = sel_best$MaxTerms
) |>
  dplyr::filter(Power >= op_detailed$Tau)

kw_terms_union(
  .lexicon    = lex_mined_holdout, # mined on folds 1-4 only
  .terms_file = .lP$Input$TermsDetailed, # generated from folds 1-4 only
  .path_out   = .lP$Output$Union
)

perf_union <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Output$Union,
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords,
  .stopwords     = cfg_detailed$Stopwords,
  .folds         = .lP$Param$HoldoutFold,
  .tau           = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

```{r}
#| label: validate-compare-arms
kw_report_arms(
  .tabs = list(
    mined = perf_final |>
      dplyr::filter(
        LabelCol == "ClassDetailed", Source == "text",
        TestFold == .lP$Param$HoldoutFold
      ),
    generated = perf_generated,
    union = perf_union
  )
)
```

The number to read first is the count of categories labelled. A union matching both arms on precision
while labelling more categories establishes that mining and reading recover different vocabulary and
that neither substitutes for the other. A union matching the mined arm on every column establishes the
opposite, that the generated terms add nothing the statistics had not already found, which is a
weaker but equally reportable result.

A union can also label **fewer** categories than one of its parts, and that is a property of the
decision rule rather than a fault in the assembly. A document is assigned to the category whose
best-firing term carries the highest Power, so a thin category reachable only through a low-Power term
loses its documents as soon as a higher-Power term from another category is added. Adding terms raises
coverage monotonically; it does not raise the number of categories monotonically. Where the union
trails a parent on category count, that parent is labelling those documents only because the competing
evidence was absent from its list.

# Robustness

The remaining tasks are scored the same way, from the same folds, with the same gates.

```{r}
#| label: robust-generated-other-tasks
perf_generated_broad <- kw_terms_evaluate(
  .path_data = .lP$Input$Prepared,
  .terms_file = .lP$Input$TermsBroad,
  .label_col = "ClassBroad",
  .source = "text",
  .nwords = cfg_mine |> dplyr::filter(LabelCol == "ClassBroad", Source == "text") |>
    dplyr::pull(NWords),
  .stopwords = cfg_mine |> dplyr::filter(LabelCol == "ClassBroad", Source == "text") |>
    dplyr::pull(Stopwords),
  .folds = .lP$Param$HoldoutFold,
  .tau = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root = .lP$Output$Mines,
  .runs_root = .lP$Output$Runs,
  .python = .lP$Engine$Python,
  .script = .lP$Engine$Script
)

perf_generated_amend <- kw_terms_evaluate(
  .path_data = .lP$Input$Prepared,
  .terms_file = .lP$Input$TermsAmend,
  .label_col = "AmendType",
  .source = "text",
  .nwords = cfg_mine |> dplyr::filter(LabelCol == "AmendType", Source == "text") |>
    dplyr::pull(NWords),
  .stopwords = cfg_mine |> dplyr::filter(LabelCol == "AmendType", Source == "text") |>
    dplyr::pull(Stopwords),
  .folds = .lP$Param$HoldoutFold,
  .tau = op_detailed$Tau,
  .min_precision = .lP$Param$TargetPrecision[["AmendType"]], # amendment promises less; see below
  .mines_root = .lP$Output$Mines,
  .runs_root = .lP$Output$Runs,
  .python = .lP$Engine$Python,
  .script = .lP$Engine$Script
)
```

Amendment is held to a lower promise than the categorical tasks, and the reason is structural rather
than a concession. The categorical tables abstain, so their precision is a promise about the subset
they choose to label and can be set as high as the terms allow. Amendment does not abstain: it assigns
one of two labels to every document, so its precision is a property of the whole corpus and is bounded
by how separable the two classes are. Demanding the categorical target of it leaves a handful of terms
and a worse classifier, which is not a stricter table but a broken one.

The stopword regime is not neutral between the two arms, and the union forces them to share one. The
miner forms n-grams after removal, so under a regime its terms name words that need not be adjacent,
and the regime is what makes them fire at all. A written list is folded through the same tokeniser on
the way in, which is what makes it comparable, but folding also collapses phrases the session wrote as
distinct: an article-led phrase and its bare form become the same entry, and the surviving unigram is
less precise than either. Scoring the generated list under both regimes measures that cost directly.

```{r}
#| label: robust-generated-own-regime
perf_generated_none <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Input$TermsDetailed,
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords, # window held at the mined arm's choice
  .stopwords     = "none", # the only axis varied
  .folds         = .lP$Param$HoldoutFold,
  .tau           = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

```{r}
#| label: robust-compare-regimes
kw_report_arms(
  .tabs = list(
    `generated, shared regime` = perf_generated,
    `generated, own regime`    = perf_generated_none
  )
)
```

A written list scoring better under its own regime than under the shared one bounds what the union
costs: the comparison in the previous section understates the generated arm by that difference, and
the difference is the price of expressing both arms in one vocabulary. Amendment, which runs without
removal, shows the same arm unfolded and is the cleanest read on what reading contributes.

```{r}
#| label: robust-compare-tasks
kw_report_arms(
  .tabs = list(
    `broad, mined` = perf_final |>
      dplyr::filter(LabelCol == "ClassBroad", TestFold == .lP$Param$HoldoutFold),
    `broad, generated` = perf_generated_broad,
    `amendment, mined` = perf_final |>
      dplyr::filter(LabelCol == "AmendType", TestFold == .lP$Param$HoldoutFold),
    `amendment, generated` = perf_generated_amend
  )
)
```

Amendment is the sharpest test of the two arms, because the phrase that most obviously marks an
amendment is a title convention appearing on many genuine originals. A statistical miner cannot know
that; it can only observe that the phrase is imprecise and discard it. A reader can recognise the
convention and look instead for the structural markers of modification, which is what the session was
asked to do.

## Whether the threshold grid decides its own answer

The operating point is chosen from a grid of thresholds, and a grid is a statement about where to
look. An optimum on its lower edge was therefore not found by the acceptance rule; it was supplied by
the edge. The binary task is where this is most likely to happen and least likely to be noticed:
coverage is one for every threshold, because a document firing no term is still labelled, so the
rule's first two criteria -- most categories, then widest coverage -- tie everywhere and the choice
falls entirely to the last one, which prefers the lowest threshold on offer.

The check traces every published cell below the floor and selects twice from one curve: once
restricted to the thresholds the table was actually chosen from, once over the whole extension.
Agreement means the floor is documentation. Disagreement means it is a parameter, and one set by the
shape of a sequence rather than by an argument. Every cell rather than one per task, because which
window ships is settled downstream of here and a check that covered only the crowned window would
answer for a table that may not be the one published.

Nothing published moves either way. Extending the grid would change an artifact, and that is not a
change to make as a side effect of asking whether it should be made.

```{r}
#| label: robust-tau-floor
tab_tau_floor <- purrr::pmap(plan_pub, function(Task, NWords) {
  kw_tau_floor_probe(
    .label_col        = Task, # task to probe
    .n_words          = NWords, # every published window, not one
    .idx_mine         = idx_mine, # every mining cell
    .cfg_mine         = cfg_mine, # crowned cell names the held axes
    .floors           = floors_task[[Task]], # this task's selection floors
    .target_precision = .lP$Param$TargetPrecision[[Task]], # this task's promise
    .min_classes      = .lP$Param$MinClasses[[Task]], # breadth it must reach
    .taus_published   = .lP$Param$TausPublished, # the grid the tables were chosen from
    .taus_extended    = .lP$Param$TausProbe, # the same grid, extended downward
    .tolerance        = .lP$Param$Tolerance, # differences too small to measure
    .source           = "text" # the field the shipped arm reads
  )
}) |>
  purrr::list_rbind()
```

```{r}
#| label: robust-report-tau-floor
kw_report_tau_floor(.tab = tab_tau_floor)
```

Two facts are reported because they are two. `Moves` is whether the threshold the rule names changed;
`Binds` is whether anything followed from it. They come apart wherever a range of thresholds selects
the same lexicon, which is the ordinary case here rather than an edge one: the evidence and precision
gates bound Power from below, since the weakest term that can pass a floor of five hits at the
promised precision still carries a Wilson bound near 0.5, so every threshold beneath that selects an
identical table. The rule prefers the lowest acceptable threshold and therefore reports the bottom of
that range, and moves to a new bottom as soon as one exists, having changed nothing.

This is the reading of an operating point at the floor on a task where coverage is one by
construction. It is not a corner solution and nothing is being left on the table; the threshold is
simply not identified below the point where the gates already bind. It is also why the realised
precision and not the threshold is the number to quote about a published table.

Where a floor does bind, the row to read is the extended one against the published one. More terms at
held precision means the floor is costing coverage and should move. More terms at lower precision
means it is protecting the promise, and should be argued as a floor rather than left to look like an
optimum.

# Deployment

The folds pay for the estimate; the all-data mine produces the artifact. A published term must also
have been chosen independently by at least the required number of fold mines, a filter applied here
and nowhere else: mine `k` trains on every fold but `k`, so filtering a fold lexicon on agreement
across all mines would let the held-out fold influence selection. An all-data mine holds nothing out,
so the filter is legitimate against it. The reported precision and coverage therefore describe the
unfiltered procedure, while the published table carries one further filter that can only remove
terms.

**Every task, and every window.** Nothing in the procedure was specific to the detailed taxonomy; it
was written once, for one task, and the other two were left with run folders and no shippable
artifact. And the truncation window is this arm's cost knob and its coverage knob at once -- a shorter
window is cheaper to apply and more precise, a longer one labels more -- so which window to ship is a
decision worth leaving open until someone has throughput figures in hand. Publishing every window
costs a threshold curve each and a few kilobytes of parquet, against the alternative of re-mining to
change one's mind.

What is held fixed is the n-gram order, the stopword regime and the text source, at the values the
mining sweep crowned. Those are not deployment knobs: nobody applying a published table chooses to
read the filer's title instead of the contract. They were settled on the evidence and stay settled.

```{r}
#| label: deploy-publish-tables
# The crossing was settled with the floors, in the section that reports the evidence for both.
# Named for the pair they describe. The catalogue below is sorted for reading, so an index taken
# from it and applied here would return a different task's table -- and silently, since a lexicon is
# a lexicon whatever categories it holds.
pubs <- purrr::pmap(plan_pub, function(Task, NWords) {
  kw_publish_lexicon(
    .label_col        = Task, # task to publish
    .n_words          = NWords, # truncation window
    .idx_mine         = idx_mine, # every mining cell, folds and all-data
    .cfg_mine         = cfg_mine, # crowned cell names the held axes
    .floors           = floors_task[[Task]], # this task's selection floors
    .target_precision = .lP$Param$TargetPrecision[[Task]], # this task's promise
    .min_classes      = .lP$Param$MinClasses[[Task]], # breadth it must reach
    .taus             = .lP$Param$TausPublished, # thresholds to trace
    .tolerance        = .lP$Param$Tolerance, # differences too small to measure
    .min_folds        = .lP$Param$MinFolds, # fold agreement a term must show
    .source           = "text" # the field the shipped arm reads
  )
}) |>
  purrr::set_names(paste0(plan_pub$Task, "_W", plan_pub$NWords))
```

```{r}
#| label: deploy-report-catalogue
catalogue <- kw_catalogue(
  .pubs      = pubs, # every task crossed with every window
  .tolerance = .lP$Param$Tolerance # precision band treated as indistinguishable
)
kw_report_catalogue(.tab = catalogue)
```

Read coverage against reached. A table holds its promise by declining, so one labelling a fifth of
the corpus and one labelling half are making the same promise about very different fractions of the
work. Where a window reaches fewer categories, the mining found no publishable vocabulary for the
rest at that truncation, which is a finding about the window rather than a threshold to lower.

The marked row is what the deployment stage applies unless a caller asks for another. It is the
widest table that holds its promise, ties broken on coverage and then on the shorter window -- chosen
from this table rather than inherited from the mining sweep, which ranks windows at one common
threshold and therefore understates the short ones. A shorter window holds precision at a lower
evidence bar, so judging it at a long window's threshold measures the threshold rather than the
window.

Two breadth columns appear because they are not the same thing. `Reached` counts the categories the
threshold curve says the procedure labels; `Categories` counts those with a surviving term in the
published file, after the fold-agreement filter. The default ranks on the second, because it names an
artifact and the artifact is the file.

```{r}
#| label: deploy-report-lexicon
# The crowned window of the detailed taxonomy, as the worked example. Every other table has the same
# shape and is written to disk beside it.
kw_report_lexicon(
  .tab = kw_default_pub(.pubs = pubs, .catalogue = catalogue, .label_col = "ClassDetailed")$Lexicon,
  .top = 8L
)
```

```{r}
#| label: deploy-save-tables
purrr::walk(pubs, function(.p) {
  kw_save_lexicon(
    .tab  = .p$Lexicon, # this window's published table
    .dir  = .lP$Output$Table, # one directory, many tables
    .stem = kw_table_stem(.label_col = .p$LabelCol, .n_words = .p$NWords)
  )
})
```

```{r}
#| label: deploy-save-catalogue
# Written after the tables, not before them, because it names them: a catalogue that reached disk
# ahead of a failed write would describe artifacts nobody can open. The deployment stage reads this
# file rather than rebuilding the choice, which is what keeps the row marked here and the table
# applied there from disagreeing.
arrow::write_parquet(
  x    = catalogue, # one row per task and window
  sink = fs::path(.lP$Output$Table, "catalogue.parquet") # beside the tables it describes
)
```

## The table as an arm

A published table is an artifact, and until now that is all it was: a file with a precision printed on
it, sitting outside the comparison every other arm takes part in. That is a gap rather than a
modesty. The orchestration stage ranks arms on out-of-fold macro-F1 and votes among them, and an arm
it cannot see cannot be ranked, cannot be voted on, and cannot be named in a manifest -- so a voting
set naming this one describes something the manifest is unable to pin.

Closing the gap needs runs, and the runs must estimate the right thing. Scoring the published file
against a fold's held-out documents would score it on documents it was built from: the terms were
selected on the all-data mine and their Power estimated there, and every fold's held-out documents
contributed to both. The number would be optimistic, and it would then sit on a leaderboard beside
transformer arms whose fold scores are genuinely held out.

So what is estimated is the **procedure** -- mine at these axes, select at these floors, decide at this
threshold -- measured on documents the mine never read, exactly as the transformer arm is. The artifact
is the all-data table, exactly as the transformer's artifact is an all-data refit whose weights are
never scored out of fold either. Artifact and estimate are joined by configuration name, computed once
where the table is published and asserted where the runs are written.

The estimate describes the procedure **before** the fold-agreement filter, which can only remove
terms. That gap is the price of a filter that would otherwise let a held-out fold influence its own
selection, and it is stated at the top of this section rather than hidden in a caption.

```{r}
#| label: deploy-check-parity
# Run before the tables become arms, not in Validation, because it is a gate on what follows rather
# than a check on what came before: a run written under a lexicon the applier matches differently is
# worse than no run at all, since it is a plausible number for the wrong system.
tab_parity <- purrr::map(pubs, function(.p) {
  kw_parity_check(
    .pub      = .p, # this task and window
    .mine_dir = .p$Dirs[[1]], # one fold is enough; the tokenisation is not fold-specific
    .docs     = tab_prep, # the text the mine does not carry
    .python   = .lP$Engine$Python, # the interpreter the miner ran under
    .script   = .lP$Engine$ScriptApply # the applier
  )
}) |>
  purrr::list_rbind()
```

```{r}
#| label: deploy-report-parity
kw_report_parity(.tab = tab_parity)
```

The two producers reach the same tokenisation by different routes. The miner transformed the held-out
fold against its full candidate vocabulary while mining; the applier transforms the same documents
against the published lexicon alone. The lexicon is held fixed across both, so a disagreement here is
about matching and never about selection. Terms appearing only on the mine's side mean the applier
under-matches, which is the failure this seam exists to remove; terms appearing only on the applier's
side mean the mine's candidate filters dropped a term the published table still names.

```{r}
#| label: deploy-publish-runs
runs_published <- purrr::map(pubs, function(.p) {
  kw_publish_runs(
    .pub       = .p, # this task and window
    .runs_root = .lP$Output$Runs, # the same root the sweep writes to
    .seed      = .lP$Param$Seed # stamped for parity with the other engines
  )
}) |>
  purrr::list_rbind()
```

They are written to the same run directory as everything else in this document, not to a directory of
their own. A separate root would let the published tables into the orchestration stage's inventory
without passing the fold-coverage filter every other arm passes, and an arm exempt from a filter is
exactly how a configuration estimated on some folds ends up ranked against configurations estimated on
all of them.

```{r}
#| label: deploy-report-runs
runs_published |>
  dplyr::summarise(
    Folds = dplyr::n(),
    Coverage = mean(Coverage),
    Precision = mean(SelPrecision),
    MacroF1 = mean(F1_macro),
    Terms = round(mean(nTerms)),
    Classes = round(mean(nClassesHit)),
    .by = ConfigName
  ) |>
  # Joined back for the labels. The configuration name is the key and is far too long to print, so
  # the table is read by task and window and the name stays where the join needs it.
  dplyr::inner_join(
    catalogue |> dplyr::select(ConfigName, Task, NWords),
    by = dplyr::join_by(ConfigName)
  ) |>
  dplyr::mutate(
    Window    = dplyr::if_else(NWords == 0L, "full", as.character(NWords)),
    Coverage  = tbl_pct(Coverage),
    Precision = tbl_pct(Precision)
  ) |>
  dplyr::arrange(Task, dplyr::desc(MacroF1)) |>
  dplyr::select(Task, Window, Folds, Terms, Classes, Coverage, Precision, MacroF1) |>
  tbl_say(.title = "Out-of-fold estimates for the published configurations")
```

Every row must read five folds. A configuration short of that was estimated on a different quantity
from its neighbours, and a mean over three folds and a mean over five are not comparable however close
they look.


# Overview

```{r}
#| label: overview-report-all
kw_report_all(
  .perf_mines       = perf_mines,
  .perf_sel         = perf_sel,
  .curve            = curve_detailed,
  .tab_pred         = pred_final,
  .tab_lexicon      = kw_default_pub(pubs, catalogue, "ClassDetailed")$Lexicon,
  .label_col        = "ClassDetailed",
  .target_precision = .lP$Param$TargetPrecision[["ClassDetailed"]],
  .min_classes      = .lP$Param$MinClasses[["ClassDetailed"]]
)
```

## What the table pays for its promise

::: {.panel-tabset}

### Per category

```{r}
#| label: fig-perclass-keyword
#| fig-height: !expr plot_height(12)
#| fig-cap: "Per-category F1 for the keyword table at its operating point. The axis is the same fixed
#|   zero-to-one scale the transformer figures use, so the two arms can be compared bar for bar."
clf_plot_perclass(.tab_pred = pred_final)
```

A category with high precision and low recall is one the table labels rarely and reliably, which is
the intended behaviour. A bar at zero is a category the table declines entirely, and that is a finding
about the category rather than a gap to be closed by lowering the bar.

### Where it abstains

```{r}
#| label: fig-confusion-keyword
#| fig-height: !expr plot_height(12, .square = TRUE)
#| fig-cap: "Confusion matrix at the operating point, row-normalised. The rightmost column is the
#|   abstention: the share of each category's documents that no term reached. Reading down that column
#|   shows where the vocabulary runs out."
clf_plot_confusion(
  .tab_pred  = pred_final, # committed and abstained predictions at the operating point
  .normalize = TRUE, # each row sums to one, so the abstention share is directly readable
  .limits    = c(0, 1), # same fill scale as the transformer matrices
  .label_min = 0.005 # a cell below half a percent is drawn but not labelled
)
```

The abstention column is the artifact's honest disclosure. A transformer matrix has no such column
because it must answer; this one does, and the categories with the largest entries there are the ones
a reader applying the table by hand should expect it to stay silent about.

:::

## How the table was chosen

```{r}
#| label: fig-window
#| fig-height: !expr plot_height(7)
#| fig-cap: "Performance against the truncation window. The reference line marks the transformer's
#|   reading window; anything right of it is signal no model in this study sees."
kw_plot_window(
  .tab        = perf_mines, # every mining cell
  .label_col  = "ClassDetailed", # task to plot
  .window_ref = 512L # the transformer's context window, in words
)
```

```{r}
#| label: fig-tau
#| fig-height: !expr plot_height(7)
#| fig-cap: "Precision bought by declining to label. Point area is the number of categories the table
#|   still reaches, which is the constraint that stops the curve being read as free."
kw_plot_tau(
  .curve            = curve_detailed, # one point per evidence threshold
  .target_precision = .lP$Param$TargetPrecision[["ClassDetailed"]] # drawn as a reference line
)
```

## How long a list needs to be

```{r}
#| label: fig-reach
#| fig-height: !expr plot_height(12, .square = TRUE)
#| fig-cap: "Share of each category reached by successive terms, panels in taxonomic order. A curve
#|   flattening early marks the point at which a list stops earning its length; one still climbing at
#|   the last term marks a category the list was truncated before covering. An empty panel is a
#|   category for which the mining found no publishable term at all."
kw_plot_reach(
  .tab = kw_default_pub(.pubs = pubs, .catalogue = catalogue, .label_col = "ClassDetailed")$Lexicon,
  .key = "ClassDetailed" # panels follow the registered taxonomic order
)
```

# Next

03E ranks every arm on one leaderboard and searches for a routing policy among them. The published
tables now enter it on the same terms as the transformer configurations: run folders under a
configuration name, five folds each, joined to the artifact this document wrote. That is what lets a
voting set name the keyword arm and the manifest pin what it named -- until now it could do the first
and not the second, so no confidence flag could ship.

03F applies the manifest to the corpus. It calls the same applier this document calls and the same
decision this document decides with, through the parameters pinned in the catalogue, so the precision
printed on a table is the precision it realises on 1.4 million documents rather than a number about a
similar system.

The tables also ship as artifacts in their own right, alongside the archived dataset, which is what
they were built for and remains the reason the objective here is publishable precision rather than
aggregate accuracy.
