---
title: "Contract Classification -- Orchestration & Routing (03D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = FALSE, warning = FALSE)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_Format.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

# 03D consumes the whole stack: 03A (prep + scoring + plots), 03B (BERT per-doc
# classification + crowned config), 03C (the keyword gate). Source all three, then
# this file. None are re-run -- 03D reads the predictions they already wrote.
for (.s in c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword")) {
  cat(.s, "function file: ")
  print(.p <- init_create_script_fun(here::here(), .s))
  source(.p)
}

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

# What 03D is

03D is the **orchestrator**. 03B and 03C each produced pooled out-of-fold
predictions on the *identical* frozen folds; 03D takes both and asks the one
question it exists to answer: **does routing between BERT and keyword (or an LLM
tiebreak on the hard cases) beat just running BERT everywhere?**

The honest prior is *no, or barely*. The head-to-head (03B vs 03C) showed BERT
winning every class, so per-class accuracy routing has little to route toward. That
makes 03D a **methods experiment, not an accuracy grab** -- and a clean null is the
finding. This document is built to make that test legible: it states the incumbent
(BERT), an unattainable ceiling (oracle), and what every *deployable* router
actually scores against the incumbent.

Nothing here retrains. Every number is read off the predictions on disk, scored
through 03A's shared `clf_scores` / `clf_perclass` so it is directly comparable with
03B and 03C. The single exception is the optional Ollama tiebreak (last section),
which adjudicates only the disagreement residue.

Three routers are deployable -- **BERT-everywhere** (baseline), **agreement +
tiebreak**, and **selective keyword + BERT backfill** -- and one is a diagnostic
**ceiling** (oracle per-class, which peeks at the true label to bound what routing
could ever buy).

## Paths

`prepared.parquet` and both runs roots come from the upstream scripts' own
directories (same path construction they wrote with, so they always match).
`clf_load_overall(c(bert, kw))` binds both method families into one leaderboard.

```{r}
.dir_prep <- init_create_script_dir(here::here(), "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(here::here(), "03B-ClassifyTrainBERT")
.dir_kw   <- init_create_script_dir(here::here(), "03C-ClassifyTrainKeyword")

.lP <- list(
  Input = list(
    Prepared = utils_file_path(.dir_prep, "prepared.parquet")
  ),
  Runs = list(
    Bert = utils_file_path(.dir_bert, "runs"),
    Kw   = utils_file_path(.dir_kw,   "runs")
  ),
  Output = list(
    OllamaCache = utils_file_path(.dir_main, "_ollama_cache")
  )
)
```

```{r}
tab_prep    <- arrow::read_parquet(.lP$Input$Prepared)
tab_overall <- clf_cache("orch_overall",
  clf_load_overall(c(.lP$Runs$Bert, .lP$Runs$Kw)))
```

The two configs 03D routes between: the crowned BERT config (03B) and the best
keyword config (03C), both for `ClassDetailed`.

```{r}
best_bert <- bert_crowned_config(tab_overall, "ClassDetailed")$config_name
best_kw   <- kw_leaderboard(dplyr::filter(tab_overall, LabelCol == "ClassDetailed")) |>
  dplyr::slice(1) |>
  dplyr::pull(ConfigName)

tibble::tibble(Method = c("BERT", "Keyword"), ConfigName = c(best_bert, best_kw)) |>
  fmt_table(.caption = "Configs 03D routes between")
```

# Assemble the routing table

One row per document, both methods side by side: BERT's argmax label with its
confidence (`Top1Prob`, `Margin`), keyword's argmax label with its `Score`, and the
`Agree` flag. Because both tracks ran identical folds, the join is one-to-one; a
shortfall would warn rather than silently drop docs.

```{r}
tab_route <- clf_cache(
  paste0("orch_route__", best_bert, "__", best_kw),
  orch_assemble(c(.lP$Runs$Bert, .lP$Runs$Kw), best_bert, best_kw, tab_prep)
)
tab_route |> dplyr::slice_head(n = 8) |>
  fmt_table(.caption = "Assembled routing table (head)", .digits = 3, .wide = TRUE)
```

# Per-class head-to-head

The table 03D rests on. Per-class F1 for each method on identical folds, with the
winner and the gap. If BERT wins every row (the expected case), accuracy routing
cannot help and the deployable routers below are predicted to tie BERT. Keyword's
strict F1 here counts an abstention as a miss -- its high-precision contribution is
the *selective* story further down, not this aggregate.

```{r}
compare_pc <- clf_cache(
  paste0("orch_perclass__", best_bert, "__", best_kw),
  orch_perclass_compare(c(.lP$Runs$Bert, .lP$Runs$Kw), best_bert, best_kw)
)
compare_pc |> fmt_table(
  .caption = "Per-class F1: BERT vs keyword (winner and gap)",
  .digits = 3
)
```

```{r}
winners <- orch_winner_map(compare_pc)
```

# Agreement and the residue

How often do the two methods agree, how accurate is each set, and -- on the docs
they dispute -- who is right more often? If BERT is right far more often than
keyword on the residue, the safe default (keep BERT) is already near-optimal there
and a tiebreak has little headroom. This is the diagnostic that predicts, before any
routing is scored, whether 03D can move the number.

```{r}
orch_agreement_summary(tab_route) |>
  fmt_table(.caption = "Agreement vs residue: share, best-of-two accuracy, who is right",
            .digits = 3, .pct = c("Share", "EitherAcc", "BertRight", "KwRight"))
```

The residue itself -- the only documents any tiebreak can change -- carried with
both candidate labels and BERT's confidence:

```{r}
residue <- orch_disagreement_set(tab_route)
cli::cli_alert_info("Residue: {nrow(residue)} of {nrow(tab_route)} docs")
residue |> dplyr::slice_head(n = 10) |>
  fmt_table(.caption = "Disagreement residue (head)", .digits = 3)
```

# The selective keyword layer (from 03C)

Rebuild 03C's high-precision keyword gate so the selective router can use it:
calibrate a per-class cutoff to 95% precision, then gate. Whatever this layer
commits to, keyword owns; BERT backfills the rest.

```{r}
pred_kw <- clf_cache(
  paste0("orch_kwpred__", best_kw),
  clf_pool_predictions(c(.lP$Runs$Bert, .lP$Runs$Kw), best_kw)
)
calib   <- kw_calibrate(pred_kw, .target_precision = 0.95, .min_keep = 5L)
thr_    <- calib |> dplyr::select(Label, Threshold) |> tibble::deframe()
pred_hi <- kw_gate(pred_kw, thr_)

kw_selective_summary(pred_hi) |>
  fmt_table(.caption = "High-precision keyword layer (per-class gated)",
            .pct = c("Coverage", "SelAccuracy"))
```

A high selective accuracy only matters relative to **what BERT scores on the very
same documents the gate kept**. Because an easy, prototypical contract is easy for
both methods, keyword's confident subset overlaps BERT's confident subset -- so the
honest test is the head-to-head on the keyword-owned partition, not the gate's
accuracy against BERT's *global* number. If BERT wins the Keyword-owned row, handing
those docs to keyword strictly loses, which is exactly why the selective router
cannot clear BERT-everywhere.

```{r}
orch_subset_compare(tab_route, pred_hi) |>
  fmt_table(.caption = "BERT vs keyword on the gate's own subset (KwAcc NA where keyword abstained)",
            .digits = 3, .pct = c("Share", "KwAcc", "BertAcc", "Gap"))
```

## Does a margin-based gate change the verdict?

The `Score` the gate above thresholds on is the engine's fold-normalised MAX class
score -- a *between-document* magnitude (how much class-exclusive vocabulary a doc
carries), not a *within-document* separation. The sharper selective signal is the
**margin**: top-1 minus top-2 class score, i.e. how decisively the winning class beats
the runner-up for *this* document. `kw_load_confidence` rebuilds the keyword
predictions with `Score` swapped for the scale-free relative margin, so the *same*
`kw_calibrate` -> `kw_gate` -> `orch_subset_compare` runs on it unchanged. If even a
margin-built gate cannot win its own covered subset, the null is robust to how keyword
confidence is defined.

```{r}
pred_kw_mr <- clf_cache(
  paste0("orch_kwpred_mr__", best_kw),
  kw_load_confidence(c(.lP$Runs$Bert, .lP$Runs$Kw), best_kw, .which = "marginrel")
)
calib_mr   <- kw_calibrate(pred_kw_mr, .target_precision = 0.95, .min_keep = 5L)
thr_mr     <- calib_mr |> dplyr::select(Label, Threshold) |> tibble::deframe()
pred_hi_mr <- kw_gate(pred_kw_mr, thr_mr)

kw_selective_summary(pred_hi_mr) |>
  fmt_table(.caption = "High-precision keyword layer, margin-gated",
            .pct = c("Coverage", "SelAccuracy"))
```

```{r}
orch_subset_compare(tab_route, pred_hi_mr) |>
  fmt_table(.caption = "Margin gate -- BERT vs keyword on the gate's own subset",
            .digits = 3, .pct = c("Share", "KwAcc", "BertAcc", "Gap"))
```

Read the `Gap` column (BertAcc - KwAcc on the keyword-owned partition) against the
max-score gate's table just above. If both stay positive, BERT wins the covered subset
no matter how keyword confidence is defined, and the selective router cannot clear
BERT-everywhere -- the null holds. A `Gap` that flips negative under the margin gate is
the one result worth chasing: it would mean the keyword arm finally isolates a subset
it wins, at which point the per-class calibration should be nested inside the folds
(calibrate on the training folds' out-of-fold predictions, apply to the held-out one)
before the gain is reported.

# Per-source escalation: can desc or text win a subset?

The tests above route BERT against the *overall* best keyword config. The escalation
idea is different: hand each **source arm** its own high-precision gate and ask whether
the clean, low-N `docdesc` arm -- or the body `text` arm -- owns a subset on which it
beats BERT. `kw_pick_source_configs` (03C) gives the best config per source; each is
gated at marginrel + 95% per-class precision and overlaid on the same routing spine
(`orch_subset_compare` reads only BERT's side from `tab_route`, so a different source's
gate is a valid overlay).

Read the `Gap` column -- BertAcc minus KwAcc on each arm's keyword-owned subset.
`Gap > 0` on every arm means no source, however clean, carves a subset it wins: the
desc -> text -> BERT cascade is dead on arrival and a single transformer suffices. A
`Gap < 0` on the desc arm is the one result that would justify building the 3-tier
router -- and then the per-class calibration should be nested inside the folds before
the gain is reported.

```{r}
src_cfgs <- kw_pick_source_configs(tab_overall, "ClassDetailed")

escalation <- src_cfgs |>
  dplyr::mutate(
    Owned = purrr::map(.data$ConfigName, function(cfg_) {
      clf_cache(paste0("orch_esc__", cfg_), {
        pred_  <- kw_load_confidence(c(.lP$Runs$Bert, .lP$Runs$Kw), cfg_, .which = "marginrel")
        calib_ <- kw_calibrate(pred_, .target_precision = 0.95, .min_keep = 5L)
        thr_   <- stats::setNames(calib_$Threshold, calib_$Label)
        gated_ <- kw_gate(pred_, thr_)
        orch_subset_compare(tab_route, gated_) |>
          dplyr::filter(.data$Owner == "Keyword-owned") |>
          dplyr::select(NDocs, Share, KwAcc, BertAcc, Gap)
      })
    })
  ) |>
  dplyr::select(Source, ConfigName, Owned) |>
  tidyr::unnest(Owned)

escalation |>
  fmt_table(
    .caption = "Per-source escalation: BERT vs each source arm on the arm's own gated subset",
    .digits = 3, .pct = c("Share", "KwAcc", "BertAcc", "Gap")
  )
```

# Router comparison (the headline)

Every router scored through the shared layer, with its deployability flag and the
delta against BERT-everywhere. A near-zero or negative delta on every *deployable*
router is the clean null the head-to-head predicts; the oracle ceiling shows the
most any per-class routing could have bought.

```{r}
compare_routers <- orch_compare(
  tab_route,
  .winners  = winners,
  .kw_gated = pred_hi
)
compare_routers |> fmt_table(
  .caption = "Routers vs BERT-everywhere (DeltaMacroF1 against the incumbent)",
  .digits = 3, .pct = c("Accuracy", "MacroF1", "Coverage")
)
```

```{r}
#| fig-cap: "Macro-F1 per router. Dashed line = BERT-everywhere; hollow = oracle ceiling (not deployable)."
orch_plot_compare(compare_routers)
```

# Optional: Ollama tiebreak on the residue

The last lever. Only the disagreement residue can change, so qwen3:32b is asked to
adjudicate *only those docs* -- shown the contract header (signal is front-loaded,
so the opening pages are enough and far cheaper than the full text) and the two
candidate labels, constrained to a JSON answer that must be one of the two, at
temperature 0. Every answer is hash-cached, so an interrupted pass resumes for free.

This is the one expensive chunk in 03D (a process spawn per disputed doc). It is
written to run as-is once a local Ollama is up; until then, leave it for the
dedicated pass. The result feeds `orch_route_agreement(.tiebreak = "ollama")`, and
re-running `orch_compare` with `.ollama_pred` adds the "Agreement + Ollama" row.

```{r}
#| eval: false
ollama_pred <- orch_ollama_tiebreak(
  residue, tab_prep,
  .cache_dir = .lP$Output$OllamaCache,
  .model = "qwen3:32b",
  .header_chars = 4000L
)

compare_all <- orch_compare(
  tab_route,
  .winners     = winners,
  .kw_gated    = pred_hi,
  .ollama_pred = ollama_pred
)
compare_all |> fmt_table(
  .caption = "Routers incl. the Ollama tiebreak",
  .digits = 3, .pct = c("Accuracy", "MacroF1", "Coverage")
)
```

# Next

03D's verdict is the router comparison table: most likely a null on the deployable
routers, with the oracle ceiling quantifying the unrealised headroom. Whatever the
outcome, it is a clean methods result -- routing was tested, not assumed.

- **Read the verdict into the paper.** If deployable routers tie BERT, the finding
  is "a single fine-tuned transformer is sufficient; routing and an LLM tiebreak add
  nothing measurable" -- a genuine contribution, since it rules out a plausible-
  sounding architecture.
- **03E -- apply.** The deployable model is BERT's `--fit-final` artifact from 03B
  (the router did not displace it). 03E loads it and labels the full corpus.
- **Lenient / round-sliced robustness.** `orch_compare(.lenient = TRUE)` and a
  LabelRound split would confirm the verdict holds on the gold (Round2) slice.
```
