---
title: "Contract Classification -- Routing Between the Arms (03D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                          # message = FALSE would discard this document's entire output
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,        # fixed for every figure; only height varies, and only with row count
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# This document consumes the whole stack. 03A owns the folds and the shared scoring layer, 03B the
# transformer predictions and the per-document probability vectors, 03C the keyword runs. Sourcing
# all three means every number below is produced by the same scoring code that produced theirs;
# nothing here is re-estimated.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/03D-ClassifyOrchestrate.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Two classifiers have been estimated on the same documents and the same folds. The transformer labels
every document; the keyword table labels only those carrying a term it trusts, and declines the rest.
An obvious question follows, and it is the one this document answers for each of the three tasks:
does a rule sending each document to whichever arm handles it best beat simply using the transformer
everywhere?

The question is easy to ask and easy to answer badly. There are a few dozen plausible routing rules,
they are separated by a fraction of a percentage point, and the sample holds 4,400 documents.
Enumerating the rules on those documents and reporting the winner would produce a number that is part
routing and part search, with no way to tell which.

So the rule is chosen the way every other decision in this pipeline is made -- inside the folds. For
each fold in turn, every rule is ranked on the other four and the winner is applied to the fifth. No
document contributes to choosing the rule that labels it. What the results report is the performance
of the **procedure**: what a reader who ran this selection would obtain.

## What counts as an arm

An **arm** is one source of per-document predictions scored on the shared folds. Arms differ in one
respect that governs everything else: whether they can decline. The transformer always commits. A
keyword arm commits only where a term clears its evidence threshold. Only an always-committing arm
can end a cascade, because every document must leave with a label.

A **policy** is an ordered list of abstaining arms, a floor applied within each, and a terminal arm
that catches the rest. Two families are searched. The **cascade** family honours every commitment
clearing the floor. The **per-class** family honours a commitment only for categories where that arm
beat the terminal on the training folds -- the deployable counterpart of an oracle, since the
decision uses training labels only.

## Ties are resolved toward doing nothing

A strict ranking crowns whichever rule leads in the fourth decimal, which on this sample is a
rounding artifact. Left alone it makes the fold-level winner change for no reason and writes a
deployment artifact that contradicts the document's own conclusion. So every ranking here resolves
through a tolerance: among rules within `Tolerance` macro-F1 of the best, the one **routing the
fewest documents** is taken. The incumbent routes none and therefore wins every tie by construction,
and routing has to earn its place by a margin the sample can measure. 03C applies the same principle
to precision when it chooses a keyword configuration.

## Amendment needs a decision, not a workaround

For `AmendType` the keyword engine mines the positive class only and assigns `Original` wherever no
amendment term fired. That label is the absence of evidence wearing the name of a class: coverage
reads as complete, the arm looks like a terminal, and the cascade space collapses to "pick one
method". 03C states the asymmetry in its own bundle script -- *Original is defined by the absence of
amendment language*.

Naming the labels that count as commitments repairs it. The keyword arm commits to `Amended` and
abstains otherwise, and the routing question becomes the real one: if an amendment term fires, call
it amended, otherwise ask the transformer. 03B predicts this fails, because *amended and restated*
titles many genuine originals. It is now testable rather than assumed.

## Which arms may enter the search

Not all of them. The mined keyword arms were estimated on all five folds; arms scored from a written
term list were not, because the reading session that produced the list read folds one to four **with
their labels**. An arm existing on one fold cannot enter a five-fold nested search without
contaminating four of the five rankings. Those arms are held back and evaluated in Robustness, on the
fold they are entitled to.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(.dir_here = here::here(), .name_script = "03B-ClassifyTrainBERT")
.dir_kw   <- init_create_script_dir(.dir_here = here::here(), .name_script = "03C-ClassifyTrainKeyword")

.lP <- list(
  Input = list(
    # Paths are rebuilt through the same helper the upstream scripts wrote with, so they cannot drift
    # from where the files actually landed.
    Prepared = utils_file_path(.dir_prep, "prepared.parquet")
  ),
  Runs = list(
    Bert = utils_file_path(.dir_bert, "runs"), # written by 03B
    Kw   = utils_file_path(.dir_kw,   "runs")  # written by 03C
  ),
  Output = list(
    Policy = utils_file_path(.dir_main, "policy") # the deployment decisions 03E reads
  ),
  Param = list(
    Floors    = c(0, 0.70, 0.80, 0.90), # score floors crossed into the policy grid
    MaxDepth  = 2L,                     # longest cascade of abstaining arms
    Families  = c("cascade", "perclass"), # gating families searched
    Folds     = 5L,                     # folds an arm must cover to enter the nested search
    Holdout   = 5L,                     # the fold a written term list never read
    Tolerance = 0.005                   # macro-F1 band treated as indistinguishable
  )
)
```

The tolerance is set below half the fold-level spread 03B reports for the leading transformer
configurations. It is a claim about measurement, not a preference: differences smaller than this are
inside the noise of a 4,400-document five-fold estimate, so resolving them by argmax reports the
resolution of the arithmetic rather than anything about the classifiers.

Nothing in this document is cached. Every step is a join over a few thousand rows and the whole
search completes in seconds, so a cache would buy no time while introducing the one failure this
pipeline has already been bitten by: a key naming a computation rather than fingerprinting its input.

```{r}
#| label: load-prepared-sample
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)
```

# The hierarchy

The broad taxonomy is a strict roll-up of the detailed one, so each level could in principle
constrain the other. 03B already guarantees a *consistent* published hierarchy by deriving the broad
label from the detailed prediction, so what is at stake here is accuracy, not consistency.

One number bounds what a broad-level constraint could buy, and it is worth stating the expectation
before reading it. 03B reports that detailed errors concentrate in substantively adjacent category
pairs. If those pairs share a broad parent, the broad prediction was already right on the documents
the detailed model got wrong and constraining the detailed decision cannot reach them.

```{r}
#| label: hierarchy-errors
tab_overall <- clf_load_overall(.runs_roots = .lP$Runs$Bert)

pred_det <- bert_best_predictions(
  .tab_overall = tab_overall,    # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert,  # run folders to pool from
  .label_col   = "ClassDetailed" # task
)

pred_broad <- bert_best_predictions(
  .tab_overall = tab_overall,   # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_col   = "ClassBroad"   # task
)

orch_report_hierarchy(
  .tab = orch_hierarchy_errors(
    .tab_pred = pred_det, # pooled out-of-fold detailed predictions
    .tab_prep = tab_prep  # supplies the detailed-to-broad mapping
  )
)
```

Reachable headroom is not the same as realisable headroom, and the two are separated by the broad
model's own error rate: every document where the constraint is imposed on a wrong parent is a
document the constraint breaks. Both directions are therefore built as arms and made to compete
rather than argued about. The detailed task gets `bert-hier`, whose detailed choice is restricted to
the predicted parent's children. The broad task gets `bert-rollup`, the detailed prediction's parent,
which is the route 03B actually deploys and so the strongest thing in the broad search to beat.

```{r}
#| label: build-derived-arms
class_det <- bert_classification(
  .runs_roots  = .lP$Runs$Bert,                                                    # run folders
  .config_name = bert_best_config(.tab_overall = tab_overall, .label_col = "ClassDetailed"),
  .tab_prep    = tab_prep                                                          # document metadata
)

arm_hier <- orch_arm_hierarchical(
  .class_detailed = class_det,  # carries the P_<Class> probability vector
  .pred_broad     = pred_broad, # the constraint
  .tab_prep       = tab_prep,   # supplies the mapping
  .arm            = "bert-hier" # name it carries through the search
)

arm_rollup <- orch_arm_rollup(
  .pred_detailed = pred_det,      # pooled detailed predictions
  .tab_prep      = tab_prep,      # supplies the mapping
  .arm           = "bert-rollup"  # name it carries through the search
)
```

# Selection

Each task is run end to end by the same call. The rules a reader would want to check are named
arguments rather than constants inside the function: how many folds an arm must cover, which labels
count as commitments, how wide the search is, and what counts as a tie.

## Detailed taxonomy

```{r}
#| label: run-detailed
res_det <- orch_run_task(
  .runs_roots  = c(.lP$Runs$Bert, .lP$Runs$Kw), # both trees; the run schema is shared
  .label_col   = "ClassDetailed",               # task
  .tab_prep    = tab_prep,                      # prepared sample
  .extra_arms  = arm_hier,                      # the broad-constrained transformer
  .floors      = .lP$Param$Floors,              # score floors to cross in
  .max_depth   = .lP$Param$MaxDepth,            # longest cascade
  .families    = .lP$Param$Families,            # gating families
  .commit_only = NULL,                          # every label is a commitment on a categorical task
  .n_folds     = .lP$Param$Folds,               # folds required to enter the nested search
  .tolerance   = .lP$Param$Tolerance,           # macro-F1 band treated as a tie
  .lenient     = FALSE,                         # strict scoring; leniency is a robustness slice
  .carry       = c("ClassDetailed2", "LabelRound") # columns the robustness slices need
)
```

```{r}
#| label: report-detailed-arms
orch_report_arms(
  .tab       = res_det$Arms,      # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_det$LabelCol   # task, for the heading
)
```

```{r}
#| label: report-detailed-spine
orch_report_spine(.spine = res_det$Spine)
```

```{r}
#| label: report-detailed-stability
orch_report_stability(.tab_nested = res_det$Nested)
```

## Broad taxonomy

```{r}
#| label: run-broad
res_broad <- orch_run_task(
  .runs_roots  = c(.lP$Runs$Bert, .lP$Runs$Kw), # both trees
  .label_col   = "ClassBroad",                  # task
  .tab_prep    = tab_prep,                      # prepared sample
  .extra_arms  = arm_rollup,                    # the rolled-up detailed prediction
  .floors      = .lP$Param$Floors,              # unchanged
  .max_depth   = .lP$Param$MaxDepth,            # unchanged
  .families    = .lP$Param$Families,            # unchanged
  .commit_only = NULL,                          # categorical task
  .n_folds     = .lP$Param$Folds,               # unchanged
  .tolerance   = .lP$Param$Tolerance,           # unchanged
  .lenient     = FALSE,                         # strict scoring
  .carry       = "LabelRound"                   # ClassDetailed2 is a detailed label; useless here
)
```

```{r}
#| label: report-broad-arms
orch_report_arms(
  .tab       = res_broad$Arms,    # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_broad$LabelCol # task, for the heading
)
```

```{r}
#| label: report-broad-stability
orch_report_stability(.tab_nested = res_broad$Nested)
```

## Amendment

`.commit_only` is the whole difference. Without it the keyword arm reports complete coverage, is
classed as a terminal, and no cascade exists to search over.

```{r}
#| label: run-amendment
res_amend <- orch_run_task(
  .runs_roots  = c(.lP$Runs$Bert, .lP$Runs$Kw), # both trees
  .label_col   = "AmendType",                   # task
  .tab_prep    = tab_prep,                      # prepared sample
  .extra_arms  = NULL,                          # no hierarchy to exploit on a binary task
  .floors      = .lP$Param$Floors,              # unchanged
  .max_depth   = .lP$Param$MaxDepth,            # unchanged
  .families    = .lP$Param$Families,            # unchanged
  .commit_only = "Amended",                     # "Original" is the absence of evidence, not a label
  .n_folds     = .lP$Param$Folds,               # unchanged
  .tolerance   = .lP$Param$Tolerance,           # unchanged
  .lenient     = FALSE,                         # strict scoring
  .carry       = "LabelRound"                   # dual labels do not apply to a binary task
)
```

```{r}
#| label: report-amendment-arms
orch_report_arms(
  .tab       = res_amend$Arms,    # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_amend$LabelCol # task, for the heading
)
```

```{r}
#| label: report-amendment-stability
orch_report_stability(.tab_nested = res_amend$Nested)
```

The coverage the keyword arm reports here is the share of documents in which an amendment term fired
at all. Read it against 03B's finding: if that share is large and its selective precision is modest,
the arm is firing on originals, which is exactly the failure that made a transformer necessary.

# Results

```{r}
#| label: results-verdicts
verdicts <- orch_verdicts(.results = list(res_det, res_broad, res_amend))
orch_report_verdicts(.tab = verdicts)
```

The `Moved` column is the one to read first. A procedure that moved no documents did not fail to find
a gain; it declined to route, on every fold, and the tolerance is what let it. A procedure that moved
many documents for a delta near zero found real structure and traded it away, which reads differently
in the text and is visible only in the movement table below.

## Detailed taxonomy

```{r}
#| label: results-detailed-compare
orch_report_compare(.tab = res_det$Compare, .title = "ClassDetailed")
```

```{r}
#| label: results-detailed-movement
orch_report_movement(.tab = res_det$Movement)
```

```{r}
#| label: results-detailed-perclass
clf_report_perclass(
  .tab_pred = res_det$Nested,                          # routed, held-out predictions
  .title    = "Routed procedure -- per category"       # heading
)
```

Per-category scores are where a null aggregate becomes informative or stays inert. Routing that
leaves macro-F1 unchanged while lifting one thin category and depressing another has found structure
and traded it away; routing that leaves every category where it was has found nothing.

## Broad taxonomy

```{r}
#| label: results-broad-compare
orch_report_compare(.tab = res_broad$Compare, .title = "ClassBroad")
```

```{r}
#| label: results-broad-movement
orch_report_movement(.tab = res_broad$Movement)
```

## Amendment

```{r}
#| label: results-amendment-compare
orch_report_compare(.tab = res_amend$Compare, .title = "AmendType")
```

```{r}
#| label: results-amendment-movement
orch_report_movement(.tab = res_amend$Movement)
```

```{r}
#| label: results-amendment-confusion
clf_say_table(
  .tab   = clf_confusion(.tab_pred = res_amend$Nested), # routed labels against the truth
  .title = "Amendment -- confusion after routing"       # heading
)
```

# Validation

The routed labels must not contradict each other across taxonomy levels in a released dataset. Rolling
the routed detailed prediction up to its parent and scoring it at the broad level says whether routing
broke the property 03B established, and whether the routed detailed labels remain at least as good a
route to the broad taxonomy as the broad task's own output.

```{r}
#| label: validation-hierarchy
dplyr::bind_rows(
  clf_scores(
    .tab_pred = clf_rollup_to_broad(
      .tab_pred = res_det$Nested, # routed detailed predictions
      .tab_prep = tab_prep        # supplies the detailed-to-broad mapping
    )
  ) |>
    dplyr::mutate(Route = "Routed detailed, rolled up", .before = 1),
  clf_scores(
    .tab_pred = clf_rollup_to_broad(.tab_pred = pred_det, .tab_prep = tab_prep)
  ) |>
    dplyr::mutate(Route = "Transformer detailed, rolled up", .before = 1),
  clf_scores(.tab_pred = res_broad$Nested) |>
    dplyr::mutate(Route = "Routed broad, direct", .before = 1),
  clf_scores(.tab_pred = pred_broad) |>
    dplyr::mutate(Route = "Transformer broad, direct", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  clf_say_table(.title = "Four routes to the broad taxonomy, all scored at the broad level")
```

Four routes converging within noise is the substantive finding, not a null: it says the two taxonomy
levels carry the same information and neither improves the other. That turns 03B's decision to derive
the published broad label by roll-up from a consistency argument into a measured one.

# Robustness

## The curated arms, on the fold they are entitled to

Arms scored from a written term list read folds one to four with their labels, so the fifth fold is
their only honest test. The check is paired: the same selection runs on the same fold-five documents
with and without those arms available, so the two cascades are compared on identical rows.

The comparison is deliberately bounded. One fold holds roughly a fifth of the sample and the keyword
arms abstain on much of it, so only a large difference would be visible. A null here says the curated
terms did not change the ordering on the documents available to test them, and no more than that.

```{r}
#| label: robustness-curated-arms
# Start from the spine the headline used, restricted to the holdout fold, so the derived arm is
# present here too and the two cascades differ only in the curated arms.
spine_hold <- res_det$Spine |>
  dplyr::filter(Fold == .lP$Param$Holdout)

if (nrow(res_det$ArmsHeld) > 0L) {
  spine_hold <- dplyr::bind_rows(
    spine_hold,
    orch_spine(
      .runs_roots = c(.lP$Runs$Bert, .lP$Runs$Kw), # both trees
      .arms       = res_det$ArmsHeld,              # the fold-restricted arms
      .tab_prep   = tab_prep                       # document-level columns
    ) |>
      dplyr::filter(Fold == .lP$Param$Holdout)
  )
}

# Only arms actually committing on this fold can be gated; one absent from these rows would
# contribute nothing and make the comparison look like a null it did not earn.
roles_hold <- orch_roles(.spine = spine_hold)

policies_hold <- orch_policy_grid(
  .arms_gated = roles_hold$Arm[roles_hold$Role == "gated"],    # curated arms included
  .terminals  = roles_hold$Arm[roles_hold$Role == "terminal"], # unchanged
  .floors     = .lP$Param$Floors,                              # unchanged
  .max_depth  = .lP$Param$MaxDepth,                            # unchanged
  .families   = .lP$Param$Families                             # unchanged
)

dplyr::bind_rows(
  orch_score_policies(.spine = spine_hold, .policies = res_det$Policies) |>
    orch_pick_policy(.tolerance = .lP$Param$Tolerance) |>
    dplyr::mutate(Arms = "Mined arms only", .before = 1),
  orch_score_policies(.spine = spine_hold, .policies = policies_hold) |>
    orch_pick_policy(.tolerance = .lP$Param$Tolerance) |>
    dplyr::mutate(Arms = "Mined plus curated", .before = 1)
) |>
  dplyr::mutate(Accuracy = clf_pct(Accuracy), MacroF1 = sprintf("%.3f", MacroF1)) |>
  dplyr::select(Arms, Label, Accuracy, MacroF1, nRouted) |>
  clf_say_table(.title = "Holdout fold: does hand curation change the best cascade?")
```

With no fold-restricted arms on disk, the two rows are identical by construction and the check is
inert rather than wrong. It becomes informative as soon as a curated term list exists.

## Lenient scoring

A minority of documents carry a second valid category. Scoring the routed detailed labels leniently
asks whether predictions counted as wrong were in fact the document's other valid answer -- a rule
that appears to break labels may only be choosing the second valid one. The check applies to the
detailed task alone, since `ClassDetailed2` is a detailed label.

```{r}
#| label: robustness-lenient
dplyr::bind_rows(
  clf_scores(.tab_pred = res_det$Nested, .lenient = FALSE) |>
    dplyr::mutate(Scoring = "Strict", .before = 1),
  clf_scores(.tab_pred = res_det$Nested, .lenient = TRUE) |>
    dplyr::mutate(Scoring = "Lenient", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  clf_say_table(.title = "Routed detailed procedure under strict and lenient scoring")
```

## Label provenance

The second labelling round is the harder subset rather than a random sample, so a rule helping only
on the first round would be exploiting the easier documents.

```{r}
#| label: robustness-label-round
purrr::map(
  .x = list(res_det, res_broad, res_amend),
  .f = function(.r) {
    dplyr::bind_rows(
      clf_scores(.tab_pred = .r$Nested) |>
        dplyr::mutate(Labels = "Both rounds", .before = 1),
      clf_scores(.tab_pred = dplyr::filter(.r$Nested, LabelRound == "Round2")) |>
        dplyr::mutate(Labels = "Round 2 only", .before = 1)
    ) |>
      dplyr::mutate(LabelCol = .r$LabelCol, .before = 1)
  }
) |>
  purrr::list_rbind() |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  dplyr::select(LabelCol, Labels, Accuracy, F1_macro, N) |>
  clf_say_table(.title = "Routed procedures by label provenance")
```

# Deployment

The folds paid for the estimate; the full sample produces the artifact. The policy deployed is the one
the same selection crowns with every fold available, under the same tolerance, so the artifact cannot
contradict the document's own conclusion by preferring a fourth-decimal winner.

```{r}
#| label: deploy-leaderboards
purrr::map(
  .x = list(res_det, res_broad, res_amend),
  .f = function(.r) {
    .r$Final$Rank |>
      head(5) |>
      dplyr::mutate(LabelCol = .r$LabelCol, .before = 1)
  }
) |>
  purrr::list_rbind() |>
  dplyr::mutate(Accuracy = clf_pct(Accuracy), MacroF1 = sprintf("%.3f", MacroF1)) |>
  dplyr::select(LabelCol, Label, Accuracy, MacroF1, nRouted) |>
  clf_say_table(.title = "All-fold leaderboards, top five per task")
```

```{r}
#| label: deploy-save-policies
purrr::walk2(
  .x = list(res_det, res_broad, res_amend),
  .y = list(NULL, NULL, "Amended"), # what each task let a keyword arm commit to
  .f = function(.r, .commit) {
    orch_save_policy(
      .final       = .r$Final,        # chosen policy plus its per-class gate
      .arms        = .r$Arms,         # records the ConfigName behind each arm name
      .label_col   = .r$LabelCol,     # the task this policy applies to
      .dir         = .lP$Output$Policy, # destination 03E reads
      .commit_only = .commit,         # recorded so 03E reproduces the same abstention rule
      .stem        = "routing_policy" # file stem
    )
  }
)
```

03E reads these files and applies them. It makes no routing decision of its own: an apply script that
re-derived a policy would be free to re-derive it differently, and the released labels would then
depend on which script last ran.

# Overview

Everything above in one place, per task, followed by the figures. Nothing here is new.

```{r}
#| label: overview-verdicts
orch_report_verdicts(.tab = verdicts)
```

::: {.panel-tabset}

## Detailed

```{r}
#| label: overview-report-detailed
orch_report_all(.res = res_det, .n_folds = .lP$Param$Folds)
```

## Broad

```{r}
#| label: overview-report-broad
orch_report_all(.res = res_broad, .n_folds = .lP$Param$Folds)
```

## Amendment

```{r}
#| label: overview-report-amendment
orch_report_all(.res = res_amend, .n_folds = .lP$Param$Folds)
```

:::

## Strategies compared

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-compare-detailed
#| fig-height: 3.4
#| fig-cap: "Macro-F1 by strategy, detailed taxonomy. The dashed line is the incumbent; the hollow
#|   bar was selected and scored on the same documents and is not obtainable by running the procedure."
orch_plot_compare(.compare = res_det$Compare)
```

### Broad

```{r}
#| label: fig-compare-broad
#| fig-height: 3.4
#| fig-cap: "Macro-F1 by strategy, broad taxonomy."
orch_plot_compare(.compare = res_broad$Compare)
```

### Amendment

```{r}
#| label: fig-compare-amendment
#| fig-height: 2.4
#| fig-cap: "Macro-F1 by strategy, amendment task."
orch_plot_compare(.compare = res_amend$Compare)
```

:::

## How much each fold actually routed

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-stability-detailed
#| fig-height: 2.4
#| fig-cap: "Documents the crowned policy moved away from the terminal, per held-out fold. A fold at
#|   zero ran the incumbent whatever its winning policy was called."
orch_plot_stability(.tab_nested = res_det$Nested)
```

### Broad

```{r}
#| label: fig-stability-broad
#| fig-height: 2.4
#| fig-cap: "Documents routed per held-out fold, broad taxonomy."
orch_plot_stability(.tab_nested = res_broad$Nested)
```

### Amendment

```{r}
#| label: fig-stability-amendment
#| fig-height: 2.4
#| fig-cap: "Documents routed per held-out fold, amendment task."
orch_plot_stability(.tab_nested = res_amend$Nested)
```

:::

## Per-category performance after routing

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-perclass-detailed
#| fig-height: 4.6
#| fig-cap: "Per-category F1 for the routed procedure, detailed taxonomy."
clf_plot_perclass(.tab_pred = res_det$Nested)
```

### Broad

```{r}
#| label: fig-perclass-broad
#| fig-height: 3.4
#| fig-cap: "Per-category F1 for the routed procedure, broad taxonomy."
clf_plot_perclass(.tab_pred = res_broad$Nested)
```

### Amendment

```{r}
#| label: fig-perclass-amendment
#| fig-height: 2.4
#| fig-cap: "Per-category F1 for the routed procedure, amendment task."
clf_plot_perclass(.tab_pred = res_amend$Nested)
```

:::

# Next

`03E` applies the deployed models to the full corpus, reading the routing policies written here rather
than deciding its own. The keyword table remains an independent artifact of 03C: it ships alongside
the archived dataset and does not enter the labelling path, whatever this document concludes about
routing.

One extension needs no change here. Regenerating the curated term lists once per fold would promote
the written-list arms out of Robustness into the nested search proper, at which point the `nFolds`
filter admits them automatically and the mined and curated arms compete on equal terms across all five
folds.
