---
title: "Contract Classification -- Routing Between the Arms (03E)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# Figure geometry is NOT set here -- it is declared once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                         # message = FALSE would discard this document's entire output
  warning  = FALSE,
  comment  = ""          # drops the "##" prefix, so console blocks copy verbatim
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# This document consumes the whole stack. 03A owns the folds, the shared scoring layer and the
# category vocabulary; 03B, 03C and 03D own the arms whose run folders are read here. Sourcing all
# four means every arm is scored by identical code on identical splits and drawn with identical
# category order, which is the only reason their numbers and their figures belong in one table.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword",
         "03D-ClassifyLLM"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # resolves to 1_code/03E-ClassifyOrchestrate.R
))
source(file = .path_fun, encoding = "UTF-8")

# The policy search is five independent problems, one per fold, and nothing crosses between them.
# Workers are separate R sessions that inherit nothing, so the libraries the fold loop needs are
# sourced into each, IN DEPENDENCY ORDER: the design layers first, because the sample script registers
# its taxonomy and aliases the table helpers at source time and throws part-way through the file
# without them.
#
# Only the two libraries the fold loop actually calls are sent. The transformer, keyword and language
# model scripts are what produced the run folders this document reads; none of their functions runs
# inside a fold, and sourcing them into a worker would add failure surface for nothing.
.workers <- orch_daemons(
  .sources = c(
    here::here("1_code", "_Commons", "_Plots.R"),    # registry, consumed by 03A at source time
    here::here("1_code", "_Commons", "_Tables.R"),   # tbl_* helpers, aliased by 03A at source time
    purrr::map_chr(
      .x = c("03A-ClassifyPrepare", "03E-ClassifyOrchestrate"),   # scoring layer, then routing
      .f = \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
    )
  ),
  .workers = NULL   # NULL leaves two cores for this session
)
```

# Purpose

Two classifiers have been estimated on the same documents and the same folds. The transformer labels
every document; the keyword table labels only those carrying a term it trusts, and declines the rest.
An obvious question follows, and it is the one this document answers for each of the three tasks:
does a rule sending each document to whichever arm handles it best beat simply using the transformer
everywhere?

The question is easy to ask and easy to answer badly. There are a few dozen plausible routing rules,
they are separated by a fraction of a percentage point, and the sample holds 4,400 documents.
Enumerating the rules on those documents and reporting the winner would produce a number that is part
routing and part search, with no way to tell which.

So the rule is chosen the way every other decision in this pipeline is made -- inside the folds. For
each fold in turn, every rule is ranked on the other four and the winner is applied to the fifth. No
document contributes to choosing the rule that labels it. What the results report is the performance
of the **procedure**: what a reader who ran this selection would obtain.

## What counts as an arm

An **arm** is one source of per-document predictions scored on the shared folds. Arms differ in one
respect that governs everything else: whether they can decline. The transformer always commits. A
keyword arm commits only where a term clears its evidence threshold. Only an always-committing arm
can end a cascade, because every document must leave with a label.

A **policy** is an ordered list of abstaining arms, a floor applied within each, and a terminal arm
that catches the rest. Two families are searched. The **cascade** family honours every commitment
clearing the floor. The **per-class** family honours a commitment only for categories where that arm
beat the terminal on the training folds -- the deployable counterpart of an oracle, since the
decision uses training labels only.

## Ties are resolved toward doing nothing

A strict ranking crowns whichever rule leads in the fourth decimal, which on this sample is a
rounding artifact. Left alone it makes the fold-level winner change for no reason and writes a
deployment artifact that contradicts the document's own conclusion. So every ranking here resolves
through a tolerance: among rules within `Tolerance` macro-F1 of the best, the one **routing the
fewest documents** is taken. The incumbent routes none and therefore wins every tie by construction,
and routing has to earn its place by a margin the sample can measure. 03C applies the same principle
to precision when it chooses a keyword configuration.

## Amendment needs a decision, not a workaround

For `AmendType` the keyword engine mines the positive class only and assigns `Original` wherever no
amendment term fired. That label is the absence of evidence wearing the name of a class: coverage
reads as complete, the arm looks like a terminal, and the cascade space collapses to "pick one
method". 03C states the asymmetry in its own bundle script -- *Original is defined by the absence of
amendment language*.

Naming the labels that count as commitments repairs it. The keyword arm commits to `Amended` and
abstains otherwise, and the routing question becomes the real one: if an amendment term fires, call
it amended, otherwise ask the transformer. 03B predicts this fails, because *amended and restated*
titles many genuine originals. It is now testable rather than assumed.

## Which arms may enter the search

Not all of them. The mined keyword arms were estimated on all five folds; arms scored from a written
term list were not, because the reading session that produced the list read folds one to four **with
their labels**. An arm existing on one fold cannot enter a five-fold nested search without
contaminating four of the five rankings. Those arms are held back and evaluated in Robustness, on the
fold they are entitled to.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(.dir_here = here::here(), .name_script = "03B-ClassifyTrainBERT")
.dir_kw   <- init_create_script_dir(.dir_here = here::here(), .name_script = "03C-ClassifyTrainKeyword")
.dir_llm  <- init_create_script_dir(.dir_here = here::here(), .name_script = "03D-ClassifyLLM")

.lP <- list(
  Input = list(
    # Rebuilt from the same directory helper the upstream scripts wrote with, so they cannot drift
    # from where the files actually landed.
    Prepared = fs::path(.dir_prep, "prepared.parquet"),
    # What the two training stages crowned. This stage reads those decisions rather than making its
    # own: three stages ranking the same models on three criteria produced three answers, and the
    # manifest ended up naming a model nobody had fitted.
    BertCrown = fs::path(.dir_bert, "model_final", "deployed.parquet"),
    KwCatalog = fs::path(.dir_kw, "table", "catalogue.parquet")
  ),
  Runs = list(
    # fs::path for inputs, utils_file_path for outputs. The project helper creates the directory it
    # names, which is right for somewhere this document writes and wrong for somewhere it reads: a
    # runs root conjured into existence reports Found = TRUE while holding nothing.
    Bert = fs::path(.dir_bert, "runs"), # written by 03B
    Kw   = fs::path(.dir_kw,   "runs"), # written by 03C
    Llm  = fs::path(.dir_llm,  "runs")  # written by 03D; absent until that stage has run
  ),
  Output = list(
    Policy = utils_file_path(.dir_main, "policy"),    # per-task routing policies
    Deploy = utils_file_path(.dir_main, "deployment") # the manifest 03F reads
  ),
  Param = list(
    Floors    = c(0, 0.70, 0.80, 0.90),   # score floors crossed into the policy grid
    MaxDepth  = 2L,                       # longest cascade of abstaining arms
    Families  = c("cascade", "perclass"), # gating families searched
    Folds     = 5L,                     # folds an arm must cover to enter the nested search
    Holdout   = 5L,                     # the fold a written term list never read
    Tolerance = 0.005,                  # macro-F1 band treated as indistinguishable
    # The generative arm is the most independent vote and the most expensive to run at corpus scale,
    # so it is pinned in the manifest and left off unless a caller asks for it.
    DefaultVoteSet = "core",
    DefaultKinds   = c("transformer", "keyword")
  )
)
```

The tolerance is set below half the fold-level spread 03B reports for the leading transformer
configurations. It is a claim about measurement, not a preference: differences smaller than this are
inside the noise of a 4,400-document five-fold estimate, so resolving them by argmax reports the
resolution of the arithmetic rather than anything about the classifiers.

Nothing in this document is cached. Every step is a join over a few thousand rows and the whole
search completes in seconds, so a cache would buy no time while introducing the one failure this
pipeline has already been bitten by: a key naming a computation rather than fingerprinting its input.

```{r}
#| label: load-prepared-sample
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)
```

The runs roots are resolved once, against the filesystem. A stage that has not run yet leaves no
directory, and globbing a missing one aborts -- so this document would refuse to render at all
because a later, optional arm was absent. Filtering to what exists means the analysis degrades to the
arms available rather than failing, and prints which those are so a thin inventory is never a
surprise.

```{r}
#| label: load-upstream-crowns
# The arm each training stage deployed, and every variant it shipped beside it. Read here so the
# rest of this document can report what ships without deciding what ships.
kw_cat <- arrow::read_parquet(file = .lP$Input$KwCatalog)

kw_cat |>
  dplyr::filter(Default) |>
  dplyr::transmute(Task, Window = dplyr::if_else(NWords == 0L, "full", as.character(NWords)),
                   Coverage = tbl_pct(Coverage), Realised = tbl_pct(Realised)) |>
  tbl_say(.title = "Keyword tables marked for deployment")

# 03B records the configuration, not the arm: arms are named here, under a convention that reconciles
# four engines, and a second namer upstream would be a second convention. The join below is what turns
# the crowned configuration into this document's name for it.
bert_crown <- arrow::read_parquet(file = .lP$Input$BertCrown)

bert_crown |>
  dplyr::transmute(Task = LabelCol, MaxLen, Config, MacroF1 = sprintf("%.3f", MacroF1)) |>
  tbl_say(.title = "Transformer configurations crowned and deployed")
```

```{r}
#| label: resolve-runs-roots
.dir_runs <- c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm)
.dir_runs <- .dir_runs[fs::dir_exists(.dir_runs)]

tibble::tibble(
  Root  = c("BERT (03B)", "Keyword (03C)", "LLM (03D)"),
  Path  = c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm),
  Found = fs::dir_exists(c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm))
) |>
  dplyr::mutate(Path = fs::path_rel(Path, here::here())) |>
  tbl_say(.title = "Runs roots feeding this document")

if (length(.dir_runs) == 0L) cli::cli_abort("No runs on disk; run 03B before this document")
```

# The arms

The broad taxonomy is a strict roll-up of the detailed one, so each level could in principle
constrain the other. 03B already guarantees a *consistent* published hierarchy by deriving the broad
label from the detailed prediction, so what is at stake here is accuracy, not consistency.

One number bounds what a broad-level constraint could buy, and it is worth stating the expectation
before reading it. 03B reports that detailed errors concentrate in substantively adjacent category
pairs. If those pairs share a broad parent, the broad prediction was already right on the documents
the detailed model got wrong and constraining the detailed decision cannot reach them.

```{r}
#| label: hierarchy-errors
tab_overall <- clf_load_overall(.runs_roots = .lP$Runs$Bert)

pred_det <- bert_best_predictions(
  .tab_overall = tab_overall,    # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert,  # run folders to pool from
  .label_col   = "ClassDetailed" # task
)

pred_broad <- bert_best_predictions(
  .tab_overall = tab_overall,   # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_col   = "ClassBroad"   # task
)

orch_report_hierarchy(
  .tab = orch_hierarchy_errors(
    .tab_pred = pred_det, # pooled out-of-fold detailed predictions
    .tab_prep = tab_prep  # supplies the detailed-to-broad mapping
  )
)
```

Reachable headroom is not the same as realisable headroom, and the two are separated by the broad
model's own error rate: every document where the constraint is imposed on a wrong parent is a
document the constraint breaks. Both directions are therefore built as arms and made to compete
rather than argued about. The detailed task gets `bert-hier`, whose detailed choice is restricted to
the predicted parent's children. The broad task gets `bert-rollup`, the detailed prediction's parent,
which is the route 03B actually deploys and so the strongest thing in the broad search to beat.

```{r}
#| label: build-derived-arms
class_det <- bert_classification(
  .runs_roots  = .lP$Runs$Bert,                                                    # run folders
  .config_name = bert_best_config(.tab_overall = tab_overall, .label_col = "ClassDetailed"),
  .tab_prep    = tab_prep                                                          # document metadata
)

arm_hier <- orch_arm_hierarchical(
  .class_detailed = class_det,  # carries the P_<Class> probability vector
  .pred_broad     = pred_broad, # the constraint
  .tab_prep       = tab_prep,   # supplies the mapping
  .arm            = "bert-hier" # name it carries through the search
)

arm_rollup <- orch_arm_rollup(
  .pred_detailed = pred_det,      # pooled detailed predictions
  .tab_prep      = tab_prep,      # supplies the mapping
  .arm           = "bert-rollup"  # name it carries through the search
)
```

# The search

Each task is run end to end by the same call. The rules a reader would want to check are named
arguments rather than constants inside the function: how many folds an arm must cover, which labels
count as commitments, how wide the search is, and what counts as a tie.

## Detailed taxonomy

```{r}
#| label: run-detailed
res_det <- orch_run_task(
  .runs_roots  = .dir_runs,                    # every tree that exists; the run schema is shared
  .label_col   = "ClassDetailed",               # task
  .tab_prep    = tab_prep,                      # prepared sample
  .crowned     = bert_crown$ConfigName[bert_crown$LabelCol == "ClassDetailed"], # 03B's deployed config
  .extra_arms  = arm_hier,                      # the broad-constrained transformer
  .floors      = .lP$Param$Floors,              # score floors to cross in
  .max_depth   = .lP$Param$MaxDepth,            # longest cascade
  .families    = .lP$Param$Families,            # gating families
  .commit_only = NULL,                          # every label is a commitment on a categorical task
  .n_folds     = .lP$Param$Folds,               # folds required to enter the nested search
  .tolerance   = .lP$Param$Tolerance,           # macro-F1 band treated as a tie
  .lenient     = FALSE,                         # strict scoring; leniency is a robustness slice
  .carry       = c("ClassDetailed2", "LabelRound") # columns the robustness slices need
)
```

```{r}
#| label: report-detailed-arms
orch_report_arms(
  .tab       = res_det$Arms,      # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_det$LabelCol   # task, for the heading
)
```

```{r}
#| label: report-detailed-spine
orch_report_spine(.spine = res_det$Spine)
```

```{r}
#| label: report-detailed-stability
orch_report_stability(.tab_nested = res_det$Nested)
```

## Broad taxonomy

```{r}
#| label: run-broad
res_broad <- orch_run_task(
  .runs_roots  = .dir_runs,                    # every tree that exists
  .label_col   = "ClassBroad",                  # task
  .tab_prep    = tab_prep,                      # prepared sample
  .crowned     = bert_crown$ConfigName[bert_crown$LabelCol == "ClassBroad"], # 03B's deployed config
  .extra_arms  = arm_rollup,                    # the rolled-up detailed prediction
  .floors      = .lP$Param$Floors,              # unchanged
  .max_depth   = .lP$Param$MaxDepth,            # unchanged
  .families    = .lP$Param$Families,            # unchanged
  .commit_only = NULL,                          # categorical task
  .n_folds     = .lP$Param$Folds,               # unchanged
  .tolerance   = .lP$Param$Tolerance,           # unchanged
  .lenient     = FALSE,                         # strict scoring
  .carry       = "LabelRound"                   # ClassDetailed2 is a detailed label; useless here
)
```

```{r}
#| label: report-broad-arms
orch_report_arms(
  .tab       = res_broad$Arms,    # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_broad$LabelCol # task, for the heading
)
```

```{r}
#| label: report-broad-stability
orch_report_stability(.tab_nested = res_broad$Nested)
```

## Amendment

`.commit_only` is the whole difference. Without it the keyword arm reports complete coverage, is
classed as a terminal, and no cascade exists to search over.

```{r}
#| label: run-amendment
res_amend <- orch_run_task(
  .runs_roots  = .dir_runs,                    # every tree that exists
  .label_col   = "AmendType",                   # task
  .tab_prep    = tab_prep,                      # prepared sample
  .crowned     = bert_crown$ConfigName[bert_crown$LabelCol == "AmendType"], # 03B's deployed config
  .extra_arms  = NULL,                          # no hierarchy to exploit on a binary task
  .floors      = .lP$Param$Floors,              # unchanged
  .max_depth   = .lP$Param$MaxDepth,            # unchanged
  .families    = .lP$Param$Families,            # unchanged
  .commit_only = "Amended",                     # "Original" is the absence of evidence, not a label
  .n_folds     = .lP$Param$Folds,               # unchanged
  .tolerance   = .lP$Param$Tolerance,           # unchanged
  .lenient     = FALSE,                         # strict scoring
  .carry       = "LabelRound"                   # dual labels do not apply to a binary task
)
```

```{r}
#| label: report-amendment-arms
orch_report_arms(
  .tab       = res_amend$Arms,    # the inventory
  .n_folds   = .lP$Param$Folds,   # folds required to enter the nested search
  .label_col = res_amend$LabelCol # task, for the heading
)
```

```{r}
#| label: report-amendment-stability
orch_report_stability(.tab_nested = res_amend$Nested)
```

The coverage the keyword arm reports here is the share of documents in which an amendment term fired
at all. Read it against 03B's finding: if that share is large and its selective precision is modest,
the arm is firing on originals, which is exactly the failure that made a transformer necessary.

# Results

```{r}
#| label: results-verdicts
verdicts <- orch_verdicts(.results = list(res_det, res_broad, res_amend))
orch_report_verdicts(.tab = verdicts)
```

The `Moved` column is the one to read first. A procedure that moved no documents did not fail to find
a gain; it declined to route, on every fold, and the tolerance is what let it. A procedure that moved
many documents for a delta near zero found real structure and traded it away, which reads differently
in the text and is visible only in the movement table below.

## Detailed taxonomy

```{r}
#| label: results-detailed-compare
orch_report_compare(.tab = res_det$Compare, .title = "ClassDetailed")
```

```{r}
#| label: results-detailed-movement
orch_report_movement(.tab = res_det$Movement)
```

```{r}
#| label: results-detailed-perclass
clf_report_perclass(
  .tab_pred = res_det$Nested,                          # routed, held-out predictions
  .title    = "Routed procedure -- per category"       # heading
)
```

Per-category scores are where a null aggregate becomes informative or stays inert. Routing that
leaves macro-F1 unchanged while lifting one thin category and depressing another has found structure
and traded it away; routing that leaves every category where it was has found nothing.

## Broad taxonomy

```{r}
#| label: results-broad-compare
orch_report_compare(.tab = res_broad$Compare, .title = "ClassBroad")
```

```{r}
#| label: results-broad-movement
orch_report_movement(.tab = res_broad$Movement)
```

## Amendment

```{r}
#| label: results-amendment-compare
orch_report_compare(.tab = res_amend$Compare, .title = "AmendType")
```

```{r}
#| label: results-amendment-movement
orch_report_movement(.tab = res_amend$Movement)
```

```{r}
#| label: results-amendment-confusion
tbl_say(
  .tab   = clf_confusion(.tab_pred = res_amend$Nested), # routed labels against the truth
  .title = "Amendment -- confusion after routing"       # heading
)
```

## Agreement, and the flag that ships with the data

Everything above decides which single label to release. This section asks the question a user of the
released dataset actually faces, and which nothing so far answers: **how much to trust the label in
front of them.**

The dataset covers far more filings than the 4,398 that carry a hand label, so a reader currently has
one global number and no way to tell a confidently-classified contract from a marginal one. A
per-document flag changes the offer. It lets them restrict to concurring documents for a clean
sample, or split on the flag as a robustness check, which is a materially different thing from a
single macro-F1 -- and it answers directly the reviewer question about what a headline accuracy
figure means for a reader holding one contract.

## Why this is shippable and "where the model is wrong" is not

Whether two methods agree is visible on an unlabelled filing: run both and compare. Whether a method
is *wrong* is not, and no amount of care makes it so. That asymmetry is the entire reason the flag is
built from concurrence rather than from error, and it is enforced structurally:
`orch_agreement_pattern()` never selects a truth column. What it computes is exactly what can be
recomputed on a document that was never labelled. Reliability is estimated afterwards, separately,
from the labelled sample.

## Which arms may vote

Chosen on independence, not on accuracy, and stated here rather than derived from a score. The
constrained transformer is built from the plain transformer's own probability vector -- it is not a
second opinion, it agrees with its parent by construction, and counting it would manufacture
unanimity out of one model. A second checkpoint trained on the same folds is barely better: different
weights, identical supervision, and errors that concentrate in the same places. What earns a vote is
a genuinely different route to the answer.

So the rule is **one seat per method family**: lexical matching, representation learning, and a model
with no exposure to this sample at all. Role plays no part in it. The LLM arm commits on every
document and is therefore classed as a terminal rather than a gated arm, which is irrelevant to
whether its opinion is worth hearing -- a routing role and a vote are different jobs, and selecting
voters by role would have silently excluded the most independent arm available.

The transformer seat goes to the arm that actually shipped the label rather than to whichever
checkpoint scored highest, because the flag describes the label that was released.

Derived arms are excluded twice over. `ArmsCV` holds only arms read from run folders, so the
constrained transformer never reaches the seat table; and the incumbent is now chosen among terminal
arms that exist on disk, so it cannot arrive through that door either. It could before: the
constrained arm edges the plain one on accuracy, so it won the incumbent slot on a technicality and
carried itself into the vote as the transformer seat -- a model voting to agree with itself.

```{r}
#| label: agreement-voting-arms
seats_ <- res_det$ArmsCV |>
  dplyr::mutate(
    Family = dplyr::case_when(
      grepl("^keyword-", Kind) ~ "lexical",
      grepl("^llm-", Kind)     ~ "generative",
      TRUE                     ~ "transformer"
    )
  ) |>
  dplyr::slice_max(MacroF1, n = 1L, by = Family, with_ties = FALSE) |>
  dplyr::mutate(Arm = dplyr::if_else(Family == "transformer", res_det$Incumbent, Arm))

arms_voting <- intersect(seats_$Arm, unique(res_det$Spine$Arm))

# Coverage and accuracy come from the spine, not from the inventory, and only Family comes from the
# seat table. The two sources both carry those columns and a plain join would suffix them into
# ambiguity; more to the point, Role is derived from the spine, so the numbers standing beside it
# have to be the spine's or the row explains itself with figures that did not produce it. They
# coincide for a categorical task and part company for a binary one, where the spine has already
# silenced the keyword arm's negative class.
seats_ |>
  dplyr::filter(Arm %in% arms_voting) |>
  dplyr::select(Family, Arm) |>
  dplyr::left_join(
    res_det$Roles |> dplyr::select(Arm, Role, Derived, Coverage, Accuracy),
    by = dplyr::join_by(Arm)
  ) |>
  dplyr::mutate(Coverage = tbl_pct(Coverage), Accuracy = tbl_pct(Accuracy)) |>
  tbl_say(.title = "Arms permitted to vote on the confidence flag")
```

Derived arms are excluded by construction, since `ArmsCV` holds only arms read from run folders and
the constrained transformer is built in memory. If the generative row is absent, 03D has not run and
the flag rests on two families rather than three -- weaker, but still computable, and the table above
says so rather than leaving it to be inferred from a number that looks fine.

```{r}
#| label: agreement-tiers
pattern_det <- orch_agreement_pattern(
  .spine    = res_det$Spine,   # every arm's prediction, per document
  .tab_pred = res_det$Nested,  # the labels actually shipped
  .arms     = arms_voting      # who votes, decided above on independence grounds
)

agree_det <- orch_agreement(
  .pattern  = pattern_det,     # the label-free pattern
  .tab_pred = res_det$Nested   # the truth, consulted only now
)

orch_report_agreement(
  .tab  = agree_det,   # tier reliabilities
  .arms = arms_voting  # named in the heading, since a tier means nothing without them
)
```

The unanimous tier's error rate is the number that bounds what this flag can claim. Independent
methods converging on the *same wrong answer* is the failure a concurrence flag is structurally
blind to, and it is the figure to quote when describing the flag's limits rather than its strengths.

## The null: does agreement beat the transformer's own probability?

The transformer already emits a confidence signal, and 03B already showed it separates errors. If the
tiers stop separating once documents are compared at equal probability, then agreement is a proxy for
that probability and the honest recommendation is to ship the simpler number and drop the flag.

```{r}
#| label: agreement-vs-probability
agree_prob_det <- orch_agreement_vs_prob(
  .pattern   = pattern_det,        # the label-free pattern
  .tab_pred  = res_det$Nested,     # shipped labels and truth
  .spine     = res_det$Spine,      # supplies the incumbent's probability
  .incumbent = res_det$Incumbent,  # whose Score is that probability
  .n_bands   = 4L                  # equal-count bands; the distribution is massed near one
)

orch_report_agreement_vs_prob(.tab = agree_prob_det)
```

Read across a row, not down a column. Tiers separating within a band means concurrence carries
information the probability does not, and the two combined beat either alone. Flat rows mean the flag
is redundant, and saying so is a result rather than a disappointment.


## Two voting sets, because one of them costs ten hours

The generative arm is the most independent vote available and the only one that saw none of this
sample. It is also the expensive one: at the rate 03D measured, running it over the 1.1 million
contracts in the corpus is hours of inference rather than minutes. A deployment that leaves it off is
therefore a realistic case, not a hypothetical, and it needs its own reliability numbers.

A tier's reliability is a property of **who voted**. Estimating it on three arms and deploying with
two would ship numbers describing a vote that never happened, and nothing downstream could catch it:
a two-arm pattern computed at deployment looks exactly like a two-arm pattern computed here. So both
sets are estimated now and the manifest records which one a caller gets unless they ask otherwise.

```{r}
#| label: agreement-sets
sets_voting <- list(
  core = intersect(seats_$Arm[seats_$Family != "generative"], unique(res_det$Spine$Arm)),
  full = arms_voting
)
sets_voting <- sets_voting[purrr::map_int(sets_voting, length) > 0L]

agree_sets <- orch_agreement_sets(
  .spine    = res_det$Spine,  # every arm's prediction, per document
  .tab_pred = res_det$Nested, # the labels actually shipped
  .sets     = sets_voting     # one reliability table per set
)

orch_report_agreement_sets(
  .tab     = agree_sets,               # every set side by side
  .default = .lP$Param$DefaultVoteSet  # the set a caller gets unless they ask otherwise
)
```

The generative arm is pinned in the manifest but **not enabled by default**. A caller who wants the
three-family flag asks for it and pays for it; a caller who does not gets the cheaper flag with
reliability numbers that describe the vote they actually ran.

# Validation

The routed labels must not contradict each other across taxonomy levels in a released dataset. Rolling
the routed detailed prediction up to its parent and scoring it at the broad level says whether routing
broke the property 03B established, and whether the routed detailed labels remain at least as good a
route to the broad taxonomy as the broad task's own output.

```{r}
#| label: validation-hierarchy
dplyr::bind_rows(
  clf_scores(
    .tab_pred = clf_rollup_to_broad(
      .tab_pred = res_det$Nested, # routed detailed predictions
      .tab_prep = tab_prep        # supplies the detailed-to-broad mapping
    )
  ) |>
    dplyr::mutate(Route = "Routed detailed, rolled up", .before = 1),
  clf_scores(
    .tab_pred = clf_rollup_to_broad(.tab_pred = pred_det, .tab_prep = tab_prep)
  ) |>
    dplyr::mutate(Route = "Transformer detailed, rolled up", .before = 1),
  clf_scores(.tab_pred = res_broad$Nested) |>
    dplyr::mutate(Route = "Routed broad, direct", .before = 1),
  clf_scores(.tab_pred = pred_broad) |>
    dplyr::mutate(Route = "Transformer broad, direct", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Four routes to the broad taxonomy, all scored at the broad level")
```

Four routes converging within noise is the substantive finding, not a null: it says the two taxonomy
levels carry the same information and neither improves the other. That turns 03B's decision to derive
the published broad label by roll-up from a consistency argument into a measured one.

# Robustness

## The curated arms, on the fold they are entitled to

Arms scored from a written term list read folds one to four with their labels, so the fifth fold is
their only honest test. The check is paired: the same selection runs on the same fold-five documents
with and without those arms available, so the two cascades are compared on identical rows.

The comparison is deliberately bounded. One fold holds roughly a fifth of the sample and the keyword
arms abstain on much of it, so only a large difference would be visible. A null here says the curated
terms did not change the ordering on the documents available to test them, and no more than that.

```{r}
#| label: robustness-curated-arms
# Start from the spine the headline used, restricted to the holdout fold, so the derived arm is
# present here too and the two cascades differ only in the curated arms.
spine_hold <- res_det$Spine |>
  dplyr::filter(Fold == .lP$Param$Holdout)

if (nrow(res_det$ArmsHeld) > 0L) {
  spine_hold <- dplyr::bind_rows(
    spine_hold,
    orch_spine(
      .runs_roots = .dir_runs,                    # every tree that exists
      .arms       = res_det$ArmsHeld,              # the fold-restricted arms
      .tab_prep   = tab_prep                       # document-level columns
    ) |>
      dplyr::filter(Fold == .lP$Param$Holdout)
  )
}

# Only arms actually committing on this fold can be gated; one absent from these rows would
# contribute nothing and make the comparison look like a null it did not earn.
roles_hold <- orch_roles(.spine = spine_hold)

policies_hold <- orch_policy_grid(
  .arms_gated = roles_hold$Arm[roles_hold$Role == "gated"],    # curated arms included
  .terminals  = roles_hold$Arm[roles_hold$Role == "terminal"], # unchanged
  .floors     = .lP$Param$Floors,                              # unchanged
  .max_depth  = .lP$Param$MaxDepth,                            # unchanged
  .families   = .lP$Param$Families                             # unchanged
)

dplyr::bind_rows(
  orch_score_policies(.spine = spine_hold, .policies = res_det$Policies) |>
    orch_pick_policy(.tolerance = .lP$Param$Tolerance) |>
    dplyr::mutate(Arms = "Mined arms only", .before = 1),
  orch_score_policies(.spine = spine_hold, .policies = policies_hold) |>
    orch_pick_policy(.tolerance = .lP$Param$Tolerance) |>
    dplyr::mutate(Arms = "Mined plus curated", .before = 1)
) |>
  dplyr::mutate(Accuracy = tbl_pct(Accuracy), MacroF1 = sprintf("%.3f", MacroF1)) |>
  dplyr::select(Arms, Label, Accuracy, MacroF1, nRouted) |>
  tbl_say(.title = "Holdout fold: does hand curation change the best cascade?")
```

With no fold-restricted arms on disk, the two rows are identical by construction and the check is
inert rather than wrong. It becomes informative as soon as a curated term list exists.

## Lenient scoring

A minority of documents carry a second valid category. Scoring the routed detailed labels leniently
asks whether predictions counted as wrong were in fact the document's other valid answer -- a rule
that appears to break labels may only be choosing the second valid one. The check applies to the
detailed task alone, since `ClassDetailed2` is a detailed label.

```{r}
#| label: robustness-lenient
dplyr::bind_rows(
  clf_scores(.tab_pred = res_det$Nested, .lenient = FALSE) |>
    dplyr::mutate(Scoring = "Strict", .before = 1),
  clf_scores(.tab_pred = res_det$Nested, .lenient = TRUE) |>
    dplyr::mutate(Scoring = "Lenient", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Routed detailed procedure under strict and lenient scoring")
```

## Label provenance

The second labelling round is the harder subset rather than a random sample, so a rule helping only
on the first round would be exploiting the easier documents.

```{r}
#| label: robustness-label-round
purrr::map(
  .x = list(res_det, res_broad, res_amend),
  .f = function(.r) {
    dplyr::bind_rows(
      clf_scores(.tab_pred = .r$Nested) |>
        dplyr::mutate(Labels = "Both rounds", .before = 1),
      clf_scores(.tab_pred = dplyr::filter(.r$Nested, LabelRound == "Round2")) |>
        dplyr::mutate(Labels = "Round 2 only", .before = 1)
    ) |>
      dplyr::mutate(LabelCol = .r$LabelCol, .before = 1)
  }
) |>
  purrr::list_rbind() |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  dplyr::select(LabelCol, Labels, Accuracy, F1_macro, N) |>
  tbl_say(.title = "Routed procedures by label provenance")
```

# Deployment

The folds paid for the estimate; the full sample produces the artifact. The policy deployed is the one
the same selection crowns with every fold available, under the same tolerance, so the artifact cannot
contradict the document's own conclusion by preferring a fourth-decimal winner.

```{r}
#| label: deploy-derived
purrr::map(list(res_det, res_broad, res_amend), function(.r) {
  tibble::tibble(
    LabelCol  = .r$LabelCol,
    Incumbent = .r$Incumbent,
    Derived   = if (length(.r$Derived) == 0L) "-" else paste(.r$Derived, collapse = ", ")
  )
}) |>
  purrr::list_rbind() |>
  tbl_say(.title = "Derived arms: in the search, out of the deployment")
```

A derived arm competes on equal terms and can win a fold on its merits, which is why it is built at
all. What it cannot do is be deployed: the manifest has no way to express *run the broad model, then
constrain the detailed one*, so an artifact naming it would be one 03F cannot execute. Deployment
selection therefore ranks every policy and chooses among the executable ones. A derived arm winning
by a margin the tolerance recognises would be a finding worth building support for, not something to
ship quietly.

```{r}
#| label: deploy-leaderboards
purrr::map(
  .x = list(res_det, res_broad, res_amend),
  .f = function(.r) {
    .r$Final$Rank |>
      head(5) |>
      dplyr::mutate(LabelCol = .r$LabelCol, .before = 1)
  }
) |>
  purrr::list_rbind() |>
  dplyr::mutate(Accuracy = tbl_pct(Accuracy), MacroF1 = sprintf("%.3f", MacroF1)) |>
  dplyr::select(LabelCol, Label, Accuracy, MacroF1, nRouted) |>
  tbl_say(.title = "All-fold leaderboards, top five per task")
```

```{r}
#| label: deploy-save-policies
purrr::walk2(
  .x = list(res_det, res_broad, res_amend),
  .y = list(NULL, NULL, "Amended"), # what each task let a keyword arm commit to
  .f = function(.r, .commit) {
    orch_save_policy(
      .final       = .r$Final,        # chosen policy plus its per-class gate
      .arms        = .r$Arms,         # records the ConfigName behind each arm name
      .label_col   = .r$LabelCol,     # the task this policy applies to
      .dir         = .lP$Output$Policy, # destination 03F reads
      .commit_only = .commit,         # recorded so 03F reproduces the abstention rule
      .stem        = "routing_policy" # file stem
    )
  }
)
```

```{r}
#| label: deploy-save-confidence
orch_save_confidence(
  .agreement = agree_det,          # tier reliabilities estimated on the labelled sample
  .arms      = arms_voting,        # who voted, so the flag is reproducible downstream
  .label_col = res_det$LabelCol,   # the task it applies to
  .dir       = .lP$Output$Policy,  # destination 03F reads
  .stem      = "confidence_flag"   # file stem
)
```

03F recomputes the tier for every document in the corpus -- it can, since the pattern needs no labels
-- and attaches the reliability estimated here. Splitting it this way keeps the estimate out of the
apply stage: 03F does arithmetic on a rule it was handed, and cannot quietly re-estimate reliability
on a corpus that has no labels to estimate it from.

03F reads these files and applies them. It makes no routing decision of its own: an apply script that
re-derived a policy would be free to re-derive it differently, and the released labels would then
depend on which script last ran.

## The manifest

The artifacts written above name configurations, and a configuration is not a model. A string like
`ClassDetailed__nlpaueb-legal-bert...__L256_E6...` identifies a recipe that was cross-validated, not
a directory holding weights. A downstream stage handed only that string would have to reconstruct the
path from a naming convention -- and a convention shared between training and inference is one that
will eventually be changed in one place and not the other.

So the manifest resolves every arm to a concrete artifact, records the parameters it was validated
under and what it scored, and states which arms are on by default. It is the single file 03F reads
and the single thing that must be archived alongside the released labels for anyone to reproduce
them.

Paths come from each upstream stage's own helpers rather than from a convention restated here, which
is the same rule that keeps the run roots from drifting.

```{r}
#| label: deploy-artifacts
# Discovered, not constructed. Every deployed model under the training stage's output and every
# published table under the keyword stage's, joined to this task's arm inventory, with the variant
# each stage crowned marked. Building a path from a configuration name and trusting it to exist is
# what pinned a model nobody had fitted.
tab_artifacts <- purrr::map(
  .x = list(res_det, res_broad, res_amend),
  .f = function(.r) {
    orch_artifacts(
      .res          = .r,        # one task's arms and its deployed incumbent
      .dir_bert     = .dir_bert, # 03B's output root
      .dir_kw       = .dir_kw,   # 03C's output root
      .kw_catalogue = kw_cat     # what 03C published and marked
    )
  }
) |>
  purrr::list_rbind()

orch_report_catalogue(.tab = tab_artifacts)
```

Each task crowned its own configuration, so each pins its own checkpoint. A single global arm list
would name the detailed task's model for all three, and the apply stage would discover it by finding
no predictions for a terminal it had been told to use.

```{r}
#| label: deploy-save-manifest
orch_save_manifest(
  .results      = list(res_det, res_broad, res_amend), # every task's policy and validated score
  .artifacts    = tab_artifacts,                       # arm to artifact, verified on disk
  .agreement    = agree_sets,                          # reliability under every voting set
  .sets         = sets_voting,                         # the sets themselves
  .default_set  = .lP$Param$DefaultVoteSet,            # what a caller gets unless they ask
  .default_kinds = .lP$Param$DefaultKinds,             # kinds enabled without being asked for
  .dir          = .lP$Output$Deploy,                   # the directory 03F reads
  .tab_prep     = tab_prep                             # provenance: sample size and fold count
)
```

03F reads `manifest.json` and nothing else. Every default it applies is a value recorded here, so a
caller who overrides one is visibly departing from a validated configuration rather than quietly
choosing a different one.

```{r}
#| label: stop-workers
# The last policy search has run; the figures below need no workers. Stopping them here rather than
# leaving them to the session keeps a rendered document from holding processes open afterwards.
mirai::daemons(0L)
```

# Overview

Everything above in one place, per task, followed by the figures. Nothing here is new.

```{r}
#| label: overview-verdicts
orch_report_verdicts(.tab = verdicts)
```

::: {.panel-tabset}

## Detailed

```{r}
#| label: overview-report-detailed
orch_report_all(.res = res_det, .n_folds = .lP$Param$Folds)
```

## Broad

```{r}
#| label: overview-report-broad
orch_report_all(.res = res_broad, .n_folds = .lP$Param$Folds)
```

## Amendment

```{r}
#| label: overview-report-amendment
orch_report_all(.res = res_amend, .n_folds = .lP$Param$Folds)
```

:::

## Strategies compared

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-compare-detailed
#| fig-height: !expr plot_height(nrow(res_det$Compare))
#| fig-cap: "Macro-F1 by strategy, detailed taxonomy. The dashed line is the incumbent; the hollow
#|   bar was selected and scored on the same documents and is not obtainable by running the procedure."
orch_plot_compare(.compare = res_det$Compare)
```

### Broad

```{r}
#| label: fig-compare-broad
#| fig-height: !expr plot_height(nrow(res_broad$Compare))
#| fig-cap: "Macro-F1 by strategy, broad taxonomy. Same fixed axis as the panel above."
orch_plot_compare(.compare = res_broad$Compare)
```

### Amendment

```{r}
#| label: fig-compare-amendment
#| fig-height: !expr plot_height(nrow(res_amend$Compare))
#| fig-cap: "Macro-F1 by strategy, amendment task. Same fixed axis as the panels above."
orch_plot_compare(.compare = res_amend$Compare)
```

:::

## How much each fold actually routed

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-stability-detailed
#| fig-height: !expr plot_height(3)
#| fig-cap: "Documents the crowned policy moved away from the terminal, per held-out fold. A fold at
#|   zero ran the incumbent whatever its winning policy was called."
orch_plot_stability(.tab_nested = res_det$Nested)
```

### Broad

```{r}
#| label: fig-stability-broad
#| fig-height: !expr plot_height(3)
#| fig-cap: "Documents routed per held-out fold, broad taxonomy."
orch_plot_stability(.tab_nested = res_broad$Nested)
```

### Amendment

```{r}
#| label: fig-stability-amendment
#| fig-height: !expr plot_height(3)
#| fig-cap: "Documents routed per held-out fold, amendment task."
orch_plot_stability(.tab_nested = res_amend$Nested)
```

:::

## The confidence flag

```{r}
#| label: fig-agreement-tiers
#| fig-height: !expr plot_height(7)
#| fig-cap: "Accuracy of the shipped label by agreement tier, detailed taxonomy. Bar shading is the
#|   share of the corpus each tier covers: a tier can be near-perfect and still too small to use."
orch_plot_agreement(.tab = agree_det)
```

## Per-category performance after routing

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-perclass-detailed
#| fig-height: !expr plot_height(12)
#| fig-cap: "Per-category F1 for the routed procedure, detailed taxonomy."
clf_plot_perclass(.tab_pred = res_det$Nested)
```

### Broad

```{r}
#| label: fig-perclass-broad
#| fig-height: !expr plot_height(7)
#| fig-cap: "Per-category F1 for the routed procedure, broad taxonomy."
clf_plot_perclass(.tab_pred = res_broad$Nested, .key = "ClassBroad")
```

### Amendment

```{r}
#| label: fig-perclass-amendment
#| fig-height: !expr plot_height(2)
#| fig-cap: "Per-category F1 for the routed procedure, amendment task."
clf_plot_perclass(.tab_pred = res_amend$Nested, .key = "AmendType")
```

:::

# Next

`03F` applies the deployed models to the full corpus, reading the routing policies written here rather
than deciding its own. The keyword table remains an independent artifact of 03C: it ships alongside
the archived dataset and does not enter the labelling path, whatever this document concludes about
routing.

One extension needs no change here. Regenerating the curated term lists once per fold would promote
the written-list arms out of Robustness into the nested search proper, at which point the `nFolds`
filter admits them automatically and the mined and curated arms compete on equal terms across all five
folds.
