---
title: "Contract Classification -- Applying the Deployed Classifier (03F)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: the
# sample script registers its category vocabulary and aliases the table helpers at SOURCE time, not
# inside a function, so sourcing it first throws part-way through the file and every function defined
# below the failure silently never exists. A file's top-level statements are part of its interface.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A supplies the scoring and formatting layer, 03B the transformer inference call, 03D the
# generative arm's prompt machinery. Nothing here re-implements any of them: the deployed classifier
# is the same code the folds were run through, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03D-ClassifyLLM"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/03F-ClassifyApply.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every decision has been made. 03B chose a transformer and refit it on all labelled documents, 03C
published a keyword table, 03D added a generative arm, and 03E decided how to combine them and how
much to trust each result. This stage does none of that again. It reads what 03E wrote and applies
it to the corpus.

That separation is the point. An apply stage free to make its own decisions is an apply stage whose
output depends on which version of it last ran, and a released dataset cannot be defended on those
terms. So `mc_classify()` reads every default from the manifest and has almost none of its own, and
an argument passed explicitly is recorded as a **departure** in the result rather than quietly
honoured -- a caller can run a different checkpoint, they simply cannot do so invisibly.

## What comes back

One row per document per task: the label, which arm decided it, that arm's confidence, what every arm
said independently, the agreement tier, and the reliability estimated for that tier under the voting
set that was actually used. A user of the released dataset can condition on trust without re-running
anything, which is a materially different offer from a single headline accuracy.

## Why the generative arm is off by default

It is the most independent vote available and the only arm that saw none of the labelled sample, so
it is the one that most improves the flag. It is also hours of inference across a corpus of this
size rather than minutes. It is therefore pinned in the manifest and disabled: asking for it is one
argument, and a run that does not ask gets the two-family flag together with reliability numbers
estimated on the vote it actually ran.

That last clause is the part that would be easy to get wrong. A two-arm agreement pattern computed at
deployment is indistinguishable from a two-arm pattern computed on the labelled sample, so shipping
one set of reliabilities for every voting set would produce numbers that look entirely reasonable and
describe a vote that never happened. 03E estimates each set separately and the manifest records which
one a run is using.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_orch <- init_create_script_dir(.dir_here = here::here(), .name_script = "03E-ClassifyOrchestrate")

.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus tree
    # conjured into existence would report itself present while holding nothing.
    Manifest  = fs::path(.dir_orch, "deployment", "manifest.json"), # written by 03E
    Prepared  = fs::path(.dir_prep, "prepared.parquet"),            # labelled sample
    # The same parsed-contract tree 03A drew the labelled sample from, restricted to Exhibit 10.
    DirCorpus = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/",
    MetaData  = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet" # filer titles
  ),
  Cache = list(
    CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet") # DocID to Path index
  ),
  Output = list(
    # One store for every configuration, scoped by a RunKey column rather than by directory. Two
    # passes therefore coexist and are compared with a query; nothing reading it may omit that
    # filter.
    Store  = utils_file_path(.dir_main, "labels") |> fs::path("labels.duckdb"),
    Export = utils_file_path(.dir_main, "labels") # parquet lands here, one file per run key
  ),
  Engine = list(
    # The same interpreter and the same engine directory 03B trains through. here::here rather than
    # a tilde path: system2 does not expand ~, so a tilde reaches the shell literally and fails with
    # exit 127 four hours into a corpus pass.
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "classify_apply.py") # companion to classify_train.py
  ),
  Param = list(
    BatchSize = 32L,    # documents per forward pass
    ChunkSize = 2500L, # documents per output file; a corpus pass should not be one write
    IndexRerun = FALSE, # TRUE re-walks the tree; FALSE reuses the cached index
    # The switch that decides whether this document is a rehearsal or the release. An integer draws
    # that many documents at random from the whole tree and writes them to a separate directory; NULL
    # labels the corpus. Set an integer, read the numbers, then set NULL.
    Limit = 50000L,
    # Selects a non-default variant of any kind, e.g. c(transformer = "L256"). NULL applies what the
    # manifest marked. The catalogue exists so a caller with throughput figures can trade accuracy
    # against cost, so this is a supported choice rather than an escape hatch -- but every row it
    # produces is recorded as a departure and is not comparable with rows produced under the
    # defaults.
    Prefer = NULL
  )
)
```

Nothing here is cached. The expensive work is the model passes themselves, and those are checkpointed
by writing labelled chunks as they complete, which is a resumable design rather than a cache: an
interrupted run restarts at the first chunk that has no output file.

```{r}
#| label: load-manifest
man <- mc_manifest(.path = .lP$Input$Manifest)
mc_report_manifest(.man = man)
```

Read that block before anything else. Every line of it is a decision someone made once and validated,
and a run applying the wrong quarter's configuration should be visible in the first screen of output
rather than in the released labels.

The corpus is an index here, not a table. The labelled sample fits in memory and the corpus does not:
1.1 million contracts of full text is hundreds of gigabytes, so what is held throughout is one row
per document with its path and filer title, and text is read one chunk at a time and discarded. Any
code that treats corpus text as a column runs out of memory somewhere past the first hundred
thousand documents.

```{r}
#| label: load-documents
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

tab_index <- mc_corpus_index(
  .dir_corpus = .lP$Input$DirCorpus,     # the parsed-contract tree, Exhibit 10 only
  .path_meta  = .lP$Input$MetaData,      # supplies DocDesc, the filer's own title
  .path_cache = .lP$Cache$CorpusFiles,   # walking a million files is cached, not repeated
  .rerun      = .lP$Param$IndexRerun,    # TRUE after new contracts have been parsed
  .limit      = .lP$Param$Limit,         # NULL labels the corpus; an integer rehearses
  .seed       = 42L,                     # a limited run draws the same documents each time
  .tab_prep   = tab_prep                 # flags documents the model was trained on
)

# The store, and the key everything in it is scoped by. Disconnected in the last chunk of this
# document, after every read: a connection closed while anything downstream still needs it fails at
# whichever query happens to run next, which is nowhere near the line that closed it.
run_key <- mc_run_key(.man = man)
con     <- mc_db_open(.path = .lP$Output$Store)

tab_index |>
  dplyr::summarise(
    Documents = dplyr::n(),
    InSample  = sum(InSample),
    WithDesc  = sum(!is.na(DocDesc))
  ) |>
  tbl_say(.title = paste0("Corpus to label, run key ", run_key))
```

Labels go to a DuckDB store keyed on `(RunKey, DocID, Task)`. What is already done is therefore a
property of the documents rather than of the file they landed in, which matters because a
chunk-per-file layout is only sound while *chunk seven* means the same seven thousand documents in
every run -- and a changed chunk size, a changed sample cap, new contracts shifting every boundary,
or a process killed mid-write all break that without changing a filename. Every one of those failures
is silent, and the symptom is a coverage table that reconciles because the missing documents are
inside somebody else's file.

`RunKey` hashes the arms and their parameters, so re-rendering the orchestration stage without
changing what it pins does not orphan a half-finished pass, while a configuration that does change
gets its own scope in the same table. Chunking is now nothing but a transaction size: it identifies
nothing, so it can change freely, and an interrupted insert rolls back rather than leaving half a
chunk behind.

A capped run is consequently a partial corpus pass rather than a separate object. It draws from the
whole tree, its labels are valid under the same configuration, and an uncapped run afterwards picks
up whatever it missed.

`InSample` marks documents the transformer was trained on. They are still part of the corpus and
still get labels, but anyone measuring accuracy on them would be measuring training accuracy, so the
flag travels with the release rather than the documents being quietly dropped.

# A rehearsal on one chunk

Before a corpus pass, one chunk end to end. It exercises every arm and the flag lookup, and it costs
seconds -- which is the right price for discovering that a model directory moved or that the keyword
lexicon has a column the applier does not expect.

```{r}
#| label: rehearse-chunk
labelled_head <- mc_classify(
  .docs       = mc_read_chunk(dplyr::slice_head(tab_index, n = 200L)), # text read here, not held
  .manifest   = man,                                   # every default comes from here
  .tasks      = "ClassDetailed",                       # one task for the rehearsal
  .prefer     = .lP$Param$Prefer,                      # NULL applies what the manifest marked
  .voting_set = NULL,                                  # NULL takes the manifest default
  .tab_prep   = tab_prep,                              # only used if the generative arm runs
  .in_sample  = tab_prep$DocID,                        # marks documents the arms were fitted on
  .python     = .lP$Engine$Python,                     # inference environment
  .script     = .lP$Engine$Script,                     # inference script
  .batch_size = .lP$Param$BatchSize                    # documents per forward pass
)

mc_report_run(.tab = labelled_head)
```

```{r}
#| label: rehearse-inspect
labelled_head |>
  dplyr::select(DocID, dplyr::starts_with("Bert_"), dplyr::starts_with("Kw_"), Tier) |>
  head(10) |>
  tbl_say(.title = "First ten documents, as every arm saw them")
```

There is no label in that table, and there is not meant to be. Every routing rule 03E searched is a
deterministic function of these columns -- a cascade is "take the terminal's first choice, override
where the gated arm committed above the floor", which on a finished table is one `mutate` -- and
inference over the corpus is hours against seconds for the rule. Deciding the label here would buy
nothing and would foreclose changing one's mind without a second corpus pass, so the label is derived
downstream and this stage ships the evidence for it.

Read the two `Score2` columns as different objects. `Bert_Score2` is softmax mass over categories;
`Kw_Score2` is a Wilson lower bound on training precision, and it is `NA` wherever only one class
matched at all. They occupy the same slot because they answer the same question of their own arm, not
because they are comparable across arms.

`Kw_Pred1` reading `(none)` is the keyword table declining rather than failing. The published table
holds its precision by abstaining, so its share of committed documents on this corpus is the figure
to check against the coverage 03C promised.

# The corpus pass

Chunked, and each chunk written as it completes. A corpus pass is measured in hours, so a failure at
document nine hundred thousand should cost one chunk rather than the run, and a restart should
resume rather than begin again.

```{r}
#| label: apply-corpus
mc_corpus_pass(
  .index      = tab_index,               # what this run drew
  .con        = con,                     # the label store
  .run_key    = run_key,                 # scopes what counts as already done
  .chunk_size = .lP$Param$ChunkSize,     # documents per transaction, identifying nothing
  .fn = function(.docs) {
    mc_classify(
      .docs       = .docs,              # this chunk, text and all
      .manifest   = man,                # every default comes from here
      .tasks      = NULL,               # NULL labels every task the manifest carries
      .prefer     = .lP$Param$Prefer,   # NULL applies what the manifest marked
      .tab_prep   = tab_prep,           # only used if the generative arm runs
      .in_sample  = tab_prep$DocID,     # marks documents the arms were fitted on
      .python     = .lP$Engine$Python,  # inference environment
      .script     = .lP$Engine$Script,  # inference script
      .batch_size = .lP$Param$BatchSize,# documents per forward pass
      .quiet      = TRUE                # the progress bar is the only output a long pass needs
    )
  }
)
```

```{r}
#| label: apply-throughput
mc_report_throughput(
  .con       = con,                            # timings live beside the labels
  .run_key   = run_key,                        # this configuration's chunks only
  # The whole tree, not this run's index. Under a cap the two differ by exactly the cap, and the
  # projection is the number a night gets planned around.
  .n_corpus  = attr(tab_index, "nCorpus"),     # documents a full pass would cover
  .n_tasks   = 3L,                             # tasks a full pass would label
  .n_indexed = nrow(tab_index)                 # this run's draw, so inherited timings are named
)
```

`FullPassHrs` prices the whole tree whatever this run was capped at, so it is directly the figure to
plan around; the rate behind it is measured on this machine under this configuration. Set `Limit` to
`NULL` once that number is acceptable.

Timings accumulate in the labels directory, which is what lets a resumed pass keep the measurements
it already paid for. The cost is that a chunk size changed between runs leaves both regimes in one
average, and the report says so rather than presenting the blend as a rate.

# Results

```{r}
#| label: results-summary
# Scoped by run key, always. The store holds every configuration ever run against it, so a read that
# omitted the filter would silently pool two sets of arms into one table and every statistic below
# would describe a classifier that never existed.
tab_labels <- mc_db_labels(.con = con, .run_key = run_key)

tab_labels |>
  dplyr::summarise(nDocs = dplyr::n_distinct(DocID), .by = Task) |>
  tbl_say(.title = "Documents labelled, per task")
```

## Coverage

A pass drops documents whose parquet is missing or holds no text, rather than stopping a run measured
in days. That is the right trade and it leaves a hole, so the hole is measured here rather than left
to be inferred by subtracting one table from another. The reconciliation survives a restart, which
the per-chunk warnings do not: on a resumed render the chunks that dropped documents are skipped and
report nothing at all.

The labelled sample is carried through the same reconciliation because it is the one set of documents
whose contents are known. If it reaches the output at the corpus rate, the loss is a property of the
archive and the released labels are missing a random slice. If it reaches at a different rate, the
loss is selective, and a dataset missing a describable kind of document is a different object from
one missing an arbitrary one.

```{r}
#| label: results-coverage
mc_report_coverage(
  .tab_index  = tab_index,   # what this run drew
  .tab_labels = tab_labels,  # what came back
  .tab_prep   = tab_prep     # the one set whose contents are known
)

# The identifiers, not just the count: a count says how much is missing and a list says what, and the
# path travels with it so the claim is checkable against the archive rather than taken on trust.
arrow::write_parquet(
  x    = mc_missing(.tab_index = tab_index, .tab_labels = tab_labels),
  sink = fs::path(.lP$Output$Export, paste0("missing_", run_key, ".parquet"))
)
```

The corpus will not look like the labelled sample, and it should not: the sample was drawn to support
estimation, with thin categories deliberately over-represented so they could be learnt at all. A gap
is expected. What a gap cannot distinguish on its own is whether it comes from that sampling design
or from the model drifting toward frequent categories on documents unlike anything it trained on --
and those have very different consequences for the released labels.

The confidence tiers separate the two. If documents the arms agreed on look like the labelled sample
while the ones they disagreed on carry the skew, the drift sits on uncertain documents and the flag
is already isolating it. If every tier is skewed alike, the difference is composition, the labels are
unaffected, and what carries the sample's composition is the reliability estimate rather than the
classifier.

```{r}
#| label: results-distribution
dist_det <- mc_distribution(
  .tab_labels = tab_labels,     # the corpus pass
  .tab_prep   = tab_prep,       # the labelled sample
  .label_col  = "ClassDetailed" # the only task carrying a flag
)

mc_report_distribution(.tab = dist_det)
```

```{r}
#| label: results-confidence
tab_labels |>
  dplyr::filter(!is.na(Tier)) |>
  dplyr::count(Task, VotingSet, Tier, name = "nDocs") |>
  dplyr::mutate(Share = tbl_pct(nDocs / sum(nDocs)), .by = Task) |>
  tbl_say(.title = "Confidence tiers across the corpus")
```

If the tier distribution here differs markedly from 03E's on the labelled sample, the flag is
behaving differently outside the data it was estimated on, and its reliability numbers should be
treated with more caution than the table suggests. That comparison belongs in the paper.

## What the corpus looks like

Everything below is measured **without labels**, which is the only kind of statement available at
this scale and is less limiting than it sounds. Two arms trained on different evidence, a taxonomy
with a known hierarchy, and a runner-up beside every first choice give three independent handles on
where the released labels carry weight and where they are close calls -- none of which needs the
truth for a single corpus document.

None of it substitutes for the validated estimate. Agreement is not accuracy: two arms can be wrong
together, and the keyword arm shares vocabulary with the transformer's early layers. Read these as a
map of where to look.

```{r}
#| label: stats-profile-detailed
mc_report_task_profile(.tab = tab_labels, .task = "ClassDetailed")
```

```{r}
#| label: stats-profile-broad
mc_report_task_profile(.tab = tab_labels, .task = "ClassBroad")
```

```{r}
#| label: stats-profile-amend
mc_report_task_profile(.tab = tab_labels, .task = "AmendType")
```

### The two taxonomies against each other

The broad task is predicted independently of the detailed one, and the taxonomy fixes which broad
parent each detailed category belongs to. Those two facts can be checked against one another on every
released document: where the independently-predicted parent differs from the parent of the predicted
detailed category, at least one of the two is wrong.

It bounds joint error from below and nothing from above -- both predictions can be wrong the same way
-- but it is measured on the corpus rather than on 4,398 documents, and it says *which* parents the
two taxonomies pull apart on.

```{r}
#| label: stats-hierarchy
mc_hierarchy_agreement(.tab = tab_labels, .map = mc_taxonomy_map(.tab_prep = tab_prep)) |>
  dplyr::mutate(Coherent = tbl_pct(Coherent)) |>
  tbl_say(.title = "Detailed prediction's parent against the independent broad prediction")
```

### The taxonomy, filled in

One row per detailed category, under its broad parent, with what each arm found and how the two
taxonomies disagree. Read down the hierarchy rather than down a ranking: a category the classifier
never predicted keeps its row at zero, and an absent category and a zero are different findings.

The two arms have two denominators. The keyword table abstains by design -- on the amendment task as
well as the detailed one -- so `nKw` counts documents it was willing to speak about and is not a
smaller estimate of the same quantity as `nBert`. `KwCommit` carries that gap so it is attributable
rather than mysterious.

`Incoherent` is the disagreement between the two taxonomies, localised. Each of those documents has an
independently-predicted broad class that is not this row's parent, so at least one of the two
predictions is wrong -- which the hierarchy establishes without a single label.

```{r}
#| label: stats-hierarchy-table
mc_report_hierarchy_table(
  .tab = tab_labels,                              # every task, every arm
  .map = mc_taxonomy_map(.tab_prep = tab_prep)    # the hierarchy, read off the sample that defines it
)
```

```{r}
#| label: stats-amend
mc_amend_profile(.tab = tab_labels) |>
  dplyr::mutate(Amended = tbl_pct(Amended)) |>
  tbl_say(.title = "Amendment share, by detailed category")
```

### The second guess

The runner-up is the only statement about alternatives available without labels, and at corpus scale
the recurring first-to-second pairs are the taxonomy's fault lines: two categories the model
repeatedly cannot separate are two a reader should not treat as cleanly distinct, whichever way any
single document went.

Read `MeanMargin` alongside the count. A pair recurring at a margin of 0.9 is the model being certain
about many similar documents; the same pair at 0.05 is a coin toss it keeps making the same way, and
only the second is a fault line.

```{r}
#| label: stats-second-detailed
mc_second_guess(.tab = tab_labels, .task = "ClassDetailed") |>
  dplyr::mutate(Share = tbl_pct(Share), Close = tbl_pct(Close),
                MeanMargin = sprintf("%.3f", MeanMargin)) |>
  tbl_say(.title = "ClassDetailed: most frequent first-to-runner-up pairs")
```

```{r}
#| label: stats-second-broad
mc_second_guess(.tab = tab_labels, .task = "ClassBroad", .n = 8L) |>
  dplyr::mutate(Share = tbl_pct(Share), Close = tbl_pct(Close),
                MeanMargin = sprintf("%.3f", MeanMargin)) |>
  tbl_say(.title = "ClassBroad: most frequent first-to-runner-up pairs")
```

### When the arms disagree

A disagreement in which the keyword table names the category the transformer ranked *second* is a
different object from one in which it names something the transformer never considered. The first is
two arms splitting a close call; the second is a genuine conflict, and only the second is worth
anyone's time.

```{r}
#| label: stats-near-miss
mc_near_miss(.tab = tab_labels) |>
  dplyr::mutate(ShareOfCommitted = tbl_pct(ShareOfCommitted), IsRunnerUp = tbl_pct(IsRunnerUp),
                MeanMargin = sprintf("%.3f", MeanMargin)) |>
  tbl_say(.title = "Disagreements, and how many are the transformer's runner-up")
```

# Validation

The deployed classifier applied to the labelled sample must reproduce what 03E measured. Any gap is a
deployment fault -- a wrong checkpoint, a different context length, a lexicon that moved -- rather
than a modelling result, and it is the one check that catches an artifact mismatch the manifest's
existence test cannot.

```{r}
#| label: validation-roundtrip
round_trip <- mc_classify(
  .docs     = tab_prep |>
    dplyr::select(DocID, Text, dplyr::any_of("DocDesc")) |>
    dplyr::slice_head(n = 1000L), # the labelled sample already carries its text
  .manifest = man,                # the deployed configuration
  .tasks     = "ClassDetailed",    # the headline task
  .prefer    = .lP$Param$Prefer,   # NULL applies what the manifest marked
  .tab_prep  = tab_prep,           # only used if the generative arm runs
  .in_sample = tab_prep$DocID,     # every document here is in sample, by construction
  .python    = .lP$Engine$Python,  # inference environment
  .script    = .lP$Engine$Script   # inference script
)

# Scored on the terminal arm's first choice, which is what the estimating stage scored while nothing
# routed. Scoring a derived label here would test a rule this stage does not apply.
round_trip |>
  dplyr::inner_join(
    tab_prep |> dplyr::select(DocID, TrueLabel = ClassDetailed),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::summarise(
    nDocs       = dplyr::n(),
    BertCorrect = mean(Bert_Pred1 == TrueLabel),
    KwCommits   = mean(Kw_Pred1 != "(none)"),
    KwCorrect   = mean(Kw_Pred1[Kw_Pred1 != "(none)"] == TrueLabel[Kw_Pred1 != "(none)"])
  ) |>
  dplyr::mutate(dplyr::across(-nDocs, tbl_pct)) |>
  tbl_say(.title = "Deployed arms on labelled documents")
```

`BertCorrect` will sit **above** the cross-validated estimate, and that is expected rather than
reassuring: the deployed model was refit on every labelled document, so these are documents it has
seen. It is a plumbing check, not a performance claim. The honest figure for the paper remains 03E's
nested estimate, and quoting this one instead would be reporting training accuracy.

`KwCommits` is the check with real content. The keyword table promised a coverage at a published
precision, and that promise was measured under the truncation window the table was mined at. If the
share committed here departs from what 03C published, the applier is reading a different amount of
text than the miner did, and the published precision does not hold on this corpus.

# Overview

Everything above in one place: what the manifest committed this run to, what the run produced, and
how each arm behaved on the documents it was asked about. Nothing here is new.

## What ran

```{r}
#| label: overview-manifest
mc_report_manifest(.man = man)
```

## What came back

```{r}
#| label: overview-run
mc_report_run(.tab = tab_labels)
```

## Where the arms agreed

```{r}
#| label: fig-agreement-corpus
#| fig-height: !expr plot_height(4)
#| fig-cap: "Share of the corpus on which each pair of arms made the same first choice, by task.
#|   Read against the keyword arm's commitment share: two arms cannot agree where one abstains."
mc_plot_agreement(.tab = tab_labels)
```

## What each arm committed to

```{r}
#| label: fig-margin-corpus
#| fig-height: !expr plot_height(6)
#| fig-cap: "Distribution of the transformer's decision margin -- first choice minus runner-up -- by
#|   task. Mass at one is clean separation; weight near zero is documents where a different seed
#|   would plausibly have produced a different released label."
mc_plot_margin(.tab = tab_labels)
```

```{r}
#| label: fig-second-guess-detailed
#| fig-height: !expr plot_height(12, .square = TRUE)
#| fig-cap: "Where each detailed category's documents send their runner-up, as a share of that
#|   category. A confusion matrix built without labels: the off-diagonal mass is the taxonomy's own
#|   ambiguity rather than any document's truth."
mc_plot_second_guess(.tab = tab_labels, .task = "ClassDetailed")
```

```{r}
#| label: fig-commitment-corpus
#| fig-height: !expr plot_height(3)
#| fig-cap: "Share of documents each arm committed to, by task. The transformer always answers, so
#|   the gap between the bars is the keyword table declining rather than failing."
mc_plot_commitment(.tab = tab_labels)
```

The store is a working file, not the deliverable. Parquet goes beside it because the regression stage
reads flat files, and because DuckDB's on-disk format has changed across versions before -- a single
database holding the only copy of a pass measured in days is a worse artifact than a file anything can
open. It costs seconds against that pass.

```{r}
#| label: deploy-export
mc_db_export(
  .con     = con,                                                       # the store
  .run_key = run_key,                                                   # this configuration only
  .path    = fs::path(.lP$Output$Export, paste0("labels_", run_key, ".parquet"))
)
```

```{r}
#| label: deploy-disconnect
# LAST EXECUTABLE CHUNK, and it has to stay last. A connection closed while anything below still
# reads from it fails at whichever query runs next, which is nowhere near the line that closed it.
DBI::dbDisconnect(con, shutdown = TRUE)
```

# Next

The released dataset is these labels plus the manifest that produced them. Both have to be archived
together: labels without the manifest cannot be reproduced, and the manifest without the labels is a
recipe nobody ran.

Set `Limit` to `NULL` once the rehearsal reads sensibly, and note that the capped run is not wasted:
it drew from the whole tree under this same configuration, so its labels are already in the store and
the uncapped run simply picks up the documents it did not reach. Raising the cap in stages and
finishing with `NULL` is a supported way to work through the corpus, not a sequence of false starts.

Two things remain open and belong in the paper rather than in code. Whether the generative arm is
worth enabling for the release is a cost decision that 03E's voting-set comparison answers
empirically -- if the three-family flag separates the corpus no better than the two-family one, it is
not worth the hours. And the corpus tier distribution against the labelled sample's is the evidence
for how far the confidence flag can be trusted outside the data that produced it.
