---
title: "Contract Classification -- Applying the Deployed Classifier (03F)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# 03A supplies the scoring and formatting layer, 03B the transformer inference call, 03D the
# generative arm's prompt machinery. Nothing here re-implements any of them: the deployed classifier
# is the same code the folds were run through, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03D-ClassifyLLM"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/03F-ClassifyApply.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every decision has been made. 03B chose a transformer and refit it on all labelled documents, 03C
published a keyword table, 03D added a generative arm, and 03E decided how to combine them and how
much to trust each result. This stage does none of that again. It reads what 03E wrote and applies
it to the corpus.

That separation is the point. An apply stage free to make its own decisions is an apply stage whose
output depends on which version of it last ran, and a released dataset cannot be defended on those
terms. So `mc_classify()` reads every default from the manifest and has almost none of its own, and
an argument passed explicitly is recorded as a **departure** in the result rather than quietly
honoured -- a caller can run a different checkpoint, they simply cannot do so invisibly.

## What comes back

One row per document per task: the label, which arm decided it, that arm's confidence, what every arm
said independently, the agreement tier, and the reliability estimated for that tier under the voting
set that was actually used. A user of the released dataset can condition on trust without re-running
anything, which is a materially different offer from a single headline accuracy.

## Why the generative arm is off by default

It is the most independent vote available and the only arm that saw none of the labelled sample, so
it is the one that most improves the flag. It is also hours of inference across a corpus of this
size rather than minutes. It is therefore pinned in the manifest and disabled: asking for it is one
argument, and a run that does not ask gets the two-family flag together with reliability numbers
estimated on the vote it actually ran.

That last clause is the part that would be easy to get wrong. A two-arm agreement pattern computed at
deployment is indistinguishable from a two-arm pattern computed on the labelled sample, so shipping
one set of reliabilities for every voting set would produce numbers that look entirely reasonable and
describe a vote that never happened. 03E estimates each set separately and the manifest records which
one a run is using.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_orch <- init_create_script_dir(.dir_here = here::here(), .name_script = "03E-ClassifyOrchestrate")

.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus file
    # whose directory was conjured into existence would make the fallback below unreachable.
    Manifest = fs::path(.dir_orch, "deployment", "manifest.json"), # written by 03E
    Prepared = fs::path(.dir_prep, "prepared.parquet"),            # labelled sample
    Corpus   = fs::path(.dir_prep, "corpus.parquet")               # documents to label
  ),
  Output = list(
    Labels = utils_file_path(.dir_main, "labels") # the released labels
  ),
  Engine = list(
    Python = "~/.venvs/contracts-engine/bin/python",   # the environment 03B trains in
    Script = here::here("1_code", "_Engines", "bert_classify.py")
  ),
  Param = list(
    BatchSize = 32L,   # documents per forward pass
    ChunkSize = 50000L # documents per output file; a corpus pass should not be one write
  )
)
```

Nothing here is cached. The expensive work is the model passes themselves, and those are checkpointed
by writing labelled chunks as they complete, which is a resumable design rather than a cache: an
interrupted run restarts at the first chunk that has no output file.

```{r}
#| label: load-manifest
man <- mc_manifest(.path = .lP$Input$Manifest)
mc_report_manifest(.man = man)
```

Read that block before anything else. Every line of it is a decision someone made once and validated,
and a run applying the wrong quarter's configuration should be visible in the first screen of output
rather than in the released labels.

```{r}
#| label: load-documents
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

# The labelled sample stands in for the corpus until the full extract is wired in, so this document
# renders end to end from the first day rather than waiting on the upstream join. Every number below
# is therefore a rehearsal, and the switch to the corpus changes one path.
tab_docs <- if (fs::file_exists(.lP$Input$Corpus)) {
  arrow::read_parquet(file = .lP$Input$Corpus)
} else {
  cli::cli_alert_warning(
    "No corpus extract at {.lP$Input$Corpus}; rehearsing on the labelled sample instead."
  )
  tab_prep |> dplyr::select(DocID, Text, dplyr::any_of("DocDesc"))
}

cli::cli_alert_info("{nrow(tab_docs)} document{?s} to label.")
```

# A rehearsal on one chunk

Before a corpus pass, one chunk end to end. It exercises every arm, the routing policy and the flag
lookup, and it costs seconds -- which is the right price for discovering that a model directory moved
or that the keyword lexicon has a column the applier does not expect.

```{r}
#| label: rehearse-chunk
labelled_head <- mc_classify(
  .docs       = dplyr::slice_head(tab_docs, n = 200L), # one chunk
  .manifest   = man,                                   # every default comes from here
  .tasks      = "ClassDetailed",                       # one task for the rehearsal
  .arms       = NULL,                                  # NULL takes the manifest's enabled set
  .voting_set = NULL,                                  # NULL takes the manifest default
  .tab_prep   = tab_prep,                              # only used if the generative arm runs
  .python     = .lP$Engine$Python,                     # inference environment
  .script     = .lP$Engine$Script,                     # inference script
  .batch_size = .lP$Param$BatchSize                    # documents per forward pass
)

mc_report_run(.tab = labelled_head)
```

```{r}
#| label: rehearse-inspect
labelled_head |>
  dplyr::select(DocID, Label, DecidedBy, Prob, Tier, Reliability) |>
  head(10) |>
  clf_say_table(.title = "First ten labelled documents")
```

A `DecidedBy` column showing only the terminal arm is the expected result rather than a
disappointment: 03E concluded that routing does not beat the transformer, so a policy that routes
nothing is the policy it deployed. What the other arms contribute here is the confidence flag, not
the label.

# The corpus pass

Chunked, and each chunk written as it completes. A corpus pass is measured in hours, so a failure at
document nine hundred thousand should cost one chunk rather than the run, and a restart should
resume rather than begin again.

```{r}
#| label: apply-corpus
fs::dir_create(.lP$Output$Labels)

chunks_ <- split(
  tab_docs,
  ceiling(seq_len(nrow(tab_docs)) / .lP$Param$ChunkSize)
)
cli::cli_alert_info("{length(chunks_)} chunk{?s} of up to {.lP$Param$ChunkSize} documents.")

purrr::iwalk(chunks_, function(.chunk, .i) {
  path_ <- fs::path(.lP$Output$Labels, sprintf("labels_%04d.parquet", as.integer(.i)))
  if (fs::file_exists(path_)) {
    cli::cli_alert_info("Chunk {.i}: already written, skipping.")
    return(invisible(NULL))
  }
  out_ <- mc_classify(
    .docs       = .chunk,             # this chunk
    .manifest   = man,                # every default comes from here
    .tasks      = NULL,               # NULL labels every task the manifest carries
    .tab_prep   = tab_prep,           # only used if the generative arm runs
    .python     = .lP$Engine$Python,  # inference environment
    .script     = .lP$Engine$Script,  # inference script
    .batch_size = .lP$Param$BatchSize # documents per forward pass
  )
  arrow::write_parquet(out_, path_)
  cli::cli_alert_success("Chunk {.i}: {nrow(out_)} row{?s} written.")
})
```

# Results

```{r}
#| label: results-summary
tab_labels <- fs::dir_ls(.lP$Output$Labels, glob = "*.parquet") |>
  purrr::map(arrow::read_parquet) |>
  purrr::list_rbind()

tab_labels |>
  dplyr::summarise(nDocs = dplyr::n_distinct(DocID), .by = Task) |>
  clf_say_table(.title = "Documents labelled, per task")
```

```{r}
#| label: results-distribution
tab_labels |>
  dplyr::filter(Task == "ClassDetailed") |>
  dplyr::count(Label, name = "nDocs", sort = TRUE) |>
  dplyr::mutate(Share = clf_pct(nDocs / sum(nDocs))) |>
  clf_say_table(.title = "Category distribution across the corpus")
```

The corpus distribution against the labelled sample's is the first thing worth checking, and it is a
validity check rather than a curiosity. The labelled sample was drawn to be representative; a
category that is common in the corpus and rare in the sample, or the reverse, is either a sampling
artifact worth documenting or a model failing systematically outside the distribution it was trained
on. Which of the two it is cannot be settled here, but a large gap is a reason to look.

```{r}
#| label: results-confidence
tab_labels |>
  dplyr::filter(Task == "ClassDetailed") |>
  dplyr::count(VotingSet, Tier, name = "nDocs") |>
  dplyr::mutate(Share = clf_pct(nDocs / sum(nDocs))) |>
  clf_say_table(.title = "Confidence tiers across the corpus")
```

If the tier distribution here differs markedly from 03E's on the labelled sample, the flag is
behaving differently outside the data it was estimated on, and its reliability numbers should be
treated with more caution than the table suggests. That comparison belongs in the paper.

# Validation

The deployed classifier applied to the labelled sample must reproduce what 03E measured. Any gap is a
deployment fault -- a wrong checkpoint, a different context length, a lexicon that moved -- rather
than a modelling result, and it is the one check that catches an artifact mismatch the manifest's
existence test cannot.

```{r}
#| label: validation-roundtrip
round_trip <- mc_classify(
  .docs     = tab_prep |> dplyr::select(DocID, Text, dplyr::any_of("DocDesc")) |>
    dplyr::slice_head(n = 1000L),
  .manifest = man,                # the deployed configuration
  .tasks    = "ClassDetailed",    # the headline task
  .tab_prep = tab_prep,           # only used if the generative arm runs
  .python   = .lP$Engine$Python,  # inference environment
  .script   = .lP$Engine$Script   # inference script
)

round_trip |>
  dplyr::inner_join(
    tab_prep |> dplyr::select(DocID, TrueLabel = ClassDetailed),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::summarise(
    nDocs    = dplyr::n(),
    Accuracy = mean(Label == TrueLabel)
  ) |>
  dplyr::mutate(Accuracy = clf_pct(Accuracy)) |>
  clf_say_table(.title = "Deployed classifier on labelled documents")
```

This number will sit **above** the cross-validated estimate, and that is expected rather than
reassuring: the deployed model was refit on every labelled document, so these are documents it has
seen. It is a plumbing check, not a performance claim. The honest figure for the paper remains 03E's
nested estimate, and quoting this one instead would be reporting training accuracy.

# Overview

```{r}
#| label: overview-report
mc_report_manifest(.man = man)
mc_report_run(.tab = tab_labels)
```

# Next

The released dataset is these labels plus the manifest that produced them. Both have to be archived
together: labels without the manifest cannot be reproduced, and the manifest without the labels is a
recipe nobody ran.

Two things remain open and belong in the paper rather than in code. Whether the generative arm is
worth enabling for the release is a cost decision that 03E's voting-set comparison answers
empirically -- if the three-family flag separates the corpus no better than the two-family one, it is
not worth the hours. And the corpus tier distribution against the labelled sample's is the evidence
for how far the confidence flag can be trusted outside the data that produced it.
