---
title: "04A -- Entity Extraction"
subtitle: "Nine engine-model combinations over the labelled sample"
---

```{r}
#| label: setup
#| include: false

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(message = TRUE, warning = TRUE, comment = "")
options(cli.num_colors = 1)

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")

# The extraction layer: suites, store, ledger, benchmarks. Sourced before this document's own
# library, which calls into it.
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# 03A owns the sample, the folds, the contract-type vocabulary and the fixed-width console formatter
# every document in the monorepo reports through. Sourcing it means the entity work joins to exactly
# the partition the classifiers were scored on, and orders contract types the same way in every
# table.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

# This document's own library. init_create_script_fun() resolves it from the script name rather than
# from a typed path, so the pair cannot drift.
.name_script <- "04A-EntityExtract"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),
  .name_script = .name_script
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),
  .name_script = .name_script
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This script runs every available entity extractor over the labelled sample and stores what each one
found, span by span. It is the evidence base for the rules in 04B: nothing here decides which
extractor to use, which spans to keep, or what any of them mean.

## Why it only describes

An entity extractor is a proposal, not an answer. LexNLP proposes that a run of characters is an
organisation; spaCy proposes something different about the same characters; a regex proposes a third
thing. Choosing among those proposals requires evidence about how they behave on this corpus, and
that evidence cannot be gathered without first running all of them and keeping the results side by
side. Selecting an engine here, before the comparison exists, would be choosing on prior belief and
then reporting the consequence as a finding.

So this document extracts and reports, and 04B argues.

## The one decision that cannot be undone later

Every span is stored as **character offsets into the sample text**, half-open and over code points,
such that `text[Start:Stop]` reproduces the span exactly. That is what makes a later rule able to
ask questions no extractor answered: how far is this money amount from the nearest redaction, does
this place name sit inside an organisation's name, which party does this date belong to.

An extractor that returned only strings would make all of those unanswerable without re-reading
every document, and the offsets cannot be recovered afterwards because the same string occurs many
times in one contract. The offsets are checked on every span in the store, in the Validation section
below, because everything downstream is worthless if they are wrong.

## One store, and the grid inside it is ragged

Not every engine produces every label. spaCy finds organisations, people and places; LexNLP adds
dates and money; the matcon suite adds redaction indicators and stated contract terms, and finds no
people at all. The store holds one table per label rather than one per engine, so a question about
dates reaches every engine that produces dates without knowing in advance which those are.

Two labels have exactly one producer -- REDACT and TERM -- so cross-engine agreement does not exist
for them and is not reported. Coverage and the offset contract still apply.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 03A's prepared sample: the one file every downstream method reads. Read, never written. The
    # directory resolves through the same helper 03A used to create it, so a renumbering cannot
    # desynchronise the two.
    Prepared = utils_file_path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    )
  ),
  Output = list(
    # .dir_main is 2_output/04A-EntityExtract, resolved in the setup chunk from the script name.
    # Each script writes only into its own output directory.
    Sample = utils_file_path(.dir_main, "sample_text.parquet"),
    Stage  = utils_file_path(.dir_main, "Stage"),
    Store  = utils_file_path(.dir_main, "Store", "EntityCandidates.duckdb")
  ),
  Params = list(
    # ONE SET OF TUNING VALUES FOR ALL THREE SUITES. The per-combination values this replaces were
    # calibrated against extractors that no longer exist: gazetteer-v1 ran at roughly five seconds a
    # document and needed a chunk of eight, and gazetteer-v2 runs at two thousand a second.
    NProcess  = 20L,
    BatchSize = 32L,
    Timeout   = 600L,
    # Benchmark grid. Ten workers rather than twenty so a batch of 256 still gives every worker a
    # full batch on a 4,398-document sample.
    BenchBatches = c(8L, 32L, 128L, 256L),
    BenchWorkers = 10L
  ),
  Models = list(
    Spacy = c("en_core_web_sm", "en_core_web_md", "en_core_web_lg", "en_core_web_trf")
  )
)

fs::dir_create(c(.lP$Output$Stage, fs::path_dir(.lP$Output$Store)))
```

**Twenty workers rather than twenty-four, and the reason is the machine.** Measured throughput rises
1.60x from eight workers to sixteen and only 1.15x from sixteen to twenty-four, which is the shape
of a 28-core M3 Ultra: twenty performance cores and eight efficiency cores. Workers past the
twentieth land on efficiency cores running at roughly a third the speed, so they add scheduling
pressure and very little work.

The transformer is the one apparent exception and it needs no configuration: `extract_spacy.py`
forces a single worker whenever a GPU is active, because one Metal device cannot be shared across
worker processes.

**The timeout is a hang detector, not a budget.** At the regex suite's throughput a document taking
ten minutes is running five orders of magnitude beyond the median. LexNLP's geoentity pass averages
about five seconds per document and scales with length, so ten minutes is roughly two orders of
magnitude of headroom -- deliberately generous, because a timeout there is not one lost document but
documents lost *systematically in the longest agreements*, which is the worst possible place for a
missing-at-random assumption to fail.

# Sample

```{r}
#| label: build-sample

tab_sample <- ent_build_sample(
  .path_prepared = .lP$Input$Prepared,   # 03A's prepared sample, the one file downstream reads
  .text_col      = "Text"                # 03A's name for it; renamed to TextRaw on the way out
)

arrow::write_parquet(tab_sample, .lP$Output$Sample)
ent_report_sample(.tab = tab_sample, .class_col = "ClassDetailed")
```

**The text is copied rather than referenced, and that is the point.** Every offset in the store
indexes this file. If the text a span points into could change -- because 03A re-read the corpus, or
normalised it differently -- then an offset would be a promise nobody can keep. One script writes
this file and nothing else rebuilds it.

The column is renamed from `Text` to `TextRaw` on the way through. Every extractor defaults to
`TextRaw` and the whole 04 family reads that name, so one place decides what the canonical text is
called and nothing downstream needs configuring.

# Engines

```{r}
#| label: describe-suites

tab_declared <- ner_describe(.spacy_models = .lP$Models$Spacy)

# WHAT IS DECLARED AND WHAT IS AVAILABLE ARE DIFFERENT QUESTIONS. A spaCy model named here but not
# downloaded fails at load time, which on this pipeline is after every faster combination has run.
tab_describe  <- ner_runnable(.describe = tab_declared)
tab_grid      <- ner_report_describe(.describe = tab_describe, .labels = NULL)
tab_producers <- ner_producers(.grid = tab_grid)
```

**The matcon rows describe themselves.** `matcon-extract --describe` reports its models, labels and
spec hashes, and R reads that rather than restating it. The alternative -- a table in R naming what
each extractor produces -- was silently wrong the moment one extractor gained a second label: the
table said one thing, the request asked for one thing, the second label was filtered out inside
Python, and the run recorded success. Nothing errored and no check could have caught it, because the
two declarations agreed about everything R could see.

spaCy and LexNLP do not self-describe, so their label sets are declared and then checked against
what arrives. That asymmetry is honest rather than inconsistent: ours describes itself because we
wrote it.

**A model name is not a model.** The spaCy suite is asked which models it actually has, and any that
were declared but not installed are excluded here and named. That is recoverable rather than fatal:
the remaining combinations are still worth running, and the producer table above records that the
comparison covered three models where four were intended.

**The spec hash is what makes a model tag mean something.** It fingerprints the constants that
determine an extractor's output -- pattern tables, vocabularies, and for the gazetteer a content hash
of its 116,000-entry lookup. A hash that has moved under an unchanged model tag means a rule was
edited without a version bump, which would silently change what an existing store's rows mean.

# Smoke test

```{r}
#| label: smoke-test

# Opened here rather than at extraction, because the benchmark's timing log lives in the same store
# and runs before any extraction does. This is the only document that writes it.
con <- ner_db_connect(.db_path = .lP$Output$Store, .read_only = FALSE)
ner_db_init(.con = con)

dir_smoke <- fs::path(tempdir(), "04A-smoke")

tab_smoke <- ent_smoke_test(
  .tab_sample = tab_sample,                                             # draw from the real sample
  .spec       = dplyr::select(tab_describe, "Suite", "Engine", "Model", "Labels"),
  .dir        = dir_smoke,                                              # temporary; never the store
  .n          = 50L,                                                    # enough to exercise every path
  .seed       = 42L,                                                    # a failure is reproducible
  .n_process  = .lP$Params$NProcess,
  .batch_size = .lP$Params$BatchSize,
  .timeout    = .lP$Params$Timeout
)

ent_report_smoke(.tab = tab_smoke)
fs::dir_delete(dir_smoke)
```

**The cheapest question, asked first.** A full pass over this sample takes hours and most of it sits
in one suite, yet every structural failure it can have is visible on fifty documents: a missing
interpreter, a container that no longer matches its sources, a schema that moved, an offset that
does not round-trip. Asking after the hours have been spent is asking too late.

Five checks per combination, each of them an assertion something later depends on. One
`(Engine, Model)` per file, because ingest refuses anything else. The core columns in order. Every
document present, so that processed-and-empty stays distinguishable from never-processed. Offsets
that round-trip exactly. Sentinel rows carrying nothing but their stamp.

It writes to a temporary directory and never to the store. A smoke test that ingests is not a test;
it is a partial run somebody has to undo.

# Benchmark

```{r}
#| label: bench-run

tab_bench <- ner_bench_run(
  .con      = con,                                   # the benchmark log lives in the same store
  .spec     = dplyr::select(tab_describe, "Suite", "Model", "Labels"),
  .path_in  = .lP$Output$Sample,                     # the same documents the real run used
  .n_doc    = nrow(tab_sample),                      # for the key and the rate
  .batches  = .lP$Params$BenchBatches,               # 8, 32, 128, 256
  .workers  = .lP$Params$BenchWorkers                # 10, so a batch of 256 fills every worker
)

tbl_say(
  .tab   = dplyr::select(tab_bench, "Suite", "Model", "Batch", "Workers", "Seconds", "DocPerS"),
  .title = "Throughput by suite, model and batch size"
)
```

**The first render of this section is expensive and every later one is not.** Results are keyed on
suite, model, labels, batch, workers, document count and machine, and only cells absent from that key
are measured. Adding a batch size measures that batch size. Nothing is skippable and nothing is
switched off, which is what distinguishes this from disabling the chunk: the table is always
complete, and completeness is what makes it evidence.

**The machine is part of the key** because a timing from a different box is a different measurement.
Without it, running this on a laptop would silently overwrite the numbers this section reports.

Ten workers rather than twenty, so that the largest batch under test still gives every worker a full
batch: 256 documents across ten workers needs 2,560 documents, and the sample has more. Throughput
scales close to linearly below the performance-core ceiling, so the ranking transfers.

**This runs before the extraction it informs, not after it.** The batch size the next section uses is
declared in the configuration, and until this table exists that declaration is a guess. Reporting the
measurement after the pass it should have guided would make it a description of a decision already
taken.

The declared value stays declared. This section reports what each setting costs; it does not pick
one, because a run whose parameters depend on a timing would produce different work on different
machines and nothing would record which.


# Extraction

```{r}
#| label: extract-run

tab_runs <- ent_extract_all(
  .con        = con,                                    # store connection
  .path_in    = .lP$Output$Sample,                      # the text every offset will index
  .doc_ids    = tab_sample$DocID,                       # what the ledger is asked about
  .spec       = dplyr::select(tab_describe, "Suite", "Engine", "Model", "Labels"),
  .stage_dir  = .lP$Output$Stage,                       # where suites write their parquets
  .n_process  = .lP$Params$NProcess,                    # 20
  .batch_size = .lP$Params$BatchSize,                   # 32
  .timeout    = .lP$Params$Timeout,                     # 600 seconds per document
  .force      = FALSE                                   # FALSE skips work the ledger records as done
)

tbl_say(.tab = tab_runs, .title = "What ran, and what was skipped")
```

By this point the plumbing is established and the cost of each setting is measured, so this is the
only expensive step whose outcome was not already known.

**The ledger is what makes re-rendering cheap.** A combination whose documents are all recorded is
skipped entirely, so the first render pays for extraction and later ones cost seconds. That is also
why no chunk in this document needs a switch: expense is handled by knowing what has been done, not
by turning work off.

```{r}
#| label: verify-stamps

ner_describe_verify(
  .paths    = fs::dir_ls(.lP$Output$Stage, glob = "*.parquet"),   # everything the suites wrote
  .grid     = tab_grid,                                          # what they were asked for
  .describe = tab_describe                                       # and what they said they would stamp
)
```

Every label that arrived must appear in the grid for its combination. A label outside it has no
ledger entry, so it would be stored and then never counted as done -- invisible to every completeness
check that follows.

# Coverage

```{r}
#| label: report-coverage

tab_coverage <- ent_report_coverage(
  .con   = con,              # store connection
  .n_doc = nrow(tab_sample)  # denominator for the coverage share
)
```

Coverage is the share of sample documents in which a combination found at least one span of a label.
It is not a quality measure and should not be read as one: an engine that tags every capitalised word
as an organisation reaches complete coverage and is useless. What it establishes is which comparisons
are possible at all, since two engines can only be compared where both fire.

**Timeouts and errors are reported apart from clean misses.** A document that was processed and
matched nothing is a coverage fact; a document whose extractor crashed is a defect, and pooling the
two hides it. Until recently they were indistinguishable -- a crash produced the same empty result as
a clean miss, so a pattern failing on a whole class of documents looked exactly like that class
having no matches.

# Agreement

```{r}
#| label: report-agreement

lst_agreement <- ent_report_agreement(
  .con       = con,           # store connection
  .producers = tab_producers  # which labels have more than one producer
)
```

Agreement is measured on **exact offsets**. Two engines agreeing that a document mentions an
organisation is not agreement about which characters that organisation occupies, and only the second
is checkable without judgement. The Jaccard figure is therefore a lower bound on any looser notion of
agreement, and a pair that disagrees here may still be describing the same entity differently.

```{r}
#| label: report-geo-concordance

tab_geo <- ent_geo_concordance(.con = con)

if (nrow(tab_geo) > 0L) {
  tbl_say(
    .tab   = dplyr::count(tab_geo, Verdict, name = "NSpan"),
    .title = "Where both engines fire on the same place, do they resolve the same one?"
  )
}
```

**This comparison did not exist before the gazetteer began emitting geographic identifiers.** Both it
and LexNLP report `Iso2` in the same `US-MN` form -- the geo lookup was built that way *because*
LexNLP emits it -- so for the first time two independent methods produce the same identifier for the
same characters, and disagreement is checkable rather than a matter of reading both outputs and
forming an impression.

A null on one side is not disagreement. The gazetteer refuses to resolve a name whose parent is
ambiguous, and reports how many parents it has instead: SPRINGFIELD is a populated place in
thirty-three states, and naming one of them would be inventing a value.

# Validation

```{r}
#| label: report-validation

lst_validation <- ent_report_validation(
  .con      = con,         # store connection
  .tab_text = tab_sample,  # the text every offset must index
  .grid     = tab_grid     # every combination that should have run
)
```

Two invariants, both of which abort rather than warn.

**The offset contract**, checked on every span in the store. `text[Start:Stop] == Span`, over code
points, sliced with `stringi::stri_sub` -- base `substr` indexes bytes and misaligns roughly
ninety-nine per cent of spans on this corpus, so getting this wrong is not a subtle error.

**Ledger completeness.** Every sample document must have an outcome recorded for every combination it
was sent to. A document missing from the ledger is invisible in any span count, because a document
with no spans and a document never processed produce the same empty result.

# Deployment

```{r}
#| label: deploy-summary

tbl_say(.tab = ner_db_summary(.con = con), .title = "What the store holds")

cli::cli_alert_success("Sample: {(.lP$Output$Sample)}")
cli::cli_alert_success("Store:  {(.lP$Output$Store)}")

DBI::dbDisconnect(con, shutdown = TRUE)
```

Two artifacts, and both are contracts rather than conveniences. `sample_text.parquet` is the text
every offset in the store indexes, and the store is what 04B reads. Everything else this document
produces is insight and can change freely.

# Overview

```{r}
#| label: overview

con <- ner_db_connect(.db_path = .lP$Output$Store, .read_only = TRUE)

tbl_say(.tab = tab_producers, .title = "Producers per label")
tbl_say(.tab = ent_coverage(.con = con, .n_doc = nrow(tab_sample)), .title = "Coverage")
tbl_say(
  .tab   = dplyr::select(tab_bench, "Suite", "Model", "Batch", "DocPerS"),
  .title = "Throughput"
)

DBI::dbDisconnect(con, shutdown = TRUE)
```

No figures yet. The old version of this document plotted agreement matrices and span-position
densities; whether either is worth reproducing depends on what 04B turns out to need, and inventing
figures before then would fill this section with charts nobody reads. It is a compact re-report until
that question is answered.

# Next

**04B** takes this store and argues from it: one document per entity, each proposing rules that turn
candidate spans into variables, and each measuring what its rules keep and discard against an
unadjusted baseline. Nothing there re-extracts; every rule is a query against the offsets stored
here.
