---
title: "Entity Extraction -- Running Every Engine Over the Classified Sample (04A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                          # message = FALSE would discard this document's entire output
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,        # fixed for every figure; only height varies, and only with row count
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# 03A owns the sample, the folds and the fixed-width console formatter every document in the
# monorepo reports through. Sourcing it means the entity work is described in the same table style
# as the classification work, and joins to exactly the partition the classifiers were scored on.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04A-EntityExtract.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Four quantities are wanted from each contract: who the parties are, when the agreement runs from and
to, where the parties are, and what it is worth. None of them is read directly. Each is assembled
from spans that an extraction engine proposed, and every engine proposes many spans that are not the
thing being looked for. This document runs every available engine over the 4,400 hand-classified
contracts, stores every span it proposed, and describes what came back.

It does not choose between the engines, and the reason is worth stating plainly because it shapes the
whole family. The classification pipeline had 4,400 hand labels, so a configuration could be scored
and ranked. **There are no entity labels.** Without them the only measurable quantity here is
*yield*: candidates per document, documents with a hit. Yield does not order engines. An engine
returning twice as many organisations is either recovering parties the others miss or admitting twice
as much noise, and nothing in this document can tell those apart. Ranking on yield would reliably
select whichever engine matches most loosely.

What the absence of labels still permits is a question that turns out to be more useful at this
stage: **where do the engines differ?** Two models whose outputs are nested carry one model's worth of
information and the choice between them is free. Two models that disagree are the only place a gold
standard has anything to adjudicate. The agreement analysis below is therefore not a scoreboard; it
is the sampling design for 04B.

## The one decision that cannot be undone later

An offset is an integer into a specific string. Every candidate in the store, every context window
the adjudicator will read, and every span rehydrated for manual checking indexes *that* string. If
two scripts disagree about what a document's text is, every offset in the project is quietly wrong,
`is.na()` catches nothing, and the numbers look entirely normal.

The two available candidates for that string are not identical. 03A built its `Text` column by
concatenating a document's parquet rows with newlines, so any document stored in more than one row
has a prepared text that differs from its on-disk `TextRaw`. This document therefore derives the
canonical text from `prepared.parquet` and writes it once, as `sample_text.parquet`. The two are then
the same string by construction rather than by assumption, and no later script reconstructs text.

## Two settings that are frozen by the first run

The store's completeness ledger records that a document was processed by an engine. It does not
record which labels were requested, and it does not record whether the text was truncated first. A
store built under one truncation and re-run under another therefore does nothing at all and reports
success. Both settings are consequently fixed here, and a manifest records them so that a later
mismatch is visible rather than silent.

**No truncation.** The paper's original extraction read the first 250 words, on the argument that
parties appear in the preamble. That is true of parties and false of everything else: expiry dates
sit in the term clause, governing law sits near the signature block, and payment amounts sit in the
schedules. Truncating at extraction discards that evidence irreversibly, whereas keeping it costs
only compute on a 4,400-document sample. The positional evidence this produces is what tells 04E
where the corpus pass may safely be capped, which is a better basis for that cap than inheriting a
number from the earlier design.

**All labels each engine supports.** Organisations, places, dates and money, subject to what each
engine can emit.

## Two stores

The same blindness has a second consequence. Because the ledger cannot tell a full-text extraction
from a truncated one, a single store cannot hold both: the second would be skipped as already done
and the document would report success. Measuring what truncation costs therefore needs its own
store, with its own manifest, and that is what the section on cost builds.

The two questions truncation raises are answered differently, and only one of them needs that
store. What a head window would COST in recall is already answered by the full-text extraction,
because every candidate carries its offsets and the share falling inside any window is a query.
What truncation SAVES in time is not, because a truncated pass is not a filtered full pass -- the
engines see a document that stops mid-sentence, and the gazetteer can lose the jurisdiction that
licensed a place two lines further down. That has to be run to be known.

## What is missing, and why one engine is absent

Geography is the weakest channel in this extraction and the one a referee has asked about directly,
so it is worth saying what the gazetteer contributes and why it is not simply a dictionary match.

The lookup holds 181,810 place names, 31,925 of which are also English dictionary words. Matching
them all is useless -- Enterprise, Superior, Mobile, Reading and Bath are all US populated places --
and excluding them all is worse than it sounds: every single-word US state name is in the
dictionary, so a blanket exclusion removes forty of the fifty states, Delaware and California among
them, and leaves a state-level geography consisting of the ten whose names happen to run to two
words. The extractor keeps those names and gates them on context instead: states and countries are
self-evidencing, a distinctive place name needs a jurisdiction within a couple of hundred
characters, and a place name that is also an ordinary word needs one immediately adjacent, with
only punctuation between. That last rule is what separates the city from the street it stands on,
since an address block puts a state within forty characters of every token in it.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 03A's output: labels, folds, and the text this document makes canonical.
    Prepared = "2_output/03A-ClassifyPrepare/prepared.parquet",
    # EDGAR document metadata: filer name, CIK, filing date, and the HashIndex the landing
    # page is keyed on.
    MetaData = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    # EDGAR landing page: the registered addresses, which are keyed on the filing rather than
    # on the document and so are absent from the table above.
    LandingPage = "../pMatDisc/2_output/01-GetEDGAR/Output/LandingPage.parquet"
  ),
  Sample = list(
    Text    = utils_file_path(.dir_main, "sample_text.parquet"),      # THE offset basis
    Anchors = utils_file_path(.dir_main, "sample_anchors.parquet")    # labels, folds, EDGAR facts
  ),
  Store = list(
    NerDB        = utils_file_path(.dir_main, "Store", "EntityCandidates.duckdb"),
    Manifest     = utils_file_path(.dir_main, "Store", "manifest.parquet"),
    # The head-window store. Separate file and separate manifest, because the ledger cannot
    # distinguish a truncated extraction from a full one.
    NerDBHead    = utils_file_path(.dir_main, "StoreHead", "EntityCandidatesHead.duckdb"),
    ManifestHead = utils_file_path(.dir_main, "StoreHead", "manifest.parquet"),
    # Append-only record of what each engine cost, shared by both stores.
    TimingLog    = utils_file_path(.dir_main, "Store", "timings.parquet")
  ),
  Params = list(
    RefCombo     = "spacy:en_core_web_trf",   # engine the per-class fingerprint is printed for
    DocsPerRun   = 2500L,                     # R-side corpus slice; bounds Python memory
    OffsetSample = 2000L,                     # candidates rehydrated per engine in Validation
    HeadWords    = 512L,                      # word budget the head window should correspond to
    CorpusDocs   = 1135840L                   # Exhibit-10 documents in the full corpus, for costing
  )
)

# These two cannot live in .lP. Assigning NULL to a list element removes the element rather than
# storing it, so .lP$Params$MaxChars would silently vanish and the call site would read NULL from a
# name that was never set -- indistinguishable from a typo.
.max_chars_extract <- NULL   # NULL = no truncation; see Purpose. Changing this invalidates the store.
.labels_extract    <- NULL   # NULL = each engine's own supported label set

fs::file_exists(c(.lP$Input$Prepared, .lP$Input$MetaData))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

Two files come out of this section, and every later script in the family reads them rather than
reaching back to 03A. The first is the canonical text. The second is everything known about a
document from outside its own text.

```{r}
#| label: write-canonical-text
ent_write_text(
  .path_prepared = .lP$Input$Prepared,   # 03A's output, including its Text column
  .path_out      = .lP$Sample$Text       # the string every offset in this family indexes
)
```

There is deliberately no reuse guard on that write. Skipping it when the file already exists would
disable the run manifest at the moment it matters: the manifest fingerprints this file, so a changed
sample behind a reused text file would produce an unchanged fingerprint and report agreement while
the store was built on documents that are no longer in the sample. Copying one column of 4,400 rows
costs seconds, which is far less than that failure.

The anchors are the reason this section is not merely bookkeeping. A contract's filer, its CIK, its
filing date and its registered addresses are facts recorded by EDGAR and never derived from the
contract text. They can therefore test an extraction without anyone annotating anything: the filer
must be a party to its own contract, the signing date cannot post-date the filing, and a joint filing
must name both filers. 04B turns those into recall floors. 04A only establishes that they are present
and reports which are not, because an anchor discovered to be missing after the adjudication budget
has been spent is an anchor that cannot be used.

```{r}
#| label: build-sample
tab_sample <- ent_build_sample(
  .path_prepared = .lP$Input$Prepared,      # labels, folds; Text deliberately not read here
  .path_meta     = .lP$Input$MetaData,      # document-level EDGAR facts, keyed on DocID
  .path_landing  = .lP$Input$LandingPage,   # filing-level facts, keyed on HashIndex
  .cols_anchor   = c(
    "CIK",             # filer identity, and the join key to Compustat downstream
    "CompanyName",     # the filer must appear among the extracted organisations
    "DateFiled",       # a signing date cannot post-date this
    "nCIK",            # joint filings: more than one filer
    "MultFiler"        # the flag form of the same fact
  ),
  .cols_landing  = c(
    "BusinessAddress", # the filer's own location, testable against extracted places
    "MailingAddress"   # a second location for the same test
  )
)

ent_write_anchors(
  .tab      = tab_sample,          # labels, folds and whichever anchors resolved
  .path_out = .lP$Sample$Anchors   # the table every later script joins entities to
)
```

# Extraction

## The engine set

Eight combinations run. Each carries its own throughput settings, because the constraints differ in
kind rather than degree: the CNN spaCy models parallelise across CPU processes, the transformer
occupies one device and cannot be shared across processes, LexNLP runs in a container and its date
grammar stalls pathologically on a small number of documents, and the three ported paper extractors
are pattern matching, dictionary lookup and bracket matching, with nothing to tune beyond their
worker count.

The last of those is not an entity extractor in the usual sense. `paper:redaction-v1` emits the
bracketed redaction indicators the published analysis counted -- `[***]`, `[CONFIDENTIAL TREATMENT
REQUESTED]`, `[INTENTIONALLY OMITTED]` -- as spans under the label `REDACT`. A count carries no
position and so can say how much was withheld but not what; putting the indicators in the same
coordinate system as the candidates turns "how far is this amount from the nearest redaction" into a
window function. That is the only external evidence money admits, since a marker sits exactly where
a commercially material figure used to be.

The order is cheapest first. That is not cosmetic. The regex and the small spaCy model together
produce the positional evidence and most of the per-class picture within minutes, so the document's
substantive claims can be inspected and argued with long before the transformer finishes.

```{r}
#| label: configure-engines
ner_tuning <- list(
  "paper:dateregex-v1"    = list(n_process =  1L, batch_size = NULL, timeout =   0L),
  "spacy:en_core_web_sm"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_md"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_lg"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "lexnlp"                = list(n_process = 24L, batch_size =   8L, timeout =  60L),
  "spacy:en_core_web_trf" = list(n_process =  1L, batch_size = 128L, timeout = 600L),
  "paper:gazetteer-v1"    = list(n_process = 16L, batch_size =   8L, timeout = 120L),
  "paper:redaction-v1"    = list(n_process = 16L, batch_size =  64L, timeout =   0L)
)

lst_run_args <- ner_run_args(.tuning = ner_tuning)
```

## What the store is being built under

```{r}
#| label: check-manifest
tab_manifest <- ent_manifest_sync(
  .path_manifest = .lP$Store$Manifest,
  .manifest      = ent_manifest(
    .path_text = .lP$Sample$Text,        # fingerprinted, so a changed sample is not a warm store
    .run       = lst_run_args$.run,      # which engines
    .labels    = .labels_extract,        # which labels
    .max_chars = .max_chars_extract      # whether the text was truncated first
  )
)

clf_say_table(.tab = tab_manifest, .title = "Store fingerprint")
```

Two kinds of row, and they call for opposite responses.

A **fingerprint** row that fails means the store was built on different text, a different truncation
or a different label set from the one now declared. The ledger cannot detect any of those, so the
extraction below would skip every document and report success while answering the wrong question.
Rename `Store/` aside and rebuild; nothing is deleted, so the superseded store remains available as
a record of what was previously concluded.

The **inventory** row is not a fingerprint. Which engines have been asked for says nothing about
what is already stored, and adding one is the ordinary incremental case the ledger handles
correctly: the new combo reports its documents missing and the rest report none. The manifest
records the addition and stops mentioning it. Only a combo that has *disappeared* is worth a look,
and then only because the store now holds more than this document describes.

## Running

The step is idempotent and resumable. Each combination asks the ledger which documents it has not yet
seen, processes only those in slices, and appends. An interrupted run repeats only its unfinished
slice, which is what makes a multi-hour extraction affordable inside a document that always executes.

Engines are dispatched one at a time rather than as a set. The ledger behaves identically either
way, and running them separately turns the same call into a measurement: what each engine costs is
the input to every decision 04E has to make, and `ner_run()` on the whole set reports how much was
extracted rather than how long any one engine took.

```{r}
#| label: extract-entities
tab_extract <- ent_time_engines(
  .path_text    = .lP$Sample$Text,        # the canonical text, not the per-document tree
  .db_path      = .lP$Store$NerDB,        # the full-text candidate store
  .tuning       = ner_tuning,             # engines and their per-combo knobs, cheapest first
  .labels       = .labels_extract,        # NULL = each engine's own supported set
  .max_chars    = .max_chars_extract,     # NULL = full text; frozen by the manifest above
  .docs_per_run = .lP$Params$DocsPerRun,  # slice size; bounds Python-side memory
  .device       = "auto"                  # CNN models to CPU, transformer to Metal
)

ent_timing_append(
  .tab      = tab_extract,          # only rows where work actually happened are recorded
  .path_log = .lP$Store$TimingLog   # append-only, so a re-measurement never erases the last one
)

clf_say_table(.tab = dplyr::select(tab_extract, Combo, Missing, Docs, Candidates, Seconds),
              .title = "This run")
```

Zeros in `Missing` are the expected steady state: on a second render every document is already in the
ledger and the whole section costs seconds. A non-zero `Missing` with zero `Docs` is the failure to
look for, because it means an engine was asked for work and returned none.

# Results

```{r}
#| label: summarise-store
.ov <- ner_overview(
  .db_path  = .lP$Store$NerDB,     # the store just written
  .inputs   = .lP$Sample$Text,     # supplies document lengths and relative positions
  .id_col   = "DocID",
  .text_col = "TextRaw",
  .quiet    = FALSE
)

ent_report_store(.ov = .ov)
```

```{r}
#| label: align-engines
.al <- ner_alignment(
  .db_path = .lP$Store$NerDB,   # overlapping spans are merged into mentions inside DuckDB
  .quiet   = FALSE
)

ent_report_agreement(
  .al = .al,   # consensus and directional containment
  .n  = 12L    # the most complementary engine pairs, which is where 04B must sample
)
```

# Yield

## What is expected before looking

Stating the expectation first makes the check falsifiable rather than decorative, and makes it
obvious when it was wrong.

| Check | Expectation | If otherwise |
|:--|:--|:--|
| ORG per doc | Highest in merger and credit, lowest in employment | Party extraction is not measuring parties |
| MONEY per doc | Concentrated in credit and leases, near zero in employment | Spans catch section numbers, not amounts |
| REDACT per doc | Highest in licences and R&D, where royalties sit | Indicators are boilerplate, not withheld terms |
| ORG position | Mass in the opening tenth | Preamble truncation discarded parties, not noise |
| DATE position | Bimodal: preamble and signature block | Signing or expiry is not found at all |
| GPE position | Opening and the governing-law clause | Places found are incidental, not party locations |
| Amendments | Fewer ORG and MONEY per doc than originals | Amendments read as restating the original in full |

The first row is a replication: the published extraction reports 4.2 partners for merger and debt
agreements against 2 for employment, and those spans should reproduce it. The places row is the one
that matters most. If the distribution is flat, the geographic variable as currently defined cannot
be described as the location of the contracting parties, and 04D has to classify each place by its
role rather than count them.

## Yield by contract type

The classification used is the hand-assigned category from 03A, not a predicted one, so the picture
below is not contaminated by classifier error.

```{r}
#| label: profile-detailed
.prof_detailed <- ner_profile_by_class(
  .db_path       = .lP$Store$NerDB,           # candidates
  .class_parquet = .lP$Sample$Anchors,        # the sample table written above
  .class_col     = "ClassDetailed",           # 12 hand-assigned categories
  .id_col        = "DocID",
  .run           = NULL,                      # NULL profiles every engine in the store
  .ref_combo     = .lP$Params$RefCombo,       # engine the printed fingerprint is taken from
  .mentions      = .al$mentions,              # enables the cross-engine consensus view
  .min_combos    = 2L,                        # "high confidence" = at least two engines agree
  .quiet         = FALSE
)

ent_report_yield(
  .prof      = .prof_detailed,
  .ref_combo = .lP$Params$RefCombo
)
```

The table above ranks contract types partly by how long they are. Median document length differs by
more than a factor of two across this taxonomy, so a type can lead every column for no reason beyond
page count. Dividing by the text each type actually contains removes that, and reporting median
length beside it keeps the size difference visible instead of absorbing it.

```{r}
#| label: profile-normalised
tab_yield_norm <- ent_yield_by_class(
  .db_path    = .lP$Store$NerDB,        # candidates
  .path_text  = .lP$Sample$Text,        # per-document character counts, the denominator
  .path_class = .lP$Sample$Anchors,     # the sample table written above
  .class_col  = "ClassDetailed",        # 12 hand-assigned categories
  .ref_combo  = .lP$Params$RefCombo     # one engine, else the columns are not comparable
)

ent_report_yield_norm(.tab = tab_yield_norm)
```

```{r}
#| label: profile-amendment
.prof_amend <- ner_profile_by_class(
  .db_path       = .lP$Store$NerDB,
  .class_parquet = .lP$Sample$Anchors,
  .class_col     = "AmendType",               # Original against Amended
  .id_col        = "DocID",
  .run           = NULL,
  .ref_combo     = .lP$Params$RefCombo,
  .mentions      = NULL,                      # the consensus view is reported on the detailed cut only
  .min_combos    = 2L,
  .quiet         = FALSE
)

ent_report_yield(
  .prof      = .prof_amend,
  .ref_combo = .lP$Params$RefCombo
)
```

# Validation

The round-trip below is the check the rest of the family rests on. Each sampled candidate is sliced
back out of the canonical text at its own offsets and compared to the span the engine recorded. A
share below one means the offsets index a string that is not the one on disk, in which case every
context window the adjudicator reads in 04B would be the wrong characters and no downstream number
would mean anything.

```{r}
#| label: validate-offsets
tab_offsets <- ent_check_offsets(
  .db_path   = .lP$Store$NerDB,             # candidates
  .path_text = .lP$Sample$Text,             # the canonical text they claim to index
  .n         = .lP$Params$OffsetSample      # candidates per engine, sampled deterministically
)

ent_report_offsets(.tab = tab_offsets)
```

# Cost of truncation

Reading only the head of every document is the difference between a corpus pass that finishes
overnight and one that does not. What it costs is two separate questions, and only the second needs
work.

The window is set in characters because that is what the extractors take, but it is reasoned about
in words. The conversion is a property of the text rather than a constant: legal prose runs long
words and dense citation, so a rate borrowed from general English would be wrong in the direction
that matters. It is measured here instead.

```{r}
#| label: derive-head-cap
tab_cap <- ent_head_cap(
  .path_text = .lP$Sample$Text,        # the canonical text
  .n_words   = .lP$Params$HeadWords,   # the word budget the cap should correspond to
  .round_to  = 100L                    # round up, so the cap is a reportable number
)

.cap_head <- tab_cap$Cap
```

## What the window would keep

This needs no extraction. Every candidate in the full-text store carries its offsets, so the share
of them ending inside the cap is a count.

```{r}
#| label: measure-head-coverage
tab_head_cov <- ent_head_coverage(
  .db_path = .lP$Store$NerDB,   # the full-text store
  .cap     = .cap_head          # the window derived above
)
```

## What the window would save

This does need extraction, into a store of its own. A truncated pass is not the full pass filtered
to the same window: the engines see a document that stops mid-sentence, and the gazetteer can lose
the jurisdiction that licensed a place two lines further down. Whether the two agree is itself the
result, and it is reported below.

```{r}
#| label: extract-head-window
tab_head_manifest <- ent_manifest_sync(
  .path_manifest = .lP$Store$ManifestHead,
  .manifest      = ent_manifest(
    .path_text = .lP$Sample$Text,     # same text
    .run       = lst_run_args$.run,   # same engines
    .labels    = .labels_extract,     # same labels
    .max_chars = .cap_head            # and the one thing that differs
  )
)

clf_say_table(.tab = tab_head_manifest, .title = "Head-store fingerprint")

tab_time_head <- ent_time_engines(
  .path_text    = .lP$Sample$Text,          # same input
  .db_path      = .lP$Store$NerDBHead,      # a separate store; the ledger cannot tell caps apart
  .tuning       = ner_tuning,               # same engines and knobs, so the comparison is paired
  .labels       = .labels_extract,          # same labels
  .max_chars    = .cap_head,                # the window
  .docs_per_run = .lP$Params$DocsPerRun,
  .device       = "auto"
)

ent_timing_append(
  .tab      = tab_time_head,
  .path_log = .lP$Store$TimingLog   # both stores write to one log, keyed by cap
)
```

```{r}
#| label: compare-head-full
tab_head_cmp <- ent_head_vs_full(
  .db_head = .lP$Store$NerDBHead,   # the truncated pass
  .db_full = .lP$Store$NerDB,       # the full pass, filtered to the same window
  .cap     = .cap_head
)

ent_report_head(
  .tab_cap = tab_cap,
  .tab_cov = tab_head_cov,
  .tab_cmp = tab_head_cmp
)
```

## What it costs to run

```{r}
#| label: report-timing
tab_timing <- ent_timing_read(
  .path_log    = .lP$Store$TimingLog,      # append-only measurement history
  .corpus_docs = .lP$Params$CorpusDocs     # documents in the full Exhibit-10 corpus
)

ent_report_timing(
  .tab         = tab_timing,
  .corpus_docs = .lP$Params$CorpusDocs
)
```

Read the projection with its assumption in view. A capped pass does the same work on every document
whatever its length, so its cost is linear in how many there are and the projection is fair. An
uncapped pass does work proportional to text, so scaling it by document count assumes the corpus has
the same length distribution as this sample, and the corpus tail is longer.

# Robustness

Three properties are worth reading off the ledger rather than assuming.

**Timeouts.** LexNLP's date grammar stalls on a small number of very long documents, and running
without truncation makes that more likely rather than less. A stalled extractor is skipped for that
document, the document is still recorded, and its status is queryable, so the cost of a timeout is
lost recall on a known and countable set rather than a silent gap.

```{r}
#| label: inspect-timeouts
.ov$ledger |>
  dplyr::filter(.data$Timeout > 0L) |>
  dplyr::select(Combo, Docs, Timeout, Candidates) |>
  dplyr::mutate(
    PctOfDocs = clf_pct(.data$Timeout / .data$Docs),
    dplyr::across(c(Docs, Timeout, Candidates), as.integer)
  ) |>
  clf_say_table(.title = "Documents with a skipped extractor")
```

**Length outliers.** Every pooled statistic in this document is candidate-weighted, so one document
long enough to hold a percent of the sample's text carries a percent of the vote in the positional
histogram and in every per-engine total. The upstream quality screens keep tabular filings out of
the corpus; a document that passed them and still runs to several megabytes is worth identifying
before its evidence is trusted.

```{r}
#| label: inspect-length-outliers
tab_outliers <- ent_length_outliers(
  .db_path    = .lP$Store$NerDB,      # candidates, for the share of the evidence
  .path_text  = .lP$Sample$Text,      # lengths
  .path_class = .lP$Sample$Anchors,   # what kind of contract each one is
  .n          = 10L                   # the longest documents in the sample
)

ent_report_outliers(.tab = tab_outliers)
```

**Engine redundancy.** Three spaCy CNN models of increasing capacity are in the store. If their
outputs are near-nested, they carry one model's worth of information between them and 04C's engine
choice among them is free; if they are not, capacity is buying recall and the largest is worth its
cost on the corpus pass.

```{r}
#| label: inspect-cnn-nesting
ent_containment(.pairwise = .al$pairwise) |>
  dplyr::filter(
    stringr::str_detect(.data$ComboA, "en_core_web_(sm|md|lg)"),
    stringr::str_detect(.data$ComboB, "en_core_web_(sm|md|lg)")
  ) |>
  dplyr::mutate(dplyr::across(c(InA, InB, Jaccard), \(.x) clf_pct(.x))) |>
  dplyr::select(Label, ComboA, ComboB, Both, InA, InB, Jaccard) |>
  clf_say_table(.title = "Containment among the spaCy CNN models")
```

# Deployment

Six artifacts leave this document, and nothing else in the family writes any of them. Only the
first four are read downstream: the head-window store and the timing log exist to inform 04E's
truncation decision and are not inputs to 04B.

```{r}
#| label: deploy-artifacts
tibble::tibble(
  Artifact = c("Canonical text", "Sample anchors", "Candidate store", "Run manifest",
               "Head-window store", "Timing log"),
  Path     = c(.lP$Sample$Text, .lP$Sample$Anchors, .lP$Store$NerDB, .lP$Store$Manifest,
               .lP$Store$NerDBHead, .lP$Store$TimingLog)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  clf_say_table(.title = "Written by 04A")
```

# Overview

Everything already established, arranged so the parallel cases can be compared side by side.

## Where candidates sit in the document

The places panel is the one to read first. Mass at the opening and again around the governing-law
clause supports describing extracted places as party locations; a flat distribution through the body
does not, and settles the question the review raised against 04D rather than in its favour.

```{r}
#| label: fig-positions
#| fig-height: 4.6
#| fig-cap: "Relative position of every candidate within its document, by entity type and engine."
ner_plot_positions(
  .positions = .ov$positions,   # midpoint over document length, in code points
  .bins      = 30L,
  .by_combo  = TRUE,            # fill by engine, so disagreement about where a type lives is visible
  .free_y    = TRUE             # counts differ by an order of magnitude across types
)
```

## How far the engines agree

High values mean the engines are substitutes and the choice between them costs nothing. Low values
mark the spans on which they disagree, which is the only material a gold standard has to work with,
and therefore where 04B concentrates its adjudication budget.

```{r}
#| label: fig-agreement
#| fig-height: 4.6
#| fig-cap: "Jaccard overlap between engines on merged mentions, by entity type."
ner_plot_agreement(
  .pairwise = .al$pairwise,
  .digits   = 2L
)
```

## Yield per contract type

Counts, not accuracies. The hit-rate panel carries a conclusion the candidate-count panel does not:
a near-zero cell means the entity type is absent from that contract type in the text itself, so no
adjudication can rescue a variable built on it. The amendment panel tests whether a document type
known to be short and to incorporate its original by reference is read as such.

::: {.panel-tabset}

### Candidates per document

```{r}
#| label: fig-yield-detailed
#| fig-height: 5.2
#| fig-cap: "Candidates per document, by hand-assigned contract type and entity type."
ner_plot_profile(
  .profile = .prof_detailed$profile,
  .combo   = .lP$Params$RefCombo,   # one engine, else the panel is unreadable
  .metric  = "CandPerDoc",
  .digits  = 1L
)
```

### Documents with a hit

```{r}
#| label: fig-yield-hitrate
#| fig-height: 5.2
#| fig-cap: "Share of documents in which the entity type appears at all."
ner_plot_profile(
  .profile = .prof_detailed$profile,
  .combo   = .lP$Params$RefCombo,
  .metric  = "PctDocsWithHit",
  .digits  = 1L
)
```

### Amendments

```{r}
#| label: fig-yield-amendment
#| fig-height: 2.4
#| fig-cap: "Candidates per document, amendments against original agreements."
ner_plot_profile(
  .profile = .prof_amend$profile,
  .combo   = .lP$Params$RefCombo,
  .metric  = "CandPerDoc",
  .digits  = 1L
)
```

:::

## The whole extraction in one block

```{r}
#| label: report-everything
ent_report_all(
  .tab_sample   = tab_sample,
  .ov           = .ov,
  .al           = .al,
  .tab_offsets  = tab_offsets,
  .prof         = .prof_detailed,
  .ref_combo    = .lP$Params$RefCombo,
  .tab_norm     = tab_yield_norm,
  .tab_outliers = tab_outliers,
  .tab_timing   = tab_timing,
  .corpus_docs  = .lP$Params$CorpusDocs
)
```

# Next

**04B** builds the gold standard this document could not use. It scores the free anchors written
here -- filer against extracted organisations, filing date against extracted dates, filer address
against extracted places -- across the whole sample, then adjudicates a stratified subsample with a
local language model, sampling most heavily where the engines disagreed. A hand-checked slice
measures the adjudicator itself, because an unvalidated oracle is not a gold standard.

**04C** then ranks the engines per entity type and contract type, which is the question this document
deliberately declined to answer, and chooses the truncation cap against measured recall rather than
against the yield reported here. **04D** resolves spans into the four published variables and checks
them against the anchors.

**04E** applies the settled policy to the full corpus. The two numbers it needs are already on this
page: what each engine costs per document, and what a head window keeps. Neither settles the cap on
its own -- a window that halves the run and loses a third of the organisations is a bad trade, and
which trade is acceptable depends on a precision measurement that does not exist until 04B.
