---
title: "Entity Extraction over the Labelled Sample (04A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

# here::i_am() anchors the project root on a declaration rather than on whichever marker file the
# search happens to find first. _quarto.yml lives in 1_code/, so Quarto's execute-dir is 1_code/ and
# not the repository root; every path below is written against the root, which is what this line and
# the opts_knit override together guarantee.
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

# Console mode, declared rather than inherited. Everything this document prints is read on screen and
# pasted into discussion, and styled markup survives neither. Styled tables are the release script's
# job.
options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary has to be sourced after it. _Tables.R follows because _NER.R
# and this document's own library both print through tbl_say().
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")

# The extraction layer: the three families, the one entry point, the three stores, the benchmark.
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# 03A owns the sample, the folds and the contract-type vocabulary. Sourcing it means the entity work
# joins to exactly the partition the classifiers were scored on, and orders contract types the same
# way in every table. It is NOT inert: it registers that vocabulary at load time, which is why it
# comes after _Plots.R.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

# This document's own library. init_create_script_fun() resolves it from the script name rather than
# from a typed path, so the pair cannot drift.
.name_script <- "04A-EntityExtract"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04A-EntityExtract.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This script runs every available entity extractor over the labelled sample and stores what each one
found, span by span. It is the evidence base for the rules in 04B: nothing here decides which
extractor to use, which spans to keep, or what any of them mean.

## Why it only describes

An entity extractor is a proposal, not an answer. LexNLP proposes that a run of characters is an
organisation; spaCy proposes something different about the same characters; a regex proposes a third
thing. Choosing among those proposals requires evidence about how they behave on this corpus, and
that evidence cannot be gathered without first running all of them and keeping the results side by
side. Selecting an engine here, before the comparison exists, would be choosing on prior belief and
then reporting the consequence as a finding.

So this document extracts and reports, and 04B argues.

## The one decision that cannot be undone later

Every span is stored as **character offsets into the canonical text**, half-open and over code
points, such that `text[Start:Stop]` reproduces the span exactly. That is what makes a later rule
able to ask questions no extractor answered: how far is this money amount from the nearest redaction,
does this place name sit inside an organisation's name, which party does this date belong to.

An extractor that returned only strings would make all of those unanswerable without re-reading every
document, and the offsets cannot be recovered afterwards because the same string occurs many times in
one contract. The offsets are checked on every span in every store, in the Validation section below,
because everything downstream is worthless if they are wrong.

## Three families, three databases

A **family** is a piece of software with its own way of being installed, versioned and called: a
container for LexNLP, a console script for matcon, a venv interpreter for spaCy. It is the unit that
has a version, and therefore the unit a benchmark describes.

Each family writes its own DuckDB file, holding one table per entity. The previous design put all
three in one file with `Engine` and `Model` columns on every span row and a combination token --
`paper:gazetteer-v1` -- that callers typed by hand. Three of the four matcon versions have since
moved, so every one of those typed tokens is now wrong, and the failure is silent: the query matches
nothing, returns an empty result, and a document renders reporting zero spans as a success.

Splitting by family turns that class of mistake into a **missing file**. A wrong family is a wrong
path, and paths fail loudly. It also removes the shared schema: each entity table carries exactly the
columns its own family emits, with no null padding and nothing to negotiate. Where a later question
needs two families at once, DuckDB's `ATTACH` reads across the files without copying anything.

## What is recomputed, and what is not

Extraction is idempotent and the ledger is what makes it so. Every document is recorded against every
model and entity it was sent to, whatever the outcome, so a re-render asks what is missing and finds
nothing. The first render pays; later ones cost seconds. That is why no chunk here needs a switch:
expense is handled by knowing what has been done, not by turning work off.

The benchmark works the same way and is keyed on the machine, so a timing taken on a different box is
a different measurement rather than an overwrite.

## How results are reported

Console tables throughout, through the shared fixed-width formatter. No figures: whether the old
agreement matrices and position densities are worth reproducing depends on what 04B turns out to
need, and that is the open question this pass exists to inform.

## Where things are written

`sample_text.parquet`, which is the text every offset in every store indexes, and three databases
under `Output/`. Everything else this document produces is insight and can change freely.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 03A's prepared sample: the one file every downstream method reads. Read, never written. The
    # directory resolves through the same helper 03A used to create it, so a renumbering cannot
    # desynchronise the two.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    )
  ),
  Output = list(
    # .dir_main is 2_output/04A-EntityExtract, resolved in the setup chunk from the script name.
    # Each script writes only into its own output directory.
    Sample = utils_file_path(.dir_main, "Output", "sample_text.parquet"),
    Store  = utils_file_path(.dir_main, "Output"),
    Stage  = utils_file_path(.dir_main, "Stage")
  ),
  Params = list(
    # FIVE WORKERS, AND THE BENCHMARK USES THE SAME NUMBER. A batch ranking measured at one worker
    # count and applied at another is an assumption, and this pipeline has made that one silently
    # before. Measuring and running at the same width means there is nothing to assume.
    #
    # spaCy on a GPU ignores this and forces one worker, because a single Metal device cannot be
    # shared across worker processes. extract_spacy.py says so on stderr when it does.
    Workers = 5L,

    # BATCH SIZE IS TYPED HERE, FROM THE BENCHMARK TABLE BELOW. It is not read from the measurement:
    # a run whose parameters depend on a timing produces different work on different machines and
    # nothing records which. These are the values to revise after reading the table.
    Batch = list(
      matcon = 32L,
      spacy  = 32L,
      lexnlp = 8L
    ),

    # A HANG DETECTOR, NOT A BUDGET. LexNLP's cap is the one that matters, but not for the reason
    # this comment used to give: the geoentity pass runs at 64 documents a second against 4.9 for
    # ORG, DATE and MONEY together, so the expensive work is the maxent company NER and the date
    # grammar. A timeout there is not one lost document but documents lost SYSTEMATICALLY IN THE
    # LONGEST AGREEMENTS, which is the worst possible place for a missing-at-random assumption to
    # fail.
    Timeout = list(
      matcon = 120L,
      spacy  = 600L,
      lexnlp = 240L
    ),

    # The benchmark draw. 320 documents is five workers times the largest batch under test, so the
    # widest cell still gives every worker a full batch -- and every narrower cell runs the SAME
    # documents, which is what makes the cells comparable at all.
    BenchN       = 320L,
    # A nested prefix of that draw for the transformer, which runs at one worker on the GPU. 64
    # divides evenly across the whole sweep, so no cell carries a ragged final batch.
    BenchNSpacy  = 64L,
    BenchBatches = c(4L, 8L, 16L, 32L, 64L),
    Seed         = 42L,

    # Bins across the unit interval for the positional profiles. A multiple of ten, so the decile
    # zones the contrast is built on fall on bin boundaries exactly rather than approximately.
    Bins         = 30L
  ),
  Models = list(
    # All four declared. Three are not run -- see SkipModels -- and declaring them anyway is what
    # makes the exclusion a recorded decision rather than an absence a reader has to notice.
    Spacy = c("en_core_web_sm", "en_core_web_md", "en_core_web_lg", "en_core_web_trf")
  )
)

# WHAT EACH FAMILY IS ASKED FOR. Not the same question as what it can produce. GPE is asked of both
# LexNLP and matcon because it has two candidate producers and the choice between them is 04B's to
# make, which it cannot do without both. It is also nearly free: the geoentity pass runs at 64
# documents a second against 4.9 for LexNLP's other three extractors together.
.lP$Plan <- tibble::tribble(
  ~Family,   ~Entities,
  "matcon",  c("GPE", "DATE", "TERM", "MONEY", "REDACT"),
  "spacy",   c("ORG", "PERSON", "GPE"),
  "lexnlp",  c("ORG", "GPE", "DATE", "MONEY")
)

# THE THREE CNN MODELS ARE DECLARED AND NOT RUN. They were measured against the transformer on this
# sample and lost on every entity; running them again would spend minutes to reproduce a finding
# that is already settled. They stay in the table so the exclusion is visible.
.lP$Params$SkipModels <- c("en_core_web_sm", "en_core_web_md", "en_core_web_lg")

fs::dir_create(c(.lP$Output$Stage, .lP$Output$Store))
```

**Five workers rather than twenty, and the reason is the benchmark rather than the machine.** The
sweep below ranks batch sizes at five workers. Running the pass at a different width would mean
assuming that ranking transfers, which is exactly the kind of unstated assumption that has cost this
project renders before. Measuring and running at one width costs some throughput on a 28-core machine
and buys a table that describes the work actually done.

# Input

```{r}
#| label: build-sample

tab_sample <- ent_build_sample(
  .path_prepared = .lP$Input$Prepared,   # 03A's prepared sample, the one file downstream reads
  .text_col      = "Text"                # 03A's name for it; renamed to TextRaw on the way out
)

ent_write_sample(.tab = tab_sample, .path = .lP$Output$Sample)
ent_report_sample(.tab = tab_sample, .class_col = "ClassDetailed")
```

**The text is copied rather than referenced, and that is the point.** Every offset in all three
databases indexes this file. If the text a span points into could change -- because 03A re-read the
corpus, or normalised it differently -- then an offset would be a promise nobody can keep. One script
writes this file and nothing else rebuilds it.

The write is guarded on content. A render that changes nothing leaves the file's timestamp untouched;
a render that changes something says so loudly, because a changed canonical text invalidates every
span in every store at once.

The column is renamed from `Text` to `TextRaw` on the way through. Every extractor defaults to
`TextRaw` and the whole 04 family reads that name, so one place decides what the canonical text is
called and nothing downstream needs configuring.

# Families

```{r}
#| label: describe-families

# WHAT IS DECLARED AND WHAT IS AVAILABLE ARE DIFFERENT QUESTIONS. A spaCy model named here but not
# downloaded fails at load time, which on this pipeline is after every faster family has run.
tab_describe <- ner_describe(
  .spacy_models = .lP$Models$Spacy,   # all four; three are excluded from the run, not from the table
  .lexnlp_image = "contracts-lexnlp"  # the container, whose spec hash is read from its build label
)

ner_report_describe(.describe = tab_describe)
```

**The matcon rows describe themselves.** `matcon-extract --describe` reports its models, entities and
spec hashes, and R reads that rather than restating it. The alternative -- a table in R naming what
each extractor produces -- was silently wrong the moment one extractor gained a second entity: the
table said DATE, the request asked for DATE, TERM was filtered out inside Python, and the run recorded
success. Nothing errored and no check could have caught it, because the two declarations agreed about
everything R could see.

spaCy and LexNLP do not self-describe, so their entity sets are declared and then checked against what
arrives. That asymmetry is honest rather than inconsistent: ours describes itself because we wrote it.

**PERSON is absent from LexNLP's row**, and that is a fact about the library rather than a policy. Its
person extractor returns no offsets, so a span it found could not be located in the text and the
offset contract could not hold for it.

**The spec hash is what makes a model tag mean something.** For matcon it fingerprints the constants
that determine an extractor's output -- pattern tables, vocabularies, and for the gazetteer a content
hash of its 116,000-entry lookup. For LexNLP it is the label stamped into the container at build time,
read back from the image rather than recomputed from the sources, so a stale image records the hash it
actually carries. For spaCy it is the installed model's version. A hash that has moved under an
unchanged tag means a rule was edited without a version bump, which would silently change what an
existing store's rows mean, and the ingest refuses it.

## The two GPE producers are not two opinions about one task

They work at different granularities, and every comparison in 04B has to be framed that way rather
than as an accuracy contest.

LexNLP's geo dictionary holds **437 entities**: countries and territories, nothing below that level.
A contract naming Frankfurt, Germany yields `Germany` and not `Frankfurt`. matcon's `gazetteer-v2`
carries a **116,000-entry** lookup reaching down to cities and administrative subdivisions. So an
apparent disagreement between them is usually a difference in resolution, not a difference of opinion.

**LexNLP's ISO codes are dropped as MATCH ALIASES and kept as OUTPUT.** The distinction matters and an
earlier version of this paragraph collapsed it, concluding that the columns arrive empty. They do not.

Dropping them as aliases is right: LexNLP's default alias set includes the ISO-3166-2 and ISO-3166-3
columns, and both are ordinary English words in a contract. `IN` matches "IN WITNESS WHEREOF" on
essentially every document; on twenty sample contracts `NOR` was the single most frequent span at 188
hits, from "neither ... nor", with `AND` (Andorra) at 37. So the extractor names its alias columns
rather than filtering by length.

But a code is a property of the entity that matched, not of the alias that matched it, so a country
found by its name still carries one. The store holds ISO-3166-2 on **82,013 of 82,016** GPE spans.
`Iso3` is narrower and that is the dictionary rather than the extractor: of its 437 entities only the
253 countries carry a three-letter code, so `Iso3` identifies a country and `Iso2` identifies a
country **or a subdivision** -- `US-AL`, `CA-AB`, `CN-13`. 04B2 uses the first as the country key and
the prefix of the second to recover the parent country of a subdivision.

The costly omission is elsewhere: postal abbreviations are lost, so "New York, NY 10167" contributes
only "New York". That is acceptable because matcon's gazetteer recovers a state code where a ZIP
follows it, a constraint this dictionary cannot express.

```{r}
#| label: declare-plan

tab_plan <- ent_plan(
  .describe    = tab_describe,             # what each family and model can produce
  .plan        = .lP$Plan,                 # what this pass asks each family for
  .skip_models = .lP$Params$SkipModels     # declared, not run
)

ent_report_plan(.tab = tab_plan)
```

Checked before any work starts rather than discovered inside the extraction loop. Asking a family for
an entity it does not produce currently costs a full pass that quietly produces nothing: the entity is
filtered out inside Python, the parquet is well formed, and the ledger records success.

# Benchmark

```{r}
#| label: bench-draw

draw <- ner_bench_draw(
  .tab_sample = tab_sample,                                     # drawn from the real sample
  .path       = fs::path(.lP$Output$Stage, "bench-draw.parquet"),
  .n          = .lP$Params$BenchN,                              # 320
  .seed       = .lP$Params$Seed                                 # 42, so the draw never moves
)

cli::cli_alert_info(
  "Benchmark draw: {format(draw$NDoc, big.mark = ',')} \\
   {cli::qty(draw$NDoc)}document{?s}, fingerprint {(draw$DrawHash)}."
)
```

**One draw, frozen, for every cell.** Runtime is dominated by document length, so cells that process
different documents cannot be compared -- a difference in throughput would confound scheduling with
the draw. Every cell in a family runs the same documents and only the batch size varies. The
fingerprint is part of the benchmark key, so a draw that moved would miss the cache rather than
silently serve a timing taken on other documents.

320 is five workers times the largest batch under test, so even the widest cell gives every worker a
full batch. The narrower cells split the same work into more tasks.

```{r}
#| label: bench-matcon

con_matcon <- ner_db_connect(
  .db_path   = ner_db_path(.dir = .lP$Output$Store, .family = "matcon"),
  .read_only = FALSE
)
ner_db_init(.con = con_matcon)

tab_bench_matcon <- ner_bench_run(
  .con      = con_matcon,                                       # the timings live beside the spans
  .family   = "matcon",
  .model    = NULL,                                             # matcon versions itself
  .entity   = .lP$Plan$Entities[[which(.lP$Plan$Family == "matcon")]],
  .draw     = draw,
  .n_doc    = .lP$Params$BenchN,                                # 320
  .batches  = .lP$Params$BenchBatches,                          # 4, 8, 16, 32, 64
  .workers  = .lP$Params$Workers,                               # 5
  .describe = tab_describe,
  .timeout  = .lP$Params$Timeout$matcon                         # 120 seconds per document
)

ner_report_bench(
  .tab  = tab_bench_matcon,
  .live = ent_live_keys(.plan = tab_plan)   # a stored timing outlives the model that made it
)
```

```{r}
#| label: bench-spacy

con_spacy <- ner_db_connect(
  .db_path   = ner_db_path(.dir = .lP$Output$Store, .family = "spacy"),
  .read_only = FALSE
)
ner_db_init(.con = con_spacy)

tab_bench_spacy <- ner_bench_run(
  .con      = con_spacy,
  .family   = "spacy",
  .model    = "en_core_web_trf",                                # the only model that will run
  .entity   = .lP$Plan$Entities[[which(.lP$Plan$Family == "spacy")]],
  .draw     = draw,
  .n_doc    = .lP$Params$BenchNSpacy,                           # 64, a prefix of the same draw
  .batches  = .lP$Params$BenchBatches,
  .workers  = .lP$Params$Workers,                               # forced to 1 on the GPU
  .describe = tab_describe,
  .timeout  = .lP$Params$Timeout$spacy
)

ner_report_bench(
  .tab  = tab_bench_spacy,
  .live = ent_live_keys(.plan = tab_plan)   # a stored timing outlives the model that made it
)
```

**The transformer's cells are smaller, and they are a prefix rather than a second draw.**
`extract_spacy.py` forces one worker whenever a GPU is active, so five workers is a fiction here and
320 documents would run sequentially. Sixty-four is the largest batch under test, so the widest cell
is exactly one batch and every narrower one divides it evenly. Being a prefix of the same draw is what
keeps its length distribution comparable with the other two families.

```{r}
#| label: bench-lexnlp

con_lexnlp <- ner_db_connect(
  .db_path   = ner_db_path(.dir = .lP$Output$Store, .family = "lexnlp"),
  .read_only = FALSE
)
ner_db_init(.con = con_lexnlp)

tab_bench_lexnlp <- ner_bench_run(
  .con      = con_lexnlp,
  .family   = "lexnlp",
  .model    = NULL,
  .entity   = .lP$Plan$Entities[[which(.lP$Plan$Family == "lexnlp")]],
  .draw     = draw,
  .n_doc    = .lP$Params$BenchN,
  .batches  = .lP$Params$BenchBatches,
  .workers  = .lP$Params$Workers,
  .describe = tab_describe,
  .timeout  = .lP$Params$Timeout$lexnlp
)

ner_report_bench(
  .tab  = tab_bench_lexnlp,
  .live = ent_live_keys(.plan = tab_plan)   # a stored timing outlives the model that made it
)
```

**The first render of these three sections is expensive and every later one is not.** Results are
keyed on model, entity set, batch, workers, document count, draw fingerprint and machine, and only
cells absent from that key are measured. Adding a batch size measures that batch size. Nothing is
skippable and nothing is switched off, which is what distinguishes this from disabling the chunk: the
table is always complete, and completeness is what makes it evidence.

**The machine is part of the key** because a timing from a different box is a different measurement.
Without it, running this on a laptop would silently overwrite the numbers this section reports.

**These run before the extraction they inform, not after it.** The batch size the next section uses is
declared in the configuration, and until this table exists that declaration is a guess. Reporting the
measurement after the pass it should have guided would make it a description of a decision already
taken. The declared value stays declared: a run whose parameters depend on a timing would produce
different work on different machines and nothing would record which.

# Extraction

```{r}
#| label: extract-matcon

tab_run_matcon <- ent_extract_family(
  .con        = con_matcon,
  .family     = "matcon",
  .plan       = tab_plan,                    # what to run, and which models are excluded
  .path_in    = .lP$Output$Sample,           # the text every offset will index
  .doc_ids    = tab_sample$DocID,            # what the ledger is asked about
  .stage_dir  = .lP$Output$Stage,            # where the family writes its parquets
  .describe   = tab_describe,
  .workers    = .lP$Params$Workers,          # 5
  .batch_size = .lP$Params$Batch$matcon,     # typed from the benchmark above
  .timeout    = .lP$Params$Timeout$matcon,   # 120 seconds per document
  .force      = FALSE                        # FALSE skips work the ledger records as done
)

ent_report_extract(.tab = tab_run_matcon)
```

```{r}
#| label: extract-spacy

tab_run_spacy <- ent_extract_family(
  .con        = con_spacy,
  .family     = "spacy",
  .plan       = tab_plan,
  .path_in    = .lP$Output$Sample,
  .doc_ids    = tab_sample$DocID,
  .stage_dir  = .lP$Output$Stage,
  .describe   = tab_describe,
  .workers    = .lP$Params$Workers,
  .batch_size = .lP$Params$Batch$spacy,
  .timeout    = .lP$Params$Timeout$spacy,
  .force      = FALSE
)

ent_report_extract(.tab = tab_run_spacy)
```

```{r}
#| label: extract-lexnlp

tab_run_lexnlp <- ent_extract_family(
  .con        = con_lexnlp,
  .family     = "lexnlp",
  .plan       = tab_plan,
  .path_in    = .lP$Output$Sample,
  .doc_ids    = tab_sample$DocID,
  .stage_dir  = .lP$Output$Stage,
  .describe   = tab_describe,
  .workers    = .lP$Params$Workers,
  .batch_size = .lP$Params$Batch$lexnlp,
  .timeout    = .lP$Params$Timeout$lexnlp,
  .force      = FALSE
)

ent_report_extract(.tab = tab_run_lexnlp)
```

**One chunk per family, cheapest first.** A render interrupted in the expensive family leaves the
other two complete, and each chunk's label names what is running while it runs, which is the
difference between a live account and a silent wait.

**The ledger is what makes re-rendering cheap.** A model whose documents are all recorded is skipped
entirely, so the first render pays for extraction and later ones cost seconds. That is also why no
chunk here needs a switch: expense is handled by knowing what has been done, not by turning work off.

**Sentinel rows do not become spans.** Each extractor emits a null-offset row for a document it
processed and found nothing in; those rows drive the ledger's `nohit` state and are not stored. A
document that was processed and matched nothing therefore has no row in any entity table and a
complete record in the ledger, which is the only arrangement in which "processed and empty" and "never
processed" stay distinguishable.

# Validation

```{r}
#| label: validate-matcon

lst_valid_matcon <- ent_report_validation(
  .con      = con_matcon,     # still open from the extraction above
  .family   = "matcon",
  .tab_text = tab_sample,     # the text every offset must index
  .plan     = tab_plan,       # every model and entity that should have run
  .describe = tab_describe
)
```

```{r}
#| label: validate-spacy

lst_valid_spacy <- ent_report_validation(
  .con      = con_spacy,
  .family   = "spacy",
  .tab_text = tab_sample,
  .plan     = tab_plan,
  .describe = tab_describe
)
```

```{r}
#| label: validate-lexnlp

lst_valid_lexnlp <- ent_report_validation(
  .con      = con_lexnlp,
  .family   = "lexnlp",
  .tab_text = tab_sample,
  .plan     = tab_plan,
  .describe = tab_describe
)
```

Two invariants per family, and both abort rather than warn.

**The offset contract**, checked on every span in every entity table. `text[Start:Stop] == Span`, over
code points, sliced with `stringi::stri_sub` -- base `substr` indexes bytes and misaligns roughly
ninety-nine per cent of spans on this corpus, so getting this wrong is not a subtle error. It is
checked per table rather than through a union view, because the tables no longer share a schema and
there is no view to check through.

**Ledger completeness.** Every sample document must have an outcome recorded for every model and
entity it was sent to. A document missing from the ledger is invisible in any span count, because a
document with no spans and a document never processed produce the same empty result.

# Results

```{r}
#| label: report-coverage

tab_coverage <- dplyr::bind_rows(
  ent_coverage(.summary = ner_db_summary(.con = con_matcon), .family = "matcon",
               .n_doc = nrow(tab_sample)),
  ent_coverage(.summary = ner_db_summary(.con = con_spacy),  .family = "spacy",
               .n_doc = nrow(tab_sample)),
  ent_coverage(.summary = ner_db_summary(.con = con_lexnlp), .family = "lexnlp",
               .n_doc = nrow(tab_sample))
)

ent_report_coverage(
  .tab  = tab_coverage,   # what the three stores hold
  .plan = tab_plan        # what was intended, so an absent family is named rather than invisible
)
```

Coverage is the share of sample documents in which a model found at least one span of an entity. **It
is not a quality measure and should not be read as one:** an engine that tags every capitalised word
as an organisation reaches complete coverage and is useless. What it establishes is which comparisons
are possible at all, since two engines can only be compared where both fire.

**Timeouts and errors are reported apart from clean misses.** A document that was processed and matched
nothing is a coverage fact; a document whose extractor crashed is a defect, and pooling the two hides
it. Until recently they were indistinguishable -- a crash produced the same empty result as a clean
miss, so a pattern failing on a whole class of documents looked exactly like that class having no
matches.

**Two entities have exactly one producer.** REDACT and TERM come only from matcon, so cross-family
agreement does not exist for them and is not reported. Coverage and the offset contract still apply.

```{r}
#| label: report-grid

tab_grid <- ent_producer_grid(.coverage = tab_coverage)

ent_report_grid(.grid = tab_grid)
```

The same numbers as above, reshaped into the form the question is usually asked in: which producer
reaches which entity. **An empty cell is not a zero.** It means that producer does not attempt that
entity at all, where `0.000` would mean it attempted and never fired. Pivoting long to wide
manufactures missing values that look exactly like real ones, which is the defect 03E found in its
own panel and the reason this note exists.

```{r}
#| label: attach-families

# THE ONLY PLACE THE THREE DATABASES ARE OPEN AT ONCE. A separate read-only connection rather than
# one family's, so a comparison cannot depend on which file happened to be open, and cannot write to
# a store it is describing.
con_all <- ner_attach(.dir = .lP$Output$Store, .families = .ner_families)

tab_tables    <- ner_attached_tables(.con = con_all)
tab_producers <- ent_producers(.tables = tab_tables)

tbl_say(.tab = tab_tables, .title = "Entity tables across the three databases")
```

```{r}
#| label: build-mentions

# OVERLAPPING SPANS ARE MERGED INTO MENTIONS BEFORE ANYTHING IS COMPARED. Gaps-and-islands over
# half-open spans, in SQL because the window functions are the whole algorithm.
ent_build_mentions(
  .con          = con_all,
  .tables       = tab_tables,
  .spacy_models = "en_core_web_trf"   # each model its own producer; pooling would inflate overlap
)

tab_consensus <- ent_consensus(.con = con_all)
tab_pairwise  <- ent_pairwise(.con = con_all)

ent_report_alignment(.consensus = tab_consensus, .pairwise = tab_pairwise)
```

**Exact offsets are the wrong unit to compare on, and there is direct evidence.** A single-sentence
probe returned the LexNLP DATE span `of January 15, 2019 by` where the regex engine returns
`January 15, 2019`. Both found the same date. On identical offsets they agree on nothing, and a
figure built from that would report two engines that disagree completely.

So overlapping spans within a document and entity are merged into a **mention** -- a place in the
text where something was found -- and agreement is asked at that level. Boundary disagreement stops
being noise and becomes a separate, reportable quantity:

| Column | What it asks |
|:--|:--|
| `NProducer` | how many producers found this mention -- the consensus distribution |
| `Jaccard` | do two producers agree about **what is there** |
| `ExactShare` | among mentions both found, do they agree about **where it ends** |

**The two are independent, and which one is low is the diagnosis.** A high `Jaccard` with a low
`ExactShare` means the producers agree about the world and disagree about boundaries -- a
normalisation problem, and 04B's job. A low `Jaccard` with a high `ExactShare` means something
harder: they mostly propose *different things*, and where they do meet they meet cleanly. Those
producers are complements rather than substitutes, and 04B cannot pick one and discard the other
without losing coverage. The report names whichever pattern occurs rather than assuming one.

All eligible pairs are assembled rather than only those that co-occur, so two producers that never
meet show a Jaccard of zero instead of vanishing from the table. A missing row and a zero are
different findings.

```{r}
#| label: report-positions

tab_positions <- ent_positions(
  .con       = con_all,
  .path_text = .lP$Output$Sample,   # document lengths, so position is comparable across documents
  .bins      = .lP$Params$Bins      # a multiple of ten, so the decile zones below are exact
)

tab_contrast <- ent_contrast(.tab = tab_positions, .by = c("Producer", "Entity"))

tbl_say(.tab = tab_contrast, .title = "End-of-document concentration, by producer and entity")
cli::cli_alert_info(
  "Contrast is the mean share in the first and last deciles over the mean share through the middle. \\
   A producer that spreads an entity evenly scores 1.0 by construction."
)
```

**One number for a thirty-bin distribution**, because thirty shares per producer and entity are
readable pooled and unreadable once anything is crossed with them. The contrast answers what the
shares are consulted for: does this producer concentrate the entity where parties are named, or
spread it through the text.

The second and ninth deciles are excluded from the middle deliberately. They are shoulder -- a
preamble spills into the second decile of a short document and a signature block into the ninth --
so counting them as middle would blunt the very contrast being measured.

# Deployment

```{r}
#| label: deploy-summary

ent_report_artifacts(
  .dir         = .lP$Output$Store,   # the directory holding the three databases
  .families    = .ner_families,      # matcon, spacy, lexnlp
  .path_sample = .lP$Output$Sample   # the canonical text
)
```

Four artifacts, and all of them are contracts rather than conveniences. `sample_text.parquet` is the
text every offset in every store indexes; the three databases are what 04B reads. Everything else this
document produces is insight and can change freely.

# Overview

```{r}
#| label: overview

tbl_say(
  .tab   = dplyr::select(tab_plan, "Family", "Model", "Run", "Note"),
  .title = "What ran"
)

ent_report_grid(.grid = tab_grid)

tbl_say(
  .tab   = dplyr::bind_rows(tab_bench_matcon, tab_bench_spacy, tab_bench_lexnlp) |>
    dplyr::transmute(.data$Model, .data$Batch, .data$NDoc, DocPerS = round(.data$DocPerS, 2)) |>
    dplyr::arrange(.data$Model, .data$Batch),
  .title = "Throughput"
)
```

```{r}
#| label: fig-positions
#| fig-height: !expr ent_facet_height(length(unique(tab_positions$Entity)))
#| fig-cap: "Candidate position across the document, by entity. Shares are within producer; the axis includes zero."

ent_plot_positions(
  .positions = tab_positions,   # already shared within producer and entity by ent_positions()
  .free_y    = TRUE             # entities differ in concentration; a shared scale flattens panels
)
```

```{r}
#| label: fig-consensus
#| fig-height: !expr plot_height(length(unique(tab_consensus$Entity)))
#| fig-cap: "Share of mentions by how many producers found them. One producer renders as a single segment."

ent_plot_consensus(.consensus = tab_consensus)
```

```{r}
#| label: fig-agreement
#| fig-height: !expr ent_facet_height(length(unique(tab_pairwise$Entity)), .square = TRUE)
#| fig-cap: "Pairwise agreement over mentions, as an upper triangle. The diagonal is a producer against itself."

ent_plot_agreement(
  .pairwise      = tab_pairwise,   # zero where two producers never meet, rather than absent
  .accuracy      = 0.01,
  .min_producers = 2L              # with the diagonal, two producers is a readable triangle
)
```

```{r}
#| label: disconnect

# LAST, AND DELIBERATELY SO. Every section above reads from an open connection, and a disconnect
# written where the work happened would silently strand any section added below it. This chunk sits
# immediately before # Next for exactly that reason: if a section is added, it goes above this.
DBI::dbDisconnect(con_all,    shutdown = TRUE)
DBI::dbDisconnect(con_matcon, shutdown = TRUE)
DBI::dbDisconnect(con_spacy,  shutdown = TRUE)
DBI::dbDisconnect(con_lexnlp, shutdown = TRUE)

cli::cli_alert_success("All stores closed.")
```

**The figures answer what the tables cannot, and one of them corrects a table's reading.** The
positional profiles say whether two producers disagree about volume or about *place* -- a difference
invisible in any count. The vertical axis includes zero deliberately: with free scales and no
baseline, ORG rendered as violent oscillation across a range of 2.9 to 4.1 per cent while the
contrast table reported 0.97, a distribution uniform to within rounding. A shape that survives a zero
baseline is a shape.

**The consensus bar is the agreement figure**, because it works at any producer count and states the
number as the thing it implies: a Jaccard of 0.44 is a ratio to reason about, where "fifty-six per
cent of GPE mentions were found by one engine and not the other" is the finding.

**The matrix is an upper triangle with the diagonal intact**, which is how a correlation matrix is
read: the diagonal anchors the eye at the top of the scale, so every off-diagonal cell is judged
against what perfect agreement looks like in this palette rather than against the legend alone. It
is drawn wherever an entity has two producers, which with the diagonal is a readable three-cell
triangle; below that a panel would be one cell reading 1.00 and saying nothing.

# Next

**04B** takes these stores and argues from them: one document per entity, each proposing rules that
turn candidate spans into variables, and each measuring what its rules keep and discard against an
unadjusted baseline. Nothing there re-extracts; every rule is a query against the offsets stored here.

**04C** runs the same families over the whole Exhibit-10 corpus through the same `ner_extract()` and
`ner_ingest()`, which is what makes the two sets of stores comparable rather than merely similar.
