---
title: "Entity Measurement -- Locating the Contracting Party (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: the
# level registry is rebuilt empty every time _Plots.R is sourced, so a library that registers a
# vocabulary has to be sourced after it -- and 03A registers its taxonomy at SOURCE time rather than
# inside a function, so a failure part-way through that file leaves every function below it
# silently undefined.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the fixed-width console formatter every document in the
# monorepo reports through; 04A owns the sample, the canonical text and the candidate store.
# Sourcing both rather than re-registering is what keeps a figure here and a figure there from
# ordering the same axis two ways.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B-EntityMeasure.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran nine extractors over 4,398 hand-classified contracts and stored 7.4 million candidate spans.
It ranked none of them, because ranking needs labels and there are no entity labels. This document
supplies the one label EDGAR does record -- the filer's own name -- and uses it to answer a single
question: **where in each contract is the contracting party named?**

That is deliberately less than it sounds, and deliberately more.

Less, because the party's *identity* was never in doubt. EDGAR records who filed the document, so
the question is not which company this is. More, because a span offset is a coordinate rather than a
verdict, and every quantity this family still owes the paper is defined relative to it. The
counterparty is whoever else is named beside the filer. The party's location is whatever place name
sits next to it. The signing date is the date in the same sentence. None of those can be found
before the filer has been.

## Why location rather than membership

The obvious use of the anchor is to ask whether the filer appears *somewhere* among a document's
organisations. That question is almost always answered yes, and the reason is arithmetic: the
engines return between 80 and 509 organisations per document, so a rule scored against membership is
scored against a base rate of a fraction of a percent. Rules cannot be separated at that resolution
and neither can engines.

Asking where the filer is named restricts the answer to a region a hundred times smaller, and inside
that region the base rate is high enough that a rule either works or visibly does not.

## What a match is, and why the direction is recorded

A span matches when one normalised form contains the other, after both sides are reduced to a
comparable key: uppercased, punctuation removed, a leading `THE` dropped, and trailing corporate
suffixes stripped. *The Boeing Company* and `BOEING CO` both reduce to `BOEING`.

The two directions are not equally safe and are therefore kept apart.

- **Forward** -- the span contains the key. `ACME HOLDINGS, INC.` contains `ACME HOLDINGS`. Safe.
- **Reverse** -- the key contains the span, so the span is a *fragment* of the recorded name. This
  has no length floor of its own, and the consequence is not theoretical: the single character `G`
  is contained in `GEORGIA PACIFIC`, and that match fired 73 times in one document.

Around half of every spaCy engine's anchor matches are reverse matches with a median length of six
characters. An unguarded reverse arm therefore does not merely add noise, it inflates apparent
recall, and it inflates it most for the engines that emit the most fragments. A minimum length is
imposed here and the surviving reverse matches earn their place: they are cases like
`Resources Accrued Mortgage Investors` against a registered `... LP SERIES 86`, where EDGAR holds
the longer form.

## Position leads, quality follows

Where several spans qualify, the earliest wins and the match kind settles ties. Ordering by quality
first would prefer an exact match at character 8,000 to a forward match at character 200 -- which is
the wrong preference for a coordinate, and on this sample moves roughly a hundred documents out of
the preamble and into a signature block.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file and nothing else
    # reconstructs it.
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    # 04A's sample table: labels, folds, and the EDGAR facts the anchor is built from.
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    # 04A's candidate store, attached read-only.
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Party = utils_file_path(.dir_main, "contracting_party.parquet") # one row per contract
  ),
  Params = list(
    CapLocated = 3000L,   # a span beyond this offset is reported as late rather than located
    MinReverse = 10L,     # shortest fragment admitted as a reverse match
    WindowN    = 20L,     # located spans read back in context
    WindowCtx  = 200L,    # characters either side of those spans
    Seed       = 42L      # fixed, so the same documents are read on every render
  )
)

fs::file_exists(unlist(.lP$Input))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

The anchor keys come first, because their availability bounds everything below. A document whose
recorded name reduces to fewer than five characters carries no key at all, and is reported as such
rather than counted as a failure to find something that was never being looked for.

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(
  .path_anchors = .lP$Input$Anchors   # 04A's sample table, not the raw EDGAR metadata
)

ent_report_keys(.tab = tab_keys)
```

```{r}
#| label: open-session
con <- ent_session(
  .db_path   = .lP$Input$Store,   # attached read-only; nothing here can write to 04A's artifact
  .keys      = tab_keys,          # registered so every query below joins on it
  .path_text = .lP$Input$Text     # supplies document lengths, so an offset becomes a position
)
```

# The party

Two steps. The first finds every organisation span matching the filer's name, one row per engine per
occurrence. The second chooses one of them per document and says how far it can be trusted.

```{r}
#| label: match-anchor
ent_anchor_org(
  .con   = con,
  .quiet = FALSE   # the count is the first sign that the store holds what this document expects
)
```

```{r}
#| label: locate-party
tab_party <- ent_locate_party(
  .con         = con,
  .keys        = tab_keys,                 # runs from the key side, so unmatched documents survive
  .cap         = .lP$Params$CapLocated,    # beyond this the span is reported, not used
  .min_reverse = .lP$Params$MinReverse     # fragments shorter than this are refused
)

ent_report_party(.tab = tab_party)
```

Four of the five statuses are ways of not having an answer, and they are not the same problem.
**No key** is a limit of the recorded metadata. **No match** means no engine proposed the filer's
name anywhere in its own contract, which is an extraction gap. **Fragment only** means spans were
proposed but all of them were pieces too short to trust, which is a matching gap and would be
narrowed by a better normaliser rather than by a better extractor. **Late** means the name was found
where a preamble is not, and those documents are the ones the windows below should be read for.

```{r}
#| label: inspect-match-kind
ent_report_match(.tab = tab_party)
```

# Windows

Every table above is equally consistent with the chosen span being a preamble party and with it
being a letterhead, a page footer or a defined term. The text is what separates them, so a fixed
sample is read back on every render.

```{r}
#| label: read-windows
tab_windows <- ent_party_windows(
  .tab       = tab_party,
  .path_text = .lP$Input$Text,          # the same canonical text the offsets index
  .n         = .lP$Params$WindowN,      # documents drawn
  .ctx       = .lP$Params$WindowCtx,    # characters either side of the span
  .status    = "located",               # the working set; "late" is read separately below
  .seed      = .lP$Params$Seed          # fixed, so a change here is a change in the extraction
)

ent_report_windows(.tab = tab_windows)
```

The second question those windows answer is the one that decides what can be built next. A contract
opening `by and between X and Y` carries a counterparty, a jurisdiction and an address within a few
hundred characters of the party. A stock incentive plan opening `X 2017 STOCK INCENTIVE PLAN` is the
company's own instrument and carries no counterparty at all. Both are Exhibit 10 material contracts
and both will be located correctly here, so the share of each is a fact about the corpus that has to
be measured before a counterparty rule is written against it.

```{r}
#| label: read-windows-late
ent_party_windows(
  .tab       = tab_party,
  .path_text = .lP$Input$Text,
  .n         = 8L,                      # fewer, because this is a diagnostic rather than the case
  .ctx       = .lP$Params$WindowCtx,
  .status    = "late",                  # found, but past the point a preamble would be
  .seed      = .lP$Params$Seed
) |>
  ent_report_windows()
```

# Validation

```{r}
#| label: validate-located
tibble::tibble(
  Check = c(
    "Located spans that round-trip to their own text",
    "Located spans starting at or after character zero",
    "Located spans whose trimmed name is non-empty",
    "Documents with more than one status"
  ),
  N = c(
    sum(!is.na(tab_windows$Snippet) & stringi::stri_detect_fixed(tab_windows$Snippet, ">>>")),
    sum(tab_party$Start >= 0L, na.rm = TRUE),
    sum(nzchar(dplyr::coalesce(tab_party$Party, "")), na.rm = TRUE),
    0L   # one row per document by construction; reported so the claim is visible
  ),
  Of = c(
    nrow(tab_windows),
    sum(!is.na(tab_party$Start)),
    sum(!is.na(tab_party$Start)),
    nrow(tab_party)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "The located set")
```

The last row is zero by construction rather than by observation: `ent_locate_party()` returns the
key table with one match joined onto it, so a document cannot carry two statuses. It is reported so
a reader can see the constraint exists rather than infer it.

# Robustness

```{r}
#| label: inspect-by-class
tab_class <- ent_party_by_class(.tab = tab_party)

ent_report_class(.tab = tab_class)
```

```{r}
#| label: inspect-by-amendment
tab_party |>
  dplyr::summarise(
    Docs      = dplyr::n(),
    Located   = sum(.data$Status == "located"),
    MedDocLen = as.integer(stats::median(.data$DocLen, na.rm = TRUE)),
    MedStart  = as.integer(stats::median(.data$Start[.data$Status == "located"], na.rm = TRUE)),
    .by = AmendType
  ) |>
  dplyr::mutate(PctLocated = tbl_pct(.data$Located / .data$Docs)) |>
  tbl_say(.title = "Amendments against original agreements")
```

An amendment is roughly a third the length of an original and incorporates its agreement by
reference, so it has less occasion to name its own parties. Reading the located share against median
document length is what separates a genuine difference in drafting from an artifact of the
character cap: a shorter document reaches a fixed cap sooner in relative terms, which flatters it.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_party, .lP$Output$Party)

DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = "Contracting party",
  Path     = .lP$Output$Party
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B")
```

The artifact carries every document, not only the located ones. A consumer filtering on `Status`
makes that decision visibly; a consumer handed a pre-filtered file makes it without knowing.

# Overview

```{r}
#| label: fig-party-status
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Status of the contracting-party match by contract type, as shares within each type.
#|   The leftmost segment is the working set; the three to its right are three different problems,
#|   and the rightmost is a limit of the recorded metadata rather than of the extraction."
ent_plot_party_status(
  .tab       = tab_class,
  .key_class = "ClassDetailed"   # the vocabulary 03A registered, so rows match the 03 family
)
```

Read the bars against each other rather than against an absolute standard. A type whose located
share is low and whose *no match* segment is large is one where the extractors are not finding the
filer at all; a type where *late* dominates instead is one whose documents genuinely name their
parties somewhere other than the opening, which is a fact about how that kind of agreement is
drafted and not something a better extractor would repair.

```{r}
#| label: report-everything
ent_report_all_party(
  .keys  = tab_keys,
  .party = tab_party,
  .class = tab_class
)
```

# Next

The party is a coordinate, and the next steps are all measured from it.

**The counterparty**, which is whichever other organisation or person is named inside the same
region. That rule has to branch on what the windows above show: a bilateral agreement has a
counterparty and a unilateral instrument does not, and applying one rule to both would report a
correct result as a failure across a large part of the sample.

**The party's location**, which is the place name adjacent to the party rather than any place name
in the document. That one can be tested against ground truth, because EDGAR records the filer's
registered address and the rule can be checked where the answer is already known.

**The signing date**, which is the date in the same sentence rather than the earliest date anywhere.
