---
title: "Entity Rules -- Organisations and the Contracting Party (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: the
# level registry is rebuilt empty every time _Plots.R is sourced, so a library that registers a
# vocabulary has to be sourced after it -- and 03A registers its taxonomy at SOURCE time rather than
# inside a function, so a failure part-way through that file leaves every function below it
# silently undefined.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the fixed-width console formatter every document in the
# monorepo reports through; 04A owns the sample, the canonical text and the candidate store.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B-EntityRules.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran nine extractors over 4,398 hand-classified contracts and stored several million candidate
spans. It ranked none of them, because ranking needs labels and there are no entity labels. This
document writes the rules that turn those spans into parties, and it takes one entity at a time.

**Organisations first**, because every other quantity a party carries is measured from where an
organisation was found. The counterparty is whoever else is named beside the filer; the party's
jurisdiction is the place name adjacent to it; the signing date is the date in the same sentence.
None of those can be resolved before an organisation has been located.

Three questions, in order:

1. **Where does an engine write organisations?** A description of the extractor, using no external
   fact, so nothing in it can be circular.
2. **Does the region containing most of them contain the filer?** The one external fact EDGAR
   supplies, turned into a recall floor.
3. **How many distinct organisations does that region actually hold?** The candidate set every rule
   after this one has to survive.

## What the anchor can and cannot establish

EDGAR records the registrant's own name, independently of the contract text. That is one side of one
party. It can establish that an engine found *a* party; it can never establish that a span *is* a
party, because nothing external records the counterparty. Every coverage figure below is therefore a
**recall floor with its failure modes reported**, and precision on party role is measured only by
reading the text.

## Why a window, and why `max()`

LexNLP's organisations are bimodal: 22.6% of spans in the first tenth of a document, 25.2% in the
last, and 4.1% in the trough. The middle is body prose naming every company a contract mentions; the
ends are the preamble and the signature block. A window is the cheapest instrument that separates
them, and it costs nothing to revise, because every candidate already carries its offsets and a
window is a `WHERE` clause over offsets that are already written.

The window is `max(floor, share x DocLen)` rather than either arm alone, and the reason is that the
two arms fail at opposite ends. An absolute head admits 93.3% of parties overall but only 85.4% of
the longest length decile. A relative head admits 89.7% overall but only 58.2% of the *shortest*
decile, because a tenth of a 2,473-character amendment is 247 characters and the party's offset runs
past that. `max()` lets the floor bind on short documents and the share bind on long ones; `min()`
caps the long documents and scores worse than either arm by itself.

## Noise is expected here

Nothing below applies a stoplist, suppresses defined terms, or repairs a span boundary beyond
removing one leading connective. The counts are deliberately unfiltered. What the noise looks like
is the evidence the next rule is written against, and filtering it before reading it would remove
exactly the material that decides what to filter.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file and nothing else
    # reconstructs it.
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    # 04A's sample table: labels, folds, and the EDGAR facts the anchor is built from.
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    # 04A's candidate store, attached read-only.
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Party = utils_file_path(.dir_main, "contracting_party.parquet"), # one row per document
    Head  = utils_file_path(.dir_main, "org_head.parquet")           # one row per document per name
  ),
  Params = list(
    # The candidate set reads the selective engine. LexNLP's positional contrast runs 3.16 to 6.81
    # across twelve contract types where every spaCy model runs 0.68 to 1.33, and its read examples
    # return companies where spaCy returns filenames and section references.
    ComboCand  = "lexnlp",
    # The anchor arm reads every engine that emits ORG. Locating the filer is a RECALL problem, so
    # an engine reaching it two per cent more often is worth more here than one that is cleaner.
    ComboAnch  = NULL,
    HeadShare  = 0.10,               # head runs to max(HeadFloor, HeadShare x DocLen)
    HeadFloor  = 3000L,              # the arm that binds on short documents
    TailShare  = 0.20,               # tail runs back from the end
    GridHead   = c(0.05, 0.10, 0.15, 0.20),  # swept, so the choice is visible rather than asserted
    GridFloor  = c(0L, 3000L),               # zero is the pure-relative arm, for comparison
    GridTail   = c(0.10, 0.20, 0.30),
    MinReverse = 10L,                # shortest fragment admitted as a reverse anchor match
    Bins       = 50L,                # bins across relative position in the density figure
    TermsN     = 25L,                # names listed in the document-frequency block
    ReadN      = 10L,                # spans read back in context
    ReadDocs   = 8L,                 # documents whose whole head is listed
    ReadCtx    = 200L,               # characters either side of a span
    Seed       = 42L                 # fixed, so the same documents are read on every render
  )
)

fs::file_exists(unlist(.lP$Input))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

The anchor keys come first, because their availability bounds everything below. A document whose
recorded name reduces to fewer than five characters carries no key, and is reported as such rather
than counted as a failure to find something that was never being looked for.

Both sides of the comparison run through one reduction: uppercase, punctuation to space, whitespace
collapsed, a leading connective dropped, trailing corporate suffixes stripped repeatedly. *The
Boeing Company* and `BOEING CO` both reduce to `BOEING`; `between Precision BioSciences, Inc.`
reduces to `PRECISION BIOSCIENCES`.

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(
  .path_anchors = .lP$Input$Anchors   # 04A's sample table, not the raw EDGAR metadata
)

ent_report_keys(.tab = tab_keys)
```

```{r}
#| label: open-session
con <- ent_session(
  .db_path   = .lP$Input$Store,   # attached read-only; nothing here can write to 04A's artifact
  .keys      = tab_keys,          # registered so every query below joins on it
  .path_text = .lP$Input$Text     # supplies document lengths, so an offset becomes a position
)
```

Two candidate tables, and the split is the point. The **candidate** set is what a rule will read, so
it takes the selective engine. The **anchor** set is what establishes whether the filer was found at
all, which is a recall question, so it reads every engine emitting the label.

```{r}
#| label: load-candidates
ent_load_label(
  .con    = con,
  .name   = "org",                    # the candidate set the rules read
  .label  = "ORG",
  .combos = .lP$Params$ComboCand,     # lexnlp alone
  .quiet  = FALSE
)

ent_load_label(
  .con    = con,
  .name   = "org_all",                # the anchor set, for recall
  .label  = "ORG",
  .combos = .lP$Params$ComboAnch,     # NULL = every engine emitting ORG
  .quiet  = FALSE
)
```

# Windows

Where the engine writes, using no external fact. This section would read identically if EDGAR
recorded nothing at all, which is what keeps the cutoff choice from being fitted to the thing it is
later validated against.

```{r}
#| label: sweep-windows
tab_grid <- tidyr::expand_grid(
  Side  = "head",
  Share = .lP$Params$GridHead,
  Floor = .lP$Params$GridFloor
) |>
  dplyr::bind_rows(
    tidyr::expand_grid(Side = "tail", Share = .lP$Params$GridTail, Floor = 0L)
  ) |>
  dplyr::mutate(Floor = as.integer(.data$Floor))

tab_grid_win <- ent_window_grid(
  .con   = con,
  .table = "org",     # the candidate engine; the anchor set is swept separately below
  .grid  = tab_grid
)

ent_report_windows(.tab = tab_grid_win)
```

Two numbers per cell because they answer different questions. `PctSpans` is where the mass is;
`PctDocs` is whether the region is populated in most contracts or crowded in a few. An engine
reaching 3,053 spans in a single document can put a quarter of its output in the head while reaching
only half the documents, and only the second column would show it.

`MedKeys` is the cost. It is the number of distinct normalised names a rule reading that region has
to survive, and it is what the recall gains below have to be weighed against.

```{r}
#| label: measure-density
tab_density <- ent_density(
  .con   = con,
  .table = "org",           # the candidate engine
  .bins  = .lP$Params$Bins  # bins across relative position
)

tab_density |>
  dplyr::summarise(
    D0     = tbl_pct(sum(.data$Share[.data$Pos < 0.10])),
    Trough = tbl_pct(min(.data$Share)),
    D9     = tbl_pct(sum(.data$Share[.data$Pos > 0.90])),
    .by = Weight
  ) |>
  tbl_say(.title = "First tenth, trough and last tenth, under both weightings")
```

Computed here rather than in Overview because the session closes at Deployment. The figure drawn
from it is the last thing in the document; the numbers behind it belong beside the sweep they
explain. Where the two weightings agree, the bimodality is a property of contracts. Where they
diverge, it is a property of a handful of table-heavy filings, and 04A measured one document
carrying 3,053 organisation spans.

# The anchor

```{r}
#| label: match-anchor
ent_anchor_match(
  .con         = con,
  .table       = "org_all",              # every engine, because this is a recall question
  .min_reverse = .lP$Params$MinReverse,  # fragments shorter than this are refused
  .quiet       = FALSE
)
```

A span matches when one normalised form contains the other, and the direction is recorded rather
than collapsed. **Forward** containment -- the span holds the key -- is safe. **Reverse** containment
means the span is a *fragment* of the recorded name and has no length floor of its own: the single
character `G` is contained in `GEORGIA PACIFIC`, and that match fired seventy-three times in one
document. Roughly half of every spaCy engine's raw anchor matches are reverse matches with a median
length of six characters, so an unguarded reverse arm does not merely add noise -- it inflates
apparent recall, and inflates it most for the engines emitting the most fragments.

# Choosing the head

```{r}
#| label: sweep-anchor
tab_grid_anchor <- ent_anchor_grid(
  .con  = con,
  .keys = tab_keys,   # supplies both denominators: keyed documents, and the whole sample
  .grid = tab_grid    # head rows only; the tail carries no anchor
)

ent_report_anchor_grid(.tab = tab_grid_anchor)
```

This is the only table that decides anything. Everything above describes the extractor; this says
whether a rule reading the head would find the party. Read it against `MedKeys` in the window sweep:
the cutoff worth taking is the one past which recall stops rising faster than the candidate count,
and the `Floor = 0` rows are the pure-relative arm kept in the grid so the cost of dropping the floor
is a number rather than an argument.

```{r}
#| label: locate-party
tab_party <- ent_locate_party(
  .con   = con,
  .keys  = tab_keys,               # runs from the key side, so unmatched documents survive
  .head  = .lP$Params$HeadShare,   # the chosen share
  .floor = .lP$Params$HeadFloor    # the chosen floor
)

ent_report_party(.tab = tab_party)
```

Four of the five statuses are ways of not having an answer and they are not the same problem. **No
key** is a limit of the recorded metadata. **No match** means no engine proposed the filer's name
anywhere in its own contract, which is an extraction gap. **Fragment only** means spans were
proposed but all of them were pieces too short to trust, which a better normaliser would narrow and
a better extractor would not. **Late** means the name was found where a preamble is not.

```{r}
#| label: inspect-match-kind
ent_report_match(.tab = tab_party)
```

# Entities in the head

The candidate set every later rule reads, and the deduplication that makes it countable. LexNLP
returns `Icosavax, Inc.`, `Icosavax Inc` and `Icosavax, Inc` as three distinct spans in one
contract. They are one company, and the key built for the anchor collapses them at no extra cost.

```{r}
#| label: assign-region
tab_region <- ent_assign_region(
  .con   = con,
  .table = "org",
  .head  = .lP$Params$HeadShare,
  .floor = .lP$Params$HeadFloor,
  .tail  = .lP$Params$TailShare
)

tab_head <- ent_head_entities(
  .con         = con,
  .table       = "org",                 # the selective engine; the anchor set is far too noisy here
  .head        = .lP$Params$HeadShare,
  .floor       = .lP$Params$HeadFloor,
  .min_reverse = .lP$Params$MinReverse  # the same floor the anchor match uses
)

ent_report_dedup(.head = tab_head, .region = tab_region)
```

```{r}
#| label: inspect-terms
tab_terms <- ent_head_terms(
  .tab    = tab_head,
  .n_docs = nrow(tab_keys)   # the whole sample, so the share is comparable across sections
)

ent_report_terms(.tab = tab_terms, .n = .lP$Params$TermsN)
```

Reported rather than applied. A name occurring in one contract is a party; a name occurring in a
tenth of them is a defined term the drafting convention supplies, and where the list stops being
generic is where a threshold would go. Choosing that threshold before reading the list would be a
guess, and this document does not yet need it: the rules below tolerate the noise.

# Reading

Every table above is equally consistent with the chosen span being a preamble party and with it
being a letterhead, a page footer or a defined term. The text is what separates them, so a fixed
sample is read on every render.

```{r}
#| label: read-located
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "located"),
  .path_text = .lP$Input$Text,        # the same canonical text the offsets index
  .n         = .lP$Params$ReadN,      # documents drawn
  .ctx       = .lP$Params$ReadCtx,    # characters either side of the span
  .seed      = .lP$Params$Seed        # fixed, so a change here is a change in the extraction
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "MatchKind", "Start", "NEngine"),
    .title = "Located spans in context"
  )
```

```{r}
#| label: read-late
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "late"),
  .path_text = .lP$Input$Text,
  .n         = 6L,                    # fewer, because this is a diagnostic rather than the case
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "MatchKind", "Start", "DocLen"),
    .title = "Spans found past the head"
  )
```

```{r}
#| label: read-head-entities
ent_read_head(
  .tab  = tab_head,
  .keys = tab_keys,
  .n    = .lP$Params$ReadDocs,   # documents whose entire head is listed
  .seed = .lP$Params$Seed
) |>
  ent_report_head()
```

The last block is the one that says whether the deduplicated count means anything. A list of six
names is equally consistent with six parties and with two parties written four ways, and only the
words separate those readings. What remains after the anchor-marked rows is the counterparty
candidate set the next rule will be written against.

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "located"),
  .path_text = .lP$Input$Text,
  .n         = 500L,                  # a sample large enough to catch a systematic offset error
  .ctx       = 0L,                    # no context; the span itself is what is being checked
  .seed      = .lP$Params$Seed
)

# The two implementations of the same reduction, compared on the same input. They are written in
# different languages over different row counts, and a drift between them would move every match
# kind without raising an error anywhere.
sql_key_ <- DBI::dbGetQuery(con, paste0(
  "SELECT DocID, ", ent_sql_key(.col = "CompanyName"), " AS SqlKey FROM keys"
)) |>
  tibble::as_tibble() |>
  dplyr::left_join(dplyr::select(tab_keys, DocID, AnchorKey), by = dplyr::join_by(DocID)) |>
  dplyr::filter(!is.na(.data$AnchorKey))

tibble::tibble(
  Check = c(
    "Located spans that round-trip to their own text",
    "Located spans starting at or after character zero",
    "Anchor keys where the R and SQL reductions agree",
    "Documents carrying exactly one status"
  ),
  N = c(
    sum(stringi::stri_detect_fixed(tab_check$Snippet, tab_check$Party)),
    sum(tab_party$Start >= 0L, na.rm = TRUE),
    sum(sql_key_$SqlKey == sql_key_$AnchorKey),
    nrow(tab_party)
  ),
  Of = c(
    nrow(tab_check),
    sum(!is.na(tab_party$Start)),
    nrow(sql_key_),
    nrow(tab_party)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "The located set")
```

The third row is the check the roxygen in the library promises and the previous version of this
document did not perform. The R reduction strips corporate suffixes with a token loop and the SQL
reduction with a repeated-group regex; anything below 100% there means the two have drifted, and a
drift moves every match kind silently.

# Robustness

```{r}
#| label: inspect-by-class
ent_report_class(.tab = tab_party)
```

```{r}
#| label: inspect-by-length
ent_report_length(.tab = tab_party)
```

The length table is where the window earns its shape. `MedHeadEnd` flat across the first deciles and
rising across the last is the floor binding on short documents and the share binding on long ones. A
located share that sags at either end means the arm covering that end is set wrong, and the sweep
above says by how much.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_party, .lP$Output$Party)
arrow::write_parquet(tab_head, .lP$Output$Head)

DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = c("Contracting party, per document", "Organisations in the head, per name"),
  Path     = c(.lP$Output$Party, .lP$Output$Head)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B")
```

The first artifact carries every document, not only the located ones. A consumer filtering on
`Status` makes that decision visibly; a consumer handed a pre-filtered file makes it without knowing.

# Overview

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of LexNLP organisation spans by relative position in the document, weighted two
#|   ways. The dashed rules mark the nominal head and tail cutoffs; on short documents the floor
#|   pushes the effective head further right than the rule drawn. Where the two lines agree the
#|   bimodality is a property of contracts rather than of a few large filings."
ent_plot_density(
  .tab  = tab_density,             # measured in Windows, before the session closed
  .head = .lP$Params$HeadShare,    # nominal cutoff, drawn as a rule
  .tail = .lP$Params$TailShare
)
```

```{r}
#| label: fig-party-status
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Status of the contracting-party match by contract type, as shares within each type. The
#|   leftmost segment is the working set; the three to its right are three different problems, and
#|   the rightmost is a limit of the recorded metadata rather than of the extraction."
ent_plot_party_status(
  .tab       = tab_party,
  .key_class = "ClassDetailed"   # the vocabulary 03A registered, so rows match the 03 family
)
```

```{r}
#| label: report-everything
ent_report_all_org(
  .keys        = tab_keys,
  .grid_win    = tab_grid_win,
  .grid_anchor = tab_grid_anchor,
  .party       = tab_party,
  .head        = tab_head,
  .region      = tab_region,
  .terms       = tab_terms
)
```

# Next

The head is a region and the anchor is a coordinate inside it. Three rules follow, in dependency
order, and each is added to this document as its own entity section.

**The document family.** A contract opening `by and between X and Y` carries a counterparty; a stock
incentive plan opening `X 2017 STOCK INCENTIVE PLAN` is the company's own instrument and carries
none. Roughly half the sample is the second kind, so a counterparty rule applied blindly would report
a correct result as a failure across the largest classes in the taxonomy.

**Counterparties.** Whatever the head holds that the anchor did not match. The candidate set is
written above; what it still lacks is a way to separate a counterparty from a signatory, and a way
to admit the natural persons that employment and indemnity agreements name on the other side.

**The remaining labels.** Geography, dates and money are resolved in 04D against this same head, and
each needs a role assignment before an engine can be chosen for it.
