---
title: "Entity Measurement -- Scoring Engines and Rules Against EDGAR (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message = TRUE, # mandatory: cli writes through the message stream under knitr, so
  # message = FALSE would discard this document's entire output
  warning = FALSE,
  comment = "", # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5, # fixed for every figure; only height varies, and only with row count
  fig.align = "center",
  dpi = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# 03A owns the fixed-width console formatter every document in the monorepo reports through.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script # resolves to 1_code/04B-EntityMeasure.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A extracted 7.4 million candidates and declined to rank anything, because ranking needs labels and
there are no entity labels. This document supplies the missing judge, and it does so without
annotation.

For every contract, EDGAR records the filer's name, the filing date and the registered addresses.
None was derived from the contract text, and each identifies **an entity that must be present**: a
company is a party to its own contract, a contract cannot be signed after it is filed, and a filer's
registered address is a place the contract has reason to name. That is enough to score an engine's
recall, to score a proposed rule, and to choose an extraction window.

## What the anchor is, and what it is not

One known-true entity per document, not a complete labelling. A span that fails to match the anchor
is **unlabelled, not wrong** -- most organisations in a contract are counterparties, agents and third
parties EDGAR never recorded.

The two directions therefore mean different things, and conflating them would be the easiest mistake
to make here:

- **Recall against the anchor is exact.** An engine that never proposes the filer's own name did not
  find it. No hedging is needed and none is offered.
- **Precision against the anchor is a lower bound.** A rule keeping ten spans of which one is the
  filer might have kept nine counterparties or nine street names, and this document cannot tell them
  apart. It behaves well for *ranking* rules against each other and badly as a level.

## Roles the anchor speaks to, and in which direction

The filer is a party, and that cuts two ways. A `party` cue should concentrate on it -- but an
`agent`, `regulator` or `statutory` cue should **avoid** it. "Act of 1933" is never a contract's own
date; a company is not its own administrative agent; an expiry date falls after the filing while the
anchor requires one at or before it.

So roles are judged in a direction. For `high` roles the pass condition is lift above the base rate;
for `low` roles it is lift near zero. The second is falsification rather than confirmation, and the
verdict says so -- a regulator cue scoring near zero has been shown not to fire on parties, which is
weaker than being shown correct. It still removes mislabelled rules, which is most of what is wanted
from a set nobody has validated.

Three groups stay outside the frame in either direction. An `affiliate` shares the filer's name, so
the anchor matches it and high lift means nothing. `governing_law` is Delaware about as often as the
state of incorporation is. Money has no anchor at all.

Stops are judged universally wherever the label has an anchor: a stop asserts that a span is never
the entity, so a single anchor it kills refutes it outright.

## Addresses are stored in codes, not names

EDGAR writes an address as street, city, **state code**, ZIP -- `ABBOTT PARK IL 60064`,
`THE WOODLANDS TX 77380`. Contracts write "the State of Illinois". A containment test between the
two can only ever fire through the city, so every state a contract names is invisible to it, and
states are most of what a contract names geographically.

`ent_expand_states()` appends the implied names before the test. The code is located by the ZIP that
follows it rather than as a bare token, because bare two-letter tokens are unsafe here -- IN, OR,
OK, ME, LA and DE are ordinary words, and ST, FL and PO occur in street lines.

## Which fold, and why it differs between sections

The reading session read folds 1 to 4, so its rules are scored on fold 5 alone. Engine recall
involves no rules and cannot have been taught, so it uses all 4,398 documents and is the more precise
for it. The two are reported separately and never averaged.

## Money is absent from most of this document

EDGAR records no contract value. There is no anchor, so nothing in the engine table, the rule table
or the window grid can be computed for it, and it is omitted rather than filled with zeros that would
read as failure. The 64 money cues are carried through unscored, and the honest position is that they
need either the redaction cross-check or hand labels.

# Configuration

```{r}
#| label: configure-paths
# The bundle root, and the folder each reading session wrote to. Two sessions have run; the first
# was moved aside before the second was built, so the names differ on disk.
.DIR_COWORK <- fs::path(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts",
  "MatContractData"
)
.FOLDER_RUN1 <- "_EntitiesClaude" # <- the backup of the first session
.FOLDER_RUN2 <- "EntitiesClaude" # <- the second session

.lP <- list(
  Input = list(
    Text = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb",
    # Written by 04B-CoWorkCompile.R from each reading session's responses. Both are scored:
    # the sessions read different documents, so their union covers more vocabulary than either,
    # and Source keeps the recurrence question answerable afterwards.
    #
    # SET .FOLDER_RUN1 BELOW to whatever the first bundle was renamed to. Getting it wrong is not
    # fatal and not silent -- ent_read_rules() reports the file as missing -- but the run scores
    # only the session it found, and the rules the other one validated never reach 04C.
    Rules = c(
      run1 = fs::path(.DIR_COWORK, .FOLDER_RUN1, "compiled", "entity_rules.parquet"),
      run2 = fs::path(.DIR_COWORK, .FOLDER_RUN2, "compiled", "entity_rules.parquet")
    )
  ),
  Output = list(
    Hits   = utils_file_path(.dir_main, "anchor_hits.parquet"), # per-span anchor labels
    Scores = utils_file_path(.dir_main, "rule_scores.parquet"), # every rule, measured
    Kept   = utils_file_path(.dir_main, "rules_kept.parquet"), # the survivors, for 04D
    Policy = utils_file_path(.dir_main, "extraction_policy.parquet") # engine and cap, for 04E
  ),
  Params = list(
    FoldHoldout    = 5L, # the fold the reading session never saw
    DateWindowDays = 730L, # how far before its filing a contract may be dated
    CtxMax         = 400L, # widest context materialised; caps the window any rule may use
    MinFire        = 30L, # below this a rule is too rare to judge on precision
    MinLift        = 1.2, # kept rules must beat the base rate by at least this factor
    RecallTol      = 0.10, # recall points an engine may trail the best and still be considered
    CostTol        = 0.15, # relative cost gap treated as a tie between engines
    HeadChars      = c(1500L, 3000L, 5000L, 10000L, 20000L),
    TailChars      = c(0L, 2000L, 5000L),
    CapChars       = 3000L # retained for reference; the artifact takes its window from .WINDOW
  )
)

# Formats tried, in order, against a date span. Naming them rather than using a general-purpose
# parser is what makes this affordable: a heuristic parser managed 242 strings a second on this
# corpus, so the 198k distinct date spans would take a quarter of an hour; this is about a second.
# Month-first precedes day-first, so an ambiguous slash date reads as US convention -- correct for
# an SEC filing -- while an unambiguous day-first date such as 26/8/2013 still resolves.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", # January 5, 2019
  "%b %d, %Y", "%b %d %Y", # Jan 5, 2019
  "%d %B, %Y", "%d %B %Y", # 5 August 2005
  "%d %b, %Y", "%d %b %Y", # 5 Oct 2015
  "%m/%d/%Y",  "%d/%m/%Y", # 8/26/2013, then unambiguous day-first
  "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d",
  "%d-%b-%Y",  "%m.%d.%Y"
)

# The span is cleaned before it reaches the parser -- see ent_sql_dateclean(). Requiring the whole
# span to be a date resolved only 6.6% of them, because the extractors return the date with
# whatever abuts it and legal drafting adds ordinals and "the 15th day of April, 2007".

# Which roles the anchor can speak to, and in which DIRECTION. The filer is a party at its own
# registered address on the date the contract was made, so a party cue should concentrate on it --
# and an agent, regulator or statutory cue should AVOID it. For the second group low lift is the
# pass condition, which turns roles that were previously unjudged into falsifiable ones.
#
# Roles absent from this table are outside the anchor's reach in either direction: an affiliate
# shares the filer's name so the anchor matches it either way, and a parent GUARANTOR usually does
# too, which is why guarantor is not listed; governing law is Delaware about as often as the state
# of incorporation is; and money has no anchor at all.
#
# Add "GPE", "incorporation", "high" here if a state-of-incorporation column turns up in the
# metadata -- ent_anchor_keys() reports whether it found one.
.ALIGNED <- tibble::tribble(
  ~Label,  ~Role,           ~Direction,
  "ORG",   "party",         "high",
  "ORG",   "agent",         "low", # the filer is not its own administrative agent
  "ORG",   "regulator",     "low", # the SEC is never a party to the contract it receives
  "ORG",   "third_party",   "low", # counsel, accountants, brokers
  "DATE",  "signing",       "high",
  "DATE",  "effective",     "high",
  "DATE",  "term_start",    "high",
  "DATE",  "statutory",     "low", # "Act of 1933" is never the contract's own date
  "DATE",  "expiry",        "low", # expiry follows the filing; the anchor precedes it
  "GPE",   "party_address", "high",
  "GPE",   "performance",   "low",
  "GPE",   "incidental",    "low"
)

# Headings probed for by search rather than enumerated from line structure. The list mixes the
# conventional Exhibit-10 furniture with the four the reading session proposed.
.HEADINGS <- c(
  "GOVERNING LAW", "NOTICES", "DEFINITIONS", "MISCELLANEOUS", "TERM", "TERMINATION",
  "ARBITRATION", "COUNTERPARTS", "REPRESENTATIONS AND WARRANTIES", "CONFIDENTIALITY",
  "INDEMNIFICATION", "ASSIGNMENT", "SEVERABILITY", "ENTIRE AGREEMENT", "WITNESS WHEREOF",
  "PURCHASE PRICE", "RENT", "PAYMENT", "COMPENSATION", "LICENSE FEES", "INITIAL PAYMENT",
  "LENGTH OF THE TERM", "BROKERS COMMISSION"
)

# Which of the redaction roles the surviving punctuation can speak to. A removed party name and a
# deleted clause body leave nothing behind that identifies them, so they are absent here and are
# reported as unmeasured rather than scored against a signal that cannot see them.
.REDACT_SHAPE <- tibble::tribble(
  ~Role,                ~Shape,
  "royalty_rate",       "ShapeRate", # a percent sign survived the gap
  "aggregate_amount",   "ShapeValue", # a currency symbol did
  "milestone_payment",  "ShapeValue",
  "unit_price",         "ShapeUnit", # "per share", "per barrel"
  "term_length",        "ShapePeriod" # "days", "months"
)

# Engines for the labels the anchor cannot rank. Money has no external record of a contract's value
# and redaction has no ground truth at all, so neither can be chosen on recall -- but both must be
# NAMED, or 04C joins its candidate set against a policy with a hole in it and drops the label
# without saying so. LexNLP fires on money in under a fifth of documents, which leaves the
# transformer; redaction has one extractor.
.DEFAULT_ENGINE <- c(MONEY = "spacy:en_core_web_trf", REDACT = "paper:redaction-v1")

# The window each label is read under. ORG and GPE are set from the character grid below. DATE is
# NOT, and the reason matters: the date anchor is the contract's own date, which sits in the
# preamble, so the grid measures how well a window finds a START and is silent about an END. A term
# clause sits thousands of characters later, and a head-only window returned an expiry date for 22
# of 4,398 documents. The tail here is a declared correction to a measurement that could not see
# the quantity it was being used to choose.
.WINDOW <- tibble::tribble(
  ~Label, ~CapChars, ~TailChars, ~WindowBasis,
  "ORG", 3000L, 0L, "measured: 91.7% document recall, 4.8% of characters",
  "DATE", 3000L, 5000L, "declared: the anchor is a start date and cannot see expiry",
  "GPE", 100000000L, 0L, "full text: extraction is cheap and the window is not measurable",
  "MONEY", 100000000L, 0L, "full text: same",
  "REDACT", 100000000L, 0L, "full text: a cap drops 86% of markers"
)

fs::file_exists(c(.lP$Input$Text, .lP$Input$Anchors, .lP$Input$Store, .lP$Input$Rules))
```

Failing here rather than three chunks later is deliberate. The rules path in particular points
outside the repository, into the folder the reading session wrote to.

# Anchors

The anchor set is built once and written to disk, because three separate analyses read it and 04D
wants it too. Organisations and places resolve inside DuckDB, where the test is string containment on
a normalised form. Dates need a parser, so the *distinct* date strings -- far fewer than their
occurrences -- are brought into R, parsed once, and the verdict joined back.

```{r}
#| label: build-anchors
tab_keys <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)

con <- ent_session(
  .db_path = .lP$Input$Store, # attached read-only; nothing here can write to 04A's artifact
  .keys    = tab_keys # registered so the anchor tests can join on it
)

ent_write_anchor_hits(
  .con         = con,
  .path_out    = .lP$Output$Hits, # read by every section below, and by 04D
  .window_days = .lP$Params$DateWindowDays, # a contract dated earlier than this is not its own
  .formats     = .DATE_FORMATS # parsed in the database, not in R; see above
)

tab_cov <- ent_anchor_coverage(.con = con)
ent_report_anchors(.tab = tab_cov)
```

`PctMatched` is the ceiling on everything that follows. It is the share of documents in which *some*
engine proposed the known entity, so no individual engine can exceed it, and the gap below 100% is
documents where every engine missed a company that is certainly named in its own contract.

# Engines

This is the section that costs nothing and settles the question 04A could not touch. No rule enters
it, so it runs on all 4,398 documents.

```{r}
#| label: score-engines
tab_eng <- ent_engine_recall(.con = con)

ent_report_engines(.tab = tab_eng)
```

The comparison to read first is LexNLP against spaCy on organisations. 04A established that LexNLP
returns roughly one twentieth of spaCy's organisation spans and that its output is largely contained
within spaCy's. If its recall on the filer is close to spaCy's, then twenty times the volume bought
very little, and the corpus policy is the narrow engine. If it is far below, breadth is doing real
work and the cost of adjudicating it is the price of the recall.

`SpansPerAnchor` is the second half of that judgement: how many candidates an engine returns for each
known entity it recovers. It is the adjudication cost per unit of recall, and it is the number that
makes an engine affordable or not at corpus scale.

# Rules

Every proposed rule is applied to the candidates in the held-out fold. Context is materialised once
per candidate and the rules tested against it, rather than the reverse -- the join is a few hundred
rules against a few hundred thousand candidates, and doing it the other way would slice the same text
hundreds of times over.

```{r}
#| label: score-rules
tab_rules <- ent_read_rules(.paths = .lP$Input$Rules)

clf_say_table(
  .tab = tab_rules |> dplyr::count(.data$Source, .data$Label, name = "N") |>
    tidyr::pivot_wider(names_from = Label, values_from = N, values_fill = 0L),
  .title = "Rules by session"
)

tab_scores <- ent_rule_scores(
  .con       = con,
  .path_text = .lP$Input$Text, # supplies the context either side of each span
  .rules     = tab_rules, # cues and stops; sections and notes are not machine-applied
  .fold      = .lP$Params$FoldHoldout,
  .ctx_max   = .lP$Params$CtxMax # widest context held, so no rule can reach further
)

tab_rules_scored <- ent_rule_verdict(
  .tab      = tab_scores,
  .aligned  = .ALIGNED, # which roles the anchor can speak to
  .min_fire = .lP$Params$MinFire # below this, precision is noise
)

ent_report_rules(.tab = tab_rules_scored, .n = 10L)
```

Two conventions in that scoring are worth stating because getting either wrong would invert the
result.

**Stops are matched whole-span, never as substrings.** The reading session raised this itself, and it
is right: 34 of its 53 stops are single tokens, and a substring match on `company` would kill *Blue
Ridge Real Estate Company*, which is a party. Equality on the normalised span is the only safe
reading of what a stop asserts.

**A rule that never fires is reported, not dropped.** A grouped count returns nothing for a rule with
no matches, so the scores are joined back onto the full rule table. Firing zero times is the
commonest outcome and it is a result; a rule silently missing from the output would be
indistinguishable from one nobody proposed.

## Money: the one check external data supports

Money has no anchor, so 64 of its cues cannot be scored, and that stays true. One role is the
exception. A redacted amount leaves a bracketed marker in the text -- `[***]`, `[ * * * ]`, `[*]` --
and that is a different kind of evidence from a phrase in the surrounding sentence.

Only the **symbol** form is used. The explicit form, `[confidential treatment requested]`, shares
vocabulary with the cues themselves, so testing one against the other would be circular; the symbol
form shares none.

```{r}
#| label: check-redaction
tab_redact <- ent_redaction_check(
  .con   = con, # reuses the context table built for rule scoring
  .rules = tab_rules # only the MONEY cues carrying the redacted role
)

ent_report_redaction(.tab = tab_redact)
```

```{r}
#| label: check-redaction-shape
tab_shape <- ent_redaction_shape(
  .con       = con,
  .rules     = tab_rules, # the redaction cues, whatever session proposed them
  .shape_map = .REDACT_SHAPE # which roles the surviving punctuation can speak to
)

ent_report_redaction_shape(.tab = tab_shape)
```

The second table is the stronger of the two and it comes from the redaction unit. Where a marker
replaced a value, the currency symbol before it usually survived; where it replaced a rate, the
percent sign after it did; where it replaced a period or a unit price, the noun following did. Those
characters are not a phrase, so agreeing with a phrase cue is genuine corroboration rather than the
same evidence counted twice.

## Which money engine reaches a withheld amount

Money is the one label with no anchor, so its engine went into the policy as a declared default.
Cross-engine agreement narrows the question but does not settle it: the regex arm and the
transformer overlap at Jaccard 0.77, the highest cross-family pair in the store, and agreement on
what both find says nothing about what only one of them can.

A redaction marker is where an amount used to be. Whether an engine proposes a span there is a
capability rather than a tuned score, and it is the case that matters most, because a figure is
withheld precisely when it is commercially material.

```{r}
#| label: classify-redaction-sites
ent_redaction_sites(.con = con, .path_text = .lP$Input$Text)

tab_reach <- ent_redaction_reach(
  .con  = con,
  .near = 3L # a span touching the marker or its currency symbol counts as reaching it
)

ent_report_redaction_reach(.tab = tab_reach)
```

The site classes are read off the characters either side of the marker, not from any engine's
output, so the definition does not presuppose the answer. Read the two differently. On
`after_currency` the regex arm has a pattern written for that shape and a transformer has nothing to
tag -- the number it would recognise is the thing that was removed -- so a difference is expected
and its size is the result. On `before_unit` neither engine has any reason to fire, and a low figure
for both bounds what is recoverable at all rather than separating them.

This validates six cues, not sixty-four, and the honest position on the rest is unchanged. It is
worth having for a second reason: the reading session observed that redacted figures are
systematically the commercially material ones, so a per-document count of them is a variable rather
than only a nuisance, and this is the evidence that would establish it.

# Window geometry

The reading session reported, from three units independently, that confirmed entities cluster at both
ends of a contract while the bulk of candidates do not. 04A concluded the opposite for organisations
-- that they are spread flat -- but 04A measured every organisation span, and if the session is right
then the flatness is the noise and the parties are not flat at all.

That distinction decides the shape of the corpus pass, so it is measured rather than adopted.

```{r}
#| label: measure-window
tab_window <- ent_window_grid(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = c(0.02, 0.05, 0.10, 0.20), # fraction of the document read from the front
  .tail      = c(0, 0.05, 0.10, 0.20) # and from the back; 0 is the prefix window 04A costed
)

ent_report_window(.tab = tab_window)
```

Both columns are needed and neither means anything alone. The share of *anchors* kept is the recall
the window buys; the share of *all spans* kept is the cost it fails to avoid. A window keeping 80% of
anchors and 20% of spans is a good trade; one keeping 80% of both has done nothing.

Compare each head-only row against the same head with a tail added. If the tail buys more anchors
than spans, a prefix window is the wrong *shape* and not merely the wrong size -- which would carry a
cost, since `--max-chars` truncates a prefix and a head-plus-tail pass needs either a new extractor
flag or a splice with an offset map.

## The cap in characters

The grid above is in fractions, and `--max-chars` takes a character count. A character cap is not a
fixed fraction of anything: 3,300 characters is thirteen percent of the median contract here and
three hundredths of a percent of the longest.

It also uses the wrong denominator. It reports the share of anchor **mentions** a window retains, and
a party has to be found **once**, not every time it is named. The share of **documents** in which at
least one mention survives is the quantity a cap should be chosen on, and the two differ sharply.

```{r}
#| label: measure-window-chars
tab_wchar <- ent_window_chars(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = .lP$Params$HeadChars, # character budgets from the front
  .tail      = .lP$Params$TailChars, # and from the back; 0 is the plain prefix window
  .policy    = NULL # every engine pooled, which is the optimistic reading
)

ent_report_window_chars(.tab = tab_wchar)
```

Three columns because a cap is three trade-offs at once. `DocRecall` is what it buys, `SpansKept` is
what 04D must then resolve, and `CharsKept` is what 04E must read -- the only one of the three that
maps to wall-clock time.

The table above pools every engine, so a document counts as recovered when ANY of eight found the
anchor inside the window. One of them will run, and what that one achieves is measured below --
after the engine has been chosen, because it cannot be measured before.

# Policy

The tables above are the evidence; this is the decision, applied by rule rather than asserted in
prose so that it is reproducible and its sensitivity to the tolerances is visible.

Take the engines within `RecallTol` of the best recall for their label, prefer the cheapest, and
where several sit within `CostTol` of the cheapest take the most accurate of those. The second
tolerance is not decoration: on dates two engines sit at 2.7 and 2.8 spans per anchor, a gap well
inside measurement error, and without it the rule would trade three points of recall for a rounding
difference.

```{r}
#| label: choose-engines
tab_policy <- ent_choose_engines(
  .tab        = tab_eng,
  .defaults   = .DEFAULT_ENGINE, # labels the anchor cannot rank still need an engine
  .recall_tol = .lP$Params$RecallTol,
  .cost_tol   = .lP$Params$CostTol
) |>
  dplyr::left_join(.WINDOW, by = dplyr::join_by(Label))

ent_report_policy(.tab = tab_policy)
```

## What the chosen engines achieve

The grid above the policy pools every engine. This one restricts to the engine each label will
actually run, which is the number the corpus pass delivers and the number the artifact carries.

```{r}
#| label: measure-window-deployed
tab_wdeploy <- ent_window_chars(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = .lP$Params$HeadChars,
  .tail      = .lP$Params$TailChars,
  .policy    = dplyr::select(tab_policy, Label, Combo) # one engine per label
)

ent_report_window_chars(.tab = tab_wdeploy)
```

Money is absent from the policy table above and should be. With no anchor there is no recall to rank on, so its
engine is a stated default rather than a measured choice, and 04E should carry it as such.

# Sections

The heading scan in the bundle script returned a table in which every heading occurred in exactly one
of 4,398 documents. That is impossible -- "GOVERNING LAW" alone appears in most contracts ever filed
-- and the reading session reported it four times rather than building on it.

Two causes, and the replacement has to survive both. This corpus carries Windows line endings, which
DuckDB's `trim()` does not strip, so a case-sensitive filter rejects every line it sees; and
HTML-to-text conversion leaves long stretches carrying no newline at all, so what remains is whatever
short line a particular document happens to hold.

Searching for known headings needs no line structure. It also answers the question that actually
mattered, which was never "what headings exist" but "does this heading appear, and where".

```{r}
#| label: probe-sections
tab_sections <- ent_probe_sections(
  .path_text = .lP$Input$Text,
  .headings  = .HEADINGS # conventional Exhibit-10 furniture plus the session's four proposals
)

ent_report_sections(.tab = tab_sections)
```

A heading is usable only when it is both frequent and *narrow*: present in most documents, and
sitting in a tight band of the document. Frequent but scattered locates nothing, and narrow but rare
covers nothing. `MedianPos` against the quartiles is where that reads off.

# Validation

Two checks on the anchor itself, because everything above rests on it.

```{r}
#| label: validate-anchor
tibble::tibble(
  Check = c(
    "Documents with a company key",
    "Documents with an address",
    "Documents with a filing date",
    "Company keys under 5 characters (dropped)",
    "Date-anchored spans that post-date the filing"
  ),
  N = c(
    sum(!is.na(tab_keys$AnchorKey)),
    sum(!is.na(tab_keys$AnchorText)),
    sum(!is.na(tab_keys$DateFiled)),
    sum(is.na(tab_keys$AnchorKey) & !is.na(tab_keys$Class)),
    0L # excluded by construction in ent_write_anchor_hits(); reported so the claim is visible
  )
) |>
  clf_say_table(.title = "Anchor construction")
```

The last row is zero by construction rather than by observation: the SQL requires a parsed date at or
before the filing date, so a later date cannot be flagged. It is reported because a reader should be
able to see that the constraint exists rather than infer it.

```{r}
#| label: validate-basereate
tab_scores |>
  dplyr::distinct(Label, NCand, NAnchor, BaseRate) |>
  dplyr::mutate(BaseRate = clf_pct(.data$BaseRate, .digits = 2L)) |>
  clf_say_table(.title = "Held-out fold: what a rule must beat")
```

A base rate of a fraction of a percent means the anchor is a needle, and a rule reaching a precision
of five percent has done something substantial even though five percent sounds like nothing. Reading
these numbers as if they were ordinary precision would dismiss every useful rule in the set.

# Robustness

```{r}
#| label: inspect-unmeasured
tab_rules_scored |>
  dplyr::count(.data$Label, .data$Measurable, name = "N") |>
  tidyr::pivot_wider(
    names_from = Measurable, values_from = N, values_fill = 0L,
    names_prefix = "Measurable_"
  ) |>
  clf_say_table(.title = "Rules the anchor can and cannot judge")
```

The unmeasured rules are not failures and must not be dropped on this document's evidence. They
address roles EDGAR never recorded -- agents, guarantors, regulators, governing law, every money role
-- and settling them needs adjudication or hand labels.

```{r}
#| label: inspect-anchor-sensitivity
purrr::map(c(365L, 730L, 1095L), function(.w) {
  ent_write_anchor_hits(
    .con = con, .path_out = NULL, .window_days = .w,
    .formats = .DATE_FORMATS
  ) # session only
  ent_anchor_coverage(.con = con) |>
    dplyr::filter(.data$Label == "DATE") |>
    dplyr::transmute(WindowDays = .w, DocsMatched, PctMatched, BaseRate)
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(PctMatched = clf_pct(.data$PctMatched), BaseRate = clf_pct(.data$BaseRate, 2L)) |>
  clf_say_table(.title = "Date anchor: sensitivity to the window")
```

The date anchor is the one with a free parameter, and the paper's own delay analysis says contracts
are filed some time after they are signed. If the matched share moves sharply between one and three
years, the window is doing the work rather than the data, and the date results below should be read
as conditional on it.

```{r}
#| label: restore-anchor-hits
ent_write_anchor_hits(
  .con         = con,
  .path_out    = NULL, # the file on disk was never touched by the loop
  .window_days = .lP$Params$DateWindowDays,
  .formats     = .DATE_FORMATS
)
```

The sensitivity loop rebuilt the in-session anchor table three times, so it is restored to the
configured window before the sections below read it. The artifact on disk was written once, in
`# Anchors`, and no variant of it ever reached the filesystem.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_rules_scored, .lP$Output$Scores)

tab_kept <- tab_rules_scored |>
  dplyr::filter(
    .data$Verdict %in% c(
      "strong", "useful", "safe", "consistent: avoids the anchor",
      "role misassigned: fires on anchor"
    ) |
      (stringr::str_starts(.data$Verdict, "unmeasured") & .data$NFire >= .lP$Params$MinFire)
  ) |>
  dplyr::select(
    Kind, Label, Role, SuggestedRole, Pattern, Side, Window, NFire, Precision, Recall,
    Lift, Direction, Measurable, Verdict
  )

arrow::write_parquet(tab_kept, .lP$Output$Kept)

# The policy artifact 04E consumes: one engine per label, the cap, and the document-level recall
# each choice implies at that cap. Written as a table rather than described in prose so that 04E
# reads a decision instead of re-deriving one.
tab_policy_out <- tab_policy |>
  dplyr::left_join(
    tab_wdeploy |>
      dplyr::select(Label, Head, Tail,
        DocRecallAtCap = DocRecall,
        SpansKeptAtCap = SpansKept, CharsKeptAtCap = CharsKept
      ),
    by = dplyr::join_by(Label, CapChars == Head, TailChars == Tail)
  )

arrow::write_parquet(tab_policy_out, .lP$Output$Policy)
clf_say_table(
  .tab = tab_policy_out |>
    dplyr::mutate(dplyr::across(
      c(Recall, DocRecallAtCap, SpansKeptAtCap, CharsKeptAtCap),
      \(.x) clf_pct(.x)
    )) |>
    dplyr::select(
      Label, Combo, Basis, CapChars, TailChars, Recall, DocRecallAtCap,
      SpansKeptAtCap, CharsKeptAtCap
    ),
  .title = "Extraction policy for 04E"
)

tab_kept |>
  dplyr::count(.data$Label, .data$Kind, name = "N") |>
  clf_say_table(.title = "Rules carried into 04D")
```

Unmeasured rules that fire often enough are carried through rather than discarded. Dropping them
would be treating "the anchor cannot see this" as "this is wrong", and the roles they address --
agents, guarantors, governing law -- are ones 04D needs.

```{r}
#| label: close-session
DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = c("Anchor hits", "Rule scores", "Rules kept", "Extraction policy"),
  Path     = c(.lP$Output$Hits, .lP$Output$Scores, .lP$Output$Kept, .lP$Output$Policy)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  clf_say_table(.title = "Written by 04B")
```

# Overview

## Engine recall against the known entity

```{r}
#| label: fig-engine-recall
#| fig-height: 3.6
#| fig-cap: "Recall on the known entity against spans returned per anchor recovered, by engine."
tab_eng |>
  dplyr::filter(.data$Label != "MONEY", !is.na(.data$Recall), .data$SpansPerAnchor > 0) |>
  ggplot2::ggplot(ggplot2::aes(x = SpansPerAnchor, y = Recall, label = Combo)) +
  ggplot2::geom_point(size = 2) +
  ggplot2::geom_text(size = 2.4, hjust = -0.1, check_overlap = TRUE) +
  ggplot2::scale_x_log10() +
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ggplot2::facet_wrap(~Label, nrow = 1) +
  ggplot2::expand_limits(x = 1) +
  ggplot2::labs(x = "Spans returned per anchor recovered (log)", y = "Recall on the known entity") +
  ggplot2::theme_bw(base_size = 9)
```

Up and to the left is better: the same recall for fewer spans. An engine sitting far right at the
same height as one on the left is paying an order of magnitude in adjudication cost for nothing.

## What each window shape keeps

```{r}
#| label: fig-window
#| fig-height: 4.0
#| fig-cap: "Share of known entities kept against share of all candidates kept, by window shape."
tab_window |>
  dplyr::filter(.data$Label != "MONEY") |>
  ggplot2::ggplot(ggplot2::aes(
    x = SpansKept, y = AnchorKept,
    colour = factor(Tail), group = factor(Tail)
  )) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = 2, colour = "grey60") +
  ggplot2::geom_line() +
  ggplot2::geom_point(size = 1.6) +
  ggplot2::scale_x_continuous(labels = scales::percent) +
  ggplot2::scale_y_continuous(labels = scales::percent) +
  ggplot2::facet_wrap(~Label, nrow = 1) +
  ggplot2::labs(
    x = "Share of all candidates kept", y = "Share of known entities kept",
    colour = "Tail"
  ) +
  ggplot2::theme_bw(base_size = 9)
```

The diagonal is the null: a window that keeps entities and candidates in equal proportion has
selected nothing. Distance above it is the enrichment, and a tail line sitting above the
tail-of-zero line is the reading session's claim confirmed.

## Rule lift by label

```{r}
#| label: fig-rule-lift
#| fig-height: 3.6
#| fig-cap: "Lift over the base rate against how often a rule fires, measurable cues only."
tab_rules_scored |>
  dplyr::filter(.data$Kind == "cue", .data$Measurable, .data$NFire > 0L, !is.na(.data$Lift)) |>
  ggplot2::ggplot(ggplot2::aes(x = NFire, y = Lift)) +
  ggplot2::geom_hline(yintercept = 1, linetype = 2, colour = "grey60") +
  ggplot2::geom_point(size = 1.6, alpha = 0.7) +
  ggplot2::scale_x_log10() +
  ggplot2::scale_y_log10() +
  ggplot2::facet_wrap(~Label, nrow = 1) +
  ggplot2::labs(x = "Candidates the rule fires on (log)", y = "Lift over base rate (log)") +
  ggplot2::theme_bw(base_size = 9)
```

The useful region is upper right: a rule that concentrates the known entity *and* fires often enough
to matter. High lift on a handful of candidates is a curiosity; lift near one at any volume is the
base rate wearing a phrase.

## The whole measurement in one block

```{r}
#| label: report-everything
ent_report_all(
  .tab_cov      = tab_cov,
  .tab_eng      = tab_eng,
  .tab_rules    = tab_rules_scored,
  .tab_window   = tab_window,
  .tab_sections = tab_sections,
  .tab_wchar    = tab_wchar,
  .tab_policy   = tab_policy,
  .tab_redact   = tab_redact,
  .tab_shape    = tab_shape,
  .tab_reach    = tab_reach
)
```

# Next

**04D** resolves spans into the four published variables, using the surviving rules to assign a role
per occurrence. The reading session's constraint applies there and not here: the same place name
carries several roles inside one document, so roles attach to occurrences and never to strings.

Three things this document cannot settle, and they should be taken to 04D as open rather than
assumed. **Money has no anchor**, so its 64 cues are carried unscored; the redaction rules can be
cross-checked against `06-Redactions`, and the rest need hand labels. **Unmeasured roles** -- agents,
guarantors, regulators, governing law -- were never in the anchor's reach and are carried on coverage
alone. And the span-shape prefilters the reading session described in its notes, requiring a
four-digit year on a date or a currency marker on an amount, are not implemented here: they are
hypotheses of the same kind as the cues and belong in the same scoring frame, not ahead of it.

Whether **04C** is still needed is worth deciding on this document's output rather than in advance.
If the engine table settles the corpus policy and the window grid settles its shape, a separate
selection script has nothing left to select, and the family collapses to extract, measure, resolve,
apply.
