---
title: "Entity Rules -- Organisations and the Contracting Party (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Store.R supersedes ner_db_init(), ner_db_append() and ner_db_clear() in
# _NER.R and must be sourced after it. This document only reads, but it reads the per-label `org`
# table rather than the `candidates` view, and the schema those extra columns live in is declared
# there.
source("1_code/_Commons/_Store.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING here
# too: the level registry is rebuilt empty every time _Plots.R is sourced, so a library registering a
# vocabulary has to be sourced after it.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the fixed-width console formatter every document in the
# monorepo reports through; 04A owns the sample, the canonical text and the candidate store.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B-EntityRules.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran nine extractors over 4,398 hand-classified contracts and stored several million candidate
spans. It ranked none of them, because ranking needs labels and there are no entity labels. This
document writes the rules that turn those spans into party variables, one entity at a time.

**Organisations first**, because every other quantity a party carries is measured from where an
organisation was found. The counterparty is whoever else is named beside the filer; the party's
jurisdiction is the place name adjacent to it; the signing date is the date in the same sentence.

## One engine, and why that decides the rest

04C extracts the corpus with five engines and none of them is spaCy. For organisations that leaves
LexNLP alone, which emits 81,467 spans across the sample against spaCy's 5.3 million. The whole rule
therefore runs in R over a table that fits in memory, and DuckDB is read once.

## The party is the anchor, not a region

An earlier design read a fixed head of each document and asked whether the filer was inside it.
Sweeping that head across twenty settings showed the located share rising from 70.6% to 75.1% -- and
the *late* share falling from 6.5% to 2.0%, with the two summing to **77.1% in every single cell**.

That is an identity rather than a finding. The match runs on names and cannot depend on a region, so
a wider head buys no filer at all: it only relabels one already found, while the candidate count
doubles. A region-based head was optimising a label.

So this version has no head. The filer is matched **anywhere** in the document, the window is centred
on **where it was found**, and every document gets its own bounds, stored and printed. The window is
the only thing a counterparty count depends on, which is also why the window sweep is now cheap: the
match is computed once and each window is re-cut over the same result.

## The window, and why it is not scaled by length

Two forms are swept. **Fixed** takes a constant number of characters either side of the party.
**Gap** grows outward through every name whose distance to its neighbour is at most *G*, and stops at
the first larger gap.

The gap arm exists because of a real failure of a constant width: a syndicated credit preamble is
long *because it lists twelve lenders*, and a fixed window truncates the list mid-way. But scaling
the window on document length is the wrong fix, since the same twelve-lender preamble appears in a
forty-page and a four-hundred-page agreement. The gap rule is per-document without being per-class
or per-length, and it uses the clustering itself rather than a proxy for it. Adjacent names sit a
median of 130 characters apart in this sample, with a P90 of 2,540.

## The tail, and why it is relative

The tail is a share of document length rather than a flat width, and the argument that retired the
relative head does not carry over. A preamble names parties **compactly** -- twelve lenders in one
sentence -- while a signature block does not: twelve lenders take twelve blocks of `By: /s/ ...` at
the end. The signature block genuinely scales with the number of parties, and the preamble does not.

The tail is **clamped past the window end**, so the two regions cannot overlap. That changes what it
measures: a name found there cannot also sit beside the party, so the tail now answers *does anything
outside the party's neighbourhood get named* rather than *does the signature block add names*.
Where the window swallows the document there is no tail, and that is reported rather than dropped.

## Noise is expected, and it is reported against a baseline

Nothing below applies a stoplist, a defined-term filter or a geography exclusion. What every table
carries instead is the **unadjusted** count -- every distinct organisation the contract names
anywhere, which is the quantity this rule replaces. The reader sees what the rule removed rather than
being asked to trust that it removed the right things.

Two consequences are accepted rather than engineered away. A filer first named at character 50,000
anchors a window there: it is still the right company, so the document is **flagged as deep** and
kept. And a document where no name matches the registrant takes its first name as the party, which
is a guess; `Status` records it, and the counterparty tables are reported separately for the two
populations because the count survives a wrong anchor better than the named party does.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    # 04A's sample table: labels, folds, and the EDGAR facts the anchor is built from.
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    # 04A's candidate store, opened read-only.
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Roles = utils_file_path(.dir_main, "roles_org.parquet"), # one row per document per name
    Party = utils_file_path(.dir_main, "party_org.parquet")  # one row per document
  ),
  Params = list(
    Combo    = "lexnlp", # the only ORG engine 04C runs over the corpus
    Bins     = 50L,      # bins across relative position in the density figure
    TermsN   = 25L,      # names listed in the document-frequency block
    ReadN    = 10L,      # spans read back in context
    ReadDocs = 6L,       # documents read whole
    ReadMax  = 12L,      # rows shown per document, so one table-heavy filing cannot fill the page
    ReadCtx  = 200L,     # characters either side of a span
    CheckN   = 500L,     # spans cut from the text and compared to what was stored
    Seed     = 42L       # fixed, so the same documents are read on every render
  )
)

# THE MATCH IS ONE VALUE AND THE WINDOW IS ANOTHER. They are separate because the match is
# window-free: it decides which entity anchors the window, never how many names fall inside it.
.lP$Params$Rule <- ent_rule(
  .key         = "core",  # the resolved name, which lexnlp fills on every span it emits
  .min_key     = 2L,      # shortest key admitted for EQUALITY
  .min_contain = 5L,      # shortest key admitted for CONTAINMENT or family
  .tight       = TRUE,    # also compare with spaces removed: UNITED AIRLINES = UNITED AIR LINES
  .frag_min    = 10L,     # shortest fragment admitted as a reverse match
  .frag_share  = 0.6,     # and it must cover this much of the recorded name
  .fam_tokens  = 2L,      # leading tokens two keys must share to be one corporate family
  .fam_share   = 0.5,     # and those tokens must be this much of the shorter key
  .fam_df      = 0.005,   # or ONE token, if it opens a name in at most this share of documents
  .deep        = 5000L    # a match past this offset is flagged, not rejected
)

# The window carried into the released artifacts. Every specification below is reported; this is the
# one the parquet files are written from.
.lP$Params$Spec <- ent_window_spec(
  .kind       = "fixed", # constant characters either side of the party
  .par        = 2000,    # half-width; the median other-name distance is well inside this
  .tail_share = 0.10     # tail as a share of the document, clamped past the window
)

# Reported side by side, in this order, so the fixed widths bracket the gap arm and the whole
# document sits at the end as the unadjusted reference.
.lP$Params$Specs <- list(
  ent_window_spec(.kind = "fixed", .par = 500,  .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 1000, .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 2000, .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 4000, .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 250,  .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 500,  .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 1000, .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = Inf,  .tail_share = 0.10)
)

fs::file_exists(unlist(.lP$Input))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

Both sides of the comparison run through one reduction: strip EDGAR's conformed-name artifact,
uppercase, an ampersand between spaces to `AND`, punctuation to space, whitespace collapsed, a
leading connective dropped, trailing corporate suffixes stripped. *The Boeing Company* and
`BOEING CO` both reduce to `BOEING`; `UGI CORP /PA/` reduces to `UGI` rather than `UGI PA`, which
matched nothing; `PETROL OIL & GAS INC` reduces to `PETROL OIL AND GAS`, which is what the contract
writes out in full.

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(
  .path_anchors = .lP$Input$Anchors   # 04A's sample table, not the raw EDGAR metadata
)

ent_report_keys(
  .tab  = tab_keys,
  .rule = .lP$Params$Rule   # supplies the two floors, so the table reports what the rule will do
)
```

```{r}
#| label: load-lengths
tab_lens <- ent_doc_lens(
  .path_text = .lP$Input$Text   # the canonical text; length in code points, not bytes
)
```

```{r}
#| label: load-spans
tab_spans <- ent_load_org(
  .db_path = .lP$Input$Store,     # opened read-only; nothing here can write to 04A's artifact
  .lens    = tab_lens,            # supplies document length, so an offset becomes a position
  .combo   = .lP$Params$Combo,    # lexnlp, the only ORG engine the corpus pass carries
  .quiet   = FALSE
)
```

# Entities and the match

Everything in this section is window-free, which is what makes the window sweep affordable: the match
is computed once and every window below is cut over the same result.

Mentions of the same company collapse to one row per document per name -- LexNLP returns
`Icosavax, Inc.`, `Icosavax Inc` and `Icosavax, Inc` as three spans and one party. That row is the
**earliest mention taken whole**, so its start, stop and span come from a single mention rather than
from two.

```{r}
#| label: apply-base-rule
res_base <- ent_apply(
  .spans = tab_spans,           # every lexnlp ORG span
  .keys  = tab_keys,            # runs from the key side, so unmatched documents survive
  .lens  = tab_lens,            # so a document with no organisation at all still carries a length
  .rule  = .lP$Params$Rule,     # the match
  .spec  = .lP$Params$Spec      # the window carried into the artifacts
)

tab_ent    <- res_base$Ent      # one row per document per distinct name, window-free
tab_facts  <- res_base$Facts    # the same, with the comparison to the recorded name
tab_party  <- res_base$Party    # one row per document
tab_roles  <- res_base$Roles    # entities with the window, the tail and the assigned role
tab_counts <- res_base$Counts   # one row per document, the counts and the bounds

ent_report_match(.tab = tab_party)
```

A span matches when the two normalised forms are identical -- with or without spaces -- when one
contains the other, or when they share a corporate prefix. **Forward** containment, the span holding
the recorded name, is safe. **Reverse** containment means the span is a *fragment* and needs a floor:
`G` is contained in `GEORGIA PACIFIC`, and an unfloored reverse arm inflates apparent recall rather
than merely adding noise. **Family** reaches what the others cannot -- `Elephant & Castle Group`
against `Elephant & Castle International` -- and a single shared token is admitted only when it is
distinctive, because `CHENIERE` is evidence and `NATIONAL` is not.

```{r}
#| label: measure-boundary
tab_boundary <- ent_boundary(.ent = tab_ent)

ent_report_boundary(.tab = tab_boundary)
```

```{r}
#| label: measure-distances
tab_dist <- ent_dist_profile(.roles = tab_roles)

ent_report_dist(.tab = tab_dist)
```

# Where the party sits

```{r}
#| label: table-where
tab_where <- ent_table_where(.counts = tab_counts)

ent_report_where(.tab = tab_where)
```

# What the window yields

Three populations of the same table. All documents is the released figure; the split says how much of
it rests on a guessed anchor.

```{r}
#| label: sweep-windows
tab_sweep_window <- ent_sweep_window(
  .fact  = tab_facts,           # the match, computed once
  .party = tab_party,           # the anchor every window is centred on
  .specs = .lP$Params$Specs,    # eight specifications, re-cut over the same facts
  .quiet = FALSE
)
```

```{r}
#| label: table-window-all
tab_win_all <- ent_table_window(
  .sweep  = tab_sweep_window,
  .status = "all"               # every document, however its party was found
)

ent_report_window_table(.tab = tab_win_all, .title = "All documents")
```

```{r}
#| label: table-window-matched
tab_win_matched <- ent_table_window(
  .sweep  = tab_sweep_window,
  .status = "matched"           # the party matched the registrant's recorded name
)

ent_report_window_table(.tab = tab_win_matched, .title = "Matched parties only")
```

```{r}
#| label: table-window-first
tab_win_first <- ent_table_window(
  .sweep  = tab_sweep_window,
  .status = "first"             # the first name in the document was taken instead
)

ent_report_window_table(.tab = tab_win_first, .title = "Fallback parties only")
```

```{r}
#| label: table-window-length
tab_length <- ent_table_length(.sweep = tab_sweep_window)

ent_report_length(.tab = tab_length)
```

# Selection

```{r}
#| label: sweep-match
tab_sweep_match <- ent_sweep_match(
  .spans = tab_spans,
  .keys  = tab_keys,
  .lens  = tab_lens,
  .base  = .lP$Params$Rule,     # every row differs from this in exactly one parameter
  .spec  = .lP$Params$Spec,     # held fixed, so only the match moves
  .quiet = FALSE
)

ent_report_sweep_match(.tab = tab_sweep_match)
```

```{r}
#| label: inspect-terms
tab_terms <- ent_head_terms(
  .roles  = tab_roles,        # the names inside the window, with the role assigned to them
  .n_docs = nrow(tab_keys)    # the whole sample, so the share is comparable across sections
)

ent_report_terms(.tab = tab_terms, .n = .lP$Params$TermsN)
```

# Reading

Every table above is equally consistent with a chosen span being a preamble party and with it being
a letterhead, a page footer or a defined term. The text is what separates them, so a fixed sample is
read on every render.

```{r}
#| label: read-matched
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "matched"),
  .path_text = .lP$Input$Text,        # the same canonical text the offsets index
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = .lP$Params$ReadN,      # documents drawn
  .ctx       = .lP$Params$ReadCtx,    # characters either side of the span
  .seed      = .lP$Params$Seed        # fixed, so a change here is a change in the extraction
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "MatchKind", "PartyStart"),
    .title = "Matched parties in context"
  )
```

```{r}
#| label: read-family
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$MatchKind == "family"),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 10L,                   # the arm that can locate the wrong company and report success
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "PartyKey", "PartyStart"),
    .title = "Family matches, where the two names genuinely differ"
  )
```

A shared corporate prefix covers three situations and only the words separate them: a span-boundary
failure the arm rescues, a parent matched to its own subsidiary, and two unrelated companies opening
with the same words. The middle case is not obviously an error -- when a parent files a contract its
subsidiary signed, the subsidiary *is* the party.

```{r}
#| label: read-deep
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$IsDeep, .data$Status == "matched"),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 8L,                    # the windows that are neighbourhoods rather than preambles
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "MatchKind", "PartyStart"),
    .title = "Deep anchors, where the party is first named well into the document"
  )
```

```{r}
#| label: read-fallback
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "first"),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 8L,                    # the guess, read as a guess
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "Status", "PartyStart"),
    .title = "Documents where the first name was taken instead"
  )
```

```{r}
#| label: read-documents
ent_read_entities(
  .roles = tab_roles,
  .keys  = tab_keys,
  .n     = .lP$Params$ReadDocs,   # documents read whole
  .max   = .lP$Params$ReadMax,    # rows per document
  .seed  = .lP$Params$Seed
) |>
  ent_report_entities(.counts = tab_counts)
```

The window bounds are printed above each document because they *are* the rule. A counterparty count
is only as good as the bounds it was taken from, and those bounds differ for every contract.

# Validation

```{r}
#| label: validate-offsets
# AN EQUALITY, NOT A CONTAINMENT. Asking whether the span appears somewhere inside the slice is
# answered YES more easily the wider the slice runs. The slice must BE the span.
tab_check <- ent_check_offsets(
  .tab       = tab_party,
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .col_span  = "PartySpan",           # the span as stored, not the whitespace-collapsed name
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Party offsets at or after character zero",
    "Documents carrying exactly one row",
    "Window contains the party it is centred on",
    "Tail begins at or after the window ends",
    "Roles are mutually exclusive"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(tab_party$PartyStart >= 0L, na.rm = TRUE),
    dplyr::n_distinct(tab_party$DocID),
    sum(tab_counts$WinStart <= tab_counts$PartyStart &
          tab_counts$WinEnd >= tab_counts$PartyStart, na.rm = TRUE),
    sum(tab_counts$TailStart >= tab_counts$WinEnd, na.rm = TRUE),
    sum(tab_counts$NFull >= tab_counts$NCounter + tab_counts$NTailNew + tab_counts$NOther)
  ),
  Of = c(
    nrow(tab_check),
    sum(!is.na(tab_party$PartyStart)),
    nrow(tab_party),
    sum(!is.na(tab_counts$WinStart)),
    sum(!is.na(tab_counts$WinEnd)),
    nrow(tab_counts)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

The first row is the offset discipline. Python emits code-point offsets, and any R operation reaching
for `substr` rather than `stri_sub` would index bytes, misaligning roughly every document carrying a
multibyte character -- with no error raised anywhere. It is also the check that an entity's offsets
came from one mention rather than two. The fourth and fifth rows are the window's own invariants: it
must contain its anchor, and the clamp must hold.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_roles, .lP$Output$Roles)
arrow::write_parquet(tab_counts, .lP$Output$Party)

tibble::tibble(
  Artifact = c("Organisations with roles and window flags, per document per name",
               "Party, window bounds and counts, per document"),
  Path     = c(.lP$Output$Roles, .lP$Output$Party)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B")
```

Both artifacts carry every document, not only the matched ones, and both carry the unadjusted count
beside the rule's. A consumer filtering on `Status` makes that decision visibly; a consumer handed a
pre-filtered file makes it without knowing.

# Overview

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of LexNLP organisation spans by relative position in the document, weighted by
#|   spans and by documents. No cutoff is drawn, because this version has no region rule: the shape
#|   describes the engine and the window is centred on the party rather than on the page."
ent_plot_density(.tab = ent_density(.spans = tab_spans, .bins = .lP$Params$Bins))
```

```{r}
#| label: fig-party-status
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "How the contracting party was found, by contract type, as shares within each type. The
#|   middle segment is the fallback -- the first name in the document, taken because none matched the
#|   registrant -- and the counterparty tables report it separately for that reason."
ent_plot_status(.tab = tab_counts)
```

```{r}
#| label: fig-window
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Mean counterparties per document by contract type and window specification. The
#|   rightmost column is the whole document, which is the unadjusted count of every organisation the
#|   contract names; every column to its left is what a window removes."
ent_plot_window(.tab = tab_sweep_window)
```

```{r}
#| label: fig-baseline
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "The rule against the count it replaces. Each bar is the mean number of distinct
#|   organisations named anywhere in the contract, split into those the window keeps as
#|   counterparties and those it removes."
ent_plot_baseline(.tab = tab_counts)
```

```{r}
#| label: report-everything
ent_report_all_org(
  .keys        = tab_keys,
  .rule        = .lP$Params$Rule,
  .boundary    = tab_boundary,
  .dist        = tab_dist,
  .party       = tab_party,
  .where       = tab_where,
  .win_all     = tab_win_all,
  .win_matched = tab_win_matched,
  .win_first   = tab_win_first,
  .length      = tab_length,
  .sweep       = tab_sweep_match,
  .terms       = tab_terms,
  .n_terms     = .lP$Params$TermsN
)
```

# Next

Geography is resolved against the parties located here: for each party, the nearest place name
forward of it, stopping at the next organisation. The three roles that adjacency separates -- state
of incorporation, party location, governing law -- are named from the resulting table rather than
declared in advance, and the filer's row is validated against the registered address EDGAR records.
The boundary block above says whether a ragged span can move that assignment.

Dates and money follow, neither of them anchored on a party, and both are added to this document as
their own entity sections under the same discipline: the rule is a value, one function applies it,
and the tables and the artifacts come from the same call.
