---
title: "Rules -- Who the Parties Are (04B1)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
purrr::walk(
  .x = c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  .f = \(.s) source(here::here("1_code", "_Commons", paste0(.s, ".R")), encoding = "UTF-8")
)

.name_script <- "04B1-Rules-ORG"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

An extractor proposes organisation names. This turns them into **parties**: it groups the spellings
of one company, decides which parties are registrants by comparing against the names EDGAR recorded,
and assigns every other party a role from where it sits relative to the registrant.

## The rule, in five steps

**Reduce.** Strip legal suffixes, so `ACME CORPORATION` and `ACME CORP.` share one key.

**Group.** Within a document, two keys are one party when one is a word-prefix of the other, or when
one is a single word unambiguously taken from one longer name. `ACME` where both `ACME CORP` and
`ACME HOLDINGS` exist is refused.

**Match.** Against the **primary filer**, agreement until one name runs out, so `ACME` reaches
`ACME CORPORATION`; earliest match wins and that party is the registrant. Against **every other
filer of the same document**, full agreement in both directions only; those parties are co-filers.
Where nothing matches the primary, the first party named is taken and `MatchKind` records it.

The asymmetry is the point. One anchor can afford a loose rule because the alternative is the
fallback. Up to 445 anchors cannot: a bare `AURORA` agrees with twenty-six siblings on one token,
and admitting that would make a whole corporate group registrants of every contract any of them
touched.

**Assign roles**, first match winning: registrant, then co-filer, then counterparty within +/-2,000
characters of the registrant, then signatory in the final tenth, then other. Co-filer sits above
counterparty because a subsidiary named as guarantor in the preamble is inside the window and is on
the same side of the contract as the filer.

**Write** one row per contract per party per mention.

## Why the file is at mention grain

04B2 attaches a place to the party named nearest before it, and a party named once in the preamble
and again in the signature block is reachable from two positions. A party-grain file carries the
first mention only, and the signature block is exactly where a party is named *with* an address.

Every count is a group-by over that file and none is stored. A stored count is a derived copy that
can disagree with its source, and none of them would survive to corpus scale.

## How results are reported

Console tables throughout, and one sorting rule: **Input** describes the data, **Construction**
walks the rule's steps, **Selection** justifies the numbers, **Results** reports the output,
**Validation** proves identities, **Robustness** reads examples. Every figure is in Overview.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument and the family is the
    # filename, so there is no engine token to type.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE ANCHOR IS BUILT, NOT READ. 03A's prepared sample supplies the labels, 02B's register the
    # identity and the filing date, and _Entity.R joins them.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    # ONE FILE. One row per contract per party per mention; every count is a group-by over it.
    Mentions = utils_file_path(.dir_main, "Output", "org_mentions.parquet")
  ),
  Params = list(
    Family    = "lexnlp",  # the only ORG family 04C ran over the corpus
    Entity    = "ORG",
    # This project's names for lexnlp's resolved company and legal form. ent_load_entity()
    # translates; nothing below sees lexnlp's own names.
    Extras    = c("NameCore", "LegalForm", "Description"),
    Bounds    = c(500, 1000, 2000, 4000, 10000), # half-widths the distance profile reports
    Widths    = c(1000, 2000, 3000),             # the released value, bracketed one either side
    TermsN    = 25L,       # names listed in the document-frequency block
    ReadDocs  = 6L,        # documents read whole
    ReadMax   = 12L,       # rows per document, so one table-heavy filing cannot fill the page
    ReadMerge = 8L,        # documents whose merges are read back
    CheckN    = 500L,      # party spans cut from the text and compared to what was stored
    Seed      = 42L        # fixed, so the same documents are read on every render
  )
)

# TWO PARAMETERS AND ONE CAP. The rule is window-free -- it decides which names are one party and
# which party is the registrant, and neither depends on a distance. The window is applied afterwards
# and is the only number swept.
.lP$Params$Rule <- ent_rule(
  .key             = "core",  # the reduced key, suffixes stripped
  .merge_fragments = TRUE     # a single word unambiguously taken from one longer name
)

.lP$Params$Spec <- ent_window_spec(
  .par        = 2000,  # characters either side of the registrant
  .tail_share = 0.10   # the final tenth, counted as signatories
)

fs::dir_create(fs::path_dir(.lP$Output$Mentions))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, fs::file_exists)
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

# Input

## The anchor, from EDGAR

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,   # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,   # 02B: CIK, CompanyName, DateFiled, nCIK
  .path_landing  = NULL,                 # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

ent_report_keys(.tab = tab_keys)
```

## Every filer, not only the one whose copy was extracted

```{r}
#| label: build-filers

tab_filers <- ent_filer_keys(
  .path_register = .lP$Input$Register,  # HashDocument is what says two copies are one document
  .doc_ids       = tab_keys$DocID,      # the documents this rule will run on
  .quiet         = FALSE
)
```

**A contract filed by several registrants exists in EDGAR once per filer, and 04C extracts the
primary copy only.** So an anchor built from that copy knows one filer, and every other registrant
of the same contract would be found by the extractor, match nothing, and be counted as a
counterparty.

The primary is not stable within a corporate group, which is what makes this more than a labelling
problem. One diagnostics group filed twenty-nine contracts under twenty-six co-registrants and the
primary is a different subsidiary each time, so a contract naming the parent matches an anchor
naming a subsidiary and falls through to the fallback. Matching against every filer rescues exactly
those.

## The document lengths, and the spans

```{r}
#| label: load-spans

tab_lens <- ent_doc_lens(
  .path_text = .lP$Input$Text   # the canonical text; length in code points, not bytes
)

tab_spans <- ent_load_org(
  .dir_store = .lP$Input$Store,      # the directory; the family is the filename
  .lens      = tab_lens,             # supplies document length, so an offset becomes a position
  .family    = .lP$Params$Family,    # lexnlp, the only ORG family the corpus pass carries
  .extras    = .lP$Params$Extras,    # the resolved name and the legal form
  .quiet     = FALSE
)
```

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- ent_apply(
  .spans  = tab_spans,           # every lexnlp ORG span, with both candidate keys
  .keys   = tab_keys,            # runs from the key side, so unmatched documents survive
  .lens   = tab_lens,            # so a document with no organisation at all still carries a length
  .rule   = .lP$Params$Rule,     # the grouping and the match
  .spec   = .lP$Params$Spec,     # the one window
  .filers = tab_filers           # every registrant of the document, for the co-filer rule
)

tab_ent     <- res_base$Ent      # one row per document per distinct key, window-free
tab_parties <- res_base$Parties  # one row per document per party, after grouping
tab_party   <- res_base$Party    # one row per document, the contracting party
tab_roles   <- res_base$Roles    # parties with the window, the tail and the assigned role
tab_release <- res_base$Release  # THE FILE: one row per contract per party per mention

ent_report_match(.tab = tab_party)
```

## What the grouping merged

```{r}
#| label: report-grouping

tab_party_facts <- ent_party_facts(.release = tab_release)

ent_report_group(.tab = ent_table_group(.party = tab_party_facts))
```

**Read from the released file rather than from the chain.** The shares here describe the object a
reader has, not one this render alone ever held.

## How far apart the names sit

```{r}
#| label: measure-distances

ent_report_dist(
  .dist = ent_dist_profile(.roles = tab_roles, .bounds = .lP$Params$Bounds),
  .gap  = ent_gap_profile(.roles = tab_roles, .bound = 4000)
)
```

**This is the evidence the window is chosen against.** A half-width has to clear the gap between
adjacent names, or the rule cuts a party rather than noise.

# Selection

## What the other widths would have counted

```{r}
#| label: sweep-widths

tab_doc <- ent_doc_facts(
  .release = tab_release,     # every published per-document quantity, from the file
  .lens    = tab_lens,        # supplies DocLen, which the window bounds are derived from
  .spec    = .lP$Params$Spec  # so the bounds follow the specification rather than a stored copy
) |>
  dplyr::left_join(
    # JOINED, NEVER STORED ON 22.6 MILLION ROWS. Class and AmendType are 03A's label spine and
    # NFilers is the register's; none is a result of this rule.
    dplyr::select(tab_keys, DocID, Class, AmendType, NFilers),
    by = dplyr::join_by(DocID)
  )

tab_sweep <- ent_sweep_window(
  .party_tab  = tab_parties,               # the grouped parties, computed once
  .party      = tab_party,                 # the contracting party each width is centred on
  .pars       = .lP$Params$Widths,         # the released value, bracketed one either side
  .tail_share = .lP$Params$Spec$TailShare, # held at the released value throughout
  .quiet      = FALSE
)

ent_report_window_table(.tab = ent_table_window(.sweep = tab_sweep, .doc = tab_doc))
```

**Three widths and not five.** The released value is bracketed rather than surveyed: a sweep is
worth its render time only while the answer is in question, and one width either side is enough to
show the count is not sitting on a cliff.

## What the grouping is worth

```{r}
#| label: sweep-rule

ent_report_sweep_rule(
  .tab = ent_sweep_rule(
    .spans = tab_spans,
    .keys  = tab_keys,
    .lens  = tab_lens,
    .base   = .lP$Params$Rule,  # the released rule
    .spec   = .lP$Params$Spec,  # the window held at the released value
    .filers = tab_filers,       # held constant, so only the grouping differs between the arms
    .quiet  = FALSE
  )
)
```

# Results

## The naive ladder

```{r}
#| label: table-naive

tab_naive <- ent_table_naive(.doc = tab_doc)

ent_report_naive(.tab = tab_naive)
```

**Each column assumes one more thing the rule can do and a reader cannot**, so a reader who rejects
the grouping takes the spellings column and one who rejects the window takes the naive column.
Every one of them is a group-by over the released file, so neither has to re-run anything.

## Where the party was found

```{r}
#| label: table-where

ent_report_where(.tab = ent_table_where(.doc = tab_doc))
```

## What the signature block adds

```{r}
#| label: table-tail

tab_tail <- ent_table_tail(.doc = tab_doc)

ent_report_tail(.tab = tab_tail)
```

## The commonest counterparty names

```{r}
#| label: inspect-terms

ent_report_terms(
  .tab = ent_window_terms(.roles = tab_roles, .n_docs = nrow(tab_keys)),
  .n   = .lP$Params$TermsN
)
```

# Validation

## Offsets index the canonical text

```{r}
#| label: validate-offsets

# CHECKED ON THE RELEASED FILE AND NOT ON AN INTERMEDIATE, and the difference is the whole point.
# ent_party_names() names a party after its BEST member -- matched, then most mentioned -- while its
# offsets are the EARLIEST member's, which is exactly what the dictionary documents. Those are two
# different mentions on purpose, so slicing one's offsets never returns the other's text and a check
# comparing them fails on every party whose best name is not its first. On the mention file the span
# and its offsets are one row by construction, so the contract is testable rather than only asserted.
tab_verify <- ent_verify_span(
  .tab       = dplyr::filter(tab_release, !is.na(.data$MentionStart)),
  .path_text = .lP$Input$Text,
  .col_start = "MentionStart",
  .col_stop  = "MentionStop",
  .col_span  = "SpanText",
  .n         = .lP$Params$CheckN,  # drawn rather than exhaustive; the text read is the cost
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Mention spans checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "Anything below 100% here is an offset problem and not a rule one: Python emits code-point \\
   offsets and stringi::stri_sub reads them the same way, so a mismatch means the two ends \\
   disagree about what the document is."
)
```

## Three identities the file cannot violate

```{r}
#| label: validate-counts

tibble::tibble(
  Item = c("Documents",
           "Where the five roles sum to the party count",
           "Where the naive count is below the rule's count",
           "Where a co-filer was found but the document has one filer"),
  N    = c(nrow(tab_doc),
           sum(tab_doc$NCounter + tab_doc$NCoFiler + tab_doc$NTailNew + tab_doc$NOther +
                 as.integer(tab_doc$Status != "no entity") == tab_doc$NParties),
           sum(tab_doc$NaiveCounter < tab_doc$NCounter),
           sum(tab_doc$NCoFiler > 0L & dplyr::coalesce(tab_doc$NFilers, 1L) <= 1L))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / nrow(tab_doc))) |>
  tbl_say(.title = "Three identities the counts cannot violate")

cli::cli_alert_info(
  "The second row must be every document. The third and fourth must be ZERO. A nonzero THIRD is a \\
   grouping defect and not a window one, because the window is a subset of the parties and can \\
   never keep more than the naive baseline. A nonzero FOURTH means the filer join fanned out: a \\
   document with one registrant has no other filer to match against, so a co-filer there is a join \\
   producing rows rather than a rule finding parties."
)
```

# Robustness

## The merges, read rather than trusted

```{r}
#| label: read-merged

ent_report_merged(.tab = ent_read_merged(.roles = tab_roles, .n = .lP$Params$ReadMerge))
```

## Whole documents, read in order

```{r}
#| label: read-documents

ent_report_entities(
  .tab  = ent_read_entities(
    .roles = tab_roles,
    .keys  = tab_keys,
    .docs  = NULL,               # drawn at random rather than chosen
    .n     = .lP$Params$ReadDocs,
    .max   = .lP$Params$ReadMax,
    .seed  = .lP$Params$Seed
  ),
  .doc = tab_doc
)
```

**The block that would show a wrong rule.** A fallback document, a merge that should not have
happened and a window that cut a real party all look the same in a table and different on the page.

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Mentions)

ent_report_release(.tab = tab_release, .party = tab_party_facts)
```

## The released file, read

```{r}
#| label: read-release

ent_report_release_sample(
  .tab  = ent_release_sample(.tab = tab_release, .n = 4L, .seed = .lP$Params$Seed),
  .keys = tab_keys     # CompanyName and Class, joined for reading; neither is a column of the file
)
```

**A registrant that is not the filer is the fallback, not a defect.** Where a contract names nothing
resembling the company EDGAR recorded, the first party named is taken and `MatchKind` says
`fallback`. That is 22.4% of contracts, so a drawn handful will usually contain one: a factoring
agreement filed by a borrower names the lender first, and the rule has no basis for preferring
either. The alternative is a null registrant on more than a fifth of the sample, which loses the
party the window is measured from and with it every counterparty count on those documents.

**Read `MatchKind` before reading `PartyRole`.** `exact` and `prefix` mean the registrant is the
filer; `fallback` means it is the first organisation the contract named. Anyone conditioning on the
registrant being the filing company should filter on the first two.

## What every column means

```{r}
#| label: report-dictionary

ent_report_dictionary(.tab = ent_dictionary_mentions(.tab = tab_release))
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

ent_report_headline(.doc = tab_doc, .release = tab_release)
```

## What the rule removed

```{r}
#| label: fig-naive
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_naive$Class))
#| fig-cap: "Counterparties per contract without a rule and with one, by contract type. The gap is the rule."

ent_plot_naive(.tab = tab_naive)
```

## Counterparties and signatories, side by side

```{r}
#| label: fig-tail
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_tail$Class))
#| fig-cap: "What the window kept and what the signature block adds, by contract type."

ent_plot_tail(.tab = tab_tail)
```

## How the registrant was found

```{r}
#| label: fig-party-status
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_doc$Class))
#| fig-cap: "Matched, fallback or nothing found, by contract type."

ent_plot_status(.tab = tab_doc)
```

## How many spellings each party had

```{r}
#| label: fig-group
#| fig-height: 2.4
#| fig-cap: "Share of parties by how the grouping merged them. Alone is a party the grouping never touched."

ent_plot_group(.tab = tab_party_facts)
```

# Next

**04B2** reads this file and attaches a place to each party, using the mention offsets rather than
the party's first mention alone. It writes the geography beside these columns; nothing here is
recomputed there.
