---
title: "Entity Rules -- The Contracting Party and its Counterparties (04B1)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

# here::i_am() anchors the project root on a declaration rather than on whichever marker file the
# search happens to find first. _quarto.yml lives in 1_code/, so Quarto's execute-dir is 1_code/ and
# not the repository root; every path below is written against the root.
here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")

# What every 04B document shares: the name reduction, the anchor build, the entity-table loader, the
# span reader, the offset check and the table shapes.
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the label spine; 04A owns the sample, the canonical text
# and the sample stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B1-Rules-ORG"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B1-Rules-ORG.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document decides, for every contract in the labelled sample, which organisation is the
contracting party and which of the others are its counterparties.

## What comes out

**One file: `parties_org.parquet`, one row per contract per party.** Every contract-level number is
a group-by over it, so there is no second file that can disagree with the first.

Each party carries a role, and the four roles partition every organisation the rule found:

| Role | What it means |
|:--|:--|
| `registrant` | the SEC filer, matched to its EDGAR name -- exactly one per contract |
| `counterparty` | a party named within 2,000 characters of the registrant |
| `signatory` | a party named only in the final tenth of the document |
| `other` | named somewhere else, and not counted |
| `none` | a sentinel: this contract named no organisation at all |

**The naive baseline is everything except the registrant. The rule's answer is the counterparties
alone.** That distinction runs through every table below, and the difference between the two is what
the rule did.

## The rule, in one paragraph

Every organisation name LexNLP found is reduced to a comparable key, and keys naming the same party
are merged into one. A party whose key agrees with the registrant's EDGAR name -- **word for word,
until one of the two names runs out** -- is the contracting party; where several agree the earliest
wins, and where none does the first party named is taken and flagged. Every other party within
**2,000 characters** of the contracting party is a counterparty. Parties in the **final tenth** of
the document are counted separately, and everything else is not counted at all.

Three steps, two numbers. Nothing else in this document enters an answer.

## One engine, and why that decides the rest

04C ran two families over the corpus and neither is spaCy, so for organisations LexNLP is the only
producer this rule can use. The whole rule therefore runs in R over a table that fits in memory.

04A's measurements are why spaCy is not the loss it looks like. On this sample the transformer emitted
**915,716** ORG spans against LexNLP's **81,467** -- eleven times as many -- but volume is not the
argument, position is. LexNLP's organisations concentrate at the document ends with a contrast of
**4.36**, the strongest of any producer and entity 04A measured; spaCy's is **0.97**, uniform to
within rounding. spaCy finds every organisation named anywhere. LexNLP finds the ones named where
parties are named.

## Comparing whole words replaced four arms and a corpus-wide count

The comparison used to have four outcomes -- exact, forward containment, corporate family, reverse
containment -- gated by two length floors and a document-frequency threshold. All four say the same
thing at different strengths, and comparing whole words from the beginning says it once:

| EDGAR name | Contract name | |
|:--|:--|:--|
| `BOEING` | `BOEING` | agree, both run out |
| `BOEING` | `BOEING CAPITAL` | agree, one runs out |
| `PENNSYLVANIA POWER LIGHT` | `PENNSYLVANIA POWER` | agree, one runs out |
| `CHENIERE ENERGY` | `CHENIERE CREOLE TRAIL` | differ at word two |
| `NATIONAL BANK` | `NATIONAL SEMICONDUCTOR` | differ at word two |

**The length floors go with it.** They existed for *substring* matching, where `CA` sits inside
`CATERPILLAR` and no floor below five could stop it. Whole words cannot make that mistake.

**And so does the only corpus-wide quantity in this pipeline.** The old family arm admitted a single
shared leading word when that word opened a company name in at most 0.5% of documents -- a share
computed across every contract in the corpus, whose value therefore depended on how the corpus was
partitioned. That is why the organisation chain could not be run in chunks. Comparing whole words
needs no such gate.

**What it cost is measured rather than assumed.** The old rule matched 77.1% of documents and this one
matches 74.9% -- about 97 contracts, which now fall to the fallback. And 91.9% of the matches that
remain are exact agreements, so the four arms were one arm and a rounding error.

## Grouping runs before matching

LexNLP splits one name across mentions -- `Florida East Coast Railway` at one offset and the bare word
`Railway` at another -- and glues neighbouring text onto others, as in `Grant Date, Hubbell` where a
heading ran into the party name. Both are one company arriving as two entities.

Two names in one contract are one party when **one is the beginning of the other**, or when **one is a
single word taken unambiguously from the other** -- a word inside two longer names joins neither.
Grouping first means neither reaches the EDGAR comparison alone, and it means the fallback's "first
party named" is the first *unique party* rather than the first raw span.

**It also decides what the party is called:**

> A party takes the name of the member that matched EDGAR. Where no member matched, it takes the name
> of the member mentioned most often, with the earliest mention breaking ties.

Neither longest nor earliest would do: both hand `GRANT DATE HUBBELL` the name over `HUBBELL`, the
first because it has more words and the second because the glued heading is usually the first mention.

**And it made a parameter disappear.** The rule used to carry a 500-character reach that preferred a
clean exact match sitting just behind a contaminated one. Once the two are one party there is nothing
left to arbitrate: swept at 0 and at 500 it produced identical output on every column of every row.

## Why there is no head, and why there is one window

An earlier design read a fixed head and asked whether the registrant was inside it. Sweeping that head
across twenty settings showed the located share rising from 70.6% to 75.1% and the late share falling
from 6.5% to 2.0%, **the two summing to 77.1% in every cell**. That is an identity: the match runs on
names and cannot depend on a region.

A **gap window** -- growing outward through every name whose distance to its neighbour is under a
threshold -- was measured against the fixed one and tracks it, agreeing to within a few hundredths on
every contract type. Two rules that agree leave nothing to choose between them but simplicity, so the
fixed window is the rule and the gap arm is not in the code.

The **tail is relative rather than flat**, and the evidence is direct: a flat 3,000-character tail is
wider on the median than a 10% tail -- 3,000 against 2,320 on credit agreements -- and finds fewer
names, 2.97 against 5.04, because a relative tail puts its width on the long agreements where the
signature blocks with many parties actually are.

## Every table carries the naive count

**Naive** is every unique party the contract names anywhere, less one for the registrant -- what a
reader gets without a rule. It sits beside the rule's count in every table and in the headline figure,
because the difference between the two *is* what the grouping and the window did. It is not a released
column: it is one subtraction from a count over the released file, and computing it where it is used
rather than storing it is what stops the two disagreeing.

## How results are reported

Console tables throughout, five figures in `# Overview`, and two reading blocks where a count cannot
settle the question: the documents where grouping merged the most keys, and whole documents read in
position order.

## Where things are written

**One file**, one row per contract per party. Every contract-level quantity is a group-by over it.

Beside it a four-column **mention index** -- where else each party was named -- which 04B2 reads and
nobody analyses.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument and the family is the
    # filename, so there is no engine token to type -- and no combination string to get wrong.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE ANCHOR IS BUILT, NOT READ. The registrant's own facts are not extraction results, so no
    # artifact of 04A's owes them to this document: 03A's prepared sample supplies the labels and the
    # folds, 02B's register supplies the identity and the filing date, and _Entity.R joins them.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    # THE RELEASE, one row per contract per party.
    Parties  = utils_file_path(.dir_main, "Output", "parties_org.parquet"),
    # AND A POSITIONAL INDEX, one row per mention. Not a release: four columns that let a later rule
    # measure what sits beside a party wherever it was named, rather than only where it was named
    # first. 04B2 reads it; nothing else does.
    Mentions = utils_file_path(.dir_main, "Output", "mentions_org.parquet")
  ),
  Params = list(
    Family    = "lexnlp",  # the only ORG family 04C ran over the corpus
    Entity    = "ORG",
    # This project's names for lexnlp's resolved company and legal form. ent_load_entity()
    # translates; nothing below sees lexnlp's own names.
    Extras    = c("NameCore", "LegalForm", "Description"),
    Bins      = 50L,       # bins across relative position in the density figure
    TermsN    = 25L,       # names listed in the document-frequency block
    ReadDocs  = 6L,        # documents read whole
    ReadMax   = 12L,       # rows per document, so one table-heavy filing cannot fill the page
    ReadMerge = 8L,        # documents whose merges are read back
    CheckN    = 500L,      # party spans cut from the text and compared to what was stored
    Bounds    = c(500, 1000, 2000, 4000, 10000), # half-widths the distance profile reports
    Widths    = c(500, 1000, 2000, 4000),        # half-widths the evidence table reports
    Seed      = 42L        # fixed, so the same documents are read on every render
  )
)

# TWO PARAMETERS, AND THE SECOND IS THE ONLY ONE SWEPT. The rule is window-free: it decides which
# party anchors the window, never how many names fall inside it.
.lP$Params$Rule <- ent_rule(
  .key             = "core", # the resolved name, which lexnlp fills on every span it emits
  .merge_fragments = TRUE    # a single word taken unambiguously from a longer name is that name
)

# ONE WINDOW. +/- 2,000 clears the P90 gap between adjacent names reported below, which is the
# argument for it: a window narrower than that gap cuts a list of parties in half, and the distance
# distribution itself has no elbow to pick a width from. The alternatives are reported in Selection
# as evidence rather than offered as a choice.
.lP$Params$Spec <- ent_window_spec(
  .par        = 2000, # half-width in characters either side of the contracting party
  .tail_share = 0.10  # tail as a share of the document, clamped past the window
)

fs::dir_create(fs::path_dir(.lP$Output$Parties))

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is computed")
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop the
document where the path is declared. `Store` is a directory rather than a file, because the family is
the filename and `ent_load_entity()` resolves it.

# Input

## The anchor, from EDGAR

Both sides run through one reduction: strip EDGAR's conformed-name artifact, uppercase, an ampersand
between spaces to `AND`, punctuation to space, whitespace collapsed, a leading connective dropped,
trailing corporate suffixes stripped.

The suffix list holds the **dotted forms as separate tokens** -- `L P`, `L L C`, `N V` -- because
punctuation-to-space turns `WILLIAMS PARTNERS L.P.` into `WILLIAMS PARTNERS L P`, and a list holding
only `LP` strips nothing.

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,   # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,   # 02B: CIK, CompanyName, DateFiled
  .path_landing  = NULL,                 # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

ent_report_keys(.tab = tab_keys)
```

**The join is reported rather than assumed.** A document the register does not carry has no company
name to match against and can only take a fallback party. A left join makes that visible; an inner
join would have computed coverage over the documents that worked.

**The one-word anchor is the case to watch.** A registrant whose reduced name is a single word agrees
with any contract name beginning with that word. That is right for `BOEING` and would be wrong for a
registrant reducing to a common word, which is why the count is reported rather than assumed to be
zero.

## The document lengths

```{r}
#| label: load-lengths

tab_lens <- ent_doc_lens(
  .path_text = .lP$Input$Text   # the canonical text; length in code points, not bytes
)
```

## The organisation spans

```{r}
#| label: load-spans

tab_spans <- ent_load_entity(
  .dir_store = .lP$Input$Store,      # the directory; the family is the filename
  .family    = .lP$Params$Family,    # lexnlp, the only ORG family the corpus pass carries
  .entity    = .lP$Params$Entity,    # the org table inside it
  .lens      = tab_lens,             # supplies document length, so an offset becomes a position
  .extras    = .lP$Params$Extras,    # the resolved name and the legal form
  .quiet     = FALSE
) |>
  dplyr::mutate(
    # Both keys are built once, outside the rule: the reduction depends on no rule parameter, and
    # rebuilding it per sweep cell would run the same strings through the same regex to produce the
    # identical answer.
    SpanKey = ent_norm_key(.x = .data$Span, .min = 1L),
    CoreKey = ent_norm_key(.x = dplyr::coalesce(.data$NameCore, .data$Span), .min = 1L)
  )
```

**Asking for a column that is not there is an abort, not a silent absence.** The loader reads the
table's real schema and names what is missing, because `any_of()` would have dropped `NameCore`
without a word -- and the `coalesce` above would then have fallen back to `Span` on every row, turning
a documented rule into a fallback nobody could see.

**The span count covers fewer documents than the sample holds**, and every mean below is over the
sample rather than over that subset. Documents in which LexNLP proposed no organisation carry no
offsets, no window and no tail, and enter every average as a zero. That is the honest denominator: the
rule has to answer for a document it found nothing in.

# Construction

Everything in this section is window-free, which is what makes the width table in Selection
affordable: the grouping and the match are computed once and every width is cut over the same parties.

## Applying the rule

```{r}
#| label: apply-rule

res_base <- ent_apply(
  .spans = tab_spans,           # every lexnlp ORG span, with both candidate keys
  .keys  = tab_keys,            # runs from the key side, so unmatched documents survive
  .lens  = tab_lens,            # so a document with no organisation at all still carries a length
  .rule  = .lP$Params$Rule,     # the grouping and the match
  .spec  = .lP$Params$Spec      # the one window
)

tab_ent      <- res_base$Ent       # one row per document per distinct key, window-free
tab_parties  <- res_base$Parties   # one row per document per party, after grouping
tab_party    <- res_base$Party     # one row per document, the contracting party
tab_roles    <- res_base$Roles     # parties with the window, the tail and the assigned role
tab_counts   <- res_base$Counts    # one row per document; NOT written, only reported from
tab_mentions <- res_base$Mentions  # one row per mention, mapped back to its party

ent_report_match(.tab = tab_party)
```

## What the grouping merged

```{r}
#| label: report-grouping

tab_group <- ent_table_group(.roles = tab_roles)

ent_report_group(.tab = tab_group)
```

**Keys above Parties is the whole of what grouping removed.** If the two are equal nothing merged, and
every table below is measuring the window alone rather than the window and the collapse together.

## Where the spans sit

```{r}
#| label: measure-density

tab_density <- ent_density(
  .spans = tab_spans,
  .bins  = .lP$Params$Bins   # bins across relative position
)
```

## How far spans overshoot their names

```{r}
#| label: measure-boundary

tab_boundary <- ent_boundary(.tab = tab_ent)

ent_report_boundary(
  .tab  = tab_boundary,
  .note = paste("Nothing in the party rule depends on a tight boundary. The geography rule assigns",
                "a place to the NEAREST organisation, so its scale is the neighbour gap reported",
                "below, and the overshoot has to be read against that.")
)
```

## How far apart the names sit

```{r}
#| label: measure-distances

tab_dist <- ent_dist_profile(
  .roles  = tab_roles,
  .bounds = .lP$Params$Bounds   # the candidate half-widths, so the profile answers the same question
)

tab_gap <- ent_gap_profile(
  .roles = tab_roles,
  .bound = 4000                 # only names near the party; across a contract the gaps are prose
)

ent_report_dist(.dist = tab_dist, .gap = tab_gap)
```

# Selection

## What the other widths would have counted

```{r}
#| label: sweep-widths

tab_sweep <- ent_sweep_window(
  .party_tab  = tab_parties,               # the grouped parties, computed once
  .party      = tab_party,                 # the contracting party each width is centred on
  .pars       = .lP$Params$Widths,         # the candidates, the released value among them
  .tail_share = .lP$Params$Spec$TailShare, # held at the released value throughout
  .quiet      = FALSE
)

tab_win <- ent_table_window(.sweep = tab_sweep, .counts = tab_counts)

ent_report_window_table(.tab = tab_win)
```

## The window against document length

```{r}
#| label: table-length

tab_length <- ent_table_length(.sweep = tab_sweep)

ent_report_length(.tab = tab_length)
```

## What the grouping is worth

```{r}
#| label: sweep-rule

tab_sweep_rule <- ent_sweep_rule(
  .spans = tab_spans,
  .keys  = tab_keys,
  .lens  = tab_lens,
  .base  = .lP$Params$Rule,    # the released rule
  .spec  = .lP$Params$Spec,    # the window held at the released value
  .quiet = FALSE
)

ent_report_sweep_rule(.tab = tab_sweep_rule)
```

**Two rows, and they are the only decision left.** Whether single-word fragments merge is the last
thing in this rule a reader could disagree with: the comparison itself carries no threshold, and the
window is one number whose alternatives are printed above.

# Results

## Where the party was found

```{r}
#| label: table-where

tab_where <- ent_table_where(.counts = tab_counts)

ent_report_where(.tab = tab_where)
```

## The rule against the naive count

```{r}
#| label: table-naive

tab_naive <- ent_table_naive(.counts = tab_counts)

ent_report_naive(.tab = tab_naive)
```

**This is the table the document exists to produce.** `Naive` is what a reader gets by counting every
distinct party a contract names and subtracting one for the registrant. `Count` is what the window
kept. `PctRemove` is the share of the naive total the rule discarded: too low and the rule is doing
nothing, too high and it is cutting parties rather than noise.

**`PctZero` must be read against the contract type, not on its own.** Two-thirds of employment
agreements end with no counterparty because an employment agreement's counterparty is a *person*, and
no organisation extractor can find one. The zero rate tracking contract type in exactly that direction
is the rule working, not failing.

## What the signature block adds

```{r}
#| label: table-tail

tab_tail <- ent_table_tail(.counts = tab_counts)

ent_report_tail(.tab = tab_tail)
```

**The two counts are released apart because their ratio is not constant.** A credit agreement names its
lending syndicate in the signature block and nowhere near the preamble; an employment agreement names
nobody there. Pooling them would make one column mean different things by contract type, so the file
carries the role and the reader decides.

## The commonest counterparty names

```{r}
#| label: inspect-terms

tab_terms <- ent_window_terms(
  .roles  = tab_roles,
  .n_docs = nrow(tab_keys)   # the sample, so the share is over every document rather than over hits
)

ent_report_terms(.tab = tab_terms, .n = .lP$Params$TermsN)
```

# Validation

## Offsets index the canonical text

```{r}
#| label: validate-offsets

# AN EQUALITY, NOT A CONTAINMENT. Asking whether the span appears somewhere inside the slice is
# answered YES more easily the wider the slice runs. The slice must BE the span.
tab_verify <- ent_verify_span(
  .tab       = tab_party,          # the chosen party, whose offsets the window is cut from
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .col_span  = "PartySpan",
  .n         = .lP$Params$CheckN,  # drawn rather than exhaustive; the text read is the cost
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Party spans checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "Anything below 100% here is an offset problem and not a rule one: Python emits code-point \\
   offsets and stringi::stri_sub reads them the same way, so a mismatch means the two ends \\
   disagree about what the document is."
)
```

## Two identities the counts cannot violate

```{r}
#| label: validate-counts

# Every party is exactly one of four roles, so the four counts plus the registrant must equal the
# party total in every document. A shortfall is a role that failed to assign; an excess is a party
# counted twice by the grouping.
tibble::tibble(
  Item = c("Documents",
           "Where registrant + counterparty + signatory + other equals the party count",
           "Where the naive count is below the rule's count"),
  N    = c(nrow(tab_counts),
           sum(tab_counts$NCounter + tab_counts$NTailNew + tab_counts$NOther +
                 as.integer(tab_counts$Status != "no entity") == tab_counts$NParties),
           sum(tab_counts$NNaive < tab_counts$NCounter))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / nrow(tab_counts))) |>
  tbl_say(.title = "Two identities the counts cannot violate")

cli::cli_alert_info(
  "The second row must be every document. The third must be ZERO: the window is a subset of the \\
   parties, so the rule can never count more counterparties than the naive baseline does. A nonzero \\
   third row is a grouping defect, not a window one."
)
```

# Robustness

## The merges, read rather than trusted

```{r}
#| label: read-merged

tab_merged <- ent_read_merged(
  .roles = tab_roles,
  .n     = .lP$Params$ReadMerge   # the documents where grouping did the most work
)

ent_report_merged(.tab = tab_merged)
```

**A wrong merge puts two companies under one name and no count would reveal it**, which is why this
block reads rather than counts. The rows to check are the ones where the chosen name looks like a
heading glued to a company: that is the case the naming rule exists for, and it should have been
resolved in favour of the clean name.

## Whole documents, read in order

```{r}
#| label: read-documents

tab_read <- ent_read_entities(
  .roles = tab_roles,
  .keys  = tab_keys,
  .docs  = NULL,                  # drawn at random rather than chosen
  .n     = .lP$Params$ReadDocs,
  .max   = .lP$Params$ReadMax,
  .seed  = .lP$Params$Seed
)

ent_report_entities(.tab = tab_read, .counts = tab_counts)
```

## The fallback documents

```{r}
#| label: read-fallback

# The documents where nothing matched, so the first party named was taken. This is the block that
# says how much the fallback can be trusted, and it cannot be settled by a count.
ent_read_entities(
  .roles = dplyr::semi_join(
    tab_roles,
    dplyr::filter(tab_counts, .data$Status == "first"),
    by = dplyr::join_by(DocID)
  ),
  .keys  = tab_keys,
  .docs  = NULL,
  .n     = .lP$Params$ReadDocs,
  .max   = .lP$Params$ReadMax,
  .seed  = .lP$Params$Seed
) |>
  ent_report_entities(.counts = tab_counts, .title = "Fallback documents, read in order")
```

# Deployment

## The release

```{r}
#| label: write-artifact

tab_release <- ent_release_parties(
  .roles = tab_roles,   # every party with its role and offsets
  .party = tab_party    # supplies every document, including those with no party at all
)

arrow::write_parquet(tab_release, .lP$Output$Parties)
arrow::write_parquet(tab_mentions, .lP$Output$Mentions)

ent_report_release(.tab = tab_release)
```

```{r}
#| label: report-mentions

ent_report_mentions(.tab = tab_mentions, .release = tab_release)
```

**The index is not a second release.** `parties_org.parquet` is the file: one row per contract per
party, everything a reader analyses. `mentions_org.parquet` is four columns saying where else each of
those parties was named, and it exists because a rule measuring what sits *beside* a party needs every
occurrence rather than the first. 04B2 reads it to reach the addresses written in signature blocks;
filtering it to `IsFirst` reproduces the release's own offsets exactly.

**`other` is the largest role, and that is the design.** Those are the parties the window excluded,
kept in the file so a reader can recompute the naive count or re-cut the window from the release
rather than from this render. They are the control group, not discarded data.

## The released file, read

```{r}
#| label: read-release

tab_sample <- ent_release_sample(
  .tab  = tab_release,
  .n    = 4L,                  # one of them is a sentinel, drawn deliberately
  .seed = .lP$Params$Seed
)

ent_report_release_sample(
  .tab  = tab_sample,
  .keys = tab_keys     # CompanyName, joined for reading; it is not a column of the file
)
```

**This is the file.** Everything else in this document describes it; the block above shows it. Read
one contract's rows top to bottom: one `registrant`, the parties the window kept beside it, and the
`other` rows it excluded.

**`Matched` is read against the first table.** A registrant marked `FALSE` is the fallback -- nothing
in that contract resembled the name EDGAR records, so the first party found was taken. Seeing the two
strings side by side is the only way to tell a comparison that failed from a contract that genuinely
never names its filer.

## What every column means

```{r}
#| label: report-dictionary

tab_dict <- ent_dictionary_parties(.tab = tab_release)

ent_report_dictionary(.tab = tab_dict)
```

**The dictionary is checked against the file rather than written beside it.** A column added or
renamed without a matching entry aborts this chunk, which is the only way a dictionary stays true to
the thing it documents.

**A contract in which nothing was found still gets a row.** LexNLP proposed no organisation at all in
116 of the 4,398 contracts. Without a sentinel those documents have no rows, so a mean computed over
the file divides by 4,282 -- about 2.6% too high, with nothing to notice.

**Every contract-level variable is one `summarise`:**

```r
tab_release |>
  dplyr::summarise(
    PartyStatus     = dplyr::if_else(any(.data$Matched), "matched", "fallback"),
    NParties        = sum(.data$PartyRole != "none"),
    NCounterparties = sum(.data$PartyRole == "counterparty"),
    NSignatories    = sum(.data$PartyRole == "signatory"),
    .by = c(DocID, Class, AmendType)
  )
```

The naive baseline is `NParties - 1`, computed wherever it is used and stored nowhere.

# Overview

## The rule in one table

```{r}
#| label: report-headline

ent_report_headline(.counts = tab_counts, .release = tab_release)
```

## What the rule removed

```{r}
#| label: fig-naive
#| fig-cap: "Mean counterparties per contract by type, as the rule counts them and as a naive count
#|   would. Both bars exclude the registrant; the gap between each pair is what the grouping and the
#|   window removed."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_naive$Class))

ent_plot_naive(.tab = tab_naive)
```

## Counterparties and signatories, side by side

```{r}
#| label: fig-tail
#| fig-cap: "The two released counts, stacked, neither including the registrant. Signatories are a
#|   rounding error on employment agreements and a lending syndicate on credit agreements, which is
#|   why they are counted apart rather than pooled."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_tail$Class))

ent_plot_tail(.tab = tab_tail)
```

## How the registrant was found

```{r}
#| label: fig-party-status
#| fig-cap: "How each document's contracting party was found, by contract type. The flagged share is
#|   the fallback, where no party agreed with the EDGAR name."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_counts$Class))

ent_plot_status(.tab = tab_counts)
```

## How many spellings each party had

```{r}
#| label: fig-group
#| fig-cap: "What grouping did to every party found, the registrant included: merged as the
#|   beginning of a longer name, merged as a single word taken from one, or reached by nothing."
#| fig-height: 2.4

ent_plot_group(.tab = tab_roles)
```

## Where the names sit in the document

```{r}
#| label: fig-density
#| fig-cap: "Where organisation spans sit in the document, weighted by spans and by documents. The
#|   two ends are the preamble and the signature block, and the contrast between them and the middle
#|   is what makes position a usable instrument."
#| fig-height: 3.4

ent_plot_density(.tab = tab_density)
```

# Next

04B2 reads `parties_org.parquet` and attaches a place to every party this document found, using the
same anchor: a place is a party's when the party is named within 200 characters before it. It excludes
places sitting inside a governing-law clause, which name the applicable law rather than any party's
address.
