---
title: "Entity Rules -- Where Each Organisation Is (04B2)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary; 04A owns the sample, the canonical text and the stores. This
# document does NOT source 04B1: it reads 04B1's artifact, which is the point of writing one.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B2-Rules-GPE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B2-Rules-GPE.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04B1 found a contracting party in each contract and labelled every other organisation beside it. This
document answers one question about each of them: **where is it.**

## The question a referee asked

The published paper reports 1.9 geoentities per contract and a figure of occurrence by continent.
Referee 1: *"it is unclear whether the countries mentioned are the locations of the contracting
entities... it seems possible that mentioned countries may simply be mentioned in contract pertaining
to some planned business activity."* That is right. The answer is not to find more places, it is to
attach the ones already found to the organisation they belong to.

## Two producers at different tiers, not two opinions about one

matcon's gazetteer carries **116,000** entries and reaches cities and counties. LexNLP carries **437**
-- countries and first-level subdivisions -- and reaches no city at all.

04A measured what that means. The two agree on only **44.5%** of GPE mentions, and where they do meet
they agree on boundaries **97.6%** of the time. That is the signature of complements rather than
substitutes: most of what each proposes, the other never sees, and where both see something they see
it identically. Neither can be discarded without losing coverage, so both are resolved onto one
hierarchy, marked, and stacked. **Never pooled inside a table.**

## The grain is one row per organisation

Not one per document. A document-level variable is then a filter on this table rather than a separate
computation, and "which party is this the address of" stops being a question the release cannot
answer. Every organisation is computed; filer and counterparty are a column, exactly as in 04B1.

## One rule, and one cue

**The place nearest an organisation is that organisation's place.** Search backwards, because a
preamble names the company and then qualifies it -- "X, a Delaware corporation, with offices at 100
Main Street, Springfield, Illinois". Stop at the first organisation. Refuse beyond the reach. That is
the whole of it.

**One cue, and only because proximity cannot reach it.** A governing-law clause sits nowhere near a
party: 95% of the spans its cue catches are attached to no organisation at all. An earlier version
also carried incorporation and location cues, which fired beside a party that proximity had already
caught -- and, because the cue outranked proximity, assigned a role to 14,227 spans attached to
nothing. Those two families are gone. One signal per question.

## Cities are an input, not an output

A city resolves to its state and the state is released; no reported variable is a city. That is the
only way the location variable can be read against the incorporation variable, because they then live
on the same tier. Cities stay in the span-level artifact, because they are what validates against
EDGAR's registered address -- 45.0% at city level against 3.2% at state level, which is the
separation this whole document rests on.

Noise is expected and is not eliminated. No place-name stoplist, no check that a city beside a party
is the party's own rather than its lawyer's. Every table carries the unadjusted count -- every
distinct place the contract names anywhere -- so a reader sees what the rule removed.

## What is recomputed, and what is not

Everything, on every render. Both families' GPE tables fit in memory and the attachment is a fill
down an ordered stack, so nothing here is cached and nothing needs to be.

The stores are opened **read-only**, so no path through this document can write to an artifact it does
not own. The one file read past a package boundary is the gazetteer's own lookup, and the Input
section says why that is safe.

## How results are reported

Console tables throughout, four maps in `# Maps` and three figures in `# Overview`. Every table
carrying a rule's count carries the unadjusted count beside it, and every table is per family.

## Where things are written

Three artifacts: the place spans with their hierarchy, the release at organisation grain, and a
document-level view of it. 04B3 reads none of them; the release is for the paper.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument; the family is the filename.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE ANCHOR IS BUILT, NOT READ. 03A supplies the labels and folds, 02B the identity, and 01C the
    # registered addresses -- which this document, unlike 04B1, actually needs: they are the only
    # external check any of its variables has.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    ),
    # THE GAZETTEER'S OWN LOOKUP, inside the matcon-extract package. Reading a package's data tree is
    # crossing the CLI seam, and it is safe here for a specific reason rather than by convention:
    # gazetteer.py's spec() folds a content hash of this exact file into gazetteer-v2's spec hash, so
    # a lookup that changed moves the model's hash and ner_manifest_write() aborts on the next
    # ingest. This document and the store cannot silently disagree about which lookup they used.
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet"),
    # 04B1's organisations, with the position and the role every place attaches to.
    Org = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04B1-Rules-ORG"),
      "Output", "roles_org.parquet"
    )
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "Output", "roles_gpe.parquet"), # one row per place span
    Org   = utils_file_path(.dir_main, "Output", "geo_org.parquet"),   # per organisation: the release
    Doc   = utils_file_path(.dir_main, "Output", "geo_doc.parquet")    # per document: a view of it
  ),
  Params = list(
    # BOTH FAMILIES, marked and stacked. Never pooled inside a table. The extras differ per family
    # and are declared once in _Entity.R, because the two gpe tables no longer share a schema: matcon
    # emits GeoKey, IsWord, NParent and MatchKind; lexnlp emits GeoName, GeoAlias and GeoCategory.
    Families = c("lexnlp", "matcon"),
    LawWin   = 120L,     # characters read before a span for the governing-law cue
    Bins     = 50L,      # bins across relative position in the density figure
    ReadN    = 10L,      # spans read back in context
    ReadCtx  = 200L,     # characters either side of a span
    CheckN   = 500L,     # spans cut from the text and compared to what was stored
    MapCombo = "matcon", # the family the maps and the class table are drawn from
    LabelN      = 12L,   # countries labelled with their count on a world map
    LabelStates = 15L,   # states labelled on the US map
    Seed     = 42L       # fixed, so the same documents are read on every render
  )
)

# The attachment carried into the released artifacts. ONE REACH for every level: states attach at a
# median of five characters and cities at seventy-six, so a per-level reach fits the data better and
# costs a paragraph in the paper to defend. It is swept as one alternative row and adopted only if
# the registered-address check says so.
.lP$Params$Spec <- geo_spec(
  .reach      = 200,   # furthest an organisation may be and still claim a place
  .reach_city = NULL,  # one number for every level
  .party_only = FALSE  # every organisation gets its geography; the role is a column
)

.lP$Params$Specs <- list(
  geo_spec(.reach = 40),
  geo_spec(.reach = 100),
  geo_spec(.reach = 200),
  geo_spec(.reach = 400),
  geo_spec(.reach = 200, .reach_city = 400),  # the per-level variant, reported not adopted
  geo_spec(.reach = 200, .party_only = TRUE)  # parties only, against every organisation
)

fs::dir_create(fs::path_dir(.lP$Output$Spans))

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is computed")
```

Failing here rather than six chunks later is deliberate: a missing upstream artifact should stop the
document where the path is declared. `Org` is 04B1's artifact, read rather than recomputed, which is
the reason for splitting the family -- a change to the date rule should not re-run the party sweep.

# Input

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,   # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,   # 02B: CIK, CompanyName, DateFiled
  .path_landing  = .lP$Input$Landing,    # 01C: the registered addresses this document validates on
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_org <- arrow::read_parquet(.lP$Input$Org) |>
  dplyr::select("DocID", "Key", "Name", "Role", "Start", "Stop")

tibble::tibble(
  Item = c("Documents in the sample",
           "Documents with a registered address",
           "Organisations carried from 04B1",
           "...filers",
           "...counterparties",
           "...signatories and others"),
  N    = c(nrow(tab_keys),
           sum(!is.na(tab_keys$BusinessAddress)),
           nrow(tab_org),
           sum(tab_org$Role == "filer"),
           sum(tab_org$Role == "counterparty"),
           sum(!tab_org$Role %in% c("filer", "counterparty")))
) |>
  tbl_say(.title = "What this document is built on")
```

**The address coverage is the second row and it is the ceiling on the only precision measure here.**
Nothing upstream has ever reported it: 04B1 passed `NULL` for the landing page because ORG has no use
for an address, so this is the first render in which that join runs at all. A low number is not a
defect -- it is the denominator every figure in Validation is read against.

```{r}
#| label: load-lookup

tab_lookup <- geo_lookup(
  .path_lookup = .lP$Input$Lookup   # the two parent columns gazetteer-v2 does not emit
)

tab_cand <- geo_candidates(
  .path_lookup = .lP$Input$Lookup   # every state a city name exists in, kept rather than collapsed
)
```

**The lookup does much less than it used to.** `gazetteer-v2` emits `GeoKey`, `NParent`, `IsWord`,
`Iso2` and `Iso3` on every row it writes, so only the state and its county are recovered here. Under
the flat store none of those arrived and all five were joined in.

```{r}
#| label: load-spans

tab_raw <- purrr::map(
  .x = .lP$Params$Families,
  .f = \(.fam) ent_load_entity(
    .dir_store = .lP$Input$Store,               # the directory; the family is the filename
    .family    = .fam,
    .entity    = "GPE",
    .lens      = tab_lens,                      # supplies document length
    .extras    = ent_extras(.fam, "GPE"),       # declared per family in _Entity.R
    .quiet     = FALSE
  ) |>
    geo_resolve(.lookup = tab_lookup, .family = .fam) |>
    dplyr::mutate(Combo = .fam, .before = 1L)
) |>
  purrr::list_rbind()
```

**The extras are asked for per family**, because the two `gpe` tables no longer share a schema. Under
the flat store a caller named one list for both and the ingest padded whatever an extractor did not
emit; here asking matcon for `GeoName` is an abort naming the columns it does have.

**And two of them are renamed on read, because a shared column name is not a shared quantity.** Both
families emit an `Iso2` and an `Iso3`, and the four columns mean four things. matcon's own
documentation is explicit: its `Iso2` resolves *"all 50 states, 81% of populated places, 95% of
counties, and NEVER a country"*, while its `Iso3` is *"every country, and USA for every US entity"*.
LexNLP is the other way round -- `Iso3` on countries alone, `Iso2` on a country **or** a subdivision.

Read under one pair of names the two disagree silently, and the first version of this document did
exactly that. It rendered clean and produced the right answer by luck: `geo_country()` reads the
country column first and matcon's happened to be one, while the subdivision-prefix recovery sat dead
at 0.0% of matcon's rows and 4.2% of LexNLP's. They arrive as `SubIso` and `CountryIso3` now, and
`geo_resolve()` is the one place their meaning is mapped onto the shared hierarchy.

```{r}
#| label: resolve-cities

tab_geo <- tab_raw |>
  geo_city_state(.cand = tab_cand) |>   # every state a city name exists in
  geo_country()                          # the country, from three sources in a stated order

geo_report_resolve(.geo = tab_geo)
```

```{r}
#| label: report-cities

geo_report_city(.geo = tab_geo)
```

```{r}
#| label: report-coverage

tab_cover <- geo_coverage(.geo = tab_geo)

geo_report_coverage(.tab = tab_cover, .country = tab_geo)
```

**This table exists because a claim about a column belongs in a render rather than in a paragraph.**
04A's prose asserted that LexNLP emits no ISO codes, reasoning from the fact that the codes are
dropped as **match aliases** -- which is true, and does not follow. `IN`, `NOR` and `AND` are English
words appearing in nearly every contract, so admitting them as aliases would be ruinous; but the codes
are a property of the entity that matched, not of the alias that matched it, and they arrive
populated. That error survived one document because nothing printed the column.

The country rollup is reported for the same reason. It is the one place a country is **inferred**
rather than read: of the geo dictionary's 437 entities only the 253 countries carry an ISO-3166-3, so
Ontario, Guangdong and Scotland have none. Their ISO-3166-2 is a subdivision code -- `CA-AB`, `CN-13`,
`GB-ENG` -- whose prefix is exactly the country, and splitting on the hyphen recovers it. An earlier
version claimed those rows "keep their ISO code, so they roll to a country" and they did not; they
came out missing.

# Construction

```{r}
#| label: attach-base
tab_roles <- geo_attach(
  .geo  = tab_geo,            # every place span, resolved
  .org  = tab_org,            # 04B1's organisations, with their roles
  .spec = .lP$Params$Spec     # the attachment carried into the artifacts
)
```

```{r}
#| label: build-org-table
tab_org_geo <- geo_org_table(
  .roles = tab_roles,
  .org   = tab_org,           # every organisation, so one with nothing beside it still gets a row
  .keys  = tab_keys
)

geo_report_org(.orgtab = tab_org_geo)
```

This is the release. Everything below is either a check on it or a view of it.

## Governing law

```{r}
#| label: build-law
tab_ctx <- geo_context(
  .geo       = tab_geo,
  .path_text = .lP$Input$Text,
  .win       = .lP$Params$LawWin   # characters read before the span
)

tab_law <- geo_law(
  .geo       = tab_ctx,
  .lens      = tab_lens,           # supplies every document, including those with no clause
  .path_text = .lP$Input$Text      # for the self-referential scan
)
```

```{r}
#| label: build-doc-table
tab_doc <- geo_doc_table(
  .orgtab = tab_org_geo,
  .roles  = tab_roles,
  .law    = tab_law,
  .keys   = tab_keys
)

geo_report_law(.doc = tab_doc)
```

# Selection

```{r}
#| label: sweep-specs
tab_sweep <- geo_sweep(
  .geo   = tab_geo,
  .org   = tab_org,
  .keys  = tab_keys,            # so every specification is scored against the address, not only sized
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

geo_report_sweep(.tab = tab_sweep)
```

**A wider reach always attaches more places; whether the extra ones are right is only visible in the
address column.** That is why the sweep carries it rather than reporting size alone -- a specification
can be judged only on the one quantity this document has an external check for.

# Results

```{r}
#| label: report-class
geo_report_class(
  .doc   = tab_doc,
  .combo = "matcon"     # named, not taken as whichever family came first
)
```

# Validation

```{r}
#| label: validate-address
tab_validate <- geo_validate(.roles = tab_roles, .keys = tab_keys)

geo_report_validate(.tab = tab_validate)
```

```{r}
#| label: validate-offsets
# The same equality the party document runs: the text cut at the stored offsets must BE the stored
# span, which is the only form of this check that can fail.
tab_check <- ent_verify_span(
  .tab       = tab_roles,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every span carries a level",
    "Every attached span carries an organisation and a distance",
    "Every unattached span carries neither",
    "Every resolved city carries a state",
    "A county appears only with a state",
    "Every organisation from 04B1 has a row per engine"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_roles$GeoLevel)),
    sum(!is.na(tab_roles$OrgKey[tab_roles$Attached]) &
          !is.na(tab_roles$DistToOrg[tab_roles$Attached])),
    sum(is.na(tab_roles$OrgKey[!tab_roles$Attached])),
    sum(!is.na(tab_roles$State[tab_roles$GeoHow %in% c("unique", "nearest named")])),
    sum(!is.na(tab_roles$State[!is.na(tab_roles$County)])),
    nrow(tab_org_geo)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_roles),
    sum(tab_roles$Attached),
    sum(!tab_roles$Attached),
    sum(tab_roles$GeoHow %in% c("unique", "nearest named")),
    sum(!is.na(tab_roles$County)),
    nrow(tab_org) * dplyr::n_distinct(tab_roles$Combo)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

# Robustness

```{r}
#| label: read-state
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "State", .data$Attached),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "GeoUnit", "OrgName", "OrgRole", "DistToOrg"),
    .title = "States, read as the jurisdiction of the organisation before them"
  )
```

```{r}
#| label: read-city
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "City", .data$Attached,
                             .data$GeoHow == "nearest named"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("GeoUnit", "State", "County", "OrgName", "OrgRole", "DistToOrg"),
    .title = "Ambiguous cities resolved by a state the contract itself names"
  )
```

The block that has to be read rather than trusted. The rule required the state to be one the city
could actually be in, so a wrong answer here means the contract named two candidate states and the
nearer one was not the right one.

```{r}
#| label: read-unresolved
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "City", .data$Attached,
                             .data$GeoHow == "unresolved"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("GeoUnit", "NParent", "OrgName", "DistToOrg"),
    .title = "Cities beside a party that the contract never disambiguates"
  )
```

```{r}
#| label: read-law
ent_read_spans(
  .tab       = dplyr::filter(
    tab_ctx,
    .data$GeoLevel %in% c("State", "Country"),
    stringi::stri_detect_fixed(.data$Before, "LAWS OF THE STATE OF")
  ),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "GeoUnit", "GeoLevel"),
    .title = "Governing law, where a jurisdiction is named"
  )
```

```{r}
#| label: read-nothing
# Organisations with nothing beside them. Not a failure -- a counterparty named once in passing has
# no address in the contract -- but the block that says whether the blank is honest.
ent_read_spans(
  .tab       = tab_org_geo |>
    dplyr::filter(!.data$HasGeo, .data$OrgRole == "counterparty", .data$Combo == "matcon") |>
    dplyr::left_join(dplyr::select(tab_org, DocID, Key, Stop), by = dplyr::join_by(DocID,
                                                                                   OrgKey == Key)),
  .path_text = .lP$Input$Text,
  .col_start = "OrgStart",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("OrgName", "OrgRole", "NGeoNear"),
    .title = "Counterparties with no place beside them"
  )
```

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_roles, -dplyr::any_of("Reach")), .lP$Output$Spans)
arrow::write_parquet(tab_org_geo, .lP$Output$Org)
arrow::write_parquet(tab_doc, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Place spans with the hierarchy and the organisation each attached to",
               "Where each organisation is -- the release",
               "Document view, with governing law and the unadjusted count"),
  Path     = c(.lP$Output$Spans, .lP$Output$Org, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B2")
```

`geo_org.parquet` is the release: one row per document, engine and organisation, carrying the role
04B1 assigned and the geography this document attached. Cities live only in the span file, which is
what the registered-address check reads and what anyone re-deriving the resolution would need.

# Overview

## Maps

Four views of the same count, all document-weighted: a contract either names a place or it does not,
so one table-heavy filing cannot colour a country on its own. The fill is logarithmic, because the
United States outweighs everywhere else by three orders of magnitude and a linear scale would paint
one country and leave the rest indistinguishable from empty. The largest areas carry their count.

**The first two tabs are the argument.** Unadjusted is every place the contracts name -- the
published figure of 1.9 geoentities per contract, and what referee 1 could not interpret. Parties is
the same count restricted to places this document attached to a filer or a counterparty. The
difference between them is the rule.

::: {.panel-tabset}

### Unadjusted

```{r}
#| label: fig-map-unadjusted
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Countries by the number of contracts naming a place in them, with no rule applied. Every
#|   place span counts, wherever it sits and whatever it refers to -- a party's address, a planned
#|   business activity, a court's seat. This is the map the published geoentity count would draw."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "all",        # every span, attached or not
  .level    = "country",
  .by_class = FALSE
) |>
  plot_map_world(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelN
  )
```

### Parties

```{r}
#| label: fig-map-parties
#| fig-height: !expr plot_height(6L)
#| fig-cap: "The same count, restricted to places attached to a filer or a counterparty. A country
#|   that fades between this tab and the last is one the contracts mention without any party being
#|   there, which is exactly the distinction the referee asked for."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "parties",    # attached to a filer or a counterparty
  .level    = "country",
  .by_class = FALSE
) |>
  plot_map_world(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelN
  )
```

### By contract type

The twelve per-class world maps that stood here have been replaced by a table, for two reasons and
both are evidence rather than taste.

**The construct failed twice.** They were drawn one per class through `knitr::knit_child()` inside a
nested tabset. In the 03 pass Quarto's tabset filter emptied `panel-tabset` divs built from
R-generated HTML, and the project recorded that construct as abandoned. Here it failed differently: a
plot recorded inside a child is replayed onto a device that has not registered the theme's font, and
`grid` raises `invalid font type` at the first label drawn -- which is why the two unlabelled stages
before it completed and the labelled draw did not.

**And the figure was the weakest in the document.** The US map's own caption says a world map of US
contracts is one dark country and a scattering; twelve of those is twelve dark countries. The
question they were asked -- which contract types reach outside the United States -- is answered
better by counting.

```{r}
#| label: report-class-countries

tab_class_geo <- geo_class_countries(
  .roles = tab_roles,
  .keys  = tab_keys,                 # supplies the type and the denominator
  .combo = .lP$Params$MapCombo,      # matcon, the family that reaches a city
  .scope = "parties",                # attached to a filer or a counterparty
  .n     = .lP$Params$LabelN         # countries shown as columns, most frequent first
)

geo_report_class_countries(.tab = tab_class_geo, .combo = .lP$Params$MapCombo)
```

### US states

```{r}
#| label: fig-map-states
#| fig-height: !expr plot_height(6L)
#| fig-cap: "US states by the number of contracts placing a party there. This is the tier the rule
#|   actually releases, and the one with enough mass to show structure -- a world map of US contracts
#|   is one dark country and a scattering. Delaware is incorporation rather than location, which is
#|   the distinction the registered-address check measures."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "parties",
  .level    = "state",      # the released tier
  .by_class = FALSE
) |>
  plot_map_usa(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelStates
  )
```

:::

## The rule in three figures

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of place spans by relative position in the document, weighted by documents, per
#|   engine. LexNLP's jurisdictions and matcon's cities do not sit in the same part of a
#|   contract, which is the first sign that they are measuring different things."
tab_geo |>
  dplyr::group_split(.data$Combo) |>
  purrr::map(function(.d) {
    ent_density(.spans = .d, .bins = .lP$Params$Bins) |>
      dplyr::mutate(Combo = dplyr::first(.d$Combo))
  }) |>
  purrr::list_rbind() |>
  geo_plot_density()
```

```{r}
#| label: fig-role
#| fig-height: !expr plot_height(5L)
#| fig-cap: "What each organisation got, by the role 04B1 assigned it, as shares within the role. The
#|   filer is named first and in a preamble with its jurisdiction immediately after; a counterparty
#|   named once in passing often has nothing beside it, and that segment is the honest size of the
#|   gap."
geo_plot_role(.orgtab = tab_org_geo)
```

```{r}
#| label: fig-dist
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of the distance from a place to the organisation it attached to,
#|   by level, pooled beyond 400 characters. A level rising steeply in the first fifty characters sits
#|   immediately beside a company name, which is what the preamble form predicts of a jurisdiction and
#|   not of an address."
geo_plot_dist(.tab = tab_roles, .cap = 400)
```

```{r}
#| label: report-everything
geo_report_all(
  .geo      = tab_geo,
  .orgtab   = tab_org_geo,
  .doc      = tab_doc,
  .validate = tab_validate,
  .sweep    = tab_sweep,
  .combo    = .lP$Params$MapCombo
)
```

# Next

Two things here are provisional and both are decided by a number rather than by argument. The reach
is one figure for every level; the sweep carries a per-level row and the registered-address column is
what would justify taking it. And the release is built from both engines side by side; the resolution
table says matcon matches LexNLP on states, beats it on countries and adds every city, so matcon may
end up carrying the release with LexNLP retained only for the subdivisions the hierarchy has no tier
for.

04B3 takes dates, which are not anchored on a party and answer a different referee. Contract duration
is currently the filing date to the farthest future date in the text, and Table 3 Panel B reports a
standard deviation of 40.78 years against a stated cap of 30 -- arithmetically impossible on
non-negative support, where the maximum is half the range. Reproducing that number is the first block
of that document.
