---
title: "Rules -- Where Each Party Is (04B2)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- _Entity.R, 04B1 and this document's own file
# all do.
purrr::walk(
  .x = c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  .f = \(.s) source(here::here("1_code", "_Commons", paste0(.s, ".R")), encoding = "UTF-8")
)

# 04B1 OWNS THE PARTY COLLAPSE, and this document reads its file rather than reimplementing the
# group-by. ent_party_facts() is the one definition of "one row per party".
source(here::here("1_code", "04B1-Rules-ORG.R"), encoding = "UTF-8")

.name_script <- "04B2-Rules-GPE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

matcon proposes place names with offsets. This decides which of them describe a party's location,
which one names the governing law rather than an address, and what each resolves to.

## The rule, in five steps

**Resolve.** Look each name up in the gazetteer. A name existing under more than one parent --
`SPRINGFIELD` is in 33 states -- is marked ambiguous and given no state. The gazetteer refuses to
guess.

**Exclude the law.** A place whose offsets fall *inside* a governing-law clause names the law, not an
address. Containment rather than proximity: in *"...the laws of the State of New York. Delaware
corporations shall..."* Delaware is 47 characters from the cue and is not the jurisdiction.

**Attach.** A place belongs to the party named within **200 characters before it** -- any mention,
not only the first. Backwards only, because a preamble names a company and then qualifies it.

**Resolve the ambiguous city.** It takes whichever of *its own* candidate states the contract names,
nearest first and ties to the one named most often. A name whose candidates the contract never
mentions keeps no state: a fallback would send every unresolved `SPRINGFIELD` to the same state, and
a constant error reads as a real geographic pattern.

**Collapse -- defined here, written nowhere.** The **nearest** attached place wins, ties broken by
the earliest place offset. State and country are read off that one place, so they cannot disagree.

## Two long files, and no per-party table

`places_geo.parquet` is one row per place **including the ones the rule refused**, and
`law_clauses.parquet` is one row per governing-law clause. `geo_collapse()` turns the first into one
row per party; this document scores it, reports it and checks its shape, and the export calls it.

A collapse stored as data cannot be changed without re-releasing. A collapse stored as a query can be
changed by whoever disagrees with it, and there is a decision inside this one that a reader may well
want to change.

The clauses are a second file because of one level. A clause naming no place at all produces no place
row, so a jurisdiction carried as a column of a file of places could never express it -- and that is
exactly what distinguishes a contract with no governing-law clause from one whose clause named no
jurisdiction.

## How results are reported

Console tables throughout, and the same sorting rule 04B1 uses: **Input** describes the data,
**Construction** walks the rule's steps, **Selection** justifies the numbers, **Results** reports the
output, **Validation** proves identities, **Robustness** reads examples. Every figure is in Overview.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument and the family is the
    # filename.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE GAZETTEER'S OWN LOOKUP, inside the matcon-extract package. Reading it crosses the CLI seam
    # and is safe for a specific reason: gazetteer.py folds a content hash of this exact file into
    # its spec hash, so a lookup that changed moves the model's hash and the next ingest aborts.
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet"),
    # 04B1's mention index: one row per contract per party per mention. The attachment interleaves
    # place offsets with THESE, so a place beside a party's third mention still reaches it.
    Mentions = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04B1-Rules-ORG"),
      "Output", "org_mentions.parquet"
    ),
    # The anchor, for the registered address the precision check reads.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    ),
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    )
  ),
  Output = list(
    Places = utils_file_path(.dir_main, "Output", "places_geo.parquet"),
    Law    = utils_file_path(.dir_main, "Output", "law_clauses.parquet")
  ),
  Params = list(
    Family   = "matcon",         # the only family reaching cities and counties
    Reaches  = c(100, 200, 400), # the released value, bracketed one either side
    LawTopN  = 15L,              # jurisdictions listed
    ReadDocs = 4L,               # contracts read whole from the released file
    Seed     = 42L               # fixed, so the same contracts are read on every render
  )
)

# ONE NUMBER. 200 characters is generous for a state -- "a Delaware corporation" attaches at a median
# of a few characters -- and tight enough that a place in the next sentence does not reach back.
.lP$Params$Spec <- geo_spec(.reach = 200)

fs::dir_create(fs::path_dir(.lP$Output$Places))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, fs::file_exists)
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before: a mistyped
# Landing path read FALSE in this very table while the document rendered a precision measure as NA
# with confident prose beside it saying what the number meant.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

# Input

## The anchor and the parties

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = .lP$Input$Landing,   # 01C: the registered address the precision check reads
  .quiet         = FALSE
)

tab_mentions <- arrow::read_parquet(.lP$Input$Mentions)

# ONE DEFINITION OF "ONE ROW PER PARTY", and it is 04B1's. Recomputing the collapse here would be a
# second implementation of a group-by that already exists, free to disagree at the third decimal.
tab_party_facts <- ent_party_facts(.release = tab_mentions)

tibble::tibble(
  Item = c("Documents", "Mentions 04B1 released", "Parties behind them"),
  N    = c(nrow(tab_keys), sum(!is.na(tab_mentions$MentionStart)), nrow(tab_party_facts))
) |>
  tbl_say(.title = "What 04B1 hands over")
```

## The gazetteer

```{r}
#| label: load-gazetteer

geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)
)
```

## The places and the clauses

```{r}
#| label: load-spans

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_spans <- ent_load_entity(
  .dir_store = .lP$Input$Store,
  .family    = .lP$Params$Family,
  .entity    = "GPE",
  .lens      = tab_lens,
  .extras    = ent_extras(.lP$Params$Family, "GPE"),  # declared in _NER.R, not typed here
  .quiet     = FALSE
)

tab_law <- ent_load_entity(
  .dir_store = .lP$Input$Store,
  .family    = .lP$Params$Family,
  .entity    = "LAW",
  .lens      = tab_lens,
  .extras    = ent_extras(.lP$Params$Family, "LAW"),  # none; the cue is in the core LabelRaw
  .quiet     = FALSE
)
```

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- geo_apply(
  .spans    = tab_spans,      # every matcon GPE span
  .law      = tab_law,        # the governing-law clauses, as spans with offsets
  .mentions = tab_mentions,   # 04B1's mention index; the attachment interleaves with it
  .geo      = geo_once,       # the gazetteer, read once
  .spec     = .lP$Params$Spec # the one reach
)

tab_places  <- res_base$Places    # every place, resolved, before anything was removed
tab_inside  <- res_base$Inside    # the places a governing-law clause contains
tab_free    <- res_base$Attached  # the places offered to the attachment, with its columns
tab_release <- res_base$Release   # THE FILE: one row per place, refusals included
tab_law_rel <- res_base$Law       # THE FILE: one row per governing-law clause
```

## What the gazetteer resolved

```{r}
#| label: report-resolve

geo_report_resolve(.tab = geo_table_resolve(.geo = tab_places))
```

## How every city got its state

```{r}
#| label: report-city

tab_city <- geo_table_city(.geo = tab_places)

geo_report_city(.tab = tab_city)
```

**The constraint on the middle arm is what makes it safe.** Taking the nearest state named anywhere
would put `SPRINGFIELD` in Delaware whenever the party is a Delaware corporation. Requiring that a
`SPRINGFIELD` exist in that state does not, and it uses no new data -- the candidate list is already
in the lookup.

## What the governing-law exclusion withheld

```{r}
#| label: report-exclude

geo_report_exclude(.tab = geo_table_exclude(.places = tab_places, .inside = tab_inside))
```

## How far a place sits from its party

```{r}
#| label: measure-distances

geo_report_dist(.tab = geo_dist_profile(.roles = tab_free))
```

**This is the evidence the reach is chosen against.** A reach has to clear the gap between a party
name and the place that qualifies it, and not so much more that the next sentence reaches back.

# Selection

## What the other reaches would have attached

```{r}
#| label: sweep-reach

geo_report_sweep(
  .tab = geo_sweep_reach(
    .geo      = tab_places,          # resolved once; each arm only re-attaches
    .party    = tab_party_facts,     # the parties, held constant
    .mentions = tab_mentions,
    .keys     = tab_keys,
    .inside   = tab_inside,          # the exclusion, held constant across arms
    .reaches  = .lP$Params$Reaches,  # the released value, bracketed one either side
    .quiet    = FALSE
  )
)
```

**Three reaches and not five.** The released value is bracketed rather than surveyed, and each arm is
scored by the same `geo_collapse()` that scores the released rule -- so a difference between arms
cannot come from a difference in how they were counted.

# Results

## The naive ladder

```{r}
#| label: table-naive

tab_doc <- geo_doc_facts(
  .release = tab_release,       # every place, refusals included
  .party   = tab_party_facts,   # supplies the role, so the rule rung can take counterparties only
  .keys    = tab_keys           # the population, so a contract naming no place still gets a row
) |>
  dplyr::left_join(
    dplyr::select(tab_keys, DocID, Class),  # joined for the by-class cut; never stored on a place
    by = dplyr::join_by(DocID)
  )

tab_naive <- geo_table_naive(.doc = tab_doc)

geo_report_naive(.tab = tab_naive)
```

## What the collapse gives each party

```{r}
#| label: table-cover

tab_collapse <- geo_collapse(.release = tab_release, .party = tab_party_facts)

tab_cover <- geo_table_cover(.tab = tab_collapse)

geo_report_cover(.tab = tab_cover)
```

## The governing law

```{r}
#| label: table-law

geo_report_law(
  .tab = geo_table_law(.law = tab_law_rel, .keys = tab_keys),
  .top = geo_table_law_top(.law = tab_law_rel, .n = .lP$Params$LawTopN)
)
```

# Validation

## Four identities the files cannot violate

```{r}
#| label: validate-counts

hold_ <- dplyr::filter(tab_release, .data$InLawClause)

tibble::tibble(
  Item = c("Places in the file",
           "Where a law-clause place was never attached",
           "Where an attached place has a party and a distance",
           "Where an attached distance is inside the reach",
           "Parties in the collapse, against 04B1's count"),
  N    = c(nrow(tab_release),
           sum(!hold_$Attached),
           sum(tab_release$Attached &
                 !is.na(tab_release$PartyKey) & !is.na(tab_release$DistToParty)),
           sum(tab_release$DistToParty[tab_release$Attached] <= .lP$Params$Spec$Reach),
           nrow(tab_collapse))
) |>
  dplyr::mutate(
    Of    = c(nrow(tab_release), nrow(hold_), sum(tab_release$Attached),
              sum(tab_release$Attached), nrow(tab_party_facts)),
    Share = tbl_pct(.data$N / pmax(.data$Of, 1L))
  ) |>
  tbl_say(.title = "Four identities the files cannot violate")

cli::cli_alert_info(
  "ROWS TWO TO FIVE MUST ALL READ 100%. A law-clause place is never offered to the attachment, so \\
   one below 100% means the exclusion ran after the attachment rather than before it. An attached \\
   place without a party or a distance is a join that produced a row it should not have. And the \\
   collapse adds geography to 04B1's parties rather than filtering them, so the party count cannot \\
   move."
)
```

## Offsets index the canonical text

```{r}
#| label: validate-offsets

tab_verify <- ent_verify_span(
  .tab       = tab_release,
  .path_text = .lP$Input$Text,
  .col_start = "PlaceStart",
  .col_stop  = "PlaceStop",
  .col_span  = "PlaceText",
  .n         = 500L,            # drawn rather than exhaustive; the text read is the cost
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Place spans checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "The span and the two offsets are one row of the released file, so this compares a thing with \\
   itself and must be 100%. Anything below is an offset problem rather than a rule one."
)
```

# Robustness

## The place file, read

```{r}
#| label: read-release

geo_report_release_sample(
  .tab = geo_release_sample(
    .tab  = tab_release,
    .n    = .lP$Params$ReadDocs,   # one of them carries a refusal, drawn deliberately
    .seed = .lP$Params$Seed
  )
)
```

# Deployment

## The two releases

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Places)
arrow::write_parquet(tab_law_rel, .lP$Output$Law)

geo_report_release(.places = tab_release, .law = tab_law_rel)
```

## What every column means

```{r}
#| label: report-dictionary

geo_report_dictionary(
  .tab   = geo_dictionary_places(.tab = tab_release),
  .title = "places_geo.parquet"
)

geo_report_dictionary(
  .tab   = geo_dictionary_law(.tab = tab_law_rel),
  .title = "law_clauses.parquet"
)

# THE COLLAPSE IS CHECKED TOO, AND IT IS NOT A FILE. Nothing writes this shape; the export calls
# geo_collapse() and gets it. Checking the function's output is what says the export cannot produce
# a different one.
geo_report_dictionary(
  .tab   = geo_dictionary_parties(.tab = tab_collapse),
  .title = "geo_collapse(), which is checked but never written"
)
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

geo_report_headline(.doc = tab_doc, .collapse = tab_collapse, .places = tab_release)
```

## The ladder, by contract type

```{r}
#| label: fig-naive
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_naive$Class))
#| fig-cap: "Distinct states per contract at three rungs, by contract type."

geo_plot_naive(.tab = tab_naive)
```

## Coverage by role

```{r}
#| label: fig-cover
#| fig-height: 2.4
#| fig-cap: "Share of parties given a state and a country, by role."

geo_plot_cover(.tab = tab_cover)
```

## Where the ambiguous cities landed

```{r}
#| label: fig-city
#| fig-height: 2.4
#| fig-cap: "How each city got its state: uniquely, from a state the contract named, or not at all."

geo_plot_city(.tab = tab_city)
```

## The commonest jurisdictions

```{r}
#| label: fig-law
#| fig-height: 4.6
#| fig-cap: "The jurisdictions contracts choose, as a share of the clauses that named one."

geo_plot_law(.tab = geo_table_law_top(.law = tab_law_rel, .n = .lP$Params$LawTopN))
```

# Next

**04B3** reads the DATE and TERM spans and needs nothing from this document. **04D** calls
`geo_apply()` on chunks of the corpus and writes the same two files at scale, and the **export**
calls `geo_collapse()` to turn the places into one row per party.
