---
title: "Entity Rules -- Where Each Party Is (04B2)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")

# _Entity.R registers PartyRole, which 04B1 writes and this document orders every table by.
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the label spine; 04A owns the sample and the stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B2-Rules-GPE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B2-Rules-GPE.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04B1 found the parties of every contract. This document attaches a place to each of them, and records
the jurisdiction whose law the contract chose.

## What comes out

**One file: `parties_geo.parquet`, one row per contract per party.** It is 04B1's file with geography
added to the same rows, so every count anyone computed over the party file survives unchanged and a
party with no place keeps its row and carries nulls.

| Level | Columns added |
|:--|:--|
| Party | `GeoState`, `GeoStateFrom`, `GeoCity`, `GeoCounty` |
| Party | `GeoCountry`, `GeoCountryIso`, `NGeoNear`, `EdgarAgrees` |
| Contract | `GoverningLaw`, `LawSpecified` -- repeated on every row, like `Class` |

**Governing law is a contract term and never a party's address**, which is the whole reason the rule
below withholds those places from attachment.

## The rule, in one paragraph

A place sitting **inside a governing-law clause** leaves the attachment entirely: it names the law
that applies, and it becomes a contract variable instead. Every other place belongs to the party
named within **200 characters before it**, because a preamble names the company and then qualifies
it. Where several places attach to one party, the nearest of each kind wins.

One number, 200. Nothing else in this document enters an answer.

## One engine, and the reason is coverage rather than quality

matcon's gazetteer carries **181,810 rows** and reaches cities and counties. LexNLP's dictionary
carries **437 entities and has no cities and no counties at all** -- it reaches countries and
first-level subdivisions and stops. Releasing both engines would give every second row a
guaranteed-null half: no city, no county, and a state that could never be inferred from a city. So
matcon is the release, and the family comparison stays in 04A where it belongs.

## The governing-law exclusion repairs a defect

Attachment used to run over every place with no exception. In
*"...ACME CORPORATION. This Agreement shall be governed by the laws of the State of New York"*, a
clause falling within reach of a company name put **New York in that company's state column**. 04B2
measured 95% of governing-law spans attaching to no organisation, which bounds the damage without
removing it: the 5% that did attach biased the released geography toward New York and Delaware.

`lawregex` emits the clause as a span, so the fix is **containment rather than proximity** -- a
non-equi join on offsets that reads no text at all. And the same join answers both questions: which
places to withhold, and which jurisdiction the contract chose.

**Containment beats proximity, and one document says why.** In *"...governed by the laws of the State
of New York. Delaware corporations shall deliver..."* Delaware begins 47 characters after the cue --
comfortably inside any window, and not the jurisdiction. The full stop closes the clause before
Delaware begins.

**A heading is a clause too, and it outranks nothing.** *"GOVERNING LAW. This Agreement is made under
the laws of the State of Texas."* is two clauses: the heading, closed by its own full stop at zero
useful characters, and the sentence carrying Texas. Ordering by position alone takes the heading and
discards Texas, so a clause that found a place outranks one that did not.

## The ambiguous city is the only real decision in the resolution

Two thirds of city names exist in more than one state: `SPRINGFIELD` sits in 33 of them, and the
gazetteer has no population, rank or primary-place column to order them by. Three arms:

| The city name | Gets |
|:--|:--|
| exists in one state only | that state |
| ambiguous, and the contract names one of **its** states | the nearest; ties to the one named most often |
| ambiguous, and the contract names none of them | no state |

**The constraint on the second arm is what makes it safe.** Taking the nearest state named *anywhere*
would put `SPRINGFIELD` in Delaware whenever the party is a Delaware corporation -- and Delaware is
incorporation boilerplate in a large share of contracts, so every Delaware-registered filer would drag
its cities there and the release would show a concentration that is an artifact of the rule.

**Position first, frequency second.** *"Springfield, Illinois"* puts the state two characters away and
position settles it outright; frequency first would lose that wherever the contract mentioned another
candidate state more often. Frequency counts mentions **within the contract**, so nothing here depends
on how the corpus is partitioned.

**The third arm refuses rather than guesses**, and that is a decision. A fallback would send every
unresolved `SPRINGFIELD` to the same state, and a constant error is not noise -- it averages out of
nothing and reads as a real geographic pattern.

## What is upstream and not in this document

`gazetteer.py` admits a place through a three-tier gate before this document sees it: a country or a
state unconditionally, a **distinctive** city name only where a state anchor sits within 200
characters, and a **word-like** name -- `Mobile`, `Reading`, `Enterprise` -- only within 40. A bare
city with no state beside it is refused. That is why city coverage looks the way it does.

## How results are reported

Console tables throughout, four figures in `# Overview`, and one reading block: whole contracts as the
file holds them.

## Where things are written

**One file**, one row per contract per party, superseding 04B1's for downstream use.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument and the family is the
    # filename.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE GAZETTEER'S OWN LOOKUP, inside the matcon-extract package. Reading it crosses the CLI seam
    # and is safe for a specific reason: gazetteer.py folds a content hash of this exact file into
    # its spec hash, so a lookup that changed moves the model's hash and the next ingest aborts.
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet"),
    # 04B1's parties: the role, the name and the offsets of the FIRST mention.
    Party = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04B1-Rules-ORG"),
      "Output", "parties_org.parquet"
    ),
    # AND EVERY MENTION OF THEM. A place beside a party's third mention cannot reach that party
    # through a table holding only its first, and a signature block is exactly where a party is
    # named WITH an address. This index is what the attachment interleaves.
    Mentions = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04B1-Rules-ORG"),
      "Output", "mentions_org.parquet"
    ),
    # The anchor, for the registered address the precision check reads.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    )
  ),
  Output = list(
    Parties = utils_file_path(.dir_main, "Output", "parties_geo.parquet")
  ),
  Params = list(
    Family   = "matcon",  # the only family reaching cities and counties
    Reaches  = c(50, 100, 200, 400, 800), # candidates the evidence table reports
    LawTopN  = 15L,       # jurisdictions listed
    ReadDocs = 4L,        # contracts read whole from the released file
    Seed     = 42L        # fixed, so the same contracts are read on every render
  )
)

# ONE NUMBER. 200 characters is generous for a state -- "a Delaware corporation" attaches at a median
# of five -- and about right for a city behind an address. The alternatives are reported in Selection
# as evidence rather than offered as a choice, and the registered-address check is what says whether
# the number is too wide.
.lP$Params$Spec <- geo_spec(
  .reach = 200   # furthest a party may be and still claim a place
)

fs::dir_create(fs::path_dir(.lP$Output$Parties))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference cost a render: a mistyped Landing path
# read FALSE in this very table while the document went on to print a whole precision measure as
# NA%, with confident prose beside it saying what the number meant. ent_anchor_keys() takes the
# address path as OPTIONAL and skips it where the file is absent, which is right for a document that
# does not need it and wrong for this one, which is the only place the addresses are used.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}.",
    "i" = "Every path here is required. Landing carries the registered addresses, and without it
           the precision check silently reports nothing rather than failing."
  ))
}
```

# Input

## The anchor, from EDGAR

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = .lP$Input$Landing,   # 01C: the registered address, for the precision check
  .quiet         = FALSE
)
```

The registered address is read here and nowhere else. It is the **only precision measure** in this
document, and it is a flag rather than a fill: using EDGAR to supply a missing location would make the
variable partly what the contract says and partly what EDGAR says, with nothing able to tell which.

## The gazetteer

```{r}
#| label: load-gazetteer

geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),      # the state and county per place
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)   # every state a city name exists in
)

tibble::tibble(
  Item = c("Rows in the lookup", "Distinct city names", "City names in more than one state"),
  N    = c(nrow(geo_once$Lookup),
           dplyr::n_distinct(geo_once$Cand$GeoKey),
           sum(dplyr::count(geo_once$Cand, .data$GeoKey)$n > 1L))
) |>
  tbl_say(.title = "What the gazetteer supplies")
```

**The candidate list is what the ambiguous-city rule runs on.** `geo_lookup()` nulls the parents of a
name existing in several states; `geo_candidates()` keeps them, so a city can be resolved by asking
which of *its own* states the contract names rather than which state is nearest.

## The parties

```{r}
#| label: load-parties

tab_party    <- arrow::read_parquet(.lP$Input$Party)
tab_mentions <- arrow::read_parquet(.lP$Input$Mentions)

tab_party |>
  dplyr::summarise(Rows = dplyr::n(), Docs = dplyr::n_distinct(.data$DocID), .by = PartyRole) |>
  dplyr::arrange(plot_factor(.data$PartyRole, .key = "PartyRole")) |>
  tbl_say(.title = "What 04B1 released")

tibble::tibble(
  Item = c("Parties", "Mentions of them", "Mentions that are not the first"),
  N    = c(sum(tab_party$PartyRole != "none"), nrow(tab_mentions), sum(!tab_mentions$IsFirst))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_mentions), 1L))) |>
  tbl_say(.title = "And where else each of them was named")
```

**The attachment runs over mentions, not parties.** 04B1's release carries a party at the offsets of
its first mention, which is the right shape for a file about parties and the wrong one for anything
measuring what sits beside them. The last row above is what a first-mention table cannot see, and a
signature block -- where a party is named *with* an address -- is almost always among them.

## The places, and the governing-law clauses

```{r}
#| label: load-spans

tab_lens <- tab_party |>
  dplyr::distinct(.data$DocID) |>
  dplyr::left_join(
    dplyr::transmute(tab_keys, DocID, DocLen = as.integer(.data$nChars)),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::filter(!is.na(.data$DocLen), .data$DocLen > 0L)

tab_spans <- ent_load_entity(
  .dir_store = .lP$Input$Store,
  .family    = .lP$Params$Family,
  .entity    = "GPE",
  .lens      = tab_lens,
  .extras    = ent_extras(.lP$Params$Family, "GPE"),  # declared in _NER.R, not typed here
  .quiet     = FALSE
)

tab_law <- ent_load_entity(
  .dir_store = .lP$Input$Store,
  .family    = .lP$Params$Family,
  .entity    = "LAW",                                 # lawregex: the clause as a span
  .lens      = tab_lens,
  .extras    = ent_extras(.lP$Params$Family, "LAW"),  # none; the cue is in the core LabelRaw
  .quiet     = FALSE
)
```

**The length comes from the register rather than from the text.** `nChars` was measured against
`stri_length()` on 31,981 documents and agreed exactly on every one, and recomputing it here would
open every contract to reproduce a stored column.

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- geo_apply(
  .spans    = tab_spans,       # every matcon place, unresolved
  .law      = tab_law,         # the governing-law clauses, as spans
  .party    = tab_party,       # 04B1's parties: the role, the name, the released row
  .mentions = tab_mentions,    # where each of them was named, every time
  .keys     = tab_keys,        # runs from the key side, so a document with no clause survives
  .geo      = geo_once,        # the lookup and the candidate list
  .spec     = .lP$Params$Spec  # the one reach
)

tab_places  <- res_base$Places   # every place, resolved to a level and a country
tab_inside  <- res_base$Inside   # the places sitting inside a governing-law clause
tab_law_doc <- res_base$Law      # one row per document: the jurisdiction
tab_roles   <- res_base$Roles    # every place, with the party it attached to
tab_geo     <- res_base$Party    # one row per party, with its geography
tab_release <- res_base$Release  # the file
```

## What the gazetteer resolved

```{r}
#| label: report-resolve

tab_resolve <- geo_table_resolve(.geo = tab_places)

geo_report_resolve(.tab = tab_resolve)
```

## How every city got its state

```{r}
#| label: report-city

tab_city <- geo_table_city(.geo = tab_places)

geo_report_city(.tab = tab_city)
```

## What the governing-law exclusion withheld

```{r}
#| label: report-exclude

tab_exclude <- geo_table_exclude(.places = tab_places, .inside = tab_inside)

geo_report_exclude(.tab = tab_exclude)
```

**Every one of those places was available to a party before.** The exclusion is an anti-join on the
same offsets the jurisdiction is found by, so a place cannot be withheld from attachment and missing
from the governing-law variable at the same time.

## How far a place sits from its party

```{r}
#| label: report-dist

tab_dist <- geo_dist_profile(.roles = tab_roles)

geo_report_dist(.tab = tab_dist)
```

# Selection

## What the other reaches would have attached

```{r}
#| label: sweep-reach

tab_sweep <- geo_sweep_reach(
  .geo      = dplyr::anti_join(tab_places, tab_inside, by = dplyr::join_by(DocID, Start)),
  .party    = tab_party,
  .mentions = tab_mentions,
  .keys     = tab_keys,
  .reaches  = .lP$Params$Reaches,  # the candidates, the released value among them
  .quiet    = FALSE
)

geo_report_sweep(.tab = tab_sweep)
```

**Coverage rises with the reach and precision is what stops it.** A wider window attaches more places
to every party; whether the extra ones are right is a different question, and the registered-address
check is the only thing in this document that can answer it.

# Results

## What geography each role got

```{r}
#| label: table-cover

tab_cover <- geo_table_cover(.tab = tab_release)

geo_report_cover(.tab = tab_cover)
```

## What reaching past the first mention bought

```{r}
#| label: table-gain

tab_gain <- geo_table_gain(.tab = tab_geo)

geo_report_gain(.tab = tab_gain)
```

**The change can only add.** The roll-up prefers a party's earliest mention, so a party that already
had a state under the previous release keeps exactly that state -- `PctLater` is coverage that was
simply unreachable, not coverage taken from somewhere else.

## The governing law

```{r}
#| label: table-law

tab_law_tab <- geo_table_law(.law = tab_law_doc)
tab_law_top <- geo_table_law_top(.law = tab_law_doc, .n = .lP$Params$LawTopN)

geo_report_law(.tab = tab_law_tab, .top = tab_law_top)
```

# Validation

## Every party 04B1 released still has its row

```{r}
#| label: validate-rows

# THE IDENTITY THIS DOCUMENT CANNOT VIOLATE. Geography is added to rows rather than filtered onto
# them, so the release must carry exactly the rows 04B1 wrote -- no more and no fewer. A shortfall is
# a join that dropped parties; an excess is one that duplicated them.
tibble::tibble(
  Item = c("Rows 04B1 released",
           "Rows this document releases",
           "Documents in both",
           "Parties carrying a place they were not attached to"),
  N    = c(nrow(tab_party),
           nrow(tab_release),
           dplyr::n_distinct(intersect(tab_party$DocID, tab_release$DocID)),
           sum(tab_release$NGeoNear == 0L &
                 (!is.na(tab_release$GeoState) | !is.na(tab_release$GeoCity))))
) |>
  tbl_say(.title = "The release is 04B1's rows, widened")

cli::cli_alert_info(
  "The first two rows must be equal and the fourth must be ZERO: a party with nothing attached \\
   cannot carry a place, so a nonzero fourth row is a join fanning out rather than a rule."
)
```

## No governing-law place reached a party

```{r}
#| label: validate-exclusion

# THE EXCLUSION, CHECKED RATHER THAN ASSUMED. Every place inside a clause should be absent from the
# attachment table entirely, so the intersection of the two offset sets must be empty.
tibble::tibble(
  Item = c("Places inside a governing-law clause",
           "Of those, still present in the attachment table",
           "Of those, attached to a party"),
  N    = c(nrow(tab_inside),
           sum(paste(tab_inside$DocID, tab_inside$Start) %in%
                 paste(tab_roles$DocID, tab_roles$Start)),
           sum(paste(tab_inside$DocID, tab_inside$Start) %in%
                 paste(tab_roles$DocID[tab_roles$Attached], tab_roles$Start[tab_roles$Attached])))
) |>
  tbl_say(.title = "The exclusion holds")

cli::cli_alert_info(
  "The second and third rows must both be ZERO. A nonzero third row means a jurisdiction is sitting \\
   in some party's state column, which is the exact defect this rule exists to remove."
)
```

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Parties)

geo_report_release(.tab = tab_release)
```

## The released file, read

```{r}
#| label: read-release

tab_sample <- geo_release_sample(
  .tab  = tab_release,
  .n    = .lP$Params$ReadDocs,   # drawn from contracts that placed something
  .seed = .lP$Params$Seed
)

geo_report_release_sample(.tab = tab_sample)
```

**This is the file.** Read one contract's rows top to bottom: the registrant with the place its
preamble qualified it with, the counterparties beside it, and the governing law reported once above
because it belongs to the contract rather than to any of them.

## What every column means

```{r}
#| label: report-dictionary

tab_dict <- geo_dictionary_parties(.tab = tab_release)

geo_report_dictionary(.tab = tab_dict)
```

**Every contract-level variable is one `summarise`, as it was in 04B1:**

```r
tab_release |>
  dplyr::summarise(
    GoverningLaw    = dplyr::first(.data$GoverningLaw),
    RegistrantState = .data$GeoState[.data$PartyRole == "registrant"][1L],
    NCounterparties = sum(.data$PartyRole == "counterparty"),
    NPlaced         = sum(!is.na(.data$GeoState)),
    .by = c(DocID, Class, AmendType)
  )
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

geo_report_headline(.release = tab_release, .law = tab_law_doc, .inside = tab_inside)
```

## Registrant against counterparty

```{r}
#| label: fig-cover
#| fig-cap: "The share of parties given a state, a city and a country, by the role 04B1 assigned
#|   them. The registrant should lead every other role, because the preamble qualifies it first and
#|   at length."
#| fig-height: 3.4

geo_plot_cover(.tab = tab_cover)
```

## Where the ambiguous cities landed

```{r}
#| label: fig-city
#| fig-cap: "How each city mention was placed in a state. Unresolved is an ambiguous name whose
#|   states the contract never mentions, left empty rather than guessed."
#| fig-height: 2.4

geo_plot_city(.tab = tab_city)
```

## Coverage against precision, by reach

```{r}
#| label: fig-sweep
#| fig-cap: "What each candidate reach attaches, and how often the registrant's place then appears
#|   in the address EDGAR records. Coverage rises with the reach; agreement is what says whether the
#|   extra places are right."
#| fig-height: 3.4

geo_plot_sweep(.tab = tab_sweep)
```

## The commonest jurisdictions

```{r}
#| label: fig-law
#| fig-cap: "The jurisdictions contracts name most often, among those naming one at all. Read
#|   against the exclusion: every one of these would otherwise have been some party's address."
#| fig-height: !expr plot_height(.n_rows = nrow(tab_law_top))

geo_plot_law(.tab = tab_law_top)
```

# Next

04B3 turns parsed dates and stated terms into a contract duration. It reads the same stores and the
same anchor, and it is the last of the rules that measures anything from where a party was found.
