---
title: "Entity Rules -- When a Contract Starts, Ends and How Long it Runs (04B3)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the label spine; 04A owns the sample and the stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B3-Rules-DATE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B3-Rules-DATE.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document decides, for every contract in the labelled sample, when it was signed, when it ends,
and how long it runs.

## The number that made it necessary

Table 3 Panel B reports contract duration with a mean of **2.38** years, a median of **0.40** and a
standard deviation of **40.78**, under a stated cap of **30** years. A variable supported on
`[0, 30]` cannot have a standard deviation above 15 -- the maximum, reached by a 50/50 split on the
endpoints. So the cap was not applied to what was tabulated, or something was in the wrong unit.
Referee 1 saw the symptom and asked whether there were errors in identifying dates affecting the
right tail.

**The published definition is the naive baseline here**, not something this document replaces sight
unseen: take the farthest future date the contract mentions and call the distance to it the duration.
It is a row in the sweep, a column in the released file, and the thing every table is read against.

## What comes out

**One file: `contracts_date.parquet`, one row per contract.** A duration belongs to a contract and to
no party in it, so it is its own file rather than four more columns on 04B2's. That is not the
two-file problem 04B1 removed -- the counts in that second file were *derived* from the first and
could contradict it, while a duration is an independent measurement that nothing else computes.

## The rule, in one paragraph

The **start** is the latest date at or before the filing, or the filing date itself where no date
precedes it. The **end** comes from the first of four rungs that answers: a stated term, an
open-ended clause (which leaves the duration *missing*, because a perpetual agreement has no
duration), the farthest future date carrying a termination cue, or the farthest future date of any
kind. `DurationSource` says which, because they are four kinds of evidence rather than four attempts
at one thing.

## The longest stated period is the term

A contract states several periods and only one of them is its duration:

```
3.1  Buyer shall cure any breach within a period of thirty (30) days.
5.2  Seller warrants the Products for a period of twelve (12) months.
9.1  This Agreement shall continue for a period of five (5) years.
```

All three are real contract terms; only 9.1 is how long the contract lasts. **All three match the
same pattern**, because the drafter wrote *"period of N units"* three times -- so no filter on
pattern names can separate them, and taking the first by position releases the *cure period* as the
duration.

**Taking the longest needs no threshold and cannot delete a contract's only term.** A minimum length
would also work on that example, and it has two costs the longest does not: a number to defend, and
the deletion of a genuine three-month agreement's only stated term. A selection cannot delete
anything.

**What it costs is stated rather than discovered.** It is wrong exactly where a contract states a
longer *non-duration* period than its own duration -- a one-year agreement with a ten-year
confidentiality survival clause. Survival clauses are the real exposure, because they are common and
deliberately long. The trade is accepted because a cure period is far commoner, and the comparison
against position-first is reported and read back in context rather than asserted.

## One engine, and it settles the right-tail question by construction

matcon's patterns **require a year in the text** -- four digits in nine of them, two in `SlashShort`
-- so there is no partial match to complete and no clock to complete it from. LexNLP's grammar has no
such constraint, and `dateregex.py` measured the consequence on this sample: of its spans carrying no
written year, **76% resolve to the future at a median of 11.6 years out**, and **80.8% of all dates
more than fifteen years out are year-less**.

Running matcon alone is therefore not a preference between two producers. It is the guard against the
exact failure the referee asked about, and it retires a dial with it: `RequireYear` existed to drop
spans whose year the parser invented, which is a LexNLP failure mode and cannot happen here.

## The cue is a column now, and this was the last text read in the family

`dte_describe()` used to open 04A's canonical text and cut 120 characters before every date to test
for a termination cue. Every matcon span now carries `CueBefore` -- 160 raw characters, stored at
extraction where the document and the offsets were already in one scope -- so the test is a column
read.

**That matters beyond this file.** It was the last of three rules that opened a document, and with it
gone **no rule in the 04B family touches contract text at all.** 04D's `Cues` dial existed to switch
those reads off at corpus scale, and switching them off is what made the governing-law columns vanish
from the release. There is nothing left for it to gate.

## The cap drops, it does not winsorise

A duration of exactly thirty years that is not one is worse than a missing value, and
`DurationDropped` says which of the two reasons applied.

## How results are reported

Console tables throughout, four figures in `# Overview`, and two reading blocks where a count cannot
settle the question: the contracts where the two term rules disagree, and whole contracts as the file
holds them.

## Where things are written

**One file**, one row per contract.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04A's sample stores, ONE PER FAMILY. The directory is the argument and the family is the
    # filename.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE ANCHOR. 03A's prepared sample supplies the labels, 02B's register the filing date --
    # which every date in this document is measured against.
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Contracts = utils_file_path(.dir_main, "Output", "contracts_date.parquet")
  ),
  Params = list(
    Family   = "matcon",  # the only family whose patterns require a written year
    CueWin   = 120L,      # characters of the stored cue window this rule reads
    ReadDocs = 8L,        # contracts read whole from the released file
    ReadTerm = 12L,       # disagreements between the two term rules, read in context
    Seed     = 42L        # fixed, so the same contracts are read on every render
  )
)

# TWO DIALS AND A CAP. Start and End are the rule; the cap is the only number, and it drops rather
# than winsorises.
.lP$Params$Spec <- dte_spec(
  .start     = "latest",  # the latest date at or before the filing
  .end       = "term",    # the full cascade: term, open, cue, farthest future date
  .cap_years = 30         # dropped above this, not winsorised to it
)

# EVERY DEFINITION SIDE BY SIDE, and the FIRST ROW IS THE PUBLISHED ONE. The naive baseline is not a
# separate computation: "filed / any / uncapped" is Table 3's definition exactly, and each later row
# differs from its neighbour in one thing.
.lP$Params$Specs <- list(
  dte_spec(.start = "filed",  .end = "any",  .cap_years = Inf, .label = "published (naive)"),
  dte_spec(.start = "filed",  .end = "any",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "any",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "cue",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .cap_years = Inf)
)

fs::dir_create(fs::path_dir(.lP$Output$Contracts))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before: a mistyped
# path read FALSE in this very table while the document went on to print a measure as NA with
# confident prose beside it saying what the number meant.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}.",
    "i" = "Every path here is required."
  ))
}
```

# Input

## The anchor, from EDGAR

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- tab_keys |>
  dplyr::transmute(DocID, DocLen = as.integer(.data$nChars)) |>
  dplyr::filter(!is.na(.data$DocLen), .data$DocLen > 0L)
```

**`DateFiled` is the anchor every date in this document is measured against**, and it is EDGAR's
record rather than anything the contract wrote. That is deliberate for the start -- a contract signed
before it was filed is the normal case, so the latest pre-filing date is the signing date wherever it
sits -- and it is a fallback that has to be visible: where no date precedes the filing, `StartSource`
records that the filing date itself was used.

## The dates, and the stated terms

```{r}
#| label: load-spans

tab_dates <- dte_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,   # matcon: every pattern requires a year in the text
  .quiet     = FALSE
)

tab_terms <- dte_load_terms(
  .dir_store = .lP$Input$Store,     # dateregex emits TERM from the same pass that produces DATE
  .lens      = tab_lens,
  .quiet     = FALSE
)

dte_report_input(.dates = tab_dates, .terms = tab_terms, .keys = tab_keys)
```

# Construction

## The cue, read from a column

```{r}
#| label: describe-dates

tab_desc <- dte_describe(
  .dates = dplyr::filter(tab_dates, .data$Parsed),
  .keys  = tab_keys,               # supplies DateFiled, so every date gets a gap
  .win   = .lP$Params$CueWin       # characters of the stored window this rule reads
)
```

**This is the last text read in the 04B family, and it is gone.** The cue used to be tested by
opening 04A's canonical text and cutting 120 characters before every date. `CueBefore` carries 160
raw characters stored at extraction, and the window is narrowed here rather than there -- so
refining the cue list never means re-extracting.

## Applying the rule

```{r}
#| label: apply-rule

res_base <- dte_apply(
  .dates = tab_desc,
  .terms = tab_terms,
  .keys  = tab_keys,               # runs from the key side, so a document with no date survives
  .spec  = .lP$Params$Spec
)

tab_dur     <- res_base$Duration   # one row per contract, every intermediate carried
tab_release <- res_base$Release    # the file
```

## What the stated terms look like

```{r}
#| label: report-terms

tab_term_tab <- dte_table_terms(.terms = tab_terms)
tab_term_cmp <- dte_term_compare(.terms = tab_terms)

dte_report_terms(.tab = tab_term_tab, .cmp = tab_term_cmp)
```

## How often each termination cue fires

```{r}
#| label: report-cues

tab_cues <- dte_cue_hits(.dates = tab_desc)

dte_report_cues(.tab = tab_cues)
```

# Selection

## Every definition side by side

```{r}
#| label: sweep-specs

tab_sweep <- dte_sweep(
  .dates = tab_desc,
  .terms = tab_terms,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,       # the published definition first, then one change at a time
  .quiet = FALSE
)

dte_report_sweep(.tab = tab_sweep)
```

**`SdOverCap` is the diagnostic.** On non-negative support under a correctly applied cap the standard
deviation cannot exceed half the cap. Table 3 reports 40.78 against a cap of 30 -- a ratio of 1.36,
which no distribution on `[0, 30]` can produce. Any row above 0.5 means the cap did not reach what is
being summarised.

# Results

## Which rung supplied the end

```{r}
#| label: table-source

tab_source <- dte_table_source(.dur = tab_dur)

dte_report_source(.tab = tab_source)
```

## The rule against the naive duration

```{r}
#| label: table-naive

tab_naive <- dte_table_naive(.dur = tab_dur)

dte_report_naive(.tab = tab_naive)
```

**This is the table the document exists to produce.** `Naive` is the farthest future date the
contract mentions, which is the definition Table 3 was built with; `Rule` is the cascade. Read the two
standard deviations against each other -- that is the referee's question in one comparison.

## What is missing, and why

```{r}
#| label: table-missing

tab_drop  <- dte_table_dropped(.dur = tab_dur)
tab_start <- dte_table_start(.dur = tab_dur)

dte_report_missing(.drop = tab_drop, .start = tab_start)
```

# Validation

## Three identities the durations cannot violate

```{r}
#| label: validate-durations

# EVERY CONTRACT GETS EXACTLY ONE ROW, a duration is never negative once it has survived the drop,
# and an open-ended contract never carries one. The third is the easiest to break: it is the only
# rung that produces a missing value on purpose.
tibble::tibble(
  Item = c("Documents in the sample",
           "Rows in the released file",
           "Reported durations that are negative",
           "Open-ended contracts carrying a duration",
           "Durations above the cap"),
  N    = c(nrow(tab_keys),
           nrow(tab_release),
           sum(dplyr::coalesce(tab_release$DurationYears, 0) < 0),
           sum(tab_release$DurationSource == "open" & !is.na(tab_release$DurationYears)),
           sum(dplyr::coalesce(tab_release$DurationYears, 0) > .lP$Params$Spec$CapYears))
) |>
  tbl_say(.title = "Three identities the durations cannot violate")

cli::cli_alert_info(
  "The first two rows must be equal. The last three must all be ZERO: a negative duration survived \\
   a filter that exists to remove it, an open-ended contract carrying a duration means the rung \\
   below overwrote the missing value, and a duration above the cap means the cap was applied to \\
   something other than what is reported."
)
```

# Robustness

## Where the longest term is not the first one written

```{r}
#| label: read-terms

tab_read_terms <- dte_read_terms(
  .terms = tab_terms,
  .n     = .lP$Params$ReadTerm,
  .seed  = .lP$Params$Seed
)

dte_report_read_terms(.tab = tab_read_terms)
```

**No count can replace this block.** Where the two rules disagree, the longest is right if it is the
contract's duration and wrong if it is a survival clause -- and only the span says which. If survival
clauses dominate, the answer is a cue on the span rather than a different threshold.

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Contracts)

dte_report_release(.tab = tab_release)
```

## The released file, read

```{r}
#| label: read-release

tab_sample <- dte_release_sample(
  .tab  = tab_release,
  .n    = .lP$Params$ReadDocs,   # two contracts from each rung, drawn deliberately
  .seed = .lP$Params$Seed
)

dte_report_release_sample(.tab = tab_sample)
```

**This is the file.** Read `DurationYears` against `NaiveYears` row by row: where the rung is `term`
the difference is a stated duration replacing a maximum over unrelated dates, and where the rung is
`maxdate` they are equal by construction.

## What every column means

```{r}
#| label: report-dictionary

tab_dict <- dte_dictionary(.tab = tab_release)

dte_report_dictionary(.tab = tab_dict)
```

**`DurationSource` is what makes the rest usable.** Filtering it to `term` and `open` keeps only what
the contract stated about itself; keeping `maxdate` as well reproduces the published definition.

# Overview

## The rule in one table

```{r}
#| label: report-headline

dte_report_headline(.dur = tab_dur, .release = tab_release)
```

## Where each contract's end came from

```{r}
#| label: fig-source
#| fig-cap: "Which rung supplied each contract's end, by type. The first two categories are what the
#|   contract stated about itself; the last is a maximum over dates it mentions for reasons it never
#|   states."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_dur$Class))

dte_plot_source(.dur = tab_dur)
```

## Duration by contract type

```{r}
#| label: fig-naive
#| fig-cap: "Median duration by contract type, as the cascade measures it and as the published
#|   farthest-future-date definition would. Medians rather than means, because the naive definition's
#|   right tail is the thing under examination."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_naive$Class))

dte_plot_naive(.tab = tab_naive)
```

## How the four rungs are distributed

```{r}
#| label: fig-spread
#| fig-cap: "Duration by the rung that supplied it. A stated term should be tight and a maximum over
#|   unrelated dates should be wide, and the difference between those two spreads is the referee's
#|   question drawn."
#| fig-height: 3.4

dte_plot_spread(.dur = tab_dur)
```

## Which cues actually mark a termination

```{r}
#| label: fig-cues
#| fig-cap: "The share of all future dates each cue sits beside. A high bar means the term is marking
#|   dates rather than terminations, which is the suspicion hanging over THROUGH and UNTIL."
#| fig-height: !expr plot_height(.n_rows = nrow(tab_cues))

dte_plot_cues(.tab = tab_cues)
```

# Next

04B4 turns parsed amounts into document-level money variables, and 04B5 counts what was withheld. Both
read the same stores and the same anchor, and neither opens a contract -- this document was the last
that did.
