---
title: "Rules -- When a Contract Runs (04B3)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- _Entity.R and this document's own file do.
purrr::walk(
  .x = c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  .f = \(.s) source(here::here("1_code", "_Commons", paste0(.s, ".R")), encoding = "UTF-8")
)

.name_script <- "04B3-Rules-DATE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

A contract states dates and it states periods. This turns them into a start, an end and a duration.

## The rule, in one start and four rungs

**Start** is the latest date at or before the filing, or the filing date where none precedes it.

**End**, in order: a **stated term** -- the longest period the contract names | an **open-ended
clause**, which leaves the duration *missing* because a perpetual agreement has no duration | the
farthest **cued** future date | the farthest future date **of any kind**.

`DurationSource` distinguishes all four. The last rung alone is the published definition, and it is
reproducible from the file as `NaiveYears`.

**The cap drops, it does not winsorise.** A duration of exactly thirty years that is not one is worse
than a missing value, and `DurationDropped` records why each one went.

## Two long files, and no per-contract table

`date_spans.parquet` is one row per date span, parsed or not. `term_spans.parquet` is one row per
stated period. `dte_collapse()` runs the cascade over them; this document scores it, reports it and
checks its shape, and the export calls it.

Three things stop being stored and become queries: `DurationSource` is which rung the two files
support, `NaiveYears` is the last rung alone, and **the thirty-year cap is a filter rather than a
decision baked into a release**. That last one is the point. A published standard deviation of 40.78
against a stated cap of 30 is impossible on `[0, 30]`, and with the cap as a query a reader computes
the distribution at any cap, or none, from the file.

## What is released and not acted on

A contract states **4.66 periods on average**, and the longest is not always the term: **7.0% of
released durations come from a cure or notice window of thirty days** rather than from the life of
the agreement. Two candidate fixes were measured and both made it worse -- excluding those kinds
swapped thirty days for a shorter period on half the affected contracts.

So the rule is unchanged and `PeriodKind` ships as a column. It has good precision and poor recall:
where it fires the medians are exactly right, and two thirds of periods match nothing. Anyone
excluding remedy deadlines writes one filter over the term file.

## How results are reported

Console tables throughout, and the same sorting rule the rest of 04B uses: **Input** describes the
data, **Construction** walks the rule's steps, **Selection** justifies the numbers, **Results**
reports the output, **Validation** proves identities, **Robustness** reads examples. Every figure is
in Overview.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Dates = utils_file_path(.dir_main, "Output", "date_spans.parquet"),
    Terms = utils_file_path(.dir_main, "Output", "term_spans.parquet")
  ),
  Params = list(
    Family   = "matcon",  # every pattern requires a year IN THE TEXT; LexNLP's do not
    CueWin   = 120L,      # characters of the stored 160 this rule narrows to
    ReadDocs = 8L,        # documents read whole from the collapse
    ReadTerm = 12L,       # documents whose competing periods are read back
    Seed     = 42L
  )
)

# TWO DIALS AND A CAP. Start and End are the rule; the cap is the only number, and it drops rather
# than winsorises.
.lP$Params$Spec <- dte_spec(
  .start     = "latest",  # the latest date at or before the filing
  .end       = "term",    # the full four-rung cascade
  .cap_years = 30         # dropped above this, not winsorised
)

# EVERY DEFINITION SIDE BY SIDE, and the FIRST ROW IS THE PUBLISHED ONE. "filed / any / uncapped" is
# Table 3's definition exactly, and each later row differs from its neighbour in one thing.
.lP$Params$Specs <- list(
  dte_spec(.start = "filed",  .end = "any",  .cap_years = Inf, .label = "filed / any / uncapped"),
  dte_spec(.start = "filed",  .end = "any",  .cap_years = 30,  .label = "filed / any / capped"),
  dte_spec(.start = "latest", .end = "any",  .cap_years = 30,  .label = "latest / any / capped"),
  dte_spec(.start = "latest", .end = "cue",  .cap_years = 30,  .label = "latest / cue / capped"),
  .lP$Params$Spec
)

fs::dir_create(fs::path_dir(.lP$Output$Dates))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, fs::file_exists)
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

# Input

## The anchor, the dates and the periods

```{r}
#| label: load-spans

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_dates <- dte_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,  # matcon: every pattern requires a year in the text
  .quiet     = FALSE
)

tab_terms <- dte_load_terms(
  .dir_store = .lP$Input$Store,   # span grain now; the choosing happens in the collapse
  .lens      = tab_lens,
  .quiet     = FALSE
)
```

# Construction

## Describing every date

```{r}
#| label: describe-dates

tab_desc <- dte_describe(
  .dates = dplyr::filter(tab_dates, .data$Parsed),  # the cascade reads parsed dates only
  .keys  = tab_keys,                                # supplies DateFiled, so a gap is computable
  .win   = .lP$Params$CueWin                        # of the stored 160 characters, read the last 120
)

dte_report_input(.dates = tab_desc, .terms = tab_terms, .keys = tab_keys)
```

**The cue is a column read and it used to be a text read.** `CueBefore` carries 160 raw characters
stored at extraction, where the document and the offsets were already in one scope. The window is
narrowed here rather than at extraction, so refining the cue list never means re-extracting.

## Applying the rule

```{r}
#| label: apply-rule

res_base <- dte_apply(
  .dates = tab_desc,          # every parsed date, with its gap and its cue flag
  .terms = tab_terms,         # every stated period, at span grain
  .keys  = tab_keys,          # runs from the key side, so a document with no date still gets a row
  .spec  = .lP$Params$Spec    # the start, the cascade and the cap
)

tab_dates_rel <- res_base$Dates     # THE FILE: one row per date span, parsed or not
tab_terms_rel <- res_base$Terms     # THE FILE: one row per stated period
# CLASS IS JOINED FOR REPORTING AND NEVER STORED. It is 03A's label spine rather than a result of
# this rule, and repeating it across every date span of a contract would duplicate the spine without
# adding anything a join on DocID does not give.
tab_dur <- res_base$Duration |>                  # the collapse: written nowhere
  dplyr::left_join(
    dplyr::select(tab_keys, DocID, Class, AmendType),
    by = dplyr::join_by(DocID)
  )

tab_terms_doc <- dte_terms_collapse(.terms = tab_terms_rel)
```

## Which cue fires, and how often

```{r}
#| label: report-cues

tab_cues <- dte_cue_hits(.dates = tab_desc)

dte_report_cues(.tab = tab_cues)
```

**`THROUGH` is the entry under suspicion.** It is the top cue by volume and the highest on both share
of cued dates and share of future dates, which is the pattern of a common word rather than a cue. The
exposure is bounded by how often the cue rung fires at all -- and with `CueHit` in the released file,
testing a shorter list is a query rather than a re-run.

## What the stated periods actually are

```{r}
#| label: report-period

tab_period <- dte_table_period(.terms = tab_terms_rel)

dte_report_period(.tab = tab_period)
```

# Selection

## Every definition side by side

```{r}
#| label: sweep-specs

tab_sweep <- dte_sweep(
  .dates = tab_dates_rel,        # the released file, so each arm is scored on what ships
  .terms = tab_terms_rel,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,     # the published definition first, the released one last
  .quiet = FALSE
)

dte_report_sweep(.tab = tab_sweep)
```

**The first row is Table 3's definition and the last is this document's**, and each row differs from
its neighbour in exactly one thing. Read the standard deviation down the column: a duration capped at
thirty years cannot have one above fifteen.

# Results

## Which rung supplied the end

```{r}
#| label: table-source

dte_report_source(.tab = dte_table_source(.dur = tab_dur))
```

## The rule against the naive definition

```{r}
#| label: table-naive

tab_naive <- dte_table_naive(.dur = tab_dur)

dte_report_naive(.tab = tab_naive)
```

## Why a duration is missing

```{r}
#| label: table-dropped

dte_report_missing(
  .drop  = dte_table_dropped(.dur = tab_dur),
  .start = dte_table_start(.dur = tab_dur)
)
```

## The stated terms

```{r}
#| label: table-terms

dte_report_terms(
  .tab = dte_table_terms(.terms = tab_terms_doc),
  .cmp = dte_term_compare(.terms = tab_terms_doc)
)
```

# Validation

## Three identities the files cannot violate

```{r}
#| label: validate-counts

open_ <- dplyr::filter(tab_dur, .data$DurationSource == "open")
kept_ <- dplyr::filter(tab_dur, .data$DurationDropped == "kept")

max_ <- dplyr::filter(tab_dur, .data$DurationSource == "maxdate")

tibble::tibble(
  Item = c("Contracts in the collapse",
           "Where an open-ended contract carries no duration",
           "Where a kept duration is between zero and the cap",
           "Where the farthest-date rung equals the naive definition"),
  N    = c(nrow(tab_dur),
           sum(is.na(open_$DurationYears)),
           sum(kept_$DurationYears >= 0 & kept_$DurationYears <= .lP$Params$Spec$CapYears),
           sum(dplyr::near(max_$RawYears, max_$NaiveYears)))
) |>
  dplyr::mutate(
    Of    = c(nrow(tab_dur), nrow(open_), nrow(kept_), nrow(max_)),
    Share = tbl_pct(.data$N / pmax(.data$Of, 1L))
  ) |>
  tbl_say(.title = "Three identities the files cannot violate")

cli::cli_alert_info(
  "ROWS TWO TO FOUR MUST ALL READ 100%. An open-ended contract states that it HAS no length, so \\
   recording one would contradict the rung that found it. A kept duration outside the cap means the \\
   drop ran on the wrong column. And the last rung IS the naive definition, so where it fires the \\
   two must agree exactly -- anything else means the cascade and the baseline are reading different \\
   dates."
)

# NOT AN IDENTITY, AND IT WAS WRITTEN AS ONE. A stated term is computed from the START plus a period,
# so it is bounded by nothing the document wrote; the rule can therefore reach FURTHER than the
# farthest date the contract names. That is the term rung working rather than failing, and the count
# is the strongest single argument for having it.
over_ <- sum(dplyr::coalesce(tab_dur$DurationYears, 0) >
               dplyr::coalesce(tab_dur$NaiveYears, Inf))

cli::cli_alert_info(
  "ON {format(over_, big.mark = ',')} CONTRACTS ({tbl_pct(over_ / nrow(tab_dur))}) THE STATED TERM \\
   OUTLASTS EVERY DATE THE DOCUMENT WRITES. Those are contracts the naive definition would have \\
   given a duration ending before the agreement does, or no duration at all -- and reading a period \\
   the contract states about itself is the only way to reach them."
)
```

## Offsets index the canonical text

```{r}
#| label: validate-offsets

tab_verify <- ent_verify_span(
  .tab       = tab_dates_rel,
  .path_text = .lP$Input$Text,
  .col_start = "DateStart",
  .col_stop  = "DateStop",
  .col_span  = "DateText",
  .n         = 500L,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Date spans checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "The span and the two offsets are one row of the released file, so this compares a thing with \\
   itself and must be 100%. Anything below is an offset problem rather than a rule one."
)
```

# Robustness

## Contracts read, one per rung

```{r}
#| label: read-release

dte_report_release_sample(
  .tab = dte_release_sample(.tab = tab_dur, .n = .lP$Params$ReadDocs, .seed = .lP$Params$Seed)
)
```

## The competing periods, read

```{r}
#| label: read-terms

dte_report_read_terms(
  .tab = dte_read_terms(.terms = tab_terms_doc, .n = .lP$Params$ReadTerm,
                        .seed = .lP$Params$Seed)
)
```

# Deployment

## The two releases

```{r}
#| label: write-artifact

arrow::write_parquet(tab_dates_rel, .lP$Output$Dates)
arrow::write_parquet(tab_terms_rel, .lP$Output$Terms)

dte_report_release(.dates = tab_dates_rel, .terms = tab_terms_rel)
```

## What every column means

```{r}
#| label: report-dictionary

dte_report_dictionary(
  .tab   = dte_dictionary_dates(.tab = tab_dates_rel),
  .title = "date_spans.parquet"
)

dte_report_dictionary(
  .tab   = dte_dictionary_terms(.tab = tab_terms_rel),
  .title = "term_spans.parquet"
)
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

dte_report_headline(.dur = tab_dur, .dates = tab_dates_rel, .terms = tab_terms_rel)
```

## Which rung supplied the end

```{r}
#| label: fig-source
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_dur$Class))
#| fig-cap: "Where each contract's end came from, by contract type."

dte_plot_source(.dur = tab_dur)
```

## The rule against the naive definition

```{r}
#| label: fig-naive
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_naive$Class))
#| fig-cap: "Mean duration under the rule and under the published definition."

dte_plot_naive(.tab = tab_naive)
```

## The spread the cap is for

```{r}
#| label: fig-spread
#| fig-height: 3.4
#| fig-cap: "Duration under both definitions. The naive tail is what the cap removes."

dte_plot_spread(.dur = tab_dur)
```

## Which cue fires

```{r}
#| label: fig-cues
#| fig-height: 3.4
#| fig-cap: "Each termination cue, by how often it fires and on what share of future dates."

dte_plot_cues(.tab = tab_cues)
```

# Next

**04B4** reads the MONEY spans and needs nothing from this document. **04D** calls `dte_apply()` on
chunks of the corpus and writes the same two files at scale, and the **export** calls `dte_collapse()`
to turn the spans into one row per contract.
