---
title: "Entity Rules -- What a Contract Says It Is Worth (04B4)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the label spine; 04A owns the sample and the stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B4-Rules-MONEY"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B4-Rules-MONEY.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document turns parsed amounts into contract-level money variables.

## The least opinionated of the five, and it should be

There is no external fact to anchor an amount against and no taxonomy that says what a contract's
value is, so this document does not invent one. It reports what the extractor found, removes the two
things that are demonstrably not amounts anybody owes, and puts the numbers beside the contract type
so a reader can see whether the ordering makes sense.

## What comes out

**One file: `contracts_money.parquet`, one row per contract.** A contract's value belongs to the
contract and to no party in it. That is not the two-file problem 04B1 removed -- the counts in that
second file were *derived* from the first and could contradict it, while an amount is an independent
measurement nothing else computes.

| Level | Columns |
|:--|:--|
| Kept | `NAmounts`, `NAmountsUSD`, `NAmountsOther`, `MoneyMaxUSD`, `MoneySumUSD`, `NDistinctUSD` |
| Kept, other currencies | `MoneyMaxOther`, `MoneySumOther`, `NDistinctOther` |
| Unfiltered | `NAmountsRaw`, `NaiveMaxUSD`, `NaiveSumUSD`, `NaiveMaxOther`, `NaiveSumOther` |
| Removed | `NDroppedZero`, `NDroppedPar` |
| Withheld by the contract | `NWithheldUSD`, `NWithheldOther` |

## The rule is two filters and no number

**A zero is not an amount.** The store's two commonest money spans are `$ 0` and `$ 0.00`, which is
boilerplate about share denomination rather than anything a party owes.

**A figure beside par-value language is not an amount either.** `"par value $0.0001 per share"`,
`"stated value of $0.01"`, `"shares of $0.01 par value per share"` -- share denomination again, and
the commonest way a contract names a number that means nothing about its worth.

Neither is a judgement about whether a figure *matters*. Both are figures that are not amounts, and
the unfiltered count stays in the released file so a reader who disagrees can put them back.

## A withheld figure is a measurement, not a parse failure

`moneyregex` has three patterns for an amount the filer removed -- `symbol_redact` for `$[***]`,
`$**`, `$TBD` and `$____`; `symbol_redact_open` for an unclosed `$[ ***`; and `symbol_bare` for a
currency symbol immediately before `per`, as in *"a minimum market price of $ per share"*. All three
emit a **currency and a null amount**, deliberately, and the module says why:

> the amounts a filer withholds are systematically the material ones. Returning zero, or dropping the
> row, would erase exactly the observation that matters.

**This document was erasing it.** `Parsed` required both an amount and a currency and the aggregation
began by filtering on it, so every withheld figure was gone before the first `summarise` and the parse
table counted it as a failure to cast. It is not a failure. It is a contract naming a price and
refusing to say what it is.

**And it is sharper than anything 04B5 can offer.** `NRedactSymbol` counts `[***]` wherever it falls
-- in a schedule, a definition, a party's name. A `symbol_redact` span is `[***]` *standing where a
dollar figure belongs*, which is the measure referee 2's question about redaction intensity actually
points at.

They enter no arithmetic: a withheld figure carries no number, so a sum or a maximum including it
would have to invent one. They are counted as an event.

## One engine, and the measurement is decisive

**LexNLP's money grammar accepts one phrasing in six.** Measured on a fixture and confirmed on the
sample: of `$9,752,233.001`, `$2,500,000`, `US$5,000,000`, `5,000,000 dollars`, `USD 5,000,000` and
`Five Million Dollars`, only the last matches. At scale that is a coverage of **0.163** against
matcon's **0.712** on the corpus pass, and **0.260** against **0.830** on the sample.

**And it settles a claim that was in the prose.** An earlier version kept both families on *"of 2,541
mentions the two both found, zero share identical offsets, so neither replaces the other"*. That
sentence is true and its reading was wrong: zero agreement between a producer finding five phrasings
in six and one finding one is not two engines disagreeing, it is one engine largely **absent**.

## The par cue is a column now, and this was the last text read in the family

`mny_load()` used to open 04A's canonical text and cut sixty characters before every amount. Every
matcon span carries `CueBefore` and `CueAfter` -- 160 raw characters either side, stored at extraction
where the document and the offsets were already in one scope -- so the test is a column read.

**With 04B2 and 04B3 already moved, no rule in the 04B family opens a document.** 04D's `Cues` dial
existed to switch those three reads off at corpus scale, and switching them off is what made the
governing-law columns vanish from the release. There is nothing left for it to gate.

**And the window reads both sides, which it could not before.** The old roxygen promised *"characters
either side of an amount"* and the code cut a window *ending* at the span, so par language written
after the figure was structurally invisible: `"shares of $0.01 par value per share"` passed the filter
every time. `Test-MatCon-MONEY.R` pinned both halves of that, and its `doc08` check is written to
**flip** when a rule reads `CueAfter` -- which is how this change proves itself rather than being
asserted.

## Currencies are never pooled

A maximum across currencies is not a quantity. Currency is populated on 100% of matcon's rows, so the
split costs no coverage at all, and USD and non-USD sit in columns of one row rather than in two
tables nobody joins.

## The repetition ratio is why sum survives

A contract restating the same fifty million across five clauses sums to two hundred and fifty million,
and no filter can tell a restatement from a second obligation. So distinct amounts over total spans is
reported beside the sum: it says how much of a total is repetition, which is the caveat the sum needs
rather than an argument for dropping it.

**`MoneyMaxUSD` is the one unambiguous figure** -- the largest amount the contract names -- and it is
the column a reader wanting one number should take.

## Every table carries the unfiltered count

**Naive** is every parsed amount, both filters off: what a reader gets by summing what the extractor
emitted. It sits beside the rule in every table and in the released file, because the difference
between the two *is* what the filters did.

## How results are reported

Console tables throughout, four figures in `# Overview`, and one reading block: whole contracts as the
file holds them, drawn so that some are contracts where a filter bit.

## Where things are written

**One file**, one row per contract.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Contracts = utils_file_path(.dir_main, "Output", "contracts_money.parquet")
  ),
  Params = list(
    Family   = "matcon",  # the only family that finds more than one phrasing in six
    ReadDocs = 8L,        # contracts read whole from the released file
    Seed     = 42L        # fixed, so the same contracts are read on every render
  )
)

# TWO DIALS, AND THE SECOND IS THE ONE A READER COULD DISAGREE WITH. The window is a real parameter
# again: it used to sit in the specification while IsPar was computed once at load time, so a sweep
# over specifications changed the label and nothing else.
.lP$Params$Spec <- mny_spec(
  .filter  = "par",  # drops a zero, and a figure with par-value language beside it
  .cue_win = 60L     # characters read EITHER SIDE, out of the 160 the store holds
)

# THE UNFILTERED ROW IS FIRST, so what the rule removes is visible rather than asserted. The last two
# rows sweep the window, which the old specification could not: with IsPar computed at load time,
# every swept width named a number and changed none.
.lP$Params$Specs <- list(
  mny_spec(.filter = "none"),
  mny_spec(.filter = "zero"),
  mny_spec(.filter = "par",  .cue_win = 30L, .label = "drop zero and par / 30"),
  mny_spec(.filter = "par",  .cue_win = 60L, .label = "drop zero and par / 60"),
  mny_spec(.filter = "par",  .cue_win = 120L, .label = "drop zero and par / 120")
)

fs::dir_create(fs::path_dir(.lP$Output$Contracts))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}.",
    "i" = "Every path here is required."
  ))
}
```

# Input

## The anchor, from EDGAR

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- tab_keys |>
  dplyr::transmute(DocID, DocLen = as.integer(.data$nChars)) |>
  dplyr::filter(!is.na(.data$DocLen), .data$DocLen > 0L)
```

## The amounts

```{r}
#| label: load-spans

tab_money <- mny_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,   # matcon: five phrasings in six against LexNLP's one
  .quiet     = FALSE
)

tab_parse <- mny_table_parse(.money = tab_money)

mny_report_parse(.tab = tab_parse)
```

**No filter runs at load.** Both depend on a specification, so applying either here would put them
beyond the reach of the sweep -- which is exactly what the old version did with the par cue, leaving a
dial that appeared in every swept label and changed nothing.

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- mny_apply(
  .money = tab_money,
  .keys  = tab_keys,             # runs from the key side, so a contract naming nothing survives
  .spec  = .lP$Params$Spec
)

tab_marked  <- res_base$Marked   # every span, with the par cue read from both sides
tab_agg     <- res_base$Agg      # one row per contract and currency block
tab_release <- res_base$Release  # the file
```

## Where the par-value language sat

```{r}
#| label: report-par-side

tab_side <- mny_par_side(.marked = tab_marked)

mny_report_par_side(.tab = tab_side)
```

**`after` is what the previous rule could not see.** It cut a window ending at the span, so the phrase
written after the figure passed the filter every time. Reading the second side can only mark more and
never unmark, so this is a gain with no cost column.

## What the two filters removed

```{r}
#| label: report-dropped

tab_drop <- mny_table_dropped(.release = tab_release)

mny_report_dropped(.tab = tab_drop)
```

# Selection

## What each filter and window would have kept

```{r}
#| label: sweep-filters

tab_sweep <- mny_sweep(
  .money = tab_money,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,   # the unfiltered one first, then the window
  .quiet = FALSE
)

mny_report_sweep(.tab = tab_sweep)
```

**A window that changes no number is a finding rather than an artefact.** Under the old code the three
window rows were guaranteed identical, because `IsPar` was computed before any specification was
consulted. If they are identical now it is because the par language sits close to the figure, which is
worth knowing.

# Results

## The rule against the unfiltered count

```{r}
#| label: table-naive

tab_naive <- mny_table_naive(.release = tab_release)

mny_report_naive(.tab = tab_naive)
```

**Both `MedMax` columns are over the same contracts** -- the ones that kept a USD amount -- so
`MedMaxRule` can never exceed `MedMaxNaive`. Computing each over its own non-missing rows compares a
set including the contracts whose every figure was boilerplate with one excluding them, and reports
the filters as having *raised* contract value. `PctAllPar` is that excluded population: contracts that
named a USD figure and kept none of it.

## What each contract type is worth

```{r}
#| label: table-class

tab_class <- mny_table_class(.release = tab_release)

mny_report_class(.tab = tab_class)
```

**The ordering is the only external check this document has.** There is no ground truth for what a
contract is worth, but a credit agreement should out-value an employment agreement and a reader can
say whether it does.

# Validation

## Three identities the amounts cannot violate

```{r}
#| label: validate-amounts

# THE FILTERS ARE SUBTRACTIVE, so the kept count can never exceed the parsed count and the two drop
# counts must account for the whole difference. A maximum over a subset can never exceed a maximum
# over the whole, either.
tibble::tibble(
  Item = c("Documents in the sample",
           "Rows in the released file",
           "Where kept exceeds parsed",
           "Where the drops do not account for the difference",
           "Where the kept maximum exceeds the unfiltered one"),
  N    = c(nrow(tab_keys),
           nrow(tab_release),
           sum(tab_release$NAmounts > tab_release$NAmountsRaw),
           sum(tab_release$NAmountsRaw - tab_release$NAmounts !=
                 tab_release$NDroppedZero + tab_release$NDroppedPar),
           sum(dplyr::coalesce(tab_release$MoneyMaxUSD, 0) >
                 dplyr::coalesce(tab_release$NaiveMaxUSD, 0)))
) |>
  tbl_say(.title = "Three identities the amounts cannot violate")

cli::cli_alert_info(
  "The first two rows must be equal and the last three must all be ZERO. A filter that added amounts \\
   is not a filter; a difference the two drop counts cannot explain means a third thing is being \\
   removed silently; and a subset with a larger maximum than its superset is arithmetically \\
   impossible."
)
```

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Contracts)

mny_report_release(.tab = tab_release)
```

## The released file, read

```{r}
#| label: read-release

tab_sample <- mny_release_sample(
  .tab  = tab_release,
  .n    = .lP$Params$ReadDocs,   # some drawn from contracts where a filter bit
  .seed = .lP$Params$Seed
)

mny_report_release_sample(.tab = tab_sample)
```

## What every column means

```{r}
#| label: report-dictionary

tab_dict <- mny_dictionary(.tab = tab_release)

mny_report_dictionary(.tab = tab_dict)
```

**The naive columns are what make the rest arguable.** Keeping only what the rule kept would leave a
reader unable to check what it removed; publishing both means the filters are a choice the file
supports rather than one it hides.

# Overview

## The rule in one table

```{r}
#| label: report-headline

mny_report_headline(.release = tab_release, .side = tab_side)
```

## What the filters removed

```{r}
#| label: fig-naive
#| fig-cap: "Mean amounts per contract by type, before and after the two filters. The gap between
#|   each pair is the boilerplate: zeros and par values, which are figures rather than amounts."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_naive$Class))

mny_plot_naive(.tab = tab_naive)
```

## The largest amount, by type

```{r}
#| label: fig-max
#| fig-cap: "The largest USD amount each contract names, by type, on a log scale. This is the
#|   ordering check: there is no ground truth for a contract's value, but the ranking should be one a
#|   reader recognises."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_release$Class))

mny_plot_max(.release = tab_release)
```

## Which side the phrase was written on

```{r}
#| label: fig-par-side
#| fig-cap: "Which side of the figure the par-value phrase was written on. Everything but the first
#|   bar was invisible to the rule this replaces, which read only the characters before the amount."
#| fig-height: 2.4

mny_plot_par_side(.tab = tab_side)
```

## How much of a total is repetition

```{r}
#| label: fig-repeat
#| fig-cap: "Distinct amounts over amounts kept, per contract. A low ratio is a contract restating one
#|   figure many times, and it is the caveat the sum needs."
#| fig-height: 3.4

mny_plot_repeat(.release = tab_release)
```

# Next

04B5 counts what was withheld: the redaction markers a contract carries, and what they sit beside. It
is the last of the five, and like this one it opens no document.
