---
title: "Entity Rules -- Amounts (04B4)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B4-Rules-MONEY"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B4-Rules-MONEY.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document turns parsed amounts into document-level money variables.

## The least opinionated of the five, and it should be

There is no external fact to anchor an amount against and no taxonomy that says what a contract's
value is, so this document does not invent one. It reports what the extractors found, filters the two
things that are demonstrably not amounts, and puts the numbers beside the contract type so a reader
can see whether the ordering makes sense.

## One family is barely usable, and the document says so

Over the corpus LexNLP reaches **0.170** coverage against matcon's **0.710**, at 3.0 spans a document
against 14.6. 04A measured the sharper version on the sample: of **2,541** mentions the two families
*both* found, **zero** share identical offsets.

Zero out of thousands is not a disagreement. It is a systematic convention difference -- one family
is including something the other is not, on every single co-occurrence -- and the reading blocks
below are where that becomes visible rather than inferred. Both families are loaded, marked and
reported apart; the class tables are drawn from matcon and say so.

## Whole document, no region rule

Money is genuinely distributed: no engine exceeds a positional contrast of 1.85 between the ends and
the middle, against 22.6% and 25.2% in the two ends for organisations. There is nothing for a window
to separate.

## Currencies are never pooled

A maximum across currencies is not a quantity. Currency is populated on 100% of both families' rows
-- 42,937 of 42,937 -- so the split costs nothing.

## The repetition ratio is why sum survives

A contract restating the same fifty million across five clauses sums to two hundred and fifty
million, and no filter can tell a restatement from a second obligation. So distinct amounts over
total spans is reported beside the sum: it says how much of a class's total is repetition, which is
the caveat the sum needs rather than an argument for dropping it.

## Two filters, both on things that are not amounts

A zero, and a figure sitting next to "par value" -- the store's two commonest money spans are `$ 0`
and `$ 0.00`, which is boilerplate about share denomination rather than anything a party owes. Both
are swept, and the unfiltered row stays in every table.

## What is recomputed, and what is not

Everything, on every render. The context is read once, outside the filter, because it depends on no
specification.

## How results are reported

Console tables throughout, two figures in `# Overview`, every table per family and per currency.

## Where things are written

Two artifacts: the amount spans with their context flags, and one row per document, family and
currency block.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "Output", "roles_money.parquet"), # per amount span
    Doc   = utils_file_path(.dir_main, "Output", "money_doc.parquet")    # per document and family
  ),
  Params = list(
    Families   = c("lexnlp", "matcon"),
    ClassCombo = "matcon",     # the family the class tables and figures are drawn from
    CueWin     = 60L,          # characters read before a span for the par-value cue
    ReadN      = 10L,
    ReadCtx    = 200L,
    CheckN     = 500L,
    Seed       = 42L
  )
)

# The filter carried into the released artifacts.
.lP$Params$Spec <- mny_spec(
  .filter  = "par",              # drops a zero, and a figure preceded by par-value language
  .cue_win = .lP$Params$CueWin
)

# Every filter, unfiltered first, so what the rule removes is visible rather than asserted.
.lP$Params$Specs <- list(
  mny_spec(.filter = "none"),
  mny_spec(.filter = "zero"),
  mny_spec(.filter = "par")
)

fs::dir_create(fs::path_dir(.lP$Output$Spans))

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is computed")
```

# Input

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,
  .path_register = .lP$Input$Register,
  .path_landing  = NULL,             # no address is used here
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)
```

```{r}
#| label: load-money

tab_money <- mny_load(
  .dir_store = .lP$Input$Store,      # the directory; the family is the filename
  .lens      = tab_lens,
  .path_text = .lP$Input$Text,       # for the par-value context, read once
  .families  = .lP$Params$Families,
  .win       = .lP$Params$CueWin,
  .quiet     = FALSE
)

mny_report_parse(.money = tab_money)
```

**`Amount` arrives as text and is cast here.** `moneyregex` writes it as a string so a contract value
crosses the seam intact, and the store keeps the string because its schema is the parquet's rather
than a declaration. `as.numeric()` in the loader is the first arithmetic anything does with it, which
is where the cast belongs -- and a value that will not cast becomes `NA` and is counted by the parse
report rather than silently dropped.

# Construction

```{r}
#| label: aggregate-base
tab_agg <- mny_aggregate(
  .money = tab_money,
  .keys  = tab_keys,
  .spec  = .lP$Params$Spec   # the filter carried into the artifacts
)

tab_doc <- mny_doc_table(.agg = tab_agg, .keys = tab_keys)
```

# Selection

```{r}
#| label: sweep-filters
tab_sweep <- mny_sweep(
  .money = tab_money,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

mny_report_sweep(.tab = tab_sweep)
```

# Results

```{r}
#| label: report-class-usd
mny_report_class(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "USD"
)
```

```{r}
#| label: report-class-other
mny_report_class(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "non-USD"
)
```

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_money,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every parsed span carries a currency block",
    "No aggregated maximum is smaller than its median",
    "No aggregated sum is smaller than its maximum",
    "Distinct amounts never exceed spans",
    "Every document has a row per engine"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_money$Block[tab_money$Parsed])),
    sum(tab_agg$MoneyMax >= tab_agg$MoneyMed),
    sum(tab_agg$MoneySum >= tab_agg$MoneyMax),
    sum(tab_agg$NDistinct <= tab_agg$NSpans),
    nrow(tab_doc)
  ),
  Of = c(
    nrow(tab_check),
    sum(tab_money$Parsed),
    nrow(tab_agg),
    nrow(tab_agg),
    nrow(tab_agg),
    nrow(tab_keys) * dplyr::n_distinct(tab_agg$Combo)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

The middle three are arithmetic identities rather than tests of the extraction, and that is the
point: they fail only if an aggregation is wrong, which is the failure mode this document is most
exposed to and least able to see any other way.

# Robustness

```{r}
#| label: read-largest
# The largest figure in each of a few contracts, read to see whether it is an obligation, a cap, a
# share count that survived the parser or an authorised-capital line.
ent_read_spans(
  .tab       = tab_money |>
    dplyr::filter(.data$Parsed, !.data$IsZero, !.data$IsPar, .data$Block == "USD",
                  .data$Combo == .lP$Params$ClassCombo) |>
    dplyr::slice_max(.data$Amount, n = 400L, with_ties = FALSE),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "The largest amounts in the sample"
  )
```

```{r}
#| label: read-par
ent_read_spans(
  .tab       = dplyr::filter(tab_money, .data$IsPar),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "Figures preceded by par-value language -- what the filter removes"
  )
```

```{r}
#| label: read-nonusd
ent_read_spans(
  .tab       = dplyr::filter(tab_money, .data$Parsed, .data$Block == "non-USD"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "Non-USD amounts"
  )
```

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_money, -dplyr::any_of("Before")), .lP$Output$Spans)
arrow::write_parquet(tab_doc, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Amount spans with currency, zero and par-value flags",
               "Money variables per document and engine, USD and non-USD side by side"),
  Path     = c(.lP$Output$Spans, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B4")
```

The span file keeps the flags rather than the filtered set, so a consumer wanting the unfiltered
count has it and one wanting the filter can apply the same two columns this document did.

# Overview

```{r}
#| label: fig-max
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Median of the largest USD amount named in a contract, by type. The sanity test is the
#|   ordering rather than the level: credit agreements and mergers should sit at the top and
#|   compensation agreements at the bottom."
mny_plot_max(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "USD"
)
```

```{r}
#| label: fig-repeat
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of distinct amounts over total amount spans, for contracts
#|   naming at least three, by currency block. A contract near one names a different figure every
#|   time; one near zero repeats the same figure, and its sum is that figure counted again."
mny_plot_repeat(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo
)
```

```{r}
#| label: report-everything
mny_report_all(
  .money = tab_money,
  .sweep = tab_sweep,
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo
)
```

# Next

Two things are deliberately not attempted, and both would need a judgement this document has no
evidence for.

**No contract value.** Naming the largest figure "the contract value" would be a claim about which
obligation matters, and nothing in the data supports it. The maximum is released as the maximum.

**No scale correction.** A figure written "in thousands" in a table header is parsed at face value,
and no engine reads the header. That is a known understatement in an unknown share of documents; the
read blocks are where it would first become visible.
