---
title: "Rules -- What a Contract Is Worth (04B4)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- _Entity.R and this document's own file do.
purrr::walk(
  .x = c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  .f = \(.s) source(here::here("1_code", "_Commons", paste0(.s, ".R")), encoding = "UTF-8")
)

.name_script <- "04B4-Rules-MONEY"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

moneyregex proposes figures with a currency. Two of them are not amounts anybody owes, and a third is
a price the filer removed.

## Two filters and no number

**A zero is not an amount.** The two commonest money spans in this corpus are `$ 0` and `$ 0.00`.

**A figure beside par-value language is not an amount.** The cue is read on **both sides**, because a
drafter writes the phrase either way round: *par value $0.0001 per share* puts it before the figure
and *shares of $0.01 par value per share* puts it after. A rule reading only backwards makes the
second form structurally invisible.

**A withheld figure is a third outcome, not a parse failure.** Three moneyregex patterns match a
currency with no number. They are counted and never summed, because an arithmetic including them
would have to invent a value -- and `Withheld` keys on the *pattern name* rather than on a null
amount, so a price the filer removed and a figure this document could not read stay distinguishable.

## One long file, and no per-contract table

`money_spans.parquet` is one row per figure with **every filter as a column** rather than as a
filter. `mny_collapse()` aggregates it per contract and currency block; this document scores it,
reports it and checks its shape, and the export calls it.

Nothing is discarded, which is why this entity was the easiest to move: the filters were already
computed as flags and applied one step later, so the long file is what the chain already held.

The naive figures stop being stored, because each is the same aggregate with one filter switched off:

| Rung | Filter |
|:--|:--|
| every figure read | `Parsed` |
| after the zero filter | `Parsed & !IsZero` |
| the rule | `Parsed & !IsZero & !IsPar` |

## How results are reported

Console tables throughout, and the same sorting rule the rest of 04B uses: **Input** describes the
data, **Construction** walks the rule's steps, **Selection** justifies the numbers, **Results**
reports the output, **Validation** proves identities, **Robustness** reads examples. Every figure is
in Overview.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Money = utils_file_path(.dir_main, "Output", "money_spans.parquet")
  ),
  Params = list(
    Family   = "matcon",  # 04A: five phrasings in six against LexNLP's one
    ReadDocs = 8L,        # contracts read whole from the collapse
    Seed     = 42L
  )
)

# TWO DIALS. The filter is the rule; the window is the only number, and it is the one a reader could
# disagree with.
.lP$Params$Spec <- mny_spec(
  .filter  = "par",  # drops a zero, and a figure with par-value language beside it
  .cue_win = 60L     # characters read EITHER SIDE, out of the 160 the store holds
)

# EVERY DEFINITION SIDE BY SIDE, and the FIRST ROW IS THE UNFILTERED ONE. Each later row differs from
# its neighbour in one thing, so the sweep reads as a ladder rather than as a grid.
.lP$Params$Specs <- list(
  mny_spec(.filter = "none", .cue_win = 60L,  .label = "no filter"),
  mny_spec(.filter = "zero", .cue_win = 60L,  .label = "drop zero"),
  mny_spec(.filter = "par",  .cue_win = 30L,  .label = "drop zero and par, 30 chars"),
  .lP$Params$Spec,
  mny_spec(.filter = "par",  .cue_win = 120L, .label = "drop zero and par, 120 chars")
)

fs::dir_create(fs::path_dir(.lP$Output$Money))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, fs::file_exists)
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

# Input

## The anchor and the figures

```{r}
#| label: load-spans

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_money <- mny_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,
  .quiet     = FALSE
)
```

## What the extractor could read

```{r}
#| label: report-parse

mny_report_parse(.tab = mny_table_parse(.money = tab_money))
```

**Three outcomes, not two.** A parsed figure is one this document can compute with. A withheld figure
is one the contract removed. Everything else failed to cast, and calling the third by the same name
as the second is what made the withheld amounts disappear from an earlier version.

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- mny_apply(
  .money = tab_money,        # every matcon MONEY span, with its parse and its currency
  .keys  = tab_keys,         # runs from the key side, so a contract naming no figure gets a row
  .spec  = .lP$Params$Spec   # the filter and the window
)

tab_marked  <- res_base$Marked   # the spans with the par cue read on both sides
tab_release <- res_base$Release  # THE FILE: one row per figure, every filter a column

# CLASS IS JOINED FOR REPORTING AND NEVER STORED. It is 03A's label spine rather than a result of
# this rule, and repeating it across every figure of a contract would duplicate the spine without
# adding anything a join on DocID does not give.
tab_agg <- res_base$Agg |>                       # the collapse: written nowhere
  dplyr::left_join(
    dplyr::select(tab_keys, DocID, Class, AmendType),
    by = dplyr::join_by(DocID)
  )
```

## Which side the par cue sat on

```{r}
#| label: report-par-side

mny_report_par_side(.tab = mny_par_side(.marked = tab_marked))
```

**This is the evidence for reading both sides.** A rule cutting a window that ends at the span sees
only the `before` rows, so every `after` row is a figure it would have kept.

## What became of every figure

```{r}
#| label: report-outcome

mny_report_outcome(
  .tab     = mny_table_outcome(.release = tab_release),
  .release = tab_release
)
```

# Selection

## Every definition side by side

```{r}
#| label: sweep-specs

mny_report_sweep(
  .tab = mny_sweep(
    .money = tab_money,
    .keys  = tab_keys,
    .specs = .lP$Params$Specs,  # unfiltered first, the released one in the middle
    .quiet = FALSE
  )
)
```

**The window is a real parameter again.** It used to sit in the specification while `IsPar` was
computed once at load time, so a sweep over specifications changed the label and nothing else. Both
filters now run where the sweep can reach them.

# Results

## The naive ladder

```{r}
#| label: table-ladder

tab_ladder <- mny_table_ladder(.doc = tab_agg)

mny_report_ladder(.tab = tab_ladder)
```

## What the filters dropped

```{r}
#| label: table-dropped

mny_report_dropped(.tab = mny_table_dropped(.release = tab_agg))
```

## The amounts, by contract type

```{r}
#| label: table-class

mny_report_class(.tab = mny_table_class(.release = tab_agg))
```

# Validation

## Four identities the file cannot violate

```{r}
#| label: validate-counts

par_ <- dplyr::filter(tab_release, .data$IsPar)

tibble::tibble(
  Item = c("Figures in the file",
           "Where a par figure names the phrase that fired it",
           "Where the four outcomes cover every figure",
           "Where the rule kept no more than the naive rung"),
  N    = c(nrow(tab_release),
           sum(!is.na(par_$ParCue)),
           sum(tab_release$MoneyDrop %in% c("kept", "zero", "par", "unparsed")),
           sum(tab_agg$NAmounts <= tab_agg$NAmountsRaw))
) |>
  dplyr::mutate(
    Of    = c(nrow(tab_release), nrow(par_), nrow(tab_release), nrow(tab_agg)),
    Share = tbl_pct(.data$N / pmax(.data$Of, 1L))
  ) |>
  tbl_say(.title = "Four identities the file cannot violate")

cli::cli_alert_info(
  "ROWS TWO TO FOUR MUST ALL READ 100%. IsPar is derived from ParCue, so a par figure without a \\
   phrase means the two were computed separately and can disagree. The four outcomes are exhaustive \\
   by construction. And both filters only ever REMOVE figures, so the rule can never keep more than \\
   the rung above it -- a failure there is a filter that added rows, which is a join rather than a \\
   rule."
)
```

## Offsets index the canonical text

```{r}
#| label: validate-offsets

tab_verify <- ent_verify_span(
  .tab       = tab_release,
  .path_text = .lP$Input$Text,
  .col_start = "MoneyStart",
  .col_stop  = "MoneyStop",
  .col_span  = "MoneyText",
  .n         = 500L,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Figures checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "The span and the two offsets are one row of the released file, so this compares a thing with \\
   itself and must be 100%. Anything below is an offset problem rather than a rule one."
)
```

# Robustness

## Contracts read from the collapse

```{r}
#| label: read-release

mny_report_release_sample(
  .tab = mny_release_sample(.tab = tab_agg, .n = .lP$Params$ReadDocs, .seed = .lP$Params$Seed)
)
```

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Money)

mny_report_release(.release = tab_release, .agg = tab_agg)
```

## What every column means

```{r}
#| label: report-dictionary

mny_report_dictionary(
  .tab   = mny_dictionary_spans(.tab = tab_release),
  .title = "money_spans.parquet"
)
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

mny_report_headline(
  .release = tab_agg,                              # the collapse: one row per contract
  .side    = mny_par_side(.marked = tab_marked),
  .n_spans = nrow(tab_release)                     # the released FILE: one row per figure
)
```

## The rule against the naive definition

```{r}
#| label: fig-naive
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_ladder$Class))
#| fig-cap: "Figures per contract before and after the filters, by contract type."

mny_plot_naive(.tab = tab_ladder)
```

## The largest amount each contract names

```{r}
#| label: fig-max
#| fig-height: 3.4
#| fig-cap: "The distribution of the largest USD figure per contract, under both definitions."

mny_plot_max(.release = tab_agg)
```

## Which side the par cue sat on

```{r}
#| label: fig-par-side
#| fig-height: 2.4
#| fig-cap: "Par-value cues by the side of the figure they sat on. The after rows are what a backwards-only rule missed."

mny_plot_par_side(.tab = mny_par_side(.marked = tab_marked))
```

## How often an amount repeats

```{r}
#| label: fig-repeat
#| fig-height: 3.4
#| fig-cap: "Distinct USD amounts against total figures per contract, by contract type."

mny_plot_repeat(.release = tab_agg)
```

# Next

**04B5** reads the REDACT spans and needs nothing from this document. **04D** calls `mny_apply()` on
chunks of the corpus and writes the same file at scale, and the **export** calls `mny_collapse()` to
turn the figures into one row per contract.
