---
title: "Rules -- What a Contract Withheld (04B5)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- _Entity.R, 04B4 and this document's own file
# all do.
purrr::walk(
  .x = c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  .f = \(.s) source(here::here("1_code", "_Commons", paste0(.s, ".R")), encoding = "UTF-8")
)

# 04B4 OWNS THE MONEY LOADER, and this document reads its withheld spans rather than reimplementing
# the pattern list. mny_load() is the one definition of "a price the filer removed".
source(here::here("1_code", "04B4-Rules-MONEY.R"), encoding = "UTF-8")

.name_script <- "04B5-Rules-REDACT"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

redaction.py marks six kinds of place where text was removed. This counts them, matches them to what
they replaced, and applies **no filter at all**.

## Six classes and no rule

`RedactExplicit` | `RedactSymbol` | `RedactBlank` | `OmitExplicit` | `OmitSymbol` | `RedactBare`

There is nothing to choose here. The rule is a taxonomy, and the three candidate definitions are
three predicates over one column:

| Column | Predicate | What it is |
|:--|:--|:--|
| `NBracketed` | `Bracketed` | **the published definition** -- `06-Redactions.R` matched bracketed text |
| `NWithheld` | `Withheld` | redaction rather than omission; `[INTENTIONALLY OMITTED]` is a placeholder |
| `NRedact` | every row | everything the extractor marked |

Releasing the classes separately makes every candidate definition a **filter** rather than a decision
taken in the code.

## The marker, matched to what it replaced

moneyregex emits a currency whose number was removed -- `$[***]`, `$**` -- and redaction.py marks the
bracket inside it. The same redaction is therefore in two files, described from two sides: one knows
a **price** was withheld, the other knows a **marker** is there.

Overlapping their offsets gives each marker a `RedactedEntity`, and `NRedactMoney` becomes *how many
prices a contract withheld* -- which is a different variable from how many markers it carries.

**The test is interval overlap, not proximity, and the tolerance was measured before it was chosen.**
`$[***]` puts the marker five characters inside the money span; the observed gaps run from -9 to +6
with nothing beyond, so ten characters covers the cluster and reaches no further.

## And that match is a validation result

A withheld money span is **independent evidence that something was redacted**. So the markers sitting
on those spans are a population where the redaction is not in doubt, and what share of them a
bracketed measure would see is a statement about the published definition rather than about one
unusual filing.

## How results are reported

Console tables throughout, and the same sorting rule the rest of 04B uses: **Input** describes the
data, **Construction** walks the rule's steps, **Results** reports the output, **Validation** proves
identities, **Robustness** reads examples. Every figure is in Overview.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Marks = utils_file_path(.dir_main, "Output", "redact_spans.parquet")
  ),
  Params = list(
    Family    = "matcon",  # the only family emitting a redaction marker
    ReadKinds = 4L,        # markers of each class read in context
    ReadHeavy = 10L,       # the most heavily redacted contracts, read
    Bins      = 50L,       # bins across relative position in the density figure
    Seed      = 42L
  )
)

# ONE DIAL, AND IT IS A TOLERANCE RATHER THAN A REACH. A marker and the withheld money span that
# contains it are the SAME redaction seen twice, so the test is overlap; the tolerance exists only
# for the adjacent form where moneyregex stopped at the currency symbol.
.lP$Params$Spec <- red_spec(.tol = 10L)

fs::dir_create(fs::path_dir(.lP$Output$Marks))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, fs::file_exists)
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

# Input

## The anchor, the markers and the withheld prices

```{r}
#| label: load-spans

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled, nWords
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_marks <- red_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,
  .quiet     = FALSE
)

# 04B4'S LOADER, NOT A SECOND PATTERN LIST. Withheld keys on the moneyregex pattern name, and one
# definition of "a price the filer removed" is what keeps the two documents' counts comparable.
tab_money <- mny_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,
  .quiet     = TRUE
)

# THE DENOMINATOR, FROM THE REGISTER. Every ratio below divides by a word count no extractor
# produced, so a reader can check it independently.
tab_words <- red_words(.keys = tab_keys, .path_text = NULL, .quiet = FALSE)
```

# Construction

## Applying the rule

```{r}
#| label: apply-rule

res_base <- red_apply(
  .marks = tab_marks,        # every marker, with the class the extractor assigned
  .money = tab_money,        # filtered to Withheld inside; the match needs only those
  .words = tab_words,        # the register's word count
  .keys  = tab_keys,         # runs from the key side, so a contract with no marker gets a row
  .spec  = .lP$Params$Spec   # the overlap tolerance
)

tab_release <- res_base$Release   # THE FILE: one row per marker

# CLASS IS JOINED FOR REPORTING AND NEVER STORED. It is 03A's label spine rather than a result of
# this rule, and one filing carries 14,689 markers -- repeating the spine across those rows would
# duplicate it fourteen thousand times for a contract fact.
tab_counts <- res_base$Counts |>                 # the collapse: written nowhere
  dplyr::left_join(
    dplyr::select(tab_keys, DocID, Class, AmendType),
    by = dplyr::join_by(DocID)
  )
```

## Each class, and how much of the corpus it carries

```{r}
#| label: report-kind

tab_kind <- red_table_kind(.marks = tab_marks, .release = tab_counts)

red_report_kind(.tab = tab_kind)
```

**`MaxPerDoc` is the number to read.** One filing carries 14,689 bare markers, which is a quarter of
every span in the sample. Any measure built on the bracketed classes never sees it, and a mean over
markers is a mean over that filing.

## What the markers replaced

```{r}
#| label: report-money

tab_money_tab <- red_table_money(.release = tab_release, .money = tab_money)

red_report_money(.tab = tab_money_tab)
```

# Results

## The definitions against each other

```{r}
#| label: report-contrast

red_report_contrast(.tab = red_contrast(.marks = tab_marks, .release = tab_counts))
```

## Which contracts withhold a price

```{r}
#| label: report-money-class

tab_money_class <- red_table_money_class(.release = tab_release, .counts = tab_counts)

red_report_money_class(.tab = tab_money_class)
```

**This is the one variable the match produces that neither document had alone.** 04B4 counts a
currency with its number removed; this counts the places a redaction marker sits on one. The second
is what a contract *withheld*, and the bracketed share beside it says how much of that a published
measure would have seen.

## Redaction by contract type

```{r}
#| label: report-class

red_report_class(.tab = red_table_class(.release = tab_counts))
```

# Validation

## Four identities the file cannot violate

```{r}
#| label: validate-counts

brack_ <- dplyr::filter(tab_release, .data$Bracketed)
hit_   <- dplyr::filter(tab_release, .data$RedactedEntity == "money")

tibble::tibble(
  Item = c("Markers in the file",
           "Where a bracketed marker is one of the five classes",
           "Where a matched marker names the span it matched",
           "Where the three totals nest inside each other"),
  N    = c(nrow(tab_release),
           sum(brack_$Kind %in% .red_bracketed),
           sum(!is.na(hit_$RedactedRef)),
           sum(tab_counts$NBracketed <= tab_counts$NRedact &
                 tab_counts$NWithheld <= tab_counts$NRedact))
) |>
  dplyr::mutate(
    Of    = c(nrow(tab_release), nrow(brack_), nrow(hit_), nrow(tab_counts)),
    Share = tbl_pct(.data$N / pmax(.data$Of, 1L))
  ) |>
  tbl_say(.title = "Four identities the file cannot violate")

cli::cli_alert_info(
  "ROWS TWO TO FOUR MUST ALL READ 100%. Bracketed is membership in a declared five-of-six list, so \\
   a bracketed marker outside it means the column and the list were computed separately. A matched \\
   marker without a reference is a join that produced a row with nothing on the other side. And \\
   both NBracketed and NWithheld are subsets of every marker, so neither can exceed NRedact."
)
```

## Offsets index the canonical text

```{r}
#| label: validate-offsets

tab_verify <- ent_verify_span(
  .tab       = tab_release,
  .path_text = .lP$Input$Text,
  .col_start = "MarkStart",
  .col_stop  = "MarkStop",
  .col_span  = "MarkText",
  .n         = 500L,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Item = c("Markers checked", "Sliced text equals the stored span"),
  N    = c(nrow(tab_verify), sum(tab_verify$Exact))
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / pmax(nrow(tab_verify), 1L))) |>
  tbl_say(.title = "Offsets index the canonical text")

cli::cli_alert_info(
  "The span and the two offsets are one row of the released file, so this compares a thing with \\
   itself and must be 100%. Anything below is an offset problem rather than a rule one."
)
```

# Robustness

## Markers of each class, read in context

```{r}
#| label: read-kinds

red_report_read_kinds(
  .tab = red_read_kinds(.release = tab_release, .n = .lP$Params$ReadKinds, .seed = .lP$Params$Seed)
)
```

## The most heavily redacted contracts

```{r}
#| label: read-heavy

red_report_heavy(.tab = red_read_heavy(.release = tab_counts, .n = .lP$Params$ReadHeavy))
```

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Marks)

red_report_release(.release = tab_release, .counts = tab_counts)
```

## What every column means

```{r}
#| label: report-dictionary

red_report_dictionary(
  .tab   = red_dictionary_spans(.tab = tab_release),
  .title = "redact_spans.parquet"
)
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

red_report_headline(
  .release = tab_counts,        # the collapse: one row per contract
  .marks   = tab_marks,
  .n_spans = nrow(tab_release)  # the released FILE: one row per marker
)
```

## What a bracketed measure sees on a withheld price

```{r}
#| label: fig-money
#| fig-height: 3.4
#| fig-cap: "Markers on a price found withheld, split by whether a bracketed measure sees them."

red_plot_money(.tab = tab_money_tab)
```

## Where a price gets withheld

```{r}
#| label: fig-money-class
#| fig-height: !expr plot_height(dplyr::n_distinct(tab_money_class$Class))
#| fig-cap: "Share of contracts withholding at least one price, by contract type."

red_plot_money_class(.tab = tab_money_class)
```

## Each class, by how much it carries

```{r}
#| label: fig-kind
#| fig-height: 3.4
#| fig-cap: "Each marker class by share of all spans and share of documents carrying one."

red_plot_kind(.tab = tab_kind)
```

## Redaction density

```{r}
#| label: fig-ratio
#| fig-height: 3.4
#| fig-cap: "Bracketed markers per thousand words, by contract type."

red_plot_ratio(.release = tab_counts)
```

## Where in a document the markers fall

```{r}
#| label: fig-density
#| fig-height: 3.4
#| fig-cap: "Relative position of every marker across the document."

red_plot_density(.marks = tab_marks, .bins = .lP$Params$Bins)
```

# Next

**04D** calls `red_apply()` on chunks of the corpus and writes the same file at scale, and the
**export** calls `red_collapse()` to turn the markers into one row per contract. `RedactedEntity` is
a column rather than a boolean, so DATE and GPE join the same way later without a second rule.
