---
title: "Entity Rules -- Redactions (04B5)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B5-Rules-REDACT"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B5-Rules-REDACT.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document counts redaction markers and turns them into a per-document intensity.

## One producer, so every table is a description

matcon's `redaction-v2` is the only extractor in the project that emits a redaction marker at all --
LexNLP has no such label and spaCy is not in the corpus pass. So there is no second opinion to report
against, and nothing below is a comparison. That is a fact about the instrument rather than a choice.

## The variable is bimodal and should be reported as two things

Over the corpus, REDACT coverage is **0.193** at **43.4 spans per document**. A fifth of contracts
carry a marker at all, and the ones that do carry many. Presence and intensity are two questions, and
a mean over every document answers neither: it is the product of a rate and a conditional mean, and
the interesting variation is in both.

## The denominator comes from the register

Markers per thousand words needs a word count, and contracts run from four thousand to seventeen
thousand words by class. An earlier version counted `\S+` over the canonical text, which works on
4,398 documents and cannot work on 1.19 million -- 04C writes no corpus text file. 02B's register
carries `nWords` for all 1,771,923, so the ratio can reach the corpus.

**The two counts are printed side by side rather than assumed equal.** One counts whitespace-separated
runs in R and the other was computed upstream; where they disagree materially the ratio is sensitive
to which is used, and a reader of a per-thousand-words figure should know that before reading it.

## What sat beside a marker is reported and not released

A marker beside a currency symbol hid an amount; beside an organisation, a party name. The nearest
labelled span within reach is the cheapest statement of that, and it is the same proximity instrument
04B2 uses. On the earlier check **82%** of markers had no labelled entity within forty characters,
and a variable missing four times in five is a diagnostic rather than a measure. What it can say is
which labels sit near markers at all, which is the first thing to know before anyone builds on it.

## What is recomputed, and what is not

Everything, on every render.

## How results are reported

Console tables throughout, two figures in `# Overview`. The two marker kinds are separate columns,
never a total.

## Where things are written

Two artifacts: the markers with their kind and nearest neighbour, and one row per document.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "Output", "roles_redact.parquet"), # per marker
    Doc   = utils_file_path(.dir_main, "Output", "redact_doc.parquet")    # per document
  ),
  Params = list(
    Family = "matcon",   # the only family that emits a redaction marker
    # WHAT A MARKER MIGHT HAVE REPLACED, each read from the family the corpus pass carries for it.
    # ORG is LexNLP's because matcon emits none; the other three are matcon's.
    Neighbours = c(MONEY = "matcon", ORG = "lexnlp", DATE = "matcon", GPE = "matcon"),
    Reach   = 40L,      # furthest a labelled span may be and still be the marker's neighbour
    Bins    = 50L,
    ReadN   = 10L,
    ReadCtx = 200L,
    CheckN  = 500L,
    Seed    = 42L
  )
)

fs::dir_create(fs::path_dir(.lP$Output$Spans))

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is computed")
```

# Input

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,
  .path_register = .lP$Input$Register,   # carries nWords, which is the ratio's denominator
  .path_landing  = NULL,
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)
```

```{r}
#| label: load-markers

tab_marks <- red_load(
  .dir_store = .lP$Input$Store,   # the directory; the family is the filename
  .lens      = tab_lens,
  .family    = .lP$Params$Family,
  .quiet     = FALSE
)

tab_words <- red_words(
  .keys      = tab_keys,          # the register's count, which is the one that reaches the corpus
  .path_text = .lP$Input$Text,    # the recount, for the agreement check and the fallback
  .quiet     = FALSE
)

tab_counts <- red_counts(
  .marks = tab_marks,             # every marker, with its kind
  .words = tab_words,             # the denominator
  .keys  = tab_keys               # so a document with no marker at all still carries a row
)

red_report_found(.marks = tab_marks, .counts = tab_counts)
```

# Construction

```{r}
#| label: find-neighbours
tab_near <- red_neighbour(
  .marks   = tab_marks,
  .dir_store = .lP$Input$Store,
  .lens    = tab_lens,
  .labels  = .lP$Params$Neighbours,   # money, org, date and gpe at the corpus engines
  .reach   = .lP$Params$Reach,
  .quiet   = TRUE
)

red_report_neighbour(.marks = tab_near, .reach = .lP$Params$Reach)
```

```{r}
#| label: report-cto
# The base rate stands unchecked until the confidential-treatment match is joined here. 05-CheckItem101
# already establishes which filings carry an order, and if that rate and this one disagree materially,
# one of them is wrong -- which matters for the intensity figures referee 2 asked for.
red_report_cto(.counts = tab_counts, .cto = NULL)
```

# Results

```{r}
#| label: report-contrast
tab_contrast <- red_contrast(.marks = tab_marks, .counts = tab_counts)

red_report_contrast(.tab = tab_contrast)
```

The prediction this table exists to test, stated before it runs: **Employment: Compensation collapses
toward the other classes** once bare markers are excluded and documents are weighted equally. If it
does not, the 13.29 was a real finding about where compensation exhibits redact, and it can go in the
paper -- but not until the four cells agree.

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_marks,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every marker carries one of the two kinds",
    "Bracketed and bare sum to the total",
    "Every document carries a word count",
    "Documents carrying exactly one row",
    "Every neighbour distance is within the reach"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(tab_marks$Kind %in% c("bracketed", "bare")),
    sum(tab_counts$NBracketed + tab_counts$NBare == tab_counts$NRedact),
    sum(!is.na(tab_counts$NWords)),
    dplyr::n_distinct(tab_counts$DocID),
    sum(tab_near$NearDist <= .lP$Params$Reach, na.rm = TRUE)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_marks),
    nrow(tab_counts),
    nrow(tab_counts),
    nrow(tab_counts),
    sum(!is.na(tab_near$NearDist))
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

# Robustness

```{r}
#| label: read-bracketed
ent_read_spans(
  .tab       = dplyr::filter(tab_near, .data$Kind == "bracketed", .data$NearLabel != "nothing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Kind", "NearLabel", "NearDist"),
    .title = "Bracketed markers with something labelled beside them"
  )
```

```{r}
#| label: read-bare
ent_read_spans(
  .tab       = dplyr::filter(tab_near, .data$Kind == "bare"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Kind", "NearLabel", "NearDist"),
    .title = "Bare markers -- the kind that floods"
  )
```

```{r}
#| label: read-flood
# The documents with the most markers, read rather than averaged. An average over a distribution with
# one observation at 14,689 is a fiction, and this is what that observation looks like.
tab_counts |>
  dplyr::slice_max(.data$NRedact, n = 10L, with_ties = FALSE) |>
  dplyr::select(DocID, Class, NWords, NBracketed, NBare, RedactRatio) |>
  dplyr::mutate(RedactRatio = round(.data$RedactRatio, 2)) |>
  tbl_say(.title = "The ten most heavily marked documents")
```

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_near, .lP$Output$Spans)
arrow::write_parquet(tab_counts, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Markers with their kind and what sat beside them",
               "Redaction counts and intensity, per document"),
  Path     = c(.lP$Output$Spans, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B5")
```

The document table carries both kinds as separate columns and both ratios, so a consumer who
disagrees about whether bare markers count can pool them without re-deriving anything.

# Overview

```{r}
#| label: fig-ratio
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Mean bracketed markers per thousand words, by contract type, weighting every contract
#|   equally. This is the document-weighted, bare-excluded cell of the four-way table, and the one a
#|   redaction-intensity figure should be built from."
red_plot_ratio(.counts = tab_counts)
```

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of markers by relative position in the document, weighted by documents, by kind.
#|   A kind that clusters at one end is following a drafting convention; one spread evenly is being
#|   used for something other than withholding a term."
red_plot_density(.marks = tab_marks, .bins = .lP$Params$Bins)
```

```{r}
#| label: report-everything
red_report_all(
  .marks    = tab_marks,
  .near     = tab_near,
  .counts   = tab_counts,
  .contrast = tab_contrast,
  .reach    = .lP$Params$Reach
)
```

# Next

Two things this document points at rather than answers.

**The base rate needs the confidential-treatment match.** 05-CheckItem101 already establishes which
filings carry an order; joining it here turns an unchecked share into a cross-tab, and a marker with
no order or an order with no marker is a finding either way.

**The money-adjacent case is the one worth pursuing.** A marker beside a currency symbol hid an
amount, and that is the single place where this label and 04B4 have something to say to each other -- 
a contract whose largest amount is redacted has a maximum that means something different from one
whose largest amount is stated.
