---
title: "Entity Rules -- What Was Withheld (04B5)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the label spine; 04A owns the sample and the stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B5-Rules-REDACT"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B5-Rules-REDACT.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document counts what each contract withheld, and asks what the markers replaced.

## Six kinds, one column each, and that is the whole rule

`redaction.py` assigns a class to every span, and this releases all six of them separately:

| Class | What it matches |
|:--|:--|
| `RedactExplicit` | a bracket naming confidential treatment -- CONFIDENTIAL, REDACT, CTR |
| `RedactSymbol` | a bracket of whitespace and asterisks -- `[***]`, `[ * * * ]`, `[*]` |
| `RedactBlank` | a bracket of whitespace and underscores -- `[___]`, `[__]` |
| `OmitExplicit` | a bracket recording deletion -- INTENTIONALLY, OMITTED, DELETE |
| `OmitSymbol` | a bracket of bullets or ellipses, or three dots |
| `RedactBare` | an unbracketed run of three or more asterisks |

**The version this replaces threw five of them away.** It tested whether `LabelRaw` contained
`"BARE"` and called everything else "bracketed", so the four published classes and the one addition
arrived as a single bucket. Releasing them separately costs four columns and makes every question
below a **filter** rather than a decision taken here.

## The published method is brackets only, and that is not an inference

`06-Redactions.R` extracted `\[.+?\]` from uppercased, whitespace-collapsed text and joined a curated
indicator list. No unbracketed pattern could reach it.

So **`NBracketed`** -- the five bracketed classes summed -- is the quantity Table 3 was built on, and
it is released as its own column. The published figure is reproducible from this file rather than only
from the old code, which is the same discipline as `NaiveYears` in 04B3 and the naive columns in 04B4.

## Redact is not Omit

`[INTENTIONALLY OMITTED]` is a placeholder where a schedule was left out. `[***]` is confidential
treatment. Both are gaps in a contract and only one is a redaction, so **`NWithheld`** carries the
`Redact` classes and leaves the `Omit` ones out.

## One filing carries 14,689 bare markers

**24% of every redaction span in the sample, from a single document.** Nothing here removes it: it is
a real count of a real document, and the by-class columns make it visible without a rule -- its
markers are entirely `RedactBare`, so any measure built on the bracketed classes never sees it.

**What it cost when the kinds were pooled** is why the class contrast is computed **four ways** --
span-weighted and document-weighted, with bare markers and without. Employment: Compensation once
showed a positional contrast of 13.29 against 1 to 5 everywhere else, and that was one filing. A
finding surviving all four cells is a finding; one appearing only in the span-weighted pooled cell is
a flood document.

## The ratio is the comparable quantity

Contracts run from roughly 4,200 to 17,400 words by class, so a count of markers is partly a count of
words. Markers per thousand words is what makes a class or industry comparison mean anything, and it
is what referee 2 asked for when they wanted redaction intensity by firm-quarter.

## The denominator comes from the register, and this document opens nothing

02B carries `nWords` for all 1,771,923 documents. Counting `\S+` over the canonical text works on
4,398 and cannot work on 1.19 million, because 04C writes no corpus text file. The recount is
available as an **agreement check** on the sample and is skipped entirely when no text path is given,
which is what the corpus run does.

**With 04B2, 04B3 and 04B4 already moved to stored cue columns, no rule in the 04B family needs a
document.** 04D's `Cues` dial has nothing left to gate.

## What sat beside a marker is reported and not released

A marker beside a currency symbol hid an amount; beside an organisation, a party name. That is a
proximity question of exactly the kind 04B2 answers, and it reads no text. It stays a diagnostic
because 82% of markers had no labelled entity within forty characters, and a variable missing four
times in five is not a measure.

## How results are reported

Console tables throughout, four figures in `# Overview`, and two reading blocks: **real markers of
every class**, which is what decides whether a class belongs in a headline variable, and the ten
heaviest documents.

## Where things are written

**One file**, one row per contract.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    # THE CANONICAL TEXT, FOR A CHECK AND NOT A SOURCE. red_words() takes NULL here and skips the
    # recount entirely, which is what the corpus run does; on the sample it is worth knowing whether
    # the register's count and a recount agree.
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Contracts = utils_file_path(.dir_main, "Output", "contracts_redact.parquet")
  ),
  Params = list(
    Family    = "matcon",                    # the only family emitting a redaction marker at all
    NearLabel = c("MONEY", "GPE", "DATE"),   # what a marker might have replaced
    Reach     = 40L,                         # characters either side, for the neighbour check
    ReadKinds = 4L,                          # spans shown per class
    ContextWidth = 108L,                     # characters a context line may use; must not wrap
    ReadHeavy = 10L,                         # heaviest documents listed
    Seed      = 42L                          # fixed, so the same spans are read on every render
  )
)

fs::dir_create(fs::path_dir(.lP$Output$Contracts))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before. TEXT IS THE
# ONE EXCEPTION AND IT IS DECLARED RATHER THAN ASSUMED: it feeds an agreement check on the sample and
# is deliberately absent on the corpus, where 04C writes no text file at all. Aborting on it would
# make the corpus path fail on a file it is right not to have.
.lP$Params$Optional <- "Text"

need_ <- dplyr::filter(tab_inputs, !.data$Exists, !.data$Input %in% .lP$Params$Optional)

if (nrow(need_) > 0L) {
  cli::cli_abort(c(
    "{nrow(need_)} required input{?s} {?does/do} not resolve.",
    "x" = "{paste(need_$Input, collapse = ', ')}."
  ))
}

# AND AN ABSENT OPTIONAL INPUT IS NULLED HERE rather than left as a path that does not exist, so the
# functions below take one decision from one place: red_words() sees NULL and skips the recount,
# exactly as it does on the corpus.
gone_ <- dplyr::filter(tab_inputs, !.data$Exists, .data$Input %in% .lP$Params$Optional)

if (nrow(gone_) > 0L) {
  .lP$Input[gone_$Input] <- list(NULL)
  cli::cli_alert_info(
    "{nrow(gone_)} optional input{?s} absent: {paste(gone_$Input, collapse = ', ')}. The word-count \\
     agreement check is skipped and the register's count is used, which is what the corpus run does \\
     in every case."
  )
}
```

# Input

## The anchor, and the denominator

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,  # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled, nWords
  .path_landing  = NULL,                # the addresses are 04B2's; not read here
  .quiet         = FALSE
)

tab_lens <- tab_keys |>
  dplyr::transmute(DocID, DocLen = as.integer(.data$nChars)) |>
  dplyr::filter(!is.na(.data$DocLen), .data$DocLen > 0L)

tab_words <- red_words(
  .keys      = tab_keys,
  .path_text = .lP$Input$Text,   # NULL on the corpus run, and then nothing is opened
  .quiet     = FALSE
)
```

**The register's count is the one used either way.** The recount exists to say whether the two agree,
because where they disagree materially every per-thousand-words figure below is sensitive to which was
taken -- and only the register's can reach the corpus.

## The markers

```{r}
#| label: load-spans

tab_marks <- red_load(
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .family    = .lP$Params$Family,
  .quiet     = FALSE
)
```

**The class arrives as the extractor wrote it.** `redaction.py`'s `CLASSES` tuple and this document's
vocabulary are two statements of one list, so a class emitted there and unregistered here aborts
rather than ordering arbitrarily in every table and appearing in no column of the release.

# Construction

## Applying the rule

```{r}
#| label: apply-rule

tab_release <- red_release(
  .marks = tab_marks,
  .words = tab_words,
  .keys  = tab_keys    # runs from the key side, so a contract with no marker still gets a row
)
```

## What each class contributes

```{r}
#| label: report-kind

tab_kind <- red_table_kind(.marks = tab_marks, .release = tab_release)

red_report_kind(.tab = tab_kind)
```

## What sat beside a marker

```{r}
#| label: neighbour

tab_near <- red_neighbour(
  .marks     = tab_marks,
  .dir_store = .lP$Input$Store,
  .lens      = tab_lens,
  .labels    = .lP$Params$NearLabel,   # MONEY, GPE, DATE -- what a marker might have replaced
  .reach     = .lP$Params$Reach,
  .quiet     = TRUE
)

tab_near |>
  dplyr::summarise(Spans = dplyr::n(), Docs = dplyr::n_distinct(.data$DocID), .by = Near) |>
  dplyr::mutate(Share = tbl_pct(.data$Spans / sum(.data$Spans))) |>
  dplyr::arrange(plot_factor(.data$Near, .key = "RedactNear")) |>
  tbl_say(.title = "The nearest labelled entity within forty characters")

cli::cli_alert_info(
  "REPORTED AND NOT RELEASED. Most markers have nothing labelled beside them at all, and a variable \\
   missing four times in five is a diagnostic rather than a measure. It is a comparison of offsets \\
   and reads no text, which is the same instrument 04B2 attaches a place with."
)
```

# Results

## Redaction intensity by contract type

```{r}
#| label: table-class

tab_class <- red_table_class(.release = tab_release)

red_report_class(.tab = tab_class)
```

## The class contrast, four ways

```{r}
#| label: table-contrast

tab_contrast <- red_contrast(.marks = tab_marks, .release = tab_release)

red_report_contrast(.tab = tab_contrast)
```

# Validation

## Three identities the counts cannot violate

```{r}
#| label: validate-counts

# THE TOTALS ARE SUMS OF THE SIX CLASSES, so they cannot disagree with them, and the published
# definition can never exceed the whole. A contract with no marker must carry zeros rather than
# missing values, because withholding nothing is a measurement.
six_ <- rowSums(dplyr::select(tab_release, "NRedactExplicit", "NRedactSymbol", "NRedactBlank",
                              "NOmitExplicit", "NOmitSymbol", "NRedactBare"))

tibble::tibble(
  Item = c("Documents in the sample",
           "Rows in the released file",
           "Where the six classes do not sum to NRedact",
           "Where NBracketed exceeds NRedact",
           "Markers loaded, against the released total"),
  N    = c(nrow(tab_keys),
           nrow(tab_release),
           sum(six_ != tab_release$NRedact),
           sum(tab_release$NBracketed > tab_release$NRedact),
           nrow(tab_marks) - sum(tab_release$NRedact))
) |>
  tbl_say(.title = "Three identities the counts cannot violate")

cli::cli_alert_info(
  "The first two rows must be equal and the last three must all be ZERO. A total that is not the sum \\
   of its parts means a class is being counted twice or not at all; a published definition larger \\
   than the whole is arithmetically impossible; and a difference in the last row means markers were \\
   loaded that no document's row accounts for."
)
```

# Robustness

## What each class actually catches

```{r}
#| label: read-kinds

tab_read <- red_read_kinds(
  .marks = tab_near,               # carries Near, so the block says what sat beside each span
  .n     = .lP$Params$ReadKinds,
  .seed  = .lP$Params$Seed
)

red_report_read_kinds(.tab = tab_read)
```

**This is the block that decides which classes a headline variable should use.** Six classes are six
claims about what a bracket means, and no count says whether `[INTENTIONALLY OMITTED]` belongs in a
redaction measure -- only the span does. Read the `Omit` rows against the `Redact` ones.

## What one marker of each class sits in

```{r}
#| label: read-context

tab_context <- red_read_context(
  .marks = tab_marks,
  .width = .lP$Params$ContextWidth   # budgeted so the line never wraps
)

red_report_context(.tab = tab_context)
```

**A span says what a class matches; the sentence says what the drafter was doing.** `[***]` is
unambiguous once `$ [***] per share` is around it, and `[.]` is not a redaction at all until the text
says whether something was withheld or a bullet was left in. The context is `CueBefore` and
`CueAfter` -- cut at extraction from the offsets that produced the span -- so this opens no
document either.

## The documents carrying the most markers

```{r}
#| label: read-heavy

tab_heavy <- red_read_heavy(.release = tab_release, .n = .lP$Params$ReadHeavy)

red_report_heavy(.tab = tab_heavy)
```

**A mean over a distribution with one observation at 14,689 is a fiction**, and this is what that
observation looks like beside the ones around it.

# Deployment

## The release

```{r}
#| label: write-artifact

arrow::write_parquet(tab_release, .lP$Output$Contracts)

red_report_release(.tab = tab_release)
```

## What every column means

```{r}
#| label: report-dictionary

tab_dict <- red_dictionary(.tab = tab_release)

red_report_dictionary(.tab = tab_dict)
```

**Every candidate definition is a column rather than a decision taken here:**

```r
tab_release |>
  dplyr::summarise(
    Published = sum(.data$NBracketed),   # what Table 3 counted
    Withheld  = sum(.data$NWithheld),    # redaction, not omission
    Everything = sum(.data$NRedact),
    .by = Class
  )
```

# Overview

## The rule in one table

```{r}
#| label: report-headline

red_report_headline(.release = tab_release, .marks = tab_marks)
```

## Spans against documents, by class

```{r}
#| label: fig-kind
#| fig-cap: "Each class as a share of all markers, and as a share of the contracts carrying one. A
#|   class large on spans and small on documents is concentrated in few filings, which is what the
#|   bare row is."
#| fig-height: 3.4

red_plot_kind(.tab = tab_kind)
```

## Markers per thousand words

```{r}
#| label: fig-ratio
#| fig-cap: "Bracketed markers per thousand words, by contract type, over the contracts carrying one.
#|   The ratio rather than the count, because contracts run from roughly 4,200 to 17,400 words by
#|   class."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_release$Class))

red_plot_ratio(.release = tab_release)
```

## Where the markers sit

```{r}
#| label: fig-density
#| fig-cap: "Position through the document, by class. Confidential treatment concentrates where the
#|   commercial terms are; an omitted schedule sits where schedules sit, which is one reason the two
#|   are separate columns."
#| fig-height: 4.2

red_plot_density(.marks = tab_marks)
```

## The nearest labelled entity

```{r}
#| label: fig-near
#| fig-cap: "The nearest labelled entity within forty characters of each marker. Most markers have
#|   nothing labelled beside them, which is why this is a diagnostic and not a released variable."
#| fig-height: 2.6

red_plot_near(.near = tab_near)
```

# Next

**04D** applies all five rules at corpus scale. Nothing there re-extracts and nothing there opens a
document: every rule in this family now reads spans and stored cue columns, so the corpus pass is a
query rather than a second reading of 1.19 million contracts.
