---
title: "Entity Extraction over the Corpus (04C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library registering a vocabulary must follow it.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# 03A owns clf_read_text(), which is how every document in this project is read off the mirror. The
# corpus is read by the same function that read the labelled sample, not by a copy that agrees today.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

# 04A owns the plot vocabularies and the coverage reporting this document compares against.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
  encoding = "UTF-8"
)

.name_script <- "04C-EntityCorpus"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04C-EntityCorpus.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This script runs the entity extractors over every Exhibit 10 attachment in the corpus and stores what
they found, span by span, in the same shape 04A produced for the labelled sample.

## Why the same code and not similar code

04A established what each engine does on 4,398 documents whose classification is known. That is only
evidence about the corpus if the corpus is extracted by the same code -- so `ner_extract()` and
`ner_ingest()` are called here unmodified, and everything in this document is about *which* documents
reach them and how their text gets off disk.

The two sets of stores then carry identical schemas, identical model tags and identical spec hashes,
which is what makes "the sample says X" a statement about the corpus rather than about the sample.

## What each family is asked for

The same plan 04A ran, minus spaCy: **matcon** for `GPE`, `DATE`, `TERM`, `MONEY`, `REDACT` and
`LAW`, and **LexNLP** for `ORG`, `GPE`, `DATE`, `MONEY`. Asking a family for everything it can produce
costs nothing extra -- both read each document exactly once regardless of how many entities are
requested -- and asking for less risks a re-run when a rule wants an entity this pass skipped.

`LAW` is the one addition since the store was first built. `lawregex` emits a governing-law clause as
a span with offsets, which is what lets 04B2 withhold a jurisdiction from a party's address by
containment rather than by reading text.

## Why spaCy is not here

On 04A's evidence, and it is worth stating plainly because it is the largest single decision in the
04 family.

The transformer runs at 2.13 documents a second against LexNLP's 4.47 and matcon's 26.68, so it would
have cost **more than the other two combined** -- six and a half days against three and a half. What
it buys is measurable: its ORG has a positional contrast of 0.97, meaning organisations spread evenly
through the document, against LexNLP's 4.36, the strongest end-of-document concentration in the whole
table. spaCy proposes eleven times as many organisations, uniformly distributed through the body.

For extracting the parties to a contract, LexNLP's ORG is not the compromise. It is the better
instrument, and it is six days cheaper.

**PERSON goes with it**, since only spaCy produces it. No 04B document uses PERSON and no variable in
the paper depends on it.

## What is recomputed, and what is not

Nothing that has been done. Every document is recorded against every model and entity it was sent to,
whatever the outcome, so a re-render asks what is missing and extracts only that. An interrupted pass
costs at most the chunk in flight.

**Resumption is a property here, not a feature.** There is no state to remember between renders and
nothing that could be wrong about itself: the ledger is written per chunk and a document with a row
is never sent again.

## How results are reported

Console tables throughout. The one substantive comparison is against 04A's coverage on the labelled
sample, because a corpus rate far from the sample rate is either a finding about representativeness
or a defect in this pass, and both are worth having before a rule is written against these spans.

## Where things are written

Two databases under `Output/`, one per family, each holding one table per entity plus the ledger, the
manifest, the corpus index and the failure log. 04B reads them; nothing else does.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # THE REGISTER IS THE CORPUS. 02B holds every document with its ladder step attached, so
    # membership, population and deduplication all come from one place. The alternative -- walking a
    # parsed tree -- makes a second, independent statement about what is in the corpus, one that can
    # disagree with the register without either of them reporting it.
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Store = utils_file_path(.dir_main, "Output"),
    Stage = utils_file_path(.dir_main, "Stage")
  ),
  Params = list(
    # 01B's parsed mirror. The register stores no path -- DocTypeMod, YQ and DocID determine one --
    # so the mirror root is a parameter and utils_doc_path() rebuilds the rest.
    DirMirror = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01B-EdgarDocuments"),
      "GetEDGAR"
    ),

    # "all" is every Exhibit 10 attachment, and it is close to free. Deduplication removes 18.7% of
    # the copies, so an "all" pass reads 1,189,805 attachments against "descriptive"'s 1,136,095 --
    # 4.7% more work for a store that never needs revisiting. Deduplicated "all" is in fact cheaper
    # than an undeduplicated "descriptive" pass would have been, and every narrower question is then
    # a filter on a store that already exists.
    Population = "all",
    DocType    = "Exhibit10",

    # DOCUMENTS PER ENGINE INVOCATION. Each chunk is read, staged as one parquet and handed to the
    # extractor, so this trades container startups against staging-file size: at 5,000 documents the
    # pass makes about 240 invocations and stages roughly 165 MB a time.
    ChunkSize = 50000L,

    # TWO WORKER COUNTS, BECAUSE THEY ARE TWO RESOURCES. The daemons read parquet files off disk and
    # finish before the container starts, so the two never contend -- but they are separate settings
    # and one number standing for both would hide that.
    #
    # The read is the dominant cost of the pass and not the extractors: one arrow::read_parquet() per
    # document, 1.19 million times. That is why the parallelism goes there, where it also cannot
    # change a result, because a read is pure.
    ReadWorkers   = 20L,
    EngineWorkers = 20L,

    # BATCH SIZE FROM 04A'S BENCHMARK, and the honest note is that it barely matters. Over 4 to 64 the
    # spread was 6% for matcon and 18% for LexNLP, against a worker count that is worth multiples. The
    # benchmark measured at five workers and these run at twenty-four, so the ranking is assumed to
    # transfer -- which is acceptable for a parameter this flat and would not be for the worker count.
    Batch = list(matcon = 16L, lexnlp = 8L),

    # A HANG DETECTOR, NOT A BUDGET. At matcon's throughput a document taking two minutes is running
    # orders of magnitude beyond the median. LexNLP's cap is the one that matters and its expensive
    # work is the maxent company NER and the date grammar, not the geoentity pass -- a timeout there
    # is not one lost document but documents lost SYSTEMATICALLY IN THE LONGEST AGREEMENTS.
    Timeout = list(matcon = 120L, lexnlp = 240L),

    # Chunks between progress lines. The first and last always report, so a run is never silent.
    ReportEvery = 5L,

    # Documents drawn for the offset check. See the Validation section for why it is a sample here
    # and every span in 04A.
    OffsetSample = 500L,

    # NULL takes the whole outstanding queue. An integer names a FIXED COHORT: the same n documents
    # on every render, of which this one extracts whichever are not already done. A second render at
    # the same number is therefore a no-op rather than another n documents, so a rehearsal can be
    # repeated and its numbers compared. The cohort is drawn in hash order, so it is a slice of the
    # corpus rather than its oldest registrants. See cor_pending().
    Limit  = NULL,
    Reload = FALSE,  # rebuild the corpus index from the register rather than reusing the store's

    # CLEARING A CORPUS STORE DISCARDS DAYS OF EXTRACTION, so it happens on an explicit flag and
    # never because a check found a reason. FALSE stops the pass and names the models whose rules
    # have moved; TRUE clears exactly those and re-extracts them.
    Rebuild = FALSE
  )
)

# THE SAME PLAN 04A RAN, MINUS spaCy. Everything each family can produce, because asking for less
# risks a re-run when a rule wants an entity this pass skipped and asking for all of it costs nothing
# extra -- both families read each document exactly once regardless of how many entities are named.
#
# LAW IS THE ONE ADDITION since the store was first built, and it is what lets 04B2 withhold a
# jurisdiction from a party's address by containment rather than by reading text.
.lP$Plan <- tibble::tribble(
  ~Family,   ~Entities,
  "matcon",  c("GPE", "DATE", "TERM", "MONEY", "REDACT", "LAW"),
  "lexnlp",  c("ORG", "GPE", "DATE", "MONEY")
)

fs::dir_create(c(.lP$Output$Store, .lP$Output$Stage))
```

# Families

## What each engine is, and what it would write

```{r}
#| label: describe-families

# The same description 04A ran, and it must agree with it: the model tags and spec hashes recorded
# beside the corpus spans are what make the two sets of stores comparable.
tab_describe <- ner_describe(
  .spacy_models = character(),        # spaCy is not in this pass; see the Purpose
  .lexnlp_image = "contracts-lexnlp"
)

ner_report_describe(.describe = tab_describe)

# WHAT A FINISHED DOCUMENT LOOKS LIKE, per family. The ledger is keyed on (DocID, Model, Entity), so
# the queue needs to know how many rows a completed document carries -- and that number comes from
# here rather than from the ledger, which cannot say on an empty store and says the wrong thing on a
# partial one.
tab_pairs <- .lP$Plan |>
  purrr::pmap(\(Family, Entities) dplyr::mutate(
    cor_pairs(.describe = tab_describe, .family = Family, .entity = Entities),
    Family = Family, .before = 1L
  )) |>
  purrr::list_rbind()

tbl_say(.tab = tab_pairs, .title = "Model and entity pairs the corpus spans will carry")

cli::cli_alert_info(
  "A document is finished when it has one ledger row for each of these pairs: \\
   {paste(paste0(names(table(tab_pairs$Family)), ' ', as.integer(table(tab_pairs$Family))),
          collapse = ', ')}."
)
```

# Input

## Opening the two stores, and loading the corpus index

```{r}
#| label: connect-and-load

con_matcon <- ner_db_connect(
  .db_path   = ner_db_path(.dir = .lP$Output$Store, .family = "matcon"),
  .read_only = FALSE
)
ner_db_init(.con = con_matcon)
cor_db_init(.con = con_matcon)

con_lexnlp <- ner_db_connect(
  .db_path   = ner_db_path(.dir = .lP$Output$Store, .family = "lexnlp"),
  .read_only = FALSE
)
ner_db_init(.con = con_lexnlp)
cor_db_init(.con = con_lexnlp)

# THE INDEX IS LOADED INTO EACH FAMILY DATABASE, so every store answers its own questions: what is
# outstanding is an anti-join inside one file rather than a join across two, and a family can be
# cleared or shipped alone. An index of 1.19 million rows costs a few hundred megabytes twice.
n_corpus <- cor_corpus_load(
  .con           = con_matcon,
  .path_register = .lP$Input$Register,      # 02B's register: the gate, not a directory walk
  .dir_mirror    = .lP$Params$DirMirror,    # 01B's parsed mirror, where the text lives
  .population    = .lP$Params$Population,   # "all"
  .doc_type      = .lP$Params$DocType,      # "Exhibit10"
  .reload        = .lP$Params$Reload
)

invisible(cor_corpus_load(
  .con           = con_lexnlp,
  .path_register = .lP$Input$Register,
  .dir_mirror    = .lP$Params$DirMirror,
  .population    = .lP$Params$Population,
  .doc_type      = .lP$Params$DocType,
  .reload        = .lP$Params$Reload
))
```

## Preflight: what the store holds against what the extractors are

```{r}
#| label: preflight

tab_pre <- dplyr::bind_rows(
  dplyr::mutate(cor_manifest_check(
    .con      = con_matcon,
    .describe = tab_describe,
    .family   = "matcon",
    .entity   = .lP$Plan$Entities[[which(.lP$Plan$Family == "matcon")]]
  ), Family = "matcon", .before = 1L),
  dplyr::mutate(cor_manifest_check(
    .con      = con_lexnlp,
    .describe = tab_describe,
    .family   = "lexnlp",
    .entity   = .lP$Plan$Entities[[which(.lP$Plan$Family == "lexnlp")]]
  ), Family = "lexnlp", .before = 1L)
)

cor_report_manifest(
  .con     = con_matcon,
  .tab     = dplyr::filter(tab_pre, .data$Family == "matcon"),
  .family  = "matcon",
  .rebuild = .lP$Params$Rebuild   # TRUE clears a moved model; FALSE stops and names it
)

cor_report_manifest(
  .con     = con_lexnlp,
  .tab     = dplyr::filter(tab_pre, .data$Family == "lexnlp"),
  .family  = "lexnlp",
  .rebuild = .lP$Params$Rebuild
)
```

**`ner_ingest()` makes this comparison already, and it makes it too late.** It refuses to write where
a model tag is unchanged and its hash has moved -- because that means the rules were edited without
the version being bumped, and the rows already stored mean something else. But it fires at the first
ingest, which on a three-day pass is hours in and after the read has been paid for.

**The case is live rather than hypothetical.** Adding `CueBefore` and `CueAfter` to the extractors
moved every matcon spec hash and the LexNLP image hash with them. A store built before that carries
rows this pass cannot be ingested beside -- and, separately, rows `ent_load_entity()` will refuse to
read, because `ent_extras()` now names two columns those tables do not have.

**`MOVED` is a decision rather than a warning.** Either the store is cleared for that model and the
corpus re-extracted, or the pass does not run. Continuing is the one option that is never right, and
an alert would have allowed exactly that. Clearing discards days of work, so it needs `Rebuild = TRUE`
-- a flag someone set on purpose, not a consequence of a check.

**Attachments, not copies, and this is the decision that saves seventeen hours.** 01C left it open --
classification wants one copy, entity extraction "may want each, because the registrant-side metadata
differs even where the text does not". The resolution is that the metadata differing is an
*anchoring* input, applied downstream of extraction: the text of two copies of one attachment is
identical, extraction reads text, so extracting both produces identical spans at 23% more cost.

One row per attachment here. Fanning back out to all 1,462,939 registrant copies is a join on
`HashDocument` at release, exactly as 03F does.

**Which attachment answers for the population** is the subtler half. `PrimaryFiler` is chosen
globally while `EstiSample` depends on a per-CIK Compustat match, so an attachment can have its
primary outside a population and another copy inside it -- 4,432 of them for the estimation sample and
none for the descriptive one, which is exactly where the mechanism predicts them. So the rule is to
extract the primary of every attachment with *at least one* copy in the population. That also makes
the store population-independent: a pass run for one population is reused verbatim by any other.

# Extraction

## Running matcon

```{r}
#| label: extract-matcon

tab_pass_matcon <- cor_pass(
  .con            = con_matcon,
  .family         = "matcon",
  .entity         = .lP$Plan$Entities[[which(.lP$Plan$Family == "matcon")]],
  .describe       = tab_describe,                # supplies the model tags AND the pair count
  .stage_path     = fs::path(.lP$Output$Stage, "matcon-chunk.parquet"),
  .stage_dir      = fs::path(.lP$Output$Stage, "matcon"),
  .chunk_size     = .lP$Params$ChunkSize,        # documents per engine invocation
  .read_workers   = .lP$Params$ReadWorkers,      # daemons reading parquet off the mirror
  .engine_workers = .lP$Params$EngineWorkers,    # processes inside the extractor
  .batch_size     = .lP$Params$Batch$matcon,
  .timeout        = .lP$Params$Timeout$matcon,
  .limit          = .lP$Params$Limit,            # NULL takes everything; n is a fixed cohort
  .report_every   = .lP$Params$ReportEvery
)
```

## Running LexNLP

```{r}
#| label: extract-lexnlp

tab_pass_lexnlp <- cor_pass(
  .con            = con_lexnlp,
  .family         = "lexnlp",
  .entity         = .lP$Plan$Entities[[which(.lP$Plan$Family == "lexnlp")]],
  .describe       = tab_describe,
  .stage_path     = fs::path(.lP$Output$Stage, "lexnlp-chunk.parquet"),
  .stage_dir      = fs::path(.lP$Output$Stage, "lexnlp"),
  .chunk_size     = .lP$Params$ChunkSize,
  .read_workers   = .lP$Params$ReadWorkers,
  .engine_workers = .lP$Params$EngineWorkers,
  .batch_size     = .lP$Params$Batch$lexnlp,
  .timeout        = .lP$Params$Timeout$lexnlp,
  .limit          = .lP$Params$Limit,
  .report_every   = .lP$Params$ReportEvery
)
```

## What the pass did

```{r}
#| label: report-pass

tab_pass <- dplyr::bind_rows(tab_pass_matcon, tab_pass_lexnlp)

cor_report_pass(.tab = tab_pass, .n_corpus = n_corpus)
```

**A capped run is a fixed cohort, so re-rendering it does nothing.** `Limit` names the same *n*
documents every time -- the first *n* of the corpus in hash order -- and this pass extracts whichever
of them the ledger does not already hold. That makes a rehearsal repeatable: the second render reports
an empty queue, and a coverage figure from one render can be compared with the next. Raising the
number extends the cohort rather than replacing it, so the work already done is kept.

**Cheapest family first**, so a pass interrupted in the expensive one still leaves the other complete.
Measured on the corpus at twenty-four workers, matcon runs at roughly 150 documents a second and
LexNLP at 20, so matcon is under two hours and LexNLP is the overnight job. Both are faster than
04A's benchmark predicted -- that benchmark ran at five workers over 320 documents, so it amortised
interpreter and container startup badly and understated the cheap family by nearly a factor of six.

**Only the read is parallel.** The extractors are subprocesses already running their own workers;
adding R-side concurrency around them would contend rather than help. The daemons read parquet files
off the mirror and are finished before the container starts, so the two never compete for anything.

**A failure is recorded rather than retried, and that is a correction.** The first version of this
document logged failures and sent them again on every render, on the reasoning that a mount which
hiccuped must not be blacklisted. The reasoning was right and the consequence was not: 736 documents
in this corpus hold no text, so the queue never emptied, the failure log grew by 736 rows a render,
and the status report advised re-rendering to continue -- advice that could not work.

They now get a ledger row with status `error`, which excludes them, counts them honestly, and leaves
them recoverable by hand. The evidence that they are permanent rather than transient is independent:
**03F's classification pass over the same population failed on the same 736 documents.** Two passes,
different engines, identical count.

Two exclusions, two prospects. A **timeout** may complete under a longer cap. An **error** is a
document with no text, and no cap changes that.

# Validation

## Checking matcon

```{r}
#| label: validate-matcon

lst_valid_matcon <- cor_report_validation(
  .con       = con_matcon,
  .family    = "matcon",
  .describe  = tab_describe,
  .entity    = .lP$Plan$Entities[[which(.lP$Plan$Family == "matcon")]],
  .n_offsets = .lP$Params$OffsetSample
)
```

## Checking LexNLP

```{r}
#| label: validate-lexnlp

lst_valid_lexnlp <- cor_report_validation(
  .con       = con_lexnlp,
  .family    = "lexnlp",
  .describe  = tab_describe,
  .entity    = .lP$Plan$Entities[[which(.lP$Plan$Family == "lexnlp")]],
  .n_offsets = .lP$Params$OffsetSample
)
```

**The offset check is a sample here and every span in 04A, and the reason is structural rather than
cost.** 04A's spans all index one file, so verifying them is one read. The corpus text is 1.19 million
separate parquets, so verifying every span means reading the corpus a second time.

A systematic failure -- a byte rather than code-point slice, a truncation the extractor did not report
-- shows in any sample at all. A failure confined to a handful of documents would not, and nothing
here claims otherwise. The draw is seeded, so a re-render checks the same documents and a new failure
is a new finding rather than a new sample.

**An empty store is not a pass.** Both checks are satisfied by having nothing to check, which is
exactly how 04A's first version reported two green ticks on a store that held nothing at all. Each
reports the size of what it checked, and a store with no spans says so.

# Results

## Corpus coverage, against the labelled sample

```{r}
#| label: report-summary

tab_summary <- dplyr::bind_rows(
  cor_summary(.con = con_matcon, .family = "matcon", .n_corpus = n_corpus),
  cor_summary(.con = con_lexnlp, .family = "lexnlp", .n_corpus = n_corpus)
)

# 04A's coverage on the labelled sample, read from its own stores rather than restated here.
con_sample <- ner_attach(
  .dir      = fs::path(
    init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"), "Output"
  ),
  .families = c("matcon", "lexnlp")
)

tab_sample_cov <- purrr::map(c("matcon", "lexnlp"), \(.f) {
  con_ <- ner_db_connect(
    .db_path = ner_db_path(
      .dir = fs::path(
        init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
        "Output"
      ),
      .family = .f
    ),
    .read_only = TRUE
  )
  on.exit(DBI::dbDisconnect(con_, shutdown = TRUE), add = TRUE)
  n_ <- as.integer(DBI::dbGetQuery(con_, "SELECT COUNT(DISTINCT DocID) AS n FROM runs")$n[[1L]])
  ent_coverage(.summary = ner_db_summary(.con = con_), .family = .f, .n_doc = n_)
}) |>
  purrr::list_rbind()

DBI::dbDisconnect(con_sample, shutdown = TRUE)

cor_report_summary(.tab = tab_summary, .sample = tab_sample_cov)
```

**The comparison against the labelled sample is the point of running 04A first.** Every one of these
engines was measured on 4,398 documents whose classification is known; if the corpus rate differs
sharply from the sample rate, either the sample is not representative of the corpus for that entity
or something in this pass is wrong. Both are findings worth having before a rule is written against
these spans, and the two are told apart by reading spans rather than by reading the table.

**The manifest is printed with the results deliberately.** A reader of this page can say which version
of which extractor produced the corpus without opening a store -- and when the gazetteer is next
revised, the hash beside these rows is what says whether they predate it.

# Deployment

## The artifacts

```{r}
#| label: deploy-summary

cor_report_artifacts(
  .dir      = .lP$Output$Store,
  .families = c("matcon", "lexnlp")
)
```

Two databases, and they are contracts rather than conveniences. 04B reads them; every offset in them
indexes the mirror's parsed text, which nothing in this repository rewrites.

# Overview

## What is finished and what is outstanding

```{r}
#| label: overview

tab_status <- dplyr::bind_rows(
  cor_status(
    .con    = con_matcon, .family = "matcon", .describe = tab_describe,
    .entity = .lP$Plan$Entities[[which(.lP$Plan$Family == "matcon")]]
  ),
  cor_status(
    .con    = con_lexnlp, .family = "lexnlp", .describe = tab_describe,
    .entity = .lP$Plan$Entities[[which(.lP$Plan$Family == "lexnlp")]]
  )
)

cor_report_status(.tab = tab_status)

tbl_say(
  .tab   = dplyr::select(tab_summary, "Family", "Model", "Entity", "NSpan", "NDoc",
                         "Coverage", "SpansPerDoc"),
  .title = "What the corpus pass produced"
)
```

## Closing the stores

```{r}
#| label: disconnect

# LAST, AND DELIBERATELY SO. Every section above reads from an open connection, and a disconnect
# written where the work happened would silently strand any section added below it. If a section is
# added, it goes above this.
DBI::dbDisconnect(con_matcon, shutdown = TRUE)
DBI::dbDisconnect(con_lexnlp, shutdown = TRUE)

cli::cli_alert_success("Both stores closed.")
```

**No figures.** 04A carries the positional profiles and the agreement matrix, drawn on a sample where
every engine ran including the ones excluded here. Repeating them on the corpus with two families
would say less, and what the corpus adds -- scale -- is a table rather than a picture.

# Next

**04B** turns these spans into variables: one document per entity, each proposing rules and measuring
what they keep and discard against an unadjusted baseline. Nothing there re-extracts; every rule is a
query against the offsets stored here.

Two things are open and neither blocks 04B. **The anchors** -- the filer's own name, filing date and
registered addresses, against which an extracted entity can be scored -- are derived from the register
rather than from any extraction, so they can be built wherever 04B wants them. And **the release**,
which fans these attachment-level spans back out to all 1,462,939 registrant copies on
`HashDocument`, carrying the population flags as columns so a reader subsets without the register.
