---
title: "Entity Extraction over the Corpus (04C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks. Figure geometry is declared once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Store.R supersedes ner_db_init(), ner_db_append() and ner_db_clear(), so
# it must come AFTER _NER.R or the flat-table versions win and the corpus store is built without the
# per-label tables -- which would be discovered only after the run.
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A supplies the console formatter; 04A the entity vocabularies, the store overview, the
# description helpers and the relabelling clear. THE CORPUS IS EXTRACTED BY THE CODE THE SAMPLE WAS
# EXTRACTED WITH, pointed at documents that carry no labels -- which is what makes the two stores
# comparable at all.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),
  .name_script = .name_script
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),
  .name_script = .name_script  # resolves to 1_code/04C-EntityCorpus.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran nine engines over 4,398 labelled contracts and produced the evidence for choosing between
them. **This document runs the chosen ones over the whole Exhibit-10 corpus** -- around 1.46 million
documents -- and writes their spans into a store with the same schema.

It resolves nothing, selects nothing, and reports no finding beyond what came back.

## Why this can run before the rules are settled

Because extraction is rule-independent. Every candidate carries its offsets into the canonical text,
every engine reads the whole document, and every window a rule might later impose is a `WHERE`
clause over what is already stored.

The asymmetry is the whole argument: **a rule decided in six weeks costs a query; a rule decided
before extraction and then changed costs the pass.** So the pass runs now and 04B is argued in
parallel.

## The engine set, and why these

Declared here rather than read from a policy artifact. Engine evidence lives in 04A, the choice is
an argument, and an argument belongs where a reader can see it.

| Engine | Labels | Why |
|:--|:--|:--|
| `lexnlp` | ORG, GPE, DATE, MONEY | Settled for ORG: contrast 3.16-6.81 against 0.68-1.33 for spaCy |
| `paper:gazetteer-v1` | GPE | The other place candidate, and the only one that reaches cities |
| `paper:dateregex-v2` | DATE | The other date candidate; it reaches expiry cues in 415 documents against LexNLP's 113 |
| `paper:moneyregex-v6` | MONEY | Keeps the currency symbol where the alternatives drop it |
| `paper:redaction-v1` | REDACT | The only engine |

Two labels carry two engines each, deliberately. DATE and GPE are **undecided**, and undecided
means both candidates run: the choice needs role-level analysis that does not exist yet, and
re-running a corpus pass to recover a discarded engine costs far more than storing it.

## What the corpus pass now carries that the last one did not

Every engine in the plan resolves as well as finds. LexNLP writes the parsed date, the ISO code, the
company legal form and the amount; `dateregex-v2` writes a parsed date for 99.6% of what it matches;
`moneyregex-v6` writes an amount and an ISO currency. Those columns had nowhere to live in the flat
store and were discarded at the seam for the whole life of the project.

**This is the reason not to defer.** LexNLP's geoentity pass costs around five seconds a document
and roughly three and a half days at twenty workers over the corpus. A pass that finds the spans and
throws the resolution away is a pass that has to be repeated, and this is not a repeatable pass.

## What is absent, and what that costs

**No spaCy, so no PERSON.** The transformer is the only usable person engine -- contrast 3.93
against 1.55, 1.35 and 1.08 for the CNN models -- and it runs at `n_process = 1` because a single
Metal device cannot be shared across workers. That is a different order of cost from everything
above.

It is also **recoverable**. The ledger records a document against an engine, so adding the
transformer later extracts only the transformer and touches nothing already written. Postponing it
is a deferral, not a foreclosure.

## Resumption is the ledger, not the output

A pass killed at any point resumes by asking the store what is missing. There is no checkpoint file
and no partial-progress state to reconcile: `ner_run()` records a document against an engine when
its rows are written, so restarting is idempotent by construction.

The corollary is that **adding an engine makes every document incomplete again** -- correctly -- and
`ent_store_status()` is where that becomes visible rather than surprising.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus tree
    # conjured into existence would report itself present while holding nothing.
    DirCorpus   = fs::path("../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/"),
    MetaData    = fs::path("../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet"),
    LandingPage = fs::path("../pMatDisc/2_output/01-GetEDGAR/Output/LandingPage.parquet")
  ),
  Cache = list(
    CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet") # DocID to Path index
  ),
  Store = list(
    NerDB    = utils_file_path(.dir_main, "Store", "CorpusCandidates.duckdb"),
    Manifest = utils_file_path(.dir_main, "Store", "manifest.parquet"),
    # Plain text, one line per chunk, appended. This is what makes a two-day pass watchable: tail it
    # from another terminal, read it after RStudio has been closed, check it on a machine running
    # headless. Console output is buffered by knitr and gone when the session ends; a file is not.
    Progress = utils_file_path(.dir_main, "Store", "progress.log")
  ),
  Work = list(
    Dir = utils_file_path(.dir_main, "Work")   # per-chunk text parquet, deleted as it is consumed
  ),
  Param = list(
    ChunkSize  = 50000L,  # documents held in memory at once; not a unit of resumption
    IndexRerun = FALSE,  # TRUE re-walks the tree; FALSE reuses the cached index
    Device     = "auto",
    # The switch that decides whether this render is a rehearsal or the release. An integer draws
    # that many documents at random and writes to a separate store; NULL processes the corpus.
    # SET AN INTEGER, READ THE THROUGHPUT, THEN SET NULL. Every rate this project has is from the
    # 4,398-document sample, whose length distribution is not the corpus's.
    Limit      = NULL
  )
)

fs::dir_exists(.lP$Input$DirCorpus)
fs::file_exists(.lP$Input$MetaData)
```

# The plan

```{r}
#| label: declare-plan
tab_plan <- tibble::tribble(
  ~Combo,                  ~Labels,
  "lexnlp",                c("ORG", "GPE", "DATE", "MONEY"),
  "paper:gazetteer-v1",    "GPE",
  "paper:dateregex-v2",    "DATE",
  "paper:moneyregex-v6",   "MONEY",
  "paper:redaction-v1",    "REDACT"
)

lst_labels <- ent_plan_labels(.plan = tab_plan)   # named list, as ner_run() takes it

tab_plan |>
  dplyr::mutate(Labels = purrr::map_chr(.data$Labels, \(.x) paste(sort(.x), collapse = ", "))) |>
  tbl_say(.title = "Engines and the labels each is asked for")
```

Labels are passed **per combination**, not as one vector, and the difference is not cosmetic: asking
the gazetteer for DATE returns nothing, while asking LexNLP for GPE runs its geoentity pass, which
costs more than its other three extractors combined.

```{r}
#| label: declare-knobs
.KNOBS <- list(
  # TWENTY WORKERS, NOT TWENTY-FOUR, and the reason is the machine rather than the extraction.
  # Throughput rises 1.60x from eight workers to sixteen and only 1.15x from sixteen to twenty-four
  # on a 28-core M3 Ultra: twenty performance cores and eight efficiency cores, and workers past the
  # twentieth land on the latter at roughly a third the speed.
  #
  # BATCH SIZE EIGHT FOR LEXNLP IS MEASURED, NOT INHERITED. 04A's sweep puts it at 7.92 doc/s
  # against 1.32 at a batch of 128 -- six times slower for identical output, because the pool hands
  # out one task per batch and a large batch strands whichever worker draws a 500,000-character
  # credit agreement while the rest finish early.
  #
  # The 240-second cap is per extractor per document and exists for the geoentity pass, which scans
  # a dictionary over the whole text. At 60 the longest agreements time out, and they time out
  # SYSTEMATICALLY in the longest documents -- the worst possible place for a missing-at-random
  # assumption to fail. Four such timeouts appeared in the sample even at 240.
  "lexnlp"              = list(n_process = 20L, batch_size = 8L,  timeout = 240L),
  # The gazetteer's sweep is sub-second in every cell on 200 documents, so 32 nominally beats 8 by
  # noise. Taken anyway: at corpus scale the difference is 0.6 hours against 0.9, and neither
  # setting can be wrong when the engine runs at several hundred documents a second.
  "paper:gazetteer-v1"  = list(n_process = 20L, batch_size = 32L, timeout = 120L),
  # dateregex was single-process because the extractor had no Pool, not because regex resists
  # parallelism. It has one now. The cap is non-zero because the greedy overlap resolution is
  # quadratic in candidate count and a date table can yield tens of thousands in one document.
  "paper:dateregex-v2"  = list(n_process = 20L, batch_size = 64L, timeout = 120L),
  "paper:moneyregex-v6" = list(n_process = 20L, batch_size = 64L, timeout = 120L),
  "paper:redaction-v1"  = list(n_process = 20L, batch_size = 64L, timeout = 120L)
)

ent_check_plan(
  .plan  = tab_plan,
  .knobs = .KNOBS
)
```

Checked before any work starts rather than discovered inside the extraction loop. `ner_run()`
dispatches through a chain of branches, so an engine it does not cover would abort after the index
is built and the first chunks have run -- hours into a corpus pass.

# The corpus

```{r}
#| label: build-index
tab_index <- ent_corpus_index(
  .dir_corpus   = .lP$Input$DirCorpus,
  .path_meta    = .lP$Input$MetaData,      # filer name, CIK, filing date, HashIndex
  .path_landing = .lP$Input$LandingPage,   # registered addresses, joined via HashIndex
  .path_cache   = .lP$Cache$CorpusFiles,
  .rerun        = .lP$Param$IndexRerun,    # FALSE reuses the cached walk
  .limit        = .lP$Param$Limit          # integer = rehearsal draw; NULL = the corpus
)
```

The tree walk is cached because it is slow and does not change between renders. `IndexRerun = TRUE`
is the only way to pick up documents added since -- worth remembering rather than assuming a render
sees the current tree.

The metadata join carries the EDGAR facts alongside each document so that 04D has an anchor without
reaching back to the raw exports.

# The store

Adding a label to an engine no longer forces a re-extraction. The ledger is keyed on the label as
well as the combination, so a policy addition leaves the existing labels marked done and only the
addition is missing -- which `ner_run()` then groups and dispatches on its own. There is nothing to
clear and nothing to reconcile, which is why the mechanism that used to do both is gone.

```{r}
#| label: check-manifest
ent_corpus_manifest_sync(
  .path_manifest = .lP$Store$Manifest,
  .manifest      = ent_corpus_manifest(
    .index  = tab_index,
    .run    = tab_plan$Combo,
    .labels = lst_labels
  )
) |>
  tbl_say(.title = "Store settings against this run")
```

# Extraction

```{r}
#| label: store-status
.dir_store <- fs::path_dir(.lP$Store$NerDB)   # the timing log lives beside the store

ent_store_status(
  .db_path  = .lP$Store$NerDB,
  .n_corpus = ent_corpus_n(.index = tab_index, .what = "docs"),
  .run      = tab_plan$Combo,
  .dir      = .dir_store    # supplies the measured rate for the remaining-time estimate
)

tab_todo <- ent_pending(
  .db_path = .lP$Store$NerDB,
  .index   = tab_index,
  .run     = tab_plan$Combo,
  .labels  = lst_labels   # complete means every combination AND label, not every combination
)
```

The first thing a reader of a two-day pass needs. A second render finds every document extracted, so
the loop has nothing to do and prints nothing -- which is indistinguishable from a loop that is
broken. This says "finished" out loud.

```{r}
#| label: extract-corpus
chunks_ <- if (nrow(tab_todo) == 0L) {
  list()
} else {
  split(tab_todo, ceiling(seq_len(nrow(tab_todo)) / .lP$Param$ChunkSize))
}

if (length(chunks_) == 0L) {
  cli::cli_alert_success(
    "Nothing to extract: every document in scope is already in the store. Raise Limit or set it \\
     to NULL to take in more of the corpus."
  )
}

prog_ <- ent_progress_new(
  .n_chunks = length(chunks_),
  .n_docs   = nrow(tab_todo),
  .path_log = .lP$Store$Progress   # tail -f this to watch a long pass from anywhere
)

tab_timing <- purrr::imap(chunks_, function(.chunk, .i) {
  out_ <- ent_extract_corpus_chunk(
    .chunk    = .chunk,
    .db_path  = .lP$Store$NerDB,   # one store for the whole corpus
    .run      = tab_plan$Combo,
    .labels   = lst_labels,        # per combination, not one vector for every engine
    .dir_work = .lP$Work$Dir,      # the chunk's text parquet, written and deleted
    .knobs    = .KNOBS,
    .device   = .lP$Param$Device
  )
  ent_write_timing(
    .dir     = .dir_store,
    .chunk   = .i,
    .n_docs  = out_$nDocs,   # documents in the chunk
    .n_new   = out_$nNew,    # of which this many actually had to be extracted
    .seconds = out_$Seconds
  )
  ent_progress_step(.progress = prog_, .n_new = out_$nNew, .seconds = out_$Seconds)
  out_
}) |>
  purrr::list_rbind()
```

Chunked because 1.46 million documents do not fit in memory, and because a chunk boundary is a
natural place to write progress. **The chunk is not the unit of resumption** -- the ledger is -- so a
pass killed mid-chunk loses only the documents whose rows had not yet been written.

# Description

```{r}
#| label: summarise-store
.ov <- ent_overview(.db_path = .lP$Store$NerDB)

ent_report_store(.ov = .ov)
```

```{r}
#| label: report-throughput
ent_report_throughput(
  .dir      = .dir_store,
  .n_corpus = ent_corpus_n(.index = tab_index, .what = "docs"),
  .n_cands  = sum(.ov$ledger$Candidates)   # what has been written, for the store-size projection
)
```

**This is what the rehearsal is for.** 04A measures LexNLP at 7.92 documents per second on a
200-document random draw at these settings, which projects to roughly 51 hours over 1.46 million --
a little over two days, with the four regex engines adding comparatively little. But that draw comes
from 4,398 hand-picked material contracts with a median around 33,000 characters, and the corpus
carries every Exhibit 10 filed, including short amendments and very long credit agreements. Read the
per-engine rate here against that projection before setting `Limit` to `NULL`.

No cross-engine agreement is computed. On the sample that produced four million merged mentions from
4,398 documents; at corpus scale it would be roughly 1.3 billion, and the question it answers --
which engine adds what over another -- was already answered in 04A on documents that carry labels.

# Deployment

```{r}
#| label: deploy-summary
tibble::tibble(
  Artifact = c("Candidate store", "Run manifest", "Corpus index"),
  Path     = c(.lP$Store$NerDB, .lP$Store$Manifest, .lP$Cache$CorpusFiles)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04C")
```

```{r}
#| label: deploy-guard
if (!is.null(.lP$Param$Limit)) {
  cli::cli_alert_warning(
    "THIS IS A REHEARSAL. Limit is {(.lP$Param$Limit)}, so the store holds a random draw and not \\
     the corpus. Nothing downstream should read it."
  )
} else {
  cli::cli_alert_success("Full corpus pass; the store is the deliverable.")
}
```

Stated rather than inferred. A rehearsal store and a release store have the same name and the same
schema, and the only thing separating them is a parameter three hundred lines above.

# Next

**04B** develops the rules on the labelled sample, where the EDGAR anchor makes a rule testable.
Nothing here depends on that work and nothing there is blocked by this pass.

**04D** applies those rules to this store and resolves spans into published variables. Every window
a rule imposes is a `WHERE` clause over offsets already written, which is why the order of these two
documents does not matter.

**Persons are not extracted here.** Adding `spacy:en_core_web_trf` later costs one transformer pass
over the corpus and touches nothing already written -- the ledger sees the new combination as
missing for every document and leaves the five above alone. Whether that is worth doing is a
question for 04B, which is where the counterparty rule will show whether person spans carry a
variable or not.
