---
title: "Entity Resolution -- Spans into the Published Variables (04C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                          # message = FALSE would discard this document's entire output
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,        # fixed for every figure; only height varies, and only with row count
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# 03A owns the console formatter. 04B owns the anchor logic, the session helper and the date
# cleaner; sourcing it rather than copying is what keeps the anchor this document validates against
# identical to the one 04B measured with.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "04B-EntityMeasure"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04C-EntityResolve.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A extracted candidates and described them. 04B measured which engine to keep, which window to
read, and which of the two reading sessions' rules survive contact with the EDGAR anchors. Neither
produced a variable.

This document does. It applies the settled policy to the candidate store, assigns a role to each
surviving span, and collapses those into one row per contract carrying the parties, the contract
dates, the party locations, and what can honestly be said about value.

## It resolves what 04E will produce, not what 04A extracted

The store holds eight engines over full text. The corpus pass will run **one engine per label over a
capped window**. Resolving the union here would validate a pipeline nobody deploys, so the candidate
set is filtered through `extraction_policy.parquet` first and every number below describes the
deployed configuration rather than the extraction that informed it.

## Three constraints inherited from the measurement

**Role attaches to an occurrence, never to a string.** A reading session found "New York" serving as
a party address, as the governing law, as a court venue and inside an exchange name within one
contract. Any design that resolves a place once per document is wrong before it starts, so the
geographic output below is a mix of roles rather than a location.

**Party counts need deduplication.** Mentions per document are inflated by length; mentions per
thousand characters are deflated by repetition. The truth is bracketed between two measures that are
each wrong in a known direction, and only collapsing names to a common form resolves it.

**A stop matches a whole span, never a substring.** A rule against `company` applied as a substring
removes *Blue Ridge Real Estate Company*, which is a party.

## The duration measure is the point of the date section

The published contract term is the latest date found in a document minus its filing date. A referee
observed that it carries a standard deviation of **46.8 years** on debt contracts -- impossible for
an instrument whose mean term is under three years, and the signature of statutory references and
long-dated maturities entering a maximum.

Both measures are computed here, on the same documents, side by side. The difference is shown rather
than argued.

## Money is the honest weak case and stays that way

EDGAR records no contract value, so nothing about amounts is validated the way parties, dates and
places are. Two things are still carried: the largest amount in a document, which a reading session
argued separates an aggregate principal from the per-share prices that repeat around it; and the
count of redaction markers, which is a variable in its own right because the figures withheld are
systematically the commercially material ones.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb",
    # Written by 04B: the surviving rules, and the engine and window per label.
    Kept    = "2_output/04B-EntityMeasure/rules_kept.parquet",
    Policy  = "2_output/04B-EntityMeasure/extraction_policy.parquet"
  ),
  Output = list(
    Roles = utils_file_path(.dir_main, "span_roles.parquet"),          # one row per resolved span
    Vars  = utils_file_path(.dir_main, "contract_variables.parquet")   # one row per contract
  ),
  Params = list(
    CtxMax  = 400L,    # widest context materialised; caps the reach of any rule
    HeadPos = 0.10,    # an organisation this far into the document, with no cue, still reads as a
                       # party: the preamble is where parties are named and a cue list is never
                       # complete
    # Redaction markers closer than this belong to one withheld thing. A redacted schedule puts a
    # marker in every cell, and 85% of all markers on this sample come from 106 documents, so the
    # count that means "how much was withheld" is regions rather than markers.
    RedactGap = 200L
  )
)

# Same formats 04B parsed with. Naming them here rather than sourcing a constant keeps the two
# documents' date handling visibly identical instead of implicitly so.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", "%b %d, %Y", "%b %d %Y",
  "%d %B, %Y", "%d %B %Y", "%d %b, %Y", "%d %b %Y",
  "%m/%d/%Y",  "%d/%m/%Y", "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d", "%d-%b-%Y", "%m.%d.%Y"
)

fs::file_exists(unlist(.lP$Input))
```

# Policy

```{r}
#| label: read-policy
tab_policy <- ent_read_policy(.path = .lP$Input$Policy)
tab_keys   <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)
tab_rules  <- arrow::read_parquet(.lP$Input$Kept)

clf_say_table(
  .tab = tab_policy |>
    dplyr::select(Label, Combo, CapChars, TailChars) |>
    dplyr::mutate(dplyr::across(c(CapChars, TailChars), as.integer)),
  .title = "Extraction policy this document resolves"
)
```

A tail of zero is the ordinary prefix case. Geography is the label that needs a non-zero one: a
governing-law clause sits in the final fifth of a contract and no prefix reaches it, which the
character-window grid in 04B showed costs twenty-six points of document-level recall.

```{r}
#| label: build-deployed
con <- ent_session(.db_path = .lP$Input$Store, .keys = tab_keys)

n_deployed <- ent_deploy_candidates(
  .con       = con,
  .policy    = tab_policy,     # one engine per label, and that label's window
  .path_text = .lP$Input$Text  # supplies document lengths, so the tail is measured from the end
)
```

# Roles

The document's own definitions come first, because they are the strongest of the organisation
filters and they are cheap. A reading session put it plainly: a span that is a single capitalised
common noun already introduced in parentheses -- Tenant, Company, Buyer, Holder -- is never an
organisation name, and a rule dropping those is worth more than the hand-written stop list beside
it. What makes it stronger than a stop list is that it is **per document**: `Company` is a defined
term in the contract that defines it, and part of a name in *Blue Ridge Real Estate Company*.

```{r}
#| label: build-defined-terms
ent_defined_terms(.con = con, .path_text = .lP$Input$Text)
```

```{r}
#| label: assign-roles
n_roles <- ent_assign_roles(
  .con       = con,
  .path_text = .lP$Input$Text,
  .rules     = tab_rules,          # the rules 04B measured, with their lifts
  .ctx_max   = .lP$Params$CtxMax
)
```

Where several cues fire on one span with different roles, the highest measured lift wins. That is
the only non-arbitrary tie-break available and it uses the measurement rather than an ordering
someone chose: it prefers the rule the anchor showed to be most concentrated on the thing it claims
to mark.

A span no cue reaches keeps a null role and is carried rather than discarded. For organisations that
matters, because position in the preamble is itself evidence and the party resolver uses it.

# Variables

```{r}
#| label: resolve-parties
tab_parties <- ent_resolve_parties(.con = con, .head_pos = .lP$Params$HeadPos)
tab_dates   <- ent_resolve_dates(.con = con, .formats = .DATE_FORMATS)
tab_places  <- ent_resolve_places(.con = con)
tab_value   <- ent_resolve_value(.con = con, .gap = .lP$Params$RedactGap)

# The published measure has to come from the UNFILTERED store over full text. Taking it from the
# deployed set leaves only preamble dates, every one of which precedes the filing, and the measure
# comes out negative -- a different quantity wearing the published name.
tab_pubdates <- ent_published_dates(.con = con, .formats = .DATE_FORMATS)

tab_vars <- ent_assemble(
  .keys     = tab_keys,
  .parties  = tab_parties,
  .dates    = tab_dates,
  .places   = tab_places,
  .value    = tab_value,
  .pubdates = tab_pubdates
)

ent_report_resolve(.n_deployed = n_deployed, .n_roles = n_roles, .tab = tab_vars)
```

# Contract term

```{r}
#| label: compare-duration
tab_duration <- ent_report_duration(.tab = tab_vars)
```

Read the standard deviation and the maximum together. The published definition takes the latest date
anywhere in the document, so a reference to an Act of 1933 or a maturity in 2099 enters the term of
a contract that runs for two years, and a single such document moves the moment for the whole class.
The role-classified measure can only see dates a cue reached, which is a narrower set and a smaller
one -- the trade is coverage for a measure that means what it says.

## Does the window preserve an expiry date?

The character grid in 04B chooses a window on how often it recovers the **anchor**, and the date
anchor is the contract's own date, which sits in the preamble. Nothing there measures whether an
expiry date survives the same window. A head-only cap returned one for 22 documents of 4,398 while
the same cues fire in their thousands over full text, so the window was chosen on one quantity and
applied to another.

```{r}
#| label: measure-expiry-coverage
ent_role_coverage(
  .con   = con,
  .label = "DATE",
  .roles = "expiry",       # the role the anchor cannot speak to and the window was chosen without
  .head  = c(3000L, 5000L, 10000L),
  .tail  = c(0L, 2000L, 5000L, 10000L)
) |>
  dplyr::mutate(PctDocs = clf_pct(.data$PctDocs)) |>
  clf_say_table(.title = "Documents with an expiry date inside the window")
```

Read the tail column against the head column. If a tail of five thousand characters recovers more
than trebling the head does, the term clause sits at the end of a contract and no prefix will reach
it however generous.

# Places

```{r}
#| label: report-places
tab_placemix <- ent_report_places(.tab = tab_vars)
```

This is the answer to the question a reviewer asked of Figure 6: whether the countries counted are
the locations of the contracting entities or mentions of somewhere else. It is an answer about
**occurrences**, because the same place name serves several roles inside one contract and a
per-document location would be the wrong object to report.

# Validation

```{r}
#| label: validate-variables
tab_val <- ent_report_validation(.tab = tab_vars)
```

The first row is the one carrying weight. The filer is a party to its own contract, so a resolved
party set that omits it is missing a party that is certainly there -- and unlike a precision figure,
this needs no hedging about counterparties the anchor cannot see.

The third row is arithmetic rather than evidence: a contract cannot end before it starts, and
anything below 100% there is a resolution error rather than a finding.

# Robustness

```{r}
#| label: inspect-by-class
tab_vars |>
  dplyr::summarise(
    NDocs        = dplyr::n(),
    MedParties   = stats::median(.data$NParties, na.rm = TRUE),
    PctWithStart = mean(!is.na(.data$ContractStart)),
    PctWithEnd   = mean(!is.na(.data$ContractEnd)),
    PctWithValue = mean(!is.na(.data$MaxAmount)),
    MedRedact    = stats::median(dplyr::coalesce(.data$NRedact, 0L)),
    PctRedacted  = mean(dplyr::coalesce(.data$NRedact, 0L) > 0L),
    .by = Class
  ) |>
  dplyr::arrange(dplyr::desc(.data$NDocs)) |>
  dplyr::mutate(dplyr::across(dplyr::starts_with("Pct"), \(.x) clf_pct(.x))) |>
  clf_say_table(.title = "Resolution by contract type")
```

Coverage is not uniform and should not be reported as though it were. A variable present in a third
of leases and nine tenths of credit agreements is two different variables, and the column that
matters for the paper is which contract types can carry each one at all.

```{r}
#| label: inspect-unassigned
DBI::dbGetQuery(con, paste0(
  "SELECT Label, COUNT(*) AS Spans, ",
  "  SUM(CASE WHEN Role IS NULL THEN 1 ELSE 0 END) AS NoRole ",
  "FROM roles GROUP BY Label ORDER BY Label"
)) |>
  dplyr::mutate(
    dplyr::across(c(Spans, NoRole), as.integer),
    PctNoRole = clf_pct(.data$NoRole / .data$Spans)
  ) |>
  clf_say_table(.title = "Spans no cue reached")
```

A high share here is not a failure of the rules so much as a statement about how much of the
candidate pool is noise: most organisation spans in a contract are not parties, and a cue list that
labelled all of them would be labelling the wrong thing.

# Deployment

```{r}
#| label: write-artifacts
DBI::dbExecute(con, paste0(
  "COPY (SELECT DocID, Label, Start, Stop, Span, SpanNorm, LabelRaw, Pos, Role FROM roles) TO '",
  as.character(fs::path_abs(.lP$Output$Roles)), "' (FORMAT PARQUET)"
))
arrow::write_parquet(tab_vars, .lP$Output$Vars)

DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = c("Span roles", "Contract variables"),
  Path     = c(.lP$Output$Roles, .lP$Output$Vars)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  clf_say_table(.title = "Written by 04C")
```

# Overview

## The contract term, both ways

```{r}
#| label: fig-duration
#| fig-height: 3.4
#| fig-cap: "Contract term under the published definition and under role classification."
tab_vars |>
  dplyr::select(DocID, DurationPaper, DurationNew) |>
  tidyr::pivot_longer(-DocID, names_to = "Measure", values_to = "Years") |>
  dplyr::filter(!is.na(.data$Years), .data$Years > -1, .data$Years < 60) |>
  ggplot2::ggplot(ggplot2::aes(x = Years)) +
  ggplot2::geom_histogram(bins = 60) +
  ggplot2::facet_wrap(~Measure, nrow = 1, scales = "free_y") +
  ggplot2::labs(x = "Contract term (years)", y = "Documents") +
  ggplot2::theme_bw(base_size = 9)
```

The published panel is the one to read for its right tail; the axis is truncated at sixty years and
the values beyond it are the reason the standard deviation is what a referee found it to be.

## Place occurrences by role and contract type

```{r}
#| label: fig-place-roles
#| fig-height: 4.6
#| fig-cap: "Share of place occurrences carrying each role, by contract type."
tab_vars |>
  dplyr::select(Class, NPartyAddress, NIncorporation, NGoverningLaw, NPerformance,
                NIncidental, NUnassigned) |>
  tidyr::pivot_longer(-Class, names_to = "Role", values_to = "N") |>
  dplyr::summarise(N = sum(.data$N, na.rm = TRUE), .by = c(Class, Role)) |>
  dplyr::mutate(Share = .data$N / sum(.data$N), .by = Class) |>
  ggplot2::ggplot(ggplot2::aes(x = Share, y = Class, fill = Role)) +
  ggplot2::geom_col() +
  ggplot2::scale_x_continuous(labels = scales::percent) +
  ggplot2::labs(x = "Share of place occurrences", y = NULL) +
  ggplot2::theme_bw(base_size = 9)
```

## Everything again

```{r}
#| label: report-everything
ent_report_all_resolve(.n_deployed = n_deployed, .n_roles = n_roles, .tab = tab_vars)
```

# Next

**04E** applies the same policy to the corpus. It needs nothing this document has not written: the
engine and window come from `extraction_policy.parquet`, the rules from `rules_kept.parquet`, and
the resolution logic is the functions above run over a larger store.

Two things this document cannot settle, and they should reach the paper as limitations rather than
be discovered later. **Money remains unvalidated** -- the largest-amount heuristic and the redaction
count are carried because they are the best available, not because either has been checked against
anything. And **nothing here validates the variables themselves**: the anchors confirm that the
filer appears among the resolved parties and that the contract date precedes its filing, which
establishes the extraction is finding real things, not that the party count, the term or the value
are right. That needs a document-level gold set of fifty to eighty contracts, and it is the one
piece of this family that cannot be built from EDGAR facts or a reading session.
