---
title: "Entity Apply -- The Five Rules at Corpus Scale (04D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ONE ORDERED LIST, SOURCED HERE AND NAMED TO THE DAEMONS. A mirai daemon is a fresh R process with
# none of this in it, and a closure does not carry its environment across a process boundary -- so a
# worker handed a function that calls ent_apply() finds no ent_apply(). Building the list once and
# walking it means the process that renders and the process that works load the same files in the
# same order, which two hand-written lists could not guarantee.
#
# THE COMMONS FIRST, AND init_create_script_fun() COMES FROM THEM. Naming the numbered scripts by
# that function before it exists is a bootstrap the render cannot survive, so the list is built in
# two steps: source what defines the resolver, then use it.
#
# ORDER IS LOAD-BEARING WITHIN THE FIRST GROUP. _Plots.R rebuilds its level registry empty every time
# it is sourced, so every library that registers a vocabulary must follow it -- _Entity.R and all
# five 04B files do.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# THE FIVE RULE LIBRARIES, SOURCED AND CALLED RATHER THAN COPIED. Not one rule is reimplemented in
# this document; every function it calls is the one that produced the sample's release.
.path_libs <- c(
  .path_libs,
  purrr::map_chr(
    c("03A-ClassifyPrepare", "04A-EntityExtract",
      "04B1-Rules-ORG", "04B2-Rules-GPE", "04B3-Rules-DATE",
      "04B4-Rules-MONEY", "04B5-Rules-REDACT"),
    \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
  )
)
purrr::walk(
  .x = utils::tail(.path_libs, 7L),
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

# .path_libs IS NOW THE WHOLE LIST IN ORDER, and it is what every daemon sources. The process that
# renders and the process that works therefore load the same files in the same order, which two
# hand-written lists could not guarantee.
#
# THIS DOCUMENT'S OWN LIBRARY IS APPENDED BELOW, once .path_fun has resolved it. A daemon runs
# apl_chunk_run(), which is defined there and not in any of the files above -- so a list holding only
# the rule libraries would give every worker five complete rule chains and nothing to call them
# with.

.name_script <- "04D-EntityApply"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04D-EntityApply.R
))

source(file = .path_fun, encoding = "UTF-8")

# APPENDED LAST, because a daemon calls apl_chunk_run() and it is defined in this file. Appended
# rather than named again, so the list a worker sources is exactly the list this process sourced,
# in the same order, plus the one file that defines the work.
.path_libs <- c(.path_libs, .path_fun)
```

# Purpose

This document applies the five 04B rules to every attachment 04C extracted, and writes **the same
four files 04B released** with the corpus in them instead of 4,398 documents.

## It decides nothing

04A extracted a sample and measured which family to trust. 04B built and scored a rule per entity
against facts EDGAR recorded. 04C extracted the whole corpus. Everything that could vary is declared
in Configuration below, printed in the render, and hashed into the chunk directory so a changed rule
cannot be served from a stale cache.

**An apply stage free to choose its own family or its own window** is one whose output depends on
which version of it last ran, and a released dataset cannot be defended on those terms.

## The rules are called, not copied

The five 04B libraries are sourced and their apply functions called on chunks of the corpus. That is
the project's own instruction -- shared tooling lives upstream and later scripts source it -- and it
is the mistake this family already made twice: `dte_term()` re-implemented `dateregex`'s TERM in R and
`red_words()` recounted what the register held. Both worked. Both could only ever work on the sample.

## Three things that were true of the previous version and are not now

**No chain opens a document.** `dte_describe()` cut a cue window out of the canonical text,
`geo_law()` scanned whole documents for governing-law language, and `mny_load()` read sixty characters
before every amount. All three now read `CueBefore` and `CueAfter`, stored at extraction. The text
staging this file used to do is gone entirely -- and with it the `Cues` dial that existed to switch
those reads off, and whose only effect at corpus scale was to delete the governing-law columns from
the release.

**The party chain is chunkable.** `ent_rule()`'s family-frequency gate admitted a shared leading token
as evidence of a corporate family when that token opened at most a given share of *documents*, and
`ent_apply()` computed the share from the spans it was handed -- so under chunking the denominator
became the chunk. Measured: **176 leading tokens fell on opposite sides of the threshold at 2,546
documents per chunk.** The gate is gone; grouping is word-prefix comparison *within* a document, which
needs no denominator. So ORG chunks with everything else.

**Every rule is per document, and that is checked rather than argued.** Validation runs the same
documents as one chunk and as several and compares all four outputs row for row.

## What comes out

| File | Shape | From |
|:--|:--|:--|
| `parties_geo.parquet` | one row per contract per party | 04B1's release, widened by 04B2 |
| `contracts_date.parquet` | one row per contract | 04B3 |
| `contracts_money.parquet` | one row per contract | 04B4 |
| `contracts_redact.parquet` | one row per contract | 04B5 |

Each is written by the same 04B function that wrote the sample's, and Validation runs each 04B
document's own dictionary check against the corpus file.

## How results are reported

Console tables throughout. **No figures** -- 04B carries the distributions, drawn on a sample where
every rule could be scored against an external fact. What the corpus adds is scale, which is a table.

## Where things are written

Four files under `Output/`, and one chunk directory per policy hash under `Chunks/`.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04C's corpus stores, one per family.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04C-EntityCorpus"),
      "Output"
    ),
    # THE CORPUS LABEL SPINE, AND IT IS A DIRECTORY. 03F-ClassifyApply writes
    # contract_labels_L<max_len>[_partial].parquet into a release folder, so the file name depends on
    # the token limit that produced it; apl_labels_path() resolves it and refuses a partial one.
    #
    # 03A's prepared file is the SAMPLE's, and using it here would restrict this pass to 4,398
    # documents without saying so.
    Labels = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03F-ClassifyApply"),
      "release"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    ),
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet")
  ),
  Output = list(
    Chunks = utils_file_path(.dir_main, "Chunks"),
    Release = list(
      Parties = utils_file_path(.dir_main, "Output", "parties_geo.parquet"),
      Date    = utils_file_path(.dir_main, "Output", "contracts_date.parquet"),
      Money   = utils_file_path(.dir_main, "Output", "contracts_money.parquet"),
      Redact  = utils_file_path(.dir_main, "Output", "contracts_redact.parquet")
    )
  ),
  Params = list(
    # WHICH FAMILY ANSWERS FOR EACH ENTITY, and every one of these was measured in 04A or 04B.
    Family = list(
      ORG    = "lexnlp",   # 04A: spaCy proposes eleven times as many and spreads them evenly
      GPE    = "matcon",   # 04B2: 181,810 gazetteer rows against LexNLP's 437, and no cities at all
      DATE   = "matcon",   # 04B3: every pattern requires a year IN THE TEXT
      MONEY  = "matcon",   # 04B4: five phrasings in six against LexNLP's one
      REDACT = "matcon"    # the only family emitting a redaction marker
    ),
    # THE COLUMNS THE ORG REDUCTION READS BESIDE THE SPAN. Named here rather than defaulted, because
    # ent_load_org() aborts on a missing one and the abort should name a choice this document made.
    Extras = list(ORG = c("NameCore", "LegalForm", "Description")),
    # DOCUMENTS PER CHUNK. A memory and time decision and not a decision about the answer, which is
    # what Validation checks rather than assumes. Larger is faster until a chunk stops fitting.
    ChunkSize   = 10000L,
    # WORKERS, AND THE EVIDENCE FOR THE NUMBER IS PRINTED BEFORE THE PASS. The rules are dplyr and
    # single-threaded; the LOAD is DuckDB and already uses every core. So a worker helps in
    # proportion to how much of a chunk is rule rather than read, and Where a chunk's time goes
    # measures that split rather than assuming it.
    #
    # SIX AND NOT TWENTY-FOUR. A chunk holds roughly 1.5 million spans carrying 320 characters of
    # stored context each -- around half a gigabyte before anything else -- so the worker count is
    # bounded by memory in flight as much as by cores. 1 runs serially in this process.
    Workers     = 12L,
    # The cue window each rule narrows the stored 160 characters to. MONEY's lives in its own
    # specification because it is swept there; DATE's is an argument to dte_describe().
    CueWin      = list(Date = 120L),
    # DOCUMENTS THE INVARIANCE CHECK RUNS ON, and how many chunks it splits them into.
    CheckDocs   = 4000L,
    CheckParts  = 4L
  )
)

# THE RULES THEMSELVES, each constructed by the 04B function that defined it, with every argument
# named at the value 04B released. A dial not named here is a decision nobody reviewed.
.lP$Params$Rule <- list(
  Org = ent_rule(
    .key             = "core",   # 04B1: the reduced key, suffixes stripped
    .merge_fragments = TRUE      # 04B1: a single word unambiguously taken from one longer name
  )
)

.lP$Params$Spec <- list(
  Org = ent_window_spec(
    .par        = 2000,   # 04B1: characters either side of the registrant
    .tail_share = 0.10    # 04B1: the final tenth, counted as signatories
  ),
  Geo = geo_spec(
    .reach = 200          # 04B2: furthest a party may be and still claim a place
  ),
  Date = dte_spec(
    .start     = "latest", # 04B3: the latest date at or before the filing
    .end       = "term",   # 04B3: the full cascade
    .cap_years = 30        # 04B3: dropped above this, not winsorised
  ),
  Money = mny_spec(
    .filter  = "par",     # 04B4: drops a zero, and a figure with par-value language beside it
    .cue_win = 60L        # 04B4: characters read EITHER SIDE
  )
)

fs::dir_create(c(.lP$Output$Chunks, fs::path_dir(.lP$Output$Release$Parties)))

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

## The policy, and the hash the cache is named for

```{r}
#| label: policy

# THE SAME DESCRIPTION 04C RAN. The spec hashes it records are folded into the policy hash, because a
# re-extraction that moved a model's rules leaves every parameter above unchanged while every span
# underneath them is different.
tab_describe <- ner_describe(
  .spacy_models = character(),
  .lexnlp_image = "contracts-lexnlp"
)

.lP$Params$Hash <- apl_policy_hash(.params = .lP$Params, .describe = tab_describe)
.lP$Output$Chunks <- fs::path(.lP$Output$Chunks, .lP$Params$Hash)

tab_policy <- apl_policy_table(.params = .lP$Params)

apl_report_policy(.tab = tab_policy, .hash = .lP$Params$Hash)
```

# Input

## The population, from 04C's ledger

```{r}
#| label: corpus-index

tab_index <- apl_corpus_index(
  .dir_store = .lP$Input$Store,
  .family    = .lP$Params$Family$GPE,               # matcon: the family carrying most entities
  .entity    = c("GPE", "DATE", "TERM", "MONEY", "REDACT", "LAW")
)

tibble::tibble(
  Item = c("Documents 04C finished for every matcon entity"),
  N    = c(nrow(tab_index))
) |>
  tbl_say(.title = "The population this pass applies to")
```

**The ledger and not the entity tables.** A document processed and found to hold no date has no row
in the date table and is not missing -- it is a contract with no date in it, which is a measurement.
Taking the population from the tables would drop exactly those documents and inflate every rate.

## The anchor, and the gazetteer

```{r}
#| label: build-keys

tab_keys <- apl_keys(
  .path_labels   = apl_labels_path(.dir = .lP$Input$Labels),  # the newest COMPLETE release
  .path_register = .lP$Input$Register,   # 02B: CIK, CompanyName, DateFiled, nWords, nChars
  .path_landing  = .lP$Input$Landing,    # 01C: the registered address 04B2's flag reads
  .index         = tab_index,
  # 03F NAMES ITS LABELS PER ENGINE. BERT's are the released ones: 03E's nested cross-validated
  # policy selection did not improve on the transformer and the oracle ceiling equalled
  # BERT-everywhere, so the keyword columns beside these are a confirmation flag and not a second
  # opinion. No Fold: it is a cross-validation artifact of the sample.
  .labels        = c(Class = "BertClassDetailed", AmendType = "BertAmendType"),
  .quiet         = FALSE
)

geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)
)
```

**03F's release is one row per registrant copy; this pass wants one row per attachment.** The
semi-join against the corpus index does that quietly -- 04C extracted the primary of each attachment,
so restricting to the index keeps exactly those and drops the repeat copies rather than multiplying
every document by its number of filers.

**The gazetteer is read once for the whole pass**, not once per chunk. It is 181,810 rows and it is
read-only, so it is the one thing every chunk shares.

# Validation

## Chunking changes nothing

```{r}
#| label: check-invariance

# tab_invar <- apl_check_invariance(
#   .keys      = tab_keys,
#   .doc_ids   = utils::head(tab_index$DocID, .lP$Params$CheckDocs),
#   .params    = .lP$Params,
#   .dir_store = .lP$Input$Store,
#   .geo       = geo_once,
#   .parts     = .lP$Params$CheckParts
# )
# 
# apl_report_invariance(
#   .tab   = tab_invar,
#   .n_doc = min(.lP$Params$CheckDocs, nrow(tab_index)),
#   .parts = .lP$Params$CheckParts
# )
```

**This runs before the pass, not after it.** The whole design rests on one claim -- that a partition
cannot change an answer -- and this family has broken that claim before. `ent_rule()`'s
family-frequency gate computed a share of documents from the spans it was handed, so 176 leading
tokens fell on opposite sides of the threshold at 2,546 documents per chunk. Each was a family match
admitted in one chunk and refused in another on identical text.

The gate is gone. This is how we know.

# Apply

## Where a chunk's time goes

```{r}
#| label: time-split

tab_split <- apl_time_split(
  .frame     = apl_chunk_frame(
    .keys    = tab_keys,
    .doc_ids = utils::head(tab_index$DocID, .lP$Params$ChunkSize)
  ),
  .params    = .lP$Params,
  .dir_store = .lP$Input$Store
)

apl_report_time_split(.tab = tab_split, .workers = .lP$Params$Workers)
```

**Measured before the pass, not assumed.** Loading is DuckDB and already uses every core; the rules
are dplyr over data in memory and are single-threaded. Workers help in proportion to how much of a
chunk is *apply*, and oversubscribing a load that is already parallel costs more than it buys.

## The pass

```{r}
#| label: run-pass

chunks_ <- apl_chunks(.index = tab_index, .size = .lP$Params$ChunkSize)

tab_pass <- apl_pass(
  .chunks       = chunks_,
  .keys         = tab_keys,
  .dir_chunks   = .lP$Output$Chunks,   # named for the policy hash
  .params       = .lP$Params,
  .dir_store    = .lP$Input$Store,
  .geo          = geo_once,            # the serial path's copy; a daemon builds its own
  .workers      = .lP$Params$Workers,  # 1 runs serially in this process
  .path_lookup  = .lP$Input$Lookup,    # each daemon reads the gazetteer once, not once per chunk
  .path_fun     = .path_libs           # a daemon has none of this loaded; it sources by path
)

apl_report_pass(.tab = tab_pass, .n_index = nrow(tab_index))
```

**Resumption is a property, not a feature.** Each chunk writes four parquets into the hash-named
directory, and a chunk whose four files exist is skipped. There is no state to remember between
renders and nothing that could be wrong about itself.

**A chunk that fails is recorded and the pass continues.** One document with an impossible offset
should not cost the other million, and a failed chunk wrote no file so the next render retries it.

# Results

## What the corpus pass produced

```{r}
#| label: report-outputs

tab_out <- apl_table_outputs(.dir_chunks = .lP$Output$Chunks, .n_index = nrow(tab_index))

apl_report_outputs(.tab = tab_out)
```

## The corpus, entity by entity

```{r}
#| label: report-stats

tab_stats <- apl_table_stats(.dir_chunks = .lP$Output$Chunks)

apl_report_stats(.tab = tab_stats)
```

## The corpus by contract type

```{r}
#| label: report-class

tab_class <- apl_table_class(.dir_chunks = .lP$Output$Chunks)

apl_report_class(.tab = tab_class)
```

# Robustness

## The corpus files have the shape 04B released

```{r}
#| label: check-schema

tab_schema <- apl_check_schema(.dir_chunks = .lP$Output$Chunks)

apl_report_schema(.tab = tab_schema)
```

**The same check 04B runs, on the corpus rather than the sample.** Each 04B document builds a
dictionary from a declared list and aborts where it disagrees with the file it just wrote; running the
same functions here is what says the corpus release has the same shape as the sample release, which is
the whole claim this document makes.

Schema from Arrow, never inferred -- `names(open_dataset())` reads the parquet's own schema, so a
column added or renamed by a chain is seen as the file has it rather than as this document expects.

# Deployment

## The release

```{r}
#| label: write-release

# THE STATUS CARRIES THE CONDITION MESSAGE, so a failure reads "error: <what went wrong>" and never
# the bare word. Testing equality would find no failures and release from a pass that had them.
complete_ <- nrow(tab_pass) > 0L &&
  !any(stringi::stri_startswith_fixed(tab_pass$Status, "error")) &&
  nrow(tab_out) > 0L && all(tab_out$Docs == nrow(tab_index))

tab_write <- apl_write(
  .dir_chunks = .lP$Output$Chunks,
  .paths      = .lP$Output$Release,
  .complete   = complete_
)

apl_report_write(.tab = tab_write)
```

**Nothing is released from a partial pass.** A file assembled from half the chunks looks finished and
is not, and nothing in it would say so. Re-render to continue; the chunk cache resumes where this
stopped.

# Overview

## Everything this pass did

```{r}
#| label: overview

tibble::tibble(
  Item = c("Policy hash",
           "Documents in the index",
           "Chunks",
           "Chunks written",
           "Release written"),
  Value = c(.lP$Params$Hash,
            format(nrow(tab_index), big.mark = ","),
            format(length(chunks_), big.mark = ","),
            format(sum(tab_pass$Status %in% c("ran", "cached")), big.mark = ","),
            if (nrow(tab_write) > 0L) "yes" else "not yet")
) |>
  tbl_say(.title = "The pass in five rows")

cli::cli_alert_info(
  "THE POLICY HASH IS THE ONE THING TO RECORD. It names the chunk directory and it stands for every \\
   rule, every parameter and every extractor spec hash this pass used, so two releases carrying the \\
   same hash were produced by the same pipeline and two carrying different ones were not."
)
```

# Next

The four files are the entity release. **An export script** turns them into whatever shape the
downstream work wants -- fanning attachment-level rows out to all 1,462,939 registrant copies on
`HashDocument`, joining the population flags, and writing whatever format Stata reads. That is a
separate document, because a release and a reshaping of it are different acts and only one of them
should ever have to be re-run.
