---
title: "04D -- Applying the entity rules to the corpus"
subtitle: "One document-level variable per entity, over 1.19 million attachments"
---

```{r}
#| label: setup
#| include: false

here::i_am("1_code/_Commons/_Initialize.R")

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,
  warning   = FALSE,
  comment   = "",
  fig.width = 7.5,
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")

.name_script <- "04D-EntityApply"
.dir_main    <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script)

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

source(here::here("1_code", "03A-ClassifyPrepare.R"), encoding = "UTF-8")
source(here::here("1_code", "04C-EntityCorpus.R"),    encoding = "UTF-8")

source(here::here("1_code", "04B1-Rules-ORG.R"),    encoding = "UTF-8")
source(here::here("1_code", "04B2-Rules-GPE.R"),    encoding = "UTF-8")
source(here::here("1_code", "04B3-Rules-DATE.R"),   encoding = "UTF-8")
source(here::here("1_code", "04B4-Rules-MONEY.R"),  encoding = "UTF-8")
source(here::here("1_code", "04B5-Rules-REDACT.R"), encoding = "UTF-8")

source(init_create_script_fun(.dir_here = here::here(), .name_script = .name_script),
       encoding = "UTF-8")
```

# Purpose

04B built one rule per entity on a sample of 4,398 contracts and measured each against facts EDGAR
recorded independently of the text: the filer's own name, its filing date, its registered address.
04C ran the extractors over the whole corpus and produced 125 million spans. This document is the
join of the two. It decides nothing, measures nothing new, and reads its entire policy from a list
printed below.

**An apply stage with decisions of its own is one whose output depends on which version of it last
ran.** A released dataset cannot be defended on those terms, so everything that could vary is
declared in `Configuration`, printed in the render, and hashed into the directory the intermediate
results are cached in. Changing any dial produces a different directory rather than a file mixing two
rules.

**Not one rule is reimplemented here.** The five 04B libraries are sourced and their functions called
on chunks of the corpus instead of on the sample. That is what makes the corpus variables comparable
with the sample ones a referee can check: they are the same code on different inputs rather than two
implementations that agree today. The family has already paid for the alternative twice, in a
duration extractor that re-derived in R what the Python extractor already emitted, and in a word
count that recomputed what the register stored.

Three properties of the 04B chain had to be established before chunking was sound, and all three were
measured rather than assumed. They are set out where the code depends on them: the definition of a
chunk in `Input`, the chunk size in `Configuration`, and in `Apply` the reason the party chain is the
one chain that is not chunked at all.

# Configuration

Every path this document reads, every rule it applies, and the two numbers that control what it
costs. Nothing below this chunk introduces a parameter.

**The class comes from 03F, and which engine supplies it is a decision.** 03F's release carries
`BertClassDetailed`, `KwClassDetailed` and a runner-up for each, side by side, and deliberately no
resolved `Class` column -- exactly as the entity stores carry one table per family rather than a
merged one. `MONEY` and `REDACT` both need a class to contrast on, so one engine is named here.
`Bert` is that engine because it is the deployed all-data refit, because its pooled out-of-fold
macro-F1 is 0.882, and because 03E found the oracle routing ceiling equal to using it everywhere:
there is no headroom for a rule that picks between engines per document.

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04C's stores: spans, plus the corpus table that resolves the population and holds every path.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04C-EntityCorpus"), "Output"
    ),
    # 02B's register: the anchor, and nChars, which is the document length. See Input.
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    # 03F's release: the corpus classification. The file is found rather than named.
    Release = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03F-ClassifyApply"),
      "release"
    ),
    # The gazetteer, read past the CLI seam. gazetteer-v2's spec hash covers a content hash of this
    # file, so a direct read is still covered by the manifest that guards the extraction.
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet")
  ),
  Output = list(
    Doc = list(
      Org    = utils_file_path(.dir_main, "Output", "party_org.parquet"),    # per document
      Geo    = utils_file_path(.dir_main, "Output", "geo_doc.parquet"),      # per document
      Date   = utils_file_path(.dir_main, "Output", "duration_doc.parquet"), # per document
      Money  = utils_file_path(.dir_main, "Output", "money_doc.parquet"),    # per document, family
      Redact = utils_file_path(.dir_main, "Output", "redact_doc.parquet")    # per document
    ),
    Roles  = utils_file_path(.dir_main, "Output", "roles_org.parquet"),  # per document per name
    Chunks = utils_file_path(.dir_main, "Cache"),                 # per-chunk results, policy-keyed
    Stage  = utils_file_path(.dir_main, "Stage", "chunk.parquet") # one chunk of text at a time
  ),
  Params = list(
    # WHICH FAMILY ANSWERS FOR WHICH ENTITY. Each is 04A's or 04B's finding, and the alternative is
    # printed beside it in the policy table below rather than left implicit.
    Family = list(
      ORG    = "lexnlp",                 # 04A: positional contrast 4.36, the strongest of any pair
      GPE    = "matcon",                 # 04B2: 4,525 distinct cities against lexnlp's none
      DATE   = "matcon",                 # 04B3: requires a written year, which the guard needs
      MONEY  = c("lexnlp", "matcon"),    # 04B4: zero exact agreement, so neither replaces the other
      REDACT = "matcon"                  # 04A: the only family emitting a marker at all
    ),
    Extras = list(
      ORG = c("NameCore", "LegalForm", "Description"),
      GPE = ent_extras("matcon", "GPE")  # declared per family in _Entity.R, not typed here
    ),
    ClassEngine = "Bert",  # 03F label prefix; Kw is the alternative, BertClassDetailed2 the runner-up
    # THE CUE WINDOWS ARE OFF, AND THIS IS THE ONE DIAL THAT COSTS SOMETHING.
    # Three rules read the characters preceding a span to test for a cue phrase, and it is the only
    # reason this stage touches contract text at all. Every other operation runs on offsets and the
    # register. Measured cost of switching it off, per entity, in the policy table below.
    Cues        = FALSE,
    LawWin      = 120L,    # characters read before a place span for the governing-law cue
    # EIGHT THOUSAND IS EVIDENCE. dte_describe() and geo_context() build one vector element per span,
    # each holding a whole document, then cut a window out of each. Time growth over document growth
    # was 0.94 from 2,000 to 8,000 and 4.72 from 8,000 to 32,000, so the cost stops being linear
    # between them. _Tests/04D-Preflight.R is the sweep.
    ChunkSize = 8000L,
    Workers   = 12L,       # daemons for the staged text read; 04C's corpus pass used 24
    Seed      = 42L
  )
)

# The rules themselves, each constructed by the 04B function that defined it, with every argument
# named at the value 04B released. A dial not named here is a decision nobody reviewed.
.lP$Params$Rule <- ent_rule(
  .key               = "core",  # the resolved name lexnlp fills on every span
  .min_key           = 2L,      # shortest key admitted for equality
  .min_contain       = 5L,      # shortest key admitted for containment or family
  .tight             = TRUE,    # also compare with spaces removed
  .frag_min          = 10L,     # shortest fragment admitted as a reverse match
  .frag_share        = 0.6,     # and it must cover this much of the recorded name
  .fam_tokens        = 2L,      # leading tokens two keys must share to be one corporate family
  .fam_share         = 0.5,     # and those tokens must be this much of the shorter key
  .fam_df            = 0.005,   # or ONE token, if it opens a name in at most this share of documents
  .deep              = 5000L,   # a match past this offset is flagged, not rejected
  .exact_within      = 500,     # prefer an exact match this close behind a contaminated one
  .guard_deep_family = FALSE    # off: reading found most of what it would refuse to be correct
)

.lP$Params$Spec <- list(
  Org = ent_window_spec(
    .kind           = "fixed",  # constant characters either side of the party
    .par            = 2000,     # half-width; 04B1's P90 neighbour gap is 1,343 characters
    .tail_share     = 0.10,     # tail as a share of the document, clamped past the window
    .tail_floor     = 0,        # no absolute minimum
    .drop_fragments = FALSE     # swept and not adopted
  ),
  Geo = geo_spec(
    .reach      = 200,          # furthest an organisation may be and still claim a place
    .reach_city = NULL,         # one number for every level
    .party_only = FALSE         # every organisation gets its geography; the role is a column
  ),
  Date = dte_spec(
    .start        = "latest",   # the reference date the duration is measured from
    .end          = "term",     # the stated term where there is one, a cue date otherwise
    .family       = "matcon",
    .cap_years    = 30,         # dropped, not winsorised
    .require_year = FALSE,      # near-vacuous under matcon, which requires one anyway
    .term_kinds   = c("UnitTerm", "ContinueFor", "PeriodOf", "Anniversary"),
    .term_floor   = 0
  ),
  Money = mny_spec(
    # THE PAR FILTER NEEDS A CUE AND THE ZERO FILTER DOES NOT. Par-value boilerplate is recognised
    # from the words beside the amount; a zero is recognised from the amount. With cues off the
    # filter drops to zero rather than claiming a par filter that never ran.
    .filter  = if (.lP$Params$Cues) "par" else "zero",
    .cue_win = 60L,             # characters either side of an amount, for the class cue
    .label   = NULL
  )
)

fs::dir_create(fs::path_dir(unlist(.lP$Output$Doc)))
fs::dir_create(fs::path_dir(.lP$Output$Stage))
```

The policy is fingerprinted and the fingerprint names the cache directory. A pass costs about nine
hours, which is exactly the cost that tempts a document into skipping its own work; instead each
chunk is written as it completes and a chunk already present is reused. **A cache keyed on the chunk
number alone would serve chunk seven from the last render whatever changed in between**, and a corpus
scored half under one rule and half under another is a file no downstream check would catch.

```{r}
#| label: policy

hash_policy <- apl_policy_hash(.params = .lP$Params)
.lP$Output$Chunks <- fs::path(.lP$Output$Chunks, hash_policy)

apl_report_policy(.params = .lP$Params, .hash = hash_policy)
```

# Input

Three things are read before anything is applied: which documents the corpus holds, what the anchor
for each of them is, and where the class came from.

**A chunk is the keys and the lengths cut together, and `apl_chunk_frame()` is the only place that
is decided.** `ent_apply()` runs from the key side so that a document in which the family found
nothing still gets a row -- which is right, and which means the output is one row per *key*. Handed
the corpus keys with an eight-thousand-document lens it builds 1.19 million rows to describe eight
thousand documents, and does it again for every chunk. The preflight probe found this by timing it,
and the answer is not to be careful but to have one function that cannot get it wrong.

**The document length is the register's `nChars`, not a recount.** `ent_doc_lens()` reads every
document to compute the character length of its text; the register stores that number for all 1.77
million rows. The two were compared on 31,981 corpus documents and agreed **exactly on every one**,
maximum relative difference 0.000. Recomputing it would be an hour of reading to reproduce a stored
column, and it is the same mistake as the word count 04B5 removed.

```{r}
#| label: load-index

tab_index <- apl_corpus_index(
  .dir_store = .lP$Input$Store,       # 04C's stores; the corpus table is identical in each
  .family    = "matcon"               # any family; matcon is named because it is always present
)

path_release <- ent_release_path(.dir_release = .lP$Input$Release)

tab_keys <- ent_corpus_keys(
  .path_register = .lP$Input$Register,      # the anchor, and nChars
  .path_release  = path_release,            # 03F's corpus classification
  .engine        = .lP$Params$ClassEngine,  # which engine's label is Class
  .doc_ids       = tab_index$DocID,         # only what 04C extracted
  .quiet         = FALSE
)
```

The gazetteer is loaded once here rather than inside the chunk loop. Reading it per chunk is a fixed
cost charged 149 times, and at two thousand documents it was most of the geography chain's elapsed
time -- which would have read as a chain that scales beautifully rather than as a constant dwarfing
the work.

```{r}
#| label: load-gazetteer

geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),      # the two parent columns v2 omits
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)   # every state a city name exists in
)

chunks_ <- apl_chunks(.index = tab_index, .size = .lP$Params$ChunkSize)

cli::cli_alert_info(
  "{format(nrow(tab_index), big.mark = ',')} {cli::qty(nrow(tab_index))} attachment{?s} in \\
   {length(chunks_)} {cli::qty(length(chunks_))} chunk{?s} of \\
   {format(.lP$Params$ChunkSize, big.mark = ',')}."
)
```

# Apply

## The party stage, which is not chunked

`ent_rule()`'s `.fam_df` admits a **single** shared leading token as evidence of a corporate family
when that token opens the name of at most half a per cent of documents: `ENERGY` against `CHENIERE
CREOLE TRAIL PIPELINE` is one family, `NATIONAL` opens hundreds and shares nothing. `ent_apply()`
derives that share from the spans it is given.

**Chunk it and the rule becomes a property of the partition.** Measured over 31,981 corpus documents:
176 leading tokens fell on opposite sides of the threshold at 2,546 documents per chunk, 1,077 at
509, and 2,512 at 255. Each one is a family match admitted in one chunk and refused in another, on
identical text.

The obvious repair is to compute the share over the corpus and pass it in, which needs an argument
`ent_apply()` does not have. **The better repair is not to partition this chain.** It is the one
chain that reads no text, and the preflight measured it getting *faster* as the set grows -- 110,
then 289, then 518 documents per second, sublinear at both steps, because its fixed costs amortise.
So it runs once, over everything, through 04B1's function called exactly as 04B1 calls it. The
denominator is the corpus because the input is the corpus, and nothing upstream changes.

The spans are read chunk by chunk so no single DuckDB result has to be materialised, then bound: the
read is partitioned, the rule is not.

```{r}
#| label: run-party

if (fs::file_exists(.lP$Output$Roles) && fs::file_exists(.lP$Output$Doc$Org)) {
  res_org <- list(
    Counts = arrow::read_parquet(.lP$Output$Doc$Org),
    Roles  = arrow::read_parquet(.lP$Output$Roles)
  )
  cli::cli_alert_info("Party stage read from its artifacts; delete them to recompute.")
} else {
  res_org <- apl_org_whole(
    .dir_store = .lP$Input$Store,        # 04C's spans
    .family    = .lP$Params$Family$ORG,  # lexnlp
    .keys      = tab_keys,               # the corpus, cut once against the lengths
    .chunks    = chunks_,                # the READ is chunked; the rule is not
    .rule      = .lP$Params$Rule,        # the match
    .spec      = .lP$Params$Spec$Org,    # the window carried into the artifacts
    .extras    = .lP$Params$Extras$ORG,  # NameCore, LegalForm, Description
    .quiet     = TRUE
  )
  fs::dir_create(fs::path_dir(.lP$Output$Roles))
  arrow::write_parquet(res_org$Roles,  .lP$Output$Roles)
  arrow::write_parquet(res_org$Counts, .lP$Output$Doc$Org)
}

apl_report_org(.org = res_org, .n_doc = nrow(tab_keys))
```

**The organisations are written before the chunk loop starts**, and not only so the stage can be
resumed. `geo_attach()` needs them, so geography can be chunked only because they already exist as a
file the loop reads a slice of. Writing them is what makes the dependency explicit rather than a
variable that happens to be in scope.

## The pass

One loop, four chains inside it, and with cue windows off **no contract text is opened at all**.
Every rule that survives runs on what 04C already stored: the span, its offsets, its parsed value,
and the register beside it. The stage is written empty so the 04B loaders keep their one calling
convention, and the windows they cut out of it come back empty.

What that costs, and it is worth stating plainly rather than discovering in a table:

| Entity | With cues | Without |
|:--|:--|:--|
| REDACT | markers over register words | unchanged |
| ORG | offsets and the anchor | unchanged |
| GPE | place, resolution, role, **governing law** | place, resolution, role |
| MONEY | par-value boilerplate dropped | zeros dropped; 1.7% more matcon spans kept |
| DATE | term, then cue, then fallback | term, then fallback; 464 of 2,580 fall a rung |

Governing law is **dropped rather than reported as absent**. 04B2 measured 95% of the spans its cue
catches attaching to no organisation at all, so proximity cannot reach the clause and the cue is the
only thing that identifies it. A column asserting that every contract names no governing law would be
false rather than missing, so the columns do not appear.

That variable belongs in the extractor rather than here. A governing-law clause is a legal object
that happens to contain a place name, in the way a term is one that happens to contain a date, and
`dateregex-v3` already shows the shape: emit it as its own entity and record which pattern matched.
The extractor has the text open, which is the one place reading context is free.

```{r}
#| label: run-pass

par_ok <- if (isTRUE(.lP$Params$Cues)) cor_daemons_start(.workers = .lP$Params$Workers) else FALSE

tab_pass <- apl_pass(
  .chunks     = chunks_,                    # the partition, in DocID order so it is stable
  .keys       = tab_keys,                   # cut to each chunk by apl_chunk_frame()
  .dir_chunks = .lP$Output$Chunks,          # named for the policy hash
  .stage      = .lP$Output$Stage,           # overwritten each chunk; never read after the chunk
  .params     = .lP$Params,                 # every rule, unchanged from Configuration
  .dir_store  = .lP$Input$Store,            # 04C's spans
  .path_roles = .lP$Output$Roles,           # the party stage's organisations, read per chunk
  .geo        = geo_once,                   # the gazetteer, loaded once above
  .workers    = if (par_ok) .lP$Params$Workers else 1L
)

if (par_ok) mirai::daemons(0L)
```

# Results

```{r}
#| label: report-pass

tab_all <- c(list(Org = res_org$Counts), apl_bind(.dir_chunks = .lP$Output$Chunks))

apl_report_all(.pass = tab_pass, .tabs = tab_all, .n_index = nrow(tab_index))
```

**The bind reads from disk rather than from what the pass returned.** A resumed render therefore
produces exactly what an uninterrupted one would: a pass that returned only the chunks it computed
this time would hand a second render a file covering a tenth of the corpus, and nothing inside the
file would say so.

# Validation

Three checks, each of which would reveal a different failure.

```{r}
#| label: check-keys

# 1. EVERY ENTITY COVERS THE SAME DOCUMENTS. The five chains ran on one chunk frame, so a
#    disagreement here is a chain dropping rows rather than a population difference.
purrr::imap(tab_all, \(.t, .k) tibble::tibble(
  Entity   = .k,
  Docs     = dplyr::n_distinct(.t$DocID),
  Distinct = dplyr::n_distinct(.t$DocID) == nrow(.t) |
    .k == "Money"   # MONEY is one row per document AND family, by design
)) |>
  purrr::list_rbind() |>
  tbl_say(.title = "Documents per entity, and whether rows are unique within it")
```

```{r}
#| label: check-missing

# 2. A DOCUMENT THAT COULD NOT BE READ IS NOT A DOCUMENT WITH NOTHING IN IT. 04C found 736
#    attachments holding no text and 03F's classification pass failed on the same 736, which makes
#    it a property of the corpus rather than of either engine. They must appear here as absent, not
#    as zero: a contract with no redaction marker and a file that would not open are different
#    facts, and averaging them together understates every rate in the paper.
tibble::tibble(
  Indexed   = nrow(tab_index),
  Keyed     = nrow(tab_keys),
  Staged    = sum(tab_pass$nStaged, na.rm = TRUE),
  InOutput  = dplyr::n_distinct(tab_all$Redact$DocID)
) |>
  dplyr::mutate(Unread = .data$Indexed - .data$InOutput) |>
  tbl_say(.title = "Attachments at each stage")
```

```{r}
#| label: check-chunks

# 3. THE PARTS MUST SUM TO THE WHOLE. A row whose components do not add to its total is
#    unreadable, and this family has produced one before: nDone sat beside a Share that had
#    subtracted the 736 errors when nDone had not.
tab_pass |>
  dplyr::summarise(
    Chunks  = dplyr::n(),
    nIndex  = sum(.data$nIndex),
    nStaged = sum(.data$nStaged, na.rm = TRUE),
    .by     = Status
  ) |>
  tbl_say(.title = "Chunks by status")
```

# Robustness

The rules were built on 4,398 documents and are applied here to 1.19 million. The question a referee
would ask is whether they survive the move, and 04A answered the same question one level down: every
family's document-level *span* coverage on the corpus sat within 3.3 points of its rate on the
labelled sample. The equivalent statement for the rules is the share of documents each variable
resolves.

```{r}
#| label: robust-coverage

purrr::imap(tab_all, \(.t, .k) tibble::tibble(
  Entity = .k,
  Docs   = dplyr::n_distinct(.t$DocID),
  Share  = tbl_pct(dplyr::n_distinct(.t$DocID) / nrow(tab_index))
)) |>
  purrr::list_rbind() |>
  tbl_say(.title = "Documents each variable reaches")

cli::cli_alert_info(
  "These are documents the chain produced a row for, not documents in which it found something. \\
   The second is a property of each variable and is reported where that variable is described."
)
```

# Deployment

Five files, one per entity, each the corpus-scale counterpart of what 04B wrote for the sample and
carrying the same name -- so a reader who has followed 04B3 knows what `duration_doc.parquet` holds
without opening it.

**The fan-out is not done here.** These are attachment-level: 1,189,805 rows, the primary of every
attachment with at least one copy in the population. Expanding to all 1,462,939 registrant copies on
`HashDocument` belongs to the release, because doing it here would multiply five files by 23% each
and force every later reader to undo it before joining anything.

```{r}
#| label: write-artifacts

apl_write(.tabs = tab_all, .paths = .lP$Output$Doc)
```

# Overview

```{r}
#| label: fig-chunk-cost
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Elapsed seconds per chunk, in the order chunks were processed. A flat cloud is the
#|   expectation, since every chunk holds the same number of documents. A rising one means the cost
#|   depends on something accumulating across the pass rather than on the documents in each chunk,
#|   which is the failure the eight-thousand chunk size was chosen to avoid."

tab_pass |>
  dplyr::filter(.data$Status == "done", !is.na(.data$Secs)) |>
  dplyr::mutate(Order = dplyr::row_number()) |>
  ggplot2::ggplot(ggplot2::aes(x = .data$Order, y = .data$Secs)) +
  ggplot2::geom_point(alpha = 0.55, size = 1.2) +
  ggplot2::labs(x = "Chunk, in processing order", y = "Seconds") +
  plot_theme(.grid = "y")
```

```{r}
#| label: fig-doc-reach
#| fig-height: !expr plot_height(5L)
#| fig-cap: "Share of the indexed attachments each variable produced a row for. Every chain ran on
#|   one chunk frame, so these should agree: a short bar is a chain dropping documents, not a
#|   variable finding nothing in them."

purrr::imap(tab_all, \(.t, .k) tibble::tibble(
  Entity = .k, Share = dplyr::n_distinct(.t$DocID) / nrow(tab_index)
)) |>
  purrr::list_rbind() |>
  plot_bar_ranked(
    .cat   = "Entity",
    .val   = "Share",
    .key   = NULL,
    .short = FALSE,
    .label = TRUE
  ) +
  plot_scale_x_pct()
```

# Next

The release fans these five tables out from 1,189,805 attachments to all 1,462,939 registrant copies
on `HashDocument`, joins them into one document-level table, and carries the population flags as
columns so a reader subsets without the register. It is also where the styled tables and figure files
this document deliberately does not write are produced, for every pair in the family at once.
