---
title: "Entity Apply -- The Five Rules at Corpus Scale (04D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ONE ORDERED LIST, SOURCED HERE AND NAMED TO THE DAEMONS. A mirai daemon is a fresh R process with
# none of this in it, and a closure does not carry its environment across a process boundary -- so a
# worker handed a function that calls ent_apply() finds no ent_apply(). Building the list once and
# walking it means the process that renders and the process that works load the same files in the
# same order, which two hand-written lists could not guarantee.
#
# THE COMMONS FIRST, AND init_create_script_fun() COMES FROM THEM. Naming the numbered scripts by
# that function before it exists is a bootstrap the render cannot survive, so the list is built in
# two steps: source what defines the resolver, then use it.
#
# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so
# every library that registers a vocabulary must follow it -- _Entity.R and all five 04B files do.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# THE FIVE RULE LIBRARIES, SOURCED AND CALLED RATHER THAN COPIED. Not one rule is reimplemented in
# this document; every function it calls is the one that produced the sample's release.
.path_libs <- c(
  .path_libs,
  purrr::map_chr(
    c("04B1-Rules-ORG", "04B2-Rules-GPE", "04B3-Rules-DATE",
      "04B4-Rules-MONEY", "04B5-Rules-REDACT"),
    \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
  )
)
purrr::walk(
  .x = utils::tail(.path_libs, 5L),
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "04D-EntityApply"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")

# APPENDED LAST, because a daemon calls apl_doc_apply() and it is defined in this file. Appended
# rather than named again, so the list a worker sources is exactly the list this process sourced.
.path_libs <- c(.path_libs, .path_fun)
```

# Purpose

This document applies the five 04B rules to the corpus 04C extracted and writes **the same eight long
files 04B released**, with 1.19 million contracts in them instead of 4,398.

## It decides nothing

04A measured which family to trust. 04B built and scored a rule per entity. 04C extracted the corpus.
Everything that could vary is declared in Configuration, printed in the render, and hashed into a
chunk directory so a changed rule cannot be served from a stale cache.

## Five passes, five hashes

| Pass | Hash covers | Reads |
|:--|:--|:--|
| ORG | party rule, window, lexnlp spec hashes | -- |
| GPE | reach, matcon spec hashes, **Hash(ORG)** | `org_mentions` |
| DATE | cascade, cap, matcon spec hashes | -- |
| MONEY | filter, window, matcon spec hashes | -- |
| REDACT | tolerance, matcon spec hashes | -- |

GPE folds in ORG's hash because it reads ORG's file. **REDACT depends on the extractor and not on
04B4** -- it reads matcon's money spans to find the ones the filer emptied, and "emptied" is a
pattern name rather than a filtered result.

## The unit of work is one document

A worker is handed **one document's spans** and returns that document's rows. Nothing else can be
affected by it: a contract with an impossible offset, a name the grouping cannot reduce, a date
outside every range costs exactly that contract and no other.

It is also the only unit that is provably safe. Every 04B rule reads one document -- grouping
compares names within a document, the window measures from a party in the same document, the
ambiguous city takes a state the same contract names. So a rule applied per document cannot be
computing a quantity over the group it happened to be handed. An earlier version needed a whole
Validation section to establish that; here there is no group to compute over.

**The read is per window and the work is per document.** One DuckDB query loads `WindowSize`
documents' spans, the parent splits them by `DocID`, and the workers take one each. The database is
asked a few hundred times over a corpus rather than a million.

## Resumption is by document

A pass asks which documents the ledger has and which are already written; the difference is the work.
Nothing is named for a position, so the window size can change between renders at no cost and a
population that grew -- a family still finishing extraction -- simply adds to the queue.

**A window commits as a directory.** Outputs and a `_done.parquet` go into a hidden name which is
then renamed into place. A rename within one filesystem is atomic, so a killed process leaves a
dotfile no glob sees.

**`_done.parquet` names every document processed**, not every document that produced a row. Seven of
the eight releases carry a row only where the extractor found something -- `redact_spans` reaches 14%
of documents -- so resuming on the outputs would reprocess the other 86% on every render, forever. A
document that *failed* is left out of it and retried.

## The output directory is the release

A directory of parquets already *is* an arrow dataset, so there is no final bind. **No collapse is
written** -- the export calls `geo_collapse()`, `dte_collapse()`, `mny_collapse()` and
`red_collapse()`.

## Testing before committing

`Limit` takes the first N documents of every population and writes into its own directory.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04C's corpus stores, one per family.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04C-EntityCorpus"),
      "Output"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet")
  ),
  Params = list(
    # THE FIVE PASSES IN DEPENDENCY ORDER. GPE reads ORG's file, so ORG runs first; the other three
    # are independent of both and of each other and could run in any order at all.
    Passes = c("ORG", "GPE", "DATE", "MONEY", "REDACT"),

    # THE COLUMNS THE ORG REDUCTION READS BESIDE THE SPAN. Named here rather than defaulted, because
    # ent_load_org() aborts on a missing one and the abort should name a choice this document made.
    Extras = list(ORG = c("NameCore", "LegalForm", "Description")),

    # DOCUMENTS READ AT ONCE. The window is how many documents' spans one DuckDB query loads; the
    # unit of WORK below it is one document. It is in no hash and names no directory, so it can
    # change between renders freely.
    #
    # SMALLER THAN IT LOOKS LIKE IT SHOULD BE, and the reason is the split rather than the read. A
    # window becomes one R object per document per input table, each carrying its own class, names
    # and row-names attributes -- so twenty thousand documents across four tables is eighty thousand
    # tibbles live in the parent at once, which is gigabytes of overhead for a few hundred thousand
    # rows of data. Five thousand keeps that bounded while still asking DuckDB only a few hundred
    # times over the corpus.
    WindowSize = 5000L,

    # WORKERS. Each takes one document at a time. The rules are single-threaded R, so this is where
    # the parallelism is; the LOADS are DuckDB and already use every core, which is why they happen
    # once per window in the parent rather than per document in a worker. 1 runs serially.
    Workers = 24L,

    # NULL IS THE FULL CORPUS. Set this to a number to test: a limited run takes the first N
    # documents of every population -- the same first N, because every index is ordered by DocID --
    # and writes into its own directory.
    Limit = NULL,

    # The cue window DATE narrows the stored 160 characters to. MONEY's lives in its own
    # specification because it is swept there.
    CueWin = list(Date = 120L)
  )
)

# ent_filer_keys() TAKES A PATH AND A WINDOW LOAD RUNS IN THE PARENT, so the register's location travels
# inside the parameter list rather than through a closure that would not survive the process
# boundary.
.lP$Params$PathRegister <- .lP$Input$Register

# THE RULES THEMSELVES, each constructed by the 04B function that defined it, with every argument
# named at the value 04B released. A dial not named here is a decision nobody reviewed.
.lP$Params$Rule <- list(
  Org = ent_rule(
    .key             = "core",   # 04B1: the reduced key, suffixes stripped
    .merge_fragments = TRUE      # 04B1: a single word unambiguously taken from one longer name
  )
)

.lP$Params$Spec <- list(
  Org = ent_window_spec(
    .par        = 2000,   # 04B1: characters either side of the registrant
    .tail_share = 0.10    # 04B1: the final tenth, counted as signatories
  ),
  Geo = geo_spec(
    .reach = 200          # 04B2: furthest a party may be and still claim a place
  ),
  Date = dte_spec(
    .start     = "latest", # 04B3: the latest date at or before the filing
    .end       = "term",   # 04B3: the full four-rung cascade
    .cap_years = 30        # 04B3: dropped above this, not winsorised
  ),
  Money = mny_spec(
    .filter  = "par",     # 04B4: drops a zero, and a figure with par-value language beside it
    .cue_win = 60L        # 04B4: characters read EITHER SIDE
  ),
  Redact = red_spec(
    .tol = 10L            # 04B5: slack between a marker and a withheld price that do not overlap
  )
)

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

## The five policies, and the directories they name

```{r}
#| label: policy

# THE SAME DESCRIPTION 04C RAN. The spec hashes it records are folded into each pass's hash, because
# a re-extraction that moved a model's rules leaves every parameter above unchanged while every span
# underneath them is different.
tab_describe <- ner_describe(
  .spacy_models = character(),
  .lexnlp_image = "contracts-lexnlp"
)

# THE HASHES ARE BUILT IN DEPENDENCY ORDER, because GPE's folds in ORG's. Computing them in a loop
# rather than by hand is what keeps that true when a sixth pass arrives.
.lP$Params$Hash <- purrr::reduce(
  .x    = .lP$Params$Passes,
  .f    = function(.acc, .p) {
    dep_ <- apl_pass_spec(.pass = .p)$Depends
    c(.acc, purrr::set_names(
      apl_policy_hash(
        .pass     = .p,
        .params   = .lP$Params,
        .describe = tab_describe,
        .depends  = if (is.na(dep_)) NULL else .acc[dep_]
      ),
      .p
    ))
  },
  .init = character(0)
)

# THE LIMIT NAMES THE DIRECTORY AND THE BATCH SIZE DOES NOT. A test run and a full run must never
# share output; how the work was divided is nobody's business once it is written.
.suffix <- if (is.null(.lP$Params$Limit)) "" else paste0("-limit", .lP$Params$Limit)

.lP$Output <- list(
  # A NAMED CHARACTER VECTOR AND NOT A LIST, so every use is [["ORG"]] rather than $ORG. map_chr()
  # returns atomic, and $ on an atomic vector is an error rather than a lookup.
  Store = purrr::set_names(
    purrr::map_chr(
      .lP$Params$Passes,
      \(.p) utils_file_path(.dir_main, "Store", .p, paste0(.lP$Params$Hash[[.p]], .suffix))
    ),
    .lP$Params$Passes
  )
)

fs::dir_create(.lP$Output$Store)

apl_report_policy(
  .tab    = apl_policy_table(.params = .lP$Params),
  .hashes = .lP$Params$Hash,
  .limit  = .lP$Params$Limit
)
```

# Input

## The population, one per pass

```{r}
#| label: corpus-index

tab_index <- purrr::set_names(
  purrr::map(
    .lP$Params$Passes,
    \(.p) apl_corpus_index(
      .dir_store = .lP$Input$Store,
      .pass      = .p,
      .limit     = .lP$Params$Limit
    )
  ),
  .lP$Params$Passes
)

tibble::tibble(
  Pass       = names(tab_index),
  Family     = purrr::map_chr(names(tab_index), \(.p) apl_pass_spec(.p)$Family),
  Needs      = purrr::map_chr(names(tab_index), \(.p) paste(apl_pass_spec(.p)$Needs,
                                                            collapse = ", ")),
  Population = purrr::map_int(tab_index, nrow)
) |>
  dplyr::mutate(Population = format(.data$Population, big.mark = ",")) |>
  tbl_say(.title = "What each pass will reach")
```

**The population is per family, not per entity.** The preflight measured it: every matcon entity
finished the same documents and every lexnlp entity the same. So ORG runs on lexnlp's population and
the other four on matcon's, and the gap between them is documents where places exist and parties do
not yet.

**That gap is correct behaviour rather than a defect.** The long file keeps refusals: a place with no
party to attach to carries `Attached = FALSE` and a null `PartyKey`, which is a measurement. The gap
closes on its own as LexNLP finishes.

## The anchors and the gazetteer

```{r}
#| label: build-keys

tab_keys <- purrr::set_names(
  purrr::map(
    .lP$Params$Passes,
    \(.p) apl_keys(
      .path_register = .lP$Input$Register,  # 02B: CIK, CompanyName, DateFiled, nWords, nChars, nCIK
      .index         = tab_index[[.p]]
    )
  ),
  .lP$Params$Passes
)

geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)
)

```

**The register and nothing else.** No release function reads `Class` -- it appears only in the
collapses and in reports, both of which join it at their own time. So this document needs no label
release, no partial-release check and no dependency on the classification stage, which is three
failure modes removed rather than handled.

**The gazetteer is read once for the whole render**, and each daemon reads it once for itself. It is
181,810 rows and read-only, so it is the one thing every GPE chunk shares.

# Apply

Each section reads what its ledger has, subtracts what is written, and runs the rest. **ORG first**,
because GPE reads its file; the other three are independent of both and of each other.

```{r}
#| label: apply-setup

# ASKED FRESH IN EVERY SECTION rather than once here, because a pass that just ran has changed its
# own done set and a family still extracting has a larger population than it did a minute ago.
apl_todo <- function(.pass) {
  setdiff(tab_index[[.pass]]$DocID, apl_done_ids(.dir = .lP$Output$Store[[.pass]]))
}
```

## ORG

```{r}
#| label: run-org

res_org <- apl_entity_run(
  .pass        = "ORG",
  .keys        = tab_keys$ORG,
  .todo        = apl_todo(.pass = "ORG"),
  .dir_out     = .lP$Output$Store[["ORG"]],
  .params      = .lP$Params,
  .dir_store   = .lP$Input$Store,
  .path_fun    = .path_libs          # a daemon has none of this loaded; it sources by path
)
```

## GPE

```{r}
#| label: run-gpe

# THE ONE CROSS-PASS READ. Built here rather than inside a window, because it scans one column of
# each of ORG's files and would otherwise do so once per window.
tab_dep_org <- apl_dep_index(.dir = .lP$Output$Store[["ORG"]], .stem = "org_mentions")

res_gpe <- apl_entity_run(
  .pass        = "GPE",
  .keys        = tab_keys$GPE,
  .todo        = apl_todo(.pass = "GPE"),
  .dir_out     = .lP$Output$Store[["GPE"]],
  .params      = .lP$Params,
  .dir_store   = .lP$Input$Store,
  .geo         = geo_once,           # the serial path's copy; a daemon builds its own
  .dep_index   = tab_dep_org,        # which of ORG's files each window overlaps
  .path_lookup = .lP$Input$Lookup,   # each daemon reads the gazetteer once, not once per document
  .path_fun    = .path_libs
)
```

## DATE

```{r}
#| label: run-date

res_date <- apl_entity_run(
  .pass      = "DATE",
  .keys      = tab_keys$DATE,
  .todo      = apl_todo(.pass = "DATE"),
  .dir_out   = .lP$Output$Store[["DATE"]],
  .params    = .lP$Params,
  .dir_store = .lP$Input$Store,
  .path_fun  = .path_libs
)
```

## MONEY

```{r}
#| label: run-money

res_money <- apl_entity_run(
  .pass      = "MONEY",
  .keys      = tab_keys$MONEY,
  .todo      = apl_todo(.pass = "MONEY"),
  .dir_out   = .lP$Output$Store[["MONEY"]],
  .params    = .lP$Params,
  .dir_store = .lP$Input$Store,
  .path_fun  = .path_libs
)
```

## REDACT

```{r}
#| label: run-redact

res_redact <- apl_entity_run(
  .pass      = "REDACT",
  .keys      = tab_keys$REDACT,
  .todo      = apl_todo(.pass = "REDACT"),
  .dir_out   = .lP$Output$Store[["REDACT"]],
  .params    = .lP$Params,
  .dir_store = .lP$Input$Store,
  .path_fun  = .path_libs
)
```

## What the five did

```{r}
#| label: report-pass

tab_pass <- purrr::list_rbind(list(res_org, res_gpe, res_date, res_money, res_redact))

apl_report_pass(.tab = tab_pass, .index = tab_index, .dirs = .lP$Output$Store)
```

**`LoadShare` is the read against the rules.** Loading is DuckDB and already uses every core; the
rules are single-threaded R, one document at a time. A high share means the window is too small and
the database is being asked too often; a low one means workers are what help.

# Results

## What the eight files hold

```{r}
#| label: report-outputs

tab_out <- apl_table_outputs(.dirs = .lP$Output$Store, .index = tab_index)

apl_report_outputs(.tab = tab_out)
```

## The rule against the naive definition

```{r}
#| label: report-naive

tab_facts <- purrr::set_names(
  purrr::map(.lP$Params$Passes, function(.p) {
    dep_ <- apl_pass_spec(.pass = .p)$Depends
    apl_facts(
      .pass      = .p,
      .dir       = .lP$Output$Store[[.p]],
      .keys      = tab_keys[[.p]],
      .params    = .lP$Params,
      .dep_index = if (.p == "GPE") tab_dep_org else NULL
    )
  }),
  .lP$Params$Passes
)

tab_naive <- apl_table_naive(.facts = tab_facts)

apl_report_naive(.tab = tab_naive, .limit = .lP$Params$Limit)
```

**Every pair comes from the same collapse function 04B reports from.** `ent_doc_facts()`,
`geo_doc_facts()`, `dte_collapse()`, `mny_collapse()` and `red_collapse()` run here chunk by chunk,
so a corpus figure and a sample figure are one query on different data rather than two
implementations free to disagree at the third decimal.

**Only the document-level result is kept.** Each collapse is per document, so a chunk's collapse is
exact; binding the document rows gives about a million rows and a dozen columns. Collecting the long
files themselves would not fit that description.

**The denominator is the chunk's document list and never the file's.** Seven of the eight releases
carry a row only where the extractor found something, so a rate computed over the documents present
would report every contract as having redacted something, named a place, or stated a term. What the
chunk was *asked* about is the only honest denominator.

# Robustness

## The corpus files have the shape 04B released

```{r}
#| label: check-schema

apl_report_schema(.tab = apl_check_schema(.dirs = .lP$Output$Store))
```

**The same check 04B runs, on the corpus rather than the sample.** Each 04B document builds a
dictionary from a declared list and aborts where it disagrees with the file it wrote; running the
same functions here is what says the corpus release has the same shape as the sample release.

Schema from Arrow, never inferred -- `names(open_dataset())` reads the parquet's own schema, so a
column added or renamed by a chain is seen as the file has it rather than as this document expects.

# Overview

## The five passes in one table

```{r}
#| label: report-headline

apl_report_headline(.out = tab_out, .hashes = .lP$Params$Hash, .index = tab_index)
```

# Next

The eight files are the entity release. **An export script** turns them into whatever shape the
downstream work wants -- calling `ent_party_facts()`, `geo_collapse()`, `dte_collapse()`,
`mny_collapse()` and `red_collapse()` to produce one row per party or per contract, fanning
attachment-level rows out to all 1,462,939 registrant copies on `HashDocument`, joining the
classification labels, and writing whatever format Stata reads.

That is a separate document, because a release and a reshaping of it are different acts and only one
of them should ever have to be re-run.
