---
title: "Entity Extraction at Scale -- Applying the Deployed Policy (04D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# 03A supplies the console formatter and the text reader; 04B the anchor logic, the session helpers
# and the date cleaner; 04C the resolvers. Nothing here re-implements any of them: the corpus is
# resolved by the code the sample was validated with, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04B-EntityMeasure", "04C-EntityResolve"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04D-EntityApply.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every decision has been made. 04A extracted eight engines over full text and described what came
back. 04B measured which engine to keep per label, which character budget to read it under, and
which of two reading sessions' rules survive contact with the EDGAR anchors. 04C turned spans into
the four published variables and checked them against facts EDGAR recorded.

This stage does none of that again. It reads `extraction_policy.parquet` and `rules_kept.parquet`
and applies them to a corpus that carries no labels.

That separation is the point. An apply stage free to choose its own engine or its own window is one
whose output depends on which version of it last ran, and a released dataset cannot be defended on
those terms. The engine per label, the budget from each end and the rules all arrive as artifacts.
What is left here is bookkeeping: index the tree, slice the text, run the extractors, resolve, write.

## The window is two slices, not one truncation

`--max-chars` truncates a prefix, and 04B found that geography needs the end of a contract as much
as the beginning: a governing-law clause sits in the final fifth, and a head-only window costs
twenty-six points of document-level recall on places.

So a label carrying a tail budget is extracted **twice**, from a head slice and a tail slice, and the
tail's offsets are shifted back onto the full document before anything reads them. Splicing the two
into one string would have been less code and would have made every offset index a text that exists
nowhere. A document shorter than both budgets is its own slice twice over, so the union is
deduplicated on the span rather than on the document.

## The anchors travel with the release

The filer's name and its filing date are EDGAR facts, available for every contract in the corpus and
not only for the labelled sample. The consistency checks 04C ran as diagnostics therefore run here
too, and **every released row carries** whether the filer appeared among its resolved parties and
whether its contract date precedes its filing.

A user can condition on those without re-running anything, which is a materially different offer
from a single headline number.

## What this document cannot carry over from 04C

One column changes meaning at scale and should not be read across. The published term measure is
the latest date *anywhere in the document* minus the filing date, and at corpus scale there is no
unfiltered store to take it from -- only what the deployed engines returned inside the window. The
column is still written, because it is what a corpus-scale reproduction of the published definition
can see, but the figure that reproduces that definition on full text is 04C's, on the sample.

# Configuration

```{r}
#| label: configure-paths
.dir_measure <- init_create_script_dir(.dir_here = here::here(), .name_script = "04B-EntityMeasure")

.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus tree
    # conjured into existence would report itself present while holding nothing.
    Policy      = fs::path(.dir_measure, "extraction_policy.parquet"), # written by 04B
    Kept        = fs::path(.dir_measure, "rules_kept.parquet"),        # written by 04B
    DirCorpus   = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/",
    MetaData    = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    LandingPage = "../pMatDisc/2_output/01-GetEDGAR/Output/LandingPage.parquet"
  ),
  Cache = list(
    CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet") # DocID to Path index
  ),
  Output = list(
    Vars = utils_file_path(.dir_main, "variables")  # the released variables
  ),
  Work = list(
    Dir = utils_file_path(.dir_main, "Work")        # slices and extractor output, deleted per chunk
  ),
  Param = list(
    ChunkSize  = 500L,   # documents per output file; a corpus pass should not be one write
    CtxMax     = 400L,   # context width the rules are matched in, as 04B scored them
    HeadPos    = 0.10,   # an uncued organisation this far in still reads as a party
    IndexRerun = FALSE,  # TRUE re-walks the tree; FALSE reuses the cached index
    Device     = "auto", # CNN models to CPU, transformer to Metal
    # The switch that decides whether this document is a rehearsal or the release. An integer draws
    # that many documents at random from the whole tree and writes them to a separate directory;
    # NULL processes the corpus. Set an integer, read the throughput, then set NULL.
    Limit      = 2000L
  )
)

# Per-combo throughput settings, as in 04A. The transformer occupies one device and cannot be shared
# across processes; LexNLP runs in a container and its date grammar stalls on a few long documents.
.KNOBS <- list(
  "lexnlp"                = list(n_process = 24L, batch_size =  8L, timeout = 60L),
  "spacy:en_core_web_trf" = list(n_process =  1L, batch_size = 128L, timeout = 600L),
  "paper:gazetteer-v1"    = list(n_process = 16L, batch_size =  8L, timeout = 120L),
  "paper:redaction-v1"    = list(n_process = 16L, batch_size = 64L, timeout =  0L),
  "paper:dateregex-v1"    = list(n_process =  1L, batch_size = NULL, timeout = 0L)
)

# The same formats 04B parsed with and 04C resolved with. Three copies of one list is two too many;
# they are written out rather than sourced so that a change in one is visibly a change in all.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", "%b %d, %Y", "%b %d %Y",
  "%d %B, %Y", "%d %B %Y", "%d %b, %Y", "%d %b %Y",
  "%m/%d/%Y",  "%d/%m/%Y", "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d", "%d-%b-%Y", "%m.%d.%Y"
)

fs::file_exists(c(.lP$Input$Policy, .lP$Input$Kept))
```

Nothing here is cached except the file index. The expensive work is the extractor passes, and those
are checkpointed by writing resolved chunks as they complete -- a resumable design rather than a
cache: an interrupted run restarts at the first chunk with no output file.

# The policy

```{r}
#| label: load-policy
tab_policy <- ent_read_policy(.path = .lP$Input$Policy)
tab_rules  <- arrow::read_parquet(.lP$Input$Kept)
tab_plan   <- ent_slice_plan(.policy = tab_policy)

clf_say_table(
  .tab = tab_policy |>
    dplyr::select(Label, Combo, Basis, CapChars, TailChars, DocRecallAtCap) |>
    dplyr::mutate(
      dplyr::across(c(CapChars, TailChars), as.integer),
      DocRecallAtCap = clf_pct(.data$DocRecallAtCap)
    ),
  .title = "Policy this pass applies"
)
```

Read that table before anything else. Every line is a decision made once and validated, and a run
applying the wrong configuration should be visible in the first screen of output rather than in the
released variables. `Basis` distinguishes an engine chosen on measured recall from one asserted
because no anchor could rank it -- money and redaction are the second kind.

```{r}
#| label: show-plan
clf_say_table(
  .tab = tab_plan |>
    dplyr::mutate(Labels = purrr::map_chr(.data$Labels, \(.x) paste(.x, collapse = ", "))),
  .title = "Extractor runs per chunk"
)
```

Several labels share an engine under different windows, so running once per label would extract the
same head twice. Grouping by engine and slice runs each combination once and keeps only the labels
that asked for it.

```{r}
#| label: build-index
tab_index <- ent_corpus_index(
  .dir_corpus   = .lP$Input$DirCorpus,     # the parsed-contract tree, Exhibit 10 only
  .path_meta    = .lP$Input$MetaData,      # filer name and filing date
  .path_landing = .lP$Input$LandingPage,   # registered addresses
  .path_cache   = .lP$Cache$CorpusFiles,   # walking a million files is cached, not repeated
  .rerun        = .lP$Param$IndexRerun,
  .limit        = .lP$Param$Limit,         # NULL processes the corpus; an integer rehearses
  .seed         = 42L
)

.dir_out <- ent_output_dir(.dir = .lP$Output$Vars, .limit = .lP$Param$Limit)

tab_index |>
  dplyr::summarise(
    Documents   = dplyr::n(),
    WithCompany = sum(!is.na(.data$CompanyName)),
    WithFiled   = sum(!is.na(.data$DateFiled))
  ) |>
  clf_say_table(.title = paste0("Corpus to process -> ", fs::path_rel(.dir_out, here::here())))
```

The corpus is an index here, not a table. The labelled sample fits in memory and the corpus does
not: over a million contracts of full text is hundreds of gigabytes, so what is held throughout is
one row per document with its path and the EDGAR facts. Text is read one chunk at a time and
discarded. Any code that treats corpus text as a column runs out of memory somewhere past the first
hundred thousand documents.

# A rehearsal on one chunk

Before a corpus pass, one chunk end to end. It exercises every extractor, both slices, the offset
shift and the whole resolver chain, and it costs a minute -- which is the right price for
discovering that a model directory moved or that the policy names an engine with no branch.

```{r}
#| label: rehearse-chunk
docs_head <- ent_read_chunk(.chunk = dplyr::slice_head(tab_index, n = 50L))

cand_head <- ent_extract_chunk(
  .docs     = docs_head,
  .plan     = tab_plan,             # one run per engine per slice
  .dir_work = .lP$Work$Dir,         # slices and raw output, deleted as they are consumed
  .knobs    = .KNOBS,
  .device   = .lP$Param$Device
)

cand_head |>
  dplyr::count(.data$Label, .data$Engine, .data$Model, name = "N") |>
  clf_say_table(.title = "Candidates from one rehearsal chunk")
```

```{r}
#| label: rehearse-resolve
path_text_ <- fs::path(.lP$Work$Dir, "rehearse_text.parquet")
con_head <- ent_chunk_session(.cands = cand_head, .docs = docs_head, .path_text = path_text_)

vars_head <- ent_resolve_chunk(
  .con       = con_head,
  .path_text = path_text_,
  .rules     = tab_rules,
  .keys      = dplyr::transmute(
    docs_head, DocID, Fold = NA_integer_, Class = NA_character_,
    DateFiled  = suppressWarnings(anytime::anydate(as.character(.data$DateFiled))),
    AnchorKey  = ent_norm_company(.data$CompanyName),
    AnchorText = NA_character_
  ),
  .formats   = .DATE_FORMATS,
  .ctx_max   = .lP$Param$CtxMax,
  .head_pos  = .lP$Param$HeadPos
)

DBI::dbDisconnect(con_head, shutdown = TRUE)

vars_head |>
  dplyr::select(DocID, NParties, ContractStart, ContractEnd, MaxAmount, NRedact, HasFilerParty) |>
  head(10) |>
  clf_say_table(.title = "First ten resolved documents")
```

An empty `ContractEnd` column is the expected result rather than a disappointment: 04C found an
expiry date for well under one percent of the labelled sample, and a rehearsal of fifty documents
will usually find none. What the rehearsal is checking is that every extractor ran, that the tail
slice's offsets landed on the full document, and that the resolvers produced columns rather than
errors.

# The corpus pass

Chunked, and each chunk written as it completes. A corpus pass is measured in hours, so a failure at
document nine hundred thousand should cost one chunk rather than the run, and a restart should
resume rather than begin again.

```{r}
#| label: apply-corpus
fs::dir_create(.dir_out)

chunks_ <- split(tab_index, ceiling(seq_len(nrow(tab_index)) / .lP$Param$ChunkSize))
cli::cli_alert_info("{length(chunks_)} chunk{?s} of up to {(.lP$Param$ChunkSize)} documents.")

purrr::iwalk(chunks_, function(.chunk, .i) {
  path_ <- fs::path(.dir_out, sprintf("vars_%04d.parquet", as.integer(.i)))
  if (fs::file_exists(path_)) {
    cli::cli_alert_info("Chunk {(.i)}: already written, skipping.")
    return(invisible(NULL))
  }

  t0_ <- Sys.time()
  docs_ <- ent_read_chunk(.chunk = .chunk)
  if (nrow(docs_) == 0L) {
    cli::cli_alert_warning("Chunk {(.i)}: no readable documents; nothing written.")
    return(invisible(NULL))
  }

  cand_ <- ent_extract_chunk(
    .docs = docs_, .plan = tab_plan, .dir_work = .lP$Work$Dir,
    .knobs = .KNOBS, .device = .lP$Param$Device
  )
  ptxt_ <- fs::path(.lP$Work$Dir, sprintf("text_%04d.parquet", as.integer(.i)))
  con_  <- ent_chunk_session(.cands = cand_, .docs = docs_, .path_text = ptxt_)

  out_ <- ent_resolve_chunk(
    .con       = con_,
    .path_text = ptxt_,
    .rules     = tab_rules,
    .keys      = dplyr::transmute(
      docs_, DocID, Fold = NA_integer_, Class = NA_character_,
      DateFiled  = suppressWarnings(anytime::anydate(as.character(.data$DateFiled))),
      AnchorKey  = ent_norm_company(.data$CompanyName),
      AnchorText = NA_character_
    ),
    .formats   = .DATE_FORMATS,
    .ctx_max   = .lP$Param$CtxMax,
    .head_pos  = .lP$Param$HeadPos
  )
  DBI::dbDisconnect(con_, shutdown = TRUE)
  fs::file_delete(ptxt_[fs::file_exists(ptxt_)])

  arrow::write_parquet(out_, path_)
  ent_write_timing(
    .dir     = .dir_out,
    .chunk   = .i,
    .n_docs  = nrow(out_),
    .seconds = as.numeric(difftime(Sys.time(), t0_, units = "secs")),
    .n_cands = nrow(cand_)
  )
  cli::cli_alert_success("Chunk {(.i)}: {nrow(out_)} document{?s} written.")
})
```

```{r}
#| label: apply-throughput
ent_report_throughput(.dir = .dir_out, .n_corpus = nrow(tab_index))
```

Set `Limit` to `NULL` once that projection is acceptable. The rate is measured on this machine under
this configuration, so it is the only figure worth planning a night around. `CandsPerDoc` times the
corpus is what has to be stored if the spans are released alongside the variables.

# Results

```{r}
#| label: results-summary
tab_vars <- fs::dir_ls(.dir_out, glob = "*.parquet") |>
  purrr::map(arrow::read_parquet) |>
  purrr::list_rbind()

ent_report_apply(.tab = tab_vars)
```

# Validation

```{r}
#| label: validate-release
tab_vars |>
  dplyr::summarise(
    Documents      = dplyr::n(),
    MedParties     = stats::median(.data$NParties, na.rm = TRUE),
    PctFilerParty  = mean(.data$HasFilerParty, na.rm = TRUE),
    PctStartBefore = mean(.data$ContractStart <= .data$DateFiled, na.rm = TRUE),
    PctAnyPlace    = mean(dplyr::coalesce(.data$NPlaces, 0L) > 0L),
    PctAnyAmount   = mean(!is.na(.data$MaxAmount))
  ) |>
  dplyr::mutate(dplyr::across(dplyr::starts_with("Pct"), \(.x) clf_pct(.x))) |>
  clf_say_table(.title = "The release against the EDGAR facts")
```

`PctFilerParty` is the number to compare against 04C. The sample put it at 64.8% under the same
policy, so a corpus figure far from that means the corpus differs from the sample in some way the
sample could not show -- and a figure close to it means the pipeline behaves as it was measured to.

```{r}
#| label: validate-coverage
tab_vars |>
  dplyr::summarise(
    dplyr::across(
      c(NParties, NPlaces, NPartyAddress, NRedact, NAmounts),
      \(.x) mean(dplyr::coalesce(.x, 0L) > 0L)
    )
  ) |>
  tidyr::pivot_longer(dplyr::everything(), names_to = "Variable", values_to = "Coverage") |>
  dplyr::mutate(Coverage = clf_pct(.data$Coverage)) |>
  dplyr::arrange(dplyr::desc(.data$Variable)) |>
  clf_say_table(.title = "Share of released documents carrying each variable")
```

Coverage is not uniform and must not be reported as though it were. A variable present in a third of
documents and nine tenths of another type is two different variables, and which contract types can
carry each one at all is the column that matters for the paper.

# Deployment

```{r}
#| label: deploy-summary
tibble::tibble(
  Artifact = c("Released variables", "Timings"),
  Path     = c(.dir_out, fs::path(.dir_out, "_timing"))
) |>
  dplyr::mutate(
    Files = purrr::map_int(.data$Path, \(.p) {
      if (!fs::dir_exists(.p)) return(0L)
      length(fs::dir_ls(.p, glob = "*.parquet"))
    }),
    MB   = purrr::map_dbl(.data$Path, \(.p) {
      if (!fs::dir_exists(.p)) return(0)
      round(sum(as.numeric(fs::file_size(fs::dir_ls(.p, glob = "*.parquet")))) / 1024^2, 1)
    }),
    Path = fs::path_rel(.data$Path, here::here())
  ) |>
  clf_say_table(.title = "Written by 04D")
```

# Next

The variables are written; what remains is the paper. Three things belong in it as limitations
rather than being discovered by a reader.

**Money is unvalidated.** EDGAR records no contract value, so the largest-amount heuristic is
carried because it is the best available, not because it has been checked. Only the redaction role
has external corroboration, and that speaks to six cues.

**The contract term is thin.** 04C found an expiry date for well under one percent of the sample,
and a window sensitivity check showed the cause is not the window. Until that is understood, the
term variable covers a small and possibly unrepresentative subset, and the published measure it
would replace remains the one with a standard deviation nobody can defend.

**Nothing validates the variables themselves.** The anchors confirm that the filer appears among the
resolved parties and that the contract date precedes its filing, which establishes that the
extraction finds real things. It does not establish that the party count, the term or the value are
right. That needs a document-level gold set of fifty to eighty contracts, and it is the one piece of
this family that cannot be built from EDGAR facts or a reading session.
