---
title: "Entity Apply -- The Five Rules at Corpus Scale (04D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ONE ORDERED LIST, SOURCED HERE AND NAMED TO THE DAEMONS. A mirai daemon is a fresh R process with
# none of this in it, and a closure does not carry its environment across a process boundary -- so a
# worker handed a function that calls ent_apply() finds no ent_apply(). Building the list once and
# walking it means the process that renders and the process that works load the same files in the
# same order, which two hand-written lists could not guarantee.
#
# THE COMMONS FIRST, AND init_create_script_fun() COMES FROM THEM. Naming the numbered scripts by
# that function before it exists is a bootstrap the render cannot survive, so the list is built in
# two steps: source what defines the resolver, then use it.
#
# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so
# every library that registers a vocabulary must follow it -- _Entity.R and all five 04B files do.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# THE FIVE RULE LIBRARIES, SOURCED AND CALLED RATHER THAN COPIED. Not one rule is reimplemented in
# this document; every function it calls is the one that produced the sample's release.
.path_libs <- c(
  .path_libs,
  purrr::map_chr(
    c("04B1-Rules-ORG", "04B2-Rules-GPE", "04B3-Rules-DATE",
      "04B4-Rules-MONEY", "04B5-Rules-REDACT"),
    \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
  )
)
purrr::walk(
  .x = utils::tail(.path_libs, 5L),
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "04D-EntityApply"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")

# APPENDED LAST, because a daemon calls apl_chunk_run() and it is defined in this file. Appended
# rather than named again, so the list a worker sources is exactly the list this process sourced.
.path_libs <- c(.path_libs, .path_fun)
```

# Purpose

This document applies the five 04B rules to the corpus 04C extracted and writes **the same eight long
files 04B released**, with 1.19 million contracts in them instead of 4,398.

## It decides nothing

04A measured which family to trust. 04B built and scored a rule per entity. 04C extracted the corpus.
Everything that could vary is declared in Configuration, printed in the render, and hashed into a
directory name, so a changed rule cannot be served output produced by a rule that no longer exists.

## Five passes, five hashes

| Pass | Hash covers | Reads |
|:--|:--|:--|
| ORG | party rule, window, lexnlp spec hashes | -- |
| GPE | reach, matcon spec hashes, **Hash(ORG)** | `org_mentions` |
| DATE | cascade, cap, matcon spec hashes | -- |
| MONEY | filter, window, matcon spec hashes | -- |
| REDACT | tolerance, matcon spec hashes | -- |

GPE folds in ORG's hash because it reads ORG's file. **REDACT depends on the extractor and not on
04B4** -- it reads matcon's money spans to find the ones the filer emptied, and "emptied" is a
pattern name rather than a filtered result.

## The unit of work is a chunk, and the worker reads its own

Every 04B chain is a vectorised `dplyr` pipeline over a whole table. Nothing in any of them loops
over documents: `ent_apply()` is six calls, `geo_apply()` is five, and each one groups and joins on
keys that always include `DocID`. Applying such a chain one document at a time does not isolate
anything -- it replaces one grouped `summarise()` over half a million rows with twenty-five thousand
`summarise()` calls over twenty, and pays `dplyr`'s fixed dispatch cost for every one of them.

So the unit is a **chunk of documents**, and Validation establishes that the choice of chunk cannot
change an answer rather than arguing it from the code.

**The worker reads its own data.** It is handed a list of `DocID`s and opens its own database
connection, its own anchors and its own spans. Nothing span-grain crosses a process boundary in
either direction: the parent splits a character vector and collects a row of numbers. The reverse
arrangement -- the parent reads and ships to workers -- makes the parent the bottleneck and
serialisation the dominant cost, whatever the unit of work happens to be.

Anchors cost about a fifth of a second for twenty-five thousand documents and a chunk's spans are one
range-bounded query, so a worker reading for itself is cheaper than a parent sending it the answer.

## Failure costs one document

A chunk that throws is retried in groups of `RetryFloor`, and a group that throws again one document
at a time. A single unparseable contract therefore costs itself and nothing else, and a healthy
corpus never pays for the machinery. That is the isolation a per-document unit would buy, kept as an
exception path instead of as the design.

## Resumption is by document

A pass asks which documents the ledger has and which are already written; the difference is the work.
Nothing is named for a position, so the chunk size can change between renders at no cost and a
population that grew simply adds to the queue.

**A chunk commits as a directory.** Everything it produces goes into a hidden name which is then
renamed into place. A rename within one filesystem is atomic, so a process killed mid-write leaves a
dotfile no glob sees.

**`_done.parquet` names every document processed**, not every document that produced a row. Seven of
the eight releases carry a row only where the extractor found something -- `redact_spans` reaches 19%
of documents -- so resuming on the outputs would reprocess the other 81% on every render, forever. A
document that *failed* is left out of it and retried.

## The release is eight long files

A directory of parquets already *is* an arrow dataset, so there is no final bind and no moment where
a partial pass could be assembled into something that looks finished.

Two underscore-prefixed files sit beside them and are **not part of the release**: `_done.parquet`
says which documents a chunk processed, and `_facts.parquet` carries the document-grain collapse this
document reports from. The collapse is written because the call that produced the release computed it
already -- `dte_apply()`, `mny_apply()` and `red_apply()` each return it -- so discarding it here and
rebuilding it in Results would be the same arithmetic twice, with two chances to disagree. **The
export reads neither**: it calls `ent_party_facts()`, `geo_collapse()`, `dte_collapse()`,
`mny_collapse()` and `red_collapse()` over the long files itself.

## Testing before committing

`Limit` takes the first N documents of every population and writes into its own directory, so a
rehearsal and a full run can sit on disk together without either reading the other.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # 04C's corpus stores, one DuckDB file per family.
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04C-EntityCorpus"),
      "Output"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    Lookup = here::here("contracts-extract", "src", "matcon_extract", "data", "geo_lookup.parquet"),
    # THE CORPUS LABEL SPINE, AND IT IS A DIRECTORY. 03F writes contract_labels_L<max_len>.parquet,
    # so the file name depends on the token limit that produced it and ent_release_path() resolves
    # it. READ BY THE OVERVIEW AND BY NOTHING ELSE: the five passes take their anchors from the
    # register alone, so no released file carries a class column and no pass can fail for want of
    # one. Every headline figure below is split by contract type, and a type is a label rather than
    # an extraction result.
    Labels = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03F-ClassifyApply"),
      "release"
    )
  ),
  Params = list(
    # THE FIVE PASSES IN DEPENDENCY ORDER. GPE reads ORG's file, so ORG runs first; the other three
    # are independent of both and of each other and could run in any order at all.
    Passes = c("ORG", "GPE", "DATE", "MONEY", "REDACT"),

    # THE COLUMNS THE ORG REDUCTION READS BESIDE THE SPAN. Named here rather than defaulted, because
    # ent_load_org() aborts on a missing one and the abort should name a choice this document made.
    Extras = list(ORG = c("NameCore", "LegalForm", "Description")),

    # DOCUMENTS PER CHUNK. A memory dial, not a correctness one: Validation shows the answer does not
    # depend on it. Measured on this corpus, twenty-five thousand documents is about 650,000 GPE
    # spans, which is a quarter of a gigabyte in and roughly a gigabyte through the chain.
    ChunkSize = 2500,

    # WORKERS. The chains are single-threaded R, so this is where the parallelism is. Twelve rather
    # than twenty-four because each worker holds a whole chunk and opens its own database; the reads
    # are one to two seconds against a chain of two to sixty, so contention buys nothing.
    Workers = 12L,

    # THREADS PER WORKER CONNECTION. Twelve DuckDB connections each helping themselves to every core
    # is 288 threads on a 24-core machine. Read by ner_db_connect() from an option, so nothing
    # outside this document's daemons is affected.
    DuckThreads = 2L,

    # DOCUMENTS PER RETRY GROUP. A chunk that throws is split into groups of this size, and a group
    # that throws again into single documents. Never reached on a healthy corpus.
    RetryFloor = 500L,

    # NULL IS THE FULL CORPUS. Set this to a number to rehearse: a limited run takes the first N
    # documents of every population -- the same first N, because every index is ordered by DocID --
    # and writes into its own directory.
    Limit = NULL,

    # WHICH ENGINE'S LABEL THE OVERVIEW SPLITS BY. 03F's release carries every engine side by side
    # and no single Class column, because which one is authoritative is a decision. 03B crowned
    # legal-bert, so Bert it is -- and nothing but the figures reads this.
    Engine = "Bert",

    # The cue window DATE narrows the stored 160 characters to. MONEY's lives in its own
    # specification because it is swept there.
    CueWin = list(Date = 120L)
  )
)

# THE RULES THEMSELVES, each constructed by the 04B function that defined it, with every argument
# named at the value 04B released. A dial not named here is a decision nobody reviewed.
.lP$Params$Rule <- list(
  Org = ent_rule(
    .key             = "core",   # 04B1: the reduced key, suffixes stripped
    .merge_fragments = TRUE      # 04B1: a single word unambiguously taken from one longer name
  )
)

.lP$Params$Spec <- list(
  Org = ent_window_spec(
    .par        = 2000,    # 04B1: characters either side of the registrant
    .tail_share = 0.10     # 04B1: the final tenth, counted as signatories
  ),
  Geo = geo_spec(
    .reach = 200           # 04B2: furthest a party may be and still claim a place
  ),
  Date = dte_spec(
    .start     = "latest", # 04B3: the latest date at or before the filing
    .end       = "term",   # 04B3: the full four-rung cascade
    .cap_years = 30        # 04B3: dropped above this, not winsorised
  ),
  Money = mny_spec(
    .filter  = "par",      # 04B4: drops a zero, and a figure with par-value language beside it
    .cue_win = 60L         # 04B4: characters read EITHER SIDE
  ),
  Redact = red_spec(
    .tol = 10L             # 04B5: slack between a marker and a withheld price that do not overlap
  )
)

tab_inputs <- tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
)

tbl_say(.tab = tab_inputs, .title = "Every input resolves before anything is computed")

# A TABLE OF FALSE IS A REPORT, NOT A GATE, and the difference has cost a render before.
if (any(!tab_inputs$Exists)) {
  cli::cli_abort(c(
    "{sum(!tab_inputs$Exists)} input{?s} {?does/do} not resolve.",
    "x" = "{paste(tab_inputs$Input[!tab_inputs$Exists], collapse = ', ')}."
  ))
}
```

The loader `ent_load_entity()` bounds its SQL on the `DocID` range the chunk covers. That bound
cannot change an answer -- the `inner_join` beneath it is the membership test and always was -- but
without it every chunk reads the whole entity table and discards 98% of it, which on matcon's GPE
table is 27.6 million rows carrying two 160-character cue columns, once per chunk.

## The five policies, and the directories they name

```{r}
#| label: policy

# THE SAME DESCRIPTION 04C RAN. The spec hashes it records are folded into each pass's hash, because
# a re-extraction that moved a model's rules leaves every parameter above unchanged while every span
# underneath them is different.
tab_describe <- ner_describe(
  .spacy_models = character(),
  .lexnlp_image = "contracts-lexnlp"
)

# THE HASHES ARE BUILT IN DEPENDENCY ORDER, because GPE's folds in ORG's. Computing them in a fold
# rather than by hand is what keeps that true when a sixth pass arrives.
.lP$Params$Hash <- purrr::reduce(
  .x = .lP$Params$Passes,
  .f = function(.acc, .p) {
    dep_ <- apl_pass_spec(.pass = .p)$Depends
    c(.acc, purrr::set_names(
      apl_policy_hash(
        .pass     = .p,
        .params   = .lP$Params,
        .describe = tab_describe,
        .depends  = if (is.na(dep_)) NULL else .acc[dep_]
      ),
      .p
    ))
  },
  .init = character(0)
)

# THE LIMIT NAMES THE DIRECTORY AND THE CHUNK SIZE DOES NOT. A rehearsal and a full run must never
# share output; how the work was divided is nobody's business once it is written.
.suffix <- if (is.null(.lP$Params$Limit)) "" else paste0("-limit", .lP$Params$Limit)

.lP$Output <- list(
  # A NAMED CHARACTER VECTOR AND NOT A LIST, so every use is [["ORG"]] rather than $ORG. map_chr()
  # returns atomic, and $ on an atomic vector is an error rather than a lookup.
  Store = purrr::set_names(
    purrr::map_chr(
      .lP$Params$Passes,
      \(.p) utils_file_path(.dir_main, "Store", .p, paste0(.lP$Params$Hash[[.p]], .suffix))
    ),
    .lP$Params$Passes
  )
)

fs::dir_create(.lP$Output$Store)

apl_report_policy(
  .tab    = apl_policy_table(.params = .lP$Params),
  .hashes = .lP$Params$Hash,
  .limit  = .lP$Params$Limit
)
```

# Input

## The population, one per pass

```{r}
#| label: corpus-index

tab_index <- purrr::set_names(
  purrr::map(
    .lP$Params$Passes,
    \(.p) apl_corpus_index(
      .dir_store = .lP$Input$Store,     # 04C's stores, one per family
      .pass      = .p,                  # which family's ledger and which entities
      .limit     = .lP$Params$Limit     # NULL is the full population
    )
  ),
  .lP$Params$Passes
)

tibble::tibble(
  Pass       = names(tab_index),
  Family     = purrr::map_chr(names(tab_index), \(.p) apl_pass_spec(.pass = .p)$Family),
  Needs      = purrr::map_chr(names(tab_index),
                              \(.p) paste(apl_pass_spec(.pass = .p)$Needs, collapse = ", ")),
  Population = purrr::map_int(tab_index, nrow)
) |>
  dplyr::mutate(Population = format(.data$Population, big.mark = ",")) |>
  tbl_say(.title = "What each pass will reach")
```

**The population is per family, not per entity.** Every matcon entity finished the same documents and
every lexnlp entity the same, so ORG runs on lexnlp's population and the other four on matcon's. Where
the two differ, a place in a document ORG has not reached carries `Attached = FALSE` and a null
`PartyKey` -- a refusal recorded in the file rather than a row missing from it -- and any attachment
rate is therefore reported over the documents `org_mentions` actually names.

**The ledger and not the entity tables.** A document processed and found to hold no date has no row in
the date table and is not missing: it is a contract with no date in it, which is a measurement. Taking
the population from the tables would silently drop exactly those documents.

## Output from an earlier design

```{r}
#| label: check-legacy

apl_check_legacy(.dirs = .lP$Output$Store)
```

An earlier version of this document named its committed directories `window-*`; this one names them
`chunk-*`. Nothing here reads the old name, so an interrupted run under the old design would sit in a
release directory being neither read nor counted. It is reported rather than removed, because a
superseded output is renamed out of the way and kept as a record of what was previously concluded.

## The gazetteer

```{r}
#| label: build-gazetteer

# THE SERIAL PATH'S COPY. Each daemon builds its own, once, because 181,810 rows sent with every
# chunk would cost more than the rule that reads them.
geo_once <- list(
  Lookup = geo_lookup(.path_lookup = .lP$Input$Lookup),
  Cand   = geo_candidates(.path_lookup = .lP$Input$Lookup)
)
```

# Apply

Each pass reads what its ledger has, subtracts what is written, and runs the rest. **ORG first**,
because GPE reads its file; the other three are independent of both and of each other.

```{r}
#| label: apply-setup

# ASKED FRESH IN EVERY SECTION rather than once here, because a pass that just ran has changed its
# own done set.
apl_todo <- function(.pass) {
  setdiff(tab_index[[.pass]]$DocID, apl_done_ids(.dir = .lP$Output$Store[[.pass]]))
}
```

## ORG

```{r}
#| label: run-org

res_org <- apl_pass_run(
  .pass     = "ORG",
  .todo     = apl_todo(.pass = "ORG"),          # population minus what is already written
  .dir_out  = .lP$Output$Store[["ORG"]],
  .paths    = .lP$Input,                        # a worker resolves its own reads from these
  .params   = .lP$Params,
  .geo      = NULL,                             # ORG reads no gazetteer
  .path_fun = .path_libs                        # a daemon has none of this loaded; it sources by path
)
```

## GPE

```{r}
#| label: run-gpe

# THE ONE CROSS-PASS READ. Built here rather than inside a chunk, because it scans one column of each
# of ORG's files and would otherwise do so once per chunk.
tab_dep_org <- apl_dep_index(.dir = .lP$Output$Store[["ORG"]], .stem = "org_mentions")

res_gpe <- apl_pass_run(
  .pass      = "GPE",
  .todo      = apl_todo(.pass = "GPE"),
  .dir_out   = .lP$Output$Store[["GPE"]],
  .paths     = .lP$Input,
  .params    = .lP$Params,
  .geo       = geo_once,                        # the serial path's copy; a daemon builds its own
  .dep_index = tab_dep_org,                     # which of ORG's files each chunk overlaps
  .path_fun  = .path_libs
)
```

## DATE

```{r}
#| label: run-date

res_date <- apl_pass_run(
  .pass     = "DATE",
  .todo     = apl_todo(.pass = "DATE"),
  .dir_out  = .lP$Output$Store[["DATE"]],
  .paths    = .lP$Input,
  .params   = .lP$Params,
  .path_fun = .path_libs
)
```

## MONEY

```{r}
#| label: run-money

res_money <- apl_pass_run(
  .pass     = "MONEY",
  .todo     = apl_todo(.pass = "MONEY"),
  .dir_out  = .lP$Output$Store[["MONEY"]],
  .paths    = .lP$Input,
  .params   = .lP$Params,
  .path_fun = .path_libs
)
```

## REDACT

```{r}
#| label: run-redact

res_redact <- apl_pass_run(
  .pass     = "REDACT",
  .todo     = apl_todo(.pass = "REDACT"),
  .dir_out  = .lP$Output$Store[["REDACT"]],
  .paths    = .lP$Input,
  .params   = .lP$Params,
  .path_fun = .path_libs
)
```

## What the five did

```{r}
#| label: report-pass

tab_pass <- purrr::list_rbind(list(res_org, res_gpe, res_date, res_money, res_redact))

apl_report_pass(.tab = tab_pass, .index = tab_index, .dirs = .lP$Output$Store)
```

`Secs` is worker time summed rather than wall clock, so the elapsed figure is roughly that divided by
the worker count. On a first render `Left` falls to zero across all five passes; on any later one
every pass reports nothing outstanding and the whole section takes seconds, which is what makes an
always-executed document affordable.

# Results

## What the eight files hold

```{r}
#| label: report-outputs

tab_out <- apl_table_outputs(.dirs = .lP$Output$Store, .index = tab_index)

apl_report_outputs(.tab = tab_out)
```

**Only `org_mentions` is built from the key side**, so it alone must read 100%: 04B1 writes a sentinel
row for a contract in which no organisation was found. The other seven are span files, and a
percentage below 100 there is a measurement about the corpus rather than a gap in the pass.

The denominator for any rate is therefore the pass's population and never the file's own `DocID`
count. A contract with no redaction marker has no row in `redact_spans` and still redacted nothing;
counting only the documents present would report every contract in the corpus as having redacted
something.

## The rule against the naive definition

```{r}
#| label: report-naive

tab_facts <- purrr::set_names(
  purrr::map(.lP$Params$Passes, \(.p) apl_facts(.dir = .lP$Output$Store[[.p]])),
  .lP$Params$Passes
)

tab_naive <- apl_table_naive(.facts = tab_facts)

apl_report_naive(.tab = tab_naive, .limit = .lP$Params$Limit)
```

**Every pair comes from the same collapse function 04B reports from.** `ent_doc_facts()`,
`geo_doc_facts()`, `dte_collapse()`, `mny_collapse()` and `red_collapse()` ran inside the chunk that
produced the release, so a corpus figure and a sample figure are one query on different data rather
than two implementations free to disagree at the third decimal.

**Read these against 04B's own headline tables.** A corpus rate far from the sample rate is either a
finding about representativeness or a defect in this pass, and the two are told apart by reading spans
rather than by reading this table.

# Validation

## The partition cannot change an answer

```{r}
#| label: check-split

# THE SAME DOCUMENTS, CUT TWO WAYS. Four hundred is enough for every chain to exercise its grouping:
# ORG merges spellings within a contract, GPE resolves an ambiguous city against a state the same
# contract names, REDACT matches a marker to a price by offset. If any of those ever reached outside
# the document it was handed, the halves would disagree here.
#
# TAKEN FROM THE MIDDLE AND NOT THE HEAD. A DocID begins with an accession number, which begins with
# the filer's CIK, so the first four hundred documents of a sorted population are the oldest
# registrants rather than a fair draw of contracts.
.n_split <- 400L

apl_split_ids <- function(.pass) {
  ids_  <- tab_index[[.pass]]$DocID
  from_ <- max(1L, floor(length(ids_) / 2L))
  ids_[seq.int(from_, min(length(ids_), from_ + .n_split - 1L))]
}

tab_split <- purrr::map(.lP$Params$Passes, function(.p) {
  apl_check_split(
    .pass      = .p,
    .doc_ids   = apl_split_ids(.pass = .p),
    .paths     = .lP$Input,
    .params    = .lP$Params,
    .geo       = geo_once,
    .dep_index = if (.p == "GPE") tab_dep_org else NULL
  )
}) |>
  purrr::list_rbind()

apl_report_split(.tab = tab_split, .n = .n_split)
```

This is the claim the whole design rests on, and it is checked rather than argued. Every grouping and
every join key in all five chains carries `DocID`, so a rule applied to a chunk cannot be reading a
quantity computed over the group it happened to be handed -- but that is a property of code as it
stands today, and a rule that grew a corpus-wide denominator tomorrow would make the released numbers
depend on the chunk size with nothing to notice. 04B1's family-frequency gate was removed for exactly
that reason; this is what would catch its return.

A failure here means the release is not reproducible and should not be published, which is why it
aborts rather than warns.

## The done set and the release agree

```{r}
#| label: check-done

apl_report_done(.tab = apl_check_done(.dirs = .lP$Output$Store, .index = tab_index))
```

Three ways for the partition to have leaked, all of them silent in the output. A document named in two
`_done` files was processed twice and its rows are in the release twice. A document processed that the
ledger does not name came from somewhere this document cannot account for. A file holding rows for a
document no chunk recorded processing means a chunk wrote about something it was not asked about.

# Robustness

## The corpus files have the shape 04B released

```{r}
#| label: check-schema

apl_report_schema(.tab = apl_check_schema(.dirs = .lP$Output$Store))
```

**The same check 04B runs, on the corpus rather than the sample.** Each 04B document builds a
dictionary from a declared list and aborts where it disagrees with the file it wrote; running the same
functions here is what says the corpus release has the same shape as the sample release, so a reader
who knows one knows the other.

Schema from Arrow, never inferred -- `names(open_dataset())` reads the parquet's own schema, so a
column added or renamed by a chain is seen as the file has it rather than as this document expects it.

# Deployment

```{r}
#| label: report-release

tibble::tibble(
  Pass = .lP$Params$Passes,
  Path = purrr::map_chr(.lP$Params$Passes,
                        \(.p) fs::path_rel(.lP$Output$Store[[.p]], start = here::here())),
  Chunks = purrr::map_int(.lP$Params$Passes,
                          \(.p) length(apl_chunk_dirs(.dir = .lP$Output$Store[[.p]])))
) |>
  tbl_say(.title = "Where each pass's release is, and how many chunks it holds")
```

Each path is a directory of chunk directories, and each chunk directory holds that pass's release
files plus `_done.parquet` and `_facts.parquet`. A consumer opens the release with
`arrow::open_dataset()` over the matching stem across all chunks; the two underscore-prefixed files
are this document's bookkeeping and belong to no downstream reader.

# Overview

Everything below is a corpus version of a figure one of the five 04B documents already produced on
4,398 documents. Nothing here is new: it is the same rule, the same function and the same argument,
read against 1.19 million contracts instead of a sample, so the question each figure answers is
whether the sample was telling the truth.

## The label spine the figures split by

```{r}
#| label: overview-labels

# 03F STAMPS THE TOKEN LIMIT INTO THE FILE NAME, so the release is found rather than named.
path_labels <- ent_release_path(.dir_release = .lP$Input$Labels)

tab_class <- apl_class(
  .path_release = path_labels,                    # NA aborts, naming 03F
  .engine       = .lP$Params$Engine,              # which engine's label is authoritative
  .doc_ids      = unique(unlist(purrr::map(tab_index, \(.t) .t$DocID), use.names = FALSE))
)

# THE FACTS AGAIN, RESTRICTED TO THE DOCUMENTS THAT CARRY A TYPE. Read once in Results and joined
# here; the by-type figures therefore describe a smaller population than the tables above, and the
# coverage line says how much smaller.
tab_facts_class <- apl_label_facts(.facts = tab_facts, .class = tab_class)
```

**No released file carries a class column and no pass reads one.** The five passes take their anchors
from the register alone, which is why nothing in Apply, Results or Validation can fail for want of a
label. The figures are the exception, and they are the only one.

## The tables the figures are drawn from

```{r}
#| label: overview-tables

# THE 04B TABLE FUNCTIONS, CALLED ON CORPUS INPUT. Not one of these is reimplemented here: a figure
# that looked like 04B's but was computed differently would be the worst of both.
tab_org_naive <- ent_table_naive(.doc = tab_facts_class$ORG)
tab_gpe_naive <- geo_table_naive(.doc = tab_facts_class$GPE)

tab_gpe_law <- geo_table_law_top(
  .law = apl_law(.dir = .lP$Output$Store[["GPE"]]),   # Jurisdiction and its level, nothing else
  .n   = 15L                                          # the tail is long and uninformative
)

# THE DENOMINATOR IS THE WHOLE POPULATION AND NOT THE LABELLED PART. PctDocs is the share of
# contracts carrying a marker of each kind, and restricting it to labelled documents would report a
# rate about 03F's coverage rather than about redaction.
tab_red_kind <- red_table_kind(
  .marks   = apl_marks(.dir = .lP$Output$Store[["REDACT"]]),
  .release = tab_facts$REDACT
)

# ROW COUNTS FOR THE FIGURE LADDER, taken once here so no chunk option has to compute one. Height is
# the only dimension that varies; width is global and set in _quarto.yml.
.fig_n <- list(
  Class  = dplyr::n_distinct(tab_class$Class),
  Law    = nrow(tab_gpe_law),
  Source = dplyr::n_distinct(
    dplyr::filter(tab_facts$DATE, !is.na(.data$DurationYears),
                  .data$DurationSource != "none")$DurationSource
  ),
  Kind   = nrow(tab_red_kind)
)
```

## Parties

```{r}
#| label: fig-org-naive
#| fig-height: !expr plot_height(.fig_n$Class)
#| fig-cap: "Mean counterparties per contract by type: every distinct organisation the
#|   extractor proposed, against only those the rule keeps."

ent_plot_naive(.tab = tab_org_naive)
```

The naive bar is what a reader gets by counting distinct organisation names in a contract. The rule
bar is what survives grouping spellings into parties, matching the registrant and its co-filers
against EDGAR, and keeping only what sits inside the window around the contracting party. The gap
between the two is the rule, read directly, and it is largest exactly where it should be: on the
agreement types whose exhibit lists and cross-references name companies that are not parties to
anything.

## Geography

```{r}
#| label: fig-gpe-naive
#| fig-height: !expr plot_height(.fig_n$Class)
#| fig-cap: "Distinct states per contract by type, at three rungs: every place resolved,
#|   those outside a governing-law clause, and those the rule attaches to a counterparty."

geo_plot_naive(.tab = tab_gpe_naive)
```

Each rung is one filter further than the last, so a reader who rejects a step takes the bar above it.
The step from naive to law-free removes the states named only because a contract says which law
governs it; the step to the rule removes every remaining place that sits too far from any party to be
that party's address.

```{r}
#| label: fig-gpe-law
#| fig-height: !expr plot_height(.fig_n$Law)
#| fig-cap: "The fifteen commonest governing-law jurisdictions, as a share of the clauses
#|   that name one."

geo_plot_law(.tab = tab_gpe_law)
```

The jurisdiction is not extracted as such: `lawregex` locates the clause and the jurisdiction is the
place span sitting inside it, resolved by the same gazetteer that resolves every other place. The
concentration this figure shows is the check on that -- a governing-law rule that were picking up
noise would not produce this distribution.

## Dates

```{r}
#| label: fig-date-source
#| fig-height: !expr plot_height(.fig_n$Class)
#| fig-cap: "Where each contract's duration came from, by type, as a share of contracts."

dte_plot_source(.dur = tab_facts_class$DATE)
```

The cascade tries a stated term first, then a cued end date, then any future date, and records which
rung answered. A type dominated by the stated-term rung is one whose drafters write the duration
down; a type dominated by the later rungs is one where the duration is inferred, and every figure
resting on it inherits that.

```{r}
#| label: fig-date-spread
#| fig-height: !expr plot_height(.fig_n$Source)
#| fig-cap: "Contract duration in years, by the rung that produced it. Read the spread across
#|   rungs rather than the medians."

dte_plot_spread(.dur = tab_facts$DATE)
```

This is the figure the duration argument rests on. The naive definition -- the furthest future date
anywhere in the document -- has a standard deviation the Results table puts in the hundreds of years,
because a contract mentioning a patent expiry or a perpetual licence gets that date as its term. Under
the cascade and the thirty-year cap the spread is a few years, and this figure shows where the
remaining variation actually sits.

## Money

```{r}
#| label: fig-money-max
#| fig-height: !expr plot_height(.fig_n$Class)
#| fig-cap: "The largest USD amount per contract by type, on a log scale, after the zero and
#|   par-value filters."

mny_plot_max(.release = tab_facts_class$MONEY)
```

Contract value is the quantity most likely to be read straight out of this pipeline, and the ordering
across types is the sanity check on it. The filters remove a par value of $0.0001 per share and every
zero; what remains is the largest figure the contract actually names, which is not the same thing as
its value and should not be reported as if it were.

## Redactions

```{r}
#| label: fig-redact-kind
#| fig-height: !expr plot_height(.fig_n$Kind)
#| fig-cap: "Each marker kind as a share of all markers, and as the share of contracts
#|   carrying at least one."

red_plot_kind(.tab = tab_red_kind)
```

The two bars answer different questions and disagree for a reason. A handful of contracts carry
thousands of markers, so the span-weighted share describes those documents; the document-weighted
share describes the corpus. Where a kind is large on the first bar and small on the second, it is a
property of a few filings rather than of redaction practice.

## The five passes in one table

```{r}
#| label: report-headline

apl_report_headline(.out = tab_out, .hashes = .lP$Params$Hash, .index = tab_index)
```

# Next

The eight files are the entity release. **An export script** turns them into whatever shape the
downstream work wants -- calling `ent_party_facts()`, `geo_collapse()`, `dte_collapse()`,
`mny_collapse()` and `red_collapse()` to produce one row per party or per contract, fanning
attachment-level rows out to all 1,462,939 registrant copies on `HashDocument`, joining the
classification labels, and writing whatever format Stata reads.

That is a separate document, because a release and a reshaping of it are different acts and only one
of them should ever have to be re-run.
