---
title: "Entity Extraction at Scale -- Every Engine Over the Whole Corpus (04D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: 03A
# aliases the table helpers at SOURCE time, so sourcing it first throws part-way through the file.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A supplies the console formatter and the text reader; 04A the entity vocabularies and the store
# overview; 04B the policy reader. The corpus is extracted by the code the sample was extracted
# with, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract", "04B-EntityMeasure"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04D-EntityApply.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran every available extractor over the 4,398 hand-classified contracts and described what came
back. 04B measured which engines to keep. This document runs the survivors over the whole
Exhibit-10 corpus -- around 1.46 million documents, none of them labelled -- and writes every
candidate span into one DuckDB store.

**That store is the deliverable, and nothing here resolves anything.** No roles are assigned, no
variables are built, no window is applied. Those are 04E.

## Why extraction and resolution are separate documents

They were one document, and separating them is the whole point of building a store.

Extraction is expensive, deterministic and settled: the engine set was decided in 04B on measured
recall, and running it costs days. Resolution is cheap, contested and still being designed -- the
role rules came from reading sessions rather than measurement, the tie-break between competing cues
was rewritten once already, and the window that was in force turned out to have been chosen on a
quantity it could not see.

Fused, every change to a rule meant re-extracting 1.46 million documents. Split, a rule change is a
re-read of a store that already exists. The expensive half is done once and the contested half can
be argued about for as long as it needs.

## The offset contract, and how it differs from 04A's

04A freezes one canonical text to disk and every offset in the project indexes that file. A corpus
this size cannot be frozen that way: the text alone runs to tens of gigabytes, and storing a second
copy of the corpus to guarantee a property is a poor trade.

So the contract here is the reading **function** rather than a file. Every offset indexes
`clf_read_text(Path)`, which is deterministic and is the same function 04A derived its canonical
text with. The two stores are therefore in the same coordinate system by construction.

That holds only while the parsed tree holds. Regenerate the corpus and every offset in the store
silently indexes a different string: `is.na()` catches nothing, spans rehydrate as plausible
nonsense, and no number changes visibly. The fingerprint below is what makes that failure loud, and
it is fatal rather than advisory -- on the sample a stale store wastes a render, here it produces a
released dataset whose spans point at the wrong characters.

## Resumption is the ledger, not the output

The store records each document against each engine. An interrupted run therefore resumes at the
document it stopped on rather than at the start of a chunk, and re-running a finished pass costs one
query per engine. Chunks bound memory; they do not bound work.

# Configuration

```{r}
#| label: configure-paths
.dir_measure <- init_create_script_dir(.dir_here = here::here(), .name_script = "04B-EntityMeasure")

.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus tree
    # conjured into existence would report itself present while holding nothing.
    Policy      = fs::path(.dir_measure, "extraction_policy.parquet"), # written by 04B
    DirCorpus   = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/",
    MetaData    = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    LandingPage = "../pMatDisc/2_output/01-GetEDGAR/Output/LandingPage.parquet"
  ),
  Cache = list(
    CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet") # DocID to Path index
  ),
  Store = list(
    # THE DELIVERABLE. One file, same schema as 04A's sample store, written by the same code.
    NerDB    = utils_file_path(.dir_main, "Store", "CorpusCandidates.duckdb"),
    Manifest = utils_file_path(.dir_main, "Store", "manifest.parquet"),
    # Plain text, one line per chunk, appended. This is what makes a two-day pass watchable: tail
    # it from another terminal, read it after RStudio has been closed, check it on a machine running
    # the pass headless. Console output is buffered by knitr and gone when the session ends; a file
    # is neither.
    Progress = utils_file_path(.dir_main, "Store", "progress.log")
  ),
  Work = list(
    Dir = utils_file_path(.dir_main, "Work")   # per-chunk text parquet, deleted as it is consumed
  ),
  Param = list(
    ChunkSize  = 2000L,  # documents held in memory at once; not a unit of resumption
    IndexRerun = FALSE,  # TRUE re-walks the tree; FALSE reuses the cached index
    Device     = "auto",
    # The switch that decides whether this document is a rehearsal or the release. An integer draws
    # that many documents at random from the whole tree and writes them to a separate store; NULL
    # processes the corpus. Set an integer, read the throughput, then set NULL.
    Limit      = NULL
  )
)

# Per-combination throughput settings, and only the engines the policy names. LexNLP is the one to
# watch: it runs in a container, its date grammar stalls pathologically on a small number of long
# documents, and it now reads full text. The timeout is what keeps a stall from becoming a hang.
.KNOBS <- list(
  "lexnlp"              = list(n_process = 24L, batch_size =  8L, timeout = 60L),
  "paper:gazetteer-v1"  = list(n_process = 16L, batch_size =  8L, timeout = 120L),
  "paper:redaction-v1"  = list(n_process = 16L, batch_size = 64L, timeout =  0L),
  "paper:moneyregex-v4" = list(n_process = 16L, batch_size = 64L, timeout =  0L),
  "paper:dateregex-v1"  = list(n_process =  1L, batch_size = NULL, timeout = 0L)
)

fs::file_exists(.lP$Input$Policy)
```

# The plan

```{r}
#| label: load-policy
tab_policy <- ent_read_policy(.path = .lP$Input$Policy)
tab_plan   <- ent_engine_plan(.policy = tab_policy)
lst_labels <- ent_plan_labels(.plan = tab_plan)

# Checked before any work starts rather than discovered inside the extraction loop. The dispatch is
# a chain of branches, so an engine it does not cover would abort after the index is built and the
# first chunks have run -- hours into a corpus pass.
ent_check_plan(.plan = tab_plan, .knobs = .KNOBS)

tbl_say(
  .tab = tab_plan |>
    dplyr::mutate(Labels = purrr::map_chr(.data$Labels, \(.x) paste(.x, collapse = ", "))),
  .title = "Extractor runs per chunk"
)
```

A label appearing under two engines is not a mistake. 04B unions the cheap rule arms into the policy
regardless of the ranking, so dates are extracted by LexNLP and by the ported date patterns, and the
spans both propose are deduplicated when 04E reads them.

# The corpus

```{r}
#| label: build-index
tab_index <- ent_corpus_index(
  .dir_corpus   = .lP$Input$DirCorpus,     # the parsed-contract tree, Exhibit 10 only
  .path_meta    = .lP$Input$MetaData,      # filer name and filing date, carried for 04E
  .path_landing = .lP$Input$LandingPage,   # registered addresses, likewise
  .path_cache   = .lP$Cache$CorpusFiles,   # walking a million files is cached, not repeated
  .rerun        = .lP$Param$IndexRerun,
  .limit        = .lP$Param$Limit,         # NULL processes the corpus; an integer rehearses
  .seed         = 42L
)

# The timing log sits beside the store, and a limited run writes to the same place as a full one.
.dir_store <- fs::path_dir(.lP$Store$NerDB)
```

**A limited run is the first part of the release, not a throwaway.** Earlier versions of this
document wrote a rehearsal to a separate directory so it could not be mistaken for a corpus pass.
That was right when the output was a set of resolved variables, where a partial file read as a
complete one. It is wrong for a store: the ledger records each document against each engine, so a
rehearsal's ten thousand documents are simply ten thousand documents that no longer need doing.
Setting `Limit` to `NULL` afterwards continues from there rather than starting again.

The fingerprint is taken against the **corpus**, not against whatever the limit left in hand. A
rehearsal that fingerprinted its own draw would abort the release run reporting a regenerated tree
when nothing had changed -- the one message here that a reader would act on immediately, and
wrongly.

# The store fingerprint

```{r}
#| label: check-manifest
ent_corpus_manifest_sync(
  .path_manifest = .lP$Store$Manifest,
  .manifest      = ent_corpus_manifest(
    .index  = tab_index,        # documents and their size on disk
    .run    = tab_plan$Combo,   # which engines
    .labels = lst_labels        # and which labels each was asked for
  )
)
```

A **fingerprint** row that fails means the parsed tree has changed since this store was built --
document count or total bytes on disk, both measured over the whole corpus whatever `Limit` says. Every
offset it holds indexes text that no longer exists, and nothing downstream can detect that. Move the
store aside and rebuild.

The **inventory** row is not a fingerprint. Which engines have been asked for says nothing about
what is already stored, and adding one is the ordinary incremental case the ledger handles: the new
engine reports its documents missing and the rest report none.

# Extraction

The store is asked what it already holds before any text is read, and says so. `ner_run()` would skip completed
documents anyway, but only after each chunk had read its documents off disk and written them out --
on a corpus re-render, 1.46 million file reads to establish that the work was already done.

Asking here instead makes the remaining work the thing that gets chunked, so the progress bar counts
against a denominator that means something and the throughput rate is not diluted by chunks that
did nothing.

```{r}
#| label: store-status
fs::dir_create(fs::path_dir(.lP$Store$NerDB))

ent_store_status(
  .db_path  = .lP$Store$NerDB,
  .n_corpus = ent_corpus_n(tab_index),   # the whole tree, whatever Limit says
  .run      = tab_plan$Combo,
  .dir      = .dir_store                 # supplies the rate already measured
)

tab_todo <- ent_pending(
  .db_path = .lP$Store$NerDB,   # absent means everything is pending
  .index   = tab_index,
  .run     = tab_plan$Combo     # a document is done only when every declared engine has seen it
)
```

A document counts as complete only when **every** declared engine has seen it, which is why adding
an engine to the policy makes every document in the store incomplete again. That is correct rather
than surprising, and this is where it becomes visible.

```{r}
#| label: extract-corpus
chunks_ <- if (nrow(tab_todo) == 0L) {
  list()
} else {
  split(tab_todo, ceiling(seq_len(nrow(tab_todo)) / .lP$Param$ChunkSize))
}

if (length(chunks_) == 0L) {
  cli::cli_alert_success(
    "Nothing to extract: every document in scope is already in the store. Raise Limit or set it \\
     to NULL to take in more of the corpus."
  )
}

prog_ <- ent_progress_new(
  .n_chunks = length(chunks_),
  .n_docs   = nrow(tab_todo),
  .path_log = .lP$Store$Progress   # tail -f this to watch a long pass from anywhere
)

tab_timing <- purrr::imap(chunks_, function(.chunk, .i) {
  out_ <- ent_extract_corpus_chunk(
    .chunk    = .chunk,
    .db_path  = .lP$Store$NerDB,   # one store for the whole corpus
    .run      = tab_plan$Combo,
    .labels   = lst_labels,
    .dir_work = .lP$Work$Dir,      # the chunk's text parquet, written and deleted
    .knobs    = .KNOBS,
    .device   = .lP$Param$Device
  )
  ent_write_timing(
    .dir     = .dir_store,
    .chunk   = .i,
    .n_docs  = out_$nDocs,     # documents in the chunk
    .n_new   = out_$nNew,      # of which this many actually had to be extracted
    .seconds = out_$Seconds
  )
  ent_progress_step(.progress = prog_, .n_new = out_$nNew, .seconds = out_$Seconds)
  out_
}) |>
  purrr::list_rbind()
```

One line per chunk, written with `cat()` and flushed immediately, and appended to a plain text log.
Not through `cli`, and that matters: `cli` emits a condition through `message()`, and anything that
handles messages holds them -- knitr buffers a chunk's messages until the chunk ends, so a loop
running for two days shows nothing at all until it is over. Three earlier attempts here, a purrr
bar and a `cli` bar and `cli` alert lines, all produced silence for that reason.

The log file is the part that actually solves it. Console output is buffered under a render and gone
when the session ends; a file is neither, so `tail -f` on it works from another terminal, after
RStudio has been closed, or on a machine running the pass headless.

The rate is cumulative, so one slow chunk moves the estimate rather than dominating it, and the line
carries the number a bar's only real advantage was: when this finishes.

**A run with nothing pending prints nothing from this loop, and that is why the status table above
exists.** A silent loop and a broken loop look identical, so the state is reported before the work
rather than inferred from its absence.

Nothing is deleted on a re-run and nothing is recomputed. A second render finds every document
already in the ledger, extracts nothing, and says so.

# Results

```{r}
#| label: summarise-store
.ov <- ent_overview(
  .db_path  = .lP$Store$NerDB,
  .inputs   = NULL,   # the corpus text is not held on disk; length and position need 04E
  .id_col   = "DocID",
  .text_col = "TextRaw",
  .quiet    = FALSE
)

ent_report_store(.ov = .ov)
```

`Docs` must be identical across engines. A shortfall is an unfinished run, not a quiet engine, and
re-running this document resolves it.

Position and length are absent, and deliberately: computing them needs the text, which this document
reads a chunk at a time and does not keep. 04A reports both on the sample, where the canonical text
is on disk, and the corpus is assumed to behave the same way only where it is said so explicitly.

# Throughput

```{r}
#| label: report-throughput
ent_report_throughput(
  .dir      = .dir_store,
  # NOT nrow(tab_index). Under a rehearsal the index holds the rehearsal, so nrow() would project
  # the corpus pass onto the sample and report it as a fraction of an hour.
  .n_corpus = ent_corpus_n(tab_index),
  # From the store rather than the timing log: a resumed chunk does no work and would contribute a
  # zero. CorpusMCand is the projected store in millions of candidate spans.
  .n_cands  = sum(.ov$ledger$Candidates)
)
```

Read the projection as a floor. The draw is random across the whole tree, so it is unbiased on
document count -- but cost follows length, and 04A found the corpus tail longer than the labelled
sample's.

The rate is per document **extracted**, not per document seen. That distinction is what stops a
resumed run from flattering itself: a chunk the ledger already covered returns its full document
count in seconds, and a rate taken over documents seen would improve every time the pass was
restarted, silently and in the direction that makes it look affordable.

`CorpusMCand` is what the finished store holds, in millions of candidate spans. Multiply the store
size on disk by the same ratio for the disk figure; both scale linearly, because a candidate row is
a fixed width and the store carries one per span whatever the document it came from.

# Deployment

```{r}
#| label: deploy-summary
tibble::tibble(
  Artifact = c("Candidate store", "Store manifest", "Progress log"),
  Path     = c(.lP$Store$NerDB, .lP$Store$Manifest, .lP$Store$Progress)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_rel(.data$Path, here::here())
  ) |>
  tbl_say(.title = "Written by 04D")
```

# Next

**04E** reads this store and turns spans into the variables the paper reports. It assigns a role to
each span from the rules 04B kept, resolves the roles into parties, contract dates, party locations
and value, and writes one row per contract.

Everything still open is open there rather than here. The window is a filter over the offsets in
this store, so it can be imposed, revised or withdrawn without re-extracting anything. The role
rules, the tie-break and the expiry cue set are all questions this document deliberately does not
answer, and it costs nothing that they remain unanswered while the store is built.
