---
title: "Text Searches -- What the Corpus Says, and When (05A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and 03A, _Entity.R and this document's own
# file all do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and clf_read_text(); 04C owns the corpus reader and the
# daemon startup that carries clf_read_text() into a fresh session. Both are sourced rather than
# reimplemented, so this document reads the same bytes 04C extracted spans from.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04C-EntityCorpus"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "05A-TextSearches"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/05A-TextSearches.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document searches every document in the corpus for a list of stated terms, and records where each
one was found.

## The question that made it necessary

Filings of material contracts rose in 2020 and 2021. The manuscript reads that rise as the pandemic,
and referee 2 called the reading speculative and asked for a term search to settle it.

Nothing in the 04 family can answer that. Every rule there is built on spans a producer emitted, and
no producer emits *pandemic*. The question is about language the documents contain, which needs a
different instrument.

## The instrument is general, and that is deliberate

A term list is a configuration rather than code, so this document answers the next question of the
same shape without being rewritten. What it does is fixed: compile plain phrases into patterns, read
each document once, record every match with its offsets and its surroundings.

## The read is the cost, and three decisions follow from it

04C measured it: one `arrow::read_parquet()` per document, more than a million times, is most of the
wall clock even at matcon's throughput. A regular expression over text already in memory is nearly
free beside it.

**Every term rides one pass.** Adding a term to a running pass costs almost nothing; adding one
afterwards costs a second traversal of the corpus. The term list is therefore generous by design, and
the validation and placebo families below are free rather than indulgent.

**Hits are stored per term and never per family.** A family is a grouping decided when the results are
read, so changing one's mind about which terms constitute *pandemic* is a join rather than a re-run.

**The scan is two-stage.** One combined alternation asks whether a document contains anything at all;
only the documents saying yes pay for per-term location. That helps least where it would help most:
the boilerplate family matches nearly every agreement ever drafted, so on contracts the second stage
runs on most of the corpus rather than on a minority. It earns its place on the 8-K and CT order
sources, where the hit rate is genuinely low.

**Reading and matching happen in the same worker.** A design that read in parallel and matched here
would leave twenty-three cores idle through the half the two-stage filter does not rescue, and would
ship about a gigabyte of text per chunk back only to discard it after matching. Sending paths out and
bringing hits back moves a small fraction of the bytes and uses every core for both halves.

## Four sources, and one of them is not a slice of another

| Source | Text | Offsets index |
|:--|:--|:--|
| `Exhibit10` | the attachment, off the mirror | `TextRaw` |
| `8-K` | the report, off the mirror | `TextRaw` |
| `CTO` | the confidential-treatment order, off the mirror | `TextRaw` |
| `Item101` | 01D's extracted summary | `ItemText` |

**Item 1.01 is its own source rather than a window on the 8-K, and the reason is an offset system.**
01D locates the item span in a whitespace-normalised rendering of the `HTML` column, so its `Start`
and `Stop` do not index `TextRaw` -- which is what an 8-K scan reads. Testing an 8-K hit for
containment in the item span would compare two coordinate systems that look alike and are not, and
the failure would arrive as a plausible number rather than as an error. So the summary is searched as
its own text, and every row records which string its offsets belong to.

## What comes out

**`term_hits.parquet`, one row per occurrence** -- the term, the offsets, the matched string and eighty
characters either side. **`term_docs.parquet`, one row per document per family** -- counts, an
indicator, the first position and an intensity per thousand words. Every scanned document appears in
every family, including the families it matched nothing in, so a prevalence divides by the documents
that were looked at rather than by the documents that happened to hit.

**`term_list.parquet`** travels with them. A hit table without the vocabulary that produced it cannot
be interpreted.

## How results are reported

Console tables throughout, figures in Overview. One table is not a summary and belongs on the page:
the per-term counts. A term firing on nearly every document is not measuring an event and a term
firing on none is probably written wrongly, and only the per-term table shows either.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # THE REGISTER IS THE CORPUS. 02B holds every document with its group and ladder step attached,
    # so membership and population come from one place. Walking the mirror would make a second,
    # independent statement about what exists, one that can disagree without either side saying so.
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    # 01C's landing table, read only if the register turns out not to carry FormType. It appears in
    # 02B's reg_shape() inside relocate(any_of(...)), which ignores a name that is not there, so it
    # is checked rather than assumed.
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    ),
    # The parsed mirror. utils_doc_path() turns a DocID, a type and a year-quarter into a file here.
    Mirror = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01B-EdgarDocuments"),
      "GetEDGAR"
    ),
    # 01D's only artifact, carrying the Item 1.01 summary as its own column.
    Item101 = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01D-Item101"),
      "Output", "Item101.parquet"
    ),
    # THE CORPUS LABEL SPINE, AND IT IS A DIRECTORY. 03F writes contract_labels_L<max_len>.parquet,
    # so the file name depends on the token limit that produced it; ent_release_path() resolves it.
    # 03A's prepared file is the SAMPLE's, and using it here would silently restrict every
    # class-conditioned descriptive to 4,398 documents.
    Labels = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03F-ClassifyApply"),
      "release"
    )
  ),
  Output = list(
    Store   = utils_file_path(.dir_main, "Output", "TextSearch.duckdb"),
    Release = list(
      Hits  = utils_file_path(.dir_main, "Output", "term_hits.parquet"),
      Docs  = utils_file_path(.dir_main, "Output", "term_docs.parquet"),
      Terms = utils_file_path(.dir_main, "Output", "term_list.parquet")
    )
  ),
  Params = list(
    # ALL FOUR SOURCES. Referee 2's question is about contracts; Ann-Kristin's is about what the
    # filer said, which is the 8-K. Running both costs one pass because the read dominates either
    # way, and running only one would leave the other question needing its own traversal.
    Sources    = c("Exhibit10", "8-K", "CTO"),
    # "all" is every attachment rather than the descriptive subset. 04C's argument applies unchanged:
    # deduplication has already removed the registrant copies, so the wider population is a few per
    # cent more work for a store that never needs revisiting.
    Population = "all",
    # SEPARATOR TOLERANCE. Parsed filing text wraps, so "force majeure" arrives with a newline in the
    # middle of it often enough to matter, and covid-19 is written three ways by three drafters.
    SepTolerant = TRUE,
    # PLURAL TOLERANCE, AND IT WAS ADDED AFTER THE FIRST CORPUS PASS RATHER THAN BEFORE IT. The
    # closing word break refused every plural, so "supply chain disruption" found 43 documents in
    # 1.77 million while "force majeure" found 69,483. That gap is not contract language, it is the
    # boundary. Terms written as singular nouns -- disruption, pandemic, epidemic, quarantine, loan
    # -- were all affected.
    PluralTolerant = TRUE,
    # CHARACTERS KEPT EITHER SIDE OF EVERY MATCH. Enough to read the clause the term sits in and
    # judge whether the match is real. This is the only defence against a false positive that a
    # prevalence series cannot show.
    Cue         = 80L,
    # DOCUMENTS PER CHUNK, and a memory decision rather than a decision about the answer. Larger is
    # faster until a chunk stops fitting.
    ChunkSize   = 20000L,
    # DAEMONS THAT READ AND SCAN. One count rather than two, because one worker does both halves:
    # it opens the parquet files in its batch and matches against them without the text ever
    # returning here. 04C measured the read alone at roughly 150 documents a second on this machine.
    Workers     = 24L,
    # NULL SCANS THE WHOLE QUEUE. An integer names a fixed cohort, and the ordering is md5(DocID) --
    # a DocID is a filer number and a content hash, so its digest carries no trace of when the
    # document was filed, which type it is or how long it runs. A capped run is therefore a
    # proportional random sample of the queue rather than its alphabetical head, and the shape of a
    # time series survives it even where a thin cell does not.
    #
    # THE COHORT IS FIXED, SO A REHEARSAL IS NOT WASTED WORK. The same n documents are chosen every
    # render, and raising the number extends that set rather than drawing a new one -- so a capped
    # pass followed by an uncapped one scans each document exactly once. That holds only while the
    # vocabulary holds: change a term and the hash changes, and the rehearsal is discarded with
    # everything else.
    Limit       = NULL,
    ReportEvery = 5L,
    # THE REPORTING WINDOW, AND IT IS A DISPLAY DIAL RATHER THAN A DATA ONE. The pass reads every
    # attachment EDGAR holds, which reaches back to 1993; the study window opens in 2001. Those
    # earlier years were really scanned and they stay in the store and in the released files, so
    # nothing has to be read again to recover them -- they are simply not drawn, because eight years
    # of thin counts on the left of a time series invite a reading the paper does not make. The
    # sample restriction proper is applied once, at export, with the rest of the sample definition.
    YearMin     = 2001L,
    # NULL runs to the end of the corpus. Set it when a partial final quarter starts pulling the
    # right-hand end of a line somewhere the underlying documents do not go.
    YearMax     = NULL,
    # THE QUARTER THE COMPOSITION CHECK EXAMINES, and the quarters it is read against. 2021Q1 is the
    # largest single quarter in the series and the one the pandemic reading cannot explain, because
    # pandemic language peaked three quarters earlier.
    Focus       = 2021.1,
    FocusBase   = c(2019.1, 2020.1),
    # THE RUN OF QUARTERS THE COMPOSITION IS READ OVER. 2021Q1 was decomposed against the same quarter
    # in two prior years, which is right for one spike and wrong for asking whether 2020 moved too --
    # and the memo currently attributes the 2020 elevation to the pandemic without anyone checking.
    # Built as year plus quarter tenths, which is how the register writes YQ, so the equality match
    # in the filter compares numbers produced the same way rather than two roundings of one idea.
    CompQuarters = sort(as.numeric(outer(2019:2021, (1:4) / 10, "+"))),
    # The peak quarter and the recent quarters it is read against, for the intensive margin.
    Peak        = 2020.2,
    Later       = c(2023.4, 2024.1, 2024.2),
    # Named spans for the position comparison. Two is enough: the shock and the settled period after.
    Periods     = list(`2020 shock` = 2020L, `2022-2024` = 2022:2024),
    # THE BREAK THE PER-TERM DIAGNOSTIC TESTS AT. First year of the post period, so a term is
    # measured on 2001-2019 against 2020 onward. An event term steps here and a boilerplate term does
    # not, whatever the term appears to mean.
    Break       = 2020L,
    # Ratio bounds for the verdict. At or below Flat a term is called flat; at or above Step it is
    # called stepped; between them it is mixed and needs a human.
    Flat        = 1.5,
    Step        = 3,
    # Documents re-read to check that the stored offsets still index the stored text.
    CheckDocs   = 200L,
    Engine      = "Bert"
  )
)

.lP$Params$Bins <- 20L
```

## The term list

This is the study design, so it is on the page rather than in the library. Five families, and only the
first answers the referee.

```{r}
#| label: build-terms

tab_terms <- txt_terms(
  .families        = NULL,                          # NULL takes all five
  .sep_tolerant    = .lP$Params$SepTolerant,        # internal spaces and hyphens compile to one class
  .plural_tolerant = .lP$Params$PluralTolerant      # a trailing s or es joins the match
)

term_hash <- txt_terms_hash(.terms = tab_terms)

tbl_out(
  .tab   = dplyr::summarise(tab_terms, Terms = paste(.data$Term, collapse = ", "), .by = "Family"),
  .title = paste0("The published term list (hash ", term_hash, ")")
)
```

**PANDEMIC is the question.** It carries the disease names, the public-health vocabulary, and the
United States relief statute -- CARES Act, Paycheck Protection Program, PPP loan -- because a large
share of 2020 material agreements were relief loans. A filing spike made of PPP loans is a pandemic
explanation stated in the only language a credit agreement has for it.

**It no longer carries `epidemic` or `quarantine`, and that is measured rather than stylistic.** On
the first corpus pass `epidemic` came out as the *largest* term in this family, ahead of `covid`,
which cannot be right. The break diagnostic in Robustness then put its pre-2020 rate at 1.0% of
contracts against 2.7% after -- a ratio of 2.7, where `covid` is unbounded and `pandemic` is 43. Both
terms live inside force-majeure enumerations that predate COVID-19 by decades, so they were carrying
this family's baseline without measuring the event. **The move costs something and it is worth saying
so:** ratios of 2.7 and 2.2 are real responses, so some genuine signal leaves with them. It is
affordable because `covid`, `covid-19`, `coronavirus` and `pandemic` already cover the event.

**DISRUPTION is the mechanism**, and now also the home of those two. Force majeure and business
interruption are how an agreement responds to a pandemic without naming one, which separates *the
contract discusses it* from *the contract was reopened because of it*. `epidemic` and `quarantine`
behave like the rest of this family -- present in every year, moving mildly with events -- rather than
like event markers.

**RATEREFORM is the instrument check, and it matters more than anything here except the first family.**
The LIBOR cessation has a date this project did not choose: panels ceased through 2021 and 2023, and
SOFR replaced them in credit agreements. If this pass cannot recover a shock whose timing is
externally known, its verdict on a shock whose timing is contested is worth nothing. REGULATION is the
same check further back, so the instrument is shown to work at both ends of the window.

**BOILERPLATE is the placebo.** Governing law, counterparts and severability appear in nearly every
agreement in every year, so their series must be flat. If it moves in 2020, what moved is the corpus
-- its composition, its lengths, its parse quality -- and not its language, and every other series on
this page inherits that and means nothing.

**Regrouping a term is free; changing one is not.** `txt_terms_hash()` hashes the compiled patterns
and not the family labels, so moving `epidemic` and `quarantine` between families left the hash
untouched, the ledger matched, and the corpus was not read again. That is the whole reason hits are
stored per term rather than per family.

**Changing any dial above changes every pattern, and therefore the hash.** The ledger is keyed on
that hash, so a corpus already scanned under the old vocabulary contributes nothing to the new one
and the pass reads all 1.77 million documents again. That is the cost of the plural repair, and it is
the reason to settle the vocabulary in one sitting rather than to discover it a term at a time.

**The prediction, and what became of it.** The first version of this document predicted that pandemic
prevalence would be low but not zero before 2020, because *epidemic* and *quarantine* sit in
force-majeure boilerplate that long predates COVID-19. That prediction was correct and has been acted
on: the break diagnostic measured the contamination and both terms moved to DISRUPTION, so the
baseline this version reports is the residual rather than the original. Prevalence still rises sharply
in 2020Q2. If the rise is what drove the filing spike rather than
accompanying it, the rise concentrates in amendments and in credit agreements. Boilerplate is flat
throughout. RateReform is near zero before 2018 and rises through 2021 to 2023.

# Input

## The documents to scan

```{r}
#| label: build-index

tab_source <- txt_source_index(
  .path_register = .lP$Input$Register,      # 02B's register: the corpus
  .dir_mirror    = .lP$Input$Mirror,        # where utils_doc_path() resolves against
  .sources       = .lP$Params$Sources,      # Exhibit10, 8-K and CTO
  .population    = .lP$Params$Population    # "all" attachments rather than the descriptive subset
)

tab_item <- txt_item_index(.path_item = .lP$Input$Item101)

# ATTACHMENTS, NOT REGISTRANT COPIES. A filing naming several registrants produces one file per
# registrant of the same attachment, and scanning all of them would count one contract's language
# once per co-filer. PrimaryFiler marks the copy that was read; fanning back out is a join on
# HashDocument that any firm-level question performs for itself.
tab_index <- dplyr::bind_rows(
  tab_source,
  dplyr::mutate(tab_item, Path = NA_character_, HashDocument = NA_character_) |>
    dplyr::select("DocID", "Source", "Path", "HashDocument")
)

tbl_out(
  .tab   = dplyr::count(tab_index, .data$Source, name = "Documents"),
  .title = "The queue, by source"
)
```

## The per-document facts every descriptive needs

```{r}
#| label: build-keys

path_release <- ent_release_path(.dir_release = .lP$Input$Labels)

tab_keys <- txt_keys(
  .path_register = .lP$Input$Register,   # identity, filing date and length
  .path_release  = path_release,         # 03F's corpus labels; NA leaves the class columns missing
  .engine        = .lP$Params$Engine,    # which engine's label is authoritative
  .doc_ids       = NULL                  # NULL takes every primary-filer row
)
```

Class and amendment type exist for contracts and not for reports, so the join is left and the hole is
real rather than an error. An 8-K keeps its row with a missing class.

# Construction

## The store

```{r}
#| label: open-store

con <- txt_store_open(.path = .lP$Output$Store)

# ONE PASS LIVES HERE AT A TIME. Every query already filters on the hash, so a stale pass would not
# corrupt an answer -- it would just sit in the file forever, one vocabulary per revision. Dropping
# it is safe because nothing in this store is a source: every row was derived from the mirror by a
# stated term list, so the cost of being wrong is the corpus read and not the data.
txt_store_purge(
  .con       = con,          # the store
  .term_hash = term_hash,    # the pass to KEEP; every other hash is dropped
  .drop_all  = FALSE         # TRUE empties the store completely, including this hash
)

n_queue <- txt_store_queue(.con = con, .tab_index = tab_index)
```

The ledger is keyed on the document and the term-list hash, not on the document and the term. A
per-term ledger would write twenty-nine rows per document to record that a document was looked at and
would buy nothing, because the text is not retained: scanning one new term still means reading the
document again. **A changed term list is a new pass over the corpus, and that is a property of the
problem rather than of this implementation.**

## The pass

```{r}
#| label: run-pass

tab_pass <- txt_pass(
  .con          = con,                        # the store
  .terms        = tab_terms,                  # the published list
  .item_text    = tab_item,                   # Item 1.01 carries its text and is not read off disk
  .term_hash    = term_hash,                  # what the ledger is keyed on
  .sources      = NULL,                       # NULL scans every source in the queue
  .chunk_size   = .lP$Params$ChunkSize,       # documents per chunk
  .cue          = .lP$Params$Cue,             # characters kept either side of a match
  .workers      = .lP$Params$Workers,         # daemons that read and scan, both in the worker
  .limit        = .lP$Params$Limit,           # NULL takes everything outstanding
  .report_every = .lP$Params$ReportEvery      # chunks between progress lines
)
```

**A completed pass makes this chunk a no-op.** Every document carries a ledger row under this hash, so
the queue comes back empty and a re-render costs a query. That is what allows the document to run its
own work on every render rather than hiding an expensive step behind a switch.

# Selection

## From occurrences to documents

```{r}
#| label: build-doc-table

tab_doc <- txt_doc_table(
  .con       = con,          # the store
  .terms     = tab_terms,    # supplies the term-to-family map
  .term_hash = term_hash,    # which pass to read
  .keys      = tab_keys      # supplies nWords, the intensity denominator
)
```

The family is applied here and not in the store, which is the whole point of holding hits per term: a
different grouping of the same terms is this join and nothing more.

Intensity is per thousand words because the sources differ in length by an order of magnitude. An
Item 1.01 summary is a paragraph and a credit agreement is a hundred pages, so a raw count would
compare them on length rather than on language.

# Results

## What the pass cost

```{r}
#| label: report-pass

txt_report_pass(.tab = tab_pass, .n_queue = n_queue)
```

## What was scanned

```{r}
#| label: report-sources

tab_src <- txt_report_sources(.con = con, .term_hash = term_hash)

n_seen <- sum(tab_src$nScanned)
```

## Every term, and what it found

```{r}
#| label: report-terms

tab_term_counts <- txt_report_terms(
  .con       = con,          # the store
  .terms     = tab_terms,    # the published list, so a silent term still gets a row
  .term_hash = term_hash,    # which pass to read
  .n_seen    = n_seen        # the denominator
)
```

**This is the table that settles a term list.** The family totals average away exactly the two failures
worth catching: a term that fires everywhere is not measuring an event, and a term that fires nowhere
is more often a broken pattern than a fact about contract language.

## The matches, as they appear

```{r}
#| label: report-examples

txt_report_examples(
  .con       = con,          # the store
  .term_hash = term_hash,    # which pass to read
  .terms     = tab_terms,    # supplies the family's terms
  .family    = "Pandemic",   # the family under examination
  .n         = 12L,          # rows to show
  .chars     = 60L           # characters of context either side
)
```

A prevalence series cannot show that *cares act* matched a sentence about who cares, or that
*epidemic* matched a metaphor. Sixty characters either side can, and the sample is drawn on a hash so
the same twelve rows return on a re-render and are not all from one filer or one quarter.

# Validation

## Do the stored offsets still index the stored text

```{r}
#| label: validate-offsets

tab_check <- txt_check_offsets(
  .con       = con,                    # the store
  .term_hash = term_hash,              # which pass to check
  .tab_index = tab_index,              # supplies Path for the disk-backed sources
  .item_text = tab_item,               # supplies text for the Item 1.01 source
  .n         = .lP$Params$CheckDocs    # documents re-read
)

txt_report_checks(.tab = tab_check)
```

Every hit carries its offsets and the substring they were taken from, so re-slicing the text at those
offsets must return that substring. **This is the check that would have caught treating Item 1.01 as a
window on the 8-K**: an offset system is either right or wrong, so a few hundred documents settle it
as firmly as a million would.

## Two identities the tables cannot violate

```{r}
#| label: validate-identities

# EVERY SCANNED DOCUMENT APPEARS IN EVERY FAMILY, exactly once. A count other than five per document
# is a join fault in txt_doc_table(), not a fact about the corpus.
chk_rows <- tab_doc |>
  dplyr::summarise(nFamilies = dplyr::n(), .by = c("DocID", "Source")) |>
  dplyr::count(.data$nFamilies, name = "Documents")

# A DOCUMENT WITH HITS MUST HAVE AN INDICATOR, and one without must not. The two are derived from the
# same column, so a disagreement is impossible unless the derivation is wrong.
chk_flag <- tab_doc |>
  dplyr::summarise(
    Contradictions = sum((.data$nHits > 0L) != (.data$HasTerm == 1L)),
    NoFirstPos     = sum(.data$nHits > 0L & is.na(.data$FirstPos))
  )

tbl_out(.tab = chk_rows, .title = "Families per scanned document")
tbl_out(.tab = chk_flag, .title = "Indicator against count")
```

# Robustness

## Prevalence over time

```{r}
#| label: build-prevalence

tab_prev <- txt_prevalence(
  .tab_doc  = tab_doc,            # one row per document per family
  .keys     = tab_keys,           # supplies the quarter and the year
  .sources  = NULL,               # NULL keeps every source and reports them separately
  .by       = NULL,               # no extra grouping
  .year_min = .lP$Params$YearMin, # the study window opens in 2001
  .year_max = .lP$Params$YearMax
)

tab_prev_c <- txt_prevalence(
  .tab_doc  = tab_doc,
  .keys     = tab_keys,
  .sources  = "Exhibit10",        # contracts only, which is what the manuscript's figure counts
  .by       = NULL,
  .year_min = .lP$Params$YearMin,
  .year_max = .lP$Params$YearMax
)

tab_count <- tab_prev_c |>
  dplyr::filter(.data$Family == "Pandemic") |>
  dplyr::select("YQ", "nDocs")

tbl_out(
  .tab = tab_prev_c |>
    dplyr::filter(.data$YQ >= 2019, .data$YQ <= 2021.75,
                  .data$Family %in% c("Pandemic", "Disruption", "Boilerplate")) |>
    dplyr::select("YQ", "Family", "nDocs", "Share") |>
    tidyr::pivot_wider(names_from = "Family", values_from = "Share"),
  .title = "Contract prevalence around the spike",
  .pct   = c("Pandemic", "Disruption", "Boilerplate"),
  .notes = c(
    Boilerplate = "Flat is the result. Movement here would mean the corpus moved, not the language."
  )
)
```

## The amendment split

```{r}
#| label: build-amend

tab_prev_amend <- txt_prevalence(
  .tab_doc  = tab_doc,
  .keys     = tab_keys,
  .sources  = "Exhibit10",
  .by       = "AmendType",        # Original against Amended
  .year_min = .lP$Params$YearMin,
  .year_max = .lP$Params$YearMax
)

tbl_out(
  .tab = tab_prev_amend |>
    dplyr::filter(.data$Family == "Pandemic", .data$YQ >= 2019.75, .data$YQ <= 2021.25) |>
    dplyr::select("YQ", "AmendType", "nDocs", "Share"),
  .title = "Pandemic prevalence by amendment type, around the spike",
  .pct   = "Share",
  .notes = c(Share = "A spike concentrated in amendments is a renegotiation story.")
)
```

## By contract category

```{r}
#| label: build-class

tab_prev_class <- txt_prevalence_class(
  .tab_doc = tab_doc,        # one row per document per family
  .keys    = tab_keys,       # supplies Class and Year
  .family  = "Pandemic",     # the family under examination
  .years   = 2020:2021       # the spike years
)

tbl_out(
  .tab   = tab_prev_class,
  .title = "Pandemic prevalence by contract category, 2020 and 2021",
  .pct   = "Share"
)
```

## Does each term measure the event, or sit there all along

```{r}
#| label: build-break

tab_break <- txt_term_break(
  .con       = con,                  # the store
  .term_hash = term_hash,            # which pass to read
  .terms     = tab_terms,            # the published vocabulary
  .keys      = tab_keys,             # supplies the filing year
  .source    = "Exhibit10",          # contracts, which is what the claim is about
  .break     = .lP$Params$Break,     # first year of the post period
  .year_min  = .lP$Params$YearMin,
  .year_max  = .lP$Params$YearMax,
  .flat      = .lP$Params$Flat,      # at or below this ratio, flat
  .step      = .lP$Params$Step       # at or above this ratio, stepped
)

txt_report_break(.tab = tab_break, .family = "Pandemic")
```

**This exists because the first corpus pass produced a result that could not be right.** `epidemic`
came out as the largest term in the pandemic family, ahead of `covid`, and the stored context said
why: *war, terrorism, civil commotion, labor strike or lock-out, epidemic* is a force-majeure
enumeration that predates COVID-19 by decades. One example is a suspicion; a rate either side of a
date is evidence.

**An event term steps and a boilerplate term does not, and that is the whole test.** `covid` cannot
appear before 2020 and must appear after. `counterparts` is in most agreements of every year. A term
sitting in the pandemic family whose ratio is near one is not measuring the pandemic, whatever it
appears to mean.

**The pre-period rate matters separately from the ratio.** A term can step convincingly and still
carry a large pre-period rate, and that rate is contamination -- the part of the family's baseline
that has nothing to do with the event. The ratio says whether the term responds to the break; the
pre-period rate says what including it costs.

**Boilerplate is the control here too.** It must be flat at *any* break, which is what makes a step
elsewhere on this page readable. Rate reform steps at this break for a reason of its own, the LIBOR
cessation falling in the same window, and should not be read as a pandemic response.

## What kind of filing the 2021 contracts arrived under

```{r}
#| label: build-composition

tab_forms <- txt_form_types(
  .path_register = .lP$Input$Register,   # FormType if it is there
  .path_landing  = .lP$Input$Landing     # 01C's landing table if it is not
)

tab_comp <- txt_table_composition(
  .keys     = tab_keys,             # supplies the quarter
  .forms    = tab_forms,            # supplies the filing form
  .year_min = .lP$Params$YearMin,
  .year_max = .lP$Params$YearMax
)

txt_report_composition(
  .tab      = tab_comp,
  .focus    = .lP$Params$Focus,          # 2021Q1
  .base     = .lP$Params$FocusBase,      # the same quarter in the two prior years
  .quarters = .lP$Params$CompQuarters    # 2019Q1 to 2021Q4, so 2020 is decomposed as well
)

tab_form_fam <- txt_table_form_family(
  .tab_doc  = tab_doc,
  .keys     = tab_keys,
  .forms    = tab_forms,
  .family   = "Pandemic",
  .quarters = .lP$Params$Focus
)

txt_report_form_family(.tab = tab_form_fam, .label = "2021Q1")
```

**This is where the referee's question is actually settled, and the paper's own Figure 2 points at
it.** That figure pools 8-K with S-1, S-4, F-1 and F-4 as "ad-hoc filings", and in 2021 the ad-hoc
share jumps while annual filings collapse. But those two things are not alike: an 8-K reports a
material agreement as it happens, while an S-1 or S-4 registers an offering or a merger and carries
whatever exhibits that transaction produced.

**The two candidate explanations land in different halves of that pool.** Pandemic contracting is
8-K. A transaction wave -- and 2021Q1 was the peak of the SPAC boom, a shell's S-1 followed by a
de-SPAC S-4 -- is registration. Pooled, they cannot be told apart, which is why the question cannot
be answered from Figure 2 as drawn.

**The second table is the harder test.** Composition alone shows only that the mix changed. If the
rise were pandemic contracting, the surging form would carry pandemic language at least as often as
the others do; a transaction wave brings a great many exhibits drafted for a deal rather than for a
year, and those should carry it less.

## Was it a blank cheque wave, or capital markets in general

```{r}
#| label: build-sic

tab_sic <- txt_filer_sic(
  .path_register = .lP$Input$Register,   # DocID and HashIndex
  .path_landing  = .lP$Input$Landing     # SIC, which the register does not carry
)

tab_forms_split <- txt_form_types(
  .path_register = .lP$Input$Register,
  .path_landing  = .lP$Input$Landing,
  .split         = TRUE                  # S-1 offerings apart from S-4 mergers
)

tab_comp_split <- txt_table_composition(
  .keys     = tab_keys,
  .forms    = tab_forms_split,
  .year_min = .lP$Params$YearMin,
  .year_max = .lP$Params$YearMax
)

txt_report_composition(
  .tab      = tab_comp_split,
  .focus    = .lP$Params$Focus,
  .base     = .lP$Params$FocusBase,
  .quarters = .lP$Params$CompQuarters
)

tab_sic_reg <- txt_table_sic(
  .keys       = tab_keys,
  .forms      = tab_forms,
  .sic        = tab_sic,
  .quarters   = .lP$Params$CompQuarters,
  .form_group = "Registration"           # who filed the exhibits that surged
)

txt_report_sic(
  .tab   = tab_sic_reg,
  .focus = .lP$Params$Focus,
  .base  = .lP$Params$FocusBase
)
```

**SIC 6770 is the SEC's own code for blank cheque companies**, so this is the difference between
naming the wave and describing it. A special purpose acquisition company is a shell with no
operations that lists purely to raise cash into trust and then merges with a private business, which
is why it files twice -- an S-1 for the shell and an S-4 for the merger -- and why each filing carries
an unusual number of material agreements.

**Three patterns are distinguishable and they mean different things.** A blank cheque wave lifts both
registration forms, with offerings leading and mergers following as the shells complete. A
conventional listing boom lifts offerings alone. Ordinary M&A lifts mergers alone. Read against
*other finance* rather than against everything, because shells are financial filers and a rise that
came with banks and funds would be finance in general.

## How much a mentioning contract says

```{r}
#| label: build-intensity

tab_int <- txt_table_intensity(
  .tab_doc  = tab_doc,
  .keys     = tab_keys,
  .family   = "Pandemic",
  .year_min = 2019L,                 # the shock and everything after it
  .year_max = .lP$Params$YearMax
)

txt_report_intensity(
  .tab   = tab_int,
  .peak  = .lP$Params$Peak,          # 2020Q2
  .later = .lP$Params$Later          # the most recent quarters
)
```

**This is the question the prevalence series cannot answer, and a referee will ask it.** The line
peaks at 11.8% and settles near 6% through 2024 -- still tens of times the pre-2020 level. It never
comes back down. Two stories produce that shape. Under **templating**, drafters added a pandemic
carve-out to the material-adverse-effect definition and never removed it, so every agreement now says
COVID once, in the same place, indefinitely. Under **substantive contracting**, agreements are still
being written around pandemic conditions.

**Conditional on mentioning, and that is the whole design.** An unconditional mean would fall simply
because fewer contracts mention anything, which is the extensive margin again in a different coat.
Under templating this figure collapses toward one while prevalence holds; under substantive
contracting it does not.

## Where in a document the hits sit

```{r}
#| label: build-position

tab_pos <- txt_position(
  .con       = con,               # the store
  .term_hash = term_hash,         # which pass to read
  .terms     = tab_terms,         # supplies the term-to-family map
  .keys      = tab_keys,          # supplies the filing year, which the hits table does not carry
  .bins      = .lP$Params$Bins,   # bins across the relative position
  .year_min  = .lP$Params$YearMin,
  .year_max  = .lP$Params$YearMax,
  .periods   = .lP$Params$Periods # the shock read against the settled period after it
)
```

Position separates two things a count cannot. Boilerplate is positional by construction -- governing
law and counterparts sit in the closing articles -- so its distribution is the shape a
document-structure effect makes. A pandemic family concentrated in the same place is a boilerplate
insertion; one spread through the body is substantive drafting.

**Split by period, this becomes independent evidence on the templating question.** If the 2022-2024
mentions concentrate at whatever relative position the definitions article occupies while the 2020
ones are spread through the body, the language migrated into a template. Position and intensity are
measured from different columns -- `RelPos` against `nHits` -- so agreement between them is two facts
rather than one fact reported twice.

## Which industries the pandemic contracts came from

```{r}
#| label: build-class-sic

tab_class_sic <- txt_table_class_sic(
  .tab_doc = tab_doc,
  .keys    = tab_keys,
  .sic     = tab_sic,
  .family  = "Pandemic",
  .years   = 2020:2021
)

txt_report_class_sic(.tab = tab_class_sic, .class = "R&D")
```

**R&D leads the category ranking and everyone has read that as vaccine and therapeutic collaboration
-- including this document, repeatedly, without checking.** It is an inference from a class label
until a filer industry code agrees with it. This is the check, and it can come back negative.

## The clauses themselves

```{r}
#| label: report-clauses

ids_peak_ <- tab_keys$DocID[tab_keys$Source == "Exhibit10" &
                              !is.na(tab_keys$YQ) & tab_keys$YQ == .lP$Params$Peak]

ids_late_ <- tab_keys$DocID[tab_keys$Source == "Exhibit10" &
                              !is.na(tab_keys$Year) & tab_keys$Year %in% 2023:2024]

txt_report_examples(
  .con       = con,
  .term_hash = term_hash,
  .terms     = tab_terms,
  .family    = "Pandemic",
  .n         = 10L,
  .chars     = 60L,
  .doc_ids   = ids_peak_,          # the shock quarter
  .label     = "2020Q2"
)

txt_report_examples(
  .con       = con,
  .term_hash = term_hash,
  .terms     = tab_terms,
  .family    = "Pandemic",
  .n         = 10L,
  .chars     = 60L,
  .doc_ids   = ids_late_,          # three and four years later
  .label     = "2023-2024"
)
```

**The only check here that can surprise anyone.** Every other test on this page turns a number into a
different number; this one puts the actual clauses side by side. If the later matches read as
carve-out language in a definitions list while the earlier ones read as operative terms, the
templating question is settled in a way no ratio settles it.

# Deployment

```{r}
#| label: deploy-release

txt_write_release(
  .con       = con,                    # the store
  .tab_doc   = tab_doc,                # one row per document per family
  .terms     = tab_terms,              # the vocabulary, written beside the results
  .term_hash = term_hash,              # which pass is being released
  .paths     = .lP$Output$Release      # the three destinations
)

DBI::dbDisconnect(con, shutdown = TRUE)
```

`term_hits` is the file anyone re-reading a match or testing one against a matcon span wants;
`term_docs` is the file a regression joins to; `term_list` is what makes either interpretable.

**A capped pass writes `_partial` files instead, and the name is doing real work.** A rehearsal over a
hundred thousand documents produces a `term_docs` with the same columns, the same types and entirely
plausible prevalences, and it joins to anything without complaint -- nothing downstream could discover
that its denominator was a twentieth of the corpus. Coverage is measured against the queue rather than
read off the `Limit` argument, so an interrupted pass and an excluded source are caught by the same
test as a deliberate cap.

# Overview

Every figure below is one of two kinds, and the difference matters more than any single panel.

**Every figure reports 2001 onwards**, which is the study window. The pass itself reads back to 1993,
because EDGAR holds filings from then and excluding them from the queue would mean another corpus read
to recover them; they are in the store and in the released files and simply are not drawn here.

**The contract figures** use Exhibit 10 attachments only -- 1,189,805 documents, the corpus the
manuscript's tables are built on. **The source figures** put all four document types beside each
other. They are four witnesses to the same events rather than four samples of one population: a
contract is what the parties agreed, an 8-K is what the registrant told the market it had agreed,
Item 1.01 is the regulated paragraph of that report, and a CT order is the Commission's reply about
what may stay hidden. Their levels are not comparable -- an Item 1.01 summary is a paragraph and a
credit agreement is a hundred pages, so the short document mentions fewer of everything -- but their
shapes are, and the shape is what a claim about timing rests on.

## Contracts: the question referee 2 asked

```{r}
#| label: fig-spike
#| fig-cap: "Exhibit 10 attachments filed each quarter, with pandemic prevalence over them. The bars
#|   are the rise referee 2 asked about; the line is whether the documents behind it say anything
#|   different. Read apart these are two facts, and read together they are an answer -- including if
#|   the two peaks fall in different quarters."
#| fig-height: 3.4

txt_plot_spike(.tab_prev = tab_prev_c, .tab_count = tab_count, .family = "Pandemic")
```

```{r}
#| label: fig-prevalence
#| fig-cap: "Prevalence by quarter for every family, contracts only. Boilerplate is the control: it
#|   is flat only if the corpus itself is stable, so any drift in that line is the amount of movement
#|   that must be discounted from every other line on the panel."
#| fig-height: 3.4

txt_plot_prevalence(.tab = tab_prev_c, .families = NULL)
```

```{r}
#| label: fig-break
#| fig-cap: "Each term's prevalence in contracts before and after 2020, on a log scale. The line
#|   length is the finding: a term whose two points sit together does not respond to the break, and a
#|   term in the pandemic family that does not respond is not measuring the pandemic."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_break$Term))

txt_plot_break(.tab = tab_break, .families = c("Pandemic", "Disruption", "Boilerplate"))
```

## Contracts: is the pandemic where the mechanism says it should be

```{r}
#| label: fig-amend
#| fig-cap: "Pandemic prevalence by amendment type, contracts only. The mechanism claim: a pandemic
#|   that reopened existing agreements separates these two lines, and one that merely accompanied new
#|   agreements leaves them together."
#| fig-height: 3.4

txt_plot_amend(.tab = tab_prev_amend, .family = "Pandemic")
```

```{r}
#| label: fig-class
#| fig-cap: "Pandemic prevalence by contract category across 2020 and 2021, contracts only. Which
#|   kind of agreement carries the language is a sharper claim than how many do, because each
#|   category implies a different story about why the agreement was signed."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_prev_class$Class))

txt_plot_class(.tab = tab_prev_class)
```

```{r}
#| label: fig-position
#| fig-cap: "Where each family's hits fall through a contract, 0 at the start and 1 at the end,
#|   contracts only. Boilerplate is the reference shape a positional effect makes; a family matching
#|   that shape is sitting in inserted clauses rather than in drafted terms."
#| fig-height: 4.6

txt_plot_position(.tab = tab_pos, .families = c("Pandemic", "Disruption", "Boilerplate"))
```

```{r}
#| label: fig-intensity
#| fig-cap: "Prevalence in bars against mentions per mentioning contract as a line. If the bars hold
#|   while the line falls toward one, the language has become a clause that was added once and left
#|   in place rather than a subject contracts are still being written about."
#| fig-height: 3.4

txt_plot_intensity(.tab = tab_int)
```

```{r}
#| label: fig-composition
#| fig-cap: "Contract attachments by the filing form they arrived under, each quarter. The paper's
#|   Figure 2 pools 8-K with S-1 and S-4 as ad-hoc; separated, the 2021 rise is visible as a shift
#|   into registration statements rather than into current reports."
#| fig-height: 3.4

txt_plot_composition(.tab = tab_comp)
```

```{r}
#| label: fig-composition-split
#| fig-cap: "The same composition with the registration pool opened into offerings and mergers. A
#|   blank cheque wave lifts both with offerings leading; a listing boom lifts offerings alone;
#|   ordinary M&A lifts mergers alone."
#| fig-height: 3.4

txt_plot_composition(.tab = tab_comp_split, .key = "FormDetail")
```

## Contracts: does the instrument find a shock whose date is already known

```{r}
#| label: fig-validation
#| fig-cap: "The instrument on shocks whose dates were set elsewhere, contracts only. Rate reform
#|   should turn on through 2021 to 2023 and regulation early in the window. A series that cannot
#|   find these cannot be trusted on a date that is contested."
#| fig-height: 3.4

txt_plot_prevalence(.tab = tab_prev_c, .families = c("RateReform", "Regulation"))
```

## All four document types compared

```{r}
#| label: fig-sources-pandemic
#| fig-cap: "Pandemic prevalence by quarter across all four document types. The 8-K and Item 1.01
#|   series are the filer's own account of why an agreement was entered, which is a different witness
#|   from the agreement itself. CT orders are the Commission's reply and carry none of this language
#|   at all, which is why their line sits on zero."
#| fig-height: 3.4

txt_plot_sources(.tab = tab_prev, .family = "Pandemic", .drop_silent = FALSE)
```

```{r}
#| label: fig-sources-disruption
#| fig-cap: "Disruption prevalence by quarter across the document types that carry it. Force majeure
#|   and business interruption are contract machinery, so the contract line should sit far above the
#|   report lines -- a summary describes an agreement without reciting its clauses."
#| fig-height: 3.4

txt_plot_sources(.tab = tab_prev, .family = "Disruption", .drop_silent = TRUE)
```


# Next

06 builds the paper's descriptive tables and figures. It reads `term_docs.parquet` for the pandemic
indicator, joins it to the register on `DocID`, and reports the prevalence series beside the filing
counts as the answer to referee 2's fourth comment. `term_hits.parquet` stays available for anyone
wanting to read the matches behind a number.
