---
title: "Text Searches -- What the Corpus Says, and When (05A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and 03A, _Entity.R and this document's own
# file all do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary and clf_read_text(); 04C owns the corpus reader and the
# daemon startup that carries clf_read_text() into a fresh session. Both are sourced rather than
# reimplemented, so this document reads the same bytes 04C extracted spans from.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04C-EntityCorpus"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "05A-TextSearches"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/05A-TextSearches.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document searches every document in the corpus for a list of stated terms, and records where each
one was found.

## The question that made it necessary

Filings of material contracts rose in 2020 and 2021. The manuscript reads that rise as the pandemic,
and referee 2 called the reading speculative and asked for a term search to settle it.

Nothing in the 04 family can answer that. Every rule there is built on spans a producer emitted, and
no producer emits *pandemic*. The question is about language the documents contain, which needs a
different instrument.

## The instrument is general, and that is deliberate

A term list is a configuration rather than code, so this document answers the next question of the
same shape without being rewritten. What it does is fixed: compile plain phrases into patterns, read
each document once, record every match with its offsets and its surroundings.

## The read is the cost, and three decisions follow from it

04C measured it: one `arrow::read_parquet()` per document, more than a million times, is most of the
wall clock even at matcon's throughput. A regular expression over text already in memory is nearly
free beside it.

**Every term rides one pass.** Adding a term to a running pass costs almost nothing; adding one
afterwards costs a second traversal of the corpus. The term list is therefore generous by design, and
the validation and placebo families below are free rather than indulgent.

**Hits are stored per term and never per family.** A family is a grouping decided when the results are
read, so changing one's mind about which terms constitute *pandemic* is a join rather than a re-run.

**The scan is two-stage.** One combined alternation asks whether a document contains anything at all;
only the documents saying yes pay for per-term location. That helps least where it would help most:
the boilerplate family matches nearly every agreement ever drafted, so on contracts the second stage
runs on most of the corpus rather than on a minority. It earns its place on the 8-K and CT order
sources, where the hit rate is genuinely low.

**Reading and matching happen in the same worker.** A design that read in parallel and matched here
would leave twenty-three cores idle through the half the two-stage filter does not rescue, and would
ship about a gigabyte of text per chunk back only to discard it after matching. Sending paths out and
bringing hits back moves a small fraction of the bytes and uses every core for both halves.

## Four sources, and one of them is not a slice of another

| Source | Text | Offsets index |
|:--|:--|:--|
| `Exhibit10` | the attachment, off the mirror | `TextRaw` |
| `8-K` | the report, off the mirror | `TextRaw` |
| `CTO` | the confidential-treatment order, off the mirror | `TextRaw` |
| `Item101` | 01D's extracted summary | `ItemText` |

**Item 1.01 is its own source rather than a window on the 8-K, and the reason is an offset system.**
01D locates the item span in a whitespace-normalised rendering of the `HTML` column, so its `Start`
and `Stop` do not index `TextRaw` -- which is what an 8-K scan reads. Testing an 8-K hit for
containment in the item span would compare two coordinate systems that look alike and are not, and
the failure would arrive as a plausible number rather than as an error. So the summary is searched as
its own text, and every row records which string its offsets belong to.

## What comes out

**`term_hits.parquet`, one row per occurrence** -- the term, the offsets, the matched string and eighty
characters either side. **`term_docs.parquet`, one row per document per family** -- counts, an
indicator, the first position and an intensity per thousand words. Every scanned document appears in
every family, including the families it matched nothing in, so a prevalence divides by the documents
that were looked at rather than by the documents that happened to hit.

**`term_list.parquet`** travels with them. A hit table without the vocabulary that produced it cannot
be interpreted.

## How results are reported

Console tables throughout, figures in Overview. One table is not a summary and belongs on the page:
the per-term counts. A term firing on nearly every document is not measuring an event and a term
firing on none is probably written wrongly, and only the per-term table shows either.

# Configuration

## The parameters, and where they came from

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # THE REGISTER IS THE CORPUS. 02B holds every document with its group and ladder step attached,
    # so membership and population come from one place. Walking the mirror would make a second,
    # independent statement about what exists, one that can disagree without either side saying so.
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    ),
    # The parsed mirror. utils_doc_path() turns a DocID, a type and a year-quarter into a file here.
    Mirror = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01B-EdgarDocuments"),
      "GetEDGAR"
    ),
    # 01D's only artifact, carrying the Item 1.01 summary as its own column.
    Item101 = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01D-Item101"),
      "Output", "Item101.parquet"
    ),
    # THE CORPUS LABEL SPINE, AND IT IS A DIRECTORY. 03F writes contract_labels_L<max_len>.parquet,
    # so the file name depends on the token limit that produced it; ent_release_path() resolves it.
    # 03A's prepared file is the SAMPLE's, and using it here would silently restrict every
    # class-conditioned descriptive to 4,398 documents.
    Labels = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03F-ClassifyApply"),
      "release"
    )
  ),
  Output = list(
    Store   = utils_file_path(.dir_main, "Output", "TextSearch.duckdb"),
    Release = list(
      Hits  = utils_file_path(.dir_main, "Output", "term_hits.parquet"),
      Docs  = utils_file_path(.dir_main, "Output", "term_docs.parquet"),
      Terms = utils_file_path(.dir_main, "Output", "term_list.parquet")
    )
  ),
  Params = list(
    # ALL FOUR SOURCES. Referee 2's question is about contracts; Ann-Kristin's is about what the
    # filer said, which is the 8-K. Running both costs one pass because the read dominates either
    # way, and running only one would leave the other question needing its own traversal.
    Sources    = c("Exhibit10", "8-K", "CTO"),
    # "all" is every attachment rather than the descriptive subset. 04C's argument applies unchanged:
    # deduplication has already removed the registrant copies, so the wider population is a few per
    # cent more work for a store that never needs revisiting.
    Population = "all",
    # SEPARATOR TOLERANCE. Parsed filing text wraps, so "force majeure" arrives with a newline in the
    # middle of it often enough to matter, and covid-19 is written three ways by three drafters.
    SepTolerant = TRUE,
    # CHARACTERS KEPT EITHER SIDE OF EVERY MATCH. Enough to read the clause the term sits in and
    # judge whether the match is real. This is the only defence against a false positive that a
    # prevalence series cannot show.
    Cue         = 80L,
    # DOCUMENTS PER CHUNK, and a memory decision rather than a decision about the answer. Larger is
    # faster until a chunk stops fitting.
    ChunkSize   = 10000L,
    # DAEMONS THAT READ AND SCAN. One count rather than two, because one worker does both halves:
    # it opens the parquet files in its batch and matches against them without the text ever
    # returning here. 04C measured the read alone at roughly 150 documents a second on this machine.
    Workers     = 24L,
    # NULL SCANS THE WHOLE QUEUE. An integer names a fixed cohort -- the first n in hash order -- so a
    # capped rehearsal is repeatable and raising the number extends the cohort rather than replacing
    # it.
    Limit       = NULL,
    ReportEvery = 5L,
    # Documents re-read to check that the stored offsets still index the stored text.
    CheckDocs   = 200L,
    Engine      = "Bert"
  )
)

.lP$Params$Bins <- 20L
```

## The term list

This is the study design, so it is on the page rather than in the library. Five families, and only the
first answers the referee.

```{r}
#| label: build-terms

tab_terms <- txt_terms(
  .families     = NULL,                       # NULL takes all five
  .sep_tolerant = .lP$Params$SepTolerant      # internal spaces and hyphens compile to one class
)

term_hash <- txt_terms_hash(.terms = tab_terms)

tbl_out(
  .tab   = dplyr::summarise(tab_terms, Terms = paste(.data$Term, collapse = ", "), .by = "Family"),
  .title = paste0("The published term list (hash ", term_hash, ")")
)
```

**PANDEMIC is the question.** It carries the disease names, the public-health vocabulary, and the
United States relief statute -- CARES Act, Paycheck Protection Program, PPP loan -- because a large
share of 2020 material agreements were relief loans. A filing spike made of PPP loans is a pandemic
explanation stated in the only language a credit agreement has for it.

**DISRUPTION is the mechanism.** Force majeure and business interruption are how an agreement responds
to a pandemic without naming one, which separates *the contract discusses it* from *the contract was
reopened because of it*.

**RATEREFORM is the instrument check, and it matters more than anything here except the first family.**
The LIBOR cessation has a date this project did not choose: panels ceased through 2021 and 2023, and
SOFR replaced them in credit agreements. If this pass cannot recover a shock whose timing is
externally known, its verdict on a shock whose timing is contested is worth nothing. REGULATION is the
same check further back, so the instrument is shown to work at both ends of the window.

**BOILERPLATE is the placebo.** Governing law, counterparts and severability appear in nearly every
agreement in every year, so their series must be flat. If it moves in 2020, what moved is the corpus
-- its composition, its lengths, its parse quality -- and not its language, and every other series on
this page inherits that and means nothing.

**The prediction, before anything runs.** Pandemic prevalence is low but not zero before 2020, because
*epidemic* and *quarantine* sit in insurance and force-majeure boilerplate that long predates
COVID-19. It rises sharply in 2020Q2. If the rise is what drove the filing spike rather than
accompanying it, the rise concentrates in amendments and in credit agreements. Boilerplate is flat
throughout. RateReform is near zero before 2018 and rises through 2021 to 2023.

# Input

## The documents to scan

```{r}
#| label: build-index

tab_source <- txt_source_index(
  .path_register = .lP$Input$Register,      # 02B's register: the corpus
  .dir_mirror    = .lP$Input$Mirror,        # where utils_doc_path() resolves against
  .sources       = .lP$Params$Sources,      # Exhibit10, 8-K and CTO
  .population    = .lP$Params$Population    # "all" attachments rather than the descriptive subset
)

tab_item <- txt_item_index(.path_item = .lP$Input$Item101)

# ATTACHMENTS, NOT REGISTRANT COPIES. A filing naming several registrants produces one file per
# registrant of the same attachment, and scanning all of them would count one contract's language
# once per co-filer. PrimaryFiler marks the copy that was read; fanning back out is a join on
# HashDocument that any firm-level question performs for itself.
tab_index <- dplyr::bind_rows(
  tab_source,
  dplyr::mutate(tab_item, Path = NA_character_, HashDocument = NA_character_) |>
    dplyr::select("DocID", "Source", "Path", "HashDocument")
)

tbl_out(
  .tab   = dplyr::count(tab_index, .data$Source, name = "Documents"),
  .title = "The queue, by source"
)
```

## The per-document facts every descriptive needs

```{r}
#| label: build-keys

path_release <- ent_release_path(.dir_release = .lP$Input$Labels)

tab_keys <- txt_keys(
  .path_register = .lP$Input$Register,   # identity, filing date and length
  .path_release  = path_release,         # 03F's corpus labels; NA leaves the class columns missing
  .engine        = .lP$Params$Engine,    # which engine's label is authoritative
  .doc_ids       = NULL                  # NULL takes every primary-filer row
)
```

Class and amendment type exist for contracts and not for reports, so the join is left and the hole is
real rather than an error. An 8-K keeps its row with a missing class.

# Construction

## The store

```{r}
#| label: open-store

con <- txt_store_open(.path = .lP$Output$Store)

n_queue <- txt_store_queue(.con = con, .tab_index = tab_index)
```

The ledger is keyed on the document and the term-list hash, not on the document and the term. A
per-term ledger would write twenty-nine rows per document to record that a document was looked at and
would buy nothing, because the text is not retained: scanning one new term still means reading the
document again. **A changed term list is a new pass over the corpus, and that is a property of the
problem rather than of this implementation.**

## The pass

```{r}
#| label: run-pass

tab_pass <- txt_pass(
  .con          = con,                        # the store
  .terms        = tab_terms,                  # the published list
  .item_text    = tab_item,                   # Item 1.01 carries its text and is not read off disk
  .term_hash    = term_hash,                  # what the ledger is keyed on
  .sources      = NULL,                       # NULL scans every source in the queue
  .chunk_size   = .lP$Params$ChunkSize,       # documents per chunk
  .cue          = .lP$Params$Cue,             # characters kept either side of a match
  .workers      = .lP$Params$Workers,         # daemons that read and scan, both in the worker
  .limit        = .lP$Params$Limit,           # NULL takes everything outstanding
  .report_every = .lP$Params$ReportEvery      # chunks between progress lines
)
```

**A completed pass makes this chunk a no-op.** Every document carries a ledger row under this hash, so
the queue comes back empty and a re-render costs a query. That is what allows the document to run its
own work on every render rather than hiding an expensive step behind a switch.

# Selection

## From occurrences to documents

```{r}
#| label: build-doc-table

tab_doc <- txt_doc_table(
  .con       = con,          # the store
  .terms     = tab_terms,    # supplies the term-to-family map
  .term_hash = term_hash,    # which pass to read
  .keys      = tab_keys      # supplies nWords, the intensity denominator
)
```

The family is applied here and not in the store, which is the whole point of holding hits per term: a
different grouping of the same terms is this join and nothing more.

Intensity is per thousand words because the sources differ in length by an order of magnitude. An
Item 1.01 summary is a paragraph and a credit agreement is a hundred pages, so a raw count would
compare them on length rather than on language.

# Results

## What the pass cost

```{r}
#| label: report-pass

txt_report_pass(.tab = tab_pass, .n_queue = n_queue)
```

## What was scanned

```{r}
#| label: report-sources

tab_src <- txt_report_sources(.con = con, .term_hash = term_hash)

n_seen <- sum(tab_src$nScanned)
```

## Every term, and what it found

```{r}
#| label: report-terms

tab_term_counts <- txt_report_terms(
  .con       = con,          # the store
  .terms     = tab_terms,    # the published list, so a silent term still gets a row
  .term_hash = term_hash,    # which pass to read
  .n_seen    = n_seen        # the denominator
)
```

**This is the table that settles a term list.** The family totals average away exactly the two failures
worth catching: a term that fires everywhere is not measuring an event, and a term that fires nowhere
is more often a broken pattern than a fact about contract language.

## The matches, as they appear

```{r}
#| label: report-examples

txt_report_examples(
  .con       = con,          # the store
  .term_hash = term_hash,    # which pass to read
  .terms     = tab_terms,    # supplies the family's terms
  .family    = "Pandemic",   # the family under examination
  .n         = 12L,          # rows to show
  .chars     = 60L           # characters of context either side
)
```

A prevalence series cannot show that *cares act* matched a sentence about who cares, or that
*epidemic* matched a metaphor. Sixty characters either side can, and the sample is drawn on a hash so
the same twelve rows return on a re-render and are not all from one filer or one quarter.

# Validation

## Do the stored offsets still index the stored text

```{r}
#| label: validate-offsets

tab_check <- txt_check_offsets(
  .con       = con,                    # the store
  .term_hash = term_hash,              # which pass to check
  .tab_index = tab_index,              # supplies Path for the disk-backed sources
  .item_text = tab_item,               # supplies text for the Item 1.01 source
  .n         = .lP$Params$CheckDocs    # documents re-read
)

txt_report_checks(.tab = tab_check)
```

Every hit carries its offsets and the substring they were taken from, so re-slicing the text at those
offsets must return that substring. **This is the check that would have caught treating Item 1.01 as a
window on the 8-K**: an offset system is either right or wrong, so a few hundred documents settle it
as firmly as a million would.

## Two identities the tables cannot violate

```{r}
#| label: validate-identities

# EVERY SCANNED DOCUMENT APPEARS IN EVERY FAMILY, exactly once. A count other than five per document
# is a join fault in txt_doc_table(), not a fact about the corpus.
chk_rows <- tab_doc |>
  dplyr::summarise(nFamilies = dplyr::n(), .by = c("DocID", "Source")) |>
  dplyr::count(.data$nFamilies, name = "Documents")

# A DOCUMENT WITH HITS MUST HAVE AN INDICATOR, and one without must not. The two are derived from the
# same column, so a disagreement is impossible unless the derivation is wrong.
chk_flag <- tab_doc |>
  dplyr::summarise(
    Contradictions = sum((.data$nHits > 0L) != (.data$HasTerm == 1L)),
    NoFirstPos     = sum(.data$nHits > 0L & is.na(.data$FirstPos))
  )

tbl_out(.tab = chk_rows, .title = "Families per scanned document")
tbl_out(.tab = chk_flag, .title = "Indicator against count")
```

# Robustness

## Prevalence over time

```{r}
#| label: build-prevalence

tab_prev <- txt_prevalence(
  .tab_doc = tab_doc,     # one row per document per family
  .keys    = tab_keys,    # supplies the quarter
  .sources = NULL,        # NULL keeps every source and reports them separately
  .by      = NULL         # no extra grouping
)

tab_prev_c <- txt_prevalence(
  .tab_doc = tab_doc,
  .keys    = tab_keys,
  .sources = "Exhibit10",   # contracts only, which is what the manuscript's figure counts
  .by      = NULL
)

tab_count <- tab_prev_c |>
  dplyr::filter(.data$Family == "Pandemic") |>
  dplyr::select("YQ", "nDocs")

tbl_out(
  .tab = tab_prev_c |>
    dplyr::filter(.data$YQ >= 2019, .data$YQ <= 2021.75,
                  .data$Family %in% c("Pandemic", "Disruption", "Boilerplate")) |>
    dplyr::select("YQ", "Family", "nDocs", "Share") |>
    tidyr::pivot_wider(names_from = "Family", values_from = "Share"),
  .title = "Contract prevalence around the spike",
  .pct   = c("Pandemic", "Disruption", "Boilerplate"),
  .notes = c(
    Boilerplate = "Flat is the result. Movement here would mean the corpus moved, not the language."
  )
)
```

## The amendment split

```{r}
#| label: build-amend

tab_prev_amend <- txt_prevalence(
  .tab_doc = tab_doc,
  .keys    = tab_keys,
  .sources = "Exhibit10",
  .by      = "AmendType"    # Original against Amended
)

tbl_out(
  .tab = tab_prev_amend |>
    dplyr::filter(.data$Family == "Pandemic", .data$YQ >= 2019.75, .data$YQ <= 2021.25) |>
    dplyr::select("YQ", "AmendType", "nDocs", "Share"),
  .title = "Pandemic prevalence by amendment type, around the spike",
  .pct   = "Share",
  .notes = c(Share = "A spike concentrated in amendments is a renegotiation story.")
)
```

## By contract category

```{r}
#| label: build-class

tab_prev_class <- txt_prevalence_class(
  .tab_doc = tab_doc,        # one row per document per family
  .keys    = tab_keys,       # supplies Class and Year
  .family  = "Pandemic",     # the family under examination
  .years   = 2020:2021       # the spike years
)

tbl_out(
  .tab   = tab_prev_class,
  .title = "Pandemic prevalence by contract category, 2020 and 2021",
  .pct   = "Share"
)
```

## Where in a document the hits sit

```{r}
#| label: build-position

tab_pos <- txt_position(
  .con       = con,             # the store
  .term_hash = term_hash,       # which pass to read
  .terms     = tab_terms,       # supplies the term-to-family map
  .bins      = .lP$Params$Bins  # bins across the relative position
)
```

Position separates two things a count cannot. Boilerplate is positional by construction -- governing
law and counterparts sit in the closing articles -- so its distribution is the shape a
document-structure effect makes. A pandemic family concentrated in the same place is a boilerplate
insertion; one spread through the body is substantive drafting.

# Deployment

```{r}
#| label: deploy-release

txt_write_release(
  .con       = con,                    # the store
  .tab_doc   = tab_doc,                # one row per document per family
  .terms     = tab_terms,              # the vocabulary, written beside the results
  .term_hash = term_hash,              # which pass is being released
  .paths     = .lP$Output$Release      # the three destinations
)

DBI::dbDisconnect(con, shutdown = TRUE)
```

`term_hits` is the file anyone re-reading a match or testing one against a matcon span wants;
`term_docs` is the file a regression joins to; `term_list` is what makes either interpretable.

# Overview

```{r}
#| label: fig-spike
#| fig-cap: "Attachments filed each quarter, with pandemic prevalence over them. The bars are the rise
#|   referee 2 asked about; the line is whether the documents behind it say anything different. Read
#|   apart these are two facts, and read together they are an answer."
#| fig-height: 3.4

txt_plot_spike(.tab_prev = tab_prev_c, .tab_count = tab_count, .family = "Pandemic")
```

```{r}
#| label: fig-prevalence
#| fig-cap: "Prevalence by quarter for every family, contracts only. Boilerplate is the control: a
#|   flat line there is what licenses reading movement in the others as language rather than as a
#|   change in the corpus."
#| fig-height: 3.4

txt_plot_prevalence(.tab = tab_prev_c, .families = NULL)
```

```{r}
#| label: fig-validation
#| fig-cap: "The instrument on shocks whose dates were set elsewhere. Rate reform should turn on
#|   through 2021 to 2023 and regulation early in the window. A series that cannot find these cannot
#|   be trusted on a date that is contested."
#| fig-height: 3.4

txt_plot_prevalence(.tab = tab_prev_c, .families = c("RateReform", "Regulation"))
```

```{r}
#| label: fig-amend
#| fig-cap: "Pandemic prevalence by amendment type. The mechanism claim: a pandemic that reopened
#|   existing agreements shows here, and one that only accompanied new ones does not."
#| fig-height: 3.4

txt_plot_amend(.tab = tab_prev_amend, .family = "Pandemic")
```

```{r}
#| label: fig-class
#| fig-cap: "Pandemic prevalence by contract category across 2020 and 2021. Credit agreements carry
#|   the relief-loan vocabulary, so a category ranking led by credit is the PPP explanation rather
#|   than a general one."
#| fig-height: !expr plot_height(.n_rows = dplyr::n_distinct(tab_prev_class$Class))

txt_plot_class(.tab = tab_prev_class)
```

```{r}
#| label: fig-position
#| fig-cap: "Where each family's hits fall through a contract, 0 at the start and 1 at the end.
#|   Boilerplate is the reference shape a positional effect makes; a family matching that shape is
#|   sitting in inserted clauses rather than in drafted terms."
#| fig-height: 4.6

txt_plot_position(.tab = tab_pos, .families = c("Pandemic", "Disruption", "Boilerplate"))
```

```{r}
#| label: fig-sources
#| fig-cap: "Prevalence by quarter across all four sources, pandemic family only. The 8-K and Item
#|   1.01 series are the filer's own account of why an agreement was entered, which is a different
#|   witness from the agreement itself."
#| fig-height: 3.4

txt_plot_prevalence(
  .tab      = dplyr::filter(tab_prev, .data$Family == "Pandemic") |>
    dplyr::mutate(Family = plot_factor(.x = .data$Source, .key = "TextSource")),
  .families = NULL
)
```

# Next

06 builds the paper's descriptive tables and figures. It reads `term_docs.parquet` for the pandemic
indicator, joins it to the register on `DocID`, and reports the prevalence series beside the filing
counts as the answer to referee 2's fourth comment. `term_hits.parquet` stays available for anyone
wanting to read the matches behind a number.
