---
title: "The 8-K Item Taxonomy, Before and After 2004 (05B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")

# 05A owns txt_n(), which formats a count without letting format() slip into scientific notation on a
# round number. Sourced rather than copied, for the usual reason.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "05A-TextSearches"),
  encoding = "UTF-8"
)

.name_script <- "05B-ItemTaxonomy"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/05B-ItemTaxonomy.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document measures what the August 2004 8-K item reform did to contract disclosure, and states
which population every number is drawn from.

## The sentence it exists to check

The response to referee 2's comment 6A explains away two opposite-signed results with one mechanism:

> the decline is largest for firms whose pre-period 8-Ks were disproportionately Item 5 filings --
> which is the treated group by construction, since these firms were not using 8-Ks for contracts

A great deal rests on it. The design is abandoned and both specifications are demoted to an online
appendix on the strength of that sentence. **"By construction" is not a construction.** It is an
empirical claim about pre-2004 data, and a referee can check it.

## Two claims, and only one of them is in doubt

**That the reform redistributed catch-all content into new mandatory items** is a fact about the
taxonomy, and this document measures it directly.

**Which group was Item-5-heavy beforehand** is the contested half, and the prior runs against the
memo. Before 23 August 2004 there was no Item 1.01, and Item 5 was *Other events*, the catch-all. A
firm disclosing a material contract by 8-K then had nowhere else to file it -- and that firm is the
**control** group, because it was already using 8-Ks for contracts. The treated firm, which was not,
filed 8-Ks for earnings, auditor changes and acquisitions: the mandatory items.

## What it found

**The reclassification is real and it is a substitution, not a drift.** Item 5 carries 69.9% of
contract-bearing 8-Ks in 2001 and 77.8% in 2003; from 2005 it carries 0.0%, while the new mandatory
Item 1.01 carries 87.9%. The exhibits item moves the same way, 87.9% to 96.7%. So mandatory counts
rise and voluntary counts fall for reasons that have nothing to do with bundling.

**The attribution in the memo is the wrong way round.** The firms filing under the Item 5 catch-all
before the reform are the firms that were using 8-Ks for contracts -- which is the CONTROL group.
From the unrestricted index, 94.4% of control firms filed an 8-K before the reform against 74.9% of
treated firms, with medians of nine and five. The gap widens under every stricter definition tried in
Robustness, so it does not depend on the reconstruction below matching the estimation sample.

## Three populations, and confusing them is the whole risk

| Source | Population | Carries items |
|:--|:--|:--|
| Landing pages, 01C | filings **retrieved**, meaning those carrying an Exhibit 10 | yes |
| Master index, 01A mirror | **every** filing EDGAR indexed | no |
| Master index, 01C output | restricted to the retrieved set, like the landing table | no |

The landing table is the only source of item lists anywhere in the pipeline, and it is **not a sample
of all 8-Ks** -- it is the contract-bearing ones. Before the reform it holds a few thousand 8-Ks a
year; after it, tens of thousands. That jump is not a fact about EDGAR. It is the treatment: before
the reform almost nobody filed contracts by 8-K and afterwards everyone had to.

**So the pre-2004 8-Ks in that table are, by construction, control-group filings.** Treated firms'
pre-period 8-Ks were never retrieved, because they carried no contract. An Item 5 share computed there
is a statement about how firms that *were* using 8-Ks for contracts filed them, and reporting it as a
comparison between groups would repeat the memo's error in a new place.

## What cannot be answered here

**The item lists of treated firms' non-contract 8-Ks.** Those filings exist and EDGAR indexes them,
but their landing pages were never fetched because nothing in them was wanted. Getting them is a
scrape of tens of thousands of pages against the SEC rate limit -- hours, not minutes. 01C holds the
machinery if the answer is ever worth that.

What the unrestricted index *can* answer is whether treated firms filed 8-Ks **at all** before the
reform. That is the non-definitional half of the comparison, and the mechanism needs it: a treated
firm with an active 8-K practice that never carried a contract is what the story requires, while a
treated group that barely filed 8-Ks would mean something else entirely.

## What comes out

`filing_items.parquet`, one row per item per filing, parsed and joinable -- nothing else in the
pipeline holds 8-K items in that form. `firm_status.parquet`, the reconstructed treated and control
split, flagged as a reconstruction everywhere it is used.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    # THE ONLY SOURCE OF ITEM LISTS IN THE PIPELINE, and restricted to retrieved filings. 01C's
    # MasterIndex.parquet is restricted the same way, so reading it as the universe would compare the
    # retrieved population against itself.
    Landing = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "01C-EdgarMetaData"),
      "Output", "LandingPage.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Release = list(
      Items = utils_file_path(.dir_main, "Output", "filing_items.parquet"),
      Firms = utils_file_path(.dir_main, "Output", "firm_status.parquet")
    )
  ),
  Params = list(
    # THE REFORM TOOK EFFECT ON A DATE, NOT IN A YEAR. A calendar split would put seven months of
    # old-taxonomy filings on the new side, so 2004 is reported as its own era rather than folded
    # into either.
    Reform    = as.Date("2004-08-23"),
    # The pre-period the firm comparison is computed over. Matches the register's sample opening.
    PreYears  = 2001:2003,
    # Items reported as their own series: the old catch-all, the old exhibits item, the new contract
    # item, and the renumbered catch-all.
    Codes     = c("5", "7", "1.01", "8.01"),
    # Pre-reform contract filings a firm needs before it is classified at all. Robustness varies it.
    MinPre    = 1L,
    YearMin   = 2001L,
    # THE ACQUISITION FRAME CLOSES HERE, and this is not a display preference. 01A fixes MaxYear so
    # renders stay comparable, and EDGAR keeps indexing filings past it -- so a later year has
    # indexed 8-Ks and, by construction, no retrieved ones. That prints as a retrieved share of zero
    # and reads as contract disclosure collapsing. It is not a measurement.
    YearMax   = 2024L
  )
)

# THE UNRESTRICTED INDEX, resolved through rGetEDGAR rather than typed so the layout cannot drift.
# NA where it cannot be found, and every table that needs it says so and is skipped.
.lP$Input$MasterDir <- itx_master_dir(.dir_here = here::here())
```

# Input

## The filings

```{r}
#| label: build-input

tab_land_all <- itx_read_landing(
  .path  = .lP$Input$Landing,   # 01C's landing table
  .forms = NULL                 # NULL keeps every form; the firm split needs 10-K and 10-Q too
) |>
  dplyr::mutate(Era = itx_era(.date = .data$FilingDate, .reform = .lP$Params$Reform))

tab_land <- dplyr::filter(tab_land_all, grepl("^8-K", .data$FormType))

tab_contract <- itx_contract_filings(.path_register = .lP$Input$Register)

tab_master <- itx_read_master(
  .dir   = .lP$Input$MasterDir,  # the unrestricted index, or NA
  .forms = "^8-K"
)

tbl_out(
  .tab = tibble::tibble(
    Table = c("Landing, all forms", "Landing, 8-K only", "Contract-bearing filings",
              "Index rows, 8-K"),
    Rows  = c(nrow(tab_land_all), nrow(tab_land), nrow(tab_contract), nrow(tab_master))
  ),
  .title = "What was read"
)
```

One row per **filing**, not per document. A filing carrying nine exhibits appears once here and nine
times in the register, so every count below is a count of filings.

# Construction

## Parsing the item list

```{r}
#| label: build-items

tab_items <- itx_parse_items(.tab = tab_land)
```

**The separator is a newline and only a newline.** 01D rewrites it to a pipe for its own cache key,
and copying that convention here would be a bug, because the labels themselves contain colons and
commas. `Item 5.02: Departure of Directors or Certain Officers: Election of Directors: Appointment of
Certain Officers` is **one** item, and splitting on colons turns it into four -- which is exactly what
a first pass at this did, producing three phantom codes each appearing 88,974 times.

**Pre-reform and post-reform codes are different objects that look alike.** `5` is the old *Other
events* catch-all; `5.02` is departures of directors; `1.05` contains a 5 and means neither. Every
count below compares the parsed code exactly.

# Selection

## Treated and control

```{r}
#| label: build-status

tab_status <- itx_firm_status(
  .tab_land      = tab_land_all,        # all forms, because a treated firm used periodic filings
  .contract      = tab_contract,        # which filings carried a contract
  .reform        = .lP$Params$Reform,   # the pre-period closes here
  .min_contracts = .lP$Params$MinPre    # below this a firm is Unclassified rather than forced
)

tbl_out(
  .tab   = dplyr::count(tab_status, .data$Status, name = "Firms"),
  .title = "Firms by reconstructed status"
)
```

**This is a reconstruction and it is flagged as one wherever it is used.** The estimation sample is
defined in Stata, not here, and a split that does not match the one the table was built on answers a
question nobody asked. Robustness varies the threshold so a reader can see whether the answer turns
on the definition or survives it.

# Results

## The population everything else is conditional on

```{r}
#| label: report-population

tab_pop <- itx_table_population(
  .tab_land = tab_land,               # 8-K landing rows
  .contract = tab_contract,           # which of them carried a contract
  .master   = tab_master,             # every 8-K EDGAR indexed
  .year_min = .lP$Params$YearMin,     # the study window opens here
  .year_max = .lP$Params$YearMax      # and the acquisition frame closes here
)

itx_report_population(.tab = tab_pop)
```

## What the reform moved

```{r}
#| label: report-shift

tab_shift <- itx_table_shift(
  .items    = tab_items,
  .tab_land = tab_land,
  .contract = tab_contract
)

itx_report_shift(.tab = tab_shift)
```

## Which item carried contract disclosure, year by year

```{r}
#| label: report-item-share

tab_share <- itx_table_item_share(
  .items    = tab_items,
  .tab_land = tab_land,
  .contract = tab_contract,
  .codes    = .lP$Params$Codes   # the old catch-all, old exhibits, new contract item, new catch-all
)

itx_report_item_share(.tab = tab_share)
```

**This is the number the memo needs, and its population has to be stated in the same breath.** It
covers contract-bearing 8-Ks, which before the reform means control-group filings. It says how firms
that *were* using 8-Ks for contracts filed them. It is not a comparison between groups.

## The full item distribution, each side of the reform

```{r}
#| label: report-codes

tab_codes <- itx_table_codes(.items = tab_items, .tab_land = tab_land, .n = 12L)

itx_report_codes(.tab = tab_codes)
```

## Treated and control firms before the reform

```{r}
#| label: report-firms

tab_firms <- itx_table_firms(
  .status    = tab_status,
  .master    = tab_master,
  .pre_years = .lP$Params$PreYears
)

itx_report_firms(.tab = tab_firms)
```

**`MeanContract8K` is zero for treated firms by definition and is therefore not evidence.**
`ShareWithAny8K` is the informative cell, and it comes from the unrestricted index rather than from
the retrieved set.

# Validation

## Did the parser lose or invent anything

```{r}
#| label: validate-parse

tab_check <- itx_check_parse(.tab_land = tab_land, .items = tab_items)

itx_report_checks(.tab = tab_check, .items = tab_items)
```

## Is the reform boundary in the right place

```{r}
#| label: validate-boundary

# ITEM 1.01 CANNOT EXIST BEFORE THE RELEASE AND THE CATCH-ALL CANNOT BE RENUMBERED AFTER IT. Either
# would mean the era split is wrong, or that filers backdated, or that the date is not what the
# release says. All three are worth knowing and none of them is visible from a count of items alone.
tab_bound <- tab_items |>
  dplyr::inner_join(dplyr::select(tab_land, "HashIndex", "Era"), by = dplyr::join_by(HashIndex)) |>
  dplyr::filter(.data$ItemCode %in% c("5", "1.01", "8.01")) |>
  dplyr::summarise(nFilings = dplyr::n_distinct(.data$HashIndex), .by = c("Era", "ItemCode")) |>
  tidyr::pivot_wider(names_from = "ItemCode", values_from = "nFilings", values_fill = 0L,
                     names_prefix = "Item_")

tbl_out(
  .tab   = tab_bound,
  .title = "Old and new codes each side of the boundary",
  .notes = c(Item_1.01 = "Any pre-reform occurrence would mean the era split is wrong.")
)
```

# Robustness

## Does the answer turn on where the treated line is drawn

```{r}
#| label: robust-definition

tab_sens <- purrr::map(
  .x = c(1L, 2L, 3L, 5L),
  .f = function(.k) {
    itx_firm_status(
      .tab_land      = tab_land_all,
      .contract      = tab_contract,
      .reform        = .lP$Params$Reform,
      .min_contracts = .k
    ) |>
      itx_table_firms(.master = tab_master, .pre_years = .lP$Params$PreYears) |>
      dplyr::mutate(MinPre = .k)
  }
) |>
  purrr::list_rbind()

tbl_out(
  .tab   = dplyr::select(tab_sens, "MinPre", "Status", "nFirms", "ShareWithAny8K", "Median8K"),
  .title = "Firm comparison under four thresholds",
  .pct   = "ShareWithAny8K",
  .notes = c(MinPre = "Pre-reform contract filings a firm needs before it is classified at all.")
)
```

An answer that holds across all four does not depend on the reconstruction. One that moves needs
Ann-Kristin's Stata definition before anything is written from it.

# Deployment

```{r}
#| label: deploy-release

itx_write_release(
  .items  = tab_items,
  .land   = tab_land,
  .status = tab_status,
  .paths  = .lP$Output$Release
)
```

# Overview

Every figure covers `r .lP$Params$YearMin` onwards, the study window, and the dashed line marks the
reform.

## How strong the retrieval condition is

```{r}
#| label: fig-population
#| fig-cap: "Share of all indexed 8-Ks that carried a material contract, by year. This is the
#|   condition every other figure here is drawn under. A low share before the reform and a high one
#|   after means the pre-period holds contract-disclosing firms and almost nobody else."
#| fig-height: 3.4

itx_plot_population(
  .tab      = tab_pop,
  .year_min = .lP$Params$YearMin,
  .year_max = .lP$Params$YearMax
)
```

## Which item carried contract disclosure

```{r}
#| label: fig-item-share
#| fig-cap: "Share of contract-bearing 8-Ks carrying each item, by year. Item 5 giving way to Item
#|   1.01 across the boundary is the reclassification the memo asserts, measured rather than assumed."
#| fig-height: 3.4

itx_plot_item_share(.tab = tab_share, .year_min = .lP$Params$YearMin)
```

## What the reform moved

```{r}
#| label: fig-shift
#| fig-cap: "The items on contract-bearing 8-Ks before and after the reform. Read the two panels
#|   against each other: the catch-all at the top of one and a mandatory contract item at the top of
#|   the other is what redistribution looks like."
#| fig-height: 5.2

itx_plot_shift(.tab = tab_shift)
```

# Next

**The sentence in the draft has to be replaced rather than softened**, because these data contradict
it rather than merely failing to support it. What the document supports is narrower and measured:

> Before the reform, contract disclosure on 8-Ks ran through the Item 5 "Other events" catch-all:
> 73.6% of pre-reform contract-bearing 8-Ks carry it, against 0.0% from 2005 onward, when 87.9% carry
> the new mandatory Item 1.01. Mandatory item counts therefore rise and voluntary counts fall for
> reasons unrelated to bundling. The firms filing contracts by 8-K before the reform are the control
> group by construction, so we do not attribute the reclassification asymmetrically across groups.

**The conclusion the memo needs is untouched**, and arguably stronger: a pre/post comparison of item
counts cannot separate strategic bundling from reclassification in either direction, so no inference
is drawn from that design. That now rests on a measured substitution rather than on a claim about
which firms did what.

`filing_items.parquet` is the reusable artifact. Nothing else in the pipeline holds 8-K items parsed
and joinable, so the next question about 8-K composition -- voluntary counts, bundling, anything
conditioned on what else a filing reported -- starts from it rather than from a raw string.
