---
title: "Export Data -- One File per Task (10)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# ONE ORDERED LIST, AND ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time
# it is sourced, so every library that registers a vocabulary must follow it -- _Entity.R and the
# five 04B files all do.
#
# THE COMMONS FIRST, AND init_create_script_fun() COMES FROM THEM. Naming the numbered scripts by
# that function before it exists is a bootstrap the render cannot survive, so the list is built in
# two steps: source what defines the resolver, then use it.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# THE FIVE RULE LIBRARIES AND 04D. 04B3's dte_collapse() is the only collapse this export calls
# rather than re-derives, and 04B2, 04B4 and 04B5 supply the vocabularies the pivots take their shape
# from. 04D supplies apl_dataset(), which is how a release directory is opened without picking up its
# own bookkeeping files.
.path_libs <- c(
  .path_libs,
  purrr::map_chr(
    c(
      "04B1-Rules-ORG", "04B2-Rules-GPE", "04B3-Rules-DATE", "04B4-Rules-MONEY",
      "04B5-Rules-REDACT", "04D-EntityApply"
    ),
    \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
  )
)
purrr::walk(
  .x = utils::tail(.path_libs, 6L),
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "10-ExportData"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04D released eight long files holding 93.7 million spans. 02B holds the register and 03F the labels.
This turns them into **eight contract-level caches and one joined file** -- the file the Stata
analysis reads.

| Chunk | Cache | Reads | Holds |
|:--|:--|:--|:--|
| Sample | `Sample` | 02B register | one row per registrant copy; the spine |
| Classification | `Classification` | 03F release | both engines, all three tasks |
| Parties | `EntityORG` | `org_mentions` | distinct parties by role, and the naive rung |
| Geography | `EntityGPE` | `places_geo`, `org_mentions` | distinct states and countries, by role |
| Governing law | `EntityLAW` | `law_clauses` | every jurisdiction named, pipe-separated |
| Dates | `EntityDATE` | `date_spans`, `term_spans` | start, end, duration, and which rung decided |
| Money | `EntityMONEY` | `money_spans` | how many amounts, and how large |
| Redactions | `EntityREDACT` | `redact_spans` | markers by kind |
| Contracts | `Contracts` | the eight above | the join, as parquet and Stata |

**One function per cache, and each takes paths.** Nothing is built in a chunk and passed to a
function: each export opens its own input, names the columns it reads at the call site, does its own
work and writes one parquet. Running one chunk on its own does exactly what a full render does.

**Each returns the table it wrote**, so `tab_EntityORG` is the party file exactly as it went to disk.

**Cached on modification time, not on existence.** A cache is used only where every input it reads is
older than it; an input that moved rebuilds it and says which one. `.rerun = TRUE` forces it. That is
the whole reason for eight files rather than one: a changed counterparty rule rebuilds the party file
and the join, and touches nothing else.

Existence alone was the earlier rule and it was wrong. Rebuilding the sample with two new columns left
the joined file holding the old one -- the row count had not changed, so every identity check passed
against a file that no longer matched its own spine, and nothing in the render said so.

**Every diagnostic reads a returned table, not the file being written.** An export that reported on
itself would print on a cold render and say nothing on a warm one, and the rendered document is the
artifact a reader opens. So each task has a report chunk beneath its export chunk, driven off
`tab_EntityORG` and its siblings, and a cached render says exactly what a cold one does.

## What the export decides, and what it does not

The counts are re-derived here rather than taken from 04B's collapse functions, because a count of
distinct parties by role is six lines of dplyr and reading them at the call site is worth more than
the indirection. **Dates are the exception**: duration is a four-rung cascade with a term parser in
it, so `dte_collapse()` is called rather than reimplemented.

Two decisions are deliberately *not* made:

**Governing law is not picked.** A contract naming several jurisdictions gets all of them,
pipe-separated, aligned with the `LawKind` that named each. The cue regexes are unanchored, so
"organized under the laws of the State of Delaware" produces a `LawsOfState` clause indistinguishable
from a governing-law clause -- and it is always earlier in the document. Any first-wins rule would
substitute the incorporation state systematically. `LawKind` is what lets a reader tell them apart.

**Party and place names are not exported.** Only counts. A contract can name several registrants and
several counterparties, so a single name column would need a pick rule of the same kind.

## Grain, and where the fan-out happens

Every cache is at **attachment grain** -- one row per primary copy, which is what 04D extracted. The
sample is at **registrant-copy grain**: a filing naming several registrants lists the same attachment
under each of them, and the register has a row for each.

`export_final()` fans the entity caches out on `HashDocument`, so every copy carries the values of
its attachment. That is 03F's own decision -- its release is already at copy grain -- applied to the
entity blocks too. Two things follow:

- entity values **repeat** across copies, so a corpus mean over the raw file double-counts and wants
  `PrimaryFiler == 1`
- a row still empty after the join means 04D did not reach that attachment, **not** that it is a
  co-filer copy

## Nothing opens a document

No export reads contract text. Every word count comes from the register. The text seam 04A
established holds through to the released file.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    FilSample         = "2_output/02B-Register/Output/Documents.parquet",
    # WHY A DOCUMENT WAS FLAGGED lives here and not in the register: 02B relocates RemClass without
    # ever having joined it, so Removed says which documents were caught and nothing says why.
    FilRemoved        = "2_output/01C-EdgarMetaData/Output/RemovedDocs.parquet",
    FilClassification = "2_output/03F-ClassifyApply/release/contract_labels_L256.parquet",
    # THE POLICY HASH IS IN THE PATH. 04D names each directory for a hash folding in its rules and
    # the extractor's own spec hashes, so pinning it here is what says which release this reads --
    # and a rehearsal directory sitting beside the full one cannot be picked up by accident.
    DirEntityORG      = "2_output/04D-EntityApply/Store/ORG/812b63f438c5/",
    DirEntityGPE      = "2_output/04D-EntityApply/Store/GPE/2374951841a7/",
    DirEntityDATE     = "2_output/04D-EntityApply/Store/DATE/79c379586f6a/",
    DirEntityMONEY    = "2_output/04D-EntityApply/Store/MONEY/58e9be52f1b9/",
    DirEntityREDACT   = "2_output/04D-EntityApply/Store/REDACT/7b84db9925eb/"
  ),
  # THE CACHES ARE INTERMEDIATE. Each is one task's contract-level table, rebuilt on its own by
  # passing .rerun = TRUE to that chunk.
  Cache = list(
    CacheSample         = utils_file_path(.dir_main, "Cache", "Sample.parquet"),
    CacheClassification = utils_file_path(.dir_main, "Cache", "Classification.parquet"),
    CacheEntityORG      = utils_file_path(.dir_main, "Cache", "EntityORG.parquet"),
    CacheEntityGPE      = utils_file_path(.dir_main, "Cache", "EntityGPE.parquet"),
    CacheEntityLAW      = utils_file_path(.dir_main, "Cache", "EntityLAW.parquet"),
    CacheEntityDATE     = utils_file_path(.dir_main, "Cache", "EntityDATE.parquet"),
    CacheEntityMONEY    = utils_file_path(.dir_main, "Cache", "EntityMONEY.parquet"),
    CacheEntityREDACT   = utils_file_path(.dir_main, "Cache", "EntityREDACT.parquet")
  ),
  # THE DELIVERABLE. The dta and the codebook are written beside the parquet.
  Output = list(
    FilContracts = utils_file_path(.dir_main, "Output", "Contracts.parquet")
  )
)

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is read")
```

The five hashes above should reproduce what 04D reported when it wrote the release. Where one
differs, a dial moved since the corpus pass ran, and the export would read a directory that no longer
answers to the rules in 04B.

# Sample

The register cut to Exhibit 10, with the columns worth releasing named and `DateFiled` coerced once.
**Nothing is filtered out**: 02B removes no document ever, and a sample that quietly excluded the
malformed ones would leave every later study unable to see what was lost. `Removed` says which they
are, `RemClass` says why -- too short, not prose, mostly digits -- and `UrlDocument` is the link back
to EDGAR.

**`RemClass` is joined from 01C**, because the register does not carry it: `reg_shape()` relocates
the name without ever having joined the column. Referee 1 asked whether the malformed contracts are
noted anywhere in the data, and without this they are flagged but unexplained.

01D's three columns -- `Items`, `HasItem101`, `Item101Outcome` -- are deliberately **not** exported.
They are joined onto the register by `DocID` from a table of 8-K reports, so on an Exhibit 10 row
`HasItem101` is identically zero and the other two identically missing. A contract reaches its own
8-K through `HashIndex`, which is the filing and is exported.

The report below lists every register column the selection leaves behind, so anything that ought to
be in the release surfaces there rather than being missed.

```{r}
#| label: export-sample

tab_Sample <- export_sample(
  .path_in      = .lP$Input$FilSample,
  .path_removed = .lP$Input$FilRemoved,   # RemClass: why a document was flagged
  .path_out     = .lP$Cache$CacheSample,
  .doc_type     = "Exhibit10",            # the register also holds 8-K reports and CT orders
  .rerun        = FALSE                   # the cache check below rebuilds when an input has moved
)
```

```{r}
#| label: report-sample

exp_report_columns(
  .tab = exp_table_columns(.tab = tab_Sample, .path_register = .lP$Input$FilSample)
)

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_Sample),
  .title = "The sample, column by column"
)

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_Sample, .col = "SampleStepDesc"),
  .title = "Where each contract sits on the sample ladder"
)
```

`PrimaryFiler` and `MultFiler` read as means, which are the shares: how much of the file is the copy
04D actually extracted, and how much is a second registrant listing the same attachment. `Removed`
reads the same way, and `RemClass` beside it is non-missing on exactly those rows.

The `Min` and `Max` on the date columns are the fastest sanity check in this document.
`CtoReleaseFirst` and `CtoReleaseLast` currently run to **3036-08-03**, which is a parse error in
01E's release dates rather than anything this export does -- it reaches 1.2% of rows and is worth
fixing upstream.

# Classification

03F's release as it wrote it: both engines, all three tasks, every probability and every agreement
flag. Five columns are dropped because the sample already carries them and Stata's `merge` fails
rather than choosing when two files define a variable.

`Class`, `ClassBroad` and `AmendType` are **added as copies** of the crowned engine's, so no
downstream script has to know which engine won. The originals stay, because the agreement flags refer
to them by name.

**This is already one row per registrant copy** -- 03F fans out on `HashDocument` before it writes --
so a co-filer copy carries the label computed from its attachment's primary.

```{r}
#| label: export-classification

tab_Classification <- export_classification(
  .path_in  = .lP$Input$FilClassification,
  .path_out = .lP$Cache$CacheClassification,
  .engine   = "Bert",                  # 03B crowned legal-bert; the keyword arm stays in the file
  .rerun    = FALSE
)
```

```{r}
#| label: report-classification

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_Classification, .col = "Class"),
  .title = "Contract type, the crowned engine",
  .notes = c(Pct = "Share of the classified copies, not of the sample.")
)

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_Classification, .col = "ClassDetailedFlag"),
  .title = "Where the keyword arm agrees with Bert"
)
```

The flag is the two engines differenced, not a validation: the keyword arm has no claim to be right
where they part. It is the cheapest signal available for which contracts are hard.

# Parties

Distinct parties per contract, by role, plus the rung above them.

`nUniSpellingsNaive` is the number of distinct names the extractor proposed **before** grouping merged
them into parties -- 8.18 per contract at corpus scale against 7.28 parties. It is stored because it
cannot be recovered from the role counts; the other naive rungs can be, and are not.

`HasNoParty` marks the sentinel row 04B1 writes for a contract in which no organisation was found at
all. Every count is zero there, but nothing else in the file would say why.

```{r}
#| label: export-org

tab_EntityORG <- export_ORG(
  .dir_in   = .lP$Input$DirEntityORG,
  .path_out = .lP$Cache$CacheEntityORG,
  .rerun    = FALSE
)
```

```{r}
#| label: report-org

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_EntityORG),
  .title = "Parties per contract",
  .notes = c(Mean = "nUniSpellingsNaive against nUniRegistrant + nUniCounterparty + the rest is the
                     rung: distinct spellings before grouping, against parties after it.")
)
```

`HasNoParty` reads as a mean, which is the share of contracts in which the extractor found no
organisation at all. Every count is zero on those rows, so the mean of `nUniRegistrant` is bounded
above by one minus that share.

# Geography

Distinct states and countries, naive and split by role.

The naive rung counts every place outside a governing-law clause; the role columns count those the
extractor attached to a party. **The join is the attachment filter**: `geo_attach()` nulls `PartyKey`
on any place it did not offer to a party, and a SQL join never matches a null.

**Law-clause places are excluded everywhere, including the naive rung.** "The laws of the State of
Delaware" is a jurisdiction rather than a location and belongs to the law file. That moves the naive
number below the published 2.56 states and 1.81 countries, which count them in.

This task reads `org_mentions` as well, because a role is a property of the party and `places_geo`
carries only the key. That is 04D's own dependency: its GPE pass folds ORG's hash into its own.

```{r}
#| label: export-gpe

tab_EntityGPE <- export_GPE(
  .dir_in   = .lP$Input$DirEntityGPE,
  .dir_org  = .lP$Input$DirEntityORG,   # roles live in the mention file
  .path_out = .lP$Cache$CacheEntityGPE,
  .rerun    = FALSE
)
```

```{r}
#| label: report-gpe

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_EntityGPE),
  .title = "States and countries per contract",
  .notes = c(Mean = "The naive pair against the four role columns is the ladder. Naive counts every
                     place outside a law clause; the role columns count those attached to a party.")
)
```

`nUniStateRegistrant` above one does not mean two registrants -- there is one registrant party per
contract. It means two distinct states were attached to that one party, which measures ambiguity as
much as location.

# Governing law

Every jurisdiction the contract's law clauses named, pipe-separated in document order, with
`LawJurisdictionLevel` and `LawKind` aligned element for element.

Nothing is picked, and that is deliberate -- see Purpose. `nUniJurisdiction > 1` is the honesty
column: it says the contract named more than one place and the reader has to choose.

`law_clauses` is released beside `places_geo` because one 04D pass wrote both, which is why this
chunk points at the GPE directory.

```{r}
#| label: export-law

tab_EntityLAW <- export_LAW(
  .dir_in   = .lP$Input$DirEntityGPE,   # law_clauses sits beside places_geo
  .path_out = .lP$Cache$CacheEntityLAW,
  .rerun    = FALSE
)
```

```{r}
#| label: report-law

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_EntityLAW),
  .title = "Clauses and jurisdictions per contract",
  .notes = c(Max = "nUniJurisdiction above one is a contract naming several places. Its mean is how
                    often the pick this file refuses to make would have had to be made.")
)

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_EntityLAW, .col = "LawJurisdiction", .top = 15L),
  .title = "The commonest jurisdiction strings",
  .notes = c(Level = "A pipe means the contract named more than one; read LawKind beside it.")
)
```

A single `Delaware` and a `Delaware|New York` are different levels here, deliberately. The pipe is
the signal.

# Dates

The one export that does not count anything. Duration is a cascade, and `DurationSource` says which
rung answered:

- **term** -- the contract states its own length. Outranks everything.
- **open** -- it states that it has no length. A finding, not a gap.
- **cue** -- a future date with an end cue beside it: MATURIT, THROUGH, EXPIR.
- **maxdate** -- the farthest future date, for no stated reason.

`DateEndNaive` is that last rung on its own, and `NaiveYears` measures it from the **same**
`DateStart`, so the naive and rule durations differ in one decision rather than two. It is missing
wherever the contract names no future date -- which is the coverage argument for the cascade, not a
fault: a contract stating "a term of two years" and mentioning only past dates has a duration under
the term rung and none at all under the naive definition.

The register supplies the filing date, because `DateStart` falls back to it where no date sits at or
before filing.

```{r}
#| label: export-date

tab_EntityDATE <- export_DATE(
  .dir_in        = .lP$Input$DirEntityDATE,
  .path_register = .lP$Input$FilSample,   # DateStart falls back to the filing date
  .path_out      = .lP$Cache$CacheEntityDATE,
  .spec          = dte_spec(
    .start     = "latest",   # 04B3: the latest date at or before filing, else the filing date
    .end       = "term",     # 04B3: the full four-rung cascade
    .cap_years = 30          # 04B3: a longer duration is dropped, not winsorised
  ),
  .rerun         = FALSE
)
```

```{r}
#| label: report-date

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_EntityDATE, .col = "DurationSource"),
  .title = "Which rung decided the duration",
  .notes = c(Level = "term outranks open outranks cue outranks maxdate. none is a contract that says
                      nothing about when it ends, which is a finding rather than a failure.")
)

exp_report_levels(
  .tab   = exp_table_levels(.tab = tab_EntityDATE, .col = "DurationDropped"),
  .title = "Why a duration is missing where it is"
)

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_EntityDATE),
  .title = "Dates and durations",
  .notes = c(Median = "DurationYears against NaiveYears is the comparison: 2.80 against 11.75 at
                       corpus scale, and a naive standard deviation that moves with the sample.")
)
```

`NaiveYears` reaching fewer contracts than `DurationYears` is the coverage argument for the cascade,
not a defect: a contract stating a two-year term and naming only past dates has a duration under the
term rung and none at all under the naive definition.

**Only `DurationYears` is capped.** It tops out at exactly 30 and `DurationDropped` says how many
were dropped for it. `DateStart`, `DateEnd`, `DateEndNaive`, `TermYears` and `NaiveYears` are as the
extractor found them, so their extremes -- a start in 1415, an end in 9999, a stated term of 999
years -- are real spans in real documents rather than failures of this export. That is the house
position: the span stays as found and the rule column is the clean one.

# Money

How many amounts a contract names and how large they are, split by currency because there is no FX
conversion anywhere in this pipeline. The naive rung is every parsed, non-withheld figure; the rule
additionally drops a zero and a figure with par-value language beside it.

**A known defect travels in this file.** `MoneyMaxUSD` and `MoneyMaxOther` inherit 04B4's digit-run
concatenation: HTML flattening removed table cell boundaries and the money regex read the run as one
number, so `$ 201620172018201...` is four fiscal years glued together. Roughly 1,200 contracts of the
844,931 carrying money are affected. **The medians are far less affected, which is not the same as
immune**: a single glued run cannot move a median, but a contract whose figures are mostly glued runs
has a glued median, and 118 contracts carry one above 1e11 against roughly 1,500 for the maximum. The
tail is not the problem either way -- two glued four-digit cells give `20162017`, twenty million
dollars, plausible and undetectable by magnitude. The report below counts what exceeds 1e11 in every
column.

```{r}
#| label: export-money

tab_EntityMONEY <- export_MONEY(
  .dir_in   = .lP$Input$DirEntityMONEY,
  .path_out = .lP$Cache$CacheEntityMONEY,
  .rerun    = FALSE
)
```

```{r}
#| label: report-money

exp_report_numeric(
  .tab    = exp_table_numeric(.tab = tab_EntityMONEY, .ceiling = 1e11),
  .title  = "Amounts per contract",
  .notes  = c(NAbove = "Contracts whose figure exceeds 1e11, the ceiling 04B4 would declare. That is
                        the visible tail of the digit-run concatenation; the glued four-digit pairs
                        beneath it cannot be found by magnitude.")
)
```

Read `Max` on `MoneyMaxUSD` before anything else. It is the defect in one number, and the distance
between it and `Median` is why the medians are the columns to use -- but read `NAbove` on
`MoneyMedUSD` too, because it is not zero.

Anything at or above 1e15 prints in scientific notation. That is the point past which a double stops
holding consecutive integers, so the digits beyond it are the representation rather than the
measurement.

# Redactions

Six marker counts and nothing else, because every aggregate anyone wants is a sum of them:

- **every marker** -- all six
- **bracketed only** -- the first five; `RedactBare` is the only unbracketed kind
- **text actually withheld** -- the four `Redact` kinds; the two `Omit` kinds are a section left out,
  not text taken from a reader

The two splits cut across each other, so **no single total is "redactions"**. Storing one would be
choosing a denominator on the reader's behalf. `nRedactMoney` is the exception -- it comes from
matching a marker to a withheld price beside it and is not a sum of the others.

`Bracketed` and `Withheld` are not read: 04B5 declares both as functions of `Kind`.

```{r}
#| label: export-redact

tab_EntityREDACT <- export_REDACT(
  .dir_in   = .lP$Input$DirEntityREDACT,
  .path_out = .lP$Cache$CacheEntityREDACT,
  .rerun    = FALSE
)
```

```{r}
#| label: report-redact

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_EntityREDACT),
  .title = "Redaction markers per contract",
  .notes = c(Mean = "Sum the first three and nRedactBare for text withheld; sum the first five for
                     brackets, which is the published measure. Neither is 'redactions' on its own.")
)
```

The two `Omit` means are the size of the difference between those definitions: markers that are
inside brackets and withhold nothing.

# Contracts

The join, and the only place a `.dta` is written.

The sample is the spine and every join is a left join, so the row count is the register's and no
contract disappears because one pass could not read it. The classification joins on `DocID`; the six
entity caches are re-keyed from their primary `DocID` onto `HashDocument` and joined many-to-one, so
every registrant copy carries the values of its attachment.

Both `relationship =` arguments are checks as much as hints: a duplicate key on either side stops the
render rather than silently multiplying the sample. Every join is tested for name collisions first,
because dplyr suffixes `Column.x` and `Column.y` in silence and a file this wide is where that would
go unnoticed.

**This chunk reads all eight caches, so it rebuilds whenever any of them does.** The row count cannot
catch a stale join -- it is the sample's either way -- so the check has to be on the inputs rather
than on the output.

```{r}
#| label: export-final

tab_Contracts <- export_final(
  .path_sample  = .lP$Cache$CacheSample,
  .path_class   = .lP$Cache$CacheClassification,
  .paths_entity = .lP$Cache[c(
    "CacheEntityORG", "CacheEntityGPE", "CacheEntityLAW",
    "CacheEntityDATE", "CacheEntityMONEY", "CacheEntityREDACT"
  )],
  .path_out     = .lP$Output$FilContracts,
  .rerun        = FALSE,
  .dta          = TRUE                  # writes Contracts.dta and Contracts_Codebook.csv beside it
)
```

```{r}
#| label: report-final

# BUILT ONCE AND HANDED TO BOTH CHECKS. The reconciliation needs it for the row counts and the
# identity check needs it for the column names, and two lists would be two things to keep in step.
lst_Caches <- list(
  Sample         = tab_Sample,
  Classification = tab_Classification,
  ORG            = tab_EntityORG,
  GPE            = tab_EntityGPE,
  LAW            = tab_EntityLAW,
  DATE           = tab_EntityDATE,
  MONEY          = tab_EntityMONEY,
  REDACT         = tab_EntityREDACT
)

exp_report_final(
  .tab = exp_check_final(
    .tab      = tab_Contracts,
    .tabs     = lst_Caches,        # every column these hold must be in the join
    .n_sample = nrow(tab_Sample)
  )
)

exp_report_files(
  .tab = exp_table_files(.tabs = lst_Caches, .final = tab_Contracts)
)
```

`InFinal` exceeding `Rows` on an entity cache is the fan-out working: an attachment filed by three
registrants contributes one cache row and three rows of the joined file. That is also why a corpus
mean over this file double-counts and wants `PrimaryFiler == 1`.

**`Cache columns missing from the join` is the check that catches a stale join**, and it is the only
one that can. The row counts are the sample's whether the join is current or a year old, so a file
built from an earlier sample passes every count above it. Differencing the caches' column names
against the joined file's does not.

The codebook written here is **mechanical**: which cache each column came from, its type, and the
name Stata will see. What each column means is the separate document below.

# Column dictionary

One row per column of `Contracts`, in eight sections rather than tabsets: Quarto's tabset filter
intercepts `panel-tabset` divs and empties them when the content is R-generated HTML, which every
table below is.

**`Missing` is the column nobody can reconstruct from the data.** In the joined file an `NA` means
two different things -- the contract is not in that block's cache at all, or it is and this
particular value does not exist -- and nothing in the file distinguishes them. `Marker` in the table
below is how: where it is missing the whole block is absent, and every other `NA` in the block is the
second kind.

`structural` in `Missing` means the column is never missing where its block reached the row. A count
of zero is then a measurement -- the extractor looked and found none -- rather than an absence.

```{r}
#| label: report-grain

exp_report_grain()
```

```{r}
#| label: build-dictionary

# THE DECLARATION IS DIFFERENCED AGAINST THE FILE, BOTH WAYS, and aborts on either. A column in the
# file and not the dictionary is undocumented; a column in the dictionary and not the file describes
# something that no longer exists. Type and the Stata name are read off the data rather than
# declared, so the dictionary cannot claim a type the file does not have.
tab_Dictionary <- exp_table_dictionary(.tab = tab_Contracts)
```

## Sample

The register as 02B holds it, restricted to Exhibit 10. One row per registrant copy, nothing
excluded.

```{r}
#| label: dict-sample
exp_report_dictionary(.tab = tab_Dictionary, .block = "Sample")
```

## Classification

Both engines side by side. The keyword arm is an independent measurement rather than a validation --
it has no claim to be right where the two differ, which is what the `Flag` columns record.

```{r}
#| label: dict-classification
exp_report_dictionary(.tab = tab_Dictionary, .block = "Classification")
```

## Parties

```{r}
#| label: dict-parties
exp_report_dictionary(.tab = tab_Dictionary, .block = "Parties")
```

## Geography

```{r}
#| label: dict-geography
exp_report_dictionary(.tab = tab_Dictionary, .block = "Geography")
```

## Law

```{r}
#| label: dict-law
exp_report_dictionary(.tab = tab_Dictionary, .block = "Law")
```

## Dates

```{r}
#| label: dict-dates
exp_report_dictionary(.tab = tab_Dictionary, .block = "Dates")
```

## Money

```{r}
#| label: dict-money
exp_report_dictionary(.tab = tab_Dictionary, .block = "Money")
```

## Redactions

```{r}
#| label: dict-redactions
exp_report_dictionary(.tab = tab_Dictionary, .block = "Redactions")
```

# Next

`Contracts_Codebook.csv` now carries both halves: `Source`, `Type` and `StataName` derived from the
file, `Block`, `Meaning` and `Missing` declared above. It is written whenever the join is, so the
archive never holds a codebook describing a different file.

Two items are known and outstanding, and both are upstream of this document. `MoneyMaxUSD` and
`MoneyMaxOther` carry 04B4's digit-run concatenation until a ceiling is declared in `mny_spec()`,
which re-runs the MONEY pass alone. And the entity variables have not been checked against a
document-level gold set.

Three smaller things this document surfaced and does not fix: `CtoReleaseFirst` and `CtoReleaseLast`
run to 3036 on a few rows, which is a parse error in 01E; `nUniCountryNaive` reaches 224, more
countries than exist; and the released date columns other than `DurationYears` are uncapped, so a
start in 1415 and an end in 9999 are spans the extractor really found rather than failures here.
