---
title: "Regressions -- The Paper's Ten Tables, from One File (20)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")


.name_script <- "20-RunRegression"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/20-RunRegression.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document estimates the paper's ten regression tables from `Contracts.parquet` and three external
inputs, and writes each table as a `.tex` file.

## What it replaces

The submitted tables came from seven Stata do-files. The first three of those assembled a contract
table out of eight pipeline releases, matched it to Compustat, and built the variables; the last
three estimated on the result. The eight releases are now one file, and the matching happens
upstream in `02A`, so the assembly step no longer exists. What is left -- three external inputs, two
panels, ten specifications -- is small enough to be stated in the repo's own language, next to
everything that produced its inputs.

## Two grains

**The firm-quarter panel** is the one place a non-event exists. Every Compustat firm-quarter appears;
those with no contract carry a zero count; the filing-decision table is estimated on it.

**The contract panel** is one row per attachment copy, carrying its firm-quarter's variables by a
many-to-one join. Every other table is estimated on it. Nothing is computed at contract grain that
the quarter panel does not already hold, so the two grains control for the same numbers.

## Three estimators, and why the firm-effect column is linear

The paper reports each specification pooled and with firm fixed effects, and estimates the latter
two ways: a conditional logit and a linear model with the firm effect absorbed. Both are here. The
conditional logit is `survival::clogit()` with the exact conditional likelihood, which is the same
estimator Stata's `clogit` computes, and it is slow enough on 1.4 million rows that it is opt-in.

What is deliberately **not** here is a logit with the firm effect absorbed by `fixest`. That
estimator maximises the unconditional likelihood with the firm intercepts concentrated out, which is
the incidental-parameters-biased estimator conditional logit exists to avoid. It would look like the
paper's column and would not be it.

## Two departures from the do-files, each a correction rather than a choice

**Quarterly operating cash flow.** The do-file differenced the year-to-date figure and then, on the
first quarter, replaced the result with itself. A first quarter's quarterly flow is its year-to-date
flow; that is what is used here. The equity-issuance block in the same file handles the identical
case correctly, so this is what was intended. The variable is in every table's control set.

**The DiD treatment intensity.** The do-file divided a count grouped on CIK by a count grouped on
gvkey, and regressed whichever contract row survived a de-duplication rather than the firm-quarter
average its table notes describe. Both are computed within gvkey here, and the outcome is the mean.

## What is not here

Figures, which are `21-Figures`; and descriptives beyond the control-variable table, which are
`105` in the Stata folder until they move.

# Configuration

Every path, and every definitional choice the paper leaves open, in one place. **The defaults
reproduce the submitted tables**: the naive duration, the bracketed redaction count, item counts
coalesced to zero, and every attachment copy in the contract panel. Switch one at a time.

```{r}
#| label: config

.lP <- list(
  Input = list(
    FilContracts = "2_output/10-ExportData/Output/Contracts.parquet",
    # THE THREE EXTERNAL INPUTS. WRDS pulls and a Hoberg-Phillips download; not in the repo.
    FilCompustat = "0_data/External/Compustat_quarterly_data_2024.dta",
    FilSegments  = "0_data/External/segment_data.dta",
    FilFluidity  = "0_data/External/FluidityData/FluidityData.txt"
  ),
  Params = list(
    Duration   = "naive",      # "naive" = NaiveYears, the submitted measure; "cascade" = DurationYears
    Redaction  = "bracketed",  # "bracketed" (published), "withheld", or "money"
    Items      = "zero",       # "zero" coalesces a filing with no item structure; "missing" leaves it
    Voluntary  = "era",        # "era" counts 12/9/5 before the reform; "dotted" is the submitted measure
    Primary    = FALSE,        # TRUE restricts counts and the contract sample to primary copies
    SameSample = FALSE,        # TRUE estimates pooled Table 7 on the firm-effect sample, as submitted
    Estimators = c("logit", "lpm")   # add "clogit" for the exact conditional logit; slow
  ),
  Output = list(
    FilQuarter  = utils_file_path(.dir_main, "Output", "PanelQuarter.parquet"),
    FilContract = utils_file_path(.dir_main, "Output", "PanelContract.parquet"),
    DirTables   = utils_file_path(.dir_main, "Tables")
  )
)
```

**`fixest` is not in `renv.lock`.** It is installed with `renv::install("fixest")` and recorded with
`renv::snapshot()` before this document renders.

# Inputs

## The contract table

```{r}
#| label: input-contracts

contracts <- reg_read_contracts(
  .path      = .lP$Input$FilContracts,   # 10-ExportData's release
  .duration  = .lP$Params$Duration,      # which duration column stands in for the paper's
  .redaction = .lP$Params$Redaction,     # which redaction count feeds Redacted
  .items     = .lP$Params$Items,         # zero or missing on a filing with no item structure
  .voluntary = .lP$Params$Voluntary      # era-aware count, or the three post-reform codes only
)
```

## The vocabulary covers the data

The twelve contract types are restated in this document's library, ordered so that `Other` is the
reference level in every table that enters type. The order is this document's; the set is the
file's. A label in the file that the library does not know would become a missing factor level and
leave three tables silently, so the set is checked here rather than assumed.

```{r}
#| label: input-check-vocabulary

in_file_ <- sort(setdiff(unique(contracts$ClassLabel), c("", NA)))
stopifnot(setequal(in_file_, .reg_class_levels))
cli::cli_alert_success("{length(in_file_)} contract types in the file, all twelve known to this document")
```

## The three external inputs

```{r}
#| label: input-external

compustat <- reg_read_compustat(.path = .lP$Input$FilCompustat)
segments  <- reg_read_segments(.path = .lP$Input$FilSegments)
fluidity  <- reg_read_fluidity(.path = .lP$Input$FilFluidity)
```

# Panels

## Firm-quarter

Counts first, on the full Compustat panel so a non-filing quarter is a zero rather than an absent
row; then the accounting variables, winsorised once over the whole panel before any sample is drawn.

```{r}
#| label: panel-quarter

quarter <- reg_build_quarter(
  .contracts = contracts,             # the contract table
  .compustat = compustat,             # every Compustat firm-quarter
  .fluidity  = fluidity,              # Hoberg-Phillips, joined on gvkey-year
  .primary   = .lP$Params$Primary     # count primary copies only, or every row
) |>
  reg_add_firm_vars()
```

## Contract

```{r}
#| label: panel-contract

contract <- reg_build_contract(
  .contracts = contracts,             # the contract table
  .quarter   = quarter,               # carries the firm-quarter variables onto each
  .primary   = .lP$Params$Primary     # the same rule the quarter counts used
)
```

```{r}
#| label: panel-report

reg_report_panels(.quarter = quarter, .contract = contract)
```

# Samples

Two rules the paper applies before any table, made visible because they define what is estimated.

The **filing-decision sample** keeps firm-quarters from 2001 to 2024 with every control present, and
drops firms that never file within the window: a firm that cannot be observed filing carries no
information about the decision to file.

The **contract sample** keeps matched, well-formed contracts filed from a start year the table sets,
with every control present. Delay and contract-type tables start in 2005, redaction in 2008 when
orders became observable, bundling in 2004 when the item taxonomy that defines it appeared.

```{r}
#| label: sample-quarter

sample_quarter <- reg_sample_quarter(
  .quarter     = quarter,                 # the full firm-quarter panel
  .years       = c(2001L, 2024L),         # calendar window on datadate
  .same_sample = .lP$Params$SameSample    # drop non-varying firms before the pooled columns too
)

reg_report_controls(.quarter = sample_quarter, .vars = .reg_controls$Quarter)
```

```{r}
#| label: sample-contract

sample_delay <- reg_sample_contract(
  .contract = contract,              # the contract panel
  .min_year = 2005L,                 # first filing year in the delay tables
  .controls = .reg_controls$Full,    # the long control set must be complete
  .primary  = .lP$Params$Primary     # every copy, or primary copies only
)

sample_type <- reg_sample_contract(
  .contract = contract,
  .min_year = 2005L,
  .controls = .reg_controls$Contract,   # Table E1 uses the shorter set
  .primary  = .lP$Params$Primary
)

sample_redact <- reg_sample_contract(
  .contract = contract,
  .min_year = 2008L,                 # orders are observable from 2008
  .controls = .reg_controls$Full,
  .primary  = .lP$Params$Primary
)

sample_bundle <- reg_sample_contract(
  .contract = contract,
  .min_year = 2004L,                 # the dotted item taxonomy dates from August 2004
  .controls = .reg_controls$Full,
  .primary  = .lP$Params$Primary
)
```

# Results

Console output only; every table is written to disk under Deployment.

## Table 7: the decision to file

```{r}
#| label: results-filed

tab_filed <- reg_table_filed(
  .sample     = sample_quarter,          # firm-quarters
  .estimators = .lP$Params$Estimators    # pooled logit plus the firm-effect columns
)
reg_report_models(.models = tab_filed, .title = "Table 7: Filing decision")
```

## Table E1: which contract types are disclosed late

```{r}
#| label: results-contract-type

tab_type <- reg_table_contract_type(.sample = sample_type)
reg_report_models(.models = tab_type, .title = "Table E1: Contract type and delayed filing", .keep = "^Class")
```

## Table 9: delayed filing

Competition enters two ways, product-market fluidity and a two-digit sales Herfindahl, on the
paper's grounds that the two disagree about which firms face rivals and a result that holds under
both is the one worth reporting.

```{r}
#| label: results-delay

tab_delay_fluid <- reg_table_outcome(
  .sample      = sample_delay,
  .dv          = "Delayed",
  .competition = "Fluidity",             # primary measure
  .estimators  = .lP$Params$Estimators
)
tab_delay_hhi <- reg_table_outcome(
  .sample      = sample_delay,
  .dv          = "Delayed",
  .competition = "HhiSic2Win",           # robustness measure
  .estimators  = .lP$Params$Estimators
)
reg_report_models(.models = tab_delay_fluid, .title = "Table 9: Delayed filing, fluidity")
```

## Table 10: redaction

```{r}
#| label: results-redaction

tab_redact_fluid <- reg_table_outcome(
  .sample      = sample_redact,
  .dv          = "Redacted",
  .competition = "Fluidity",
  .estimators  = .lP$Params$Estimators
)
tab_redact_hhi <- reg_table_outcome(
  .sample      = sample_redact,
  .dv          = "Redacted",
  .competition = "HhiSic2Win",
  .estimators  = .lP$Params$Estimators
)
reg_report_models(.models = tab_redact_fluid, .title = "Table 10: Redaction, fluidity")
```

## Appendix D1: bundling with voluntary items

```{r}
#| label: results-bundling

tab_bundle <- reg_table_bundling(
  .sample     = sample_bundle,
  .estimators = .lP$Params$Estimators
)
reg_report_models(.models = tab_bundle, .title = "Appendix D1: Bundling", .keep = "^(Size|Loss|Class)")
```

## Table 8: the 2004 reform, both ways

The outcome is the number of voluntary items on the parent 8-K. Counting only the three post-reform
codes returns zero on every filing before 23 August 2004, because those items were then numbered 12,
9 and 5; the submitted table was built that way, and its `Post` coefficient is the rise from a
pre-period that was zero by construction. The era-aware count measures the pre-period. Both are
estimated so the difference is on the page with its cause.

```{r}
#| label: results-did

tab_did <- reg_table_did(.contract = contract)
reg_report_models(.models = tab_did, .title = "Table 8: 2004 reform, era-aware count",
                  .keep = "^(Share|Post|Trend)")

contract_dotted <- reg_read_contracts(
  .path      = .lP$Input$FilContracts,
  .duration  = .lP$Params$Duration,
  .redaction = .lP$Params$Redaction,
  .items     = .lP$Params$Items,
  .voluntary = "dotted"                  # the submitted measure: post-reform codes only
) |>
  reg_build_contract(.quarter = quarter, .primary = .lP$Params$Primary)

tab_did_dotted <- reg_table_did(.contract = contract_dotted)
reg_report_models(.models = tab_did_dotted, .title = "Table 8: 2004 reform, post-reform codes only",
                  .keep = "^(Share|Post|Trend)")
```

# Validation

Three checks between the panels, each stated before it is read.

**Every contract sits on a firm-quarter the quarter panel counts as filing.** Both panels take
their rows from one filter, `reg_rows_counted()`, so this holds by construction. A violation means
the two builders were given different arguments, which is the one way the shared filter can be
defeated.

**The reverse is not expected to hold exactly.** A firm-quarter counted as filing can carry no
contract in the contract panel where its only contracts failed the many-to-one join, so the count of
such quarters is reported rather than asserted.

**The year-to-date correction leaves Q1 operating cash flow equal to the year-to-date figure.** This
is the departure from the do-file, so it is checked rather than assumed.

```{r}
#| label: validation-panels

keys_q_ <- quarter |> dplyr::filter(.data$Filed == 1L) |> dplyr::distinct(.data$gvkey, .data$fyear, .data$fqtr)
keys_c_ <- contract |> dplyr::distinct(.data$gvkey, .data$fyear, .data$fqtr)

stopifnot(nrow(dplyr::anti_join(keys_c_, keys_q_, by = c("gvkey", "fyear", "fqtr"))) == 0L)
cli::cli_alert_success("every contract firm-quarter is in the quarter panel")

n_only_q_ <- nrow(dplyr::anti_join(keys_q_, keys_c_, by = c("gvkey", "fyear", "fqtr")))
cli::cli_alert_info("{n_only_q_} filing firm-quarters carry no contract in the contract panel")

q1_ <- quarter |> dplyr::filter(.data$fqtr == 1L, !is.na(.data$Ocf))
stopifnot(all(q1_$Ocf == q1_$oancfy))
cli::cli_alert_success("Q1 operating cash flow equals the year-to-date figure on {format(nrow(q1_), big.mark = ',')} rows")
```

# Deployment

The two panels, and every table as `.tex`. The panels are what a reader re-estimates from; the
tables are what the manuscript includes.

```{r}
#| label: deploy-panels

fs::dir_create(fs::path_dir(.lP$Output$FilQuarter))
arrow::write_parquet(quarter,  .lP$Output$FilQuarter)
arrow::write_parquet(contract, .lP$Output$FilContract)
cli::cli_alert_success("wrote {.file {fs::path_file(.lP$Output$FilQuarter)}}")
cli::cli_alert_success("wrote {.file {fs::path_file(.lP$Output$FilContract)}}")
```

```{r}
#| label: deploy-tables

tex_ <- function(.name) fs::path(.lP$Output$DirTables, paste0(.name, ".tex"))

reg_tex(.models = tab_filed,        .path = tex_("filed"),           .title = "Filing decision")
reg_tex(.models = tab_type,         .path = tex_("contract_type"),   .title = "Contract type and delayed filing",
        .keep = "^Class")
reg_tex(.models = tab_delay_fluid,  .path = tex_("delay_fluidity"),  .title = "Delayed filing, fluidity")
reg_tex(.models = tab_delay_hhi,    .path = tex_("delay_hhi"),       .title = "Delayed filing, HHI")
reg_tex(.models = tab_redact_fluid, .path = tex_("redaction_fluidity"), .title = "Redaction, fluidity")
reg_tex(.models = tab_redact_hhi,   .path = tex_("redaction_hhi"),   .title = "Redaction, HHI")
reg_tex(.models = tab_bundle,       .path = tex_("bundling"),        .title = "Bundling with voluntary items")
reg_tex(.models = tab_did,          .path = tex_("did_2004"),        .title = "The 2004 reform, era-aware count")
reg_tex(.models = tab_did_dotted,   .path = tex_("did_2004_dotted"), .title = "The 2004 reform, post-reform codes only")
```

# Overview

```{r}
#| label: overview-panels

reg_report_panels(.quarter = quarter, .contract = contract)
```

```{r}
#| label: overview-config

tibble::tibble(
  Parameter = c("Duration", "Redaction", "Items", "Voluntary items", "Primary copies", "Same sample",
                "Estimators"),
  Value     = c(.lP$Params$Duration, .lP$Params$Redaction, .lP$Params$Items, .lP$Params$Voluntary,
                as.character(.lP$Params$Primary), as.character(.lP$Params$SameSample),
                paste(.lP$Params$Estimators, collapse = ", "))
) |>
  tbl_out(.title = "The choices this render made")
```

# Next

`21-Figures` draws the paper's figures from `PanelContract.parquet` and `PanelQuarter.parquet`. The
geographic-diversity figure waits on a place-level release from the GPE store, which `10-ExportData`
does not yet write.
