---
title: "Story Tests -- Each Claim, One Table (21)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")

# 20 owns reg_fit(), the control sets, the dictionary and the sample rules. Sourced first so this
# document's library can extend the dictionary and every specification here is fitted by the same
# code that fitted the reproduction.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "20-RunRegression"),
  encoding = "UTF-8"
)

.name_script <- "21-StoryTests"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/21-StoryTests.R
))

# source(file = .path_fun, encoding = "UTF-8")
source(here::here("1_code", "20-RunRegression.R"), encoding = "UTF-8")
source(here::here("1_code", "21-StoryTests.R"),    encoding = "UTF-8")
```

# Purpose

This document estimates one table per claim in Section 5 of the paper. It reads the two panels
`20-RunRegression` writes and fits nothing that document does not already know how to fit; what
changes is which coefficient each table is built around.

## Reproduction and test are different jobs

`20` reproduces the submitted tables so that a port can be reconciled against them. A reproduced
table is evidence that the code is right; it is not evidence that the claim is. The draft's tables
were assembled as antecedent regressions, one per outcome, and the story is read off them
afterwards -- the three incentives sit twenty pages apart, a shift between two periods is two
columns the reader compares by eye, and the paper's direct evidence on whether the levers are
complements is a sentence beginning "untabulated results".

Here each claim is stated first, the coefficient that tests it is named, the predicted sign is
committed to, and then the table is estimated. A prediction stated before the number makes the
test falsifiable; a prediction read off the number afterwards does not.

## The claims

| | Claim | Test coefficient | Predicted |
|---|---|---|---|
| A | three incentives drive three strategies | each incentive x each outcome | competition -,+,+; loss +,+,+; growth +,-,- |
| B | loss firms cannot omit because of litigation exposure | Loss x litigation-risk industry on filing | + |
| C | competition drives redaction only under SEC review | Fluidity x Post-FAST on redaction | - |
| D | the 2004 reform pushed delayers into bundling | Share delayed x Post on voluntary items, 8-K quarters only | + |
| E | FAST shifted who redacts | each incentive x Post-FAST | leverage +, competition -, loss 0, growth 0 |
| F | redaction and delay are complements | Redacted on delay; x Post-FAST | +; 0 if complements, - if substitutes |

Claim G, on summary quality, needs the Item 1.01 text and is not here. Claim H, on contract
types, is reproduced in `20` and needs nothing.

## Two design rules every table follows

**Shifts are interactions, not split samples.** The draft shows what the FAST Act changed by
estimating before and after and comparing columns. A comparison by eye has no standard error.
Every shift here is an interaction with `PostFast`, and year-quarter fixed effects absorb the
main effect of time along with any trend.

**The 2004 test counts only quarters that have an 8-K.** A firm whose contracts sat on a 10-K has
no item count that quarter, because a 10-K has no items. Coalescing that to zero -- which the
draft did and `20` reproduces -- makes every habitual delayer look like a firm that bundled
nothing before the reform and something after it, which is the mechanical effect referee 2
described. Restricting to quarters with a contract 8-K asks the question the claim actually
makes: given an 8-K, how many voluntary items did the firm attach?

# Configuration

```{r}
#| label: config

.lP <- list(
  Input = list(
    FilQuarter  = "2_output/20-RunRegression/Output/PanelQuarter.parquet",
    FilContract = "2_output/20-RunRegression/Output/PanelContract.parquet"
  ),
  Output = list(
    DirTables = utils_file_path(.dir_main, "Tables")
  )
)
```

The panels carry the choices `20` made: naive duration, bracketed redaction, every copy. Nothing
here re-decides them. To test a claim under a different definition, change `20`'s parameter and
re-render both.

# Inputs

```{r}
#| label: input-panels

panels <- clm_read_panels(
  .path_quarter  = .lP$Input$FilQuarter,    # firm-quarter panel from 20
  .path_contract = .lP$Input$FilContract    # contract panel from 20
)
```

The samples are `20`'s, called through `20`'s functions so the rows are the same rows.

```{r}
#| label: input-samples

sample_quarter <- reg_sample_quarter(
  .quarter     = panels$quarter,
  .years       = c(2001L, 2024L),
  .same_sample = FALSE                 # the pooled population; firm-effect models drop non-varying firms themselves
)
sample_delay <- reg_sample_contract(
  .contract = panels$contract,
  .min_year = 2005L,
  .controls = .reg_controls$Full,
  .primary  = FALSE
)
sample_redact <- reg_sample_contract(
  .contract = panels$contract,
  .min_year = 2008L,
  .controls = .reg_controls$Full,
  .primary  = FALSE
)
```

# Claim A: three incentives, three strategies

The paper's frame is that proprietary cost, bad news and disclosure benefit each shape every
disclosure choice. That is one claim, and it needs one table: the three incentives as rows, the
three outcomes as columns, so the reader can see whether competition does the same thing to
filing as it does to delay.

The filing column gains competition and growth. The draft's firm-quarter specification carried
neither, so two of the three incentives were never tested on the decision to file at all.

**Predicted**: competition lowers filing and raises delay and redaction; loss raises all three, or
leaves filing unchanged; growth raises filing and lowers delay and redaction.

```{r}
#| label: claim-a-incentives

tab_incentives <- clm_table_incentives(
  .sample_quarter = sample_quarter,
  .sample_delay   = sample_delay,
  .sample_redact  = sample_redact,
  .firm_fe        = FALSE            # pooled logit; the firm-effect version is in Robustness
)
reg_report_models(.models = tab_incentives, .title = "Claim A: the three incentives, three outcomes",
                  .keep = "^(Product market|Loss|Sales growth)")
```

# Claim B: loss firms cannot omit

The story's pivot from "bad news raises the incentive to withhold" to "loss firms delay and redact
but still file" runs through litigation: non-disclosure of bad news raises exposure (Skinner 1994;
Kothari et al. 2009), and in the contract setting firms facing it accelerate rather than suppress
(Li 2013). If that is the mechanism, loss should raise filing more where litigation risk is higher.

The litigation-risk industries are Francis, Philbrick and Schipper's (1994): biotechnology,
computers, electronics, retail, software, from four-digit SIC.

**Predicted**: `Loss x LitRisk` positive on filing. No prediction on delay or redaction; those are
reported so the reader can see where the mechanism does and does not reach.

```{r}
#| label: claim-b-litigation

tab_litigation <- clm_table_litigation(
  .sample_quarter = sample_quarter,
  .sample_delay   = sample_delay,
  .sample_redact  = sample_redact
)
reg_report_models(.models = tab_litigation, .title = "Claim B: loss and litigation risk",
                  .keep = "^(Loss|Litigation)")
```

# Claims C and E: what the FAST Act changed

The draft's Table 5 shows that leverage and competition predict redaction before the FAST Act and
not after, by estimating the two periods separately. The claim is about the difference, and the
difference has no standard error in that design. Here every incentive enters twice, as a main
effect and interacted with `PostFast`, with year-quarter fixed effects absorbing the level of
time. The post-FAST effect of an incentive is its main effect plus its interaction; the shift is
the interaction alone.

Claim C is the competition row: proprietary cost drives redaction while the SEC screens requests,
and stops when redaction becomes self-executing. Claim E is the same table read across all four
rows.

**Predicted**: competition main effect positive, interaction negative and of the same size;
leverage main effect negative, interaction positive; loss and growth interactions zero.

```{r}
#| label: claim-ce-fast-shift

tab_fast <- clm_table_fast_shift(.sample = sample_redact)
reg_report_models(.models = tab_fast, .title = "Claims C and E: the FAST Act shift in who redacts",
                  .keep = "^(Product market|Loss|Sales growth|Leverage)")
```

# Claim D: the 2004 reform, cleanly

The one claim the draft tests with a natural experiment, and the one where the reproduction in
`20` flips sign against the submitted table. Three things change here.

The outcome is era-aware, so a pre-reform Item 5 is counted as the voluntary item it was. Only
firm-quarters with at least one contract on an 8-K enter; a quarter whose contracts all sat on a
10-K is absent rather than zero. And year-quarter fixed effects replace the quadratic trend, as
referee 2 asked, so `Post` is absorbed and the interaction is the only treatment coefficient.

The treatment share is still computed over all of a firm's pre-reform contracts, 10-K ones
included. "Share delayed" means the share that went to the 10-K; restricting that to 8-Ks would
define it away.

**Predicted**: `Did` positive. **If it is zero here**, the +0.426 in `20` was composition -- delayers
going from no items to some because their contracts moved from a document without items to one
with them -- and the referee's mechanical reading is correct.

```{r}
#| label: claim-d-did-clean

tab_did <- clm_table_did_clean(.contract = panels$contract)
reg_report_models(.models = tab_did, .title = "Claim D: the 2004 reform on 8-K quarters, year-quarter FE",
                  .keep = "^(Share|Post)")
```

# Claim F: are the levers complements?

Section 5.1 sets this up as the empirical question: a redacting firm has extra reason to lower
awareness of the contract, so redaction and delay should travel together; but if they are
substitutes, a firm that can redact cheaply needs delay less. The draft answers in one untabulated
sentence -- positive both periods, smaller after FAST. That is the direct evidence on the paper's
framing and it belongs in a table.

**Predicted**: `Redacted` positive on delay. The interaction with `PostFast` is the test between the
two readings: zero means complements throughout; negative means substitution at the margin once
redaction became cheap.

```{r}
#| label: claim-f-complements

tab_complements <- clm_table_complements(.sample = sample_redact)
reg_report_models(.models = tab_complements, .title = "Claim F: redaction and delay",
                  .keep = "^Redacted")
```

# Validation

The claims were stated with their predictions before any of the tables above were estimated. This
reads each test coefficient back and says whether it confirms. A claim absent from the scorecard
was not tested; a claim marked "does not" is one the paper has to rewrite or drop.

```{r}
#| label: validation-scorecard

scorecard <- clm_report_scorecard(
  .inc  = tab_incentives,
  .lit  = tab_litigation,
  .fast = tab_fast,
  .did  = tab_did,
  .comp = tab_complements
)
```

# Robustness

Claim A with the firm effect absorbed. The pooled logit compares firms; this compares each firm's
quarters or contracts to its own. Loss and growth are within-firm variables and should survive;
competition is mostly between-firm and may not, which would itself be informative.

```{r}
#| label: robustness-incentives-firm-fe

tab_incentives_fe <- clm_table_incentives(
  .sample_quarter = sample_quarter,
  .sample_delay   = sample_delay,
  .sample_redact  = sample_redact,
  .firm_fe        = TRUE
)
reg_report_models(.models = tab_incentives_fe, .title = "Claim A with firm effects",
                  .keep = "^(Product market|Loss|Sales growth)")
```

# Deployment

```{r}
#| label: deploy-tables

tex_ <- function(.name) fs::path(.lP$Output$DirTables, paste0(.name, ".tex"))

reg_tex(.models = tab_incentives,    .path = tex_("claim_a_incentives"),    .title = "Three incentives, three outcomes")
reg_tex(.models = tab_incentives_fe, .path = tex_("claim_a_incentives_fe"),
        .title = "Three incentives, firm effects")
reg_tex(.models = tab_litigation,    .path = tex_("claim_b_litigation"),    .title = "Loss and litigation risk",
        .keep = "^(Loss|Litigation)")
reg_tex(.models = tab_fast,          .path = tex_("claim_ce_fast_shift"),
        .title = "The FAST Act shift in who redacts", .keep = "^(Product market|Loss|Sales growth|Leverage)")
reg_tex(.models = tab_did,           .path = tex_("claim_d_did_clean"),     .title = "The 2004 reform on 8-K quarters",
        .keep = "^(Share|Post)")
reg_tex(.models = tab_complements,   .path = tex_("claim_f_complements"),   .title = "Redaction and delay",
        .keep = "^Redacted")

readr::write_csv(scorecard, fs::path(.lP$Output$DirTables, "scorecard.csv"))
cli::cli_alert_success("wrote {.file scorecard.csv}")
```

# Overview

```{r}
#| label: overview-scorecard

tbl_out(scorecard, .title = "Scorecard", .digits = 3L)
```

# Next

`22-Omission`, if built, would test the lever the story leads with and concedes is unobservable:
an Item 1.01 announcement in `01D` whose exhibit never appears in `02B`'s register, on the 8-K or
the next two periodic reports, is an observed omission.
