---
title: "Descriptives -- The Paper's Tables and Figures, from the Release (30)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# THE COMMONS FIRST. _Plots.R rebuilds its level registry empty every time it is sourced, so every
# library that registers a vocabulary must follow it: 03A registers the taxonomy, this file registers
# the paper's order of it and the form families.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# TWO UPSTREAM LIBRARIES, FOR THREE THINGS. 03A owns the class vocabulary and the check that the data
# carries it. 10 owns exp_cache_hit(), the modification-time rule every cache in the monorepo obeys,
# and the column-by-column report used on every table read below.
.path_libs <- c(
  .path_libs,
  purrr::map_chr(
    c("03A-ClassifyPrepare", "10-ExportData"),
    \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s)
  )
)
purrr::walk(.x = utils::tail(.path_libs, 2L), .f = \(.p) source(file = .p, encoding = "UTF-8"))

.name_script <- "30-Descriptives"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document produces the descriptive half of the paper -- the sample table, the filing and content
figures, the firm-level and redaction descriptives, the summary comparison -- from the files
Ann-Kristin's Stata analysis reads. It estimates nothing. The regressions stay in her `106` and in
`20-RunRegression`.

## One source, and it is hers

Every input is a file under her `MatContractPipeline` folder: the two releases `10-ExportData` deploys
there, and the outputs of her `101` and `103` do-files. Where the input is a `.dta` it is converted once
to parquet under this document's `Cache` and read from there; the conversion is keyed on the `.dta`'s
modification time, through the same `exp_cache_hit()` rule `10` applies to its own caches, so her
re-running `103` rebuilds the cache here on the next render and nothing else. What this buys is that a
number in this document and a number in one of her tables come from the same bytes, and a difference
between them is a difference in definition rather than in data.

Two things are deliberately **not** rebuilt. The Compustat variables -- size, leverage, the
Herfindahls, the winsorising -- are read from her quarter panel as `103` computed them, because Table 4
has to show the values her regressions control for. And the sample ladder is read from
`Contracts.parquet`, where `02B` wrote it, rather than re-derived.

## One exhibit at a time

The document reads, derives, names the samples and validates first. Each exhibit of the specification
is then added as one compute function returning a tibble, one render function drawing or typesetting
it, and one report function printing its headline numbers beside the manuscript's; the tibble is what
goes to disk, and it is enough to redraw the figure without the data behind it. Every exhibit is drawn
on more than one sample -- the paper's, and the ones beside it on the ladder -- so what the ladder
does to a picture is on the page rather than assumed. The Overview at the end holds every figure, one
tabset per exhibit, one tab per sample.

## Definitions are switches

Four measures the paper uses have more than one candidate in the release, and the specification lists
them as open questions. They are arguments to `des_read_contracts()` with the current manuscript's
choice as default: redaction is `Symbol + Explicit` markers with one marker enough, which is `103`'s
rule and reproduces Figure 10; duration is the cascade `DurationYears`, which reproduces Table 3;
words are `nWordsAdj`, the 8,825 the text prints; parties are the recital parties. Flipping one is one
edit in Configuration, and the Robustness section, when it exists, flips them one at a time.

# Configuration

```{r}
#| label: configure

.lP <- list(
  # WHERE HER FOLDER IS. The Dropbox root on this machine; ~/Downloads/Pipeline is a copy with the same
  # layout and works as a drop-in while Dropbox is offline.
  Root = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Redaction = "symbolexplicit",   # 103's nRedact; "bracketed" is 20's default, "withheld", "money"
    RedactMin = 1L,                 # markers needed to count as redacted by text; the notes say 5, 103 says 1
    Duration  = "cascade",          # DurationYears, as Table 3 of the revision; "naive" is NaiveYears
    Words     = "adjusted",         # nWordsAdj, the 8,825 in the text; "raw" is nWords
    Parties   = "recital"           # registrant + co-filers + counterparties; "counterparty"; "spellings"
  )
)

.lP$Input <- list(
  FilContracts     = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),
  FilSummaries     = fs::path(.lP$Root, "100_Data_Export", "Summaries.parquet"),
  # HER FIRM-QUARTER PANEL, every Compustat quarter of a firm that filed at least once, with the
  # winsorised variables. Two and a half gigabytes as .dta; the conversion keeps 36 columns.
  DtaQuarter       = fs::path(.lP$Root, "103_Variable_Creation", "103_Output",
                              "quarter_dictionary_COMPUSTAT_variables.dta"),
  # HER CONTRACT-LEVEL FILE, read for seven columns: her sample flag and her redaction indicators, so
  # that the two sides can be reconciled row by row rather than by their totals.
  DtaAkContract    = fs::path(.lP$Root, "103_Variable_Creation", "103_Output",
                              "full_dictionary_contract_level_AK.dta"),
  # SEGMENT CONCENTRATION AND DIVERSITY, one row per gvkey-year, as 101 computed it. Figure 7.
  DtaConcentration = fs::path(.lP$Root, "101_Data_prep", "101_Output", "concentration.dta")
)

.lP$Cache <- list(
  CacheQuarter       = utils_file_path(.dir_main, "Cache", "Quarter.parquet"),
  CacheAkContract    = utils_file_path(.dir_main, "Cache", "AkContract.parquet"),
  CacheConcentration = utils_file_path(.dir_main, "Cache", "Concentration.parquet")
)

.lP$Output <- list(
  DirData    = utils_file_path(.dir_main, "Output", "Data"),
  DirFigures = utils_file_path(.dir_main, "Output", "Figures"),
  DirTables  = utils_file_path(.dir_main, "Output", "Tables")
)

purrr::walk(.x = unlist(.lP$Output), .f = fs::dir_create)

des_report_inputs(.inputs = unlist(.lP$Input))
```

Two inputs the specification names are **not** on her side and are not read yet: the `04D` GPE store,
which Figure 6's maps need because the export carries counts and not names, and `05A`'s term hits for
the pandemic check referee 2 asked for. Both are repository outputs and both wait on the exhibit
decisions; when they come in they are added here, under `.lP$Repo`, with the same existence report.

# Input

## Conversion

The three `.dta` files, converted once. Each call names the columns it keeps and what they are called
from here on; a column she renames is reported by name before anything is read.

```{r}
#| label: input-convert

des_convert_dta(
  .path_dta = .lP$Input$DtaQuarter,          # 103's quarter panel
  .path_out = .lP$Cache$CacheQuarter,
  .cols     = .des_quarter_cols,             # 36 columns: keys, counts, the regression variables
  .rerun    = FALSE                          # TRUE reconverts regardless of timestamps
)

des_convert_dta(
  .path_dta = .lP$Input$DtaAkContract,       # her contract-level file
  .path_out = .lP$Cache$CacheAkContract,
  .cols     = .des_ak_contract_cols,         # seven columns, reconciliation only
  .rerun    = FALSE
)

des_convert_dta(
  .path_dta = .lP$Input$DtaConcentration,    # 101's segment concentration
  .path_out = .lP$Cache$CacheConcentration,
  .cols     = NULL,                          # small; every column under its Stata name
  .rerun    = FALSE
)
```

## The contract table

Every row of `Contracts.parquet`, ladder step 1 included, with the derived columns and the four
switches applied. Nothing is filtered here: the samples are named in the next section, where the
filters are on the page.

```{r}
#| label: input-contracts

tab_contracts <- des_read_contracts(
  .path       = .lP$Input$FilContracts,
  .redaction  = .lP$Params$Redaction,   # which marker kinds count
  .redact_min = .lP$Params$RedactMin,   # how many of them
  .duration   = .lP$Params$Duration,    # cascade or naive
  .words      = .lP$Params$Words,       # adjusted or raw
  .parties    = .lP$Params$Parties      # recital, counterparty or spellings
)
```

```{r}
#| label: input-contracts-vocabulary

# THE VOCABULARY COVERS THE DATA, both ways. A label in the file this document does not know would
# become a missing factor level and leave every class figure silently; a registered class no contract
# carries is a taxonomy that has drifted from its data. 03A's check reports both.
clf_report_vocabulary(
  .tab = tab_contracts |>
    dplyr::filter(.data$Keep) |>
    dplyr::rename(ClassDetailed = "Class")   # 03A's check reads the three task columns by their registry keys
)

stopifnot(setequal(
  setdiff(unique(tab_contracts$Class), NA),
  .des_class_levels
))
cli::cli_alert_success("{length(.des_class_levels)} contract types in the file, all known to this document")
```

```{r}
#| label: input-contracts-report

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = dplyr::filter(tab_contracts, .data$Keep)),
  .title = "The descriptive sample, column by column",
  .notes = c(Mean = "Indicator columns read as shares. The marker counts are coalesced to zero, so their
                     means are corpus rates rather than rates among marked contracts.")
)
```

## The announcements

```{r}
#| label: input-summaries

tab_summaries <- des_read_summaries(
  .path          = .lP$Input$FilSummaries,
  .tab_contracts = tab_contracts          # for the number of exhibits on each 8-K
)
```

## The firm-quarter panel and the segment file

```{r}
#| label: input-quarter

tab_quarter <- des_read_quarter(.path = .lP$Cache$CacheQuarter)

exp_report_numeric(
  .tab   = exp_table_numeric(.tab = tab_quarter),
  .title = "The quarter panel, column by column",
  .notes = c(NonMiss = "Every variable as 103 winsorised it. A count below the row total on a control is
                        the missing-data step of Table 2 Panel B in the making.")
)
```

```{r}
#| label: input-concentration

tab_concentration <- des_read_concentration(.path = .lP$Cache$CacheConcentration)
```

## Her contract-level flags, joined

```{r}
#| label: input-ak-contract

tab_ak <- des_read_ak_contract(.path = .lP$Cache$CacheAkContract)

exp_check_collide(.a = names(tab_contracts), .b = names(tab_ak), .by = "DocID", .what = "the reconciliation join")

tab_contracts <- dplyr::left_join(tab_contracts, tab_ak, by = dplyr::join_by(DocID), relationship = "one-to-one")

cli::cli_alert_info(
  "{format(sum(!is.na(tab_contracts$AkKeep)), big.mark = ',')} of {format(nrow(tab_contracts), big.mark = ',')} \\
   rows have a counterpart on her file; the rest are ladder step 1, which her 102 drops."
)
```

# Samples

The filters are written out because they are the sample definition of every exhibit that follows.
Each contract-level sample is a logical column on the contract table, so an exhibit's samples are
named at its call site and cost no memory; the announcement and quarter samples are their own tables.

```{r}
#| label: samples-define

# A SAMPLE IS A COLUMN, NOT A COPY. Each contract-level sample is one logical column on the contract
# table, and an exhibit is drawn on a sample by filtering on the column of that name. The filters are
# the sample definitions and are written here, once, in ladder order.
tab_contracts <- tab_contracts |>
  dplyr::mutate(
    # S00: every row of the release, ladder step 1 included. The one sample the manuscript never
    # shows; it is here so that what the 2001-2024 window removes is a tab rather than a sentence.
    S00_Edgar       = TRUE,
    # S0: every row at ladder steps 2-6, every copy. What the paper calls the full sample.
    S0_Universe     = .data$SampleStepCode >= 2L,
    # S1: one row per attachment, whatever its ladder step.
    S1_Unique       = .data$PrimaryFiler == 1L,
    # S2: the descriptive sample. Inside the window, well-formed, one copy per attachment.
    S2_Descriptive  = .data$Keep,
    # S2s: the descriptive sample restricted to seasoned filers, contracts filed more than two years
    # after the filer's first one in S2. 104_SPAC.do's definition; Online Appendix Figure C2's sample.
    S2s_Seasoned    = .data$Keep & .data$IsSeasoned == 1L,
    # S3: S2 with a matched Compustat quarter, which is what any firm-level exhibit needs. The two
    # rungs beneath it start where the paper's contract-level tables start: 2005 for delay, 2008 for
    # redaction, the years the 8-K item reform and the first published orders make the variables
    # observable.
    S3_Matched      = .data$Keep & .data$Matched,
    S3a_Matched2005 = .data$Keep & .data$Matched & .data$Year >= 2005L,
    S3b_Matched2008 = .data$Keep & .data$Matched & .data$Year >= 2008L,
    # S6: the redaction window on the descriptive sample, matched or not. Orders are observable from
    # 2008; Figure 10 is drawn here.
    S6_Redaction    = .data$Keep & .data$Year >= 2008L
  )

# THE CONTRACT-LEVEL SAMPLES, in ladder order: what every contract-grain exhibit is drawn on unless it
# names a subset.
.des_contract_samples <- c(
  "S00_Edgar", "S0_Universe", "S1_Unique", "S2_Descriptive", "S2s_Seasoned", "S3_Matched", "S3a_Matched2005",
  "S3b_Matched2008", "S6_Redaction"
)

# THE REDACTION SAMPLES: those in which the redaction variables exist. Orders are observable from 2008,
# so the samples that start earlier are drawn from 2008 within, and S00, S0 and S1 -- which carry
# malformed rows and co-filer copies the redaction extraction never saw -- are left out.
.des_redaction_samples <- c("S2_Descriptive", "S2s_Seasoned", "S3_Matched", "S3b_Matched2008", "S6_Redaction")

# THE TWO SAMPLES THAT ARE NOT CONTRACT TABLES.
lst_other <- list(
  # S7: single-agreement announcements on 8-Ks carrying at most one Exhibit 10, attached or not.
  S7_Summaries = dplyr::filter(tab_summaries, .data$SumIsSingle == 1L, .data$nExhibits <= 1L),
  # S5: her firm-quarter panel inside the window. 103 leaves 1997-2026 on the file and every do-file
  # drops year_fe outside 2001-2024 at the point of use; here it is dropped once. The regression-sample
  # restriction -- every control present, never-filers dropped -- is applied where Table 4 is built.
  S5_Quarter   = dplyr::filter(tab_quarter, dplyr::between(.data$cyear, 2001L, 2024L))
)

tab_ladder  <- des_table_ladder(.tab = tab_contracts)
tab_steps   <- des_table_steps(.tab = tab_contracts)
tab_samples <- des_table_samples(.tab = tab_contracts, .samples = .des_contract_samples, .others = lst_other)

des_report_samples(.tab_ladder = tab_ladder, .tab_steps = tab_steps, .tab_samples = tab_samples)
```

S4, the contract panel with every control present, is not built here because it is what
`20-RunRegression` writes and what her `106` estimates on; the descriptives that need it -- Table 2
Panel B, Figure 7, Figure 9 -- will take it from `20`'s `PanelContract.parquet` or build the same join
from `S3_Matched` and `S5_Quarter`, whichever the exhibit discussion settles on.

# Validation

Three checks, each stated before it is read.

**Table 2 Panel A reproduces exactly.** The revision's 1,436,667 / 31,289 / 269,283 / 1,136,095 and
43,123 / 26,915 firms are the ladder columns counted, or the file on Dropbox is not the one the table
came from. This aborts on any difference; there is no tolerance because there is no rounding.

**One copy per attachment is not the same copy on both sides.** Her `Keep` is the first row per
`HashDocument`; this document's is `PrimaryFiler`. Both give 1,136,095. Where they differ, a contract
is attributed to a different registrant or form in her figures than here, and the count of such
contracts is what decides whether that matters.

**The redaction flags agree row by row from 2008.** With the default switches this document applies
`103`'s rule, so `Redacted` and `RedactedText` must equal her `redacted` and `redacted_text` on every
contract in the descriptive sample. Before 2019 the flag is the confidential-treatment order, and a
disagreement there is `HasCto` differing between the release this reads and the one her `102` last
ran on -- the September relinking of orders moved a few hundred contracts. From 2019 the flag is the
markers, and a disagreement there is the marker rule itself. The cross-tabulation is split by era so
the two cannot be confused.

```{r}
#| label: validation-reference

des_check_reference(.tab_ladder = tab_ladder, .ref = .des_reference)
```

```{r}
#| label: validation-copies

des_check_copies(.tab = tab_contracts)
```

```{r}
#| label: validation-redaction

des_check_redaction(
  .tab          = tab_contracts,
  .path_release = .lP$Input$FilContracts,    # dated, so a release gap is named as one
  .path_hers    = .lP$Input$DtaAkContract
)
```

```{r}
#| label: validation-summaries

des_check_summaries(.tab_summaries = tab_summaries)
```

# Filing characteristics

Every exhibit from here on follows one pattern: a compute function returns a tibble carrying a
`Sample` column, a report function prints its headline numbers beside whatever the manuscript
printed, and the figure is drawn from the tibble alone, once per sample, in the Overview. The samples
an exhibit is drawn on are named at its call site.

## Figure 1: distribution of filing types

Contracts by the form they arrived in, US and foreign forms side by side, each bar split into
original agreements and amendments, with the form's share of the sample above it. The manuscript
draws it on S2; here it is drawn on every contract-level sample, from every row of the release down
to the matched contracts from 2008, so what each rung of the ladder does to the picture is a tab
rather than a sentence.

An unlabelled contract keeps its bar as a third, grey segment. On S2 that is 735 contracts and
invisible; on S0 it is the malformed rows, which never reached the classifier, and it shows where
they sit.

```{r}
#| label: f01-data

tab_f01 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,   # every contract-level sample, ladder order
  .fun     = des_data_f01
)

des_report_f01(.tab_data = tab_f01, .ref = .des_reference_f01)
```

Between S0 and S2 the shares move in one place, and it is the right place: S-4 and F-4 carry 13.2 and
4.3 percent of every copy against 2.3 and 0.4 percent of unique contracts. A merger registration
statement names every registrant to the combination, so its exhibits are repeated once per registrant
in the register, and the co-filer fan-out lands almost entirely on the two merger forms. That is the
one-figure case for counting attachments rather than copies. Between S2 and S3 the registration
statements lose weight again -- S-1 from 13.1 to 10.6 percent -- because a firm filing an S-1 is, as
often as not, a firm Compustat does not cover yet, which every firm-level section below inherits.

## Figure 2: filings over time

Each year's contracts split by filing group, shares stacked to one, with the year's total above them.
The manuscript overlays the total as a line on a second axis; two scales on one panel are arbitrary
relative to each other, so the total gets a short panel of its own sharing the year axis. Two
groupings from one tibble: the paper's three, where the registration statements sit inside ad-hoc,
and four, where they stand alone. The four-group version is the one that can answer referee 2's
question about 2020 and 2021, because the rise is theirs. Both regime dates are marked.

```{r}
#| label: f02-data

tab_f02 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,
  .fun     = des_data_f02
)

des_report_f02(.tab_data = tab_f02)
```

Two numbers the text carries are wrong against the release and the reconciliation shows which way.
The 2021 peak is 59,969 contracts on S2, not "around 80 thousand"; and the ad-hoc share after the
reform is 60 percent only when registration statements are counted in it -- 8-Ks alone are 40 to 45
percent of every year from 2005. In 2021 the registration share reaches 36 percent against 17 the
year before, and on the seasoned-filer sample 2021 has 28,249 contracts against 29,332 in 2020: the
spike is new registrants, and it is entirely in the forms new registrants file.

# Content

## Figure 3: contract types

Panel A is each type's count and share of the sample; Panel B is contracts per firm-year of that
type, over the firm-years in which the firm filed at least one of it. Same twelve rows, same order,
in both panels, as referee 1 asked.

```{r}
#| label: f03-data

tab_f03 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,
  .fun     = des_data_f03
)

des_report_f03(.tab_data = tab_f03, .ref = .des_reference_f03)
```

Every S2 share matches the revision's label to two decimals. Across samples the shares are stable to
within two points except for Other, which is 5.6 percent of every copy and 3.4 percent of unique
contracts: the malformed rows and the co-filer copies are disproportionately the residual class.

## Figure 4: contract types over time

Each year's contracts by type, shares stacked, with the year's amendment share drawn over them; and
the same shares as twelve small multiples, which is the Online Appendix C figure in a form where
twelve series can be told apart. The seasoned-filer tab is Online Appendix Figure C2.

```{r}
#| label: f04-data

tab_f04 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,
  .fun     = des_data_f04
)

des_report_f04(.tab_data = tab_f04)
```

The amendment share is 28 to 31 percent in every year but 2009 (38) and 2021 (22), on every sample;
the text's "about 20 percent" predates the reclassification. The equity share is the seasoned-filer
argument in one row: 23.8 percent of all 2021 contracts, 11.0 percent of seasoned filers' -- flat
against 10.8 the year before -- so the 2021 rise in equity agreements is entirely new registrants.

## Figure 5: content characteristics over time

Mean and median per year of the four content measures under the switches in Configuration: the
cascade duration, countries outside governing-law clauses, recital parties, adjusted words.

```{r}
#| label: f05-data

tab_f05 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,
  .fun     = des_data_f05
)

des_report_f05(.tab_data = tab_f05, .ref = .des_reference_f05)
```

Words and duration reproduce the text (8,825 and 2.79 on S2). Parties and countries do not, and
should not: the text's 2.94 and 1.9 are the old extractor's. The recital-party count is 2.28 and the
country count 2.08, and both are the numbers the manuscript's sentence is rewritten from.

## Table 3: length and duration by type

Words and duration by type with N, mean, SD and quartiles; and a third panel, which referee 2 asked
for from Table 3 onward, giving the share redacted by type before and after the FAST Act.

```{r}
#| label: t03-data

tab_t03 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_contract_samples,
  .fun     = des_data_t03
)

des_report_t03(.tab_data = tab_t03, .ref = .des_reference_t03)
```

Panels A and B reproduce revision 1 row by row on S2 -- Credit 17,437 words, Leases 4.24 years,
Total 2.79 (SD 3.28) on 779,440. Panel C is where referee 2's two literatures separate on one page:
R&D and Licenses are redacted in 42 and 31 percent of pre-FAST contracts and 70 and 55 percent after,
against 1.3 and 7.9 percent for Credit.

# Redactions

## Figure 10: redactions over time

The share of contracts redacted per year from 2008, three ways: by the order alone, which ends in
2019; by the markers alone; and by the union, which is the paper's "RegEx identification" line.
Drawn on the samples in which the redaction variables exist.

```{r}
#| label: f10-data

tab_f10 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_redaction_samples,
  .fun     = des_data_f10
)

des_report_f10(.tab_data = tab_f10, .ref = .des_reference_f10)
```

The S6 series are the revision's figure to the decimal. The marker-only line is the one the figure
has never shown, and it is the one that makes the pre-FAST period readable: markers alone find 2.7
to 4.6 percent of contracts in 2008-2018 against 2.2 to 3.8 with an order, so the text-based
identification was already picking up most of what the orders certified before it had to.

## Appendix Figure F1: redaction share by type

```{r}
#| label: ff1-data

tab_ff1 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_redaction_samples,
  .fun     = des_data_ff1
)

des_report_ff1(.tab_data = tab_ff1)
```


# Summaries

## Table 7: Item 1.01 summaries, delayed against attached

Nine measures of the announcement narrative by whether the contract rode on the 8-K: the paper's six,
and the boilerplate share, the announcement lag and the four-business-day compliance the export added.
Delayed less attached, Welch t. Drawn on the paper's sample -- single-agreement announcements on 8-Ks
with at most one exhibit -- and on every announcement, to show what the restriction does.

```{r}
#| label: t07-data

lst_other$S7_All <- tab_summaries   # every announcement, the restriction lifted

tab_t07 <- purrr::imap(lst_other[c("S7_Summaries", "S7_All")], \(.s, .n) des_data_t07(.tab = .s, .sample = .n)) |>
  purrr::list_rbind()

des_report_t07(.tab_data = tab_t07, .ref = .des_reference_t07)
```

Every difference the paper reports keeps its sign on the release: delayed summaries are longer, more
uncertain, and carry fewer numbers. The levels move -- the Fog index is four points lower under the
export's implementation -- and Table 7 in the revision is the old pipeline's, so this is the table
that replaces it rather than confirms it.

## Announcement compliance by year

```{r}
#| label: t07b-data

tab_t07b <- purrr::imap(lst_other[c("S7_Summaries", "S7_All")], \(.s, .n) des_data_t07b(.tab = .s, .sample = .n)) |>
  purrr::list_rbind()

tab_t07b |>
  dplyr::filter(.data$Sample == "S7_Summaries") |>
  dplyr::mutate(Share = 100 * .data$Share) |>
  dplyr::select("Year", "Group", "Share") |>
  tidyr::pivot_wider(names_from = "Group", values_from = "Share") |>
  des_fmt(1L) |>
  tbl_out(.title = "Announcements within four business days of the agreement date, percent, by year")
```

# Sample composition

## Table 1: agreement titles by type

The filer's own exhibit description, normalised to a title, counted within type. The eight most
frequent per type are the representative agreements referee 2 asked for, and beside them the share
of the type on which the keyword lexicon fired and agreed with the classifier.

```{r}
#| label: t01-data

tab_t01 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = c("S2_Descriptive", "S3_Matched"),
  .fun     = des_data_t01,
  .top     = 8L
)

des_print_t01(.tab_data = des_slice(tab_t01, "S2_Descriptive"))
```

## Confidential treatment, the contract side

What the release says about the orders: contracts covered, extensions, orders per contract, and the
orders against the markers. The order-side counts -- orders issued, exhibits named, exhibits that
could not be linked -- are 01E's and wait for the export to carry them.

```{r}
#| label: cto-data

tab_cto <- des_over_samples(
  .tab     = tab_contracts,
  .samples = .des_redaction_samples,
  .fun     = des_data_cto
)

des_report_cto(.tab_data = tab_cto)
```

## Where the ladder loses attachments

```{r}
#| label: loss-data

tab_loss <- des_data_loss(.tab = tab_contracts, .sample = "S0_Universe")

des_report_loss(.tab_data = tab_loss)
```

## Within the calendar year

```{r}
#| label: fa1-data

tab_fa1 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = c("S2_Descriptive", "S3_Matched"),
  .fun     = des_data_fa1
)

des_report_fa1(.tab_data = tab_fa1)
```

## Table 2 Panel B: the estimation ladder

The panel marked "Update from here" in the revision, counted from the ladder and the quarter panel:
every copy at steps 2-6, less the malformed, less the CIKs Compustat does not cover, less the copies
with no fiscal quarter, less the rows whose quarter is missing a control. Missing data is defined on
the full control set the contract-level tables use, and again on the shorter filing-decision set.
The two firm-level rows are Table 4's samples, built the way her `105` builds them.

```{r}
#| label: t02b-data

lst_ladder_b <- des_report_ladder_b(.tab = tab_contracts, .quarter = tab_quarter)
```

# Firm level

## Table 4: filing against non-filing firm-quarters

Her quarter panel inside the window, on two samples built step for step as her `105` builds them:
the regression sample -- her `105` control set present (the filing-decision controls plus the
Herfindahl and the one-quarter sales change), the fiscal quarter, the industry and the state on the
row, every state in which filing never varies dropped (`105` hard-codes it as state 36; here it is
the rule, so it holds on any release), and firms that never file inside what is left dropped, firms
being CIKs as in `105` -- and that sample after the firm-effect trimming, which drops every firm whose
filing never varies, overall or within either FAST period. The trimmed sample is the one the revision's
table counts. Market-to-book and fluidity, which referee 2 asked about, are rows; fluidity is missing
on two quarters in five, which is why it is a row here and not a control.

```{r}
#| label: t04-data

tab_q <- des_quarter_samples(.quarter = lst_other$S5_Quarter, .controls = .des_controls$Filing)   # her 105's set

tab_t04 <- purrr::map(c("T4_Regression", "T4_Trimmed"), \(.s) {
  des_data_t04(.tab = tab_q[tab_q[[.s]], , drop = FALSE], .sample = .s)
}) |>
  purrr::list_rbind()

des_report_t04(.tab_data = tab_t04, .ref = .des_reference_t04)
```

## Figure 8: filing metrics by firm fundamentals

Panel A takes the size quartiles within fiscal year and the channel counts from the contract table,
so that registration statements are a channel of their own rather than folded into current reports.
Panel B is the mean over every firm-quarter in the window, filing or not, by industry.

```{r}
#| label: f08-data

tab_channel <- des_channel_counts(.tab = tab_contracts, .sample = "S3_Matched")

tab_f08a <- des_data_f08a(.tab = lst_other$S5_Quarter, .sample = "S5_Quarter", .counts = tab_channel)
tab_f08b <- des_data_f08b(.tab = lst_other$S5_Quarter, .sample = "S5_Quarter")

des_report_f08(.tab_a = tab_f08a, .tab_b = tab_f08b, .ref = .des_reference_f08)
```

## Figure 9: redaction by industry and type

```{r}
#| label: f09-data

tab_f09 <- des_over_samples(
  .tab     = tab_contracts,
  .samples = c("S3_Matched", "S3b_Matched2008"),
  .fun     = des_data_f09,
  .quarter = tab_quarter
)

des_report_f09(.tab_data = tab_f09)
```

## Figure 7: geographic diversity

```{r}
#| label: f07-data

tab_f07 <- dplyr::bind_rows(
  des_data_f07(.tab = tab_contracts[tab_contracts$S3_Matched, , drop = FALSE], .sample = "S3_Matched",
               .conc = tab_concentration, .grain = "mean"),
  des_data_f07(.tab = tab_contracts[tab_contracts$S3_Matched, , drop = FALSE], .sample = "S3_AK",
               .conc = tab_concentration, .grain = "first")
)

des_report_f07(.tab_data = tab_f07, .ref = .des_reference_f07)
```


# Deployment

Every exhibit's tibble to `Output/Data/`, one parquet per exhibit with every sample inside it, and
every figure to `Output/Figures/`, one file pair per sample, drawn by the exhibit's own plot function.

```{r}
#| label: deploy-f01

des_save_data(.tab_data = tab_f01, .name = "F01", .dir = .lP$Output$DirData)

des_save_figures(
  .tab_data = tab_f01,
  .fun      = des_plot_f01,
  .name     = "F01",
  .dir      = .lP$Output$DirFigures,
  .height   = plot_height(8L)      # eight forms across two panels: the Medium rung
)
```

```{r}
#| label: deploy-batch

# ONE LINE PER EXHIBIT AND VIEW. The height is the ladder rung the figure's rows put it on; the two
# stacked-panel figures take the Large rung, the small-multiple figures a derived height.
purrr::pwalk(
  list(
    tab  = list(tab_f02, tab_f02, tab_f03, tab_f04, tab_f04, tab_f05, tab_f10, tab_ff1),
    fun  = list(des_plot_f02, des_plot_f02b, des_plot_f03, des_plot_f04, des_plot_f04b, des_plot_f05,
                des_plot_f10, des_plot_ff1),
    name = c("F02", "F02b", "F03", "F04", "F04b", "F05", "F10", "FF1"),
    h    = c(plot_height(12L), plot_height(12L), plot_height(12L), plot_height(12L), plot_height(18L),
             plot_height(12L), plot_height(5L), plot_height(18L))
  ),
  \(tab, fun, name, h) des_save_figures(.tab_data = tab, .fun = fun, .name = name, .dir = .lP$Output$DirFigures,
                                       .height = h)
)

purrr::walk(
  list(tab_f02, tab_f03, tab_f04, tab_f05, tab_t03, tab_f10, tab_ff1) |>
    purrr::set_names(c("F02", "F03", "F04", "F05", "T03", "F10", "FF1")) |>
    names(),
  \(n) des_save_data(.tab_data = get(paste0("tab_", tolower(n))), .name = n, .dir = .lP$Output$DirData)
)

# TABLE 3 AS TEX, three files per sample.
purrr::walk(
  unique(tab_t03$Sample),
  \(s) des_tex_t03(.tab_data = des_slice(tab_t03, s), .sample = s, .dir = .lP$Output$DirTables)
)
```

```{r}
#| label: deploy-batch-b

purrr::pwalk(
  list(
    tab  = list(tab_t07b, tab_fa1, tab_f08a, tab_f08b, tab_f09, tab_f07),
    fun  = list(des_plot_t07b, des_plot_fa1, des_plot_f08a, des_plot_f08b, des_plot_f09, des_plot_f07),
    name = c("T07b", "FA1", "F08a", "F08b", "F09", "F07"),
    h    = c(plot_height(5L), plot_height(8L), plot_height(8L), plot_height(12L), plot_height(12L, .square = TRUE),
             plot_height(8L))
  ),
  \(tab, fun, name, h) des_save_figures(.tab_data = tab, .fun = fun, .name = name, .dir = .lP$Output$DirFigures,
                                       .height = h)
)
plot_save(.plot = des_plot_loss(.tab_data = tab_loss), .name = "LOSS_S0_Universe", .dir = .lP$Output$DirFigures,
          .height = plot_height(8L))

purrr::iwalk(
  list(T07 = tab_t07, T07b = tab_t07b, T01 = tab_t01, CTO = tab_cto, LOSS = tab_loss, FA1 = tab_fa1,
       T02B = dplyr::bind_rows(Full = lst_ladder_b$Full, Quarter = lst_ladder_b$Quarter, .id = "Controls"),
       T04 = tab_t04, F08a = tab_f08a, F08b = tab_f08b, F09 = tab_f09, F07 = tab_f07),
  \(t, n) des_save_data(.tab_data = t, .name = n, .dir = .lP$Output$DirData)
)

tex_ <- function(.tab, .fun) {
  purrr::walk(unique(.tab$Sample), \(s) .fun(.tab_data = des_slice(.tab, s), .sample = s, .dir = .lP$Output$DirTables))
}
tex_(tab_t07, des_tex_t07)
tex_(tab_t01, des_tex_t01)
tex_(tab_t04, des_tex_t04)

des_manifest(
  .dirs = c(Data = .lP$Output$DirData, Figures = .lP$Output$DirFigures, Tables = .lP$Output$DirTables),
  .path = utils_file_path(.dir_main, "Output", "Manifest.csv")
)
```

# Overview

## Figure 1

Eight tabs, one per contract-level sample, generated from the same tibble the report above read. The
chunk labels the child carries are `fig-f01-<sample>`, so each figure file is named for its sample.

```{r}
#| label: fig-f01-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f01",            # the exhibit tibble, by name
  .fun_name = "des_plot_f01",       # its plot function, by name
  .id       = "f01",                # chunk-label stem
  .height   = plot_height(8L),      # eight forms across two panels: the Medium rung
  .caption  = "Contracts by form, original and amended, with the form's share of the sample above each bar.",
  .samples  = NULL                  # every sample in the tibble, ladder order
)
```

## Figure 2

Three groups, as the paper draws it.

```{r}
#| label: fig-f02-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f02", .fun_name = "des_plot_f02", .id = "f02", .height = plot_height(12L),
  .caption  = "Contracts per year (top) and their split into ad-hoc, yearly and quarterly filings.",
  .samples  = NULL
)
```

Four groups: registration statements on their own.

```{r}
#| label: fig-f02b-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f02", .fun_name = "des_plot_f02b", .id = "f02b", .height = plot_height(12L),
  .caption  = "Contracts per year (top) and their split into 8-K, registration, yearly and quarterly filings.",
  .samples  = NULL
)
```

## Figure 3

```{r}
#| label: fig-f03-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f03", .fun_name = "des_plot_f03", .id = "f03", .height = plot_height(12L),
  .caption  = "Contracts by type: count with the type's share (left) and contracts per firm-year of the type (right).",
  .samples  = NULL
)
```

## Figure 4

```{r}
#| label: fig-f04-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f04", .fun_name = "des_plot_f04", .id = "f04", .height = plot_height(12L),
  .caption  = "Each year's contracts by type, shares stacked, with the amendment share as a line.",
  .samples  = NULL
)
```

The same shares as small multiples (Online Appendix C).

```{r}
#| label: fig-f04b-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f04", .fun_name = "des_plot_f04b", .id = "f04b", .height = plot_height(18L),
  .caption  = "Each type's share of the year's contracts, one panel per type.",
  .samples  = NULL
)
```

## Figure 5

```{r}
#| label: fig-f05-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f05", .fun_name = "des_plot_f05", .id = "f05", .height = plot_height(12L),
  .caption  = "Mean and median per year of duration, countries, parties and words.",
  .samples  = NULL
)
```

## Table 3

```{r}
#| label: tbl-t03-tabs
#| output: asis

des_tabs_table(
  .tab_name = "tab_t03", .fun_name = "des_print_t03", .id = "t03",
  .samples  = NULL
)
```

## Figure 10

```{r}
#| label: fig-f10-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f10", .fun_name = "des_plot_f10", .id = "f10", .height = plot_height(5L),
  .caption  = "Share of contracts redacted per year: by order, by markers, and by either.",
  .samples  = NULL
)
```

## Appendix Figure F1

```{r}
#| label: fig-ff1-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_ff1", .fun_name = "des_plot_ff1", .id = "ff1", .height = plot_height(18L),
  .caption  = "Share of contracts redacted per year, one panel per type.",
  .samples  = NULL
)
```

## Table 7

```{r}
#| label: tbl-t07-tabs
#| output: asis

des_tabs_table(.tab_name = "tab_t07", .fun_name = "des_print_t07", .id = "t07", .samples = NULL)
```

```{r}
#| label: fig-t07b-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_t07b", .fun_name = "des_plot_t07b", .id = "t07b", .height = plot_height(5L),
  .caption  = "Share of announcements filed within four business days of the agreement date, by year.",
  .samples  = NULL
)
```

## Table 1

```{r}
#| label: tbl-t01-tabs
#| output: asis

des_tabs_table(.tab_name = "tab_t01", .fun_name = "des_print_t01", .id = "t01", .samples = NULL)
```

## Sample losses and the calendar year

```{r}
#| label: fig-loss
#| fig-cap: "Attachments lost to format and to Compustat coverage, by year (left) and by form (right)."
#| fig-height: !expr plot_height(8L)

des_plot_loss(.tab_data = tab_loss)
```

```{r}
#| label: fig-fa1-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_fa1", .fun_name = "des_plot_fa1", .id = "fa1", .height = plot_height(8L),
  .caption  = "Each day's share of the group's yearly contracts, averaged over years, reporting seasons shaded.",
  .samples  = NULL
)
```

## Table 4

```{r}
#| label: tbl-t04-tabs
#| output: asis

des_tabs_table(.tab_name = "tab_t04", .fun_name = "des_print_t04", .id = "t04", .samples = NULL)
```

## Figure 8

```{r}
#| label: fig-f08a
#| fig-cap: "Contracts per firm-quarter for the smallest and largest size quartile, by channel and fiscal quarter."
#| fig-height: !expr plot_height(8L)

des_plot_f08a(.tab_data = des_slice(tab_f08a, "S5_Quarter"))
```

```{r}
#| label: fig-f08b
#| fig-cap: "Contracts per firm-quarter by Fama-French industry, every quarter in the window."
#| fig-height: !expr plot_height(12L)

des_plot_f08b(.tab_data = des_slice(tab_f08b, "S5_Quarter"))
```

## Figure 9

```{r}
#| label: fig-f09-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f09", .fun_name = "des_plot_f09", .id = "f09", .height = plot_height(12L, .square = TRUE),
  .caption  = paste("Share of contracts redacted within each industry and type, before and after the FAST Act;",
                    "cells under 30 contracts unlabelled."),
  .samples  = NULL
)
```

## Figure 7

```{r}
#| label: fig-f07-tabs
#| output: asis

des_tabs_figure(
  .tab_name = "tab_f07", .fun_name = "des_plot_f07", .id = "f07", .height = plot_height(8L),
  .caption  = "Countries mentioned per contract against segment geographical diversity, bin means and the fitted line.",
  .samples  = c("S3_Matched", "S3_AK")
)
```

## Reconciliation

```{r}
#| label: overview-reconcile

tab_reconcile <- des_table_reconcile()
```

## Samples

```{r}
#| label: overview-samples

tbl_out(.tab = tab_samples, .title = "The named samples every exhibit cites")

tibble::tibble(
  Parameter = names(.lP$Params),
  Value     = as.character(unlist(.lP$Params))
) |>
  tbl_out(.title = "The choices this render made")
```

# Next

The remaining exhibits, one compute and one render function each, in the order of the specification: the
sample table, the filing figures, the content figures and tables, the firm-level figures, the
redaction figures, the summary table. Every tibble goes to `Output/Data/`, every figure to
`Output/Figures/` through `plot_save()`, every table to `Output/Tables/` as `.tex`, and a manifest maps
each exhibit to its files.
