---
title: "Final Exhibits -- Every Table and Figure of the Paper, in One Store (31)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

# THE COMMONS FIRST. _Plots.R rebuilds its level registry empty every time it is sourced, so every
# library that registers a vocabulary must follow it. _OnlineAppendix.R carries what the builders moved from 40
# use: their table frame, their writer, their staleness test and the pandoc conversion that shows their tables.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_NER", "_Plots", "_Tables", "_Entity", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(.x = .path_libs, .f = \(.p) source(file = .p, encoding = "UTF-8"))

# THE UPSTREAM LIBRARIES, IN THIS ORDER. 03A owns the class vocabulary, the folds and the scoring
# helpers; 03B, 03C and 03D are sourced for their path helpers and crown records, as 03E does, and
# no engine is invoked; 03E owns the arm panel this document rebuilds for the classification tables;
# 10 owns exp_cache_hit() and the column-by-column report. The readers of the release, the
# vocabulary the figures agree on and the reference numbers are this document's own (section 0 of
# its library, carried over from the retired 30-Descriptives); its library registers the paper's
# class order and the form families when sourced, which is why it comes after _Plots.
.libs_up <- c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword", "03D-ClassifyLLM",
              "03E-ClassifyOrchestrate", "10-ExportData")
.path_libs <- c(
  .path_libs,
  purrr::map_chr(.libs_up, \(.s) init_create_script_fun(.dir_here = here::here(), .name_script = .s))
)
purrr::walk(.x = utils::tail(.path_libs, length(.libs_up)), .f = \(.p) source(file = .p, encoding = "UTF-8"))

.name_script <- "30-FinalExhibits"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is the one store of the paper's exhibits: every table and figure the manuscript, the online appendix
and the response memo print, and every tibble a number is read from. It writes each under its name -- the tibble to
`Output/Data`, the tabular to `Output/Tables`, the figure as png to `Output/Figures`, the note to
`Output/Notes` -- and no other document is to write there: `50-Numbers` reads the tibbles, `41-Methods` and the
`42-OnlineAppendix` chapters read the exhibits, and none of them builds one.

## What moved in

Everything `30-FinalExhibits` built, unchanged, and every exhibit `50-Numbers` built for the appendix chapters,
together with the two tibbles only numbers read (`CtoAhci`, `CtoMarkers`). The moved builders keep their chapter
prefixes (`oaa_`, `oab_`, `oac_`, `oad_`) and 40's (`num_`) until the clean-up; they write in the same layout under
this document's output directory and rebuild only where an input or this library is newer than their files. 30 and
40 still write their own copies until their consumers are pointed here, and Validation compares the two sets file by
file. Exhibits first built here -- the content readings table, for one -- carry origin 31 and nothing to compare.

## By topic, not by the paper's order

The manuscript's structure is still moving, so the sections below follow the subject: data sources and software,
sample selection, filing behaviour, contract types, classification performance, content variables, geography,
redactions, and the Item 1.01 announcements. The registry's `Topic` column is this order; where an exhibit is
printed -- manuscript, appendix chapter, memo, or nowhere -- is its `Where` column, decided separately.

## One stem, one exhibit

Six classification tables existed twice under one name: 30's full versions, with the fold scores the authors read,
and the appendix's cuts of them, which the chapters print. In one folder a cut would overwrite the table it reads.
The full versions are therefore `ClassLabelledFull`, `ClassTransformerFull`, `ClassAmendmentFull`,
`ClassKeywordFull`, `ClassArmsFull` (with `ClassArmsFullCeiling`) and `ClassConfusionFull`; the cuts keep the plain
names, which are the ones the appendix fragments input.

## What is read

The release on her Dropbox folder, the outputs of her `101` and `103` do-files (converted under this document's own
cache), and the pipeline stage outputs the classification and appendix exhibits need: the run folders of `03A` to
`03D`, `03B`'s crowned classification, `01A`'s index mirror and landing pages, and `04A`'s span stores. Nothing
downstream of the release is an input; the one exception is the check of the move, which reads 30's and 40's output
directories and goes with the move back to 30.

## Prepared once per render, read lazily ever after

Each input is read once, given its derived and membership columns, and written under
`Output/Prepared` as one parquet per table, keyed on what it was built from: the release file or the
`.dta` conversion, this document's library, and for the contract table the definitional switches. A prepared
table is rebuilt when any of those is newer than it and read as it stands otherwise, so it is never
stale and a repeat render costs a few file checks. Every exhibit then opens the prepared files
through Arrow and DuckDB and pulls the columns and rows it needs; nothing else sits in memory.

## One release, and it is dated

The paper is written on the 9 September release, the first to carry the corrected state and country
counts. Every parquet in the release is checked against that date before anything is read; an older
file is named on the page and, for the manuscript render, aborts.

# Configuration

```{r}
#| label: configure

.lP <- list(
  # WHERE HER FOLDER IS. The Dropbox root on this machine; ~/Downloads/Pipeline is a copy with the same
  # layout and works as a drop-in while Dropbox is offline.
  Root = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    # THE RELEASE THE PAPER IS WRITTEN ON. Every .parquet under Input should be at least this new.
    ReleaseMin = "2026-09-09",
    # THE FOUR DEFINITIONAL SWITCHES: 103's redaction rule with one marker enough, the
    # cascade duration that reproduces Table 3, the adjusted word count the text prints, and the
    # recital parties. Each is settled or overturned in the exhibit that depends on it.
    Redaction  = "symbolexplicit",
    RedactMin  = 1L,
    Duration   = "cascade",
    Words      = "adjusted",
    Parties    = "recital"
  )
)

.lP$Input <- list(
  FilContracts     = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),
  FilSummaries     = fs::path(.lP$Root, "100_Data_Export", "Summaries.parquet"),
  FilPlaces        = fs::path(.lP$Root, "100_Data_Export", "Places.parquet"),
  FilTermDocs      = fs::path(.lP$Root, "100_Data_Export", "TermDocs.parquet"),
  FilCtoOrders     = fs::path(.lP$Root, "100_Data_Export", "CtoOrders.parquet"),
  DtaQuarter       = fs::path(.lP$Root, "103_Variable_Creation", "103_Output",
                              "quarter_dictionary_COMPUSTAT_variables.dta"),
  DtaAkContract    = fs::path(.lP$Root, "103_Variable_Creation", "103_Output",
                              "full_dictionary_contract_level_AK.dta"),
  DtaConcentration = fs::path(.lP$Root, "101_Data_prep", "101_Output", "concentration.dta")
)

# THE PIPELINE'S OWN OUTPUTS, which the builders moved from 40 read: 01A's index mirror and landing pages, 03B's
# crowned classification, 04A's span stores, and this library, a change in which rebuilds them. Kept apart from
# .lP$Input, whose files the vintage check dates against the release.
.dirs_edgar <- rGetEDGAR::get_directories(here::here("2_output", "01A-EdgarIndex", "GetEDGAR"))

.lP$Pipeline <- list(
  DirMaster = .dirs_edgar$MasterIndex$DirParquet,                                        # filings per form, first filings
  DirLinks  = .dirs_edgar$DocLinks$DirMain$Links,                                        # the document lists, by quarter
  Landing   = here::here("2_output", "01A-EdgarIndex", "Output", "LandingPageAll.parquet"), # SIC per filing
  ClassFile = here::here("2_output", "03B-ClassifyTrainBERT", "classification",
                         "crowned_classification.parquet"),                             # first and second choice
  DirStore  = here::here("2_output", "04A-EntityExtract", "Output"),                     # the span stores
  Sample    = here::here("2_output", "04A-EntityExtract", "Output", "sample_text.parquet"), # the labelled documents
  Lib       = here::here("1_code", "30-FinalExhibits.R")                                 # a changed builder rebuilds
)

# THE MOVED BUILDERS' SWITCHES, as 40 set them. Kept apart from Params, whose hash keys the prepared contract table.
.lP$Build <- list(
  Rebuild    = FALSE,             # TRUE rebuilds the moved exhibits even where their inputs have not changed
  MinMarkers = 1L,                # markers a contract needs to count as redacted by text (CtoMarkers)
  AhciTo     = 2019L,             # last order year of the Ahci (2025) comparison
  FilesFrom  = 1998.1,            # the exhibit-files table's first quarter, as 01A writes year-quarters
  FilesTo    = 2001.2,            # and its last
  Titles     = 5L,                # descriptions per category in the titles table
  SpacyModel = "en_core_web_trf"  # the spaCy model 04A ran
)

# THE CLASSIFICATION STAGES' OUTPUT DIRECTORIES, resolved the way 03E resolves them.
.dir_03 <- purrr::map(
  purrr::set_names(c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword", "03D-ClassifyLLM"),
                   c("Prep", "Bert", "Kw", "Llm")),
  \(.s) init_create_script_dir(.dir_here = here::here(), .name_script = .s)
)

# THIS DOCUMENT'S OWN CACHE: her .dta files converted to parquet here, keyed on their size. Nothing
# under another document's output directory is ever read.
.lP$Cache <- list(
  CacheQuarter       = utils_file_path(.dir_main, "Cache", "Quarter.parquet"),
  CacheAkContract    = utils_file_path(.dir_main, "Cache", "AkContract.parquet"),
  CacheConcentration = utils_file_path(.dir_main, "Cache", "Concentration.parquet")
)

# WHERE THE PAPER READS FROM. One folder on Dropbox; a deployment moves its current/ to _archive/
# and fills a new one (see Deployment).
.lP$Paper <- fs::path(.lP$Root, "200-Paper_figures")

# THE PREPARED TABLES, and where the manuscript's copies go.
.lP$Output <- list(
  DirPrepared = utils_file_path(.dir_main, "Output", "Prepared"),
  DirFigures  = utils_file_path(.dir_main, "Output", "Figures"),
  DirTables   = utils_file_path(.dir_main, "Output", "Tables"),
  DirNotes    = utils_file_path(.dir_main, "Output", "Notes"),
  DirData     = utils_file_path(.dir_main, "Output", "Data")
)

purrr::walk(.x = unlist(.lP$Output), .f = fs::dir_create)

# WHERE THE MOVED BUILDERS WRITE: the parent of the four exhibit folders above, in the same layout.
.lP$DirOwn <- fs::path(.dir_main, "Output")

# ONE DUCKDB CONNECTION for the document, in memory; every prepared table is registered on it below.
con <- DBI::dbConnect(duckdb::duckdb(), dbdir = ":memory:")

# THE APPENDIX MACHINERY'S STATE, fresh for this render: the moved builders report into it.
oa_state_reset()
```

# Input

## The release, dated

```{r}
#| label: input-vintage

tab_vintage <- fin_check_vintage(
  .inputs   = unlist(.lP$Input),        # every path above
  .min_date = .lP$Params$ReleaseMin,    # the release the paper is written on
  .strict   = FALSE                     # older parquet warns; TRUE aborts, for the manuscript render
)
```

## Her .dta files, converted here

Three conversions under this document's own cache, each rebuilt when the `.dta`'s size changes --
a Dropbox re-sync moves the modification time without changing a byte, and the size is what tells
the two apart.

```{r}
#| label: input-convert

fin_convert_dta(
  .path_dta   = .lP$Input$DtaQuarter,        # her quarter panel, 103's output
  .path_cache = .lP$Cache$CacheQuarter,
  .cols       = .fin_quarter_cols,           # 36 columns under this document's names
  .rerun      = FALSE                        # TRUE reconverts regardless
)

fin_convert_dta(
  .path_dta   = .lP$Input$DtaAkContract,     # her contract-level flags
  .path_cache = .lP$Cache$CacheAkContract,
  .cols       = .fin_ak_contract_cols,
  .rerun      = FALSE
)

fin_convert_dta(
  .path_dta   = .lP$Input$DtaConcentration,  # 101's segment concentration
  .path_cache = .lP$Cache$CacheConcentration,
  .cols       = NULL,                        # small; every column under its Stata name
  .rerun      = FALSE
)
```

## The pipeline's own outputs

The builders moved from 40 read four of the pipeline's stages directly; this table says which of their paths exist
before any of them runs.

```{r}
#| label: input-pipeline
tibble::tibble(
  Input  = names(.lP$Pipeline),
  Path   = unname(unlist(.lP$Pipeline)),
  Exists = fs::file_exists(unname(unlist(.lP$Pipeline)))
) |>
  tbl_out(.title = "The pipeline outputs this document reads")
```

# Prepare

Seven tables, each read once and written under `Output/Prepared`. The contract
table carries the nine membership columns `fin_add_samples()` documents, one logical per sample, so
an exhibit is drawn on a sample by filtering on the column of that name. Summaries is built after
Contracts because the exhibit count on each 8-K comes from it. A prepared table is rebuilt when its
release file, its `.dta` conversion, this document's library or -- for Contracts -- a definitional
switch is newer than it, and read as it stands otherwise; `.rerun = TRUE` on any call forces the
rebuild.

```{r}
#| label: prepare-tables

fin_prepare_contracts(
  .path    = .lP$Input$FilContracts,        # the release
  .path_ak = .lP$Cache$CacheAkContract,     # her flags, joined on DocID
  .params  = .lP$Params,                    # the definitional switches; a flip rebuilds
  .dir     = .lP$Output$DirPrepared,
  .rerun   = FALSE                          # TRUE rebuilds regardless
)

fin_prepare_summaries(
  .path           = .lP$Input$FilSummaries,
  .path_contracts = fs::path(.lP$Output$DirPrepared, "Contracts.parquet"),   # for the exhibit count per 8-K
  .dir            = .lP$Output$DirPrepared,
  .rerun          = FALSE
)

fin_prepare_quarter(
  .path_cache = .lP$Cache$CacheQuarter,     # the conversion of her quarter panel
  .dir        = .lP$Output$DirPrepared,
  .rerun      = FALSE
)

fin_prepare_concentration(
  .path_cache = .lP$Cache$CacheConcentration,   # the conversion of 101's concentration.dta
  .dir        = .lP$Output$DirPrepared,
  .rerun      = FALSE
)

fin_prepare_places(
  .path  = .lP$Input$FilPlaces,             # the release
  .dir   = .lP$Output$DirPrepared,
  .rerun = FALSE
)

fin_prepare_term_docs(
  .path  = .lP$Input$FilTermDocs,           # the release
  .dir   = .lP$Output$DirPrepared,
  .rerun = FALSE
)

fin_prepare_cto_orders(
  .path  = .lP$Input$FilCtoOrders,          # the release
  .dir   = .lP$Output$DirPrepared,
  .rerun = FALSE
)
```

## Opened lazily, registered once

```{r}
#| label: prepare-open

lst_ds <- fin_open_prepared(
  .dir    = .lP$Output$DirPrepared,
  .tables = .fin_tables                     # the seven, in build order
)

fin_register_prepared(
  .con      = con,                          # the document's connection
  .datasets = lst_ds
)

fin_report_prepared(.datasets = lst_ds)
```

From here, `lst_ds$Contracts` is the contract table as an Arrow dataset and `Contracts` is a DuckDB
view over the same parquet file; `dplyr::tbl(con, "Contracts")` or a `DBI::dbGetQuery()` reads it in
place with every predicate pushed down.

## The classification panel

Nothing about the classifiers is in the release. What `03E` assembles at render -- one row per
labelled document and task, the truth beside every engine's out-of-fold prediction, `NA` where an
engine declined -- is built here once, from the run folders and crown records of `03B`, `03C` and
`03D`, and written beside the other prepared tables with the labelled sample, the crowned
configurations and the sweep metrics. Keyed on those folders, so a retrained model rebuilds it.

```{r}
#| label: prepare-classification

fin_prepare_classification(
  .dir_prep = .dir_03$Prep,                 # prepared.parquet: the labelled sample and the folds
  .dir_bert = .dir_03$Bert,                 # runs, model_final/deployed.parquet
  .dir_kw   = .dir_03$Kw,                   # runs, table/catalogue.parquet
  .dir_llm  = .dir_03$Llm,                  # runs, if that stage ran
  .dir      = .lP$Output$DirPrepared,
  .rerun    = FALSE
)

lst_ds_class <- fin_open_prepared(
  .dir    = .lP$Output$DirPrepared,
  .tables = .fin_class_tables
)

fin_register_prepared(
  .con      = con,
  .datasets = lst_ds_class
)

fin_report_prepared(.datasets = lst_ds_class)
```

# Samples

```{r}
#| label: samples-table

tab_samples <- fin_table_samples(
  .con     = con,
  .samples = .fin_contract_samples          # the nine contract-level samples, ladder order
)
```

## The ladder nests, and S2 is the paper's number

Two checks, each stated before it is read. **The samples nest as the ladder says**: S00 holds S0 and
S1, both hold S2, and S2 holds its subsets and the redaction window; a row outside its parent is a
definition that drifted. **S2 is the paper's number**: 1,135,360 unique contracts on the 10 September
release (the revision printed 1,136,095 before the copies without readable text were folded into
the malformatted rung), with no tolerance because there is no rounding.

```{r}
#| label: validation-samples

tab_counts <- fin_check_samples(
  .ds      = lst_ds$Contracts,
  .samples = .fin_contract_samples,
  .ref     = .fin_reference                 # the revision's Table 2 Panel A
)
```

# Data sources and software

What the SEC requires and which forms carry material contracts, what the database holds of them, which Exhibit 10
attachments exist as separate files, the counts the text cites that no table prints, and the software the database
is built with. All seven come from the appendix chapters A and B; two of them are data only.

```{r}
#| label: build-sources

# THE MOVED BUILDERS' SHARED ARGUMENTS: where they write, whether to force, and the library a change in which
# rebuilds them.
.b_a <- list(
  .dir_own  = .lP$DirOwn,
  .force    = .lP$Build$Rebuild,
  .path_lib = .lP$Pipeline$Lib
)

st_sources <- c(
  ExhibitRequired  = do.call(oaa_build_exhibit_table, .b_a),
  FormDescriptions = do.call(oaa_build_form_descriptions, .b_a),
  FormCoverage     = do.call(oaa_build_coverage, c(.b_a, list(
    .dir_master     = .lP$Pipeline$DirMaster,   # filings per form type
    .path_contracts = .lP$Input$FilContracts    # the contracts the database holds
  ))),
  ExhibitFiles     = do.call(oaa_build_files, c(.b_a, list(
    .dir_links = .lP$Pipeline$DirLinks,         # the document lists of the index pages, by quarter
    .from      = .lP$Build$FilesFrom,
    .to        = .lP$Build$FilesTo
  ))),
  TextCounts       = do.call(oaa_build_counts, c(.b_a, list(.path_contracts = .lP$Input$FilContracts))),
  PipelineStages   = oab_build_stages(
    .dir_own  = .lP$DirOwn,                     # the table's wording lives in the library
    .force    = .lP$Build$Rebuild,
    .path_lib = .lP$Pipeline$Lib
  ),
  PackageVersions  = oab_build_versions(
    .dir_own = .lP$DirOwn                       # rebuilt on every render: the installed versions
  )
)

oa_report_builds(.status = st_sources)
```

```{r}
#| label: show-sources
#| results: asis
fin_show_built(
  .names = names(st_sources),
  .dirs  = .lP$Output
)
```

# Sample selection

Panel A from the release's ladder columns, checked against the revision's Table 2 and aborting on
any difference. Panel B as her `106` builds the estimation samples: every registrant copy, less the
malformed, less the CIKs Compustat does not cover, less the rows whose fiscal quarter lacks a
regression variable, the industry, the state, or sits in a state where filing never varies; then
the two start years; then the firm-level sample of `105`, non-filing quarters included, firms whose
filing never varies within a FAST Act period excluded. The control set is the resubmission's --
the revision's plus product-market fluidity -- and it is what moves the Panel B numbers off the
revision's page; `.fin_controls$Revision` prints the old set for comparison.

```{r}
#| label: tbl-sample
#| results: asis

tab_sample <- fin_table_sample(
  .ds_contracts = lst_ds$Contracts,           # ladder columns and the Compustat keys
  .ds_quarter   = lst_ds$Quarter,             # her panel, inside the window
  .controls     = .fin_controls$Resubmission, # 105/106's control set, September 2026
  .dirs         = .lP$Output,
  .name         = "SampleSelection"
)
```

## What each requirement costs

Two diagnostics under the sample table (decided 10 September). The attrition table is a marginal
ladder: with the estimation sample's requirements as the reference -- fiscal quarter, industry,
state, a state in which filing varies, and each control -- how many rows each removes on its own,
at the contract grain and at the firm-quarter grain; a sequential ladder would depend on the order
the requirements are listed in. The fluidity table asks who the firm-quarters without fluidity
are, because Ann-Kristin's check found the gaps clustered in loss firms.

```{r}
#| label: tbl-attrition
#| results: asis

tab_attrition <- fin_table_attrition(
  .ds_contracts = lst_ds$Contracts,
  .ds_quarter   = lst_ds$Quarter,
  .controls     = .fin_controls$Resubmission, # the same set the sample table uses
  .dirs         = .lP$Output,
  .name         = "SampleAttrition"
)
```

```{r}
#| label: tbl-fluidity
#| results: asis

tab_fluidity <- fin_table_fluidity(
  .ds_quarter = lst_ds$Quarter,
  .dirs       = .lP$Output,
  .name       = "FluidityMissing"
)
```

# Filing behaviour and filers

## Filing types

Contracts by the form they arrived in, U.S. and foreign forms side by side, each bar split into
original agreements and amendments, the form's share above it. Unique contracts. Decided on 9
September for the online appendix.

```{r}
#| label: fig-filing-types
#| results: asis
#| fig-cap: "Distribution of filing types on the unique-contract sample."
#| fig-height: !expr plot_height(8L)

fig_filing_types <- fin_figure_filing_types(
  .ds_contracts = lst_ds$Contracts,
  .dirs         = .lP$Output,
  .name         = "FilingTypes",
  .ref          = .fin_reference_f01       # the revision's share labels, checked on the render
)
```

## Filings over time

Each year's contracts by filing group, shares stacked, the year's total as a line on the right axis.
Four groups: the
registration statements stand on their own, because the 2021 spike is theirs and the three-group
version hides it inside ad-hoc. Unique contracts. Decided on 9 September for the manuscript; the
four-group form is the recommendation, the three-group form is one call to `fin_plot_f02()`.

```{r}
#| label: fig-filings-time
#| results: asis
#| fig-cap: "Distribution of filings over time on the unique-contract sample, four groups."
#| fig-height: !expr plot_height(8L)

fig_filings_time <- fin_figure_filings_time(
  .ds_contracts = lst_ds$Contracts,
  .dirs         = .lP$Output,
  .name         = "FilingsTime"
)
```

## Within the year

When in the calendar year contracts are filed; from the appendix's Chapter A.

```{r}
#| label: build-within-year
st_within <- c(
  FilingsWithinYear = do.call(oaa_build_within_year, c(.b_a, list(.path_contracts = .lP$Input$FilContracts)))
)

oa_report_builds(.status = st_within)
```

```{r}
#| label: show-within-year
#| results: asis
fin_show_built(
  .names = names(st_within),
  .dirs  = .lP$Output
)
```

## Seasoned filers

The referee's SPAC question in one figure: all filers against firms more than two years past their
first contract. If the 2021 rise were existing firms filing faster it would show among the seasoned;
it does not.

```{r}
#| label: fig-filings-seasoned
#| results: asis
#| fig-cap: "Contracts per year and the registration share, all filers against seasoned filers."
#| fig-height: !expr plot_height(12L)

fig_seasoned <- fin_figure_seasoned(
  .ds_contracts = lst_ds$Contracts,
  .dirs         = .lP$Output,
  .name         = "FilingsSeasoned"
)
```

### Three panels, for the appendix

The form Chapter A prints: all filers against seasoned filers in three panels, with the first EDGAR filing of each
CIK from the master index and the industry from the landing pages.

```{r}
#| label: build-seasoned
st_seasoned <- c(
  SeasonedFilers = do.call(oaa_build_seasoned, c(.b_a, list(
    .path_contracts = .lP$Input$FilContracts,   # the sample, its forms and its labels
    .path_landing   = .lP$Pipeline$Landing,     # the SIC code of each filing
    .dir_master     = .lP$Pipeline$DirMaster    # the first EDGAR filing of each CIK
  )))
)

oa_report_builds(.status = st_seasoned)
```

```{r}
#| label: show-seasoned
#| results: asis
fin_show_built(
  .names = names(st_seasoned),
  .dirs  = .lP$Output
)
```

## Filing metrics by firm fundamentals

Her `104` step for step, on the full quarter panel inside the window -- the sample restrictions
written above the figure in `104` are commented out, so every firm-quarter of every ever-filing firm
counts, non-filing quarters included. Panel A: smallest against largest size quartile, quartiles
within fiscal year, periodic against current reports, by fiscal quarter. Panel B: contracts per
firm-quarter by industry. "Current reports" is every non-periodic form, registration statements
included, which her legend calls 8-K.

```{r}
#| label: fig-firm-fundamentals
#| results: asis
#| fig-cap: "Contracts per firm-quarter by size quartile and channel (A) and by industry (B), firm-quarter panel."
#| fig-height: !expr plot_height(8L)
#| fig-width: 10

fig_firm_fundamentals <- fin_figure_firm_fundamentals(
  .ds_quarter = lst_ds$Quarter,
  .dirs       = .lP$Output,
  .name       = "FirmFundamentals",
  .ref        = .fin_reference_f08          # the revision's Panel B, checked on the render
)
```

### Layouts under choice (16 September)

The figure above is ten inches wide; set at the manuscript's text width of 5.65 inches, its 11-point type prints at
about six points. The forms below use the standard 7.5-inch canvas. A to C stack the two panels and differ only in
Panel A's time axis -- fiscal quarters as above, the mean of each complete fiscal year, or a trailing mean over four
quarters; the saw-tooth in the periodic series is the 10-K quarter. D and E split the figure in two. Once a form is
chosen it takes the stem `FirmFundamentals`, and the other forms go.

#### A. Stacked, by fiscal quarter

```{r}
#| label: fig-firm-a
#| results: asis
#| fig-cap: "Firm fundamentals, stacked: size quartile and channel by fiscal quarter (A) and industry (B)."
#| fig-height: !expr plot_height(18L)

fig_firm_a <- fin_figure_firm_forms(
  .ds_quarter = lst_ds$Quarter,
  .form       = "a",                     # Panel A above Panel B, by fiscal quarter as today
  .dirs       = .lP$Output,
  .name       = "FirmFundamentalsA"
)
```

#### B. Stacked, fiscal-year means

```{r}
#| label: fig-firm-b
#| results: asis
#| fig-cap: "Firm fundamentals, stacked: size quartile and channel as fiscal-year means (A) and industry (B)."
#| fig-height: !expr plot_height(18L)

fig_firm_b <- fin_figure_firm_forms(
  .ds_quarter = lst_ds$Quarter,
  .form       = "b",                     # the same layout, the four quarters of each fiscal year averaged
  .dirs       = .lP$Output,
  .name       = "FirmFundamentalsB"
)
```

#### C. Stacked, trailing four-quarter means

```{r}
#| label: fig-firm-c
#| results: asis
#| fig-cap: "Firm fundamentals, stacked: size quartile and channel as trailing four-quarter means (A) and industry (B)."
#| fig-height: !expr plot_height(18L)

fig_firm_c <- fin_figure_firm_forms(
  .ds_quarter = lst_ds$Quarter,
  .form       = "c",                     # the same layout, quarterly resolution kept
  .dirs       = .lP$Output,
  .name       = "FirmFundamentalsC"
)
```

#### D. Split, first half: size and channel

```{r}
#| label: fig-firm-size
#| results: asis
#| fig-cap: "Contracts per firm-quarter by size quartile and channel, fiscal-year means."
#| fig-height: !expr plot_height(8L)

fig_firm_size <- fin_figure_firm_forms(
  .ds_quarter = lst_ds$Quarter,
  .form       = "size",                  # Panel A alone, fiscal-year means
  .dirs       = .lP$Output,
  .name       = "FirmSize"
)
```

#### E. Split, second half: industry

```{r}
#| label: fig-firm-industry
#| results: asis
#| fig-cap: "Contracts per firm-quarter by Fama-French 12 industry."
#| fig-height: !expr plot_height(12L)

fig_firm_industry <- fin_figure_firm_forms(
  .ds_quarter = lst_ds$Quarter,
  .form       = "industry",              # Panel B alone
  .dirs       = .lP$Output,
  .name       = "FirmIndustry"
)
```

# Contract types

## Contract categories

The taxonomy's definition, hand-written. Rows in the revision's taxonomic order; `.order = "paper"`
sorts them into the numbered order every other exhibit uses, which is the class-order question
still open with Ann-Kristin.

```{r}
#| label: tbl-categories
#| results: asis

tab_categories <- fin_table_categories(
  .order = "taxonomic",       # "paper" for the numbered order (1) M&A ... (12) Other
  .dirs  = .lP$Output,        # Data, Tables, Notes
  .name  = "Categories"       # the stem of every file written
)
```

## What filers call their contracts

The descriptions filers give their contracts, the most frequent per category; from the appendix's Chapter C.

```{r}
#| label: build-titles
st_titles <- c(
  CategoryTitles = oac_build_titles(
    .path_contracts = .lP$Input$FilContracts,   # the filer's description of each contract
    .n              = .lP$Build$Titles,         # descriptions per category
    .dir_own        = .lP$DirOwn,
    .force          = .lP$Build$Rebuild,
    .path_lib       = .lP$Pipeline$Lib
  )
)

oa_report_builds(.status = st_titles)
```

```{r}
#| label: show-titles
#| results: asis
fin_show_built(
  .names = names(st_titles),
  .dirs  = .lP$Output
)
```

## Contract types

Each category's count with its share, and contracts per firm-year of that category; categories in
the Categories table's order, sub-categories under their super-category strip, no numbers. Unique
contracts. Decided on 9 September: the new version, super-categories visible.

```{r}
#| label: fig-contract-types
#| results: asis
#| fig-cap: "Contracts by category on the unique-contract sample: count and share (A), contracts per firm-year (B)."
#| fig-height: !expr plot_height(12L)

fig_contract_types <- fin_figure_contract_types(
  .ds_contracts = lst_ds$Contracts,
  .dirs         = .lP$Output,
  .name         = "ContractTypes",
  .ref          = .fin_reference_f03       # the revision's share labels, checked on the render
)
```

## Contract types over time

Four forms of one tibble, each under its own sub-header until one is chosen; decided on 9 September
for the online appendix. The revision's twelve-colour stack (D) is drawn only as the reference. The
amendment share, which the revision draws as a line over the stack, stays on the stacked forms and
goes into the note of the others.

### A. Stacked by super-category, amendment share as a line

```{r}
#| label: fig-types-time-a
#| results: asis
#| fig-cap: "Each year's contracts by super-category, shares stacked, with the amendment share."
#| fig-height: !expr plot_height(8L)

fig_types_time_a <- fin_figure_types_time(
  .ds_contracts = lst_ds$Contracts,
  .form         = "a",
  .dirs         = .lP$Output,
  .name         = NULL                     # TypesTimeA
)
```

### B. One panel per category, twelve small multiples

```{r}
#| label: fig-types-time-b
#| results: asis
#| fig-cap: "Each category's share of the year's contracts, one panel per category."
#| fig-height: !expr plot_height(18L)

fig_types_time_b <- fin_figure_types_time(
  .ds_contracts = lst_ds$Contracts,
  .form         = "b",
  .dirs         = .lP$Output,
  .name         = NULL                     # TypesTimeB
)
```

### C. One panel per super-category, sub-categories as lines

```{r}
#| label: fig-types-time-c
#| results: asis
#| fig-cap: "Each super-category's sub-categories over time, one panel per super-category."
#| fig-height: !expr plot_height(12L)

fig_types_time_c <- fin_figure_types_time(
  .ds_contracts = lst_ds$Contracts,
  .form         = "c",
  .dirs         = .lP$Output,
  .name         = NULL                     # TypesTimeC
)
```

### D. The revision's form: twelve on one stack

```{r}
#| label: fig-types-time-d
#| results: asis
#| fig-cap: "Each year's contracts by category, shares stacked, with the amendment share (reference)."
#| fig-height: !expr plot_height(12L)

fig_types_time_d <- fin_figure_types_time(
  .ds_contracts = lst_ds$Contracts,
  .form         = "d",
  .dirs         = .lP$Output,
  .name         = NULL                     # TypesTimeD
)
```

## Classifier confidence by category

The probability the transformer put on the category it assigned, by category: mean, SD and
quartiles; beside them, how often the keyword-based classifier fired and confirmed or contradicted
it. Labelled contracts only, so the 735 without text are outside the N (Open Issues).

```{r}
#| label: tbl-confidence
#| results: asis

tab_confidence <- fin_table_confidence(
  .ds_contracts = lst_ds$Contracts,         # BertClassDetailedProb, ClassDetailedFlag
  .dirs         = .lP$Output,
  .name         = "ClassConfidence"
)
```

# Classification performance

Everything about the classifiers, for the authors, until the manuscript's set is chosen. Every
score is out of fold: five folds dealt once in `03A` and shared by every arm, each document predicted
once by a model that never saw it; there is no held-out test set, by design, because the rarest
category has seventy-one documents. Tables by category follow the Categories order, the super rows
scoring the detailed predictions rolled up to their parent.

## The labelled sample

```{r}
#| label: tbl-class-sample
#| results: asis

tab_class_sample <- fin_table_class_sample(
  .ds_sample = lst_ds_class$ClassSample,
  .dirs      = .lP$Output,
  .name      = "ClassLabelledFull"
)
```

## The transformer, out of fold

```{r}
#| label: tbl-class-transformer
#| results: asis

tab_class_transformer <- fin_table_class_transformer(
  .ds_panel   = lst_ds_class$ClassPanel,
  .ds_sample  = lst_ds_class$ClassSample,   # the second label, for lenient recall
  .ds_crowned = lst_ds_class$ClassCrowned,  # which length ships
  .dirs       = .lP$Output,
  .name       = "ClassTransformerFull"
)
```

## The amendment classifier

```{r}
#| label: tbl-class-amendment
#| results: asis

tab_class_amendment <- fin_table_class_amendment(
  .ds_panel   = lst_ds_class$ClassPanel,
  .ds_crowned = lst_ds_class$ClassCrowned,
  .dirs       = .lP$Output,
  .name       = "ClassAmendmentFull"
)
```

## The keyword arm

```{r}
#| label: tbl-class-keyword
#| results: asis

tab_class_keyword <- fin_table_class_keyword(
  .ds_panel  = lst_ds_class$ClassPanel,
  .ds_sample = lst_ds_class$ClassSample,
  .dirs      = .lP$Output,
  .name      = "ClassKeywordFull"
)
```

## The arms compared

```{r}
#| label: tbl-class-arms
#| results: asis

lst_class_arms <- fin_table_class_arms(
  .ds_panel   = lst_ds_class$ClassPanel,
  .ds_crowned = lst_ds_class$ClassCrowned,
  .dirs       = .lP$Output,
  .name       = "ClassArmsFull"
)
```

## Model selection

```{r}
#| label: tbl-class-sweep
#| results: asis

tab_class_sweep <- fin_table_class_sweep(
  .ds_sweep   = lst_ds_class$ClassSweep,
  .ds_crowned = lst_ds_class$ClassCrowned,
  .dirs       = .lP$Output,
  .name       = "ClassSweep"
)
```

## The confusion matrix

```{r}
#| label: tbl-class-confusion
#| results: asis

tab_class_confusion <- fin_table_class_confusion(
  .ds_panel   = lst_ds_class$ClassPanel,
  .ds_sample  = lst_ds_class$ClassSample,
  .ds_crowned = lst_ds_class$ClassCrowned,
  .dirs       = .lP$Output,
  .name       = "ClassConfusionFull"
)
```

## The appendix's cuts

The tables Chapter C prints, each a cut of the full table above it: no fold scores, the categories numbered
(1)-(12) in the taxonomic order, undefined scores as a dash. Each reads its `...Full` tibble from this document's
`Data/` and writes under the plain name, which is the one the chapter inputs; the deployed-models table reads
`ClassSweep`, and the second-label pair reads `03B`'s crowned classification.

```{r}
#| label: build-class-cuts
.b_c <- c(
  .b_a,
  list(.dir_data = .lP$Output$DirData)   # the full tables above, written by this document
)

st_class <- c(
  ClassLabelled    = do.call(oac_build_labelled, .b_c),  # ClassLabelledFull, without round and words
  ClassDeployed    = do.call(oac_build_deployed, .b_c),  # ClassSweep, the crowned and deployed rows only
  ClassTransformer = do.call(oac_build_scores, c(.b_c, list(
    .name    = "ClassTransformer",
    .columns = c("Precision", "Recall", "F1", "RecallLenient"),
    .header  = c("Precision", "Recall", "F1", "Lenient recall"),
    .note    = paste(
      "Out-of-fold scores of the transformer that ships on the labeled sample. Sub-category rows score the",
      "detailed prediction against the detailed label; parent rows score the same predictions rolled up to their",
      "parent, so an error inside a parent does not count there. Precision, recall and F1 are per category; the",
      "Total row reports their macro averages. Lenient recall credits a prediction that equals the contract's",
      "second valid category; in the Total row it is overall accuracy under lenient scoring, the figure the main",
      "text cites."
    )
  ))),
  ClassConfusion   = do.call(oac_build_confusion, .b_c),
  ClassAmendment   = do.call(oac_build_amendment, .b_c),
  ClassKeyword     = do.call(oac_build_scores, c(.b_c, list(
    .name    = "ClassKeyword",
    .columns = c("Coverage", "Precision", "RecallSel", "F1"),
    .header  = c("Coverage", "Precision", "Recall where committed", "F1"),
    .note    = paste(
      "Out-of-fold scores of the published keyword table on the labeled sample. Coverage is the share of a",
      "category's contracts on which a term of the table fired; the table abstains on the rest. Precision is",
      "over the contracts assigned the category; recall where committed is over the contracts of the category on",
      "which the table committed; F1 combines precision with recall over all contracts of the category, so an",
      "abstention counts as a miss. A dash marks a score that is undefined because the table never assigned the",
      "category to any contract. The Total row reports the macro averages."
    )
  ))),
  ClassArms        = do.call(oac_build_arms, .b_c),
  ClassSecond      = oac_build_second(       # writes ClassSecondPairs and ClassSecond together
    .path_class = .lP$Pipeline$ClassFile,    # first and second choice per labelled document
    .dir_own    = .lP$DirOwn,
    .force      = .lP$Build$Rebuild,
    .path_lib   = .lP$Pipeline$Lib
  )
)

oa_report_builds(.status = st_class)
```

```{r}
#| label: show-class-cuts
#| results: asis
fin_show_built(
  .names = c("ClassLabelled", "ClassDeployed", "ClassTransformer", "ClassConfusion", "ClassAmendment",
             "ClassKeyword", "ClassArms", "ClassSecondPairs", "ClassSecond"),
  .dirs  = .lP$Output
)
```

# Content variables

## The extractors on the labelled sample

What each extractor proposed on the labelled sample, where in the contract its candidates fall, and how far the
extractors agree; from the appendix's Chapter D, computed from `04A`'s span stores, opened read-only.

```{r}
#| label: build-entities
st_entities <- c(
  EntityCoverage  = oad_build_coverage(
    .dir_store   = .lP$Pipeline$DirStore,   # 04A's three stores, opened read-only
    .path_sample = .lP$Pipeline$Sample,     # the documents every store indexes
    .spacy_model = .lP$Build$SpacyModel,    # the spaCy model printed
    .dir_own     = .lP$DirOwn,
    .force       = .lP$Build$Rebuild,
    .path_lib    = .lP$Pipeline$Lib
  ),
  EntityAlignment = oad_build_alignment(    # writes EntityPositions and EntityAgreement from one pass
    .dir_store   = .lP$Pipeline$DirStore,
    .path_sample = .lP$Pipeline$Sample,
    .spacy_model = .lP$Build$SpacyModel,
    .dir_own     = .lP$DirOwn,
    .force       = .lP$Build$Rebuild,
    .path_lib    = .lP$Pipeline$Lib
  )
)

oa_report_builds(.status = st_entities)
```

```{r}
#| label: show-entities
#| results: asis
fin_show_built(
  .names = c("EntityCoverage", "EntityPositions", "EntityAgreement"),
  .dirs  = .lP$Output
)
```

## Content characteristics by category

Words, duration, parties, countries and states by category on the unique-contract sample, in the Categories
table's order: super-categories pooled and bold, sub-categories indented, Total last. Twice, from
the same rows: the rule-based arm is what the pipeline's rules made of the extraction and is the
manuscript's table; the naive arm is what the extractor proposed before any rule, and the pair
shows where the rules move the level and the N. Duration carries its own N because it is undefined
where no end was found; parties, countries and states are counts, so nothing extracted is a zero. The note
states the sample and its size, and the function prints the size the revision assumed beside the
size counted here.

### Rule-based

```{r}
#| label: tbl-content-rule
#| results: asis

tab_content_rule <- fin_table_content(
  .ds_contracts = lst_ds$Contracts,   # S2 rows, the raw columns of both arms
  .con          = con,                # Places, for countries and states attached to a party
  .arm          = "rule",             # the manuscript's table
  .roles        = .fin_roles_recital, # registrant, co-filers, counterparties: parties, countries, states alike
  .dirs         = .lP$Output,
  .name         = NULL,               # ContentRule
  .digits       = c(Mean = 2L, SD = 2L),  # two decimals throughout (decided 16 September)
  .words_scale  = 1000,                   # words in thousands, as the header says
  .ref          = .fin_reference      # the revision's unique-contract count
)
```

### Naive

```{r}
#| label: tbl-content-naive
#| results: asis

tab_content_naive <- fin_table_content(
  .ds_contracts = lst_ds$Contracts,
  .con          = con,
  .arm          = "naive",            # before the rules
  .roles        = .fin_roles_recital, # unused on this arm; kept so both calls read alike
  .dirs         = .lP$Output,
  .name         = NULL,               # ContentNaive
  .digits       = c(Mean = 2L, SD = 2L),  # two decimals throughout (decided 16 September)
  .words_scale  = 1000,                   # words in thousands, as the header says
  .ref          = .fin_reference
)
```

## Observation contrast

The same rows, N against N: on how many contracts each measure is defined or found something under
each arm, and the difference. Words have no block because both arms define them on every contract.
Duration is where the cascade adds coverage -- a stated term needs no future date in the text --
and parties, countries and states are where the rules subtract: a recital party is a stricter thing
than an organisation name, and a place attached to one is stricter than a place mentioned.

```{r}
#| label: tbl-content-contrast
#| results: asis

tab_content_contrast <- fin_table_content_contrast(
  .tab_rule  = tab_content_rule,      # the two tables above, same rows
  .tab_naive = tab_content_naive,
  .dirs      = .lP$Output,
  .name      = "ContentContrast"
)
```

## Parties by role

For the two of us, not the manuscript: where the party count comes from. The naive spellings, then
the parties after grouping by the role the rules assigned, their sum, and the two shares that say
how often the extractor found nothing and how often it found the registrant. The recital parties of
the content tables are the first three role columns; signatory-block and other parties are what the
rule-based count leaves out. The two extra role columns are not in the reader's column list and are read
from the release by `DocID`.

```{r}
#| label: tbl-parties
#| results: asis

tab_parties <- fin_table_parties(
  .ds_contracts = lst_ds$Contracts,
  .path_release = .lP$Input$FilContracts,   # nUniSignatory, nUniOther
  .dirs         = .lP$Output,
  .name         = "PartiesDetail"
)
```

## Money by category

For the two of us. How often the extractor found a monetary amount and how many, before and after
the zero and par-value filter, in USD and in other currencies; and the largest and the median USD
amount as medians across contracts. Medians, because the release documents a defect in the amounts
themselves -- flattened HTML tables glued adjacent cells into one figure on roughly 1,500 contracts --
and a mean of maxima measures that defect. The money columns are not in the reader's column list and are
read from the release by `DocID`.

```{r}
#| label: tbl-money
#| results: asis

tab_money <- fin_table_money(
  .ds_contracts = lst_ds$Contracts,
  .path_release = .lP$Input$FilContracts,   # the seven money columns
  .dirs         = .lP$Output,
  .name         = "MoneyDetail"
)
```

## Values, and where each end date comes from

What each content measure is worth under the naive and the rule-based reading, and which rung of the duration
cascade answered; from the appendix's Chapter D, read from the release.

```{r}
#| label: build-values
st_values <- c(
  ContentValues = oad_build_values(
    .path_contracts = .lP$Input$FilContracts,   # the naive and rule-based content columns
    .dir_own        = .lP$DirOwn,
    .force          = .lP$Build$Rebuild,
    .path_lib       = .lP$Pipeline$Lib
  ),
  DurationRungs = oad_build_duration(
    .path_contracts = .lP$Input$FilContracts,   # DurationSource, DurationDropped and the two durations
    .dir_own        = .lP$DirOwn,
    .force          = .lP$Build$Rebuild,
    .path_lib       = .lP$Pipeline$Lib
  )
)

oa_report_builds(.status = st_values)
```

```{r}
#| label: show-values
#| results: asis
fin_show_built(
  .names = names(st_values),
  .dirs  = .lP$Output
)
```

## The two readings, at a glance

The appendix's one content table (decided 16 September): it replaces the observation contrast and the values table
there. For each measure, the share of contracts on which it takes a value and what it is worth, under the naive and
the rule-based reading, totals only; the category rows stay in the tibbles above. Rule-based countries and states
are the content table's -- places attached to any recital party -- with the registrant and counterparty split
beneath. Nothing is computed anew, and the means two builders compute separately are checked against each other.

```{r}
#| label: tbl-content-readings
#| results: asis
tab_content_readings <- fin_table_content_readings(
  .dirs = .lP$Output,
  .name = "ContentReadings"
)
```

## Content characteristics over time

Mean per year of duration, countries, parties and words. Decided on 9 September: the median goes
(it is flat at 1 and 2 for countries and parties) and a band replaces it; the band is what is open.
One function, four forms under their own sub-headers, all on the rule-based arm of the content table.

### A. Mean with one standard deviation

The 9 September decision as stated. The SD exceeds the mean on words and duration, so the lower edge
is cut at zero and the band says "wide" more than it says anything about the trend.

```{r}
#| label: fig-content-time-sd
#| results: asis
#| fig-cap: "Mean per year of the content measures with a one-SD band, unique-contract sample."
#| fig-height: !expr plot_height(12L)

fig_content_time_sd <- fin_figure_content_time(
  .ds_contracts = lst_ds$Contracts,
  .con          = con,                      # Places, for the rule-based countries
  .form         = "sd",
  .measures     = c("Duration", "Countries", "Parties", "Words"),   # add "States" for a fifth panel
  .dirs         = .lP$Output,
  .name         = NULL                      # ContentTimeSD
)
```

### B. Mean with the interquartile range

```{r}
#| label: fig-content-time-iqr
#| results: asis
#| fig-cap: "Mean per year of the content measures with the interquartile range, unique-contract sample."
#| fig-height: !expr plot_height(12L)

fig_content_time_iqr <- fin_figure_content_time(
  .ds_contracts = lst_ds$Contracts,
  .con          = con,
  .form         = "iqr",
  .measures     = c("Duration", "Countries", "Parties", "Words"),
  .dirs         = .lP$Output,
  .name         = NULL                      # ContentTimeIQR
)
```

### C. Mean with its confidence interval

The uncertainty of the mean rather than the spread of the contracts. With forty to sixty thousand
contracts a year the band is thin, which is the message: the movements are not noise.

```{r}
#| label: fig-content-time-ci
#| results: asis
#| fig-cap: "Mean per year of the content measures with its 95 percent confidence interval, unique-contract sample."
#| fig-height: !expr plot_height(12L)

fig_content_time_ci <- fin_figure_content_time(
  .ds_contracts = lst_ds$Contracts,
  .con          = con,
  .form         = "ci",
  .measures     = c("Duration", "Countries", "Parties", "Words"),
  .dirs         = .lP$Output,
  .name         = NULL                      # ContentTimeCI
)
```

### D. Index, one panel

Every measure relative to its 2001 mean, so the four trends sit on one axis: the sentence the text
makes -- words up, duration down -- as one picture.

```{r}
#| label: fig-content-time-index
#| results: asis
#| fig-cap: "The content measures' means per year relative to 2001 (= 100), unique-contract sample."
#| fig-height: !expr plot_height(8L)

fig_content_time_index <- fin_figure_content_time(
  .ds_contracts = lst_ds$Contracts,
  .con          = con,
  .form         = "index",
  .measures     = c("Duration", "Countries", "Parties", "Words"),
  .dirs         = .lP$Output,
  .name         = NULL                      # ContentTimeIndex
)
```

# Geography

## Maps

Places attached to a party, on the unique-contract sample, the rule-based arm: where the
counterparties are, and where the registrant's own footprint is. Two forms under their own
sub-headers. The ranked map takes the full width, fills every area and numbers the ten largest in
circles; their names, counts and shares are set into the map's empty corner (`.counts = "inset"`,
decided 10 September) and written into the note as well; `"note"` leaves the map alone and
`"table"` puts the list beside it. The flow
map draws a curve from the registrant's place to the counterparty's, which is the contracting
relation referee 1 asked about. Colombia and Iceland are suppressed on the country panels until
the gazetteer is fixed (Open Issues).

### A. States, counterparties

```{r}
#| label: fig-map-states-counterparty
#| results: asis
#| fig-cap: "Contracts by the U.S. state attached to a counterparty, unique-contract sample."
#| fig-height: !expr plot_height(8L)
#| fig-width: 8

fig_map_states_cp <- fin_figure_map(
  .con      = con,
  .panel    = "State",
  .roles    = "counterparty",               # contracting locations
  .top      = 10L,
  .counts   = "inset",                  # the ten set into the map's empty corner; the note has them too
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "MapStatesCounterparty"
)
```

### B. States, every recital party

```{r}
#| label: fig-map-states-recital
#| results: asis
#| fig-cap: "Contracts by the U.S. state attached to a recital party, unique-contract sample."
#| fig-height: !expr plot_height(8L)
#| fig-width: 8

fig_map_states_all <- fin_figure_map(
  .con      = con,
  .panel    = "State",
  .roles    = .fin_roles_recital,           # registrant, co-filers, counterparties
  .top      = 10L,
  .counts   = "inset",                  # the ten set into the map's empty corner; the note has them too
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "MapStatesRecital"
)
```

### C. Countries, counterparties

```{r}
#| label: fig-map-countries-counterparty
#| results: asis
#| fig-cap: "Contracts by the country attached to a counterparty, unique-contract sample."
#| fig-height: !expr plot_height(8L)
#| fig-width: 8

fig_map_countries_cp <- fin_figure_map(
  .con      = con,
  .panel    = "Country",
  .roles    = "counterparty",
  .top      = 10L,
  .counts   = "inset",                  # the ten set into the map's empty corner; the note has them too
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "MapCountriesCounterparty"
)
```

### D. Countries, every recital party

```{r}
#| label: fig-map-countries-recital
#| results: asis
#| fig-cap: "Contracts by the country attached to a recital party, unique-contract sample."
#| fig-height: !expr plot_height(8L)
#| fig-width: 8

fig_map_countries_all <- fin_figure_map(
  .con      = con,
  .panel    = "Country",
  .roles    = .fin_roles_recital,
  .top      = 10L,
  .counts   = "inset",                  # the ten set into the map's empty corner; the note has them too
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "MapCountriesRecital"
)
```

### E. Flows between states

From the registrant's state to the counterparty's; contracts with both in one state are counted in
the note and not drawn.

```{r}
#| label: fig-flows-states
#| results: asis
#| fig-cap: "The largest flows from the registrant's state to the counterparty's state, unique-contract sample."
#| fig-height: !expr plot_height(8L)

fig_flows_states <- fin_figure_flows(
  .con      = con,
  .panel    = "State",
  .top      = 25L,
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "FlowsStates"
)
```

### F. Flows from the United States to the world

```{r}
#| label: fig-flows-countries
#| results: asis
#| fig-cap: "The largest flows from a U.S. registrant to the counterparty's country, unique-contract sample."
#| fig-height: !expr plot_height(8L)

fig_flows_countries <- fin_figure_flows(
  .con      = con,
  .panel    = "Country",
  .top      = 20L,
  .suppress = .fin_map_suppress,
  .dirs     = .lP$Output,
  .name     = "FlowsCountries"
)
```

## Geographic diversity

Her `104` step for step: one contract per firm and fiscal year, the top percentile of both variables
dropped, 85 equal-count bins, the line from an OLS on the firm-years. Two things the manuscript's
note says that the code does not do -- "trim at the 99th percentile" and "50 bins" -- so the note
written here describes the code, and the choice is on the page as arguments. Decided on 9 September
for the online appendix.

```{r}
#| label: fig-diversity
#| results: asis
#| fig-cap: "Countries mentioned per contract against segment geographical diversity, bin means and the OLS line."
#| fig-height: !expr plot_height(8L)

fig_diversity <- fin_figure_diversity(
  .ds_contracts     = lst_ds$Contracts,
  .ds_concentration = lst_ds$Concentration,   # 101's segment diversity, one row per gvkey-year
  .grain            = "first",                # 104's rule; "mean" for the firm-year mean
  .bins             = 85L,                    # 104's binscatter; the note said 50
  .trim             = "drop",                 # 104 drops the top percentile; "p99" clips instead
  .dirs             = .lP$Output,
  .name             = "Diversity"
)
```

# Redactions

## Orders, their links, and the text markers

Confidential treatment orders from the order to the contract it covers (the appendix's Chapter A), the orders on
the forms Ahci (2025) covers, and the orders against the text markers from 2008 to 2018 -- the last two data only,
for the numbers.

```{r}
#| label: build-orders
st_orders <- c(
  CtoLinkage = do.call(oaa_build_cto, c(.b_a, list(
    .path_orders    = .lP$Input$FilCtoOrders,   # one row per reference an order makes
    .path_contracts = .lP$Input$FilContracts    # the release's flag on the sample
  ))),
  CtoAhci    = num_build(
    .name    = "CtoAhci",                       # orders on the forms Ahci (2025) covers
    .fun     = \() num_data_cto_ahci(
      .path_orders = .lP$Input$FilCtoOrders,
      .to          = .lP$Build$AhciTo
    ),
    .inputs  = c(.lP$Input$FilCtoOrders, .lP$Pipeline$Lib),
    .dir_own = .lP$DirOwn,
    .force   = .lP$Build$Rebuild
  ),
  CtoMarkers = num_build(
    .name    = "CtoMarkers",                    # orders against text markers, 2008-2018
    .fun     = \() num_data_cto_markers(
      .path_contracts = .lP$Input$FilContracts,
      .min_markers    = .lP$Build$MinMarkers
    ),
    .inputs  = c(.lP$Input$FilContracts, .lP$Pipeline$Lib),
    .dir_own = .lP$DirOwn,
    .force   = .lP$Build$Rebuild
  )
)

oa_report_builds(.status = st_orders)
```

```{r}
#| label: show-orders
#| results: asis
fin_show_built(
  .names = names(st_orders),
  .dirs  = .lP$Output
)
```

## Redactions by category

On the redaction window from 2008, two identifications side by side. The text: the share of
contracts whose text carries at least one redaction marker (the manuscript's measure), and, among
those contracts, how many markers they carry and how many carry five or more -- the threshold the
notes record and `103` does not apply. The SEC: the share of the 2008-2018 contracts under a
granted order. A contract can be in either, both or neither, which is why the two are columns and
not one. The other marker kinds and the price-withholding count stay in the data file (decided 10
September).

```{r}
#| label: tbl-redactions
#| results: asis

tab_redact <- fin_table_redactions(
  .ds_contracts = lst_ds$Contracts,         # the marker counts, coalesced to zero at read time
  .dirs         = .lP$Output,
  .name         = "RedactionsDetail"
)
```

## Redactions over time

The two identifications as the revision draws them: orders through 2018, order-or-markers
throughout. Unique contracts from 2008. The report prints the revision's readings beside the
render; `.markers = TRUE` adds the marker-only line for an appendix version.

```{r}
#| label: fig-redactions-time
#| results: asis
#| fig-cap: "Share of contracts with redactions per year, two identifications, unique contracts from 2008."
#| fig-height: !expr plot_height(5L)

fig_redactions_time <- fin_figure_redactions_time(
  .ds_contracts = lst_ds$Contracts,
  .markers      = FALSE,                    # TRUE adds the marker-only series
  .dirs         = .lP$Output,
  .name         = "RedactionsTime",
  .ref          = .fin_reference_f10       # the revision's readings, checked on the render
)
```

## Redactions by category over time

Ann-Kristin's ask of 18 September: the redaction share per contract type over the years, in the shape the contract
types already have. The old draft drew twelve lines in one frame. Two forms, as for the types: a panel per category,
or a panel per super-category with its sub-categories as lines. Once one is chosen it takes the stem
`RedactionsTypes` and the other goes. The measure is the paper's, so the dashed line sits on 2019, the year it
changes from orders to markers.

### A. One panel per category

```{r}
#| label: fig-redactions-types-a
#| fig-cap: "Share of contracts redacted per year and category, a panel per category, contracts from 2008."
#| fig-height: !expr plot_height(18L)

fig_redactions_types_a <- fin_figure_redactions_types(
  .ds_contracts = lst_ds$Contracts,
  .form         = "a",                      # twelve panels, four to a row
  .dirs         = .lP$Output,
  .name         = "RedactionsTypesA"
)
```

### B. One panel per super-category, sub-categories as lines

```{r}
#| label: fig-redactions-types-b
#| fig-cap: "Share of contracts redacted per year, a panel per super-category, contracts from 2008."
#| fig-height: !expr plot_height(12L)

fig_redactions_types_b <- fin_figure_redactions_types(
  .ds_contracts = lst_ds$Contracts,
  .form         = "b",                      # seven panels, the sub-categories labelled at the line's end
  .dirs         = .lP$Output,
  .name         = "RedactionsTypesB"
)
```

## Redactions by industry and category

The cell is the share redacted among the contracts of that industry and category, which is what
referee 2 asked for; the revision's version averaged year-by-category shares within industry, which
is why its rows barely differed. Three figures from one tibble -- the whole window from 2008, before
the FAST Act, after it -- on one fill scale, because the measure changes meaning at 2019 and two
rows in one figure were too small to read. Matched contracts from 2008. Her reading of "full sample
classification" for this figure is still open (Open Issues).

### A. From 2008

```{r}
#| label: fig-redactions-heat-all
#| results: asis
#| fig-cap: "Share of contracts redacted within industry and category, contracts from 2008."
#| fig-height: !expr plot_height(12L)
#| fig-width: 10

fig_redactions_heat_all <- fin_figure_redactions_heat(
  .ds_contracts = lst_ds$Contracts,
  .ds_quarter   = lst_ds$Quarter,           # the industry of the filing firm
  .period       = "all",
  .min_n        = 30L,                      # cells below this are grey with a dash
  .limit        = 0.8,                      # top of the fill, shared by the three
  .accuracy     = 0.1,                      # one decimal in every cell
  .strips       = "top",                    # super-categories above their columns, as text
  .dirs         = .lP$Output,
  .name         = NULL                      # RedactionsIndustryAll
)
```

### B. Before the FAST Act

```{r}
#| label: fig-redactions-heat-pre
#| results: asis
#| fig-cap: "Share of contracts redacted within industry and category, before the FAST Act."
#| fig-height: !expr plot_height(12L)
#| fig-width: 10

fig_redactions_heat_pre <- fin_figure_redactions_heat(
  .ds_contracts = lst_ds$Contracts,
  .ds_quarter   = lst_ds$Quarter,
  .period       = "pre",
  .min_n        = 30L,
  .limit        = 0.8,
  .accuracy     = 0.1,
  .strips       = "top",
  .dirs         = .lP$Output,
  .name         = NULL                      # RedactionsIndustryPre
)
```

### C. After the FAST Act

```{r}
#| label: fig-redactions-heat-post
#| results: asis
#| fig-cap: "Share of contracts redacted within industry and category, after the FAST Act."
#| fig-height: !expr plot_height(12L)
#| fig-width: 10

fig_redactions_heat_post <- fin_figure_redactions_heat(
  .ds_contracts = lst_ds$Contracts,
  .ds_quarter   = lst_ds$Quarter,
  .period       = "post",
  .min_n        = 30L,
  .limit        = 0.8,
  .accuracy     = 0.1,
  .strips       = "top",
  .dirs         = .lP$Output,
  .name         = NULL                      # RedactionsIndustryPost
)
```

# Item 1.01 announcements

Three tables on the announcement sample: single-agreement Item 1.01 8-Ks carrying at most one
Exhibit 10. Delayed means the 8-K carried no contract -- it came later, in a periodic filing;
attached means it rode on the 8-K. First the measures, defined once; then the revision's
comparison, replaced on the release with the three measures the export added; then the same nine
measures as outcomes of a regression on the delay indicator, which asks what the comparison cannot:
whether the same firm writes differently when it delays.

## The announcement sample

From every Item 1.01 8-K the pipeline recovered to the sample the tests run on. The single-agreement
restriction is a proxy -- the number of distinct agreement-date openings in the narrative -- and the
ladder shows what it costs on each side.

```{r}
#| label: tbl-summary-sample
#| results: asis

tab_summary_sample <- fin_table_summary_sample(
  .ds_summaries = lst_ds$Summaries,
  .dirs         = .lP$Output,
  .name         = "SummarySample"
)
```

## The announcement lag

Its tails before winsorising, and the winsorised mean the tables report. For the authors; the
manuscript carries the decision in the notes.

```{r}
#| label: tbl-summary-lag
#| results: asis

tab_summary_lag <- fin_table_summary_lag(
  .ds_summaries = lst_ds$Summaries,
  .sample       = "S7_Summaries",
  .winsor       = c(0.01, 0.99),            # the clip points every summary table uses
  .dirs         = .lP$Output,
  .name         = "SummaryLag"
)
```

## Summary measures

```{r}
#| label: tbl-summary-variables
#| results: asis

tab_summary_variables <- fin_table_summary_variables(
  .dirs = .lP$Output,
  .name = "SummaryVariables"
)
```

## Delayed against attached

```{r}
#| label: tbl-summaries
#| results: asis

tab_summaries <- fin_table_summaries(
  .ds_summaries = lst_ds$Summaries,
  .sample       = "S7_Summaries",           # the paper's announcement sample
  .dirs         = .lP$Output,
  .name         = "Summaries"
)
```

## Delayed against attached, the text measures only

The same table without the announcement lag and the four-business-day indicator (decided 10
September); the nine-row version above stays.

```{r}
#| label: tbl-summaries-text
#| results: asis

tab_summaries_text <- fin_table_summaries(
  .ds_summaries = lst_ds$Summaries,
  .sample       = "S7_Summaries",
  .measures     = c("Words", "Fog", "Uncertainty", "Numbers", "Dollars", "Percents", "Boilerplate"),
  .dirs         = .lP$Output,
  .name         = "SummariesText"
)
```

## The delay indicator in a regression

Nine outcomes across, three specifications down: year effects; year and firm effects, which asks
whether the same firm's delayed summaries differ from its attached ones; and the resubmission's
firm-quarter controls on the announcements matched to a fiscal quarter. Delayed announcements
carry no contract row and hence no Compustat key, so every announcement, delayed or attached, is
matched by one rule -- the firm's first quarter ending on or after the filing, at most a hundred
days later. Standard errors clustered by firm.

```{r}
#| label: tbl-summaries-regression
#| results: asis

tab_summaries_regression <- fin_table_summaries_regression(
  .ds_summaries = lst_ds$Summaries,
  .ds_quarter   = lst_ds$Quarter,           # the controls
  .con          = con,                      # the quarter match
  .sample       = "S7_Summaries",
  .controls     = .fin_controls$Resubmission,
  .dirs         = .lP$Output,
  .name         = "SummariesRegression"
)
```

## The delay indicator in a regression, the text measures only

```{r}
#| label: tbl-summaries-text-regression
#| results: asis

tab_summaries_text_regression <- fin_table_summaries_regression(
  .ds_summaries = lst_ds$Summaries,
  .ds_quarter   = lst_ds$Quarter,
  .con          = con,
  .sample       = "S7_Summaries",
  .measures     = c("Words", "Fog", "Uncertainty", "Numbers", "Dollars", "Percents", "Boilerplate"),
  .controls     = .fin_controls$Resubmission,
  .dirs         = .lP$Output,
  .name         = "SummariesTextRegression"
)
```

# Validation

The checks this document runs are the ones its exhibits carry: every table note states the sample it is drawn on
and its N, written from the count, and the writer warns where the assumed N differs; the manifest under Deployment
is checked on disk. Every number the paper cites from these exhibits is resolved and validated by `50-Numbers`,
which reads `Output/Data` and reports any key the manuscript or the appendix cites without a definition. The
comparison of this document against its two predecessors (30 and 40) was retired when it took the name 30.

# Deployment

Every exhibit this document writes lands under `Output/` by its name: the tibble under `Data`,
the tabular under `Tables`, the figure under `Figures`, the note under `Notes`. The manifest lists
them by stem with the sample each is drawn on and which files exist, checked on disk, and goes to
`Output/Manifest.csv`; the `Where` column -- manuscript, online appendix, memo -- is empty until it
is decided and is the list to decide it on.

The paper reads from `200-Paper_figures/current/` on Dropbox: `Figures/`, `Tables/`, `Notes/`, the
manifest and this document's html. A deployment first moves the previous `current/` to
`_archive/<timestamp>/`, never overwriting, and writes a `VERSION.txt` with the deploy time and the
release date. The html of the render that is running cannot be copied from inside it -- Quarto
writes it last -- so the chunk copies the html that exists and records its time, and one line from
the console after the render, `fin_deploy_html()`, refreshes it. The exhibit tibbles do not go to
the paper folder; they are the replication site's business.

While 30 and 40 still write their own exhibits and the consumers read theirs, the deployment from here is a dry
run: it names what it would archive and copy and touches nothing. It is switched on once `50-Numbers` and the
appendix chapters read this document's output.

```{r}
#| label: deploy-manifest
#| results: asis

tab_manifest <- fin_manifest(
  .dirs     = .lP$Output,
  .registry = .fin_registry,                # every stem, its kind, its sample
  .path     = utils_file_path(.dir_main, "Output", "Manifest.csv")
)
```

```{r}
#| label: deploy-paper

fin_deploy_paper(
  .dirs      = .lP$Output,
  .dir_paper = .lP$Paper,                                  # 200-Paper_figures on Dropbox
  .path_html = fs::path(.dir_main, "30-FinalExhibits.html"),
  .manifest  = tab_manifest,                               # refuses an incomplete set
  .release   = .lP$Params$ReleaseMin,                      # recorded in VERSION.txt
  .run       = TRUE                                       # dry run until the consumers read 31
)

# AFTER THE RENDER, from the console, to put this render's html beside the exhibits:
# fin_deploy_html(.path_html = fs::path(.dir_main, "30-FinalExhibits.html"), .dir_paper = .lP$Paper)
```

# Overview

```{r}
#| label: overview-samples

tbl_out(
  .tab   = tab_samples,
  .title = "The named samples every exhibit cites"
)

tibble::tibble(
  Parameter = names(.lP$Params),
  Value     = as.character(unlist(.lP$Params))
) |>
  tbl_out(.title = "The choices this render made")
```

```{r}
#| label: overview-topics
.fin_registry |>
  dplyr::mutate(
    Topic = factor(.data$Topic, levels = names(.fin_topic_of)),   # the runbook's order
    Kind  = factor(.data$Kind, levels = c("Table", "Figure", "Data"))
  ) |>
  dplyr::count(
    dplyr::across(dplyr::all_of(c("Topic", "Kind"))),
    name = "Exhibits"
  ) |>
  tidyr::pivot_wider(
    names_from  = "Kind",
    values_from = "Exhibits",
    values_fill = 0L,
    names_sort  = TRUE
  ) |>
  tbl_out(.title = "Exhibits by topic, as registered")
```

# Explanations

Definitions a reader of the tables above will ask about, written once here rather than repeated
under each table. Every note refers back to this section by its heading.

## Naive against rule-based extraction

Every content measure except words exists in two arms. The **naive** arm is what the extractor
proposed before any rule was applied; the **rule-based** arm is what the pipeline's rules made of
it. The two are built from the same rows, so where they differ they differ in exactly one
definition, and the observation contrast above shows where that moves the N.

**Duration.** The naive measure asks one question of the text: is there a calendar date written out
that lies after the filing date? If so, duration is the farthest such date less the start date,
uncapped; if not, it is undefined. The rule-based measure is a cascade that stops at the first rung
that answers: (1) a **stated term** -- "for a period of five years from the Effective Date",
"36 months" -- from which the end is computed as start plus term and no future date need appear in
the text; (2) an **open-ended clause** -- "until terminated by either party"; (3) a **cue-word
date** -- a future date with MATURITY, THROUGH or EXPIRE beside it; (4) the **farthest future
date**, which is the naive rule as the fallback. The stated term alone answers 56 percent of
contracts, which is why the rule-based arm is defined on far more contracts than the naive one
(779,440 against 450,940 on the unique-contract sample): everything the naive rule answers, rung
four answers too, and rungs one to three add the contracts that state their length in words rather
than as a date. Employment compensation plans are the extreme case -- "ten years from the date of
grant" -- and their N more than doubles. In the other direction the cascade caps at 30 years and
drops the rest, and drops negative spans; uncapped, a single mistyped year dominates a mean, which is
why the naive arm gives leases a mean of 35 years with a standard deviation of 400 and the cascade
4.2 with 4.4.

**Parties.** The naive count is the number of distinct organisation names the extractor proposed,
before grouping merged spellings of one organisation into one party -- about eight per contract.
The rule-based count is the parties in the recital: the registrant, its co-filers and the
counterparties, after grouping and after role assignment -- about two. A recital party is a stricter
thing than a name, so the rule-based arm finds at least one party on fewer contracts than the naive
arm finds a name.

**Countries and states.** The naive counts are every distinct country, and every distinct U.S.
state, named outside a governing-law clause, attached to a party or not; a state mention carries its
country, so nearly every contract names at least one country. The rule-based counts are the distinct
countries and states attached to a recital party, outside a governing-law clause, which is the count
that reads as a contracting location rather than a mention. The law-clause places are excluded from
both because they are jurisdictions, not locations. States are U.S. states, so foreign parties
contribute none, and the state count is a U.S.-footprint measure rather than a geography measure.
Parties, countries and states use one role set -- registrant, co-filers, counterparties -- so the
three columns describe the same parties; the parties-by-role table shows what the other roles add.

**Words.** The naive count is the words of the flattened text; the rule-based count subtracts the
words the filing header contributed. Both are defined on every contract, and the difference is
eleven words on the mean.

## The diversity figure, line by line

What `104` does to draw the geographic-diversity figure, beside the argument of
`fin_figure_diversity()` that does the same thing, so the equivalence is on the page and not in a
memory (checked again on 10 September at Ann-Kristin's request).

| `104_Figures.do` | What it does | `30` | Same? |
|:--|:--|:--|:--|
| `drop if Keep == 0` (at the top of `104`) | unique contracts only | `S3_Matched` (`Keep` and a matched quarter) | yes; `104`'s later merge to Compustat drops the unmatched anyway |
| `duplicates drop gvkey fyear, force` | one contract per firm and fiscal year: the first row in Stata's memory order | `.grain = "first"`: the first by `DocID` | the same rule; not the same row. Stata's row order at that point is whatever the preceding steps left, which nobody can reproduce, and `104` does not sort first |
| `merge 1:1 gvkey fyear using concentration.dta` | attach `101`'s segment diversity; unmatched firm-years keep going with diversity missing | `fin_data_f07()` joins the prepared Concentration; rows without diversity drop | equivalent: `binscatter` drops missing diversity itself |
| `xtile xdiversity = diversity, nq(100)` / `xtile xloc_count = nUniCountryNaive, nq(100)` / `drop if xdiversity == 100` / `drop if xloc_count == 100` | the top percentile of each variable is **dropped** | `.trim = "drop"` | yes |
| `binscatter nUniCountryNaive diversity, nquantiles(85)` | 85 equal-count bins of diversity; the dot is the bin mean of the country count | `fin_bins_f07(.bins = 85)` | yes |
| `reportreg` | the line is an OLS of the country count on diversity over the underlying firm-years | `fin_bins_f07()$Fit` | yes: 1.14 with t 35.0 on 75,930 firm-years, against the revision's 1.2 and 33 |
| the manuscript's note | "trim both variables at the 99th percentile and use 50 bins" | -- | the note describes neither the tail rule nor the bin count the code uses |

Two things follow. First, the figure in this document reproduces her code, up to the row Stata
happened to keep per firm-year, and the residual difference in the slope (1.14 against 1.2) is
that row. Second, the note has to move or the code has to move. The recommendation is the code:
`.grain = "mean"` (each firm-year contributes the mean country count of its contracts, which is
what "countries mentioned in the firm's contracts" means), `.trim = "p99"` (winsorise both
variables, as the note says) and `.bins = 50` (as the note says). On the 8 September release that
gives a slope of 1.84 with t 63.9 on 77,481 firm-years; the direction and the sentence in the
text do not change, and the figure becomes reproducible by anyone with the release. Recorded
under Open Issues, decision with Ann-Kristin.

**Zero against missing.** Parties, countries and states are counts and are zero, not missing, where nothing
was extracted; duration is missing where no end was established, and only duration carries its own
N in the notes.

# Open Issues

What the tables above turned up that needs a decision, with the evidence on the page. Each item
names the options and the recommendation; the decision is Ann-Kristin's and Matthias's, and once
taken it is recorded here and the item closed.

## Contracts without readable text were in the descriptive sample (closed 10 September)

735 contracts in the unique-contract sample carried no category, and every one of them had zero
words: the exhibit is a placeholder for a PDF or an image -- "EXHIBIT 10.1 PDF REFERENCE",
"ORIGINAL ARABIC PDF REFERENCE" -- and no classifier, extractor or word count ever saw text. They
passed `02B`'s malformed test because that test is about format, not about whether any text
survived, and they sat on every rung of the ladder. Decided with Ann-Kristin and done the same day:
`10-ExportData` folds the copies without a classification into the malformatted rung
(`exp_fold_unclassified()`); the release of 10 September has 1,135,360 unique contracts and every
one of them carries a class. The probe below is kept as the check that it stays so: it should
report zero.

```{r}
#| label: issue-unlabelled

lst_unlabelled <- fin_issue_unlabelled(
  .ds_contracts = lst_ds$Contracts,
  .path_release = .lP$Input$FilContracts   # nChars, not in the reader's column list
)
```

Decision: closed. Folded at the export, no new ladder row; malformatted 32,029, unique contracts
1,135,360, firms 26,914. Her `102`/`103` rerun on this release is still pending.

## The resubmission's control set shrinks the estimation samples by a fifth

Her `105` and `106` now control for the revision's set plus market-to-book and product-market
fluidity (referee 2's request), and drop the Herfindahl and the one-quarter sales change. Fluidity
is missing on roughly two quarters in five. On the 9 September release, Panel B of the sample
table on that set gives a contract-level sample of 523,687 (revision: 647,429), 171,840 firm-quarters
(209,692) and 9,735 firms (12,303); the firm-level sample 335,249 quarters (462,572) and 9,080 firms
(12,017). Every regression in `106` inherits this. Options: keep fluidity as a control and report the
smaller samples; move fluidity to a robustness column and keep the larger samples for the main
tables; impute nothing. `.fin_controls$Revision` reproduces the old ladder for comparison.

Decision: open.

## Panel B counts registrant copies

`106` estimates on every registrant copy of a contract (it never filters `Keep == 1`), so Panel B of
the sample table counts copies, as the revision did, while Panel A counts unique contracts. The
primary-copy count rides in `Data/SampleSelection.parquet`. Either the note says that Panel B is at
copy grain, or `106` moves to primary copies and Panel B follows.

Decision: open.

## Marker threshold for the textual redaction measure

The project notes record a minimum of five markers post-2018 to match the historical rate; `103`
applies one. With one marker the 2008-2018 textual rate is 3.9 percent against 3.2 percent under
orders; with five it is 3.1. The redactions table above reports, by category, the share of marked
contracts with five or more, which is the fact the threshold decision needs. `Params$RedactMin`
carries the choice.

Decision: open.

## Vintage

The `Summaries` release on Dropbox predates 9 September (harmless: no geography count on it) and her
`103` outputs predate the corrected release. Table 2 Panel B, the firm-level tables and the redaction
reconciliation close only after her `102`/`103` rerun on the 9 September export.

Decision: open, waiting on the rerun.

## The single-agreement filter is a date proxy

The announcement sample keeps Item 1.01 8-Ks whose narrative names exactly one agreement, and
`01D` implements "exactly one agreement" as exactly one distinct "On <Month> <D>, <YYYY>" opening
in the text. Two agreements signed the same day pass; one agreement whose narrative repeats a
second date -- an amendment date, an effective date -- is dropped. The ladder above the summary
tables shows the N on each side. `01D`'s own comment says the pattern will be widened; candidates
are counting "entered into" clauses or agreement nouns. That is a `01D` change and a `10`
re-export, not a change here.

Decision: acceptable for now, stated in the note; widening deferred.

## The diversity figure's note does not describe its code

Three gaps between `104` and the revision's note, and one between `104` and reproducibility:

| | `104` does | the note says | `30` default |
|:--|:--|:--|:--|
| Grain | one contract per firm-year, the first in Stata's current row order | "the number of unique countries mentioned in the material contracts" | first by `DocID` (deterministic; not the same row) |
| Tail | drops the top percentile of both variables | "trim both variables at the 99th percentile" | drop |
| Bins | 85 | 50 | 85 |

The figure here follows the code, and its note says what the code does. The Stata row order is not
reproducible by anyone, so "the same figure" cannot be promised whatever we do.

Recommendation: change the code, not the note. `.grain = "mean"` (each firm-year contributes the
mean country count of its contracts, which is what "countries mentioned in the firm's contracts"
means and what a referee expects), `.trim = "p99"` (winsorise, as the note says), `.bins = 50` (as
the note says). On the 8 September release that gives slope 1.84 and t 63.9 against 1.14 and 35.1;
the direction and the sentence in the text are unchanged. All three are arguments on the call, so
the switch is one line and the note rewrites itself.

Decision: open -- Ann-Kristin to confirm the mean grain; then `104` and `30` say the same thing.

## Which broad label the release carries

`03B` states that the published broad label is the roll-up of the detailed prediction, not the
separately fitted broad model. The release's `ClassBroad` disagrees with the parent of `Class` on
29,607 unique contracts (2.6 percent), so the export appears to carry the broad head. The transformer
table above scores both readings -- the super rows are the roll-up -- and whichever the paper
describes is the one `10` should export.

Decision: open; check `03F` / `10`.

## Nine copies with a class but no word count

On the 9 September release, nine copies carry a classification -- so the classifier saw text --
but `nWords` is missing. That is a gap on the text-metrics side of `10`'s assembly (or a missing
count in `01C`), not a sample problem: the copies stay in the sample with their class, and every
word-based exhibit drops a missing count. Worth finding which join left them behind.

Decision: open; check the `nWords` join in `10`.

## Monetary amounts carry glued figures

Flattened HTML tables glued adjacent cells into one number on roughly 1,500 contracts, so the
largest USD amount is unusable as a mean and only medians are reported. A fix is in `04B4`, not
here; until then no manuscript exhibit reports a mean amount.

Decision: medians only; fix deferred.

## One stem, one exhibit: what the renames leave to do (opened 16 September)

The six full classification tables carry `Full` here, and 30's `ClassArmsCeiling` is `ClassArmsFullCeiling`. Five
of the cuts write the full tibble as their own data, so the plain-named tibbles hold the rows `50-Numbers` reads
today; the arms cut writes the arms and the ceiling rows together, with a `Block` column. When 40 is pointed here,
its rows that read `ClassArmsCeiling` move to `ClassArmsFullCeiling`, and its rows that read `ClassArms` get their
filter checked against the combined tibble.

Decision: open, with the re-pointing of 40.

## Every PDF came from the base pdf device (opened 16 September, decided 17 September)

On this machine `cairo_pdf` left no file, so `plot_save()` fell back to the base `pdf` device for every figure,
and the render warned once per figure. Overleaf reads the PNG, so the figures are now written as PNG only: no pdf
device is opened, the manifest and the deployment count a figure complete with its png, and a pdf an earlier
render left in `Output/Figures` is not deployed.

Decision: PNG only.

## Which mean the amounts row reports (opened 18 September)

The content readings table checks the means two builders compute apart, and they part on the amounts: 4.74 figures
read per contract against 6.53, and 4.40 kept in dollars against 6.06. The first pair counts a contract without an
amount as zero, as the paper counts every other content measure; the second is the mean over the contracts on which
an amount was read, which is what `ContentValues` computes and what the appendix prints today. The readings table
prints the first pair. Chapter D's sentence -- amounts falling from 6.53 to 6.06 -- is the second and has to say
which it means, or change.

Decision: open.

## The contract table is wider than the text block (opened 17 September)

Every fragment now carries the manuscript's frame: row spacing 1.2, a `tabular*` filling `\columnwidth`, `\hline`
rules, centred headers, no size command. Nothing is scaled; the frame cuts the column padding instead, and reports
a table that does not fit even at the tightest. Measured in the class at `\footnotesize`, the text block is 408 pt
and the content table with its eleven number columns wants about 500 pt, 414 pt at the tightest padding. It is
scaled for now, and the render names it. Three ways out: the means alone, without the five SD columns (about
349 pt); the table split in two, words and duration over parties and places (317 pt and 342 pt); or scaling this
one table. Ann-Kristin's own descriptive table has the same trouble on a smaller scale -- 435 pt as it stands, which
the frame's padding step would fix.

Decision: open.

## Two switches for one redaction rule (opened 16 September)

`Params$RedactMin` (30's, the prepared contract table) and `Build$MinMarkers` (40's, `CtoMarkers`) state the same
rule twice, both at one marker. One of them goes in the clean-up; the marker-threshold issue above decides the value.

Decision: open.

# Next

1. Render, and read the table under Validation: every file "same", or a difference explained.
2. Point `50-Numbers` at this document's `Output/Data` alone, remove its builders, and move its rows for the renamed
   tibbles; `Numbers.tex` must come out unchanged apart from its date line.
3. Point the `42-OnlineAppendix` chapters at this document's output, stop them sourcing 40's library for builders,
   and let `oa_publish()` deploy the fragment alone. Chapter D then sets `ContentReadings` in place of
   `ContentContrast` and `ContentValues`, whose tibbles stay for the numbers.
4. Deploy from here (`.run = TRUE`) and give Overleaf one exhibits folder.
5. The agreed standardization of figures and tables, topic by topic, in this document.
6. Move this document back to `30-FinalExhibits`, and retire the old 30 and 40's exhibit outputs.
