---
title: "Online Appendix -- The Appendix Text, Rendered for Overleaf (31)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS ONLY. init_*() resolve this document's paths and tbl_say() is the fixed-width printer every report
# below uses. No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "31-OnlineAppendix"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is the online appendix. Its text is written here once and rendered twice: to html, the runbook a
reader of the replication site follows, and to a LaTeX fragment that the paper's Overleaf project inputs. The
fragment carries the appendix and nothing else. Everything that makes this a runbook -- this section, the
configuration, the checks -- sits in blocks the LaTeX pass removes.

This first version is the structure: the five sections, every exhibit in its place, and the machinery the text
needs. Most passages are still marked as to be written or to be decided, and Validation counts them.

## Why the text lives here and not in Overleaf

Most sentences of the appendix carry a number the pipeline produced -- the size of the labelled sample, a macro-F1, a
coverage. Typed into Overleaf, each of those is a copy that stops being true the next time an upstream stage runs,
and nothing reports it. Written here, a number is read from the tibble 30 wrote beside the exhibit that prints it,
so the sentence and the table cannot disagree.

The cost is that the fragment is not a file to edit. An edit made to it in Overleaf is lost at the next render;
comments and suggested changes come back into this document.

## What the fragment may contain

Prose, headings, citations, numbers, cross-references and floats. No code and no console output: the LaTeX pass
renders with code hidden, every chunk that prints sits inside a block that pass removes, and the functions that
write into the appendix itself never print through `cli`. The headings map onto the appendix's own numbering: a
level-two heading here is a lettered section there, a level-three heading a numbered subsection.

## Floats point at 30's files

Every table and figure in the appendix is one 30 already writes under its name: the tabular in `Tables/`, the note in
`Notes/`, the figure in `Figures/`. The fragment reads them by name through one macro, `\oaexhibits`, which the
Overleaf file sets to wherever those folders sit in the project. What this document decides about an exhibit is its
caption and its place, and both are in one table under Configuration. The three tables the paper already holds as
files of its own -- the regulation overview and the two EDGAR variable lists -- are read through a second macro,
`\oastatic`. A table from 30 is input bare: 30's writer gives every table its own frame -- size, row spacing, the
text width, and a box that shrinks a wide one -- so a float adds nothing around it.

The html shows each exhibit where the paper prints it, numbered as the paper numbers it: a figure as 30's png copy, a
table as 30's own tabular converted by the Pandoc that Quarto runs. So the two renders set the same content, and the
html can be read as the appendix. The static tables live only in the Overleaf project and appear here as a framed
line naming the file.

An exhibit 30 has not built yet is not an error. It is set as a framed line naming it, so the paper still compiles,
and Validation lists it. With `Strict` on, it stops the render instead.

## Why there is no Overview

A runbook collects its figures in an Overview at the end. Here the body is the appendix itself, and its figures stand
where the paper prints them; an Overview would print every one of them a second time, so it is omitted.

## Numbers come from 30's tibbles

Every number the text cites is declared once, under Numbers: the exhibit it comes from, the column, and the rows. A
number that does not resolve is set in the text as a bold marker carrying its key, in both renders, and listed.

## What is recomputed, and what is not

Everything, on every render, once per format. Nothing here is expensive -- a few small parquet reads and file checks
-- so nothing is cached beyond keeping each tibble read once within a pass.

## Where things are written

Two files. Quarto writes the fragment to `_rendered/1_code/31-OnlineAppendix.tex`, beside this document's html, but
only in the LaTeX pass, which the Render button does not run: RStudio renders the first format the YAML lists, and
that is this html. And every render writes `Output/OA-Numbers.tex` under this document's output directory: the
numbers the text cites, as macros the manuscript can use too. `oa_publish()` renders both passes, copies the two
files to the paper folder, and lists which of them changed -- which, while Overleaf is updated by hand, is the list of
files to upload. See Deployment.

# Configuration

```{r}
#| label: configure
.lP <- list(
  # THE DROPBOX ROOT, used for deployment only; nothing is read from it.
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict   = FALSE, # TRUE stops the render on an exhibit 30 has not built or a number that does not resolve
    FigWidth = 0.96   # a figure's width as a share of the text width, as the previous appendix set it
  )
)

.lP$Input <- list(
  # 30'S OUTPUT, READ IN PLACE: Data/ for the numbers, and Tables/, Notes/ and Figures/ to check what the fragment
  # will ask Overleaf for. Pointing this at the deployed current/ folder is this one line, once 30 deploys Data/ too.
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),       # the LaTeX pass's template
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"), # the html pass's bibliography
  Qmd         = here::here("1_code", "31-OnlineAppendix.qmd")            # this document, scanned for markers
)

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "31-OnlineAppendix.tex"),  # written by Quarto, in the LaTeX pass
  Numbers = utils_file_path(.dir_main, "Output", "OA-Numbers.tex"),      # written below, on every render
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")    # where oa_deploy_tex() copies both
)

# A FRESH RECORD FOR THIS PASS. The emitters in the text record what they set, and Validation reads the record.
oa_state_reset()
```

## The appendix's exhibits

One row per exhibit, in the order the appendix prints them. `Name` is the stem 30 writes every file under, and
`Caption` is the only text about an exhibit written here. An exhibit that is planned but not built is registered like
any other: it is set as a placeholder now and becomes the real float the first time 30 writes it.

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,                  ~Kind,    ~Caption,
  "A",      "FilingRequirements",   "table",  "Exhibits required with each form",
  "A",      "FilingTypes",          "figure", "Contracts by filing type",
  "A",      "FilingsWithinYear",    "figure", "Contract filings within the calendar year",
  "A",      "FilingsSeasoned",      "figure", "Contract filings of all filers and of seasoned filers",
  "B",      "MasterIndexVariables", "table",  "Variables of the SEC EDGAR master index",
  "B",      "LandingPageVariables", "table",  "Variables of the SEC EDGAR filing landing pages",
  "B",      "SampleAttrition",      "table",  "What each sample requirement costs",
  "C",      "ClassLabelled",        "table",  "The labelled sample",
  "C",      "ClassSweep",           "table",  "Transformer model selection",
  "C",      "ClassTransformer",     "table",  "Transformer classifier: out-of-fold scores by category",
  "C",      "ClassConfusion",       "table",  "Transformer classifier: confusion matrix",
  "C",      "ClassAmendment",       "table",  "Amendment classifier: out-of-fold scores",
  "C",      "ClassKeyword",         "table",  "Keyword tables: out-of-fold scores by category",
  "C",      "ClassArms",            "table",  "All classification approaches compared",
  "C",      "ClassConfidence",      "table",  "Classifier confidence in the corpus, by category",
  "D",      "NerEngines",           "table",  "Entity extractors compared on the labelled sample",
  "D",      "PartiesDetail",        "table",  "Contract partners by role",
  "D",      "DurationRungs",        "table",  "The source of each contract's end date",
  "D",      "MoneyDetail",          "table",  "Monetary amounts by category",
  "D",      "RedactionsDetail",     "table",  "Redaction markers by category",
  "D",      "ContentContrast",      "table",  "Naive and rule-based content variables",
  "E",      "TypesTimeA",           "figure", "Contract types over time",
  "E",      "ContentTimeSD",        "figure", "Content characteristics over time",
  "E",      "Diversity",            "figure", "Geographic dispersion of contracts and segment diversity"
)
```

The three static tables are files the paper already holds, so they are read from the Overleaf project through
`\oastatic` and cannot be checked here. Their notes are written out below, because no `Notes/` file exists for them.

```{r}
#| label: configure-static
.note_requirements <- paste(
  "Source: 17 C.F.R. 229.601 (2022). The table lists the documents that must be filed as exhibits to each form.",
  "An X marks a document required with the form even if it was filed previously with another document; a",
  "previously filed document may be incorporated by reference. * An exhibit need not be provided about a company",
  "if an election has been made under Form S-4 or F-4 to provide information about it at the level prescribed",
  "by Form S-3 or F-3, and the form so elected would not require the exhibit for a primary offering."
)

tab_static <- tibble::tribble(
  ~Name,                  ~File,                            ~Note,
  "FilingRequirements",   "appendix_C1_filing_requirement", .note_requirements,
  "MasterIndexVariables", "OA_MasterIndex",                 "The variables of the master index acquisition step.",
  "LandingPageVariables", "OA_LandingPage",                 "The variables of the landing page parsing step."
)
```

The context joins the two tables, checks them, and records for every exhibit what 30 must have written for the
fragment to set it.

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats       = tab_floats,                  # the appendix's exhibits, in print order
  .static       = tab_static,                  # the three read from the Overleaf project
  .dir_exhibits = .lP$Input$DirExhibits,       # where 30 writes Tables/, Notes/ and Figures/
  .dir_doc      = fs::path_dir(.lP$Input$Qmd), # html image paths are written relative to this document
  .fig_width    = .lP$Params$FigWidth,         # every figure at this width
  .strict       = .lP$Params$Strict            # stop on a missing exhibit rather than mark it
)

oa_report_floats(.files = ctx_oa$Files)
```

Read the status before the text. Ready means the fragment asks Overleaf for files that exist here; whether Overleaf
holds them too depends on what was uploaded there, which this document cannot see.

# Input

30 is the only source. This document calls none of 30's functions and reads only what 30 wrote, so it renders on the
state of 30's last render -- and says so if 30 has not rendered at all.

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits, # 30's output, read in place
  .template     = .lP$Input$Template,    # without it the LaTeX pass fails
  .bib          = .lP$Input$Bib          # without it the html pass cannot resolve a citation
)
```

# Numbers

Each row is one number the text cites. `Where` is a filter over the exhibit tibble's own columns, evaluated as
written; `Fun` reduces the matching rows to one value, and `one` demands exactly one matching row, which is what
catches a filter that silently matches two. The keyword table's coverage and accuracy are taken from the comparison
of all approaches rather than from its own table: that table's total row averages recall over categories, where the
comparison counts documents.

```{r}
#| label: numbers-resolve
# A LEAF OF THE TAXONOMY is a sub-category, or a category without sub-categories. The smallest leaf bounds how thin a
# fold can become, which is the argument for pooled out-of-fold scoring in section C.
.where_leaf <- "Level1 != 'Amendment' & (Kind == 'sub' | Level1 %in% c('Licenses', 'Leases', 'Other'))"
.where_kw   <- "Task == 'ClassDetailed' & Engine == 'Kw'"
.where_llm  <- "Task == 'ClassDetailed' & Engine == 'Llm'"

tab_numbers_spec <- tibble::tribble(
  ~Key,              ~Exhibit,           ~Column,         ~Fun,  ~Format, ~Where,
  "NLabelled",       "ClassLabelled",    "N",             "one", "count", "Kind == 'total'",
  "NRarest",         "ClassLabelled",    "N",             "min", "count", .where_leaf,
  "AccDetailed",     "ClassTransformer", "Accuracy",      "one", "prop3", "Kind == 'total'",
  "F1Detailed",      "ClassTransformer", "F1",            "one", "prop3", "Kind == 'total'",
  "LenientDetailed", "ClassTransformer", "RecallLenient", "one", "prop3", "Kind == 'total'",
  "AccAmend",        "ClassAmendment",   "Accuracy",      "one", "prop3", "Label == 'Total'",
  "F1Amend",         "ClassAmendment",   "F1",            "one", "prop3", "Label == 'Total'",
  "KwCoverage",      "ClassArms",        "Coverage",      "one", "pct1",  .where_kw,
  "KwAccCommitted",  "ClassArms",        "AccuracySel",   "one", "prop3", .where_kw,
  "F1Llm",           "ClassArms",        "MacroF1",       "one", "prop3", .where_llm
)

tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,                       # every number the text cites
  .dir_data = fs::path(.lP$Input$DirExhibits, "Data") # the tibbles behind 30's exhibits
)

oa_report_numbers(
  .tab    = tab_numbers,      # resolved above
  .strict = .lP$Params$Strict # TRUE stops the render on an unresolved number
)
```

The same numbers are written as LaTeX macros, so the manuscript cites them too rather than typing copies that go
stale at the next re-export: with the file input in the paper's preamble, `\oanum{F1Detailed}` prints the macro-F1
this render resolved. A key the file does not hold prints in bold as `??Key`, so a typo shows in the PDF.

```{r}
#| label: numbers-write
oa_numbers_write(
  .tab  = tab_numbers,         # resolved above
  .path = .lP$Output$Numbers   # deployed beside the fragment
)
```

:::

::: {.content-visible when-format="html"}

# Online appendix

Everything from here to Validation is the appendix: shown here as the runbook renders it, and written in the LaTeX
pass as the fragment Overleaf inputs. Each exhibit stands where the paper prints it, with the paper's number: figures
from 30's png copies, tables converted from 30's own LaTeX.

:::

```{=latex}
\clearpage
```

## SEC filing requirements and filing timing {#sec-oa-filing}

Firms can append material contracts to several SEC forms, and the form determines when a contract becomes public.
This section documents which forms require which exhibits, how the contracts in the database distribute across
forms, when in the calendar year they are filed, and how the registration wave of 2020 and 2021 enters the annual
counts.

### Filing requirements by form {#sec-oa-filing-requirements}

`r oa_ref(.name = "FilingRequirements")` lists the exhibits Item 601 of Regulation S-K requires with each Securities
Act and Exchange Act form. The database covers Exhibit 10 filed with Forms 8-K, 10-K, 10-Q, 20-F, S-1, S-4, F-1 and
F-4, including their amendments.

```{r}
#| label: float-filing-requirements
#| results: asis
oa_float(.name = "FilingRequirements")
```

### Filing types {#sec-oa-filing-types}

`r oa_ref(.name = "FilingTypes")` shows the unique contracts by the form they were filed with, U.S. and foreign
forms side by side, each split into original agreements and amendments. **[TO WRITE: the amendment share, which is
higher than in the previous draft, and the reason.]**

```{r}
#| label: float-filing-types
#| results: asis
oa_float(.name = "FilingTypes")
```

### Filings within the calendar year {#sec-oa-filing-year}

**[TO WRITE: the within-year distribution of ad-hoc, annual and quarterly filings, with the reporting seasons of
December year-end filers marked; the figure is still to be built in 30.]**

```{r}
#| label: float-filings-within-year
#| results: asis
oa_float(.name = "FilingsWithinYear")
```

### Seasoned filers {#sec-oa-filing-seasoned}

The number of contracts rises sharply in 2020 and 2021. `r oa_ref(.name = "FilingsSeasoned")` compares all filers
with firms more than two years past their first contract filing. Had the rise come from existing firms filing more,
it would appear among the seasoned filers; it does not, so it reflects new registrants, among them many special
purpose acquisition companies that file a standard set of equity agreements at registration.

```{r}
#| label: float-filings-seasoned
#| results: asis
oa_float(.name = "FilingsSeasoned")
```

```{=latex}
\clearpage
```

## Data collection and sample construction {#sec-oa-data}

The database is built from EDGAR in four steps -- the quarterly master index, the landing page of every filing in
scope, the attached documents, and a set of quality rules -- implemented in the rGetEDGAR package and the pipeline's
acquisition scripts. This section documents the decisions in each step that determine what the database contains;
the mechanics are documented in the pipeline's runbooks on the replication site.

### Acquisition {#sec-oa-data-acquisition}

The frame is every filing of seventeen form types in EDGAR's quarterly master index through 2024: the periodic
reports, the current report, the registration statements that carry material agreements, each with its amendment
variant, and the confidential treatment order. For each filing, the landing page lists the attached documents. An
attachment counts as Exhibit 10 where its exhibit type maps to Exhibit 10 in a lookup of the raw exhibit-type
strings filers use, rather than where it matches a pattern: filers write `EX-10.1`, `EX-10`, `EXHIBIT 10.23` and many
further variants, and a pattern silently excludes the spellings its author did not anticipate. Three groups of
documents are downloaded: Exhibit 10 attachments, 8-K filings reporting Item 1.01, and confidential treatment
orders. `r oa_ref(.name = "MasterIndexVariables")` and `r oa_ref(.name = "LandingPageVariables")` list the variables
the first two steps record. **[TO DECIDE: keep the two variable lists, or replace them with the release codebook.]**

```{r}
#| label: float-master-index
#| results: asis
oa_float(.name = "MasterIndexVariables")
```

```{r}
#| label: float-landing-page
#| results: asis
oa_float(.name = "LandingPageVariables")
```

### Quality rules {#sec-oa-data-quality}

Three rules flag documents whose conversion to text failed: ten words or fewer after the SEC header; fewer than 20%
stopwords together with fewer than 100 words; or 75% or more numeric tokens. Each threshold sits far from anything a
genuine agreement produces, so the rules remove conversion debris -- a PDF rendered as coordinates, a hyperlink in
place of a document, a financial statement filed under an exhibit number -- rather than short agreements. Flagged
documents stay in the release with the reason and are excluded from the samples. Exhibits whose text is only a
placeholder for a PDF or an image carry no readable text and are counted with the malformatted documents.
**[TO WRITE: the counts, from the sample table.]**

### Attachments and registrant copies {#sec-oa-data-copies}

A filing can list several registrants, and EDGAR lists its attachments under each of them, so one attachment can
appear as several documents. Each attachment is identified by a hash of its address and each registrant's copy by
its own identifier, and one copy per attachment is designated primary. Classification and entity extraction read
the primary copy once; the release carries every copy with its attachment's values, so unique contracts are the
primary copies and every registrant's copy remains available to an analysis at the filer level. Two parties that
each file their own copy of one agreement produce two attachments; finding those would require comparing texts and
is not attempted. **[TO DECIDE: the estimation samples count registrant copies while the descriptive sample counts
unique contracts; say so in the sample table's note, or move the estimation to primary copies.]**

### Sample construction {#sec-oa-data-ladder}

**[TO WRITE: the steps from the full index to the descriptive sample and the estimation samples, as in
`r oa_ref_main(.name = "SampleSelection", .kind = "table")`, and what each requirement costs on its own.]**

```{r}
#| label: float-sample-attrition
#| results: asis
oa_float(.name = "SampleAttrition")
```

```{=latex}
\clearpage
```

## Contract classification {#sec-oa-classification}

Each contract is classified on three tasks, all from the same text: its type in the twelve categories of
`r oa_ref_main(.name = "Categories", .kind = "table")` (detailed), the seven parent categories (broad), and whether it
is an original agreement or an amendment. Four approaches are evaluated on identical cross-validation folds -- a
fine-tuned transformer, a keyword table, a local language model, and routing between them -- and the transformer
labels the corpus.

### Taxonomy and labelled sample {#sec-oa-class-sample}

The labelled sample holds `r oa_n(.key = "NLabelled")` contracts with readable text
(`r oa_ref(.name = "ClassLabelled")`). The labels come from two rounds: a first round mapped from an earlier coding
scheme, and a second round of direct manual classification aimed at the categories the current taxonomy introduced.
A contract that fits two categories carries a second label. Training uses the primary label only, which was set by
manual review; the second label is used only to score leniently. The broad taxonomy is a strict roll-up of the
detailed one, and the smallest detailed category holds `r oa_n(.key = "NRarest")` contracts. **[TO WRITE: the
labelling protocol, the annotation tool, and who labelled; agreement between annotators is not measured.]**

```{r}
#| label: float-class-labelled
#| results: asis
oa_float(.name = "ClassLabelled")
```

### Evaluation design {#sec-oa-class-design}

Folds are dealt once, stratified on the detailed category, and every approach is scored on the same five folds. Each
contract is predicted once, by the fold model that did not see it in training, and the scores pool these out-of-fold
predictions. No test set is held out beyond the folds: with `r oa_n(.key = "NRarest")` contracts in the smallest
category, a further holdout would leave too few documents to estimate that category's performance. The headline
metric is macro-F1, the unweighted mean of the per-category F1 scores, because accuracy is dominated by the largest
categories; accuracy is reported beside it. Lenient scores count a prediction as correct where it equals the
contract's second valid category, so the gap between strict and lenient scores measures ambiguity in the taxonomy
rather than error in the model.

### Transformer classifier {#sec-oa-class-transformer}

Two encoders are fine-tuned, Legal-BERT [@chalkidis2020legal] and RoBERTa [@liu2019roberta], on every combination of
two learning rates (2e-5 and 3e-5), two context lengths (256 and 512 tokens), two training budgets (three and six
epochs), and loss weighting by inverse class frequency or none, separately for each task. A learning rate of 1e-5
and ten epochs were each evaluated against the centre of the grid and did not improve on it, so they are not carried
through the full crossing. `r oa_ref(.name = "ClassSweep")` reports every configuration; the configuration with the
highest macro-F1 is refitted on the full labelled sample and deployed at both context lengths. **[TO DECIDE: which
configuration is crowned.]**

Out of fold, the deployed detailed classifier reaches an accuracy of `r oa_n(.key = "AccDetailed")` and a macro-F1
of `r oa_n(.key = "F1Detailed")` (`r oa_ref(.name = "ClassTransformer")`); counting a contract's second valid category
as correct raises accuracy to `r oa_n(.key = "LenientDetailed")`. The errors concentrate in adjacent categories
(`r oa_ref(.name = "ClassConfusion")`), the same pairs that produced second labels during manual labelling. The
amendment classifier reaches an accuracy of `r oa_n(.key = "AccAmend")` and a macro-F1 of `r oa_n(.key = "F1Amend")`
(`r oa_ref(.name = "ClassAmendment")`). **[TO DECIDE: whether the released broad label is the roll-up of the
detailed prediction or the separately trained broad model.]**

```{r}
#| label: float-class-sweep
#| results: asis
oa_float(.name = "ClassSweep")
```

```{r}
#| label: float-class-transformer
#| results: asis
oa_float(.name = "ClassTransformer")
```

```{r}
#| label: float-class-confusion
#| results: asis
oa_float(.name = "ClassConfusion")
```

```{r}
#| label: float-class-amendment
#| results: asis
oa_float(.name = "ClassAmendment")
```

### Keyword tables {#sec-oa-class-keyword}

The keyword approach is built as a published artifact rather than as a competing classifier: a short, ranked table
of terms per category that anyone can apply to a filing with a text editor, with a stated precision. A term's
evidence is the Wilson lower bound on its training precision [@wilson1927probable], which ranks a term found in 190
of 200 contracts above one found in 2 of 2. A term is admitted only where its precision exceeds the category's base
rate, where it catches contracts no accepted term caught, and where at least three of the five fold mines selected
it; a contract is assigned the category of the single strongest term that fires. The tables target a precision of
95% for contract types and 85% for amendments, and abstain where no term fires. Out of fold, the detailed table
commits on `r oa_n(.key = "KwCoverage")`% of contracts, with an accuracy of `r oa_n(.key = "KwAccCommitted")` where
it commits (`r oa_ref(.name = "ClassKeyword")`). **[TO WRITE: the mined and the generated term lists, and how the
generated lists were produced; the generated list is estimated on the fifth fold only.]**

```{r}
#| label: float-class-keyword
#| results: asis
oa_float(.name = "ClassKeyword")
```

### Language model and routing {#sec-oa-class-routing}

**[TO DECIDE: report the language-model arm or leave it out.]** A local instruction-tuned model, Qwen3 with eight
billion parameters, classifies each contract from its opening characters, either from the category names alone or
with worked examples drawn from the other folds, so that no prompt contains a contract from the fold it scores. On
the detailed task it reaches a macro-F1 of `r oa_n(.key = "F1Llm")`. `r oa_ref(.name = "ClassArms")` compares all
approaches on every task and reports the accuracy a perfect router would reach by taking any approach's correct
answer. **[TO WRITE: the two routing rules -- the transformer's own confidence, and disagreement between its
detailed and broad models -- and what they gain.]**

```{r}
#| label: float-class-arms
#| results: asis
oa_float(.name = "ClassArms")
```

### Application to the corpus {#sec-oa-class-apply}

The deployed transformer labels every Exhibit 10 attachment once, reading its primary copy, and the release carries
the label on every registrant copy. The keyword table runs over the same attachments as an independent second
opinion; where it fires, the release records whether the two agree. The transformer's probability for the category
it chose is released with each label, so an analysis can restrict itself to confident classifications
(`r oa_ref(.name = "ClassConfidence")`). **[TO WRITE: which context length labels the corpus, and why.]**

```{r}
#| label: float-class-confidence
#| results: asis
oa_float(.name = "ClassConfidence")
```

```{=latex}
\clearpage
```

## Entity extraction and rule-based variables {#sec-oa-entities}

Contract partners, places, dates, monetary amounts and redaction markers are extracted in two stages. Extractors
propose spans of text, each stored with its character offsets in the contract; rules then turn the spans into
variables. The release carries both the naive variables, which count what the extractors proposed, and the
rule-based variables, so an analysis that rejects a rule can fall back to the step before it.

### Extractors {#sec-oa-ent-extractors}

Three families of extractors ran over the labelled sample: LexNLP [@bommarito2021lexnlp]; a set of pattern and
gazetteer extractors written for this database, covering dates, stated terms, monetary amounts, places, redaction
markers and governing-law clauses; and the named-entity recogniser of spaCy. Every span is stored as offsets into the
text, so a later rule can relate spans to each other -- a place to the party named before it, a redaction marker to
the amount it replaced -- without reading the contract again. **[TO WRITE: why spaCy was not applied to the corpus
-- its throughput, and where in a contract its organisation names fall.]**

```{r}
#| label: float-ner-engines
#| results: asis
oa_float(.name = "NerEngines")
```

### Contract partners {#sec-oa-ent-parties}

LexNLP proposes organisation names, and a rule turns them into parties in four steps. It strips legal suffixes, so
that ACME CORPORATION and ACME CORP. share one key; groups the spellings of one company within a contract; matches
the parties against the registrant EDGAR records, by prefix for the filer and exactly for the co-registrants of the
same filing; and assigns roles: registrant, co-registrant, counterparty where named within 2,000 characters of the
registrant, signatory where named in the final tenth of the contract, and other. Where no party matches the filer,
the first party named is taken as the registrant, and the release records that fallback. The parties the paper
counts are the registrant, the co-registrants and the counterparties. **[TO WRITE: how often the fallback applies.]
[TO DECIDE: whether the parties-by-role table belongs in the appendix.]**

```{r}
#| label: float-parties-detail
#| results: asis
oa_float(.name = "PartiesDetail")
```

### Places and governing law {#sec-oa-ent-places}

Places come from a gazetteer built from the U.S. Geological Survey's domestic names and international country data.
A place name that is also an English word, such as Enterprise, Mobile or Reading, is accepted only where a state or
country name follows it directly, and any other place name only where a state or country is named nearby; a name
that exists in several states, such as Springfield, is assigned a state only where the contract itself names one of
its candidate states. A place belongs to the party named within 200 characters before it. Places inside a
governing-law clause name a jurisdiction rather than a location and are excluded from the geography counts; the
jurisdictions are released separately, every one a contract names.

### Dates and duration {#sec-oa-ent-dates}

Every date pattern requires a year written in the text, so the extractor cannot supply a year the contract does not
state; numeric dates are read month first, as in U.S. filings. A contract's start is the latest date at or before
its filing date, or the filing date where no such date exists. Its end comes from the first of four sources present:
a stated term ("for a period of five years"), an open-ended clause ("until terminated"), which leaves the duration
missing, a future date next to an end cue (maturity, through, expiration), and the farthest future date. Durations
above 30 years are dropped rather than capped. The naive duration, from the farthest future date alone, is released
beside it. **[TO WRITE: the share of contracts each source answers.]**

```{r}
#| label: float-duration-rungs
#| results: asis
oa_float(.name = "DurationRungs")
```

### Monetary amounts {#sec-oa-ent-money}

An amount is recognised only together with a currency marker, which excludes section numbers by construction. Zero
amounts, and figures with par-value language within 60 characters on either side, are dropped; figures a filer
withheld, such as `$[***]`, are counted separately and never summed. A known defect remains: flattened tables can
join adjacent cells into a single figure, so only medians are reported. **[TO DECIDE: whether the money table
belongs in the appendix.]**

```{r}
#| label: float-money-detail
#| results: asis
oa_float(.name = "MoneyDetail")
```

### Redaction markers {#sec-oa-ent-redactions}

Six kinds of marker are identified: brackets naming confidential treatment, brackets of asterisks, brackets of
underscores, brackets recording an omission, brackets of bullets or ellipses, and unbracketed runs of three or more
asterisks. The release counts each kind, so every definition of a redacted contract is a sum of released columns;
the paper's measure counts bracketed asterisks and explicit redactions. A marker that sits inside a withheld amount
identifies a withheld price. **[TO DECIDE: whether one marker or five define a redacted contract after 2018.]**

```{r}
#| label: float-redactions-detail
#| results: asis
oa_float(.name = "RedactionsDetail")
```

### Naive and rule-based variables {#sec-oa-ent-contrast}

`r oa_ref(.name = "ContentContrast")` reports, by category, on how many contracts each measure is defined or finds
something under the naive and under the rule-based definition. **[TO WRITE: where the rules add coverage -- a stated
term needs no future date -- and where they remove it.]**

```{r}
#| label: float-content-contrast
#| results: asis
oa_float(.name = "ContentContrast")
```

```{=latex}
\clearpage
```

## Additional descriptive evidence {#sec-oa-descriptives}

### Contract types over time {#sec-oa-desc-types}

`r oa_ref(.name = "TypesTimeA")` shows the composition of each year's contracts by super-category, with the share of
amendments as a line. **[TO DECIDE: which of the four forms of this figure.]**

```{r}
#| label: float-types-time
#| results: asis
oa_float(.name = "TypesTimeA")
```

### Content characteristics over time {#sec-oa-desc-content}

`r oa_ref(.name = "ContentTimeSD")` shows the yearly mean of duration, countries, parties and words, with a band of
one standard deviation. **[TO DECIDE: the band -- standard deviation, interquartile range or confidence interval.]**

```{r}
#| label: float-content-time
#| results: asis
oa_float(.name = "ContentTimeSD")
```

### Geographic diversity {#sec-oa-desc-diversity}

`r oa_ref(.name = "Diversity")` relates the number of countries the contracts of a firm-year mention to the
geographic diversity of the firm's segment sales. **[TO DECIDE: the grain, the treatment of the tails and the number
of bins.]**

```{r}
#| label: float-diversity
#| results: asis
oa_float(.name = "Diversity")
```

::: {.content-visible when-format="html"}

# Validation

Two checks on the text itself. **Every registered exhibit is set exactly once, in the registry's order**: a registered
exhibit the text never sets would be listed as ready above and be absent from the paper, with nothing else to say so.
**The open markers are counted by section**, which is the appendix's progress report while it is being written.

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

The fragment is written only by the LaTeX pass. A terminal render, `quarto render 1_code/31-OnlineAppendix.qmd`, runs
both passes, html first; the Render button runs the html alone. Either way, the check below sees the fragment as it
stood before this render began.

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,        # the fragment as the last LaTeX pass left it
  .path_qmd     = .lP$Input$Qmd,         # a fragment older than this document or its library is stale
  .dir_exhibits = .lP$Input$DirExhibits  # and so is one older than what 30 wrote
)
```

To bring Overleaf up to date, one call from the console. It renders both passes in a separate R process, as a
terminal render would, checks that the fragment and the numbers file were written by this call, copies them to the
paper folder, archives the ones they replace, and ends with the files that changed -- the ones to upload.

```r
source(here::here("1_code", "31-OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "31-OnlineAppendix.qmd"),                          # this document
  .path_tex     = here::here("_rendered", "1_code", "31-OnlineAppendix.tex"),             # the LaTeX pass writes it
  .path_numbers = here::here("2_output", "31-OnlineAppendix", "Output", "OA-Numbers.tex"), # every render writes it
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),                   # tested for staleness
  .dir_deploy   = fs::path(                                                               # the paper folder
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL                                                                    # found as a terminal would
)
```

The fragment goes to `online_appendix/` in the Overleaf project, and so does `OA-Numbers.tex`, which the paper's
preamble inputs once: `\input{online_appendix/OA-Numbers}`. 30's exhibits reach Overleaf as they always have, from
`200-Paper_figures/current/`.

On the Overleaf side, `9-online_appendix.tex` sets the lettered numbering, points `\oaexhibits` and `\oastatic` at the
project's folders, and inputs the fragment.

# Next

The three static tables move into 30 as exhibits of its own, written through the same frame as every other table;
the static path here then disappears. The appendix's text follows, section by section, starting with classification,
and the manuscript's method section switches its numbers to `\oanum{}`.

:::
