---
title: "Online Appendix -- The Appendix Text, Rendered for Overleaf (31)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS ONLY. init_*() resolve this document's paths, tbl_say() is the fixed-width printer every report below
# uses, and _Plots.R gives the figures built here the house theme. No upstream library is sourced: this document
# reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "31-OnlineAppendix"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is the online appendix. Its text is written here once and rendered twice: to html, the runbook a
reader of the replication site follows, and to a LaTeX fragment that the paper's Overleaf project inputs. The
fragment carries the appendix and nothing else. Everything that makes this a runbook -- this section, the
configuration, the checks -- sits in blocks the LaTeX pass removes.

This version is the first full draft of the text. The appendix has six sections -- the filings, the two packages,
classification, entity extraction, additional analysis, data access -- and every passage is written as far as the
facts in hand allow. What is still open is marked in the text as to write, to decide or to verify, and Validation
counts the markers by section.

## Why the text lives here and not in Overleaf

Most sentences of the appendix carry a number the pipeline produced -- the size of the labelled sample, a macro-F1, a
coverage. Typed into Overleaf, each of those is a copy that stops being true the next time an upstream stage runs,
and nothing reports it. Written here, a number is read from the tibble 30 wrote beside the exhibit that prints it,
so the sentence and the table cannot disagree.

The cost is that the fragment is not a file to edit. An edit made to it in Overleaf is lost at the next render;
comments and suggested changes come back into this document.

## What the fragment may contain

Prose, headings, citations, numbers, cross-references and floats. No code and no console output: the LaTeX pass
renders with code hidden, every chunk that prints sits inside a block that pass removes, and the functions that
write into the appendix itself never print through `cli`. The headings map onto the appendix's own numbering: a
level-two heading here is a lettered section there, a level-three heading a numbered subsection.

## Floats point at 30's files

Almost every table and figure in the appendix is one 30 already writes under its name: the tabular in `Tables/`, the
note in `Notes/`, the figure in `Figures/`. The few 30 does not have yet are built by this document itself, in the
same layout, and read through a macro of their own, `\oaown`; Build explains which and how. The fragment reads them by
name through one macro, `\oaexhibits`, which the Overleaf file sets to wherever those folders sit in the project. What
this document decides about an exhibit is its caption and its place, and both are in one table under Configuration. A
table the paper holds as a file of its own, outside 30, can be read through a second macro, `\oastatic`; none is
registered at present. A table from 30 is input bare: 30's writer gives every table its own frame -- size, row
spacing, the text width, and a box that shrinks a wide one -- so a float adds nothing around it.

The html shows each exhibit where the paper prints it, numbered as the paper numbers it: a figure as 30's png copy, a
table as 30's own tabular converted by the Pandoc that Quarto runs. So the two renders set the same content, and the
html can be read as the appendix.

An exhibit 30 has not built yet is not an error. It is set as a framed line naming it, so the paper still compiles,
and Validation lists it. With `Strict` on, it stops the render instead.

## Why there is no Overview

A runbook collects its figures in an Overview at the end. Here the body is the appendix itself, and its figures stand
where the paper prints them; an Overview would print every one of them a second time, so it is omitted.

## Numbers come from 30's tibbles

Every number the text cites is declared once, under Numbers: the exhibit it comes from, the column, and the rows. A
number that does not resolve is set in the text as a bold marker carrying its key, in both renders, and listed.

## What is recomputed, and what is not

The text, the numbers and the floats on every render, once per format: a few small parquet reads and file checks.
The exhibits this document builds itself are the exception. They read the release and the master index, so each
build runs only where its outputs are missing or older than its inputs or this library; `Rebuild` forces them.

## Where things are written

Two files. Quarto writes the fragment to `_rendered/1_code/31-OnlineAppendix.tex`, beside this document's html, but
only in the LaTeX pass, which the Render button does not run: RStudio renders the first format the YAML lists, and
that is this html. And every render writes `Output/OA-Numbers.tex` under this document's output directory: the
numbers the text cites, as macros the manuscript can use too. `oa_publish()` renders both passes, copies the two
files to the paper folder, and lists which of them changed -- which, while Overleaf is updated by hand, is the list of
files to upload. See Deployment.

# Configuration

```{r}
#| label: configure
.lP <- list(
  # THE DROPBOX ROOT: the release is read from it, and deployment writes to it.
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict   = FALSE, # TRUE stops the render on an exhibit that is not built or a number that does not resolve
    FigWidth = 0.96,  # a figure's width as a share of the text width, as the previous appendix set it
    Rebuild  = FALSE  # TRUE rebuilds this document's own exhibits even where their inputs have not changed
  )
)

.lP$Input <- list(
  # 30'S OUTPUT, READ IN PLACE: Data/ for the numbers, and Tables/, Notes/ and Figures/ to check what the fragment
  # will ask Overleaf for. Pointing this at the deployed current/ folder is this one line, once 30 deploys Data/ too.
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  Contracts   = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),            # the release, for the builds
  Orders      = fs::path(.lP$Root, "100_Data_Export", "CtoOrders.parquet"),            # the orders' references
  DirMaster   = rGetEDGAR::get_directories(                                           # the master index 01A mirrors
    here::here("2_output", "01A-EdgarIndex", "GetEDGAR")
  )$MasterIndex$DirParquet,
  Landing     = here::here("2_output", "01A-EdgarIndex", "Output", "LandingPageAll.parquet"), # SIC per filing
  DirKeyword  = here::here("2_output", "03C-ClassifyTrainKeyword", "table"),          # 03C's published tables
  DirEntities = here::here("2_output", "04A-EntityExtract", "Output"),  # 04A's span stores, one per family
  SampleText  = here::here("2_output", "04A-EntityExtract", "Output", "sample_text.parquet"), # document lengths
  Lib         = here::here("1_code", "31-OnlineAppendix.R"),                          # a changed builder rebuilds
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),       # the LaTeX pass's template
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"), # the html pass's bibliography
  Qmd         = here::here("1_code", "31-OnlineAppendix.qmd")            # this document, scanned for markers
)

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "31-OnlineAppendix.tex"),  # written by Quarto, in the LaTeX pass
  Numbers = utils_file_path(.dir_main, "Output", "OA-Numbers.tex"),      # written below, on every render
  DirOwn  = fs::path(.dir_main, "Output"),                               # the exhibits built here, in 30's layout
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")    # where oa_deploy_tex() copies all of it
)

# A FRESH RECORD FOR THIS PASS. The emitters in the text record what they set, and Validation reads the record.
oa_state_reset()
```

## The appendix's exhibits

One row per exhibit, in the order the appendix prints them. `Name` is the stem every file of the exhibit is written
under, `Source` says who writes them -- 30, or this document itself (31) -- and `Caption` is the only text about an
exhibit written here. An exhibit that is planned but not built is registered like
any other: it is set as a placeholder now and becomes the real float the first time 30 writes it.

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,                ~Kind,    ~Source, ~Caption,
  "A",      "RegulatoryTimeline", "table",  "31",    "Regulatory events that shape the database",
  "A",      "FormCoverage",       "table",  "31",    "Forms that carry material contracts, and the database's coverage",
  "A",      "FilingTypes",        "figure", "30",    "Contracts by filing type",
  "A",      "FilingsWithinYear",  "figure", "31",    "Contract filings within the calendar year",
  "A",      "SeasonedFilers",     "figure", "31",    "Contract filings of all filers and of seasoned filers",
  "A",      "SampleAttrition",    "table",  "30",    "What each sample requirement costs",
  "A",      "FluidityMissing",    "table",  "30",    "Firm-quarters without product-market fluidity",
  "C",      "ClassLabelled",      "table",  "30",    "The labelled sample",
  "C",      "CategoryTitles",     "table",  "31",    "The descriptions filers most often give their contracts, by category",
  "C",      "ClassSweep",         "table",  "30",    "Transformer model selection",
  "C",      "ClassTransformer",   "table",  "30",    "Transformer classifier: out-of-fold scores by category",
  "C",      "ClassConfusion",     "table",  "30",    "Transformer classifier: confusion matrix",
  "C",      "ClassAmendment",     "table",  "30",    "Amendment classifier: out-of-fold scores",
  "C",      "ClassKeyword",       "table",  "30",    "Keyword table: out-of-fold scores by category",
  "C",      "KeywordTerms",       "table",  "31",    "The strongest terms of the keyword table, by category",
  "C",      "ClassArms",          "table",  "30",    "All classification approaches compared",
  "C",      "ClassConfidence",    "table",  "30",    "Classifier confidence in the corpus, by category",
  "C",      "TypesTimeC",         "figure", "30",    "Contract types over time",
  "D",      "NerEngines",         "table",  "31",    "Entity extractors compared on the labelled sample",
  "D",      "PartiesDetail",      "table",  "30",    "Contract partners by role",
  "D",      "DurationRungs",      "table",  "31",    "The source of each contract's end date",
  "D",      "MoneyDetail",        "table",  "30",    "Monetary amounts by category",
  "D",      "RedactionsDetail",   "table",  "30",    "Redaction markers by category",
  "D",      "ContentContrast",    "table",  "30",    "Naive and rule-based content variables",
  "E",      "ContentTimeSD",      "figure", "30",    "Content characteristics over time",
  "E",      "Diversity",          "figure", "30",    "Geographic dispersion of contracts and segment diversity"
)
```

No table is read from the Overleaf project at present, so the static table is empty. It keeps its columns, so a
table the paper holds as a file of its own can be registered here again: its name, its file under `\oastatic`, and
its note, since no `Notes/` file exists for it.

```{r}
#| label: configure-static
tab_static <- tibble::tibble(
  Name = character(0), # the exhibit's name in the registry above
  File = character(0), # its file stem under \oastatic in the Overleaf project
  Note = character(0)  # its note, written out here
)
```

# Input

30 is the only source. This document calls none of 30's functions and reads only what 30 wrote, so it renders on the
state of 30's last render -- and says so if 30 has not rendered at all.

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits, # 30's output, read in place
  .template     = .lP$Input$Template,    # without it the LaTeX pass fails
  .bib          = .lP$Input$Bib          # without it the html pass cannot resolve a citation
)
```

# Build

Some exhibits the appendix needs are not among 30's, and for now this document builds them itself: into its own
output directory, in the layout 30 uses, read by the fragment through `\oaown` as 30's are read through
`\oaexhibits`. Their rows in the registry carry `Source` 31, so moving one to 30 later changes one field and moves one
function. Every exhibit this appendix needs beyond 30's is built here: the regulatory timeline, the coverage table, the
within-year figure, the seasoned-filer figure, which replaces 30's version so that its three panels rest on one
source, the table of filer descriptions, the keyword table's strongest terms, the comparison of extractors, and the
sources of a contract's end date. One build prints nothing: it writes the counts the text of Appendix A cites, which
belong to no table.

A build runs when its inputs change. The release and the master index are large and change rarely, and the render runs
twice, so each build compares its outputs with its inputs and with this document's library, and runs only where an
output is missing or older. `Rebuild` forces them all.

```{r}
#| label: build-exhibits
st_build <- c(
  RegulatoryTimeline = oa_build_timeline(
    .dir_own  = .lP$Output$DirOwn,  # this document's own exhibits
    .force    = .lP$Params$Rebuild, # TRUE rebuilds regardless
    .path_lib = .lP$Input$Lib       # a changed builder rebuilds
  ),
  FormCoverage = oa_build_coverage(
    .dir_master     = .lP$Input$DirMaster, # filings per form type
    .path_contracts = .lP$Input$Contracts, # the contracts the database holds
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  FilingsWithinYear = oa_build_within_year(
    .path_contracts = .lP$Input$Contracts, # filing dates of the unique contracts
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  CategoryTitles = oa_build_titles(
    .path_contracts = .lP$Input$Contracts, # the labels and the filers' descriptions
    .n              = 5L,                  # descriptions per category
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  KeywordTerms = oa_build_keyword_terms(
    .dir_table = .lP$Input$DirKeyword, # the published tables and their catalogue
    .n         = 5L,                   # terms per category
    .dir_own   = .lP$Output$DirOwn,
    .force     = .lP$Params$Rebuild,
    .path_lib  = .lP$Input$Lib
  ),
  NerEngines = oa_build_ner_engines(
    .dir_store = .lP$Input$DirEntities, # the spans each extractor proposed, and its benchmark
    .path_text = .lP$Input$SampleText,  # document lengths, so a span's position is comparable
    .dir_own   = .lP$Output$DirOwn,
    .force     = .lP$Params$Rebuild,
    .path_lib  = .lP$Input$Lib
  ),
  DurationRungs = oa_build_duration(
    .path_contracts = .lP$Input$Contracts, # which rung answered, and the two durations
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  TextCounts = oa_build_counts(
    .path_contracts = .lP$Input$Contracts, # counts the text cites that no exhibit prints
    .path_orders    = .lP$Input$Orders,    # one row per reference an order makes
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  SeasonedFilers = oa_build_seasoned(
    .path_contracts = .lP$Input$Contracts, # the sample, its forms and its labels
    .path_landing   = .lP$Input$Landing,   # the SIC code of each filing
    .dir_master     = .lP$Input$DirMaster, # the first EDGAR filing of each CIK
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  )
)

oa_report_builds(.status = st_build)
```

## The exhibits against disk

The context joins the registry and the static table, checks them, and records for every exhibit what its writer --
30, or the builds above -- must have written for the fragment to set it.

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats       = tab_floats,                  # the appendix's exhibits, in print order
  .static       = tab_static,                  # the three read from the Overleaf project
  .dir_exhibits = .lP$Input$DirExhibits,       # where 30 writes Tables/, Notes/ and Figures/
  .dir_own      = .lP$Output$DirOwn,           # where this document writes the exhibits it builds
  .dir_doc      = fs::path_dir(.lP$Input$Qmd), # html image paths are written relative to this document
  .fig_width    = .lP$Params$FigWidth,         # every figure at this width
  .strict       = .lP$Params$Strict            # stop on a missing exhibit rather than mark it
)

oa_report_floats(.files = ctx_oa$Files)
```

Read the status before the text. Ready means the fragment asks Overleaf for files that exist here; whether Overleaf
holds them too depends on what was uploaded there, which this document cannot see.

# Numbers

Each row is one number the text cites. `Where` is a filter over the exhibit tibble's own columns, evaluated as
written; `Fun` reduces the matching rows to one value, and `one` demands exactly one matching row, which is what
catches a filter that silently matches two. The keyword table's coverage and accuracy are taken from the comparison
of all approaches rather than from its own table: that table's total row averages recall over categories, where the
comparison counts documents.

```{r}
#| label: numbers-resolve
# A LEAF OF THE TAXONOMY is a sub-category, or a category without sub-categories. The smallest leaf bounds how thin a
# fold can become, which is the argument for pooled out-of-fold scoring in section C.
.where_leaf <- "Level1 != 'Amendment' & (Kind == 'sub' | Level1 %in% c('Licenses', 'Leases', 'Other'))"
.where_kw   <- "Task == 'ClassDetailed' & Engine == 'Kw'"
.where_llm  <- "Task == 'ClassDetailed' & Engine == 'Llm'"

# THE SEASONED-FILER FIGURE holds one row per group of filers and year.
.where_all      <- \(.y) paste0("Filers == 'All filers' & Year == ", .y)
.where_seasoned <- \(.y) paste0("Filers == 'Seasoned filers' & Year == ", .y)
.where_group    <- \(.g, .y) paste0("grepl('", .g, "', Filers) & Year == ", .y)

# THE COVERAGE TABLE holds one row per group and a total per counted panel.
.where_reg <- "Group %in% c('Exchange Act registrations', 'Real-estate registrations')"
.where_out <- "Panel == 'Outside it' & Kind == 'total'"
.where_in  <- "Panel == 'In the database' & Kind == 'total'"

# THE DESCRIPTIONS TABLE holds one row per category and rank; pNamed is a column of the category, so one row of it.
.where_credit <- "Class == 'Financial Instruments: Credit'"

tab_numbers_spec <- tibble::tribble(
  ~Key,              ~Exhibit,           ~Column,         ~Fun,  ~Format, ~Where,
  "NLabelled",       "ClassLabelled",    "N",             "one", "count", "Kind == 'total'",
  "NRarest",         "ClassLabelled",    "N",             "min", "count", .where_leaf,
  "AccDetailed",     "ClassTransformer", "Accuracy",      "one", "prop3", "Kind == 'total'",
  "F1Detailed",      "ClassTransformer", "F1",            "one", "prop3", "Kind == 'total'",
  "LenientDetailed", "ClassTransformer", "RecallLenient", "one", "prop3", "Kind == 'total'",
  "AccAmend",        "ClassAmendment",   "Accuracy",      "one", "prop3", "Label == 'Total'",
  "F1Amend",         "ClassAmendment",   "F1",            "one", "prop3", "Label == 'Total'",
  "KwCoverage",      "ClassArms",        "Coverage",      "one", "pct1",  .where_kw,
  "KwAccCommitted",  "ClassArms",        "AccuracySel",   "one", "prop3", .where_kw,
  "F1Llm",           "ClassArms",        "MacroF1",       "one", "prop3", .where_llm,
  "NSecond",         "ClassLabelled",    "Second",        "one", "count", "Kind == 'total'",
  "NAll2020",        "SeasonedFilers",   "N",             "one", "count", .where_all(.y = 2020),
  "NAll2021",        "SeasonedFilers",   "N",             "one", "count", .where_all(.y = 2021),
  "NSeasoned2020",   "SeasonedFilers",   "N",             "one", "count", .where_seasoned(.y = 2020),
  "NSeasoned2021",   "SeasonedFilers",   "N",             "one", "count", .where_seasoned(.y = 2021),
  "RegAll2021",      "SeasonedFilers",   "ShareReg",      "one", "pct1",  .where_all(.y = 2021),
  "RegSeasoned2021", "SeasonedFilers",   "ShareReg",      "one", "pct1",  .where_seasoned(.y = 2021),
  "EqAll2021",       "SeasonedFilers",   "ShareEquity",   "one", "pct1",  .where_all(.y = 2021),
  "EqSeasoned2021",  "SeasonedFilers",   "ShareEquity",   "one", "pct1",  .where_seasoned(.y = 2021),
  "NBlankCheck2021", "SeasonedFilers",   "N",             "one", "count", .where_group(.g = "Blank-check", .y = 2021),
  "NSeasonedEdgar2021", "SeasonedFilers", "N",            "one", "count", .where_group(.g = "first EDGAR", .y = 2021),
  "CovSmallBusiness", "FormCoverage",    "Filings",       "sum", "count",    "grepl('Small business', Group)",
  "CovTenKVariants",  "FormCoverage",    "Filings",       "one", "count",    "Group == '10-K variants'",
  "CovRegistrations", "FormCoverage",    "Filings",       "sum", "count",    .where_reg,
  "Cov20FFilings",    "FormCoverage",    "Filings",       "one", "count",    "Group == 'Foreign annual reports'",
  "Cov20FContracts",  "FormCoverage",    "Contracts",     "one", "count",    "Group == 'Foreign annual reports'",
  "CovOutside",       "FormCoverage",    "Filings",       "one", "count",    .where_out,
  "CovInside",        "FormCoverage",    "Filings",       "one", "count",    .where_in,
  "TitlesNamed",      "CategoryTitles",  "pNamed",        "mean", "pct1",    "Rank == 1",
  "TitlesTop",        "CategoryTitles",  "Share",         "sum",  "pct1",    .where_credit,
  "KwTerms",          "KeywordTerms",    "nTerms",        "sum",  "count",   "Rank == 1",
  "NerRateMatcon",    "NerEngines",      "DocsPerSec",    "one", "num1",     "Producer == 'matcon'",
  "NerRateLexnlp",    "NerEngines",      "DocsPerSec",    "one", "num1",     "Producer == 'lexnlp'",
  "NerRateSpacy",     "NerEngines",      "DocsPerSec",    "max", "num1",     "Family == 'spacy'",
  "NerContrastLexnlp", "NerEngines",     "ContrastOrg",   "one", "num2",     "Producer == 'lexnlp'",
  "NerContrastSpacy", "NerEngines",      "ContrastOrg",   "max", "num2",     "Family == 'spacy'",
  "NerDocs",          "NerEngines",      "Documents",     "max", "count",    "Family == 'lexnlp'",
  "DurTerm",          "DurationRungs",   "Share",         "one", "pct1",     "Rung == 'term'",
  "DurOpen",          "DurationRungs",   "Share",         "one", "pct1",     "Rung == 'open'",
  "DurCue",           "DurationRungs",   "Share",         "one", "pct1",     "Rung == 'cue'",
  "DurMaxDate",       "DurationRungs",   "Share",         "one", "pct1",     "Rung == 'maxdate'",
  "DurNone",          "DurationRungs",   "Share",         "one", "pct1",     "Rung == 'none'",
  "DurCapped",        "DurationRungs",   "N",             "one", "count",    "Rung == 'dropped-capped'",
  "DurMedRule",       "DurationRungs",   "Med",           "one", "num1",     "Rung == 'all-rule'",
  "DurMedNaive",      "DurationRungs",   "Med",           "one", "num1",     "Rung == 'all-naive'",
  "DurDefRule",       "DurationRungs",   "Defined",       "one", "count",    "Rung == 'all-rule'",
  "DurDefNaive",      "DurationRungs",   "Defined",       "one", "count",    "Rung == 'all-naive'",
  "DocsAll",          "TextCounts",      "Value",         "one", "count",    "Key == 'DocsAll'",
  "DocsUnique",       "TextCounts",      "Value",         "one", "count",    "Key == 'DocsUnique'",
  "DocsFlagged",      "TextCounts",      "Value",         "one", "count",    "Key == 'DocsFlagged'",
  "RuleShort",        "TextCounts",      "Value",         "one", "count",    "Key == 'RuleShort'",
  "RuleStopwords",    "TextCounts",      "Value",         "one", "count",    "Key == 'RuleStopwords'",
  "RuleNumeric",      "TextCounts",      "Value",         "one", "count",    "Key == 'RuleNumeric'",
  "DocsWithCto",      "TextCounts",      "Value",         "one", "count",    "Key == 'DocsWithCto'",
  "DocsWithSummary",  "TextCounts",      "Value",         "one", "count",    "Key == 'DocsWithSummary'",
  "Orders",           "TextCounts",      "Value",         "one", "count",    "Key == 'Orders'",
  "OrderRefs",        "TextCounts",      "Value",         "one", "count",    "Key == 'OrderRefs'",
  "OrderRefsLinked",  "TextCounts",      "Value",         "one", "count",    "Key == 'OrderRefsLinked'"
)

tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,                       # every number the text cites
  .dir_data = c(                                       # the tibbles behind the exhibits, 30's first
    fs::path(.lP$Input$DirExhibits, "Data"),
    fs::path(.lP$Output$DirOwn, "Data")
  )
)

oa_report_numbers(
  .tab    = tab_numbers,      # resolved above
  .strict = .lP$Params$Strict # TRUE stops the render on an unresolved number
)
```

The same numbers are written as LaTeX macros, so the manuscript cites them too rather than typing copies that go
stale at the next re-export: with the file input in the paper's preamble, `\oanum{F1Detailed}` prints the macro-F1
this render resolved. A key the file does not hold prints in bold as `??Key`, so a typo shows in the PDF.

```{r}
#| label: numbers-write
oa_numbers_write(
  .tab  = tab_numbers,         # resolved above
  .path = .lP$Output$Numbers   # deployed beside the fragment
)
```

:::

::: {.content-visible when-format="html"}

# Online appendix

Everything from here to Validation is the appendix: shown here as the runbook renders it, and written in the LaTeX
pass as the fragment Overleaf inputs. Each exhibit stands where the paper prints it, with the paper's number: figures
from 30's png copies, tables converted from 30's own LaTeX.

:::

```{=latex}
\clearpage
```

## SEC filing requirements and distribution {#sec-oa-filings}

This appendix documents which filings the database draws on and why, the regulatory events that shape it, the
material contracts it does not cover, how the contracts it does cover distribute across forms and over the calendar
year, and the steps that turn filings into the samples used in the paper.

### Filing requirements and what the database collects {#sec-oa-requirements}

Item 601 of Regulation S-K requires a firm to file every material contract as Exhibit 10 to its registration
statements under the Securities Act -- Forms S-1, S-4 and S-11, and Forms F-1 and F-4 for foreign private issuers --
and to its reports under the Exchange Act: the registration on Form 10 and the periodic reports on Forms 10-Q and
10-K. A current report on Form 8-K need not carry the contract. Since 2004, an 8-K must report the entry into a
material definitive agreement within four business days under Item 1.01, but the contract itself may follow as an
exhibit to the next periodic report (Section 2 of the paper). Two groups of filers followed rules of their own.
Foreign private issuers file their annual report on Form 20-F, whose instructions list material contracts as
Exhibit 4 rather than Exhibit 10 (Instruction 4(a) of the Instructions as to Exhibits of Form 20-F). And until
2008--09, small business issuers reported under Regulation S-B on Forms 10-KSB, 10-QSB and SB-2, whose own Item 601
required material contracts as exhibits in the same way **[TO VERIFY: against 17 C.F.R. 228.601 as in force before
2008]**. `r oa_ref(.name = "FormCoverage")` lists every form that carries material contracts, the regime it belongs
to, and whether the database covers it.

`r oa_ref(.name = "RegulatoryTimeline")` lists the regulatory events that determine what the database contains and
when. EDGAR filing became mandatory for all domestic registrants in 1996. The database starts in 2001, when EDGAR
stores the exhibits of a filing as documents of their own **[TO VERIFY: the year, against the main text's reason for
the sample start]**. The 2004 reform of Form 8-K introduced Item 1.01 and the four-day deadline. EDGAR publishes
confidential treatment orders from 2008, where the database's orders begin. And since April 2, 2019, the amendments
to Item 601 that followed the FAST Act allow a firm to redact a contract without a confidential treatment request.

Before April 2019, a firm that wanted to redact a contract filed a confidential treatment request (CTR): it uploaded
the redacted contract to EDGAR and submitted the unredacted text to the SEC staff for review. About 10 to 11 percent
of requests were denied at least in part [@thompson2023; @ahci2025]. A firm whose request was denied refiled the
contract with fewer redactions, so the database holds such a contract twice, once with each filing (Appendix A.4).
Since April 2019, a firm redacts without a request, and the staff reviews redacted contracts selectively.

The database downloads three groups of documents from the filings of the forms it covers. The first is every
attachment filed as Exhibit 10. An attachment counts as Exhibit 10 where its exhibit type maps to Exhibit 10 in a
lookup of the raw exhibit-type strings filers use, rather than where it matches a pattern: filers write `EX-10.1`,
`EX-10`, `EXHIBIT 10.23` and many further variants, and a pattern silently excludes the spellings its author did not
anticipate. The second group is every 8-K that reports Item 1.01, whose text the paper uses to measure how firms
announce their contracts. The third is every confidential treatment order, which links a redacted exhibit to the
SEC's grant of confidential treatment. The first group yields `r oa_n(.key = "DocsAll")` documents, of which
`r oa_n(.key = "DocsUnique")` are distinct attachments; the second supplies the announcement text of
`r oa_n(.key = "DocsWithSummary")` of them; and the third holds `r oa_n(.key = "Orders")` orders.

```{r}
#| label: float-regulatory-timeline
#| results: asis
oa_float(.name = "RegulatoryTimeline")
```

```{r}
#| label: float-form-coverage
#| results: asis
oa_float(.name = "FormCoverage")
```

### Scope and what lies outside it {#sec-oa-scope}

The database is defined by EDGAR form type and exhibit number: it contains the documents filed as Exhibit 10 with the
EDGAR form types 10-K, 10-Q, 8-K, 20-F, S-1, S-4, F-1 and F-4, including their amendments, between 2001 and 2024.
Material contracts filed under other form types or exhibit numbers fall outside this definition.
`r oa_ref(.name = "FormCoverage")` counts the filings of every form that carries material contracts, from the EDGAR
master index, and the contracts the database holds from the forms it covers.

Four groups lie outside the scope. The largest are the forms of small business issuers -- 10-KSB, 10-QSB, SB-2 and
Form 10-SB -- used until 2008--09, after which these firms file on Forms 10-K and 10-Q, which the database covers;
EDGAR lists `r oa_n(.key = "CovSmallBusiness")` such filings. The second group consists of EDGAR's separate form
types for variants of the annual report: 10-K405, a 10-K on which the Item 405 box is checked, used until 2002, and
10-KT, the transition report after a change of fiscal year, together `r oa_n(.key = "CovTenKVariants")` filings. The
third consists of registrations on Form 10, among them spin-offs, and on Form S-11, the registration statement of
real-estate companies, `r oa_n(.key = "CovRegistrations")` filings. The fourth lies inside a form the database
covers: Form 20-F lists material contracts as Exhibit 4 rather than Exhibit 10, so the database holds only the 20-F
contracts that filers number as Exhibit 10, `r oa_n(.key = "Cov20FContracts")` contracts from
`r oa_n(.key = "Cov20FFilings")` filings. The registration statements of foreign issuers, Forms F-1 and F-4, follow
Item 601 and number their contracts as Exhibit 10, so they are covered.

Together, the forms outside the scope account for `r oa_n(.key = "CovOutside")` filings. Their contracts were never
downloaded, so the table does not count them, and the two panels are not directly comparable: the filings of the
forms in the database include every current report, most of which carry no contract at all, while the small-business
forms are concentrated in the years before 2009 and the annual reports among them carry contracts at about the rate
a 10-K does. The gap matters most for small firms
before 2009: their contracts filed with current reports are in the database, while those filed with periodic reports
and registration statements are not. The paper's comparison of small and large firms and its firm-quarter regressions
for 2005 to 2008 are therefore repeated without the firms that filed on small-business forms in the respective
quarter (Appendix E). **[TO WRITE: the result]** Two further groups are excluded by design. Asset-backed issuers
(Forms SF-1, SF-3 and 10-D) are securitisation vehicles rather than operating firms, and the current reports of
foreign private issuers on Form 6-K carry no exhibit numbering; a contract filed with one usually carries the type
EX-99.

### Distributions of filings {#sec-oa-distributions}

`r oa_ref(.name = "FilingTypes")` shows the unique contracts by the form they were filed with, U.S. and foreign forms
side by side, each split into original agreements and amendments. Current reports carry the largest share, ahead of
the two periodic reports and the registration statements, and the forms of foreign private issuers carry a small
fraction of the whole -- which follows from the coverage of Exhibit 10 on Form 20-F rather than from how often
foreign issuers contract. **[TO VERIFY: the ranking, against the figure]**

```{r}
#| label: float-filing-types
#| results: asis
oa_float(.name = "FilingTypes")
```

`r oa_ref(.name = "FilingsWithinYear")` shows when in the calendar year contracts are filed. Contracts filed with
current reports spread evenly over the year, at about a third of a percent a day, with dips on public holidays.
Contracts filed with periodic reports follow the reporting deadlines. Among annual reports, the spikes fall on the
deadlines of 60, 75 and 90 days after a December year-end -- around 1 March, mid-March and 31 March, the first the
largest -- and a smaller one follows in mid-April, fifteen days later, which is the extension a late filer obtains
under Rule 12b-25. Among quarterly reports, the spikes fall on the deadlines of 40 and 45 days after each quarter's
end, in May, August and November; the small peak in February comes from filers whose fiscal year does not end in
December.

```{r}
#| label: float-filings-within-year
#| results: asis
oa_float(.name = "FilingsWithinYear")
```

The number of contracts rises sharply in 2020 and 2021. A newly reporting firm must file the material contracts it
entered into during the two years before its registration (Item 601(b)(10)(i)), so every wave of registrations
arrives with a backlog of contracts. `r oa_ref(.name = "SeasonedFilers")` separates that backlog from the filing of
established firms: a seasoned filer is one more than two years past its first contract in the database, the same
two-year window. All filers file `r oa_n(.key = "NAll2020")` contracts in 2020 and `r oa_n(.key = "NAll2021")` in
2021; seasoned filers file `r oa_n(.key = "NSeasoned2020")` and `r oa_n(.key = "NSeasoned2021")`. Registration
statements carry `r oa_n(.key = "RegAll2021")` percent of all contracts in 2021, against
`r oa_n(.key = "RegSeasoned2021")` percent of the contracts of seasoned filers. Many of the new registrants are
special purpose acquisition companies [@gahng2023spacs], and the figure counts them directly: registrants under SIC
code 6770, EDGAR's code for blank-check companies, file `r oa_n(.key = "NBlankCheck2021")` contracts in 2021. Such
registrants file a standard set of equity agreements at registration, and equity contracts make up
`r oa_n(.key = "EqAll2021")` percent of all contracts in 2021, against `r oa_n(.key = "EqSeasoned2021")` percent
among seasoned filers. Dating a firm by its first contract uses the very filings under study; dated by its first
EDGAR filing of any form instead, seasoned filers file `r oa_n(.key = "NSeasonedEdgar2021")` contracts in 2021, so
the reading does not depend on the definition.

The three panels say the same thing in three ways. The count of contracts rises and falls with the registration wave
while the seasoned line stays flat; the share filed with a registration statement moves with it and the seasoned
share does not; and the equity share does the same. A firm that had been filing for years did not change what it
filed in 2020 and 2021. What changed is who was filing.

```{r}
#| label: float-seasoned-filers
#| results: asis
oa_float(.name = "SeasonedFilers")
```

### From filings to the samples {#sec-oa-samples}

Three rules flag documents whose conversion to text failed: ten words or fewer after the SEC header; fewer than 20
percent stopwords together with fewer than 100 words; or 75 percent or more numeric tokens. Each threshold sits far
from anything a genuine agreement produces, so the rules remove conversion debris -- a PDF rendered as coordinates, a
hyperlink in place of a document, a financial statement filed under an exhibit number -- rather than short
agreements. Exhibits whose text is only a placeholder for a PDF or an image carry no readable text and are counted
with them. Flagged documents stay in the release with the rule that flagged them and are excluded from the samples.
Of the `r oa_n(.key = "DocsUnique")` unique attachments, `r oa_n(.key = "DocsFlagged")` are flagged:
`r oa_n(.key = "RuleShort")` for length, `r oa_n(.key = "RuleStopwords")` for a want of prose, and
`r oa_n(.key = "RuleNumeric")` for numeric tokens, the remainder being the placeholders that carry no text at all.

A filing can list several registrants, and EDGAR lists its attachments under each of them, so one attachment can
appear as several documents. Each attachment is identified by a hash of its address and each registrant's copy by an
identifier of its own, and one copy per attachment is designated primary. Classification and entity extraction read
the primary copy; the release carries every copy with its attachment's values, so unique contracts are the primary
copies, and every registrant's copy remains available for analyses at the filer level. The release holds
`r oa_n(.key = "DocsAll")` documents and `r oa_n(.key = "DocsUnique")` unique attachments. Two cases produce distinct
attachments for one agreement and are not merged: two parties that each file their own copy of it, and a contract
refiled with fewer redactions after a partially denied confidential treatment request.

Confidential treatment orders are parsed for the exhibits they cover, which an order identifies by filing and
exhibit number, and each named exhibit is linked to the attachment it identifies. As in @ahci2025, orders that deny
or extend earlier treatment are excluded, so every linked order is a grant. EDGAR lists orders from May 2008
**[TO VERIFY]**, which bounds the period in which a redaction can be traced to an order. The
`r oa_n(.key = "Orders")` orders make `r oa_n(.key = "OrderRefs")` references to exhibits, of which
`r oa_n(.key = "OrderRefsLinked")` reach the attachment they name; the rest fail at a point the release records for
each, from a reference that could not be parsed to an exhibit number that is not among those acquired. An order is
linked to `r oa_n(.key = "DocsWithCto")` contracts of the sample.

For every 8-K that reports Item 1.01, the text of the item is extracted from the filing, running from the item's
heading to the next heading, or to the signature block where it is the last item. A heading is recognised
differently in the two formats a filing comes in: in markup it follows a closing tag, and in plain text it begins a
line. Both anchors are needed, because the word "item" appears inside most agreements, and a rule that ignored the
markup would find a heading in the middle of a sentence. The narrative is recovered for
`r oa_n(.key = "DocsWithSummary")` contracts of the sample, which is what allows an announcement to be compared with
the contract it announces. **[TO VERIFY: whether the paper's summary measures use every recovered narrative or only
those of an 8-K that announces a single agreement]**

Filings are linked to Compustat by CIK and filing date. Each firm-quarter covers a fixed window from its fiscal
quarter's end (`datadate`) to one quarter later, and a filing is assigned to the firm-quarter whose window contains
its filing date; a filing that falls inside two windows is discarded as ambiguous **[TO VERIFY: the window as
implemented]**. CIK and gvkey are deduplicated to a one-to-one mapping. Compustat reports one CIK per gvkey, its
current one, so contracts filed under a firm's earlier CIK -- after a reorganisation, for instance -- find no match;
a dated link between CIK and gvkey would recover them and is not used.

`r oa_ref(.name = "SampleAttrition")` reports what each requirement of the estimation samples costs, at the contract
and at the firm-quarter level, beside the construction of the samples in
`r oa_ref_main(.name = "SampleSelection", .kind = "table")`. Each row is the cost of that requirement alone, against
the sample before any requirement is applied, so the rows overlap and do not sum to the total: a contract can fail
several at once. **[TO VERIFY: the requirements that cost most, against the table]**
**[TO DECIDE: keep the table of firm-quarters without product-market fluidity only if the main regressions control
for fluidity]**

```{r}
#| label: float-sample-attrition
#| results: asis
oa_float(.name = "SampleAttrition")
```

```{r}
#| label: float-fluidity-missing
#| results: asis
oa_float(.name = "FluidityMissing")
```

```{=latex}
\clearpage
```

## Open-source packages {#sec-oa-packages}

The database is built with two R packages published with the paper: rGetEDGAR, which retrieves and parses EDGAR
filings, and rLabelDocs, which supports the manual labelling of documents. Neither is tied to material contracts:
rGetEDGAR retrieves any filing EDGAR holds, and rLabelDocs labels documents against any scheme. The database was
built with rGetEDGAR 0.1.0, published at `github.com/MatthiasUckert/rGetEDGAR`, and
labelled with rLabelDocs 0.1.1. **[TO WRITE: the rLabelDocs repository, whose DESCRIPTION still carries the
placeholder URL `github.com/yourusername/rLabelDocs`.]**

### rGetEDGAR {#sec-oa-rgetedgar}

rGetEDGAR retrieves EDGAR filings in three stages, each of which stores its result, so that a later stage never
repeats an earlier stage's requests and an interrupted run resumes where it stopped. What the package retrieves is
set by its arguments -- the period, the filers, the form types and the exhibit types -- so the frame of this database
is one selection among many it supports. Every request carries the User-Agent the SEC requires and a keep-alive
connection, and a request that fails is logged with its reason and skipped rather than retried, so that one bad
response cannot stall a run of hundreds of thousands.

The first stage downloads EDGAR's quarterly master index files, which list every filing since 1993 with its filer's
Central Index Key (CIK), company name, form type, filing date and the address of its full-text submission. The
package derives the address of the filing's index page from it, pads CIKs to ten digits, and identifies each filing
by a hash of that index page's address, which the later stages use to link and deduplicate records. A quarter
already on disk is not downloaded again.

The second stage visits the index page of every selected filing and records its documents -- sequence number,
description, file name, exhibit type, size and address -- together with the filing's own metadata. Each document is
identified by a hash of its address and its sequence number, and carries an identifier that prefixes the filer's
CIK, which is what separates a filing's attachment from the copy of it that another registrant of the same filing
carries. Requests are made in batches of ten, and a batch that finishes in under 1.05 seconds waits out the
remainder, which holds the run under the SEC's ten-requests-a-second limit without a global clock. Each batch's
result is written to a SQLite database for the quarter as it arrives, and the quarter is written to Parquet once it
is complete, so an interrupted quarter costs at most one batch.

The third stage downloads the selected documents and converts them to text. HTML is parsed with rvest, permissively
and with the parser's huge-document limit lifted, taking the whitespace-preserving reading of the text unless the
document is dense enough in line breaks and non-breaking spaces for that reading to oscillate, in which case the
plain one is taken; PDFs are read with readtext; and text, XML and schema files are read as they are. Each document
is stored with both its raw text and a standardised version -- punctuation and special characters removed, runs of
whitespace collapsed, transliterated to ASCII and upper-cased, with digits kept -- in a Parquet file compressed with
gzip. Downloads are sequential, as the SEC's limit requires, while parsing runs in parallel across as many workers
as the caller asks for. The original files are retained in a zip archive per form type and quarter unless the caller
asks for them to be discarded.

### rLabelDocs {#sec-oa-rlabeldocs}

rLabelDocs is a Shiny application for labelling documents against a classification scheme, built for annotation
projects with several annotators. A project is a directory holding the documents, the scheme and the labels, and the
scheme -- which questions an annotator answers about a document, and which answers each admits -- is a table of three
columns read from the project, so the package is not tied to contracts or to any one taxonomy. Several schemes can
run side by side over the same documents, which is how a contract receives its category and its amendment flag in one
pass.

Labels are stored as an append-only log: every answer is written with the document, the annotator, the session and
the time, and the current label is the newest entry for that question. Nothing is overwritten, so a correction leaves
both the original answer and the correction in place, and the state of the labelling at any past moment can be
recovered. The package records a hash of the scheme when labelling begins and warns if the scheme has changed since,
which is the failure that would otherwise pass unnoticed: answers given under one set of categories, read under
another.

The application has five tabs. The first sets up a project, taking the documents and the scheme and preparing them
for use. The second is where labelling happens: a document beside the scheme's questions, with the answers given so
far, a free-text note, and a queue that can be set to all documents, to those still unlabelled, to those already
labelled, or to the ones the annotator has marked to return to; answers are saved on an explicit save, so an annotator
can look at a document and leave it untouched. The third reports progress: how many documents are labelled and how
many remain, each annotator's activity over time, and the distribution of the answers given so far. The fourth lists
labelled documents filtered by any combination of scheme, question and answer, which is how labels are reviewed for
consistency. The fifth exports the labels, at the present moment or as they stood at any earlier one.

The labelled sample of Appendix C was produced with it.

```{=latex}
\clearpage
```

## Classification approach {#sec-oa-classification}

Each contract is classified on three tasks, all from the same text: its type in the twelve categories of
`r oa_ref_main(.name = "Categories", .kind = "table")` (detailed), the seven parent categories (broad), and whether it
is an original agreement or an amendment. A fine-tuned transformer labels the corpus. A keyword table, published as
an artifact in its own right, and a local language model are evaluated beside it on the same cross-validation
folds.

### Taxonomy and labelled sample {#sec-oa-class-sample}

The twelve detailed categories nest in seven broad ones, and the amendment flag is orthogonal to both: an amendment
carries the category of the agreement it amends. The labelled sample holds `r oa_n(.key = "NLabelled")` contracts
with readable text (`r oa_ref(.name = "ClassLabelled")`), labelled with rLabelDocs (Appendix B.2) in two rounds: a
first round in which contracts labelled under an earlier coding scheme were mapped to the current categories, and a
second round of direct classification aimed at the categories the mapping could not fill. **[TO WRITE: who labelled,
the guideline they followed, and how doubtful cases were resolved]** A contract that fits two categories carries a
second label, which `r oa_n(.key = "NSecond")` contracts do. Training uses the primary label only; the second label
serves to score leniently.

Agreement between annotators was not measured. The data provide a different measure of ambiguity: counting a
contract's second label as correct raises the detailed classifier's accuracy from `r oa_n(.key = "AccDetailed")` to
`r oa_n(.key = "LenientDetailed")`, so ambiguity in the taxonomy explains few of its errors. **[TO DECIDE: whether to
measure agreement on a double-coded subsample]**

```{r}
#| label: float-class-labelled
#| results: asis
oa_float(.name = "ClassLabelled")
```

### Category boundaries and example titles {#sec-oa-class-boundaries}

A contract's category follows from its primary obligation, and the boundaries that matter most follow from the
definitions in `r oa_ref_main(.name = "Categories", .kind = "table")`. A contract for the purchase or sale of
tangible or intangible assets is Assets, unless the assets are inventory or operational services, which make it
Customer / Supplier: selling a plant is Assets, supplying from it is Customer / Supplier. Research and development
agreements, including the related consulting, form a category of their own within Purchases and Sales. M&A covers
the business combination and the agreements that stem from it, such as tax-matters agreements, while collaborations
that leave the firms separate -- joint ventures, alliances, co-development -- are Peer Agreements. Employment splits
into compensation plans and the employment relationship itself: offer letters, severance, non-competition and
change-in-control agreements. **[TO VERIFY: the boundary rules against the labelling guideline]**
`r oa_ref(.name = "CategoryTitles")` shows, for each category, the five descriptions filers most often give their
contracts. The description is the filer's own free text and the only human-written label an attachment carries, so it
is the most direct view of what a category holds -- and, unlike an example contract, it is a count rather than a
choice. Filers supply a description beyond the exhibit number for `r oa_n(.key = "TitlesNamed")` percent of
contracts; for the rest, the exhibit number is all they write. The five most frequent descriptions account for
`r oa_n(.key = "TitlesTop")` percent of credit contracts. **[TO WRITE: the reading, once the table is rendered on the
real data -- which categories are named consistently and which are not]**

Each contract receives one label. A contract that combines several agreements -- a merger agreement with employment
terms, a license with a supply obligation -- is labelled by its primary obligation, and for every contract the
release carries the two most likely categories with their probabilities (Appendix C.7), so an analysis can treat a
contract whose second probability is high as mixed.

```{r}
#| label: float-category-titles
#| results: asis
oa_float(.name = "CategoryTitles")
```

### Evaluation design {#sec-oa-class-design}

The folds are dealt once, stratified on the detailed category, and every approach is scored on the same five folds.
Each contract is predicted once, by the fold model that did not see it in training, and the scores pool these
out-of-fold predictions. No test set is held out beyond the folds: with `r oa_n(.key = "NRarest")` contracts in the
smallest category, a further holdout would leave too few to estimate that category's performance. The headline
metric is macro-F1, the unweighted mean of the per-category F1 scores, because accuracy is dominated by the largest
categories; accuracy is reported beside it. Lenient scores count a prediction as correct where it equals the
contract's second label, so the gap between strict and lenient scores measures ambiguity in the taxonomy rather
than error in the model.

### Transformer classifier {#sec-oa-class-transformer}

Two encoders are fine-tuned: Legal-BERT [@chalkidis2020legal], pre-trained on legal text, and RoBERTa
[@liu2019roberta], pre-trained on general text. The grid crosses two learning rates (2e-5 and 3e-5), two context
lengths (256 and 512 tokens), two training budgets (three and six epochs) and loss weighting by inverse class
frequency or none, separately for each task; a learning rate of 1e-5 and ten epochs were each evaluated against the
centre of the grid and did not improve on it. `r oa_ref(.name = "ClassSweep")` reports every configuration. The
configuration with the highest out-of-fold macro-F1 is refitted on the full labelled sample; for both the detailed
and the amendment task, the classifier that labels the corpus reads the first 256 tokens of a contract. **[TO VERIFY:
the crowning rule, including how ties are broken, and the base encoder and settings of the shipped configurations,
from the sweep output]**

Out of fold, the detailed classifier reaches an accuracy of `r oa_n(.key = "AccDetailed")` and a macro-F1 of
`r oa_n(.key = "F1Detailed")` (`r oa_ref(.name = "ClassTransformer")`). Its errors concentrate in adjacent categories
(`r oa_ref(.name = "ClassConfusion")`). **[TO VERIFY: that these are the pairs in which manual labelling produced
second labels]** The amendment classifier reaches an accuracy of `r oa_n(.key = "AccAmend")` and a macro-F1 of
`r oa_n(.key = "F1Amend")` (`r oa_ref(.name = "ClassAmendment")`). The broad label is the roll-up of the detailed
label, so the two never contradict each other; a classifier trained on the seven broad categories directly reaches
**[TO WRITE: its scores]**, and its label is released as a separate column. **[TO DECIDE: the broad label as the
roll-up of the detailed label, which is one mapping in the export]**

```{r}
#| label: float-class-sweep
#| results: asis
oa_float(.name = "ClassSweep")
```

```{r}
#| label: float-class-transformer
#| results: asis
oa_float(.name = "ClassTransformer")
```

```{r}
#| label: float-class-confusion
#| results: asis
oa_float(.name = "ClassConfusion")
```

```{r}
#| label: float-class-amendment
#| results: asis
oa_float(.name = "ClassAmendment")
```

### Keyword table {#sec-oa-class-keyword}

The keyword approach produces a published artifact rather than a competing classifier: a short, ranked table of
terms per category that anyone can apply to a filing with a text editor, each term with a stated precision. A term's
evidence is the Wilson lower bound on its training precision [@wilson1927probable], which ranks a term found in 190
of 200 contracts above one found in 2 of 2. A term enters the table only where its precision exceeds the category's
base rate, where it catches contracts that no accepted term caught, and where at least three of the five fold-wise
mines select it. A contract is assigned the category of the strongest term it contains, and the table abstains where
no term fires. The tables target a precision of 95 percent for contract types and 85 percent for amendments.

A table that abstains is judged on two numbers rather than one. Out of fold, the detailed table commits on
`r oa_n(.key = "KwCoverage")` percent of contracts, with an accuracy of `r oa_n(.key = "KwAccCommitted")` where it
commits (`r oa_ref(.name = "ClassKeyword")`). The published table holds `r oa_n(.key = "KwTerms")` terms across the
twelve categories. `r oa_ref(.name = "KeywordTerms")` prints the five strongest of each, with the evidence behind
them; the full table
is part of the release. **[TO WRITE: the reading, once the table is rendered on the real data -- which categories a
short list serves and which need many terms]**

```{r}
#| label: float-class-keyword
#| results: asis
oa_float(.name = "ClassKeyword")
```

```{r}
#| label: float-keyword-terms
#| results: asis
oa_float(.name = "KeywordTerms")
```

### Language model {#sec-oa-class-llm}

A local language model with open weights, Qwen3 with eight billion parameters [@qwen2025qwen3], classifies each
contract from its opening text, either from the category names and definitions alone or with worked examples drawn
from the other folds, so that no prompt contains a contract from the fold it scores. It runs offline, so its results
can be reproduced. **[TO VERIFY: the length of the text the prompt includes, and the decoding settings]** On the
detailed task it reaches a macro-F1 of `r oa_n(.key = "F1Llm")`, well below the fine-tuned transformer;
`r oa_ref(.name = "ClassArms")` compares all approaches on every task. **[TO DECIDE: keep the language model]**

```{r}
#| label: float-class-arms
#| results: asis
oa_float(.name = "ClassArms")
```

### Application to the corpus {#sec-oa-class-apply}

The classifier labels every Exhibit 10 attachment once, reading its primary copy, and the release carries the label
on every registrant copy. For each contract, the release holds the most likely and the second most likely category,
each with its probability, for the detailed and the broad task and for the amendment flag; where a keyword fires, the
keyword table's category, the term and its strength; and a flag that records whether the keyword table and the
classifier agree **[TO VERIFY: the flag's definition]**. `r oa_ref(.name = "ClassConfidence")` reports the
classifier's confidence by category in the corpus.

Three uses follow. An analysis of contract types uses the detailed or the broad label. An analysis that needs
clear-cut contracts restricts the sample to labels whose probability exceeds a threshold, at the cost in contracts
the table shows. And an analysis of mixed contracts treats a contract as mixed where its second probability is high.
`r oa_ref(.name = "TypesTimeC")` shows the share of each category among the contracts of each year. **[TO WRITE: the
reading]** **[TO DECIDE: this figure here or in Appendix E]**

```{r}
#| label: float-class-confidence
#| results: asis
oa_float(.name = "ClassConfidence")
```

```{r}
#| label: float-types-time
#| results: asis
oa_float(.name = "TypesTimeC")
```

```{=latex}
\clearpage
```

## Named entity recognition and the rule set {#sec-oa-entities}

Contract partners, places, dates, monetary amounts and redaction markers are extracted in two stages. Extractors
propose spans of text, each stored with its character offsets in the contract; rules then turn the spans into
variables. The release carries both the naive variables, which count what the extractors proposed, and the
rule-based variables, so an analysis that rejects a rule can fall back to the step before it.

### Extractors {#sec-oa-ent-extractors}

Three families of extractors are run on the same `r oa_n(.key = "NerDocs")` contracts of the labelled sample: LexNLP
[@bommarito2021lexnlp]; the named-entity recogniser of spaCy [@honnibal2020spacy], in each of its four models; and a
set of pattern and gazetteer extractors written for this database, covering dates, stated terms, monetary amounts,
places, redaction markers and governing-law clauses. Every span is stored as offsets into the full text of the
contract, so a rule can relate spans to each other -- a place to the party named before it, a marker to the amount it
replaced -- without reading the contract again.

`r oa_ref(.name = "NerEngines")` compares what they propose and where. Two findings keep spaCy off the corpus. The
first is what its spans are: its organisation names are spread through the contract rather than concentrated where
the parties are named. Measured as the share of a producer's organisation names at the two ends of a contract
against their share through the middle, spaCy scores `r oa_n(.key = "NerContrastSpacy")`, which is what an even
scattering through the text gives, while LexNLP scores `r oa_n(.key = "NerContrastLexnlp")`. What spaCy adds is
mentions of companies inside the text, which the parties rule does not use. The second is cost: spaCy reads
`r oa_n(.key = "NerRateSpacy")` contracts a second, against `r oa_n(.key = "NerRateLexnlp")` for LexNLP and
`r oa_n(.key = "NerRateMatcon")` for the pattern extractors, and over 1.2 million attachments that is the difference
between hours and days. **[TO VERIFY: the three throughputs, which are the benchmark's and the one thing in this
appendix not read from the data; and the number of attachments the corpus run covers]**

```{r}
#| label: float-ner-engines
#| results: asis
oa_float(.name = "NerEngines")
```

### Contract partners {#sec-oa-ent-parties}

LexNLP proposes organisation names, and a rule turns them into parties in four steps. It strips legal suffixes, so
that ACME CORPORATION and ACME CORP. share one key; it groups the spellings of one company within a contract; it
matches the parties against the EDGAR records of the filing's registrants, by prefix for the filer and exactly for
the co-registrants of the same filing; and it assigns each party a role: registrant, co-registrant, counterparty
where named within 2,000 characters of the registrant, signatory where named in the final tenth of the contract, and
other. Where no party matches the filer, the first party named is taken as the registrant, and the release records
that fallback. The parties the paper counts are the registrant, the co-registrants and the counterparties.
`r oa_ref(.name = "PartiesDetail")` reports the parties by role and category. **[TO VERIFY: the share of contracts
that rely on the fallback, 22.4 percent in the rule's runbook]** **[TO DECIDE: keep the table]**

```{r}
#| label: float-parties-detail
#| results: asis
oa_float(.name = "PartiesDetail")
```

### Places and governing law {#sec-oa-ent-places}

Places come from a gazetteer built from the U.S. Geological Survey's domestic names and international country data.
A place name that is also an English word, such as Enterprise, Mobile or Reading, is accepted only where a state or
country name follows it directly, and any other place name only where a state or country is named nearby; a name that
exists in several states, such as Springfield, is assigned a state only where the contract itself names one of its
candidate states. A place belongs to the party named within 200 characters before it, which separates the locations
of the contracting parties from places a contract merely mentions. Places inside a governing-law clause name a
jurisdiction rather than a location and are excluded from the geography counts; the jurisdictions are released
separately, every one a contract names.

### Dates and duration {#sec-oa-ent-dates}

Every date pattern requires a year written in the text, so the extractor cannot supply a year the contract does not
state, and numeric dates are read month first, as in U.S. filings. A contract's start is the latest date at or
before its filing date, or the filing date where no such date exists. Its end comes from the first of four sources
present: a stated term ("for a period of five years"); an open-ended clause ("until terminated"), which leaves the
duration missing; a future date next to an end cue (maturity, through, expiration); and the farthest future date.
Durations above 30 years are dropped rather than capped, which removes `r oa_n(.key = "DurCapped")` contracts. The
release carries the naive duration beside it, measured from the farthest future date alone.

`r oa_ref(.name = "DurationRungs")` reports what each source answers. A stated term settles
`r oa_n(.key = "DurTerm")` percent of contracts, a cued date `r oa_n(.key = "DurCue")` percent, and the farthest
future date `r oa_n(.key = "DurMaxDate")` percent; an open-ended clause accounts for `r oa_n(.key = "DurOpen")`
percent. For the remaining `r oa_n(.key = "DurNone")` percent no rung answers: the contract states no term, carries
no cue, and names no date beyond its filing, which is what a contract of indefinite length looks like in the text.

The rules buy coverage where the text states what a naive reading has to guess. The rule-based duration is defined
on `r oa_n(.key = "DurDefRule")` contracts, the naive one on `r oa_n(.key = "DurDefNaive")`, and the difference is
almost entirely contracts that state a term without naming a future date. The two also differ in what they yield: a
median of `r oa_n(.key = "DurMedRule")` years against `r oa_n(.key = "DurMedNaive")`, because the farthest future
date in a contract is often a date the contract mentions rather than the date it runs to. **[TO VERIFY: that the gap
between the two is the stated-term contracts, once rendered]**

```{r}
#| label: float-duration-rungs
#| results: asis
oa_float(.name = "DurationRungs")
```

### Monetary amounts {#sec-oa-ent-money}

An amount is recognised only together with a currency marker, which excludes section numbers by construction. Zero
amounts, and figures with par-value language within 60 characters on either side, are dropped; figures a filer
withheld, such as `$[***]`, are counted separately and never summed. Flattened tables can join adjacent cells into
a single figure, so only medians are reported (`r oa_ref(.name = "MoneyDetail")`). **[TO DECIDE: keep the table]**

```{r}
#| label: float-money-detail
#| results: asis
oa_float(.name = "MoneyDetail")
```

### Redaction markers {#sec-oa-ent-redactions}

Six kinds of marker are identified: brackets naming confidential treatment, brackets of asterisks, brackets of
underscores, brackets recording an omission, brackets of bullets or ellipses, and unbracketed runs of three or more
asterisks. The release counts each kind, so every definition of a redacted contract is a sum of released columns;
the paper's measure counts bracketed asterisks and explicit redactions. A marker that sits inside a withheld amount
identifies a withheld price. `r oa_ref(.name = "RedactionsDetail")` reports the markers by category. **[TO DECIDE:
whether one marker or five define a redacted contract after 2018]**

```{r}
#| label: float-redactions-detail
#| results: asis
oa_float(.name = "RedactionsDetail")
```

### Naive and rule-based variables {#sec-oa-ent-contrast}

`r oa_ref(.name = "ContentContrast")` reports, by category, on how many contracts each measure is defined or finds
something under the naive and under the rule-based definition. The rules add coverage where the text states what a
naive measure has to guess -- a stated term needs no future date -- and remove it where a naive measure counts what
the rule rejects, such as places in governing-law clauses. **[TO WRITE: the reading]**

```{r}
#| label: float-content-contrast
#| results: asis
oa_float(.name = "ContentContrast")
```

### Validation {#sec-oa-ent-validation}

Every rule-based variable is traceable to the spans it rests on, because each span keeps its offsets in the text.
**[TO DECIDE: a hand-coded check of about 200 contracts for parties, locations and duration]**

```{=latex}
\clearpage
```

## Additional analysis {#sec-oa-additional}

This appendix collects analyses that complement the paper. **[TO DECIDE: the analyses in this appendix. Candidates:
the two redaction measures compared (orders against text markers, one against five markers); redactions by industry
and category before and after the FAST Act; the Item 1.01 announcement sample and its measures; the geography of all
recital parties and contracting flows; and the regressions with firm fixed effects, by contract type, with
alternative redaction definitions and control sets, and without small-business filers before 2009.]**

### Content characteristics over time {#sec-oa-add-content}

`r oa_ref(.name = "ContentTimeSD")` shows the yearly mean of duration, countries, parties and words, with a band of
one standard deviation. **[TO WRITE: the reading]**

```{r}
#| label: float-content-time
#| results: asis
oa_float(.name = "ContentTimeSD")
```

### Geographic diversity {#sec-oa-add-diversity}

`r oa_ref(.name = "Diversity")` relates the number of countries the contracts of a firm-year mention to the
geographic diversity of the firm's segment sales. **[TO DECIDE: the grain, the treatment of the tails and the number
of bins]**

```{r}
#| label: float-diversity
#| results: asis
oa_float(.name = "Diversity")
```

```{=latex}
\clearpage
```

## Data access {#sec-oa-access}

**[TO WRITE: once the publication route is decided -- the files of the release with their grain, keys and contents;
the variables by block, condensed from the codebook; the identifiers that lead from each contract back to EDGAR (CIK,
accession number, file name and the document's address); and where the README and the codebook are found.]**

::: {.content-visible when-format="html"}

# Validation

Two checks on the text itself. **Every registered exhibit is set exactly once, in the registry's order**: a registered
exhibit the text never sets would be listed as ready above and be absent from the paper, with nothing else to say so.
**The open markers are counted by section**, which is the appendix's progress report while it is being written.

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

The fragment is written only by the LaTeX pass. A terminal render, `quarto render 1_code/31-OnlineAppendix.qmd`, runs
both passes, html first; the Render button runs the html alone. Either way, the check below sees the fragment as it
stood before this render began.

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,        # the fragment as the last LaTeX pass left it
  .path_qmd     = .lP$Input$Qmd,         # a fragment older than this document or its library is stale
  .dir_exhibits = .lP$Input$DirExhibits  # and so is one older than what 30 wrote
)
```

To bring Overleaf up to date, one call from the console. It renders both passes in a separate R process, as a
terminal render would, checks that the fragment and the numbers file were written by this call, copies them to the
paper folder, archives the ones they replace, and ends with the files that changed -- the ones to upload.

```r
source(here::here("1_code", "31-OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "31-OnlineAppendix.qmd"),                          # this document
  .path_tex     = here::here("_rendered", "1_code", "31-OnlineAppendix.tex"),             # the LaTeX pass writes it
  .path_numbers = here::here("2_output", "31-OnlineAppendix", "Output", "OA-Numbers.tex"), # every render writes it
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),                   # tested for staleness
  .dir_own      = here::here("2_output", "31-OnlineAppendix", "Output"),                  # the exhibits built here
  .dir_deploy   = fs::path(                                                               # the paper folder
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL                                                                    # found as a terminal would
)
```

The fragment goes to `online_appendix/` in the Overleaf project, and so does `OA-Numbers.tex`, which the paper's
preamble inputs once: `\input{online_appendix/OA-Numbers}`. 30's exhibits reach Overleaf as they always have, from
`200-Paper_figures/current/`.

On the Overleaf side, `9-online_appendix.tex` sets the lettered numbering, points `\oaexhibits` and `\oastatic` at the
project's folders, and inputs the fragment.

# Next

Every exhibit is built. What remains is in the text: the passages marked above, the decisions on which exhibits and
analyses to keep, and the facts to check before they are stated. Appendix E is a list of candidates rather than a
section, and Appendix F waits on the publication route.

:::
