---
title: "Numbers -- every number the paper and the online appendix cite (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  html: default
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr. comment = "" removes the "##"
# prefix from console blocks so they can be copied verbatim.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

```{r}
#| label: load-libraries

# THE COMMONS, AND THIS PAIR'S OWN. _Plots.R gives the figures built here the house theme; _OnlineAppendix.R holds the
# number machinery every chapter shares -- one row of
# the registry resolved over the tibble beside the exhibit that prints it -- and this document is now the one place
# that machinery runs. No chapter's library is sourced: this document reads the files 30 and the chapters wrote and
# calls none of their functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "40-Numbers"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every number the manuscript and the online appendix cite is resolved here, once, and written as one LaTeX file the
Overleaf project inputs. A number is a row of the registry below: the tibble it is read from, the column, the rows,
how several rows reduce to one value, how it is printed, the section of the paper it appears in, and one line saying
what it is. The tibbles are the ones the exhibits are printed from -- 30's under `30-FinalExhibits/Output/Data`, the
appendix chapters' under their own `Data/`, and two built here that no exhibit holds -- so a sentence and the table
beside it cannot disagree.

## Why one file

Until now each appendix chapter wrote its own numbers file and the manuscript typed its numbers. Typed copies stop
being true at the next re-export and nothing reports it; the introduction and Section 4 of the revision disagreed
on the size of the sample, the Compustat match and the share of 8-K filings for exactly that reason. With one
registry a key is unique across the paper, cited as `\pnum{Key}` in the manuscript and `\oanum{Key}` in the
appendix, and both names read the same table.

## What is written

Three files under this document's `Output/`, on every render: `Numbers.tex`, the file Overleaf inputs;
`Numbers.csv`, the same numbers as a register with their source and note, readable without compiling anything;
and `Numbers-unresolved.txt`, the keys that did not resolve and why, empty when all did. `num_deploy()` copies the
first to the paper folder beside the appendix fragments and says whether Overleaf needs a new upload.

## What is not here

Prose. The manuscript's method chapter is `41-Methods`, the appendix chapters are `42-OnlineAppendix-A` to `-D`;
they cite keys and format tibbles, and compute nothing. The regression numbers of Sections 5 and 6 are not in the
registry yet; when they come, they come from the release through 30, not as typed values.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict     = FALSE, # TRUE stops the render on a number that does not resolve or a citation without a key
    Rebuild    = FALSE, # TRUE rebuilds this pair's own tibbles even where their inputs have not changed
    MinMarkers = 1L,    # markers a contract needs to count as redacted by text; the paper's rule (5 = robustness)
    AhciTo     = 2019L, # last order year of the Ahci (2025) comparison
    # THE CHAPTERS' PARAMETERS, moved here with their builders.
    FilesFrom  = 1998.1,           # A: the exhibit-files table's first quarter, as 01A writes year-quarters
    FilesTo    = 2001.2,           # A: and its last
    Titles     = 5L,               # C: descriptions per category in the titles table
    SpacyModel = "en_core_web_trf" # D: the spaCy model 04A ran
  )
)

.dirs_edgar <- rGetEDGAR::get_directories(here::here("2_output", "01A-EdgarIndex", "GetEDGAR"))

.lP$Input <- list(
  Contracts = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"), # the release
  Orders    = fs::path(.lP$Root, "100_Data_Export", "CtoOrders.parquet"), # one row per reference an order makes
  Lib       = here::here("1_code", "40-Numbers.R"),                      # a changed builder rebuilds
  # 30'S OUTPUT, read in place: Data/ for the tibbles its tables print from.
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  DirData30   = here::here("2_output", "30-FinalExhibits", "Output", "Data"),
  # THE CHAPTERS' INPUTS, moved here with their builders.
  DirMaster = .dirs_edgar$MasterIndex$DirParquet,                            # A: the master index 01A mirrors
  DirLinks  = .dirs_edgar$DocLinks$DirMain$Links,                            # A: the document lists 01A mirrors
  Landing   = here::here("2_output", "01A-EdgarIndex", "Output", "LandingPageAll.parquet"), # A: SIC per filing
  ClassFile = here::here("2_output", "03B-ClassifyTrainBERT", "classification",           # C: 03B's output
                         "crowned_classification.parquet"),
  DirStore  = here::here("2_output", "04A-EntityExtract", "Output"),                        # D: the span stores
  Sample    = here::here("2_output", "04A-EntityExtract", "Output", "sample_text.parquet"), # D: the documents
  # THE DATA DIRECTORIES, in search order: 31's first (the moved builders write there), then 30's, then this pair's own.
  DirData   = c(
    here::here("2_output", "31-FinalExhibits", "Output", "Data"),   # the moved builders' data (A, C, D) live here now
    here::here("2_output", "30-FinalExhibits", "Output", "Data"),
    here::here("2_output", "40-Numbers", "Output", "Data")
  ),
  # THE FILES THAT CITE KEYS, scanned under Validation: the manuscript's section files as exported from Overleaf
  # (a folder of .tex, optional) and the appendix chapters' sources.
  DirManuscript = fs::path(.lP$Root, "200-Paper_figures", "Manuscript"),
  Chapters      = here::here("1_code", c("41-Methods.qmd", paste0("42-OnlineAppendix-", c("A", "B", "C", "D"), ".qmd")))
)

.lP$Output <- list(
  DirOwn  = fs::path(.dir_main, "Output"),                            # Data/ for the tibbles built here
  Numbers = fs::path(.dir_main, "Output", "Numbers.tex"),             # the file Overleaf inputs
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix") # beside the appendix fragments
)

# THE SECTIONS OF THE REGISTER, in print order: the manuscript's sections first, then the appendix chapters. A key
# is filed under the first section that cites it.
.num_sections <- c("Intro", "3.1", "3.2", "3.3", "3.4", "4.1", "OA-A", "OA-B", "OA-C", "OA-D")

oa_state_reset()
```

# Input

30 is the one input the builders below do not make for themselves: the release readers and the classification
tibbles its tables print from. The chapters' former inputs -- the master index, the document lists, 03B's
classification file, 04A's span stores -- are listed above and opened by the builders that need them.

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits,                               # 30's output, read in place
  .template     = here::here("1_code", "_Templates", "oa-body.tex"),   # the chapters' template, checked once here
  .bib          = here::here("1_code", "_Templates", "oa-references.bib")
)
```

# Build

Every exhibit any chapter sets, and the two tibbles no exhibit holds. The builders came from the chapters unchanged
and write in 30's layout -- `Tables/`, `Notes/`, `Figures/`, `Data/` -- under this document's output directory,
which the chapters' sources tables name as their own. Each build compares its outputs with its inputs and with this
library, and runs only where an output is missing or older; `Rebuild` forces them all.

```{r}
#| label: build-own
st_own <- c(
  CtoAhci = num_build(
    .name    = "CtoAhci",                                                   # orders on the forms Ahci (2025) covers
    .fun     = \() num_data_cto_ahci(
      .path_orders = .lP$Input$Orders,
      .to          = .lP$Params$AhciTo
    ),
    .inputs  = c(.lP$Input$Orders, .lP$Input$Lib),
    .dir_own = .lP$Output$DirOwn,
    .force   = .lP$Params$Rebuild
  ),
  CtoMarkers = num_build(
    .name    = "CtoMarkers",                                                # orders against text markers, 2008-2018
    .fun     = \() num_data_cto_markers(
      .path_contracts = .lP$Input$Contracts,
      .min_markers    = .lP$Params$MinMarkers
    ),
    .inputs  = c(.lP$Input$Contracts, .lP$Input$Lib),
    .dir_own = .lP$Output$DirOwn,
    .force   = .lP$Params$Rebuild
  )
)
```

```{r}
#| label: build-appendix-a
.b_a <- list(.dir_own = .lP$Output$DirOwn, .force = .lP$Params$Rebuild, .path_lib = .lP$Input$Lib)

st_a <- c(
  ExhibitRequired  = do.call(oaa_build_exhibit_table, .b_a),
  FormDescriptions = do.call(oaa_build_form_descriptions, .b_a),
  FormCoverage     = do.call(oaa_build_coverage, c(.b_a, list(
    .dir_master     = .lP$Input$DirMaster,    # filings per form type
    .path_contracts = .lP$Input$Contracts     # the contracts the database holds
  ))),
  FilingsWithinYear = do.call(oaa_build_within_year, c(.b_a, list(.path_contracts = .lP$Input$Contracts))),
  CtoLinkage       = do.call(oaa_build_cto, c(.b_a, list(
    .path_orders    = .lP$Input$Orders,       # one row per reference an order makes
    .path_contracts = .lP$Input$Contracts     # the release's flag on the sample
  ))),
  TextCounts       = do.call(oaa_build_counts, c(.b_a, list(.path_contracts = .lP$Input$Contracts))),
  ExhibitFiles     = do.call(oaa_build_files, c(.b_a, list(
    .dir_links = .lP$Input$DirLinks,          # the document lists of the index pages, by quarter
    .from      = .lP$Params$FilesFrom,
    .to        = .lP$Params$FilesTo
  ))),
  SeasonedFilers   = do.call(oaa_build_seasoned, c(.b_a, list(
    .path_contracts = .lP$Input$Contracts,    # the sample, its forms and its labels
    .path_landing   = .lP$Input$Landing,      # the SIC code of each filing
    .dir_master     = .lP$Input$DirMaster     # the first EDGAR filing of each CIK
  )))
)
```

```{r}
#| label: build-appendix-b
st_b <- c(
  PipelineStages  = oab_build_stages(
    .dir_own  = .lP$Output$DirOwn,  # the table's wording lives in the library
    .force    = .lP$Params$Rebuild,
    .path_lib = .lP$Input$Lib
  ),
  PackageVersions = oab_build_versions(
    .dir_own = .lP$Output$DirOwn    # rebuilt on every render: the installed versions
  )
)
```

```{r}
#| label: build-appendix-c
.b_c <- list(.dir_data = .lP$Input$DirData30, .dir_own = .lP$Output$DirOwn, .force = .lP$Params$Rebuild,
             .path_lib = .lP$Input$Lib)

st_c <- c(
  ClassLabelled    = do.call(oac_build_labelled, .b_c),  # 30's ClassLabelled, without round and words
  ClassDeployed    = do.call(oac_build_deployed, .b_c),  # 30's ClassSweep, the crowned and deployed rows only
  ClassTransformer = do.call(oac_build_scores, c(.b_c, list(
    .name    = "ClassTransformer",
    .columns = c("Precision", "Recall", "F1", "RecallLenient"),
    .header  = c("Precision", "Recall", "F1", "Lenient recall"),
    .note    = paste(
      "Out-of-fold scores of the transformer that ships on the labelled sample. Sub-category rows score the",
      "detailed prediction against the detailed label; parent rows score the same predictions rolled up to their",
      "parent, so an error inside a parent does not count there. Precision, recall and F1 are per category; the",
      "Total row reports their macro averages. Lenient recall credits a prediction that equals the contract's",
      "second valid category."
    )
  ))),
  ClassConfusion   = do.call(oac_build_confusion, .b_c),
  ClassAmendment   = do.call(oac_build_amendment, .b_c),
  ClassKeyword     = do.call(oac_build_scores, c(.b_c, list(
    .name    = "ClassKeyword",
    .columns = c("Coverage", "Precision", "RecallSel", "F1"),
    .header  = c("Coverage", "Precision", "Recall where committed", "F1"),
    .note    = paste(
      "Out-of-fold scores of the published keyword table on the labelled sample. Coverage is the share of a",
      "category's contracts on which a term of the table fired; the table abstains on the rest. Precision is",
      "over the contracts assigned the category; recall where committed is over the contracts of the category on",
      "which the table committed; F1 combines them. A dash marks a score that is undefined because the table never",
      "assigned the category to any contract. The Total row reports the macro averages."
    )
  ))),
  ClassArms        = do.call(oac_build_arms, .b_c),
  CategoryTitles   = oac_build_titles(
    .path_contracts = .lP$Input$Contracts,  # the filer's description of each contract
    .n              = .lP$Params$Titles,    # descriptions per category
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  ClassSecond      = oac_build_second(      # writes ClassSecondPairs and ClassSecond together
    .path_class = .lP$Input$ClassFile,      # first and second choice per labelled document
    .dir_own    = .lP$Output$DirOwn,
    .force      = .lP$Params$Rebuild,
    .path_lib   = .lP$Input$Lib
  )
)
```

```{r}
#| label: build-appendix-d
st_d <- c(
  EntityCoverage  = oad_build_coverage(
    .dir_store   = .lP$Input$DirStore,      # 04A's three stores, opened read-only
    .path_sample = .lP$Input$Sample,        # the documents every store indexes
    .spacy_model = .lP$Params$SpacyModel,   # the spaCy model printed
    .dir_own     = .lP$Output$DirOwn,
    .force       = .lP$Params$Rebuild,
    .path_lib    = .lP$Input$Lib
  ),
  EntityAlignment = oad_build_alignment(    # writes EntityPositions and EntityAgreement from one pass
    .dir_store   = .lP$Input$DirStore,
    .path_sample = .lP$Input$Sample,
    .spacy_model = .lP$Params$SpacyModel,
    .dir_own     = .lP$Output$DirOwn,
    .force       = .lP$Params$Rebuild,
    .path_lib    = .lP$Input$Lib
  ),
  ContentValues   = oad_build_values(
    .path_contracts = .lP$Input$Contracts,  # the naive and rule-based content columns
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  DurationRungs   = oad_build_duration(
    .path_contracts = .lP$Input$Contracts,  # DurationSource, DurationDropped and the two durations
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  )
)

oa_report_builds(.status = c(st_own, st_a, st_b, st_c, st_d))
```

# The registry

One row per number. `Where` is a filter over the tibble's own columns, evaluated as written; `Fun` reduces the
matching rows to one value, and `one` demands exactly one matching row, which is what catches a filter that silently
matches two. `Column` names a column, or an expression over the tibble's columns where the text needs a share the
tibble holds as two counts. `Section` is where the number first appears in the paper; `Note` is what it is.

The rows are grouped by the section of the paper. The appendix chapters' rows are their former specifications,
moved here unchanged; the manuscript's rows are new.

```{r}
#| label: registry-manuscript
# FILTER HELPERS, named once. The linkage funnel holds one row per step; Code is the release's LinkStatus prefix.
.where_step <- \(.c) paste0("Code == '", .c, "'")
.where_form <- \(.f) paste0("FormFamily == '", .f, "'")
.where_amd  <- \(.f) paste0("FormFamily == '", .f, "' & Amend == 'Amended'")
.where_ahci <- "Row == '10-K, 10-Q and 8-K' & Period != 'all years' & Kind == 'granting-new'"
# THE LADDER (Table 2) holds one row per rung and panel; exclusions are negative, so a count is abs() and a level
# is the sum of the rows down to it.
.where_a   <- \(.r) paste0("Panel == 'Panel A: Unique contracts' & Row == '", .r, "'")
.where_b   <- \(.r) paste0("Panel == 'Panel B: Estimation samples' & Row == '", .r, "'")
.where_b_k <- "Panel == 'Panel B: Estimation samples' & Kind == 'firm'"
.rows_uni  <- "Panel == 'Panel A: Unique contracts' & Row %in% c('Full sample', 'Multiple filer')"
.rows_cs   <- paste0("Panel == 'Panel B: Estimation samples' & ",
                     "Row %in% c('Full sample', 'Malformatted documents', 'Missing Compustat match')")

spec_manuscript <- tibble::tribble(
  ~Key,                        ~Section, ~Exhibit,        ~Column,      ~Fun,  ~Format, ~Where,
  ~Note,
  # 3.1 -- what is downloaded
  "DocsAll",                   "3.1",    "SampleSelection", "Contracts", "one", "count", .where_a(.r = "Full sample"),
  "Exhibit 10 attachments 2001-2024, every registrant copy counted: Table 2's first line",
  "Docs8K",                    "3.1",    "SummarySample", "All",        "one", "count",
  "Rung == 'Item 1.01 announcements recovered'",
  "8-K filings from which an Item 1.01 narrative was recovered",
  "Orders",                    "3.1",    "CtoLinkage",    "N",          "one", "count", "Step == 'Orders in the release'",
  "Confidential treatment orders on EDGAR, 2008 onwards, whatever their status",
  # 3.4 -- orders and their linkage
  "OrderRefs",                 "3.4",    "CtoLinkage",    "N",          "one", "count",
  "Step == 'References to exhibits they make'",
  "Exhibit references the orders make; one order names one or several exhibits",
  "OrderRefsLinked",           "3.4",    "CtoLinkage",    "N",          "one", "count", .where_step(.c = "A-linked"),
  "References that reach an attachment in the register",
  "DocsWithCto",               "3.4",    "CtoLinkage",    "N",          "one", "count", "Kind == 'result'",
  "Unique contracts covered by at least one granted order",
  "OrdersAhci",                "3.4",    "CtoAhci",       "Orders",     "one", "count", .where_ahci,
  "New grants through 2019 whose references name a 10-K, 10-Q or 8-K: the comparison with Ahci (2025)",
  "OrderRefsAhci",             "3.4",    "CtoAhci",       "References", "one", "count", .where_ahci,
  "Exhibit references of those orders",
  "CtoMarkerAgree",            "3.4",    "CtoMarkers",    "Share",      "one", "pct1",
  "Row == 'Share of ordered contracts with a marker'",
  "Share of CTO-covered unique contracts of 2008-2018 that also carry a bracketed redaction marker",
  "MarkerCtoAgree",            "3.4",    "CtoMarkers",    "Share",      "one", "pct1",
  "Row == 'Share of marked contracts with an order'",
  "Share of marked unique contracts of 2008-2018 that are covered by an order",
  # 3.4 -- announcements
  "AnnouncementsNoDate",       "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'No agreement date read in the narrative'",
  "8-Ks whose narrative names no agreement date, dropped before the single-agreement test",
  "AnnouncementsMultiSummary", "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'Two or more agreement dates'",
  "8-Ks dropped because the narrative opens with two or more agreement dates",
  "AnnouncementsMultiExhibit", "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'More than one Exhibit 10 on the 8-K'",
  "8-Ks dropped because more than one Exhibit 10 rides on them",
  "Announcements",             "3.4",    "SummarySample", "All",        "one", "count", "Rung == 'Announcement sample'",
  "Single-agreement Item 1.01 announcements on 8-Ks with at most one Exhibit 10: the paper's sample",
  # 4.1 -- filing types and the ladder, as chapter A defines them
  "Share8K",                   "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "8-K"),
  "Share of unique contracts filed with an 8-K, percent",
  "Share10K",                  "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "10-K"),
  "Share filed with a 10-K, percent",
  "Share10Q",                  "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "10-Q"),
  "Share filed with a 10-Q, percent",
  "ShareS1",                   "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "S-1"),
  "Share filed with an S-1, percent",
  "FirmsAll",                  "4.1",    "SampleSelection", "Firms",     "one", "count", .where_a(.r = "Full sample"),
  "Firms (CIKs) in the full sample",
  "DocsFlagged",               "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_a(.r = "Malformatted documents"),
  "Attachments excluded as malformatted (three text rules and PDF/image placeholders), all copies",
  "DocsCopies",                "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_a(.r = "Multiple filer"),
  "Additional registrant copies of an attachment filed under several CIKs",
  "DocsUnique",                "4.1",    "SampleSelection", "Contracts", "sum", "count", .rows_uni,
  "Distinct attachments 2001-2024: the full sample less the registrant copies",
  "DocsSample",                "4.1",    "SampleSelection", "Contracts", "one", "count", .where_a(.r = "Unique contracts"),
  "Unique contracts with readable text: the descriptive sample",
  "FirmsSample",               "4.1",    "SampleSelection", "Firms",     "one", "count", .where_a(.r = "Unique contracts"),
  "Firms with at least one unique contract",
  "DocsNoCompustat",           "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_b(.r = "Missing Compustat match"),
  "Contracts without a Compustat match in their filing quarter",
  "DocsCompustat",             "4.1",    "SampleSelection", "Contracts", "sum", "count", .rows_cs,
  "Contracts merged to quarterly Compustat: the full sample less malformatted and unmatched",
  "DocsEstimation",            "4.1",    "SampleSelection", "Contracts", "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Contract-level estimation sample",
  "QuartersEstimation",        "4.1",    "SampleSelection", "Quarters",  "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Firm-quarters in the contract-level sample",
  "FirmsEstimation",           "4.1",    "SampleSelection", "Firms",     "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Firms in the contract-level sample",
  "DocsEstimation2008",        "4.1",    "SampleSelection", "Contracts", "one", "count", .where_b(.r = "from 2008"),
  "Contract-level sample from 2008",
  "QuartersFirmLevel",         "4.1",    "SampleSelection", "Quarters",  "one", "count", .where_b_k,
  "Firm-quarters in the firm-level sample, non-filing quarters included",
  "FirmsFirmLevel",            "4.1",    "SampleSelection", "Firms",     "one", "count", .where_b_k,
  "Firms in the firm-level sample"
)

```

```{r}
#| label: registry-appendix-a
# CHAPTER A's rows, as its specification had them, less the keys the manuscript now owns.
.where_reg <- "Group %in% c('Exchange Act registrations', 'Real-estate registrations')"
.where_out <- "Panel == 'Outside it' & Kind == 'total'"
.where_in  <- "Panel == 'In the database' & Kind == 'total'"
.where_all      <- \(.y) paste0("Filers == 'All filers' & Year == ", .y)
.where_seasoned <- \(.y) paste0("Filers == 'Seasoned filers' & Year == ", .y)
.where_group    <- \(.g, .y) paste0("grepl('", .g, "', Filers) & Year == ", .y)

spec_a <- tibble::tribble(
  ~Key,                 ~Exhibit,         ~Column,       ~Fun,  ~Format, ~Where,
  "DocsRelease",        "TextCounts",     "Value",       "one", "count", "Key == 'DocsAll'",
  "DocsReleaseUnique",  "TextCounts",     "Value",       "one", "count", "Key == 'DocsUnique'",
  "DocsReleaseFlagged", "TextCounts",     "Value",       "one", "count", "Key == 'DocsFlagged'",
  "DocsPre2001",        "TextCounts",     "Value",       "one", "count", "Key == 'DocsPre2001'",
  "CovInside",          "FormCoverage",   "Filings",     "one", "count", .where_in,
  "CovSmallBusiness",   "FormCoverage",   "Filings",     "sum", "count", "grepl('Small business', Group)",
  "CovTenKVariants",    "FormCoverage",   "Filings",     "one", "count", "Group == '10-K variants'",
  "CovRegistrations",   "FormCoverage",   "Filings",     "sum", "count", .where_reg,
  "Cov20FFilings",      "FormCoverage",   "Filings",     "one", "count", "Group == 'Foreign annual reports'",
  "Cov20FContracts",    "FormCoverage",   "Contracts",   "one", "count", "Group == 'Foreign annual reports'",
  "CovOutside",         "FormCoverage",   "Filings",     "one", "count", .where_out,
  "FilesShare2000Q2",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '2000 Q2'",
  "FilesShare2000Q3",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '2000 Q3'",
  "FilesShare1999Q4",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '1999 Q4'",
  "ShareForeign",       "FilingTypes",    "N / sum(N)",  "sum", "pct1",  "Region == 'Foreign filings'",
  "Amend8K",            "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "8-K"),
  "Amend10K",           "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "10-K"),
  "Amend10Q",           "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "10-Q"),
  "RuleShort",          "TextCounts",     "Value",       "one", "count", "Key == 'RuleShort'",
  "RuleStopwords",      "TextCounts",     "Value",       "one", "count", "Key == 'RuleStopwords'",
  "RuleNumeric",        "TextCounts",     "Value",       "one", "count", "Key == 'RuleNumeric'",
  "Placeholders",       "TextCounts",     "Value",       "one", "count", "Key == 'Placeholders'",
  "OrderRefsNotEx10",   "CtoLinkage",     "N",           "one", "count", .where_step(.c = "2-"),
  "OrderRefsFrame",     "CtoLinkage",     "N",           "one", "count", .where_step(.c = "6-"),
  "OrderRefsMissing",   "CtoLinkage",     "N",           "one", "count", .where_step(.c = "9-"),
  "LinkedExtensions",   "CtoLinkage",     "N",           "one", "count", "Step == 'Extends an earlier grant'",
  "LinkedDenials",      "CtoLinkage",     "N",           "one", "count", "grepl('^Denies', Step)",
  "NAll2020",           "SeasonedFilers", "N",           "one", "count", .where_all(.y = 2020),
  "NAll2021",           "SeasonedFilers", "N",           "one", "count", .where_all(.y = 2021),
  "NSeasoned2020",      "SeasonedFilers", "N",           "one", "count", .where_seasoned(.y = 2020),
  "NSeasoned2021",      "SeasonedFilers", "N",           "one", "count", .where_seasoned(.y = 2021),
  "RegAll2021",         "SeasonedFilers", "ShareReg",    "one", "pct1",  .where_all(.y = 2021),
  "RegSeasoned2021",    "SeasonedFilers", "ShareReg",    "one", "pct1",  .where_seasoned(.y = 2021),
  "EqAll2021",          "SeasonedFilers", "ShareEquity", "one", "pct1",  .where_all(.y = 2021),
  "EqSeasoned2021",     "SeasonedFilers", "ShareEquity", "one", "pct1",  .where_seasoned(.y = 2021),
  "NBlankCheck2021",    "SeasonedFilers", "N",           "one", "count", .where_group(.g = "Blank-check", .y = 2021),
  "NSeasonedEdgar2021", "SeasonedFilers", "N",           "one", "count", .where_group(.g = "first EDGAR", .y = 2021)
) |>
  dplyr::mutate(
    Section = "OA-A",
    Note    = paste0("Appendix A, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-b
# CHAPTER B's rows: the installed package versions, cited as text.
spec_b <- tibble::tribble(
  ~Key,               ~Exhibit,          ~Column, ~Fun,  ~Format, ~Where,
  "VersionGetEDGAR",  "PackageVersions", "Value", "one", "text",  "Key == 'rGetEDGAR'",
  "VersionLabelDocs", "PackageVersions", "Value", "one", "text",  "Key == 'rLabelDocs'"
) |>
  dplyr::mutate(
    Section = "OA-B",
    Note    = paste0("Appendix B, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-c
# CHAPTER C's rows. The manuscript's Section 3.2 cites the first block, so those are filed under 3.2.
.where_leaf <- "Level1 != 'Amendment' & (Kind == 'sub' | Level1 %in% c('Licenses', 'Leases', 'Other'))"
.where_bert <- "Task == 'ClassDetailed' & startsWith(Engine, 'Bert') & Ships"
.where_kw   <- "Task == 'ClassDetailed' & Engine == 'Kw'"
.where_llm  <- "Task == 'ClassDetailed' & Engine == 'Llm'"
# THE SWEEP TIBBLE holds one row per configuration; the learning rate and the epochs sit in ConfigName (_E6_, _LR2e-05_).
# The factorial is the two learning rates and the two epoch budgets; the runs at 1e-5 and at ten epochs are the two
# checks of the dropped levels and are counted apart.
.in_grid     <- "grepl('_E(3|6)_', ConfigName) & grepl('_LR(2|3)e-05_', ConfigName)"
.where_sweep <- paste0("Task %in% c('ClassDetailed', 'AmendType') & ", .in_grid)
.where_task  <- paste0("Task == 'ClassDetailed' & ", .in_grid)
.where_check <- paste0("Task == 'ClassDetailed' & !(", .in_grid, ")")

spec_c_manuscript <- tibble::tribble(
  ~Key,              ~Exhibit,           ~Column,         ~Fun,   ~Format, ~Where,
  ~Note,
  "NLabelled",       "ClassLabelled",    "N",             "one",  "count", "Kind == 'total'",
  "Manually labeled contracts with readable text",
  "NAmended",        "ClassLabelled",    "N",             "one",  "count", "Row == 'Amended'",
  "Of which amendments",
  "NSecond",         "ClassLabelled",    "Second",        "one",  "count", "Kind == 'total'",
  "Labeled contracts that carry a second category",
  "NRarest",         "ClassLabelled",    "N",             "min",  "count", .where_leaf,
  "Labeled contracts in the smallest detailed category",
  "SweepConfigs",    "ClassSweep",       "1L",            "sum",  "count", .where_sweep,
  "Factorial configurations across the category and the amendment task (32 each; the broad task is a roll-up)",
  "AccDetailed",     "ClassTransformer", "Accuracy",      "one",  "prop3", "Kind == 'total'",
  "Out-of-fold accuracy of the deployed model, category task",
  "F1Detailed",      "ClassTransformer", "F1",            "one",  "prop3", "Kind == 'total'",
  "Out-of-fold macro-F1, category task",
  "LenientDetailed", "ClassTransformer", "RecallLenient", "one",  "prop3", "Kind == 'total'",
  "Accuracy counting a prediction that matches the second label as correct",
  "AccAmend",        "ClassAmendment",   "Accuracy",      "one",  "prop3", "Label == 'Total'",
  "Out-of-fold accuracy, amendment task",
  "F1Amend",         "ClassAmendment",   "F1",            "one",  "prop3", "Label == 'Total'",
  "Out-of-fold macro-F1, amendment task",
  "KwCoverage",      "ClassArms",        "Coverage",      "one",  "pct1",  .where_kw,
  "Share of labeled contracts the keyword table classifies, percent",
  "KwAccCommitted",  "ClassArms",        "AccuracySel",   "one",  "prop3", .where_kw,
  "Accuracy of the keyword table where it classifies"
) |>
  dplyr::mutate(Section = "3.2")

spec_c <- tibble::tribble(
  ~Key,           ~Exhibit,           ~Column,   ~Fun,   ~Format, ~Where,
  "TitlesNamed",  "CategoryTitles",   "pNamed",  "mean", "pct1",  "Rank == 1",
  "SweepPerTask", "ClassSweep",       "1L",      "sum",  "count", .where_task,
  "SweepChecks",  "ClassSweep",       "1L",      "sum",  "count", .where_check,
  "F1Llm",        "ClassArms",        "MacroF1", "one",  "prop3", .where_llm,
  "AccLlm",       "ClassArms",        "Accuracy", "one", "prop3", .where_llm,
  "AccBert",      "ClassArms",        "Accuracy", "one", "prop3", .where_bert,
  "AccCeiling",   "ClassArmsCeiling", "Accuracy", "max", "prop3", "TRUE",
  "CeilGain512",  "ClassArmsCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512'",
  "CeilGainKw",   "ClassArmsCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512 or Kw'",
  "CeilGainLlm",  "ClassArmsCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512 or Kw or Llm'",
  "SecondDocs",   "ClassSecond",      "N",       "one",  "count", "Kind == 'total'",
  "SecondHit1",   "ClassSecond",      "Hit1 / N", "one", "pct1",  "Kind == 'total'",
  "SecondHit2",   "ClassSecond",      "Hit2 / N", "one", "pct1",  "Kind == 'total'",
  "SecondBoth",   "ClassSecond",      "Both / N", "one", "pct1",  "Kind == 'total'",
  "MarginDual",   "ClassSecond",      "Value",   "one",  "prop3", "Row == 'Margin, two labels'",
  "MarginSingle", "ClassSecond",      "Value",   "one",  "prop3", "Row == 'Margin, one label'"
) |>
  dplyr::mutate(
    Section = "OA-C",
    Note    = paste0("Appendix C, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-d
# CHAPTER D's rows. Section 3.3 cites the values and the duration rungs; the rest is the appendix's.
.where_cov <- \(.f, .e) paste0("Family == '", .f, "' & Entity == '", .e, "'")
.where_gpe <- "Block == 'pairwise' & Entity == 'GPE' & ProducerA == 'lexnlp' & ProducerB == 'matcon'"

spec_d_manuscript <- tibble::tribble(
  ~Key,           ~Exhibit,        ~Column,     ~Fun,  ~Format, ~Where,
  ~Note,
  "ValPartNaive", "ContentValues", "PartNaive", "one", "num2",  "Kind == 'total'",
  "Distinct organizations a contract names, mean",
  "ValPartRule",  "ContentValues", "PartRule",  "one", "num2",  "Kind == 'total'",
  "Contracting parties (registrant, co-registrants, counterparties), mean",
  "ValCtryNaive", "ContentValues", "CtryNaive", "one", "num2",  "Kind == 'total'",
  "Countries a contract mentions, mean",
  "ValCtryReg",   "ContentValues", "CtryReg",   "one", "num2",  "Kind == 'total'",
  "Countries attributed to the registrant, mean",
  "ValCtryCpty",  "ContentValues", "CtryCpty",  "one", "num2",  "Kind == 'total'",
  "Countries attributed to the counterparties, mean",
  "DurTerm",      "DurationRungs", "Share",     "one", "pct1",  "Rung == 'term'",
  "Share of contracts whose end comes from a stated term, percent",
  "DurMedRule",   "DurationRungs", "Med",       "one", "num1",  "Rung == 'all-rule'",
  "Median duration in years under the rule",
  "DurMedNaive",  "DurationRungs", "Med",       "one", "num1",  "Rung == 'all-naive'",
  "Median duration in years reading the latest date in the contract as its end"
) |>
  dplyr::mutate(Section = "3.3")

spec_d <- tibble::tribble(
  ~Key,                ~Exhibit,          ~Column,      ~Fun,  ~Format, ~Where,
  "NerDocs",           "EntityCoverage",  "nDocs",      "max", "count", "TRUE",
  "CovOrgSpacy",       "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "ORG"),
  "CovOrgLexnlp",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "ORG"),
  "SpansOrgSpacy",     "EntityCoverage",  "Spans",      "one", "count", .where_cov(.f = "spacy",  .e = "ORG"),
  "SpansOrgLexnlp",    "EntityCoverage",  "Spans",      "one", "count", .where_cov(.f = "lexnlp", .e = "ORG"),
  "CovPersonSpacy",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "PERSON"),
  "CovGpeSpacy",       "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "GPE"),
  "CovGpeLexnlp",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "GPE"),
  "CovDateLexnlp",     "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "DATE"),
  "CovMoneyLexnlp",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "MONEY"),
  "CovMoneyMatcon",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "MONEY"),
  "CovTermMatcon",     "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "TERM"),
  "CovRedactMatcon",   "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "REDACT"),
  "CovLawMatcon",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "LAW"),
  "ContrastOrgLexnlp", "EntityPositions", "Contrast",   "max", "num2",  "Producer == 'lexnlp' & Entity == 'ORG'",
  "ContrastOrgSpacy",  "EntityPositions", "Contrast",   "max", "num2",  "Producer == 'spacy:trf' & Entity == 'ORG'",
  "JaccardOrg",        "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'ORG'",
  "JaccardGpeLex",     "EntityAgreement", "Jaccard",    "one", "num2",  .where_gpe,
  "ExactGpeLex",       "EntityAgreement", "ExactShare", "one", "pct1",  .where_gpe,
  "JaccardGpeSpacy",   "EntityAgreement", "Jaccard",    "max", "num2",
                       "Block == 'pairwise' & Entity == 'GPE' & (ProducerA == 'spacy:trf' | ProducerB == 'spacy:trf')",
  "JaccardDate",       "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'DATE'",
  "ExactDate",         "EntityAgreement", "ExactShare", "one", "pct1",  "Block == 'pairwise' & Entity == 'DATE'",
  "JaccardMoney",      "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'MONEY'",
  "OneProducerGpe",    "EntityAgreement", "Share",      "one", "pct1",
                       "Block == 'consensus' & Entity == 'GPE' & NProducer == 1",
  "OneProducerOrg",    "EntityAgreement", "Share",      "one", "pct1",
                       "Block == 'consensus' & Entity == 'ORG' & NProducer == 1",
  "DurOpen",           "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'open'",
  "DurCue",            "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'cue'",
  "DurMaxDate",        "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'maxdate'",
  "DurNone",           "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'none'",
  "DurCapped",         "DurationRungs",   "N",          "one", "count", "Rung == 'dropped-capped'",
  "DurDefRule",        "DurationRungs",   "Defined",    "one", "count", "Rung == 'all-rule'",
  "DurDefNaive",       "DurationRungs",   "Defined",    "one", "count", "Rung == 'all-naive'"
) |>
  dplyr::mutate(
    Section = "OA-D",
    Note    = paste0("Appendix D, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-assemble
tab_numbers_spec <- dplyr::bind_rows(
  spec_manuscript,
  spec_c_manuscript,
  spec_d_manuscript,
  spec_a,
  spec_b,
  spec_c,
  spec_d
) |>
  num_registry_check(.sections = .num_sections)

n_sec_ <- dplyr::n_distinct(tab_numbers_spec$Section)
cli::cli_alert_info("{nrow(tab_numbers_spec)} numbers registered across {n_sec_} sections.")

tab_sources <- num_report_sources(
  .spec     = tab_numbers_spec,   # which tibbles the registry names
  .dir_data = .lP$Input$DirData   # and where each is looked for, in order
)
```

# Numbers

```{r}
#| label: numbers-resolve
tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,  # every number the paper and the appendix cite
  .dir_data = .lP$Input$DirData  # the tibbles behind the exhibits, 30's first
)

oa_report_numbers(
  .tab    = tab_numbers,       # resolved above
  .strict = .lP$Params$Strict  # TRUE stops the render on an unresolved number
)
```

```{r}
#| label: numbers-write
paths_numbers <- num_numbers_write(
  .tab     = tab_numbers,        # resolved above
  .dir_own = .lP$Output$DirOwn,  # Numbers.tex, Numbers.csv, Numbers-unresolved.txt
  .doc     = .name_script
)
```

# Validation

**Every citation resolves, and every key is cited.** The manuscript's section files, where a folder of them exists,
and the appendix chapters' sources are scanned for `\pnum{}`, `\oanum{}` and `oa_n("")`. A cited key the registry
does not hold would print as `??Key`; a registered key cited nowhere is either dead weight or a chapter not yet
written, and is listed so the registry stays honest.

```{r}
#| label: validate-citations
paths_cite <- c(
  if (fs::dir_exists(.lP$Input$DirManuscript)) fs::dir_ls(.lP$Input$DirManuscript, glob = "*.tex"),
  .lP$Input$Chapters
)

tab_cited <- num_cited_keys(.paths = paths_cite)

lst_check <- num_check_citations(
  .tab    = tab_numbers,       # what is defined
  .cited  = tab_cited,         # what is cited, where
  .strict = .lP$Params$Strict  # TRUE aborts on a citation without a key
)
```

**The register, as written.** The same table `Numbers.csv` holds; what a reader opens to check a value.

```{r}
#| label: validate-register
tab_numbers |>
  dplyr::select(dplyr::all_of(c("Section", "Key", "Value", "Status", "Note"))) |>
  tbl_say()
```

# Deployment

Every render writes `Output/Numbers.tex`. One call copies it to the paper folder beside the appendix fragments,
archives the version it replaces, and says whether the content changed -- which, while Overleaf is updated by hand,
is whether to upload it.

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")
source(here::here("1_code", "40-Numbers.R"), encoding = "UTF-8")

num_deploy(
  .path_numbers = here::here("2_output", "40-Numbers", "Output", "Numbers.tex"),
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  )
)
```

On the Overleaf side, the preamble inputs this one file in place of the four chapter files:
`\input{online_appendix/Numbers}`. The chapter files can be removed once it compiles.

```{r}
#| label: deploy-status
if (fs::file_exists(.lP$Output$Numbers)) {
  cli::cli_alert_info(
    "{.file Numbers.tex} last written {format(fs::file_info(.lP$Output$Numbers)$modification_time, '%Y-%m-%d %H:%M')}."
  )
}
```

# Overview

```{r}
#| label: overview
tab_numbers |>
  dplyr::count(.data$Section, Resolved = .data$Status == "ok", name = "N") |>
  tidyr::pivot_wider(names_from = "Resolved", values_from = "N", values_fill = 0L) |>
  tbl_say()
```

# Next

- Rename the moved builders (`oaa_*`, `oac_*`, `oad_*`) to `num_*` once the identity checks against the chapters'
  last outputs have passed; until then the names say where each came from.
- The introduction and Section 4 keys beyond chapter A's (words per contract by class, contracts per filing quarter
  by industry, the amendment share, the redaction shares before and after the FAST Act): rows over 30's
  `ContentDetail`, `FirmFundamentals`, `ContractTypes` and `RedactionsTime`, once their columns are confirmed.
- `AnnouncementsNoDate` is a third exclusion the manuscript does not mention; either the sentence names it or the
  sample definition folds it into the single-agreement test.
