---
title: "Online Appendix B -- The Software (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THE APPENDIX'S OWN. init_*() resolve this document's paths, tbl_say() is the fixed-width printer
# every report below uses, _Plots.R gives the figures built here the house theme, and _OnlineAppendix.R is the
# machinery every chapter of the appendix shares: numbers, floats, references, markers, the LaTeX pass, deployment.
# No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "40-OnlineAppendix-B"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is Appendix B of the online appendix: the software the database is built with -- the pipeline as a
whole, the two R packages published with the paper, and the classification and extraction code. Its text is written
here once and rendered twice: to html, the runbook a reader of the replication site follows, and to a LaTeX
fragment that the paper's Overleaf project inputs. The fragment carries the chapter and nothing else; everything
that makes this a runbook sits in blocks the LaTeX pass removes.

The conventions are those of every chapter of the appendix and are set out once, in the Purpose of
`40-OnlineAppendix-A`: why the text lives here and not in Overleaf, what a fragment may contain, where exhibits come
from, and what is recomputed. This chapter is the smallest of the six. It has one exhibit of its own, the pipeline
table, whose content is text rather than data and is kept in the library as a tibble so that it deploys like every
other exhibit; and two numbers, the versions of the packages, read from the installed packages so that the text
cannot name a version the database was not built with.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict   = FALSE, # TRUE stops the render on an exhibit that is not built or a number that does not resolve
    FigWidth = 0.96,  # a figure's width as a share of the text width; no figure here, kept for the context
    Rebuild  = FALSE  # TRUE rebuilds this chapter's own exhibits even where their inputs have not changed
  )
)

.lP$Input <- list(
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),          # 30's output, for the input check
  Lib         = here::here("1_code", "40-OnlineAppendix-B.R"),                 # the table's only input
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"),
  Qmd         = here::here("1_code", "40-OnlineAppendix-B.qmd")
)

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "40-OnlineAppendix-B.tex"),
  Numbers = utils_file_path(.dir_main, "Output", "OA-Numbers-B.tex"),
  DirOwn  = fs::path(.dir_main, "Output"),
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")
)

oa_state_reset()
```

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,             ~Kind,   ~Source, ~Caption,
  "B",      "PipelineStages",  "table", "B",     "The pipeline, stage by stage"
)

tab_sources <- tibble::tribble(
  ~Source, ~Dir,                            ~Macro,
  "30",    .lP$Input$DirExhibits,           "\\oaexhibits",
  "B",     as.character(.lP$Output$DirOwn), "\\oaown"
)

tab_static <- tibble::tibble(
  Name = character(0),
  File = character(0),
  Note = character(0)
)
```

# Input

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits, # 30's output; nothing of it is set here, but the check is the same
  .template     = .lP$Input$Template,
  .bib          = .lP$Input$Bib
)
```

# Build

```{r}
#| label: build-exhibits
st_build <- c(
  PipelineStages  = oab_build_stages(
    .dir_own  = .lP$Output$DirOwn,  # this chapter's own exhibits
    .force    = .lP$Params$Rebuild, # TRUE rebuilds regardless
    .path_lib = .lP$Input$Lib       # the table's wording lives in the library
  ),
  PackageVersions = oab_build_versions(
    .dir_own = .lP$Output$DirOwn    # rebuilt on every render
  )
)

oa_report_builds(.status = st_build)
```

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats    = tab_floats,
  .static    = tab_static,
  .sources   = tab_sources,
  .own       = "B",
  .dir_doc   = fs::path_dir(.lP$Input$Qmd),
  .fig_width = .lP$Params$FigWidth,
  .strict    = .lP$Params$Strict
)

oa_report_floats(.files = ctx_oa$Files)
```

# Numbers

```{r}
#| label: numbers-resolve
tab_numbers_spec <- tibble::tribble(
  ~Key,                 ~Exhibit,          ~Column, ~Fun,  ~Format, ~Where,
  "VersionGetEDGAR",    "PackageVersions", "Value", "one", "text",  "Key == 'rGetEDGAR'",
  "VersionLabelDocs",   "PackageVersions", "Value", "one", "text",  "Key == 'rLabelDocs'"
)

tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,
  .dir_data = fs::path(.lP$Output$DirOwn, "Data")
)

oa_report_numbers(
  .tab    = tab_numbers,
  .strict = .lP$Params$Strict
)
```

```{r}
#| label: numbers-write
oa_numbers_write(
  .tab  = tab_numbers,
  .path = .lP$Output$Numbers,
  .doc  = .name_script
)
```

:::

::: {.content-visible when-format="html"}

# Appendix B

:::

```{=latex}
\clearpage
```

## The software {#sec-oa-b}

The database is built by a pipeline of six stages, two of which are R packages published with the paper and two of
which are code published alongside it. This appendix describes them at the level a reader needs to place the chapters
that follow; each package carries its own documentation, and how the code is obtained is set out in Appendix F.

### The pipeline {#sec-oa-b-pipeline}

`r oa_ref(.name = "PipelineStages")` lists the stages in the order they run. Each reads what the previous one
produced and writes its own result, so a stage can be rerun -- with a new model, a changed rule, a further year --
without repeating the ones before it. Acquisition is the work of rGetEDGAR (Section B.2) and is described, with
what it downloads and what it leaves out, in Appendix A. The database stage turns downloaded documents into contract
rows (Section A.4). The labelled sample is produced with rLabelDocs (Section B.3). Classification and entity
extraction are the subject of Appendices C and D, and the code that runs them is described in Section B.4. The
release is Appendix F.

```{r}
#| label: float-pipeline-stages
#| results: asis
oa_float(.name = "PipelineStages")
```

### rGetEDGAR {#sec-oa-b-rgetedgar}

rGetEDGAR retrieves EDGAR filings and converts them to text. It is not tied to material contracts: a run is defined
by a period, a set of filers, the form types and the exhibit types wanted, so the frame of this database is one
selection among many the package supports. Retrieval runs in three stages -- EDGAR's quarterly master index, which
lists every filing; the index page of each selected filing, which lists its documents; and the documents themselves
-- and each stage stores its result, so that a later stage never repeats an earlier stage's requests and an
interrupted run resumes where it stopped. Requests carry the identification the SEC requires and stay under its rate
limit; a request that fails is logged and skipped, so one bad response cannot stall a run of hundreds of thousands.
Each document is stored twice: as the text of the filed document, with the reading of HTML that preserves the
whitespace filers use to lay out a contract, and in a standardised form -- punctuation removed, whitespace collapsed,
transliterated to ASCII and upper-cased -- on which the keyword table and the text searches of this paper run. The
database was built with version `r oa_n(.key = "VersionGetEDGAR")`, published at
`github.com/MatthiasUckert/rGetEDGAR`.

### rLabelDocs {#sec-oa-b-rlabeldocs}

rLabelDocs is an application for labelling documents against a classification scheme, built for projects with
several annotators. A scheme -- the questions an annotator answers about a document and the answers each admits --
is a table the project supplies, so the package is tied neither to contracts nor to any one taxonomy, and several
schemes can run over the same documents in one pass, which is how a contract received its category and its amendment
flag together. Labels are kept as an append-only log: every answer is recorded with its document, annotator and
time, the current label is the newest entry, and nothing is overwritten, so a correction leaves the original in
place and the labelling can be read as it stood at any earlier moment. The application records a hash of the scheme
when labelling begins and warns if the scheme changes afterwards -- the error that would otherwise pass unnoticed,
answers given under one set of categories and read under another. The labelled sample of Appendix C was produced
with version `r oa_n(.key = "VersionLabelDocs")`, published at `github.com/MatthiasUckert/rLabelDocs`.

### The classifier and the extractors {#sec-oa-b-code}

The classification and extraction stages are code rather than packages, written in Python where the model libraries
live and in R where the pipeline does. The classifier is a pair of scripts around the Hugging Face transformers
library: one fine-tunes a pre-trained legal-domain transformer on the labelled sample, with the training run set by
a configuration file rather than by edits to the code, and one applies the resulting model to the corpus and writes,
for every contract, the top categories with their probabilities. The keyword table is derived from the labelled
sample by the pipeline itself and is published as a file, so that it can be applied without the model. The entity
extractors are of two kinds: two scripts that run the LexNLP and spaCy libraries over every contract and write each
entity as a span with its position in the text, and the pattern and gazetteer extractors of the pipeline, which find
what those libraries do not -- exhibit-style party definitions, contract dates, monetary amounts, redaction markers
-- and are regular expressions and lookup tables rather than models. The rules that turn spans into the release's
variables (Appendix D) are part of the pipeline. All of it is published with the paper; the form of the publication
is set out in Appendix F.

::: {.content-visible when-format="html"}

# Validation

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,
  .path_qmd     = .lP$Input$Qmd,
  .dir_exhibits = .lP$Input$DirExhibits
)
```

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "40-OnlineAppendix-B.qmd"),
  .path_tex     = here::here("_rendered", "1_code", "40-OnlineAppendix-B.tex"),
  .path_numbers = here::here("2_output", "40-OnlineAppendix-B", "Output", "OA-Numbers-B.tex"),
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  .dir_own      = here::here("2_output", "40-OnlineAppendix-B", "Output"),
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL
)
```

# Next

**40-OnlineAppendix-C** -- the classification approach.

:::
