---
title: "Online Appendix D -- Entity Extraction and the Rules (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THE APPENDIX'S OWN. init_*() resolve this document's paths, tbl_say() is the fixed-width printer
# every report below uses, _Plots.R gives the figures built here the house theme, and _OnlineAppendix.R is the
# machinery every chapter of the appendix shares: numbers, floats, references, markers, the LaTeX pass, deployment.
# No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "40-OnlineAppendix-D"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is Appendix D of the online appendix: how the content variables of the release -- partners, places,
dates and duration, amounts, redaction markers -- are extracted from the text, and why they are extracted the way
they are. The chapter tells one story. Two general-purpose recognisers were the natural candidates and were tried;
what each does well and where each falls short led to purpose-built extractors; all of them disagree enough that
the release keeps every span with its position, so that a rule is a query over stored context; five such rules turn
spans into variables; and the last section reads what the rules change against the naive reading. The chapter is
upfront that the rules are pre-work: even with them, the extraction is not certain, and a reader with a different
question writes a different rule over the same spans.

The conventions are those of every chapter of the appendix and are set out once, in the Purpose of
`40-OnlineAppendix-A`. Five exhibits are built here: what each extractor found on the labelled sample, counted from
the span stores 04A wrote; where in a contract the candidates fall and how far the extractors agree, computed from
the same stores with 04A's definitions; where each contract's end date comes from, and what the content variables are
worth under both readings, from the release. The naive-against-rule coverage by category is 30's.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict     = FALSE,
    FigWidth   = 0.96,
    Rebuild    = FALSE,
    SpacyModel = "en_core_web_trf"  # the spaCy model 04A ran; the others are declared there and not run
  )
)

.lP$Input <- list(
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  Contracts   = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),           # the release
  DirStore    = here::here("2_output", "04A-EntityExtract", "Output"),                 # the three span stores
  Sample      = here::here("2_output", "04A-EntityExtract", "Output", "sample_text.parquet"),
  Lib         = here::here("1_code", "40-OnlineAppendix-D.R"),
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"),
  Qmd         = here::here("1_code", "40-OnlineAppendix-D.qmd")
)

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "40-OnlineAppendix-D.tex"),
  Numbers = utils_file_path(.dir_main, "Output", "OA-Numbers-D.tex"),
  DirOwn  = fs::path(.dir_main, "Output"),
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")
)

oa_state_reset()
```

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,             ~Kind,   ~Source, ~Caption,
  "D",      "EntityCoverage",  "table",  "D",     "What each extractor found on the labelled sample",
  "D",      "EntityPositions", "figure", "D",     "Where in the contract each extractor's candidates fall",
  "D",      "EntityAgreement", "figure", "D",     "How far the extractors agree about what is there",
  "D",      "DurationRungs",   "table",  "D",     "The source of each contract's end date",
  "D",      "ContentContrast", "table",  "30",    "Naive and rule-based content variables, by category: coverage",
  "D",      "ContentValues",   "table",  "D",     "Naive and rule-based content variables, by category: values"
)

tab_sources <- tibble::tribble(
  ~Source, ~Dir,                            ~Macro,
  "30",    .lP$Input$DirExhibits,           "\\oaexhibits",
  "D",     as.character(.lP$Output$DirOwn), "\\oaown"
)

tab_static <- tibble::tibble(
  Name = character(0),
  File = character(0),
  Note = character(0)
)
```

# Input

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits,
  .template     = .lP$Input$Template,
  .bib          = .lP$Input$Bib
)
```

# Build

```{r}
#| label: build-exhibits
st_build <- c(
  EntityCoverage = oad_build_coverage(
    .dir_store   = .lP$Input$DirStore,      # 04A's three stores, opened read-only
    .path_sample = .lP$Input$Sample,        # the documents every store indexes
    .spacy_model = .lP$Params$SpacyModel,   # the spaCy model printed
    .dir_own     = .lP$Output$DirOwn,
    .force       = .lP$Params$Rebuild,
    .path_lib    = .lP$Input$Lib
  ),
  EntityAlignment = oad_build_alignment(   # writes EntityPositions and EntityAgreement from one pass
    .dir_store   = .lP$Input$DirStore,      # the same three stores
    .path_sample = .lP$Input$Sample,        # document lengths, so a position is comparable across documents
    .spacy_model = .lP$Params$SpacyModel,
    .dir_own     = .lP$Output$DirOwn,
    .force       = .lP$Params$Rebuild,
    .path_lib    = .lP$Input$Lib
  ),
  ContentValues = oad_build_values(
    .path_contracts = .lP$Input$Contracts,  # the naive and rule-based content columns
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  ),
  DurationRungs = oad_build_duration(
    .path_contracts = .lP$Input$Contracts,  # DurationSource, DurationDropped and the two durations
    .dir_own        = .lP$Output$DirOwn,
    .force          = .lP$Params$Rebuild,
    .path_lib       = .lP$Input$Lib
  )
)

oa_report_builds(.status = st_build)
```

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats    = tab_floats,
  .static    = tab_static,
  .sources   = tab_sources,
  .own       = "D",
  .dir_doc   = fs::path_dir(.lP$Input$Qmd),
  .fig_width = .lP$Params$FigWidth,
  .strict    = .lP$Params$Strict
)

oa_report_floats(.files = ctx_oa$Files)
```

# Numbers

```{r}
#| label: numbers-resolve
# THE COVERAGE TABLE: one row per family, model and entity; spaCy at the model 04A ran.
.where_cov <- \(.f, .e) paste0("Family == '", .f, "' & Entity == '", .e, "'",
                               if (.f == "spacy") paste0(" & Model == '", .lP$Params$SpacyModel, "'") else "")

tab_numbers_spec <- tibble::tribble(
  ~Key,             ~Exhibit,         ~Column,    ~Fun,  ~Format, ~Where,
  "NerDocs",        "EntityCoverage", "nDocs",    "max", "count", "TRUE",
  "CovOrgSpacy",    "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "spacy",  .e = "ORG"),
  "CovOrgLexnlp",   "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "lexnlp", .e = "ORG"),
  "SpansOrgSpacy",  "EntityCoverage", "Spans",    "one", "count", .where_cov(.f = "spacy",  .e = "ORG"),
  "SpansOrgLexnlp", "EntityCoverage", "Spans",    "one", "count", .where_cov(.f = "lexnlp", .e = "ORG"),
  "CovPersonSpacy", "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "spacy",  .e = "PERSON"),
  "CovGpeSpacy",    "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "spacy",  .e = "GPE"),
  "CovGpeLexnlp",   "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "lexnlp", .e = "GPE"),
  "CovDateLexnlp",  "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "lexnlp", .e = "DATE"),
  "CovMoneyLexnlp", "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "lexnlp", .e = "MONEY"),
  "CovMoneyMatcon", "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "matcon", .e = "MONEY"),
  "CovTermMatcon",  "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "matcon", .e = "TERM"),
  "CovRedactMatcon", "EntityCoverage", "Coverage", "one", "pct1", .where_cov(.f = "matcon", .e = "REDACT"),
  "CovLawMatcon",   "EntityCoverage", "Coverage", "one", "pct1",  .where_cov(.f = "matcon", .e = "LAW"),
  # POSITIONS AND AGREEMENT carry 04A's contrast (end-of-document share over mid-document share) and Jaccard.
  "ContrastOrgLexnlp", "EntityPositions", "Contrast", "max", "num2", "Producer == 'lexnlp' & Entity == 'ORG'",
  "ContrastOrgSpacy",  "EntityPositions", "Contrast", "max", "num2", "Producer == 'spacy:trf' & Entity == 'ORG'",
  "JaccardOrg",     "EntityAgreement", "Jaccard",  "one", "num2",  "Block == 'pairwise' & Entity == 'ORG'",
  "JaccardGpeLex",  "EntityAgreement", "Jaccard",  "one", "num2",
                    "Block == 'pairwise' & Entity == 'GPE' & ProducerA == 'lexnlp' & ProducerB == 'matcon'",
  "ExactGpeLex",    "EntityAgreement", "ExactShare", "one", "pct1",
                    "Block == 'pairwise' & Entity == 'GPE' & ProducerA == 'lexnlp' & ProducerB == 'matcon'",
  "JaccardGpeSpacy", "EntityAgreement", "Jaccard", "max", "num2",
                    "Block == 'pairwise' & Entity == 'GPE' & ProducerA == 'spacy:trf'",
  "JaccardDate",    "EntityAgreement", "Jaccard",  "one", "num2",  "Block == 'pairwise' & Entity == 'DATE'",
  "ExactDate",      "EntityAgreement", "ExactShare", "one", "pct1", "Block == 'pairwise' & Entity == 'DATE'",
  "JaccardMoney",   "EntityAgreement", "Jaccard",  "one", "num2",  "Block == 'pairwise' & Entity == 'MONEY'",
  "OneProducerGpe", "EntityAgreement", "Share",    "one", "pct1",
                    "Block == 'consensus' & Entity == 'GPE' & NProducer == 1",
  "OneProducerOrg", "EntityAgreement", "Share",    "one", "pct1",
                    "Block == 'consensus' & Entity == 'ORG' & NProducer == 1",
  # THE VALUES COMPANION: the Total row.
  "ValPartNaive",   "ContentValues",  "PartNaive", "one", "num2",  "Kind == 'total'",
  "ValPartRule",    "ContentValues",  "PartRule",  "one", "num2",  "Kind == 'total'",
  "ValCtryNaive",   "ContentValues",  "CtryNaive", "one", "num2",  "Kind == 'total'",
  "ValCtryReg",     "ContentValues",  "CtryReg",   "one", "num2",  "Kind == 'total'",
  "ValCtryCpty",    "ContentValues",  "CtryCpty",  "one", "num2",  "Kind == 'total'",
  "ValAmtNaive",    "ContentValues",  "AmtNaive",  "one", "num2",  "Kind == 'total'",
  "ValAmtRule",     "ContentValues",  "AmtRule",   "one", "num2",  "Kind == 'total'",
  "DurTerm",        "DurationRungs",  "Share",    "one", "pct1",  "Rung == 'term'",
  "DurOpen",        "DurationRungs",  "Share",    "one", "pct1",  "Rung == 'open'",
  "DurCue",         "DurationRungs",  "Share",    "one", "pct1",  "Rung == 'cue'",
  "DurMaxDate",     "DurationRungs",  "Share",    "one", "pct1",  "Rung == 'maxdate'",
  "DurNone",        "DurationRungs",  "Share",    "one", "pct1",  "Rung == 'none'",
  "DurCapped",      "DurationRungs",  "N",        "one", "count", "Rung == 'dropped-capped'",
  "DurMedRule",     "DurationRungs",  "Med",      "one", "num1",  "Rung == 'all-rule'",
  "DurMedNaive",    "DurationRungs",  "Med",      "one", "num1",  "Rung == 'all-naive'",
  "DurDefRule",     "DurationRungs",  "Defined",  "one", "count", "Rung == 'all-rule'",
  "DurDefNaive",    "DurationRungs",  "Defined",  "one", "count", "Rung == 'all-naive'"
)

tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,
  .dir_data = c(
    fs::path(.lP$Input$DirExhibits, "Data"),
    fs::path(.lP$Output$DirOwn, "Data")
  )
)

oa_report_numbers(
  .tab    = tab_numbers,
  .strict = .lP$Params$Strict
)
```

```{r}
#| label: numbers-write
oa_numbers_write(
  .tab  = tab_numbers,
  .path = .lP$Output$Numbers,
  .doc  = .name_script
)
```

:::

::: {.content-visible when-format="html"}

# Appendix D

:::

```{=latex}
\clearpage
```

## Entity extraction and the rules {#sec-oa-d}

The release carries, for every contract, its partners, the places they are located, its start, end and duration,
the amounts it names and the markers of what its filer redacted. The paper uses these variables descriptively, and
this appendix describes how they are extracted and how far they can be trusted. Section D.1 sets out what the two
general-purpose recognisers that were the natural candidates do well and where they fall short; D.2 the extractors
written for the database; D.3 why the release keeps every span with its position rather than a count; D.4 the
five rules that turn spans into variables; and D.5 what the rules change against a naive reading of the same spans.

### Two general-purpose recognisers {#sec-oa-d-recognisers}

Named-entity recognition is a solved problem for news text, and two systems bring it to legal text: LexNLP
[@bommarito2021lexnlp], a library of extractors written for contracts, and spaCy [@honnibal2020spacy], whose
transformer model is the general recogniser of the field. Both were run on the `r oa_n(.key = "NerDocs")` contracts
of the labelled sample, and `r oa_ref(.name = "EntityCoverage")` reports what each proposed. Both cover the sample:
spaCy finds an organisation in `r oa_n(.key = "CovOrgSpacy")` percent of contracts and LexNLP in
`r oa_n(.key = "CovOrgLexnlp")` percent, and both find places in more than nine contracts in ten. spaCy is the more
complete recogniser -- it also finds persons, in `r oa_n(.key = "CovPersonSpacy")` percent of contracts, and it
finds every company a contract mentions. LexNLP reads dates and countries reliably, and its organisations sit where
the parties are named. `r oa_ref(.name = "EntityPositions")` shows where each extractor's candidates fall in the
contract: LexNLP's organisations concentrate at the two ends, the preamble and the signature block, where the
share of candidates in the first and last tenth of a contract is `r oa_n(.key = "ContrastOrgLexnlp")` times the
share through the middle; spaCy's organisations draw a flat line, `r oa_n(.key = "ContrastOrgSpacy")` times, which
is what an even spread through the body gives. For places and dates, LexNLP and the pattern extractors trace the
same curve.

Neither is sufficient, for different reasons. spaCy proposes `r oa_n(.key = "SpansOrgSpacy")` organisations against
LexNLP's `r oa_n(.key = "SpansOrgLexnlp")`, spread evenly through the text: it recognises every mention of every
company, which is the right answer to a different question. Finding the parties to a contract among eleven times
as many candidates is harder, not easier, and the model reads a contract in the time the other extractors read
ten. LexNLP's geography stops at the country -- its dictionary holds countries and territories, so a contract
naming Frankfurt yields Germany -- and its money extractor fires in `r oa_n(.key = "CovMoneyLexnlp")` percent of
contracts, where a pattern finds an amount in `r oa_n(.key = "CovMoneyMatcon")` percent. And neither system finds
what the paper most needs: stated terms, redaction markers and governing-law clauses are not classes any general
recogniser has.

```{r}
#| label: float-entity-coverage
#| results: asis
oa_float(.name = "EntityCoverage")
```

```{r}
#| label: float-entity-positions
#| results: asis
oa_float(.name = "EntityPositions")
```

### Purpose-built extractors {#sec-oa-d-patterns}

So the pipeline adds extractors of its own, written for these contracts: a gazetteer of places built from the U.S.
Geological Survey's domestic names and international country data, reaching down to cities and recovering a state
from the postal code that follows a city; a date extractor that requires a year and also reads stated periods --
"for a period of five years" -- which it finds in `r oa_n(.key = "CovTermMatcon")` percent of contracts; a money
extractor that accepts a figure only with a currency marker and records a figure the filer withheld, `$[***]`, as
a case of its own; a redaction extractor that marks six kinds of place where text was removed, found in
`r oa_n(.key = "CovRedactMatcon")` percent of contracts; and a governing-law extractor that returns the clause as a
span, found in `r oa_n(.key = "CovLawMatcon")` percent. They are regular expressions and lookup tables rather than
models, so they can be read, and they are published with the paper (Appendix B.4). Where they overlap with LexNLP
they agree: on places the two find the same mentions -- a Jaccard index of `r oa_n(.key = "JaccardGpeLex")` over
mentions, with the same boundaries on `r oa_n(.key = "ExactGpeLex")` percent of those both find -- and differ in
resolution, not in opinion. Where LexNLP is the
better instrument it is kept: the corpus is extracted with LexNLP for organisations and the pattern extractors for
everything else, and spaCy is not run on it.

### Why the release keeps spans {#sec-oa-d-spans}

Extractors disagree, and `r oa_ref(.name = "EntityAgreement")` shows how far: overlapping spans of one entity are
merged into mentions, and agreement is the share of mentions both extractors found among those either found. On
organisations, spaCy and LexNLP agree on `r oa_n(.key = "JaccardOrg")` of what is there, since most of what spaCy
proposes LexNLP never does; on places, spaCy agrees with either of the others on `r oa_n(.key = "JaccardGpeSpacy")`,
and `r oa_n(.key = "OneProducerGpe")` percent of all place mentions were found by one extractor only; on dates,
LexNLP and the pattern extractor agree on `r oa_n(.key = "JaccardDate")` of what is there but on only
`r oa_n(.key = "ExactDate")` percent of where it ends, a difference of normalisation rather than of reading; on
amounts, they barely meet at all (`r oa_n(.key = "JaccardMoney")`), because LexNLP's money extractor fires so
rarely. They disagree, that is, about what is there rather than about where it ends. Which of them is right depends
on the question. A study of supply chains wants every company
a contract mentions; a study of contracting parties wants the two named in the preamble; a study of foreign
operations wants the places attached to those parties and not the jurisdiction whose law governs the contract. No
extractor answers those questions, and a count of spans answers none of them. So every span is stored with its
character offsets in the text, and the release keeps the spans with their context rather than a count: which party
a place follows and at what distance, which of four sources a duration came from, which pattern a figure matched,
what a marker replaced. A rule is then a query over that context, and a reader who disagrees with a rule of this
paper writes a different one over the same file.

```{r}
#| label: float-entity-agreement
#| results: asis
oa_float(.name = "EntityAgreement")
```

That is also the honest statement of what the rules are: they let
the text decide where it states the answer, and they are not certain where it does not; a semantic model would
resolve more, at the cost of reading every contract again with a system whose errors cannot be read.

### From spans to variables: the five rules {#sec-oa-d-rules}

**Partners.** LexNLP proposes organisation names, and the rule turns them into parties in four steps. It strips
legal suffixes, so that ACME CORPORATION and ACME CORP. share one key; it groups the spellings of one company
within a contract, refusing a bare name that could belong to two; it matches the parties against the names EDGAR
recorded for the filing -- the filer by prefix, so that ACME reaches ACME CORPORATION, every co-registrant of the
same filing exactly, because a loose rule over hundreds of siblings would make a corporate group party to every
contract any of them touched; and it assigns each party a role, first match winning: registrant, co-registrant,
counterparty where named within 2,000 characters of the registrant, signatory where named in the final tenth of
the contract, and other. Where no party matches the filer, the first party named is taken as the registrant and
the release records the fallback. The parties the paper counts are the registrant, the co-registrants and the
counterparties.

**Places.** A place is looked up in the gazetteer; a name that exists under several parents -- Springfield is in
33 states -- is marked ambiguous and given no state unless the contract itself names one of its candidate states,
because a fallback would send every unresolved Springfield to the same state and a constant error reads as a
geographic pattern. A place whose offsets fall inside a governing-law clause names the law, not a location, and
is excluded by containment rather than proximity; the jurisdictions are released separately. A place belongs to
the party named within 200 characters before it, which is what separates the locations of the contracting
parties from places a contract merely mentions and answers the question whether the countries the paper counts
are the parties' locations: they are. Where a party has several places, the nearest is taken.

**Dates and duration.** Every date pattern requires a year, so the extractor cannot supply one the contract does
not state. A contract's start is the latest date at or before its filing, or the filing date where none precedes
it. Its end comes from the first of four sources present: a stated term; an open-ended clause -- "until
terminated" -- which leaves the duration missing, because a perpetual agreement has no duration; a future date
beside an end cue; and the farthest future date of any kind, which alone is the naive reading. Durations above 30
years are dropped rather than capped, and the release records why each one went, so the cap is a filter a reader
can move. One caveat is measured and left in: a contract states 4.7 periods on average and the longest is not
always the term -- 7 percent of durations come from a cure or notice window of thirty days -- and the release
carries the kind of each period, so that excluding remedy deadlines is one filter over the term file.

**Monetary amounts.** A figure counts only with a currency marker, which excludes section numbers by
construction. A zero is not an amount, and the two most common money spans in the corpus are `$ 0` and `$ 0.00`;
a figure beside par-value language, read on both sides of it, is a share's face value and not a sum anybody owes;
and a figure the filer withheld is a third outcome, counted and never summed. Flattened tables can join adjacent
cells into one figure, so the paper reports medians and not means.

**Redaction markers.** Six kinds of marker are identified -- brackets naming confidential treatment, brackets of
asterisks, brackets of underscores, brackets recording an omission, brackets of bullets or ellipses, and
unbracketed runs of asterisks -- and no filter is applied: the release counts each kind, so the three candidate
definitions of a redacted contract are three predicates over one column, and the paper's is the bracketed one.
A marker that sits inside a withheld amount identifies a withheld price, and that overlap is also a check: the
withheld amounts are a population where a redaction is not in doubt, and the share of them the bracketed
definition sees is a statement about the definition rather than about one filing.

`r oa_ref(.name = "DurationRungs")` reports what each source of the end date answers. A stated term settles
`r oa_n(.key = "DurTerm")` percent of contracts, a cued date `r oa_n(.key = "DurCue")` percent, and the farthest
future date `r oa_n(.key = "DurMaxDate")` percent; an open-ended clause accounts for `r oa_n(.key = "DurOpen")`
percent. For the remaining `r oa_n(.key = "DurNone")` percent no source answers: the contract states no term,
carries no cue and names no date beyond its filing, which is what a contract of indefinite length looks like in
the text. `r oa_n(.key = "DurCapped")` contracts fall to the 30-year rule.

```{r}
#| label: float-duration-rungs
#| results: asis
oa_float(.name = "DurationRungs")
```

### The rules against the naive reading {#sec-oa-d-contrast}

`r oa_ref(.name = "ContentContrast")` reports, by category, on how many contracts each measure is defined under the
naive reading of the spans and under the rule, and `r oa_ref(.name = "ContentValues")` what it is worth on them. The
rules add coverage where the text states what a naive reading
has to guess, and remove it where a naive reading counts what the rule rejects. The duration is the clearest case.
The rule-based duration is defined on `r oa_n(.key = "DurDefRule")` contracts and the naive one on
`r oa_n(.key = "DurDefNaive")`, the difference being contracts that state a term without naming a future date;
and the two yield different lengths, a median of `r oa_n(.key = "DurMedRule")` years against
`r oa_n(.key = "DurMedNaive")`, because the farthest future date in a contract is often a date the contract
mentions rather than the date it runs to. Partners are the clearest case of the rule removing what a naive count adds:
a contract names
`r oa_n(.key = "ValPartNaive")` distinct organisation spellings on average and `r oa_n(.key = "ValPartRule")`
parties, the rest being subsidiaries, lenders, agents and companies the contract mentions. Countries move the same
way: `r oa_n(.key = "ValCtryNaive")` mentioned per contract against `r oa_n(.key = "ValCtryReg")` attached to the
registrant and `r oa_n(.key = "ValCtryCpty")` to the counterparties, which is the difference between the countries
a contract talks about and the countries its parties are in. Amounts fall from `r oa_n(.key = "ValAmtNaive")`
figures read to `r oa_n(.key = "ValAmtRule")` kept in dollars once zeros and par values are gone. Where the rule
loses coverage, it loses what it should. What remains
is not certain -- the rules let the text decide, and are silent where it does not -- and the release is built so
that a reader can see, for every variable of every contract, the spans it rests on and the rule that produced it.

```{r}
#| label: float-content-contrast
#| results: asis
oa_float(.name = "ContentContrast")
```

```{r}
#| label: float-content-values
#| results: asis
oa_float(.name = "ContentValues")
```

::: {.content-visible when-format="html"}

# Validation

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,
  .path_qmd     = .lP$Input$Qmd,
  .dir_exhibits = .lP$Input$DirExhibits
)
```

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "40-OnlineAppendix-D.qmd"),
  .path_tex     = here::here("_rendered", "1_code", "40-OnlineAppendix-D.tex"),
  .path_numbers = here::here("2_output", "40-OnlineAppendix-D", "Output", "OA-Numbers-D.tex"),
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  .dir_own      = here::here("2_output", "40-OnlineAppendix-D", "Output"),
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL
)
```

# Next

**40-OnlineAppendix-E** -- additional analysis.

:::
