---
title: "Methodology and data -- the manuscript's Section 3 (41)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK: the chapter as it will read, with the values 40 resolved in place of the macros.
  html: default
  # THE FRAGMENT: 4-method.tex for Overleaf. wrap: none keeps one paragraph on one line, as the paper's files are
  # kept; natbib leaves \citet and \citep to the paper's bibliography.
  latex:
    template: _Templates/manuscript-body.tex
    cite-method: natbib
    wrap: none
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THIS PAIR'S OWN. Nothing upstream is sourced: this document reads 40's register and writes prose.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "41-Methods"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),
  .name_script = .name_script
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),
  .name_script = .name_script
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document is the manuscript's Section 3, "Methodology and data". The text is written here once and rendered
twice: to html, the runbook, where every number appears as the value `40-Numbers` last resolved; and to a LaTeX
fragment, `4-method.tex`, where every number is a `\pnum{Key}` macro that Overleaf reads from `Numbers.tex`. The
fragment replaces the file of the same name in the Overleaf project.

## What comes from where

Numbers: 40's register, `Numbers.csv`, and nothing else -- this document computes no value. Table 1 stays the static
table Ann-Kristin keeps in Overleaf (`tables/T1_contract_classification.tex`); the fragment carries its environment
verbatim. Citations and cross-references are written through two helpers so the html reads and the LaTeX resolves.

## How edits flow

The fragment is not a file to edit. Formatting decided in Overleaf -- a paragraph break, a footnote moved, a
sentence cut -- comes back into this document, and the next render carries it. An edit left in Overleaf is lost at
the next paste.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict = FALSE # TRUE stops the render on a cited key that 40 did not resolve
  )
)

.lP$Input <- list(
  Register = here::here("2_output", "40-Numbers", "Output", "Numbers.csv"), # every number, as 40 last resolved it
  Qmd      = here::here("1_code", "41-Methods.qmd"),
  Template = here::here("1_code", "_Templates", "manuscript-body.tex")
)

.lP$Output <- list(
  Tex    = here::here("_rendered", "1_code", "41-Methods.tex"),          # written by Quarto, in the LaTeX pass
  Deploy = fs::path(.lP$Root, "200-Paper_figures", "Manuscript")        # where met_deploy() copies it
)
```

# Input

```{r}
#| label: input-register
tab_register <- met_numbers_load(.path_register = .lP$Input$Register)
```

:::

```{r}
#| label: load-quiet
#| include: false
# THE LATEX PASS sees none of the blocks above, so the library and the register are loaded again here, silently.
if (!exists("met_n")) {
  purrr::walk(
    .x = purrr::map_chr(c("_Initialize", "_Utils", "_Tables"), \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))),
    .f = \(.p) source(file = .p, encoding = "UTF-8")
  )
  source(file = here::here("1_code", "41-Methods.R"), encoding = "UTF-8")
  met_numbers_load(.path_register = here::here("2_output", "40-Numbers", "Output", "Numbers.csv"))
}
```

# Methodology and data {#sec:method}

Next, we describe our methodology and data. In the following, we explain the data retrieval process from the SEC
EDGAR database and the resulting material contract database (`r met_ref("sec:data")`), the contract classification
(`r met_ref("sec:classification")`), the extraction of content-related information such as contract partners,
locations, and durations (`r met_ref("sec:content")`), the identification of redactions (`r met_ref("sec:redactions")`), and the
extraction of 8-K Item 1.01 contract summaries (`r met_ref("sec:announcements")`). For each step, we provide open-source R and
Python packages. The Online Appendix provides an extended description of the SEC filing requirements and the database
(`r met_ref("sec-oa-a", "Online Appendix")`), the software (`r met_ref("sec-oa-b", "Online Appendix")`), the
classification approach (`r met_ref("sec-oa-c", "Online Appendix")`), and the information extraction
(`r met_ref("sec-oa-d", "Online Appendix")`).

## Data extraction {#sec:data}

All SEC filings, including material contracts, are publicly available via the EDGAR database. However, EDGAR is
designed for targeted searches rather than for comprehensive data collection. The platform offers a full-text search,
filtering by company identifier (CIK) and by form type, but no index of the exhibits attached to a filing. Material
contracts can be identified by their standardized designation in the filing index (e.g., "EX-10.1"), but each exhibit
must be located and retrieved individually, and the SEC limits access to ten requests per second. Bulk retrieval of
specific exhibit types across hundreds of thousands of filings therefore requires a systematic approach.

To address these challenges, we developed the rGetEDGAR R package. First, we retrieve the quarterly master index
files published by the SEC, which contain the metadata of all filings. Second, we retrieve each filing's index page to
extract document-level metadata, including document descriptions, types, and URLs. Third, we download the identified
documents and convert them to text. Each step stores the results, so that an interrupted retrieval resumes where it
stopped and no request is repeated. The package is not tied to material contracts: a retrieval is defined by the
period, the filers, and the form and exhibit types of interest. `r met_ref("sec-oa-b-rgetedgar", "Online Appendix")`
describes the package in detail.

Using rGetEDGAR, we download three groups of documents. First, we retrieve all attachments filed as Exhibit 10 with
Forms 10-K, 10-Q, 8-K, S-1, S-4, 20-F, F-1, and F-4 and their amendments, resulting in `r met_n("DocsAll")`
documents.^[Material contracts filed under other form types, or under other exhibit numbers, are not part of our
database. `r met_ref("sec-oa-a-holds", "Online Appendix")` lists all form types carrying material contracts and their
coverage.] Second, we retrieve all Form 8-K filings that report the entry into a material definitive agreement under
Item 1.01 (`r met_n("Docs8K")` filings), whose contract summaries we analyze in `r met_ref("sec:announcements")`.
Third, we retrieve all confidential treatment orders (`r met_n("Orders")` orders), which we use to identify redacted
contracts before the 2019 FAST Act. Our sample period starts in 2001. Although EDGAR lists filings from 1993 (when the
phase-in of electronic filing began) and electronic filing has been mandatory for all domestic registrants since May
1996, exhibits were included in the text of the complete submission until mid-2000 and only became separately
retrievable documents with EDGAR Release 7.0 in May 2000.^[The phase-in of mandated electronic filing under Regulation
S-T began on April 26, 1993 (SEC Release 33-6977) and ended on May 6, 1996 (SEC Release 33-7122). EDGAR Release 7.0
took effect on May 30, 2000 (SEC Release 33-7855). `r met_ref("sec-oa-a-holds", "Online Appendix")` documents the
share of Exhibit 10 attachments available as separate files by quarter around this date.] The year 2001 is therefore
the first full year in which every material contract is available as a document of its own.

## Contract classification {#sec:classification}

Material contracts are a heterogeneous group of documents including credit, employment, and leasing contracts.
`r met_ref("fig:contract_ex", "Appendix")` provides a contract example. As these contracts cover very different
economic transactions, prior studies classify them in different ways and at different levels of granularity. We start
with the classification of `r met_cite("verrecchia2006redacted")` and extend it with recent schemes used in the
contracting literature (e.g., `r met_cite(c("Boone2016", "Bao2022DoNews", "Thompson2023", "Bao2025"), "p")`).
Comparing these schemes, we design our twelve categories to (i) cover the contract types that recur across studies,
(ii) remain granular enough to separate contracts with distinct disclosure incentives, and (iii) avoid categories that
are too narrow to support meaningful empirical analysis. Our aim is a categorization that balances coverage and
granularity and offers a useful reference point for future research.
`r met_ref("tab:contract_classification", "Table")` defines each category.

```{=latex}
\begin{table}[h!]
    \caption{Contract Categories}\label{tab:contract_classification}
    \footnotesize
        \input{tables/T1_contract_classification.tex}

    {\footnotesize
    Notes: Table \ref{tab:contract_classification} defines the twelve contract categories and provides
    representative agreement titles. The categorization builds on \citet{verrecchia2006redacted} and incorporates
    the schemes used in \cite{Boone2016}, \cite{Bao2022DoNews}, \cite{Thompson2023}, and \cite{Bao2025}.
    Categories are mutually exclusive; contracts are classified according to their primary obligation.}
\end{table}
```

::: {.content-visible when-format="html"}
*[Table 1, the static contract-category table Ann-Kristin keeps in Overleaf, is set here in the fragment.]*
:::

Our classification addresses two tasks: (1) the classification of each contract into one of the twelve categories,
which nest in seven broad categories so that both levels of granularity are available, and (2) the amendment
classification, distinguishing original contracts from amendments and modifications. To ensure classification quality
and consistency, we developed rLabelDocs, an interactive Shiny-based package for systematic document annotation, which
provides a structured interface for document classification, progress tracking, and controls across multiple
annotators (`r met_ref("sec-oa-b-rlabeldocs", "Online Appendix")`). Using this package, we manually labeled a sample
of `r met_n("NLabelled")` contracts, `r met_n("NAmended")` of which are amendments. Where a contract fits two
categories, the annotators recorded a second label (`r met_n("NSecond")` contracts); we train on the primary label
only. `r met_ref("sec-oa-c-sample", "Online Appendix")` explains the boundaries between adjacent categories and shows
the most frequent contract titles per category.

Our classification approach employs transformer-based models. We evaluate all models with five-fold cross-validation
stratified on the contract category, so that every labeled contract is predicted once by a model that did not see it
in training. Given the small number of contracts in the rarest category (`r met_n("NRarest")`), a further held-out
test set would leave too few observations to evaluate that category. As accuracy is dominated by the three largest
categories, which hold almost half of the sample, we select models on macro-F1, the unweighted mean of the
per-category F1 scores, and report accuracy beside it. We compare Legal-BERT, a model pre-trained on legal texts
`r met_cite("chalkidis2020legal", "p")`, with the general-purpose RoBERTa `r met_cite("liu2019roberta", "p")` and
vary the learning rate, the number of tokens read from the beginning of the contract (256 or 512), the number of
training epochs, and whether classes are weighted by their inverse frequency, resulting in `r met_n("SweepConfigs")`
configurations across both tasks. For each task, we select the configuration with the highest cross-validated
macro-F1 and re-train it on the full labeled sample. For both tasks, the selected model is Legal-BERT reading the
first 256 tokens of each contract; reading 512 tokens does not improve
performance.^[`r met_ref("sec-oa-c-transformer", "Online Appendix")` reports the full grid and the performance of all
configurations.]

Our classification procedure achieves a robust performance across both tasks. For the contract category
classification, we obtain an accuracy of `r met_n("AccDetailed")` and a macro-F1 of `r met_n("F1Detailed")`. Counting
a prediction as correct if it matches the contract's second label raises the accuracy to `r met_n("LenientDetailed")`,
so few errors reflect the ambiguity of mixed contracts. The remaining errors concentrate in adjacent categories, such
as the two employment categories or credit and equity instruments. The amendment classification achieves an accuracy
of `r met_n("AccAmend")` and a macro-F1 of `r met_n("F1Amend")`. For each contract, our database provides the two most
likely categories and the amendment flag with their probabilities, and the broad category as the roll-up of the
detailed one.

As methodological validation, we implement a rule-based classification using domain keywords comparable to
`r met_cite(c("Ahci2024", "Boone2016"))`. Instead of selecting keywords manually, we derive a keyword table from the
labeled sample: a term enters the table for a category only if its precision in the training folds exceeds the
category's base rate, and a contract receives the category of its most precise term, or no category if no term
applies. Out of fold, the keyword table classifies `r met_n("KwCoverage")`\% of the contracts with an accuracy of
`r met_n("KwAccCommitted")`, confirming the value of explicit terminology for contracts that carry it and the
limitations of rule-based approaches for comprehensive coverage. We publish the keyword table alongside the
transformer's labels as an independent second opinion. `r met_ref("sec-oa-c-arms", "Online Appendix")` additionally
reports the performance of a local large language model on the same folds, which remains well below the fine-tuned
transformer, and shows that no combination of the three approaches could substantially exceed the transformer alone.

## Content variable creation {#sec:content}

To facilitate quantitative analysis of contract characteristics, we extract three content-based variables from each
contract text (i.e., contract partners, contract dates and duration, and geographic locations), translating these
textual concepts into machine-readable formats following established practices in computational text analysis
`r met_cite("gentzkow2019text", "p")`. We combine LexNLP, an open-source Python package designed for legal text
`r met_cite("bommarito2021lexnlp", "p")`, with purpose-built extractors based on regular expressions and lookup
tables. LexNLP identifies the organizations named in a contract, which concentrate in the preamble and the signature
block where the parties are named; our own extractors handle dates, stated terms, locations, and redaction markers,
which no general-purpose recognizer provides.^[We compared LexNLP with spaCy's transformer-based model on the labeled
sample. spaCy recognizes every mention of every company in a contract, which suits questions about the companies a
contract refers to rather than about its parties, so we use LexNLP for organizations and do not run spaCy on the
database. `r met_ref("sec-oa-d", "Online Appendix")` reports the comparison.] Rather than counts, our database
stores every extracted entity as a span with its position in the text, together with the context the rules below
rely on, so that researchers can apply their own rules to the same data. `r met_ref("sec-oa-d", "Online Appendix")`
documents the extractors, their agreement, and the rules in detail.

For contract partners, we turn the organizations LexNLP identifies into contracting parties. We strip legal suffixes
and group the spellings of one company within a contract, match the parties against the registrant names EDGAR
records for the filing, and assign each party a role: registrant, co-registrant, counterparty if named close to the
registrant in the preamble, signatory if named in the final part of the contract, and other. The partners we count
are the registrant, its co-registrants, and the counterparties. On average, a contract names `r met_n("ValPartNaive")`
distinct organizations and `r met_n("ValPartRule")` contracting parties; the rest are subsidiaries, lenders, agents,
and companies the contract merely mentions.

For contract dates, we identify dates in all common formats with regular expressions that require a year, so that no
date is inferred. A contract's start date is the latest date at or before its filing date. Its end date is taken from
the first of four sources present in the text: a stated term (e.g., "for a period of five years"), an open-ended
clause ("until terminated"), which leaves the duration undefined, a future date next to an end cue, and, as a last
resort, the latest future date mentioned in the contract. A stated term settles `r met_n("DurTerm")`\% of contracts,
and durations above 30 years are excluded. Using the latest date mentioned in the contract alone, as in prior work,
yields a median duration of `r met_n("DurMedNaive")` years against `r met_n("DurMedRule")` years under our approach,
because the latest date in a contract is often a date it refers to rather than the date it runs to.

For geographic locations, we develop a custom gazetteer combining the U.S. Geological Survey (USGS) Domestic Names
dataset with international country data, covering U.S. states, counties, cities, and populated places as well as
countries, with their spelling variations. A place name that exists in several states is left unresolved unless the
contract names one of its states, and a place that appears within a governing-law clause names the applicable law
rather than a location and is excluded. We attribute each location to the contracting party named directly before
it, so that the locations we count are those of the parties rather than every place a contract mentions: a contract
mentions `r met_n("ValCtryNaive")` countries on average, of which `r met_n("ValCtryReg")` are attributed to the
registrant and `r met_n("ValCtryCpty")` to its counterparties.

## Contract redactions {#sec:redactions}

We identify redacted contracts in two ways, corresponding to the two regimes described in
`r met_ref("ch:inst_set")`. Until the FAST Act, a firm withholding information had to obtain a confidential treatment
order (CTO), which the SEC publishes on EDGAR since 2008. Each order names the filing it refers to, the exhibit numbers
it covers, and the date the withheld information becomes public, so that we can link every order to the contracts in
our database. Comparable to `r met_cite("Ahci2024")`, we count orders that grant confidential treatment, including
extensions of an earlier grant, and exclude denials. Overall, we identify `r met_n("Orders")` CTOs naming
`r met_n("OrderRefs")` exhibits, of which we link `r met_n("OrderRefsLinked")` to a contract in our database; the
remaining references name exhibits other than Exhibit 10, filings outside our form types, or exhibit numbers we
cannot locate in the filing.^[When restricting the sample to new grants through 2019 on 10-K, 10-Q, and 8-K filings,
our numbers closely align with `r met_cite("Ahci2024")` for both CTOs (`r met_n("OrdersAhci")` vs. 9,625) and exhibits
(`r met_n("OrderRefsAhci")` vs. 16,397).] In total, `r met_n("DocsWithCto")` unique contracts are covered by at least
one order.

After the FAST Act in 2019, firms are required to "include a prominent statement on the first page of the redacted
exhibit"^[17 C.F.R. \S229.601(b)(2)(ii)] and to indicate the omitted information with brackets. Comparable to
`r met_cite("Thompson2023")`, we use a set of regular expressions to identify these redactions in the contract text,
distinguishing between different types of redaction indicators. We classify a contract as redacted if it contains at
least one bracketed redaction marker, such as asterisks (e.g., "[\*\*\*]"), underscores, or explicit omission notes
(e.g., "[REDACTED]"). We exclude bullet points, ellipses, and similar formatting characters, which typically indicate
redactions of personal information such as names and addresses rather than sensitive contract terms. Throughout the
paper, a contract is redacted if it is covered by a CTO in the years through 2018, and if it is covered by a CTO or
contains a redaction marker from 2019 onwards.^[Both indicators are available for all years in the database. In 2008
to 2018, `r met_n("CtoMarkerAgree")`\% of the contracts covered by a CTO also contain a redaction marker, which
supports the textual identification in the period without CTOs.]

## 8-K Item 1.01 disclosures {#sec:announcements}

SEC regulations mandate that firms file Form 8-K within four business days of entering a material definitive
agreement, providing a summary of its material terms under Item 1.01. `r met_ref("sec: contract_sum_ex", "Appendix")`
provides an example of such a summary. While firms must include these summaries in an 8-K, they retain discretion over
whether to attach the full contract text immediately or delay its disclosure until the next periodic filing. We
extract the Item 1.01 text between the item's heading and the next item or the signature section from all
`r met_n("Docs8K")` 8-K filings that report the item. To ensure a clean link between a summary and its contract, we
retain only 8-Ks that announce a single agreement, which we proxy by the number of agreement dates the narrative opens
with, and that attach at most one Exhibit 10; this excludes `r met_n("AnnouncementsNoDate")` filings whose narrative
names no agreement date, `r met_n("AnnouncementsMultiSummary")` filings that announce several agreements, and
`r met_n("AnnouncementsMultiExhibit")` filings that attach several contracts. The resulting `r met_n("Announcements")`
announcements are linked to our contract database to determine whether the firm attached the full contract
immediately or delayed its disclosure. For each summary, we calculate the Gunning Fog index as an indicator of
complexity `r met_cite("Li2008", "p")`, the share of uncertainty-related words per 1,000 words based on the
`r met_cite("Loughran2011")` dictionary, and the number of numerical values per 1,000 words, distinguishing dollar
amounts, percentages, and other numbers `r met_cite("Siano2018", "p")`.

::: {.content-visible when-format="html"}

# Validation

```{r}
#| label: validate-cited
tab_cited <- met_report_cited(.strict = .lP$Params$Strict)
```

# Deployment

The fragment is written only by the LaTeX pass. A terminal render, `quarto render 1_code/41-Methods.qmd`, runs both
passes; the Render button runs the html alone. Then one call copies the fragment to the paper folder as
`4-method.tex`, archiving the version it replaces:

```r
source(here::here("1_code", "41-Methods.R"), encoding = "UTF-8")

met_deploy(
  .path_tex   = here::here("_rendered", "1_code", "41-Methods.tex"),
  .path_qmd   = here::here("1_code", "41-Methods.qmd"),
  .dir_deploy = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "Manuscript"
  )
)
```

In Overleaf, the file replaces `4-method.tex`. The preamble must input `Numbers.tex` (deployed by 40) for the
`\pnum{}` macros to print, and the bibliography must hold `chalkidis2020legal` and `liu2019roberta` (both in
`_Templates/oa-references.bib`).

```{r}
#| label: deploy-status
if (fs::file_exists(.lP$Output$Tex)) {
  cli::cli_alert_info(
    "Fragment last written {format(fs::file_info(.lP$Output$Tex)$modification_time, '%Y-%m-%d %H:%M')}."
  )
} else {
  cli::cli_alert_warning("No fragment yet: run the LaTeX pass from a terminal.")
}
```

# Next

- Fold the "Matching identifier and external data" paragraph (label `matching`) into Section 4.1 in Overleaf; it is
  no longer part of this chapter.
- The no-date exclusion of the announcement sample (`AnnouncementsNoDate`) is now stated; confirm with Ann-Kristin
  that her Table 7 sample applies the same three filters.
- Table 2's Panel B in Overleaf types values that 30's `SampleSelection` no longer matches; once Section 4 cites
  `\pnum{}` keys the two cannot drift.

:::
