---
title: "Online Appendix D -- Entity Extraction and the Rules (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THE APPENDIX'S OWN. init_*() resolve this document's paths, tbl_say() is the fixed-width printer
# every report below uses, _Plots.R gives the figures built here the house theme, and _OnlineAppendix.R is the
# machinery every chapter of the appendix shares: numbers, floats, references, markers, the LaTeX pass, deployment.
# No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "42-OnlineAppendix-D"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
source(file = here::here("1_code", "40-Numbers.R"), encoding = "UTF-8") # the builders and the register loader
```

# Purpose

This document is Appendix D of the online appendix: how the content variables of the release -- partners, places,
dates and duration, amounts, redaction markers -- are extracted from the text, and why they are extracted the way
they are. The chapter tells one story. Two general-purpose recognisers were the natural candidates and were tried;
what each does well and where each falls short led to purpose-built extractors; all of them disagree enough that
the release keeps every span with its position, so that a rule is a query over stored context; five such rules turn
spans into variables; and the last section reads what the rules change against the naive reading. The chapter is
upfront that the rules are pre-work: even with them, the extraction is not certain, and a reader with a different
question writes a different rule over the same spans.

The conventions are those of every chapter of the appendix and are set out once, in the Purpose of
`42-OnlineAppendix-A`. Five exhibits are built here: what each extractor found on the labelled sample, counted from
the span stores 04A wrote; where in a contract the candidates fall and how far the extractors agree, computed from
the same stores with 04A's definitions; where each contract's end date comes from, and what the content variables are
worth under both readings, from the release. The naive-against-rule coverage by category is 30's.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict     = FALSE,
    FigWidth   = 0.96,
    Rebuild    = FALSE,
    SpacyModel = "en_core_web_trf"  # the spaCy model 04A ran; the others are declared there and not run
  )
)

.lP$Input <- list(
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  Contracts   = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),           # the release
  DirStore    = here::here("2_output", "04A-EntityExtract", "Output"),                 # the three span stores
  Sample      = here::here("2_output", "04A-EntityExtract", "Output", "sample_text.parquet"),
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"),
  Qmd         = here::here("1_code", "42-OnlineAppendix-D.qmd")
)

.lP$Input$Register <- here::here("2_output", "40-Numbers", "Output", "Numbers.csv") # every number, as 40 resolved it

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-D.tex"),
  DirOwn  = here::here("2_output", "40-Numbers", "Output"),
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")
)

oa_state_reset()
```

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,             ~Kind,   ~Source, ~Caption,
  "D",      "EntityCoverage",  "table",  "D",     "What each extractor found on the labelled sample",
  "D",      "EntityPositions", "figure", "D",     "Where in the contract each extractor's candidates fall",
  "D",      "EntityAgreement", "figure", "D",     "How far the extractors agree about what is there",
  "D",      "DurationRungs",   "table",  "D",     "The source of each contract's end date",
  "D",      "ContentContrast", "table",  "30",    "Naive and rule-based content variables, by category: coverage",
  "D",      "ContentValues",   "table",  "D",     "Naive and rule-based content variables, by category: values"
)

tab_sources <- tibble::tribble(
  ~Source, ~Dir,                            ~Macro,
  "30",    .lP$Input$DirExhibits,           "\\oaexhibits",
  "D",     as.character(.lP$Output$DirOwn), "\\oaown"
)

tab_static <- tibble::tibble(
  Name = character(0),
  File = character(0),
  Note = character(0)
)
```

# Input

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits,
  .template     = .lP$Input$Template,
  .bib          = .lP$Input$Bib
)
```

# Build

This chapter builds nothing. Every exhibit it sets -- 30's and its own -- is built by `40-Numbers`, which writes
them in 30's layout under its own output directory, the directory the sources table names as this chapter's.
A missing exhibit is therefore a render of 40 away, not of this document.

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats    = tab_floats,
  .static    = tab_static,
  .sources   = tab_sources,
  .own       = "D",
  .dir_doc   = fs::path_dir(.lP$Input$Qmd),
  .fig_width = .lP$Params$FigWidth,
  .strict    = .lP$Params$Strict
)

oa_report_floats(.files = ctx_oa$Files)
```

# Numbers

Every number the text cites is a key in 40's registry, resolved there over the tibble beside the exhibit that
prints it. This chapter loads the register 40 last wrote and cites through `oa_n()`, as before; a key it does not
hold aborts the render, and a key it holds but could not resolve prints as a marker and is listed under Validation.

```{r}
#| label: numbers-load
tab_numbers <- num_numbers_load(.path_register = .lP$Input$Register)

oa_report_numbers(
  .tab    = tab_numbers,       # as 40 resolved them
  .strict = .lP$Params$Strict  # TRUE stops the render on an unresolved number
)
```

# Appendix D

:::

```{=latex}
\clearpage
```

## Content variable creation {#sec-oa-d}

Our database carries, for every contract, its partners, the locations of these partners, its start date, end date
and duration, the amounts it names, and the markers of what its filer redacted. The paper uses these variables
descriptively, and this appendix describes how we extract them and how far they can be trusted. Section D.1 sets
out what the two general-purpose recognizers that were the natural candidates do well and where they fall short;
D.2 the extractors we wrote for our database; D.3 why we keep every span with its position rather than a count;
D.4 the five rules that turn spans into variables; and D.5 what the rules change against a naive reading of the
same spans.

### Two general-purpose recognizers {#sec-oa-d-recognisers}

Named-entity recognition is a solved problem for news text, and two systems bring it to legal text: LexNLP
[@bommarito2021lexnlp], a library of extractors written for contracts, and spaCy [@honnibal2020spacy], whose
transformer model is the general recognizer of the field. We ran both on the `r oa_n(.key = "NerDocs")` contracts
of the labeled sample, and `r oa_ref(.name = "EntityCoverage")` reports what each proposed. Both cover the sample:
spaCy finds an organization in `r oa_n(.key = "CovOrgSpacy")` percent of contracts and LexNLP in
`r oa_n(.key = "CovOrgLexnlp")` percent, and both find locations in more than nine contracts in ten. spaCy is the
more complete recognizer -- it also finds persons, in `r oa_n(.key = "CovPersonSpacy")` percent of contracts, and
it finds every company a contract mentions. LexNLP reads dates and countries reliably, and its organizations sit
where the parties are named. `r oa_ref(.name = "EntityPositions")` shows where each extractor's candidates fall in
the contract: LexNLP's organizations concentrate at the two ends, the preamble and the signature block, where the
share of candidates in the first and last tenth of a contract is `r oa_n(.key = "ContrastOrgLexnlp")` times the
share through the middle; spaCy's organizations draw a flat line, `r oa_n(.key = "ContrastOrgSpacy")` times, which
is what an even spread through the body gives. For locations and dates, LexNLP and our pattern extractors trace the
same curve.

Neither is sufficient, for different reasons. spaCy proposes `r oa_n(.key = "SpansOrgSpacy")` organizations against
LexNLP's `r oa_n(.key = "SpansOrgLexnlp")`, spread evenly through the text: it recognizes every mention of every
company, which is the right answer to a different question. Finding the parties to a contract among eleven times
as many candidates is harder, not easier, and the model reads a contract in the time the other extractors read
ten. LexNLP's geography stops at the country -- its dictionary holds countries and territories, so a contract
naming Frankfurt yields Germany -- and its money extractor fires in `r oa_n(.key = "CovMoneyLexnlp")` percent of
contracts, where a pattern finds an amount in `r oa_n(.key = "CovMoneyMatcon")` percent. And neither system finds
what the paper most needs: stated terms, redaction markers and governing-law clauses are not classes any general
recognizer has.

```{r}
#| label: float-entity-coverage
#| results: asis
oa_float(.name = "EntityCoverage")
```

```{r}
#| label: float-entity-positions
#| results: asis
oa_float(.name = "EntityPositions")
```

### Purpose-built extractors {#sec-oa-d-patterns}

We therefore add extractors of our own, written for these contracts: a gazetteer of locations built from the U.S.
Geological Survey's domestic names and international country data, reaching down to cities and recovering a state
from the postal code that follows a city; a date extractor that requires a year and also reads stated periods --
"for a period of five years" -- which it finds in `r oa_n(.key = "CovTermMatcon")` percent of contracts; a money
extractor that accepts a figure only with a currency marker and records a figure the filer withheld, `$[***]`, as
a case of its own; a redaction extractor that marks six kinds of place where text was removed, found in
`r oa_n(.key = "CovRedactMatcon")` percent of contracts; and a governing-law extractor that returns the clause as a
span, found in `r oa_n(.key = "CovLawMatcon")` percent. They are regular expressions and lookup tables rather than
models, so they can be read, and we publish them with the paper (Appendix B.4). Where they overlap with LexNLP
they agree: on locations the two find the same mentions -- a Jaccard index of `r oa_n(.key = "JaccardGpeLex")` over
mentions, with the same boundaries on `r oa_n(.key = "ExactGpeLex")` percent of those both find -- and differ in
resolution, not in opinion. Where LexNLP is the better instrument we keep it: we extract the full database with
LexNLP for organizations and our pattern extractors for everything else, and do not run spaCy on it.

### Why we keep spans {#sec-oa-d-spans}

Extractors disagree, and `r oa_ref(.name = "EntityAgreement")` shows how far: overlapping spans of one entity are
merged into mentions, and agreement is the share of mentions both extractors found among those either found. On
organizations, spaCy and LexNLP agree on `r oa_n(.key = "JaccardOrg")` of what is there, since most of what spaCy
proposes LexNLP never does; on locations, spaCy agrees with either of the others on
`r oa_n(.key = "JaccardGpeSpacy")`, and `r oa_n(.key = "OneProducerGpe")` percent of all location mentions were
found by one extractor only; on dates, LexNLP and our pattern extractor agree on `r oa_n(.key = "JaccardDate")` of
what is there but on only `r oa_n(.key = "ExactDate")` percent of where it ends, a difference of normalization
rather than of reading; on amounts, they barely meet at all (`r oa_n(.key = "JaccardMoney")`), because LexNLP's
money extractor fires so rarely. They disagree, that is, about what is there rather than about where it ends. Which
of them is right depends on the question. A study of supply chains wants every company a contract mentions; a
study of contracting parties wants the two named in the preamble; a study of foreign operations wants the locations
attached to those parties and not the jurisdiction whose law governs the contract. No extractor answers those
questions, and a count of spans answers none of them. We therefore store every span with its character offsets in
the text, and our database keeps the spans with their context rather than a count: which party a location follows
and at what distance, which of four sources a duration came from, which pattern a figure matched, what a marker
replaced. A rule is then a query over that context, and a reader who disagrees with a rule of this paper writes a
different one over the same file.

```{r}
#| label: float-entity-agreement
#| results: asis
oa_float(.name = "EntityAgreement")
```

That is also the honest statement of what our rules are: they let the text decide where it states the answer, and
they are not certain where it does not; a semantic model would resolve more, at the cost of reading every contract
again with a system whose errors cannot be read.

### From spans to variables: the five rules {#sec-oa-d-rules}

**Contract partners.** LexNLP proposes organization names, and our rule turns them into parties in four steps. It
strips legal suffixes, so that ACME CORPORATION and ACME CORP. share one key; it groups the spellings of one company
within a contract, refusing a bare name that could belong to two; it matches the parties against the names EDGAR
recorded for the filing -- the filer by prefix, so that ACME reaches ACME CORPORATION, every co-registrant of the
same filing exactly, because a loose rule over hundreds of siblings would make a corporate group party to every
contract any of them touched; and it assigns each party a role, first match winning: registrant, co-registrant,
counterparty where named within 2,000 characters of the registrant, signatory where named in the final tenth of
the contract, and other. Where no party matches the filer, the first party named is taken as the registrant and
the database records the fallback. The partners the paper counts are the registrant, the co-registrants and the
counterparties.

**Locations.** A location is looked up in the gazetteer; a name that exists under several parents -- Springfield is
in 33 states -- is marked ambiguous and given no state unless the contract itself names one of its candidate
states, because a fallback would send every unresolved Springfield to the same state and a constant error reads as
a geographic pattern. A location whose offsets fall inside a governing-law clause names the law, not a place, and
is excluded by containment rather than proximity; we release the jurisdictions separately. A location belongs to
the party named within 200 characters before it, which is what separates the locations of the contracting
parties from places a contract merely mentions and answers the question whether the countries the paper counts
are the parties' locations: they are. Where a party has several locations, the nearest is taken.

**Dates and duration.** Every date pattern requires a year, so the extractor cannot supply one the contract does
not state. A contract's start date is the latest date at or before its filing date, or the filing date where none
precedes it. Its end date comes from the first of four sources present: a stated term; an open-ended clause --
"until terminated" -- which leaves the duration missing, because a perpetual agreement has no duration; a future
date beside an end cue; and the farthest future date of any kind, which alone is the naive reading. Durations above
30 years are dropped rather than capped, and the database records why each one went, so the cap is a filter a
reader can move. One caveat is measured and left in: a contract states 4.7 periods on average and the longest is
not always the term -- 7 percent of durations come from a cure or notice window of thirty days -- and the database
carries the kind of each period, so that excluding remedy deadlines is one filter over the term file.

**Monetary amounts.** A figure counts only with a currency marker, which excludes section numbers by
construction. A zero is not an amount, and the two most common money spans in the database are `$ 0` and
`$ 0.00`; a figure beside par-value language, read on both sides of it, is a share's face value and not a sum
anybody owes; and a figure the filer withheld is a third outcome, counted and never summed. Flattened tables can
join adjacent cells into one figure, so we report medians and not means.

**Redaction markers.** We identify six kinds of marker -- brackets naming confidential treatment, brackets of
asterisks, brackets of underscores, brackets recording an omission, brackets of bullets or ellipses, and
unbracketed runs of asterisks -- and apply no filter: the database counts each kind, so the three candidate
definitions of a redacted contract are three predicates over one column, and the paper's is the bracketed one.
A marker that sits inside a withheld amount identifies a withheld price, and that overlap is also a check: the
withheld amounts are a population where a redaction is not in doubt, and the share of them the bracketed
definition sees is a statement about the definition rather than about one filing.

`r oa_ref(.name = "DurationRungs")` reports what each source of the end date answers. A stated term settles
`r oa_n(.key = "DurTerm")` percent of contracts, a cued date `r oa_n(.key = "DurCue")` percent, and the farthest
future date `r oa_n(.key = "DurMaxDate")` percent; an open-ended clause accounts for `r oa_n(.key = "DurOpen")`
percent. For the remaining `r oa_n(.key = "DurNone")` percent no source answers: the contract states no term,
carries no cue and names no date beyond its filing, which is what a contract of indefinite length looks like in
the text. `r oa_n(.key = "DurCapped")` contracts fall to the 30-year rule.

```{r}
#| label: float-duration-rungs
#| results: asis
oa_float(.name = "DurationRungs")
```

### The rules against the naive reading {#sec-oa-d-contrast}

`r oa_ref(.name = "ContentContrast")` reports, by category, on how many contracts each measure is defined under the
naive reading of the spans and under our rule, and `r oa_ref(.name = "ContentValues")` what it is worth on them. The
rules add coverage where the text states what a naive reading has to guess, and remove it where a naive reading
counts what the rule rejects. The duration is the clearest case. The rule-based duration is defined on
`r oa_n(.key = "DurDefRule")` contracts and the naive one on `r oa_n(.key = "DurDefNaive")`, the difference being
contracts that state a term without naming a future date; and the two yield different lengths, a median of
`r oa_n(.key = "DurMedRule")` years against `r oa_n(.key = "DurMedNaive")`, because the farthest future date in a
contract is often a date the contract mentions rather than the date it runs to. Contract partners are the clearest
case of the rule removing what a naive count adds: a contract names `r oa_n(.key = "ValPartNaive")` distinct
organization spellings on average and `r oa_n(.key = "ValPartRule")` partners, the rest being subsidiaries, lenders,
agents and companies the contract mentions. Countries move the same way: `r oa_n(.key = "ValCtryNaive")` mentioned
per contract against `r oa_n(.key = "ValCtryReg")` attached to the registrant and `r oa_n(.key = "ValCtryCpty")`
to the counterparties, which is the difference between the countries a contract talks about and the countries its
partners are in. Amounts fall from `r oa_n(.key = "ValAmtNaive")` figures read to `r oa_n(.key = "ValAmtRule")`
kept in dollars once zeros and par values are gone. Where the rule loses coverage, it loses what it should. What
remains is not certain -- the rules let the text decide, and are silent where it does not -- and our database is
built so that a reader can see, for every variable of every contract, the spans it rests on and the rule that
produced it.

```{r}
#| label: float-content-contrast
#| results: asis
oa_float(.name = "ContentContrast")
```

```{r}
#| label: float-content-values
#| results: asis
oa_float(.name = "ContentValues")
```

::: {.content-visible when-format="html"}

# Validation

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,
  .path_qmd     = .lP$Input$Qmd,
  .dir_exhibits = .lP$Input$DirExhibits
)
```

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "42-OnlineAppendix-D.qmd"),
  .path_tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-D.tex"),
  .path_numbers = NULL,                                                                     # 40 deploys Numbers.tex
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  .dir_own      = here::here("2_output", "40-Numbers", "Output"),                            # the exhibits 40 built
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL
)
```

# Next

**42-OnlineAppendix-E** -- additional analysis.

:::
