---
title: "Online Appendix A -- SEC Filing Requirements and Distributions (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THE APPENDIX'S OWN. init_*() resolve this document's paths, tbl_say() is the fixed-width printer
# every report below uses, _Plots.R gives the figures built here the house theme, and _OnlineAppendix.R is the
# machinery every chapter of the appendix shares: numbers, floats, references, markers, the LaTeX pass, deployment.
# No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "42-OnlineAppendix-A"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
source(file = here::here("1_code", "40-Numbers.R"), encoding = "UTF-8") # the builders and the register loader
```

# Purpose

This document is Appendix A of the online appendix: which filings the database draws on and why, how the contracts
distribute across forms, over the year, over time by contract type and between new and established filers, and
what a row of the release is. Its text is written here once and
rendered twice: to html, the runbook a reader of the replication site follows, and to a LaTeX fragment that the
paper's Overleaf project inputs. The fragment carries the chapter and nothing else. Everything that makes this a
runbook -- this section, the configuration, the checks, and the exhibits built for the response memo -- sits in
blocks the LaTeX pass removes.

The online appendix is one such document per chapter, `42-OnlineAppendix-A` to `-F`, each with its own library of
builders and its own output directory. What the chapters share -- how a number is read from the tibble beside the
exhibit that prints it, how a float points at an exhibit's files, how the fragment is rendered and deployed -- is
one library, `_Commons/_OnlineAppendix.R`, sourced as the commons are.

## Why the text lives here and not in Overleaf

Most sentences of this chapter carry a number the pipeline produced -- a count of filings, a share of contracts, the
references an order makes. Typed into Overleaf, each of those is a copy that stops being true the next time an
upstream stage runs, and nothing reports it. Written here, a number is read from the tibble written beside the
exhibit that prints it, so the sentence and the table cannot disagree.

The cost is that the fragment is not a file to edit. An edit made to it in Overleaf is lost at the next render;
comments and suggested changes come back into this document.

## What the fragment may contain

Prose, headings, citations, numbers, cross-references and floats. No code and no console output: the LaTeX pass
renders with code hidden, every chunk that prints sits inside a block that pass removes, and the functions that
write into the appendix itself never print through `cli`. The headings map onto the appendix's own numbering: the
level-two heading here is the lettered chapter there, a level-three heading a numbered section.

## Where the exhibits come from

Each exhibit is registered once, under Configuration, with the source that writes its files: 30, the manuscript's
exhibits document, whose tables and figures the fragment reads through `\oaexhibits`; or this chapter itself, whose
own exhibits are built under Build, in the same layout, and read through `\oaown`. The html shows each exhibit where
the paper prints it, numbered as the paper numbers it: a figure as the writer's png copy, a table as the writer's own
tabular converted by the Pandoc that Quarto runs. So the two renders set the same content, and the html can be read
as the chapter.

One exhibit built here belongs to the response memo rather than to the appendix: the quarterly count of exhibit
files behind the 2001 start. It is registered under Section M, shown at the end of this page, and left out of the
fragment; the memo sets it from this chapter's output directory.

An exhibit not built yet is not an error. It is set as a framed line naming it, so the paper still compiles, and
Validation lists it. With `Strict` on, it stops the render instead.

## What is recomputed, and what is not

The text, the numbers and the floats on every render, once per format: a few small parquet reads and file checks.
The exhibits this chapter builds itself are the exception. They read the release, the master index and the mirrored
links table, so each build runs only where its outputs are missing or older than its inputs or this chapter's
library; `Rebuild` forces them.

## Where things are written

One file. Quarto writes the fragment to `_rendered/1_code/42-OnlineAppendix-A.tex`, beside this document's html,
but only in the LaTeX pass, which the Render button does not run: RStudio renders the first format the YAML lists,
and that is this html. The numbers the text cites are not written here: `40-Numbers` resolves them and writes the
one `Numbers.tex` the paper inputs. `oa_publish()` renders both passes, copies the fragment and the exhibits 40 built
for this chapter to the paper folder, and lists which of them changed -- which, while Overleaf is updated by hand, is
the list of files to upload. See Deployment.

# Configuration

```{r}
#| label: configure
.lP <- list(
  # THE DROPBOX ROOT: the release is read from it, and deployment writes to it.
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict   = FALSE, # TRUE stops the render on an exhibit that is not built or a number that does not resolve
    FigWidth = 0.96,  # a figure's width as a share of the text width, as the previous appendix set it
    Rebuild  = FALSE, # TRUE rebuilds this chapter's own exhibits even where their inputs have not changed
    FilesFrom = 1998.1, # the exhibit-files table's first quarter, as 01A writes year-quarters
    FilesTo   = 2001.2  # and its last
  )
)

.dirs_edgar <- rGetEDGAR::get_directories(here::here("2_output", "01A-EdgarIndex", "GetEDGAR"))

.lP$Input <- list(
  # 30'S OUTPUT, READ IN PLACE: Data/ for the numbers, and Tables/, Notes/ and Figures/ to check what the fragment
  # will ask Overleaf for. Pointing this at the deployed current/ folder is this one line, once 30 deploys Data/ too.
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  Contracts   = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),  # the release, for the builds
  Orders      = fs::path(.lP$Root, "100_Data_Export", "CtoOrders.parquet"),  # one row per reference an order makes
  DirMaster   = .dirs_edgar$MasterIndex$DirParquet,                          # the master index 01A mirrors
  DirLinks    = .dirs_edgar$DocLinks$DirMain$Links,                          # the document lists 01A mirrors
  Landing     = here::here("2_output", "01A-EdgarIndex", "Output", "LandingPageAll.parquet"), # SIC per filing
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),           # the LaTeX pass's template
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"),     # the html pass's bibliography
  Qmd         = here::here("1_code", "42-OnlineAppendix-A.qmd")             # this document, scanned for markers
)

.lP$Input$Register <- here::here("2_output", "40-Numbers", "Output", "Numbers.csv") # every number, as 40 resolved it

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-A.tex"), # written by Quarto, in the LaTeX pass
  DirOwn  = here::here("2_output", "40-Numbers", "Output"),                                 # the exhibits built here, in 30's layout
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")      # where oa_deploy_tex() copies all of it
)

# A FRESH RECORD FOR THIS PASS. The emitters in the text record what they set, and Validation reads the record.
oa_state_reset()
```

## The chapter's exhibits

One row per exhibit, in the order the chapter prints them. `Name` is the stem every file of the exhibit is written
under, `Source` says who writes them -- 30, or this chapter (A) -- and `Caption` is the only text about an exhibit
written here. Section M is the response memo: built and shown here, set by the memo.

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,               ~Kind,    ~Source, ~Caption,
  "A",      "ExhibitRequired",   "table",  "A",     "Forms on which Exhibit 10 is required, and which the database covers",
  "A",      "FormDescriptions",  "table",  "A",     "The forms, and the regulations that establish them",
  "A",      "FormCoverage",      "table",  "A",     "Forms that carry material contracts, and the database's coverage",
  "A",      "FilingTypes",       "figure", "30",    "Contracts by filing type",
  "A",      "FilingsWithinYear", "figure", "A",     "Contract filings within the calendar year",
  "A",      "TypesTimeA",        "figure", "30",    "Contract types over time, and the share of amendments",
  "A",      "TypesTimeC",        "figure", "30",    "Contract types over time, by category",
  "A",      "SeasonedFilers",    "figure", "A",     "Contract filings of all filers and of seasoned filers",
  "A",      "CtoLinkage",        "table",  "A",     "From confidential treatment orders to the contracts they cover",
  "M",      "ExhibitFiles",      "table",  "A",     "Exhibit 10s listed on EDGAR's index pages, and those that are files"
)

tab_sources <- tibble::tribble(
  ~Source, ~Dir,                          ~Macro,
  "30",    .lP$Input$DirExhibits,         "\\oaexhibits", # the manuscript's exhibits, in current/ in Overleaf
  "A",     as.character(.lP$Output$DirOwn), "\\oaown"     # this chapter's own, in online_appendix/ in Overleaf
)

tab_static <- tibble::tibble(
  Name = character(0), # the exhibit's name in the registry above
  File = character(0), # its file stem under \oastatic in the Overleaf project
  Note = character(0)  # its note, written out here
)
```

No table is read from the Overleaf project, so the static table is empty. It keeps its columns, so a table the paper
holds as a file of its own can be registered here: its name, its file under `\oastatic`, and its note, since no
`Notes/` file exists for it.

# Input

30 is the one input this chapter does not build for itself. It calls none of 30's functions and reads only what 30
wrote, so it renders on the state of 30's last render -- and says so if 30 has not rendered at all.

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits, # 30's output, read in place
  .template     = .lP$Input$Template,    # without it the LaTeX pass fails
  .bib          = .lP$Input$Bib          # without it the html pass cannot resolve a citation
)
```

# Build

This chapter builds nothing. Every exhibit it sets -- 30's and its own -- is built by `40-Numbers`, which writes
them in 30's layout under its own output directory, the directory the sources table names as this chapter's.
A missing exhibit is therefore a render of 40 away, not of this document.

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats    = tab_floats,                  # the chapter's exhibits, in print order
  .static    = tab_static,                  # the ones read from the Overleaf project; none
  .sources   = tab_sources,                 # who writes what, and the macro that reads it
  .own       = "A",                         # this chapter's key in the sources table
  .dir_doc   = fs::path_dir(.lP$Input$Qmd), # html image paths are written relative to this document
  .fig_width = .lP$Params$FigWidth,         # every figure at this width
  .strict    = .lP$Params$Strict,           # stop on a missing exhibit rather than mark it
  .long      = character(0)                 # no table of this chapter runs longer than a page
)

oa_report_floats(.files = ctx_oa$Files)
```

Read the status before the text. Ready means the fragment asks Overleaf for files that exist here; whether Overleaf
holds them too depends on what was uploaded there, which this document cannot see.

# Numbers

Every number the text cites is a key in 40's registry, resolved there over the tibble beside the exhibit that
prints it. This chapter loads the register 40 last wrote and cites through `oa_n()`, as before; a key it does not
hold aborts the render, and a key it holds but could not resolve prints as a marker and is listed under Validation.

```{r}
#| label: numbers-load
tab_numbers <- num_numbers_load(.path_register = .lP$Input$Register)

oa_report_numbers(
  .tab    = tab_numbers,       # as 40 resolved them
  .strict = .lP$Params$Strict  # TRUE stops the render on an unresolved number
)
```

# Sources

Every regulatory claim in the chapter, with its source, a link, and what the source says. The footnotes in the text
cite the same sources; this register is where they are checked. A row marked "check" cites a reference the drafter is
confident of but did not open while writing.

```{r}
#| label: sources-register
#| results: asis
tab_sources_a <- tibble::tribble(
  ~No, ~Claim, ~Source, ~Url, ~Says, ~Status,
  1L, "Every material contract is filed as Exhibit 10",
  "17 CFR 229.601(b)(10)(i)",
  "https://www.ecfr.gov/current/title-17/chapter-II/part-229/subpart-229.600/section-229.601",
  paste("Every contract not made in the ordinary course of business that is material to the registrant, to be",
        "performed after the filing or entered into within two years before it."),
  "verified",
  2L, "Which forms require Exhibit 10; an 8-K does not",
  "17 CFR 229.601(a), exhibit table",
  "https://www.ecfr.gov/current/title-17/chapter-II/part-229/subpart-229.600/section-229.601",
  paste("Row (10) of the exhibit table: required on S-1, S-4, S-11, SF-1, SF-3, F-1, F-4, 10, 10-D, 10-Q, 10-K;",
        "not on S-3, S-8, F-3 or 8-K."),
  "verified",
  3L, "Item 1.01 within four business days since August 2004; the contract follows with the next periodic report",
  "Release 33-8400 (16 Mar 2004), effective 23 Aug 2004",
  "https://www.sec.gov/rules-regulations/2004/03/additional-form-8-k-disclosure-requirements-acceleration-filing-date",
  paste("The agreement must be filed as an exhibit to the next periodic report or registration statement; filing",
        "with the 8-K is encouraged when feasible, particularly when no confidential treatment is requested."),
  "verified",
  4L, "Why the 8-K exhibit was not required; attaching it is now best practice",
  "Form 8-K C&DI 102.02 (22 Mar 2022)",
  "https://www.sec.gov/rules-regulations/staff-guidance/compliance-disclosure-interpretations/exchange-act-form-8-k",
  paste("The Commission did not require the agreement as an 8-K exhibit because registrants needed time to request",
        "confidential treatment; since 2019 that reason no longer holds and attaching it is best practice."),
  "verified",
  5L, "Form 20-F lists material contracts as Exhibit 4",
  "Form 20-F, Instructions as to Exhibits, 4(a)",
  "https://www.sec.gov/files/form20-f.pdf",
  paste("Material contracts not made in the ordinary course, to be performed after the filing or entered into within",
        "two years. Form 20-F's exhibit list does not reference Item 601 (Release 33-10618, fn. 56)."),
  "verified",
  6L, "Small business issuers reported under Regulation S-B until 2008; its Item 601 mirrored S-K's",
  "17 CFR 228.601 (repealed); Release 33-8876 (19 Dec 2007), effective 4 Feb 2008",
  "https://www.sec.gov/rules/final/2007/33-8876.pdf",
  paste("Eliminates Regulation S-B and the SB forms, with a transition; transition end dates (10-QSB after 31 Oct",
        "2008; 10-KSB for fiscal years ending before 15 Dec 2008) to be read from the release."),
  "check the transition dates",
  7L, "Before April 2019 a confidential treatment request; the redacted contract public while under review",
  "Securities Act Rule 406; Exchange Act Rule 24b-2",
  "https://www.ecfr.gov/current/title-17/chapter-II/part-240/section-240.24b-2",
  paste("The two rules set the request procedure: the redacted exhibit is filed publicly and the unredacted text",
        "submitted separately for review under FOIA exemption 4. Rule 406 is at 17 CFR 230.406."),
  "verified",
  8L, "About 10 percent of requests denied at least in part; refiled with fewer redactions",
  "Thompson (2023); Ahci (2025)",
  "",
  "Cited in the text.",
  "literature",
  9L, "Since 2 April 2019, redaction without a request",
  "Release 33-10618 (20 Mar 2019), effective 2 Apr 2019; Item 601(b)(10)(iv)",
  "https://www.sec.gov/files/rules/final/2019/33-10618.pdf",
  paste("Information may be omitted that is not material and would likely cause competitive harm; marked by",
        "brackets, with a statement on the first page of the exhibit."),
  "verified",
  10L, "The standard changed in November 2020",
  "Release 33-10825 (2 Nov 2020)",
  "https://www.sec.gov/rules/final/2020/33-10825.pdf",
  paste("Competitive harm dropped: the information must be of a kind the registrant customarily and actually treats",
        "as private or confidential."),
  "verified",
  11L, "Confidential treatment orders listed on EDGAR from May 2008",
  "The master index (form type CT ORDER)",
  "",
  "Our own data, not a rule; the text says so.",
  "own data",
  12L, "EDGAR filing mandatory for domestic registrants by 1996",
  "Release 33-7122 (19 Dec 1994); phase-in completed May 1996",
  "https://www.sec.gov/rules/final/33-7122.txt",
  "Final phase-in of mandated electronic filing.",
  "check the release number and link",
  13L, "Release 7.0 effective 30 May 2000; legacy EDGARLink closed 27 Nov 2000; documents disseminated as files",
  "Release 33-7855 (24 Apr 2000); SEC, Accessing EDGAR Data",
  "https://www.sec.gov/search-filings/edgar-search-assistance/accessing-edgar-data",
  paste("Post-EDGAR 7.0 filings (after 26 May 2000) are also accessible via an accession-number directory holding",
        "every document submitted; the ExhibitFiles table shows the data side."),
  "dates verified; check the release number",
  15L, "What each form is for (FormDescriptions)",
  "17 C.F.R. Parts 239 and 249, one section per form",
  "https://www.ecfr.gov/current/title-17/chapter-II/part-239",
  paste("Each section's heading states the form's purpose; SF-1 (239.44) and F-1/F-3/F-4 were read today, the",
        "others are written from the same source and their headings are to be checked at the links the table's",
        "data carries (Url column of FormDescriptions.parquet). Part 249 is at",
        "https://www.ecfr.gov/current/title-17/chapter-II/part-249."),
  "check the headings not read today",
  14L, "10-K deadlines of 60, 75 and 90 days; 10-Q of 40 and 45; the 12b-25 extension",
  "Form 10-K General Instruction A(2); Form 10-Q General Instruction A(1); 17 CFR 240.12b-25",
  "https://www.ecfr.gov/current/title-17/chapter-II/part-240/section-240.12b-25",
  paste("Deadlines by filer status (large accelerated, accelerated, other); Rule 12b-25 grants 15 days for an annual",
        "report and 5 for a quarterly one."),
  "check the instruction letters"
)

# ONE cat(), so knitr emits the header and the rows as one block; three calls would split the table.
rows_ <- paste0(
  "| ", tab_sources_a$No, " | ", tab_sources_a$Claim, " | ",
  ifelse(nzchar(tab_sources_a$Url), paste0("[", tab_sources_a$Source, "](", tab_sources_a$Url, ")"),
         tab_sources_a$Source),
  " | ", tab_sources_a$Says, " | ", tab_sources_a$Status, " |"
)
cat(paste(c("", "| No | Claim | Source | Says | Status |", "|---:|---|---|---|---|", rows_, ""), collapse = "\n"))
```

:::

::: {.content-visible when-format="html"}

# Appendix A

Everything from here to the memo section is the chapter: shown here as the runbook renders it, and written in the
LaTeX pass as the fragment Overleaf inputs. Each exhibit stands where the paper prints it, with the paper's number.

:::

```{=latex}
\clearpage
```

## SEC filing requirements and distributions {#sec-oa-a}

This appendix describes what our database contains and why. Section A.1 sets out who must file a material
contract, on which forms, what we retrieve from those forms and what we leave out. Section A.2 shows how the
contracts distribute across forms and over the calendar year. Section A.3 shows how the mix of contract types moved
over the sample period, and separates the rise of 2020 and 2021 into the filings of new registrants and those of
established firms. Section A.4 describes what a row of our database is: how one attachment becomes several rows,
which rows we exclude from the sample and why they stay in the database, and how we link a contract to the
confidential treatment order that covers it and to the 8-K that announced it. The construction of the estimation
samples is described in the paper (Section 4.1).

### Who files what, and what our database holds {#sec-oa-a-holds}

Item 601 of Regulation S-K requires a firm to file every material contract as Exhibit 10 to its registration
statements under the Securities Act -- Forms S-1 and S-4, and Forms F-1 and F-4 for foreign private issuers -- and to
its periodic reports under the Exchange Act, Forms 10-K and 10-Q; `r oa_ref(.name = "ExhibitRequired")` reproduces
the row of the regulation's exhibit table that says so, form by form, and `r oa_ref(.name = "FormDescriptions")`
states what each form is for, with the regulation that establishes it. The forms on which the table requires no
material contract -- the shelf registrations on Forms S-3 and F-3, the employee-plan registration on Form S-8 --
incorporate the filer's periodic reports by reference, so the contracts of those filers reach EDGAR with the 10-K
and 10-Q rather than with the registration.^[17 C.F.R. 229.601(b)(10)(i) defines the material
contract: every contract not made in the ordinary course of business that is material to the registrant and is to be
performed after the filing, or was entered into not more than two years before it. The exhibit table in
229.601(a) lists the forms on which it must be filed: S-1, S-4, S-11, SF-1, SF-3, F-1, F-4, 10, 10-D, 10-Q and 10-K,
and not S-3, S-8, F-3 or 8-K.] A current report on Form 8-K need not carry the contract: since August 2004, an 8-K
must report the entry into a material definitive agreement within four business days under Item 1.01, but the
contract itself may follow as an exhibit to the next periodic report (Section 2 of the paper).^[SEC Release
33-8400 (March 16, 2004), effective August 23, 2004, which added Item 1.01 and set the four-business-day deadline
(Form 8-K, General Instruction B.1). The release requires the agreement to be filed with the next periodic report or
registration statement and encourages filing it with the 8-K where feasible; the staff's interpretation 102.02
(March 2022) explains that an exhibit was not required because registrants needed time to request confidential
treatment, and calls attaching it best practice now that a request is no longer needed.] Two groups of filers
followed rules of their own. Foreign private issuers file their annual report on Form 20-F, whose instructions list
material contracts as Exhibit 4 rather than Exhibit 10.^[Form 20-F, Instructions as to Exhibits, Exhibit 4(a):
material contracts not made in the ordinary course of business, to be performed after the filing or entered into
within two years before it. Form 20-F's exhibit requirements do not reference Item 601 (Release 33-10618, note
56).] And until 2008, small business issuers reported under Regulation S-B, on Forms 10-KSB, 10-QSB and SB-2, whose
Item 601 required material contracts as Exhibit 10 in the same way.^[17 C.F.R. 228.601, repealed by SEC Release
33-8876 (December 19, 2007), effective February 4, 2008, which eliminated Regulation S-B and the SB forms with a
transition period.]

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 17 C.F.R. 229.601(b)(10), Material contracts</summary>

[https://www.ecfr.gov/current/title-17/chapter-II/part-229/subpart-229.600/section-229.601](https://www.ecfr.gov/current/title-17/chapter-II/part-229/subpart-229.600/section-229.601)

> (10) Material contracts. (i) [Every contract not made in the ordinary course of business which is material to the
> registrant and is to be performed in whole or in part at or after the filing of the registration statement or
> report or was entered into not more than two years before such filing.]{.mark} Only contracts need be filed as to
> which the registrant or subsidiary of the registrant is a party or has succeeded to a party by assumption or
> assignment or in which the registrant or such subsidiary has a beneficial interest.
>
> (ii) If the contract is such as ordinarily accompanies the kind of business conducted by the registrant and its
> subsidiaries, it will be deemed to have been made in the ordinary course of business and need not be filed unless
> it falls within one or more of the following categories, in which case it shall be filed except where immaterial
> in amount or significance: [...]

The forms on which Exhibit 10 is required are read from the exhibit table in 229.601(a); the old appendix's
Table B1 reproduced it: an X under S-1, SF-1, SF-3, S-4, S-11, F-1, F-4, 10, 10-D, 10-Q and 10-K, and none under
S-3, S-8, F-3 or 8-K. To check against the current table at the link.

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> SEC Release 33-8400, Additional Form 8-K Disclosure Requirements and Acceleration of Filing Date (March 16, 2004)</summary>

[https://www.sec.gov/rules-regulations/2004/03/additional-form-8-k-disclosure-requirements-acceleration-filing-date](https://www.sec.gov/rules-regulations/2004/03/additional-form-8-k-disclosure-requirements-acceleration-filing-date)

From Section II.C, Item 1.01:

> The proposals would have required a company to file a material agreement required to be disclosed under Item 1.01
> as an exhibit to its Form 8-K. We received numerous comments on this proposal. A primary concern of commenters was
> that companies would not always be able to prepare and submit requests for confidential treatment of sensitive
> terms of the agreement within the short Form 8-K filing period. [...] [Pursuant to amended Item 601 of Regulation
> S-K, a company will have to file such agreement as an exhibit to the company's next periodic report or
> registration statement. However, we encourage companies to file the exhibit with the Form 8-K when feasible,
> particularly when no confidential treatment is requested.]{.mark}

The four-business-day deadline and the August 23, 2004 effective date are in the same release; the deadline is
General Instruction B.1 of Form 8-K.

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> Form 8-K Compliance and Disclosure Interpretation 102.02 (March 22, 2022)</summary>

[https://www.sec.gov/rules-regulations/staff-guidance/compliance-disclosure-interpretations/exchange-act-form-8-k](https://www.sec.gov/rules-regulations/staff-guidance/compliance-disclosure-interpretations/exchange-act-form-8-k)

> Question: Is a registrant required to file the material definitive agreement as an exhibit to the Item 1.01
> Form 8-K?
>
> Answer: Registrants are encouraged, as a best practice, to file the agreement as an exhibit to the Item 1.01
> Form 8-K. [The Commission did not require the material definitive agreement to be filed as an exhibit to the
> Item 1.01 Form 8-K due to the registrant's need for time to (1) request confidential treatment of sensitive
> terms of the agreement and (2) prepare the agreement in the proper EDGAR format.]{.mark} See Release No. 33-8400
> (March 16, 2004). The Commission, however, recently amended Form 8-K to permit registrants to redact sensitive
> terms of a material definitive agreement without submitting a confidential treatment request. See Instructions 5
> and 6 to Item 1.01 of Form 8-K; see also Release No. 33-10618 (March 20, 2019). The need for confidential
> treatment generally can no longer be the basis for declining to file the material definitive agreement as an
> exhibit to the Item 1.01 Form 8-K.

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> Form 20-F, Instructions as to Exhibits, Exhibit 4</summary>

[https://www.sec.gov/files/form20-f.pdf](https://www.sec.gov/files/form20-f.pdf)

The form's own text, Instructions to Item 4.A.4, instruction 2 (read from the SEC's 2006 form as filed with OMB,
reginfo.gov, object 2556001):

> If you are filing a report under Rule 13a-19 or Rule 15d-19 under the Exchange Act (17 CFR 240.13a-19 or
> 240.15d-19), you must disclose the material terms of the transaction as a result of which you ceased to be a
> shell company and [you should file as an exhibit under Item 4(a) of the Exhibits to Form 20-F any contracts
> relating to the transaction.]{.mark}

The wording of exhibit item 4 itself, as filers reproduce it in their exhibit indexes (Quartz Mountain Resources
and Great Basin Gold, Forms 20-F for 2005 and 2004); to be checked against the Instructions as to Exhibits page of
the form at the link:

> 4. a. [Material contracts not made in the ordinary course of business or which are to be performed in whole or in
> part at or after the filing of the annual report or which was entered into not more than two years before
> filing.]{.mark}
> b. (i) Agreements to which Directors, Officers, promoters, voting trustees or security holders or their
> affiliates named in the Registration Statement are parties other than contracts involving only the purchase or
> sale of current assets having a determinable market price; (ii) contracts on which the Company's business is
> substantially dependent; (iii) contracts for the acquisition or sale of property exceeding 15% of the Company's
> fixed assets; and (iv) material leases.

Release 33-10618, note 56: "Form 20-F, for use by foreign private issuers, has its own exhibit requirements that
do not reference Item 601 of Regulation S-K. See Item 19 of Form 20-F." Item 10.C of the form separately requires
a summary of each material contract of the two preceding years in the text of the report.

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> SEC Release 33-8876, Smaller Reporting Company Regulatory Relief and Simplification (December 19, 2007)</summary>

[https://www.sec.gov/rules/final/2007/33-8876.pdf](https://www.sec.gov/rules/final/2007/33-8876.pdf)

Not quoted: the release was not opened while writing. It eliminated Regulation S-B (17 C.F.R. Part 228, whose Item
601 was 228.601) and Forms 10-KSB, 10-QSB, SB-1 and SB-2, effective February 4, 2008, with a transition period.
To check at the link: the effective date, and the last dates on which the SB forms could be used.

</details>

:::

```{r}
#| label: float-exhibit-required
#| results: asis
oa_float(.name = "ExhibitRequired")
```

```{r}
#| label: float-form-descriptions
#| results: asis
oa_float(.name = "FormDescriptions")
```

EDGAR filing became mandatory for all domestic registrants in May 1996, and the master index lists filings from
1993, when the phase-in of electronic filing began.^[SEC Release 33-6977 (February 23, 1993) adopted Regulation
S-T and began the phase-in on April 26, 1993; SEC Release 33-7122 (December 19, 1994) set its final schedule,
completed on May 6, 1996.]
Our sample period starts in 2001 for a different reason. EDGAR's index page lists the documents of a filing back to
1993, read from the tags of the complete submission, but until mid-2000 an exhibit existed only inside that
submission's text file -- there was no file of its own to retrieve. Separately disseminated exhibit files arrived
with the modernized system: a handful of filings in 1999, a quarter of the listed Exhibit 10s in the second quarter
of 2000, nearly all of them in June, after Release 7.0 took effect on May 30, 2000, and every listed exhibit from
July 2000 on. The year 2001 is therefore the first full year in which every
material contract is available as a document of its own, and our sample period runs from 2001 to 2024.
The `r oa_n(.key = "DocsPre2001")` contracts of mid-1999 to 2000 that already were such documents are in our
database and outside the sample (Section A.4). Two further dates shape what our database holds: EDGAR lists
confidential treatment orders as filings of their own from May 2008, which is where our orders begin, and since
April 2, 2019, the amendments to Item 601 that followed the FAST Act allow a firm to redact a contract without a
confidential treatment request.^[SEC Release 33-7855 (April 24, 2000) put EDGAR Release 7.0 into
effect on May 30, 2000; the SEC's documentation on accessing EDGAR data states that filings after May 26, 2000 are
also reachable through an accession-number directory holding every document of the filing. The first date is the
earliest CT ORDER in EDGAR's master index, which is our database's own record. Release 33-10618 (March 20, 2019),
effective April 2, 2019, added Item 601(b)(10)(iv).]

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> SEC, Accessing EDGAR Data (post-EDGAR 7.0 filings)</summary>

[https://www.sec.gov/search-filings/edgar-search-assistance/accessing-edgar-data](https://www.sec.gov/search-filings/edgar-search-assistance/accessing-edgar-data)

As read this morning; to be checked against the page:

> [Post-EDGAR 7.0 filings (after May 26, 2000) are also accessible via an alternative path with an intermediate
> accession-number directory. [...] All the documents submitted for a given filing are in this directory.]{.mark}

Release 33-7855 (April 24, 2000), which put Release 7.0 into effect on May 30, 2000, and Release 33-7122
(December 19, 1994), which set the final phase-in of mandated electronic filing, were not opened while writing;
their numbers are to be checked. The May 2008 start of CT ORDER filings is the database's own master index.

</details>

:::

Before April 2019, a firm that wanted to redact a contract filed a confidential treatment request: it filed the
redacted contract on EDGAR and submitted the unredacted text to the SEC staff for review.^[Securities Act Rule 406
(17 C.F.R. 230.406) and Exchange Act Rule 24b-2 (17 C.F.R. 240.24b-2). The request rests on exemption 4 of the
Freedom of Information Act; the redacted exhibit is filed publicly and the unredacted text submitted separately.]
Filing was not delayed by the request; the redacted contract was public while the staff reviewed it. About 10 to
11 percent of requests were denied at least in part [@thompson2023; @ahci2025], and a firm whose request was
denied refiled the contract with fewer redactions, so our database holds such a contract twice, once with each
filing. Since April 2019, a firm redacts without a request, marking the omission with brackets and a statement on
the exhibit's first page, and the staff reviews redacted contracts selectively; the standard for what may be
omitted was information that is not material and would likely cause competitive harm, and since November 2020
information the firm customarily and actually treats as private or confidential.^[Item 601(b)(10)(iv), as adopted
by Release 33-10618 and amended by Release 33-10825 (November 2, 2020).]

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> Securities Act Rule 406 and Exchange Act Rule 24b-2 (17 C.F.R. 230.406; 240.24b-2)</summary>

[https://www.ecfr.gov/current/title-17/chapter-II/part-240/section-240.24b-2](https://www.ecfr.gov/current/title-17/chapter-II/part-240/section-240.24b-2)

Not quoted: the two rules were not opened while writing. They set the confidential-treatment application
procedure -- the redacted exhibit filed publicly, the unredacted text and the application submitted separately,
the request resting on exemption 4 of the Freedom of Information Act. Rule 406 is at
<https://www.ecfr.gov/current/title-17/chapter-II/part-230/section-230.406>.

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> SEC Release 33-10618, FAST Act Modernization and Simplification of Regulation S-K (March 20, 2019)</summary>

[https://www.sec.gov/files/rules/final/2019/33-10618.pdf](https://www.sec.gov/files/rules/final/2019/33-10618.pdf)

Note 67:

> [Both Item 601(b)(2)(ii) and new Item 601(b)(10)(iv) require the registrant to mark the exhibit index to indicate
> that portions of the exhibit or exhibits have been omitted and include a prominent statement on the first page of
> the redacted exhibit that certain identified information has been excluded from the exhibit because it is both
> (i) not material and (ii) would likely cause competitive harm to the registrant if publicly disclosed. The
> registrant also must indicate by brackets where the information is omitted from the filed version of the
> exhibit.]{.mark}

The amendments on the redaction of confidential information in exhibits became effective on April 2, 2019 (the
SEC's small-entity compliance guide for the release).

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> SEC staff guidance, Confidential Treatment Applications Submitted Pursuant to Rules 406 and 24b-2</summary>

[https://www.sec.gov/rules-regulations/staff-guidance/disclosure-guidance/corpfinconfidential-treatment-applicationshtm](https://www.sec.gov/rules-regulations/staff-guidance/disclosure-guidance/corpfinconfidential-treatment-applicationshtm)

> [Through amendments adopted in March 2019 and November 2020, the Commission changed several of its exhibit filing
> requirements to allow companies to omit immaterial information that a company customarily and actually treats as
> private or confidential without having to submit a confidential treatment request.]{.mark} Companies may follow
> the procedures outlined in Regulation S-K Item 601(b)(10)(iv) and parallel rules, referred to here as the
> redacted exhibit rules, to redact such information without separately providing copies of the unredacted
> exhibits at the time of filing, unless subsequently requested by the Commission or the staff.

The November 2020 amendment is Release 33-10825 (<https://www.sec.gov/rules/final/2020/33-10825.pdf>), not opened
while writing.

</details>

:::

Using rGetEDGAR, we download three groups of documents. The first is every attachment filed as Exhibit 10 with the
eight forms above and their amendments. An attachment counts as Exhibit 10 where its exhibit type maps to Exhibit
10 in a lookup of the raw exhibit-type strings filers use, rather than where it matches a pattern: filers write
`EX-10.1`, `EX-10`, `EXHIBIT 10.23` and many further variants, and a pattern silently excludes the spellings its
author did not anticipate. The second is every Form 8-K filing that reports Item 1.01, whose contract summary we
use to measure how firms announce their contracts. The third is every confidential treatment order, which links a
redacted contract to the SEC's grant of confidential treatment. The first group yields `r oa_n(.key = "DocsAll")`
documents in our sample period, of which `r oa_n(.key = "DocsUnique")` are distinct attachments and
`r oa_n(.key = "DocsSample")` form the unique-contract sample; the second yields the contract summary of
`r oa_n(.key = "Docs8K")` current reports; and the third holds `r oa_n(.key = "Orders")` orders.

Our database is thus defined by EDGAR form type and exhibit number, and material contracts filed under other form
types or exhibit numbers lie outside it. `r oa_ref(.name = "FormCoverage")` lists every form that carries material
contracts, the filings EDGAR lists for it from 2001 to 2024, whether our database covers it, and the contracts our
database holds from it. Four groups lie outside. The largest are the forms of small business issuers -- 10-KSB,
10-QSB, SB-2 and Form 10-SB -- used until 2008, after which these firms file on Forms 10-K and 10-Q, which our
database covers; EDGAR lists `r oa_n(.key = "CovSmallBusiness")` such filings. The second consists of EDGAR's
separate form types for variants of the annual report: 10-K405, a 10-K on which the Item 405 box is checked, used
until 2002, and 10-KT, the transition report after a change of fiscal year, together
`r oa_n(.key = "CovTenKVariants")` filings. The third consists of registrations under the Exchange Act on Form 10,
among them spin-offs, and on Form S-11, the registration statement of real-estate companies,
`r oa_n(.key = "CovRegistrations")` filings; both carry material contracts by the same rule and were left outside
our sample when we fixed it on the eight forms that hold the bulk of filings. The fourth lies inside a form our
database covers: Form 20-F lists material contracts as Exhibit 4, so our database holds only the 20-F contracts
that filers number as Exhibit 10,
`r oa_n(.key = "Cov20FContracts")` contracts from `r oa_n(.key = "Cov20FFilings")` filings. The registration
statements of foreign issuers, Forms F-1 and F-4, follow Item 601 and number their contracts as Exhibit 10, so they
are covered.

Together, the forms outside our sample account for `r oa_n(.key = "CovOutside")` filings against
`r oa_n(.key = "CovInside")` of the forms inside it. We never downloaded their contracts, so the table does not
count them, and the two counts of filings are not comparable: the forms in our database include every current
report, most of which carry no contract at all, while the small-business forms are periodic reports and registration
statements concentrated in the years before 2009. The gap matters most for small firms before 2009: their contracts
filed with current reports are in our database, while those filed with periodic reports and registration statements
are not. We therefore repeat the paper's firm-quarter analyses for the years to 2008 without the firms that filed
on small-business forms in the respective quarter (Appendix E). Two further groups are excluded by design.
Asset-backed issuers (Forms SF-1, SF-3 and 10-D) are securitization vehicles rather than operating firms, and the
current reports of foreign private issuers on Form 6-K carry no exhibit numbering; a contract filed with one usually
carries the type EX-99.

::: {.content-visible when-format="html"}

<details class="oa-authors">
<summary><strong>Note for the authors:</strong> Form 10 and Form S-11 -- was there a reason?</summary>

Both forms require Exhibit 10 (row (10) of the exhibit table) and both are filed by operating firms: Form 10
registers a class of securities under the Exchange Act without an offering -- spin-offs, companies going public
without an IPO -- and its material contracts include separation and transition-services agreements; Form S-11 is
the registration statement of real estate companies, whose leases and management agreements are filed there. They
are outside the frame because the frame was fixed on the eight forms in the first submission. Unlike the
asset-backed forms, that is a scope choice rather than a design reason, and a reviewer may ask why. Two questions
for us: was there a reason at the time that the text should state; and how many contracts would the two forms
add, which the links table can count without any download:

```{r}
#| label: authors-note-form10-s11
# THE COUNT, LIVE: Exhibit 10 files listed under Form 10 and S-11 filings since 2001, from the index pages 01A
# mirrored. No download is involved; a listed exhibit with a file name is one the database could retrieve.
idx_ <- arrow::open_dataset(sources = .lP$Input$DirMaster) |>
  dplyr::filter(.data$FormType %in% c("10", "10/A", "S-11", "S-11/A")) |>
  dplyr::filter(.data$YearQuarter >= 2001) |>
  dplyr::select("HashIndex", "FormType") |>
  dplyr::collect()

tab_form10_s11 <- arrow::open_dataset(sources = .lP$Input$DirLinks) |>
  dplyr::filter(.data$YearQuarter >= 2001) |>
  dplyr::select("HashIndex", "Type", "Document") |>
  dplyr::collect() |>
  dplyr::semi_join(idx_, by = "HashIndex") |>
  dplyr::filter(grepl("^EX-?10", toupper(.data$Type)), !is.na(.data$Document)) |>
  dplyr::inner_join(idx_, by = "HashIndex") |>
  dplyr::summarise(Filings = dplyr::n_distinct(.data$HashIndex), Exhibit10s = dplyr::n(), .by = "FormType") |>
  dplyr::arrange(.data$FormType)

tbl_say(
  .tab   = tab_form10_s11,
  .title = "Exhibit 10 files listed under Form 10 and S-11 filings, 2001-2024"
)
```

If the count is small, A.1 says so and adds that rGetEDGAR retrieves the two forms with a configuration change;
if it is large, the frame is a decision rather than an appendix sentence.

</details>

:::

```{r}
#| label: float-form-coverage
#| results: asis
oa_float(.name = "FormCoverage")
```

### Distributions of filings {#sec-oa-a-distributions}

`r oa_ref(.name = "FilingTypes")` shows the unique contracts by the form they were filed with, U.S. and foreign forms
side by side, each split into original agreements and amendments. Current reports carry the largest share,
`r oa_n(.key = "Share8K")` percent of the sample, ahead of the quarterly and annual reports with
`r oa_n(.key = "Share10Q")` and `r oa_n(.key = "Share10K")` percent, and the registration statement on Form S-1
with `r oa_n(.key = "ShareS1")` percent; the forms of foreign private issuers together carry
`r oa_n(.key = "ShareForeign")` percent of the whole, which follows from the coverage of Exhibit 10 on Form 20-F
rather than from how often foreign issuers contract. Amendments cluster in the periodic reports:
`r oa_n(.key = "Amend10K")` percent of the contracts filed with a 10-K and `r oa_n(.key = "Amend10Q")` percent of
those filed with a 10-Q are amendments, against `r oa_n(.key = "Amend8K")` percent of those filed with an 8-K,
because a firm that amends an existing agreement rarely announces the amendment as the entry into a new one.

```{r}
#| label: float-filing-types
#| results: asis
oa_float(.name = "FilingTypes")
```

`r oa_ref(.name = "FilingsWithinYear")` shows when in the calendar year contracts are filed. Contracts filed with
current reports spread evenly over the year, at about a third of a percent a day, with dips on public holidays.
Contracts filed with periodic reports follow the reporting deadlines. Among annual reports, the spikes fall on the
deadlines of 60, 75 and 90 days after a December year-end -- around 1 March, mid-March and 31 March, the first the
largest -- and a smaller one follows in mid-April, fifteen days later, which is the extension a late filer obtains
under Rule 12b-25.^[Form 10-K, General Instruction A(2), sets the deadline by filer status at 60 days for large
accelerated filers, 75 for accelerated filers and 90 for all others; Form 10-Q, General Instruction A(1), at 40, 40
and 45 days. Rule 12b-25 (17 C.F.R. 240.12b-25) extends an annual report by 15 calendar days and a quarterly
report by 5 on a timely notification.] Among quarterly reports, the spikes fall on the deadlines of 40 and 45 days
after each quarter's end, in May, August and November; the small peak in February comes from filers whose fiscal
year does not end in December.

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 17 C.F.R. 240.12b-25(b)(2)(ii), the late-filing extension</summary>

[https://www.ecfr.gov/current/title-17/chapter-II/part-240/subject-group-ECFR01f77097bde8f13/section-240.12b-25](https://www.ecfr.gov/current/title-17/chapter-II/part-240/subject-group-ECFR01f77097bde8f13/section-240.12b-25)

> (ii) [The subject annual report, semi-annual report or transition report on Form 10-K, 20-F, 11-K, N-CEN, or
> N-CSR, or portion thereof, will be filed no later than the fifteenth calendar day following the prescribed due
> date; or the subject quarterly report or transition report on Form 10-Q or distribution report on Form 10-D, or
> portion thereof, will be filed no later than the fifth calendar day following the prescribed due date]{.mark};

The 60/75/90-day and 40/40/45-day deadlines are General Instruction A(2) of Form 10-K and A(1) of Form 10-Q
(<https://www.sec.gov/files/form10-k.pdf>, <https://www.sec.gov/files/form10-q.pdf>), not opened while writing;
the instruction letters are to be checked.

</details>

:::

```{r}
#| label: float-filings-within-year
#| results: asis
oa_float(.name = "FilingsWithinYear")
```

### Contract types over time {#sec-oa-a-types}

`r oa_ref(.name = "TypesTimeA")` shows the share of each contract type among the unique contracts filed in each year,
stacked, with the share of amendments as a line above the bars. The mix is stable over two decades. Employment
agreements and financial instruments together make up about two thirds of every year's contracts; purchases and
sales, licenses, leases and business-structure agreements share the rest in proportions that hardly move. The two
visible changes are the entry of the current report in 2004, after which employment and credit agreements arrive on
8-Ks rather than with the periodic reports, and the years 2020 and 2021, when equity agreements take a larger share
of the whole. The share of amendments moves within a band of a few percentage points around a third, higher in the
years around 2009 and lower in 2021, when new agreements crowded it out.

`r oa_ref(.name = "TypesTimeC")` shows the same shares one panel per parent category, with the sub-categories as
lines, so a movement inside a parent is visible: the rise of equity agreements against credit agreements within
financial instruments from about a tenth of contracts to a sixth, with a spike in 2021; the two employment
sub-categories converging on a fifth each; and customer-supplier agreements standing well above asset purchases and
research agreements within purchases and sales, in a ranking that does not change over the period. The dashed lines
mark the 8-K reform of August 2004 and the FAST Act amendments of April 2019.

```{r}
#| label: float-types-time-a
#| results: asis
oa_float(.name = "TypesTimeA")
```

```{r}
#| label: float-types-time-c
#| results: asis
oa_float(.name = "TypesTimeC")
```

The number of contracts rises sharply in 2020 and 2021. A newly reporting firm must file the material contracts it
entered into during the two years before its registration (Item 601(b)(10)(i)), so every wave of registrations
arrives with a backlog of contracts. `r oa_ref(.name = "SeasonedFilers")` separates that backlog from the filing of
established firms: a seasoned filer is one more than two years past its first contract in the database, the same
two-year window. All filers file `r oa_n(.key = "NAll2020")` contracts in 2020 and `r oa_n(.key = "NAll2021")` in
2021; seasoned filers file `r oa_n(.key = "NSeasoned2020")` and `r oa_n(.key = "NSeasoned2021")`. Registration
statements carry `r oa_n(.key = "RegAll2021")` percent of all contracts in 2021, against
`r oa_n(.key = "RegSeasoned2021")` percent of the contracts of seasoned filers. Many of the new registrants are
special purpose acquisition companies [@gahng2023spacs], and the figure counts them directly: registrants under SIC
code 6770, EDGAR's code for blank-check companies, file `r oa_n(.key = "NBlankCheck2021")` contracts in 2021. Such
registrants file a standard set of equity agreements at registration, and equity contracts make up
`r oa_n(.key = "EqAll2021")` percent of all contracts in 2021, against `r oa_n(.key = "EqSeasoned2021")` percent
among seasoned filers. Dating a firm by its first contract uses the very filings under study; dated by its first
EDGAR filing of any form instead, seasoned filers file `r oa_n(.key = "NSeasonedEdgar2021")` contracts in 2021, so
the reading does not depend on the definition.

The three panels say the same thing in three ways. The count of contracts rises and falls with the registration wave
while the seasoned line stays flat; the share filed with a registration statement moves with it and the seasoned
share does not; and the equity share does the same. A firm that had been filing for years did not change what it
filed in 2020 and 2021. What changed is who was filing.

```{r}
#| label: float-seasoned-filers
#| results: asis
oa_float(.name = "SeasonedFilers")
```

### What a row of our database is {#sec-oa-a-rows}

A filing can list several registrants, and EDGAR lists its attachments under each of them, so one attachment can
appear as several documents. We identify each attachment by a hash of its address and each registrant's copy by an
identifier of its own, and designate one copy per attachment as primary. Classification and entity extraction read
the primary copy; our database carries every copy with its attachment's values, so unique contracts are the primary
copies, and every registrant's copy remains available for analyses at the filer level. Including the attachments of
1999 and 2000, our database holds `r oa_n(.key = "DocsRelease")` rows and `r oa_n(.key = "DocsReleaseUnique")`
unique attachments. Two cases produce distinct attachments for one agreement and are not merged: two parties that
each file their own copy of it, and a contract refiled with fewer redactions after a partially denied confidential
treatment request.

We apply three rules to flag attachments whose conversion to text failed: ten words or fewer after the SEC header;
fewer than 20 percent stopwords together with fewer than 100 words; or 75 percent or more numeric tokens. Each
threshold sits far from anything a genuine agreement produces, so the rules remove conversion debris -- a PDF
rendered as coordinates, a hyperlink in place of a document, a financial statement filed under an exhibit number --
rather than short agreements. Exhibits whose text is only a placeholder for a PDF or an image carry no readable text
and are counted with them. Of the `r oa_n(.key = "DocsReleaseUnique")` unique attachments,
`r oa_n(.key = "DocsReleaseFlagged")` are flagged: `r oa_n(.key = "RuleShort")` for length,
`r oa_n(.key = "RuleStopwords")` for a want of prose, `r oa_n(.key = "RuleNumeric")` for numeric tokens, and
`r oa_n(.key = "Placeholders")` placeholders. Flagged attachments stay in our database with the rule that flagged
them and are excluded from every sample, as are the `r oa_n(.key = "DocsPre2001")` attachments filed before 2001;
each row carries the step of the sample selection at which it left, so a study that wants either group back has it.

We parse the confidential treatment orders for the exhibits they cover. An order identifies an exhibit by the
filing it came with and its exhibit number, and we follow each such reference to the attachment in our database.
`r oa_ref(.name = "CtoLinkage")` reports where every reference ends. The `r oa_n(.key = "Orders")` orders make
`r oa_n(.key = "OrderRefs")` references, of which `r oa_n(.key = "OrderRefsLinked")` reach the attachment they
name. The rest fail at a point our database records for each reference. The largest group,
`r oa_n(.key = "OrderRefsNotEx10")` references, covers exhibits other than Exhibit 10, such as the indentures and
plans filed as Exhibit 4; `r oa_n(.key = "OrderRefsFrame")` name a filing of a form outside our sample, the
small-business forms among them; and `r oa_n(.key = "OrderRefsMissing")` name an exhibit number that is not among
the attachments downloaded from the filing, mostly where the filer numbered the exhibit differently from the order.
Of the linked references, `r oa_n(.key = "LinkedExtensions")` extend an earlier grant and
`r oa_n(.key = "LinkedDenials")` deny the request; as in @ahci2025, we count grants and their extensions and not
denials, and `r oa_n(.key = "DocsWithCto")` unique contracts of the sample are covered by at least one order.

```{r}
#| label: float-cto-linkage
#| results: asis
oa_float(.name = "CtoLinkage")
```

For every 8-K that reports Item 1.01, we extract the contract summary of the item from the filing, running from the
item's heading to the next heading, or to the signature block where it is the last item. A heading is recognized
differently in the two formats a filing comes in: in markup it follows a closing tag, and in plain text it begins a
line. Both anchors are needed, because the word "item" appears inside most agreements, and a rule that ignored the
markup would find a heading in the middle of a sentence. We recover the summary for `r oa_n(.key = "Docs8K")`
current reports. The paper's announcement sample keeps the `r oa_n(.key = "Announcements")` of them that announce
a single agreement and carry at most one Exhibit 10; the proxy for a single agreement and what each filter excludes
are reported with the sample's construction in the paper (Section 3.5).

::: {.content-visible when-format="html"}

```{=html}
<hr style="margin: 3em 0 2em 0;">
```

# For the response memo

One exhibit built by this chapter answers the reviewers rather than documents the data. It is registered under
Section M: shown here with the numbers the memo will cite, and left out of the fragment. The memo's own document
sets it from this chapter's output directory.

## The exhibit files behind the 2001 start

The previous draft said that individual filing types are generally available only from 2000 onwards, which was
imprecise, and the reviewer found the three dates the paper names -- 1993, 1996 and 2001 -- inconsistent. They are
three different things: the master index lists filings from 1993; electronic filing became mandatory in 1996; and
exhibits became documents that can be retrieved on their own in mid-2000. `r oa_ref(.name = "ExhibitFiles")` is
the evidence for the third. EDGAR's index page lists an Exhibit 10 for every filing that carried one, back to the
first quarter shown, but a listed exhibit is a file of its own for `r oa_n(.key = "FilesShare1999Q4")` percent of
them in the last quarter of 1999, `r oa_n(.key = "FilesShare2000Q2")` percent in the second quarter of 2000 and
`r oa_n(.key = "FilesShare2000Q3")` percent from the third. Before that, the exhibit sits inside the complete
submission's text file and nothing else; the pipeline's links stage, which has no year bound, could retrieve
exactly the exhibits that were files, and those are the `r oa_n(.key = "DocsPre2001")` pre-2001 rows of the
release.

```{r}
#| label: float-exhibit-files
#| results: asis
oa_float(.name = "ExhibitFiles")
```

## The 2020-21 rise

The seasoned-filer figure that answers the reviewer's question about the pandemic is part of the appendix itself,
in Section A.3; the memo points there rather than carrying a copy.

# Validation

Two checks on the text itself. **Every registered exhibit is set exactly once, in the registry's order**: a registered
exhibit the text never sets would be listed as ready above and be absent from the paper, with nothing else to say so.
**The open markers are counted by section**, which is the chapter's progress report while it is being written.

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

The fragment is written only by the LaTeX pass. A terminal render, `quarto render 1_code/42-OnlineAppendix-A.qmd`,
runs both passes, html first; the Render button runs the html alone. Either way, the check below sees the fragment
as it stood before this render began.

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,        # the fragment as the last LaTeX pass left it
  .path_qmd     = .lP$Input$Qmd,         # a fragment older than this document or its library is stale
  .dir_exhibits = .lP$Input$DirExhibits  # and so is one older than what 30 wrote
)
```

To bring Overleaf up to date, one call from the console. It renders both passes in a separate R process, as a
terminal render would, checks that the fragment and the numbers file were written by this call, copies them and
this chapter's own exhibits to the paper folder, archives the ones they replace, and ends with the files that
changed -- the ones to upload.

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "42-OnlineAppendix-A.qmd"),                          # this document
  .path_tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-A.tex"),             # the LaTeX pass writes it
  .path_numbers = NULL,                                                                     # 40 deploys Numbers.tex
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),                     # tested for staleness
  .dir_own      = here::here("2_output", "40-Numbers", "Output"),                            # the exhibits 40 built
  .dir_deploy   = fs::path(                                                                 # the paper folder
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL                                                                      # found as a terminal would
)
```

Every chapter deploys to the same `OnlineAppendix/` folder: its fragment and its numbers file at the root, its own
exhibits under `Tables/`, `Notes/` and `Figures/`. On the Overleaf side, `9-online_appendix.tex` sets the lettered
numbering, points `\oaexhibits` at 30's `current/` and `\oaown` at this folder, inputs `Numbers.tex` (deployed by 40) in
the preamble, and inputs the fragments in order.

# Next

**42-OnlineAppendix-B** -- the two open-source packages, rGetEDGAR and rLabelDocs. The response memo's own document
sets the exhibit-files table built here from this chapter's output directory.

:::
