---
title: "Online Appendix C -- The Classification Approach (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  # THE RUNBOOK. Inherits everything _quarto.yml declares for html: toc, folded code, the stylesheet, one file.
  html: default
  # THE APPENDIX. A fragment for Overleaf rather than a document: the template is the body plus a few
  # \providecommand lines, and natbib turns every citation into \citet or \citep against the paper's own .bib.
  latex:
    template: _Templates/oa-body.tex
    cite-method: natbib
# Read by the html pass only; the LaTeX pass leaves the references to the paper's bibliography in Overleaf.
bibliography: _Templates/oa-references.bib
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing messages would
# discard the runbook's entire output. comment = "" removes the "##" prefix from console blocks so they can be copied
# verbatim. Figure geometry is NOT set here -- it is declared once in _quarto.yml.
#
# ECHO FOLLOWS THE FORMAT, the one option this document sets differently from the others. The html pass is the
# runbook and shows its code folded, like every runbook. The LaTeX pass is the appendix, where code would be typeset.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = "",
  echo     = !knitr::is_latex_output()
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

::: {.content-visible when-format="html"}

```{r}
#| label: load-libraries

# THE COMMONS, AND THE APPENDIX'S OWN. init_*() resolve this document's paths, tbl_say() is the fixed-width printer
# every report below uses, _Plots.R gives the figures built here the house theme, and _OnlineAppendix.R is the
# machinery every chapter of the appendix shares: numbers, floats, references, markers, the LaTeX pass, deployment.
# No upstream library is sourced: this document reads the files 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "42-OnlineAppendix-C"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
source(file = here::here("1_code", "40-Numbers.R"), encoding = "UTF-8") # the builders and the register loader
```

# Purpose

This document is Appendix C of the online appendix: how every contract of the corpus received its category and its
amendment flag. The transformer is the paper's classifier and takes most of the chapter -- the taxonomy and the
labelled sample it learned from, the sweep that selected it, its scores by category and where it errs. The keyword
table and the language model are described more briefly, as the two alternatives the paper measured on the same
folds; every engine then stands on one table, with the ceiling any combination of them could reach. The chapter
closes with what the release carries per contract and how the model's second choice relates to the annotators'
second label.

The conventions are those of every chapter of the appendix and are set out once, in the Purpose of
`42-OnlineAppendix-A`. Every table of this chapter is written here, in the appendix's own cut. Seven read the data
tibbles 30 wrote beside its own tables and print the same numbers with fewer columns, no fold uncertainty and
numbered categories -- 30 stays the manuscript's writer and is neither changed nor rerun. Two read other sources:
the descriptions filers give their contracts, from the release, and the second-label table, from 03B's out-of-fold
classification of the labelled sample.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict   = FALSE, # TRUE stops the render on an exhibit that is not built or a number that does not resolve
    FigWidth = 0.96,  # a figure's width as a share of the text width
    Rebuild  = FALSE, # TRUE rebuilds this chapter's own exhibits even where their inputs have not changed
    Titles   = 5L     # descriptions per category in the titles table, on one line each
  )
)

.lP$Input <- list(
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  DirData30   = here::here("2_output", "30-FinalExhibits", "Output", "Data"),  # the tibbles behind 30's tables
  Contracts   = fs::path(.lP$Root, "100_Data_Export", "Contracts.parquet"),     # the release, for the titles
  ClassFile   = here::here("2_output", "03B-ClassifyTrainBERT", "classification", # 03B's per-document output
                           "crowned_classification.parquet"),
  Template    = here::here("1_code", "_Templates", "oa-body.tex"),
  Bib         = here::here("1_code", "_Templates", "oa-references.bib"),
  Qmd         = here::here("1_code", "42-OnlineAppendix-C.qmd")
)

.lP$Input$Register <- here::here("2_output", "40-Numbers", "Output", "Numbers.csv") # every number, as 40 resolved it

.lP$Output <- list(
  Tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-C.tex"),
  DirOwn  = here::here("2_output", "40-Numbers", "Output"),
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix")
)

oa_state_reset()
```

```{r}
#| label: configure-floats
tab_floats <- tibble::tribble(
  ~Section, ~Name,              ~Kind,   ~Source, ~Caption,
  "C",      "ClassLabelled",    "table", "C",     "The labelled sample",
  "C",      "CategoryTitles",   "table", "C",     "What filers call their contracts, by category",
  "C",      "ClassDeployed",    "table", "C",     "The configurations that left the sweep",
  "C",      "ClassTransformer", "table", "C",     "The transformer by category, out of fold",
  "C",      "ClassConfusion",   "table", "C",     "Confusion matrix of the detailed transformer",
  "C",      "ClassAmendment",   "table", "C",     "The amendment classifier, out of fold",
  "C",      "ClassKeyword",     "table", "C",     "The keyword table by category, out of fold",
  "C",      "ClassArms",        "table", "C",     "Every engine on every task, and the ceiling",
  "C",      "ClassSecondPairs", "table", "C",     "Contracts with two labels: primary against second label",
  "C",      "ClassSecond",      "table", "C",     "The model's two choices on the contracts with two labels"
)

tab_sources <- tibble::tribble(
  ~Source, ~Dir,                            ~Macro,
  "30",    .lP$Input$DirExhibits,           "\\oaexhibits",
  "C",     as.character(.lP$Output$DirOwn), "\\oaown"
)

tab_static <- tibble::tibble(
  Name = character(0),
  File = character(0),
  Note = character(0)
)
```

# Input

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits,
  .template     = .lP$Input$Template,
  .bib          = .lP$Input$Bib
)
```

# Build

This chapter builds nothing. Every exhibit it sets -- 30's and its own -- is built by `40-Numbers`, which writes
them in 30's layout under its own output directory, the directory the sources table names as this chapter's.
A missing exhibit is therefore a render of 40 away, not of this document.

```{r}
#| label: configure-context
ctx_oa <- oa_context_set(
  .floats    = tab_floats,
  .static    = tab_static,
  .sources   = tab_sources,
  .own       = "C",
  .dir_doc   = fs::path_dir(.lP$Input$Qmd),
  .fig_width = .lP$Params$FigWidth,
  .strict    = .lP$Params$Strict,
  .long      = character(0)               # every table of the chapter fits a page
)

oa_report_floats(.files = ctx_oa$Files)
```

# Numbers

Every number the text cites is a key in 40's registry, resolved there over the tibble beside the exhibit that
prints it. This chapter loads the register 40 last wrote and cites through `oa_n()`, as before; a key it does not
hold aborts the render, and a key it holds but could not resolve prints as a marker and is listed under Validation.

```{r}
#| label: numbers-load
tab_numbers <- num_numbers_load(.path_register = .lP$Input$Register)

oa_report_numbers(
  .tab    = tab_numbers,       # as 40 resolved them
  .strict = .lP$Params$Strict  # TRUE stops the render on an unresolved number
)
```

# Sources

Every method claim in the chapter, with the runbook that is its source and the number or exhibit that carries it.
The sources here are the pipeline's own documents, so "verified" means read in the runbook's text or code; the
boxes in the text quote the code.

```{r}
#| label: sources-register
#| results: asis
tab_sources_c <- tibble::tribble(
  ~No, ~Claim, ~Source, ~Carried, ~Status,
  1L, "Twelve detailed categories in seven parents; amendment flag orthogonal",
      "03A-ClassifyPrepare, Purpose; the paper's categories table", "ClassLabelled", "verified",
  2L, "Two labelling rounds; second labels reviewed, primary deliberate; never used in training",
      "03A-ClassifyPrepare, Purpose (second labels, LabelRound)", "NSecond; ClassSecondPairs", "verified",
  3L, "Five folds dealt once, stratified on the detailed category; pooled out of fold; no holdout",
      "03A (folds frozen); 03B bert_predictions_best() docstring", "AccDetailed, F1Detailed", "verified",
  4L, "The grid and the two dropped levels; batch 32, seed 42",
      "03B-ClassifyTrainBERT, The grid", "SweepPerTask, SweepConfigs; ClassDeployed", "verified (code quoted)",
  5L, "Crowned by the highest mean out-of-fold macro-F1",
      "03B-ClassifyTrainBERT.R, bert_best_config()", "ClassDeployed", "verified (code quoted)",
  6L, "Leading configurations within a fold SD; context length does not separate; weighting helps rare classes",
      "03B-ClassifyTrainBERT, readings after the sweep", "ClassSweep (30's data)", "verified (text quoted)",
  7L, "Legal-BERT at 256 tokens ships for the detailed and the amendment task",
      "03B deploy chunk (crowned_classification); 30's ClassSweep Crown/Deployed", "ClassDeployed", "check on render",
  8L, "Lenient scoring against the second label",
      "03B / 30 scoring (RecallLenient)", "LenientDetailed", "verified",
  9L, "Keyword table: Wilson lower bound, target precision, base-rate and marginal-reach guards, fold agreement",
      "03C-ClassifyTrainKeyword, Configuration and Purpose", "KwCoverage, KwAccCommitted", "verified (code quoted)",
  10L, "LLM arm: Qwen3 8B, zero and few shot, prompts from complement folds, written blind",
      "03D-ClassifyLLM, Configuration and Purpose", "AccLlm, F1Llm", "verified (code quoted)",
  11L, "Routing ceiling needs the true label; the gap over the transformer is small",
      "03E-ClassifyOrchestrate, Purpose, step 2", "AccBert, AccCeiling", "verified",
  12L, "The release carries top-2 with probabilities, the keyword label, the broad roll-up",
      "03F-ClassifyApply, Purpose", "(release columns)", "check the column names on the release"
)
rows_ <- paste0("| ", tab_sources_c$No, " | ", tab_sources_c$Claim, " | ", tab_sources_c$Source, " | ",
                tab_sources_c$Carried, " | ", tab_sources_c$Status, " |")
cat(paste(c("", "| No | Claim | Source | Carried by | Status |", "|---:|---|---|---|---|", rows_, ""),
          collapse = "\n"))
```

<details class="oa-authors">
<summary><strong>Note for the authors:</strong> Section 3.2 of the manuscript still describes the first submission's classifier</summary>

Every quantitative statement in 3.2 differs from this chapter: ten categories against twelve; 4,327 contracts
split 70/15/15 against 4,398 in five folds; BERT-base against RoBERTa as the comparison encoder; 512 tokens
against 256; a hand-picked list of ten keywords per category against a mined table with abstention; 93.4% and
94.7% test accuracy against out-of-fold accuracy and macro-F1; 90.9% on 54.0% against 0.919 on 52.3%. The LLM
arm, the ceiling and the second labels are absent from 3.2. The rewrite of 3.2 (41-Methods) cites the same keys through
`Numbers.tex`, so the two cannot drift again. The list is in `claude_31-OA-Structure.md`.

</details>

:::

::: {.content-visible when-format="html"}

# Appendix C

:::

```{=latex}
\clearpage
```

## Classification approach {#sec-oa-c}

We classify each contract in our database into one of the twelve categories of
`r oa_ref_main(.name = "Categories", .kind = "table")`, into its broad category among the seven, and as an original
agreement or an amendment. A fine-tuned transformer assigns these labels. This appendix describes the labeled sample
the model learned from (C.1), how we selected the model and how well it performs (C.2), the two alternatives we
evaluated on the same folds -- a keyword table (C.3) and a large language model (C.4) -- what all of them reach
together and what no combination could exceed (C.5), and which classification variables our database provides for
every contract (C.6).

### Taxonomy and labeled sample {#sec-oa-c-sample}

The twelve detailed categories nest in seven broad categories, so the broad label is a roll-up of the detailed one
and the two never contradict each other; the amendment flag is orthogonal to both, and an amendment carries the
category of the agreement it amends. A contract's category follows from its primary obligation, and four boundaries
matter most. A contract for the purchase or sale of tangible or intangible assets is Assets, unless the assets are
inventory or operational services, which make it Customer / Supplier: selling a plant is Assets, supplying from it
is Customer / Supplier. Research and development agreements, with the consulting attached to them, form a category of
their own within Purchases and Sales. M&A covers the business combination and the agreements that stem from it, such
as tax-matters agreements, while collaborations that leave the firms separate -- joint ventures, alliances,
co-development -- are Peer Agreements. Employment splits into compensation plans and the employment relationship
itself: offer letters, severance, non-competition and change-in-control agreements.

Our labeled sample holds `r oa_n(.key = "NLabelled")` contracts with readable text
(`r oa_ref(.name = "ClassLabelled")`), of which `r oa_n(.key = "NAmended")` are amendments. We labeled them with
rLabelDocs (Appendix B.3) in two rounds: a first round in which contracts labeled under an earlier scheme were mapped
to the current categories, and a second round of direct labeling aimed at the categories the mapping could not fill.
Where a contract fits two categories, the annotators recorded a second label, which is the case for
`r oa_n(.key = "NSecond")` contracts; we reviewed every such contract and recorded the intended primary label, so
the order of the two labels is deliberate. We train on the primary label only. The second label serves to score
leniently and, in Section C.6, to read the model's second choice.

```{r}
#| label: float-class-labelled
#| results: asis
oa_float(.name = "ClassLabelled")
```

`r oa_ref(.name = "CategoryTitles")` shows, for each category, the five descriptions filers most often give their
contracts. The description is the filer's own free text and the only human-written label a contract carries, so it
is the most direct view of what a category holds -- and, unlike an example contract, it is a count rather than a
choice. Filers supply a description beyond the exhibit number for `r oa_n(.key = "TitlesNamed")` percent of
contracts; for the rest, the exhibit number is all they write. The descriptions show what the boundaries above look
like from the filer's side: stock purchase agreements and plans of merger under M&A, purchase agreements and asset
purchase agreements under Assets, supply and distribution agreements under Customer / Supplier, and research and
collaboration agreements under R&D.

```{r}
#| label: float-category-titles
#| results: asis
oa_float(.name = "CategoryTitles")
```

### The transformer: selection and performance {#sec-oa-c-transformer}

We score every approach in this appendix the same way. We draw five folds once, stratified on the detailed
category, and predict each contract once, with the fold model that did not see it in training; the scores pool these
out-of-fold predictions. We hold out no test set beyond the folds: with `r oa_n(.key = "NRarest")` contracts in the
smallest category, a further holdout would leave too few to estimate that category's performance, and the
cross-validated score is a conservative estimate for the deployed model, which we train on the full sample. Our
headline metric is macro-F1, the unweighted mean of the per-category F1 scores, because accuracy is dominated by the
three largest categories, which hold close to half of the sample; we report accuracy beside it. A lenient score
counts a prediction as correct where it equals the contract's second label, so the gap between the strict and the
lenient score measures ambiguity in the taxonomy rather than error in the model.

We fine-tune two encoders: Legal-BERT [@chalkidis2020legal], pre-trained on legal text, and RoBERTa
[@liu2019roberta], pre-trained on general text. Our grid crosses them with two learning rates (2e-5 and 3e-5), two
context lengths (256 and 512 tokens read from the start of the contract), two training budgets (three and six
epochs), and loss weighting by inverse class frequency or none, separately for each task; we also tried a learning
rate of 1e-5 and ten epochs against the center of the grid, neither of which improved on it, and dropped them rather
than carrying them through the whole factorial. We hold batch size (32) and the seed (42) fixed. This leaves
`r oa_n(.key = "SweepPerTask")` configurations per task, `r oa_n(.key = "SweepConfigs")` across the category and the
amendment task, each estimated on the five folds, so that the effect of each axis -- encoder, context length,
epochs, weighting -- reads as a like-for-like comparison; the `r oa_n(.key = "SweepChecks")` runs at the dropped
levels stay in the leaderboard as the evidence for dropping them. We select the configuration with the highest mean
out-of-fold macro-F1 per task and refit it on the full labeled sample; the leading configurations sit within a
fold-level standard deviation of one another, so the selection is between near-equals.
`r oa_ref(.name = "ClassDeployed")` lists the configurations that left the sweep. For the contract category
classification and the amendment classification alike, the model that labels our database is Legal-BERT reading the
first 256 tokens; we deploy the longer context beside it, and Section C.5 reports what it buys.

```{r}
#| label: float-class-deployed
#| results: asis
oa_float(.name = "ClassDeployed")
```

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 03B-ClassifyTrainBERT, "The grid" (the sweep as configured in code)</summary>

The full crossing, and the two levels dropped after a centre check, as the runbook declares them:

```r
grid_full <- tidyr::expand_grid(
  model         = c("nlpaueb/legal-bert-base-uncased", "roberta-base"),   # legal-domain vs general encoder
  label_col     = c("ClassDetailed", "ClassBroad", "AmendType"),          # the three tasks
  lr            = c(1e-5, 2e-5, 3e-5),                                    # learning rate
  max_len       = c(256L, 512L),                                          # tokens read per document
  epochs        = c(3, 6, 10),                                            # passes over the training data
  class_weights = c(FALSE, TRUE),                                         # inverse-frequency loss weighting
  fold          = 1:5                                                     # cross-validation folds from 03A
)

grid_all <- grid_full |>
  dplyr::filter(epochs != 10, lr != 1e-5)
```

> [Two levels are dropped rather than estimated everywhere. Ten epochs and a learning rate of 1e-5 were each
> evaluated against the centre configuration and neither improved on six epochs at 2e-5; carrying them through
> the whole factorial would roughly double the sweep in order to re-answer a question already settled. Every
> remaining combination is estimated.]{.mark}

The sweep call holds `.batch_size = 32L` and `.seed = 42L` fixed ("held fixed across the study; not a swept
axis"). The runbook's reading of the completed sweep: "Differences between the leading configurations are smaller
than the spread across folds within any one of them"; on class weighting, "Weighting the loss by inverse class
frequency improves macro-F1 by a margin that is small but consistent across folds. The effect is concentrated in
the rarest categories."

</details>

:::

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 03B-ClassifyTrainBERT.R, bert_best_config() (the crowning rule)</summary>

> Thin wrapper over clf_leaderboard() that returns only the winning ConfigName. [...] @return Character scalar:
> [the ConfigName ranked first by mean macro-F1.]{.mark}

```r
bert_best_config <- function(.tab_overall, .label_col = "ClassDetailed") {
  .tab_overall |>
    dplyr::filter(.data$LabelCol == .label_col) |>
    clf_leaderboard() |>
    dplyr::slice(1) |>
    dplyr::pull(.data$ConfigName)
}
```

And the pooling rule, from the function that follows it: "Each document is predicted exactly once, by the fold
model that did not see it in training."

</details>

:::


Out of fold, the contract category classification reaches an accuracy of `r oa_n(.key = "AccDetailed")` and a
macro-F1 of `r oa_n(.key = "F1Detailed")` (`r oa_ref(.name = "ClassTransformer")`); scored leniently, its accuracy
rises to `r oa_n(.key = "LenientDetailed")`, so the second labels explain few of its errors. The remaining errors
concentrate in adjacent categories (`r oa_ref(.name = "ClassConfusion")`): between the two employment categories,
between credit and equity instruments, and among the purchase-and-sale categories whose boundaries Section C.1
draws -- the pairs on which the annotators, too, most often recorded a second label. The amendment classification
reaches an accuracy of `r oa_n(.key = "AccAmend")` and a macro-F1 of `r oa_n(.key = "F1Amend")`
(`r oa_ref(.name = "ClassAmendment")`). The broad category we publish is the roll-up of the detailed prediction; we
deploy a classifier trained on the seven broad categories directly as a consistency check, not as the source of the
label.

```{r}
#| label: float-class-transformer
#| results: asis
oa_float(.name = "ClassTransformer")
```

```{r}
#| label: float-class-confusion
#| results: asis
oa_float(.name = "ClassConfusion")
```

```{r}
#| label: float-class-amendment
#| results: asis
oa_float(.name = "ClassAmendment")
```

### The keyword table {#sec-oa-c-keyword}

The keyword table is a published artifact rather than a competing classifier: a short, ranked table of terms per
category that anyone can apply to a filing with a text editor and no model, each term with a stated precision. A
term's evidence is the Wilson lower bound on its precision in training [@wilson1927probable], which ranks a term
found in 190 of 200 contracts above one found in 2 of 2. A term enters the table only where its precision exceeds
the category's base rate, where it catches contracts that no accepted term caught, and where the fold-wise mines
agree on it; a contract receives the category of the strongest term it contains, and the table abstains where no
term fires. A table that abstains is judged on two numbers rather than one. Out of fold, the keyword table classifies
`r oa_n(.key = "KwCoverage")` percent of contracts, with an accuracy of `r oa_n(.key = "KwAccCommitted")` where it
does (`r oa_ref(.name = "ClassKeyword")`). Coverage is uneven: credit agreements and leases are named by their
terms and the table covers most of them, while the two thinnest categories, research agreements and peer agreements,
have no term precise enough to enter the table at all, so it never assigns them and their precision is undefined. We
publish the table itself with our database.

```{r}
#| label: float-class-keyword
#| results: asis
oa_float(.name = "ClassKeyword")
```

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 03C-ClassifyTrainKeyword, Configuration (the keyword table's admission thresholds)</summary>

```r
TargetPrecision = c(ClassDetailed = 0.95, ClassBroad = 0.95, AmendType = 0.85),
MinClasses      = c(ClassDetailed = 9L, ClassBroad = 5L, AmendType = 2L),
Tolerance       = 0.01, # precision band treated as indistinguishable; roughly two SEs here
MinFolds        = 3L,   # fold agreement required of a published term
```

The runbook mines the filer's own description of the contract as one arm and the text at 256 and 512 words as
the like-for-like comparison with the transformer; it judges mines "on the terms they produce, not on the
accuracy column". The Wilson lower bound and the base-rate and marginal-reach guards are the admission rules of
the library (kw_*); the released table is the one the catalogue marks as default.

</details>

:::


### The language model {#sec-oa-c-llm}

A reader will ask why a fine-tuned encoder was necessary when an open-weight instruction model can be handed a
contract and asked what it is. The answer is a number on the same folds. We prompt a local model, Qwen3 with eight
billion parameters [@qwen2025qwen3], to classify each contract from its opening text, with the category names and
definitions alone or with worked examples drawn from the other folds, so that no prompt contains a contract from the
fold it scores; we wrote the prompts from the taxonomy without sight of any prediction or labeled contract, so that
the comparison is not fitted to the transformer's errors. The model runs offline and its results reproduce. On the
contract category classification it reaches an accuracy of `r oa_n(.key = "AccLlm")` and a macro-F1 of
`r oa_n(.key = "F1Llm")`, well below the fine-tuned transformer, at a cost per contract several orders of magnitude
above it.

::: {.content-visible when-format="html"}

<details class="oa-source">
<summary><strong>Source:</strong> 03D-ClassifyLLM, Configuration (the language-model arm)</summary>

```r
Models = "qwen3:8b",
```

> [qwen3:32b is installed on this machine and deliberately not swept]{.mark} [...]

Prompts are the category list with definitions, plus categories-times-shots worked examples drawn from the
complement folds, so that no prompt contains a contract of the fold it scores; the zero-shot prompt shows no
labelled example. The runbook notes that a four-shot prompt over twelve categories is several thousand tokens,
which is why the arm is measured on the labelled sample rather than run over the corpus.

</details>

:::

### Every approach on one table, and the ceiling {#sec-oa-c-arms}

`r oa_ref(.name = "ClassArms")` puts the three approaches on every task, with the transformer at both context
lengths. We read two things from it. The longer context does not separate itself from the shorter one on any task,
which is why we deploy the shorter, cheaper one. And the last row is the ceiling: the accuracy that perfect routing
would reach -- for every contract, whichever approach is right -- which requires the true label and therefore cannot
be run, but bounds what any rule for combining the approaches could achieve. The transformer alone reaches an
accuracy of `r oa_n(.key = "AccBert")` on the contract category classification; the ceiling over all approaches is
`r oa_n(.key = "AccCeiling")`. The gap is what the other approaches know that the transformer does not, and it is
small: on the contracts the transformer gets wrong, the keyword table mostly abstains and the language model is
mostly wrong too. We therefore publish the transformer's label and the keyword label as an independent second
opinion, and no combination of them.

```{r}
#| label: float-class-arms
#| results: asis
oa_float(.name = "ClassArms")
```

### Classification variables in the database {#sec-oa-c-apply}

The classifier labels every Exhibit 10 attachment once, reading its primary copy, and our database carries the label
on every registrant copy. For each contract, the database holds the most likely and the second most likely category,
each with its probability, for the contract category classification and the amendment classification, the broad
category as the roll-up of the detailed one, and, where a term of the keyword table fires, the table's category and
the term. Each contract thus receives one label, and a contract that combines several agreements -- a merger
agreement with employment terms, a license with a supply obligation -- is labeled by its primary obligation, with
the second probability as the reading of how mixed it is.

The `r oa_n(.key = "SecondDocs")` labeled contracts that carry a second label show where that happens.
`r oa_ref(.name = "ClassSecondPairs")` sets their primary label against their second: the pairs concentrate on the
boundaries Section C.1 draws -- research agreements against customer-supplier and license agreements, asset
purchases against customer-supplier agreements -- and hardly occur elsewhere. `r oa_ref(.name = "ClassSecond")`
then asks whether the model's two choices are the annotators' two labels. On these contracts the model's first
choice is the primary label in `r oa_n(.key = "SecondHit1")` percent of cases and its runner-up the second label in
`r oa_n(.key = "SecondHit2")` percent, both in `r oa_n(.key = "SecondBoth")` percent. The model is also less sure
on them than on the rest: the margin between its first and second choice averages `r oa_n(.key = "MarginDual")` on
contracts with two labels against `r oa_n(.key = "MarginSingle")` on contracts with one. A high second probability
in our database therefore marks a contract the annotators would also have read as mixed, and an analysis of mixed
contracts can select on it.

```{r}
#| label: float-class-second-pairs
#| results: asis
oa_float(.name = "ClassSecondPairs")
```

```{r}
#| label: float-class-second
#| results: asis
oa_float(.name = "ClassSecond")
```

::: {.content-visible when-format="html"}

# Validation

```{r}
#| label: validate-floats
tab_emitted <- oa_report_emitted(.strict = .lP$Params$Strict)
```

```{r}
#| label: validate-markers
tab_markers <- oa_markers(.path_qmd = .lP$Input$Qmd)

oa_report_markers(.tab = tab_markers)
```

# Deployment

```{r}
#| label: deploy-status
oa_report_tex(
  .path_tex     = .lP$Output$Tex,
  .path_qmd     = .lP$Input$Qmd,
  .dir_exhibits = .lP$Input$DirExhibits
)
```

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")

oa_publish(
  .path_qmd     = here::here("1_code", "42-OnlineAppendix-C.qmd"),
  .path_tex     = here::here("_rendered", "1_code", "42-OnlineAppendix-C.tex"),
  .path_numbers = NULL,                                                                     # 40 deploys Numbers.tex
  .dir_exhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  .dir_own      = here::here("2_output", "40-Numbers", "Output"),                            # the exhibits 40 built
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  ),
  .quarto       = NULL
)
```

# Next

**42-OnlineAppendix-D** -- named entity recognition and the rule set.

:::
