---
title: "Numbers -- every number the paper and the online appendix cite (40)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  html: default
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr. comment = "" removes the "##"
# prefix from console blocks so they can be copied verbatim.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

```{r}
#| label: load-libraries

# THE COMMONS, AND THIS PAIR'S OWN. _OnlineAppendix.R holds the number machinery -- one row of the registry
# resolved over the tibble beside the exhibit that prints it -- and this document is the one place that machinery
# runs. 30's library is not sourced: this document reads the tibbles 30 wrote and calls none of its functions.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables", "_Plots", "_OnlineAppendix"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "50-Numbers"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every number the manuscript and the online appendix cite is resolved here, once, and written as one LaTeX file the
Overleaf project inputs. A number is a row of the registry below: the tibble it is read from, the column, the rows,
how several rows reduce to one value, how it is printed, the section of the paper it appears in, and one line saying
what it is. The tibbles are the ones the exhibits are printed from, 30's under `30-FinalExhibits/Output/Data`, plus
the data package's report read here, so a sentence and the table beside it cannot disagree.

## Why one file

Until now each appendix chapter wrote its own numbers file and the manuscript typed its numbers. Typed copies stop
being true at the next re-export and nothing reports it; the introduction and Section 4 of the revision disagreed
on the size of the sample, the Compustat match and the share of 8-K filings for exactly that reason. With one
registry a key is unique across the paper, cited as `\pnum{Key}` in the manuscript and `\oanum{Key}` in the
appendix, and both names read the same table.

## What is written

Three files under this document's `Output/`, on every render: `Numbers.tex`, the file Overleaf inputs;
`Numbers.csv`, the same numbers as a register with their source and note, readable without compiling anything;
and `Numbers-unresolved.txt`, the keys that did not resolve and why, empty when all did. `num_deploy()` copies the
first to the paper folder beside the appendix fragments and says whether Overleaf needs a new upload.

## What is not here

Prose and exhibits. The manuscript and the online appendix live in Overleaf and cite keys; every exhibit and the
tibble behind it is 30's. The regression numbers of Sections 5 and 6 are not in the registry yet; when they come,
they come from the release through 30, not as typed values.

# Configuration

```{r}
#| label: configure
.lP <- list(
  Root   = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
  Params = list(
    Strict     = FALSE, # TRUE stops the render on a number that does not resolve or a citation without a key
    Rebuild    = FALSE  # TRUE rebuilds this pair's own tibble even where its inputs have not changed
  )
)

.lP$Input <- list(
  Lib         = here::here("1_code", "50-Numbers.R"),                   # a changed builder rebuilds
  # 30'S OUTPUT, read in place: Data/ for the tibbles its exhibits print from, which is where every registry row
  # but chapter F's resolves.
  DirExhibits = here::here("2_output", "30-FinalExhibits", "Output"),
  # 40B'S REPORT on the data package it published: chapter F's one input.
  Package     = here::here("2_output", "40B-PublishData", "Stage", "sample", "package_numbers.csv"),
  # THE DATA DIRECTORIES, in search order: 30's, then this pair's own (PackageNumbers).
  DirData     = c(
    here::here("2_output", "30-FinalExhibits", "Output", "Data"),
    here::here("2_output", "50-Numbers", "Output", "Data")
  ),
  # THE FILES THAT CITE KEYS, scanned under Validation: the manuscript's and the appendix's .tex files as exported
  # from Overleaf (a folder of .tex, optional).
  DirManuscript = fs::path(.lP$Root, "200-Paper_figures", "Manuscript")
)

.lP$Output <- list(
  DirOwn  = fs::path(.dir_main, "Output"),                            # Data/ for the tibbles built here
  Numbers = fs::path(.dir_main, "Output", "Numbers.tex"),             # the file Overleaf inputs
  Deploy  = fs::path(.lP$Root, "200-Paper_figures", "OnlineAppendix") # beside the appendix fragments
)

# THE SECTIONS OF THE REGISTER, in print order: the manuscript's sections first, then the appendix chapters. A key
# is filed under the first section that cites it.
.num_sections <- c("Intro", "3.1", "3.2", "3.3", "3.4", "4.1", "OA-A", "OA-B", "OA-C", "OA-D", "OA-F")

oa_state_reset()
```

# Input

30 is the input: every tibble its exhibits print from, under its `Output/Data`, is what the registry resolves
over. The one file 30 does not hold is 40B's report on the data package, read under Build.

```{r}
#| label: input-check
oa_report_inputs(
  .dir_exhibits = .lP$Input$DirExhibits,                               # 30's output, read in place
  .template     = here::here("1_code", "_Templates", "oa-body.tex"),   # the chapters' template, checked once here
  .bib          = here::here("1_code", "_Templates", "oa-references.bib")
)
```

# Build

One tibble is built here: the data package's numbers, read from the report 40B writes beside the staged sample.
Everything else the registry names is 30's, built when 30 renders. The build compares its output with its input and
with this library, and runs only where the output is missing or older; `Rebuild` forces it.

```{r}
#| label: build-appendix-f
# CHAPTER F reads what 40B reported about the package it published: the package must exist for the appendix to
# describe it, so a missing report stops here.
st_f <- c(
  PackageNumbers = oaf_build_package(
    .path_numbers = .lP$Input$Package,    # 40B's package_numbers.csv, beside the staged sample
    .dir_own      = .lP$Output$DirOwn,
    .force        = .lP$Params$Rebuild,
    .path_lib     = .lP$Input$Lib
  )
)

oa_report_builds(.status = st_f)
```

# The registry

One row per number. `Where` is a filter over the tibble's own columns, evaluated as written; `Fun` reduces the
matching rows to one value, and `one` demands exactly one matching row, which is what catches a filter that silently
matches two. `Column` names a column, or an expression over the tibble's columns where the text needs a share the
tibble holds as two counts. `Section` is where the number first appears in the paper; `Note` is what it is.

The rows are grouped by the section of the paper: the manuscript's sections first, then the appendix chapters.

```{r}
#| label: registry-manuscript
# FILTER HELPERS, named once. The linkage funnel holds one row per step; Code is the release's LinkStatus prefix.
.where_step <- \(.c) paste0("Code == '", .c, "'")
.where_form <- \(.f) paste0("FormFamily == '", .f, "'")
.where_amd  <- \(.f) paste0("FormFamily == '", .f, "' & Amend == 'Amended'")
.where_ahci <- "Row == '10-K, 10-Q and 8-K' & Period != 'all years' & Kind == 'granting-new'"
# THE LADDER (Table 2) holds one row per rung and panel; exclusions are negative, so a count is abs() and a level
# is the sum of the rows down to it.
.where_a   <- \(.r) paste0("Panel == 'Panel A: Unique contracts' & Row == '", .r, "'")
.where_b   <- \(.r) paste0("Panel == 'Panel B: Estimation samples' & Row == '", .r, "'")
.where_b_k <- "Panel == 'Panel B: Estimation samples' & Kind == 'firm'"
.rows_uni  <- "Panel == 'Panel A: Unique contracts' & Row %in% c('Full sample', 'Multiple filer')"
.rows_cs   <- paste0("Panel == 'Panel B: Estimation samples' & ",
                     "Row %in% c('Full sample', 'Malformatted documents', 'Missing Compustat match')")

spec_manuscript <- tibble::tribble(
  ~Key,                        ~Section, ~Exhibit,        ~Column,      ~Fun,  ~Format, ~Where,
  ~Note,
  # 3.1 -- what is downloaded
  "DocsAll",                   "3.1",    "SampleSelection", "Contracts", "one", "count", .where_a(.r = "Full sample"),
  "Exhibit 10 attachments 2001-2024, every registrant copy counted: Table 2's first line",
  "Docs8K",                    "3.1",    "SummarySample", "All",        "one", "count",
  "Rung == 'Item 1.01 announcements recovered'",
  "8-K filings from which an Item 1.01 narrative was recovered",
  "Orders",                    "3.1",    "CtoLinkage",    "N",          "one", "count", "Step == 'Orders in the release'",
  "Confidential treatment orders on EDGAR, 2008 onwards, whatever their status",
  # 3.4 -- orders and their linkage
  "OrderRefs",                 "3.4",    "CtoLinkage",    "N",          "one", "count",
  "Step == 'References to exhibits they make'",
  "Exhibit references the orders make; one order names one or several exhibits",
  "OrderRefsLinked",           "3.4",    "CtoLinkage",    "N",          "one", "count", .where_step(.c = "A-linked"),
  "References that reach an attachment in the register",
  "DocsWithCto",               "3.4",    "CtoLinkage",    "N",          "one", "count", "Kind == 'result'",
  "Unique contracts covered by at least one granted order",
  "OrdersAhci",                "3.4",    "CtoAhci",       "Orders",     "one", "count", .where_ahci,
  "New grants through 2019 whose references name a 10-K, 10-Q or 8-K: the comparison with Ahci (2025)",
  "OrderRefsAhci",             "3.4",    "CtoAhci",       "References", "one", "count", .where_ahci,
  "Exhibit references of those orders",
  "CtoMarkerAgree",            "3.4",    "CtoMarkers",    "Share",      "one", "pct1",
  "Row == 'Share of ordered contracts with a marker'",
  "Share of CTO-covered unique contracts of 2008-2018 that also carry a bracketed redaction marker",
  "MarkerCtoAgree",            "3.4",    "CtoMarkers",    "Share",      "one", "pct1",
  "Row == 'Share of marked contracts with an order'",
  "Share of marked unique contracts of 2008-2018 that are covered by an order",
  # 3.4 -- announcements
  "AnnouncementsNoDate",       "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'No agreement date read in the narrative'",
  "8-Ks whose narrative names no agreement date, dropped before the single-agreement test",
  "AnnouncementsMultiSummary", "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'Two or more agreement dates'",
  "8-Ks dropped because the narrative opens with two or more agreement dates",
  "AnnouncementsMultiExhibit", "3.4",    "SummarySample", "abs(All)",   "one", "count",
  "Rung == 'More than one Exhibit 10 on the 8-K'",
  "8-Ks dropped because more than one Exhibit 10 rides on them",
  "Announcements",             "3.4",    "SummarySample", "All",        "one", "count", "Rung == 'Announcement sample'",
  "Single-agreement Item 1.01 announcements on 8-Ks with at most one Exhibit 10: the paper's sample",
  # 4.1 -- filing types and the ladder, as chapter A defines them
  "Share8K",                   "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "8-K"),
  "Share of unique contracts filed with an 8-K, percent",
  "Share10K",                  "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "10-K"),
  "Share filed with a 10-K, percent",
  "Share10Q",                  "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "10-Q"),
  "Share filed with a 10-Q, percent",
  "ShareS1",                   "4.1",    "FilingTypes",   "Share",      "max", "pct1",  .where_form(.f = "S-1"),
  "Share filed with an S-1, percent",
  "FirmsAll",                  "4.1",    "SampleSelection", "Firms",     "one", "count", .where_a(.r = "Full sample"),
  "Firms (CIKs) in the full sample",
  "DocsFlagged",               "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_a(.r = "Malformatted documents"),
  "Attachments excluded as malformatted (three text rules and PDF/image placeholders), all copies",
  "DocsCopies",                "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_a(.r = "Multiple filer"),
  "Additional registrant copies of an attachment filed under several CIKs",
  "DocsUnique",                "4.1",    "SampleSelection", "Contracts", "sum", "count", .rows_uni,
  "Distinct attachments 2001-2024: the full sample less the registrant copies",
  "DocsSample",                "4.1",    "SampleSelection", "Contracts", "one", "count", .where_a(.r = "Unique contracts"),
  "Unique contracts with readable text: the descriptive sample",
  "FirmsSample",               "4.1",    "SampleSelection", "Firms",     "one", "count", .where_a(.r = "Unique contracts"),
  "Firms with at least one unique contract",
  "DocsNoCompustat",           "4.1",    "SampleSelection", "abs(Contracts)", "one", "count",
  .where_b(.r = "Missing Compustat match"),
  "Contracts without a Compustat match in their filing quarter",
  "DocsCompustat",             "4.1",    "SampleSelection", "Contracts", "sum", "count", .rows_cs,
  "Contracts merged to quarterly Compustat: the full sample less malformatted and unmatched",
  "DocsEstimation",            "4.1",    "SampleSelection", "Contracts", "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Contract-level estimation sample",
  "QuartersEstimation",        "4.1",    "SampleSelection", "Quarters",  "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Firm-quarters in the contract-level sample",
  "FirmsEstimation",           "4.1",    "SampleSelection", "Firms",     "one", "count",
  .where_b(.r = "Contract-level sample"),
  "Firms in the contract-level sample",
  "DocsEstimation2008",        "4.1",    "SampleSelection", "Contracts", "one", "count", .where_b(.r = "from 2008"),
  "Contract-level sample from 2008",
  "QuartersFirmLevel",         "4.1",    "SampleSelection", "Quarters",  "one", "count", .where_b_k,
  "Firm-quarters in the firm-level sample, non-filing quarters included",
  "FirmsFirmLevel",            "4.1",    "SampleSelection", "Firms",     "one", "count", .where_b_k,
  "Firms in the firm-level sample"
)

```

```{r}
#| label: registry-appendix-a
# CHAPTER A's rows, as its specification had them, less the keys the manuscript now owns.
.where_reg <- "Group %in% c('Exchange Act registrations', 'Real-estate registrations')"
.where_out <- "Panel == 'Outside it' & Kind == 'total'"
.where_in  <- "Panel == 'In the database' & Kind == 'total'"
.where_all      <- \(.y) paste0("Filers == 'All filers' & Year == ", .y)
.where_seasoned <- \(.y) paste0("Filers == 'Seasoned filers' & Year == ", .y)
.where_group    <- \(.g, .y) paste0("grepl('", .g, "', Filers) & Year == ", .y)

spec_a <- tibble::tribble(
  ~Key,                 ~Exhibit,         ~Column,       ~Fun,  ~Format, ~Where,
  "DocsRelease",        "TextCounts",     "Value",       "one", "count", "Key == 'DocsAll'",
  "DocsReleaseUnique",  "TextCounts",     "Value",       "one", "count", "Key == 'DocsUnique'",
  "DocsReleaseFlagged", "TextCounts",     "Value",       "one", "count", "Key == 'DocsFlagged'",
  "DocsPre2001",        "TextCounts",     "Value",       "one", "count", "Key == 'DocsPre2001'",
  "RowsPre2001",        "TextCounts",     "Value",       "one", "count", "Key == 'RowsPre2001'",
  "RowsFlagged",        "TextCounts",     "Value",       "one", "count", "Key == 'RowsFlagged'",
  "DocsSample2008",     "TextCounts",     "Value",       "one", "count", "Key == 'DocsSample2008'",
  "NSeasonedAll",       "SeasonedFilers", "N",           "sum", "count", "Filers == 'Seasoned filers'",
  "CovInside",          "FormCoverage",   "Filings",     "one", "count", .where_in,
  "CovSmallBusiness",   "FormCoverage",   "Filings",     "sum", "count", "grepl('Small business', Group)",
  "CovTenKVariants",    "FormCoverage",   "Filings",     "one", "count", "Group == '10-K variants'",
  "CovRegistrations",   "FormCoverage",   "Filings",     "sum", "count", .where_reg,
  "Cov20FFilings",      "FormCoverage",   "Filings",     "one", "count", "Group == 'Foreign annual reports'",
  "Cov20FContracts",    "FormCoverage",   "Contracts",   "one", "count", "Group == 'Foreign annual reports'",
  "CovOutside",         "FormCoverage",   "Filings",     "one", "count", .where_out,
  "FilesShare2000Q2",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '2000 Q2'",
  "FilesShare2000Q3",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '2000 Q3'",
  "FilesShare1999Q4",   "ExhibitFiles",   "ShareFile",   "one", "pct1",  "Quarter == '1999 Q4'",
  "ShareForeign",       "FilingTypes",    "N / sum(N)",  "sum", "pct1",  "Region == 'Foreign filings'",
  "Amend8K",            "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "8-K"),
  "Amend10K",           "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "10-K"),
  "Amend10Q",           "FilingTypes",    "N / NForm",   "one", "pct1",  .where_amd(.f = "10-Q"),
  "RuleShort",          "TextCounts",     "Value",       "one", "count", "Key == 'RuleShort'",
  "RuleStopwords",      "TextCounts",     "Value",       "one", "count", "Key == 'RuleStopwords'",
  "RuleNumeric",        "TextCounts",     "Value",       "one", "count", "Key == 'RuleNumeric'",
  "Placeholders",       "TextCounts",     "Value",       "one", "count", "Key == 'Placeholders'",
  "OrderRefsNotEx10",   "CtoLinkage",     "N",           "one", "count", .where_step(.c = "2-"),
  "OrderRefsFrame",     "CtoLinkage",     "N",           "one", "count", .where_step(.c = "6-"),
  "OrderRefsMissing",   "CtoLinkage",     "N",           "one", "count", .where_step(.c = "9-"),
  "LinkedExtensions",   "CtoLinkage",     "N",           "one", "count", "Step == 'Extends an earlier grant'",
  "LinkedDenials",      "CtoLinkage",     "N",           "one", "count", "grepl('^Denies', Step)",
  "NAll2020",           "SeasonedFilers", "N",           "one", "count", .where_all(.y = 2020),
  "NAll2021",           "SeasonedFilers", "N",           "one", "count", .where_all(.y = 2021),
  "NSeasoned2020",      "SeasonedFilers", "N",           "one", "count", .where_seasoned(.y = 2020),
  "NSeasoned2021",      "SeasonedFilers", "N",           "one", "count", .where_seasoned(.y = 2021),
  "RegAll2021",         "SeasonedFilers", "ShareReg",    "one", "pct1",  .where_all(.y = 2021),
  "RegSeasoned2021",    "SeasonedFilers", "ShareReg",    "one", "pct1",  .where_seasoned(.y = 2021),
  "EqAll2021",          "SeasonedFilers", "ShareEquity", "one", "pct1",  .where_all(.y = 2021),
  "EqSeasoned2021",     "SeasonedFilers", "ShareEquity", "one", "pct1",  .where_seasoned(.y = 2021),
  "NBlankCheck2021",    "SeasonedFilers", "N",           "one", "count", .where_group(.g = "Blank-check", .y = 2021),
  "NSeasonedEdgar2021", "SeasonedFilers", "N",           "one", "count", .where_group(.g = "first EDGAR", .y = 2021)
) |>
  dplyr::mutate(
    Section = "OA-A",
    Note    = paste0("Appendix A, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-b
# CHAPTER B's rows: the installed package versions, cited as text.
spec_b <- tibble::tribble(
  ~Key,               ~Exhibit,          ~Column, ~Fun,  ~Format, ~Where,
  "VersionGetEDGAR",  "PackageVersions", "Value", "one", "text",  "Key == 'rGetEDGAR'",
  "VersionLabelDocs", "PackageVersions", "Value", "one", "text",  "Key == 'rLabelDocs'"
) |>
  dplyr::mutate(
    Section = "OA-B",
    Note    = paste0("Appendix B, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-c
# CHAPTER C's rows. The manuscript's Section 3.2 cites the first block, so those are filed under 3.2.
.where_leaf <- "Level1 != 'Amendment' & (Kind == 'sub' | Level1 %in% c('Licenses', 'Leases', 'Other'))"
.where_bert <- "Task == 'ClassDetailed' & startsWith(Engine, 'Bert') & Ships"
.where_kw   <- "Task == 'ClassDetailed' & Engine == 'Kw'"
.where_llm  <- "Task == 'ClassDetailed' & Engine == 'Llm'"
# THE SWEEP TIBBLE holds one row per configuration; the learning rate and the epochs sit in ConfigName (_E6_, _LR2e-05_).
# The factorial is the two learning rates and the two epoch budgets; the runs at 1e-5 and at ten epochs are the two
# checks of the dropped levels and are counted apart.
.in_grid     <- "grepl('_E(3|6)_', ConfigName) & grepl('_LR(2|3)e-05_', ConfigName)"
.where_sweep <- paste0("Task %in% c('ClassDetailed', 'AmendType') & ", .in_grid)
.where_task  <- paste0("Task == 'ClassDetailed' & ", .in_grid)
.where_check <- paste0("Task == 'ClassDetailed' & !(", .in_grid, ")")

spec_c_manuscript <- tibble::tribble(
  ~Key,              ~Exhibit,           ~Column,         ~Fun,   ~Format, ~Where,
  ~Note,
  "NLabelled",       "ClassLabelled",    "N",             "one",  "count", "Kind == 'total'",
  "Manually labeled contracts with readable text",
  "NAmended",        "ClassLabelled",    "N",             "one",  "count", "Row == 'Amended'",
  "Of which amendments",
  "NSecond",         "ClassLabelled",    "Second",        "one",  "count", "Kind == 'total'",
  "Labeled contracts that carry a second category",
  "NRarest",         "ClassLabelled",    "N",             "min",  "count", .where_leaf,
  "Labeled contracts in the smallest detailed category",
  "SweepConfigs",    "ClassSweep",       "1L",            "sum",  "count", .where_sweep,
  "Factorial configurations across the category and the amendment task (32 each; the broad task is a roll-up)",
  "AccDetailed",     "ClassTransformer", "Accuracy",      "one",  "prop3", "Kind == 'total'",
  "Out-of-fold accuracy of the deployed model, category task",
  "F1Detailed",      "ClassTransformer", "F1",            "one",  "prop3", "Kind == 'total'",
  "Out-of-fold macro-F1, category task",
  "LenientDetailed", "ClassTransformer", "RecallLenient", "one",  "prop3", "Kind == 'total'",
  "Accuracy counting a prediction that matches the second label as correct",
  "AccAmend",        "ClassAmendment",   "Accuracy",      "one",  "prop3", "Label == 'Total'",
  "Out-of-fold accuracy, amendment task",
  "F1Amend",         "ClassAmendment",   "F1",            "one",  "prop3", "Label == 'Total'",
  "Out-of-fold macro-F1, amendment task",
  "KwCoverage",      "ClassArms",        "Coverage",      "one",  "pct1",  .where_kw,
  "Share of labeled contracts the keyword table classifies, percent",
  "KwAccCommitted",  "ClassArms",        "AccuracySel",   "one",  "prop3", .where_kw,
  "Accuracy of the keyword table where it classifies"
) |>
  dplyr::mutate(Section = "3.2")

spec_c <- tibble::tribble(
  ~Key,           ~Exhibit,           ~Column,   ~Fun,   ~Format, ~Where,
  "TitlesNamed",  "CategoryTitles",   "pNamed",  "mean", "pct1",  "Rank == 1",
  "SweepPerTask", "ClassSweep",       "1L",      "sum",  "count", .where_task,
  "SweepChecks",  "ClassSweep",       "1L",      "sum",  "count", .where_check,
  "F1Llm",        "ClassArms",        "MacroF1", "one",  "prop3", .where_llm,
  "AccLlm",       "ClassArms",        "Accuracy", "one", "prop3", .where_llm,
  "AccBert",      "ClassArms",        "Accuracy", "one", "prop3", .where_bert,
  "AccCeiling",   "ClassArmsFullCeiling", "Accuracy", "max", "prop3", "TRUE",
  "CeilGain512",  "ClassArmsFullCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512'",
  "CeilGainKw",   "ClassArmsFullCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512 or Kw'",
  "CeilGainLlm",  "ClassArmsFullCeiling", "Marginal", "one", "prop3", "Engines == 'Bert256 or Bert512 or Kw or Llm'",
  "SecondDocs",   "ClassSecond",      "N",       "one",  "count", "Kind == 'total'",
  "SecondHit1",   "ClassSecond",      "Hit1 / N", "one", "pct1",  "Kind == 'total'",
  "SecondHit2",   "ClassSecond",      "Hit2 / N", "one", "pct1",  "Kind == 'total'",
  "SecondBoth",   "ClassSecond",      "Both / N", "one", "pct1",  "Kind == 'total'",
  "MarginDual",   "ClassSecond",      "Value",   "one",  "prop3", "Row == 'Margin, two labels'",
  "MarginSingle", "ClassSecond",      "Value",   "one",  "prop3", "Row == 'Margin, one label'"
) |>
  dplyr::mutate(
    Section = "OA-C",
    Note    = paste0("Appendix C, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-d
# CHAPTER D's rows. Section 3.3 cites the values and the duration rungs; the rest is the appendix's.
.where_cov <- \(.f, .e) paste0("Family == '", .f, "' & Entity == '", .e, "'")
.where_gpe <- "Block == 'pairwise' & Entity == 'GPE' & ProducerA == 'lexnlp' & ProducerB == 'matcon'"

spec_d_manuscript <- tibble::tribble(
  ~Key,           ~Exhibit,        ~Column,     ~Fun,  ~Format, ~Where,
  ~Note,
  "ValPartNaive", "ContentValues", "PartNaive", "one", "num2",  "Kind == 'total'",
  "Distinct organizations a contract names, mean",
  "ValPartRule",  "ContentValues", "PartRule",  "one", "num2",  "Kind == 'total'",
  "Contracting parties (registrant, co-registrants, counterparties), mean",
  "ValCtryNaive", "ContentValues", "CtryNaive", "one", "num2",  "Kind == 'total'",
  "Countries a contract mentions, mean",
  "ValCtryReg",   "ContentValues", "CtryReg",   "one", "num2",  "Kind == 'total'",
  "Countries attributed to the registrant, mean",
  "ValCtryCpty",  "ContentValues", "CtryCpty",  "one", "num2",  "Kind == 'total'",
  "Countries attributed to the counterparties, mean",
  "DurTerm",      "DurationRungs", "Share",     "one", "pct1",  "Rung == 'term'",
  "Share of contracts whose end comes from a stated term, percent",
  "DurMedRule",   "DurationRungs", "Med",       "one", "num1",  "Rung == 'all-rule'",
  "Median duration in years under the rule",
  "DurMedNaive",  "DurationRungs", "Med",       "one", "num1",  "Rung == 'all-naive'",
  "Median duration in years reading the latest date in the contract as its end"
) |>
  dplyr::mutate(Section = "3.3")

spec_d <- tibble::tribble(
  ~Key,                ~Exhibit,          ~Column,      ~Fun,  ~Format, ~Where,
  "NerDocs",           "EntityCoverage",  "nDocs",      "max", "count", "TRUE",
  "CovOrgSpacy",       "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "ORG"),
  "CovOrgLexnlp",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "ORG"),
  "SpansOrgSpacy",     "EntityCoverage",  "Spans",      "one", "count", .where_cov(.f = "spacy",  .e = "ORG"),
  "SpansOrgLexnlp",    "EntityCoverage",  "Spans",      "one", "count", .where_cov(.f = "lexnlp", .e = "ORG"),
  "CovPersonSpacy",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "PERSON"),
  "CovGpeSpacy",       "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "spacy",  .e = "GPE"),
  "CovGpeLexnlp",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "GPE"),
  "CovDateLexnlp",     "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "DATE"),
  "CovMoneyLexnlp",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "lexnlp", .e = "MONEY"),
  "CovMoneyMatcon",    "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "MONEY"),
  "CovTermMatcon",     "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "TERM"),
  "CovRedactMatcon",   "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "REDACT"),
  "CovLawMatcon",      "EntityCoverage",  "Coverage",   "one", "pct1",  .where_cov(.f = "matcon", .e = "LAW"),
  "ContrastOrgLexnlp", "EntityPositions", "Contrast",   "max", "num2",  "Producer == 'lexnlp' & Entity == 'ORG'",
  "ContrastOrgSpacy",  "EntityPositions", "Contrast",   "max", "num2",  "Producer == 'spacy:trf' & Entity == 'ORG'",
  "JaccardOrg",        "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'ORG'",
  "JaccardGpeLex",     "EntityAgreement", "Jaccard",    "one", "num2",  .where_gpe,
  "ExactGpeLex",       "EntityAgreement", "ExactShare", "one", "pct1",  .where_gpe,
  "JaccardGpeSpacy",   "EntityAgreement", "Jaccard",    "max", "num2",
                       "Block == 'pairwise' & Entity == 'GPE' & (ProducerA == 'spacy:trf' | ProducerB == 'spacy:trf')",
  "JaccardDate",       "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'DATE'",
  "ExactDate",         "EntityAgreement", "ExactShare", "one", "pct1",  "Block == 'pairwise' & Entity == 'DATE'",
  "JaccardMoney",      "EntityAgreement", "Jaccard",    "one", "num2",  "Block == 'pairwise' & Entity == 'MONEY'",
  "OneProducerGpe",    "EntityAgreement", "Share",      "one", "pct1",
                       "Block == 'consensus' & Entity == 'GPE' & NProducer == 1",
  "OneProducerOrg",    "EntityAgreement", "Share",      "one", "pct1",
                       "Block == 'consensus' & Entity == 'ORG' & NProducer == 1",
  "DurOpen",           "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'open'",
  "DurCue",            "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'cue'",
  "DurMaxDate",        "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'maxdate'",
  "DurNone",           "DurationRungs",   "Share",      "one", "pct1",  "Rung == 'none'",
  "DurCapped",         "DurationRungs",   "N",          "one", "count", "Rung == 'dropped-capped'",
  "DurDefRule",        "DurationRungs",   "Defined",    "one", "count", "Rung == 'all-rule'",
  "DurDefNaive",       "DurationRungs",   "Defined",    "one", "count", "Rung == 'all-naive'"
) |>
  dplyr::mutate(
    Section = "OA-D",
    Note    = paste0("Appendix D, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-appendix-f
# CHAPTER F's rows: the package as 40B reported it. Rows the manuscript already owns (DocsRelease, Docs8K, OrderRefs,
# NLabelled, Orders) are not repeated; the appendix cites those keys.
.where_pkg <- \(.k) paste0("Key == '", .k, "'")

spec_f <- tibble::tribble(
  ~Key,             ~Exhibit,         ~Column, ~Fun,  ~Format, ~Where,
  "PkgVersion",     "PackageNumbers", "Text",  "one", "text",  .where_pkg(.k = "package.version"),
  "PkgFiles",       "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "package.files"),
  "PkgSizeGB",      "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "package.gb"),
  "FilesCore",      "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "folder.files.core"),
  "FilesSpans",     "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "folder.files.spans"),
  "FilesText",      "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "folder.files.text"),
  "FilesModels",    "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "folder.files.models"),
  "FilesLexnlp",    "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "folder.files.lexnlp"),
  "SizeCoreGB",     "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "folder.gb.core"),
  "SizeSpansGB",    "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "folder.gb.spans"),
  "SizeTextGB",     "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "folder.gb.text"),
  "SizeModelsGB",   "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "folder.gb.models"),
  "SizeLexnlpGB",   "PackageNumbers", "Value", "one", "num1",  .where_pkg(.k = "folder.gb.lexnlp"),
  "RowsPlaces",     "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "rows.places"),
  "RowsTermDocs",   "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "rows.termdocs"),
  "KwTerms",        "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "rows.keywordterms"),
  "SpansTotal",     "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "spans.total"),
  "Texts8K",        "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "text.documents.8k"),
  "Texts8KA",       "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "text.documents.8ka"),
  "ModelsCount",    "PackageNumbers", "Value", "one", "count", .where_pkg(.k = "models.count")
) |>
  dplyr::mutate(
    Section = "OA-F",
    Note    = paste0("Appendix F, read from ", .data$Exhibit, " where ", .data$Where)
  )
```

```{r}
#| label: registry-assemble
tab_numbers_spec <- dplyr::bind_rows(
  spec_manuscript,
  spec_c_manuscript,
  spec_d_manuscript,
  spec_a,
  spec_b,
  spec_c,
  spec_d,
  spec_f
) |>
  num_registry_check(.sections = .num_sections)

n_sec_ <- dplyr::n_distinct(tab_numbers_spec$Section)
cli::cli_alert_info("{nrow(tab_numbers_spec)} numbers registered across {n_sec_} sections.")

tab_sources <- num_report_sources(
  .spec     = tab_numbers_spec,   # which tibbles the registry names
  .dir_data = .lP$Input$DirData   # and where each is looked for, in order
)
```

# Numbers

```{r}
#| label: numbers-resolve
tab_numbers <- oa_numbers_set(
  .spec     = tab_numbers_spec,  # every number the paper and the appendix cite
  .dir_data = .lP$Input$DirData  # the tibbles behind the exhibits, 30's first
)

oa_report_numbers(
  .tab    = tab_numbers,       # resolved above
  .strict = .lP$Params$Strict  # TRUE stops the render on an unresolved number
)
```

```{r}
#| label: numbers-write
paths_numbers <- num_numbers_write(
  .tab     = tab_numbers,        # resolved above
  .dir_own = .lP$Output$DirOwn,  # Numbers.tex, Numbers.csv, Numbers-unresolved.txt
  .doc     = .name_script
)
```

# Validation

**Every citation resolves, and every key is cited.** The manuscript's and the appendix's `.tex` files, where a
folder of them exists, are scanned for `\pnum{}` and `\oanum{}`. A cited key the registry
does not hold would print as `??Key`; a registered key cited nowhere is either dead weight or a chapter not yet
written, and is listed so the registry stays honest.

```{r}
#| label: validate-citations
paths_cite <- if (fs::dir_exists(.lP$Input$DirManuscript)) {
  fs::dir_ls(.lP$Input$DirManuscript, glob = "*.tex")
} else {
  cli::cli_alert_warning("No manuscript folder at {.path {(.lP$Input$DirManuscript)}}; no citations scanned.")
  character(0)
}

tab_cited <- num_cited_keys(.paths = paths_cite)

lst_check <- num_check_citations(
  .tab    = tab_numbers,       # what is defined
  .cited  = tab_cited,         # what is cited, where
  .strict = .lP$Params$Strict  # TRUE aborts on a citation without a key
)
```

**The register, as written.** The same table `Numbers.csv` holds; what a reader opens to check a value.

```{r}
#| label: validate-register
tab_numbers |>
  dplyr::select(dplyr::all_of(c("Section", "Key", "Value", "Status", "Note"))) |>
  tbl_say()
```

# Deployment

Every render writes `Output/Numbers.tex`. One call copies it to the paper folder beside the appendix fragments,
archives the version it replaces, and says whether the content changed -- which, while Overleaf is updated by hand,
is whether to upload it.

```r
source(here::here("1_code", "_Commons", "_OnlineAppendix.R"), encoding = "UTF-8")
source(here::here("1_code", "50-Numbers.R"), encoding = "UTF-8")

num_deploy(
  .path_numbers = here::here("2_output", "50-Numbers", "Output", "Numbers.tex"),
  .dir_deploy   = fs::path(
    "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractPipeline",
    "200-Paper_figures",
    "OnlineAppendix"
  )
)
```

On the Overleaf side, the preamble inputs this one file in place of the four chapter files:
`\input{online_appendix/Numbers}`. The chapter files can be removed once it compiles.

```{r}
#| label: deploy-status
if (fs::file_exists(.lP$Output$Numbers)) {
  cli::cli_alert_info(
    "{.file Numbers.tex} last written {format(fs::file_info(.lP$Output$Numbers)$modification_time, '%Y-%m-%d %H:%M')}."
  )
}
```

# Overview

```{r}
#| label: overview
tab_numbers |>
  dplyr::count(.data$Section, Resolved = .data$Status == "ok", name = "N") |>
  tidyr::pivot_wider(names_from = "Resolved", values_from = "N", values_fill = 0L) |>
  tbl_say()
```

# Next

- Rename the moved builders (`oaa_*`, `oac_*`, `oad_*`) to `num_*` once the identity checks against the chapters'
  last outputs have passed; until then the names say where each came from.
- The introduction and Section 4 keys beyond chapter A's (words per contract by class, contracts per filing quarter
  by industry, the amendment share, the redaction shares before and after the FAST Act): rows over 30's
  `ContentDetail`, `FirmFundamentals`, `ContractTypes` and `RedactionsTime`, once their columns are confirmed.
- `AnnouncementsNoDate` is a third exclusion the manuscript does not mention; either the sentence names it or the
  sample definition folds it into the single-agreement test.
