---
title: "Publish Code -- the published copy of the pipeline and its packages (50A)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  html: default
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr. comment = "" removes the "##"
# prefix from console blocks so they can be copied verbatim.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

```{r}
#| label: load-libraries

# THE COMMONS THIS DOCUMENT NEEDS, AND ITS OWN LIBRARY. _Initialize.R resolves this document's output directory and
# function file; _Tables.R prints every console table. Nothing of the pipeline itself is sourced: this document reads
# git, not data.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "50A-PublishCode"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document produces the published copy of the code: the pipeline that builds the database, the Python tools the
pipeline calls, and the two R packages behind retrieval and labelling. It writes that copy into the published
repository, `matcon-data-and-methods`, under `pipeline/` and `packages/`, and touches nothing else there.

Three decisions shape it.

**What is published is a commit, not a folder.** The copy is taken with `git archive` from the commit each source is
on. An edit that is not committed is therefore not published -- and it is listed below, so it is not missed either.
The commit of every source is written into the copy, so each published file can be traced to the version it came
from.

**Every file is decided by a visible rule.** The rule tables below are the whole publication policy. Every committed
file matches one rule, the first match decides, and a file that no rule matches stops the document. A new file is
therefore decided about before it goes public, instead of being published or left out by accident.

**What must never be public is searched for, not assumed absent.** Before anything reaches the published repository,
the staged copy is scanned for paths into a home directory, credentials, data files, files GitHub refuses, code that
does not parse, and references to files that are left out. While the published repository is private the findings
are reported and the copy proceeds (`Strict = FALSE`); before it is made public, `Strict = TRUE` turns every
violation into a stop.

Committing and pushing stay manual. The document prepares the change in the published repository and shows it; the
decision to publish is taken there, in the RStudio Git pane.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Source = list(
    # THE PIPELINE is this repository.
    DirPipeline = here::here(),
    NamePipeline = "material-contracts",
    # THE PACKAGES live in their own clones. The paths are built from this repository's location, so no home
    # directory is written down.
    DirPackages = c(
      rGetEDGAR  = fs::path_norm(fs::path(here::here(), "..", "..", "Packages", "rGetEDGAR")),
      rLabelDocs = fs::path_norm(fs::path(here::here(), "..", "..", "Packages", "rLabelDocs"))
    )
  ),
  Target = list(
    # THE PUBLISHED REPOSITORY, cloned beside this one.
    DirRepo     = fs::path_norm(fs::path(here::here(), "..", "matcon-data-and-methods")),
    # THE ONLY TWO DIRECTORIES THIS DOCUMENT WRITES THERE.
    SubPipeline = "pipeline",
    SubPackages = "packages"
  ),
  Output = list(
    # THE STAGE is a temporary copy of the commits, where the checks run before anything reaches the published
    # repository. It lives in this R session's temporary directory and disappears when the render ends, so nothing
    # of it stays in this repository.
    DirStage    = fs::path(tempdir(), "50A-PublishCode-Stage"),
    FilManifest = utils_file_path(.dir_main, "Output", "Manifest.csv")
  ),
  Params = list(
    Strict = FALSE,  # FALSE reports violations and copies anyway; set TRUE before the target is made public
    Fetch  = TRUE,   # fetch every source first, so that "behind GitHub" is known
    Apply  = TRUE,   # FALSE shows what the target would receive without changing it
    WarnMB = 50,     # GitHub warns above this size
    MaxMB  = 100     # GitHub refuses above this size
  )
)

tibble::tibble(
  Location = c(names(.lP$Source$DirPackages), "pipeline", "target"),
  Path     = c(.lP$Source$DirPackages, .lP$Source$DirPipeline, .lP$Target$DirRepo),
  IsClone  = fs::dir_exists(fs::path(c(.lP$Source$DirPackages, .lP$Source$DirPipeline, .lP$Target$DirRepo), ".git"))
) |>
  tbl_say(.title = "Every location is a git clone", .n = NULL)
```

Every row above must read `TRUE`. A `FALSE` means a clone is not where this document expects it, and nothing below
can run.

# Rules

The rules are the publication policy, so they stand here rather than in a function. Each is a regular expression on
the path within its repository; the first rule that matches decides. Exceptions therefore come first, above the
broad rule they carve out of.

**The pipeline.** Everything this repository needs to rebuild the database and the paper is published: the runbooks
and their libraries, the shared functions, the templates, the Python tools, and the R environment. Left out are a
runbook that belongs to another project, an empty leftover, the working probes, the LexNLP exploration scripts --
`image_spec.py` records that they change no output -- and a backup the gazetteer rebuild writes beside the lookup it
produces. Of the tests folder, the checks that published files cite are kept: the parse check, the 04D preflight,
and the recogniser tests the LexNLP image and the benchmark refer to.

```{r}
#| label: rules-pipeline

rules_pipeline <- tibble::tribble(
  ~Pattern, ~Action, ~Reason,
  # Exceptions first.
  "^1_code/01B-EDGAR\\.qmd$",
  "exclude", "a runbook of another project",
  "^1_code/40-OnlineAppendix-B\\.R$",
  "exclude", "empty leftover; the appendix chapters are the 42 pairs",
  "^1_code/_Tests/(Parse-Check|04D-Preflight|Test-[A-Za-z-]+)\\.R$",
  "include", "checks that published files cite",
  "^1_code/_Tests/",
  "exclude", "working probes and scratch",
  "^contracts-lexnlp/probe_[a-z_]+\\.py$",
  "exclude", "exploration probes; image_spec.py records that they change no output",
  "^contracts-extract/src/matcon_extract/data/geo_lookup_pre_hierarchy\\.parquet$",
  "exclude", "backup written by rebuild-geo-lookup.R; the package reads geo_lookup.parquet",
  # The pipeline.
  "^1_code/[^/]+\\.(qmd|R)$",
  "include", "runbooks and their function libraries",
  "^1_code/(_Commons|_Templates)/",
  "include", "shared functions and the appendix templates",
  "^1_code/(_quarto\\.yml|_styles\\.css|\\.gitignore)$",
  "include", "runbook project settings",
  "^contracts-(classify|extract|lexnlp|spacy)/",
  "include", "the Python tools the pipeline calls",
  "^(renv\\.lock|\\.Rprofile|\\.here|\\.renvignore|\\.gitignore|material-contracts\\.Rproj)$|^renv/",
  "include", "the R environment and the project root"
)
```

**The packages.** Each package is published as committed, without the folder metadata macOS writes, superseded code
kept beside the package, and a template figure.

```{r}
#| label: rules-packages

rules_packages <- tibble::tribble(
  ~Pattern, ~Action, ~Reason,
  "(^|/)\\.DS_Store$",
  "exclude", "macOS folder metadata",
  "^_old/",
  "exclude", "superseded code kept beside the package",
  "^man/figures/README-pressure-1\\.png$",
  "exclude", "template figure left by usethis",
  ".",
  "include", "the package as committed"
)
```

# Input

Where each source stands. The commit in each row is what gets published.

```{r}
#| label: input-state

tab_state <- pub_repo_states(
  .dirs  = c(
    purrr::set_names(.lP$Source$DirPipeline, .lP$Source$NamePipeline),  # the pipeline, first
    .lP$Source$DirPackages                                             # then the packages
  ),
  .fetch = .lP$Params$Fetch  # fetch first, so that "behind GitHub" means something
)
pub_report_state(.tab = tab_state)
```

An uncommitted change is the one to read carefully: the published copy will not have it. A source that is behind
GitHub publishes an older state than GitHub holds, and one that is ahead names a commit GitHub cannot show. Both are
fixed in the source, with a pull or a push, before rendering again.

```{r}
#| label: input-files

tab_files <- purrr::map2(
  tab_state$Repo,
  tab_state$Dir,
  \(.n, .d) pub_repo_files(
    .name = .n,  # the repository, as named above
    .dir  = .d   # its clone
  )
) |>
  purrr::list_rbind()

tab_files |>
  dplyr::count(.data$Repo, name = "Files") |>
  tbl_say(.title = "Files in each commit", .n = NULL)
```

# Selection

The rules applied: the pipeline's to this repository, the package rules to each package. The document stops here if
any file is undecided.

```{r}
#| label: select-files

tab_sel <- dplyr::bind_rows(
  pub_classify(
    .files = dplyr::filter(tab_files, .data$Repo == .lP$Source$NamePipeline),  # the pipeline's files
    .rules = rules_pipeline                                                  # decided by its rules
  ),
  pub_classify(
    .files = dplyr::filter(tab_files, .data$Repo != .lP$Source$NamePipeline),  # the packages' files
    .rules = rules_packages                                                  # decided by theirs
  )
)
pub_require_decided(.tab = tab_sel)
pub_report_selection(.tab = tab_sel)
```

The list of left-out files is complete by construction. A file that should be public but appears there needs a rule,
not a manual copy.

# Staging

The published files are copied out of their commits into a temporary stage: the pipeline under `pipeline/`, each package
under `packages/<name>/`, each subtree with a note naming the commits it comes from.

```{r}
#| label: stage-copy

tab_staged <- pub_stage(
  .tab           = tab_sel,                      # what the rules decided
  .state         = tab_state,                    # which commit each repository is on
  .dir_stage     = .lP$Output$DirStage,          # emptied and rebuilt
  .name_pipeline = .lP$Source$NamePipeline,      # which source is the pipeline
  .sub_pipeline  = .lP$Target$SubPipeline,       # where the pipeline goes
  .sub_packages  = .lP$Target$SubPackages        # where the packages go
)
cli::cli_alert_success("{nrow(tab_staged)} files staged in {.path {(.lP$Output$DirStage)}}")
```

# Validation

The staged copy is what would be published, so it is what the checks read. One left-out file may be named by a
published one: the gazetteer rebuild writes its backup under that name, so a reader of the rebuild script is not
pointed at anything missing.

```{r}
#| label: validate-checks

tab_checks <- pub_checks(
  .tab      = tab_staged,                                                          # the staged copy
  .excluded = unique(fs::path_file(tab_sel$Path[tab_sel$Action %in% "exclude"])),  # names that must not be cited
  .refs_ok  = "geo_lookup_pre_hierarchy.parquet",                                  # written, not read, by the rebuild
  .warn_mb  = .lP$Params$WarnMB,                                                   # GitHub warns above
  .max_mb   = .lP$Params$MaxMB                                                     # GitHub refuses above
)
pub_report_checks(.tab = tab_checks)
pub_require_clean(
  .tab    = tab_checks,          # the findings
  .strict = .lP$Params$Strict    # stop on a violation only when strict
)
```

A path into a home directory is the violation to expect while the pipeline still writes to shared folders by
absolute path; it is fixed in the source by building the path from `here::here()` or from a setting. A credential is
never acceptable, strict or not.

# Deployment

The owned subtrees of the published repository are made to match the stage: new files added, changed files
replaced, dropped files deleted. Files that git ignores there -- local state of that clone -- are left alone.

```{r}
#| label: deploy-mirror

tab_mirror <- pub_mirror(
  .dir_stage  = .lP$Output$DirStage,                                   # the staged copy
  .dir_target = .lP$Target$DirRepo,                                    # the published repository
  .subtrees   = c(.lP$Target$SubPipeline, .lP$Target$SubPackages),     # the only directories written
  .apply      = .lP$Params$Apply                                       # FALSE only reports
)
pub_report_mirror(
  .tab     = tab_mirror,          # the plan
  .applied = .lP$Params$Apply     # whether it was carried out
)
```

```{r}
#| label: deploy-manifest

tab_manifest <- pub_write_manifest(
  .tab   = tab_staged,                  # the staged copy
  .state = tab_state,                   # the commits
  .path  = .lP$Output$FilManifest       # one row per published file
)
cli::cli_alert_success("Manifest: {nrow(tab_manifest)} files, {.path {(.lP$Output$FilManifest)}}")
```

```{r}
#| label: deploy-target-status

tab_target <- pub_report_target(
  .dir_target = .lP$Target$DirRepo,                                 # the published repository
  .subtrees   = c(.lP$Target$SubPipeline, .lP$Target$SubPackages)  # what this document owns there
)
```

This is what a commit in the published repository would contain. To publish it, open that repository's project in
RStudio, tick the files in the Git pane, commit, and push.

# Overview

```{r}
#| label: overview-summary

pub_report_overview(
  .state  = tab_state,    # where each source stands
  .sel    = tab_sel,      # what the rules decided
  .checks = tab_checks,   # what the checks found
  .mirror = tab_mirror    # what the target received
)
```

# Next

`50B-PublishData` assembles the data package -- the release, the entity spans, the texts, the models and the
replication inputs -- and deploys it to the shared Drive folder the published repository links to.
