---
title: "Publish Data -- the data package of the database (50B)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  html: default
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr. comment = "" removes the "##"
# prefix from console blocks so they can be copied verbatim.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

```{r}
#| label: load-libraries

# THE COMMONS THIS DOCUMENT NEEDS, AND ITS OWN LIBRARY. _Utils.R holds the input stamp every expensive step is keyed
# on; _Tables.R prints the console tables. No pipeline library is sourced: this document reads what the stages wrote.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "50B-PublishData"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document builds the published data package of the database: one versioned folder with five parts, a checksum
for every file and a README, copied to the shared Drive folder. It also cuts the sample the site's examples run on
and writes it into the site repository. Nothing upstream changes; every file is built from what the pipeline stages
wrote.

| Part | What it holds |
|:--|:--|
| `core/` | the release tables, the labelled sample, the keyword terms in use, the contract index, their codebooks |
| `spans/` | the entity spans the rules kept, one file per kind |
| `text/` | the documents, as filed and as read |
| `models/` | the six fine-tuned classifiers, with a usage guide |
| `lexnlp/` | the image that extracted the organisation candidates, with a usage guide |

Three decisions shape it.

**One public schema decides what is published.** `1_code/_Publish/PublicSchema.csv` lists every column of every
published table -- kept, dropped or added -- with its type, its meaning and its Stata name. Every source is held
against it before anything is written, and a column it does not list stops the build: nothing reaches the package
without a decision, and nothing renamed upstream can vanish unnoticed. The codebooks are written from the same file,
so they cannot disagree with the tables.

**What is published is what the paper used.** Two kinds of content come out: the Compustat fields, which are
licensed, and everything about amounts, which the paper does not use. The EDGAR links are repaired, because the
pipeline writes them with a missing slash, and one column is added, `ClassRollup`, the broad category as the paper
uses it. Everything else is published as built. The text is published exactly as the classifiers and extractors
read it, so every published label and span can be reproduced from it; the README gives the one-line repair for the
quotation marks that some HTML documents carry as control characters.

**Every expensive output is stamped.** A stamp is a hash of an output's input files and of the statement that builds
it; an output whose stamp matches is skipped. The text step is unchanged from the first build, so the 45 GB of text
keep their stamps and are neither rebuilt nor copied again.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    DirRelease       = here::here("2_output", "10-ExportData", "Output"),
    FilPrepared      = here::here("2_output", "03A-ClassifyPrepare", "prepared.parquet"),
    DirKeywordTables = here::here("2_output", "03C-ClassifyTrainKeyword", "table"),
    DirSpanStore     = here::here("2_output", "04D-EntityApply", "Store"),
    DirParsed        = here::here("2_output", "01B-EdgarDocuments", "GetEDGAR", "DocumentData", "Parsed"),
    DirModels        = here::here("2_output", "03B-ClassifyTrainBERT", "model_final"),
    # THE IMAGE THAT EXTRACTED THE CORPUS, archived on the external drive when it ran.
    FilLexnlpImage   = "/Volumes/Ext20TB/ContractsBackUp/contracts-lexnlp-17a366b025fe.tar.gz",
    FilLexnlpLock    = here::here("contracts-lexnlp", "requirements.lock.txt"),
    # THE PUBLICATION'S OWN FILES: the schema and the two usage guides.
    FilSchema        = here::here("1_code", "_Publish", "PublicSchema.csv"),
    FilModelsReadme  = here::here("1_code", "_Publish", "models-README.md"),
    FilLexnlpReadme  = here::here("1_code", "_Publish", "lexnlp-README.md")
  ),
  Params = list(
    Version         = "v1.0.0",                                                       # the package version
    SiteUrl         = "https://matthiasuckert.github.io/matcon-data-and-methods/",   # documentation
    CodeUrl         = "https://github.com/MatthiasUckert/material-contracts",         # the pipeline
    LexnlpCommit    = "e3f97216ef96d58d6001faf23bc2e5017eed5b7a",   # the commit the image was built from
    LabelledContext = 256L,       # context length of the models that labelled the published data
    Threads         = 16L,        # DuckDB worker threads
    Memory          = "96GB",     # DuckDB memory limit; it spills to Temp beyond this
    TextRowGroup    = 1000L,      # documents per row group in text/
    TextYears       = NULL,       # every year; a single year, e.g. "2012", tests the document quickly
    Rerun           = FALSE,      # TRUE rebuilds every output regardless of its stamp
    Deploy          = TRUE,      # FALSE builds and checks the package without copying it to Drive
    SampleN         = 15L,        # sample documents per detailed category
    SampleExtras    = 3L,         # rejected attachments, and multi-registrant attachments, added to the sample
    SampleWrite     = TRUE       # TRUE writes the new sample into the site repository; do that once the site is
                                  # adapted to its layout (core/, spans/, text/ as in the package)
  )
)

.lP$Output <- list(
  DirPackage       = fs::path(.dir_main, "Stage", "matcon-data", .lP$Params$Version),
  DirSample        = fs::path(.dir_main, "Stage", "sample"),
  DirSuperseded    = fs::path(.dir_main, "Superseded"),
  DirRepo          = fs::path_norm(fs::path(here::here(), "..", "matcon-data-and-methods")),
  DirStamps        = utils_file_path(.dir_main, "Stamps"),
  DirTemp          = utils_file_path(.dir_main, "Temp"),
  FilManifestCache = utils_file_path(.dir_main, "Output", "manifest_cache.csv"),
  # THE DRIVE FOLDER IS FOUND ON THIS MACHINE, not written down; see pbd_drive_root().
  DirDrive         = fs::path(pbd_drive_root(), "matcon-data", .lP$Params$Version)
)
fs::dir_create(.lP$Output$DirPackage)

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = unlist(.lP$Input),
  Exists = file.exists(unlist(.lP$Input))
) |>
  tbl_say(.title = "Every input resolves before anything is read", .n = NULL)
cli::cli_alert_info("Drive target: {.path {(.lP$Output$DirDrive)}}")
```

Every input must exist. The LexNLP image is on the external drive, which has to be mounted.

# The public schema

```{r}
#| label: schema-read

schema <- pbd_schema_read(.path = .lP$Input$FilSchema)   # stops on a column without meaning, type or Stata name
schema |>
  dplyr::summarise(
    Published = sum(.data$Action != "drop"),
    Dropped   = sum(.data$Action == "drop"),
    Added     = sum(.data$Action == "add"),
    .by       = "Table"
  ) |>
  pbd_report(.title = "The public schema", .note = NULL, .n = NULL)
```

```{r}
#| label: connect

con <- pbd_connect(
  .threads  = .lP$Params$Threads,    # worker threads
  .memory   = .lP$Params$Memory,     # memory limit before spilling
  .dir_temp = .lP$Output$DirTemp     # where it spills
)
```

**Specifications.** The span files and the text types, as they are built. MONEY is not among the spans.

```{r}
#| label: spec-spans

specs_spans <- tibble::tribble(
  ~Stem,          ~Pass,    ~Hash,
  "org_mentions", "ORG",    "812b63f438c5",
  "places_geo",   "GPE",    "2374951841a7",
  "law_clauses",  "GPE",    "2374951841a7",
  "date_spans",   "DATE",   "79c379586f6a",
  "term_spans",   "DATE",   "79c379586f6a",
  "redact_spans", "REDACT", "7b84db9925eb"
) |>
  dplyr::mutate(DirHash = as.character(fs::path(.lP$Input$DirSpanStore, .data$Pass, .data$Hash))) |>
  dplyr::select("Stem", "Pass", "DirHash")
```

```{r}
#| label: spec-text

specs_text <- tibble::tribble(
  ~Type,       ~Slug,       ~Table,           ~File,               ~Column,
  "Exhibit10", "exhibit10", "keys_contracts", "Contracts.parquet", "DocID",
  "8-K",       "8k",        "keys_summaries", "Summaries.parquet", "DocID",
  "8-KA",      "8ka",       "keys_summaries", "Summaries.parquet", "DocID",
  "CTO",       "cto",       "keys_orders",    "CtoOrders.parquet", "OrderDocID"
) |>
  dplyr::mutate(
    Dir  = as.character(fs::path(.lP$Input$DirParsed, .data$Type)),
    File = as.character(fs::path(.lP$Input$DirRelease, .data$File))
  )
```

Every source is now held against the schema. A column the schema does not list, or a listed column the source
no longer has, stops the document here.

```{r}
#| label: schema-check

keywords <- pbd_keywords_from(
  .con        = con,                              # DuckDB
  .dir_tables = .lP$Input$DirKeywordTables        # 03C's tables and the catalogue that marks the ones in use
)
rel_src <- function(.f) sprintf("read_parquet(%s)", pbd_lit(fs::path(.lP$Input$DirRelease, .f)))
sources_schema <- dplyr::bind_rows(
  tibble::tibble(
    Table = c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders"),
    From  = rel_src(paste0(c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders"), ".parquet"))
  ),
  tibble::tibble(Table = "Labels", From = sprintf("read_parquet(%s)", pbd_lit(.lP$Input$FilPrepared))),
  tibble::tibble(Table = "KeywordTerms", From = sprintf("read_parquet(%s)", pbd_lit(keywords$Files[1]))),
  tibble::tibble(
    Table = specs_spans$Stem,
    From  = sprintf("read_parquet(%s, union_by_name = true)",
                    pbd_lit(fs::path(specs_spans$DirHash, "chunk-*", paste0(specs_spans$Stem, ".parquet"))))
  )
)
tab_schema <- pbd_schema_check(
  .con     = con,              # DuckDB
  .schema  = schema,           # the decisions
  .sources = sources_schema    # every source whose columns must all be decided
)
pbd_report(
  .tab   = dplyr::select(tab_schema, -"Unlisted", -"Missing"),
  .title = "Sources against the schema",
  .note  = NULL,
  .n     = NULL
)
```

# Core

The broad category the paper uses rolls up the detailed one. The labelled sample holds the map, since the annotators
gave every contract both.

```{r}
#| label: core-rollup

rollup_map <- pbd_rollup_map(
  .con         = con,                          # DuckDB
  .path_labels = .lP$Input$FilPrepared         # the labelled sample
)
pbd_report(.tab = rollup_map, .title = "Detailed to broad", .note = NULL, .n = NULL)
```

Each table is written through the schema: the published columns in the published order, the computed ones through
an expression. For the contract file that means the two repaired links and `ClassRollup`; the other release tables
pass through as built.

```{r}
#| label: core-tables

dir_core <- fs::path(.lP$Output$DirPackage, "core")
stamp_core <- function(.f) pbd_stamp_path(.lP$Output$DirStamps, paste0("core/", .f))
exprs_contracts <- c(
  UrlDocument  = "regexp_replace(\"UrlDocument\", '^https:/+', 'https://')",    # one slash after the scheme, repaired
  UrlIndexPage = "regexp_replace(\"UrlIndexPage\", '^https:/+', 'https://')",
  ClassRollup  = pbd_rollup_sql(.map = rollup_map, .col = "Class")              # the paper's broad category
)
tab_core <- dplyr::bind_rows(
  pbd_table(
    .con        = con,
    .schema     = schema,
    .table      = "Contracts",
    .from       = rel_src("Contracts.parquet"),
    .sources    = fs::path(.lP$Input$DirRelease, "Contracts.parquet"),
    .path_out   = fs::path(dir_core, "Contracts.parquet"),
    .path_stamp = stamp_core("Contracts.parquet"),
    .exprs      = exprs_contracts,
    .rerun      = .lP$Params$Rerun
  ),
  purrr::map(c("Summaries", "Places", "TermDocs", "CtoOrders"), \(.t) pbd_table(
    .con        = con,
    .schema     = schema,
    .table      = .t,
    .from       = rel_src(paste0(.t, ".parquet")),
    .sources    = fs::path(.lP$Input$DirRelease, paste0(.t, ".parquet")),
    .path_out   = fs::path(dir_core, paste0(.t, ".parquet")),
    .path_stamp = stamp_core(paste0(.t, ".parquet")),
    .rerun      = .lP$Params$Rerun
  )) |>
    purrr::list_rbind(),
  pbd_table(
    .con        = con,
    .schema     = schema,
    .table      = "Labels",
    .from       = sprintf("read_parquet(%s)", pbd_lit(.lP$Input$FilPrepared)),
    .sources    = .lP$Input$FilPrepared,
    .path_out   = fs::path(dir_core, "Labels.parquet"),
    .path_stamp = stamp_core("Labels.parquet"),
    .rerun      = .lP$Params$Rerun
  ),
  pbd_table(
    .con        = con,
    .schema     = schema,
    .table      = "KeywordTerms",
    .from       = keywords$From,
    .sources    = keywords$Files,
    .path_out   = fs::path(dir_core, "KeywordTerms.parquet"),
    .path_stamp = stamp_core("KeywordTerms.parquet"),
    .rerun      = .lP$Params$Rerun
  )
)
tab_core <- dplyr::bind_rows(
  tab_core,
  pbd_table(
    .con        = con,
    .schema     = schema,
    .table      = "ContractIndex",
    .from       = sprintf("read_parquet(%s)", pbd_lit(fs::path(dir_core, "Contracts.parquet"))),
    .sources    = fs::path(dir_core, "Contracts.parquet"),
    .path_out   = fs::path(dir_core, "ContractIndex.csv.gz"),
    .path_stamp = stamp_core("ContractIndex.csv.gz"),
    .exprs      = c(   # the accession number, read off the index page's address
      AccessionNumber = "NULLIF(regexp_extract(\"UrlIndexPage\", '([0-9]{10}-[0-9]{2}-[0-9]{6})', 1), '')"
    ),
    .format     = "csv",
    .rerun      = .lP$Params$Rerun
  )
)
pbd_report(.tab = tab_core, .title = "Core tables", .note = "RowsOut must equal RowsIn in every row.", .n = NULL)
keywords$Windows |>
  dplyr::mutate(File = fs::path_file(.data$File)) |>
  pbd_report(.title = "Keyword terms: the window in use per task", .note = NULL, .n = NULL)
```

```{r}
#| label: core-contracts-check

tab_contracts_check <- pbd_query(
  .con = con,
  .sql = sprintf(
    paste(
      "SELECT count(*) FILTER (WHERE UrlIndexPage NOT LIKE 'https://%%'",
      "OR UrlDocument NOT LIKE 'https://%%') AS LinksBroken,",
      "count(*) FILTER (WHERE Class IS NOT NULL AND ClassRollup IS NULL) AS RollupMissing,",
      "count(*) FILTER (WHERE HierConsistent <> (ClassRollup = ClassBroad)) AS HierDisagrees",
      "FROM read_parquet(%s)"
    ),
    pbd_lit(fs::path(dir_core, "Contracts.parquet"))
  )
)
pbd_report(.tab = tab_contracts_check, .title = "Contract file", .note = "All three must be 0.", .n = NULL)
```

`HierDisagrees` checks that `ClassRollup` is the roll-up the classifier's consistency flag was computed against.

# Spans

```{r}
#| label: spans-build

tab_spans <- pbd_spans(
  .con        = con,                                       # DuckDB
  .schema     = schema,                                    # the columns each file publishes
  .specs      = specs_spans,                               # what to merge
  .dir_out    = fs::path(.lP$Output$DirPackage, "spans"),  # destination
  .dir_stamps = .lP$Output$DirStamps,                      # stamps
  .rel_out    = "spans",                                   # destination, relative to the package
  .rerun      = .lP$Params$Rerun                           # FALSE skips files whose inputs are unchanged
)
pbd_report(
  .tab   = tab_spans,
  .title = "Span files",
  .note  = "RowsOut must equal RowsIn in every row: the merge adds and drops nothing.",
  .n     = NULL
)
```

# Text

The text step is exactly the one of the first build, so its stamps still hold.

```{r}
#| label: text-keys

tab_keys <- pbd_text_keys(
  .con   = con,          # DuckDB
  .specs = specs_text    # which release file keys which document type
)
pbd_report(.tab = tab_keys, .title = "Release documents per key table", .note = NULL, .n = NULL)
```

Then one file per document type and year. The first full run reads every document once and takes hours; later
runs rebuild only years whose documents or release keys changed. With `TextYears` set, only those years are built,
which tests the whole document in minutes; the coverage check below then counts the documents of every other year as
missing, as it should.

```{r}
#| label: text-build

tab_text <- pbd_text(
  .con        = con,                                                  # DuckDB
  .specs      = specs_text,                                           # where each type is, and its key table
  .dir_out    = fs::path(.lP$Output$DirPackage, "text"),              # destination
  .dir_stamps = .lP$Output$DirStamps,                                 # stamps
  .rel_out    = "text",                                               # destination, relative to the package
  .extra      = list(Release = pbd_stamp(.dirs = unique(specs_text$File), .extra = NULL)),  # keys changed?
  .row_group  = .lP$Params$TextRowGroup,                              # documents per row group
  .years      = .lP$Params$TextYears,                                 # NULL builds every year
  .rerun      = .lP$Params$Rerun                                      # FALSE skips unchanged years
)
tab_coverage <- pbd_text_coverage(
  .con     = con,
  .specs   = specs_text,
  .dir_out = fs::path(.lP$Output$DirPackage, "text")
)
pbd_report_text(.text = tab_text, .coverage = tab_coverage)
```

# Codebooks

```{r}
#| label: codebooks

tab_codebooks <- pbd_codebooks(
  .schema      = schema,                                  # the one source of every meaning
  .dir_package = .lP$Output$DirPackage,                   # the package
  .core        = c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders", "Labels", "KeywordTerms",
                   "ContractIndex"),
  .spans       = specs_spans$Stem
)
pbd_report(.tab = tab_codebooks, .title = "Codebooks", .note = NULL, .n = NULL)
```

# Models

Each model folder is copied, its run configuration and log have the machine's paths rewritten, and the copy is
zipped; the selection record gets the same rewrite. The index says which archive labelled the published data and
which one cross-validation selected.

```{r}
#| label: models-build

tab_models <- pbd_models(
  .con          = con,                                        # DuckDB
  .dir_models   = .lP$Input$DirModels,                        # 03B's refits
  .dir_out      = fs::path(.lP$Output$DirPackage, "models"),  # destination
  .dir_stamps   = .lP$Output$DirStamps,                       # stamps
  .rel_out      = "models",                                   # destination, relative to the package
  .root         = here::here(),                               # the prefix rewritten out of every path
  .labelled_ctx = .lP$Params$LabelledContext,                 # the models behind the published labels
  .path_readme  = .lP$Input$FilModelsReadme,                  # the usage guide
  .rerun        = .lP$Params$Rerun
)
pbd_report(
  .tab   = dplyr::select(tab_models, "Zip", "Context", "LabelledPublished", "Selected", "MacroF1", "LocalPaths",
                         "Bytes", "Status"),
  .title = "Models",
  .note  = "LocalPaths must be 0 in every row.",
  .n     = NULL
)
```

# LexNLP

```{r}
#| label: lexnlp-copy

tab_lexnlp <- pbd_lexnlp(
  .path_image  = .lP$Input$FilLexnlpImage,                    # the archived image
  .path_lock   = .lP$Input$FilLexnlpLock,                     # its lockfile
  .path_readme = .lP$Input$FilLexnlpReadme,                   # the usage guide
  .commit      = .lP$Params$LexnlpCommit,                     # the commit the image was built from
  .dir_out     = fs::path(.lP$Output$DirPackage, "lexnlp")    # destination
)
pbd_report(.tab = tab_lexnlp, .title = "LexNLP image", .note = NULL, .n = NULL)
```

# The package, exactly

The package is these files and no others. Anything else in the stage -- a part that is no longer published, a file
an earlier build wrote under another name -- is moved aside into `Superseded/`, dated, before the manifest is
written.

```{r}
#| label: package-define

files_text <- tab_text |>
  dplyr::filter(.data$RowsOut > 0) |>
  dplyr::left_join(dplyr::select(specs_text, "Type", "Slug"), by = dplyr::join_by("Type")) |>
  dplyr::transmute(Path = as.character(fs::path("text", .data$Slug, paste0(.data$Slug, "_", .data$Year, ".parquet"))))
expected <- c(
  "README.md", "MANIFEST.sha256",
  as.character(fs::path("core", c(
    paste0(c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders", "Labels", "KeywordTerms"), ".parquet"),
    "ContractIndex.csv.gz"
  ))),
  tab_codebooks$File,
  as.character(fs::path("spans", c(paste0(specs_spans$Stem, ".parquet"), "Spans_Codebook.csv"))),
  files_text$Path, "text/Text_Codebook.csv",
  as.character(fs::path("models", c(tab_models$Zip, "models_index.csv", "deployed.parquet", "README.md"))),
  as.character(fs::path("lexnlp", c(fs::path_file(.lP$Input$FilLexnlpImage), "requirements.lock.txt", "NOTICE.md",
                                    "README.md")))
)
tab_aside <- pbd_supersede(
  .dir_package = .lP$Output$DirPackage,     # the stage
  .expected    = expected,                  # the package
  .dir_aside   = .lP$Output$DirSuperseded   # where anything else goes
)
pbd_report(
  .tab   = tab_aside,
  .title = "Moved aside",
  .note  = "Files an earlier build left that the package no longer holds.",
  .n     = 40L
)
```

# Validation

Every output against its source, every file against the schema, and the whole package against machine paths.

```{r}
#| label: validate-package

targets_conform <- dplyr::bind_rows(
  tibble::tibble(
    Table  = c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders", "Labels", "KeywordTerms"),
    Path   = as.character(fs::path(dir_core, paste0(c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders",
                                                      "Labels", "KeywordTerms"), ".parquet"))),
    Format = "parquet"
  ),
  tibble::tibble(
    Table  = "ContractIndex",
    Path   = as.character(fs::path(dir_core, "ContractIndex.csv.gz")),
    Format = "csv"
  ),
  tibble::tibble(
    Table  = specs_spans$Stem,
    Path   = as.character(fs::path(.lP$Output$DirPackage, "spans", paste0(specs_spans$Stem, ".parquet"))),
    Format = "parquet"
  ),
  tibble::tibble(
    Table  = "Text",
    Path   = as.character(fs::path(.lP$Output$DirPackage, "text", unique(fs::path_file(fs::path_dir(files_text$Path))),
                                   "*.parquet")),
    Format = "parquet"
  )
)
tab_conform <- pbd_conform(.con = con, .schema = schema, .targets = targets_conform)
tab_paths <- pbd_scan_paths(.con = con, .dir_package = .lP$Output$DirPackage)
left_over <- setdiff(list.files(.lP$Output$DirPackage, recursive = TRUE, all.files = TRUE), expected)
row_of <- function(.t) tab_core[tab_core$Table == .t, ]

tab_valid <- pbd_validate(.checks = list(
  pbd_check("schema: source columns not decided", 0, sum(nchar(tab_schema$Unlisted) > 0)),
  pbd_check("schema: published files that do not conform", 0, sum(!tab_conform$Ok)),
  pbd_check("contracts: one row per release row", row_of("Contracts")$RowsIn, row_of("Contracts")$RowsOut),
  pbd_check("contracts: links left broken", 0, tab_contracts_check$LinksBroken),
  pbd_check("contracts: ClassRollup missing where Class is set", 0, tab_contracts_check$RollupMissing),
  pbd_check("contracts: HierConsistent disagrees with ClassRollup", 0, tab_contracts_check$HierDisagrees),
  pbd_check("core: tables with rows lost or added", 0, sum(tab_core$RowsIn != tab_core$RowsOut)),
  pbd_check("index: one row per contract row", row_of("Contracts")$RowsOut, row_of("ContractIndex")$RowsOut),
  pbd_check("spans: rows out equal rows in", sum(tab_spans$RowsIn), sum(tab_spans$RowsOut)),
  pbd_check("text: every year built or current", 0,
            sum(!tab_text$Status %in% c("built", "current", "no release documents"))),
  pbd_check("text: release documents without text", 0, sum(tab_coverage$WithoutText)),
  pbd_check("text: every document published once", 0, sum(tab_coverage$Duplicates)),
  pbd_check("models: one archive per model", 6L, nrow(tab_models)),
  pbd_check("package: files with machine paths", 0, sum(tab_paths$Hits > 0)),
  pbd_check("package: files outside the definition", 0, length(left_over))
))
pbd_report(.tab = tab_valid, .title = "Validation", .note = "Every row must read Ok = TRUE.", .n = NULL)
pbd_report(.tab = tab_conform[!tab_conform$Ok, ], .title = "Files that do not conform", .note = NULL, .n = NULL)
pbd_report(.tab = tab_paths[tab_paths$Hits > 0, ], .title = "Files with machine paths", .note = NULL, .n = NULL)
```

# Deployment

The README is written first so the manifest covers it, the manifest last so it covers everything.

```{r}
#| label: deploy-readme-manifest

pbd_readme(
  .dir_package = .lP$Output$DirPackage,  # the package
  .version     = .lP$Params$Version,     # its version
  .site_url    = .lP$Params$SiteUrl,     # the documentation
  .code_url    = .lP$Params$CodeUrl      # the pipeline
)
tab_manifest <- pbd_manifest(
  .dir_package = .lP$Output$DirPackage,        # the package
  .path_cache  = .lP$Output$FilManifestCache   # checksums of the last run, reused where unchanged
)
tab_manifest |>
  dplyr::mutate(Folder = ifelse(grepl("/", .data$Path), sub("/.*$", "", .data$Path), ".")) |>
  dplyr::summarise(Files = dplyr::n(), Bytes = sum(.data$Bytes), .by = "Folder") |>
  dplyr::mutate(Size = pbd_size(.data$Bytes)) |>
  pbd_report(.title = "The package", .note = NULL, .n = NULL)
```

**The sample for the site** keeps the package's layout, names and columns, cut to the labelled contracts richest in
entities, plus a few rejected attachments and multi-registrant contracts so that `Removed` and `PrimaryFiler` can be
shown at work. Only the markup column of the text is left out.

```{r}
#| label: deploy-sample

sample_ids <- dplyr::bind_rows(
  pbd_sample_pick(.con = con, .dir_package = .lP$Output$DirPackage, .n_per_class = .lP$Params$SampleN) |>
    dplyr::transmute(.data$DocID, Why = "labelled"),
  pbd_sample_extras(.con = con, .dir_package = .lP$Output$DirPackage, .n = .lP$Params$SampleExtras)
)
specs_sample <- tibble::tribble(
  ~File,                                  ~Source,                                  ~Key,
  "core/Contracts.parquet",               "core/Contracts.parquet",                 "DocID",
  "core/Summaries.parquet",               "core/Summaries.parquet",                 "HashIndex",
  "core/Places.parquet",                  "core/Places.parquet",                    "DocID",
  "core/TermDocs.parquet",                "core/TermDocs.parquet",                  "DocID",
  "core/CtoOrders.parquet",               "core/CtoOrders.parquet",                 "DocID",
  "core/Labels.parquet",                  "core/Labels.parquet",                    "DocID",
  "core/KeywordTerms.parquet",            "core/KeywordTerms.parquet",              "ALL",
  "text/exhibit10/exhibit10_sample.parquet", "text/exhibit10/*.parquet",           "DocID"
) |>
  dplyr::bind_rows(
    tibble::tibble(
      File   = paste0("spans/", specs_spans$Stem, ".parquet"),   # every span file, cut to the documents
      Source = paste0("spans/", specs_spans$Stem, ".parquet"),
      Key    = "DocID"
    ),
    tibble::tibble(File = tab_codebooks$File, Source = tab_codebooks$File, Key = "")   # the codebooks, copied
  )
tab_sample <- pbd_sample_write(
  .con         = con,                         # DuckDB
  .specs       = specs_sample,                # which file is cut on which key
  .ids         = sample_ids$DocID,            # the documents
  .dir_package = .lP$Output$DirPackage,       # the published files
  .dir_out     = .lP$Output$DirSample         # the staged sample, emptied first
)
pbd_report(.tab = dplyr::count(sample_ids, .data$Why, name = "Documents"), .title = "The sample", .note = NULL, .n = NULL)
pbd_report(.tab = tab_sample, .title = "The sample, file by file", .note = NULL, .n = NULL)
```

```{r}
#| label: deploy-site

tab_numbers <- pbd_site_numbers(
  .con         = con,                                                  # DuckDB
  .dir_package = .lP$Output$DirPackage,                                # the published files
  .manifest    = tab_manifest,                                         # sizes and counts
  .spans       = tab_spans,
  .text        = tab_text,
  .models      = tab_models,
  .version     = .lP$Params$Version,
  .path_out    = fs::path(.lP$Output$DirSample, "package_numbers.csv")  # read by the site
)
tab_sample_repo <- pbd_mirror_repo(
  .dir_from = .lP$Output$DirSample,                       # the staged sample
  .dir_to   = fs::path(.lP$Output$DirRepo, "sample"),     # the only folder this writes in the site repository
  .apply    = .lP$Params$SampleWrite                      # FALSE reports the plan only
)
tab_sample_repo |>
  dplyr::count(.data$Action, name = "Files") |>
  pbd_report(
    .title = "The sample in the site repository",
    .note  = "Commit and push happen there; this document only writes the folder sample/.",
    .n     = NULL
  )
```

The package goes to Drive only when Drive holds nothing the package does not; files left there by an earlier build
are listed, and the copy waits until they are deleted by hand. Nothing on Drive is ever deleted by this document.

```{r}
#| label: deploy-drive

if (is.na(pbd_drive_root())) {
  cli::cli_abort("Google Drive for desktop is not mounted under ~/Library/CloudStorage; nothing can be deployed.")
}
tab_deploy <- pbd_deploy(
  .dir_package = .lP$Output$DirPackage,   # the package
  .dir_target  = .lP$Output$DirDrive,     # the version folder on Drive
  .manifest    = tab_manifest,            # what the package holds
  .apply       = .lP$Params$Deploy        # FALSE only reports
)
tab_deploy |>
  dplyr::summarise(Files = dplyr::n(), Bytes = sum(.data$Bytes, na.rm = TRUE), .by = "Action") |>
  dplyr::mutate(Size = pbd_size(.data$Bytes)) |>
  pbd_report(
    .title = if (.lP$Params$Deploy) "Copied to Drive" else "Would be copied to Drive",
    .note  = "\"only on Drive\" files must be deleted by hand before Deploy = TRUE can copy.",
    .n     = NULL
  )
pbd_report(.tab = tab_deploy[tab_deploy$Action == "only on Drive", "Path"], .title = "Only on Drive: delete these",
           .note = NULL, .n = 60L)
```

```{r}
#| label: deploy-close

DBI::dbDisconnect(conn = con, shutdown = TRUE)
```

# Overview

```{r}
#| label: overview-summary

tibble::tibble(
  Part    = c("core", "spans", "text", "models", "lexnlp"),
  Built   = c(sum(tab_core$Status == "built"), sum(tab_spans$Status == "built"), sum(tab_text$Status == "built"),
              sum(tab_models$Status == "built"), sum(tab_lexnlp$Status %in% c("copied", "written"))),
  Current = c(sum(tab_core$Status == "current"), sum(tab_spans$Status == "current"),
              sum(tab_text$Status == "current"), sum(tab_models$Status == "current"),
              sum(tab_lexnlp$Status == "current"))
) |>
  tbl_say(.title = "What this render built, and what was already current", .n = NULL)
tbl_say(.tab = tab_valid, .title = "Validation", .n = NULL)
```

# Next

Once Drive holds the package, the version folder and each of the five parts are shared as "Anyone with the link can
view", and the links go into the site repository: `data/parts.csv` for the parts, `_variables.yml` for the folder.
The site is then rendered against the new sample.
