---
title: "Publish Data -- the data package of the database (50B)"
author: "Matthias Uckert"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
format:
  html: default
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr. comment = "" removes the "##"
# prefix from console blocks so they can be copied verbatim.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(
  cli.num_colors = 1,
  cli.width      = 120,
  mc.table_mode  = "console"
)
```

```{r}
#| label: load-libraries

# THE COMMONS THIS DOCUMENT NEEDS, AND ITS OWN LIBRARY. _Utils.R holds the input stamp every expensive step is keyed
# on; _Tables.R prints the console tables. No pipeline library is sourced: this document reads what the stages wrote.
.path_libs <- purrr::map_chr(
  c("_Initialize", "_Utils", "_Tables"),
  \(.s) here::here("1_code", "_Commons", paste0(.s, ".R"))
)
purrr::walk(
  .x = .path_libs,
  .f = \(.p) source(file = .p, encoding = "UTF-8")
)

.name_script <- "50B-PublishData"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),  # the repository root
  .name_script = .name_script   # this document's stem
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document assembles the data package of the database: one versioned folder holding everything published as
data, with a checksum for every file and a README, copied to the shared Drive folder the published repository links
to. It changes nothing upstream; every file is built from what the pipeline stages wrote.

The package has six parts. `core/` holds the release files and their codebooks, a contract index, the labelled
sample and the keyword tables. `spans/` holds every entity span the extractors found. `text/` holds the retrieved
documents. `models/` holds the fine-tuned classifiers, `lexnlp/` the image that extracted the entities, and
`replication/` what the paper's exhibits, numbers and appendix read beyond `core/`.

Four decisions shape it.

**Parquet throughout.** Parquet is an open, column-oriented format that R, Python, DuckDB and Stata 19.5 read
directly, and it lets a reader download and open one table instead of a database. Stata files are not published:
the release's Stata copy is ten times the size of its parquet, and the codebooks carry the Stata name of every
column for readers who convert.

**One file per span type, and per document type and year.** 04D wrote each span type in 476 chunks, and 01B wrote
one file per document -- right for building the data, wrong for reading it. The package merges both into files a
reader can list and download one at a time: seven span files, and one text file per document type and year.

**The documents as filed and as text.** `text/` keeps each document's original markup (`HTML`) and the text
extracted from it (`TextRaw`). The markup is what EDGAR serves and what a reader needs to re-parse a table or a
signature block; the text is what every measure in the paper was computed from. The standardised text is not kept,
because `rGetEDGAR::standardize_text()` derives it from `TextRaw`. Only documents the release refers to are
published, and those left out are counted.

**Nothing licensed, nothing that cannot be traced.** Compustat and everything computed from it stay out, so the
Final Exhibits outputs are not part of `replication/`. The raw candidate spans behind 04D (28 GB) stay out too; the
span files carry every span a rule used, with its offsets and context.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    DirRelease       = here::here("2_output", "10-ExportData", "Output"),
    FilPrepared      = here::here("2_output", "03A-ClassifyPrepare", "prepared.parquet"),
    FilLabelsRaw     = here::here("0_data", "Labels", "ClassificationLabels.csv"),
    DirKeywordTables = here::here("2_output", "03C-ClassifyTrainKeyword", "table"),
    DirSpanStore     = here::here("2_output", "04D-EntityApply", "Store"),
    DirParsed        = here::here("2_output", "01B-EdgarDocuments", "GetEDGAR", "DocumentData", "Parsed"),
    DirModels        = here::here("2_output", "03B-ClassifyTrainBERT", "model_final"),
    # THE IMAGE THAT EXTRACTED THE CORPUS, archived on the external drive when it ran.
    FilLexnlpImage   = "/Volumes/Ext20TB/ContractsBackUp/contracts-lexnlp-17a366b025fe.tar.gz",
    FilLexnlpLock    = here::here("contracts-lexnlp", "requirements.lock.txt"),
    DirOutputRoot    = here::here("2_output")
  ),
  Params = list(
    Version      = "v1.0.0",                                                     # the package version
    RepoUrl      = "https://github.com/MatthiasUckert/matcon-data-and-methods",  # code and documentation
    Threads      = 16L,       # DuckDB worker threads
    Memory       = "96GB",    # DuckDB memory limit; it spills to Temp beyond this
    TextRowGroup = 1000L,     # documents per row group in text/; markup makes rows large
    Rerun        = FALSE,     # TRUE rebuilds every output regardless of its stamp
    Deploy       = TRUE,      # FALSE builds and checks the package without copying it to Drive
    SkipDeploy   = character(0)  # top-level folders to leave out of this copy, e.g. "text"
  )
)

.lP$Output <- list(
  DirPackage       = fs::path(.dir_main, "Stage", "matcon-data", .lP$Params$Version),
  DirStamps        = utils_file_path(.dir_main, "Stamps"),
  DirTemp          = utils_file_path(.dir_main, "Temp"),
  FilManifestCache = utils_file_path(.dir_main, "Output", "manifest_cache.csv"),
  # THE DRIVE FOLDER IS FOUND ON THIS MACHINE, not written down; see pbd_drive_root().
  DirDrive         = fs::path(pbd_drive_root(), "matcon-data", .lP$Params$Version)
)
fs::dir_create(.lP$Output$DirPackage)

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = unlist(.lP$Input),
  Exists = fs::file_exists(unlist(.lP$Input))
) |>
  tbl_say(.title = "Every input resolves before anything is read", .n = NULL)
cli::cli_alert_info("Drive target: {.path {(.lP$Output$DirDrive)}}")
```

Every input must exist. The LexNLP image is on the external drive, which has to be mounted for this document to run.

# Specifications

These three tables decide what the package holds, so they stand here rather than in a function.

**Spans.** One file per span type. The hash in each row is the 04D policy the release was built with, the same one
10 reads; a rehearsal directory beside it cannot be picked up by accident.

```{r}
#| label: spec-spans

specs_spans <- tibble::tribble(
  ~Stem,          ~Pass,    ~Hash,
  "org_mentions", "ORG",    "812b63f438c5",
  "places_geo",   "GPE",    "2374951841a7",
  "law_clauses",  "GPE",    "2374951841a7",
  "date_spans",   "DATE",   "79c379586f6a",
  "term_spans",   "DATE",   "79c379586f6a",
  "money_spans",  "MONEY",  "58e9be52f1b9",
  "redact_spans", "REDACT", "7b84db9925eb"
) |>
  dplyr::mutate(DirHash = as.character(fs::path(.lP$Input$DirSpanStore, .data$Pass, .data$Hash))) |>
  dplyr::select("Stem", "Pass", "DirHash")
```

**Texts.** One row per document type: where 01B keeps it, the file prefix in the package, and the release file whose
key decides which documents are published. Current reports and their amendments share one key table, because the
release lists both in `Summaries`.

```{r}
#| label: spec-text

specs_text <- tibble::tribble(
  ~Type,       ~Slug,       ~Table,           ~File,               ~Column,
  "Exhibit10", "exhibit10", "keys_contracts", "Contracts.parquet", "DocID",
  "8-K",       "8k",        "keys_summaries", "Summaries.parquet", "DocID",
  "8-KA",      "8ka",       "keys_summaries", "Summaries.parquet", "DocID",
  "CTO",       "cto",       "keys_orders",    "CtoOrders.parquet", "OrderDocID"
) |>
  dplyr::mutate(
    Dir  = as.character(fs::path(.lP$Input$DirParsed, .data$Type)),
    File = as.character(fs::path(.lP$Input$DirRelease, .data$File))
  )
```

**Replication.** One zip per stage, holding exactly what the exhibits (30), the numbers (40) and the appendix (42)
read from it, in the layout they read it in. The master index is included and the per-filing link stores are not:
the documents read the former, and the latter are rebuilt from it.

```{r}
#| label: spec-replication

specs_replication <- tibble::tribble(
  ~Zip,                           ~Paths,
  "01A-EdgarIndex.zip",           list(c("01A-EdgarIndex/GetEDGAR/MasterIndex",
                                         "01A-EdgarIndex/Output/LandingPageAll.parquet")),
  "03A-ClassifyPrepare.zip",      list("03A-ClassifyPrepare"),
  "03B-ClassifyTrainBERT.zip",    list(c("03B-ClassifyTrainBERT/runs", "03B-ClassifyTrainBERT/classification")),
  "03C-ClassifyTrainKeyword.zip", list("03C-ClassifyTrainKeyword"),
  "03D-ClassifyLLM.zip",          list("03D-ClassifyLLM"),
  "03F-ClassifyApply.zip",        list("03F-ClassifyApply/release"),
  "04A-EntityExtract.zip",        list("04A-EntityExtract/Output"),
  "04B-Rules.zip",                list(c("04B1-Rules-ORG", "04B2-Rules-GPE", "04B3-Rules-DATE", "04B4-Rules-MONEY",
                                         "04B5-Rules-REDACT")),
  "40-Numbers.zip",               list("40-Numbers")
)
```

# Connection

```{r}
#| label: connect

con <- pbd_connect(
  .threads  = .lP$Params$Threads,    # worker threads
  .memory   = .lP$Params$Memory,     # memory limit before spilling
  .dir_temp = .lP$Output$DirTemp     # where it spills
)
```

# Core

The release files and their codebooks are copied as 10 wrote them. The Stata files are not.

```{r}
#| label: core-release

stems_release <- c("Contracts", "Summaries", "Places", "TermDocs", "CtoOrders")
tab_core <- pbd_copy(
  .paths   = fs::path(.lP$Input$DirRelease, c(paste0(stems_release, ".parquet"), paste0(stems_release, "_Codebook.csv"))),
  .dir_out = fs::path(.lP$Output$DirPackage, "core")   # destination
)
pbd_report(.tab = tab_core, .title = "Release files", .note = NULL, .n = NULL)
```

The contract index is the release reduced to what a reader needs to find a contract: filer, filing, accession
number, document, type, the redaction counts, and the links to EDGAR. It is a compressed csv, so it opens in a
spreadsheet.

```{r}
#| label: core-index

tab_index <- pbd_contract_index(
  .con            = con,                                                  # DuckDB
  .path_contracts = fs::path(.lP$Input$DirRelease, "Contracts.parquet"),  # the release
  .path_out       = fs::path(.lP$Output$DirPackage, "core", "ContractIndex.csv.gz"),
  .path_stamp     = pbd_stamp_path(.lP$Output$DirStamps, "core/ContractIndex.csv.gz")  # rebuilt when the release moves
)
pbd_report(.tab = tab_index, .title = "Contract index", .note = "NoAccession must be 0.", .n = NULL)
```

The labelled sample is published twice: as the file every classifier was trained and scored on, with its folds, and
as the labels as they were collected, which 03A reads.

```{r}
#| label: core-labels

tab_labels <- pbd_labels(
  .con           = con,                                                             # DuckDB
  .path_prepared = .lP$Input$FilPrepared,                                           # 03A's file
  .path_out      = fs::path(.lP$Output$DirPackage, "core", "ClassificationLabels.parquet"),
  .path_stamp    = pbd_stamp_path(.lP$Output$DirStamps, "core/ClassificationLabels.parquet")  # rebuilt when 03A moves
)
tab_labels_raw <- pbd_copy(
  .paths   = .lP$Input$FilLabelsRaw,                                                # the collected labels
  .dir_out = fs::path(.lP$Output$DirPackage, "core")
)
tab_keywords <- pbd_copy_dir(
  .dir_in  = .lP$Input$DirKeywordTables,                                            # 03C's published tables
  .dir_out = fs::path(.lP$Output$DirPackage, "core", "keyword_tables")
)
pbd_report(.tab = tab_labels, .title = "Labelled sample", .note = NULL, .n = NULL)
pbd_report(.tab = tab_keywords, .title = "Keyword tables", .note = NULL, .n = NULL)
```

# Spans

```{r}
#| label: spans-build

tab_spans <- pbd_spans(
  .con        = con,                                       # DuckDB
  .specs      = specs_spans,                               # what to merge
  .dir_out    = fs::path(.lP$Output$DirPackage, "spans"),  # destination
  .dir_stamps = .lP$Output$DirStamps,                      # stamps
  .rel_out    = "spans",                                   # destination, relative to the package
  .rerun      = .lP$Params$Rerun                           # FALSE skips files whose inputs are unchanged
)
tab_spans_codebook <- pbd_codebook(
  .con      = con,
  .dir      = fs::path(.lP$Output$DirPackage, "spans"),
  .path_out = fs::path(.lP$Output$DirPackage, "spans", "Spans_Codebook.csv")
)
pbd_report(
  .tab   = tab_spans,
  .title = "Span files",
  .note  = "RowsOut must equal RowsIn in every row: the merge adds and drops nothing.",
  .n     = NULL
)
```

The span codebook lists every column with its type, read from the files. Its meaning column is completed in the
documentation of the published repository.

# Text

The key tables first: which documents the release refers to.

```{r}
#| label: text-keys

tab_keys <- pbd_text_keys(
  .con   = con,          # DuckDB
  .specs = specs_text    # which release file keys which document type
)
pbd_report(.tab = tab_keys, .title = "Release documents per key table", .note = NULL, .n = NULL)
```

Then one file per document type and year. The first run reads every document once and takes hours; later runs
rebuild only years whose documents or release keys changed.

```{r}
#| label: text-build

tab_text <- pbd_text(
  .con        = con,                                                  # DuckDB
  .specs      = specs_text,                                           # where each type is, and its key table
  .dir_out    = fs::path(.lP$Output$DirPackage, "text"),              # destination
  .dir_stamps = .lP$Output$DirStamps,                                 # stamps
  .rel_out    = "text",                                               # destination, relative to the package
  .extra      = list(Release = utils_dir_stamp(.dirs = unique(specs_text$File), .extra = NULL)),  # keys changed?
  .row_group  = .lP$Params$TextRowGroup,                              # documents per row group
  .rerun      = .lP$Params$Rerun                                      # FALSE skips unchanged years
)
tab_coverage <- pbd_text_coverage(
  .con     = con,
  .specs   = specs_text,
  .dir_out = fs::path(.lP$Output$DirPackage, "text")
)
pbd_report_text(.text = tab_text, .coverage = tab_coverage)
```

# Models

```{r}
#| label: models-build

tab_models <- pbd_models(
  .dir_models = .lP$Input$DirModels,                          # 03B's refits
  .dir_out    = fs::path(.lP$Output$DirPackage, "models"),    # destination
  .dir_stamps = .lP$Output$DirStamps,                         # stamps
  .rel_out    = "models",                                     # destination, relative to the package
  .rerun      = .lP$Params$Rerun                              # FALSE skips unchanged models
)
pbd_report(
  .tab   = dplyr::select(tab_models, "Zip", "Task", "Context", "Bytes", "Status"),
  .title = "Models",
  .note  = "models_index.csv maps each zip to the configuration it was trained with; deployed.parquet says which ship.",
  .n     = NULL
)
```

# LexNLP

```{r}
#| label: lexnlp-copy

tab_lexnlp <- pbd_lexnlp(
  .path_image = .lP$Input$FilLexnlpImage,                    # the archived image
  .path_lock  = .lP$Input$FilLexnlpLock,                     # its lockfile
  .dir_out    = fs::path(.lP$Output$DirPackage, "lexnlp")    # destination
)
pbd_report(.tab = tab_lexnlp, .title = "LexNLP image", .note = NULL, .n = NULL)
```

# Replication

```{r}
#| label: replication-build

tab_replication <- pbd_replication(
  .specs           = specs_replication,                            # what each zip holds
  .dir_output_root = .lP$Input$DirOutputRoot,                      # 2_output
  .dir_out         = fs::path(.lP$Output$DirPackage, "replication"),
  .dir_stamps      = .lP$Output$DirStamps,                         # stamps
  .rel_out         = "replication",                                # destination, relative to the package
  .rerun           = .lP$Params$Rerun                              # FALSE skips unchanged zips
)
pbd_report(
  .tab   = tab_replication,
  .title = "Replication zips",
  .note  = "Each zip unpacks into 2_output/ in the layout the pipeline reads.",
  .n     = NULL
)
```

# Validation

Every output against its source. A row with `Ok = FALSE` names the step to look at.

```{r}
#| label: validate-package

n_contracts <- pbd_query(
  .con = con,
  .sql = sprintf("SELECT count(*) AS n FROM read_parquet(%s)", pbd_lit(fs::path(.lP$Input$DirRelease, "Contracts.parquet")))
)$n
n_prepared <- pbd_query(
  .con = con,
  .sql = sprintf("SELECT count(*) AS n FROM read_parquet(%s)", pbd_lit(.lP$Input$FilPrepared))
)$n

tab_valid <- pbd_validate(
  .core        = tab_core,          # release copies
  .index       = tab_index,         # contract index
  .labels      = tab_labels,        # labelled sample
  .spans       = tab_spans,         # span files
  .text        = tab_text,          # text files
  .coverage    = tab_coverage,      # release documents with text
  .models      = tab_models,        # model zips
  .replication = tab_replication,   # replication zips
  .n_prepared  = n_prepared,        # rows the labels must have
  .n_contracts = n_contracts,       # rows the index must have
  .n_models    = 6L                 # refits in 03B
)
pbd_report(.tab = tab_valid, .title = "Validation", .note = "Every row must read Ok = TRUE.", .n = NULL)
```

# Deployment

The README is written first, so the manifest covers it; the manifest last, so it covers everything. Then the package
is copied to Drive, file by file, only where the copy there differs. Nothing on Drive is deleted.

The text folder is the bulk of the package. Check the free space of the Drive account before the first copy; to copy
everything else first, set `SkipDeploy = "text"`.

```{r}
#| label: deploy-readme-manifest

pbd_readme(
  .dir_package = .lP$Output$DirPackage,  # the package
  .version     = .lP$Params$Version,     # its version
  .repo_url    = .lP$Params$RepoUrl      # where the documentation is
)
tab_manifest <- pbd_manifest(
  .dir_package = .lP$Output$DirPackage,        # the package
  .path_cache  = .lP$Output$FilManifestCache   # checksums of the last run, reused where unchanged
)
tab_manifest |>
  dplyr::mutate(Folder = ifelse(grepl("/", .data$Path), sub("/.*$", "", .data$Path), ".")) |>
  dplyr::summarise(Files = dplyr::n(), Bytes = sum(.data$Bytes), .by = "Folder") |>
  pbd_report(.title = "The package", .note = NULL, .n = NULL)
```

```{r}
#| label: deploy-drive

if (is.na(pbd_drive_root())) {
  cli::cli_abort("Google Drive for desktop is not mounted under ~/Library/CloudStorage; nothing can be deployed.")
}
tab_deploy <- pbd_deploy(
  .dir_package = .lP$Output$DirPackage,   # the package
  .dir_target  = .lP$Output$DirDrive,     # the version folder on Drive
  .manifest    = tab_manifest,            # what the package holds
  .apply       = .lP$Params$Deploy,       # FALSE only reports
  .skip        = .lP$Params$SkipDeploy    # folders left for a later copy
)
tab_deploy |>
  dplyr::summarise(Files = dplyr::n(), Bytes = sum(.data$Bytes, na.rm = TRUE), .by = "Action") |>
  pbd_report(
    .title = if (.lP$Params$Deploy) "Copied to Drive" else "Would be copied to Drive",
    .note  = "Drive for desktop uploads in the background; the files are online once its menu shows no pending uploads.",
    .n     = NULL
  )
```

```{r}
#| label: deploy-close

DBI::dbDisconnect(conn = con, shutdown = TRUE)
```

Once the upload is complete, the folder `matcon-data` in Drive is shared as "Anyone with the link can view", and
that link goes into `DATA.md` of the published repository.

# Overview

```{r}
#| label: overview-summary

tibble::tibble(
  Part    = c("core", "spans", "text", "models", "lexnlp", "replication"),
  Built   = c(sum(tab_core$Status == "copied"), sum(tab_spans$Status == "built"), sum(tab_text$Status == "built"),
              sum(tab_models$Status == "built"), sum(tab_lexnlp$Status == "copied"),
              sum(tab_replication$Status == "built")),
  Current = c(sum(tab_core$Status == "current"), sum(tab_spans$Status == "current"),
              sum(tab_text$Status == "current"), sum(tab_models$Status == "current"),
              sum(tab_lexnlp$Status == "current"), sum(tab_replication$Status == "current"))
) |>
  tbl_say(.title = "What this render built, and what was already current", .n = NULL)
tbl_say(.tab = tab_valid, .title = "Validation", .n = NULL)
```

# Next

The published repository documents the package: `DATA.md` gets the Drive link and the file list, and the codebooks
get their meanings. Once the paper is accepted, the same folder is archived with a DOI.
