---
title: "Term Ambiguity: Carol's Three Questions"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

# The questions

Carol and Holger (email, 2026-09-02) asked three things about ambiguous term-to-concept mappings:

| | Question | Answered by |
|---|---|---|
| **Q1** | After all dictionary steps, can one normalized term still map to more than one final concept? How many, which, with what frequency by concept? | Part 2 |
| **Q2** | When the dictionary is applied to a report, is one occurrence of such a term counted under **each** of its concepts, or does a further rule assign it to one? | Part 3 |
| **Q3** | Of the surviving multi-mappings, how many are parent/child or otherwise related taxonomy concepts, versus economically distinct ones? | Part 4 |

`83-TermListConsistency` already carries Q1 and Q3 in referee language. This document sources 83 for
its loader, term-grain collapse and taxonomy walk, and adds what Carol actually asked for: the
term × concept table with per-concept counts (Q1), the counting rule verified on the data with an
exposure measure (Q2, new), and the pair-level classification with the hard cases printed (Q3).

## Two things that must not be mixed

- **Taxonomy.** `CID` is `GAAP:TagMod` and term matching is taxonomy-agnostic, so every term shared
  by the US GAAP and IFRS lists mechanically has two concepts. That is by design and carried by the
  `_USGAAP` / `_IFRS` suffixes downstream. Everything here is **within** taxonomy.
- **`FrqUni` is per term.** `save_dictionary_versions()` joins the term-level corpus frequency onto
  every row of the term, so a term in three concepts carries it three times. Term grain first,
  `max()` not `sum()`. This replication in the dictionary file is the same phenomenon Q2 measures in
  the frequency fact table.

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here())

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```


# Part 0: SetUp

```{r echo=FALSE}
source("_source/Initialize.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

# Console focus makes rstudioapi return "" -> .dir_main collapses to 2_output/. Fail loudly.
stopifnot(nzchar(.name_script), basename(.dir_main) == .name_script)

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))

cat("DropBox Directory: ")
(.dir_dropbox <- init_dropbox_path())
```

```{r}
library(tidyverse)
options(scipen = 999)
options(duckdb.progress_display = FALSE)
source("_source/Utils.R")
source("1_code/83-TermListConsistency.R") # substrate: tl_load_dictionary / tl_term_grain / tl_hier_*
source(.path_fun)                          # this stage

# V2-V4 is the LLM-screen ladder. The summary tables (Q1a, Q2b, Q3a, Q3b) run for all three so Carol
# can see whether the numbers are an artifact of one version; the long lists (Q1b, Q1c, Q2c, Q2d, Q3c)
# are printed for .FOCUS only. V3 is the headline dictionary.
.VERSIONS   <- c("V2", "V3", "V4")
.FOCUS      <- "V3"
.RULES      <- c("As shipped", "With disclosure demotion")
.MEM_LIMIT  <- "160GB"
.N_EXAMPLES <- 15L   # terms per taxonomy in the Q1 example table
```

```{r}
.lP <- list(
  Input = list(
    DirDictVersions = "2_output/04-AdjustData/Output/DictionaryVersions",
    DirFrequency    = "2_output/04-AdjustData/Output/FrequencyVersions",
    FilTaxUSGAAP    = file.path(.dir_dropbox, "TaxonomiesAndMatching/InputTaxonomies/USGAAPTaxonomy2024.xlsx")
  ),
  Temp   = utils_file_path(.dir_main, "Temp"),
  Output = list(
    Tables = utils_file_path(.dir_main, "Output", "Tables"),
    Xlsx   = utils_file_path(.dir_main, "Output", "TermAmbiguity-Q1Q2Q3.xlsx")
  )
)
fs::dir_create(c(.lP$Temp, .lP$Output$Tables))

tibble::tibble(
  What   = names(.lP$Input),
  Path   = unlist(.lP$Input),
  Exists = file.exists(unlist(.lP$Input)) | dir.exists(unlist(.lP$Input))
) |>
  tl_tbl(.caption = "Inputs")

stopifnot(dir.exists(.lP$Input$DirDictVersions), dir.exists(.lP$Input$DirFrequency))
```


# Part 1: Load

```{r}
dict_all <- tl_load_dictionary(.lP$Input$DirDictVersions, .VERSIONS)

dict_all |>
  dplyr::summarise(
    Assignments = dplyr::n(),
    Terms       = dplyr::n_distinct(paste(GAAP, TID)),
    Concepts    = dplyr::n_distinct(CID),
    .by         = c(Version, GAAP)
  ) |>
  dplyr::arrange(GAAP, Version) |>
  tl_tbl(.caption = "Dictionary versions as loaded (assignment grain)")
```


# Part 2: Q1 — can a term still map to more than one concept?

**Yes.** The majority vote in `.ad_apply_majority_dedup()` runs **inside** each presentation
statement (`GAAP × TagStatement × LabelMod`) and keeps the outright winner (`V1 = V0 & Prio == 1`).
Two consequences:

- A term that wins in two different statements keeps both concepts (**cross-statement**). "Income
  taxes" naming both the expense and the cash paid is the rule working.
- Inside one statement, `dense_rank` gives rank 1 to every row that ties on filing count **and**
  taxonomy depth, so an exact dead heat survives as two concepts (**within-statement**). 83 Table B
  verifies that every V1+ within-statement case is such a tie.

The disclosure-demotion step (`fM`) is computed but never read downstream, so a term winning in a
primary statement and again in Disclosures keeps both. That is a known gap (83, Table B) and a
co-author decision, not a code change.

## Q1a — how many

```{r}
tab_q1_summary <- ta_q1_summary(dict_all)
```

```{r, results='asis', echo=FALSE}
purrr::walk(sort(unique(tab_q1_summary$GAAP)), \(.g) {
  tab_q1_summary |>
    dplyr::filter(GAAP == .g) |>
    dplyr::select(-GAAP) |>
    tl_tbl(
      .caption = sprintf("Q1a - Terms mapping to more than one concept (%s)", .g),
      .pct     = c("ShareMulti", "CorpusShareMulti", "ShareConceptsTouched"),
      .digits  = 3L
    ) |>
    print()
  cat("\n\n")
})
```

**Reading guide.** `ShareMulti` is the term-count share Carol asked for; `CorpusShareMulti` is the
one to quote next to it (share of matched corpus occurrences that sit on a multi-mapped term).
`nWithin` is the referee-facing number. `ShareConceptsTouched` is the reach into the concept list.

## Q1b — which terms, with frequency by concept

The only frequency that **can** be split by concept is the label-file count (`nLabelFiles`: how many
Exhibit 101 / iXBRL label files attach this label to this tag). It is what the vote ranked on.
`ShareLabelFiles` is its share within the term. The corpus frequency (`CorpusFrq`) is per term and
cannot be split — that is precisely Q2.

Top `r .N_EXAMPLES` multi-mapped terms per taxonomy by corpus frequency, at `r .FOCUS` (the headline dictionary):

```{r}
tab_q1_examples <- ta_q1_examples(dict_all, .FOCUS, .n = .N_EXAMPLES, .kind = c("Within", "Cross"))
```

```{r, results='asis', echo=FALSE}
purrr::walk(sort(unique(tab_q1_examples$GAAP)), \(.g) {
  tab_q1_examples |>
    dplyr::filter(GAAP == .g) |>
    dplyr::select(-Version, -GAAP, -TagDepth) |>
    tl_tbl(
      .caption = sprintf("Q1b - Most frequent multi-mapped terms and their concepts (%s, %s)", .g, .FOCUS),
      .pct     = "ShareLabelFiles",
      .digits  = 1L
    ) |>
    print()
  cat("\n\n")
})
```

## Q1c — every within-statement case, in full

These are the cases that are not mechanically forced by the per-statement vote. Short enough to read
line by line.

```{r}
tab_q1_within <- ta_q1_examples(dict_all, .FOCUS, .n = NULL, .kind = "Within")
cli::cli_alert_info("{dplyr::n_distinct(paste(tab_q1_within$GAAP, tab_q1_within$Term))} within-statement terms at {(.FOCUS)}")
```

```{r, results='asis', echo=FALSE}
tab_q1_within |>
  dplyr::select(-Version, -Kind) |>
  tl_tbl(
    .caption = sprintf("Q1c - Within-statement multi-mappings, all cases (%s)", .FOCUS),
    .pct     = "ShareLabelFiles",
    .digits  = 1L
  )
```


# Part 3: Q2 — how is one occurrence counted?

## The answer, from the code path

There is **no assignment rule at application time**. The concept is not known when the term is
counted:

1. `03-CountTerms` matches the term list against report tokens and stores positions at **`TID`**
   grain (`count_positions()`); the term list is `distinct(TID, UID, Term)`, no concept.
2. `04-AdjustData` summarises to `(DocID, TID) → FrqAll, FrqUni` (`.sf_summarize()`). Still no
   concept column.
3. `07B-extStandardization` attaches the concept with
   `frq_ |> inner_join(dict_, by = join_by(TID))` in `calc_rel_dplyr()`, where `dict_` is
   `distinct(CID, TID)` for the version.

An inner join on a key that is not unique on the right-hand side **replicates** the left row. A term
in *k* concepts therefore contributes its **full** `FrqUni` to each of the *k* `(Firm, Year, CID)`
cells. Nothing is split, nothing is assigned; the same occurrence is counted *k* times.

`FrqUni` itself (the containment flag in `.sf_flag_contained_db()`) is a different mechanism: it
prevents *nested* strings — "net income" inside "net income attributable to parent" — from being
counted twice at the **term** level. It does not touch the term → concept fan-out.

The three chunks below verify this on the data rather than asserting it.

## Q2a — fact grain on disk

```{r}
con <- ta_q2_connect(.MEM_LIMIT, .lP$Temp)
fil_frq <- ta_frq_path(.lP$Input$DirFrequency, .FOCUS)

tab_q2_grain <- purrr::map(.VERSIONS, \(.v) {
  ta_q2_fact_grain(con, ta_frq_path(.lP$Input$DirFrequency, .v)) |>
    dplyr::mutate(Version = .v, .before = 1L)
}) |>
  dplyr::bind_rows()

tab_q2_grain |>
  tl_tbl(.caption = "Q2a - Frequency fact tables (FullRep)")
```

`GrainIsDocTerm = yes` and `HasConceptCol = no` is the whole argument in two cells.

## Q2b — exposure

Three layers, each one step closer to what the measures consume:

- **Term level** — share of matched occurrences that sit on a multi-mapped term.
- **Concept level** — the same after the replicating join. `InflationFactor` is concept-level mass
  over term-level mass: exactly 1 if no term were multi-mapped.
- **Cell level** — `(Firm, Year, CID)` cells that contain at least one multi-mapped term, and the
  average share of a cell's `Rel` mass those terms carry. `Rel` is what eCBS and iCBS are built from,
  so `MeanRelMassMulti` is the closest thing to "how much of the measure is exposed".

For every version, two rows per taxonomy: the dictionary **as shipped**, and the **counterfactual
with the disclosure demotion applied** (`fM == 0`, the documented second step of the prioritization that
`create_dictionary_versions()` never reads — 83, Table B). The gap between them is what that one
switch would buy.

Version x rule grid. Each cell is one pass over that version's frequency file; V2 is the expensive
one (its dictionary is ~10x V3's) -- budget minutes, not seconds.

```{r}
grid_q2 <- tidyr::expand_grid(Version = .VERSIONS, Rule = .RULES)

tab_q2_exposure <- purrr::pmap(grid_q2, \(Version, Rule) {
  ta_q2_exposure(con, ta_frq_path(.lP$Input$DirFrequency, Version), dict_all, Version, .rule = Rule)
}) |>
  dplyr::bind_rows() |>
  dplyr::arrange(GAAP, Version, Rule)
```

```{r, results='asis', echo=FALSE}
purrr::walk(sort(unique(tab_q2_exposure$GAAP)), \(.g) {
  tab_q2_exposure |>
    dplyr::filter(GAAP == .g) |>
    dplyr::select(-GAAP) |>
    tl_tbl(
      .caption = sprintf("Q2b - Exposure of frequency mass to multi-mapped terms (%s, FullRep)", .g),
      .pct     = c("ShareDocTermMulti", "ShareTermMassMulti", "ShareConceptMassMulti",
                   "ShareCellsTouched", "MeanRelMassMulti"),
      .digits  = 3L
    ) |>
    print()
  cat("\n\n")
})
```

## Q2c — which concepts absorb it

One row per concept with any replicated mass; `ShareMassMulti` is the share of the concept's own
frequency mass that arrives via multi-mapped terms. `DbMatch` is attached where the version file
carries it, because a contaminated concept only matters for Tables 5–7 if it maps to a database item.

```{r}
tab_q2_concepts <- ta_q2_concept_exposure(con, fil_frq, dict_all, .FOCUS,
                                          .dir_dict = .lP$Input$DirDictVersions, .n = 40L)
```

```{r, results='asis', echo=FALSE}
purrr::walk(sort(unique(tab_q2_concepts$GAAP)), \(.g) {
  tab_q2_concepts |>
    dplyr::filter(GAAP == .g) |>
    dplyr::select(-GAAP, -CID) |>
    tl_tbl(
      .caption = sprintf("Q2c - Concepts most exposed to multi-mapped terms (%s, %s, top 40)", .g, .FOCUS),
      .pct     = "ShareMassMulti",
      .digits  = 1L
    ) |>
    print()
  cat("\n\n")
})
```

## Q2d — one worked example

The most frequent multi-mapped US GAAP term, in the report where it appears most often: the fact
row as stored, then the same row after the 07B join. Identical `FrqUni` on every joined line is the
"counted under each concept" answer, made visible.

```{r}
lst_q2_example <- ta_q2_worked_example(con, fil_frq, dict_all, .FOCUS, .gaap = "USGAAP")

lst_q2_example$Fact |>
  tl_tbl(.caption = "Q2d - Fact row as stored (DocID x TID)")

lst_q2_example$Joined |>
  tl_tbl(.caption = "Q2d - The same row after the 07B join on TID")
```

```{r}
DBI::dbDisconnect(con, shutdown = TRUE)
```


# Part 4: Q3 — related or economically distinct?

`Taxonomies.parquet` cannot answer this (83, Part 5: the build drops the abstract scaffolding, so it
is a forest of orphaned leaves). The source spreadsheet ships the presentation arcs explicitly;
ancestor sets are walked **within** each presentation network and unioned afterwards.

**US GAAP only.** The IFRS source has no parent column and no hierarchy to test against. IFRS
multi-mappings appear in Q1 with the within/cross split and nothing more — and saying so beats
proxying it.

Three relations, in decreasing order of how defensible they are:

- **Nested** — one concept is an ancestor of the other. A total and one of its components.
- **Sibling** — neither descends from the other, but they share an ancestor (usually an abstract
  heading): "both of these are revenue lines".
- **Unrelated** — no shared ancestor in any network. The residual that is hard to defend.

```{r}
tab_q3_pairs <- tab_q3_summary <- tab_q3_terms <- tab_q3_unrelated <- NULL

if (file.exists(.lP$Input$FilTaxUSGAAP)) {
  edges_usgaap <- tl_hier_edges(.lP$Input$FilTaxUSGAAP)
  anc_usgaap   <- tl_hier_ancestors(edges_usgaap)

  tab_q3_pairs     <- purrr::map(.VERSIONS, \(.v) ta_q3_pairs(dict_all, anc_usgaap, .v)) |>
    dplyr::bind_rows()
  tab_q3_summary   <- ta_q3_summary(tab_q3_pairs)
  tab_q3_terms     <- ta_q3_terms(tab_q3_pairs)
  tab_q3_unrelated <- dplyr::filter(tab_q3_pairs, Version == .FOCUS, Relation == "Unrelated")
} else {
  cli::cli_alert_warning("Source taxonomy not reachable - Q3 skipped")
}
```

## Q3a — pairs

Three panels in one table: by within/cross kind, pooled, and — the one that carries the finding — by
**pair type**: whether both concepts sit in primary statements (01–06), one is in Disclosures /
Deprecated (07–08), or both are. On the first render every `Unrelated` pair had a 07/08 concept on
at least one side and every primary–primary pair was `Sibling` or `Nested`. If that holds, the
"economically distinct" residual is the same disclosure copies the `fM` rule would demote, plus
deprecated tags paired with their successors — not two economic ideas sharing one word.

```{r, results='asis', echo=FALSE}
if (!is.null(tab_q3_summary)) {
  purrr::walk(.VERSIONS, \(.v) {
    tab_q3_summary |>
      dplyr::filter(Version == .v) |>
      dplyr::select(-Version) |>
      tl_tbl(
        .caption = sprintf("Q3a - Taxonomy relation between the concepts a term straddles (US GAAP, %s)", .v),
        .pct     = "SharePairs",
        .digits  = 1L
      ) |>
      print()
    cat("\n\n")
  })
} else {
  cat("\n\n*Q3 not produced: the source taxonomy spreadsheet was not reachable.*\n\n")
}
```

## Q3b — terms

A term with three concepts has three pairs that may disagree; here a term is classified by its
**least defensible** pair. `CorpusShare` is over all multi-mapped US GAAP terms, so it says how much
of the exposed corpus mass sits in each bucket.

```{r, results='asis', echo=FALSE}
if (!is.null(tab_q3_terms)) {
  tab_q3_terms |>
    tl_tbl(
      .caption = "Q3b - Multi-mapped terms by least defensible relation (US GAAP, V2-V4)",
      .pct     = c("ShareTerms", "CorpusShare"),
      .digits  = 1L
    ) |>
    print()
}
```

## Q3c — the Unrelated pairs, in full

The number to watch, printed so Carol and Holger can judge each line themselves. Many of these will
turn out to be the same economic item placed in two presentation networks the walk cannot connect;
some will be genuine polysemy. That call is a reading exercise, not a computation.

```{r, results='asis', echo=FALSE}
if (!is.null(tab_q3_unrelated)) {
  cli::cli_alert_info("{nrow(tab_q3_unrelated)} unrelated pairs over {dplyr::n_distinct(tab_q3_unrelated$TID)} terms")
  tab_q3_unrelated |>
    dplyr::select(-Version, -GAAP, -TID, -Relation, -SameStatement) |>
    tl_tbl(
      .caption = sprintf("Q3c - Concept pairs with no shared ancestor (US GAAP, %s)", .FOCUS),
      .digits  = 0L
    ) |>
    print()
}
```


# Part 5: Saved output

Parquet per table under `Output/Tables/`, plus one workbook for Carol with the same sheets.

```{r}
lst_out <- list(
  "Q1a-Summary"        = tab_q1_summary,
  "Q1b-Examples"       = tab_q1_examples,
  "Q1c-WithinFull"     = tab_q1_within,
  "Q2a-FactGrain"      = tab_q2_grain,
  "Q2b-Exposure"       = tab_q2_exposure,
  "Q2c-ConceptExposure" = tab_q2_concepts,
  "Q2d-ExampleJoined"  = lst_q2_example$Joined,
  "Q3a-PairSummary"    = tab_q3_summary,
  "Q3b-TermSummary"    = tab_q3_terms,
  "Q3c-UnrelatedPairs" = tab_q3_unrelated,
  "Q3-AllPairs"        = tab_q3_pairs
)

ta_export(lst_out, .lP$Output$Tables, .lP$Output$Xlsx)
```


# Part 6: Numbers for the reply

Plain-language sentences with the headline figures filled in, so the email can be written without
re-reading the tables. Check the wording against the tables before sending; this is a draft, not a
verdict.

```{r, results='asis', echo=FALSE}
q1_ <- dplyr::filter(tab_q1_summary, Version == .FOCUS)
q2_  <- dplyr::filter(tab_q2_exposure, Version == .FOCUS, Rule == "As shipped")
q2c_ <- dplyr::filter(tab_q2_exposure, Version == .FOCUS, Rule == "With disclosure demotion")

cat(sprintf("\n\n**Q1 (%s).** ", .FOCUS))
purrr::pwalk(q1_, \(...) {
  r_ <- list(...)
  cat(sprintf(
    "%s: %s of %s terms (%s) map to more than one concept at %s; they carry %s of matched corpus occurrences. %s are within-statement (exact ties), %s cross-statement. %s of %s concepts contain at least one such term. ",
    r_$GAAP, tl_int(r_$nMulti), tl_int(r_$nTerms), tl_pct(r_$ShareMulti), .FOCUS,
    tl_pct(r_$CorpusShareMulti), tl_int(r_$nWithin), tl_int(r_$nCross),
    tl_int(r_$nConceptsTouched), tl_int(r_$nConcepts)
  ))
})

cat(sprintf("\n\n**Q2 (%s).** An occurrence of a multi-mapped term is counted in full under each of its concepts; there is no assignment rule at application time (the join in 07B replicates the term row). ", .FOCUS))
purrr::pwalk(q2_, \(...) {
  r_ <- list(...)
  cat(sprintf(
    "%s: %s of matched occurrences sit on multi-mapped terms; after the join concept-level mass is %.4f times term-level mass; %s of firm-year-concept cells contain such a term, and on average %s of a cell's Rel mass comes from them. ",
    r_$GAAP, tl_pct(r_$ShareTermMassMulti), r_$InflationFactor,
    tl_pct(r_$ShareCellsTouched), tl_pct(r_$MeanRelMassMulti)
  ))
})
if (nrow(q2c_) > 0L) {
  cat("With the disclosure demotion applied (fM == 0), the same figures would be: ")
  purrr::pwalk(q2c_, \(...) {
    r_ <- list(...)
    cat(sprintf(
      "%s: %s of occurrences on multi-mapped terms, inflation %.4f, %s of cells touched, %s mean Rel mass. ",
      r_$GAAP, tl_pct(r_$ShareTermMassMulti), r_$InflationFactor,
      tl_pct(r_$ShareCellsTouched), tl_pct(r_$MeanRelMassMulti)
    ))
  })
}

if (!is.null(tab_q3_terms)) {
  q3_ <- tab_q3_terms |>
    dplyr::filter(Version == .FOCUS) |>
    dplyr::summarise(nTerms = sum(nTerms), CorpusShare = sum(CorpusShare), .by = WorstRelation)
  cat(sprintf("\n\n**Q3 (US GAAP only, %s).** By least defensible pair: ", .FOCUS))
  purrr::pwalk(q3_, \(...) {
    r_ <- list(...)
    cat(sprintf("%s: %s terms (%s of exposed corpus mass); ", r_$WorstRelation, tl_int(r_$nTerms), tl_pct(r_$CorpusShare)))
  })
  unrel_ <- dplyr::filter(tab_q3_pairs, Version == .FOCUS, Relation == "Unrelated")
  cat(sprintf(
    "Of the %s Unrelated pairs, %s involve a Disclosures/Deprecated concept and %s are primary-primary. ",
    tl_int(nrow(unrel_)), tl_int(sum(unrel_$PairType != "Primary - Primary")),
    tl_int(sum(unrel_$PairType == "Primary - Primary"))
  ))
  cat("IFRS has no presentation hierarchy in the source and is reported with the within/cross split only.")
}
cat("\n\n")
```


# Still open

- **The `fM` decision is now a measurement decision, not a tidiness one.** Q2b's counterfactual row
  and Q3a's pair-type panel say what the disclosure demotion buys: it targets exactly the pairs that
  are `Unrelated` in the taxonomy, and leaves the primary–primary fan-out (all `Sibling` / `Nested`)
  untouched. It cascades `04 → 07A → 07D` and invalidates 81–83; co-author decision.
- **Deprecated tags.** The Disc/Dep–Disc/Dep `Unrelated` pairs are mostly a deprecated element next
  to its successor (`...EstimatedUsefulLives` / `...UsefulLife`). The demotion cannot touch these
  when no primary copy exists; a deprecation-successor map from the taxonomy would.
- **The obvious robustness check** Carol will ask for next: drop all multi-mapped terms (or keep the
  within-statement ties only) and rerun Tables 5–7. `Q2c` says how much of the concept mass that
  removes; the rerun itself lives in 07B, not here.
- **Q3 Unrelated pairs** need a reading pass. Two presentation networks the walk cannot connect are
  not the same thing as two economic ideas.
- **CURRENT-PROJECT-STATUS-V3.md** — add the Q2 counting rule as a documented design fact once
  the numbers are confirmed.
