---
title: "Entity Rules -- Signing, End and Duration (04B3)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false

here::i_am("1_code/_Commons/_Initialize.R")
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120, mc.table_mode = "console")
```

```{r}
#| label: load-libraries
#| echo: false

source(here::here("1_code", "_Commons", "_Initialize.R"), encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Utils.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_NER.R"),        encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Plots.R rebuilds its level registry empty every time it is sourced, so any
# library that registers a vocabulary must follow it -- and both _Entity.R and this document's own
# file do.
source(here::here("1_code", "_Commons", "_Plots.R"),      encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Tables.R"),     encoding = "UTF-8")
source(here::here("1_code", "_Commons", "_Entity.R"),     encoding = "UTF-8")

# 03A owns the contract-type vocabulary; 04A owns the sample, the canonical text and the stores.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = \(.s) source(
    file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
    encoding = "UTF-8"
  )
)

.name_script <- "04B3-Rules-DATE"

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File:  ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B3-Rules-DATE.R
))

source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document turns parsed dates and stated terms into a contract duration.

## The number that made it necessary

Table 3 Panel B reports contract duration with a mean of 2.38 years, a median of 0.40 and a standard
deviation of **40.78**, under a stated cap of **30 years**. A variable supported on `[0, 30]` cannot
have a standard deviation above 15 -- the maximum, reached by a 50/50 split on the endpoints. So the
cap is not applied to what is tabulated, or something is in the wrong unit.

Referee 1 saw the symptom and asked whether there were *"errors in identifying dates affecting the
right tail"*. The published definition is therefore the **first row of the sweep** rather than
something this document replaces sight unseen, and `SdOverCap` appears in every row: it cannot exceed
one half.

## The stated term now comes from the store

An earlier version of this file carried `dte_term()`, which re-implemented stated-term extraction in
R with its own regex over the canonical text. It worked and it could never leave the sample: 04C
writes no corpus text file -- the text is 1.19 million separate parquets in the mirror -- so any
variable built on it stopped at 4,398 documents.

`dateregex-v3` emits **TERM as a second label** from the same pass that produces DATE, so terms now
arrive in the store with offsets, a parsed number, a unit and the name of the pattern that found
them. On the corpus that is 2,831,912 spans over 625,260 documents.

**The extractor states; the rule decides.** The engine emits every stated period it can find and
records which pattern found it in `LabelRaw`; this document chooses which of those count as a
contract duration. That was already the shape of the old `.term_kinds` argument -- it is now a filter
on provenance the extractor supplied rather than on a distinction re-derived in R.

**And the unit replaces the pattern as the demotion rule.** The old code split "term of" from "period
of" and demoted the second, because pooling them put 127 documents at thirty days. The pattern was a
proxy for what the number and the unit say directly: thirty **days** is a notice window, five
**years** is a term. Both dials are swept.

## The three things a contract can say about when it ends, and a fourth that is not silence

1. A **stated term** -- "for a period of five (5) years from the Effective Date". A duration with no
   end date at all, and once the start is known it is arithmetic. This is what the contract *says*,
   against a maximum over dates it happens to mention, so it outranks the other two.
2. A **dated termination** -- a future date with a termination cue beside it.
3. **Nothing**, in which case the farthest future date is taken and recorded as such. That is the
   published definition, and it picks up a patent expiry and a perpetuity boilerplate along with the
   contract's own end.
4. An **open-ended term** -- "shall continue until terminated". The engine emits this with
   `TermYears` null: a stated term of *unknown* length rather than an absent one. It gets its own
   `DurationSource` and a missing duration, because a perpetual agreement has no duration and saying
   so is a finding. Under the old code it fell through to the farthest future date, which is exactly
   the wrong answer for the one drafting form that says the contract will not end.

`DurationSource` distinguishes all four. **The cap drops, it does not winsorise:** a duration of
exactly thirty years that is not one is worse than a missing value.

## Which family supplies the dates is the right-tail test

matcon's patterns require a year in the text by construction -- four digits in nine of them, two in
one -- so there is no partial match to complete and no clock to complete it from. LexNLP's grammar
has no such constraint, and `dateregex.py` measured the consequence on this sample: **of its spans
carrying no written year, 76% resolve to the future at a median of 11.6 years out, and 80.8% of all
dates more than fifteen years out are year-less.** Section numbers and exhibit references are what
that produces.

So the duration is computed per family and pooled, with `SdOverCap` beside each. That is the direct
answer to the referee's question rather than an assurance about it.

## No region rule

Dates are not bimodal the way organisations are. Over this sample the head is 72.8% pre-filing and
the *tail* is 73.0% -- identical -- against a deep U for organisations with 22.6% and 25.2% in the
two ends. Region separates the head from the middle and separates nothing else, and excluding the
tail from the end search cost 2.5 points of coverage and left the standard deviation unchanged. So
the end rule reads the whole document, and the head restriction on the **start** is a swept row.

## What is recomputed, and what is not

Everything, on every render, and the description exactly once. An earlier version computed it per
specification -- eight reads of the canonical text and eight passes of the cue search over 102,005
spans, to produce eight identical tables. The fields that would break the sharing are asserted in
`dte_sweep()` rather than assumed.

## How results are reported

Console tables throughout, three figures in `# Overview`. Every duration table carries `SdOverCap`.

## Where things are written

Three artifacts: the date spans with their region and cue, the stated terms, and one row per document
with the duration and its source.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Input = list(
    Text = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output", "sample_text.parquet"
    ),
    Store = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "04A-EntityExtract"),
      "Output"
    ),
    Prepared = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    ),
    Register = fs::path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "02B-Register"),
      "Output", "Documents.parquet"
    )
  ),
  Output = list(
    Dates    = utils_file_path(.dir_main, "Output", "roles_date.parquet"),   # per date span
    Terms    = utils_file_path(.dir_main, "Output", "terms_stated.parquet"), # per stated term
    Duration = utils_file_path(.dir_main, "Output", "duration_doc.parquet")  # per document
  ),
  Params = list(
    # BOTH FAMILIES EMIT DATES; only matcon emits TERM. Which family the duration reads is a swept
    # axis rather than a setting, because it is the right-tail test.
    Families = c("lexnlp", "matcon"),
    ReadN    = 10L,
    ReadCtx  = 200L,
    CheckN   = 500L,
    Seed     = 42L
  )
)

# The specification carried into the released artifacts.
.lP$Params$Spec <- dte_spec(
  .start        = "latest",   # latest date at or before the filing, wherever it sits
  .end          = "term",     # stated term, then dated termination, then farthest future date
  .family       = "matcon",   # the family whose patterns require a year in the text
  .cue_win      = 120L,
  .cap_years    = 30,         # dropped, not winsorised
  .require_year = FALSE,      # near-vacuous under matcon; swept where it is not
  .term_kinds   = c("UnitTerm", "ContinueFor", "PeriodOf", "Anniversary"),
  .term_floor   = 0           # swept; the unit rather than the pattern is the demotion rule
)

# THE PUBLISHED DEFINITION IS THE FIRST ROW, uncapped and pooled, so the number this document exists
# to explain is reproduced before anything replaces it. Every later row differs from its neighbour in
# one thing.
.lP$Params$Specs <- list(
  dte_spec(.start = "filed",  .end = "any",  .family = "pooled", .cap_years = Inf,
           .label = "published (uncapped)"),
  dte_spec(.start = "filed",  .end = "any",  .family = "pooled", .cap_years = 30),

  # The right-tail test: the same rule over one family at a time.
  dte_spec(.start = "filed",  .end = "any",  .family = "lexnlp", .cap_years = Inf,
           .label = "lexnlp (uncapped)"),
  dte_spec(.start = "filed",  .end = "any",  .family = "matcon", .cap_years = Inf,
           .label = "matcon (uncapped)"),
  dte_spec(.start = "filed",  .end = "any",  .family = "lexnlp", .cap_years = Inf,
           .require_year = TRUE, .label = "lexnlp year-only (uncapped)"),

  dte_spec(.start = "latest", .end = "any",  .family = "matcon", .cap_years = 30),
  dte_spec(.start = "head",   .end = "any",  .family = "matcon", .cap_years = 30),
  dte_spec(.start = "latest", .end = "cue",  .family = "matcon", .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .family = "matcon", .cap_years = 30),

  # The two term dials, one at a time.
  dte_spec(.start = "latest", .end = "term", .family = "matcon", .cap_years = 30,
           .term_kinds = c("UnitTerm", "ContinueFor", "PeriodOf", "Anniversary", "UnitPeriod"),
           .label = "term / every pattern"),
  dte_spec(.start = "latest", .end = "term", .family = "matcon", .cap_years = 30,
           .term_floor = 1, .label = "term / at least a year"),

  dte_spec(.start = "latest", .end = "term", .family = "pooled", .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .family = "matcon", .cap_years = 10),
  dte_spec(.start = "latest", .end = "term", .family = "matcon", .cap_years = Inf)
)

fs::dir_create(fs::path_dir(.lP$Output$Dates))

tibble::tibble(
  Input  = names(.lP$Input),
  Path   = purrr::map_chr(.lP$Input, \(.p) fs::path_rel(.p, start = here::here())),
  Exists = purrr::map_lgl(.lP$Input, \(.p) fs::file_exists(.p) || fs::dir_exists(.p))
) |>
  tbl_say(.title = "Every input resolves before anything is computed")
```

# Input

```{r}
#| label: build-keys

tab_keys <- ent_anchor_keys(
  .path_prepared = .lP$Input$Prepared,   # 03A: DocID, ClassDetailed, AmendType, Fold
  .path_register = .lP$Input$Register,   # 02B: CIK, CompanyName, and DateFiled, which is the anchor
  .path_landing  = NULL,                 # the addresses are 04B2's
  .quiet         = FALSE
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)
```

**`DateFiled` is the one external fact this document has**, and every duration is measured from it or
against it. A document the register does not carry has no filing date, so it can have no start and no
side, and the coverage report above is where that count appears.

```{r}
#| label: load-dates

tab_dates <- dte_load(
  .dir_store = .lP$Input$Store,       # the directory; the family is the filename
  .lens      = tab_lens,
  .families  = .lP$Params$Families,   # both; the duration picks one per specification
  .quiet     = FALSE
)

tab_parsed <- dplyr::filter(tab_dates, .data$Parsed)

dte_report_parse(.dates = tab_dates)
```

```{r}
#| label: inspect-daymonth

tab_dm <- dte_daymonth(.dates = tab_dates)

dte_report_daymonth(.tab = tab_dm)
```

```{r}
#| label: load-terms

tab_terms <- dte_load_terms(
  .dir_store = .lP$Input$Store,   # matcon only; LexNLP emits no TERM label
  .lens      = tab_lens,
  .quiet     = FALSE
)

dte_report_terms(
  .terms  = tab_terms,
  .n_docs = nrow(tab_keys),
  .spec   = .lP$Params$Spec       # so the table says which patterns this run admits
)
```

**This is the seam that moved.** The terms used to be a regex in this file reading the canonical
text; they are now spans in the store with offsets, a number, a unit and a pattern name. Three things
follow. The rule can be applied to the corpus, which the old one structurally could not. A term can
be positioned and read back in context like every other entity. And `OpenEnded` becomes expressible
-- a stated term of unknown length, which no single number can represent.

# Construction

```{r}
#| label: describe-dates
# COMPUTED ONCE. Every specification below reads the same region, gap and cue, so describing per
# specification would re-read the canonical text and re-run the cue search over 102,005 spans to
# produce the identical table eight times -- which is what made an earlier version take six minutes.
tab_desc <- dte_describe(
  .dates     = tab_parsed,
  .keys      = tab_keys,
  .path_text = .lP$Input$Text,
  .spec      = .lP$Params$Spec
)

dte_report_year(.dates = tab_desc)
```

```{r}
#| label: apply-base-spec
tab_dur <- dte_duration(
  .dates = tab_desc,
  .terms = tab_terms,
  .keys  = tab_keys,
  .spec  = .lP$Params$Spec   # the cascade carried into the artifacts
)

dte_report_region(.dates = tab_desc)
```

```{r}
#| label: inspect-cues
tab_cues <- dte_cue_hits(.dates = tab_desc)

dte_report_cues(.tab = tab_cues)
```

A term scoring near a lift of one is a word the language uses for other things and is carrying no
information; it comes out of the list rather than getting an explanation.

## Coverage of the end statement

```{r}
#| label: inspect-nofuture
tab_nofut <- dte_nofuture(.dur = tab_dur)

dte_report_nofuture(.tab = tab_nofut)
```

# Selection

```{r}
#| label: sweep-specs
tab_sweep <- dte_sweep(
  .desc  = tab_desc,            # described once, above
  .terms = tab_terms,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

dte_report_sweep(.tab = tab_sweep)
```

The first row is the published definition. The level it reports will not match Table 3 Panel B and
should not be expected to: this is a hand-classified sample balanced across twelve contract types
and that table is the corpus, which is dominated by employment exhibits. **The like-for-like
comparison is 04D**, and until then the row is here to show what the definition does, not to
reconcile with a published figure.


# Results

```{r}
#| label: report-class
dte_report_class(.dur = tab_dur)
```

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_desc,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every described span carries a parsed value",
    "Documents carrying exactly one duration row",
    "No released duration is negative",
    "No released duration exceeds the cap",
    "Every term-sourced duration has a stated term",
    "Every cue-sourced duration has a cued future date"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_desc$DateValue)),
    dplyr::n_distinct(tab_dur$DocID),
    sum(tab_dur$DurationYears >= 0, na.rm = TRUE),
    sum(tab_dur$DurationYears <= .lP$Params$Spec$CapYears, na.rm = TRUE),
    sum(!is.na(tab_dur$TermYears[tab_dur$DurationSource == "term"])),
    sum(tab_dur$NCued[tab_dur$DurationSource == "cue"] > 0L)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_desc),
    nrow(tab_dur),
    sum(!is.na(tab_dur$DurationYears)),
    sum(!is.na(tab_dur$DurationYears)),
    sum(tab_dur$DurationSource == "term"),
    sum(tab_dur$DurationSource == "cue")
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

Rows four and five are what Table 3 Panel B could not satisfy. They hold here by construction -- a
negative or over-cap duration is set to missing rather than released -- which is why the count of
what was removed sits in the sweep rather than being left implicit. The last two rows check that
`DurationSource` says what actually happened, which is the one column a consumer will filter on.

# Robustness

```{r}
#| label: read-terms

# A TERM CAN BE READ IN CONTEXT NOW, and that is the migration paying for itself. The old dte_term()
# returned the matched text and no offsets, so the only thing this block could do was print a table
# of strings. A stated term is a span like any other, so it goes through the same reader every other
# entity uses -- and the surrounding sentence is what says whether "period of thirty days" is the
# contract's duration or its notice provision.
ent_read_spans(
  .tab       = dplyr::filter(tab_terms, .data$TermKind %in% .lP$Params$Spec$TermKinds),
  .path_text = .lP$Input$Text,
  .col_start = "TermStart",
  .col_stop  = "TermStop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("TermKind", "TermN", "TermUnit", "TermYears"),
    .title = "Admitted terms, in the sentence that states them"
  )
```

```{r}
#| label: read-terms-excluded

# THE PATTERNS THE RULE REFUSES, read for the same reason the admitted ones are. UnitPeriod is
# excluded on the argument that a "thirty (30) day period" is a notice, a cure or a payment window --
# and that argument is only worth anything if the text agrees with it.
ent_read_spans(
  .tab       = dplyr::filter(tab_terms, !.data$TermKind %in% .lP$Params$Spec$TermKinds,
                             !.data$IsOpen),
  .path_text = .lP$Input$Text,
  .col_start = "TermStart",
  .col_stop  = "TermStop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("TermKind", "TermN", "TermUnit", "TermYears"),
    .title = "Excluded patterns -- is a period of days a duration or a notice window"
  )
```

```{r}
#| label: read-terms-open

# THE OPEN-ENDED FORM, which carries no number at all. These documents now report no duration and
# say why, where the old code sent them to the farthest future date -- the wrong answer for the one
# drafting form that states the contract will not end.
ent_read_spans(
  .tab       = dplyr::filter(tab_terms, .data$IsOpen),
  .path_text = .lP$Input$Text,
  .col_start = "TermStart",
  .col_stop  = "TermStop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("TermKind", "TermSpan"),
    .title = "Open-ended terms -- a stated term of unknown length"
  )
```

```{r}
#| label: read-cued-end
ent_read_spans(
  .tab       = dplyr::filter(tab_desc, .data$HasEndCue, .data$Side == "after filing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("DateValue", "GapDays", "Region"),
    .title = "Future dates carrying a termination cue"
  )
```

```{r}
#| label: read-uncued-far
# The dates the published definition takes and the cascade declines: far future, no termination
# language anywhere near them, no stated term in the document. A patent expiry, a statutory deadline
# and a perpetuity boilerplate should be visible here.
ent_read_spans(
  .tab       = tab_desc |>
    dplyr::filter(!.data$HasEndCue, .data$Side == "after filing", .data$GapDays > 365L * 15L,
                  !.data$DocID %in% tab_terms$DocID),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("DateValue", "GapDays", "Region", "HasYear"),
    .title = "Far future dates with no cue and no stated term"
  )
```

```{r}
#| label: read-no-year
# The spans whose year the parser supplied. This is the block that says whether the right tail is
# contract language or section numbering -- "Section 3-1", "Exhibit 10-15", "10-35 Second" all parse
# to a date in the current year and none of them is one.
ent_read_spans(
  .tab       = dplyr::filter(tab_desc, !.data$HasYear, .data$Side == "after filing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 10L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "DateValue", "GapDays"),
    .title = "Spans with no written year, parsed into the future"
  )
```

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_desc, -dplyr::any_of("Before")), .lP$Output$Dates)
arrow::write_parquet(tab_terms, .lP$Output$Terms)
arrow::write_parquet(tab_dur, .lP$Output$Duration)

tibble::tibble(
  Artifact = c("Date spans with region, gap and cue",
               "Terms stated in words, per document",
               "Start, end, duration and source, per document"),
  Path     = c(.lP$Output$Dates, .lP$Output$Terms, .lP$Output$Duration)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B3")
```

The term file is released separately because it is evidence in its own right: a contract's stated
term is a fact about the contract whether or not this document's cascade happens to use it.

# Overview

```{r}
#| label: fig-gap
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of the gap between a date and the filing, in years, by region,
#|   clipped at ten years either side. The dashed rule is the filing date. The head and the tail
#|   nearly coincide, which is why no end rule reads region."
dte_plot_gap(.dates = tab_desc)
```

```{r}
#| label: fig-source
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "What the end date rests on, by contract type, as shares within each type. TERM and CUE
#|   are things the contract said; MAXDATE is a maximum over dates it merely mentions, and NONE is a
#|   contract that states no end at all."
dte_plot_source(.dur = tab_dur)
```

```{r}
#| label: fig-class
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Median contract duration in years by type, under the released cascade. A class with no
#|   bar has too few durations to report, which is a coverage fact rather than a duration of zero."
dte_plot_class(.dur = tab_dur)
```

```{r}
#| label: report-everything
dte_report_all(
  .dates    = tab_dates,
  .desc     = tab_desc,
  .cues     = tab_cues,
  .terms    = tab_terms,
  .nofut    = tab_nofut,
  .daymonth = tab_dm,
  .sweep    = tab_sweep,
  .dur      = tab_dur,
  .n_docs   = nrow(tab_keys)
)
```

# Next

The two vocabularies are what the next pass revises, and both have a table pointing at the answer.
The cue list gets cut to whatever scores a lift meaningfully above one. The term patterns catch two
families and the read block says which third family is worth adding -- `shall continue until
terminated` is a real drafting form and it is a duration of infinity rather than a missing value.

One thing is deliberately still not attempted: a contract with several terms, one per schedule, has
several durations, and this document releases one.
