---
title: "Layout Probe -- Every Rendered Surface"
subtitle: "A stylesheet test document. It computes nothing and reads nothing."
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage
set.seed(42L)
```

```{r}
#| label: setup-sources
#| echo: false

# Only the design layer. This document has no pipeline dependency by design: it must render on a
# machine with no 2_output/, no DuckDB store, no Python environment and no corpus, because its job
# is to answer a question about the stylesheet and nothing else.
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

plot_register_levels(
  .key    = "Class",                                            # the vocabulary the figures draw
  .levels = c("Leases", "Licences", "Supply", "Credit", "Employment", "M&A", "Services", "Other")
)
```

# Purpose

This document exists to be looked at. It computes nothing, reads no artifact and writes no output.
Every block below is a surface that `_styles.css` has to render well, filled with synthetic values
so the page can be judged without waiting hours for a pipeline stage to finish.

Render it after any change to `_styles.css` or to the html block of `_quarto.yml`, from the project
root:

```
quarto render 1_code/_Tests/layout-probe.qmd
```

It lives under `_Tests/`, which Quarto ignores when the project is rendered as a whole, so it is
never built by accident and never appears on the site.

## What is being checked

Seven things, in the order a reader meets them.

1. The fixed rail at four levels of heading, which is the depth `toc-depth` allows.
2. Console blocks: the fixed-width tables from `tbl_say()`, which arrive tagged as standard error
   because `cli` writes through the message stream.
3. The same tables on the rendered path, with grouped headers, a summary row and footnotes.
4. `tbl_note()` output, which is a paragraph rather than a console line.
5. Figures at three rungs of the height ladder.
6. Folded source, inline code, and a long unfoldable line.
7. Lists, links and block quotes, which appear rarely enough to be forgotten.

## Why it is not a pair

Every analysis step in this repository is a `.qmd` and a `.R` sharing a stem. This is not an analysis
step. Its content is deliberately inline, because the thing under test is what the markup looks like,
and hiding the calls that produce it in a library would make the document harder to reason about
rather than easier.

# Configuration

```{r}
#| label: configure

.lP <- list(
  Param = list(
    NRows   = 8L,      # rows in the wide console table; enough to exercise the middle ladder rung
    NCats   = 8L,      # categories in the ranked bar
    NConf   = 6L,      # side of the square matrix in the heatmap
    Seed    = 42L      # fixed, so two renders of this document are comparable
  )
)

set.seed(.lP$Param$Seed)
```

## The synthetic tables

Built here rather than in a library, because what the numbers are is the point: a column of
comma-grouped integers, a column of shares, a long identifier and a short one, so column alignment
and the tabular-figure setting can both be judged.

```{r}
#| label: build-tables

.classes <- plot_levels(.key = "Class")

tab_main <- tibble::tibble(
  Class     = .classes,
  Documents = as.integer(round(runif(length(.classes), 40, 4200))),
  Spans     = as.integer(round(runif(length(.classes), 500, 90000))),
  Coverage  = runif(length(.classes), 0.42, 0.99),
  Precision = runif(length(.classes), 0.61, 0.98)
) |>
  dplyr::arrange(dplyr::desc(.data$Documents))

# A summary row, so the bold-and-ruled treatment has something to land on.
tab_main <- dplyr::bind_rows(
  tab_main,
  tibble::tibble(
    Class     = "All",
    Documents = sum(tab_main$Documents),
    Spans     = sum(tab_main$Spans),
    Coverage  = mean(tab_main$Coverage),
    Precision = mean(tab_main$Precision)
  )
)

# The widest thing this project prints: long engine identifiers beside numbers. This is the block
# that decides whether the console font size is right, so it is deliberately near the real maximum.
tab_wide <- tibble::tibble(
  Suite     = rep(c("lexnlp", "matcon", "spacy"), each = 3L),
  Model     = c("lexnlp-2.3.0", "lexnlp-2.3.0", "lexnlp-2.3.0",
                "paper:dateregex-v3", "paper:moneyregex-v6", "paper:gazetteer-v1",
                "en_core_web_trf", "en_core_web_lg", "en_core_web_sm"),
  Label     = c("ORG", "DATE", "MONEY", "DATE", "MONEY", "GPE", "GPE", "GPE", "GPE"),
  Documents = as.integer(round(runif(9L, 4000, 4400))),
  Candidates = as.integer(round(runif(9L, 20000, 4200000))),
  DocPerSec = round(runif(9L, 1.2, 2100.5), 1),
  Timeouts  = as.integer(round(runif(9L, 0, 12))),
  Errors    = as.integer(c(0, 0, 0, 0, 0, 0, 2, 0, 0))
)
```

# The console path

This is what nineteen of twenty-one documents in this repository look like for most of their length.
`tbl_say()` prints through `cli::cli_verbatim()`; `cli` writes to the message stream; knitr wraps the
message stream in `.cell-output-stderr`. The block below is therefore tagged as standard error while
being the ordinary, correct output of the document, which is why the stylesheet must not colour
stderr as a fault.

```{r}
#| label: console-narrow

tbl_say(.tab = tab_main, .title = "Coverage by contract type")
```

The widest block the project produces. It should scroll horizontally rather than wrap: `tbl_fmt()`
pads every column to a fixed width, and a soft wrap destroys the alignment that is the only reason
to print a table this way.

```{r}
#| label: console-wide

tbl_say(.tab = tab_wide, .title = "Engine throughput over the labelled sample")
```

## The cli alert vocabulary

Four kinds of line, all of which appear in the pipeline. Under `cli.num_colors = 1` they are plain
ASCII markers rather than coloured glyphs, so the stylesheet cannot distinguish them and should not
try.

```{r}
#| label: console-alerts

cli::cli_h2("A section head, as cli draws it")
cli::cli_alert_info("What to look for: a nonzero count here is a join problem, not a labelling one.")
cli::cli_alert_success("4,398 documents extracted; 0 timed out.")
cli::cli_alert_warning("2 spans could not be cut from the canonical text and were dropped.")
cli::cli_text("")
cli::cli_h3("A third-level head")
cli::cli_bullets(c(
  "*" = "A bulleted line, which cli renders with its own marker.",
  "i" = "An informational line inside a bullet list.",
  "v" = "A success line inside a bullet list."
))
```

## A truncated block

`tbl_say()` takes an `.n` and reports how many rows it withheld, which is the shape most long tables
in this project are printed in.

```{r}
#| label: console-truncated

tbl_say(.tab = tab_wide, .title = "Engines, first four", .n = 4L)
```

# The rendered path

The same numbers through `tbl_out()` in `kable` mode: grouped column headers, a summary row set
apart, and footnotes attached to the columns they annotate. Chunks on this path need
`results: asis`, and `tbl_out()` warns rather than rendering raw markup if it is missing.

```{r}
#| label: rendered-grouped
#| results: asis

tbl_out(
  .tab   = tab_main,                                       # the same table as the console block
  .title = "Coverage by contract type",                    # becomes the caption, not a cli head
  .groups = c(" " = 1, "Volume" = 2, "Quality" = 2),       # spanning header above the last four
  .pct   = c("Coverage", "Precision"),                     # rendered as percentages
  .notes = c(
    Coverage  = "Share of documents in which the label appears at least once.",
    Precision = "One-vs-rest and dominated by correct rejections; read it beside recall."
  ),
  .summary_row = nrow(tab_main),                           # the All row
  .mode  = "kable"                                         # overrides the document setting
)
```

## Notes on their own

`tbl_note()` on the rendered path emits a paragraph rather than a console alert, because a finding
about a table is prose about the table. A `cli` alert would arrive as a monospaced block that does
not wrap, so a sentence longer than the page would need dragging through a scroll bar to be read.

```{r}
#| label: rendered-notes
#| results: asis

.mode_was <- getOption("mc.table_mode")
options(mc.table_mode = "kable")

tbl_note(
  .text = "The two windows part company on 312 documents, which is 7.1 per cent of the sample and \\
           the entire difference between the two columns above."
)
tbl_note(
  .text = "Four documents carry no text at all and are absent from every count on this page.",
  .type = "warn"
)

options(mc.table_mode = .mode_was)
```

## A wide rendered table

Eight columns and long identifiers. This is where a rendered table either fits the content column or
acquires its own scrollbar, and both outcomes are acceptable as long as nothing is clipped.

```{r}
#| label: rendered-wide
#| results: asis

tbl_out(
  .tab    = tab_wide,                                       # nine rows, eight columns
  .title  = "Engine throughput over the labelled sample",
  .groups = c(" " = 3, "Volume" = 2, "Rate" = 1, "Failures" = 2),
  .digits = 1L,
  .notes  = c(DocPerSec = "Measured on the 4,398-document sample; the corpus distribution differs."),
  .mode   = "kable"
)
```

# Figures

Three rungs of the ladder in `plot_height()`, so the relationship between row count and canvas can be
judged on one page. Width is fixed globally in `_quarto.yml` and is never set per chunk.

```{r}
#| label: fig-bar-ranked
#| fig-cap: "Documents by contract type. The middle rung of the height ladder, at eight categories."
#| fig-height: 3.4

plot_bar_ranked(
  .tab   = dplyr::filter(tab_main, .data$Class != "All"),   # the summary row is not a category
  .cat   = "Class",                                          # the categorical axis
  .val   = "Documents",                                      # the measured value
  .key   = "Class",                                          # registered vocabulary, for stable order
  .label = TRUE                                              # value labels at the end of each bar
)
```

```{r}
#| label: fig-bar-small
#| fig-cap: "A two-category figure at the ladder's lowest rung. The point is that it is not as tall as the one above."
#| fig-height: 2.4

plot_bar_ranked(
  .tab   = tibble::tibble(Outcome = c("Extracted", "Failed"), N = c(4386L, 12L)),
  .cat   = "Outcome",
  .val   = "N",
  .key   = NULL,                                             # no registered vocabulary for this one
  .label = TRUE
)
```

```{r}
#| label: fig-heatmap
#| fig-cap: "A square matrix at the square rung. Cells are labelled with shares, so ramp and text must both stay legible."
#| fig-height: 5.2

.cats <- .classes[seq_len(.lP$Param$NConf)]

tab_conf <- tidyr::expand_grid(True = .cats, Pred = .cats) |>
  dplyr::mutate(Share = ifelse(.data$True == .data$Pred, runif(dplyr::n(), 0.55, 0.95),
                               runif(dplyr::n(), 0.00, 0.14)))

plot_heatmap(
  .tab   = tab_conf,
  .x     = "Pred",                                           # predicted category
  .y     = "True",                                           # labelled category
  .fill  = "Share",                                          # the value the ramp encodes
  .pct   = TRUE,                                             # cells labelled as percentages
  .angle = 40                                                # x labels rotated to fit
)
```

# Code

## Folded source

Every chunk above is folded by default. The toggle should read as a control rather than as a line of
code that happens to be there.

```{r}
#| label: code-fold-demo
#| eval: true

# A chunk whose content is deliberately unremarkable, so the fold toggle can be judged rather than
# the code. It runs, because nothing in this repository is allowed not to.
.demo <- tab_main |>
  dplyr::filter(.data$Class != "All") |>
  dplyr::mutate(Ratio = .data$Spans / .data$Documents) |>
  dplyr::arrange(dplyr::desc(.data$Ratio))

cli::cli_alert_info("Highest span-to-document ratio: {(.demo$Class[[1]])}.")
```

## A long line

Line numbering is on and the overflow rule is `wrap`. This line is longer than the content column so
that whichever of those two wins can be seen.

```{r}
#| label: code-long-line
#| eval: false
#| echo: true

.result <- tab_wide |> dplyr::filter(.data$Suite == "matcon", .data$Label %in% c("DATE", "MONEY", "GPE")) |> dplyr::mutate(Throughput = .data$Candidates / .data$DocPerSec) |> dplyr::arrange(dplyr::desc(.data$Throughput))
```

## Inline code

A sentence carrying `ner_db_summary()`, a path like `2_output/04A-EntityExtract/Store/`, and a
parameter such as `.lP$Param$ChunkSize`, so inline code can be judged in running prose rather than on
its own line.

# Prose surfaces

## Lists

Ordered, for a sequence:

1. Read the label spine and assert the identifier joins.
2. Deal the folds once, upstream, and never re-deal them.
3. Score every arm on the same folds with the same code.

Unordered, for a set:

- **Single-writer rule.** Exactly one script writes any given artifact.
- **Unconditional checks.** Every validation runs on every render.
- **Gated network calls.** Only acquisition is behind a switch; local computation never is.

## A block quote

> A document that silently skips its own work will report numbers computed from inputs that no longer
> exist, and will look entirely normal doing it.

## Links and emphasis

A link to [the EDGAR full-text search](https://efts.sec.gov/LATEST/search-index?q=test), some **bold
text**, some *italic text*, and a horizontal rule below.

---

# Overview

Everything again, compactly. In a real document this section carries every figure; here it carries
one table in each mode side by side, which is the comparison the stylesheet exists to make readable.

```{r}
#| label: overview-console

tbl_say(.tab = tab_main, .title = "Console path")
```

```{r}
#| label: overview-rendered
#| results: asis

tbl_out(
  .tab    = tab_main,
  .title  = "Rendered path",
  .groups = c(" " = 1, "Volume" = 2, "Quality" = 2),
  .pct    = c("Coverage", "Precision"),
  .summary_row = nrow(tab_main),
  .mode   = "kable"
)
```

# Next

Nothing. This document is terminal by design: it produces no artifact and no other document reads it.
Delete it and the pipeline is unchanged.
