---
title: "Table rendering options -- a test bench"
subtitle: "Nine ways to render the same table. Pick, mix, or reject."
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    theme: cosmo
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = "", echo = TRUE)
options(knitr.kable.NA = "-")
```

## What this is

One table -- the per-category scores 03E prints for the transformer on `ClassDetailed` -- rendered
nine ways. Every option is self-contained: read the code, look at the result, and say which parts you
want. Whatever we keep becomes an extension of `tbl_render()` in `_Commons/_Tables.R`, so the runbooks
stay free of per-table formatting.

The data below is the real output from the last render, typed in so this file runs on its own.

```{r}
#| label: the-data
tab <- tibble::tribble(
  ~Category,                                   ~Support, ~nPredicted, ~Coverage, ~Accuracy, ~Precision, ~Recall, ~F1,
  "Business Structure: Investment and Merger",      301L,        314L,     1.000,     0.973,      0.793,   0.827, 0.810,
  "Business Structure: Peer Agreements",             71L,         61L,     1.000,     0.991,      0.770,   0.662, 0.712,
  "Customer / Supplier",                            383L,        399L,     1.000,     0.978,      0.857,   0.893, 0.875,
  "Employment: Compensation",                       702L,        695L,     1.000,     0.990,      0.974,   0.964, 0.969,
  "Employment: Legal",                              723L,        721L,     1.000,     0.988,      0.964,   0.961, 0.963,
  "Financial Instruments: Credit",                  659L,        644L,     1.000,     0.985,      0.961,   0.939, 0.950,
  "Financial Instruments: Equity",                  301L,        295L,     1.000,     0.975,      0.824,   0.807, 0.815,
  "Leases",                                         303L,        303L,     1.000,     0.997,      0.980,   0.980, 0.980,
  "Licenses",                                       240L,        237L,     1.000,     0.993,      0.945,   0.933, 0.939,
  "Other",                                          313L,        305L,     1.000,     0.984,      0.898,   0.875, 0.887,
  "Purchases and Sales: Assets",                    319L,        333L,     1.000,     0.982,      0.862,   0.900, 0.880,
  "R&D",                                             83L,         91L,     1.000,     0.992,      0.769,   0.843, 0.805,
  "All categories",                                4398L,       4398L,     1.000,     0.915,      0.883,   0.882, 0.882
)

# The keyword arm, which abstains -- used by the options that show two engines at once.
tab_kw <- tibble::tribble(
  ~Category,                                   ~Coverage, ~Precision, ~Recall, ~F1,
  "Business Structure: Investment and Merger",      0.402,      0.884,   0.355, 0.507,
  "Business Structure: Peer Agreements",            0.239,      0.647,   0.155, 0.250,
  "Customer / Supplier",                            0.462,      0.802,   0.371, 0.507,
  "Employment: Compensation",                       0.681,      0.981,   0.668, 0.795,
  "Employment: Legal",                              0.644,      0.958,   0.617, 0.751,
  "Financial Instruments: Credit",                  0.611,      0.975,   0.596, 0.740,
  "Financial Instruments: Equity",                  0.428,      0.860,   0.368, 0.516,
  "Leases",                                         0.706,      0.995,   0.703, 0.824,
  "Licenses",                                       0.475,      0.912,   0.433, 0.588,
  "Other",                                          0.211,      0.667,   0.141, 0.233,
  "Purchases and Sales: Assets",                    0.451,      0.847,   0.382, 0.527,
  "R&D",                                            0.313,      0.769,   0.241, 0.367,
  "All categories",                                 0.523,      0.858,   0.419, 0.550
)

n_body <- nrow(tab) - 1L   # every option treats the last row as a summary, not a category
```

---

## Option 1 -- what we print today

The fixed-width console block. Included as the baseline, not as a candidate.

```{r}
#| label: opt-1
#| echo: false
tab |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) paste0(formatC(100 * .x, format = "f", digits = 1), "%")),
                F1 = sprintf("%.3f", F1)) |>
  as.data.frame() |>
  print(row.names = FALSE)
```

It survives copy-paste into an email, which is the one thing it does better than everything below.

---

## Option 2 -- plain `kable`, which is what `tbl_render()` does now

```{r}
#| label: opt-2
tab |>
  knitr::kable(digits = 3, format.args = list(big.mark = ",")) |>
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

Already better: right-aligned numbers, real column rules. But the summary row is indistinguishable
from a category, and the percentages read as decimals.

---

## Option 3 -- percentages, striping, and the summary row set apart

Three changes, each independent of the others.

```{r}
#| label: opt-3
tab |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) scales::percent(.x, accuracy = 0.1))) |>
  knitr::kable(digits = 3, format.args = list(big.mark = ","), align = "lrrrrrrr") |>
  kableExtra::kable_styling(
    full_width        = FALSE,
    position          = "left",
    bootstrap_options = c("striped", "hover", "condensed")
  ) |>
  kableExtra::row_spec(n_body, extra_css = "border-bottom: 1px solid #333;") |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

---

## Option 4 -- grouped column headers

The columns fall into three jobs -- how big is the category, how often was the engine right, and the
summary score. Saying so in a header row removes most of the work of reading it.

```{r}
#| label: opt-4
tab |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) scales::percent(.x, accuracy = 0.1))) |>
  knitr::kable(digits = 3, format.args = list(big.mark = ","), align = "lrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::add_header_above(c(" " = 1, "Size" = 2, "Behaviour" = 2, "Quality" = 3)) |>
  kableExtra::row_spec(n_body, extra_css = "border-bottom: 1px solid #333;") |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

---

## Option 5 -- data bars in the score column

The eye reads bar length faster than three decimals. `F1` keeps its number and gains a bar behind it.

```{r}
#| label: opt-5
# The bar column is built from a NUMERIC column left untouched -- cell_spec and column_spec(image=)
# both rewrite a cell, and applying them to the same one leaves raw html in the output.
tab |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) scales::percent(.x, accuracy = 0.1)),
                F1 = sprintf("%.3f", F1),
                Score = "") |>
  knitr::kable(format = "html", escape = FALSE, format.args = list(big.mark = ","),
               align = "lrrrrrrrl") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::column_spec(
    9,
    image = kableExtra::spec_pointrange(
      x = tab$F1, xmin = 0, xmax = 1, vline = 0.882, width = 200, cex = 0.4
    )
  ) |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

The vertical rule sits at the model's own macro-F1, so a dot left of it is a category performing
below the headline. Each cell is inline SVG rather than a linked file, so it survives `embed-resources`.

**Two traps, both hit while building this file.** `cell_spec()` and `column_spec(image = ...)` each
rewrite a cell, so applying both to the same column leaves raw html in the output -- the bar column
here is a separate empty column for that reason. And any option using `cell_spec()` or an inline plot
needs `format = "html"` passed to `kable()` explicitly: without it pandoc runs its smart-quote pass
over the generated html and the span arrives as literal text with curly quotes.

---

## Option 6 -- colour instead of bars

Same idea, less ink. The number is shaded by its own value, so the weak categories surface without a
second visual channel.

```{r}
#| label: opt-6
blues <- c("#bfd7ed", "#60a3d9", "#4682b4", "#0074b7", "#00416a")

tab |>
  dplyr::mutate(
    dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                  \(.x) scales::percent(.x, accuracy = 0.1)),
    F1 = kableExtra::cell_spec(
      sprintf("%.3f", F1), "html", bold = TRUE, color = "white",
      background = kableExtra::spec_color(tab$F1, end = 0.9,
                                          option = "D", direction = 1)
    )
  ) |>
  knitr::kable(format = "html", escape = FALSE, format.args = list(big.mark = ","),
               align = "lrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

---

## Option 7 -- house palette, shaded on one column only

Option 6 with the project's own blues rather than viridis, and shading confined to the column the
reader is meant to scan.

```{r}
#| label: opt-7
ramp <- grDevices::colorRamp(c("#eaf2f9", "#003b73"))
shade <- function(.x) {
  m_ <- ramp(scales::rescale(.x, to = c(0, 1), from = c(0.6, 1)))
  grDevices::rgb(m_[, 1], m_[, 2], m_[, 3], maxColorValue = 255)
}

tab |>
  dplyr::mutate(
    dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                  \(.x) scales::percent(.x, accuracy = 0.1)),
    F1 = kableExtra::cell_spec(
      sprintf("%.3f", F1), "html", bold = TRUE,
      color = dplyr::if_else(tab$F1 > 0.88, "white", "#12263A"),
      background = shade(tab$F1)
    )
  ) |>
  knitr::kable(format = "html", escape = FALSE, format.args = list(big.mark = ","),
               align = "lrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::add_header_above(c(" " = 1, "Size" = 2, "Behaviour" = 2, "Quality" = 3)) |>
  kableExtra::row_spec(n_body, extra_css = "border-bottom: 1px solid #333;") |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

---

## Option 8 -- two engines side by side

The comparison 03E actually wants. Instead of three separate tables a reader holds in their head, one
table with a spanning header per engine.

```{r}
#| label: opt-8
# Renamed explicitly rather than relying on a join suffix: Coverage exists on one side only, so a
# suffix would leave it unmarked while marking the columns that appear on both.
dplyr::inner_join(
  tab |> dplyr::select(Category, Support,
                       BertPrecision = Precision, BertRecall = Recall, BertF1 = F1),
  tab_kw |> dplyr::select(Category, KwCoverage = Coverage,
                          KwPrecision = Precision, KwRecall = Recall, KwF1 = F1),
  by = dplyr::join_by(Category)
) |>
  dplyr::mutate(
    dplyr::across(c(BertPrecision, BertRecall, KwCoverage, KwPrecision, KwRecall),
                  \(.x) scales::percent(.x, accuracy = 0.1)),
    dplyr::across(c(BertF1, KwF1), \(.x) sprintf("%.3f", .x))
  ) |>
  stats::setNames(c("Category", "Support", "Precision", "Recall", "F1",
                    "Coverage", "Precision", "Recall", "F1")) |>
  knitr::kable(format.args = list(big.mark = ","), align = "lrrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::add_header_above(c(" " = 2, "Transformer" = 3, "Keyword table" = 4)) |>
  kableExtra::row_spec(n_body, extra_css = "border-bottom: 1px solid #333;") |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE)
```

The keyword arm carries a `Coverage` column the transformer does not need, which is the asymmetry made
visible rather than explained in a footnote.

---

## Option 9 -- footnotes instead of `cli` alerts

Everything the console currently prints as three `i` lines under the table, attached to the columns it
refers to.

```{r}
#| label: opt-9
tab |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) scales::percent(.x, accuracy = 0.1))) |>
  stats::setNames(c("Category", "Support", "nPredicted", "Coverage", "Accuracy[note]",
                    "Precision", "Recall[note]", "F1")) |>
  knitr::kable(format.args = list(big.mark = ","), align = "lrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::add_header_above(c(" " = 1, "Size" = 2, "Behaviour" = 2, "Quality" = 3)) |>
  kableExtra::row_spec(n_body, extra_css = "border-bottom: 1px solid #333;") |>
  kableExtra::row_spec(n_body + 1L, bold = TRUE) |>
  kableExtra::add_footnote(
    c(paste("One-vs-rest and dominated by correct rejections. A rare category reads near-perfect",
            "while the engine misses most of its documents."),
      paste("Counts an abstention as a miss, so it is comparable across engines. An arm that",
            "declines on half the corpus scores low here whatever its precision on the rest.")),
    notation = "number"
  )
```

---

## Option 10 -- long tables: fixed header and a scroll box

Not needed for twelve categories. It is needed for the threshold tables in sections 3 and 4 once all
three tasks and both arms are stacked.

```{r}
#| label: opt-10
dplyr::bind_rows(tab, tab, tab) |>
  dplyr::mutate(dplyr::across(c(Coverage, Accuracy, Precision, Recall),
                              \(.x) scales::percent(.x, accuracy = 0.1))) |>
  knitr::kable(format.args = list(big.mark = ","), align = "lrrrrrrr") |>
  kableExtra::kable_styling(full_width = FALSE, position = "left",
                            bootstrap_options = c("hover", "condensed")) |>
  kableExtra::scroll_box(height = "300px", fixed_thead = TRUE)
```

---

## What I would pick

**Options 3 + 4 + 9 as the default**, everywhere: percentages formatted as percentages, numbers right
aligned, grouped headers, the summary row separated by a rule and set in bold, and the caveats as
footnotes rather than as `cli` lines the reader has to hold in their head while looking back up at the
table.

**Option 8 where two engines are being compared**, which in 03E is most places. It halves the number
of tables and puts the comparison on one line per category instead of across three screens.

**Option 7 sparingly** -- shading earns its place on the one column a reader is meant to scan and
becomes noise on all of them. I would use it on `F1` in section 1 and nowhere else.

**Option 5 is better than I expected.** It emits inline SVG rather than linked images, so it survives
`embed-resources` and costs about 2 KB per row. It still does not survive to pdf, and it needs a
dedicated column. Worth it for one table, not for every table.

Everything above was rendered and checked in this container rather than written from memory, so the
code runs as printed. What I could not check is how it looks against `_styles.css`, which is not in
the copy of the repo I have -- if that file sets Times and horizontal rules only, `striped` and
`hover` may fight it.

Two things to decide before this goes into `_Commons/_Tables.R`:

- **pdf.** Everything above is html. `bootstrap_options` and `extra_css` are ignored under LaTeX, and
  `cell_spec` needs `format = "latex"`. If these documents are ever rendered to pdf the wrapper has to
  branch on `knitr::is_latex_output()`. Cheap to write, but it doubles the surface, so it is worth
  knowing whether pdf is a real target or not.
- **`tbl_say()` vs `tbl_render()`.** 03E currently prints everything through `tbl_say()`, which is the
  console formatter. Moving to kable means the tables stop being copy-pasteable as text. If you paste
  console blocks into our chats to debug, that matters, and the answer might be `tbl_say()` while
  working and `tbl_render()` for the version that gets read.
