---
title: "EDGAR Acquisition -- Documents (01B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01A owns the mirror layout and the form vocabulary this document selects from. Sourcing its
# library rather than restating any of it is what keeps the two in agreement.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "01A-EdgarIndex"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01B-EdgarDocuments.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

01A mirrored the landing pages, which say what each filing contains. This document decides which of those attachments
are worth retrieving, fetches and parses them, and writes `FilePaths.parquet` -- the `DocID` to `Path` index every later
script uses to locate a document's text on disk.

Nothing is measured about the documents here. Word counts, stopword ratios, parse-error rates and the quality rules that
drop a document from the study are 01C. The division is by cost and failure mode: this script is network-bound and has
to survive interruption; 01C is local, cheap, and re-runs from scratch in minutes.

## What gets downloaded, and why only this

Three groups, and the reasoning differs for each.

**Exhibit 10 attachments** are the object of study. Regulation S-K Item 601(b)(10) requires a registrant to file its
material contracts as exhibits, and Exhibit 10 is where they land.

**CT orders** are the SEC's confidential-treatment orders. They are not contracts, but they record which contract terms
a filer was permitted to withhold, which is the only direct evidence of what redaction removed.

**8-K filings reporting Item 1.01** are current reports announcing entry into a material definitive agreement. The
filing carries the firm's own narrative summary of the contract, which makes it the comparison case: the same
agreement, described by the filer rather than drafted by the parties.

Everything else attached to the same filings is left on EDGAR. At ten requests per second, downloading attachments that
cannot answer the research question would extend acquisition from days into weeks.

## Why exhibit types come from a lookup rather than a pattern

Filers do not spell exhibit types consistently. `EX-10.1`, `EX-10`, `EXHIBIT 10.23` and dozens of further variants all
denote the same thing. Matching them with a regular expression is how a study silently excludes whichever spellings its
author did not anticipate, and the exclusion is invisible because the omitted documents never enter any count.

`rGetEDGAR` ships a lookup enumerating observed raw strings against a modal type, and this document reads it. The
mapping is then versioned with the package rather than with this project.

## Where the documents land

`rGetEDGAR` resolves link tables and downloaded documents from a single root, so documents are written into the mirror
01A established rather than into this script's own output directory. Duplicating three hundred megabytes of link tables
to obtain a second root would buy nothing. Ownership stays unambiguous: 01A writes `MasterIndex/` and `DocLinks/`, 01B
writes `DocumentData/`, and no artifact has two writers. This script's own directory holds the index.

## The parsed tree is the only copy

Documents are fetched with `.keep_orig = FALSE`, which discards the original bytes once parsing succeeds. There is no
local source to re-parse from, and re-deriving the tree means one request per document at ten per second. That is why
acquisition is gated, and why nothing in this document deletes anything.

# Configuration

```{r}
#| label: config
.dir_index <- here::here("2_output", "01A-EdgarIndex")

.lP <- list(
  Input = list(
    Mirror         = fs::path(.dir_index, "GetEDGAR"),                 # the mirror 01A established
    LandingPageAll = fs::path(.dir_index, "LandingPageAll.parquet")    # written by 01A
  ),
  Output = list(
    FilePaths = utils_file_path(.dir_main, "FilePaths.parquet"),   # the DocID to Path index
    Figures   = utils_file_path(.dir_main, "Figures")              # figure files for the manuscript
  ),
  Param = list(
    User    = "Matthias.Uckert@Outlook.com",   # SEC requires a contact address on every request
    Item    = "1.01",                          # the 8-K item denoting a material definitive agreement
    Workers = 5L,                              # download workers; the SEC rate limit binds before this does
    Acquire = FALSE                            # TRUE permits the download to run
  )
)

# Resolved from the same root 01A used, so the two scripts cannot disagree about where the mirror is.
.lP$Edgar <- rGetEDGAR::get_directories(.lP$Input$Mirror)
.lP$Input$Links <- .lP$Edgar$DocLinks$DirMain$Links

fs::file_exists(.lP$Input$LandingPageAll)
```

# Selection

The three groups below are the inclusion rule for the entire study, so they are composed here rather than hidden behind
a function call. Each is a filter on the mirrored link tables; the plumbing that resolves raw exhibit types and file
extensions lives in the library.

```{r}
#| label: select-documents
# 1. Exhibit 10 -- the material contracts themselves.
tab_ex10 <- edg_links_with_ext(
  .path_links = .lP$Input$Links,                    # mirrored link tables
  .types      = edg_doc_types(.mod = "Exhibit 10"), # every observed spelling of an Exhibit 10 type
  .hash_index = NULL                                # NULL keeps all filings
)

# 2. CT orders -- the record of what redaction was permitted to remove.
tab_ctos <- edg_links_with_ext(
  .path_links = .lP$Input$Links,             # mirrored link tables
  .types      = edg_doc_types(.mod = "CTO"), # confidential-treatment orders
  .hash_index = NULL                         # NULL keeps all filings
)

# 3. 8-K filings reporting Item 1.01 -- the filer's own summary of the same agreements. Restricted
#    to filings whose landing page lists the item, not to all 8-Ks: an 8-K reporting only a change
#    of auditor carries no contract narrative.
vec_item_hash <- edg_hash_with_item(
  .path_landing = .lP$Input$LandingPageAll,   # unfiltered landing table from 01A
  .item         = .lP$Param$Item,             # "1.01"
  .fixed        = TRUE                        # match literally; see the validation section
)

tab_08ks <- edg_links_with_ext(
  .path_links = .lP$Input$Links,                           # mirrored link tables
  .types      = edg_doc_types(.mod = c("8-K", "8-K/A")),   # current reports and their amendments
  .hash_index = vec_item_hash                              # only those reporting the item
)

tab_selected <- dplyr::bind_rows(
  dplyr::mutate(tab_ex10, Group = "Exhibit10"),
  dplyr::mutate(tab_ctos, Group = "CTO"),
  dplyr::mutate(tab_08ks, Group = "8-K")
)

nrow(tab_selected)
```

What is already on disk is subtracted from that. The parsed tree is itself the ledger: a `DocID` with a file under it
has been retrieved, and nothing further needs to be remembered. A separate manifest would introduce a record that can
disagree with the directory it describes, and the directory is the thing that matters.

The parsed tree is listed once here and the result reused. Walking it costs about a minute, the same answer is needed
three times over, and re-listing would leave three answers that could differ.

```{r}
#| label: list-on-disk
vec_on_disk <- utils_list_files(
  .dirs = .lP$Edgar$DocumentData$Parsed,   # root of the parsed tree
  .reg  = NULL,                            # every file
  .id   = "DocID",                         # identifier taken from the filename
  .rec  = TRUE                             # descend into DocType and year-quarter
)$DocID

length(vec_on_disk)
```

```{r}
#| label: report-outstanding
edg_report_selection(
  .tab_sel  = tab_selected,        # everything the rule selects
  .ids_disk = vec_on_disk,         # what is on disk
  .acquire  = .lP$Param$Acquire    # reported, so a gap and a switch stay distinguishable
)

use_docids <- setdiff(tab_selected$DocID, vec_on_disk)
```

Two things can leave a document outstanding, and they need different responses. A count that is stable across renders is
links the SEC no longer serves, which are lost to any method rather than to this one; a count that jumps is an
interrupted acquisition, which the switch above will finish.

On the present corpus it is neither: every selected document is on disk, and every document on disk is selected. The
retrieved corpus is exactly the inclusion rule applied to the mirror, with no attrition in either direction. That is
worth stating rather than assuming, because it is the one place where a selection rule and the corpus it produced could
have drifted apart without anything downstream noticing.

# Acquisition

Gated, and reports what it did either way. PDF parsing raises errors on a minority of documents; these are recorded per
document and quantified in 01C rather than suppressed here.

```{r}
#| label: acquire-documents
if (isTRUE(.lP$Param$Acquire) && length(use_docids) > 0L) {
  rGetEDGAR::edgar_download_document(
    .dir       = .lP$Input$Mirror,   # the mirror root, shared with 01A
    .user      = .lP$Param$User,     # contact address sent with every request
    .doc_ids   = use_docids,         # only what is outstanding
    .keep_orig = FALSE,              # discard originals after parsing; see below
    .workers   = .lP$Param$Workers,  # the SEC rate limit binds before this does
    .verbose   = TRUE                # stream progress
  )
} else {
  cli::cli_alert_info("Acquisition is OFF or nothing outstanding: no documents were fetched.")
}
```

`.keep_orig = FALSE` is stated explicitly rather than left at its default because it is irreversible. It discards the
original bytes once parsing succeeds, which is why the parsed tree has no local source to be rebuilt from.

# Index

The index is rebuilt only when something was fetched. Walking the tree takes minutes and its result cannot change unless
a document was added, so the rebuild is keyed on the acquisition switch rather than on the outstanding count, which
never reaches zero.

```{r}
#| label: build-file-index
tab_index <- edg_index_documents(
  .dir_parsed = .lP$Edgar$DocumentData$Parsed,   # root of the parsed tree
  .path_out   = .lP$Output$FilePaths,            # the index downstream reads
  .rerun      = isTRUE(.lP$Param$Acquire)        # re-walk only if this render fetched anything
)

nrow(tab_index)
```

# Results

```{r}
#| label: report-corpus
edg_report_documents(.tab_idx = tab_index)
```

Quarter coverage differs by group because the forms carrying each began at different dates. Exhibit 10 runs the full
EDGAR history; the 8-K item structure that makes Item 1.01 identifiable dates from the 2004 reform, and CT orders
appear only where confidential treatment was sought.

# Validation

Three checks. Each states its expected value first, so a result that differs is a finding rather than a number to
interpret after the fact.

```{r}
#| label: validate-index
# 1. No duplicate DocID: the identifier derives from the filename, so a repeat means one document
#    was written under two year-quarters.
# 2. Every indexed document was selected. A document on disk that the rule does not select would
#    enter the corpus without ever having been chosen.
# 3. Matching the item code as a pattern rather than literally puts a wildcard in the middle of it.
#    No 8-K item code has the shape that would exploit that, so the two should agree exactly.
n_loose_ <- length(edg_hash_with_item(
  .path_landing = .lP$Input$LandingPageAll,   # unfiltered landing table from 01A
  .item         = .lP$Param$Item,             # "1.01"
  .fixed        = FALSE                       # as a pattern, for comparison only
))

tibble::tibble(
  DuplicateDocID   = sum(duplicated(tab_index$DocID)),
  IndexedNotChosen = sum(!tab_index$DocID %in% tab_selected$DocID),
  ItemFixed        = length(vec_item_hash),
  ItemPattern      = n_loose_,
  ItemDifference   = n_loose_ - length(vec_item_hash)
) |>
  tbl_out(
    .title = "Index and match-rule checks",
    .notes = c(
      IndexedNotChosen = "Nonzero means documents on disk that the inclusion rule does not select.",
      ItemDifference   = "Nonzero means the pattern matched item codes the literal string did not."
    )
  )
```

The download writes into the mirror through the same root the rest of the pipeline reads from. A nested `GetEDGAR/`
appearing inside it would mean the two resolved differently, leaving documents where nothing looks for them.

```{r}
#| label: validate-mirror-root
tibble::tibble(
  ParsedRoot  = as.character(.lP$Edgar$DocumentData$Parsed),
  StrayNested = fs::dir_exists(fs::path(.lP$Input$Mirror, "GetEDGAR"))
) |>
  tbl_out(.title = "Mirror root")
```

# Deployment

`FilePaths.parquet` is the only artifact of this script, and the single writer of the `DocID` to `Path` mapping. Every
later script reads it rather than re-walking the tree.

```{r}
#| label: deploy-report
fs::file_info(.lP$Output$FilePaths) |>
  dplyr::select("path", "size") |>
  tbl_out(.title = "Written")
```

# Overview

```{r}
#| label: fig-corpus-by-year
#| fig-height: 3.4
#| fig-cap: "Documents retrieved per calendar year by group. The 8-K series begins in 2004, when the
#|   item structure that makes a material-agreement report identifiable was introduced."
gg_corpus <- edg_plot_corpus(.tab = edg_corpus_by_quarter(.tab_idx = tab_index))

plot_save(
  .plot    = gg_corpus,                 # the figure
  .name    = "corpus-by-year",          # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 3.4,                       # from the ladder: a time series is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_corpus
```

```{r}
#| label: overview-all
edg_report_all_docs(
  .lp       = .lP,             # configuration, so the reporters resolve their own paths
  .tab_sel  = tab_selected,    # what the inclusion rule selects
  .tab_idx  = tab_index,       # the index built above
  .ids_disk = vec_on_disk      # the single listing of the parsed tree
)
```

# Next

**01C-EdgarMetaData** reads this index and measures the documents: word counts, stopword ratios and parse errors. It
applies the quality rules that drop a document from the study, restricts the landing table and the master index to the
filings that survived, and consolidates everything into `FullMetaData.parquet`, which is what 02, 03 and 04 read.
