---
title: "EDGAR Acquisition -- Document Metadata (01C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 01A owns the mirror layout; 01B owns the document index. Sourcing both rather than restating any
# of it is what keeps the three in agreement.
purrr::walk(
  .x = c("01A-EdgarIndex", "01B-EdgarDocuments"),
  .f = function(.s) {
    source(
      file     = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
      encoding = "UTF-8"
    )
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/01C-EdgarMetaData.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

01B put the documents on disk and indexed them. This is the first script that opens them.

It measures every document, decides which are too damaged to analyse, restricts the upstream metadata to the filings
that survived, and joins everything into `FullMetaData.parquet` -- the single table that 02, 03 and 04 read. Everything
the rest of the pipeline knows about a document that is not its text comes from here.

Nothing here touches the network, so nothing here is gated. Every step inspects its own output and does only what is
missing. This is the document in the family where "everything runs" holds without qualification, and it is also where
most of the numbers a referee will ask about are produced.

## Flagged, not deleted

Documents failing the quality rules are marked `Removed = 1` and kept in the table. A pipeline that drops them cannot
report its own attrition, and how much was excluded and why is a result rather than an implementation detail. Every
downstream script filters on the flag; none of them has to know the rule.

## What the rules are for

The three rules catch failures of *conversion*, not properties of the contract. A PDF that rendered as coordinates, an
attachment that is a hyperlink to a document rather than the document, a page of a financial statement filed under an
exhibit number: these arrive looking like data and are not.

Each threshold sits far from anything a real agreement produces, which is deliberate. A blunt rule that removes wreckage
is defensible; a finely tuned one that removes short agreements is a research decision disguised as data cleaning.

| Rule | Fires when | What it catches |
|:--|:--|:--|
| Too short | 10 words or fewer after the header | stubs, links, empty conversions |
| Not prose | under 20% stopwords **and** under 100 words | tables and conversion debris |
| Mostly digits | 75% or more tokens numeric | financial statements |

The second rule needs its length condition. Ordinary English runs far above twenty per cent stopwords, but a *long*
document that runs low is an exhibit schedule -- legitimate content, densely tabular. Only a short one is debris.

## The adjusted word count

Every parsed document begins with the SEC's own header block: `<TYPE>`, `<SEQUENCE>`, `<FILENAME>`, `<DESCRIPTION>`.
Those words are counted along with the contract's, so an attachment containing nothing but a header does not measure as
empty. `nWordsAdj` subtracts them, and the emptiness rule is applied to that rather than to the raw count.

## Cost

Three passes over 1.8 million documents, each opening every file once: parse status, text statistics, stopword counts.
Each writes a cache and skips if it is present, so the first run is hours and every later one is seconds.

# Configuration

```{r}
#| label: config
.dir_index <- here::here("2_output", "01A-EdgarIndex")
.dir_docs  <- here::here("2_output", "01B-EdgarDocuments")

.lP <- list(
  Input = list(
    Mirror         = fs::path(.dir_index, "GetEDGAR"),                  # the mirror 01A established
    LandingPageAll = fs::path(.dir_index, "LandingPageAll.parquet"),    # unfiltered, written by 01A
    FilePaths      = fs::path(.dir_docs, "FilePaths.parquet"),          # DocID to Path, written by 01B
    StopShort      = here::here("0_data", "Dictionaries", "LoughranMcDonald", "StopWords_Generic.txt"),
    StopLong       = here::here("0_data", "Dictionaries", "LoughranMcDonald", "StopWords_Generic.txt")
  ),
  Cache = list(
    StopWords = utils_file_path(.dir_main, "Cache", "StopWords.parquet"),   # standardised dictionary
    DocErrors = utils_file_path(.dir_main, "Cache", "DocErrors.parquet"),   # pass 1: parse status
    DocStats  = utils_file_path(.dir_main, "Cache", "DocStats.parquet"),    # pass 2: text statistics
    DocStop   = utils_file_path(.dir_main, "Cache", "DocStop.parquet")      # pass 3: stopword counts
  ),
  Output = list(
    DocStats     = utils_file_path(.dir_main, "DocStats.parquet"),       # per-document measurements
    RemovedDocs  = utils_file_path(.dir_main, "RemovedDocs.parquet"),    # what the rules flagged, and why
    LinkData     = utils_file_path(.dir_main, "LinkData.parquet"),       # links, restricted to retrieved
    MasterIndex  = utils_file_path(.dir_main, "MasterIndex.parquet"),    # index, restricted to retrieved
    LandingPage  = utils_file_path(.dir_main, "LandingPage.parquet"),    # landing, restricted to retrieved
    FullMetaData = utils_file_path(.dir_main, "FullMetaData.parquet"),   # the one table downstream reads
    Figures      = utils_file_path(.dir_main, "Figures")                 # figure files for the manuscript
  ),
  Param = list(
    Workers = 10L    # parallel workers; also the number of chunks each pass is split into
  )
)

.lP$Edgar <- rGetEDGAR::get_directories(.lP$Input$Mirror)

fs::file_exists(c(.lP$Input$FilePaths, .lP$Input$LandingPageAll, .lP$Input$StopShort))
```

Failing here, rather than three passes later, is deliberate: a missing input should stop the document at the point the
path is declared, not after two hours of measurement.

# Input

```{r}
#| label: load-index
tab_index <- arrow::read_parquet(.lP$Input$FilePaths)

nrow(tab_index)
```

# Measurement

The stopword dictionary is standardised with the same function that standardised the document text, so a word is spelled
identically on both sides of the comparison. Standardising only one side is how a stopword count comes out
systematically low without anything appearing to be wrong.

```{r}
#| label: build-dictionary
tab_stopdict <- edg_stopword_dict(
  .path_short = .lP$Input$StopShort,    # short Loughran-McDonald list
  .path_long  = .lP$Input$StopLong,     # long Loughran-McDonald list
  .path_out   = .lP$Cache$StopWords     # standardised, cached for the workers to read
)

nrow(tab_stopdict)
```

Three passes, one function. They differ only in what they compute per file, and sharing the traversal means they cannot
drift apart in how they chunk, how they handle a failure, or which documents they cover. Each writes a cache and skips
if it is present.

```{r}
#| label: measure-errors
tab_errors <- edg_measure_corpus(
  .tab_idx  = tab_index,               # every document on disk
  .path_out = .lP$Cache$DocErrors,     # cache; present means finished
  .fun      = edg_doc_error,           # reads the parse status recorded at download time
  .workers  = .lP$Param$Workers,       # parallel workers
  .label    = "parse errors"           # shown in progress output
)
```

```{r}
#| label: measure-stats
tab_stats_raw <- edg_measure_corpus(
  .tab_idx  = tab_index,               # every document on disk
  .path_out = .lP$Cache$DocStats,      # cache; present means finished
  .fun      = edg_doc_stats,           # word, character and numeric counts plus the header fields
  .workers  = .lP$Param$Workers,       # parallel workers
  .label    = "text statistics"        # shown in progress output
)
```

```{r}
#| label: measure-stopwords
tab_stop_raw <- edg_measure_corpus(
  .tab_idx  = tab_index,                                            # every document on disk
  .path_out = .lP$Cache$DocStop,                                    # cache; present means finished
  .fun      = \(.p) edg_doc_stopwords(.p, .lP$Cache$StopWords),     # dictionary path closed over
  .workers  = .lP$Param$Workers,                                    # parallel workers
  .label    = "stopword counts"                                     # shown in progress output
)
```

```{r}
#| label: report-errors
edg_report_errors(.tab_err = tab_errors)
```

The three passes are joined into one table per document. The adjusted word count is computed here, and the numeric share
is capped at one: the numerator counts numeric tokens with one pattern and the denominator counts words with another, so
on documents that are almost entirely digits the two disagree enough to exceed unity. The cap is honest because the
quantity is only ever used against a threshold well below it.

```{r}
#| label: build-docstats
tab_docstats <- edg_doc_statistics(
  .tab_stats = tab_stats_raw,   # text statistics pass
  .tab_stop  = tab_stop_raw     # stopword pass
)

arrow::write_parquet(tab_docstats, .lP$Output$DocStats)
nrow(tab_docstats)
```

# Selection

The three rules below decide what is analysable, so they are written out here rather than hidden behind a function call.
Thresholds and their order are the argument a referee would want to see.

```{r}
#| label: flag-removals
tab_removed <- edg_flag_removals(
  .tab_stats = tab_docstats,   # the per-document measurements
  .tab_idx   = tab_index       # supplies the document type for reporting
)

arrow::write_parquet(tab_removed, .lP$Output$RemovedDocs)
nrow(tab_removed)
```

```{r}
#| label: report-removals
edg_report_removals(.tab_rem = tab_removed, .tab_idx = tab_index)
```

# Restriction

Three upstream tables are restricted to the filings whose documents were actually retrieved. The unrestricted versions
stay where 01A and 01B wrote them, because they are the denominators for every coverage statement made later, and a
pipeline that overwrites its own denominator cannot report how much it lost.

```{r}
#| label: restrict-upstream
use_ids_ <- tab_index$DocID

tab_links <- arrow::open_dataset(sources = .lP$Edgar$DocLinks$DirMain$Links) |>
  dplyr::filter(.data$DocID %in% use_ids_) |>
  dplyr::rename(
    YQ = "YearQuarter", DocSeq = "Seq", DocDesc = "Description",
    DocName = "Document", DocType = "Type", DocSize = "Size"
  ) |>
  dplyr::collect()

use_idx_ <- unique(tab_links$HashIndex)

tab_master <- arrow::open_dataset(sources = .lP$Edgar$MasterIndex$DirParquet) |>
  dplyr::filter(.data$HashIndex %in% use_idx_) |>
  dplyr::rename(YQ = "YearQuarter") |>
  dplyr::select(-dplyr::any_of(c("Year", "Quarter"))) |>
  dplyr::collect()

tab_landing <- arrow::open_dataset(sources = .lP$Input$LandingPageAll) |>
  dplyr::filter(.data$HashIndex %in% use_idx_) |>
  dplyr::collect()

purrr::walk2(
  .x = list(tab_links, tab_master, tab_landing),
  .y = c(.lP$Output$LinkData, .lP$Output$MasterIndex, .lP$Output$LandingPage),
  .f = arrow::write_parquet
)

c(Links = nrow(tab_links), Master = nrow(tab_master), Landing = nrow(tab_landing))
```

# Deployment

`FullMetaData.parquet` joins the three restricted tables to the document statistics. Two derived columns are added.

`MultFiler` marks documents filed by more than one registrant. The same agreement is filed by every party to it, so one
document legitimately appears under several CIKs; the flag makes those rows identifiable rather than looking like
duplicates.

`Removed` carries the quality decision. The row stays.

```{r}
#| label: build-metadata
rem_ids_ <- tab_removed$DocID

tab_metadata <- tab_links |>
  dplyr::inner_join(tab_master, by = dplyr::join_by("HashIndex", "CIK", "YQ")) |>
  dplyr::inner_join(tab_docstats, by = dplyr::join_by("DocID")) |>
  dplyr::mutate(
    nCIK      = dplyr::n(),
    MultFiler = as.integer(.data$nCIK > 1L),
    .by       = "HashDocument"
  ) |>
  dplyr::mutate(Removed = as.integer(.data$DocID %in% rem_ids_)) |>
  dplyr::inner_join(
    y  = dplyr::select(tab_index, "DocID", DocTypeMod = "DocType", DocPath = "Path"),
    by = dplyr::join_by("DocID")
  ) |>
  dplyr::rename(DocTypeRaw = "DocType") |>
  dplyr::relocate("DocTypeMod", .after = "DocTypeRaw")

arrow::write_parquet(tab_metadata, .lP$Output$FullMetaData)
nrow(tab_metadata)
```

# Validation

Four checks. Each states its expectation first, so a result that differs is a finding rather than a number to interpret
afterwards.

```{r}
#| label: validate-metadata
# 1. The two inner joins can only lose rows. Anything lost is a document whose link row has no
#    matching index entry, which is a join failure rather than a filtering decision.
# 2. Every flagged document should appear in the final table, marked rather than absent.
# 3. DocID identifies a document, so it should be unique.
# 4. Jointly filed copies of the same agreement should be byte-identical. Where they are not, the
#    joint filing is not in fact the same document.
tibble::tibble(
  RowsLinks       = nrow(tab_links),
  RowsMetaData    = nrow(tab_metadata),
  LostInJoin      = nrow(tab_links) - nrow(tab_metadata),
  FlaggedTotal    = nrow(tab_removed),
  FlaggedInTable  = sum(tab_metadata$Removed),
  DuplicateDocID  = sum(duplicated(tab_metadata$DocID))
) |>
  tbl_out(
    .title = "Consolidation checks",
    .notes = c(
      LostInJoin     = "Nonzero means link rows with no matching master-index entry.",
      FlaggedInTable = "Should equal FlaggedTotal: flagged documents are marked, not dropped."
    )
  )
```

```{r}
#| label: validate-multifiler
edg_multifiler_check(.tab_meta = tab_metadata) |>
  tbl_out(
    .title  = "Jointly filed documents",
    .pct    = "ShareAgreeing",
    .digits = 1L,
    .notes  = c(ShareAgreeing = "Copies agreeing on both file size and character count.")
  )
```

# Overview

```{r}
#| label: fig-removals-by-rule
#| fig-height: 2.4
#| fig-cap: "Documents flagged by each quality rule. Rules are applied in order, so a document
#|   caught by two is attributed to the first."
gg_removals <- edg_plot_removals(.tab = edg_removal_summary(.tab_rem = tab_removed, .tab_idx = tab_index))

plot_save(
  .plot    = gg_removals,               # the figure
  .name    = "removals-by-rule",        # meaningful filename, not unnamed-chunk-N
  .dir     = .lP$Output$Figures,        # figure destination
  .height  = 2.4,                       # from the ladder: three rows is a low panel
  .width   = 7.5,                       # the fixed project width
  .formats = c("pdf", "png"),           # manuscript and web
  .dpi     = 300                        # print resolution
)

gg_removals
```

```{r}
#| label: overview-all
edg_report_all_meta(
  .tab_err  = tab_errors,      # parse status per document
  .tab_rem  = tab_removed,     # what the rules flagged
  .tab_idx  = tab_index,       # the corpus, as denominator
  .tab_meta = tab_metadata     # the consolidated table
)
```

# Next

**02-SelectSample** merges `FullMetaData.parquet` to Compustat and defines the descriptive and estimation samples. It is
a sibling of the classification and entity families rather than an ancestor: **03** reads this table directly for
contract classification, and **04** for named-entity extraction. All three filter on `Removed == 0`.
