---
title: "Sample Selection (02)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/02-SelectSample.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

01C produced one metadata table describing every document acquired. This joins it to Compustat fundamentals on the
filing date, applies the sample ladder, and writes one table per group for the empirical analysis.

It is a sibling of the classification and entity families rather than an ancestor. Nothing in 03 or 04 reads what this
produces: those work from 01C's metadata directly, because they need text and this needs financial covariates. A
document excluded here is still classified there, and that is intended.

## The two samples, and why there are two

**The descriptive sample** is every well-formatted document filed inside the window. It is what the corpus can describe,
and it does not require the filer to be in Compustat -- roughly a fifth of EDGAR registrants never are, being foreign
private issuers, funds, or firms too small to be covered.

**The estimation sample** is the subset that also matched a Compustat quarter. It is what a regression can use.

Reporting only the second would understate the corpus by whatever share of filers Compustat misses, and reporting only
the first would overstate what the analysis rests on. The selection table below shows both.

## Matching a filing date to a fiscal quarter

A filing carries a date; Compustat carries fiscal quarters. Matching them means turning each quarter into an interval
and asking which one contains the filing date -- which is only well defined if a firm has one observation per quarter,
and Compustat does not guarantee that.

Four deduplications run in order, each keeping the observation with the larger total assets: the same quarter can appear
under two gvkeys after a restructuring, under two CIKs, or simply twice. Sorting on assets keeps the parent rather than
a subsidiary shell where the two differ.

Each quarter's interval then runs to the start of the next. A firm that stops reporting would otherwise leave an
interval running to its next appearance years later, and a filing in that gap would be matched to a quarter it has no
business being matched to, so any interval longer than one quarter is truncated.

## Frozen acquisition

The two WRDS downloads sit behind `.lP$Param$Acquire`, defaulting to `FALSE`, exactly as the EDGAR downloads do in 01A
and 01B. Credentials are read inside that chunk and nowhere else, so a missing key file is an error only when a
connection is actually wanted -- the document renders without one.

# Configuration

```{r}
#| label: config
.dir_meta <- here::here("2_output", "01C-EdgarMetaData")

.lP <- list(
  Input = list(
    MetaData    = fs::path(.dir_meta, "FullMetaData.parquet"),   # written by 01C
    LandingPage = fs::path(.dir_meta, "LandingPage.parquet"),    # written by 01C, for the item lists
    Credentials = here::here("0_data", "ApiKeys", "WRDS.txt")    # read only when acquiring
  ),
  Compustat = list(
    AnnualData   = utils_file_path(.dir_main, "Compustat", "AnnualData.parquet"),
    QuarterData  = utils_file_path(.dir_main, "Compustat", "QuarterData.parquet"),
    QuarterRange = utils_file_path(.dir_main, "Compustat", "QuarterRange.parquet")
  ),
  Output = list(
    Exhibit10 = utils_file_path(.dir_main, "SampleExhibit10.parquet"),
    Filing08K = utils_file_path(.dir_main, "SampleFiling08K.parquet"),
    FilingCTO = utils_file_path(.dir_main, "SampleFilingCTO.parquet")
  ),
  Overview = list(
    Exhibit10 = utils_file_path(.dir_main, "Overview", "SampleSelectExhibit10.parquet"),
    Filing08K = utils_file_path(.dir_main, "Overview", "SampleSelectFiling08K.parquet"),
    FilingCTO = utils_file_path(.dir_main, "Overview", "SampleSelectFilingCTO.parquet")
  ),
  Overviews = list(
    FilingOverview = utils_file_path(.dir_main, "Overview", "FilingOverviews.parquet"),
    Ex10FormCount  = utils_file_path(.dir_main, "Overview", "Ex10FilingCount.parquet")
  ),
  Figures = utils_file_path(.dir_main, "Figures"),
  Param = list(
    YearMin = 2001L,        # window floor; see the ladder below
    YearMax = 2024L,        # window ceiling, matching the acquisition frame closed in 01A
    DateCol = "DateFiled",  # the filing-date column in FullMetaData; asserted below
    Acquire = FALSE         # TRUE permits the two WRDS downloads to run
  )
)

# The metadata schema is printed rather than assumed. The interval join names its date column
# literally, so a rename upstream would otherwise surface as an unhelpful join error much later.
cols_meta_ <- names(arrow::open_dataset(.lP$Input$MetaData))

if (!.lP$Param$DateCol %in% cols_meta_) {
  cli::cli_abort(
    "DateCol {(.lP$Param$DateCol)} is not in FullMetaData. Available: {paste(cols_meta_, collapse = ', ')}"
  )
}

tibble::tibble(Input = names(.lP$Input), Path = unname(unlist(.lP$Input))) |>
  dplyr::mutate(Exists = fs::file_exists(.data$Path)) |>
  tbl_out(.title = "Inputs", .notes = c(Exists = "Credentials are read only when acquiring."))
```

`rWRDS` is installed from `0_data/Binaries/` and is not on CRAN.

# Acquisition

Both chunks are gated and report what they did either way. `apply_screening_conditions()` is the package's standard
academic filter; requiring a non-missing CIK is what makes the table joinable to EDGAR at all, since CIK is the only
identifier the two sources share.

```{r}
#| label: acquire-annual
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "funda") |>
    dplyr::distinct() |>
    dplyr::mutate(fqtr = 4L) |>                       # annual data is the fourth quarter by convention
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Compustat$AnnualData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: annual fundamentals were not refreshed.")
}
```

```{r}
#| label: acquire-quarterly
if (isTRUE(.lP$Param$Acquire)) {
  cred_ <- readLines(.lP$Input$Credentials, warn = FALSE)
  con_  <- rWRDS::wrds_db_connect(cred_[1], cred_[2])
  on.exit(rWRDS::wrds_db_disconnect(con_), add = TRUE)

  rWRDS::wrds_get_data(con_, "comp", "fundq") |>
    dplyr::distinct() |>
    rWRDS::apply_screening_conditions() |>
    dplyr::filter(!is.na(.data$cik)) |>               # no CIK means no join to EDGAR
    arrow::write_parquet(.lP$Compustat$QuarterData)

  rm(cred_)
  invisible(gc())
} else {
  cli::cli_alert_info("Acquisition is OFF: quarterly fundamentals were not refreshed.")
}
```

# The matching frame

```{r}
#| label: build-range
tab_range <- smp_compustat_range(
  .path_quarter = .lP$Compustat$QuarterData,     # quarterly fundamentals
  .path_out     = .lP$Compustat$QuarterRange     # one interval per firm-quarter
)

smp_compustat_summary(.tab_range = tab_range) |>
  tbl_out(
    .title  = "Compustat coverage",
    .pct    = "ShareCapped",
    .digits = 1L,
    .notes  = c(ShareCapped = "Intervals truncated to one quarter because the firm stopped reporting.")
  )
```

```{r}
#| label: build-items
tab_items <- smp_filing_items(.path_landing = .lP$Input$LandingPage)

nrow(tab_items)
```

# Merging

Three groups, merged independently and reported independently throughout. Exhibit 10 is most of the corpus, so a pooled
attrition rate would be the Exhibit 10 rate with the other two averaged into invisibility.

```{r}
#| label: merge-groups
lst_merged <- purrr::map(
  .x = c(Exhibit10 = "Exhibit10", Filing08K = "8-K", FilingCTO = "CTO"),
  .f = function(.g) {
    smp_merge_group(
      .path_meta = .lP$Input$MetaData,   # 01C's consolidated table
      .group     = .g,                   # which document type
      .tab_range = tab_range,            # the Compustat intervals
      .tab_items = tab_items,            # the 8-K item lists
      .date_col  = .lP$Param$DateCol     # the filing-date column, asserted in the configuration
    )
  }
)

purrr::map_int(lst_merged, nrow)
```

The interval join returns more than one row for a document if two of a firm's quarter windows overlap. Those documents
cannot be assigned a fiscal quarter and are dropped -- but counted first, because an exclusion applied without being
counted is indistinguishable from a document that was never selected.

```{r}
#| label: report-multimatch
purrr::imap(lst_merged, \(.t, .g) dplyr::mutate(smp_multimatch_summary(.tab = .t), Group = .g)) |>
  dplyr::bind_rows() |>
  dplyr::relocate("Group") |>
  tbl_out(
    .title  = "Documents matching more than one Compustat quarter",
    .pct    = "ShareMultiMatched",
    .digits = 2L,
    .notes  = c(nMultiMatched = "Dropped below: no single fiscal quarter can be assigned to them.")
  )

lst_merged <- purrr::map(lst_merged, \(.t) dplyr::filter(.t, dplyr::n() == 1L, .by = "DocID"))
```

# Selection

The ladder below is the sample definition for the entire study, so it is written here rather than hidden behind a
function call. It is applied to each group identically; the thresholds and their order are the argument a referee would
want to see.

Order matters. A malformatted document filed outside the window is attributed to the window, not to the quality rule,
because the window is the prior restriction. A document whose filer is absent from Compustat is attributed to coverage
rather than to matching, because there was nothing to match against.

```{r}
#| label: apply-ladder
lst_samples <- purrr::map(
  .x = lst_merged,
  .f = function(.t) {
    .t |>
      dplyr::mutate(
        SampleStepDesc = dplyr::case_when(
          !dplyr::between(lubridate::year(.data$DateFiled),
                          .lP$Param$YearMin, .lP$Param$YearMax) ~ "01-Less: Outside 2001 - 2024",
          .data$Removed == 1L                                   ~ "02-Less: Malformatted Documents",
          !.data$CIK %in% tab_range$CIK                         ~ "03-Less: CIK not in Compustat",
          is.na(.data$gvkey)                                    ~ "04-Less: No Compustat Match on Filing Date",
          .default                                              = "05-Final Sample"
        )
      ) |>
      smp_sample_flags() |>
      smp_tidy_sample()
  }
)

purrr::iwalk(
  .x = lst_samples,
  .f = function(.t, .g) arrow::write_parquet(.t, .lP$Output[[.g]])
)

purrr::map_int(lst_samples, \(.t) sum(.t$EstiSample))
```

The window floor of `r .lP$Param$YearMin` is a research decision rather than a data limit: EDGAR carries filings from
1993, but the modern 8-K item structure that makes a material definitive agreement identifiable dates from the 2004
reform, and the years before 2001 are thin enough that including them would add noise without adding statistical power.
The ceiling matches the acquisition frame closed in 01A, so the two cannot drift apart.

# Results

The first row is the corpus as 01C published it, less the documents dropped above for matching more than one Compustat
quarter. That is the one exclusion in this document that happens outside the ladder, and it is named on the table
rather than left to be found by differencing two numbers.

```{r}
#| label: report-selection
purrr::iwalk(
  .x = lst_samples,
  .f = function(.t, .g) {
    sel_ <- smp_report_selection(.tab = .t, .group = .g)
    arrow::write_parquet(sel_, .lP$Overview[[.g]])
  }
)
```

# Composition

Every count reported from here on is a slice of one table, built once so the slices cannot disagree. It carries each
group under both sample definitions, and at two levels of uniqueness.

The two levels answer different questions. How many contract *documents* were filed is a question about disclosure
activity; how many distinct *contracts* exist is a question about the corpus. They differ by the roughly sixteen per
cent of documents that are one attachment fetched under several registrants, and quoting either figure without saying
which is what makes two numbers in one paper irreconcilable.

Reducing to one row per attachment means choosing which registrant's row survives. That choice is made on `DocID`, so
it is the same on every run; left to whatever order the data happened to be read in, it is not. No count depends on it
-- `FormType` is constant within an attachment, and the form-type table below is identical either way -- but the
covariates carried alongside are whichever registrant's row was kept, and that should not be arbitrary.

```{r}
#| label: build-overview
tab_overview <- smp_filing_overview(.lst_samples = lst_samples)

arrow::write_parquet(tab_overview, .lP$Overviews$FilingOverview)
tab_overview |>
  dplyr::summarise(nRows = dplyr::n(), .by = c("sType", "uType")) |>
  tidyr::pivot_wider(names_from = "uType", values_from = "nRows") |>
  tbl_out(.title = "Rows per slice")
```

```{r}
#| label: report-form-counts
tab_form_counts <- smp_form_counts(.tab_overview = tab_overview)

arrow::write_parquet(tab_form_counts, .lP$Overviews$Ex10FormCount)
tbl_out(
  .tab   = tab_form_counts,
  .title = "Contracts by form type",
  .notes = c(UniqueType = "All Contracts counts documents; Unique Contracts counts attachments.")
)
```

# Validation

Three checks. Each states its expectation first, so a result that differs is a finding rather than a number to
interpret afterwards.

```{r}
#| label: validate-samples
# 1. DocID identifies a document, so it should be unique after the multi-match drop.
# 2. Every estimation-sample row should carry a gvkey; the ladder places a missing one at step 04.
# 3. The estimation sample is a subset of the descriptive sample by construction, so no row should
#    be in the second without being in the first.
purrr::imap(
  .x = lst_samples,
  .f = function(.t, .g) {
    tibble::tibble(
      Group          = .g,
      nRows          = nrow(.t),
      DuplicateDocID = sum(duplicated(.t$DocID)),
      EstiNoGvkey    = sum(.t$EstiSample == 1L & is.na(.t$gvkey)),
      EstiNotDesc    = sum(.t$EstiSample == 1L & .t$DescSample == 0L)
    )
  }
) |>
  dplyr::bind_rows() |>
  tbl_out(
    .title = "Sample consistency",
    .notes = c(
      EstiNoGvkey = "Nonzero means a row reached step 05 without a Compustat match.",
      EstiNotDesc = "Nonzero means the two samples are not nested, which the ladder makes impossible."
    )
  )
```

# Deployment

```{r}
#| label: deploy-report
fs::file_info(c(unlist(.lP$Output), unlist(.lP$Overviews), .lP$Compustat$QuarterRange)) |>
  dplyr::mutate(Item = fs::path_file(.data$path)) |>
  dplyr::select("Item", "size") |>
  tbl_out(.title = "Written")
```

Nothing is exported to Stata here. Format conversion is not this script's concern: every stage would otherwise carry
its own exporter, they would drift in how they name and order things, and the two Compustat tables would be rewritten
on every render of a document that does not change them. One release script converts everything once, when the
pipeline is complete.

# Overview

```{r}
#| label: fig-forms
#| fig-height: 3.4
#| fig-cap: "Contracts by the SEC form they were attached to, split by whether that filing was an
#|   original or an amendment. Four panels: the descriptive and estimation samples, each counted per
#|   document and per attachment. Registration statements carry proportionally more amendments than
#|   periodic reports, which is a property of how those forms are used rather than of the contracts."
cells_ <- tab_overview |>
  dplyr::filter(startsWith(.data$sType, "EX10")) |>
  dplyr::distinct(.data$sType, .data$uType)

lst_forms <- purrr::pmap(
  .l = list(cells_$sType, cells_$uType),
  .f = function(.s, .u) {
    gg_ <- smp_plot_forms(
      .tab = smp_form_composition(
        .tab = dplyr::filter(tab_overview, .data$sType == .s, .data$uType == .u)
      )
    )

    plot_save(
      .plot    = gg_,                                                     # the figure
      .name    = gsub("[ :]", "", paste0(.u, "-", gsub(": ", "-", .s))),  # matches the published names
      .dir     = .lP$Figures,                                             # figure destination
      .height  = 3.4,                                                     # a categorical comparison
      .width   = 7.5,                                                     # the fixed project width
      .formats = c("pdf", "png"),                                         # manuscript and web
      .dpi     = 300                                                      # print resolution
    )

    gg_
  }
)

lst_forms[[1]]
```

```{r}
#| label: overview-all
smp_report_all(
  .lst_samples = lst_samples,   # the three sample tables
  .tab_range   = tab_range      # the Compustat matching frame
)
```

# Next

**03** classifies the contracts and **04** extracts named entities, both reading 01C's metadata rather than anything
written here. The estimation samples produced above feed the Stata analysis directly.
