---
title: "Contract Classification -- Building the Training Sample (03A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim.
knitr::opts_chunk$set(root.dir = here::here(), message = TRUE, warning = FALSE, comment = "")

# Plain ASCII console output; no ANSI colour codes.
options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/03A-ClassifyPrepare.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Roughly 4,400 SEC Exhibit-10 material contracts have been labelled by hand. This document turns that label list into a
single table, `prepared.parquet`, holding for each document its text, its labels for all three classification tasks, and
the cross-validation fold it belongs to.

Nothing is estimated here. The document makes three decisions and reports them:

1. **Which documents are eligible.** A label alone is not sufficient; the document also needs readable text on
disk. Every exclusion is reported with its reason.
2. **What the labels are.** Three tasks, all predicted from the same text.
3. **Which fold each document belongs to.** Dealt once, here, so that every method evaluated downstream is
scored on identical splits.

## The three tasks

| Task | Label | Categories | Question |
|:--|:--|--:|:--|
| Detailed | `ClassDetailed` | 12 | Which contract type is this? |
| Broad | `ClassBroad` | 7 | The same question, at a coarser level |
| Amendment | `AmendType` | 2 | Is this an original agreement or an amendment? |

The broad taxonomy is a strict roll-up of the detailed one rather than an independent labelling: every detailed category
has exactly one broad parent. The amendment label is orthogonal to both.

## Why folds are dealt here

Fold assignment belongs upstream of every method that uses it. Three classifiers are evaluated in this pipeline -- a
transformer, a keyword miner, and a router combining them -- and comparing them is only meaningful if each is scored on
the same held-out documents. If each dealt its own folds, a difference between methods could not be distinguished from a
difference between splits.

Folds are stratified on the detailed taxonomy, which is the finest partition, so stratification there also balances the
coarser one. The rarest detailed category is therefore the binding constraint on how thin a fold can become.

## One label per document

A minority of documents carry a second valid category, recorded as `ClassDetailed2`. Training uses the primary category
only; the second label is never a target. It is retained for lenient scoring, which asks whether a prediction counted as
wrong was in fact the document's other valid answer. The gap between strict and lenient scoring is therefore a measure of
taxonomic ambiguity rather than of model error.

The primary is not an arbitrary pick between two equivalent answers. Every dual-classified document was reviewed by hand
and the intended primary recorded, so the ordering carries information.

# Configuration

```{r}
.lP <- list(
  Input = list(
    # The reconciled label spine. Read as CSV rather than Parquet because the current export was
    # produced outside the repository; the schema is identical either way.
    ClassificationSample = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MaterialContractClassification/DocumentClassification/02-AK_classification_comparison/final_classification.csv",
    MetaData     = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",      # filer titles
    DirContracts = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/"     # parsed text
  ),
  Cache = list(
    ContractFiles = utils_file_path(.dir_main, "Cache", "ContractFiles.parquet")   # DocID to Path index
  ),
  Output = list(
    Prepared = utils_file_path(.dir_main, "prepared.parquet")                      # the one downstream input
  ),
  Runs = list(
    Bert = here::here("2_output", "03B-ClassifyTrainBERT", "runs"),                # consumers of this output
    Kw   = here::here("2_output", "03C-ClassifyTrainKeyword", "runs")
  )
)

fs::file_exists(.lP$Input$ClassificationSample)
```

Failing here, rather than three chunks later, is deliberate: a missing label spine should stop the document at the point
the path is declared.

# Input

Three sources join on `DocID`:

- **The label spine** supplies the taxonomy (`DocClassFinal1`, `DocClassFinal2`), the amendment flag, and
`Provenance`, which records which labelling round each label came from.
- **The metadata** supplies `DocDesc`, the filer's own title for the exhibit, and `DocName`, the filename.
Both are inputs to the keyword classifier only; the transformer ignores them.
- **The parsed-contract tree** supplies `Path`, locating each document's text on disk.

```{r}
# Walk the parsed-contract tree once and cache the DocID -> Path index. .rerun = FALSE reuses the
# cache; set it to TRUE after new contracts have been parsed.
fils_contract <- utils_list_project_files(
  .dir_data = .lP$Input$DirContracts,      # root of the parsed-contract tree
  .path_out = .lP$Cache$ContractFiles,     # where the index is cached
  .rerun    = FALSE                        # FALSE reuses an existing index
)

# Read the label spine with readr, not arrow::open_dataset(format = "csv"). Arrow's
# strings_can_be_null convert option defaults to FALSE, so a bare NA in a character column arrives as
# the literal two-letter string, silently creating a thirteenth category and making every document
# appear dual-labelled. readr treats "" and NA as missing by default.
fils_class_sample <- readr::read_csv(
  file      = .lP$Input$ClassificationSample,      # reconciled label spine
  col_types = readr::cols(                         # everything character except the dual-class flag
    .default  = readr::col_character(),
    DualClass = readr::col_integer()
  )
) |>
  # Keep only what the pipeline consumes; the reconciliation carries further columns of its own history.
  dplyr::select(
    DocID, AmendType, DocClassFinal1, DocClassFinal2, DualClass,
    Level1, Level2, Provenance
  ) |>
  # Attach the filer title and the filename.
  dplyr::left_join(
    y  = arrow::open_dataset(sources = .lP$Input$MetaData) |>
      dplyr::select(DocID, DocDesc, DocName) |>
      dplyr::collect(),
    by = dplyr::join_by(DocID)
  ) |>
  # Attach the path to each document's parsed text.
  dplyr::left_join(
    y  = fils_contract,
    by = dplyr::join_by(DocID)
  )
```

Coverage of each join, before any filtering. A shortfall here is a join failure; the filtering that follows is reported
separately, so the two cannot be confused.

```{r}
cli::cli_h2("Raw input")
clf_say_table(
  .tab = tibble::tibble(
    Source = c(
      "Label rows read",
      "  with a class label",
      "  with metadata (DocDesc)",
      "  with a contract file path"
    ),
    N = c(
      nrow(fils_class_sample),
      sum(!is.na(fils_class_sample$DocClassFinal1)),
      sum(!is.na(fils_class_sample$DocDesc)),
      sum(!is.na(fils_class_sample$Path))
    )
  )
)
```

# Construction

`clf_prepare_sample()` applies four gates in order -- a usable class label, a file path, a file that exists, and text that
is non-empty -- then deals the folds. It narrates each gate as it runs, so an unexpected exclusion is visible immediately
rather than surfacing as a row-count mismatch three scripts later.

```{r}
tab_prep <- clf_prepare_sample(
  .tab_input = fils_class_sample,   # joined labels, metadata and paths
  .round     = NULL,                # NULL keeps both labelling rounds; see Robustness below
  .k         = 5L,                  # number of cross-validation folds
  .seed      = 42L                  # fixes the fold deal, so the splits are reproducible
)
```

```{r}
clf_write_prepared(
  .tab      = tab_prep,             # the prepared sample
  .path_out = .lP$Output$Prepared   # the single file every downstream method reads
)
```

Training on both labelling rounds combined, rather than on the manually-checked round alone, is the most consequential
choice made in this document. The second round is enriched for the categories introduced by the current taxonomy and is
small; the first round supplies the volume the common categories need. Restricting to the second alone was tried and
produces a classifier that fails on everything except the rare categories.

# Results

One call prints the full picture: intake, tasks, class distributions, dual labels, fold balance, document length, and
missingness. This is the block to copy when something needs checking.

```{r}
clf_report_sample(.tab = tab_prep)
```

## How to read it

**Intake.** Every document that left the sample, and at which gate. A drop at *Has a class label* is expected and reflects
documents the reconciliation could not resolve. A drop at *Has a contract file path* or *File exists on disk* is a join or
path failure, not a labelling one, and is worth stopping for.

**Tasks.** How many documents each task trains on and how many categories it must separate. Documents unlabelled for one
task are dropped by that task's trainer only; they still count for the others. The smallest category matters
disproportionately because the headline metric is macro-F1, which averages per-category F1 with equal weight regardless of
size.

**Class distribution.** Split by labelling round. Categories that exist only in the current taxonomy can by construction
appear only in the second round.

**Dual-class.** How many documents span two categories, and which pairs. Direction is meaningful: the primary was chosen
by review, so a pair running heavily one way reflects a consistent rule the reviewer applied.

**Fold balance.** Each fold is held out exactly once. A category thin enough to be absent from a fold leaves that fold's
recall for it undefined and makes macro-F1 unstable, so the smallest rows are the ones to watch.

**Document length.** Most contracts overflow both the 256- and 512-token windows, so a transformer reads only the opening
pages. That is the premise the pipeline rests on: contract type is legible from the title and preamble. It is also why the
sweep in 03B tests both window sizes rather than assuming the longer is better.

**Missing data.** Two kinds of missingness, and distinguishing them is the point. `ClassDetailed2` missing means the
document has a single category, which is a definition rather than a gap. `DocDesc` empty means the filer supplied no
title, and the keyword classifier abstains on those. Anything else should be zero.

# Robustness

Two properties of the sample are worth checking against the report above rather than assumed.

**Short documents.** A handful of documents pass the non-empty gate while carrying too little text to classify. Whether
they matter depends not on how many there are but on where they fall: a few dozen spread across the large categories are
harmless, whereas the same number concentrated in the smallest category would be a material share of it.

```{r}
tab_prep |>
  dplyr::mutate(Words = stringi::stri_count_regex(.data$Text, "\\S+")) |>
  dplyr::filter(.data$Words < 50) |>
  dplyr::count(.data$ClassDetailed, name = "Docs", sort = TRUE) |>
  clf_say_table(.title = "Documents under 50 words, by category")
```

**Fold stability.** Folds are dealt from a fixed seed, so they are reproducible, but reproducibility is not the same as
balance. The fold report above shows the realised counts; what matters is that no category disappears from any fold.

# Overview

The sample as it will be consumed downstream. Nothing here is new; the figures show what the tables above have already
reported.

```{r}
clf_report_tasks(.tab = tab_prep)
```

::: {.panel-tabset}

## Detailed

```{r}
#| fig-cap: "Category distribution, detailed taxonomy (12 categories)."
clf_plot_class_distribution(
  .tab        = tab_prep,           # prepared sample
  .level      = "ClassDetailed",    # taxonomy to plot
  .include_na = FALSE               # unlabelled documents were removed at the intake gate
)
```

## Broad

```{r}
#| fig-cap: "Category distribution, broad taxonomy (7 categories)."
#| fig-height: 3.2
clf_plot_class_distribution(
  .tab        = tab_prep,        # prepared sample
  .level      = "ClassBroad",    # taxonomy to plot
  .include_na = FALSE            # unlabelled documents were removed at the intake gate
)
```

## Amendment

```{r}
#| fig-cap: "Category distribution, amendment task (2 categories)."
#| fig-height: 2.2
clf_plot_class_distribution(
  .tab        = tab_prep,       # prepared sample
  .level      = "AmendType",    # task to plot
  .include_na = TRUE            # TRUE would surface any document lacking an amendment label
)
```

:::

The imbalance is steep at every level and steepest in the detailed taxonomy, where the largest category holds roughly ten
times as many documents as the smallest. This is why macro-F1 is the headline metric downstream: accuracy on this sample
is dominated by the three largest categories, and a classifier that ignored the rarest ones entirely would still score
well on it.

# Next

`prepared.parquet` is the single input to everything that follows. **03B** fine-tunes transformer encoders on it, **03C**
mines a keyword classifier on the same folds, and **03D** tests whether routing between the two improves on either alone.
All three source this document's function file, so the folds and the scoring code they share cannot drift apart. **03E**
applies the deployed models to the full corpus.

Beyond building the sample, this file holds the **shared scoring layer** every method reports through: `clf_scores()`,
`clf_perclass()` and `clf_confusion()` for metrics, abstention-aware so a classifier that declines to predict is scored
correctly; `clf_load_overall()`, `clf_leaderboard()` and `clf_effect()` for ranking configurations; and the `clf_plot_*()`
figures. Keeping them here rather than in each method's own file is what guarantees the three methods are compared by
identical code.

Two directories must be cleared whenever this document is re-run against a changed label spine, because **neither fails
loudly**: `2_output/_cache/`, since `clf_cache()` keys on a name rather than on the data behind it, and
`2_output/03B-ClassifyTrainBERT/runs/`, since run identity is derived from hyperparameters alone and carries no
fingerprint of the sample.
