---
title: "Named Entity Recognition"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here())

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_NER.R", encoding = "UTF-8")
source("1_code/_Ollama.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

## Path Tree

```{r}
.lP <- list(
  Input = list(
    ClassificationSample = "2_output/03A-ClassifyPrepare/prepared.parquet",
    DirContracts = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/"
  ),
  Cache = list(
    ContractFiles = utils_file_path(.dir_main, "Cache", "ContractFiles.parquet"),
    NerDB = utils_file_path(.dir_main, "Cache", "NerDB.duckdb")
  ),
  Output = list()
)
```

```{r}
.docs <- arrow::open_dataset(.lP$Input$ClassificationSample) |> 
  dplyr::select(DocID) |> 
  dplyr::collect() |> 
  dplyr::pull()

fils_contract_all <- utils_list_project_files(.lP$Input$DirContracts, .lP$Cache$ContractFiles, FALSE)
fils_contract_use <- dplyr::filter(fils_contract_all, DocID %in% .docs) 
  
```

```{r}
ner_tuning_default <- list(
  "spacy:en_core_web_sm"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_md"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_lg"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_trf" = list(n_process =  1L, batch_size = 128L, timeout = 600L),
  "lexnlp"                = list(n_process = 24L, batch_size =   8L, timeout =  60L),
  "paper:dateregex-v1"    = list(n_process =  1L, batch_size = NULL, timeout =   0L),
  "paper:gazetteer-v1"    = list(n_process = 16L, batch_size =   8L, timeout = 120L)
)


lst_tuning_default <- ner_run_args(ner_tuning_default)
```

```{r}
.fils_in <- fils_contract_use$Path

res_full <- ner_run(
  .inputs = .fils_in,
  .db_path = .lP$Cache$NerDB,
  .run = lst_tuning_default$.run,
  .labels = NULL,
  .max_chars = 2500000L,
  .retry_timeout = FALSE,
  .id_col = "DocID",
  .text_col = "TextRaw",
  .docs_per_run = 2500L,
  .device = "auto",
  .n_process = lst_tuning_default$.n_process,
  .batch_size = lst_tuning_default$.batch_size,
  .timeout = lst_tuning_default$.timeout,
  .keep_staging = FALSE,
  .quiet = FALSE
)
```

```{r}
.ov <- ner_overview(.lP$Cache$NerDB, .inputs = .fils_in)
.ov$ledger        # docs by status + hit rate, per engine:model
.ov$labels        # candidate / doc counts per engine:model x label
.ov$lengths       # document-length summary
```


```{r}
ner_plot_positions(.ov$positions)
```

```{r}
.al <- ner_alignment(.lP$Cache$NerDB)
.al$consensus      # per Label: mentions found by 1, 2, ... combos (of CombosEligible)
.al$pairwise       # per Label: pairwise Jaccard between combos
.al$mentions       # drill-down: every merged mention + the combo set that found it
```


```{r}
ner_plot_agreement(.al$pairwise)
```


## Per-Class Profile

What the candidate store finds per contract type. `refine_profile()` joins the store
to the classification labels and prints coverage, the per-doc denominator, the
reference-engine fingerprint, and the high-confidence (>= 2 engines) rate. Point
`.class_parquet` / `.class_col` at wherever the DocID -> label map lives; a wrong
column name aborts with the available columns listed.

```{r}
.prof <- refine_profile(
  .db_path       = .lP$Cache$NerDB,
  .class_parquet = .lP$Input$ClassificationSample,
  .class_col     = "ClassDetailed",
  .ref_combo     = "spacy:en_core_web_trf",
  .mentions      = .al$mentions
)
```

```{r}
ner_plot_profile(.prof$profile, .combo = "spacy:en_core_web_trf", .metric = "CandPerDoc")
```

```{r}
ner_plot_profile(.prof$profile, .combo = "spacy:en_core_web_trf", .metric = "PctDocsWithHit")
```


## Targeted Re-Run / Recovery

The 4 LexNLP timeouts carry partial hits and `Status = 'timeout'` is queryable, so no
action is required. To recover them cleanly, clear just those docs and re-run LexNLP
with a tighter per-doc char cap (its date grammar stalls on the few multi-MB
documents) and a longer leash. Run manually.

```{r}
#| eval: false
ner_db_clear(.lP$Cache$NerDB, "lexnlp", .status = "timeout")

res_retry <- ner_run(
  .inputs        = .fils_in,
  .db_path       = .lP$Cache$NerDB,
  .run           = "lexnlp",
  .labels        = NULL,
  .max_chars     = 1000000L,   # lexnlp-only here -- shorter than the global 2.5M
  .retry_timeout = FALSE,
  .id_col        = "DocID",
  .text_col      = "TextRaw",
  .docs_per_run  = 2500L,
  .n_process     = 24L,
  .batch_size    = 8L,
  .timeout       = 120L,        # give the date grammar a longer leash
  .quiet         = FALSE
)
```
