---
title: "Entity Rules -- Amounts (04B4)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")
source("1_code/_Commons/_Entity.R", encoding = "UTF-8")

purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B4-Rules-MONEY.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This is the least opinionated of the five rule documents, and it should be. There is no external fact
to anchor an amount against -- nothing in EDGAR records what a contract was worth -- and no taxonomy
that says which figure in a credit agreement is *the* amount. So this document does not invent one.
It reports what the extractors found, filters the two things that demonstrably are not amounts, and
puts the numbers beside the contract type so a reader can judge whether the ordering makes sense.

## Whole document, no region rule

Money is genuinely distributed: no engine exceeds a positional contrast of 1.85 between the ends and
the middle of a contract, against 22.6% and 25.2% in the two ends for organisations. There is nothing
for a window to separate, so there is no window.

## Currencies are never pooled

A maximum across currencies is not a quantity. `Currency` is populated on 100% of both money engines'
rows -- 42,937 of 42,937 -- so USD and non-USD are reported side by side at no cost.

## Why the sum survives, with a caveat attached

A contract restating the same fifty million across five clauses sums to two hundred and fifty
million, and **no filter can tell a restatement from a second obligation**. Rather than drop the sum,
this document reports **distinct amounts over total spans** beside it. That ratio says how much of a
class's total is repetition, which is the caveat the sum needs.

Maximum is the only unambiguous statistic -- the largest figure the contract names -- and it is
reported first.

## Two filters, both on things that are not amounts

A **zero**, and a figure preceded by **par-value language**. The store's two commonest money spans
are `$ 0` and `$ 0.00`, which is boilerplate about share denomination rather than anything a party
owes. Both are swept and the unfiltered row stays in every table.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "roles_money.parquet"), # one row per amount span
    Doc   = utils_file_path(.dir_main, "money_doc.parquet")    # one row per document and engine
  ),
  Params = list(
    Combos     = c(lexnlp = "lexnlp", moneyregex = "paper:moneyregex-v6"),
    ClassCombo = "moneyregex", # the engine the class tables are drawn from
    CueWin     = 60L,          # characters read before a span for the par-value cue
    ReadN      = 10L,
    ReadCtx    = 200L,
    CheckN     = 500L,
    Seed       = 42L
  )
)

.lP$Params$Spec <- mny_spec(
  .filter  = "par",  # drop zeros and par-value figures
  .cue_win = 60L
)

.lP$Params$Specs <- list(
  mny_spec(.filter = "none"),  # the unfiltered reference, kept in every table
  mny_spec(.filter = "zero"),
  mny_spec(.filter = "par")
)

fs::file_exists(unlist(.lP$Input))
```

# Sample

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)
tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)
```

```{r}
#| label: load-money
tab_money <- mny_load(
  .db_path   = .lP$Input$Store,
  .lens      = tab_lens,
  .path_text = .lP$Input$Text,
  .combos    = .lP$Params$Combos,
  .win       = .lP$Params$CueWin,
  .quiet     = FALSE
)

mny_report_parse(.money = tab_money)
```

# The variables

```{r}
#| label: aggregate-base
tab_agg <- mny_aggregate(
  .money = tab_money,
  .keys  = tab_keys,
  .spec  = .lP$Params$Spec   # the filter carried into the artifacts
)

tab_doc <- mny_doc_table(.agg = tab_agg, .keys = tab_keys)
```

```{r}
#| label: sweep-filters
tab_sweep <- mny_sweep(
  .money = tab_money,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

mny_report_sweep(.tab = tab_sweep)
```

```{r}
#| label: report-class-usd
mny_report_class(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "USD"
)
```

```{r}
#| label: report-class-other
mny_report_class(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "non-USD"
)
```

# Reading

```{r}
#| label: read-largest
# The largest figure in each of a few contracts, read to see whether it is an obligation, a cap, a
# share count that survived the parser or an authorised-capital line.
ent_read_spans(
  .tab       = tab_money |>
    dplyr::filter(.data$Parsed, !.data$IsZero, !.data$IsPar, .data$Block == "USD",
                  .data$Combo == .lP$Params$ClassCombo) |>
    dplyr::slice_max(.data$Amount, n = 400L, with_ties = FALSE),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "The largest amounts in the sample"
  )
```

```{r}
#| label: read-par
ent_read_spans(
  .tab       = dplyr::filter(tab_money, .data$IsPar),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "Figures preceded by par-value language -- what the filter removes"
  )
```

```{r}
#| label: read-nonusd
ent_read_spans(
  .tab       = dplyr::filter(tab_money, .data$Parsed, .data$Block == "non-USD"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "Amount", "Currency"),
    .title = "Non-USD amounts"
  )
```

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_money,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every parsed span carries a currency block",
    "No aggregated maximum is smaller than its median",
    "No aggregated sum is smaller than its maximum",
    "Distinct amounts never exceed spans",
    "Every document has a row per engine"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_money$Block[tab_money$Parsed])),
    sum(tab_agg$MoneyMax >= tab_agg$MoneyMed),
    sum(tab_agg$MoneySum >= tab_agg$MoneyMax),
    sum(tab_agg$NDistinct <= tab_agg$NSpans),
    nrow(tab_doc)
  ),
  Of = c(
    nrow(tab_check),
    sum(tab_money$Parsed),
    nrow(tab_agg),
    nrow(tab_agg),
    nrow(tab_agg),
    nrow(tab_keys) * dplyr::n_distinct(tab_agg$Combo)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

The middle three are arithmetic identities rather than tests of the extraction, and that is the
point: they fail only if an aggregation is wrong, which is the failure mode this document is most
exposed to and least able to see any other way.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_money, -dplyr::any_of("Before")), .lP$Output$Spans)
arrow::write_parquet(tab_doc, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Amount spans with currency, zero and par-value flags",
               "Money variables per document and engine, USD and non-USD side by side"),
  Path     = c(.lP$Output$Spans, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B4")
```

The span file keeps the flags rather than the filtered set, so a consumer wanting the unfiltered
count has it and one wanting the filter can apply the same two columns this document did.

# Overview

```{r}
#| label: fig-max
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Median of the largest USD amount named in a contract, by type. The sanity test is the
#|   ordering rather than the level: credit agreements and mergers should sit at the top and
#|   compensation agreements at the bottom."
mny_plot_max(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo,
  .block = "USD"
)
```

```{r}
#| label: fig-repeat
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of distinct amounts over total amount spans, for contracts
#|   naming at least three, by currency block. A contract near one names a different figure every
#|   time; one near zero repeats the same figure, and its sum is that figure counted again."
mny_plot_repeat(
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo
)
```

```{r}
#| label: report-everything
mny_report_all(
  .money = tab_money,
  .sweep = tab_sweep,
  .agg   = tab_agg,
  .combo = .lP$Params$ClassCombo
)
```

# Next

Two things are deliberately not attempted, and both would need a judgement this document has no
evidence for.

**No contract value.** Naming the largest figure "the contract value" would be a claim about which
obligation matters, and nothing in the data supports it. The maximum is released as the maximum.

**No scale correction.** A figure written "in thousands" in a table header is parsed at face value,
and no engine reads the header. That is a known understatement in an unknown share of documents; the
read blocks are where it would first become visible.
