---
title: "Contract Classification -- Transformer Classifier (03B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# Figure geometry is NOT set here -- it is declared once in _quarto.yml, and restating it per
# document is what let two documents drift to more than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                         # message = FALSE would discard this document's entire output
  warning  = FALSE,
  comment  = ""          # drops the "##" prefix, so console blocks copy verbatim
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns sample construction, the shared scoring layer, and the category vocabulary. Sourcing it
# here is what makes this document comparable with the keyword classifier, the language model and the
# router: identical scoring code on identical folds, and the same twelve categories drawn in the same
# order in every figure.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/03B-ClassifyTrainBERT.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document fine-tunes transformer encoders to classify SEC Exhibit-10 material contracts, selects one configuration per
task by cross-validation, and refits the selected configurations on the full labelled sample for deployment.

Three classification tasks are estimated from the same document text:

| Task | Label | Categories | Question |
|:--|:--|--:|:--|
| Detailed | `ClassDetailed` | 12 | Which contract type is this? |
| Broad | `ClassBroad` | 7 | The same question, at a coarser level |
| Amendment | `AmendType` | 2 | Is this an original agreement or an amendment? |

The broad taxonomy is a strict roll-up of the detailed one: every detailed category has exactly one broad parent. The
amendment label is orthogonal to both.

## Method

Model selection uses **5-fold cross-validation** over a fixed grid. Folds are dealt once, in 03A, stratified on the
detailed taxonomy, and every task and every method in the wider pipeline reuses them; comparisons across configurations
and across methods are therefore paired rather than confounded by different splits.

Reported scores are **pooled out-of-fold**: each document is predicted exactly once, by the fold model that did not see it
during training. No separate held-out test set is reserved. With the rarest category at 71 documents, withholding a
further fifth would leave roughly 14 examples on which to estimate that category's performance, and the resulting estimate
would be noisier than the cross-validated one it was meant to check. Cross-validated scores are a conservative estimate of
the deployed model's performance, since each fold model trains on 80% of the data and the deployed model trains on all of
it.

The primary metric is **macro-F1**, the unweighted mean of per-category F1. Accuracy is reported alongside it but is
dominated by the three largest categories, which together account for roughly 47% of the sample. Macro-F1 gives a category
of 71 documents the same weight as one of 723, which is the appropriate criterion when the classifier's output will be
used to construct category-level samples for downstream research.

Documents carrying a second valid category are trained and scored on the primary category only. The primary was assigned
by manual review rather than by list order, so it is not an arbitrary choice between two equivalent answers.

## Reproducibility

Every chunk in this document executes and no result is read from cache. This is affordable because training is
idempotent: `bert_sweep()` inspects the run directory, trains only configurations whose metrics are absent, and skips the
rest. The first execution trains the full grid; subsequent executions complete in seconds and reproduce identical output.

There is one deliberate exception. `RunSweep` and `RunDeploy` in the configuration below gate the two steps that spend GPU
time, so the document can be rendered while the sweep is still in progress. They are separate flags because they answer
different questions: whether to keep estimating the design, and whether to fit the configurations the evidence so far has
crowned. Holding the first while setting the second deploys provisionally -- useful for exercising the stages downstream,
and stated as such wherever it has consequences. That convenience is also the failure mode the no-caching rule exists to
prevent: a partially estimated grid still yields a leaderboard, a marginal-effect table and a crowned configuration, all
of which look entirely normal. The Sweep coverage section immediately after training reports what the results rest on,
both gated steps announce the skip rather than passing over it quietly, and the deployment section reports which crowned
configurations actually have a model behind them.

Two further consequences follow, and both are deliberate. Deleting the run directory forces a complete retrain. Changing
the labelled sample without deleting it produces stale results silently, because run identity is derived from
hyperparameters alone and carries no fingerprint of the data.

Sections up to the Overview report in plain text only. All figures are collected in the Overview at the end, so that the
argument can be followed linearly and the evidence inspected as a whole.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 03A is the sole writer of prepared.parquet. Its location is resolved through the same helper 03A
    # used, so this path cannot drift from where the file was actually written.
    Prepared = utils_file_path(
      init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
      "prepared.parquet"
    )
  ),
  Runs = list(
    Bert = here::here("2_output", "03B-ClassifyTrainBERT", "runs") # one folder per training run
  ),
  Output = list(
    Classification = utils_file_path(.dir_main, "classification"), # per-document predictions
    ModelFinal     = utils_file_path(.dir_main, "model_final") # deployable models
  ),
  Engine = list(
    Python = here::here("contracts-engine", ".venv", "bin", "python"), # training environment
    Script = here::here("contracts-engine", "classify_train.py")       # training entry point
  ),
  Param = list(
    # The two GPU-spending steps are gated separately, because holding one is not a reason to hold
    # the other. TRUE on both is the only setting under which this document's claims about its own
    # design are true; anything else renders against whatever runs already exist and is reported as
    # a failure state everywhere it has consequences.
    RunSweep  = TRUE, # FALSE reports the training plan and trains nothing
    # FALSE leaves the crowned configurations unfitted, so the orchestration stage has no artifact
    # to pin. TRUE with RunSweep FALSE fits the crowns of a partial grid: a deployable pipeline built
    # on a design that is not yet estimated, which is worth having while the stages downstream are
    # still being built and is worth nothing as a result.
    RunDeploy = TRUE,
    # Destructive, and on the page for that reason. TRUE deletes any model under the deployment
    # directory that is no longer crowned, because the directory is read by glob and a superseded
    # model is a second artifact at a context length that already has one. FALSE keeps them and the
    # duplicate variants travel into the manifest.
    PruneFinal = TRUE
  )
)
```

R and Python communicate through files, not through an in-process bridge. R writes the sample and the fold assignment;
Python reads them, trains, and writes metrics and predictions back as Parquet. Neither language holds a handle on the
other's session, so a training failure surfaces as a non-zero exit status rather than a corrupted R workspace, and the
Python environment can be rebuilt independently of the R one.

# The labelled sample

```{r}
#| label: load-prepared-sample
# Read back the sample 03A froze. It is deliberately not rebuilt here: re-dealing the folds would break
# comparability with the keyword classifier and the router, which read this same file.
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

clf_report_folds(
  .tab   = tab_prep, # prepared sample
  .level = "ClassDetailed" # folds were stratified on this taxonomy, so balance is checked here
)
```

# Training

## The grid

Six hyperparameters are considered. Crossing all levels with all others across five folds would
define the complete factorial:

```{r}
#| label: build-grid-full
grid_full <- tidyr::expand_grid(
  model         = c("nlpaueb/legal-bert-base-uncased", "roberta-base"),   # legal-domain vs general encoder
  label_col     = c("ClassDetailed", "ClassBroad", "AmendType"),          # the three tasks
  lr            = c(1e-5, 2e-5, 3e-5),                                    # learning rate
  max_len       = c(256L, 512L),                                          # tokens read per document
  epochs        = c(3, 6, 10),                                            # passes over the training data
  class_weights = c(FALSE, TRUE),                                         # inverse-frequency loss weighting
  fold          = 1:5                                                     # cross-validation folds from 03A
)

nrow(grid_full)
```

Two levels are dropped rather than estimated everywhere. Ten epochs and a learning rate of 1e-5 were
each evaluated against the centre configuration and neither improved on six epochs at 2e-5; carrying
them through the whole factorial would roughly double the sweep in order to re-answer a question
already settled. Every remaining combination is estimated.

```{r}
#| label: build-grid
grid_all <- grid_full |>
  dplyr::filter(epochs != 10, lr != 1e-5)

nrow(grid_all)
```

An exhaustive design over the remaining levels is more expensive than a targeted one, and it buys
nothing on the headline score: the leading configurations already sit within a fold-level standard
deviation of each other, so no combination here is going to separate itself. What it buys is a
**balanced comparison**.

The marginal effect of an axis -- what changing the encoder, or the context length, or the number of
epochs is worth on average -- can only be read off a design in which every level of that axis appears
against the same set of levels of every other. On a targeted design it cannot: a level that appears
only alongside the strongest settings will look strong because of where it sits, not because of what
it does. Estimating the full crossing makes every axis effect reported below a like-for-like
comparison rather than a suggestive one.

```{r}
#| label: report-grid
bert_report_grid(
  .grid        = grid_all,                                        # every configuration to be estimated
  .tab_overall = clf_load_overall(.runs_roots = .lP$Runs$Bert),   # completed runs; times the outstanding ones
  .by          = c("label_col", "max_len"),                       # what drives the remaining cost
  .runs_root   = .lP$Runs$Bert,                                   # decides which rows are already done
  .text_col    = "Text",                                          # must match the sweep call below
  .batch_size  = 32L,                                             # must match the sweep call below
  .seed        = 42L                                              # must match the sweep call below
)
```

The projection is fitted on runs already completed on this machine, so it reflects actual throughput
rather than a nominal figure. Read it before starting: a sweep at this scale is measured in days, and
it is resumable but not free to interrupt. Runs already on disk from levels no longer in the grid are
not deleted; they remain in the leaderboard as evidence for the two exclusions above.

## Execution

```{r}
#| label: sweep-execute
bert_sweep(
  .path_data     = .lP$Input$Prepared,        # prepared sample written by 03A
  .grid          = grid_all,                  # configurations to train
  .runs_root     = .lP$Runs$Bert,             # destination for run folders
  .text_col      = "Text",                    # column holding the document text
  .batch_size    = 32L,                       # held fixed across the study; not a swept axis
  .seed          = 42L,                       # initialisation and shuffling seed
  .overwrite     = FALSE,                     # FALSE skips configurations already present on disk
  .run_remaining = .lP$Param$RunSweep,        # FALSE reports the plan and trains nothing
  .verbose       = FALSE                      # stream per-epoch training loss to the console
)
```

## Sweep coverage

Everything below is computed on the runs that exist, which is the same thing as the planned grid only when the sweep has
finished. Two properties are reported, and the second is the binding one: a configuration counts as estimated only when
all five of its folds are present, and the completed configurations must still form a full crossing of the swept axes for
the marginal-effect table to mean what it claims.

```{r}
#| label: report-coverage
bert_report_coverage(
  .grid       = grid_all,        # the design this document sets out to estimate
  .runs_root  = .lP$Runs$Bert,   # what actually exists
  .text_col   = "Text",          # must match the sweep call above
  .batch_size = 32L,             # must match the sweep call above
  .seed       = 42L              # must match the sweep call above
)
```

Training is serial. The engine is bound to a single GPU, so concurrent jobs would contend for it rather than overlap.
Per-epoch detail for each run is also written to `run.log` inside that run's folder, whether or not `.verbose` is set.

# Model selection

```{r}
#| label: load-run-metrics
# Bind every run's one-row metrics file into a single table. This is a cheap read of roughly one hundred
# small Parquet files and is deliberately not cached: a cache keyed on a name rather than on the data
# behind it would serve results from a previous sample without raising an error.
tab_overall <- clf_load_overall(.runs_roots = .lP$Runs$Bert)
```

## Detailed taxonomy

```{r}
#| label: leaderboard-detailed
clf_report_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "ClassDetailed", # task to rank
  .n           = 15L # rows to display
)
```

```{r}
#| label: effects-detailed
clf_report_effects(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "ClassDetailed", # task to analyse
  .axes        = c("Model", "MaxLen", "Epochs", "ClassWeights", "LR") # axes to marginalise over
)
```

The marginal-effect table is only interpretable on a fully crossed design, which is what the coverage report above
establishes; on a partial sweep it compares levels estimated against different sets of the other axes.

Differences between the leading configurations are smaller than the spread across folds within any one of them, which is
the signature of a performance plateau rather than a sharp optimum. The marginal-effect table separates the axes that
matter from those that do not: encoder choice and training budget produce consistent differences, whereas context length
and learning rate, within the ranges tested, do not.

Two axes carry substantive rather than merely technical content.

**Context length.** The overwhelming majority of contracts exceed both context windows, so the model reads only the
opening pages of most documents. That 256 and 512 tokens perform equivalently indicates the signal identifying contract
type is concentrated in the title and preamble rather than distributed through the body. This is what makes the approach
tractable: it is not necessary to read a forty-page agreement to classify it, and the shorter window halves inference cost
on the full corpus.

**Class weighting.** Weighting the loss by inverse class frequency improves macro-F1 by a margin that is small but
consistent across folds. The effect is concentrated in the rarest categories, which is where it would be expected, and it
is precisely what macro-F1 is constructed to reward.

## Broad taxonomy

```{r}
#| label: leaderboard-broad
clf_report_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "ClassBroad", # task to rank
  .n           = 15L # rows to display
)
```

## Amendment

```{r}
#| label: leaderboard-amendment
clf_report_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "AmendType", # task to rank
  .n           = 10L # rows to display
)
```

# Results

## Detailed taxonomy

```{r}
#| label: results-detailed-headline
# Selection and pooling in one step: identify the leading configuration, then gather the predictions its
# five fold models made on the documents each of them held out.
pred_det <- bert_best_predictions(
  .tab_overall = tab_overall, # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_col   = "ClassDetailed" # task
)

clf_report_scores(
  .tab_pred = pred_det, # pooled out-of-fold predictions
  .title    = "Detailed taxonomy -- headline scores" # heading
)
```

```{r}
#| label: results-detailed-perclass
clf_report_perclass(
  .tab_pred = pred_det, # pooled out-of-fold predictions
  .title    = "Detailed taxonomy -- per-category" # heading
)
```

Performance is not uniform across categories, and the pattern is informative. The categories separated most reliably are
those with distinctive drafting conventions and a large number of examples. The weakest are the smallest, and the
confusion matrix in the Overview shows their errors are not scattered: they concentrate in specific neighbouring pairs,
which are the same pairs that generated dual classifications during manual labelling. The model's residual errors and the
human annotators' hesitations fall in the same places, which suggests the remaining errors reflect genuine ambiguity in
the taxonomy rather than a deficiency in the classifier.

## Broad taxonomy

```{r}
#| label: results-broad-headline
pred_broad <- bert_best_predictions(
  .tab_overall = tab_overall, # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_col   = "ClassBroad" # task
)

clf_report_scores(
  .tab_pred = pred_broad, # pooled out-of-fold predictions
  .title    = "Broad taxonomy -- headline scores" # heading
)
```

```{r}
#| label: results-broad-perclass
clf_report_perclass(
  .tab_pred = pred_broad, # pooled out-of-fold predictions
  .title    = "Broad taxonomy -- per-category" # heading
)
```

## Amendment

```{r}
#| label: results-amendment-headline
pred_amend <- bert_best_predictions(
  .tab_overall = tab_overall, # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_col   = "AmendType" # task
)

clf_report_scores(
  .tab_pred = pred_amend, # pooled out-of-fold predictions
  .title    = "Amendment -- headline scores" # heading
)
```

```{r}
#| label: results-amendment-perclass
clf_report_perclass(
  .tab_pred = pred_amend, # pooled out-of-fold predictions
  .title    = "Amendment -- per-category" # heading
)
```

```{r}
#| label: results-amendment-confusion
tbl_say(
  .tab   = clf_confusion(.tab_pred = pred_amend), # true category by predicted category, as counts
  .title = "Amendment -- confusion matrix" # heading
)
```

Identifying an amendment cannot be reduced to keyword matching. The phrase "amended and restated" appears in the title of
many documents that are themselves original agreements, and amendments frequently do not announce themselves in their
opening lines. The distinction depends on how the document refers to a prior agreement, which requires reading in context.

# Taxonomy consistency

The two contract-type models are trained independently but make a jointly checkable claim, because every detailed category
has exactly one broad parent. Mapping the detailed model's prediction to its parent produces a broad-level prediction that
can be compared against what the broad model predicted directly. Where the two differ, at least one is wrong, and a
released dataset carrying both columns would assign the document to two mutually exclusive categories at once.

```{r}
#| label: consistency-agreement
agree_ <- bert_hierarchy_agreement(
  .tab_pred_detailed = pred_det, # out-of-fold predictions, 12-category model
  .tab_pred_broad    = pred_broad, # out-of-fold predictions, 7-category model
  .tab_prep          = tab_prep # supplies the detailed-to-broad mapping
)

bert_report_hierarchy(
  .tab_agree = agree_, # per-document agreement and adjudication
  .n         = 10L # disagreeing category pairs to list
)
```

The same comparison scored against the true labels shows whether either route is systematically more accurate at the broad
level.

```{r}
#| label: consistency-two-routes
dplyr::bind_rows(
  clf_scores(
    .tab_pred = clf_rollup_to_broad(
      .tab_pred = pred_det, # detailed predictions
      .tab_prep = tab_prep # supplies the detailed-to-broad mapping
    )
  ) |>
    dplyr::mutate(Approach = "Detailed model, rolled up", .before = 1),
  clf_scores(.tab_pred = pred_broad) |>
    dplyr::mutate(Approach = "Broad model, direct", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Two routes to the broad taxonomy, both scored at the broad level")
```

The two routes are equivalent in accuracy, so the choice between them rests on internal consistency. **The published broad
label is derived by rolling up the detailed prediction.** Doing so makes the hierarchy true by construction: no document
can be assigned a broad category that contradicts its detailed one. The independently trained broad model is retained as a
validation artifact, not as a source of published labels.

# Robustness

## Label provenance

The labelled sample was assembled in two rounds: an initial round mapped from an earlier coding scheme, and a second round
of direct manual classification. The second round is enriched for the categories introduced by the current taxonomy, so it
is the harder subset rather than a random sample of the whole.

```{r}
#| label: robustness-label-provenance
dplyr::bind_rows(
  clf_scores(.tab_pred = pred_det) |>
    dplyr::mutate(Labels = "Both rounds", .before = 1),
  clf_scores(
    .tab_pred = pred_det |>
      clf_add_labelround(.tab_prep = tab_prep) |> # attach the round each label came from
      dplyr::filter(.data$LabelRound == "Round2") # restrict to directly-labelled documents
  ) |>
    dplyr::mutate(Labels = "Round 2 only", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Performance by label provenance, detailed taxonomy")
```

Macro-F1 is lower on the second round alone. This reflects the composition of that subset rather than a failure to
generalise: the categories that exist only in the current taxonomy are by definition confined to it, and they are also the
smallest and the hardest. The comparison is between different mixtures of categories, not between an easy and a difficult
sample of the same mixture.

## Calibration

Downstream use may require not just a prediction but a defensible measure of confidence in it, for instance to restrict a
research sample to documents the classifier is sure about.

```{r}
#| label: calibration-metrics
# Attach the full probability vector to each prediction, deriving the top-two categories, the margin
# between them, and whether the prediction was correct.
class_det <- bert_classification(
  .runs_roots  = .lP$Runs$Bert, # run folders
  .config_name = bert_best_config(.tab_overall = tab_overall, .label_col = "ClassDetailed"),
  .tab_prep    = tab_prep # document metadata
)

bert_calibration_metrics(.tab_class = class_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 4))) |>
  tbl_say(.title = "Calibration summary (lower is better for ECE, MCE and Brier)")
```

```{r}
#| label: calibration-reliability-table
bert_calibration(
  .tab_class = class_det, # per-document predictions with probabilities
  .n_bins    = 10L # equal-width confidence bins
) |>
  dplyr::mutate(dplyr::across(c(MeanConf, Accuracy, Gap), ~ round(.x, 3))) |>
  tbl_say(.title = "Reliability: stated confidence against observed accuracy")
```

```{r}
#| label: calibration-margin-table
bert_margin_summary(.tab_class = class_det) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Decision margin between the top two categories, by outcome")
```

```{r}
#| label: calibration-threshold-table
bert_confidence_accuracy(
  .tab_class  = class_det, # per-document predictions with probabilities
  .thresholds = seq(0, 0.95, by = 0.05) # confidence floors to evaluate
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Confidence floor against retained sample size and accuracy")
```

The probabilities are usable but should be read against the reliability table rather than at face value. Confidence is
well calibrated in the top decile, where the great majority of documents sit, and overstated in the middle of the range. A
researcher wanting a high-purity subsample should therefore set the threshold inside the well-calibrated region rather
than at an arbitrary level; the risk-coverage table gives the exact trade-off between the share of documents retained and
the accuracy achieved on them.

# Deployment

The configurations selected above are refitted on the entire labelled sample. Cross-validation
estimates performance; deployment uses all available data, so a deployed model trains on 25% more
documents than any of the fold models whose scores are reported.

Each task is deployed at **both context lengths**, not only at the length that won outright. Context
length trades accuracy against inference cost, and on a corpus of any size that trade-off is settled
by whoever runs the classifier rather than by whoever trained it. Fitting both means the decision can
be taken later, with throughput figures in hand, and without retraining anything. Within each task
and length the configuration is still the one cross-validation selected under that constraint.

```{r}
#| label: deploy-final-models
tab_deployed <- bert_fit_final_all(
  .path_data     = .lP$Input$Prepared,                            # prepared sample
  .tab_overall   = tab_overall,                                   # bound per-fold metrics
  .model_dir     = .lP$Output$ModelFinal,                         # destination for the models
  .label_cols    = c("ClassDetailed", "ClassBroad", "AmendType"), # tasks to deploy
  .max_lens      = c(256L, 512L),                                 # context lengths to deploy at
  .batch_size    = 32L,                                           # as used throughout
  .overwrite     = FALSE,                                         # FALSE skips existing models
  .run_remaining = .lP$Param$RunDeploy,                           # FALSE reports the plan and fits nothing
  .verbose       = TRUE                                           # stream per-epoch training loss
)
```

```{r}
#| label: deploy-record-crown
# The configuration this stage crowned per task, written where the orchestration stage can read it.
# That stage used to rank the terminals again on a different criterion, which produced a third answer
# to a question already settled here -- and a manifest naming a model that was never fitted. One
# stage decides which configuration ships, and it is this one.
#
# The configuration NAME is the key, not an arm name. Arms are named by the orchestration stage,
# which reconciles four engines under one convention; producing a second name here would be a second
# convention, and the two would drift.
#
# ONE ROW PER TASK. Both context lengths are deployed and both are shipped as variants, but the
# crowned row is a single configuration: the consumer takes it as a scalar and falls back to its own
# ranking, with a warning rather than an error, if handed two.
if (is.null(tab_deployed)) {
  cli::cli_abort(c(
    "No configuration can be crowned: the sweep produced no runs at any requested length.",
    "i" = "Every claim this document makes about deployment is unsupported in that state."
  ))
}

# The tiebreak is explicit rather than inherited from row order. MacroF1 is rounded to three
# decimals, so two lengths CAN tie on the recorded value while differing underneath, and the row
# order that would otherwise decide it is an accident of how the plan was built. Preferring the
# shorter context on a tie is this document's own finding: equal measured accuracy, half the
# inference cost.
crown_ <- tab_deployed |>
  dplyr::arrange(dplyr::desc(MacroF1), MaxLen) |>
  dplyr::slice_head(n = 1L, by = LabelCol) |>
  bert_report_crown(.model_dir = .lP$Output$ModelFinal)             # marks which crowns are fitted

arrow::write_parquet(
  x    = crown_,                                                    # one row per task
  sink = fs::path(.lP$Output$ModelFinal, "deployed.parquet")        # beside the models it names
)
```

`Fitted` is the column to read. A crown is chosen from the sweep metrics and exists whether or not
anything was fitted, so a `NO` means the configuration the evidence selected has no model behind it
-- either because the crown moved since the last deployment, or because `RunDeploy` was off. The
record still ships, because it names what should run; the orchestration stage discovers models on
disk and refuses to pin an arm whose artifact is absent, so an unfitted crown fails there with a
sentence rather than being deployed by accident.

## Superseded models

The deployment directory is read by glob, so a model stays a candidate variant for as long as it sits
there. As the sweep completes a crown can move, and the configuration it moved away from is then a
second model at the same context length -- indistinguishable from the current one to anything asking
for that length, since variants are labelled by the length rather than by the configuration behind
them. Superseded models are therefore deleted rather than renamed, which is this document's one
departure from the repository's rule for retired outputs: a checkpoint is several hundred megabytes
and refitting reproduces it exactly from metrics that are still on disk, so keeping it stores a copy
of something already derivable at the cost of the largest files in the project.

Pruning waits until a task has every one of its crowns fitted. Applied to a partial deployment it
would delete the models a task has and leave it with none.

```{r}
#| label: deploy-prune-superseded
bert_prune_final(
  .tab_crown = tab_deployed,             # every task and length, NOT the one-row-per-task record
  .model_dir = .lP$Output$ModelFinal,    # the directory read by glob downstream
  .prune     = .lP$Param$PruneFinal      # FALSE reports what would be removed and removes nothing
)
```

The broad model is deployed for completeness and for the consistency check reported above. It is not
the source of the published broad label, which is derived by rolling up the detailed prediction.

## Per-document output

```{r}
#| label: deploy-save-classification
bert_save_classification(
  .tab  = class_det, # per-document predictions with probabilities
  .dir  = .lP$Output$Classification, # destination directory
  .stem = "crowned_classification", # file name stem
  .csv  = TRUE, # also write CSV alongside the Parquet
  .dta  = FALSE # TRUE renames probability columns for Stata
)
```

The classification file carries, for each labelled document, the true and predicted category, the probability assigned to
every category, the runner-up category and the margin between it and the prediction. Retaining the full probability vector
rather than only the prediction allows downstream users to apply their own confidence threshold without retraining
anything.

# Overview

Everything above in one place: the selected configurations and their scores for all three tasks,
followed by the figures. Nothing here is new; it is the same evidence, arranged so that the three
tasks can be compared directly rather than read in sequence. Figures are grouped by what they show,
with one tab per task.

## Headline results

```{r}
#| label: overview-headline
bert_report_summary(
  .tab_overall = tab_overall, # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_cols  = c("ClassDetailed", "ClassBroad", "AmendType") # tasks to summarise
)
```

Accuracy rises as the classification problem gets easier, from twelve categories to seven to two,
which is the expected ordering. Within each task the weakest category is the smallest, without
exception.

## Per-category scores, all tasks

```{r}
#| label: overview-perclass-all
bert_report_perclass_all(
  .tab_overall = tab_overall, # bound per-fold metrics
  .runs_roots  = .lP$Runs$Bert, # run folders to pool from
  .label_cols  = c("ClassDetailed", "ClassBroad", "AmendType") # tasks to summarise
)
```

Performance is limited by the number of labelled examples in the rare categories, not by the choice
of model or hyperparameters. No configuration in the grid closes that gap, and the marginal-effect
table above shows why: the axes that could be tuned have already been driven to a plateau.

## Model selection

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-leaderboard-detailed
#| fig-height: !expr plot_height(15)
#| fig-cap: "Cross-validated macro-F1 by configuration, detailed taxonomy. Intervals are one
#|   fold-level standard deviation. The axis is zoomed to the estimates, so the visible spread is
#|   smaller than it looks; the three panels here are not on a common scale."
clf_plot_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "ClassDetailed", # task to plot
  .n           = 15L # configurations to display
)
```

### Broad

```{r}
#| label: fig-leaderboard-broad
#| fig-height: !expr plot_height(15)
#| fig-cap: "Cross-validated macro-F1 by configuration, broad taxonomy. Axis zoomed as above."
clf_plot_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "ClassBroad", # task to plot
  .n           = 15L # configurations to display
)
```

### Amendment

```{r}
#| label: fig-leaderboard-amendment
#| fig-height: !expr plot_height(10)
#| fig-cap: "Cross-validated macro-F1 by configuration, amendment task. Axis zoomed as above."
clf_plot_leaderboard(
  .tab_overall = tab_overall, # bound per-fold metrics
  .label_col   = "AmendType", # task to plot
  .n           = 10L # configurations to display
)
```

:::

## Per-category performance

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-perclass-detailed
#| fig-height: !expr plot_height(12)
#| fig-cap: "Per-category F1, detailed taxonomy. All three panels share a fixed zero-to-one axis, so
#|   bar lengths are comparable across tasks."
clf_plot_perclass(.tab_pred = pred_det)
```

### Broad

```{r}
#| label: fig-perclass-broad
#| fig-height: !expr plot_height(7)
#| fig-cap: "Per-category F1, broad taxonomy."
clf_plot_perclass(.tab_pred = pred_broad, .key = "ClassBroad")
```

### Amendment

```{r}
#| label: fig-perclass-amendment
#| fig-height: !expr plot_height(2)
#| fig-cap: "Per-category F1, amendment task."
clf_plot_perclass(.tab_pred = pred_amend, .key = "AmendType")
```

:::

## Confusion

Errors concentrate in a small number of category pairs rather than spreading evenly, and those pairs
are substantively adjacent contract types. This is the visual form of the argument made earlier: what
remains is taxonomic ambiguity, not indiscriminate confusion.

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-confusion-detailed
#| fig-height: !expr plot_height(12, .square = TRUE)
#| fig-cap: "Confusion matrix, detailed taxonomy, row-normalised. Rows are true categories, columns
#|   predicted, both in taxonomic order, so errors that stay within a broad parent sit next to the
#|   diagonal and errors that cross one sit away from it."
clf_plot_confusion(
  .tab_pred  = pred_det,      # pooled out-of-fold predictions
  .normalize = TRUE,          # normalise within true category, so each row sums to one
  .limits    = c(0, 1),       # fixed, so all three panels share one fill scale
  .label_min = 0.005          # a cell below half a percent is drawn but not labelled
)
```

### Broad

```{r}
#| label: fig-confusion-broad
#| fig-height: !expr plot_height(7)
#| fig-cap: "Confusion matrix, broad taxonomy, row-normalised."
clf_plot_confusion(
  .tab_pred  = pred_broad,    # pooled out-of-fold predictions
  .key       = "ClassBroad",  # orders both axes by the registered broad vocabulary
  .normalize = TRUE,          # normalise within true category, so each row sums to one
  .limits    = c(0, 1),       # same fill scale as the detailed panel
  .label_min = 0.005          # a cell below half a percent is drawn but not labelled
)
```

### Amendment

```{r}
#| label: fig-confusion-amendment
#| fig-height: !expr plot_height(2)
#| fig-cap: "Confusion matrix, amendment task, row-normalised."
clf_plot_confusion(
  .tab_pred  = pred_amend,    # pooled out-of-fold predictions
  .key       = "AmendType",   # orders both axes by the registered amendment vocabulary
  .normalize = TRUE,          # normalise within true category, so each row sums to one
  .limits    = c(0, 1),       # same fill scale as the panels above
  .angle     = 0              # two short labels; no rotation needed
)
```

:::

## Calibration

Correct and incorrect predictions separate cleanly on the decision margin, which is what makes
confidence filtering worthwhile: errors concentrate among the documents the model is least sure
about, so a threshold removes them at a favourable rate. All three figures are for the detailed
taxonomy, the hardest of the three tasks and the one where a confidence filter is most likely to be
wanted.

::: {.panel-tabset}

### Reliability

```{r}
#| label: fig-reliability-detailed
#| fig-height: !expr plot_height(7)
#| fig-cap: "Reliability diagram. The diagonal is perfect calibration; points are sized by documents per bin."
bert_plot_reliability(.tab_class = class_det)
```

### Decision margin

```{r}
#| label: fig-margin-detailed
#| fig-height: !expr plot_height(7)
#| fig-cap: "Distribution of the decision margin for correct and incorrect predictions."
bert_plot_margin(.tab_class = class_det)
```

### Risk-coverage

```{r}
#| label: fig-risk-coverage-detailed
#| fig-height: !expr plot_height(7)
#| fig-cap: "Risk-coverage curve: accuracy on the retained subset as a rising confidence floor reduces coverage."
bert_plot_risk_coverage(.tab_class = class_det)
```

:::

# Next

`03C` mines a keyword classifier on the same folds, and `03D` tests whether routing between the two methods improves on
either alone. Both read the sample and the scoring functions from 03A, so all three methods are evaluated on identical
splits by identical code. `03E` applies the deployed models to the full corpus.
