---
title: "Contract Classification -- Building the Training Sample (03A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer. _Plots.R owns every figure's look and holds the level registry this
# document populates; _Tables.R owns every table's. Both are sourced before this document's own
# library, which registers the taxonomy against them when it loads.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),    # project root
  .name_script = .name_script     # resolves to 1_code/03A-ClassifyPrepare.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Roughly 4,400 SEC Exhibit-10 material contracts have been labelled by hand. This document turns that label list into a
single table, `prepared.parquet`, holding for each document its text, its labels for all three classification tasks, and
the cross-validation fold it belongs to.

Nothing is estimated here. The document makes three decisions and reports them:

1. **Which documents are eligible.** A label alone is not sufficient; the document also needs readable text on disk.
Every exclusion is reported with its reason.
2. **What the labels are.** Three tasks, all predicted from the same text.
3. **Which fold each document belongs to.** Dealt once, here, so that every method evaluated downstream is scored on
identical splits.

## The three tasks

| Task | Label | Categories | Question |
|:--|:--|--:|:--|
| Detailed | `ClassDetailed` | 12 | Which contract type is this? |
| Broad | `ClassBroad` | 7 | The same question, at a coarser level |
| Amendment | `AmendType` | 2 | Is this an original agreement or an amendment? |

The broad taxonomy is a strict roll-up of the detailed one rather than an independent labelling: every detailed category
has exactly one broad parent. The amendment label is orthogonal to both.

## Why folds are dealt here

Fold assignment belongs upstream of every method that uses it. Four classifiers are evaluated in this pipeline -- a
transformer, a keyword miner, a local language model, and a router combining them -- and comparing them is only
meaningful if each is scored on the same held-out documents. If each dealt its own folds, a difference between methods
could not be distinguished from a difference between splits.

Folds are stratified on the detailed taxonomy, which is the finest partition, so stratification there also balances the
coarser one. The rarest detailed category is therefore the binding constraint on how thin a fold can become.

## One label per document

A minority of documents carry a second valid category, recorded as `ClassDetailed2`. Training uses the primary category
only; the second label is never a target. It is retained for lenient scoring, which asks whether a prediction counted as
wrong was in fact the document's other valid answer. The gap between strict and lenient scoring is therefore a measure of
taxonomic ambiguity rather than of model error.

The primary is not an arbitrary pick between two equivalent answers. Every dual-classified document was reviewed by hand
and the intended primary recorded, so the ordering carries information.

## The shared vocabulary

This document also fixes the order and the display labels of the categories, registering them with the figure design
layer so that every figure produced anywhere in the pipeline draws them the same way. The order is taxonomic rather than
by frequency: ordering by size would put a different category first in every figure, which is exactly what makes two
panels incomparable, and taxonomic order additionally places siblings adjacent, so a confusion matrix shows errors that
stay inside a broad parent next to the diagonal and errors that cross one as a jump away from it.

# Configuration

```{r}
#| label: config
.lP <- list(
  Input = list(
    # The reconciled label spine. Read as CSV rather than Parquet because the current export was
    # produced outside the repository; the schema is identical either way.
    ClassificationSample = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MaterialContractClassification/DocumentClassification/02-AK_classification_comparison/final_classification.csv",
    MetaData     = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",      # filer titles
    DirContracts = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/"     # parsed text
  ),
  Cache = list(
    ContractFiles = utils_file_path(.dir_main, "Cache", "ContractFiles.parquet")   # DocID to Path index
  ),
  Output = list(
    Prepared = utils_file_path(.dir_main, "prepared.parquet"),                     # the one downstream input
    Figures  = utils_file_path(.dir_main, "Figures")                               # figure files for the manuscript
  ),
  Runs = list(
    Bert = here::here("2_output", "03B-ClassifyTrainBERT", "runs"),                # consumers of this output
    Kw   = here::here("2_output", "03C-ClassifyTrainKeyword", "runs")
  ),
  Param = list(
    Folds = 5L,     # cross-validation folds, shared by every method
    Seed  = 42L     # fixes the fold deal; constant across the whole study
  )
)

fs::file_exists(.lP$Input$ClassificationSample)
```

Failing here, rather than three chunks later, is deliberate: a missing label spine should stop the document at the point
the path is declared.

# Input

Three sources join on `DocID`:

- **The label spine** supplies the taxonomy (`DocClassFinal1`, `DocClassFinal2`), the amendment flag, and `Provenance`,
which records which labelling round each label came from.
- **The metadata** supplies `DocDesc`, the filer's own title for the exhibit, and `DocName`, the filename. Both are
inputs to the keyword classifier only; the transformer ignores them.
- **The parsed-contract tree** supplies `Path`, locating each document's text on disk.

```{r}
#| label: load-inputs
# Walk the parsed-contract tree once and cache the DocID -> Path index. .rerun = FALSE reuses the
# cache; set it to TRUE after new contracts have been parsed.
fils_contract <- utils_list_project_files(
  .dir_data = .lP$Input$DirContracts,      # root of the parsed-contract tree
  .path_out = .lP$Cache$ContractFiles,     # where the index is cached
  .rerun    = FALSE                        # FALSE reuses an existing index
)

# Read the label spine with readr, not arrow::open_dataset(format = "csv"). Arrow's
# strings_can_be_null convert option defaults to FALSE, so a bare NA in a character column arrives as
# the literal two-letter string, silently creating a thirteenth category and making every document
# appear dual-labelled. readr treats "" and NA as missing by default.
fils_class_sample <- readr::read_csv(
  file      = .lP$Input$ClassificationSample,      # reconciled label spine
  col_types = readr::cols(                         # everything character except the dual-class flag
    .default  = readr::col_character(),
    DualClass = readr::col_integer()
  )
) |>
  # Keep only what the pipeline consumes; the reconciliation carries further columns of its own history.
  dplyr::select(
    DocID, AmendType, DocClassFinal1, DocClassFinal2, DualClass,
    Level1, Level2, Provenance
  ) |>
  # Attach the filer title and the filename.
  dplyr::left_join(
    y  = arrow::open_dataset(sources = .lP$Input$MetaData) |>
      dplyr::select(DocID, DocDesc, DocName) |>
      dplyr::collect(),
    by = dplyr::join_by(DocID)
  ) |>
  # Attach the path to each document's parsed text.
  dplyr::left_join(
    y  = fils_contract,
    by = dplyr::join_by(DocID)
  )
```

Coverage of each join, before any filtering. A shortfall here is a join failure; the filtering that follows is reported
separately, so the two cannot be confused.

```{r}
#| label: report-raw-input
cli::cli_h2("Raw input")
tbl_say(
  .tab = tibble::tibble(
    Source = c(
      "Label rows read",
      "  with a class label",
      "  with metadata (DocDesc)",
      "  with a contract file path"
    ),
    N = c(
      nrow(fils_class_sample),
      sum(!is.na(fils_class_sample$DocClassFinal1)),
      sum(!is.na(fils_class_sample$DocDesc)),
      sum(!is.na(fils_class_sample$Path))
    )
  )
)
```

# Construction

`clf_prepare_sample()` applies four gates in order -- a usable class label, a file path, a file that exists, and text
that is non-empty -- then deals the folds. It narrates each gate as it runs, so an unexpected exclusion is visible
immediately rather than surfacing as a row-count mismatch three scripts later.

```{r}
#| label: build-sample
tab_prep <- clf_prepare_sample(
  .tab_input = fils_class_sample,     # joined labels, metadata and paths
  .round     = NULL,                  # NULL keeps both labelling rounds; see Robustness below
  .k         = .lP$Param$Folds,       # number of cross-validation folds
  .seed      = .lP$Param$Seed         # fixes the fold deal, so the splits are reproducible
)
```

Training on both labelling rounds combined, rather than on the manually-checked round alone, is the most consequential
choice made in this document. The second round is enriched for the categories the current taxonomy introduced and is
small; the first round supplies the volume the common categories need. Restricting to the second alone produces a
classifier that fails on everything except the rare categories.

# Validation

The registered vocabulary and the labels actually present must agree. They are declared in different places -- the
vocabulary at the top of this document's library, the labels in an external reconciliation -- so a category added to the
spine would otherwise surface much later, as a figure aborting mid-render in a downstream document.

Prediction before running it: every label in the sample is registered, and no registered category is unused. An
*unknown* count above zero means the taxonomy has gained a category and the vocabulary block needs it added. An *unused*
count above zero on the full sample means the reverse -- a category the taxonomy declares that no document carries.

```{r}
#| label: validate-vocabulary
clf_report_vocabulary(.tab = tab_prep)
```

# Results

One call prints the full picture: intake, tasks, category distributions, dual labels, fold balance, document length, and
missingness. This is the block to copy when something needs checking.

```{r}
#| label: report-sample
clf_report_sample(.tab = tab_prep)
```

## How to read it

**Intake.** Every document that left the sample, and at which gate. A drop at *Has a class label* is expected and
reflects documents the reconciliation could not resolve. A drop at *Has a contract file path* or *File exists on disk* is
a join or path failure, not a labelling one, and is worth stopping for.

**Tasks.** How many documents each task trains on and how many categories it must separate. Documents unlabelled for one
task are dropped by that task's trainer only; they still count for the others. The smallest category matters
disproportionately because the headline metric is macro-F1, which averages per-category F1 with equal weight regardless
of size.

**Category distribution.** Split by labelling round. Categories that exist only in the current taxonomy can by
construction appear only in the second round.

**Dual-class.** How many documents span two categories, and which pairs. Direction is meaningful: the primary was chosen
by review, so a pair running heavily one way reflects a consistent rule the reviewer applied.

**Fold balance.** Each fold is held out exactly once. A category thin enough to be absent from a fold leaves that fold's
recall for it undefined and makes macro-F1 unstable, so the smallest rows are the ones to watch.

**Document length.** Most contracts overflow both the 256- and 512-token windows, so a transformer reads only the opening
pages. That is the premise the pipeline rests on: contract type is legible from the title and preamble. It is also why
the sweep in 03B tests both window sizes rather than assuming the longer is better.

**Missing data.** Two kinds of missingness, and distinguishing them is the point. `ClassDetailed2` missing means the
document has a single category, which is a definition rather than a gap. `DocDesc` empty means the filer supplied no
title, and the keyword classifier abstains on those. Anything else should be zero.

# Robustness

Two properties of the sample are worth checking against the report above rather than assumed.

**Short documents.** A handful of documents pass the non-empty gate while carrying too little text to classify. Whether
they matter depends not on how many there are but on where they fall: a few dozen spread across the large categories are
harmless, whereas the same number concentrated in the smallest category would be a material share of it.

```{r}
#| label: robust-short-docs
tab_prep |>
  dplyr::mutate(Words = stringi::stri_count_regex(.data$Text, "\\S+")) |>
  dplyr::filter(.data$Words < 50) |>
  dplyr::count(.data$ClassDetailed, name = "Docs", sort = TRUE) |>
  tbl_say(.title = "Documents under 50 words, by category")
```

**Fold stability.** Folds are dealt from a fixed seed, so they are reproducible, but reproducibility is not the same as
balance. The fold report above gives the realised counts; the figure in the Overview gives the same numbers as
within-category shares, which is where an uneven deal is actually visible.

# Deployment

One file, read by everything downstream.

```{r}
#| label: deploy-prepared
clf_write_prepared(
  .tab      = tab_prep,             # the prepared sample
  .path_out = .lP$Output$Prepared   # the single file every downstream method reads
)
```

# Overview

The sample as it will be consumed downstream. Nothing here is new; the figures show what the tables above have already
reported.

```{r}
#| label: overview-tasks
clf_report_tasks(.tab = tab_prep)
```

## Category distribution

Categories appear in taxonomic order rather than by size, which is the order every figure in this pipeline uses. The
imbalance is still legible from the bar lengths, and reading it against 03B's per-category F1 is now a matter of
comparing two panels row by row.

::: {.panel-tabset}

## Detailed

```{r}
#| label: fig-distribution-detailed
#| fig-height: !expr plot_height(12)
#| fig-cap: "Category distribution, detailed taxonomy. Categories are in taxonomic order, so
#|   siblings under the same broad parent are adjacent."
clf_plot_class_distribution(
  .tab        = tab_prep,           # prepared sample
  .level      = "ClassDetailed",    # taxonomy to plot
  .include_na = FALSE               # unlabelled documents were removed at the intake gate
)
```

## Broad

```{r}
#| label: fig-distribution-broad
#| fig-height: !expr plot_height(7)
#| fig-cap: "Category distribution, broad taxonomy."
clf_plot_class_distribution(
  .tab        = tab_prep,        # prepared sample
  .level      = "ClassBroad",    # taxonomy to plot
  .include_na = FALSE            # unlabelled documents were removed at the intake gate
)
```

## Amendment

```{r}
#| label: fig-distribution-amendment
#| fig-height: !expr plot_height(2)
#| fig-cap: "Category distribution, amendment task."
clf_plot_class_distribution(
  .tab        = tab_prep,       # prepared sample
  .level      = "AmendType",    # task to plot
  .include_na = FALSE           # an unlabelled amendment flag would appear in the missingness table
)
```

:::

The imbalance is steep at every level and steepest in the detailed taxonomy, where the largest category holds roughly ten
times as many documents as the smallest. This is why macro-F1 is the headline metric downstream: accuracy on this sample
is dominated by the three largest categories, and a classifier that ignored the rarest ones entirely would still score
well on it.

## Where the labels came from

```{r}
#| label: fig-round-composition
#| fig-height: !expr plot_height(12)
#| fig-cap: "Composition of each category by labelling round. Round 1 is the automated
#|   carry-forward from the earlier taxonomy; Round 2 is the manual pass."
clf_plot_round_composition(
  .tab   = tab_prep,           # prepared sample
  .level = "ClassDetailed",    # taxonomy to plot
  .share = TRUE                # per-category composition; FALSE would show raw counts
)
```

The categories the current taxonomy introduced can only be second-round, and appear here as solid bars. Everything else
is a mixture, and the mixing ratio is what the targeted re-labelling produced: the manual pass was aimed at the
categories that changed, not spread evenly across the sample.

## Fold balance

```{r}
#| label: fig-fold-balance
#| fig-height: !expr plot_height(12)
#| fig-cap: "Share of each category falling in each fold. Rows sum to one, so an even deal is a
#|   uniform row; the smallest categories are where unevenness matters."
clf_plot_fold_balance(
  .tab   = tab_prep,          # prepared sample
  .level = "ClassDetailed"    # the taxonomy the folds were stratified on
)
```

The fill scale is anchored at twice the expected share, so a perfectly even deal sits at the exact middle of the ramp and
a uniform figure is the correct reading rather than an absence of one. Stratification is on this taxonomy, so uniformity
is expected by construction; what the figure rules out is the failure it cannot rule in. A category with too few
documents to divide evenly across five folds would show as a pale cell, and that is what makes its per-fold recall
undefined and macro-F1 unstable downstream. Nothing here is pale.

# Next

`prepared.parquet` is the single input to everything that follows. **03B** fine-tunes transformer encoders on it, **03C**
mines a keyword classifier on the same folds, **03D** tests a local language model as a third arm, and **03E** tests
whether routing between them improves on any one alone. **03F** applies the deployed policy to the full corpus. All of
them source this document's function file, so the folds, the scoring code and the category vocabulary they share cannot
drift apart.

Two directories must be cleared whenever this document is re-run against a changed label spine, because **neither fails
loudly**: `2_output/_cache/`, since `clf_cache()` keys on a name rather than on the data behind it, and
`2_output/03B-ClassifyTrainBERT/runs/`, since run identity is derived from hyperparameters alone and carries no
fingerprint of the sample.
