---
title: "Contract Classification -- Keyword Sweep (03C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = FALSE, warning = FALSE)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_Format.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

# 03A owns the common layer (prep + scoring + plots); source it, then this file.
cat("03A function file: ")
(.path_fun_prep <- init_create_script_fun(here::here(), "03A-ClassifyPrepare"))
source(.path_fun_prep)

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

# What 03C is

03C is the **keyword classifier**: a transparent, lexical counterpart to BERT (03B)
on the *identical* frozen folds. For each contract type it mines a per-class lexicon
(the discriminative terms and n-grams) on the training folds and predicts the
held-out fold by which class's lexicon fires hardest, abstaining (`(none)`) when
nothing fires. It exists for the head-to-head: where keyword matches BERT, the
cheaper, fully-interpretable method wins; where it lags, that gap motivates routing
(03D).

Two things make this clean rather than a parallel re-implementation:

- **It reuses 03A's prepared parquet and scoring layer.** The single
  `prepared.parquet` already carries `DocDesc`, so there is no keyword-specific prep
  -- the engine points `--data` at 03A's output. Scoring goes through `clf_scores` /
  `clf_perclass` / `clf_confusion`, abstention-aware by default (`.none = "(none)"`).
- **The engine writes the same run-folder schema as the BERT trainer**
  (`predictions` / `probabilities` / `metrics_overall` / `metrics_perclass` /
  `config.json`) plus `lexicon.parquet`. So `clf_load_overall` binds keyword and BERT
  runs together, and 03D consumes both with no special-casing.

The method adds three concepts: **Source** (`text` body, `docdesc` filer title, or
`combined`), **Coverage** (the share of docs it predicts, i.e. 1 - abstention rate),
and the `(none)` abstention sentinel.

Two design points this version foregrounds, because they drive the escalation idea
(03D) and the high-precision-at-low-N goal:

- **The desc and text lexicons are mined independently.** Even a `combined` run mines
  a separate per-class lexicon for each field (the engine stamps a `Zone`) and fuses
  only the *scores* (`alpha * docdesc + text`), never the lists. So an independent
  Desc list and Text list already exist for every run -- surfaced below.
- **Keyword regex is cheap**, so this version sweeps wider: `source` x `stopwords` x
  `topk` x `ngram_max`. The `topk` lift (25 -> 50) is the main lever for rare-class
  recall, and the per-class selective layer turns the result into a high-precision
  subset even where a class is small.

Scope note: amendment classification is settled to BERT (lexical separation is
intractable -- "amended and restated" is a naming convention in genuine originals,
keyword ~0.62 vs BERT ~0.86 macro-F1), so this sweep targets `ClassDetailed`.

This document renders end to end. The engine steps shell out to Python, but the sweep
is idempotent (a finished cell is skipped), so re-rendering is cheap once the grid is
on disk. Everything downstream is wrapped in `clf_cache()`; after a fresh sweep, set
`options(clf.cache.overwrite = TRUE)` once to rebuild.

## Paths

`prepared.parquet` is read from 03A's output directory (same path construction 03A
wrote it with). Keyword runs live under 03C's own runs root;
`clf_load_overall(c(bert_runs, kw_runs))` binds both for 03D.

```{r}
.dir_prep <- init_create_script_dir(here::here(), "03A-ClassifyPrepare")

.lP <- list(
  Input = list(
    Prepared = utils_file_path(.dir_prep, "prepared.parquet")
  ),
  Output = list(
    RunsDir = utils_file_path(.dir_main, "runs")
  ),
  Engine = list(
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "keyword_train.py")
  )
)
```

```{r}
tab_prep <- arrow::read_parquet(.lP$Input$Prepared)
```

# Step 0 diagnostics

Two checks on the data before modelling -- both keyword-specific validity questions
the BERT track does not care about, and both directly relevant to the desc-vs-text
escalation.

## DocDesc coverage

How much of the sample carries a non-empty filer title. Where it is empty, a
`docdesc` model has nothing to mine and must abstain -- which `Coverage` then reports
honestly. This is the N the desc arm has to work with, per class.

```{r}
kw_diag_desc_coverage(tab_prep) |>
  fmt_table(.caption = "DocDesc coverage (overall and per class)", .pct = "Coverage")
```

## Header leakage

Does the body restate the title verbatim near the top? If so, mining `text` partly
relearns `docdesc`, and the two are not independent feature sources. High leakage
means `combined` is closer to `text` than its name suggests, and -- important for 03D
-- it means the desc signal is mostly already inside what BERT reads (BERT sees
`Text`). The small non-leaked remainder is the only place desc can carry signal BERT
lacks.

```{r}
kw_diag_header_leak(tab_prep, .n_chars = 300L) |>
  fmt_table(.caption = "Body restates the title verbatim in the first 300 chars?",
            .pct = "LeakShare")
```

# The sweep grid

Wider than before, since regex is cheap. The three source fields, crossed with two
stopword regimes (confirming the "none wins" finding rather than assuming it), two
`topk` levels (25 vs 50 -- the rare-class recall lever), and two `ngram_max` (2 vs 3),
five folds each. Optional grid columns override `kw_command` defaults per row;
anything omitted falls back to the default.

```{r}
grid_main <- tidyr::expand_grid(
  label_col = "ClassDetailed",
  source    = c("text", "docdesc", "combined"),
  stopwords = c("none", "english_domain"),
  topk      = c(25L, 50L),
  ngram_max = c(2L, 3L),
  fold      = 1:5
)
grid_main |>
  dplyr::distinct(source, stopwords, topk, ngram_max) |>
  fmt_table(.caption = "Keyword sweep configs (x 5 folds each)")
cli::cli_alert_info("Total cells: {nrow(grid_main)}")
```

Note on `min_df`: the engine does not encode `min_df` in its config name, so sweeping
it would collide on disk with the existing runs. The `topk` lift covers the same
rare-class-recall ground safely; a dedicated `min_df = 1` starvation probe is a
one-line engine change (add `min_df` to `config_name`) left for a separate pass.

# Run the sweep

A quick seam check first -- one tiny cell on a 40/10 subset, end to end, to confirm
the R -> Python -> parquet path before committing the full grid:

```{r}
kw_train(.lP$Input$Prepared,
  .label_col = "ClassDetailed", .source = "combined",
  .test_fold = 1L, .runs_root = .lP$Output$RunsDir, .smoke = TRUE
)
```

Then the grid. Each cell is an independent, CPU-bound shell-out; `kw_sweep` dispatches
them across mirai daemons (spun up for the sweep, torn down on exit), discards the
console, and tees each run's narrative to its `run.log`. It prints a compact
performance table for the freshly-run cells and returns it.

```{r}
perf <- kw_sweep(grid_main, .lP$Input$Prepared, .runs_root = .lP$Output$RunsDir)
```

# Score the sweep

All scoring goes through 03A's shared layer, so these numbers are directly comparable
with BERT's. `clf_load_overall` binds the per-run `metrics_overall` rows -- that bound
table *is* the master log. Disk reads are wrapped in `clf_cache()`; after a fresh
sweep set `options(clf.cache.overwrite = TRUE)` once.

```{r}
tab_overall <- clf_cache("kw_overall", clf_load_overall(.lP$Output$RunsDir))
kw_leaderboard_show(tab_overall, .label_col = "ClassDetailed", .n = 24L) |>
  fmt_table(.caption = "Keyword configurations -- detailed taxonomy", .wide = TRUE)
```

Marginal effects of the swept axes (each averaged over everything else), so the
winner is read off main effects rather than one lucky cell:

```{r}
clf_effect(tab_overall, "Source", .label_col = "ClassDetailed") |>
  fmt_table(.caption = "Macro-F1 by source field")
clf_effect(tab_overall, "TopK", .label_col = "ClassDetailed") |>
  fmt_table(.caption = "Macro-F1 by topk")
clf_effect(tab_overall, "Stopwords", .label_col = "ClassDetailed") |>
  fmt_table(.caption = "Macro-F1 by stopword regime")
```

# The three sources, side by side

The escalation arms -- the best config for each source -- lined up on identical folds.
`docdesc` is the low-N / high-clarity arm; `text` the body arm; `combined` the score
fusion. This is the unified view the shared schema makes possible: one row per source,
same columns, directly comparable (and directly comparable with BERT in 03D).

```{r}
src_cfgs <- kw_pick_source_configs(tab_overall, "ClassDetailed")
src_cfgs |>
  fmt_table(.caption = "Best config per source (by pooled macro-F1)",
            .digits = 3, .pct = "Cov_mean", .wide = TRUE)
```

Per-class F1 by source, so the structural pattern is visible: where does the clean
`docdesc` title help, and where does the body `text` carry classes the title cannot
(the heterogeneous / rare classes)?

```{r}
perclass_src <- src_cfgs |>
  dplyr::mutate(
    PC = purrr::map(.data$ConfigName, function(cfg_) {
      pred_ <- clf_cache(paste0("kw_pred__", cfg_),
                         clf_pool_predictions(.lP$Output$RunsDir, cfg_))
      clf_perclass(pred_) |> dplyr::select(Label, F1)
    })
  ) |>
  dplyr::select(Source, PC) |>
  tidyr::unnest(PC) |>
  tidyr::pivot_wider(names_from = Source, values_from = F1)
perclass_src |>
  fmt_table(.caption = "Per-class F1 by source (pooled out-of-fold)", .digits = 3)
```

# Independent mined lexicons: Desc vs Text

The interpretable payoff, surfaced for each field separately. The `docdesc` list is
short and clean -- contract-type names ("credit agreement", "lease dated"). The `text`
list is the boilerplate verbal fingerprints ("the consultant shall", "the borrower")
that the stopwords-hurt finding predicted. Read together they show *why* the two
sources behave differently.

```{r}
desc_cfg <- src_cfgs |> dplyr::filter(.data$Source == "docdesc") |> dplyr::pull(ConfigName)
text_cfg <- src_cfgs |> dplyr::filter(.data$Source == "text")    |> dplyr::pull(ConfigName)

clf_cache(paste0("kw_lex__", desc_cfg),
  kw_load_lexicon(.lP$Output$RunsDir, desc_cfg, .min_folds = 3L, .top_per_class = 6L)) |>
  fmt_table(.caption = "Desc lexicon: stable terms, top per class", .digits = 3, .wide = TRUE)
```

```{r}
clf_cache(paste0("kw_lex__", text_cfg),
  kw_load_lexicon(.lP$Output$RunsDir, text_cfg, .min_folds = 3L, .top_per_class = 6L)) |>
  fmt_table(.caption = "Text lexicon: stable terms, top per class", .digits = 3, .wide = TRUE)
```

# Confidence: does the margin separate right from wrong?

The keyword twin of the BERT margin stat. The engine's `Score` is a fold-normalised
max; the sharper per-document signal is the **margin** (top-1 minus top-2 class
score), reconstructed by `kw_load_confidence` from the saved probabilities. If the
margin is reliably larger on the correct predictions than the incorrect ones, the gate
has something to grip -- if not, no threshold will carve a clean subset. (There is no
reliability-diagram / ECE here: the keyword score is a normalised weight-sum, not a
calibrated probability, so an ECE would mislead rather than inform.)

```{r}
best_kw <- src_cfgs |> dplyr::slice(1) |> dplyr::pull(ConfigName)
conf_mr <- clf_cache(paste0("kw_conf_mr__", best_kw),
  kw_load_confidence(.lP$Output$RunsDir, best_kw, .which = "marginrel"))
kw_margin_correctness(conf_mr) |>
  fmt_table(.caption = "Relative margin by correctness (committed predictions)",
            .digits = 3)
```

# Selective classification: a high-precision subset, per source

The per-class numbers show high precision but low recall on the hard classes: the
lexicon is usually right when it commits, and pays mostly for being forced to guess on
ambiguous documents. Gating on confidence makes that a deliberate choice -- classify
only what the lexicon is sure about, defer the rest. This is the keyword arm of 03D
routing, and the high-performance-at-low-N goal for `docdesc` lives exactly here.

The unified high-precision profile: for each source, the strict pooled macro-F1 next
to the gated operating point -- how much it can label at >= 95% per-class precision
(`SelCoverage`) and how accurate that slice is (`SelAccuracy`). The docdesc arm is the
one to watch: small coverage, but is it precise?

```{r}
src_profile <- src_cfgs |>
  dplyr::mutate(
    Profile = purrr::map(.data$ConfigName, function(cfg_) {
      pred_ <- clf_cache(paste0("kw_pred__", cfg_),
                         clf_pool_predictions(.lP$Output$RunsDir, cfg_))
      kw_selective_profile(pred_, .target_precision = 0.95, .min_keep = 5L)
    })
  ) |>
  dplyr::select(Source, ConfigName, Profile) |>
  tidyr::unnest(Profile)
src_profile |>
  fmt_table(.caption = "Strict vs high-precision (>=95%) profile, per source",
            .digits = 3,
            .pct = c("StrictCoverage", "SelCoverage", "SelAccuracy", "TargetP"))
```

The precision-coverage tradeoff for the best config, swept over a single global cutoff
-- selective accuracy (precision on the classified subset) against coverage:

```{r}
pred_best <- clf_cache(paste0("kw_pred__", best_kw),
                       clf_pool_predictions(.lP$Output$RunsDir, best_kw))
pc_curve <- kw_precision_coverage(pred_best)
pc_curve |> fmt_table(.caption = "Precision-coverage tradeoff (global Score cutoff)")
```

```{r}
#| fig-cap: "Selective accuracy against coverage: the precision bought by abstaining."
kw_plot_precision_coverage(pc_curve)
```

A single global cutoff is blunt, since `Score` is only loosely comparable across
classes. Calibrating a cutoff *per class* to a target precision is the real operating
point -- each class contributes the slice it can label at >= 95% precision, and
`Recall` reports how much of that class we still recover there:

```{r}
calib <- kw_calibrate(pred_best, .target_precision = 0.95, .min_keep = 5L)
calib |> fmt_table(
  .caption = "Per-class operating points at 95% target precision",
  .digits = 3, .wide = TRUE
)
```

Applying those per-class cutoffs gives the high-precision keyword layer. Its coverage
and selective accuracy -- not `clf_scores` accuracy, which would count every deferral
as wrong -- are the headline for routing:

```{r}
thr_ <- calib |> dplyr::select(Label, Threshold) |> tibble::deframe()
pred_hi <- kw_gate(pred_best, thr_)
kw_selective_summary(pred_hi) |>
  fmt_table(.caption = "High-precision keyword layer (per-class gated)",
            .pct = c("Coverage", "SelAccuracy"))
```

# Next

03C produces the keyword runs in their own root; 03A's overview tooling reads them,
and 03D compares methods and tests the desc -> text -> BERT escalation.

- **03D escalation.** `kw_load_confidence` works on any source config, so 03D can run
  `orch_subset_compare` on the docdesc and text configs separately -- the test of
  whether either carves a subset it wins before any cascade is built. The shared folds
  make every source row directly comparable with BERT.
- **Optional min_df starvation probe.** A `min_df = 1` sweep for the rare classes
  needs `min_df` added to the engine `config_name` first (so variants do not collide
  on disk); a small, isolated change if the topk lift proves insufficient on R&D /
  Peer.
