---
title: "Entity Rules -- Organisations and the Contracting Party (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# ORDER IS LOAD-BEARING. _Store.R supersedes ner_db_init(), ner_db_append() and ner_db_clear() in
# _NER.R and must be sourced after it. This document only reads, but it reads the per-label `org`
# table rather than the `candidates` view, and the schema those extra columns live in is declared
# there.
source("1_code/_Commons/_Store.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING here
# too: the level registry is rebuilt empty every time _Plots.R is sourced, so a library registering a
# vocabulary has to be sourced after it.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the contract-type vocabulary and the fixed-width console formatter every document in the
# monorepo reports through; 04A owns the sample, the canonical text and the candidate store.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B-EntityRules.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A ran nine extractors over 4,398 hand-classified contracts and stored several million candidate
spans. It ranked none of them, because ranking needs labels and there are no entity labels. This
document writes the rules that turn those spans into party variables, one entity at a time.

**Organisations first**, because every other quantity a party carries is measured from where an
organisation was found.

## One engine, and why that decides the rest

04C extracts the corpus with five engines and none of them is spaCy. For organisations that leaves
LexNLP alone, which emits 81,467 spans against spaCy's 5.3 million. The whole rule therefore runs in
R over a table that fits in memory, and DuckDB is read once.

## The rule, in one paragraph

Reduce the registrant's recorded name and every candidate span to a common key. Match the two
**anywhere in the document**; where nothing matches, take the first organisation the contract names
and record that it was a guess. Cut a window of fixed width around wherever the party was found, and
call the other distinct names inside it counterparties. Take a tail from the end, clamped so it
cannot reach back into the window, and call what it holds signatories. Report all of it against the
**unadjusted** count -- every distinct organisation named anywhere -- which is the quantity this
replaces.

## Why there is no head

An earlier design read a fixed head of the document and asked whether the filer was inside it.
Sweeping that head across twenty settings showed the located share rising from 70.6% to 75.1% and the
*late* share falling from 6.5% to 2.0%, the two summing to **77.1% in every single cell**. That is an
identity: the match runs on names and cannot depend on a region, so a wider head bought no filer and
only relabelled one already found, while the candidate count doubled.

## What is settled, and what is still a row in a sweep

Three things are settled by measurement and are not swept as open questions.

**The window does not scale with length.** Across length deciles the unadjusted count rises
thirteenfold while a fixed window rises about twofold: the extra organisations a long contract names
are body prose, not parties.

**A gap window buys nothing over a fixed one.** Growing outward through clustered names until the
first large gap returns the same mean counterparty count as a fixed width -- `gap 500` and
`+/- 1,000` agreed to three decimals -- and never exceeds it in any length decile. The gap columns
stay in the tables as the evidence for that, not as a candidate.

**Span boundaries are tight enough to ignore.** Median overshoot past the resolved name is 5
characters, P90 is 12, and 99.0% of spans contain their own name.

Open, and therefore swept: the released width, the tail width, and whether a one-token family match
found deep in a document should be refused.

## Noise is expected, and it is reported against a baseline

No stoplist, no defined-term filter, no geography exclusion. Two failure modes are accepted rather
than engineered away, and both are flagged: a filer first named at character 50,000 anchors a window
there and is marked **deep**, and a document where nothing matches takes its first name as the party.
The counterparty tables are reported separately for the two populations, because a count survives a
wrong anchor better than a named party does.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    # 04A's sample table: labels, folds, and the EDGAR facts the anchor is built from.
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    # 04A's candidate store, opened read-only.
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Roles = utils_file_path(.dir_main, "roles_org.parquet"), # one row per document per name
    Party = utils_file_path(.dir_main, "party_org.parquet")  # one row per document
  ),
  Params = list(
    Combo    = "lexnlp", # the only ORG engine 04C runs over the corpus
    Bins     = 50L,      # bins across relative position in the density figure
    TermsN   = 25L,      # names listed in the document-frequency block
    ReadN    = 10L,      # spans read back in context
    ReadDocs = 6L,       # documents read whole
    ReadMax  = 12L,      # rows per document, so one table-heavy filing cannot fill the page
    ReadCtx  = 200L,     # characters either side of a span
    CheckN   = 500L,     # spans cut from the text and compared to what was stored
    Bounds   = c(500, 1000, 2000, 4000, 10000), # half-widths the distance profile reports
    Seed     = 42L       # fixed, so the same documents are read on every render
  )
)

# THE MATCH IS ONE VALUE AND THE WINDOW IS ANOTHER, because the match is window-free: it decides
# which entity anchors the window, never how many names fall inside it.
.lP$Params$Rule <- ent_rule(
  .key               = "core",  # the resolved name, which lexnlp fills on every span it emits
  .min_key           = 2L,      # shortest key admitted for EQUALITY
  .min_contain       = 5L,      # shortest key admitted for CONTAINMENT or family
  .tight             = TRUE,    # also compare with spaces removed: UNITED AIRLINES = UNITED AIR LINES
  .frag_min          = 10L,     # shortest fragment admitted as a reverse match
  .frag_share        = 0.6,     # and it must cover this much of the recorded name
  .fam_tokens        = 2L,      # leading tokens two keys must share to be one corporate family
  .fam_share         = 0.5,     # and those tokens must be this much of the shorter key
  .fam_df            = 0.005,   # or ONE token, if it opens a name in at most this share of documents
  .deep              = 5000L,   # a match past this offset is flagged, not rejected
  .guard_deep_family = FALSE    # the guard is swept below before it is adopted
)

# The window carried into the released artifacts. Every specification below is reported; this is the
# one the parquet files are written from.
.lP$Params$Spec <- ent_window_spec(
  .kind       = "fixed", # constant characters either side of the party
  .par        = 2000,    # half-width
  .tail_share = 0.10,    # tail as a share of the document, clamped past the window
  .tail_floor = 0        # no absolute minimum; the flat alternative is swept separately
)

# The window sweep. Fixed widths bracket the gap arm, which is reported as evidence rather than
# offered as a choice. No whole-document row: it is the unadjusted count minus the filer, and that
# count is already a column in every table.
.lP$Params$Specs <- list(
  ent_window_spec(.kind = "fixed", .par = 500,  .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 1000, .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 2000, .tail_share = 0.10),
  ent_window_spec(.kind = "fixed", .par = 4000, .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 250,  .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 500,  .tail_share = 0.10),
  ent_window_spec(.kind = "gap",   .par = 1000, .tail_share = 0.10)
)

# The tail sweep. The window is held at the released width and only the tail moves, so the two
# parameters are never read off the same table -- which is how an earlier version reported every
# tail column as zero, having computed them from the widest window in the sweep, where the window
# swallows the document and the tail is empty by construction.
.lP$Params$TailSpecs <- list(
  ent_window_spec(.kind = "fixed", .par = 2000, .tail_share = 0.10, .tail_floor = 0,
                  .label = "tail 10%"),
  ent_window_spec(.kind = "fixed", .par = 2000, .tail_share = 0.20, .tail_floor = 0,
                  .label = "tail 20%"),
  ent_window_spec(.kind = "fixed", .par = 2000, .tail_share = 0,    .tail_floor = 3000,
                  .label = "tail 3,000 flat")
)

fs::file_exists(unlist(.lP$Input))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

Both sides run through one reduction: strip EDGAR's conformed-name artifact, uppercase, an ampersand
between spaces to `AND`, punctuation to space, whitespace collapsed, a leading connective dropped,
trailing corporate suffixes stripped.

The suffix list holds the **dotted forms as separate tokens** -- `L P`, `L L C`, `N V` -- because
punctuation-to-space turns `WILLIAMS PARTNERS L.P.` into `WILLIAMS PARTNERS L P`, and a list holding
only `LP` strips nothing. That demoted an exact pair to a family match, and partnerships and funds
are common enough in this corpus that it is not an edge case. The alternation is sorted by descending
length so a longer form is tried before a prefix of itself.

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(
  .path_anchors = .lP$Input$Anchors   # 04A's sample table, not the raw EDGAR metadata
)

ent_report_keys(
  .tab  = tab_keys,
  .rule = .lP$Params$Rule   # supplies the two floors, so the table reports what the rule will do
)
```

```{r}
#| label: load-lengths
tab_lens <- ent_doc_lens(
  .path_text = .lP$Input$Text   # the canonical text; length in code points, not bytes
)
```

```{r}
#| label: load-spans
tab_spans <- ent_load_org(
  .db_path = .lP$Input$Store,     # opened read-only; nothing here can write to 04A's artifact
  .lens    = tab_lens,            # supplies document length, so an offset becomes a position
  .combo   = .lP$Params$Combo,    # lexnlp, the only ORG engine the corpus pass carries
  .quiet   = FALSE
)
```

# Entities and the match

Everything in this section is window-free, which is what makes the window sweep affordable: the match
is computed once and every window below is cut over the same result.

Mentions of the same company collapse to one row per document per name, and that row is the
**earliest mention taken whole**, so start, stop and span come from a single mention rather than
from two.

```{r}
#| label: apply-base-rule
res_base <- ent_apply(
  .spans = tab_spans,           # every lexnlp ORG span
  .keys  = tab_keys,            # runs from the key side, so unmatched documents survive
  .lens  = tab_lens,            # so a document with no organisation at all still carries a length
  .rule  = .lP$Params$Rule,     # the match
  .spec  = .lP$Params$Spec      # the window carried into the artifacts
)

tab_ent    <- res_base$Ent      # one row per document per distinct name, window-free
tab_facts  <- res_base$Facts    # the same, with the comparison to the recorded name
tab_party  <- res_base$Party    # one row per document
tab_roles  <- res_base$Roles    # entities with the window, the tail and the assigned role
tab_counts <- res_base$Counts   # one row per document, the counts and the bounds

ent_report_match(.tab = tab_party)
```

A span matches when the two normalised forms are identical -- with or without spaces -- when one
contains the other, or when they share a corporate prefix. **Forward** containment, the span holding
the recorded name, is safe. **Reverse** containment means the span is a *fragment* and needs a floor:
`G` sits inside `GEORGIA PACIFIC`, and an unfloored reverse arm inflates apparent recall rather than
merely adding noise. **Family** reaches what the others cannot, and a single shared token is admitted
only when it is distinctive, because `CHENIERE` is evidence and `NATIONAL` is not.

```{r}
#| label: measure-boundary
tab_boundary <- ent_boundary(.ent = tab_ent)

ent_report_boundary(.tab = tab_boundary)
```

```{r}
#| label: measure-distances
tab_dist <- ent_dist_profile(
  .roles  = tab_roles,
  .bounds = .lP$Params$Bounds   # the candidate half-widths, so the profile answers the same question
)

tab_gap <- ent_gap_profile(
  .roles = tab_roles,
  .bound = 4000                 # only names near the party; across a whole contract the gaps are prose
)

ent_report_dist(.dist = tab_dist, .gap = tab_gap)
```

# Where the party sits

```{r}
#| label: table-where
tab_where <- ent_table_where(.counts = tab_counts)

ent_report_where(.tab = tab_where)
```

# What the window yields

Three populations of the same table. All documents is the released figure; the split says how much of
it rests on a guessed anchor.

```{r}
#| label: sweep-windows
tab_sweep_window <- ent_sweep_window(
  .fact  = tab_facts,           # the match, computed once
  .party = tab_party,           # the anchor every window is centred on
  .specs = .lP$Params$Specs,    # seven specifications, re-cut over the same facts
  .quiet = FALSE
)
```

```{r}
#| label: table-window-all
tab_win_all <- ent_table_window(
  .sweep  = tab_sweep_window,
  .counts = tab_counts,         # supplies the unadjusted baseline
  .status = "all"               # every document, however its party was found
)

ent_report_window_table(.tab = tab_win_all, .title = "All documents")
```

```{r}
#| label: table-window-matched
tab_win_matched <- ent_table_window(
  .sweep  = tab_sweep_window,
  .counts = tab_counts,
  .status = "matched"           # the party matched the registrant's recorded name
)

ent_report_window_table(.tab = tab_win_matched, .title = "Matched parties only")
```

```{r}
#| label: table-window-first
tab_win_first <- ent_table_window(
  .sweep  = tab_sweep_window,
  .counts = tab_counts,
  .status = "first"             # the first name in the document was taken instead
)

ent_report_window_table(.tab = tab_win_first, .title = "Fallback parties only")
```

```{r}
#| label: table-window-length
tab_length <- ent_table_length(.sweep = tab_sweep_window)

ent_report_length(.tab = tab_length)
```

# What the tail yields

```{r}
#| label: sweep-tail
tab_sweep_tail <- ent_sweep_window(
  .fact  = tab_facts,
  .party = tab_party,
  .specs = .lP$Params$TailSpecs,  # window held at the released width, only the tail moves
  .quiet = FALSE
)

tab_tail <- ent_table_tail(.sweep = tab_sweep_tail)

ent_report_tail(.tab = tab_tail)
```

# Selection

```{r}
#| label: sweep-match
tab_sweep_match <- ent_sweep_match(
  .spans = tab_spans,
  .keys  = tab_keys,
  .lens  = tab_lens,
  .base  = .lP$Params$Rule,     # every row differs from this in exactly one parameter
  .spec  = .lP$Params$Spec,     # held fixed, so only the match moves
  .quiet = FALSE
)

ent_report_sweep_match(.tab = tab_sweep_match)
```

The last row is the deep-family guard, off in the base rule. It refuses a match resting on one shared
token *and* found past the deep threshold -- the combination that produced `DUKE ENERGY PROGRESS`
matched to `Duke Energy Carolinas` at character 101,874. What it costs is the drop in `PctMatched`;
what it buys is in `PctDeepFamily` and in the read block below.

```{r}
#| label: inspect-terms
tab_terms <- ent_head_terms(
  .roles  = tab_roles,        # the names inside the window, with the role assigned to them
  .n_docs = nrow(tab_keys)    # the whole sample, so the share is comparable across sections
)

ent_report_terms(.tab = tab_terms, .n = .lP$Params$TermsN)
```

# Reading

Every table above is equally consistent with a chosen span being a preamble party and with it being
a letterhead, a page footer or a defined term. The text is what separates them, so a fixed sample is
read on every render.

```{r}
#| label: read-matched
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "matched"),
  .path_text = .lP$Input$Text,        # the same canonical text the offsets index
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = .lP$Params$ReadN,      # documents drawn
  .ctx       = .lP$Params$ReadCtx,    # characters either side of the span
  .seed      = .lP$Params$Seed        # fixed, so a change here is a change in the extraction
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "MatchKind", "PartyStart"),
    .title = "Matched parties in context"
  )
```

```{r}
#| label: read-family-deep
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$MatchKind == "family", .data$MatchTok == 1L,
                             .data$IsDeep),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 10L,                   # exactly what the deep guard would refuse
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "PartyKey", "PartyStart"),
    .title = "One shared token AND a deep anchor -- what the guard would refuse"
  )
```

```{r}
#| label: read-family-shallow
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$MatchKind == "family", !.data$IsDeep),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 8L,                    # the family matches the guard would keep
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "PartyKey", "PartyStart"),
    .title = "Family matches in a preamble -- what the guard would keep"
  )
```

A shared corporate prefix covers three situations and only the words separate them: a span-boundary
failure the arm rescues, a parent matched to its own subsidiary, and two unrelated companies opening
with the same words. The middle case is not obviously an error -- when a parent files a contract its
subsidiary signed, the subsidiary *is* the party.

```{r}
#| label: read-fallback
ent_read_spans(
  .tab       = dplyr::filter(tab_party, .data$Status == "first"),
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .n         = 8L,                    # the guess, read as a guess
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("CompanyName", "Party", "Status", "PartyStart"),
    .title = "Documents where the first name was taken instead"
  )
```

```{r}
#| label: read-documents
ent_read_entities(
  .roles = tab_roles,
  .keys  = tab_keys,
  .docs  = NULL,                  # drawn from the whole sample
  .n     = .lP$Params$ReadDocs,
  .max   = .lP$Params$ReadMax,
  .seed  = .lP$Params$Seed
) |>
  ent_report_entities(.counts = tab_counts)
```

```{r}
#| label: read-compensation
# The one cell in any table that does not move smoothly with width: among fallback documents in
# Employment: Compensation, the mean counterparty count roughly triples between +/- 1,000 and
# +/- 2,000, which happens in no other class. Read rather than adjusted -- if it is a real drafting
# pattern nothing changes, and if it is a defect it would otherwise sit inside the released number.
ent_read_entities(
  .roles = tab_roles,
  .keys  = tab_keys,
  .docs  = tab_counts$DocID[tab_counts$Class == "Employment: Compensation" &
                              tab_counts$Status == "first"],
  .n     = 5L,
  .max   = .lP$Params$ReadMax,
  .seed  = .lP$Params$Seed
) |>
  ent_report_entities(
    .counts = tab_counts,
    .title  = "Employment: Compensation, fallback anchors -- the one cell that jumps"
  )
```

# Validation

```{r}
#| label: validate-offsets
# AN EQUALITY, NOT A CONTAINMENT. Asking whether the span appears somewhere inside the slice is
# answered YES more easily the wider the slice runs. The slice must BE the span.
tab_check <- ent_check_offsets(
  .tab       = tab_party,
  .path_text = .lP$Input$Text,
  .col_start = "PartyStart",
  .col_stop  = "PartyStop",
  .col_span  = "PartySpan",           # the span as stored, not the whitespace-collapsed name
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Party offsets at or after character zero",
    "Documents carrying exactly one row",
    "Window contains the party it is centred on",
    "Tail begins at or after the window ends",
    "Roles partition the entities",
    "Tail width reported wherever a tail exists"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(tab_party$PartyStart >= 0L, na.rm = TRUE),
    dplyr::n_distinct(tab_party$DocID),
    sum(tab_counts$WinStart <= tab_counts$PartyStart &
          tab_counts$WinEnd >= tab_counts$PartyStart, na.rm = TRUE),
    sum(tab_counts$TailStart >= tab_counts$WinEnd, na.rm = TRUE),
    sum(tab_counts$NFull >= tab_counts$NCounter + tab_counts$NTailNew + tab_counts$NOther),
    sum(!is.na(tab_counts$TailWidth[tab_counts$HasTail]))
  ),
  Of = c(
    nrow(tab_check),
    sum(!is.na(tab_party$PartyStart)),
    nrow(tab_party),
    sum(!is.na(tab_counts$WinStart)),
    sum(!is.na(tab_counts$WinEnd)),
    nrow(tab_counts),
    sum(tab_counts$HasTail)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

The first row is the offset discipline: Python emits code-point offsets, and any R operation reaching
for `substr` rather than `stri_sub` would index bytes with no error raised anywhere. It is also the
check that an entity's offsets came from one mention rather than two. The last row is new, and it
exists because a missing tail width previously propagated silently through a class median.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_roles, .lP$Output$Roles)
arrow::write_parquet(tab_counts, .lP$Output$Party)

tibble::tibble(
  Artifact = c("Organisations with roles and window flags, per document per name",
               "Party, window bounds and counts, per document"),
  Path     = c(.lP$Output$Roles, .lP$Output$Party)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B")
```

Both artifacts carry every document, not only the matched ones, and both carry the unadjusted count
beside the rule's. A consumer filtering on `Status` makes that decision visibly; a consumer handed a
pre-filtered file makes it without knowing.

# Overview

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of LexNLP organisation spans by relative position in the document, weighted by
#|   spans and by documents. No cutoff is drawn, because this version has no region rule: the shape
#|   describes the engine, and the window is centred on the party rather than on the page."
ent_plot_density(.tab = ent_density(.spans = tab_spans, .bins = .lP$Params$Bins))
```

```{r}
#| label: fig-party-status
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "How the contracting party was found, by contract type, as shares within each type. The
#|   middle segment is the fallback -- the first name in the document, taken because none matched the
#|   registrant -- and the counterparty tables report it separately for that reason."
ent_plot_status(.tab = tab_counts)
```

```{r}
#| label: fig-window
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Mean counterparties per document by contract type and window specification. The gap
#|   columns are reported as evidence rather than offered as a choice: they track the fixed widths
#|   without beating them, which is what retires the gap arm."
ent_plot_window(.tab = tab_sweep_window)
```

```{r}
#| label: fig-baseline
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "The rule against the count it replaces. Each bar is the mean number of distinct
#|   organisations named anywhere in the contract, split into those the window keeps as
#|   counterparties and those it removes."
ent_plot_baseline(.tab = tab_counts)
```

```{r}
#| label: report-everything
ent_report_all_org(
  .keys        = tab_keys,
  .rule        = .lP$Params$Rule,
  .boundary    = tab_boundary,
  .dist        = tab_dist,
  .gap         = tab_gap,
  .party       = tab_party,
  .where       = tab_where,
  .win_all     = tab_win_all,
  .win_matched = tab_win_matched,
  .win_first   = tab_win_first,
  .tail        = tab_tail,
  .length      = tab_length,
  .sweep       = tab_sweep_match,
  .terms       = tab_terms,
  .n_terms     = .lP$Params$TermsN
)
```

# Next

Geography is resolved against the parties located here: for each party, the nearest place name
forward of it, stopping at the next organisation. The three roles that adjacency separates -- state
of incorporation, party location, governing law -- are named from the resulting table rather than
declared in advance, and the filer's row is validated against the registered address EDGAR records.
The boundary block above says whether a ragged span can move that assignment; on this sample it
cannot.

Dates and money follow, neither of them anchored on a party, and both are added to this document as
their own entity sections under the same discipline: the rule is a value, one function applies it,
and the tables and the artifacts come from the same call.
