---
title: "Contract Classification -- A Local LLM as a Third Arm (03D)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# Figure geometry is NOT set here -- it is declared once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                         # message = FALSE would discard this document's entire output
  warning  = FALSE,
  comment  = ""          # drops the "##" prefix, so console blocks copy verbatim
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the folds, the shared scoring layer and the category vocabulary; 03B supplies the
# transformer predictions this arm is measured against. Sourcing both means the language model is
# scored by the same code on the same splits and drawn with the same category order, which is the
# only reason its numbers and its figures can sit beside the other arms'.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # resolves to 1_code/03D-ClassifyLLM.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

A reader of this paper will ask why a fine-tuned encoder was necessary when an open-weight
instruction model can be handed a contract and asked what it is. The answer should be a number on the
same folds, not an assertion, and this document produces it.

The LLM is estimated as a **third arm**, not as a repair mechanism. It writes run folders in the
schema 03B and 03C use, so the shared leaderboard ranks it beside them and the orchestrator can route
to it with no special case anywhere. That is a deliberate constraint: the moment an LLM becomes
bespoke logic inside a router, it stops being comparable, and comparability on identical folds is the
property this whole stack exists to protect.

## The contamination this stage is built to avoid

A prompt is not a fixed object. It is written by a person, and a person who iterates it against the
documents the transformer got wrong has fitted it to the labels as surely as gradient descent would
have -- more efficiently, in fact, because errors concentrate exactly where the taxonomy is
ambiguous. Nested selection downstream cannot detect this: it protects the choice of routing rule,
not the provenance of an arm.

So arms are separated by what their author was allowed to see, and the separation is carried in the
data rather than in a promise:

| Tier | How the prompt was written | Folds | Status |
|:--|:--|:--|:--|
| **blind** | From the taxonomy alone. No prediction, no error list, no labelled document read. | 1-5 | enters the search |
| **tuned** | Iterated against folds 1-4, their errors included. | 5 only | bounded check |

This is the discipline 03C already applies to the generated keyword list, for the identical reason.

## Folds for a model that does not train

A blind prompt has no training of any kind, so every fold is held out and a single pass covers the
sample. Its per-fold metrics partition that one pass rather than forming five independent estimates:
they measure how much the documents differ, not how much the method varies. They are still written,
because the run schema must match the trained arms' and because the fold spread is the unit every
comparison in this study is expressed in. They are **not** a basis for choosing among prompts, which
is why prompt selection lives in the tuned tier and is labelled accordingly.

## Two things worth sweeping

**Whether the model may decline.** A model allowed to answer `UNSURE` becomes an abstaining arm --
which is exactly what the orchestrator's cascade is built around, since it can commit where it is
confident and leave the rest to the transformer. A model forced to choose is a terminal arm competing
head-on. Different objects, different uses, so both are estimated.

**What the model is told.** The `labels` level shows category names only and is the honest floor: it
measures what the model knows about contracts with no help. The `codebook` level adds one line per
category. The gap between them is what the taxonomy documentation is worth, which is a number worth
having, since writing that documentation is the main human cost of adopting this scheme.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(.dir_here = here::here(), .name_script = "03B-ClassifyTrainBERT")

.lP <- list(
  Input = list(
    Prepared = utils_file_path(.dir_prep, "prepared.parquet") # written by 03A
  ),
  Runs = list(
    Bert = utils_file_path(.dir_bert, "runs"),  # the arm this one is measured against
    Llm  = utils_file_path(.dir_main, "runs")   # written here, in the shared schema
  ),
  Output = list(
    Cache = utils_file_path(.dir_main, "cache"),            # one file per answered document
    Rates = utils_file_path(.dir_main, "rates.parquet")     # fitted generation rates, keyed on shape
  ),
  Engine = list(
    Host    = "http://localhost:11434", # local Ollama
    CtxMin  = 8192L,                    # floor: free on this hardware, and keeps caches valid
    CtxMax  = 32768L,                   # ceiling: above this a configuration is refused, not trimmed
    Timeout = 600                       # a 32b model on a long excerpt can take minutes
  ),
  Param = list(
    # All three taxonomies. The generative arm ran on the detailed one alone while its shape was
    # unknown, which is why the confidence flag is estimated on one task and the manifest's
    # confidence block has no task dimension. Cost is the reason it stayed there and cost is why it
    # need not: the answer is one enum token, so the bill is prefill, and prefill is the category
    # list plus categories-times-shots worked examples. Seven categories and two cost a fraction of
    # twelve at the same settings, and the two together come to roughly what the detailed taxonomy
    # cost on its own. Three independent estimates of the blind-to-crossfold gradient, across
    # taxonomies of twelve, seven and two categories, is also a far stronger claim about prompting
    # than one estimate on one taxonomy.
    Tasks       = c("ClassDetailed", "ClassBroad", "AmendType"),
    Models      = "qwen3:8b",                 # add "qwen3:32b" once the smaller model's shape is known
    Guidance    = c("labels", "codebook"),    # what the model is told about the taxonomy
    NChars      = 6000L,                      # header window; roughly the transformer's reading span
    Abstain     = FALSE,                      # forced choice: the agreement vote needs every document
    Think       = FALSE,                      # reasoning pass off; a vector here sweeps it
    Shots       = c(1L, 2L, 4L),              # examples per category; the only axis that has moved

    FoldsFull   = 1:5,                        # folds a full-coverage tier covers
    FoldHoldout = 5L,                         # the only honest fold for a tuned prompt
    ExampleFold = 1:4,                        # folds a tuned prompt may draw examples from
    # NULL runs the whole sample; an integer caps every configuration at that many documents,
    # stratified so no category drops out. A capped run is written to a sibling preview root under a
    # name carrying the cap, so its numbers can never be pooled with a full run's or picked up by the
    # orchestrator as an arm. Set an integer here to rehearse the document cheaply; NULL is what
    # produces the arm the orchestrator consumes.
    Limit       = NULL
  )
)
```

`Think` is the setting that decides whether this document takes an hour or a night. A
reasoning-capable model runs a chain-of-thought pass unless told otherwise, and on a task whose
answer is one token drawn from a fixed enum, that trace is essentially the entire cost: hundreds of
tokens generated and then discarded, per document, to arrive at a label the model had already
settled on. Turning it off is not a quality trade so much as a refusal to pay for output nobody
reads.

It stays an argument rather than becoming a constant because whether reasoning helps classification
is a fair question, and `Think = c(FALSE, TRUE)` sweeps it as an ordinary axis. It is simply not a
question worth paying for before a baseline exists.

The model list is one tag for now. Sweeping both sizes before the smaller one's behaviour is
understood spends a night of compute to learn two things at once, and the axes that matter -- whether
refusal is ever used, whether worked examples help -- are visible on the cheaper model alone. Adding
the second tag later costs nothing already paid for, since every answer caches on the tag.

`Abstain` is fixed at forced choice, and that is a decision about what this arm is for rather than a
guess about what scores better. The orchestrator uses the LLM in two ways. As a routing arm it would
prefer to abstain, committing only where confident and leaving the rest. As a **vote on the
confidence flag** it must have an opinion about every document, because a tier is computed from the
arms that committed, and an arm that declines simply drops out of the vote on exactly the documents
where a third opinion is most wanted. The flag is the more valuable of the two uses and the one that
needs full coverage, so full coverage is what this pass buys. A permitted-refusal variant is a second
pass, not a free one -- the refusal instruction changes the prompt, so it changes the cache key.

`Limit` is `NULL`, so this is the real pass. The cost projection below runs first and reports the
rate on this machine before any of it starts, and every answer is cached as it arrives, so an
interrupted run resumes rather than restarting. Reading the projection and stopping is a supported
outcome.

```{r}
#| label: configure-runs-root
# The preview root is derived rather than typed, so the sweep and the reports cannot disagree about
# which set of runs this render is talking about.
.dir_runs <- llm_runs_root(.runs_root = .lP$Runs$Llm, .limit = .lP$Param$Limit)
cat("Runs root: ", .dir_runs, "\n")
```

The instruction shown to the model is a swept level, so it is written here rather than buried in a
function. What the model was asked is exactly the sort of thing a referee reads, and the assembled
prompt is stored verbatim in each run's `config.json` so any result traces to the words that produced
it.

```{r}
#| label: configure-task-lines
.lP$TaskLines <- c(
  ClassDetailed = paste(
    "You are reading an excerpt from a material contract filed with the US Securities and Exchange",
    "Commission as an exhibit. Classify it into exactly one category."
  ),
  ClassBroad = paste(
    "You are reading an excerpt from a material contract filed with the US Securities and Exchange",
    "Commission as an exhibit. Classify it into exactly one broad category."
  ),
  AmendType = paste(
    "You are reading an excerpt from a material contract filed with the US Securities and Exchange",
    "Commission as an exhibit. Decide whether it is an original agreement or an amendment to an",
    "agreement that already exists."
  )
)
```

Definitions for the `codebook` guidance level are supplied here or not at all. Leaving the table
`NULL` collapses that level onto `labels`, which is a legitimate configuration and not a failure;
filling it in is what makes the guidance axis measurable.

```{r}
#| label: configure-definitions
# One row per category, matching the label strings in the prepared sample exactly. Where a category
# is absent from this table the prompt falls back to its name alone, so a partially filled codebook
# is usable and its effect is simply smaller.
tab_definitions <- tibble::tribble(
  ~Label, ~Definition
  # "Leases", "An agreement conveying the right to occupy or use property for a period in return for rent."
)
if (nrow(tab_definitions) == 0L) tab_definitions <- NULL

# With nothing supplied the codebook level renders identically to labels, so sweeping both would
# create configurations that differ in name only. They would cost no compute -- identical prompts hit
# identical cache keys -- but they would report a zero difference between two levels that were never
# actually different, which reads as evidence that documentation does not help.
if (is.null(tab_definitions)) .lP$Param$Guidance <- "labels"
```

Nothing here is cached at the document level by name. Every model answer is stored under a hash of
the document, the assembled prompt, the model tag, the context window and whether declining was
permitted, so changing one clause of the instruction misses the cache and re-asks. That is the
property a name-keyed cache fails to provide, and it is why this project treats name-keyed caches as
a trap.

```{r}
#| label: load-prepared-sample
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

clf_report_folds(
  .tab   = tab_prep,        # prepared sample
  .level = "ClassDetailed"  # folds were stratified on this taxonomy
)
```

# What the model is shown

The label set is read from the data rather than written as a constant, so a taxonomy revision cannot
leave the prompt describing categories that no longer exist. It is presented alphabetically: ordering
by frequency would hand the model the class prior, which on a sample this imbalanced is the single
easiest thing to exploit and is not something the blind tier is entitled to.

```{r}
#| label: show-prompt
labels_detailed <- llm_labels(
  .tab_prep  = tab_prep,       # prepared sample
  .label_col = "ClassDetailed" # task
)

cat(llm_prompt(
  .text          = "THIS LEASE AGREEMENT is made as of January 1, 2015, between ...",
  .labels_block  = llm_render_labels(
    .labels      = labels_detailed,   # category names
    .definitions = tab_definitions,   # NULL collapses codebook onto labels
    .guidance    = "labels"           # the floor level
  ),
  .task_line     = .lP$TaskLines[["ClassDetailed"]], # the instruction
  .examples      = NULL,                             # blind tier shows none
  .allow_abstain = TRUE,                             # the refusal token is offered
  .n_chars       = 200L                              # short here only so the block is readable
))
```

# Cost

A local generation is seconds and the sample is thousands of documents, so a sweep is measured in
nights rather than minutes. The projection below is fitted on this machine and this model rather than
on a nominal figure, and it is the difference between an overnight run and a week of them. Read it
before starting.

It prices every grid this document runs, and it fits a separate rate for each distinct prompt. Both
of those matter more than they sound. With the reasoning pass off the answer is a single token drawn
from an enum, so nearly the whole cost is reading the prompt -- and the prompt is the category list
plus categories-times-shots worked examples. A four-shot prompt over twelve categories is several
times the length of a blind one, and a two-category task at the same shot count is a fraction of a
twelve-category one. One rate taken from one blind cell and multiplied across the grid would
understate the long shapes and overstate the short ones at the same time, which is not a rounding
error but the difference between reading a night correctly and reading it as an afternoon.

```{r}
#| label: cost-build-grids
# Every grid is built here, before the projection, because a projection that cannot see a grid
# cannot price it -- and the two tiers it could not see are three quarters of the work. Each is
# displayed in the section that argues for it.
grid_blind <- llm_grid(
  .label_cols    = .lP$Param$Tasks,     # every taxonomy, not only the headline one
  .models        = .lP$Param$Models,    # size as an axis
  .guidance      = .lP$Param$Guidance,  # what the model is told
  .shots         = 0L,                  # a blind prompt shows no labelled example
  .n_chars       = .lP$Param$NChars,    # header window
  .allow_abstain = .lP$Param$Abstain,   # forced choice and permitted refusal
  .think         = .lP$Param$Think,     # reasoning regime
  .tier          = "blind"              # no examples at all; entitled to every fold
)

grid_cross <- llm_grid(
  .label_cols    = .lP$Param$Tasks,     # every taxonomy
  .models        = .lP$Param$Models,    # same models
  .guidance      = .lP$Param$Guidance,  # same guidance as the blind tier
  .shots         = .lP$Param$Shots,     # examples per category, drawn from the complement folds
  .n_chars       = .lP$Param$NChars,    # same window
  .allow_abstain = .lP$Param$Abstain,   # same refusal regime, so the tiers compare
  .think         = .lP$Param$Think,     # same reasoning regime
  .tier          = "crossfold"          # examples from the complement; entitled to every fold
)

# ClassDetailed alone, deliberately. This tier prices development-with-hindsight against the blind
# arm on the one fold a tuned prompt never read. It is a statement about method rather than a
# measurement of a taxonomy, and it cannot enter the router on any task, so running it three times
# would buy a second and third illustration of the same point at the cost of real inference.
grid_tuned <- llm_grid(
  .label_cols    = "ClassDetailed",      # the worked example; see above
  .models        = .lP$Param$Models,     # same models
  .guidance      = .lP$Param$Guidance,   # whatever guidance the blind tier had available
  .shots         = .lP$Param$Shots,      # worked examples, drawn from folds 1-4 only
  .n_chars       = .lP$Param$NChars,     # same window
  .allow_abstain = .lP$Param$Abstain,    # matched to the blind tier, or the tiers are not comparable
  .think         = .lP$Param$Think,      # same regime as the blind tier, so the tiers compare
  .tier          = "tuned"               # holdout fold only
)
```

```{r}
#| label: grid-blind
grid_blind |>
  dplyr::select(Task = LabelCol, Model, Guidance, Window = NChars, Abstain = AllowAbstain, Think) |>
  tbl_say(.title = paste0("Blind grid: ", nrow(grid_blind), " configurations"))
```

A missing model is the failure worth catching first. Ollama answers every request for an unpulled tag
with a 404, which the classifier treats as a declined answer, so the configuration completes with zero
coverage after several thousand futile calls and nothing errors. One check converts that into a line
naming the command that fixes it.

```{r}
#| label: preflight-models
llm_check_models(
  .models = .lP$Param$Models, # every tag the grid intends to use
  .host   = .lP$Engine$Host   # local Ollama
)
```

```{r}
#| label: cost-projection
# Every grid this document runs, not the blind one alone. The blind tier is one configuration per
# task out of the four that cover every fold, and it is the cheapest of them by a wide margin
# because it shows no worked examples -- so projecting the night from it alone understates the night
# by most of it. The grids are bound rather than projected separately because the shapes have to be
# grouped across them: a crossfold cell and a tuned cell at the same shot count carry the same
# prompt and differ only in how many documents they classify.
llm_report_cost(
  .grid          = dplyr::bind_rows(grid_blind, grid_cross, grid_tuned),
  .tab_prep      = tab_prep,            # documents to sample from
  .task_lines    = .lP$TaskLines,       # as in the real pass
  .definitions   = tab_definitions,     # as in the real pass
  .n             = 5L,                  # documents per shape used to fit its rate
  .limit         = .lP$Param$Limit,     # project what will actually run, not the whole corpus
  .seed          = 42L,                 # same documents on every render
  .example_chars = 700L,                # as in the sweep; examples dominate the long shapes
  .host          = .lP$Engine$Host,     # local Ollama
  .num_ctx       = NULL,                # derived per shape, as the sweep derives it
  .ctx_min       = .lP$Engine$CtxMin,   # floor
  .ctx_max       = .lP$Engine$CtxMax,   # ceiling
  .timeout       = .lP$Engine$Timeout,  # per-request ceiling
  .rate_store    = .lP$Output$Rates,    # fitted rates persist; only new shapes are timed
  .refit         = FALSE                # TRUE after a hardware or server change
)
```

A rate is a property of this machine, this model and this prompt shape, and none of those differs
between two renders of the same document -- so the fitted rates are kept and only a shape the store
has never seen is timed. The store is keyed on the shape and the derived window rather than on a
chunk name, which is the same discipline the answer cache follows and for the same reason: a
name-keyed store hands back the previous configuration's number without erroring. `FittedOn` travels
with each rate and is printed, so a number measured on different hardware is visible rather than
merely old.

Read the per-task rows rather than the total. The sweep skips any configuration whose runs are
already on disk and caches every individual answer besides, so a task that has already run costs
nothing and its row prices work that will not happen. The total prices a tree with nothing in it.

# The blind sweep

The sweep is idempotent: a configuration whose runs are already on disk is skipped without touching
the model, and every individual answer is cached besides. The first execution is long; every later
one costs a directory listing and reproduces identical output. That is what makes an
always-executing document affordable here, and it is the same bargain 03B and 03C strike.

```{r}
#| label: sweep-blind
swept_blind <- llm_sweep(
  .grid          = grid_blind,             # configurations to run
  .tab_prep      = tab_prep,               # prepared sample
  .definitions   = tab_definitions,        # codebook text, or NULL
  .task_lines    = .lP$TaskLines,          # the instruction per task
  .runs_root     = .lP$Runs$Llm,           # base root; a capped run is redirected to its sibling
  .cache_dir     = .lP$Output$Cache,       # one file per answered document
  .folds_full    = .lP$Param$FoldsFull,    # a full-coverage tier is held out on every fold
  .fold_holdout  = .lP$Param$FoldHoldout,  # unused for this tier; passed for one call signature
  .example_folds = .lP$Param$ExampleFold,  # likewise
  .limit         = .lP$Param$Limit,        # NULL for the full sample; an integer for a preview
  .seed          = 42L,                    # fixes which documents a preview draws
  .overwrite     = FALSE,                  # FALSE skips work already present on disk
  .host          = .lP$Engine$Host,
  .num_ctx       = NULL,                   # derived per configuration
  .ctx_min       = .lP$Engine$CtxMin,       # floor
  .ctx_max       = .lP$Engine$CtxMax,       # ceiling
  .timeout       = .lP$Engine$Timeout
)
```

# The cross-fold sweep

The blind arm is honest but weak, and the reason is visible in its per-class table rather than its
headline: it starves some categories and floods others, because nothing in the prompt tells it what
this taxonomy means in practice. Two worked examples per category fix a great deal of that. The
problem has been that examples have to come from somewhere, and drawing them from the labelled sample
is exactly the training the blind tier is defined by not having.

Rotating solves it. For each fold in turn the examples are redrawn from the **complement** of that
fold, so the prompt facing a document never contains a document from that document's own fold. That
is precisely the discipline the transformer's training follows, and it earns the same entitlement:
all five folds, which means this arm can enter the router's nested search and vote on the confidence
flag, neither of which a single-fold arm can do.

It costs one pass over the corpus -- five passes over a fifth each -- so at the measured rate it is
minutes rather than hours. The examples are redrawn per fold rather than reused, because reusing one
fold's draw would put that fold's labelled documents into the prompt facing every other fold, which
is the leak this tier exists to avoid.

```{r}
#| label: grid-crossfold
grid_cross |>
  dplyr::select(Task = LabelCol, Model, Guidance, Shots, Window = NChars, Abstain = AllowAbstain,
                Think) |>
  tbl_say(.title = paste0("Cross-fold grid: ", nrow(grid_cross), " configurations"))
```

```{r}
#| label: budget-crossfold
llm_report_budget(
  .grid       = grid_cross,        # what would be run
  .tab_prep   = tab_prep,          # supplies the worked examples
  .task_lines = .lP$TaskLines,     # the instruction per task
  .ctx_min    = .lP$Engine$CtxMin, # floor
  .ctx_max    = .lP$Engine$CtxMax  # ceiling
)
```

Worked examples dominate this budget: twelve categories at four examples each is forty-eight
excerpts against one document. The window is therefore derived per configuration rather than fixed,
because one number cannot be right for zero shots and for four. Below what a prompt needs the server
does not error -- it trims the FRONT of the prompt, removing the instruction and the category list,
and the model answers from a contract with no task. Under a JSON enum that still returns a valid
category name.

```{r}
#| label: sweep-crossfold
swept_cross <- llm_sweep(
  .grid          = grid_cross,             # configurations to run
  .tab_prep      = tab_prep,               # prepared sample
  .definitions   = tab_definitions,        # codebook text, or NULL
  .task_lines    = .lP$TaskLines,          # the instruction per task
  .runs_root     = .lP$Runs$Llm,           # same base root
  .cache_dir     = .lP$Output$Cache,       # same answer cache
  .folds_full    = .lP$Param$FoldsFull,    # every fold is classified, each from the others
  .fold_holdout  = .lP$Param$FoldHoldout,  # unused for this tier
  .example_folds = .lP$Param$ExampleFold,  # unused: the complement is computed per fold
  .limit         = .lP$Param$Limit,        # NULL for the full sample
  .seed          = 42L,                    # fixes which examples each fold draws
  .overwrite     = FALSE,                  # FALSE skips work already present on disk
  .host          = .lP$Engine$Host,
  .num_ctx       = NULL,                   # derived per configuration
  .ctx_min       = .lP$Engine$CtxMin,       # floor
  .ctx_max       = .lP$Engine$CtxMax,       # ceiling
  .timeout       = .lP$Engine$Timeout
)
```

Every configuration here carries the same name across its five folds, because the name describes the
example *recipe* -- how many per category, drawn from the complement, at a fixed seed -- rather than
any one fold's draw. No single draw describes the arm, and a name built from the first fold's would
claim to identify a configuration four fifths of which it never saw.

# Results

```{r}
#| label: load-run-metrics
# A cheap read of a few small Parquet files, deliberately not cached: a cache keyed on a name rather
# than on the data behind it would serve results from a previous sample without raising an error.
tab_overall <- clf_load_overall(.runs_roots = c(.lP$Runs$Bert, .dir_runs))
```

```{r}
#| label: results-leaderboard
purrr::walk(
  .x = .lP$Param$Tasks,
  .f = function(.t) {
    llm_report_leaderboard(
      .tab_overall = tab_overall,     # bound per-fold metrics
      .label_col   = .t,              # task
      .n           = 20L              # rows to display
    )
  }
)
```

Coverage sits beside accuracy because an abstaining configuration and a forced-choice one are not
comparable on accuracy alone. Declining protects precision at the cost of recall, so reading only the
accuracy column would rank the two by how often each was allowed to stay silent.

```{r}
#| label: results-effects
tidyr::expand_grid(
  Task = .lP$Param$Tasks,                           # every taxonomy
  Axis = c("Model", "Guidance", "AllowAbstain", "Think")   # axes that could have been swept
) |>
  purrr::pwalk(function(Task, Axis) {
    llm_report_effect(
      .tab_overall = tab_overall,  # bound per-fold metrics
      .axis        = Axis,         # axis to marginalise over
      .label_col   = Task          # task
    )
  })
```

An axis taking one level in every tier is skipped rather than printed, so this block stays silent
until something is actually swept. Two of the axes carry substantive content once they are. If a
smaller model matches a larger one, that is a practical result worth reporting -- the analysis becomes
runnable on hardware most departments have. And the `labels`-to-`codebook` difference prices the
taxonomy documentation, which is the main human cost of adopting the scheme and until now has had no
number attached.

Marginals are computed within tier and averaged over configurations rather than over runs. Pooling
tiers would turn every axis into a proxy for the blind-tuned gap, since a tuned prompt carries the
richest settings by construction; and averaging over runs would weight a configuration by how many
folds its documents happened to reach.

## Against the other arms

```{r}
#| label: results-head-to-head
purrr::walk(
  .x = .lP$Param$Tasks,
  .f = function(.t) {
    llm_report_head_to_head(
      .tab_overall = tab_overall,             # every method, identical folds, identical scoring
      .label_col   = .t,                      # task
      .tier        = c("blind", "crossfold")  # the tiers scored on the whole sample
    )
  }
)
```

```{r}
#| label: results-leading-config
# A full-coverage tier, not simply the highest scorer. A tuned configuration is scored on the single
# fold its prompt never read, so choosing on score alone would silently switch this table -- and the
# disagreement table below it -- onto a fifth of the sample, where the counts look like a full pass
# and are not. Blind and crossfold both cover every fold and are both usable by the orchestrator.
#
# Resolved per task and kept in a named list. The leading configuration is a property of a task, and
# a single object named for the detailed taxonomy would have to be rebuilt silently to describe any
# other -- which is how a table comes to be captioned for one task and computed from another.
pred_llm_task <- purrr::map(.lP$Param$Tasks, function(.t) {
  cfg_ <- tab_overall |>
    dplyr::filter(LabelCol == .t, grepl("^llm-", Model), Tier %in% c("blind", "crossfold")) |>
    dplyr::summarise(MacroF1 = mean(F1_macro), nFolds = dplyr::n_distinct(TestFold),
                     .by = ConfigName) |>
    dplyr::slice_max(MacroF1, n = 1L, with_ties = FALSE)

  cli::cli_alert_info("{(.t)}: describing {cfg_$ConfigName} over {cfg_$nFolds} folds.")

  clf_pool_predictions(
    .runs_roots  = .dir_runs,        # LLM runs for this render
    .config_name = cfg_$ConfigName   # full-coverage tier, all folds
  )
}) |>
  purrr::set_names(.lP$Param$Tasks)

# The detailed taxonomy is the one the label-provenance check and the summary block describe, both of
# which are arguments about that taxonomy rather than about the arm. Bound here so those chunks read
# a name that says which task they mean.
pred_llm <- pred_llm_task[["ClassDetailed"]]
```

```{r}
#| label: results-perclass
purrr::walk(
  .x = .lP$Param$Tasks,
  .f = function(.t) {
    clf_report_perclass(
      .tab_pred = pred_llm_task[[.t]],                                    # pooled across every fold
      .title    = paste0("Leading full-coverage LLM configuration: ", .t) # heading
    )
  }
)
```

The per-category pattern is where an aggregate becomes interpretable. A model reaching the thin
categories the transformer struggles with -- R&D and peer agreements, where labelled examples are
scarce -- would be contributing something training data cannot buy, and that is the one result that
would make this arm worth routing to regardless of its aggregate score.

## Where the two disagree

```{r}
#| label: results-disagreement
tab_bert <- clf_load_overall(.runs_roots = .lP$Runs$Bert)   # transformer metrics only, read once

pred_bert_task <- purrr::map(.lP$Param$Tasks, function(.t) {
  bert_best_predictions(
    .tab_overall = tab_bert,        # transformer metrics
    .runs_roots  = .lP$Runs$Bert,   # run folders to pool from
    .label_col   = .t               # task
  )
}) |>
  purrr::set_names(.lP$Param$Tasks)

pred_det <- pred_bert_task[["ClassDetailed"]]  # named for the chunks that mean this taxonomy

purrr::walk(
  .x = .lP$Param$Tasks,
  .f = function(.t) {
    cli::cli_h3(.t)
    llm_report_disagreement(
      .pred_llm  = pred_llm_task[[.t]],   # leading LLM configuration for this task
      .pred_bert = pred_bert_task[[.t]]   # crowned transformer configuration for this task
    )
  }
)
```

This is the diagnostic that predicts, before any routing is scored, whether the arm can contribute.
The transformer being right far more often on the disputed documents means keeping it is already
near-optimal there, and no cascade will recover much.

# Robustness

## The tuned tier

The slot reserved for anything developed with folds one to four in view -- a prompt iterated against
observed errors above all -- evaluated on the fold it never saw. Worked examples no longer belong
here: the cross-fold tier does the same job honestly on every fold, and supersedes what this tier was
originally carrying. What remains is the comparison that needs a single held-out fold, and the gap
between it and the blind arm is what development-with-hindsight is worth on this task.

The grid was built with the others so the cost projection could price it. It stays on the detailed
taxonomy: this tier measures what development-with-hindsight is worth against the blind arm, which is
a claim about method rather than about a taxonomy, and no tuned configuration can enter the router on
any task whatever it scores.

```{r}
#| label: robustness-sweep-tuned
swept_tuned <- llm_sweep(
  .grid          = grid_tuned,             # configurations to run
  .tab_prep      = tab_prep,               # prepared sample
  .definitions   = tab_definitions,        # codebook text, or NULL
  .task_lines    = .lP$TaskLines,          # the instruction per task
  .runs_root     = .lP$Runs$Llm,           # same base root
  .cache_dir     = .lP$Output$Cache,       # same answer cache
  .folds_full    = .lP$Param$FoldsFull,    # unused for this tier
  .fold_holdout  = .lP$Param$FoldHoldout,  # the only fold a tuned prompt may be scored on
  .example_folds = .lP$Param$ExampleFold,  # where worked examples come from
  .limit         = .lP$Param$Limit,        # same cap, so the tiers stay comparable
  .seed          = 42L,                    # same documents as the blind preview
  .overwrite     = FALSE,                  # FALSE skips work already present on disk
  .host          = .lP$Engine$Host,
  .num_ctx       = NULL,                   # derived per configuration
  .ctx_min       = .lP$Engine$CtxMin,       # floor
  .ctx_max       = .lP$Engine$CtxMax,       # ceiling
  .timeout       = .lP$Engine$Timeout
)
```

```{r}
#| label: robustness-tiers
clf_load_overall(.runs_roots = .dir_runs) |>
  dplyr::filter(LabelCol == "ClassDetailed", TestFold == .lP$Param$FoldHoldout) |>
  dplyr::summarise(
    Coverage = mean(Coverage),
    Accuracy = mean(Accuracy),
    MacroF1  = mean(F1_macro),
    .by = dplyr::any_of(c("Model", "Tier", "Guidance", "Shots", "Think"))
  ) |>
  dplyr::arrange(dplyr::desc(MacroF1)) |>
  dplyr::mutate(
    Model    = sub("^llm-", "", Model),
    Coverage = tbl_pct(Coverage),
    Accuracy = tbl_pct(Accuracy),
    MacroF1  = sprintf("%.3f", MacroF1)
  ) |>
  tbl_say(.title = "Blind against tuned, on the holdout fold only")
```

Both tiers are compared on the same fold-five documents, which is the only comparison available: a
blind configuration's whole-sample score and a tuned one's holdout score are not the same quantity
and must not be placed in one column.

## Label provenance

The second labelling round is enriched for the categories the current taxonomy introduced and is the
harder subset. An LLM has no training data, so unlike the transformer it has no reason to do worse
there -- if it does, the difficulty is in the categories themselves rather than in the supervision.

```{r}
#| label: robustness-label-round
dplyr::bind_rows(
  clf_scores(.tab_pred = pred_llm, .none = LLM_NONE) |>
    dplyr::mutate(Labels = "Both rounds", .before = 1),
  clf_scores(
    .tab_pred = pred_llm |>
      clf_add_labelround(.tab_prep = tab_prep) |>   # attach the round each label came from
      dplyr::filter(LabelRound == "Round2"),        # restrict to directly-labelled documents
    .none = LLM_NONE
  ) |>
    dplyr::mutate(Labels = "Round 2 only", .before = 1)
) |>
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))) |>
  tbl_say(.title = "Leading LLM configuration by label provenance")
```

# Deployment

Nothing is deployed here. This stage writes run folders and stops: which arm labels the corpus is the
orchestrator's decision, taken on the same folds against every other arm, and taking it twice in two
places is how the two would come to disagree.

```{r}
#| label: deploy-inventory
llm_report_inventory(
  .swept     = dplyr::bind_rows(swept_blind, swept_cross, swept_tuned), # every cell touched here
  .runs_root = .dir_runs                                                # what the orchestrator reads
)
```

A run folder outlives the naming scheme that produced it. Adding a term to a configuration name --
the context window, say -- leaves every existing folder perfectly readable under a name the current
scheme would never write, and nothing errors. The orchestrator then reads one prompt under two
names, ranks it as two arms carrying identical scores, and either double-counts its folds or drops
one of them arbitrarily.

So this reconciles rather than lists. Both sweeps report the configuration name of every cell they
touched, written or skipped, which makes the set of current names exact and needs no rule about
which scheme is in force. Superseded runs are named and left alone: deleting is cheap to say and
expensive to be wrong about, and these cost nights of inference to produce.

# Overview

Everything above in one place, followed by the figures. Nothing here is new.

```{r}
#| label: overview-report-all
llm_report_all(
  .tab_overall = tab_overall,     # bound per-fold metrics, both methods
  .pred_llm    = pred_llm,        # leading LLM configuration
  .pred_bert   = pred_det,        # crowned transformer configuration
  .label_col   = "ClassDetailed"  # task
)
```

```{r}
#| label: fig-llm-gradient
#| fig-height: !expr plot_height(3L)
#| fig-cap: "Macro-F1 against worked examples per category, one panel per taxonomy, full-coverage
#|   tiers only. Zero examples is the blind prompt. Ribbons are one standard error across folds. The
#|   vertical scale is free by panel: a binary decision starts near a coin flip and a twelve-way one
#|   near a twentieth, so a shared axis would put the eye on the intercepts, which are not comparable
#|   across taxonomies, rather than on the slopes, which are."
llm_plot_gradient(
  .tab_overall = tab_overall,      # bound per-fold metrics
  .tasks       = .lP$Param$Tasks   # panels, in reading order
)
```

The slope is the result, not the level. Each taxonomy is a different problem and their intercepts say
only how many categories there are; that showing the model a handful of examples from folds it is not
scored on moves every one of them, in the same direction and with the same flattening, is a statement
about prompting rather than about any one label set. It is also the claim a reader is most likely to
doubt from a single taxonomy, where a fine-grained scheme resisting a one-sentence instruction is the
obvious competing explanation.

```{r}
#| label: fig-llm-leaderboard
#| fig-height: !expr plot_height(llm_n_configs(tab_overall, "ClassDetailed", 12L))
#| fig-cap: "Macro-F1 by configuration. Hollow bars are tuned prompts, written against four of the
#|   five folds, so their score does not estimate what a new prompt would achieve. The axis is fixed
#|   at zero to one, so this panel is comparable with the other arms."
llm_plot_leaderboard(
  .tab_overall = tab_overall,     # bound per-fold metrics
  .label_col   = "ClassDetailed", # task
  .n           = 12L              # configurations to display
)
```

```{r}
#| label: fig-llm-coverage
#| fig-height: !expr plot_height(7)
#| fig-cap: "Coverage against precision on committed documents. A point high and to the left is
#|   precise only because it declined most of the corpus, which is useful in a cascade and poor
#|   standing alone."
llm_plot_coverage(
  .tab_overall = tab_overall,     # bound per-fold metrics
  .label_col   = "ClassDetailed"  # task
)
```

::: {.panel-tabset}

## Per category

```{r}
#| label: fig-llm-perclass
#| fig-height: !expr plot_height(12)
#| fig-cap: "Per-category F1 for the leading full-coverage configuration, detailed taxonomy. The axis
#|   matches the transformer and keyword figures, so the three arms compare bar for bar."
clf_plot_perclass(.tab_pred = pred_llm)
```

Whether this arm reaches the thin categories the transformer struggles with is the one result that
would make it worth routing to regardless of its aggregate score. Read this panel against the same
figure in 03B and 03C: the categories are in the same order and on the same axis in all three.

## Where it abstains

```{r}
#| label: fig-llm-confusion
#| fig-height: !expr plot_height(12, .square = TRUE)
#| fig-cap: "Confusion matrix for the leading full-coverage configuration, row-normalised. Where the
#|   schema permitted declining, the rightmost column carries the share of each category the model
#|   refused to commit on."
clf_plot_confusion(
  .tab_pred  = pred_llm,      # leading full-coverage configuration, pooled across every fold
  .normalize = TRUE,          # each row sums to one, so any abstention share is directly readable
  .limits    = c(0, 1),       # same fill scale as the transformer and keyword matrices
  .label_min = 0.005          # a cell below half a percent is drawn but not labelled
)
```

The three arms now carry the same matrix in the same orientation with the same fill scale. Reading
them together is what the routing question in 03E turns on: a cell where this arm is strong and the
transformer weak is the only place a cascade can gain anything.

:::

# Next

The orchestrator inventories these runs alongside the transformer's and the keyword table's and
decides whether routing to this arm beats the transformer alone. Nothing about that decision is taken
here; this document supplies arms and a set of numbers describing them.

It now supplies one per taxonomy, which changes what the orchestrator can do rather than only how
much of it. A confidence flag computed from the arms that committed needs a generative opinion on the
task it is flagging, so a single-task arm confined the flag to a single task and left its manifest
block with no task dimension at all. Three arms remove that constraint; taking it up is 03E's work.

One extension still costs only compute. Adding a tag to `.lP$Param$Models` extends the size axis with
no other change, since every answer caches on the tag and nothing already paid for is repaid. The
blind tier is where that is cheapest -- it shows no worked examples, so it carries the shortest prompt
of any tier -- and it is where the question a larger model raises actually lives: whether the distance
between this arm and the transformer is a fact about language models or a fact about an eight-billion
parameter one.
