---
title: "Contract Classification -- Applying the Deployed Classifier (03F)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir  = here::here(),
  message   = TRUE,       # mandatory: cli writes through the message stream under knitr
  warning   = FALSE,
  comment   = "",         # drops the "##" prefix, so console blocks copy verbatim
  fig.width = 7.5,
  fig.align = "center",
  dpi       = 200,
  out.width = "100%"
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# 03A supplies the scoring and formatting layer, 03B the transformer inference call, 03D the
# generative arm's prompt machinery. Nothing here re-implements any of them: the deployed classifier
# is the same code the folds were run through, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03D-ClassifyLLM"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/03F-ClassifyApply.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every decision has been made. 03B chose a transformer and refit it on all labelled documents, 03C
published a keyword table, 03D added a generative arm, and 03E decided how to combine them and how
much to trust each result. This stage does none of that again. It reads what 03E wrote and applies
it to the corpus.

That separation is the point. An apply stage free to make its own decisions is an apply stage whose
output depends on which version of it last ran, and a released dataset cannot be defended on those
terms. So `mc_classify()` reads every default from the manifest and has almost none of its own, and
an argument passed explicitly is recorded as a **departure** in the result rather than quietly
honoured -- a caller can run a different checkpoint, they simply cannot do so invisibly.

## What comes back

One row per document per task: the label, which arm decided it, that arm's confidence, what every arm
said independently, the agreement tier, and the reliability estimated for that tier under the voting
set that was actually used. A user of the released dataset can condition on trust without re-running
anything, which is a materially different offer from a single headline accuracy.

## Why the generative arm is off by default

It is the most independent vote available and the only arm that saw none of the labelled sample, so
it is the one that most improves the flag. It is also hours of inference across a corpus of this
size rather than minutes. It is therefore pinned in the manifest and disabled: asking for it is one
argument, and a run that does not ask gets the two-family flag together with reliability numbers
estimated on the vote it actually ran.

That last clause is the part that would be easy to get wrong. A two-arm agreement pattern computed at
deployment is indistinguishable from a two-arm pattern computed on the labelled sample, so shipping
one set of reliabilities for every voting set would produce numbers that look entirely reasonable and
describe a vote that never happened. 03E estimates each set separately and the manifest records which
one a run is using.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_orch <- init_create_script_dir(.dir_here = here::here(), .name_script = "03E-ClassifyOrchestrate")

.lP <- list(
  Input = list(
    # fs::path, not utils_file_path: the project helper creates what it names, and a corpus tree
    # conjured into existence would report itself present while holding nothing.
    Manifest  = fs::path(.dir_orch, "deployment", "manifest.json"), # written by 03E
    Prepared  = fs::path(.dir_prep, "prepared.parquet"),            # labelled sample
    # The same parsed-contract tree 03A drew the labelled sample from, restricted to Exhibit 10.
    DirCorpus = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/",
    MetaData  = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet" # filer titles
  ),
  Cache = list(
    CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet") # DocID to Path index
  ),
  Output = list(
    Labels = utils_file_path(.dir_main, "labels") # the released labels
  ),
  Engine = list(
    # The same interpreter and the same engine directory 03B trains through. here::here rather than
    # a tilde path: system2 does not expand ~, so a tilde reaches the shell literally and fails with
    # exit 127 four hours into a corpus pass.
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "classify_apply.py") # companion to classify_train.py
  ),
  Param = list(
    BatchSize = 32L,    # documents per forward pass
    ChunkSize = 5000L, # documents per output file; a corpus pass should not be one write
    IndexRerun = FALSE, # TRUE re-walks the tree; FALSE reuses the cached index
    # The switch that decides whether this document is a rehearsal or the release. An integer draws
    # that many documents at random from the whole tree and writes them to a separate directory; NULL
    # labels the corpus. Set an integer, read the numbers, then set NULL.
    Limit = 100000L
  )
)
```

Nothing here is cached. The expensive work is the model passes themselves, and those are checkpointed
by writing labelled chunks as they complete, which is a resumable design rather than a cache: an
interrupted run restarts at the first chunk that has no output file.

```{r}
#| label: load-manifest
man <- mc_manifest(.path = .lP$Input$Manifest)
mc_report_manifest(.man = man)
```

Read that block before anything else. Every line of it is a decision someone made once and validated,
and a run applying the wrong quarter's configuration should be visible in the first screen of output
rather than in the released labels.

The corpus is an index here, not a table. The labelled sample fits in memory and the corpus does not:
1.1 million contracts of full text is hundreds of gigabytes, so what is held throughout is one row
per document with its path and filer title, and text is read one chunk at a time and discarded. Any
code that treats corpus text as a column runs out of memory somewhere past the first hundred
thousand documents.

```{r}
#| label: load-documents
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

tab_index <- mc_corpus_index(
  .dir_corpus = .lP$Input$DirCorpus,     # the parsed-contract tree, Exhibit 10 only
  .path_meta  = .lP$Input$MetaData,      # supplies DocDesc, the filer's own title
  .path_cache = .lP$Cache$CorpusFiles,   # walking a million files is cached, not repeated
  .rerun      = .lP$Param$IndexRerun,    # TRUE after new contracts have been parsed
  .limit      = .lP$Param$Limit,         # NULL labels the corpus; an integer rehearses
  .seed       = 42L,                     # a limited run draws the same documents each time
  .tab_prep   = tab_prep                 # flags documents the model was trained on
)

.dir_labels <- mc_labels_dir(.dir = .lP$Output$Labels, .limit = .lP$Param$Limit)

tab_index |>
  dplyr::summarise(
    Documents = dplyr::n(),
    InSample  = sum(InSample),
    WithDesc  = sum(!is.na(DocDesc))
  ) |>
  clf_say_table(.title = paste0("Corpus to label -> ", fs::path_rel(.dir_labels, here::here())))
```

`InSample` marks documents the transformer was trained on. They are still part of the corpus and
still get labels, but anyone measuring accuracy on them would be measuring training accuracy, so the
flag travels with the release rather than the documents being quietly dropped.

# A rehearsal on one chunk

Before a corpus pass, one chunk end to end. It exercises every arm, the routing policy and the flag
lookup, and it costs seconds -- which is the right price for discovering that a model directory moved
or that the keyword lexicon has a column the applier does not expect.

```{r}
#| label: rehearse-chunk
labelled_head <- mc_classify(
  .docs       = mc_read_chunk(dplyr::slice_head(tab_index, n = 200L)), # text read here, not held
  .manifest   = man,                                   # every default comes from here
  .tasks      = "ClassDetailed",                       # one task for the rehearsal
  .arms       = NULL,                                  # NULL takes the manifest's enabled set
  .voting_set = NULL,                                  # NULL takes the manifest default
  .tab_prep   = tab_prep,                              # only used if the generative arm runs
  .python     = .lP$Engine$Python,                     # inference environment
  .script     = .lP$Engine$Script,                     # inference script
  .batch_size = .lP$Param$BatchSize                    # documents per forward pass
)

mc_report_run(.tab = labelled_head)
```

```{r}
#| label: rehearse-inspect
labelled_head |>
  dplyr::select(DocID, Label, DecidedBy, Prob, Tier, Reliability) |>
  head(10) |>
  clf_say_table(.title = "First ten labelled documents")
```

A `DecidedBy` column showing only the terminal arm is the expected result rather than a
disappointment: 03E concluded that routing does not beat the transformer, so a policy that routes
nothing is the policy it deployed. What the other arms contribute here is the confidence flag, not
the label.

# The corpus pass

Chunked, and each chunk written as it completes. A corpus pass is measured in hours, so a failure at
document nine hundred thousand should cost one chunk rather than the run, and a restart should
resume rather than begin again.

```{r}
#| label: apply-corpus
fs::dir_create(.dir_labels)

chunks_ <- split(
  tab_index,
  ceiling(seq_len(nrow(tab_index)) / .lP$Param$ChunkSize)
)
cli::cli_alert_info("{length(chunks_)} chunk{?s} of up to {(.lP$Param$ChunkSize)} documents.")

purrr::iwalk(chunks_, function(.chunk, .i) {
  path_ <- fs::path(.dir_labels, sprintf("labels_%04d.parquet", as.integer(.i)))
  if (fs::file_exists(path_)) {
    cli::cli_alert_info("Chunk {(.i)}: already written, skipping.")
    return(invisible(NULL))
  }
  # Text enters memory here and leaves when the chunk is written. Reading the whole corpus first
  # would be simpler to write and impossible to run.
  t0_ <- Sys.time()
  docs_ <- mc_read_chunk(.chunk = .chunk)
  if (nrow(docs_) == 0L) {
    cli::cli_alert_warning("Chunk {(.i)}: no readable documents; nothing written.")
    return(invisible(NULL))
  }
  out_ <- mc_classify(
    .docs       = docs_,              # this chunk, text and all
    .manifest   = man,                # every default comes from here
    .tasks      = NULL,               # NULL labels every task the manifest carries
    .tab_prep   = tab_prep,           # only used if the generative arm runs
    .python     = .lP$Engine$Python,  # inference environment
    .script     = .lP$Engine$Script,  # inference script
    .batch_size = .lP$Param$BatchSize # documents per forward pass
  )
  arrow::write_parquet(
    out_ |> dplyr::left_join(.chunk |> dplyr::select(DocID, InSample), by = dplyr::join_by(DocID)),
    path_
  )
  # Beside the labels, not inside them: the duration belongs to the chunk, and a resumed run keeps
  # the timings it already paid for.
  mc_write_timing(
    .dir     = .dir_labels,                          # same directory as the labels
    .chunk   = .i,                                   # chunk index
    .n_docs  = dplyr::n_distinct(out_$DocID),        # documents actually labelled
    .seconds = as.numeric(difftime(Sys.time(), t0_, units = "secs")),
    .n_tasks = dplyr::n_distinct(out_$Task)          # a chunk costs one pass per task
  )
  cli::cli_alert_success("Chunk {(.i)}: {nrow(out_)} row{?s} written.")
})
```

```{r}
#| label: apply-throughput
mc_report_throughput(
  .dir      = .dir_labels,     # where the timings were written
  .n_corpus = nrow(tab_index), # documents a full pass would cover
  .n_tasks  = 3L               # tasks a full pass would label
)
```

Set `Limit` to `NULL` once that projection is acceptable. The rate is measured on this machine under
this configuration, so it is the only figure worth planning a night around.

# Results

```{r}
#| label: results-summary
tab_labels <- fs::dir_ls(.dir_labels, glob = "*.parquet") |>
  purrr::map(arrow::read_parquet) |>
  purrr::list_rbind()

tab_labels |>
  dplyr::summarise(nDocs = dplyr::n_distinct(DocID), .by = Task) |>
  clf_say_table(.title = "Documents labelled, per task")
```

The corpus will not look like the labelled sample, and it should not: the sample was drawn to support
estimation, with thin categories deliberately over-represented so they could be learnt at all. A gap
is expected. What a gap cannot distinguish on its own is whether it comes from that sampling design
or from the model drifting toward frequent categories on documents unlike anything it trained on --
and those have very different consequences for the released labels.

The confidence tiers separate the two. If documents the arms agreed on look like the labelled sample
while the ones they disagreed on carry the skew, the drift sits on uncertain documents and the flag
is already isolating it. If every tier is skewed alike, the difference is composition, the labels are
unaffected, and what carries the sample's composition is the reliability estimate rather than the
classifier.

```{r}
#| label: results-distribution
dist_det <- mc_distribution(
  .tab_labels = tab_labels,     # the corpus pass
  .tab_prep   = tab_prep,       # the labelled sample
  .label_col  = "ClassDetailed" # the only task carrying a flag
)

mc_report_distribution(.tab = dist_det)
```

```{r}
#| label: results-confidence
tab_labels |>
  dplyr::filter(!is.na(Tier)) |>
  dplyr::count(Task, VotingSet, Tier, name = "nDocs") |>
  dplyr::mutate(Share = clf_pct(nDocs / sum(nDocs)), .by = Task) |>
  clf_say_table(.title = "Confidence tiers across the corpus")
```

If the tier distribution here differs markedly from 03E's on the labelled sample, the flag is
behaving differently outside the data it was estimated on, and its reliability numbers should be
treated with more caution than the table suggests. That comparison belongs in the paper.

# Validation

The deployed classifier applied to the labelled sample must reproduce what 03E measured. Any gap is a
deployment fault -- a wrong checkpoint, a different context length, a lexicon that moved -- rather
than a modelling result, and it is the one check that catches an artifact mismatch the manifest's
existence test cannot.

```{r}
#| label: validation-roundtrip
round_trip <- mc_classify(
  .docs     = tab_prep |>
    dplyr::select(DocID, Text, dplyr::any_of("DocDesc")) |>
    dplyr::slice_head(n = 1000L), # the labelled sample already carries its text
  .manifest = man,                # the deployed configuration
  .tasks    = "ClassDetailed",    # the headline task
  .tab_prep = tab_prep,           # only used if the generative arm runs
  .python   = .lP$Engine$Python,  # inference environment
  .script   = .lP$Engine$Script   # inference script
)

round_trip |>
  dplyr::inner_join(
    tab_prep |> dplyr::select(DocID, TrueLabel = ClassDetailed),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::summarise(
    nDocs    = dplyr::n(),
    Accuracy = mean(Label == TrueLabel)
  ) |>
  dplyr::mutate(Accuracy = clf_pct(Accuracy)) |>
  clf_say_table(.title = "Deployed classifier on labelled documents")
```

This number will sit **above** the cross-validated estimate, and that is expected rather than
reassuring: the deployed model was refit on every labelled document, so these are documents it has
seen. It is a plumbing check, not a performance claim. The honest figure for the paper remains 03E's
nested estimate, and quoting this one instead would be reporting training accuracy.

# Overview

```{r}
#| label: overview-report
mc_report_manifest(.man = man)
mc_report_run(.tab = tab_labels)
```

# Next

The released dataset is these labels plus the manifest that produced them. Both have to be archived
together: labels without the manifest cannot be reproduced, and the manifest without the labels is a
recipe nobody ran.

Set `Limit` to `NULL` once the rehearsal reads sensibly. A limited run writes to `labels_preview`
and a corpus pass to `labels`, so the two never mix and neither resumes from the other -- chunk one
of a two-thousand-document rehearsal holds different documents from chunk one of the full pass, and
the skip-if-present rule could not tell them apart if they shared a directory.

Two things remain open and belong in the paper rather than in code. Whether the generative arm is
worth enabling for the release is a cost decision that 03E's voting-set comparison answers
empirically -- if the three-family flag separates the corpus no better than the two-family one, it is
not worth the hours. And the corpus tier distribution against the labelled sample's is the evidence
for how far the confidence flag can be trusted outside the data that produced it.
