---
title: "Contract Classification -- Comparing the Arms (03E)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# Figure geometry is NOT set here -- it is declared once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,       # mandatory: cli writes through the message stream under knitr, so
                         # message = FALSE would discard this document's entire output
  warning  = FALSE,
  comment  = ""          # drops the "##" prefix, so console blocks copy verbatim
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

# HOW TABLES ARE RENDERED, set once for the whole document.
#   "kable"   -- grouped headers, percentages, footnotes. What a reader of this document should meet.
#   "console" -- fixed-width ASCII blocks that survive being pasted into a terminal or a chat, which
#                is what a table is for while the analysis is being built.
# Both paths receive the same specification from the same call, so the caveats below each table are
# written once and appear either as numbered footnotes or as cli lines naming the column.
options(mc.table_mode = "kable")

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the folds, the shared scoring layer and the category vocabulary, so every number below is
# produced by the same code on the same splits and drawn with the same category order. The three
# training stages are sourced for their path helpers and published catalogues; no engine is invoked.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword",
         "03D-ClassifyLLM"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(),   # project root
  .name_script = .name_script    # resolves to 1_code/03E-ClassifyOrchestrate.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Three engines have labelled the same 4,398 documents on the same five folds. A transformer commits on
every document. A keyword table commits only where a term it trusts fires, and declines the rest. A
local language model commits everywhere, at a cost per document several orders of magnitude above the
other two.

This document puts all of them on one table and tells one story in five steps.

0. **The transformer is fitted at two context lengths.** Which one ships, and what does the other
   give? The length is that engine's cost knob, so both are on the table.
1. **How good is each engine on its own**, category by category.
2. **What perfect routing would give us.** It needs the truth and nobody can run it -- which is the
   point. It is the absolute ceiling on every rule at once.
3. **Can a clue we can actually see find the documents worth rerouting?** First clue: the transformer
   is unsure.
4. **Second clue:** the transformer's own two models contradict each other across the taxonomy.

**Nothing is re-estimated here.** Every number comes from the `predictions.parquet` files the three
training stages already wrote. No checkpoint is loaded, no lexicon is applied, no prompt is sent. What
this document adds is the one thing none of those stages could do: each knows how good its own engine
is, and none can see what the others said about any particular document.

## Why these numbers are honest, and where they are not

Each training stage cross-validated over five folds, so every label on the table came from a model
that never saw that document. Any accuracy computed here is already out of sample.

What is *not* protected is the choice of which threshold to quote. Sections 3 and 4 read the labels to
decide where a swap would have helped, so the best row is optimistic. With a handful of fixed
thresholds rather than a search that optimism is small and statable, and this document is an
indication of whether combination is worth pursuing rather than a deployable rule.

## Abstention is missing, not a category

The keyword engine emits a sentinel where no term fired. It becomes `NA` on read, and that distinction
runs through every metric below. An abstention is a miss for recall over the whole corpus and is
excluded from precision, and **both numbers are reported side by side** rather than one standing in
for the other. Reporting only the second is how a table covering a quarter of the corpus comes to look
competitive with a model that answers everywhere.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(.dir_here = here::here(), .name_script = "03B-ClassifyTrainBERT")
.dir_kw   <- init_create_script_dir(.dir_here = here::here(), .name_script = "03C-ClassifyTrainKeyword")
.dir_llm  <- init_create_script_dir(.dir_here = here::here(), .name_script = "03D-ClassifyLLM")

.lP <- list(
  Input = list(
    Prepared  = fs::path(.dir_prep, "prepared.parquet"),
    # What the two training stages crowned. This document reads those decisions and makes none of
    # its own: a fourth opinion about which model is best would be a disagreement, not information.
    BertCrown = fs::path(.dir_bert, "model_final", "deployed.parquet"),
    KwCatalog = fs::path(.dir_kw, "table", "catalogue.parquet")
  ),
  Runs = list(
    Bert = fs::path(.dir_bert, "runs"), # written by 03B
    Kw   = fs::path(.dir_kw,   "runs"), # written by 03C
    Llm  = fs::path(.dir_llm,  "runs")  # written by 03D; absent until that stage has run
  ),
  Param = list(
    Tasks      = c("ClassDetailed", "ClassBroad", "AmendType"),
    # Thresholds on the transformer's own probability. They look high because the distribution is:
    # the softmax is massed against one, so a conventional 0.90 selects a few per cent of the corpus.
    # The grid runs to 0.99 so the sweep reaches the region where the transformer is actually weak.
    Thresholds = c(0.900, 0.925, 0.950, 0.960, 0.970, 0.980, 0.990)
  )
)
```

One configuration stands for each engine, read from what its stage deployed: **both** transformer
context lengths 03B fitted, the keyword table 03C marked, and the best language-model configuration
covering all five folds. Which length ships is 03B's decision and is read rather than remade; every
comparison below measures against it, and Section 0 says what the other length would have given.

The truncation windows the keyword stage published are its own cost knob and are compared in 03C.
Repeating that here would be a second opinion about a question already answered.

Nothing is cached. Every step is a group-by over a few thousand rows.

Tables render either as styled html or as fixed-width console blocks, set by `mc.table_mode` in the
setup chunk. The console path exists because a table is read on screen and pasted into discussion
while an analysis is being built, and styled markup survives neither.

```{r}
#| label: load-prepared-sample
#| results: asis
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(file = .lP$Input$Prepared)

.dir_runs <- c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm)
.dir_runs <- .dir_runs[fs::dir_exists(.dir_runs)]

tibble::tibble(
  Root  = c("BERT (03B)", "Keyword (03C)", "LLM (03D)"),
  Path  = fs::path_rel(c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm), here::here()),
  Found = fs::dir_exists(c(.lP$Runs$Bert, .lP$Runs$Kw, .lP$Runs$Llm))
) |>
  tbl_out(.title = "Runs roots feeding this document")

if (length(.dir_runs) == 0L) cli::cli_abort("No runs on disk; run 03B before this document")
```

# The panel

Which configuration stands for each engine is the study design, so it is assembled in the open.

```{r}
#| label: build-crowned
#| results: asis
# THE TRANSFORMER, AT BOTH CONTEXT LENGTHS. 03B fits one model per task AND per length under
# model_final/, so the directories there are that stage's deployment decision and reading them gives
# every length it deployed. The length is this engine's cost knob -- a second full pass over 1.1
# million documents is not free -- so both travel and Section 0 compares them.
bert_deployed <- clf_load_overall(.runs_roots = .lP$Runs$Bert) |>
  dplyr::filter(!.data$Smoke, .data$ConfigName %in% orch_final_configs(.dir_bert = .dir_bert)) |>
  dplyr::summarise(
    LabelCol = dplyr::first(.data$LabelCol),
    MaxLen   = as.integer(dplyr::first(.data$MaxLen)),
    nFolds   = dplyr::n_distinct(.data$TestFold),
    .by = ConfigName
  ) |>
  dplyr::filter(.data$nFolds >= 5L) |>
  dplyr::transmute(Task = .data$LabelCol, Engine = paste0("Bert", .data$MaxLen), ConfigName)

# WHICH LENGTH SHIPS. 03B crowns one per task and writes it beside the models; this document reads
# that decision and never remakes it. Everything downstream measures against the crowned engine, so
# a fourth opinion here would silently change what "the baseline" means.
bert_crown <- arrow::read_parquet(file = .lP$Input$BertCrown)

baselines <- bert_crown |>
  dplyr::transmute(Task = .data$LabelCol, Baseline = paste0("Bert", as.integer(.data$MaxLen))) |>
  dplyr::filter(.data$Task %in% .lP$Param$Tasks)

# THE KEYWORD TABLE: the catalogue marks one published truncation window per task as the default.
kw_cat <- arrow::read_parquet(file = .lP$Input$KwCatalog)

# THE LANGUAGE MODEL: no artifact to read a decision off, so the best configuration covering all five
# folds stands for the engine. Absent entirely where that stage has not run, which narrows the
# analysis rather than stopping it.
llm_best <- if (fs::dir_exists(.lP$Runs$Llm)) {
  clf_load_overall(.runs_roots = .lP$Runs$Llm) |>
    dplyr::filter(!.data$Smoke) |>
    dplyr::summarise(
      MacroF1  = mean(.data$F1_macro),
      nFolds   = dplyr::n_distinct(.data$TestFold),
      LabelCol = dplyr::first(.data$LabelCol),
      .by = ConfigName
    ) |>
    dplyr::filter(.data$nFolds >= 5L) |>
    dplyr::slice_max(.data$MacroF1, n = 1L, by = LabelCol, with_ties = FALSE) |>
    dplyr::transmute(Task = .data$LabelCol, Engine = "Llm", ConfigName)
} else {
  tibble::tibble(Task = character(), Engine = character(), ConfigName = character())
}

tab_crowned <- dplyr::bind_rows(bert_deployed, llm_best,
  kw_cat |> dplyr::filter(Default) |> dplyr::transmute(Task, Engine = "Kw", ConfigName)
) |>
  dplyr::filter(.data$Task %in% .lP$Param$Tasks) |>
  dplyr::left_join(baselines, by = dplyr::join_by(Task)) |>
  dplyr::mutate(Ships = dplyr::if_else(.data$Engine == .data$Baseline, "<-", ""), Baseline = NULL) |>
  dplyr::arrange(.data$Task, .data$Engine)

tbl_out(.tab = tab_crowned, .title = "The configuration standing for each engine")
```

```{r}
#| label: build-panels
# One panel per task. The keyword arm is silenced on AmendType outside "Amended": that engine mines
# the positive class only and labels everything else "Original", which is the absence of evidence
# wearing the name of a class. Left alone the arm appears to cover the whole corpus and every table
# below would report a coverage it does not have.
panels <- purrr::map(.lP$Param$Tasks, function(.t) {
  orch_panel(
    .long = orch_read(
      .runs_roots = .dir_runs,                                        # every tree that exists
      .configs    = tab_crowned |> dplyr::filter(Task == .t) |>
        dplyr::select(Engine, ConfigName)                             # what stands for each engine
    ),
    .commit_only = if (.t == "AmendType") "Amended" else NULL         # see above
  )
}) |>
  purrr::set_names(.lP$Param$Tasks)
```

The panel is the whole data structure: one row per document, one prediction and one score per engine,
with `NA` where an engine declined. Every table and figure below is a group-by on it.

# Section 0: The two context lengths

The transformer is fitted at two truncation lengths and 03B crowns one per task. Both are on the
panel, because the length is that engine's cost knob: applying the longer one to the corpus is a
second full pass over 1.1 million documents, and a reader deciding whether to pay for it needs the
two side by side rather than one of them and a note saying the other was close.

Read the disagreement row against the aggregate. Two windows within a fraction of a point of each
other can still part company on hundreds of documents, and that reads very differently from one of
them simply being better: it means they are trading documents in both directions, and the cheaper one
is then the sensible default.

`EitherRight` on that row is the ceiling a perfect choice between the two would reach. Like every
ceiling in this document it needs the label and nobody can obtain it.

```{r}
#| label: windows-all
#| results: asis
purrr::iwalk(panels, function(.p, .t) {
  bert_ <- grep("^Bert", orch_engines(.tab = .p), value = TRUE)     # the lengths on this panel
  if (length(bert_) < 2L) {
    cli::cli_alert_info(
      "{(.t)} has one context length on the panel, so there is nothing to compare."
    )
    return(invisible(NULL))
  }
  orch_report_windows(
    .tab       = orch_windows(.tab = .p, .a = bert_[[1]], .b = bert_[[2]]),
    .a         = bert_[[1]],                                        # the shorter length
    .b         = bert_[[2]],                                        # the longer one
    .crowned   = baselines$Baseline[baselines$Task == .t],          # what 03B deployed
    .label_col = .t
  )
})
```

# Section 1: Each engine on its own

Three reference tables per task. Read `Precision` against `Recall`: precision excludes abstentions,
recall counts them as misses. An abstaining arm therefore shows high precision and low recall, which
is the honest picture of a partial classifier. `RecallSel` is the same arm measured only where it
committed, and describes it on its own terms.

`Accuracy` at the category level is one-vs-rest and is dominated by correct rejections -- a rare
category reads near-perfect while the engine misses most of its documents. It is reported because it
is asked for, and it is not the column to read.

```{r}
#| label: perclass-all
perclass <- purrr::map(panels, function(.p) {
  purrr::map(orch_engines(.tab = .p), \(.e) orch_perclass(.tab = .p, .engine = .e)) |>
    purrr::set_names(orch_engines(.tab = .p))
})
```

## Detailed

```{r}
#| label: perclass-detailed
#| results: asis
purrr::iwalk(
  .x = perclass$ClassDetailed,                                        # one table per engine
  .f = \(.t, .e) orch_report_perclass(.tab = .t, .engine = .e, .label_col = "ClassDetailed")
)
```

## Broad

```{r}
#| label: perclass-broad
#| results: asis
purrr::iwalk(
  .x = perclass$ClassBroad,                                        # one table per engine
  .f = \(.t, .e) orch_report_perclass(.tab = .t, .engine = .e, .label_col = "ClassBroad")
)
```

## Amendment

```{r}
#| label: perclass-amendment
#| results: asis
purrr::iwalk(
  .x = perclass$AmendType,                                        # one table per engine
  .f = \(.t, .e) orch_report_perclass(.tab = .t, .engine = .e, .label_col = "AmendType")
)
```

The same three engines in one row each, with the aggregate measures beside each other. Macro and
micro answer different questions and the gap between them is the finding: micro weights every document
equally and therefore reports the largest categories, macro weights every category equally and reports
the problem this study is actually solving, where the smallest class has under forty documents.

```{r}
#| label: headline-all
#| results: asis
headlines <- purrr::map(panels, orch_headline)
purrr::iwalk(headlines, \(.h, .t) orch_report_headline(.tab = .h, .label_col = .t))
```

# Section 2: Perfect routing

A router can only relabel a document to something an engine already said. Taking the correct answer
wherever any engine supplied one is therefore an upper bound on every rule at once, at every threshold
and in every order.

It uses the truth to choose and nobody can run it. Its job is to bound the two sections that follow:
where the ceiling sits at the transformer's own accuracy there is nothing to find, and no clue however
clever can find it.

```{r}
#| label: ceiling-all
#| results: asis
# The transformer first because it is the baseline, then the cheap arm, then the expensive one. The
# order matters for the marginal column: it answers what each engine adds OVER what is already there,
# which is the deployment question rather than the ranking one.
ceilings <- purrr::imap(panels, function(.p, .t) {
  base_ <- baselines$Baseline[baselines$Task == .t]
  orch_ceiling(
    .tab   = .p,                                                  # the panel
    # The engine that ships goes first, because every gain below is measured against it. The rest
    # follow cheapest-first, so the generative arm's marginal row answers what it adds over a corpus
    # pass that has already happened.
    .order = c(base_, setdiff(orch_engines(.tab = .p), base_))
  )
})

purrr::iwalk(ceilings, \(.c, .t) orch_report_ceiling(.tab = .c, .label_col = .t))
```

# Section 3: Low transformer confidence

The first clue anyone would reach for, and the free one: the transformer already emits a probability,
and 03B showed it separates errors. So take the documents it is least sure about and hand them to
another arm.

The thresholds look high because the distribution is. The softmax is massed against one, so a floor at
0.90 selects a few per cent of the corpus rather than a tenth of it -- and a conventional-looking grid
stopping at 0.95 would test almost nothing and report a null earned by the size of the subset rather
than by anything about the arms.

Read `BertAcc` against `ArmAcc`: both are measured on the same documents and are directly comparable.
`SubsetAccAfter` asks whether the swap helped those documents; `OverallAccAfter` asks whether it was
worth doing. `Fixed` against `Broke` is the pair that says why.

```{r}
#| label: resolve-confidence
resolve_conf <- purrr::imap(panels, function(.p, .t) {
  base_  <- baselines$Baseline[baselines$Task == .t]
  # Every engine except the one that ships, INCLUDING the other context length: sending the documents
  # the crowned window is unsure about to the other window is a rule like any other, and it is the one
  # a reader would ask about first given both are already measured.
  chall_ <- setdiff(orch_engines(.tab = .p), base_)
  purrr::map(chall_, function(.e) {
    orch_resolve_conf(
      .tab        = .p,                     # the panel
      .engine     = .e,                     # the arm swapped in
      .baseline   = base_,                  # whose probability defines the subsets
      .thresholds = .lP$Param$Thresholds    # a document is in the subset below the value
    ) |>
      dplyr::mutate(Engine = .e, .before = 1)
  }) |>
    purrr::set_names(chall_)
})
```

## Detailed

```{r}
#| label: resolve-conf-detailed
#| results: asis
purrr::iwalk(
  .x = resolve_conf$ClassDetailed,                                    # one table per arm
  .f = \(.t, .e) orch_report_swap(.tab = .t, .engine = .e, .label_col = "ClassDetailed")
)
```

## Broad

```{r}
#| label: resolve-conf-broad
#| results: asis
purrr::iwalk(
  .x = resolve_conf$ClassBroad,                                    # one table per arm
  .f = \(.t, .e) orch_report_swap(.tab = .t, .engine = .e, .label_col = "ClassBroad")
)
```

## Amendment

```{r}
#| label: resolve-conf-amendment
#| results: asis
purrr::iwalk(
  .x = resolve_conf$AmendType,                                    # one table per arm
  .f = \(.t, .e) orch_report_swap(.tab = .t, .engine = .e, .label_col = "AmendType")
)
```

# Section 4: Broad and detailed disagree

A second clue, independent of the first and of the keyword arm entirely. Two transformers were trained
on the same folds: one predicts the detailed category, the other the broad one. Roll the detailed
prediction up to its parent and the two can be compared. Where they disagree, one of them is wrong
about the same document, and **that is visible without any label.**

It also reaches documents the first clue cannot. The lexicon is silent on roughly half the corpus; the
broad model answers on all of it.

This is not the tautology it looks like. 03B publishes the broad label by rolling up the detailed
prediction, so the *released* output is consistent by construction. The broad **model** still exists,
still made its own prediction, and still disagrees. That disagreement is what is measured here.

The section covers the detailed task only. `AmendType` has no hierarchy to be inconsistent with.

```{r}
#| label: hierarchy-flag
#| results: asis
# The two levels can ship different context lengths -- 03B crowns per task -- so each side names its
# own baseline rather than assuming they match.
base_det   <- baselines$Baseline[baselines$Task == "ClassDetailed"]
base_broad <- baselines$Baseline[baselines$Task == "ClassBroad"]

panel_hier <- orch_add_hierarchy(
  .panel_det   = panels$ClassDetailed, # the labels under test
  .panel_broad = panels$ClassBroad,    # the independent second opinion
  .tab_prep    = tab_prep,             # supplies the detailed-to-broad mapping
  .base_det    = base_det,             # the detailed engine that ships
  .base_broad  = base_broad            # the broad engine that ships
)

orch_report_hierarchy_split(.tab = orch_hierarchy_split(.tab = panel_hier))
```

If the detailed label is markedly less accurate where the broad model disagrees, the clue has found
documents worth a second opinion. Whether another arm can supply one is the next table.

```{r}
#| label: resolve-hierarchy
#| results: asis
resolve_hier <- purrr::map(
  .x = setdiff(orch_engines(.tab = panel_hier), base_det),
  .f = \(.e) orch_resolve_hier(.tab = panel_hier, .engine = .e, .baseline = base_det) |>
    dplyr::mutate(Engine = .e, .before = 1)
) |>
  purrr::list_rbind()

orch_report_swap(.tab = resolve_hier, .engine = "each arm", .label_col = "ClassDetailed")
```

# Overview

Everything above as figures. Nothing here is new.

## Per-category F1, engine by engine

```{r}
#| label: fig-perclass-detailed
#| fig-height: !expr plot_height(2 + 1.5 * (nrow(perclass$ClassDetailed[[1]]) - 1))
#| fig-cap: "F1 by category and engine, detailed taxonomy. Abstention counts as a miss, so an arm
#|   that declines on half the corpus scores low here whatever its precision on the rest."
orch_plot_perclass(.tabs = perclass$ClassDetailed, .key = "ClassDetailed")
```

```{r}
#| label: fig-perclass-broad
#| fig-height: !expr plot_height(2 + 1.5 * (nrow(perclass$ClassBroad[[1]]) - 1))
#| fig-cap: "F1 by category and engine, broad taxonomy."
orch_plot_perclass(.tabs = perclass$ClassBroad, .key = "ClassBroad")
```

```{r}
#| label: fig-perclass-amendment
#| fig-height: !expr plot_height(2 + 1.5 * (nrow(perclass$AmendType[[1]]) - 1))
#| fig-cap: "F1 by category and engine, amendment task."
orch_plot_perclass(.tabs = perclass$AmendType, .key = "AmendType")
```

## The ceiling

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-ceiling-detailed
#| fig-height: !expr plot_height(3)
#| fig-cap: "Accuracy a perfect router would reach as each engine is added, detailed taxonomy. The
#|   dashed line is the transformer alone. Every rule is bounded by the top of this line."
orch_plot_ceiling(
  .tab  = ceilings$ClassDetailed,
  .base = headlines$ClassDetailed$Accuracy[
    headlines$ClassDetailed$Engine == baselines$Baseline[baselines$Task == "ClassDetailed"]
  ]
)
```

### Broad

```{r}
#| label: fig-ceiling-broad
#| fig-height: !expr plot_height(3)
#| fig-cap: "The routing ceiling, broad taxonomy."
orch_plot_ceiling(
  .tab  = ceilings$ClassBroad,
  .base = headlines$ClassBroad$Accuracy[
    headlines$ClassBroad$Engine == baselines$Baseline[baselines$Task == "ClassBroad"]
  ]
)
```

### Amendment

```{r}
#| label: fig-ceiling-amendment
#| fig-height: !expr plot_height(3)
#| fig-cap: "The routing ceiling, amendment task."
orch_plot_ceiling(
  .tab  = ceilings$AmendType,
  .base = headlines$AmendType$Accuracy[
    headlines$AmendType$Engine == baselines$Baseline[baselines$Task == "AmendType"]
  ]
)
```

:::

## What each swap would do to the corpus

Plotted as a change rather than a level. The quantity of interest is a fraction of a percentage point
against a baseline above ninety, so on an accuracy axis every line would be flat and identical. Zero is
the transformer, above it is better, below it is worse.

::: {.panel-tabset}

### Detailed

```{r}
#| label: fig-resolve-detailed
#| fig-height: !expr plot_height(5)
#| fig-cap: "Change in corpus accuracy from swapping in each arm below a confidence threshold,
#|   detailed taxonomy. A line below zero at every threshold means the swap never pays."
orch_plot_resolve(.tab = purrr::list_rbind(resolve_conf$ClassDetailed))
```

### Broad

```{r}
#| label: fig-resolve-broad
#| fig-height: !expr plot_height(5)
#| fig-cap: "Change in corpus accuracy from swapping, broad taxonomy."
orch_plot_resolve(.tab = purrr::list_rbind(resolve_conf$ClassBroad))
```

### Amendment

```{r}
#| label: fig-resolve-amendment
#| fig-height: !expr plot_height(5)
#| fig-cap: "Change in corpus accuracy from swapping, amendment task."
orch_plot_resolve(.tab = purrr::list_rbind(resolve_conf$AmendType))
```

:::

# Next

This document writes no artifacts. It is a measurement, and what to do with it is the next decision.
If no clue finds documents worth rerouting, 03F applies the crowned models directly and needs nothing
from here. If one does, the rule it implies is small enough to state in a sentence and 03F would carry
it as a parameter rather than as a manifest.

Whether the per-document agreement between engines is worth shipping as a reliability flag beside the
released labels is a separate question, raised by the same tables and settled separately.
