---
title: "Contract Classification -- Sample & Shared Tooling (03A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = FALSE, warning = FALSE)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Initialize.R", encoding = "UTF-8")
source("1_code/_Utils.R", encoding = "UTF-8")
source("1_code/_Format.R", encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(here::here(), .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(here::here(), .name_script))
source(.path_fun)
```

# What 03A is

03A is the **foundation** of the classification pipeline. It does two jobs and
nothing else:

1. **Build the one prepared sample.** It reads the labelled documents, deals a
   frozen stratified k-fold split, and writes a single `prepared.parquet` that
   *every* downstream method consumes. The folds are dealt here, once, so BERT
   (03B) and keyword (03C) are scored on byte-for-byte identical splits.
2. **Provide the shared "overall" tooling.** A single scoring / leaderboard /
   plotting layer that every method reports through -- BERT, keyword, the 03D
   router, and the 03E deployment. Because all methods emit the same
   `predictions.parquet` schema on the same folds, scoring them head-to-head is
   just a matter of pooling predictions and calling the same functions.

The trainers do **not** live here. `bert_*` (the BERT wrapper) is 03B; `kw_*`
(the keyword miner) is 03C; both `source()` this file for prep and scoring so the
splits never drift.

Two deliberate simplifications over the earlier two-track code:

- **One prepared parquet, not two.** `clf_prepare_sample` now carries `DocDesc` /
  `DocName`, so there is a single prepared table. BERT ignores the title column;
  keyword mines it. (The old `kw_write_prepared` re-attach step is gone.)
- **One scoring layer, not `clf_` + `kw_`.** `clf_perclass` / `clf_scores` take a
  `.none` sentinel argument and are abstention-aware. With no abstention (BERT)
  they reduce *exactly* to the previous behaviour; with abstention (keyword
  `(none)`) they drop the sentinel and report `Coverage`.

## Path Tree

`prepared.parquet` is written into 03A's own output directory; 03B and 03C read
it from there. The two runs roots are referenced only so the overview / plot
helpers can be demonstrated once those sweeps have produced runs.

```{r}
.lP <- list(
  Input = list(
    ClassificationSample = "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MaterialContractClassification/DocumentClassification/02-AK_classification_comparison/final_classification.csv",
    MetaData = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    DirContracts = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/"
  ),
  Cache = list(
    ContractFiles = utils_file_path(.dir_main, "Cache", "ContractFiles.parquet")
  ),
  Output = list(
    Prepared = utils_file_path(.dir_main, "prepared.parquet")
  ),
  Runs = list(
    Bert = here::here("2_output", "03B-ClassifyTrainBERT", "runs"),
    Kw   = here::here("2_output", "03C-ClassifyTrainKeyword", "runs")
  )
)
```

## Load Sample

Labels come from `final_classification.csv` -- the reconciled Schema-1 /
Schema-2 label spine, carrying `Provenance` for `LabelRound`, `DocClassFinal2`
for the dual-class second label, and `AmendType` for the amendment task. It is
read from Ann-Kristin's shared folder as a CSV; the schema is the same one the
pipeline has always consumed, so nothing downstream changes.

`DocDesc` / `DocName` (the filer title and filename) join in from the metadata and
ride all the way into the prepared parquet for the keyword track. `Path` locates
each document's parsed text.

```{r}
fils_contract <- utils_list_project_files(.lP$Input$DirContracts, .lP$Cache$ContractFiles, FALSE)
fils_class_sample <- readr::read_csv(
  .lP$Input$ClassificationSample,
  col_types = readr::cols(.default = readr::col_character(),
                          DualClass = readr::col_integer())
) |>
  dplyr::select(DocID, AmendType, DocClassFinal1, DocClassFinal2, DualClass, Level1, Level2, Provenance) |>
  dplyr::left_join(
    y = arrow::open_dataset(.lP$Input$MetaData) |>
      dplyr::select(DocID, DocDesc, DocName) |>
      dplyr::collect(),
    by = dplyr::join_by(DocID)
  ) |>
  dplyr::left_join(fils_contract, by = dplyr::join_by(DocID))
```

Read with `readr`, not `arrow::open_dataset(format = "csv")`. Arrow's
`strings_can_be_null` convert option defaults to `FALSE`, so a bare `NA` in a
character column arrives as the literal two-letter string rather than a missing
value -- which silently turns the unresolved documents into a thirteenth class
and makes every document look dual-classified. `readr` treats `""` and `NA` as
missing by default. The file is 4.4k rows, so the lazy Arrow pipeline bought
nothing here in any case.

## Prepare Sample

The full combined sample (Round1 + Round2). Emits `ClassBroad` (7),
`ClassDetailed` (12), `ClassDetailed2` (dual-class second label, NA for
single-class docs), `AmendType`, `LabelRound`, `DocDesc`, `DocName`, and the
frozen `Fold`. Training downstream is single-label on the primary; the second
label is used only for lenient scoring.

```{r}
tab_prep <- clf_prepare_sample(
  .tab_input = fils_class_sample,
  .k         = 5L,
  .seed      = 42L
)
clf_write_prepared(tab_prep, .lP$Output$Prepared)
```

`.path_labels` is not passed: it exists only as a fallback to join `Provenance`
when the input lacks it, and the label spine always carries it. Leaving it in
would be a latent bug, since that fallback reads its path with
`arrow::read_parquet()` and the spine is now a CSV.

# The labelled sample

This is the data-resource description -- the tables and figures that document what
we are classifying. (Tables here use `knitr::kable`; pipe them through your
`plot_htmltable()` from the shared plot utils for the Times-styled look.)

## Composition

```{r}
clf_sample_composition(tab_prep) |>
  fmt_table(.caption = "Labelled sample composition")
```

`Round2` are the manually-checked gold labels; `Round1` are the first-pass
automated labels that bulk out the common classes. Four fine classes (R&D,
Customer / Supplier, Investment and Merger, Peer Agreements) exist only in Round2,
which automated Round1 cannot express -- a structural recall limit we watch rather
than fix here.

## Class distribution

```{r}
clf_class_distribution(tab_prep, "ClassBroad") |>
  fmt_table(.caption = "Broad taxonomy (7 classes)", .pct = "Pct")
```

```{r}
clf_class_distribution(tab_prep, "ClassDetailed") |>
  fmt_table(.caption = "Detailed taxonomy (12 classes)", .pct = "Pct")
```

```{r}
#| fig-cap: "Detailed-taxonomy class distribution."
clf_plot_class_distribution(tab_prep, "ClassDetailed")
```

The imbalance is steep -- Employment classes and Credit dominate, while R&D and
Peer Agreements sit an order of magnitude below them. This is exactly why we
report macro-F1 (which weights every class equally) alongside accuracy, and why
per-class scoring matters.

## Amended vs Original

The amendment task is a **separate binary label** (`AmendType`: Original vs
Amended), orthogonal to the contract-type taxonomy. It now covers the **entire**
labelled sample: the reconciliation takes `AmendType` from the live labelling log
rather than the periodic parquet export, so documents classified after the last
export no longer show a spurious `NA`. The `.include_na = TRUE` calls below are
kept as a regression check -- an unlabeled row reappearing would mean the label
spine has drifted, not that the task shrank.

```{r}
clf_class_distribution(tab_prep, "AmendType", .include_na = TRUE) |>
  dplyr::mutate(Pct = scales::percent(Pct, 0.1)) |>
  knitr::kable(caption = "Amendment task (Original vs Amended, with unlabeled)",
               format.args = list(big.mark = ","))
```

```{r}
#| fig-cap: "Amendment task distribution."
#| fig-height: 2.6
clf_plot_class_distribution(tab_prep, "AmendType", .include_na = TRUE)
```

The same breakdown by round, which should now be a clean two-column table:

```{r}
tab_prep |>
  dplyr::mutate(AmendType = dplyr::coalesce(.data$AmendType, "(unlabeled)")) |>
  dplyr::count(.data$LabelRound, .data$AmendType) |>
  tidyr::pivot_wider(names_from = "AmendType", values_from = "n", values_fill = 0L) |>
  knitr::kable(caption = "Amendment label by round")
```

Amendment is decisively a BERT task: "amended and restated" appears as a naming
convention in genuine originals, so a keyword rule cannot separate the classes
(keyword macro-F1 ~0.62 vs BERT ~0.86). That is settled; the point here is only to
quantify how much of the corpus carries a usable amendment label.

## Dual-class labels

A small minority of docs carry a **second valid label** (`ClassDetailed2`). This
section changed materially in the last revision and the distinction matters for
how the headline scores read.

Previously the two labels were treated as co-equal, and `ClassDetailed` was
whichever one the reconciliation happened to list first -- an alphabetical
accident, not a judgement. Every dual-classified document has since been through
a **manual review pass**: a worklist naming both categories, with the intended
primary filled in by hand. `ClassDetailed` is now that reviewed primary and
`ClassDetailed2` the secondary. Three-quarters of the reviewed documents had the
order reversed, so this is a correction, not a formality.

We still train and predict **single-label** on the primary. The consequence of
the review is that strict scoring is no longer a conservative lower bound
covering for an arbitrary pick -- it is scoring against the answer a human chose.
Lenient scoring becomes a genuine robustness check on taxonomic ambiguity rather
than a correction for our own bookkeeping.

```{r}
clf_dual_class_overview(tab_prep) |>
  dplyr::mutate(PctDual = scales::percent(PctDual, 0.1)) |>
  knitr::kable(caption = "Dual-class docs: count, share, Round split",
               format.args = list(big.mark = ","))
```

By construction dual labels sit in **Round2** (automated Round1 emits a single
label), so the entire strict-vs-lenient gap lives in the manually-checked subset.

Which class pairs co-occur. Direction is now meaningful, so these are reported as
primary -> secondary rather than as unordered sets:

```{r}
clf_dual_class_pairs(tab_prep) |>
  knitr::kable(caption = "Dual-class documents by primary -> secondary category",
               format.args = list(big.mark = ","))
```

These are taxonomically adjacent contract types -- the cases where a single
document genuinely spans two categories. The directional view is worth reading
alongside the review itself: where one direction dominates a pair heavily, the
reviewer was applying a consistent rule about which category leads, which is
precisely the kind of decision the earlier alphabetical ordering was destroying.
The per-class strict-vs-lenient plot in the scoring section then reads as a
diagnostic of which classes carry residual ambiguity.

## Document length

```{r}
clf_length_summary(tab_prep) |>
  knitr::kable(
    caption = "Document length in words (~200w ~ 256 tokens, ~400w ~ 512 tokens)",
    digits = c(0, 0, 0, 0, 3, 3), format.args = list(big.mark = ",")
  )
```

Contracts are long: the median runs to thousands of words, and the large majority
exceed both the 256- and 512-token windows. At 512 tokens a transformer sees only
the opening pages, which motivates the 256-vs-512 axis in the BERT sweep and the
(conditional) long-context probe. Contract *type*, though, is usually legible from
the title and preamble -- which is the bet the whole pipeline rests on.

## Fold balance

The frozen folds, dealt once here. Stratified on `ClassDetailed` and reused for
`ClassBroad` and `AmendType`, so all three tasks share splits.

```{r}
clf_fold_overview(tab_prep, "ClassDetailed") |>
  knitr::kable(caption = "Per-fold counts -- detailed taxonomy")
```

```{r}
clf_fold_overview(tab_prep, "AmendType") |>
  knitr::kable(caption = "Per-fold counts -- amendment task")
```

## Missing data

A full missingness audit across the prepared columns. Two kinds of NA appear, and
telling them apart is the whole point.

```{r}
clf_na_overview(tab_prep) |>
  fmt_table(.caption = "Missingness by column", .pct = "PctNA")
```

- **`ClassDetailed2`** is NA for every single-class doc -- the large majority. That
  is the *definition* of a single-class doc, not missing data; it is exactly the
  complement of the dual-class count above.
- **`AmendType`** should now be NA-free. The reconciliation sources it from the
  labelling log rather than the periodic parquet export, and the handful of
  documents that still lack it are unresolved ones, which never survive the label
  filter. A nonzero count here means the spine has drifted.
- **`LabelRound`** NA, if any, flags a doc whose provenance was neither Round1 nor
  Round2 -- worth a look, since every labelled doc should map to one.
- **`DocDesc` / `DocName`** never go NA (prep coalesces them to `""`), but an empty
  title surfaces as `nEmpty` -- those are the docs where the keyword docdesc model
  abstains.
- **`ClassBroad` / `ClassDetailed` / `Text` / `Fold`** are NA-free by construction.
  A nonzero count in any of these would signal an upstream problem, not a labelling
  gap.

# Shared scoring tooling

Every method -- BERT, keyword, the router -- writes the **same**
`predictions.parquet`: `DocID, TrueLabel, PredLabel, Score, Fold`. Scoring is
therefore method-agnostic. The one wrinkle is abstention: a keyword model can
return `(none)` when no term fires, whereas BERT always predicts. The unified
layer handles both through a single `.none` argument -- absent from BERT's labels,
so the abstention logic is a no-op there.

A small synthetic example makes the behaviour concrete (and lets this section
render before any real runs exist). It includes two abstentions and one dual-class
document whose "wrong-looking" prediction is in fact its valid second label.

```{r}
demo_pred <- tibble::tribble(
  ~DocID, ~TrueLabel,  ~PredLabel,  ~Score, ~ClassDetailed2,
  "d01",  "Leases",    "Leases",    0.95,   NA,
  "d02",  "Leases",    "Leases",    0.88,   NA,
  "d03",  "Leases",    "Licenses",  0.41,   "Licenses",
  "d04",  "Licenses",  "Licenses",  0.79,   NA,
  "d05",  "Licenses",  "(none)",    0.00,   NA,
  "d06",  "Licenses",  "Licenses",  0.66,   NA,
  "d07",  "R&D",       "R&D",       0.71,   NA,
  "d08",  "R&D",       "(none)",    0.00,   NA,
  "d09",  "Other",     "Other",     0.83,   NA,
  "d10",  "Other",     "Leases",    0.52,   NA,
  "d11",  "Other",     "Other",     0.77,   NA,
  "d12",  "R&D",       "Other",     0.45,   NA
)
```

**Headline scores, strict vs lenient.** Strict scores the primary label only;
lenient also accepts a dual-class doc's second label. `Coverage` is the predicted
share (here below 1 because of the two abstentions); a method that always predicts
would show `Coverage = 1`.

```{r}
dplyr::bind_rows(
  clf_scores(demo_pred, .lenient = FALSE),
  clf_scores(demo_pred, .lenient = TRUE)
) |>
  knitr::kable(caption = "Headline scores (synthetic)", digits = 3)
```

**Per-class precision / recall / F1.** The `(none)` sentinel is excluded from the
class set; an abstention costs the true class recall but never creates a false
positive.

```{r}
clf_perclass(demo_pred, .lenient = FALSE) |>
  knitr::kable(caption = "Per-class, strict (synthetic)", digits = 3)
```

**Confusion matrix.** A `(none)` column, when present, shows exactly which true
classes the method abstained on.

```{r}
clf_confusion(demo_pred) |>
  knitr::kable(caption = "Confusion matrix (synthetic)")
```

**Plots.** The same data through the publication plot helpers. These are the
method-agnostic figures 03B / 03C / 03D / 03E reuse unchanged.

```{r}
#| fig-cap: "Per-class F1 (synthetic)."
clf_plot_perclass(demo_pred)
```

```{r}
#| fig-cap: "Confusion heatmap, row-normalised (synthetic)."
#| fig-height: 4
clf_plot_confusion(demo_pred, .normalize = TRUE)
```

```{r}
#| fig-cap: "Strict vs lenient per-class F1; the gap is the dual-class cost (synthetic)."
#| fig-height: 3.5
clf_plot_strict_lenient(demo_pred)
```

# Overview across runs

This is where 03B and 03C plug in. `clf_load_overall` binds the per-run metrics
across one or more runs roots (BERT and keyword live in separate trees);
`clf_leaderboard` / `clf_leaderboard_show` rank configurations head-to-head, keyed
on `ConfigName` (which encodes every axis, so the same leaderboard handles both
methods); `clf_effect` reads off the marginal effect of any single axis. Against
real runs the load is one line:

```r
tab_overall <- clf_load_overall(c(.lP$Runs$Bert, .lP$Runs$Kw))
```

No sweeps have run yet, so to show what the final output looks like the block
below **fabricates** a small but realistic `tab_overall` -- four BERT configs and
one keyword config, five folds each. Everything downstream of it is the real code;
only the inputs are synthetic. (Note the keyword config's `Coverage` below 1, where
BERT sits at exactly 1.)

```{r}
# Synthetic stand-in for clf_load_overall() output -- illustrative only.
set.seed(42)
config_grid <- tibble::tribble(
  ~ConfigName,                 ~Model,         ~TextCol,   ~Source,    ~MaxLen, ~Epochs, ~LR,    ~F1Base, ~CovBase,
  "legalbert_ml512_e6_lr2e5",  "legal-bert",   "Text",     NA,         512L,    6L,      "2e-5", 0.852,   1.00,
  "legalbert_ml256_e6_lr2e5",  "legal-bert",   "Text",     NA,         256L,    6L,      "2e-5", 0.849,   1.00,
  "legalbert_ml512_e3_lr2e5",  "legal-bert",   "Text",     NA,         512L,    3L,      "2e-5", 0.831,   1.00,
  "roberta_ml512_e6_lr2e5",    "roberta-base", "Text",     NA,         512L,    6L,      "2e-5", 0.808,   1.00,
  "keyword_combined_none",     "keyword",      "combined", "combined", NA,      NA,      NA,     0.712,   0.93
)

tab_overall <- config_grid |>
  tidyr::expand_grid(Fold = 1:5) |>
  dplyr::mutate(
    LabelCol    = "ClassDetailed",
    Seed        = 42L,
    Smoke       = FALSE,
    F1_macro    = pmin(0.98, pmax(0.20, .data$F1Base + stats::rnorm(dplyr::n(), 0, 0.015))),
    F1_weighted = pmin(0.99, .data$F1_macro + abs(stats::rnorm(dplyr::n(), 0.030, 0.006))),
    Accuracy    = pmin(0.99, .data$F1_weighted + abs(stats::rnorm(dplyr::n(), 0.015, 0.005))),
    Coverage    = dplyr::if_else(
      .data$CovBase >= 1, 1.0,
      pmin(1.0, pmax(0, .data$CovBase + stats::rnorm(dplyr::n(), 0, 0.010)))
    )
  ) |>
  dplyr::select(-F1Base, -CovBase)
```

**Leaderboard.** One row per configuration, ranked by mean macro-F1, with Coverage
and mean +/- sd across folds. legal-bert leads; the keyword config trails and
abstains on a few percent of docs.

```{r}
clf_leaderboard_show(tab_overall, .label_col = "ClassDetailed", .n = 15L) |>
  knitr::kable(caption = "Top configurations -- detailed taxonomy (synthetic)")
```

```{r}
#| fig-cap: "Leaderboard: macro-F1 (mean +/- sd across folds) per configuration (synthetic)."
clf_plot_leaderboard(tab_overall, .label_col = "ClassDetailed", .n = 15L)
```

**Marginal effect of one axis.** `clf_effect` averages over everything else; rows
where the axis is NA (the keyword config has no `MaxLen`) drop out automatically,
so it is safe to run on a pooled BERT + keyword table.

```{r}
clf_effect(tab_overall, "Model", .label_col = "ClassDetailed") |>
  knitr::kable(caption = "Macro-F1 by model, averaged over other axes (synthetic)", digits = 3)
```

Against real runs, replace the synthetic block with the one-line `clf_load_overall`
call above, then pool the winning config's out-of-fold predictions --
`clf_pool_predictions(c(.lP$Runs$Bert, .lP$Runs$Kw), best_config)` -- to drive the
per-class and confusion plots shown earlier in the scoring section.

# Next

03A defines the seam and the tooling. 03B, 03C and 03D are built; 03E is not.

This render is a **cold start**: the label spine changed, so `prepared.parquet`
and its folds are new and every downstream artifact keyed to the old labels has
been discarded. Two of those are worth naming, because neither fails loudly:

- **`2_output/_cache/`** -- `clf_cache()` is keyed on a name, not on the data
  behind it, so a warm cache silently serves pre-review results.
- **`2_output/03B-ClassifyTrainBERT/runs/`** -- `bert_run_key()` is built from
  hyperparameters only, with no data path or hash, so `bert_sweep()` would mark
  every old run `Done` and train nothing. The folds underneath those runs no
  longer exist either.

Once the sweep is re-run:

- **03B-ClassifyTrainBERT** -- re-crown on the new labels, then `bert_fit_final()`
  for the deployable all-data model.
- **03C-ClassifyTrainKeyword** -- re-run the miner sweep (cheap; no GPU fits).
- **03D-ClassifyOrchestrate** -- re-run the router comparison against the new
  leaderboard.
- **03E** -- apply the final model to the full corpus. Not yet written.
