---
title: "Entity Release -- Resolving the Corpus Store into Variables (04E)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: 03A
# aliases the table helpers at SOURCE time, so sourcing it first throws part-way through the file.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A supplies the console formatter and the text reader; 04A the entity vocabularies; 04B the
# policy reader, the anchor helpers and the date cleaner; 04C every resolver this document applies;
# 04D the corpus index. Nothing here re-implements any of them: the corpus is resolved by the code
# the sample was validated with, pointed at documents that carry no labels.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract", "04B-EntityMeasure",
         "04C-EntityResolve", "04D-EntityApply"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04E-EntityRelease.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04D extracted every engine over the whole corpus into one candidate store and resolved nothing. This
document reads that store, assigns a role to each span from the rules 04B measured, collapses the
roles into the four variables the paper reports, and writes one row per contract.

## It is 04C at corpus scale, and deliberately the same code

Every resolver here is sourced from 04C: the role assignment, the tie-break, the party
deduplication, the duration comparison. What this document adds is chunking and the absence of
labels. A corpus resolved by a second implementation would agree with 04C at the third decimal and
disagree somewhere that mattered, with nothing to report which.

## The window lives here now, and that is the point

04D reads full text, so the window is a filter over the offsets in the store rather than a decision
taken at extraction. It can be imposed, revised or withdrawn against evidence that does not exist
yet. The policy still carries `CapChars` and `TailChars`, and this document still honours them --
they are simply no longer irreversible.

## What is still open

The role rules came from reading sessions rather than from measurement. The tie-break between
competing cues was rewritten once, and the rewrite refuted the reason it was made while earning its
place on other grounds. The expiry cue set reaches a date in well under half the corpus even reading
every character. None of that is settled, and none of it requires re-extracting anything to change:
this document is cheap to re-run, which is what splitting it from 04D bought.

## What nothing here establishes

That the variables are right. The anchors confirm that the filer appears among the resolved parties
and that the contract date precedes its filing, which shows the extraction finds real things. It does
not show that a party count of three is three. That needs a document-level gold set of fifty to
eighty contracts, and it is the one piece of this family that cannot be built from EDGAR facts or a
reading session.

# Configuration

```{r}
#| label: configure-paths
.dir_apply   <- init_create_script_dir(.dir_here = here::here(), .name_script = "04D-EntityApply")
.dir_measure <- init_create_script_dir(.dir_here = here::here(), .name_script = "04B-EntityMeasure")

.lP <- list(
  Input = list(
    Store  = fs::path(.dir_apply, "Store", "CorpusCandidates.duckdb"), # written by 04D
    Index  = fs::path(.dir_apply, "Cache", "CorpusFiles.parquet"),     # DocID, Path and EDGAR facts
    Policy = fs::path(.dir_measure, "extraction_policy.parquet"),      # written by 04B
    Kept   = fs::path(.dir_measure, "rules_kept.parquet")              # written by 04B
  ),
  Output = list(
    Vars = utils_file_path(.dir_main, "variables")   # one row per contract, chunked
  ),
  Work = list(
    Dir = utils_file_path(.dir_main, "Work")         # per-chunk text parquet, deleted as consumed
  ),
  Param = list(
    ChunkSize = 2000L,   # documents resolved at once
    CtxMax    = 400L,    # context width the rules are matched in, as 04B scored them
    HeadPos   = 0.10,    # an uncued organisation this far in still reads as a party
    RedactGap = 200L,    # markers closer than this belong to one withheld thing
    Tiebreak  = "proximity",  # nearest cue wins; see ent_assign_roles() in 04C
    Limit     = 2000L    # an integer rehearses; NULL releases
  )
)

# The same formats 04B parsed with and 04C resolved with, written out rather than sourced so that a
# change in one is visibly a change in all.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", "%b %d, %Y", "%b %d %Y",
  "%d %B, %Y", "%d %B %Y", "%d %b, %Y", "%d %b %Y",
  "%m/%d/%Y",  "%d/%m/%Y", "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d", "%d-%b-%Y", "%m.%d.%Y"
)

fs::file_exists(unlist(.lP$Input))
```

# Next

This is the release. What follows it is the paper, and three things belong in it as limitations
rather than being discovered by a reader: money is unvalidated because EDGAR records no contract
value, the contract term is thin because seven expiry cues cannot reach most contracts' term
clauses, and nothing validates the variables themselves without a gold set.
