---
title: "Entity Measurement -- Scoring Engines and Rules Against EDGAR (04B)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: 03A
# registers its category vocabulary and aliases the table helpers at SOURCE time, not inside a
# function, so sourcing it first throws part-way through the file and every function defined below
# the failure silently never exists.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the console formatter and the contract-type vocabulary; 04A owns the sample, the store
# and the entity vocabularies (Label, Combo) that every figure here orders its axes by. Sourcing
# both rather than re-registering is what keeps an entity figure in this document and one in 04A
# from ordering the same axis two ways.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script # resolves to 1_code/04B-EntityMeasure.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A extracted 7.4 million candidates and declined to rank anything, because ranking needs labels and
there are no entity labels. This document supplies the missing judge, and it does so without
annotation.

For every contract, EDGAR records the filer's name, the filing date and the registered addresses.
None was derived from the contract text, and each identifies **an entity that must be present**: a
company is a party to its own contract, a contract cannot be signed after it is filed, and a filer's
registered address is a place the contract has reason to name. That is enough to score an engine's
recall, to score a proposed rule, and to choose an extraction window.

## What the anchor is, and what it is not

One known-true entity per document, not a complete labelling. A span that fails to match the anchor
is **unlabelled, not wrong** -- most organisations in a contract are counterparties, agents and third
parties EDGAR never recorded.

The two directions therefore mean different things, and conflating them would be the easiest mistake
to make here:

- **Recall against the anchor is exact.** An engine that never proposes the filer's own name did not
  find it. No hedging is needed and none is offered.
- **Precision against the anchor is a lower bound.** A rule keeping ten spans of which one is the
  filer might have kept nine counterparties or nine street names, and this document cannot tell them
  apart. It behaves well for *ranking* rules against each other and badly as a level.

## Roles the anchor speaks to, and in which direction

The filer is a party, and that cuts two ways. A `party` cue should concentrate on it -- but an
`agent`, `regulator` or `statutory` cue should **avoid** it. "Act of 1933" is never a contract's own
date; a company is not its own administrative agent; an expiry date falls after the filing while the
anchor requires one at or before it.

So roles are judged in a direction. For `high` roles the pass condition is lift above the base rate;
for `low` roles it is lift near zero. The second is falsification rather than confirmation, and the
verdict says so -- a regulator cue scoring near zero has been shown not to fire on parties, which is
weaker than being shown correct. It still removes mislabelled rules, which is most of what is wanted
from a set nobody has validated.

Three groups stay outside the frame in either direction. An `affiliate` shares the filer's name, so
the anchor matches it and high lift means nothing. `governing_law` is Delaware about as often as the
state of incorporation is. Money has no anchor at all.

Stops are judged universally wherever the label has an anchor: a stop asserts that a span is never
the entity, so a single anchor it kills refutes it outright.

## Addresses are stored in codes, not names

EDGAR writes an address as street, city, **state code**, ZIP -- `ABBOTT PARK IL 60064`,
`THE WOODLANDS TX 77380`. Contracts write "the State of Illinois". A containment test between the
two can only ever fire through the city, so every state a contract names is invisible to it, and
states are most of what a contract names geographically.

`ent_expand_states()` appends the implied names before the test. The code is located by the ZIP that
follows it rather than as a bare token, because bare two-letter tokens are unsafe here -- IN, OR,
OK, ME, LA and DE are ordinary words, and ST, FL and PO occur in street lines.

## Which fold, and why it differs between sections

The reading session read folds 1 to 4, so its rules are scored on fold 5 alone. Engine recall
involves no rules and cannot have been taught, so it uses all 4,398 documents and is the more precise
for it. The two are reported separately and never averaged.

## Money is absent from most of this document, but not from all of it

EDGAR records no contract value. There is no anchor, so nothing in the engine table, the rule table
or the window grid can be computed for it, and it is omitted rather than filled with zeros that would
read as failure. Most of the 64 money cues are carried through unscored.

One channel remains, and it carries the engine decision. A redacted amount leaves a bracketed marker
where the figure used to be, so whether an engine proposes a span *there* is a capability that can
be tested without any label at all -- and it is the case that matters most, because a figure is
withheld precisely when it is commercially material. The policy records the money engine with a
`Basis` of `measured: proxy`, distinguishing it in the artifact from a recall ranking on one side
and a bare assertion on the other.

# Configuration

```{r}
#| label: configure-paths
# The bundle root, and the folder each reading session wrote to. Two sessions have run; the first
# was moved aside before the second was built, so the names differ on disk.
.DIR_COWORK <- fs::path(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts",
  "MatContractData"
)
.FOLDER_RUN1 <- "_EntitiesClaude" # <- the backup of the first session
.FOLDER_RUN2 <- "EntitiesClaude" # <- the second session

.lP <- list(
  Input = list(
    Text = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb",
    # Written by 04B-CoWorkCompile.R from each reading session's responses. Both are scored:
    # the sessions read different documents, so their union covers more vocabulary than either,
    # and Source keeps the recurrence question answerable afterwards.
    #
    # SET .FOLDER_RUN1 BELOW to whatever the first bundle was renamed to. Getting it wrong is not
    # fatal and not silent -- ent_read_rules() reports the file as missing -- but the run scores
    # only the session it found, and the rules the other one validated never reach 04C.
    Rules = c(
      run1 = fs::path(.DIR_COWORK, .FOLDER_RUN1, "compiled", "entity_rules.parquet"),
      run2 = fs::path(.DIR_COWORK, .FOLDER_RUN2, "compiled", "entity_rules.parquet")
    )
  ),
  Output = list(
    Hits   = utils_file_path(.dir_main, "anchor_hits.parquet"), # per-span anchor labels
    Scores = utils_file_path(.dir_main, "rule_scores.parquet"), # every rule, measured
    Kept   = utils_file_path(.dir_main, "rules_kept.parquet"), # the survivors, for 04D
    Policy = utils_file_path(.dir_main, "extraction_policy.parquet") # engine and cap, for 04C/04D
  ),
  Params = list(
    FoldHoldout    = 5L, # the fold the reading session never saw
    DateWindowDays = 730L, # how far before its filing a contract may be dated
    CtxMax         = 400L, # widest context materialised; caps the window any rule may use
    MinFire        = 30L, # below this a rule is too rare to judge on precision
    MinLift        = 1.2, # kept rules must beat the base rate by at least this factor
    RecallTol      = 0.10, # recall points an engine may trail the best and still be considered
    CostTol        = 0.15, # relative cost gap treated as a tie between engines
    # The last entry is the full-document idiom, and it is in the grid rather than beside it for two
    # reasons. It is the DEPLOYED configuration, so the policy artifact joins to it for the recall
    # each label achieves -- without it every recall column in the artifact is NA. And it is the
    # reference every capped row is read against: a cap is only interpretable as a fraction of what
    # reading everything delivers.
    HeadChars      = c(1500L, 3000L, 5000L, 10000L, 20000L, 100000000L),
    TailChars      = c(0L, 2000L, 5000L),
    CapChars       = 3000L # retained for reference; the artifact takes its window from .WINDOW
  )
)

# Formats tried, in order, against a date span. Naming them rather than using a general-purpose
# parser is what makes this affordable: a heuristic parser managed 242 strings a second on this
# corpus, so the 198k distinct date spans would take a quarter of an hour; this is about a second.
# Month-first precedes day-first, so an ambiguous slash date reads as US convention -- correct for
# an SEC filing -- while an unambiguous day-first date such as 26/8/2013 still resolves.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", # January 5, 2019
  "%b %d, %Y", "%b %d %Y", # Jan 5, 2019
  "%d %B, %Y", "%d %B %Y", # 5 August 2005
  "%d %b, %Y", "%d %b %Y", # 5 Oct 2015
  "%m/%d/%Y",  "%d/%m/%Y", # 8/26/2013, then unambiguous day-first
  "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d",
  "%d-%b-%Y",  "%m.%d.%Y"
)

# The span is cleaned before it reaches the parser -- see ent_sql_dateclean(). Requiring the whole
# span to be a date resolved only 6.6% of them, because the extractors return the date with
# whatever abuts it and legal drafting adds ordinals and "the 15th day of April, 2007".

# Which roles the anchor can speak to, and in which DIRECTION. The filer is a party at its own
# registered address on the date the contract was made, so a party cue should concentrate on it --
# and an agent, regulator or statutory cue should AVOID it. For the second group low lift is the
# pass condition, which turns roles that were previously unjudged into falsifiable ones.
#
# Roles absent from this table are outside the anchor's reach in either direction: an affiliate
# shares the filer's name so the anchor matches it either way, and a parent GUARANTOR usually does
# too, which is why guarantor is not listed; governing law is Delaware about as often as the state
# of incorporation is; and money has no anchor at all.
#
# Add "GPE", "incorporation", "high" here if a state-of-incorporation column turns up in the
# metadata -- ent_anchor_keys() reports whether it found one.
.ALIGNED <- tibble::tribble(
  ~Label,  ~Role,           ~Direction,
  "ORG",   "party",         "high",
  "ORG",   "agent",         "low", # the filer is not its own administrative agent
  "ORG",   "regulator",     "low", # the SEC is never a party to the contract it receives
  "ORG",   "third_party",   "low", # counsel, accountants, brokers
  "DATE",  "signing",       "high",
  "DATE",  "effective",     "high",
  "DATE",  "term_start",    "high",
  "DATE",  "statutory",     "low", # "Act of 1933" is never the contract's own date
  "DATE",  "expiry",        "low", # expiry follows the filing; the anchor precedes it
  "GPE",   "party_address", "high",
  "GPE",   "performance",   "low",
  "GPE",   "incidental",    "low"
)

# Headings probed for by search rather than enumerated from line structure. The list mixes the
# conventional Exhibit-10 furniture with the four the reading session proposed.
.HEADINGS <- c(
  "GOVERNING LAW", "NOTICES", "DEFINITIONS", "MISCELLANEOUS", "TERM", "TERMINATION",
  "ARBITRATION", "COUNTERPARTS", "REPRESENTATIONS AND WARRANTIES", "CONFIDENTIALITY",
  "INDEMNIFICATION", "ASSIGNMENT", "SEVERABILITY", "ENTIRE AGREEMENT", "WITNESS WHEREOF",
  "PURCHASE PRICE", "RENT", "PAYMENT", "COMPENSATION", "LICENSE FEES", "INITIAL PAYMENT",
  "LENGTH OF THE TERM", "BROKERS COMMISSION"
)

# Which of the redaction roles the surviving punctuation can speak to. A removed party name and a
# deleted clause body leave nothing behind that identifies them, so they are absent here and are
# reported as unmeasured rather than scored against a signal that cannot see them.
.REDACT_SHAPE <- tibble::tribble(
  ~Role,                ~Shape,
  "royalty_rate",       "ShapeRate", # a percent sign survived the gap
  "aggregate_amount",   "ShapeValue", # a currency symbol did
  "milestone_payment",  "ShapeValue",
  "unit_price",         "ShapeUnit", # "per share", "per barrel"
  "term_length",        "ShapePeriod" # "days", "months"
)

# Engines for the labels the anchor cannot rank. Money has no external record of a contract's value
# and redaction has no ground truth at all, so neither can be chosen on recall -- but both must be
# NAMED, or 04C joins its candidate set against a policy with a hole in it and drops the label
# without saying so.
#
# Money is the regex arm, and that is a measured choice on a proxy rather than a default. The
# section below asks which engine can propose a span at a site where the amount was WITHHELD, which
# is the case that matters most because a figure is redacted precisely when it is commercially
# material. The regex arm has a pattern written for the shape a removal leaves behind; a transformer
# has nothing to tag, because the number it would recognise is the thing that was taken out. Running
# a transformer over 1.1 million documents for a label it cannot reach at the sites that matter is
# the expensive way to be wrong.
#
# Redaction has one extractor, so its row is a default in the strict sense and says so.
.DEFAULT_ENGINE <- c(MONEY = "paper:moneyregex-v4", REDACT = "paper:redaction-v1")

# What kind of evidence stands behind a Basis of neither "measured" nor "declared". A label named
# here had no anchor to rank on but was not chosen arbitrarily either, and 04C and 04D read the
# column to know how much weight the row carries.
.PROXY_BASIS <- c(MONEY = "measured: proxy")

# Engines carried whatever the ranking says, because they are too cheap for the ranking's trade to
# apply to them. ent_choose_engines() trades recall against cost, which is right for an engine
# costing hours per corpus pass and wrong for one costing minutes: dateregex projects to three
# tenths of a corpus hour, so excluding it saves nothing measurable.
#
# It forgoes a great deal. The ranking preferred LexNLP to dateregex by 3.4 anchor-recall points,
# and 04C finds dateregex reaching an expiry cue in 415 documents against LexNLP's 113 -- because
# the anchor is the contract's own date, which sits in the preamble, so the criterion that made the
# choice was blind to the difference.
#
# THIS IS A UNION AND NOT A REPLACEMENT. 04C deploys every engine the policy names for a label and
# deduplicates on the span, so a row here widens the candidate set and cannot narrow it. What it
# costs is spans to resolve, and the artifact records that.
#
# Only dates gain anything: geography, money and redaction each have their rule arm as the ranked
# winner already, and organisations have no rule arm to add. The table is written out in full
# regardless, so the policy is visible rather than inferred from where the ranking happened to land.
.ALWAYS <- tibble::tribble(
  ~Label,  ~Combo,
  "DATE",  "paper:dateregex-v1",
  "GPE",   "paper:gazetteer-v1",
  "MONEY", "paper:moneyregex-v4",
  "REDACT", "paper:redaction-v1"
)

# THE EXTRACTION READS THE WHOLE DOCUMENT. Every label carries the full-text idiom below, and the
# reason is not that a window was found unnecessary -- the tables in this document measure exactly
# what a window would keep and what it would cost. It is that a window does not have to be decided
# at extraction time at all.
#
# Every candidate carries its offsets. So a window is a FILTER APPLIED AT RESOLUTION, not a decision
# taken at extraction: extract once over full text and any cap can be imposed, revised or withdrawn
# afterwards by a WHERE clause, on evidence that does not exist yet. Extract under a cap and the
# evidence outside it is gone irreversibly, and recovering it means re-running the corpus.
#
# That asymmetry is the whole argument. A cap saves compute once; it costs the ability to answer
# every later question about what sits outside it. The expiry work in 04C is the case in point --
# the window chosen for dates was set on the contract's own date, which sits in the preamble, and
# then applied to an end date that does not, and no amount of care in this document would have
# caught that before the variable was built.
#
# The window measurements below are therefore RETAINED AND REFRAMED. They no longer choose a cap.
# They report what a cap would have cost, which is the answer to the obvious referee question --
# why not truncate, given the corpus size -- and they remain the evidence for reimposing a cap
# later if the corpus pass proves unaffordable. The policy artifact still carries the columns, so
# nothing downstream changes shape; the numbers in them are now the full-text idiom.
.WINDOW <- tibble::tribble(
  ~Label, ~CapChars, ~TailChars, ~WindowBasis,
  "ORG", 100000000L, 0L, "full text: a window is a resolution-time filter, not an extraction choice",
  "DATE", 100000000L, 0L, "full text: same, and the expiry evidence in 04C requires it",
  "GPE", 100000000L, 0L, "full text: extraction is cheap and the window is not measurable",
  "MONEY", 100000000L, 0L, "full text: same",
  "REDACT", 100000000L, 0L, "full text: a cap drops 86% of markers"
)

fs::file_exists(c(.lP$Input$Text, .lP$Input$Anchors, .lP$Input$Store, .lP$Input$Rules))
```

Failing here rather than three chunks later is deliberate. The rules path in particular points
outside the repository, into the folder the reading session wrote to, and that folder gets renamed
whenever a session is superseded -- so the configured path goes stale on exactly the occasions when
a new session has just produced rules worth scoring. `ent_read_rules()` now aborts on a named
session that is not on disk rather than warning: it warned twice, the warning was missed twice, and
each time the document rendered against half the rule set and reported a count that looked
plausible on its own.

# Anchors

The anchor set is built once and written to disk, because three separate analyses read it and 04D
wants it too. Organisations and places resolve inside DuckDB, where the test is string containment on
a normalised form. Dates need a parser, so the *distinct* date strings -- far fewer than their
occurrences -- are brought into R, parsed once, and the verdict joined back.

```{r}
#| label: build-anchors
tab_keys <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)

con <- ent_session(
  .db_path = .lP$Input$Store, # attached read-only; nothing here can write to 04A's artifact
  .keys    = tab_keys # registered so the anchor tests can join on it
)

ent_write_anchor_hits(
  .con         = con,
  .path_out    = .lP$Output$Hits, # read by every section below, and by 04D
  .window_days = .lP$Params$DateWindowDays, # a contract dated earlier than this is not its own
  .formats     = .DATE_FORMATS # parsed in the database, not in R; see above
)

tab_cov <- ent_anchor_coverage(.con = con)
ent_report_anchors(.tab = tab_cov)
```

`PctMatched` is the ceiling on everything that follows. It is the share of documents in which *some*
engine proposed the known entity, so no individual engine can exceed it, and the gap below 100% is
documents where every engine missed a company that is certainly named in its own contract.

# Engines

This is the section that costs nothing and settles the question 04A could not touch. No rule enters
it, so it runs on all 4,398 documents.

```{r}
#| label: score-engines
tab_eng <- ent_engine_recall(.con = con)

ent_report_engines(.tab = tab_eng)
```

The comparison to read first is LexNLP against spaCy on organisations. 04A established that LexNLP
returns roughly one twentieth of spaCy's organisation spans and that its output is largely contained
within spaCy's. If its recall on the filer is close to spaCy's, then twenty times the volume bought
very little, and the corpus policy is the narrow engine. If it is far below, breadth is doing real
work and the cost of adjudicating it is the price of the recall.

`SpansPerAnchor` is the second half of that judgement: how many candidates an engine returns for each
known entity it recovers. It is the adjudication cost per unit of recall, and it is the number that
makes an engine affordable or not at corpus scale.

# Rules

Every proposed rule is applied to the candidates in the held-out fold. Context is materialised once
per candidate and the rules tested against it, rather than the reverse -- the join is a few hundred
rules against a few hundred thousand candidates, and doing it the other way would slice the same text
hundreds of times over.

```{r}
#| label: score-rules
tab_rules <- ent_read_rules(.paths = .lP$Input$Rules)

tbl_say(
  .tab = tab_rules |> dplyr::count(.data$Source, .data$Label, name = "N") |>
    tidyr::pivot_wider(names_from = Label, values_from = N, values_fill = 0L),
  .title = "Rules by session"
)

tab_scores <- ent_rule_scores(
  .con       = con,
  .path_text = .lP$Input$Text, # supplies the context either side of each span
  .rules     = tab_rules, # cues and stops; sections and notes are not machine-applied
  .fold      = .lP$Params$FoldHoldout,
  .ctx_max   = .lP$Params$CtxMax # widest context held, so no rule can reach further
)

tab_rules_scored <- ent_rule_verdict(
  .tab      = tab_scores,
  .aligned  = .ALIGNED, # which roles the anchor can speak to
  .min_fire = .lP$Params$MinFire # below this, precision is noise
)

ent_report_rules(.tab = tab_rules_scored, .n = 10L)
```

Two conventions in that scoring are worth stating because getting either wrong would invert the
result.

**Stops are matched whole-span, never as substrings.** The reading session raised this itself, and it
is right: 34 of its 53 stops are single tokens, and a substring match on `company` would kill *Blue
Ridge Real Estate Company*, which is a party. Equality on the normalised span is the only safe
reading of what a stop asserts.

**A rule that never fires is reported, not dropped.** A grouped count returns nothing for a rule with
no matches, so the scores are joined back onto the full rule table. Firing zero times is the
commonest outcome and it is a result; a rule silently missing from the output would be
indistinguishable from one nobody proposed.

## Money: the one check external data supports

Money has no anchor, so 64 of its cues cannot be scored, and that stays true. One role is the
exception. A redacted amount leaves a bracketed marker in the text -- `[***]`, `[ * * * ]`, `[*]` --
and that is a different kind of evidence from a phrase in the surrounding sentence.

Only the **symbol** form is used. The explicit form, `[confidential treatment requested]`, shares
vocabulary with the cues themselves, so testing one against the other would be circular; the symbol
form shares none.

```{r}
#| label: check-redaction
tab_redact <- ent_redaction_check(
  .con   = con, # reuses the context table built for rule scoring
  .rules = tab_rules # only the MONEY cues carrying the redacted role
)

ent_report_redaction(.tab = tab_redact)
```

```{r}
#| label: check-redaction-shape
tab_shape <- ent_redaction_shape(
  .con       = con,
  .rules     = tab_rules, # the redaction cues, whatever session proposed them
  .shape_map = .REDACT_SHAPE # which roles the surviving punctuation can speak to
)

ent_report_redaction_shape(.tab = tab_shape)
```

The second table is the stronger of the two and it comes from the redaction unit. Where a marker
replaced a value, the currency symbol before it usually survived; where it replaced a rate, the
percent sign after it did; where it replaced a period or a unit price, the noun following did. Those
characters are not a phrase, so agreeing with a phrase cue is genuine corroboration rather than the
same evidence counted twice.

## Which money engine reaches a withheld amount

Money is the one label with no anchor, so its engine went into the policy as a declared default.
Cross-engine agreement narrows the question but does not settle it: the regex arm and the
transformer overlap at Jaccard 0.77, the highest cross-family pair in the store, and agreement on
what both find says nothing about what only one of them can.

A redaction marker is where an amount used to be. Whether an engine proposes a span there is a
capability rather than a tuned score, and it is the case that matters most, because a figure is
withheld precisely when it is commercially material.

```{r}
#| label: classify-redaction-sites
ent_redaction_sites(.con = con, .path_text = .lP$Input$Text)

tab_reach <- ent_redaction_reach(
  .con  = con,
  .near = 3L # a span touching the marker or its currency symbol counts as reaching it
)

ent_report_redaction_reach(.tab = tab_reach)
```

The site classes are read off the characters either side of the marker, not from any engine's
output, so the definition does not presuppose the answer. Read the two differently. On
`after_currency` the regex arm has a pattern written for that shape and a transformer has nothing to
tag -- the number it would recognise is the thing that was removed -- so a difference is expected
and its size is the result. On `before_unit` neither engine has any reason to fire, and a low figure
for both bounds what is recoverable at all rather than separating them.

This validates six cues, not sixty-four, and the honest position on the rest is unchanged. It is
worth having for a second reason: the reading session observed that redacted figures are
systematically the commercially material ones, so a per-document count of them is a variable rather
than only a nuisance, and this is the evidence that would establish it.

# Window geometry

The reading session reported, from three units independently, that confirmed entities cluster at both
ends of a contract while the bulk of candidates do not. 04A concluded the opposite for organisations
-- that they are spread flat -- but 04A measured every organisation span, and if the session is right
then the flatness is the noise and the parties are not flat at all. 04A's positional figure supports
the session on exactly this point: LexNLP's organisations are bimodal at the two ends of the
document while all four spaCy models are flat throughout, which is what a party extractor and a
defined-term collector respectively look like.

That distinction no longer decides the shape of the corpus pass -- the extraction reads full text,
for the reason set out in the configuration -- but it decides how much a cap WOULD cost, which is
the question a reader will ask given a corpus of 1.1 million documents. It is measured rather than
adopted either way.

The grid below puts the window on a RELATIVE axis, as a fraction of each document. Its sibling in
the next section puts it on an absolute one, in characters. Both report the share of **documents**
recovered, so the two are directly comparable, and the comparison answers a question neither can
answer alone: whether a fixed character cap is the right kind of policy at all. The median contract
here runs 25,578 characters and the longest runs 10.4 million, so 3,300 characters is thirteen
percent of the median and three hundredths of a percent of the longest.

```{r}
#| label: measure-window
tab_window <- ent_window_grid(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = c(0.02, 0.05, 0.10, 0.20), # fraction of the document read from the front
  .tail      = c(0, 0.05, 0.10, 0.20) # and from the back; 0 is the prefix window 04A costed
)

ent_report_window(.tab = tab_window)
```

Both columns are needed and neither means anything alone. The share of *anchors* kept is the recall
the window buys; the share of *all spans* kept is the cost it fails to avoid. A window keeping 80% of
anchors and 20% of spans is a good trade; one keeping 80% of both has done nothing.

Compare each head-only row against the same head with a tail added. If the tail buys more anchors
than spans, a prefix window is the wrong *shape* and not merely the wrong size -- which would carry a
cost, since `--max-chars` truncates a prefix and a head-plus-tail pass needs either a new extractor
flag or a splice with an offset map.

## The cap in characters

The grid above is in fractions, and `--max-chars` takes a character count. A character cap is not a
fixed fraction of anything: 3,300 characters is thirteen percent of the median contract here and
three hundredths of a percent of the longest.

Both tables report the same denominator, and it is worth saying why it is documents rather than
mentions. A contract naming the filer forty times -- twenty in the preamble, twenty at the signature
block -- is recovered by a head-only window, because a party has to be found **once**. Counting
mentions, adding a tail records twenty further recovered spans and the tail looks valuable; counting
documents it records nothing, correctly. The mention denominator flatters tails systematically, and
a tail is precisely what is under dispute for dates.

```{r}
#| label: measure-window-chars
tab_wchar <- ent_window_chars(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = .lP$Params$HeadChars, # character budgets from the front
  .tail      = .lP$Params$TailChars, # and from the back; 0 is the plain prefix window
  .policy    = NULL # every engine pooled, which is the optimistic reading
)

ent_report_window_chars(.tab = tab_wchar)
```

Three columns because a cap is three trade-offs at once. `DocRecall` is what it buys, `SpansKept` is
what 04C must then resolve, and `CharsKept` is what 04D must read -- the only one of the three that
maps to wall-clock time.

No row of the artifact this feeds is provisional any longer, because no row is a cap. Every label
extracts over full text, and these numbers say what each label would have given up under one. Read
`CharsKept` as the saving forgone and `DocRecall` as the recall bought by forgoing it.

The DATE row is the reason the question was reopened. Its tail was originally a declared correction
for an expiry-coverage problem, justified by a diagnostic that could not have established it: the
check read a roles table built from the already windowed candidate set, so its wider head rows
queried a table holding nothing past the cap. Corrected in 04C, it showed the deployed window
discarding roughly two thirds of what the expiry cues could reach. A cap that cheap to get wrong,
on a variable nobody had yet built, is a cap not worth taking at extraction time.

The table above pools every engine, so a document counts as recovered when ANY of eight found the
anchor inside the window. One of them will run, and what that one achieves is measured below --
after the engine has been chosen, because it cannot be measured before.

# Policy

The tables above are the evidence; this is the decision, applied by rule rather than asserted in
prose so that it is reproducible and its sensitivity to the tolerances is visible.

Take the engines within `RecallTol` of the best recall for their label, prefer the cheapest, and
where several sit within `CostTol` of the cheapest take the most accurate of those. The second
tolerance is not decoration: on dates two engines sit at 2.7 and 2.8 spans per anchor, a gap well
inside measurement error, and without it the rule would trade three points of recall for a rounding
difference.

Then add the cheap rule arms regardless of where that landed, and take the **union**. The ranking
trades recall against cost, which is the right trade for an engine costing hours per corpus pass and
the wrong one for an engine costing minutes. Dates are the case that showed it: the ranking preferred
LexNLP to `dateregex` by 3.4 anchor-recall points, and 04C finds `dateregex` reaching an expiry cue
in 415 documents where LexNLP reaches 113. The anchor is the contract's own date, sitting in the
preamble, so the criterion that made the choice could not see the quantity the term variable needs.

A label with two rows below runs both engines and 04C deduplicates on the span. Adding an engine
therefore cannot narrow the candidate set; it widens it, and what it costs is spans to resolve.

```{r}
#| label: choose-engines
tab_policy <- ent_choose_engines(
  .tab        = tab_eng,
  .defaults   = .DEFAULT_ENGINE,  # labels the anchor cannot rank still need an engine
  .proxy      = .PROXY_BASIS,     # and some of them were chosen on evidence of another kind
  .always     = .ALWAYS,          # the rule arms run regardless; a union, not a replacement
  .recall_tol = .lP$Params$RecallTol,
  .cost_tol   = .lP$Params$CostTol
) |>
  dplyr::left_join(.WINDOW, by = dplyr::join_by(Label))

ent_report_policy(.tab = tab_policy)
```

## What the chosen engines achieve

The grid above the policy pools every engine. This one restricts to the engine each label will
actually run, which is the number the corpus pass delivers and the number the artifact carries.

```{r}
#| label: measure-window-deployed
tab_wdeploy <- ent_window_chars(
  .con       = con,
  .path_text = .lP$Input$Text,
  .head      = .lP$Params$HeadChars,
  .tail      = .lP$Params$TailChars,
  .policy    = dplyr::select(tab_policy, Label, Combo) # one engine per label
)

ent_report_window_chars(.tab = tab_wdeploy)
```

Money is absent from the recall ranking above and should be: with no anchor there is no recall to
rank on. It is not thereby unevidenced. The redaction sections below ask whether an engine can
propose a span at a site where the amount was withheld, and the policy records the answer as a
`Basis` of `measured: proxy` -- a measurement of a different kind, distinguished in the artifact
from both a recall ranking and a bare assertion, so that 04C and 04D can tell the three apart.

# Sections

The heading scan in the bundle script returned a table in which every heading occurred in exactly one
of 4,398 documents. That is impossible -- "GOVERNING LAW" alone appears in most contracts ever filed
-- and the reading session reported it four times rather than building on it.

Two causes, and the replacement has to survive both. This corpus carries Windows line endings, which
DuckDB's `trim()` does not strip, so a case-sensitive filter rejects every line it sees; and
HTML-to-text conversion leaves long stretches carrying no newline at all, so what remains is whatever
short line a particular document happens to hold.

Searching for known headings needs no line structure. It also answers the question that actually
mattered, which was never "what headings exist" but "does this heading appear, and where".

```{r}
#| label: probe-sections
tab_sections <- ent_probe_sections(
  .path_text = .lP$Input$Text,
  .headings  = .HEADINGS # conventional Exhibit-10 furniture plus the session's four proposals
)

ent_report_sections(.tab = tab_sections)
```

A heading is usable only when it is both frequent and *narrow*: present in most documents, and
sitting in a tight band of the document. Frequent but scattered locates nothing, and narrow but rare
covers nothing. `MedianPos` against the quartiles is where that reads off.

# Validation

Two checks on the anchor itself, because everything above rests on it.

```{r}
#| label: validate-anchor
tibble::tibble(
  Check = c(
    "Documents with a company key",
    "Documents with an address",
    "Documents with a filing date",
    "Company keys under 5 characters (dropped)",
    "Date-anchored spans that post-date the filing"
  ),
  N = c(
    sum(!is.na(tab_keys$AnchorKey)),
    sum(!is.na(tab_keys$AnchorText)),
    sum(!is.na(tab_keys$DateFiled)),
    sum(is.na(tab_keys$AnchorKey) & !is.na(tab_keys$Class)),
    0L # excluded by construction in ent_write_anchor_hits(); reported so the claim is visible
  )
) |>
  tbl_say(.title = "Anchor construction")
```

The last row is zero by construction rather than by observation: the SQL requires a parsed date at or
before the filing date, so a later date cannot be flagged. It is reported because a reader should be
able to see that the constraint exists rather than infer it.

```{r}
#| label: validate-basereate
tab_scores |>
  dplyr::distinct(Label, NCand, NAnchor, BaseRate) |>
  dplyr::mutate(BaseRate = tbl_pct(.data$BaseRate, .digits = 2L)) |>
  tbl_say(.title = "Held-out fold: what a rule must beat")
```

A base rate of a fraction of a percent means the anchor is a needle, and a rule reaching a precision
of five percent has done something substantial even though five percent sounds like nothing. Reading
these numbers as if they were ordinary precision would dismiss every useful rule in the set.

# Robustness

```{r}
#| label: inspect-unmeasured
tab_rules_scored |>
  dplyr::count(.data$Label, .data$Measurable, name = "N") |>
  tidyr::pivot_wider(
    names_from = Measurable, values_from = N, values_fill = 0L,
    names_prefix = "Measurable_"
  ) |>
  tbl_say(.title = "Rules the anchor can and cannot judge")
```

The unmeasured rules are not failures and must not be dropped on this document's evidence. They
address roles EDGAR never recorded -- agents, guarantors, regulators, governing law, every money role
-- and settling them needs adjudication or hand labels.

```{r}
#| label: inspect-anchor-sensitivity
purrr::map(c(365L, 730L, 1095L), function(.w) {
  ent_anchor_coverage(
    .con         = con,
    .window_days = .w    # re-evaluates the date test in the query; anchor_hits is not touched
  ) |>
    dplyr::filter(.data$Label == "DATE") |>
    dplyr::transmute(WindowDays = .w, DocsMatched, PctMatched, BaseRate)
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(PctMatched = tbl_pct(.data$PctMatched), BaseRate = tbl_pct(.data$BaseRate, 2L)) |>
  tbl_say(.title = "Date anchor: sensitivity to the window")
```

The date anchor is the one with a free parameter, and the paper's own delay analysis says contracts
are filed some time after they are signed. If the matched share moves sharply between one and three
years, the window is doing the work rather than the data, and the date results above should be read
as conditional on it.

The variants are computed in the query rather than by rebuilding the anchor table. The earlier
version rebuilt `anchor_hits` once per window and relied on a later chunk to restore it, which makes
every section after this point depend on that restore executing: reorder the document, or fail in
between, and the rest of it reports against a window nobody chose, with no error and nothing visibly
different. Recomputing one column in a `SELECT` removes the dependency rather than managing it.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_rules_scored, .lP$Output$Scores)

tab_kept <- tab_rules_scored |>
  dplyr::filter(
    .data$Verdict %in% c(
      "strong", "useful", "safe", "consistent: avoids the anchor",
      "role misassigned: fires on anchor"
    ) |
      (stringr::str_starts(.data$Verdict, "unmeasured") & .data$NFire >= .lP$Params$MinFire)
  ) |>
  dplyr::select(
    Kind, Label, Role, SuggestedRole, Pattern, Side, Window, NFire, Precision, Recall,
    Lift, Direction, Measurable, Verdict
  )

arrow::write_parquet(tab_kept, .lP$Output$Kept)

# The policy artifact 04C and 04D consume: one engine per label, the window, the document-level
# recall each choice implies at that window, and the Basis saying what kind of evidence stands
# behind the row. Written as a table rather than described in prose so that both read a decision
# instead of re-deriving one, and so that a provisional row is visibly provisional.
tab_policy_out <- tab_policy |>
  dplyr::left_join(
    tab_wdeploy |>
      dplyr::select(Label, Head, Tail,
        DocRecallAtCap = DocRecall,
        SpansKeptAtCap = SpansKept, CharsKeptAtCap = CharsKept
      ),
    by = dplyr::join_by(Label, CapChars == Head, TailChars == Tail)
  )

# A LEFT JOIN THAT MATCHES NOTHING IS SILENT, and this one did: the declared window was absent from
# the character grid, so the artifact shipped with an empty recall column, which reads downstream as
# "not measured" rather than as "the grid was never asked about this window". 04D printed a policy
# table of NA and nothing failed.
#
# TWO WAYS TO GET AN EMPTY CELL, AND ONLY ONE IS A FAULT. A label with no anchor has no recall to
# compute -- ent_window_chars() drops it entirely, because the denominator is documents holding a
# known entity and money and redaction have none. That NA is correct and the Basis column already
# explains it. The fault is a label that DOES appear in the grid but not at the window declared for
# it, which means the grid was asked about the wrong windows. Checking without that distinction
# aborts on the labels working exactly as designed, and tells the reader to add a grid value that
# would change nothing.
lab_measurable_ <- unique(tab_wchar$Label)
lab_noanchor_   <- setdiff(tab_policy_out$Label, lab_measurable_)

miss_ <- tab_policy_out |>
  dplyr::filter(.data$Label %in% lab_measurable_, is.na(.data$DocRecallAtCap)) |>
  dplyr::mutate(Want = paste0(.data$CapChars, "+", .data$TailChars))
if (nrow(miss_) > 0L) {
  cli::cli_abort(c(
    "The character grid does not contain the declared window for {miss_$Label}.",
    "i" = "Wanted head+tail: {miss_$Want}",
    "x" = "The policy artifact would carry an empty recall column and nothing would report it.",
    "i" = "Add the value to {.arg HeadChars} or {.arg TailChars} in the configuration."
  ))
}
if (length(lab_noanchor_) > 0L) {
  cli::cli_alert_info(
    "Recall is blank for {lab_noanchor_} because {?it has/they have} no anchor to compute it \\
     against. That is not a missing measurement; see the Basis column."
  )
}

arrow::write_parquet(tab_policy_out, .lP$Output$Policy)
tbl_say(
  .tab = tab_policy_out |>
    dplyr::mutate(dplyr::across(
      c(Recall, DocRecallAtCap, SpansKeptAtCap, CharsKeptAtCap),
      \(.x) tbl_pct(.x)
    )) |>
    dplyr::select(
      Label, Combo, Basis, CapChars, TailChars, Recall, DocRecallAtCap,
      SpansKeptAtCap, CharsKeptAtCap
    ),
  .title = "Extraction policy for 04C and 04D"
)

tab_kept |>
  dplyr::count(.data$Label, .data$Kind, name = "N") |>
  tbl_say(.title = "Rules carried into 04D")
```

Unmeasured rules that fire often enough are carried through rather than discarded. Dropping them
would be treating "the anchor cannot see this" as "this is wrong", and the roles they address --
agents, guarantors, governing law -- are ones 04D needs.

```{r}
#| label: close-session
DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = c("Anchor hits", "Rule scores", "Rules kept", "Extraction policy"),
  Path     = c(.lP$Output$Hits, .lP$Output$Scores, .lP$Output$Kept, .lP$Output$Policy)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B")
```

# Overview

## Engine recall against the known entity

```{r}
#| label: fig-engine-recall
#| fig-height: !expr ent_facet_height(4L)
#| fig-cap: "Recall on the known entity against spans returned per anchor recovered, by engine."
ent_plot_engine_recall(.tab = tab_eng)
```

Up and to the left is better: the same recall for fewer spans. An engine sitting far right at the
same height as one on the left is paying an order of magnitude in adjudication cost for nothing.

## What each window shape keeps

```{r}
#| label: fig-window
#| fig-height: !expr ent_facet_height(4L)
#| fig-cap: "Share of documents recovered against share of all candidates kept, by window shape."
ent_plot_window(.tab = tab_window)
```

The diagonal is the null: a window that recovers documents and keeps candidates in equal proportion
has selected nothing. Distance above it is the enrichment, and a tail line sitting above the
tail-of-zero line is the reading session's claim confirmed. Both axes run the full range from zero,
which is what makes the reference line readable across the panel rather than only in one corner.

Read this figure against the character table rather than on its own. Both report document recall, so
a fraction reaching a given recall for a smaller share of the candidate pool than any character cap
manages would mean the cap is on the wrong axis and document length is doing the work.

## Rule lift by label

```{r}
#| label: fig-rule-lift
#| fig-height: !expr ent_facet_height(4L)
#| fig-cap: "Lift over the base rate against how often a rule fires, measurable cues only. The two
#|   colours are the two directions and must be read separately: a high-direction cue passes above
#|   the line, a low-direction cue passes below it."
ent_plot_rule_lift(.tab = tab_rules_scored)
```

The useful region depends on the direction, which is why the two are coloured rather than pooled. A
high-direction cue passes by sitting above the reference line and firing often enough to matter;
high lift on a handful of candidates is a curiosity, and lift near one at any volume is the base
rate wearing a phrase. A low-direction cue passes by sitting *below* it, because the claim being
tested is that the cue avoids the anchor. The two groups are not comparable on the vertical axis and
a single cloud would imply they were.

## The whole measurement in one block

```{r}
#| label: report-everything
ent_report_all(
  .tab_cov      = tab_cov,
  .tab_eng      = tab_eng,
  .tab_rules    = tab_rules_scored,
  .tab_window   = tab_window,
  .tab_sections = tab_sections,
  .tab_wchar    = tab_wchar,
  .tab_policy   = tab_policy,
  .tab_redact   = tab_redact,
  .tab_shape    = tab_shape,
  .tab_reach    = tab_reach
)
```

# Next

**04D** resolves spans into the four published variables, using the surviving rules to assign a role
per occurrence. The reading session's constraint applies there and not here: the same place name
carries several roles inside one document, so roles attach to occurrences and never to strings.

Three things this document cannot settle, and they should be taken to 04D as open rather than
assumed. **Money has no anchor**, so its 64 cues are carried unscored; the redaction rules can be
cross-checked against `06-Redactions`, and the rest need hand labels. **Unmeasured roles** -- agents,
guarantors, regulators, governing law -- were never in the anchor's reach and are carried on coverage
alone. And the span-shape prefilters the reading session described in its notes, requiring a
four-digit year on a date or a currency marker on an amount, are not implemented here: they are
hypotheses of the same kind as the cues and belong in the same scoring frame, not ahead of it.

Whether **04C** is still needed is worth deciding on this document's output rather than in advance.
If the engine table settles the corpus policy and the window grid settles its shape, a separate
selection script has nothing left to select, and the family collapses to extract, measure, resolve,
apply.
