---
title: "Entity Rules -- Signing, End and Duration (04B3)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")
source("1_code/_Commons/_Entity.R", encoding = "UTF-8")

purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B3-Rules-DATE.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document turns dates into a contract duration, and it exists because of one number.

Table 3 Panel B reports duration with a mean of 2.38 years, a median of 0.40 and a **standard
deviation of 40.78**, under a stated cap of 30 years. A variable supported on [0, 30] cannot have a
standard deviation above 15 -- the maximum, reached by a 50/50 split on the endpoints. Referee 1 saw
the symptom and asked whether there were *errors in identifying dates affecting the right tail*.

The published definition is the first row of the sweep rather than something replaced sight unseen,
and `SdOverCap` appears in every row.

## The three things a contract can say about when it ends

**A stated term** -- `for a period of five (5) years from the Effective Date`. A duration with no end
date at all, invisible to any rule that reads dates, and once the start is known it is arithmetic.
This is what the contract *says*, so it outranks the other two.

**A dated termination** -- a future date with a termination cue beside it.

**Nothing**, in which case the farthest future date is taken and recorded as such. That is the
published definition, and it picks up a patent expiry and a perpetuity boilerplate along with the
contract's own end.

`DurationSource` distinguishes all three, because they are not the same evidence.

## Two corrections to the previous version

**No clustering.** An earlier version collapsed each document to one row per calendar date, keeping
the earliest occurrence. It bought nothing -- the duration is a maximum and a minimum over *values*,
which do not care how often a value appears -- and it created a bug: the termination cue was then
tested at the earliest occurrence, so `shall expire on December 31, 2020` was invisible whenever that
date had already appeared in the preamble, which in a contract is the normal case. Everything now
runs at **span level**.

**No region rule.** Dates are not bimodal the way organisations are. Measured over the sample: the
head is 72.8% pre-filing and the **tail is 73.0%** -- identical -- against a deep U for organisations.
Region separates the head from the middle and separates nothing else, and excluding the tail from the
end search cost 2.5 points of coverage and left the standard deviation unchanged. The end rule reads
the whole document; the head restriction on the *start* is a swept row rather than a rule.

## What the last render found, and what changed because of it

**The right tail is the extractor, not the contract.** The far-future read showed `Section 3-1`
parsed as 2026-03-01, `Exhibit 10-15` as 2026-10-15, `10-35 Second` as 2035-10-01 and a run-together
rent table as the year **9308**. Section and exhibit references, with the year supplied by the parser.
That is upstream of every rule here, so it is counted rather than fixed: `HasYear` flags a span that
wrote its own four-digit year, and the guard is a swept row.

**`PERIOD OF` is not a term.** The stated-term arm caught `PERIOD OF THIRTY (30) DAYS` in 127
documents and `PERIOD OF ONE MONTH` in 71 -- notice periods and payment windows, not durations, and
enough of them to drag credit agreements to a median of one year. `TERM OF` and `PERIOD OF` are now
separate families, only the first counts by default, and the second is still extracted and reported.

**The cue suspects were the wrong ones.** `UNTIL` scored a lift of 2.78 and `THROUGH` 2.35 -- both
sound. The real redundancy was that seventeen terms were nested substrings of each other, so the list
is now six stems with identical behaviour, and `MATURES` is gone at four spans and no future dates.

## Two small vocabularies, both with hit rates

The cue list and the term patterns are the only vocabularies in this family doing real work, and
neither is defended by argument. The report prints how often each cue fires and on what share of
future dates; a term that fires everywhere without marking a termination gets dropped from the list
rather than explained. `THROUGH` and `UNTIL` are the two under suspicion.

## The cap drops, it does not winsorise

A duration of exactly thirty years that is not one is worse than a missing value.

## Coverage is a finding, not a gap

Roughly 94% of contracts name a date; what 37% lack is a date *after the filing*. That splits three
ways -- a term stated in words, dates that are all pre-filing, or no dates at all -- and only the
last is an extraction question. A contract writing `for a period of five years` has said exactly when
it ends and named no date to say it with.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Dates    = utils_file_path(.dir_main, "roles_date.parquet"),   # one row per date span
    Terms    = utils_file_path(.dir_main, "terms_stated.parquet"), # one row per stated term
    Duration = utils_file_path(.dir_main, "duration_doc.parquet")  # one row per document
  ),
  Params = list(
    Combos  = c(lexnlp = "lexnlp", dateregex = "paper:dateregex-v2"),
    ReadN   = 10L,
    ReadCtx = 200L,
    CheckN  = 500L,
    Seed    = 42L
  )
)

# The specification carried into the released artifacts.
.lP$Params$Spec <- dte_spec(
  .start        = "latest",  # latest date at or before the filing, wherever it sits
  .end          = "term",    # stated term, then dated termination, then farthest future date
  .cue_win      = 120L,
  .cap_years    = 30,        # dropped, not winsorised
  .require_year = FALSE,     # swept below before it is adopted
  .term_kinds   = c("term of", "anniversary") # "period of" is a notice period as often as a term
)

# The published definition is the FIRST row, uncapped, so the number this document exists to explain
# is reproduced before anything replaces it.
.lP$Params$Specs <- list(
  dte_spec(.start = "filed",  .end = "any",  .cap_years = Inf, .label = "published (uncapped)"),
  dte_spec(.start = "filed",  .end = "any",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "any",  .cap_years = 30),
  dte_spec(.start = "head",   .end = "any",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "cue",  .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .cap_years = 30),
  dte_spec(.start = "latest", .end = "term", .cap_years = 30, .require_year = TRUE),
  dte_spec(.start = "latest", .end = "term", .cap_years = 30,
           .term_kinds = c("term of", "anniversary", "period of"), .label = "term / all families"),
  dte_spec(.start = "latest", .end = "term", .cap_years = 10),
  dte_spec(.start = "latest", .end = "term", .cap_years = Inf)
)

fs::file_exists(unlist(.lP$Input))
```

# Sample

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)  # carries DateFiled
tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)
```

```{r}
#| label: load-dates
tab_dates  <- dte_load(
  .db_path = .lP$Input$Store,
  .lens    = tab_lens,
  .combos  = .lP$Params$Combos,
  .quiet   = FALSE
)

tab_parsed <- dplyr::filter(tab_dates, .data$Parsed)

dte_report_parse(.dates = tab_dates)
```

```{r}
#| label: inspect-daymonth
tab_dm <- dte_daymonth(.dates = tab_dates)

dte_report_daymonth(.tab = tab_dm)
```

```{r}
#| label: load-terms
tab_terms <- dte_term(
  .path_text = .lP$Input$Text,   # the whole document; a term clause names no date
  .quiet     = FALSE
)

dte_report_terms(.terms = tab_terms, .n_docs = nrow(tab_keys))
```

# Where dates sit

```{r}
#| label: describe-dates
# COMPUTED ONCE. Every specification below reads the same region, gap and cue, so describing per
# specification would re-read the canonical text and re-run the cue search over 102,005 spans to
# produce the identical table eight times -- which is what made an earlier version take six minutes.
tab_desc <- dte_describe(
  .dates     = tab_parsed,
  .keys      = tab_keys,
  .path_text = .lP$Input$Text,
  .spec      = .lP$Params$Spec
)

dte_report_year(.dates = tab_desc)
```

```{r}
#| label: apply-base-spec
tab_dur <- dte_duration(
  .dates = tab_desc,
  .terms = tab_terms,
  .keys  = tab_keys,
  .spec  = .lP$Params$Spec   # the cascade carried into the artifacts
)

dte_report_region(.dates = tab_desc)
```

```{r}
#| label: inspect-cues
tab_cues <- dte_cue_hits(.dates = tab_desc)

dte_report_cues(.tab = tab_cues)
```

A term scoring near a lift of one is a word the language uses for other things and is carrying no
information; it comes out of the list rather than getting an explanation.

# Coverage

```{r}
#| label: inspect-nofuture
tab_nofut <- dte_nofuture(.dur = tab_dur)

dte_report_nofuture(.tab = tab_nofut)
```

# Duration

```{r}
#| label: sweep-specs
tab_sweep <- dte_sweep(
  .desc  = tab_desc,            # described once, above
  .terms = tab_terms,
  .keys  = tab_keys,
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

dte_report_sweep(.tab = tab_sweep)
```

The first row is the published definition. The level it reports will not match Table 3 Panel B and
should not be expected to: this is a hand-classified sample balanced across twelve contract types
and that table is the corpus, which is dominated by employment exhibits. **The like-for-like
comparison is 04D**, and until then the row is here to show what the definition does, not to
reconcile with a published figure.

```{r}
#| label: report-class
dte_report_class(.dur = tab_dur)
```

# Reading

```{r}
#| label: read-terms
tab_terms |>
  dplyr::slice_sample(n = 15L) |>
  dplyr::select(DocID, TermKind, TermYears, NTermMatch, TermText) |>
  tbl_say(.title = "Stated terms, as the contract wrote them")
```

```{r}
#| label: read-cued-end
ent_read_spans(
  .tab       = dplyr::filter(tab_desc, .data$HasEndCue, .data$Side == "after filing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("DateValue", "GapDays", "Region"),
    .title = "Future dates carrying a termination cue"
  )
```

```{r}
#| label: read-uncued-far
# The dates the published definition takes and the cascade declines: far future, no termination
# language anywhere near them, no stated term in the document. A patent expiry, a statutory deadline
# and a perpetuity boilerplate should be visible here.
ent_read_spans(
  .tab       = tab_desc |>
    dplyr::filter(!.data$HasEndCue, .data$Side == "after filing", .data$GapDays > 365L * 15L,
                  !.data$DocID %in% tab_terms$DocID),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("DateValue", "GapDays", "Region", "HasYear"),
    .title = "Far future dates with no cue and no stated term"
  )
```

```{r}
#| label: read-no-year
# The spans whose year the parser supplied. This is the block that says whether the right tail is
# contract language or section numbering -- "Section 3-1", "Exhibit 10-15", "10-35 Second" all parse
# to a date in the current year and none of them is one.
ent_read_spans(
  .tab       = dplyr::filter(tab_desc, !.data$HasYear, .data$Side == "after filing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 10L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "DateValue", "GapDays"),
    .title = "Spans with no written year, parsed into the future"
  )
```

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_desc,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every described span carries a parsed value",
    "Documents carrying exactly one duration row",
    "No released duration is negative",
    "No released duration exceeds the cap",
    "Every term-sourced duration has a stated term",
    "Every cue-sourced duration has a cued future date"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_desc$DateValue)),
    dplyr::n_distinct(tab_dur$DocID),
    sum(tab_dur$DurationYears >= 0, na.rm = TRUE),
    sum(tab_dur$DurationYears <= .lP$Params$Spec$CapYears, na.rm = TRUE),
    sum(!is.na(tab_dur$TermYears[tab_dur$DurationSource == "term"])),
    sum(tab_dur$NCued[tab_dur$DurationSource == "cue"] > 0L)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_desc),
    nrow(tab_dur),
    sum(!is.na(tab_dur$DurationYears)),
    sum(!is.na(tab_dur$DurationYears)),
    sum(tab_dur$DurationSource == "term"),
    sum(tab_dur$DurationSource == "cue")
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

Rows four and five are what Table 3 Panel B could not satisfy. They hold here by construction -- a
negative or over-cap duration is set to missing rather than released -- which is why the count of
what was removed sits in the sweep rather than being left implicit. The last two rows check that
`DurationSource` says what actually happened, which is the one column a consumer will filter on.

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_desc, -dplyr::any_of("Before")), .lP$Output$Dates)
arrow::write_parquet(tab_terms, .lP$Output$Terms)
arrow::write_parquet(tab_dur, .lP$Output$Duration)

tibble::tibble(
  Artifact = c("Date spans with region, gap and cue",
               "Terms stated in words, per document",
               "Start, end, duration and source, per document"),
  Path     = c(.lP$Output$Dates, .lP$Output$Terms, .lP$Output$Duration)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B3")
```

The term file is released separately because it is evidence in its own right: a contract's stated
term is a fact about the contract whether or not this document's cascade happens to use it.

# Overview

```{r}
#| label: fig-gap
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of the gap between a date and the filing, in years, by region,
#|   clipped at ten years either side. The dashed rule is the filing date. The head and the tail
#|   nearly coincide, which is why no end rule reads region."
dte_plot_gap(.dates = tab_desc)
```

```{r}
#| label: fig-source
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "What the end date rests on, by contract type, as shares within each type. TERM and CUE
#|   are things the contract said; MAXDATE is a maximum over dates it merely mentions, and NONE is a
#|   contract that states no end at all."
dte_plot_source(.dur = tab_dur)
```

```{r}
#| label: fig-class
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Median contract duration in years by type, under the released cascade. A class with no
#|   bar has too few durations to report, which is a coverage fact rather than a duration of zero."
dte_plot_class(.dur = tab_dur)
```

```{r}
#| label: report-everything
dte_report_all(
  .dates    = tab_dates,
  .desc     = tab_desc,
  .cues     = tab_cues,
  .terms    = tab_terms,
  .nofut    = tab_nofut,
  .daymonth = tab_dm,
  .sweep    = tab_sweep,
  .dur      = tab_dur,
  .n_docs   = nrow(tab_keys)
)
```

# Next

The two vocabularies are what the next pass revises, and both have a table pointing at the answer.
The cue list gets cut to whatever scores a lift meaningfully above one. The term patterns catch two
families and the read block says which third family is worth adding -- `shall continue until
terminated` is a real drafting form and it is a duration of infinity rather than a missing value.

One thing is deliberately still not attempted: a contract with several terms, one per schedule, has
several durations, and this document releases one.
