---
title: "Entity Rules -- What Was Withheld (04B5)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")
source("1_code/_Commons/_Entity.R", encoding = "UTF-8")

purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B5-Rules-REDACT.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

This document counts redaction markers and asks what each one replaced. It is the shortest of the
five, and almost all of its work is keeping two things apart that look the same.

## The two marker kinds never pool

A **bracketed** marker -- `[***]`, `[REDACTED]` -- follows the drafting convention the published
classification is built on. A **bare** run of asterisks does not, and one sample document carries
**14,689 of them: 24% of every redaction span in the sample, from a single filing.**

Pooling the two means one document decides a class contrast, which is what happened on the first look
at this label: Employment: Compensation showed a positional contrast of 13.29 against 1 to 5
everywhere else. So every count is reported by kind, and every class contrast is computed **four
ways** -- span-weighted and document-weighted, with bare markers and without. A finding that survives
all four is a finding; one that appears only in the span-weighted pooled cell is that document.

## The ratio is the comparable quantity

Contracts run from roughly 4,200 to 17,400 words by class, so a count of markers is partly a count of
words. **Markers per thousand words** is what makes a class or an industry comparison mean anything,
and it is what referee 2 asked for when they wanted redaction intensity by firm-quarter.

## What a marker replaced

A marker beside a currency symbol hid an amount; beside an organisation, a party name. That is the
same proximity instrument the geography rule uses, and it is the only thing here that goes beyond
counting.

It is **reported and not released**. On the earlier check 82% of markers had no labelled entity
within forty characters, and a variable missing four times in five is a diagnostic rather than a
measure. What it can say is which labels sit near markers at all, which is the first thing to know
before anyone builds on it.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb"
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "roles_redact.parquet"), # one row per marker
    Doc   = utils_file_path(.dir_main, "redact_doc.parquet")    # one row per document
  ),
  Params = list(
    Combo = "paper:redaction-v1",
    # The labels a marker might have replaced, each at the engine the corpus pass carries.
    Neighbours = c(money = "paper:moneyregex-v6", org = "lexnlp", date = "paper:dateregex-v2",
                   gpe = "paper:gazetteer-v1"),
    Reach   = 40L,      # furthest a labelled span may be and still be the marker's neighbour
    Bins    = 50L,
    ReadN   = 10L,
    ReadCtx = 200L,
    CheckN  = 500L,
    Seed    = 42L
  )
)

fs::file_exists(unlist(.lP$Input))
```

# Sample

```{r}
#| label: build-keys
tab_keys  <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)
tab_lens  <- ent_doc_lens(.path_text = .lP$Input$Text)
tab_words <- red_words(.path_text = .lP$Input$Text)
```

```{r}
#| label: load-markers
tab_marks <- red_load(
  .db_path = .lP$Input$Store,
  .lens    = tab_lens,
  .combo   = .lP$Params$Combo,
  .quiet   = FALSE
)

tab_counts <- red_counts(.marks = tab_marks, .words = tab_words, .keys = tab_keys)

red_report_found(.marks = tab_marks, .counts = tab_counts)
```

# By contract type

```{r}
#| label: report-contrast
tab_contrast <- red_contrast(.marks = tab_marks, .counts = tab_counts)

red_report_contrast(.tab = tab_contrast)
```

The prediction this table exists to test, stated before it runs: **Employment: Compensation collapses
toward the other classes** once bare markers are excluded and documents are weighted equally. If it
does not, the 13.29 was a real finding about where compensation exhibits redact, and it can go in the
paper -- but not until the four cells agree.

# What sat beside a marker

```{r}
#| label: find-neighbours
tab_near <- red_neighbour(
  .marks   = tab_marks,
  .db_path = .lP$Input$Store,
  .lens    = tab_lens,
  .labels  = .lP$Params$Neighbours,   # money, org, date and gpe at the corpus engines
  .reach   = .lP$Params$Reach,
  .quiet   = TRUE
)

red_report_neighbour(.marks = tab_near, .reach = .lP$Params$Reach)
```

```{r}
#| label: report-cto
# The base rate stands unchecked until the confidential-treatment match is joined here. 05-CheckItem101
# already establishes which filings carry an order, and if that rate and this one disagree materially,
# one of them is wrong -- which matters for the intensity figures referee 2 asked for.
red_report_cto(.counts = tab_counts, .cto = NULL)
```

# Reading

```{r}
#| label: read-bracketed
ent_read_spans(
  .tab       = dplyr::filter(tab_near, .data$Kind == "bracketed", .data$NearLabel != "nothing"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Kind", "NearLabel", "NearDist"),
    .title = "Bracketed markers with something labelled beside them"
  )
```

```{r}
#| label: read-bare
ent_read_spans(
  .tab       = dplyr::filter(tab_near, .data$Kind == "bare"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Kind", "NearLabel", "NearDist"),
    .title = "Bare markers -- the kind that floods"
  )
```

```{r}
#| label: read-flood
# The documents with the most markers, read rather than averaged. An average over a distribution with
# one observation at 14,689 is a fiction, and this is what that observation looks like.
tab_counts |>
  dplyr::slice_max(.data$NRedact, n = 10L, with_ties = FALSE) |>
  dplyr::select(DocID, Class, NWords, NBracketed, NBare, RedactRatio) |>
  dplyr::mutate(RedactRatio = round(.data$RedactRatio, 2)) |>
  tbl_say(.title = "The ten most heavily marked documents")
```

# Validation

```{r}
#| label: validate-offsets
tab_check <- ent_verify_span(
  .tab       = tab_marks,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every marker carries one of the two kinds",
    "Bracketed and bare sum to the total",
    "Every document carries a word count",
    "Documents carrying exactly one row",
    "Every neighbour distance is within the reach"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(tab_marks$Kind %in% c("bracketed", "bare")),
    sum(tab_counts$NBracketed + tab_counts$NBare == tab_counts$NRedact),
    sum(!is.na(tab_counts$NWords)),
    dplyr::n_distinct(tab_counts$DocID),
    sum(tab_near$NearDist <= .lP$Params$Reach, na.rm = TRUE)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_marks),
    nrow(tab_counts),
    nrow(tab_counts),
    nrow(tab_counts),
    sum(!is.na(tab_near$NearDist))
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(tab_near, .lP$Output$Spans)
arrow::write_parquet(tab_counts, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Markers with their kind and what sat beside them",
               "Redaction counts and intensity, per document"),
  Path     = c(.lP$Output$Spans, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B5")
```

The document table carries both kinds as separate columns and both ratios, so a consumer who
disagrees about whether bare markers count can pool them without re-deriving anything.

# Overview

```{r}
#| label: fig-ratio
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Mean bracketed markers per thousand words, by contract type, weighting every contract
#|   equally. This is the document-weighted, bare-excluded cell of the four-way table, and the one a
#|   redaction-intensity figure should be built from."
red_plot_ratio(.counts = tab_counts)
```

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of markers by relative position in the document, weighted by documents, by kind.
#|   A kind that clusters at one end is following a drafting convention; one spread evenly is being
#|   used for something other than withholding a term."
red_plot_density(.marks = tab_marks, .bins = .lP$Params$Bins)
```

```{r}
#| label: report-everything
red_report_all(
  .marks    = tab_marks,
  .near     = tab_near,
  .counts   = tab_counts,
  .contrast = tab_contrast,
  .reach    = .lP$Params$Reach
)
```

# Next

Two things this document points at rather than answers.

**The base rate needs the confidential-treatment match.** 05-CheckItem101 already establishes which
filings carry an order; joining it here turns an unchecked share into a cross-tab, and a marker with
no order or an order with no marker is a finding either way.

**The money-adjacent case is the one worth pursuing.** A marker beside a currency symbol hid an
amount, and that is the single place where this label and 04B4 have something to say to each other -- 
a contract whose largest amount is redacted has a maximum that means something different from one
whose largest amount is stated.
