---
title: "Contract Classification -- Labelling the Corpus (03F)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,       # mandatory: cli writes through the message stream under knitr
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)

# Tables render either as styled html or as fixed-width console blocks. The console path is what a
# table is for while a long run is being watched; the rendered path is what a reader meets.
options(mc.table_mode = "console")

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))
```

```{r}
#| label: setup-sources
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A supplies the text reader and the category vocabulary, 03B the deployed models, 03C the lexicon
# and -- crucially -- the decision rule that turns term hits into a class. Nothing here reimplements
# any of them: the classifier applied to the corpus is the code the folds were run through.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "03B-ClassifyTrainBERT", "03C-ClassifyTrainKeyword"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

Every decision has been made. 03B fitted a transformer per task and per context length and crowned
one of each. 03C published a keyword table per task and marked one. 03E measured what combining them
would buy and reported the answer. This document makes none of those decisions again: it reads what
those stages deployed and runs it over roughly 1.1 million Exhibit-10 contracts.

Two engines, in their own sections. The transformer supplies the label. The keyword table supplies an
independent second opinion on every document it has a term for -- worth nothing as a label, as 03E
established, and worth something as a signal that a reader can recompute on any filing.

## The store is the design

A pass over a million documents does not complete in one sitting, and it must not begin again from
zero when it fails at ninety per cent. Everything lands in one DuckDB, and three questions can be put
to it at any moment:

**What is done** -- rows under the current run key. **What is missing** -- the corpus minus what is
done minus what failed, returned as identifiers rather than a count, so the claim is checkable.
**What has changed** -- whether the configuration about to run differs from the one that wrote the
rows already there.

The third is the one that is easy to leave out and the one that quietly corrupts a released dataset.
A table holding two context lengths under one name looks exactly like a table holding one.

## What the run key is, and what it deliberately is not

The key hashes the **recipe**: the task, the configuration name and the context length. Those
determine the weights, given the seed fixed upstream, so a refit that reproduces a model
byte-for-byte does not discard three hours of work.

The artifact path and a fingerprint of its contents are **recorded rather than keyed**. A checkpoint
replaced by hand therefore surfaces in the drift report instead of being silently honoured -- which
would mix two models under one name -- or silently discarded, which would be safe and infuriating.

One key per task rather than one per pass, because tasks finish independently: a crown moving on the
broad taxonomy must not throw away a finished pass on amendments.

## Failures are retryable

A document whose parquet is missing or holds no text is recorded with a reason and excluded from the
current pass. The next pass tries it again. A file unreadable because a mount hiccuped must not be
blacklisted forever, and a file that is genuinely empty simply reappears in the report every time,
which is honest rather than tidy.

## Where the engine boundary sits

The transformer returns finished predictions, because a class is what it was trained to emit.

The keyword engine does not. `keyword_apply.py` answers one question -- which terms of this lexicon
occur in this document -- and the rule turning terms into a class lives once, in R, and is called
identically by 03C when it measures the table's precision and by this document when it applies it.
A second decision rule in a second language is what once put a hand-written substring search in front
of a lexicon mined under stopword removal: the table committed on 36% of the corpus where it had
published 52%, and nothing anywhere reported a fault.

# Configuration

```{r}
#| label: configure-paths
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")
.dir_bert <- init_create_script_dir(.dir_here = here::here(), .name_script = "03B-ClassifyTrainBERT")
.dir_kw   <- init_create_script_dir(.dir_here = here::here(), .name_script = "03C-ClassifyTrainKeyword")

.lP <- list(
  Input = list(
    Prepared  = fs::path(.dir_prep, "prepared.parquet"),
    BertCrown = fs::path(.dir_bert, "model_final", "deployed.parquet"),
    KwCatalog = fs::path(.dir_kw, "table", "catalogue.parquet"),
    DirCorpus = "../pMatDisc/2_output/01-GetEDGAR/GetEDGAR/DocumentData/Parsed/Exhibit10/"
  ),
  Runs = list(Bert = fs::path(.dir_bert, "runs")),
  Cache = list(CorpusFiles = utils_file_path(.dir_main, "Cache", "CorpusFiles.parquet")),
  Store = list(Path = utils_file_path(.dir_main, "store", "labels.duckdb")),
  Output = list(Release = utils_file_path(.dir_main, "release")),
  Engine = list(
    Python  = "contracts-engine/.venv/bin/python",
    Bert    = "contracts-engine/classify_apply.py",
    Keyword = "contracts-engine/keyword_apply.py"
  ),
  Param = list(
    Tasks = c("ClassDetailed", "ClassBroad", "AmendType"),
    # NULL takes the length 03B crowned for each task. An integer overrides it for every task, which
    # is the cost decision: the longer window is a second full pass over the corpus, and 03E measures
    # what it buys on the labelled sample.
    # One or more context lengths. Both is a legitimate plan rather than a mistake: the store keys
    # every run on its own length, so 256 and 512 coexist without mixing, and the export writes one
    # file per length. The keyword table has no context length and is shared by both.
    MaxLen     = 256L,
    NWords     = NULL,   # NULL takes the truncation window 03C marked as default
    BatchSize  = 32L,
    ChunkSize  = 5000L,  # documents per engine invocation; see the benchmark below
    # Chunks between progress lines during a pass. The first and last always report, so a short run
    # is never silent. This counts CHUNKS, not minutes, so the cadence moves with ChunkSize: at 5,000
    # documents a chunk every fifth chunk is roughly every six minutes, and at 500 it is roughly
    # every forty seconds. Set it to 1L to see every chunk.
    ReportEvery = 5L,
    Rehearsal  = 2000L,  # documents in the timing sample, fixed so timings stay comparable
    # The grid the benchmark prices. Both context lengths, because the whole point is what the longer
    # one costs; one batch size, because widening this multiplies the runs and the store remembers
    # every combination measured, so it can be widened later without repeating anything.
    BenchLens  = c(256L, 512L),
    BenchBatch = 32L,
    Rewalk     = FALSE   # walk the corpus tree again rather than reading the cached index
  )
)
```

`MaxLen` is the one parameter here that is a decision rather than a setting. 03E compares the two
lengths on the labelled sample; this document decides what to pay for on 1.1 million documents. Set
it to `NULL` to take each task's own crown instead.

`ChunkSize` matters more than it looks. `classify_apply.py` loads the tokenizer and the model on every
invocation, so a small chunk pays that cost hundreds of times over. The benchmark below measures it
rather than assuming a value.

```{r}
#| label: load-inputs
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep   <- arrow::read_parquet(file = .lP$Input$Prepared)
bert_crown <- arrow::read_parquet(file = .lP$Input$BertCrown)
kw_cat     <- arrow::read_parquet(file = .lP$Input$KwCatalog)
tab_overall <- clf_load_overall(.runs_roots = .lP$Runs$Bert)

con <- app_connect(.path = .lP$Store$Path)

n_corpus <- app_corpus_load(
  .con        = con,                        # the store
  .dir_corpus = .lP$Input$DirCorpus,        # the parsed-contract tree, Exhibit 10 only
  .path_cache = .lP$Cache$CorpusFiles,      # walking a million paths is cached, not repeated
  .rewalk     = .lP$Param$Rewalk            # TRUE after the corpus has grown
)
```

The corpus index lives in the store rather than in a parquet beside it. That is what makes "which
documents still need labelling" a single anti-join instead of a set operation across two storage
layers, and it is why the store can answer the three questions above without help.

```{r}
#| label: check-docid
# The labelled sample and the corpus must use the same identifier, or nothing downstream joins. This
# is cheap to assert and expensive to discover late: a mismatch produces a perfectly ordinary table
# of labels that merges onto nothing.
# Written to a temporary table and joined, rather than passed as a bound list. A list parameter is
# backend-specific syntax, and this check exists to catch a problem rather than to become one.
DBI::dbWriteTable(con, "tmp_labelled", tibble::tibble(DocID = tab_prep$DocID),
                  temporary = TRUE, overwrite = TRUE)
n_match <- DBI::dbGetQuery(
  con, "SELECT COUNT(*) AS n FROM corpus c INNER JOIN tmp_labelled t ON t.DocID = c.DocID"
)$n[[1]]

tibble::tibble(
  Check = c("Labelled documents", "Found in the corpus index", "Corpus documents"),
  n     = c(nrow(tab_prep), n_match, n_corpus)
) |>
  tbl_out(.title = "Do the identifiers line up?")

if (n_match < nrow(tab_prep)) {
  cli::cli_alert_warning(
    "{nrow(tab_prep) - n_match} labelled document{?s} {?is/are} absent from the corpus index."
  )
}
```

```{r}
#| label: build-specs
# WHAT WILL RUN, resolved before anything runs. Each row is one engine, one task, one configuration,
# and the key everything it writes is scoped by.
# A list rather than a vector so NULL survives as one element meaning "each task's own crown", which
# c() would flatten away.
lens_ <- if (is.null(.lP$Param$MaxLen)) list(NULL) else as.list(.lP$Param$MaxLen)

spec_bert <- purrr::map(.lP$Param$Tasks, function(.t) {
  purrr::map(lens_, function(.m) {
    app_pick_model(
      .dir_bert    = .dir_bert,        # where 03B deployed its models
      .tab_overall = tab_overall,      # supplies the context length and the score
      .crown       = bert_crown,       # what 03B crowned per task
      .task        = .t,               # the task
      .max_len     = .m                # NULL takes that task's crown
    )
  }) |>
    purrr::list_rbind()
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(Engine = "bert",
                RunKey = purrr::pmap_chr(list(Task, ConfigName, MaxLen),
                                         \(.t, .c, .m) app_run_key("bert", .t, .c, .m)))

spec_kw <- purrr::map(.lP$Param$Tasks, function(.t) {
  app_pick_lexicon(
    .dir_kw    = .dir_kw,              # where 03C published its tables
    .catalogue = kw_cat,               # what it marked
    .task      = .t,                   # the task
    .n_words   = .lP$Param$NWords      # NULL takes the marked window
  )
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(Engine = "keyword",
                RunKey = purrr::pmap_chr(list(Task, ConfigName, NWords),
                                         \(.t, .c, .w) app_run_key("keyword", .t, .c, .w)))

specs <- dplyr::bind_rows(spec_bert, spec_kw)

specs |>
  dplyr::select(Engine, Task, RunKey, dplyr::any_of(c("MaxLen", "NWords", "Tau")), ConfigName) |>
  tbl_out(.title = "What this run will apply")
```

```{r}
#| label: report-status
#| results: asis
app_report_status(.tab = app_status(.con = con, .specs = specs), .n_corpus = n_corpus)
```

# Benchmark

Before a pass that runs for hours, a pass that runs for minutes. It answers three questions.

**Does the seam work at all** -- a checkpoint on disk, a Python interpreter, a parquet round trip,
labels coming back.

**What does each setting cost** -- the context length above all. Attention is quadratic in sequence
length, so 512 is not twice 256 but somewhere between twice and four times, and the only way to know
which is to measure it on this machine with these documents.

**What would the corpus cost** -- the rate projected forward. On a short run this is pessimistic: the
first chunk on Apple silicon pays for kernel compilation and never pays again.

Two properties make this safe to run on every render. **It writes no labels** -- the predictions are
produced and discarded -- so it is free to price a context length nobody intends to deploy, and it
cannot consume the queue the real pass will work through. And **it is keyed on what it varied**, so a
combination already measured is read back rather than run again: minutes on the first render, seconds
afterwards.

```{r}
#| label: benchmark-grid
# THE GRID IS THE STUDY DESIGN, so it is written here rather than assembled inside a function. Every
# deployed context length for every task: the cost question is what the longer window is worth, and it
# cannot be answered by timing only the one that ships.
grid_bench <- purrr::map(.lP$Param$Tasks, function(.t) {
  purrr::map(.lP$Param$BenchLens, function(.m) {
    app_pick_model(
      .dir_bert    = .dir_bert,
      .tab_overall = tab_overall,
      .crown       = bert_crown,
      .task        = .t,
      .max_len     = .m                       # an explicit length, not the crown
    )
  }) |>
    purrr::list_rbind()
}) |>
  purrr::list_rbind() |>
  tidyr::expand_grid(BatchSize = .lP$Param$BenchBatch) |>
  dplyr::mutate(Engine = "bert")

bench_docs <- app_bench_docs(.con = con, .n = .lP$Param$Rehearsal)
```

The sample is the same documents every time, taken in identifier order from the corpus rather than
from what is outstanding. A grid comparing two lengths on two different samples measures the samples
as much as the lengths, and the effect being looked for is a factor of two at most.

```{r}
#| label: benchmark-run
#| results: asis
bench <- app_benchmark(
  .con        = con,                   # the store, which remembers what has been measured
  .docs       = bench_docs,            # the fixed sample
  .grid       = grid_bench,            # task by context length by batch size
  .python     = .lP$Engine$Python,
  .script     = .lP$Engine$Bert,
  .chunk_size = .lP$Param$ChunkSize    # so the model-load cost is timed as it would be paid
)

app_report_benchmark(.tab = bench, .n_corpus = n_corpus)
```

The context length is passed explicitly and never allowed to default. A model applied at a length it
was not fitted under encodes its input differently from its training data, produces perfectly ordinary
labels, and says so nowhere.

# The transformer

Three tasks, each at the context length resolved above. The pass writes every chunk before reading the
next, so an interruption costs the chunk in flight and nothing else.

The broad label is produced by its own model rather than rolled up from the detailed prediction. 03B
publishes the roll-up and 03E found the two routes equivalent, so the roll-up remains available; what
running the model buys is a second, independent opinion on every document, which the roll-up cannot
give because it is a function of the first.

```{r}
#| label: pass-bert
#| results: asis
run_bert <- purrr::map(seq_len(nrow(spec_bert)), function(.i) {
  s_ <- spec_bert[.i, ]
  app_pass(
    .con        = con,
    .spec       = s_,
    .label_fn   = function(.d) list(Labels = app_bert_chunk(
      .docs       = .d,
      .artifact   = s_$Artifact,
      .max_len    = s_$MaxLen,
      .python     = .lP$Engine$Python,
      .script     = .lP$Engine$Bert,
      .batch_size = .lP$Param$BatchSize
    )),
    .chunk_size   = .lP$Param$ChunkSize,
    .limit        = NULL,                       # NULL takes everything outstanding
    .report_every = .lP$Param$ReportEvery       # chunks between progress lines
  ) |>
    dplyr::mutate(Engine = "bert", Task = s_$Task, .before = 1)
}) |>
  purrr::list_rbind()

app_report_timing(.tab = run_bert, .n_corpus = n_corpus)
```

# The keyword table

Two steps per chunk, and the split is the point. `keyword_apply.py` reports which terms of the
published lexicon occur in each document, under the analyzer the table was mined with. `kw_decide()`
turns those terms into a class, at the threshold 03C published, using the same function that measured
the table's precision.

Both are stored. The labels are what a reader conditions on; the hits are the evidence trail, and they
are what lets a revised threshold be applied by re-running the decision rule over stored rows instead
of the lexicon over the corpus.

```{r}
#| label: pass-keyword
#| results: asis
run_kw <- purrr::map(seq_len(nrow(spec_kw)), function(.i) {
  s_       <- spec_kw[.i, ]
  classes_ <- sort(unique(tab_prep[[s_$Task]]))
  app_pass(
    .con        = con,
    .spec       = s_,
    .label_fn   = function(.d) app_keyword_chunk(
      .docs    = .d,
      .spec    = s_,             # carries the window, stopword regime and threshold it was mined at
      .classes = classes_,       # the task's categories, from the labelled sample
      .python  = .lP$Engine$Python,
      .script  = .lP$Engine$Keyword
    ),
    .chunk_size   = .lP$Param$ChunkSize,
    .limit        = NULL,
    .report_every = .lP$Param$ReportEvery       # chunks between progress lines
  ) |>
    dplyr::mutate(Engine = "keyword", Task = s_$Task, .before = 1)
}) |>
  purrr::list_rbind()

app_report_timing(.tab = run_kw, .n_corpus = n_corpus)
```

# Results

```{r}
#| label: results-summary
#| results: asis
app_summary(.con = con, .specs = specs) |>
  tbl_out(
    .title = "What each run produced",
    .pct   = "Coverage",
    .notes = c(
      Coverage = paste("Share of the corpus index carrying a label from this run. The transformer",
                       "commits everywhere, so anything below one is a document it could not read.",
                       "The keyword table abstains by design and its coverage is a property of the",
                       "lexicon rather than a fault."),
      MeanTop1 = paste("Mean top-class probability. For the keyword table this is Power, a Wilson",
                       "lower bound on the firing term's training precision, and is not comparable",
                       "with a softmax.")
    )
  )
```

```{r}
#| label: results-distribution
#| results: asis
purrr::walk(seq_len(nrow(spec_bert)), function(.i) {
  s_ <- spec_bert[.i, ]
  tbl_out(
    .tab   = app_distribution(.con = con, .spec = s_),
    .title = paste0("Corpus composition -- ", s_$Task),
    .pct   = c("Share", "MeanTop1"),
    .notes = c(MeanTop1 = "Mean top-class probability within the category.")
  )
})
```

Read the composition against the labelled sample's own distribution. The sample was drawn to cover the
categories rather than to mirror the corpus, so the two are not expected to match -- but a category
that is common in the sample and near-absent here, or the reverse, is worth understanding before the
labels are used.

```{r}
#| label: results-failures
#| results: asis
fail <- app_failures(.con = con)
if (nrow(fail) == 0L) {
  cli::cli_alert_success("No document failed.")
} else {
  tbl_out(
    .tab   = fail,
    .title = "Documents that could not be labelled",
    .notes = c(Reason = paste("Recorded, not blacklisted. These documents return to the queue on the",
                              "next pass, so a transient read failure resolves itself and a genuinely",
                              "empty file simply reappears here."))
  )
}
```

# The released file

The store is the archive: long, keyed by run, holding every term hit and every timing. This is the
deliverable -- one row per document, one column per thing a reader needs, in the shape a merge wants.

**One file per context length.** The store keys every run on its own length, so 256 and 512 coexist
without mixing, and each produces its own release. The keyword table has no context length and is
shared by both.

Both engines ship, and their scores are named apart. `BertClassDetailedProb` is a softmax probability
over classes; `KwClassDetailedPower` is a Wilson lower bound on the firing term's training precision.
Both live between zero and one and neither is the other, so naming both of them `Prob` would put two
incomparable quantities in adjacent columns and invite the comparison 03E ruled out.

Where the lexicon was silent -- or where its top two classes tied, which the decision rule treats as a
refusal rather than something to break -- the keyword columns are `NA` rather than a sentinel. Carried
through as a category it would grow a phantom class holding half the corpus in every tabulation.

```{r}
#| label: release-write
#| results: asis
releases <- purrr::map(lens_, function(.m) {
  specs_ <- if (is.null(.m)) specs else {
    specs |> dplyr::filter(.data$Engine == "keyword" | .data$MaxLen == .m)
  }
  rel_ <- app_release(
    .con      = con,                  # the store
    .specs    = specs_,               # this length's transformer runs plus the shared lexicon
    .tab_prep = tab_prep,             # supplies the detailed-to-broad mapping
    .tasks    = .lP$Param$Tasks       # column-block order in the released file
  )
  app_write_release(
    .tab      = rel_,
    .con      = con,
    .specs    = specs_,
    .dir      = .lP$Output$Release,
    .max_len  = .m,                   # stamped into the file name
    .n_corpus = n_corpus              # for the completeness statement
  )
  rel_
})
```

Rows are documents carrying **every** transformer label. One reached by the detailed pass and not yet
by the broad one leaves rather than arriving with a hole: a file where a cross-tabulation silently
drops rows reports a number computed on a subset while a reader believes they are looking at the
corpus. What is left out is counted above rather than hidden, which is the same information without
the trap.

A release written while a pass is still running is stamped `_partial` in its file name. It is a
well-formed file either way, and nothing inside it would otherwise say how much of the corpus it
covers.

```{r}
#| label: release-schema
#| results: asis
tbl_out(
  .tab   = app_release_schema(.tab = releases[[1]]),
  .title = "What the released columns mean",
  .notes = c(Column = paste("Read from the released table rather than typed, so a column added",
                            "upstream cannot go undocumented."))
)
```

```{r}
#| label: disconnect
# LAST, and it has to be: everything above reads the store, and the release is the last thing that
# does. Closing before it produced an "Invalid connection" several frames deep in the engine rather
# than a sentence saying the store was shut.
DBI::dbDisconnect(con, shutdown = TRUE)
```

# Next

The store holds raw labels: one row per document per run, with the top two classes and their
probabilities, and the term hits behind every keyword decision. Nothing is exported yet.

The release above is what a merge wants. What remains is downstream: whether the concurrence flag is
worth conditioning on in the regressions is a question for the analysis rather than for this document,
and the manifest beside each file is what lets that analysis be re-run against a different context
length without re-labelling anything.
