---
title: "Entity Resolution -- Spans into the Published Variables (04C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120)   # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: 03A
# aliases the table helpers at SOURCE time, so sourcing it first throws part-way through the file.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the console formatter and the contract-type vocabulary; 04A the entity vocabularies and
# the store; 04B the anchor logic, the session helper and the date cleaner. Sourcing rather than
# copying is what keeps the anchor this document validates against identical to the one 04B
# measured with.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract", "04B-EntityMeasure"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04C-EntityResolve.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A extracted candidates and described them. 04B measured which engine to keep, which window to
read, and which of the two reading sessions' rules survive contact with the EDGAR anchors. Neither
produced a variable.

This document does. It applies the settled policy to the candidate store, assigns a role to each
surviving span, and collapses those into one row per contract carrying the parties, the contract
dates, the party locations, and what can honestly be said about value.

## It resolves what 04D will produce, not what 04A extracted

The store holds eight engines over full text. The corpus pass will run **one engine per label over a
capped window**. Resolving the union here would validate a pipeline nobody deploys, so the candidate
set is filtered through `extraction_policy.parquet` first and every number below describes the
deployed configuration rather than the extraction that informed it.

## Three constraints inherited from the measurement

**Role attaches to an occurrence, never to a string.** A reading session found "New York" serving as
a party address, as the governing law, as a court venue and inside an exchange name within one
contract. Any design that resolves a place once per document is wrong before it starts, so the
geographic output below is a mix of roles rather than a location.

**Party counts need deduplication.** Mentions per document are inflated by length; mentions per
thousand characters are deflated by repetition. The truth is bracketed between two measures that are
each wrong in a known direction, and only collapsing names to a common form resolves it.

**A stop matches a whole span, never a substring.** A rule against `company` applied as a substring
removes *Blue Ridge Real Estate Company*, which is a party.

## The duration measure is the point of the date section

The published contract term is the latest date found in a document minus its filing date. A referee
observed that it carries a standard deviation of **46.8 years** on debt contracts -- impossible for
an instrument whose mean term is under three years, and the signature of statutory references and
long-dated maturities entering a maximum.

Both measures are computed here, on the same documents, side by side. The difference is shown rather
than argued.

## Money is the honest weak case and stays that way

EDGAR records no contract value, so nothing about amounts is validated the way parties, dates and
places are. Two things are still carried: the largest amount in a document, which a reading session
argued separates an aggregate principal from the per-share prices that repeat around it; and the
count of redaction markers, which is a variable in its own right because the figures withheld are
systematically the commercially material ones.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb",
    # Written by 04B: the surviving rules, and the engine and window per label.
    Kept    = "2_output/04B-EntityMeasure/rules_kept.parquet",
    Policy  = "2_output/04B-EntityMeasure/extraction_policy.parquet"
  ),
  Output = list(
    Roles = utils_file_path(.dir_main, "span_roles.parquet"),          # one row per resolved span
    Vars  = utils_file_path(.dir_main, "contract_variables.parquet")   # one row per contract
  ),
  Params = list(
    CtxMax  = 400L,    # widest context materialised; caps the reach of any rule
    HeadPos = 0.10,    # an organisation this far into the document, with no cue, still reads as a
                       # party: the preamble is where parties are named and a cue list is never
                       # complete
    # Redaction markers closer than this belong to one withheld thing. A redacted schedule puts a
    # marker in every cell, and 85% of all markers on this sample come from 106 documents, so the
    # count that means "how much was withheld" is regions rather than markers.
    RedactGap = 200L
  )
)

# Same formats 04B parsed with. Naming them here rather than sourcing a constant keeps the two
# documents' date handling visibly identical instead of implicitly so.
.DATE_FORMATS <- c(
  "%B %d, %Y", "%B %d %Y", "%b %d, %Y", "%b %d %Y",
  "%d %B, %Y", "%d %B %Y", "%d %b, %Y", "%d %b %Y",
  "%m/%d/%Y",  "%d/%m/%Y", "%Y-%m-%d",  "%m-%d-%Y", "%Y/%m/%d", "%d-%b-%Y", "%m.%d.%Y"
)

fs::file_exists(unlist(.lP$Input))
```

# Policy

```{r}
#| label: read-policy
tab_policy <- ent_read_policy(.path = .lP$Input$Policy)
tab_keys   <- ent_anchor_keys(.path_anchors = .lP$Input$Anchors)
tab_rules  <- arrow::read_parquet(.lP$Input$Kept)

tbl_say(
  .tab = tab_policy |>
    dplyr::select(Label, Combo, CapChars, TailChars) |>
    dplyr::mutate(dplyr::across(c(CapChars, TailChars), as.integer)),
  .title = "Extraction policy this document resolves"
)
```

Every label reads full text, so the window part of this filter is a no-op and the deployed set is the
candidate store restricted to the engines the policy names. That is deliberate rather than
incidental: every candidate carries its offsets, so a window is a filter applied here at resolution
rather than a decision taken at extraction, and imposing one later costs a `WHERE` clause where
recovering one costs a corpus pass. 04B measures what a cap would have kept and what it would have
cost; nothing in this document takes one.

A label may carry more than one engine. 04B unions the cheap rule arms in regardless of the ranking,
so dates run LexNLP and `dateregex` together and the spans both propose collapse to one. Adding an
engine widens the deployed set and cannot narrow it; the count below is the union.

```{r}
#| label: build-deployed
con <- ent_session(.db_path = .lP$Input$Store, .keys = tab_keys)

n_deployed <- ent_deploy_candidates(
  .con       = con,
  .policy    = tab_policy,     # one engine per label, and that label's window
  .path_text = .lP$Input$Text  # supplies document lengths, so the tail is measured from the end
)
```

# Roles

The document's own definitions come first, because they are the strongest of the organisation
filters and they are cheap. A reading session put it plainly: a span that is a single capitalised
common noun already introduced in parentheses -- Tenant, Company, Buyer, Holder -- is never an
organisation name, and a rule dropping those is worth more than the hand-written stop list beside
it. What makes it stronger than a stop list is that it is **per document**: `Company` is a defined
term in the contract that defines it, and part of a name in *Blue Ridge Real Estate Company*.

```{r}
#| label: build-defined-terms
ent_defined_terms(.con = con, .path_text = .lP$Input$Text)
```

Where several cues fire on one span with different roles, one has to win, and the rule that decides
it was wrong in a way that emptied the term variable.

04B judges a cue in a **direction**. A `signing` cue is validated by lift *above* the base rate,
because the anchor is the contract's own date and a signing cue should concentrate on it. An
`expiry` cue is validated by lift *below* it, because an expiry date falls after the filing, so a
correct expiry cue must avoid the anchor. The two groups therefore carry high and low lift by
construction. Ranking on raw lift descending means an expiry cue can never win a contested span: it
wins only spans no signing cue reaches. That is why the role landed on 22 documents of 4,398 while
the same cues fire in their thousands.

**Proximity replaces it.** The nearest matching cue wins. This needs no scale on which a
high-direction lift and a low-direction lift are comparable -- and none honestly exists, since the
two measure different things -- and it answers the question actually being asked, which is not which
cue is best but which cue is *about* this span. Ties in distance break on the narrower declared
window, which is the reading session's own statement of how specific a cue is.

The change was made in the expectation that it would rescue the expiry role, and **it does not**.
The table below is what settles that, and it is reported rather than quietly dropped because a
prediction that failed is evidence about the thing predicted. Expiry moves from 34 documents to 37.
Whatever is emptying the term variable, it is not this.

What the change does earn is elsewhere, and it matters more for the paper than the expiry question
does. `statutory` dates rise sharply: these are references to an Act of 1933 or an Internal Revenue
Code section, and they are exactly what inflates the published term measure to a maximum in the
thousands of years. Under lift they were being captured by broad signing cues declared at two
hundred characters; under proximity they go to `act of` and `code of`, declared at twelve and
fifteen, which are the cues genuinely adjacent to them. `other` collapses in the same movement, as
`base rent` at a 240-character window stops winning spans it was never about.

```{r}
#| label: compare-tiebreak
tab_tiebreak <- ent_compare_tiebreak(
  .con       = con,
  .path_text = .lP$Input$Text,
  .rules     = tab_rules,       # the rules 04B measured, with their lifts and declared windows
  .ctx_max   = .lP$Params$CtxMax,
  # The chosen rule is applied LAST, so the roles table is left under it and nothing below depends
  # on a restore executing.
  .tiebreaks = c("lift", "window", "proximity")
)

tab_tiebreak |>
  tidyr::pivot_wider(
    names_from = Tiebreak, values_from = c(NSpans, NDocs), values_fill = 0L
  ) |>
  tbl_say(.title = "What the tie-break changes, role by role")
```

A methodological change of this kind is measured rather than asserted, and the measurement here
refutes the reason the change was proposed while supporting the change itself. Read the rows in this
order: `DATE expiry`, which barely moves and sends the term question to the coverage grid below;
`DATE statutory` and `DATE other`, which move in opposite directions by hundreds of documents and
are the reassignment that justifies proximity; and `MONEY per_unit`, which rises by half again,
because its cues are right-sided and tight and were losing to broader neighbours.

```{r}
#| label: assign-roles
n_roles <- ent_assign_roles(
  .con       = con,
  .path_text = .lP$Input$Text,
  .rules     = tab_rules,       # the rules 04B measured
  .ctx_max   = .lP$Params$CtxMax,
  .tiebreak  = "proximity"      # nearest cue wins; ties break on the narrower declared window
)
```

A span no cue reaches keeps a null role and is carried rather than discarded. For organisations that
matters, because position in the preamble is itself evidence and the party resolver uses it.

# Variables

```{r}
#| label: resolve-parties
tab_parties <- ent_resolve_parties(.con = con, .head_pos = .lP$Params$HeadPos)
tab_dates   <- ent_resolve_dates(.con = con, .formats = .DATE_FORMATS)
tab_places  <- ent_resolve_places(.con = con)
tab_value   <- ent_resolve_value(.con = con, .gap = .lP$Params$RedactGap)

# The published measure has to come from the UNFILTERED store over full text. Taking it from the
# deployed set leaves only preamble dates, every one of which precedes the filing, and the measure
# comes out negative -- a different quantity wearing the published name.
tab_pubdates <- ent_published_dates(.con = con, .formats = .DATE_FORMATS)

tab_vars <- ent_assemble(
  .keys     = tab_keys,
  .parties  = tab_parties,
  .dates    = tab_dates,
  .places   = tab_places,
  .value    = tab_value,
  .pubdates = tab_pubdates
)

ent_report_resolve(.n_deployed = n_deployed, .n_roles = n_roles, .tab = tab_vars)
```

# Contract term

```{r}
#| label: compare-duration
tab_duration <- ent_report_duration(.tab = tab_vars)
```

Read the standard deviation and the maximum together. The published definition takes the latest date
anywhere in the document, so a reference to an Act of 1933 or a maturity in 2099 enters the term of
a contract that runs for two years, and a single such document moves the moment for the whole class.
The role-classified measure can only see dates a cue reached, which is a narrower set and a smaller
one -- the trade is coverage for a measure that means what it says.

## Does the window preserve an expiry date?

The extraction now reads full text, so the grid below no longer chooses anything. It remains, and it
remains the most useful table in this document, because it decomposes where the term variable is
actually lost -- and that decomposition was invisible while a cap was in force.

The history is worth keeping in view. The character grid in 04B ranks windows on how often they
recover the **anchor**, and the date anchor is the contract's own date, which sits in the preamble.
Nothing there measures whether an expiry date survives the same window. A cap was set on the first
quantity and applied to the second, and the check that appeared to vindicate it could not have done
so.

The earlier version of this check could not settle it, and produced a flat line that looked like a
result. It read the `roles` table, which descends from the already windowed candidate set, so its
5,000 and 10,000 head rows queried a table holding nothing past 3,000 characters and could not
differ from the 3,000 row whatever the truth was. And it filtered on the assigned role, which the
lift tie-break was stripping -- so widening the window admitted spans whose role the same mechanism
then removed. It measured the window *through* the defect it was being used to rule out.

Both faults are fixed by going back to the source. Candidates come from the unfiltered store, so a
wide head has something to find, and a span counts when any expiry cue reaches it rather than when
the tie-break awarded it the role. The result is a **ceiling**: what a window could deliver, not
what the deployed pipeline will. That is the right quantity for choosing a cap, because a cap that
cannot clear the ceiling is disqualified whatever the resolver does afterwards.

```{r}
#| label: measure-expiry-coverage
purrr::map(list(NULL, tab_policy), function(.p) {
  ent_role_coverage(
    .con       = con,
    .path_text = .lP$Input$Text,   # the context the cues are matched in
    .rules     = tab_rules,        # cues are applied here, not read off the role assignment
    .label     = "DATE",
    .roles     = "expiry",         # the role the anchor cannot speak to
    .head      = c(3000L, 5000L, 10000L, 20000L, 100000000L),  # the last is the full document
    .tail      = c(0L, 2000L, 5000L, 10000L),
    .ctx_max   = .lP$Params$CtxMax,
    .policy    = .p                # NULL pools every engine; the policy restricts to the one that runs
  )
}) |>
  purrr::list_rbind() |>
  dplyr::select(Engines, Head, Tail, NDocs, PctDocs) |>
  tidyr::pivot_wider(
    names_from = Engines, values_from = c(NDocs, PctDocs), values_fill = 0L
  ) |>
  dplyr::mutate(dplyr::across(dplyr::starts_with("PctDocs"), \(.x) tbl_pct(.x))) |>
  tbl_say(.title = "Documents with an expiry cue reaching a date, inside the window")
```

**Two columns, because there are two ceilings and they answer different questions.** Pooling every
engine in the store gives the true upper bound on what is recoverable at all. Restricting to the
engine the policy actually runs gives the number comparable to what the resolver produced. Reading
one against the other mixes a window effect with an engine effect, which is what the first version
of this table did.

Three readings, in order.

**The full-document row is the ceiling, and it is low.** Even reading every character of every
contract, an expiry cue reaches a date in well under half the sample. So this is a cue problem
before it is a window problem: the seven expiry cues are not enough vocabulary for the ways a
contract states its term, and no window can fix that. Whatever the window decision, the term
variable will not cover most of the corpus until the cue list grows.

**A cap would nonetheless cost a great deal here.** Compare the 3,000-plus-5,000 row -- the window
that was in force -- against the full-document row. The gap is roughly a factor of three, so the cap
was discarding most of what the expiry cues could reach, on a variable that had not yet been built
and against evidence that did not yet exist. That is the concrete case for extracting over full text
and filtering afterwards.

**The tie-break gap is the smallest of the three.** This table counts a document when *any* expiry
cue reaches a date, while the role assignment is winner takes all, so a span on which the expiry cue
loses counts here and not there. Set the deployed-engine figure at the current window against the
resolved contract ends in the Resolution table above: the difference is real but modest, and it is
the last term rather than the first.

**The engine is the largest gap by an order of magnitude**, and it was not on the list of suspects.
Compare the two columns at any row. The engine deployed for dates recovers a small fraction of what
the store as a whole contains, and the reason is structural rather than accidental: 04B ranks
engines on recall against the EDGAR anchor, and for dates that anchor is the contract's own date,
which sits in the preamble. An engine that is excellent at the preamble formula and blind to term
clauses scores at the top of that table and delivers almost nothing here.

That is the same criticism this document already makes of the window -- chosen on a start date and
applied to an end date -- and it turns out to hold for the engine too. The table below asks which
engines the expiry cues can actually reach, so the choice can be revisited against the quantity it
is meant to serve.

```{r}
#| label: measure-expiry-by-engine
ent_role_by_engine(
  .con       = con,
  .path_text = .lP$Input$Text,
  .rules     = tab_rules,
  .label     = "DATE",
  .roles     = "expiry",
  .ctx_max   = .lP$Params$CtxMax
) |>
  dplyr::mutate(PctDocs = tbl_pct(.data$PctDocs)) |>
  tbl_say(.title = "Which engine's dates an expiry cue can reach, over full text")
```

Read this beside `SpansPerAnchor` from 04B rather than on its own. Reaching more dates is recall,
and the precision of those reaches is unmeasured here as it is everywhere in this family: an engine
proposing five times the spans may reach five times the expiry dates and be no better for it. What
the table settles is whether the current engine is leaving a large recoverable set on the table, not
which engine should replace it.

# Places

```{r}
#| label: report-places
tab_placemix <- ent_report_places(.tab = tab_vars)
```

This is the answer to the question a reviewer asked of Figure 6: whether the countries counted are
the locations of the contracting entities or mentions of somewhere else. It is an answer about
**occurrences**, because the same place name serves several roles inside one contract and a
per-document location would be the wrong object to report.

# Validation

```{r}
#| label: validate-variables
tab_val <- ent_report_validation(.tab = tab_vars)
```

The first row is the one carrying weight. The filer is a party to its own contract, so a resolved
party set that omits it is missing a party that is certainly there -- and unlike a precision figure,
this needs no hedging about counterparties the anchor cannot see.

The third row is arithmetic rather than evidence: a contract cannot end before it starts, and
anything below 100% there is a resolution error rather than a finding.

# Robustness

```{r}
#| label: inspect-by-class
tab_vars |>
  dplyr::summarise(
    NDocs        = dplyr::n(),
    MedParties   = stats::median(.data$NParties, na.rm = TRUE),
    PctWithStart = mean(!is.na(.data$ContractStart)),
    PctWithEnd   = mean(!is.na(.data$ContractEnd)),
    PctWithValue = mean(!is.na(.data$MaxAmount)),
    MedRedact    = stats::median(dplyr::coalesce(.data$NRedact, 0L)),
    PctRedacted  = mean(dplyr::coalesce(.data$NRedact, 0L) > 0L),
    .by = Class
  ) |>
  dplyr::arrange(dplyr::desc(.data$NDocs)) |>
  dplyr::mutate(dplyr::across(dplyr::starts_with("Pct"), \(.x) tbl_pct(.x))) |>
  tbl_say(.title = "Resolution by contract type")
```

Coverage is not uniform and should not be reported as though it were. A variable present in a third
of leases and nine tenths of credit agreements is two different variables, and the column that
matters for the paper is which contract types can carry each one at all.

```{r}
#| label: inspect-unassigned
DBI::dbGetQuery(con, paste0(
  "SELECT Label, COUNT(*) AS Spans, ",
  "  SUM(CASE WHEN Role IS NULL THEN 1 ELSE 0 END) AS NoRole ",
  "FROM roles GROUP BY Label ORDER BY Label"
)) |>
  dplyr::mutate(
    dplyr::across(c(Spans, NoRole), as.integer),
    PctNoRole = tbl_pct(.data$NoRole / .data$Spans)
  ) |>
  tbl_say(.title = "Spans no cue reached")
```

A high share here is not a failure of the rules so much as a statement about how much of the
candidate pool is noise: most organisation spans in a contract are not parties, and a cue list that
labelled all of them would be labelling the wrong thing.

# Deployment

```{r}
#| label: write-artifacts
DBI::dbExecute(con, paste0(
  "COPY (SELECT DocID, Label, Start, Stop, Span, SpanNorm, LabelRaw, Pos, Role FROM roles) TO '",
  as.character(fs::path_abs(.lP$Output$Roles)), "' (FORMAT PARQUET)"
))
arrow::write_parquet(tab_vars, .lP$Output$Vars)

DBI::dbDisconnect(con, shutdown = TRUE)

tibble::tibble(
  Artifact = c("Span roles", "Contract variables"),
  Path     = c(.lP$Output$Roles, .lP$Output$Vars)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04C")
```

# Overview

## The contract term, both ways

```{r}
#| label: fig-duration
#| fig-height: !expr plot_height(2)
#| fig-cap: "Contract term under the published definition and under role classification. The axis is
#|   truncated at sixty years; the untruncated moments are in the table above."
ent_plot_duration(
  .tab       = tab_vars,
  .max_years = 60,     # the published measure runs to thousands; see the caption
  .bins      = 60L
)
```

The published panel is the one to read for its right tail; the axis is truncated at sixty years and
the values beyond it are the reason the standard deviation is what a referee found it to be.

## Place occurrences by role and contract type

```{r}
#| label: fig-place-roles
#| fig-height: !expr plot_height(length(plot_levels("ClassDetailed")))
#| fig-cap: "Share of place occurrences carrying each role, by contract type. Occurrences rather
#|   than documents: one place name serves several roles inside one contract."
ent_plot_place_roles(
  .tab       = tab_vars,
  .key_class = "ClassDetailed"   # the vocabulary 03A registered, so rows match the 03 family
)
```

Read the unassigned share first. It is the largest segment in every contract type, and it is the
honest bound on this variable: a place occurrence no cue reached is carried rather than guessed at,
so the roles below it describe a minority of the geography the extraction found.

## Everything again

```{r}
#| label: report-everything
ent_report_all_resolve(.n_deployed = n_deployed, .n_roles = n_roles, .tab = tab_vars)
```

# Next

**04D** applies the same policy to the corpus. It needs nothing this document has not written: the
engine and window come from `extraction_policy.parquet`, the rules from `rules_kept.parquet`, and
the resolution logic is the functions above run over a larger store.

Two things this document cannot settle, and they should reach the paper as limitations rather than
be discovered later. **Money remains unvalidated** -- the largest-amount heuristic and the redaction
count are carried because they are the best available, not because either has been checked against
anything. And **nothing here validates the variables themselves**: the anchors confirm that the
filer appears among the resolved parties and that the contract date precedes its filing, which
establishes the extraction is finding real things, not that the party count, the term or the value
are right. That needs a document-level gold set of fifty to eighty contracts, and it is the one
piece of this family that cannot be built from EDGAR facts or a reading session.
