---
title: "Entity Rules -- Where Each Organisation Is (04B2)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")
source("1_code/_Commons/_Entity.R", encoding = "UTF-8")

# 03A owns the contract-type vocabulary; 04A owns the sample, the canonical text and the store. This
# document does NOT source 04B1: it reads 04B1's artifact, which is the point of writing one.
purrr::walk(
  .x = c("03A-ClassifyPrepare", "04A-EntityExtract"),
  .f = function(.s) {
    source(file = init_create_script_fun(.dir_here = here::here(), .name_script = .s),
           encoding = "UTF-8")
  }
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04B2-Rules-GPE.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04B1 found a contracting party in each contract and labelled every other organisation beside it.
This document answers one question about each of them: **where is it**.

That question exists because of a referee comment. The published paper reports 1.9 geoentities per
contract and a figure of occurrence by continent, and referee 1 wrote that *it is unclear whether the
countries mentioned are the locations of the contracting entities... it seems possible that mentioned
countries may simply be mentioned in contract pertaining to some planned business activity.* Correct.
The answer is not to find more places; it is to attach the ones already found to the organisation
they belong to.

## The grain is one row per organisation

Not one per document. A document-level variable is then a filter on that table rather than a separate
computation, and *which party is this the address of* becomes a column rather than a question the
release cannot answer. Every organisation is computed; filer and counterparty are a column, exactly
as in 04B1. An organisation with nothing beside it gets a blank, and the count of what was near it
says whether that means "nothing was there" or "something was and did not resolve".

## One rule

**The place nearest an organisation is that organisation's place.** Search backwards, because a
preamble names the company and then qualifies it -- `X, a Delaware corporation, with offices at 100
Main Street, Springfield, Illinois`. Stop at the first organisation. Refuse beyond the reach.

## One cue, and only because proximity cannot reach it

A governing-law clause names a jurisdiction nowhere near a party: 95% of the spans its cue catches
are attached to no organisation at all. An earlier version also carried incorporation and location
cues, which fired beside a party that proximity had already found -- and, because the cue outranked
proximity, assigned a role to 14,227 spans attached to nothing. Those two families are gone. One
signal per question.

Where the clause fires and names no place -- `the laws of the State in which the Premises are
located` -- that is recorded as **self-referential** rather than as nothing. It is a real contract
term, not a coverage gap.

## Cities are an input, not an output

A city resolves to its state and the **state** is released; no reported variable is a city. That is
what lets the location variable be read against the incorporation variable, because they then live on
the same tier.

Two thirds of city names exist in several states. An ambiguous city takes whichever of **its own
candidate states** the contract itself names, nearest to the city -- which is what stops a
`Springfield` beside a Delaware corporation from becoming Springfield, Delaware. It uses no new data
and it is the same evidence the extractor already relies on, since a word-like city name is only
emitted where a state anchor sits within forty characters.

Cities stay in the span-level artifact because they are what validates against EDGAR's registered
address: **45.0% at city level against 3.2% at state level** on the previous render. That gap is the
entire argument for resolving cities to states rather than reading state spans as locations.

## Both engines, marked

LexNLP resolves jurisdictions and reaches no cities; the gazetteer reaches cities and resolves nothing
in the store. Every table is built **per engine and stacked**, so a combined view is a choice the
reader makes rather than one this file makes.

## Noise is expected and is not eliminated

No place-name stoplist. No check that a city beside a party is the party's own rather than its
lawyer's. Every table carries the unadjusted count -- every distinct place named anywhere -- so a
reader sees what the rule removed.

**Coverage per organisation will read lower than coverage per document, and that is arithmetic.** A
document counts as covered when any party has a state; an organisation counts only when it does.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 04A's canonical text. Every offset in this family indexes this file.
    Text    = "2_output/04A-EntityExtract/sample_text.parquet",
    # 04A's sample table: labels, folds and the registered addresses.
    Anchors = "2_output/04A-EntityExtract/sample_anchors.parquet",
    # 04A's candidate store, opened read-only.
    Store   = "2_output/04A-EntityExtract/Store/EntityCandidates.duckdb",
    # The gazetteer's own hierarchy, rebuilt by 1_code/_Scripts/rebuild-geo-lookup.R.
    Lookup  = "contracts-engine/data/gazetteer/geo_lookup.parquet",
    # 04B1's organisations, with the position and the role every place attaches to.
    Org     = "2_output/04B1-Rules-ORG/roles_org.parquet"
  ),
  Output = list(
    Spans = utils_file_path(.dir_main, "roles_gpe.parquet"), # one row per place span
    Org   = utils_file_path(.dir_main, "geo_org.parquet"),   # one row per organisation -- the release
    Doc   = utils_file_path(.dir_main, "geo_doc.parquet")    # one row per document -- a view of it
  ),
  Params = list(
    # BOTH ENGINES, marked and stacked. Never pooled inside a table.
    Combos  = c(lexnlp = "lexnlp", gazetteer = "paper:gazetteer-v1"),
    Extras  = c("GeoName", "GeoAlias", "GeoCategory", "Iso2", "Iso3"),
    LawWin  = 120L,     # characters read before a span for the governing-law cue
    Bins    = 50L,      # bins across relative position in the density figure
    ReadN   = 10L,      # spans read back in context
    ReadCtx = 200L,     # characters either side of a span
    CheckN  = 500L,     # spans cut from the text and compared to what was stored
    MapCombo = "gazetteer", # the engine the maps and the class table are drawn from
    LabelN      = 12L,  # countries labelled with their count on a world map
    LabelStates = 15L,  # states labelled on the US map
    Seed    = 42L       # fixed, so the same documents are read on every render
  )
)

# The attachment carried into the released artifacts. ONE REACH for every level: states attach at a
# median of five characters and cities at seventy-six, so a per-level reach fits the data better and
# costs a paragraph in the paper to defend. It is swept as one alternative row and adopted only if
# the registered-address check says so.
.lP$Params$Spec <- geo_spec(
  .reach      = 200,   # furthest an organisation may be and still claim a place
  .reach_city = NULL,  # one number for every level
  .party_only = FALSE  # every organisation gets its geography; the role is a column
)

.lP$Params$Specs <- list(
  geo_spec(.reach = 40),
  geo_spec(.reach = 100),
  geo_spec(.reach = 200),
  geo_spec(.reach = 400),
  geo_spec(.reach = 200, .reach_city = 400),  # the per-level variant, reported not adopted
  geo_spec(.reach = 200, .party_only = TRUE)  # parties only, against every organisation
)

fs::file_exists(unlist(.lP$Input))
```

The last path is 04B1's artifact. This document reads it rather than sourcing 04B1, which is the
reason for splitting the family: a change to the date rule should not re-run the party sweep.

# Sample

```{r}
#| label: build-keys
tab_keys <- ent_anchor_keys(
  .path_anchors = .lP$Input$Anchors   # carries the registered addresses the validation needs
)

tab_lens <- ent_doc_lens(.path_text = .lP$Input$Text)

tab_org <- arrow::read_parquet(.lP$Input$Org) |>
  dplyr::select(DocID, Key, Name, Role, Start, Stop)

tibble::tibble(
  Item = c("Documents in the sample",
           "Documents with a registered address",
           "Organisations carried from 04B1",
           "...filers",
           "...counterparties",
           "...signatories and others"),
  N    = c(nrow(tab_keys),
           sum(!is.na(tab_keys$BusinessAddress)),
           nrow(tab_org),
           sum(tab_org$Role == "filer"),
           sum(tab_org$Role == "counterparty"),
           sum(!tab_org$Role %in% c("filer", "counterparty")))
) |>
  tbl_say(.title = "What this document is built on")
```

```{r}
#| label: load-lookup
tab_lookup <- geo_lookup(
  .path_lookup = .lP$Input$Lookup   # one row per name and class, every column prefixed Lk
)

tab_cand <- geo_candidates(
  .path_lookup = .lP$Input$Lookup   # every state a city name exists in, kept rather than collapsed
)
```

```{r}
#| label: load-spans
tab_raw <- purrr::imap(
  .x = .lP$Params$Combos,
  .f = function(.combo, .engine) {
    ent_load_label(
      .db_path = .lP$Input$Store,     # opened read-only
      .lens    = tab_lens,            # supplies document length
      .label   = "gpe",
      .combo   = .combo,
      .extras  = .lP$Params$Extras,   # lexnlp's resolved columns; empty on gazetteer rows
      .quiet   = FALSE
    ) |>
      geo_resolve(.lookup = tab_lookup, .engine = .engine) |>
      dplyr::mutate(Combo = .engine, .before = 1L)
  }
) |>
  purrr::list_rbind()
```

```{r}
#| label: resolve-cities
tab_geo <- tab_raw |>
  geo_city_state(.cand = tab_cand) |>   # every state a city name exists in
  geo_country()                          # ISO alpha-3, the only country key both engines produce

geo_report_resolve(.geo = tab_geo)
```

```{r}
#| label: report-cities
geo_report_city(.geo = tab_geo)
```

# Attachment

```{r}
#| label: attach-base
tab_roles <- geo_attach(
  .geo  = tab_geo,            # every place span, resolved
  .org  = tab_org,            # 04B1's organisations, with their roles
  .spec = .lP$Params$Spec     # the attachment carried into the artifacts
)
```

```{r}
#| label: build-org-table
tab_org_geo <- geo_org_table(
  .roles = tab_roles,
  .org   = tab_org,           # every organisation, so one with nothing beside it still gets a row
  .keys  = tab_keys
)

geo_report_org(.orgtab = tab_org_geo)
```

This is the release. Everything below is either a check on it or a view of it.

# Governing law

```{r}
#| label: build-law
tab_ctx <- geo_context(
  .geo       = tab_geo,
  .path_text = .lP$Input$Text,
  .win       = .lP$Params$LawWin   # characters read before the span
)

tab_law <- geo_law(
  .geo       = tab_ctx,
  .lens      = tab_lens,           # supplies every document, including those with no clause
  .path_text = .lP$Input$Text      # for the self-referential scan
)
```

```{r}
#| label: build-doc-table
tab_doc <- geo_doc_table(
  .orgtab = tab_org_geo,
  .roles  = tab_roles,
  .law    = tab_law,
  .keys   = tab_keys
)

geo_report_law(.doc = tab_doc)
```

# Validation

```{r}
#| label: validate-address
tab_validate <- geo_validate(.roles = tab_roles, .keys = tab_keys)

geo_report_validate(.tab = tab_validate)
```

```{r}
#| label: sweep-specs
tab_sweep <- geo_sweep(
  .geo   = tab_geo,
  .org   = tab_org,
  .keys  = tab_keys,            # so every specification is scored against the address, not only sized
  .specs = .lP$Params$Specs,
  .quiet = FALSE
)

geo_report_sweep(.tab = tab_sweep)
```

```{r}
#| label: validate-offsets
# The same equality the party document runs: the text cut at the stored offsets must BE the stored
# span, which is the only form of this check that can fail.
tab_check <- ent_verify_span(
  .tab       = tab_roles,
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .col_span  = "Span",
  .n         = .lP$Params$CheckN,
  .seed      = .lP$Params$Seed
)

tibble::tibble(
  Check = c(
    "Text cut at the stored offsets equals the stored span",
    "Every span carries a level",
    "Every attached span carries an organisation and a distance",
    "Every unattached span carries neither",
    "Every resolved city carries a state",
    "A county appears only with a state",
    "Every organisation from 04B1 has a row per engine"
  ),
  N = c(
    sum(tab_check$Exact),
    sum(!is.na(tab_roles$GeoLevel)),
    sum(!is.na(tab_roles$OrgKey[tab_roles$Attached]) &
          !is.na(tab_roles$DistToOrg[tab_roles$Attached])),
    sum(is.na(tab_roles$OrgKey[!tab_roles$Attached])),
    sum(!is.na(tab_roles$State[tab_roles$GeoHow %in% c("unique", "nearest named")])),
    sum(!is.na(tab_roles$State[!is.na(tab_roles$County)])),
    nrow(tab_org_geo)
  ),
  Of = c(
    nrow(tab_check),
    nrow(tab_roles),
    sum(tab_roles$Attached),
    sum(!tab_roles$Attached),
    sum(tab_roles$GeoHow %in% c("unique", "nearest named")),
    sum(!is.na(tab_roles$County)),
    nrow(tab_org) * dplyr::n_distinct(tab_roles$Combo)
  )
) |>
  dplyr::mutate(Share = tbl_pct(.data$N / .data$Of)) |>
  tbl_say(.title = "Every row is expected at 100%")
```

# Reading

```{r}
#| label: read-state
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "State", .data$Attached),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "GeoUnit", "OrgName", "OrgRole", "DistToOrg"),
    .title = "States, read as the jurisdiction of the organisation before them"
  )
```

```{r}
#| label: read-city
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "City", .data$Attached,
                             .data$GeoHow == "nearest named"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = .lP$Params$ReadN,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("GeoUnit", "State", "County", "OrgName", "OrgRole", "DistToOrg"),
    .title = "Ambiguous cities resolved by a state the contract itself names"
  )
```

The block that has to be read rather than trusted. The rule required the state to be one the city
could actually be in, so a wrong answer here means the contract named two candidate states and the
nearer one was not the right one.

```{r}
#| label: read-unresolved
ent_read_spans(
  .tab       = dplyr::filter(tab_roles, .data$GeoLevel == "City", .data$Attached,
                             .data$GeoHow == "unresolved"),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("GeoUnit", "NParent", "OrgName", "DistToOrg"),
    .title = "Cities beside a party that the contract never disambiguates"
  )
```

```{r}
#| label: read-law
ent_read_spans(
  .tab       = dplyr::filter(
    tab_ctx,
    .data$GeoLevel %in% c("State", "Country"),
    stringi::stri_detect_fixed(.data$Before, "LAWS OF THE STATE OF")
  ),
  .path_text = .lP$Input$Text,
  .col_start = "Start",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("Combo", "GeoUnit", "GeoLevel"),
    .title = "Governing law, where a jurisdiction is named"
  )
```

```{r}
#| label: read-nothing
# Organisations with nothing beside them. Not a failure -- a counterparty named once in passing has
# no address in the contract -- but the block that says whether the blank is honest.
ent_read_spans(
  .tab       = tab_org_geo |>
    dplyr::filter(!.data$HasGeo, .data$OrgRole == "counterparty", .data$Combo == "gazetteer") |>
    dplyr::left_join(dplyr::select(tab_org, DocID, Key, Stop), by = dplyr::join_by(DocID,
                                                                                   OrgKey == Key)),
  .path_text = .lP$Input$Text,
  .col_start = "OrgStart",
  .col_stop  = "Stop",
  .n         = 8L,
  .ctx       = .lP$Params$ReadCtx,
  .seed      = .lP$Params$Seed
) |>
  ent_report_read(
    .cols  = c("OrgName", "OrgRole", "NGeoNear"),
    .title = "Counterparties with no place beside them"
  )
```

# Results

```{r}
#| label: report-class
geo_report_class(
  .doc   = tab_doc,
  .combo = "gazetteer"   # named, not taken as whichever engine came first
)
```

# Maps

Four views of the same count, all document-weighted: a contract either names a place or it does not,
so one table-heavy filing cannot colour a country on its own. The fill is logarithmic, because the
United States outweighs everywhere else by three orders of magnitude and a linear scale would paint
one country and leave the rest indistinguishable from empty. The largest areas carry their count.

**The first two tabs are the argument.** Unadjusted is every place the contracts name -- the
published figure of 1.9 geoentities per contract, and what referee 1 could not interpret. Parties is
the same count restricted to places this document attached to a filer or a counterparty. The
difference between them is the rule.

::: {.panel-tabset}

## Unadjusted

```{r}
#| label: fig-map-unadjusted
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Countries by the number of contracts naming a place in them, with no rule applied. Every
#|   place span counts, wherever it sits and whatever it refers to -- a party's address, a planned
#|   business activity, a court's seat. This is the map the published geoentity count would draw."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "all",        # every span, attached or not
  .level    = "country",
  .by_class = FALSE
) |>
  plot_map_world(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelN
  )
```

## Parties

```{r}
#| label: fig-map-parties
#| fig-height: !expr plot_height(6L)
#| fig-cap: "The same count, restricted to places attached to a filer or a counterparty. A country
#|   that fades between this tab and the last is one the contracts mention without any party being
#|   there, which is exactly the distinction the referee asked for."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "parties",    # attached to a filer or a counterparty
  .level    = "country",
  .by_class = FALSE
) |>
  plot_map_world(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelN
  )
```

## By contract type

One full-width map per type, in a nested tabset. A three-by-four grid of world maps was three hundred
pixels a panel: the titles clipped, the coastlines vanished and no country was distinguishable from
its neighbour. A small multiple has to be small AND legible, and a world map is not.

Each map is emitted through `knitr::knit_child()` rather than by writing headers with `cat()`. A
header printed from an `asis` chunk is markdown, but the figures beside it are output blocks knitr
wraps separately, so the two do not interleave and every map lands under the first tab. A child
document produces one properly wrapped cell per class, which is what the tabset needs.

::: {.panel-tabset}

```{r}
#| label: fig-map-class
#| results: asis
#| echo: false
tab_map_class <- geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "parties",
  .level    = "country",
  .by_class = TRUE          # computed once, then split one class at a time
)

purrr::walk(plot_levels("ClassDetailed"), function(.cls) {
  cat(
    knitr::knit_child(
      text  = c(
        "### `r .cls`",
        "",
        "```{r}",
        "#| echo: false",
        paste0("#| fig-height: ", plot_height(6L)),
        "tab_map_class |>",
        "  dplyr::filter(.data$Class == .cls) |>",
        "  plot_map_world(.val = \"N\", .log = TRUE, .name = \"Contracts\",",
        "                 .label_n = .lP$Params$LabelN)",
        "```",
        ""
      ),
      envir = environment(),
      quiet = TRUE
    ),
    sep = "\n"
  )
})
```

:::

## US states

```{r}
#| label: fig-map-states
#| fig-height: !expr plot_height(6L)
#| fig-cap: "US states by the number of contracts placing a party there. This is the tier the rule
#|   actually releases, and the one with enough mass to show structure -- a world map of US contracts
#|   is one dark country and a scattering. Delaware is incorporation rather than location, which is
#|   the distinction the registered-address check measures."
geo_map_input(
  .roles    = tab_roles,
  .keys     = tab_keys,
  .combo    = .lP$Params$MapCombo,
  .scope    = "parties",
  .level    = "state",      # the released tier
  .by_class = FALSE
) |>
  plot_map_usa(
    .val     = "N",
    .log     = TRUE,
    .name    = "Contracts",
    .label_n = .lP$Params$LabelStates
  )
```

:::

# Deployment

```{r}
#| label: write-artifacts
arrow::write_parquet(dplyr::select(tab_roles, -dplyr::any_of("Reach")), .lP$Output$Spans)
arrow::write_parquet(tab_org_geo, .lP$Output$Org)
arrow::write_parquet(tab_doc, .lP$Output$Doc)

tibble::tibble(
  Artifact = c("Place spans with the hierarchy and the organisation each attached to",
               "Where each organisation is -- the release",
               "Document view, with governing law and the unadjusted count"),
  Path     = c(.lP$Output$Spans, .lP$Output$Org, .lP$Output$Doc)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04B2")
```

`geo_org.parquet` is the release: one row per document, engine and organisation, carrying the role
04B1 assigned and the geography this document attached. Cities live only in the span file, which is
what the registered-address check reads and what anyone re-deriving the resolution would need.

# Overview

```{r}
#| label: fig-density
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Share of place spans by relative position in the document, weighted by documents, per
#|   engine. LexNLP's jurisdictions and the gazetteer's cities do not sit in the same part of a
#|   contract, which is the first sign that they are measuring different things."
tab_geo |>
  dplyr::group_split(.data$Combo) |>
  purrr::map(function(.d) {
    ent_density(.spans = .d, .bins = .lP$Params$Bins) |>
      dplyr::mutate(Combo = dplyr::first(.d$Combo))
  }) |>
  purrr::list_rbind() |>
  geo_plot_density()
```

```{r}
#| label: fig-role
#| fig-height: !expr plot_height(5L)
#| fig-cap: "What each organisation got, by the role 04B1 assigned it, as shares within the role. The
#|   filer is named first and in a preamble with its jurisdiction immediately after; a counterparty
#|   named once in passing often has nothing beside it, and that segment is the honest size of the
#|   gap."
geo_plot_role(.orgtab = tab_org_geo)
```

```{r}
#| label: fig-dist
#| fig-height: !expr plot_height(6L)
#| fig-cap: "Cumulative distribution of the distance from a place to the organisation it attached to,
#|   by level, pooled beyond 400 characters. A level rising steeply in the first fifty characters sits
#|   immediately beside a company name, which is what the preamble form predicts of a jurisdiction and
#|   not of an address."
geo_plot_dist(.tab = tab_roles, .cap = 400)
```

```{r}
#| label: report-everything
geo_report_all(
  .geo      = tab_geo,
  .orgtab   = tab_org_geo,
  .doc      = tab_doc,
  .validate = tab_validate,
  .sweep    = tab_sweep,
  .combo    = .lP$Params$MapCombo
)
```

# Next

Two things here are provisional and both are decided by a number rather than by argument. The reach
is one figure for every level; the sweep carries a per-level row and the registered-address column is
what would justify taking it. And the release is built from both engines side by side; the resolution
table says the gazetteer matches LexNLP on states, beats it on countries and adds every city, so the
gazetteer may end up carrying the release with LexNLP retained only for the subdivisions the
hierarchy has no tier for.

04B3 takes dates, which are not anchored on a party and answer a different referee. Contract duration
is currently the filing date to the farthest future date in the text, and Table 3 Panel B reports a
standard deviation of 40.78 years against a stated cap of 30 -- arithmetically impossible on
non-negative support, where the maximum is half the range. Reproducing that number is the first block
of that document.
