---
title: "Entity Extraction -- Freezing the Inputs and Running Every Engine (04A)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| include: false
#| purl: false
knitr::opts_knit$set(root.dir = here::here())

# message = TRUE is required: cli writes through the message stream under knitr, so suppressing
# messages would discard this document's entire output. comment = "" removes the "##" prefix from
# console blocks so they can be copied verbatim. Figure geometry is NOT set here -- it is declared
# once in _quarto.yml, and overriding it per document is how two documents came to render at more
# than twice the width of the rest.
knitr::opts_chunk$set(
  root.dir = here::here(),
  message  = TRUE,
  warning  = FALSE,
  comment  = ""
)

options(cli.num_colors = 1, cli.width = 120) # plain ASCII; ANSI codes paste as garbage

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r}
#| label: load-libraries
#| echo: false
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")
source("1_code/_Commons/_NER.R", encoding = "UTF-8")

# ORDER IS LOAD-BEARING HERE TOO. _Store.R supersedes three functions in _NER.R -- ner_db_init(),
# ner_db_append() and ner_db_clear() -- so it must be sourced AFTER it or the flat-table versions
# win and the per-label tables are never created. _Reads.R has no such dependency and is sourced
# beside it because it is the other half of what this document produces.
source("1_code/_Commons/_Store.R", encoding = "UTF-8")
source("1_code/_Commons/_Reads.R", encoding = "UTF-8")

# The shared design layer, sourced before anything that draws or prints. ORDER IS LOAD-BEARING: the
# level registry is rebuilt empty every time _Plots.R is sourced, so a library that registers a
# vocabulary must be sourced after it -- and 03A registers its taxonomy at SOURCE time rather than
# inside a function, so a failure part-way through that file leaves every function below it silently
# undefined. A file's top-level statements are part of its interface.
source("1_code/_Commons/_Plots.R", encoding = "UTF-8")
source("1_code/_Commons/_Tables.R", encoding = "UTF-8")

# 03A owns the sample, the folds, the contract-type vocabulary and the fixed-width console formatter
# every document in the monorepo reports through. Sourcing it means the entity work is described in
# the same table style as the classification work, orders contract types the same way in every
# figure, and joins to exactly the partition the classifiers were scored on.
source(
  file     = init_create_script_fun(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare"),
  encoding = "UTF-8"
)

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # this document's name; the output directory is derived from it
))

cat("Function File: ")
(.path_fun <- init_create_script_fun(
  .dir_here    = here::here(), # project root
  .name_script = .name_script  # resolves to 1_code/04A-EntityExtract.R
))
source(file = .path_fun, encoding = "UTF-8")
```

# Purpose

04A freezes one canonical text per contract, runs every entity extractor over the whole of it, and
folds the results into one DuckDB store. It then answers three questions and no others: **what came
back, where in the document it sits, and how far the engines agree with each other.**

Nothing is selected, filtered or ranked here.

## Why it only describes

The 03 family had 4,400 hand labels and could compute macro-F1. **There are no entity labels.**
Without them the only measurable quantity at this stage is yield, and yield does not order engines:
a higher count is either better recall or worse precision, and the two are indistinguishable until
something external exists to score against. So this document answers "what is there, and where do
the engines differ", and leaves "which engine is right" to 04B, which scores against facts EDGAR
recorded independently of any contract's text.

## The one decision that cannot be undone later

Offsets are integers into a specific string. Every candidate in the store and every rehydrated span
indexes *that* string. If two scripts disagree about what a document's text is, every offset in the
project is quietly wrong and nothing errors. 04A therefore writes `sample_text.parquet` and is the
only script permitted to define it; everything downstream reads that file and never reconstructs the
text.

## One store, and the grid inside it is ragged

There is one store and every engine reads the whole document. An earlier design carried a second
store holding the same engines over a truncated head, to price a truncation that was then not
adopted; both are gone.

The store is **engine by the labels that engine can emit**, not a full crossing. spaCy is the only
multi-label statistical engine and the only source of `PERSON`; LexNLP excludes persons and places
by policy; the four ported paper extractors each emit exactly one label. Empty cells in the tables
below mean *this engine does not do that*, not *this failed*. The shape is declared once in
`ner_label_policy()` and reproduced in the manifest, so it can be checked rather than assumed.

## The ledger is blind to labels, which is why the manifest records them

The ledger knows that engine E has seen document D. It does not know which labels were asked for.
Add a label to the policy and re-render, and every combination is already marked done: the store
reports itself complete while holding output built under the previous label set.

That is not hypothetical. `PERSON` was absent from the spaCy policy for the whole of the first pass
and nothing in this document could see it, because the manifest recorded only that a policy existed
rather than what it said. It now records the **resolved** set per engine, so a policy edit moves the
fingerprint, and a moved fingerprint clears the affected engines so they extract again.

Roughly half of Exhibit 10 material contracts are employment, indemnity or award documents whose
counterparty is an individual rather than a company, so a family that reads only organisations
reports the largest part of the sample as having one party. That is why the label is worth the
re-extraction.

## One table per label, and `candidates` is a view over them

Every engine used to be forced to the same eight columns, which is why LexNLP's parsed date, its
resolved ISO code, its company legal form and moneyregex's amount had nowhere to go and were
discarded at the seam for the whole life of the project. The extension axis is the **label** rather
than the engine -- an amount belongs to `MONEY` whoever found it -- so each label has its own table
with its own typed extras and the view unions their core columns. Every reader in this document
queries the view and none of them changed.

## What is not here

Engine and rule scoring against the EDGAR anchors is 04B. Field resolution is 04C. The corpus pass
is 04D. The reusable engine seam and the store itself live in `_Commons/_NER.R` and are shared with
04D; everything specific to *this* sample carries the `ent_` prefix.

# Configuration

```{r}
#| label: configure-paths
.lP <- list(
  Input = list(
    # 03A's output: labels, folds, and the text this document makes canonical.
    Prepared = "2_output/03A-ClassifyPrepare/prepared.parquet",
    # EDGAR document metadata: filer name, CIK, filing date, and the HashIndex the landing
    # page is keyed on.
    MetaData = "../pMatDisc/2_output/01-GetEDGAR/Output/FullMetaData.parquet",
    # EDGAR landing page: the registered addresses, which are keyed on the filing rather than
    # on the document and so are absent from the table above.
    LandingPage = "../pMatDisc/2_output/01-GetEDGAR/Output/LandingPage.parquet"
  ),
  Sample = list(
    Text    = utils_file_path(.dir_main, "sample_text.parquet"),      # THE offset basis
    Anchors = utils_file_path(.dir_main, "sample_anchors.parquet"),   # labels, folds, EDGAR facts
    Tuning  = utils_file_path(.dir_main, "Cache", "tuning.parquet")   # measured settings, cached
  ),
  Store = list(
    NerDB    = utils_file_path(.dir_main, "Store", "EntityCandidates.duckdb"),
    Manifest = utils_file_path(.dir_main, "Store", "manifest.parquet")
  ),
  Params = list(
    DocsPerRun   = 5000L,   # R-side slice size; bounds Python-side memory
    OffsetSample = 2000L,   # candidates rehydrated per engine in Validation
    TuneDocs     = 200L,           # documents per cell in the batch-size sweep
    TuneBatches  = c(8L, 32L, 128L),
    TuneRerun    = FALSE,          # TRUE re-measures; the cache is blind to extractor edits
    ReadDocs     = NULL,    # NULL = every document; an integer draws that many, for a quick render
    ReadOverwrite = FALSE,  # TRUE re-renders cached HTML; set after editing _Commons/_Reads.R
    ReadWorkers  = NULL,    # NULL = half the cores; the parent holds every document's text
    ContractSample = 5000L, # spans rehydrated for the offset tests in Validation
    Seed         = 42L      # fixed, so the same contracts are drawn on every render
  ),
  Output = list(
    Reads = utils_file_path(.dir_main, "Reads")   # one standalone HTML span viewer per contract
  )
)

# These two cannot live in .lP. Assigning NULL to a list element removes the element rather than
# storing it, so .lP$Params$MaxChars would silently vanish and the call site would read NULL from a
# name that was never set -- indistinguishable from a typo.
.max_chars_extract <- NULL   # NULL = no truncation. Changing this invalidates the store.
.labels_extract    <- NULL   # NULL = the per-engine policy in ner_label_policy()

fs::file_exists(c(.lP$Input$Prepared, .lP$Input$MetaData))
```

Failing here rather than three chunks later is deliberate: a missing upstream artifact should stop
the document where the path is declared.

# Sample

Two files come out of this section, and every later script in the family reads them rather than
reaching back to 03A. The first is the canonical text. The second is everything known about a
document from outside its own text -- its labels, its fold, and the EDGAR facts 04B turns into
recall floors.

```{r}
#| label: write-canonical-text
ent_write_text(
  .path_prepared = .lP$Input$Prepared,  # 03A's table; the Text column, renamed to TextRaw
  .path_out      = .lP$Sample$Text      # written on every render, deliberately
)
```

Rewritten rather than reused when present. Skipping the write would defeat the manifest exactly when
it is needed: the manifest fingerprints this file, so a changed `prepared.parquet` behind a reused
text file produces an unchanged fingerprint and reports a match while the store is stale.

```{r}
#| label: build-sample
tab_sample <- ent_build_sample(
  .path_prepared = .lP$Input$Prepared,     # labels, folds; Text deliberately not read here
  .path_meta     = .lP$Input$MetaData,     # filer name, CIK, filing date, HashIndex
  .path_landing  = .lP$Input$LandingPage,  # registered addresses, joined via HashIndex
  .cols_anchor   = c("CIK", "CompanyName", "DateFiled", "nCIK", "MultFiler"),
  .cols_landing  = c("BusinessAddress", "MailingAddress")
)

ent_write_anchors(
  .tab      = tab_sample,
  .path_out = .lP$Sample$Anchors
)

ent_report_sample(.tab = tab_sample)
```

An anchor column reported as missing costs 04B a recall floor and costs this document nothing, which
is why it is a warning rather than an abort.

# Extraction

## The engine set

```{r}
#| label: declare-engines
ner_tuning <- list(
  "paper:dateregex-v2"    = list(n_process = 24L, batch_size = NULL, timeout =   0L),
  "spacy:en_core_web_sm"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_md"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "spacy:en_core_web_lg"  = list(n_process = 24L, batch_size =  16L, timeout = 600L),
  "lexnlp"                = list(n_process = 24L, batch_size =   8L, timeout = 240L),
  "spacy:en_core_web_trf" = list(n_process =  1L, batch_size = 128L, timeout = 600L),
  "paper:gazetteer-v1"    = list(n_process = 24L, batch_size =   8L, timeout = 120L),
  "paper:redaction-v1"    = list(n_process = 24L, batch_size =  64L, timeout =   0L),
  "paper:moneyregex-v6"   = list(n_process = 24L, batch_size =  64L, timeout =   0L)
)

# THE TWO DECLARATIONS MUST AGREE, AND UNTIL NOW NOTHING CHECKED. The tuning list names the
# combinations to RUN; .ent_combos in the R file names the combinations to PLOT. Bumping a model
# version in one and not the other is what this assertion exists for: the extractor stamps its own
# constants into the parquet, ner_db_append() compares them against the dispatched token, and the
# mismatch surfaces AFTER the extraction has already run. Checking here costs nothing and fails
# before the first document is read.
stopifnot(setequal(names(ner_tuning), as.character(plot_levels(.key = "Combo"))))

lst_run_args <- ner_run_args(.tuning = ner_tuning)
```

The transformer runs at `n_process = 1` because a single Metal device cannot be shared across worker
processes; everything else takes twenty.

**Twenty rather than twenty-four, and the reason is the machine.** Measured throughput rises 1.60x
from eight workers to sixteen and only 1.15x from sixteen to twenty-four, which is the shape of a
28-core M3 Ultra: twenty performance cores and eight efficiency cores. Workers past the twentieth
land on efficiency cores running at roughly a third the speed, so they add scheduling pressure and
very little work. The Robustness section below measures the batch size, which is the knob that
actually moves.

**LexNLP's timeout is 240 seconds rather than 60, and that is the geoentity pass.** The timeout is
applied per extractor per document, so it now has to cover a dictionary scan of roughly 440 entities
and their aliases over the whole text. That averages about five seconds and scales with document
length, so a quarter-million-character credit agreement runs an order of magnitude longer than the
median contract. At 60 seconds the longest documents would be recorded as timeouts and their places
lost -- and lost systematically in the longest agreements, which is the worst possible place for a
missing-at-random assumption to fail.

```{r}
#| label: resolve-labels
tab_labels <- ent_labels_resolved(
  .run    = lst_run_args$.run,   # the nine declared combinations
  .labels = .labels_extract      # NULL, so the per-engine policy applies
)

tbl_say(.tab = tab_labels, .title = "Labels each engine is asked for")
```

This is the ragged grid, written out. It is also what the manifest fingerprints, so the table above
and the store's contents cannot disagree without the next chunk saying so.

## Reconciling the store

```{r}
#| label: reconcile-superseded
ent_report_superseded(
  .db_path = .lP$Store$NerDB,      # the one store
  .run     = lst_run_args$.run,    # what this run declares
  .clear   = TRUE                  # remove superseded versions; undeclared engines are kept
)
```

An extractor's model tag ends in a version, and bumping it is how a revised rule set is kept from
being confused with the one it replaced. `ner_run()` honours that -- a new version is a new
combination, so it is extracted rather than skipped -- but it cannot remove the old one, because the
ledger has no way to tell a retired version from one simply not asked for on this pass. A
combination the store holds and this run does not declare is reported and **left alone**: running a
subset temporarily is ordinary, and wiping the rest of the store for it would be the worse trap.

Adding a label to an engine no longer forces a re-extraction of the ones already stored. The ledger
is keyed on `(DocID, Engine, Model, Label)`, so a policy addition leaves the existing labels marked
done and only the addition comes back as missing. `ner_run()` then groups documents by what they
still need and dispatches one call per group -- on a fresh store that is one group asking for
everything, and after an addition one group asking for the addition.

That is the mechanism `PERSON` needed and did not have. It also removes the clear-and-re-extract
step this document used to carry, along with the manifest field it had to own.

```{r}
#| label: sync-manifest
ent_manifest_sync(
  .path_manifest = .lP$Store$Manifest,
  .manifest      = ent_manifest(
    .path_text = .lP$Sample$Text,      # fingerprints the inputs, not only the settings
    .run       = lst_run_args$.run,
    .labels    = .labels_extract,      # recorded for the reader; the ledger enforces it
    .max_chars = .max_chars_extract
  )
) |>
  tbl_say(.title = "Store settings against this run")
```

Two kinds of mismatch and they do not mean the same thing. A **fingerprint** row -- documents,
characters, truncation, labels -- means the store answers a different question than the one now
being asked, while reporting itself complete. An **inventory** row means the declared engine set
moved, which is the ordinary incremental case the ledger handles correctly.

## Running

```{r}
#| label: run-extraction
.t0_extract <- Sys.time()

tab_extract <- ner_run(
  .inputs       = .lP$Sample$Text,            # the canonical text, and nothing else
  .db_path      = .lP$Store$NerDB,
  .run          = lst_run_args$.run,          # nine combinations, cheapest first
  .labels       = .labels_extract,            # NULL = ner_label_policy() decides per engine
  .max_chars    = .max_chars_extract,         # NULL = the whole document, every engine
  .docs_per_run = .lP$Params$DocsPerRun,      # slice size; bounds Python-side memory
  .device       = "auto",                     # CNN models to CPU, transformer to Metal
  .n_process    = lst_run_args$.n_process,    # the three knobs ner_run_args() resolved per combo
  .batch_size   = lst_run_args$.batch_size,
  .timeout      = lst_run_args$.timeout
)

tab_extract |>
  dplyr::mutate(
    Combo = dplyr::if_else(.data$Engine == .data$Model, .data$Engine,
                           paste0(.data$Engine, ":", .data$Model)),
    .before = 1
  ) |>
  dplyr::select(Combo, Missing, Docs, Candidates) |>
  tbl_say(.title = "This run")

cli::cli_alert_info(
  "Extraction took {round(as.numeric(difftime(Sys.time(), .t0_extract, units = 'mins')), 1)} \
   minute{?s}."
)
```

The knobs are passed as the three resolved lists rather than as the tuning table, because
`ner_run()` takes them that way and resolves each per combination internally. `ner_run_args()`
exists to make that translation once.

Zeros in `Missing` are the expected steady state: on a second render every document is already in
the ledger and this section costs seconds. The failure to look for is a non-zero `Missing` with zero
`Docs`, which means an engine was asked for work and returned none.

The elapsed line is the only timing this document keeps. It is here for one downstream decision:
04D runs no spaCy engine at all, so putting `PERSON` on the corpus means adding one, and the cost of
the transformer against the CNN models on 4,398 documents is what makes that decision arithmetic
rather than guesswork.

# Description

```{r}
#| label: describe-store
.desc <- ent_describe(
  .db_path   = .lP$Store$NerDB,
  .path_text = .lP$Sample$Text   # supplies document lengths, so an offset becomes a position
)
```

```{r}
#| label: inspect-yield
ent_report_yield(.desc = .desc)
```

Read `DistinctPerDoc` rather than `PerDoc`. Total spans measure how often an engine repeats itself;
distinct spans measure how many things it found. A contract names a handful of parties and a handful
of places, so a distinct median in the hundreds is an engine collecting mentions -- signatories,
notice contacts, capitalised words -- rather than entities. The raw count cannot tell that apart
from good recall.

```{r}
#| label: inspect-position
ent_report_position(.desc = .desc)
```

Row percentages, so each engine and label is read against itself. Ten percent in every decile is a
label scattered through the document. Mass at both ends is one named in the preamble and again at
the signature block, which is what a party looks like and what an incidental mention does not.

```{r}
#| label: inspect-contrast
ent_contrast(
  .tab = .desc$position,           # the binned shares above
  .by  = c("Combo", "Label")       # pooled; the class cut follows below
) |>
  dplyr::arrange(plot_factor(.data$Label, .key = "Label"), dplyr::desc(.data$Contrast)) |>
  dplyr::mutate(dplyr::across(c(EndShare, MidShare), \(.x) tbl_pct(.x)),
                Contrast = round(.data$Contrast, 2)) |>
  tbl_say(.title = "Ends of the document over its middle")
```

Ten decile shares collapse to one comparable number: the mean share in the first and last deciles
over the mean share through the middle six. A uniform engine scores 1.0 by construction. The second
and ninth deciles are excluded from the middle because they are shoulder -- a preamble spills into
the second decile of a short document, a signature block into the ninth -- and counting them as
middle would blunt the contrast being measured.

This is the single number the engine choice turns on for a label with one job.

## By contract type

```{r}
#| label: describe-by-class
tab_class <- ent_describe_class(
  .db_path      = .lP$Store$NerDB,
  .path_text    = .lP$Sample$Text,
  .path_anchors = .lP$Sample$Anchors   # supplies the contract type
)
```

A pooled median hides an engine that behaves well on employment agreements and badly on credit
agreements, which are the two the party rules will lean on hardest. Only the two quantities carrying
the verdict are cut this way -- contrast, and distinct spans per document -- rather than the whole
yield table cut twelve ways.

```{r}
#| label: inspect-class-grid
tab_grid <- ent_class_grid(.tab = tab_class, .value = "Spans")
```

Twenty-eight rows because the grid is engine-by-label rather than engine: five engines emit `ORG`,
six emit `GPE`, one emits `REDACT`. Reading down a block of rows compares engines on one label;
reading across compares contract types for one engine.

Counts rather than a rate, deliberately. This is the first look, and a rate would hide that a class
with sixty documents and one with six hundred are not equally well observed -- `Docs` in the
stability table below carries that.

```{r}
#| label: inspect-stability
ent_report_stability(
  .tab      = tab_class,
  .min_docs = 30L    # classes thinner than this are excluded from the range, not from the grid
)
```

This is the table that says whether a pooled decision is safe. An engine whose contrast runs 4.1 to
4.9 across contract types can be crowned once; one running 1.2 to 8.0 cannot, and a large spread is
a reason to defer the choice rather than to pick the higher median -- it usually means the label is
doing two different jobs in two different kinds of contract.

## Positional contrast, one tab per label

The same quantity as the grid above, cut the other way: within a label, does the pooled positional
verdict hold in every contract type. Six tabs rather than six stacked tables, because these are read
one at a time and never against each other.

TABS ARE WRITTEN OUT RATHER THAN GENERATED. Quarto's tabset filter runs at parse time, so a `:::`
div emitted from an R chunk arrives too late to be turned into tabs -- it renders as an empty box.
The cost is that the six labels are hard-coded here and in `.ent_labels`; they are a closed set that
has not changed since the family was designed, and a seventh would be a larger decision than a tab.

::: {.panel-tabset}

## ORG

```{r}
#| label: class-org
ent_report_class(.tab = tab_class, .label = "ORG")
```

## PERSON

```{r}
#| label: class-person
ent_report_class(.tab = tab_class, .label = "PERSON")
```

## GPE

```{r}
#| label: class-gpe
ent_report_class(.tab = tab_class, .label = "GPE")
```

## DATE

```{r}
#| label: class-date
ent_report_class(.tab = tab_class, .label = "DATE")
```

## MONEY

```{r}
#| label: class-money
ent_report_class(.tab = tab_class, .label = "MONEY")
```

## REDACT

```{r}
#| label: class-redact
ent_report_class(.tab = tab_class, .label = "REDACT")
```

:::

## Reading the contracts

```{r}
#| label: write-reads
# tab_reads <- ent_reads(
#   .db_path      = .lP$Store$NerDB,
#   .path_text    = .lP$Sample$Text,
#   .path_anchors = .lP$Sample$Anchors,
#   .dir_out      = .lP$Output$Reads,
#   .doc_ids      = if (is.null(.lP$Params$ReadDocs)) NULL else {
#     withr::with_seed(.lP$Params$Seed,
#                      sample(arrow::read_parquet(.lP$Sample$Text)$DocID, .lP$Params$ReadDocs))
#   },
#   .overwrite    = .lP$Params$ReadOverwrite,
#   .workers      = .lP$Params$ReadWorkers
# )
```

Every table in this document is consistent with two different stories until the text is read. One
standalone HTML per contract: a tab per label, a tab per engine under it, every span marked in place
and every extra in the tooltip. No Quarto, no server -- a file that opens in a browser and can be
sent to a coauthor.

A distinct count of five against thirty-eight is a number. The two marked texts side by side show
*which* thirty-three the larger engine added, and whether those are parties the selective engine
missed or mentions it was right to leave out. No summary answers that.

CACHED, because this runs inside a render and the full sample is several gigabytes. A document whose
file already exists is skipped. The cache cannot know that `_Commons/_Reads.R` itself changed, which
is the one thing it will get wrong -- set `ReadOverwrite` after editing the renderer.

# Agreement

```{r}
#| label: align-engines
.al <- ent_alignment(.db_path = .lP$Store$NerDB)

ent_report_agreement(.al = .al, .n = 12L)
```

Within a document and a label, overlapping spans are merged into one mention and the contributing
engines recorded. Agreement is **any overlap** rather than exact match, which is the right notion
here: two engines that both found the organisation but disagreed about whether the comma belongs
have agreed about the organisation.

Read the pairwise table by family rather than by pair. Four of the nine combinations are spaCy, so a
mention found by four engines is usually one implementation agreeing with itself, and the family
consensus table is the one that says how much genuinely independent corroboration exists.

# The store, table by table

```{r}
#| label: inspect-store-tables
tab_tables <- ent_store_tables(.db_path = .lP$Store$NerDB)
tab_schema <- ent_store_schema(.db_path = .lP$Store$NerDB)

ent_report_store_tables(.tabs = tab_tables, .schema = tab_schema)
```

Everything above reads the data; this reads the **container**. Six tables, one per label, each with
the eight core columns and whatever extras that label admits -- and `candidates` is a view unioning
their cores, which is why no reader above this point changed when the store was split.

The split exists because the extension axis is the label rather than the engine. An amount belongs
to `MONEY` whoever found it, a legal form to `ORG`, a parsed date to `DATE`. Forced into one flat
table those columns had nowhere to live, and for the whole life of the project they were discarded
at the seam: LexNLP parsed every date it found and the parse was thrown away.

```{r}
#| label: inspect-store-peek
ent_store_peek(.db_path = .lP$Store$NerDB, .n = 2L)
```

Two rows per **engine**, not two per table. A plain head returns whichever engine sorts first, so
`org` would show LexNLP and never spaCy -- and the point of a per-label table, that several engines
write into it and only some of them resolve anything, would be invisible. Within an engine the
most-resolved rows come first, and repeated spans are dropped so the same string does not fill the
screen three times.

This is the whole argument for the rewrite in three screens: a `DATE` row carrying `2012-06-04` and
a confidence beside the string it was parsed from, a `MONEY` row carrying `23000000` and `NOK`
beside `NOK 23 million`, an `ORG` row carrying `CORP` beside a company name. None of it was
reachable before.

# Validation

```{r}
#| label: validate-offsets
tab_offsets <- ent_check_offsets(
  .db_path   = .lP$Store$NerDB,
  .path_text = .lP$Sample$Text,          # cut at the stored offsets, compared to the stored span
  .n         = .lP$Params$OffsetSample   # per engine, sampled deterministically by hash
)

ent_report_offsets(.tab = tab_offsets)
```

This is the only quantity in the entire family that is *verified* rather than corroborated, and it
has to be exactly 1.0. Below that, offsets index a string that is not the one on disk, and every
number in 04B onwards is wrong without anything erroring: the party location, every context window,
every rehydrated snippet.

```{r}
#| label: validate-contract
tab_contract <- ent_contract_tests(
  .db_path   = .lP$Store$NerDB,
  .path_text = .lP$Sample$Text,
  .n_offsets = .lP$Params$ContractSample
)

ent_report_contract(.tab = tab_contract, .db_path = .lP$Store$NerDB)
```

The same nine tests the `Check-NER-*` scripts run on twenty-five documents before an engine may be
inserted at all, run here over everything that *was* inserted. They are different questions: the
first asks whether an extractor is well formed, the second whether the store assembled from it still
is. A store built over several sessions from more than one extractor version can fail these while
every individual extraction passed.

```{r}
#| label: validate-extras
tab_extras <- ent_extras(.db_path = .lP$Store$NerDB)

ent_report_extras(.tab = tab_extras)
```

An extra filled for part of an engine's rows is the failure this block exists for. An extractor that
gained a field after some documents were already extracted leaves the rest null, the column is there
and typed, and nothing errors -- it reads as a coverage below a hundred and in no other way.

# Robustness

The knobs declared in Extraction are settings, not findings, and this is where they are checked.

```{r}
#| label: tune-batch-size
purrr::walk(
  .x = c("lexnlp", "paper:gazetteer-v1"),    # the two with real per-task cost
  .f = function(.c) {
    ent_report_tuning(
      .combo      = .c,
      .path_text  = .lP$Sample$Text,
      .path_cache = .lP$Sample$Tuning,       # a sweep costs three minutes; it is not re-run blind
      .rerun      = .lP$Params$TuneRerun,
      .batches    = .lP$Params$TuneBatches,  # the grid; changing it re-measures automatically
      .n          = .lP$Params$TuneDocs,     # documents per cell
      .n_process  = 20L                      # held fixed; this measures the batch knob
    )
  }
)
```

Batch size is the knob that moves, and it moves a great deal: LexNLP runs **4.6 times slower at a
batch of 128 than at 8**. The pool hands out one task per batch, so a 200-document subsample at 128
is two tasks for twenty workers and eighteen of them idle. Document length compounds it -- one
contract in this sample runs to 876,000 characters, and a large batch strands whichever worker draws
it while the rest finish early.

`Candidates` must be identical down each table. Batch size decides how work is handed to workers and
nothing else, so a differing count means a document was dropped or timed out rather than that a
setting was better.

**Worker count is deliberately not swept.** Throughput rises 1.60x from eight workers to sixteen and
only 1.15x from sixteen to twenty-four, which is the shape of a 28-core M3 Ultra running out of its
twenty performance cores. That is a fact about the machine rather than about the extraction, and
re-learning it on every render would cost minutes to confirm something the hardware fixes.

Each cell extracts into a scratch store that is deleted afterwards. Timing against the real store
would be circular: the ledger would report the documents already done and the second batch size
would be timed on no work at all.

**The sweep is cached**, because three minutes on every render to re-confirm a setting is three
minutes spent mostly in the cell already known to be worst. The key is the settings, so editing
`TuneBatches`, `TuneDocs` or the worker count re-measures on its own. It is blind to the extractors'
own code -- change a Python file and the stale timing survives, which is what `TuneRerun` is for.

# Deployment

```{r}
#| label: write-artifacts
tibble::tibble(
  Artifact = c("Canonical text", "Sample anchors", "Candidate store", "Run manifest"),
  Path     = c(.lP$Sample$Text, .lP$Sample$Anchors, .lP$Store$NerDB, .lP$Store$Manifest)
) |>
  dplyr::mutate(
    Exists = fs::file_exists(.data$Path),
    MB     = round(as.numeric(fs::file_size(.data$Path)) / 1024^2, 1),
    Path   = fs::path_file(.data$Path)
  ) |>
  tbl_say(.title = "Written by 04A")
```

Everything downstream reads these four and nothing else. No later script reaches back to
`prepared.parquet` or to the EDGAR exports.

# Overview

```{r}
#| label: fig-positions
#| fig-height: !expr ent_facet_height(length(plot_levels("Label")))
#| fig-cap: "Where candidates sit in the document, by entity type. Each panel is one label and each
#|   line one engine, as a density over relative position. Agreement on shape matters more than
#|   agreement on level: two engines that put a label in the same place are describing the same
#|   phenomenon at different sensitivities."
ent_plot_positions(
  .positions = .desc$position   # decile shares, per engine and label
)
```

The panel to read first is `ORG` against `PERSON`. A party type is named at the front and again at
the signature block; a mention type is spread evenly. Where an engine's organisations are flat
across the middle of the document it is collecting every company the contract refers to, not the
ones that signed it -- which is a fact about that engine and not about the contracts.

```{r}
#| label: fig-agreement
#| fig-height: !expr ent_facet_height(length(plot_levels("Label")), .square = TRUE)
#| fig-cap: "Pairwise agreement between engines, by entity type. Cells are the share of merged
#|   mentions both engines found. Blank cells are pairs with no shared label."
ent_plot_agreement(
  .pairwise = .al$pairwise   # one row per label and engine pair
)
```

Blocks of high agreement along the spaCy models are the expected shape and carry little information:
they share weights and a tokeniser. The cells worth reading are spaCy against LexNLP, and either
against the ported paper rules, because those are the only comparisons where two genuinely different
methods are being asked the same question.

```{r}
#| label: report-everything
ent_report_all(
  .tab_sample  = tab_sample,
  .ov          = ent_overview(
    .db_path = .lP$Store$NerDB   # no .inputs: positions come from ent_describe(), already binned
  ),
  .desc        = .desc,
  .class       = tab_class,
  .al          = .al,
  .tab_offsets = tab_offsets,
  .extras      = tab_extras,
  .contract    = tab_contract
)
```

# Next

**04B** scores what is in this store against the facts EDGAR recorded independently: the filer's own
name, its registered address, the filing date. That is the first point in the family where a
statement about an engine can be more than descriptive.

**PERSON is new here and unmeasured.** Nothing above says whether the person spans are parties or
signatories, and the two look identical in a yield table. The exhibit description names the
individual in a large share of employment filings -- `EMPLOYMENT AGREEMENT - CHARLES R BLAND` -- and
sits outside the body text in the same way the filer's name does, so it can serve as a recall floor
for individuals in exactly the classes where the counterparty is one. That belongs in 04B.

**The corpus pass in 04D currently runs no spaCy engine at all.** Person names are available on this
sample for free and on the corpus only at the cost of adding a spaCy model to that pass. Whether the
CNN models are adequate for `PERSON` is a separate question from their showing on organisations, and
this store now holds what is needed to answer it.



