---
title: "Contract Classification: The Keyword Table (03C)"
author: "Matthias Uckert"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(root.dir = here::here(), message = TRUE, warning = FALSE, comment = "")
options(cli.num_colors = 1, cli.width = 120)

.name_script <- if (isTRUE(getOption("knitr.in.progress"))) {
  knitr::current_input()
} else {
  rstudioapi::getActiveDocumentContext()[["path"]]
}
.name_script <- fs::path_ext_remove(basename(.name_script))

library <- function(...) suppressPackageStartupMessages(base::library(...))
```

```{r echo=FALSE}
source("1_code/_Commons/_Initialize.R", encoding = "UTF-8")
source("1_code/_Commons/_Utils.R", encoding = "UTF-8")

# 03A owns sample preparation and the shared scoring, leaderboard and reporting layer. Sourcing it
# here is what makes the keyword and transformer arms comparable: both are scored by the same code
# on the same folds rather than by two similar implementations that disagree at the third decimal.
source(init_create_script_fun(here::here(), "03A-ClassifyPrepare"), encoding = "UTF-8")

cat("Main Directory: ")
(.dir_main <- init_create_script_dir(.dir_here = here::here(), .name_script = .name_script))

cat("Function File: ")
(.path_fun <- init_create_script_fun(.dir_here = here::here(), .name_script = .name_script))
source(.path_fun)
```

# Purpose

The transformer classifier trained in 03B is the deployed model. This stage produces something it
cannot: a short, ranked, human-readable table of terms per contract type, applicable to EDGAR with a
text editor and no GPU, carrying a stated precision and a stated coverage.

That is an artifact rather than a model, and it needs a different objective. A keyword classifier
tuned for accuracy maximises an aggregate score and will accept any term that helps it, including
terms no reader could act on. A keyword table tuned for publication accepts only terms that mean what
they appear to mean, and reports honestly how much of the corpus it therefore declines to label.

## How a term earns its place

**Power** is the Wilson 95 percent lower bound on a term's training precision. It is bounded in
`[0, 1]` and monotone in both precision and evidence:

| Occurrences | Raw precision | Power |
|:--|--:|--:|
| 2 of 2 | 1.000 | 0.342 |
| 10 of 10 | 1.000 | 0.722 |
| 45 of 50 | 0.900 | 0.786 |
| 190 of 200 | 0.950 | 0.910 |

Raw precision cannot distinguish a coincidence from a pattern; it ranks two-of-two above
one-hundred-and-ninety-of-two-hundred. Power ranks them the other way and reads directly as "a hit
means this category at least this often, with 95 percent confidence". It is the sort key of the
published table and the evidence gate at scoring time.

Power is deliberately **not** the precision gate. Setting precision to one in the Wilson formula
leaves `Power_max(n) = n / (n + 3.84)`, so Power carries a support-dependent ceiling: a perfect term
needs 44 occurrences to reach 0.92 at all. The thinnest category in this sample holds 71 documents, so
no term within it can clear a high global Power threshold however clean it is. A single threshold on
Power therefore selects for category size rather than term quality and empties every small category by
arithmetic. Precision has no ceiling, so precision is the promise and Power is the evidence.

Three further rules follow from the artifact goal. A **directional guard** admits a term only where
its precision exceeds the category's base rate. **Greedy marginal reach** accepts a term only where it
catches documents no accepted term caught, which removes nested n-grams, near-synonyms and boilerplate
variants under one rule that works on document overlap rather than surface form. The **maximum-Power
decision** scores a document by the single best term that fired rather than by a weighted sum, so
every label traces to one printable term; a sum is not inspectable, and the two rules agree at the
operating point anyway, because most documents fire either no term or one.

## Two independent arms

Mining can only surface terms frequent enough to clear a document-frequency floor and distinctive
enough to win a greedy slot. Reading contracts is not subject to either constraint, and can propose
terminology that is rare, that lost to a longer n-gram containing it, or that a lawyer would name and
a frequency table would never isolate. This document evaluates both arms and their union on identical
folds under identical rules, so the only thing differing between them is where the terms came from.

## Where the work happens

The mining engine emits statistics; every decision is taken in R. Mining is expensive and selection is
cheap, so binding the floors into the engine would force a re-mine for every floor combination.
Splitting them keeps the mining grid at a few hundred cells and leaves the selection sweep
interactive. It also makes the engine task-agnostic: the amendment decision rule is a decision, so it
lives here.

# Configuration

```{r}
.dir_prep <- init_create_script_dir(.dir_here = here::here(), .name_script = "03A-ClassifyPrepare")

# The generated term lists are produced outside the repository, by 03C-CoWorkKeywords.R and
# 03C-CoWorkCompile.R, and are read from the shared project folder rather than rebuilt here.
.dir_cowork <- fs::path(
  "/Users/matthiasuckert/Dropbox/MyPapers/MaterialContracts/MatContractData",
  "KeyWordsClaude"
)

.lP <- list(
  Input = list(
    Prepared      = utils_file_path(.dir_prep, "prepared.parquet"),
    TermsDetailed = fs::path(.dir_cowork, "detailed", "cowork_terms_detailed.parquet"),
    TermsBroad    = fs::path(.dir_cowork, "broad", "cowork_terms_broad.parquet"),
    TermsAmend    = fs::path(.dir_cowork, "amendment", "cowork_terms_amendment.parquet")
  ),
  Output = list(
    Mines = utils_file_path(.dir_main, "mines"),
    Runs  = utils_file_path(.dir_main, "runs"),
    Table = utils_file_path(.dir_main, "table"),
    Union = utils_file_path(.dir_main, "table", "union_terms_detailed.parquet")
  ),
  Engine = list(
    Python = here::here("contracts-engine", ".venv", "bin", "python"),
    Script = here::here("contracts-engine", "keyword_train.py")
  ),
  Param = list(
    TargetPrecision = 0.95, # the promise the categorical tables make
    TargetAmend     = 0.85, # amendment promises less; see the Robustness section for why
    Tolerance       = 0.01, # precision band treated as indistinguishable; roughly two SEs here
    MinClasses      = 9L, # categories the table must label before a threshold is acceptable
    MinFolds        = 3L, # fold agreement required of a published term
    HoldoutFold     = 5L, # the fold the generated arm never read
    Seed            = 42L # fixed upstream in 03A and reused unchanged
  )
)
```

A mine is named after its hyperparameters and carries no fingerprint of the data it consumed. Change
the sample without emptying `mines/`, and every cell will be reported as already complete while
serving results computed from folds that no longer exist. Superseded mines should be renamed rather
than deleted, since discovery globs a known directory and a renamed sibling is invisible to the code
while remaining available as a record.

# The sample

```{r}
if (!fs::file_exists(.lP$Input$Prepared)) cli::cli_abort("Run 03A before this document")
tab_prep <- arrow::read_parquet(.lP$Input$Prepared)
```

The filer title is mined as a separate arm, so the share of documents carrying one bounds what that
arm can reach. The prediction, before looking: title coverage is high and roughly even across
categories, because a missing title reflects a filing-format accident rather than anything about the
contract.

```{r}
tab_prep |>
  dplyr::summarise(
    N = dplyr::n(),
    nHasDesc = sum(!is.na(DocDesc) & trimws(DocDesc) != ""),
    ShareHas = mean(!is.na(DocDesc) & trimws(DocDesc) != ""),
    .by = ClassDetailed
  ) |>
  dplyr::arrange(ShareHas) |>
  dplyr::mutate(ShareHas = clf_pct(ShareHas)) |>
  clf_say_table(.title = "Documents carrying a filer title")
```

The title also appears verbatim in the opening characters of the body in almost every document. As a
feature source that makes the title arm redundant, since any model reading the body already reads it.
As a mining ground for a published table it is the better field, because it is short: a term mined
from a filer's own title is close to a contract-type name by construction, where a term mined from the
body is a fragment of operative language. The consequence to expect is a measurable convergence
between the two arms at narrow truncation windows, widening as the window grows.

# Mining the candidate terms

The engine is checked end to end on a tiny subsample before the grid is committed, so a broken seam
surfaces in seconds rather than after the sweep.

```{r}
kw_mine(
  .path_data  = .lP$Input$Prepared, # sample written by 03A
  .label_col  = "ClassDetailed", # any task will do for a seam check
  .source     = "docdesc", # the cheapest field to mine
  .test_fold  = 1L, # an arbitrary held-out fold
  .mines_root = .lP$Output$Mines, # smoke mines land in a _smoke subfolder
  .python     = .lP$Engine$Python,
  .script     = .lP$Engine$Script,
  .smoke      = TRUE # tiny subsample; checks the seam, not the result
)
```

The grid crosses three tasks, two source fields, five truncation windows, two n-gram lengths and two
stopword regimes, over five folds plus an all-data mine.

Two of those axes deserve a stated expectation. **The truncation window** runs well past the 512
tokens the transformer reads: 256 and 512 words are the like-for-like comparison, and 1024, 2048 and
the whole document are windows no transformer in this study can see. If performance keeps rising past
512 words there is signal deeper in these contracts than the deployed model reads, which would matter
beyond this stage. If it flattens, that independently corroborates the assumption the pipeline already
rests on, from a method that had every opportunity to find something further in and did not.

**The stopword regime** is swept rather than fixed because its answer depends on the objective. Under
an accuracy objective, function-word collocations are discriminative and removing them costs
performance. Under a readability objective they are unusable, whatever they score. The two regimes are
therefore judged on the terms they produce, not on the accuracy column.

```{r}
grid_mine <- kw_mine_grid(
  .label_cols   = c("ClassDetailed", "ClassBroad", "AmendType"), # every task, mined directly
  .nwords_text  = c(256L, 512L, 1024L, 2048L, 0L), # 0 keeps the whole document
  .ngram_max    = c(2L, 3L), # longest n-gram mined
  .stopwords    = c("none", "english_domain"), # judged on readability, not accuracy
  .folds        = 1:5, # folds dealt once, in 03A
  .with_alldata = TRUE # fold 0 produces the published table
)

grid_mine |>
  dplyr::count(Source, Stopwords, NWords, name = "Cells") |>
  dplyr::mutate(Window = dplyr::if_else(NWords == 0L, "full", as.character(NWords))) |>
  dplyr::select(Source, Stopwords, Window, Cells) |>
  clf_say_table(.title = paste0("Mining grid: ", nrow(grid_mine), " cells"))
```

Categories are mined directly at both levels rather than rolling one up into the other. Mining is
one-against-the-rest at whatever level it runs, so a term shared evenly by three detailed categories
belonging to one broad parent scores about one third precision against each of them and is discarded,
despite marking the parent cleanly. Those terms are reachable only by working at the broad level.

The sweep is idempotent: the engine skips any cell already on disk, so this chunk runs on every render
and costs seconds after the first.

```{r}
kw_mine_sweep(
  .grid       = grid_mine, # what to mine
  .path_data  = .lP$Input$Prepared, # sample written by 03A
  .mines_root = .lP$Output$Mines, # destination; existing cells are skipped
  .python     = .lP$Engine$Python,
  .script     = .lP$Engine$Script,
  .workers    = 24L, # measured: the full grid completes in minutes
  .overwrite  = FALSE # FALSE skips work already present on disk
)

idx_mine <- kw_mine_index(.mines_root = .lP$Output$Mines)
```

```{r}
idx_mine |>
  dplyr::filter(Fold > 0L, Mode == "mine") |>
  dplyr::summarise(
    nCells = dplyr::n(),
    mVocab = round(mean(nVocab)),
    mCand = round(mean(nCand)),
    mSeconds = round(mean(MineSec), 1),
    .by = c(LabelCol, Source, NWords)
  ) |>
  dplyr::mutate(Window = dplyr::if_else(NWords == 0L, "full", as.character(NWords))) |>
  dplyr::select(LabelCol, Source, Window, nCells, mVocab, mCand, mSeconds) |>
  clf_say_table(.title = "What was mined")
```

# Choosing the configuration

The mining axes are resolved first, under one fixed selection. Crossing mining and selection at once
searches a far wider space than the transformer sweep did on the same 4,400 documents, and the winner
of a wide search on a small sample is partly a winner by luck.

```{r}
perf_mines <- kw_sweep_mines(
  .mine_index      = idx_mine, # every fold mine
  .min_precision   = 0.95, # the promise; held fixed while mining axes vary
  .min_hits        = 5L, # minimum positive-class training hits
  .min_tot         = 5L, # minimum total training hits
  .min_reach       = 0.01, # greedy acceptance bar, as a share of the category
  .max_terms       = 25L, # per-category cap
  .min_filers      = 5L, # minimum distinct registrants
  .min_filer_ratio = 0.5, # registrants per hit; catches one firm's own template
  .drop_repeats    = TRUE, # discard n-grams with a repeated token
  .tau             = 0.70, # evidence floor
  .runs_root       = NULL # NULL evaluates without writing run folders
)
```

```{r}
kw_report_mines(.tab = perf_mines, .label_col = "ClassDetailed")
```

```{r}
kw_report_mines(.tab = perf_mines, .label_col = "ClassBroad")
```

```{r}
kw_report_mines(.tab = perf_mines, .label_col = "AmendType")
```

The configuration carried forward is chosen by precision with ties broken on coverage. A precision
difference inside one percentage point is indistinguishable from the fold-to-fold spread, so taking
the maximum among such rows buys nothing measurable while discarding real coverage and, where the
winner is a wide truncation window, twenty times the mining time.

The stopword regime is stated rather than inferred. Its criterion is the readability of the terms
produced, and no column reports that, so a tiebreak on coverage would decide the axis on precisely
the ground this document rejects. Removing stopwords costs a little coverage and returns content-word
phrases in place of fragments carrying function words, so `english_domain` is preferred wherever the
two regimes are indistinguishable on the promise.

The coverage floor is advisory rather than binding, and the distinction matters because two documents
consume this choice. A table labelling less than a quarter of the corpus is not a usable artifact, so
the floor is the right bar for what this stage publishes. It is the wrong bar for what 03D consumes:
a source that commits rarely and is nearly always right is exactly what a cascade wants, since the
transformer backfills everything it declines. Enforcing one threshold for both purposes deleted the
second silently -- a source clearing nothing at the publication bar returned no rows, and mine
selection, run writing and the router's arm inventory all inherited the absence without an error
anywhere. Where nothing clears the floor the best configuration is now returned regardless, flagged
and announced. The published table filters on that flag; the router does not.

```{r}
cfg_mine <- purrr::map(
  .x = c("ClassDetailed", "ClassBroad", "AmendType"),
  .f = function(.task) {
    purrr::map(c("text", "docdesc"), function(.src) {
      kw_summarise_mines(.tab = perf_mines, .label_col = .task) |>
        dplyr::filter(Source == .src) |>
        kw_choose_config(
          .tolerance    = 0.01, # precision band treated as a tie
          .min_coverage = 0.25, # below this a configuration is not publishable
          .prefer       = list(Stopwords = "english_domain"), # readability, judged outside the table
          .fallback     = TRUE # keep the best configuration even where none clears the floor
        ) |>
        dplyr::mutate(LabelCol = .task, .before = 1L)
    }) |>
      purrr::list_rbind()
  }
) |>
  purrr::list_rbind()

cfg_mine |>
  dplyr::mutate(
    Window    = dplyr::if_else(NWords == 0L, "full", as.character(NWords)),
    Coverage  = clf_pct(mCoverage),
    Precision = clf_pct(mPrecision),
    MacroF1   = sprintf("%.3f", mMacroF1)
  ) |>
  dplyr::select(LabelCol, Source, Stopwords, Window, NgramMax,
    Classes = mClasses, Coverage,
    Precision, MacroF1, Publishable
  ) |>
  clf_say_table(.title = "Mining configuration carried forward")
```

A row marked not publishable is still evaluated, still written as a run, and still available to 03D.
It is excluded only from the table this stage ships.

The selection floors are then swept over the winning mining configurations only.

```{r}
grid_sel <- kw_select_grid(
  .min_precision = 0.95, # the promise, fixed
  .min_hits      = 5L, # evidence floor, fixed: Power already encodes it
  .min_tot       = 5L, # evidence floor, fixed
  .min_reach     = c(0.005, 0.01, 0.02, 0.05), # the greedy bar; the axis that shortens the list
  .max_terms     = c(15L, 25L, 40L) # per-category cap
)

idx_sel <- idx_mine |>
  dplyr::semi_join(cfg_mine, by = dplyr::join_by(LabelCol, Source, NWords, NgramMax, Stopwords)) |>
  dplyr::filter(Fold > 0L)

perf_sel <- kw_sweep_selection(
  .mine_index = idx_sel, # winning mining configurations only
  .grid_sel   = grid_sel, # floors to cross
  .tau        = 0.70, # evidence floor, held fixed while floors vary
  .runs_root  = NULL # NULL evaluates without writing run folders
)
```

```{r}
kw_report_selection(.tab = perf_sel, .label_col = "ClassDetailed", .n = 12L)
```

```{r}
sel_best <- kw_summarise_selection(.tab = perf_sel, .label_col = "ClassDetailed") |>
  kw_choose_config(
    .tolerance    = 0.01, # precision band treated as a tie
    .min_coverage = 0.25, # below this a configuration is not publishable
    .prefer       = NULL, # no axis here is chosen on grounds the table does not report
    .fallback     = TRUE  # these floors are swept over an already-publishable mine
  )

sel_best |>
  dplyr::mutate(Coverage = clf_pct(mCoverage), Precision = clf_pct(mPrecision)) |>
  dplyr::select(MinReach, MaxTerms, Terms = mTerms, Classes = mClasses, Coverage, Precision) |>
  clf_say_table(.title = "Selection floors carried forward")
```

# Results

The threshold filters a fixed lexicon at scoring time, so a whole curve costs one join per fold. This
curve is the instrument the stage produces: a reader consults it to choose an operating point, and the
paper reports it as a sensitivity surface rather than a single tuned number.

```{r}
dirs_detailed <- idx_sel |>
  dplyr::filter(LabelCol == "ClassDetailed", Source == "text") |>
  dplyr::pull(MineDir)

curve_detailed <- kw_tau_curve(
  .mine_dirs     = dirs_detailed, # fold mines of the chosen configuration
  .taus          = seq(0.40, 0.96, by = 0.02), # evidence floors to trace
  .min_precision = 0.95, # the promise, fixed across the curve
  .min_hits      = sel_best$MinHits,
  .min_tot       = sel_best$MinTot,
  .min_reach     = sel_best$MinReach,
  .max_terms     = sel_best$MaxTerms
)
```

Two constraints govern the choice, not one. Realised precision must reach the target, and the
resulting table must still label a required number of categories. The second constraint exists because
of the Power ceiling argued in the Purpose: without it the rule returns a very precise table that has
quietly dropped every small category, not because their terms were poor but because those categories
are too small for any term to clear a high threshold.

The target carries a tolerance for the same reason the configuration choice does. Around two thousand
documents are classified here, so the standard error of a proportion near the target is close to half
a percentage point. Comparing hard against the target would treat differences the sample cannot
measure as decisive, and because raising the threshold removes small categories first, the cost of
that false precision is paid in breadth. Among thresholds reaching the target within tolerance, the
one labelling most categories is preferred.

```{r}
op_detailed <- kw_report_tau(
  .curve            = curve_detailed,
  .target_precision = .lP$Param$TargetPrecision, # the promise
  .tolerance        = .lP$Param$Tolerance, # differences this small are not measurable here
  .min_classes      = .lP$Param$MinClasses, # categories the table must label
  .every            = 2L # the curve is dense; print every other row
)
```

The runs at the chosen operating point are written to disk, in the schema the transformer trainer
uses, so a single leaderboard ranks both arms of the study.

```{r}
perf_final <- kw_sweep_selection(
  .mine_index = idx_sel,
  .grid_sel = sel_best |>
    dplyr::select(MinPrecision, MinHits, MinTot, MinReach, MaxTerms) |>
    dplyr::mutate(SelName = "final"),
  .tau = op_detailed$Tau, # the chosen operating point
  .runs_root = .lP$Output$Runs # these are the runs the paper cites
)

pred_final <- perf_final |>
  dplyr::filter(LabelCol == "ClassDetailed", Source == "text") |>
  dplyr::pull(Pred) |>
  purrr::list_rbind()
```

```{r}
clf_report_scores(pred_final, .title = "Keyword table at the operating point")
```

```{r}
clf_report_perclass(pred_final, .title = "Per category")
```

Per-category recall is the cost the table pays for its promise. A category with high precision and low
recall is one the table labels rarely and reliably, which is the intended behaviour; a category with
no rows at all is one the table declines entirely, and that is a finding about the category rather
than a gap to be closed by lowering the bar.

```{r}
clf_confusion(pred_final) |> clf_say_table(.title = "Confusion, rows are true labels")
```

Every committed label traces to one term, so the reason for it can be printed rather than asserted.

```{r}
kw_report_audit(.tab_pred = pred_final, .per_class = 2L, .wrong = FALSE)
```

```{r}
kw_report_audit(.tab_pred = pred_final, .per_class = 2L, .wrong = TRUE)
```

# The generated arm

`03C-CoWorkKeywords.R` wrote contrastive document bundles, pairing documents of a category with
documents drawn from the rest so that a term appearing in both can be recognised as worthless. A
reading session proposed terms from those bundles, and `03C-CoWorkCompile.R` folded the responses into
one term list per task.

The bundles were drawn from folds one to four, so the session read those documents together with their
labels. Only the held-out fold is absent from every bundle, and it is therefore the only honest
estimate for this arm. Power is still computed on the folds the session read, which makes the Power
values optimistic for both arms alike; the precision and coverage reported below are not.

```{r}
purrr::walk(
  .x = c(.lP$Input$TermsDetailed, .lP$Input$TermsBroad, .lP$Input$TermsAmend),
  .f = function(.p) {
    if (!fs::file_exists(.p)) cli::cli_abort("Missing term list {(.p)}; run 03C-CoWorkCompile.R")
  }
)

cfg_detailed <- cfg_mine |> dplyr::filter(LabelCol == "ClassDetailed", Source == "text")

perf_generated <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Input$TermsDetailed, # written by 03C-CoWorkCompile.R
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords, # same window as the mined arm
  .stopwords     = cfg_detailed$Stopwords, # same regime; a mismatch makes mined terms unmatchable
  .folds         = .lP$Param$HoldoutFold, # the only fold the session never read
  .tau           = op_detailed$Tau, # same evidence floor as the mined arm
  .min_precision = 0.95, # same promise; both arms clear the same gate
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

The session was instructed to propose generously, on the reasoning that a term which fails is discarded
at no cost while a term never proposed cannot be recovered. Survival is therefore expected to be low,
and a low rate is not itself a problem; what matters is whether the survivors reach categories the
mined arm could not.

```{r}
terms_generated <- arrow::read_parquet(.lP$Input$TermsDetailed)

kw_survival(.proposed = terms_generated, .lexicon = perf_generated$Lexicon[[1]]) |>
  dplyr::mutate(ShareSurvive = clf_pct(ShareSurvive)) |>
  clf_say_table(.title = "Proposed terms surviving the precision and evidence gates")
```

# Validation

The union combines the two arms. Its mined half is taken from the fold mine trained on exactly the
folds the session read, not from the all-data mine, so that neither half has seen the evaluation fold.

Both halves are scored under the mined arm's stopword regime. Where a regime is in force the miner
forms n-grams after removal, so a mined term names two words that need not be adjacent in the raw
text; scoring it without the regime returns zero hits for every such term, and a union assembled that
way silently reduces to the list whose terms happened to survive. Supplied terms are folded to the
same tokenised form on the way in, so a phrase written in full English and a phrase mined after
removal describe the same pattern.

```{r}
lex_mined_holdout <- kw_select(
  .mine = kw_load_mine(
    .mine_dir = idx_sel |>
      dplyr::filter(
        LabelCol == "ClassDetailed", Source == "text",
        Fold == .lP$Param$HoldoutFold
      ) |>
      dplyr::pull(MineDir)
  ),
  .min_precision = 0.95,
  .min_hits = sel_best$MinHits,
  .min_tot = sel_best$MinTot,
  .min_reach = sel_best$MinReach,
  .max_terms = sel_best$MaxTerms
) |>
  dplyr::filter(Power >= op_detailed$Tau)

kw_terms_union(
  .lexicon    = lex_mined_holdout, # mined on folds 1-4 only
  .terms_file = .lP$Input$TermsDetailed, # generated from folds 1-4 only
  .path_out   = .lP$Output$Union
)

perf_union <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Output$Union,
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords,
  .stopwords     = cfg_detailed$Stopwords,
  .folds         = .lP$Param$HoldoutFold,
  .tau           = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

```{r}
kw_report_arms(
  .tabs = list(
    mined = perf_final |>
      dplyr::filter(
        LabelCol == "ClassDetailed", Source == "text",
        TestFold == .lP$Param$HoldoutFold
      ),
    generated = perf_generated,
    union = perf_union
  )
)
```

The number to read first is the count of categories labelled. A union matching both arms on precision
while labelling more categories establishes that mining and reading recover different vocabulary and
that neither substitutes for the other. A union matching the mined arm on every column establishes the
opposite, that the generated terms add nothing the statistics had not already found, which is a
weaker but equally reportable result.

A union can also label **fewer** categories than one of its parts, and that is a property of the
decision rule rather than a fault in the assembly. A document is assigned to the category whose
best-firing term carries the highest Power, so a thin category reachable only through a low-Power term
loses its documents as soon as a higher-Power term from another category is added. Adding terms raises
coverage monotonically; it does not raise the number of categories monotonically. Where the union
trails a parent on category count, that parent is labelling those documents only because the competing
evidence was absent from its list.

# Robustness

The remaining tasks are scored the same way, from the same folds, with the same gates.

```{r}
perf_generated_broad <- kw_terms_evaluate(
  .path_data = .lP$Input$Prepared,
  .terms_file = .lP$Input$TermsBroad,
  .label_col = "ClassBroad",
  .source = "text",
  .nwords = cfg_mine |> dplyr::filter(LabelCol == "ClassBroad", Source == "text") |>
    dplyr::pull(NWords),
  .stopwords = cfg_mine |> dplyr::filter(LabelCol == "ClassBroad", Source == "text") |>
    dplyr::pull(Stopwords),
  .folds = .lP$Param$HoldoutFold,
  .tau = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root = .lP$Output$Mines,
  .runs_root = .lP$Output$Runs,
  .python = .lP$Engine$Python,
  .script = .lP$Engine$Script
)

perf_generated_amend <- kw_terms_evaluate(
  .path_data = .lP$Input$Prepared,
  .terms_file = .lP$Input$TermsAmend,
  .label_col = "AmendType",
  .source = "text",
  .nwords = cfg_mine |> dplyr::filter(LabelCol == "AmendType", Source == "text") |>
    dplyr::pull(NWords),
  .stopwords = cfg_mine |> dplyr::filter(LabelCol == "AmendType", Source == "text") |>
    dplyr::pull(Stopwords),
  .folds = .lP$Param$HoldoutFold,
  .tau = op_detailed$Tau,
  .min_precision = .lP$Param$TargetAmend, # amendment promises less; see below
  .mines_root = .lP$Output$Mines,
  .runs_root = .lP$Output$Runs,
  .python = .lP$Engine$Python,
  .script = .lP$Engine$Script
)
```

Amendment is held to a lower promise than the categorical tasks, and the reason is structural rather
than a concession. The categorical tables abstain, so their precision is a promise about the subset
they choose to label and can be set as high as the terms allow. Amendment does not abstain: it assigns
one of two labels to every document, so its precision is a property of the whole corpus and is bounded
by how separable the two classes are. Demanding the categorical target of it leaves a handful of terms
and a worse classifier, which is not a stricter table but a broken one.

The stopword regime is not neutral between the two arms, and the union forces them to share one. The
miner forms n-grams after removal, so under a regime its terms name words that need not be adjacent,
and the regime is what makes them fire at all. A written list is folded through the same tokeniser on
the way in, which is what makes it comparable, but folding also collapses phrases the session wrote as
distinct: an article-led phrase and its bare form become the same entry, and the surviving unigram is
less precise than either. Scoring the generated list under both regimes measures that cost directly.

```{r}
perf_generated_none <- kw_terms_evaluate(
  .path_data     = .lP$Input$Prepared,
  .terms_file    = .lP$Input$TermsDetailed,
  .label_col     = "ClassDetailed",
  .source        = "text",
  .nwords        = cfg_detailed$NWords, # window held at the mined arm's choice
  .stopwords     = "none", # the only axis varied
  .folds         = .lP$Param$HoldoutFold,
  .tau           = op_detailed$Tau,
  .min_precision = 0.95,
  .mines_root    = .lP$Output$Mines,
  .runs_root     = .lP$Output$Runs,
  .python        = .lP$Engine$Python,
  .script        = .lP$Engine$Script
)
```

```{r}
kw_report_arms(
  .tabs = list(
    `generated, shared regime` = perf_generated,
    `generated, own regime`    = perf_generated_none
  )
)
```

A written list scoring better under its own regime than under the shared one bounds what the union
costs: the comparison in the previous section understates the generated arm by that difference, and
the difference is the price of expressing both arms in one vocabulary. Amendment, which runs without
removal, shows the same arm unfolded and is the cleanest read on what reading contributes.

```{r}
kw_report_arms(
  .tabs = list(
    `broad, mined` = perf_final |>
      dplyr::filter(LabelCol == "ClassBroad", TestFold == .lP$Param$HoldoutFold),
    `broad, generated` = perf_generated_broad,
    `amendment, mined` = perf_final |>
      dplyr::filter(LabelCol == "AmendType", TestFold == .lP$Param$HoldoutFold),
    `amendment, generated` = perf_generated_amend
  )
)
```

Amendment is the sharpest test of the two arms, because the phrase that most obviously marks an
amendment is a title convention appearing on many genuine originals. A statistical miner cannot know
that; it can only observe that the phrase is imprecise and discard it. A reader can recognise the
convention and look instead for the structural markers of modification, which is what the session was
asked to do.

# Deployment

The folds pay for the estimate; the all-data mine produces the artifact. A published term must also
have been chosen independently by at least the required number of fold mines, a filter applied here
and nowhere else: mine `k` trains on every fold but `k`, so filtering a fold lexicon on agreement
across all mines would let the held-out fold influence selection. An all-data mine holds nothing out,
so the filter is legitimate against it. The reported precision and coverage therefore describe the
unfiltered procedure, while the published table carries one further filter that can only remove terms.

```{r}
tab_keywords <- kw_lexicon_final(
  .mine_dir_all = idx_mine |>
    dplyr::semi_join(cfg_detailed, by = dplyr::join_by(LabelCol, Source, NWords, NgramMax, Stopwords)) |>
    dplyr::filter(Fold == 0L) |>
    dplyr::pull(MineDir),
  .mine_dirs_folds = dirs_detailed,
  .tau = op_detailed$Tau, # the chosen operating point
  .min_folds = .lP$Param$MinFolds, # fold agreement required of a published term
  .min_precision = 0.95,
  .min_hits = sel_best$MinHits,
  .min_tot = sel_best$MinTot,
  .min_reach = sel_best$MinReach,
  .max_terms = sel_best$MaxTerms
)
```

```{r}
kw_report_lexicon(.tab = tab_keywords, .top = 8L)
```

```{r}
kw_save_lexicon(
  .tab  = tab_keywords,
  .dir  = .lP$Output$Table,
  .stem = "keyword_table_detailed"
)
```

# Overview

```{r}
kw_report_all(
  .perf_mines       = perf_mines,
  .perf_sel         = perf_sel,
  .curve            = curve_detailed,
  .tab_pred         = pred_final,
  .tab_lexicon      = tab_keywords,
  .label_col        = "ClassDetailed",
  .target_precision = .lP$Param$TargetPrecision,
  .min_classes      = .lP$Param$MinClasses
)
```

```{r}
#| fig-cap: "Performance against the truncation window. The reference line marks the transformer's
#|   reading window; anything right of it is signal no model in this study sees."
kw_plot_window(.tab = perf_mines, .label_col = "ClassDetailed", .window_ref = 512L)
```

```{r}
#| fig-cap: "Precision bought by declining to label. Point size is the number of categories the table still reaches."
kw_plot_tau(.curve = curve_detailed, .target_precision = .lP$Param$TargetPrecision)
```

```{r}
#| fig-cap: "Share of each category reached by successive terms. A curve flattening early marks
#|   the point at which a list stops earning its length."
kw_plot_reach(.tab = tab_keywords)
```

# Next

03D compares the keyword and transformer arms on the shared leaderboard, using the run folders written
here. 03E applies the deployed transformer to the full corpus; the keyword table is an independent
artifact that does not enter that path and ships alongside the archived dataset.
